### 2013-04-09 papers/Paper1/proplyd-bowshocks.tex
Very early draft of first paper
* papers/Paper1/proplyd-bowshocks.tex

\documentclass[useAMS,usenatbib]{mn2e}

% The following is needed to fix the margins if using Letter-size paper
% REMOVE if your LaTeX uses A4 paper by default
\addtolength\topmargin{-1.8cm}

% Standard LaTeX packages
\usepackage[varg]{txfonts}
% \usepackage[varg]{newtxmath}
% \usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{color}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

%% Bundled custom packages
\usepackage{aastex-compat}
\usepackage{astrojournals}

\title{Photoionized bow shock shells.  I. Wind-wind interactions in the Orion proplyds}

\newcommand\AddressCRyA{Centro de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:intro}

\section{Conclusions}
\label{sec:conc}

\end{document}

### 2014-09-21 Proplyd distribution.tex
Find the proplyd size distribution and fit it

% Default to the notebook output style

% Inherit from the specified cell style.

\documentclass{article}

    \usepackage{graphicx} % Used to insert images
    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{color} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2

    \definecolor{orange}{cmyk}{0,0.4,0.8,0.2}
    \definecolor{darkorange}{rgb}{.71,0.21,0.01}
    \definecolor{darkgreen}{rgb}{.12,.54,.11}
    \definecolor{myteal}{rgb}{.26, .44, .56}
    \definecolor{gray}{gray}{0.45}
    \definecolor{lightgray}{gray}{.95}
    \definecolor{mediumgray}{gray}{.8}
    \definecolor{inputbackground}{rgb}{.95, .95, .85}
    \definecolor{outputbackground}{rgb}{.95, .95, .95}
    \definecolor{traceback}{rgb}{1, .95, .95}
    % ansi colors
    \definecolor{red}{rgb}{.6,0,0}
    \definecolor{green}{rgb}{0,.65,0}
    \definecolor{brown}{rgb}{0.6,0.6,0}
    \definecolor{blue}{rgb}{0,.145,.698}
    \definecolor{purple}{rgb}{.698,.145,.698}
    \definecolor{cyan}{rgb}{0,.698,.698}
    \definecolor{lightgray}{gray}{0.5}

    % bright ansi colors
    \definecolor{darkgray}{gray}{0.25}
    \definecolor{lightred}{rgb}{1.0,0.39,0.28}
    \definecolor{lightgreen}{rgb}{0.48,0.99,0.0}
    \definecolor{lightblue}{rgb}{0.53,0.81,0.92}
    \definecolor{lightpurple}{rgb}{0.87,0.63,0.87}
    \definecolor{lightcyan}{rgb}{0.5,1.0,0.83}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{Proplyd distribution}

    % Pygments definitions

\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % Exact colors from NB
    \definecolor{incolor}{rgb}{0.0, 0.0, 0.5}
    \definecolor{outcolor}{rgb}{0.545, 0.0, 0.0}

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=blue,
      linkcolor=darkorange,
      citecolor=darkgreen,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

    \begin{document}

    \maketitle

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}1}]:} \PY{o}{\PYZpc{}}\PY{k}{matplotlib} \PY{n}{inline}
\end{Verbatim}

    Calculations of distributions of proplyd distances and sizes and angles.
These translate into distributions of $\beta$.

    \subsection{Data sources}\label{data-sources}

We have the list of proplyds from Henney \& Arthur (1998) that we used
in Fig 12 of Tsamis et al (2013). This has distances and sizes.

We also have the Ricci et al (2008) catalog, which has distances but not
sizes.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}308}]:} \PY{k+kn}{from} \PY{n+nn}{astropy.table} \PY{k+kn}{import} \PY{n}{Table}
          \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
          \PY{k+kn}{import} \PY{n+nn}{seaborn} \PY{k+kn}{as} \PY{n+nn}{sns}
          \PY{k+kn}{from} \PY{n+nn}{scipy} \PY{k+kn}{import} \PY{n}{stats}
\end{Verbatim}

    Now use seaborn to get nicer graphs.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}359}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{set\PYZus{}palette}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{deep}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{desat}\PY{o}{=}\PY{l+m+mf}{0.6}\PY{p}{)}
          \PY{n}{sns}\PY{o}{.}\PY{n}{set\PYZus{}context}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{talk}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{rc}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{figure.figsize}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{p}{(}\PY{l+m+mi}{12}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}\PY{p}{\PYZcb{}}\PY{p}{)}
\end{Verbatim}

    \subsubsection{Henney \& Arthur (1998)
sample}\label{henney-arthur-1998-sample}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}3}]:} \PY{n}{datafile} \PY{o}{=} \PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd\PYZhy{}Datasets/vicente\PYZhy{}vs\PYZhy{}HA98.dat}\PY{l+s}{\PYZdq{}}
        \PY{n}{data} \PY{o}{=} \PY{n}{Table}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{n}{datafile}\PY{p}{,} \PY{n}{format}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{ascii}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}4}]:} \PY{n}{data}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}4}]:} <Table rows=28 names=('ID','d','r14','VicR14')>
        array([('163-323', 2.14, 2.2, 19.4), ('161-324', 6.05, 3.5, 25.8),
               ('168-328', 6.64, 2.8, 21.0), ('163-317', 6.91, 5.0, 27.1),
               ('166-316', 7.01, 2.5, 14.8), ('161-328', 7.74, 9.1, 20.0),
               ('167-317', 7.83, 7.9, 35.8), ('158-323', 9.42, 6.3, 30.6),
               ('158-326', 9.6, 11.3, 31.6), ('161-314', 10.24, 5.3, 17.1),
               ('158-327', 10.6, 16.6, 35.5), ('157-323', 10.97, 2.5, 18.4),
               ('171-334', 14.29, 4.7, 22.9), ('170-337', 16.2, 12.2, 36.8),
               ('176-325', 16.38, 6.9, 23.5), ('169-338', 16.47, 2.8, 16.1),
               ('154-324', 16.63, 3.2, 10.3), ('153-321', 16.97, 1.2, 8.4),
               ('159-338', 17.2, 5.0, 13.5), ('171-340', 19.11, 23.3, 23.2),
               ('152-319', 19.16, 18.2, 14.8), ('155-338', 20.48, 17.0, 29.7),
               ('173-341', 22.48, 4.1, 18.1), ('180-331', 25.12, 12.2, 29.3),
               ('177-341', 25.84, 20.4, 51.6), ('159-350', 28.35, 20.1, 44.5),
               ('182-413', 56.7, 36.9, 48.7), ('244-440', 142.3, 104.0, 180.6)], 
              dtype=[('ID', '<U7'), ('d', '<f8'), ('r14', '<f8'), ('VicR14', '<f8')])
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{k+kn}{from} \PY{n+nn}{matplotlib} \PY{k+kn}{import} \PY{n}{pyplot} \PY{k}{as} \PY{n}{plt}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}360}]:} \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{30}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of proplyds with projected distance \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Cumulative distribution of proplyds vs distance: HA98}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_10_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}361}]:} \PY{n}{m1} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{l+m+mf}{7.5}
          \PY{n}{m2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{abs}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{\PYZhy{}} \PY{l+m+mf}{13.0}\PY{p}{)} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{l+m+mf}{5.5}
          \PY{n}{m3} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{abs}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{\PYZhy{}} \PY{l+m+mf}{25.0}\PY{p}{)} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{l+m+mf}{6.5}
          \PY{n}{h1}\PY{p}{,} \PY{n}{edges} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{histogram}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m1}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{10}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{,} \PY{n}{density}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
          \PY{n}{h2}\PY{p}{,} \PY{n}{edges} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{histogram}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m2}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{10}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{,} \PY{n}{density}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
          \PY{n}{h3}\PY{p}{,} \PY{n}{edges} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{histogram}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m3}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{10}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{,} \PY{n}{density}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{bar}\PY{p}{(}\PY{n}{edges}\PY{p}{[}\PY{p}{:}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n}{h1}\PY{p}{,} \PY{l+m+mf}{2.5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.5}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{close: D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ \PYZlt{} 7.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{bar}\PY{p}{(}\PY{n}{edges}\PY{p}{[}\PY{p}{:}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n}{h2}\PY{p}{,} \PY{l+m+mf}{2.5}\PY{p}{,} \PY{n}{h1}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{g}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.5}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{medium: 7.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{ \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ \PYZlt{} 18.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{bar}\PY{p}{(}\PY{n}{edges}\PY{p}{[}\PY{p}{:}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n}{h3}\PY{p}{,} \PY{l+m+mf}{2.5}\PY{p}{,} \PY{n}{h1} \PY{o}{+} \PY{n}{h2}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.5}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{far: D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ \PYZgt{} 18.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Proplyd i\PYZhy{}front radius, 1e14 cm}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Fraction of proplyds in each size bin}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Histogram of proplyd sizes: HA98}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper right}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_11_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}362}]:} \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{o}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{30.0}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{30.0}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Distance, arcsec}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Radius, 1e14 cm}\PY{l+s}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}362}]:} <matplotlib.text.Text at 0x119f77710>
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_12_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    We need to take account of binaries

    Now we will try out some of the seaborn tools for visualizing data
distributions. See
\href{http://web.stanford.edu/~mwaskom/software/seaborn/tutorial/plotting_distributions.html}{this
tutorial}.

    In the section on the Ricci data it occured to me that we need to mirror
the data about zero because the radius and separation are
positive-definite.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}926}]:} \PY{k}{def} \PY{n+nf}{mirrored}\PY{p}{(}\PY{n}{dataset}\PY{p}{)}\PY{p}{:}
              \PY{l+s+sd}{\PYZdq{}\PYZdq{}\PYZdq{}Expand a positive\PYZhy{}definite dataset (1d sequence) to include its negative mirror set\PYZdq{}\PYZdq{}\PYZdq{}}
              \PY{k}{assert} \PY{n}{np}\PY{o}{.}\PY{n}{all}\PY{p}{(}\PY{n}{dataset} \PY{o}{\PYZgt{}}\PY{o}{=} \PY{l+m+mf}{0.0}\PY{p}{)}
              \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{r\PYZus{}}\PY{p}{[}\PY{n}{dataset}\PY{p}{,} \PY{o}{\PYZhy{}}\PY{n}{dataset}\PY{p}{]}

          \PY{k}{def} \PY{n+nf}{doubled}\PY{p}{(}\PY{n}{dataset}\PY{p}{)}\PY{p}{:}
              \PY{l+s+sd}{\PYZdq{}\PYZdq{}\PYZdq{}Double up a dataset (1d sequence)\PYZdq{}\PYZdq{}\PYZdq{}}
              \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{r\PYZus{}}\PY{p}{[}\PY{n}{dataset}\PY{p}{,} \PY{n}{dataset}\PY{p}{]}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}425}]:} \PY{n}{m30} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{l+m+mf}{30.0}
          \PY{k}{with} \PY{n}{sns}\PY{o}{.}\PY{n}{axes\PYZus{}style}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{white}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{:}
              \PY{n}{sns}\PY{o}{.}\PY{n}{jointplot}\PY{p}{(}\PY{n}{mirrored}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m30}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{mirrored}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m30}\PY{p}{]}\PY{p}{)}\PY{p}{,} 
                            \PY{n}{kind}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{hex}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{9}\PY{p}{,} \PY{n}{xlim}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{,} \PY{n}{ylim}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_17_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}446}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{kdeplot}\PY{p}{(}\PY{n}{mirrored}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{mirrored}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,} 
                      \PY{n}{clip}\PY{o}{=}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{40}\PY{p}{)}\PY{p}{,} \PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{)}\PY{p}{,}
                      \PY{n}{bw}\PY{o}{=}\PY{l+m+mf}{3.0}\PY{p}{,} \PY{n}{shade}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{cmap}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Reds}\PY{l+s}{\PYZdq{}}\PY{p}{,}
                      \PY{p}{)}
          \PY{n+nb+bp}{None}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_18_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}503}]:} \PY{n}{color} \PY{o}{=} \PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsh{}774499}\PY{l+s}{\PYZdq{}}
          \PY{n}{g} \PY{o}{=} \PY{n}{sns}\PY{o}{.}\PY{n}{JointGrid}\PY{p}{(}\PY{n}{mirrored}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m30}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{mirrored}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m30}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{9}\PY{p}{,} \PY{n}{xlim}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{,} \PY{n}{ylim}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{)}
          \PY{c}{\PYZsh{} g.plot(sns.regplot, sns.distplot, stats.pearsonr);}
          \PY{n}{g}\PY{o}{.}\PY{n}{plot\PYZus{}marginals}\PY{p}{(}\PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{10}\PY{p}{,} \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{n+nb}{dict}\PY{p}{(}\PY{n}{bw}\PY{o}{=}\PY{l+m+mf}{5.0}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{KDE}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{plot\PYZus{}joint}\PY{p}{(}\PY{n}{sns}\PY{o}{.}\PY{n}{regplot}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{,} \PY{n}{ci}\PY{o}{=}\PY{l+m+mi}{98}\PY{p}{,} \PY{n}{order}\PY{o}{=}\PY{l+m+mi}{3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Cubic regression fit with 98}\PY{l+s+si}{\PYZpc{} c}\PY{l+s}{onfidence bounds}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Projected separation, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd radius \PYZdl{}r\PYZus{}0\PYZdl{}, \PYZdl{}10\PYZca{}\PYZob{}14\PYZcb{}\PYZdl{} cm}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}marg\PYZus{}x}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper right}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}marg\PYZus{}y}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{best}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{fig}\PY{o}{.}\PY{n}{tight\PYZus{}layout}\PY{p}{(}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{fig}\PY{o}{.}\PY{n}{savefig}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{proplyd\PYZhy{}joint\PYZhy{}separation\PYZhy{}size.pdf}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{;}
          \PY{c}{\PYZsh{}g.annotate(stats.pearsonr);}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_19_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}494}]:} \PY{n}{stats}\PY{o}{.}\PY{n}{scoreatpercentile}\PY{err}{?}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}401}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{rugplot}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{height}\PY{o}{=}\PY{l+m+mf}{0.002}\PY{p}{)}
          \PY{n}{sns}\PY{o}{.}\PY{n}{kdeplot}\PY{p}{(}\PY{n}{mirrored}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{shade}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{n+nb+bp}{None}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}401}]:} (0.0, 200.0)
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_21_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    Now we will compare the sizes for different intervals of $D'$

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}407}]:} \PY{n}{datalist} \PY{o}{=} \PY{p}{[}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m1}\PY{p}{]}\PY{p}{,} \PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m2}\PY{p}{]}\PY{p}{,} \PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m3}\PY{p}{]}\PY{p}{]}
          \PY{n}{mirrored\PYZus{}datalist} \PY{o}{=} \PY{p}{[}\PY{n}{mirrored}\PY{p}{(}\PY{n}{x}\PY{p}{)} \PY{k}{for} \PY{n}{x} \PY{o+ow}{in} \PY{n}{datalist}\PY{p}{]}
          \PY{n}{namelist} \PY{o}{=} \PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{close: D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ \PYZlt{} 7.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{mid: 7.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{ \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ \PYZlt{} 18.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{far: D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ \PYZgt{} 18.5}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}}\PY{p}{]}
\end{Verbatim}

    The simplest option is \texttt{boxplot}, which shows the median and
quartiles. By setting \texttt{whis=np.inf} we make the whiskers extend
out to the full range of the data.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}408}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{boxplot}\PY{p}{(}\PY{n}{datalist}\PY{p}{,} \PY{n}{names}\PY{o}{=}\PY{n}{namelist}\PY{p}{,} \PY{n}{whis}\PY{o}{=}\PY{n}{np}\PY{o}{.}\PY{n}{inf}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{pastel}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd size, 1e14 cm}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Projected distance band}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n+nb+bp}{None}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_25_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    Alternatively we can use \texttt{violinplot}, which shows the Kernel
Density Estimate (KDE) of the values in each category. By setting
\texttt{inner="points"} it shows the actual data points instead of the
quartiles.

I am a little uncomfortable of this way of presenting the data, since we
are forcing the distance to be categorical, when really it is
continuous.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}421}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{violinplot}\PY{p}{(}\PY{n}{mirrored\PYZus{}datalist}\PY{p}{,} 
                         \PY{n}{names}\PY{o}{=}\PY{n}{namelist}\PY{p}{,}
                         \PY{n}{inner}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{points}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{bw}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{PuBuGn}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{ylim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{n+nb+bp}{None}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd size, 1e14 cm}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Projected distance band}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n+nb+bp}{None}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_27_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}422}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{jointplot}\PY{err}{?}
\end{Verbatim}

    \subsubsection{Ricci et al (2008) sample}\label{ricci-et-al-2008-sample}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}9}]:} \PY{n}{rdata} \PY{o}{=} \PY{n}{Table}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd\PYZhy{}Datasets/ricci\PYZhy{}2008.dat}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{format}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{ascii}\PY{l+s}{\PYZsq{}}\PY{p}{)}
        \PY{n}{rdata}\PY{o}{.}\PY{n}{remove\PYZus{}row}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{)} \PY{c}{\PYZsh{} First row is rubbish}
        \PY{n}{rdata}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}9}]:} <Table rows=219 names=('Name','RAJ2000','DEJ2000','[OW94]','Type','Note')>
        masked\_array(data = [('4364-146', '05 34 36.44', '-05 21 45.95', '0', 'j', 'J')
         ('4466-324', '05 34 46.59', '-05 23 24.19', '0', 'j', 'J,B')
         ('4468-605', '05 34 46.76', '-05 26 04.79', '0', 'i', 'J')
         ('4538-311', '05 34 53.79', '-05 23 10.73', '0', 'rn', '0')
         ('4596-400', '05 34 59.56', '-05 24 00.19', '4596-400', 'i', '0')
         ('4582-635', '05 34 58.16', '-05 26 35.13', '0', 'i', '0')
         ('005-514', '05 35 00.47', '-05 25 14.34', '005-514', 'i', '0')
         ('006-439', '05 35 00.58', '-05 24 38.79', '0', 'j', 'J')
         ('016-149', '05 35 01.60', '-05 21 49.35', '0', 'rn', '0')
         ('038-627', '05 35 04.19', '-05 26 27.89', '038-627', 'i', '0')
         ('044-527', '05 35 04.42', '-05 25 27.40', '044-527', 'i', '0')
         ('046-3838', '05 35 04.61', '-05 38 38.00', '0', 'rn', '0')
         ('046-245', '05 35 04.63', '-05 22 44.85', '0', 'i', '0')
         ('049-143', '05 35 04.94', '-05 21 42.99', '0', 'i', '0')
         ('051-3541', '05 35 05.05', '-05 35 40.84', '0', 'rn', 'EO')
         ('053-717', '05 35 05.40', '-05 27 16.99', '0', 'd', '0')
         ('057-419', '05 35 05.73', '-05 24 18.55', '057-419', 'i', '0')
         ('061-401', '05 35 06.09', '-05 24 00.60', '061-401', 'i', '0')
         ('064-3335', '05 35 06.44', '-05 33 35.25', '0', 'i', '0')
         ('066-3251', '05 35 06.57', '-05 32 51.49', '0', 'i', '0')
         ('066-652', '05 35 06.59', '-05 26 51.99', '066-652', 'i', 'B')
         ('069-601', '05 35 06.91', '-05 26 00.60', '069-601', 'i', '0')
         ('072-135', '05 35 07.21', '-05 21 34.43', '072-135', 'i', 'EO')
         ('073-227', '05 35 07.27', '-05 22 26.56', '073-227', 'i', '0')
         ('078-3658', '05 35 07.84', '-05 36 58.15', '0', 'j', 'J,B')
         ('090-326', '05 35 09.02', '-05 23 26.20', '0', 'd', '0')
         ('093-822', '05 35 09.59', '-05 28 22.92', '093-822', 'i', '0')
         ('099-339', '05 35 09.89', '-05 23 38.50', '0', 'i', 'J')
         ('102-233', '05 35 10.13', '-05 22 32.74', '102-233', 'i', '0')
         ('102-021', '05 35 10.19', '-05 20 20.99', '102-021', 'i', '0')
         ('102-322', '05 35 10.20', '-05 23 21.56', '102-322', 'i', '0')
         ('106-417', '05 35 10.54', '-05 24 16.70', '106-417', 'i', '0')
         ('106-156', '05 35 10.58', '-05 21 56.24', '106-156', 'i', '0')
         ('109-246', '05 35 10.90', '-05 22 46.36', '109-246', 'i', '0')
         ('109-327', '05 35 10.95', '-05 23 26.45', '109-327', 'i', 'J')
         ('110-3035', '05 35 10.98', '-05 30 35.23', '0', 'rn', 'J')
         ('114-426', '05 35 11.30', '-05 24 26.50', '114-426', 'd', 'EO,RN')
         ('117-421', '05 35 11.65', '-05 24 21.50', '117-421', 'i', '0')
         ('117-352', '05 35 11.73', '-05 23 51.70', '0', 'i', '0')
         ('119-340', '05 35 11.90', '-05 23 39.70', '119-340', 'i', '0')
         ('121-1925', '05 35 12.09', '-05 19 24.80', '121-1925', 'd', '0')
         ('121-434', '05 35 12.12', '-05 24 33.80', '121-434', 'i', '0')
         ('124-132', '05 35 12.38', '-05 21 31.39', '124-132', 'i', 'J,EO,B')
         ('131-046', '05 35 13.05', '-05 20 45.79', '131-046', 'i', '0')
         ('131-247', '05 35 13.11', '-05 22 47.11', '131-247', 'i', 'J')
         ('132-1832', '05 35 13.24', '-05 18 32.95', '0', 'd', 'EO')
         ('132-042', '05 35 13.24', '-05 20 41.94', '132-042', 'i', 'J,EO')
         ('133-353', '05 35 13.30', '-05 23 53.05', '133-353', 'i', 'B')
         ('135-220', '05 35 13.51', '-05 22 19.49', '135-220', 'i', '0')
         ('138-207', '05 35 13.78', '-05 22 07.39', '138-207', 'i', '0')
         ('139-320', '05 35 13.92', '-05 23 20.16', '0', 'i', '0')
         ('141-520', '05 35 14.05', '-05 25 20.50', '141-520', 'i', 'FO')
         ('140-1952', '05 35 14.05', '-05 19 51.90', '140-1952', 'd', 'FO')
         ('142-301', '05 35 14.15', '-05 23 00.91', '142-301', 'i', '0')
         ('143-425', '05 35 14.27', '-05 24 24.55', '143-425', 'i', '0')
         ('144-522', '05 35 14.34', '-05 25 22.30', '144-522', 'i', '0')
         ('146-201', '05 35 14.61', '-05 22 00.94', '0', 'i', '0')
         ('147-323', '05 35 14.72', '-05 23 23.01', '0', 'i', '0')
         ('148-305', '05 35 14.80', '-05 23 04.76', '148-305', 'i', 'B')
         ('149-329', '05 35 14.92', '-05 23 29.05', '149-329', 'i', '0')
         ('150-147', '05 35 15.00', '-05 21 47.34', '0', 'i', '0')
         ('150-231', '05 35 15.02', '-05 22 31.11', '150-231', 'i', 'B')
         ('152-319', '05 35 15.20', '-05 23 18.81', '152-319', 'i', '0')
         ('152-738', '05 35 15.21', '-05 27 37.85', '152-738', 'i', '0')
         ('154-324', '05 35 15.35', '-05 23 24.11', '154-324', 'i', 'B')
         ('154-225', '05 35 15.37', '-05 22 25.35', '154-225', 'i', 'B')
         ('154-240', '05 35 15.38', '-05 22 39.85', '0', 'i', '0')
         ('155-338', '05 35 15.51', '-05 23 37.45', '155-338', 'i', '0')
         ('157-323', '05 35 15.72', '-05 23 22.59', '157-323', 'i', 'B')
         ('158-323', '05 35 15.83', '-05 23 22.59', '158-323', 'i', 'B')
         ('158-327', '05 35 15.79', '-05 23 26.51', '158-327', 'i', 'B')
         ('158-326', '05 35 15.81', '-05 23 25.51', '158-326', 'i', 'B')
         ('159-338', '05 35 15.90', '-05 23 38.00', '159-338', 'i', 'B')
         ('159-418', '05 35 15.90', '-05 24 17.85', '159-418', 'i', '0')
         ('159-221', '05 35 15.93', '-05 22 21.05', '159-221', 'd', '0')
         ('159-350', '05 35 15.96', '-05 23 50.30', '159-350', 'i', 'B')
         ('160-353', '05 35 16.01', '-05 23 53.00', '160-353', 'i', 'J')
         ('161-324', '05 35 16.05', '-05 23 24.35', '161-324', 'i', '0')
         ('161-328', '05 35 16.07', '-05 23 27.81', '161-328', 'i', '0')
         ('161-314', '05 35 16.10', '-05 23 14.05', '161-314', 'i', '0')
         ('162-133', '05 35 16.19', '-05 21 32.39', '162-133', 'i', '0')
         ('163-026', '05 35 16.31', '-05 20 25.24', '0', 'd', 'B')
         ('163-210', '05 35 16.27', '-05 22 10.45', '163-210', 'i', 'B')
         ('163-317', '05 35 16.27', '-05 23 16.51', '163-317', 'i', '0')
         ('163-222', '05 35 16.30', '-05 22 21.50', '163-222', 'i', 'B,FO')
         ('163-249', '05 35 16.33', '-05 22 49.01', '163-249', 'i', 'B')
         ('164-511', '05 35 16.35', '-05 25 09.60', '164-511', 'i', '0')
         ('165-235', '05 35 16.48', '-05 22 35.16', '165-235', 'i', '0')
         ('165-254', '05 35 16.54', '-05 22 53.70', '0', 'd', 'RN')
         ('166-316', '05 35 16.61', '-05 23 16.19', '166-315', 'i', '0')
         ('166-519', '05 35 16.57', '-05 25 17.74', '166-519', 'd', '0')
         ('166-406', '05 35 16.57', '-05 24 06.00', '166-406', 'i', '0')
         ('166-250', '05 35 16.59', '-05 22 50.36', '166-250', 'i', '0')
         ('167-231', '05 35 16.73', '-05 22 31.30', '167-231', 'd', 'FO')
         ('167-317', '05 35 16.74', '-05 23 16.51', '167-317', 'i', '0')
         ('168-235', '05 35 16.81', '-05 22 34.71', '168-235', 'i', '0')
         ('168-328', '05 35 16.77', '-05 23 28.06', '168-328', 'i', 'B')
         ('168-326', '05 35 16.83', '-05 23 25.91', '168-326', 'i', 'B')
         ('169-338', '05 35 16.88', '-05 23 38.10', '169-338', 'i', 'B')
         ('170-301', '05 35 16.95', '-05 23 00.91', '170-301', 'i', '0')
         ('170-249', '05 35 16.96', '-05 22 48.51', '170-249', 'i', 'B')
         ('170-337', '05 35 16.97', '-05 23 37.15', '170-337', 'i', 'B')
         ('171-340', '05 35 17.04', '-05 23 39.75', '171-340', 'i', 'B')
         ('171-434', '05 35 17.11', '-05 24 34.40', '171-434', 'i', 'B')
         ('172-028', '05 35 17.22', '-05 20 27.84', '172-028', 'd', '0')
         ('173-341', '05 35 17.32', '-05 23 41.40', '173-341', 'i', 'B')
         ('173-236', '05 35 17.34', '-05 22 35.81', '173-236', 'i', '0')
         ('174-305', '05 35 17.37', '-05 23 04.86', '174-305', 'i', '0')
         ('174-414', '05 35 17.38', '-05 24 13.90', '174-414', 'i', '0')
         ('175-251', '05 35 17.47', '-05 22 51.26', '175-251', 'i', 'B')
         ('175-355', '05 35 17.54', '-05 23 55.05', '175-355', 'i', '0')
         ('175-543', '05 35 17.54', '-05 25 42.89', '175-543', 'i', 'J,EO,B')
         ('176-325', '05 35 17.55', '-05 23 24.96', '176-325', 'i', '0')
         ('176-252', '05 35 17.64', '-05 22 51.66', '176-252', 'i', '0')
         ('177-341W', '05 35 17.66', '-05 23 41.00', '177-341', 'i', 'B')
         ('177-454', '05 35 17.69', '-05 24 54.10', '177-454', 'i', '0')
         ('177-541', '05 35 17.71', '-05 25 40.76', '0', 'i', 'EO,B')
         ('177-444', '05 35 17.73', '-05 24 43.75', '177-444', 'i', '0')
         ('177-341E', '05 35 17.73', '-05 23 41.10', '177-341', 'i', 'B')
         ('178-441', '05 35 17.81', '-05 24 41.05', '0', 'i', '0')
         ('178-258', '05 35 17.84', '-05 22 58.15', '0', 'i', '0')
         ('179-056', '05 35 17.92', '-05 20 55.44', '179-056', 'i', 'B')
         ('179-354', '05 35 17.96', '-05 23 53.50', '179-354', 'i', '0')
         ('180-331', '05 35 18.03', '-05 23 30.80', '180-331', 'i', 'B')
         ('181-247', '05 35 18.08', '-05 22 47.10', '181-247', 'i', 'B')
         ('181-825', '05 35 18.10', '-05 28 25.04', '0', 'i', 'RN')
         ('182-316', '05 35 18.19', '-05 23 31.55', '182-316', 'd', 'B')
         ('182-413', '05 35 18.22', '-05 24 13.45', '182-413', 'i', '0')
         ('183-439', '05 35 18.28', '-05 24 38.85', '183-439', 'i', 'B')
         ('183-419', '05 35 18.31', '-05 24 18.85', '183-419', 'i', '0')
         ('183-405', '05 35 18.33', '-05 24 04.85', '183-405', 'd', 'FO,B')
         ('184-427', '05 35 18.35', '-05 24 26.85', '184-427', 'i', 'B')
         ('184-520', '05 35 18.44', '-05 25 19.29', '184-520', 'i', '0')
         ('187-314', '05 35 18.68', '-05 23 14.01', '187-314', 'i', 'B')
         ('189-329', '05 35 18.87', '-05 23 28.85', '189-329', 'i', '0')
         ('190-251', '05 35 19.03', '-05 22 50.65', '0', 'i', 'B')
         ('191-232', '05 35 19.13', '-05 22 31.20', '0', 'd', '0')
         ('191-350', '05 35 19.06', '-05 23 49.50', '191-350', 'i', 'J')
         ('193-1659', '05 35 19.25', '-05 16 58.69', '0', 'rn', '0')
         ('197-427', '05 35 19.65', '-05 24 26.70', '197-427', 'i', 'RN')
         ('198-222', '05 35 19.82', '-05 22 21.55', '198-222', 'i', '0')
         ('198-448', '05 35 19.83', '-05 24 47.95', '198-448', 'i', '0')
         ('199-1508', '05 35 19.89', '-05 15 08.25', '0', 'i', 'B')
         ('200-106', '05 35 20.04', '-05 21 05.99', '200-106', 'i', '0')
         ('201-534', '05 35 20.14', '-05 25 33.84', '201-534', 'i', '0')
         ('202-228', '05 35 20.15', '-05 22 28.30', '202-228', 'i', 'B')
         ('203-504', '05 35 20.26', '-05 25 04.05', '203-504', 'i', 'B')
         ('203-506', '05 35 20.32', '-05 25 05.55', '0', 'd', 'RN')
         ('205-330', '05 35 20.45', '-05 23 29.96', '205-330', 'i', 'B')
         ('205-052', '05 35 20.52', '-05 20 52.05', '205-052', 'i', '0')
         ('205-421', '05 35 20.53', '-05 24 21.00', '205-421', 'i', 'FO')
         ('206-446', '05 35 20.62', '-05 24 46.45', '206-446', 'i', '0')
         ('208-122', '05 35 20.83', '-05 21 21.45', '208-122', 'rn', '0')
         ('209-151', '05 35 21.00', '-05 21 52.30', '209-151', 'i', 'B')
         ('210-225', '05 35 21.03', '-05 22 25.20', '0', 'i', '0')
         ('212-557', '05 35 21.15', '-05 25 57.04', '212-557', 'i', '0')
         ('212-400', '05 35 21.19', '-05 24 00.20', '0', 'i', '0')
         ('212-260', '05 35 21.24', '-05 22 59.51', '212-260', 'i', '0')
         ('213-533', '05 35 21.28', '-05 25 33.11', '0', 'i', 'B')
         ('213-346', '05 35 21.30', '-05 23 46.10', '0', 'i', 'B')
         ('215-652', '05 35 21.45', '-05 26 52.40', '0', 'i', '0')
         ('215-317', '05 35 21.49', '-05 23 16.71', '215-317', 'i', '0')
         ('215-106', '05 35 21.55', '-05 21 05.60', '215-106', 'i', 'J')
         ('216-541', '05 35 21.60', '-05 25 40.70', '0', 'i', '0')
         ('216-715', '05 35 21.62', '-05 27 14.65', '216-715', 'i', '0')
         ('218-339', '05 35 21.77', '-05 23 39.30', '218-339', 'i', '0')
         ('218-354', '05 35 21.79', '-05 23 53.90', '218-354', 'd', 'EO,B')
         ('218-529', '05 35 21.82', '-05 25 28.46', '0', 'i', 'B')
         ('218-306', '05 35 21.84', '-05 23 06.46', '0', 'i', 'B')
         ('221-433', '05 35 22.08', '-05 24 32.95', '221-433', 'i', '0')
         ('223-414', '05 35 22.31', '-05 24 14.25', '223-414', 'i', 'B')
         ('224-728', '05 35 22.37', '-05 27 28.40', '224-728', 'i', '0')
         ('228-548', '05 35 22.83', '-05 25 47.69', '228-548', 'i', '0')
         ('230-536', '05 35 23.02', '-05 25 36.29', '0', 'd', '0')
         ('231-460', '05 35 23.05', '-05 24 59.86', '231-460', 'i', '0')
         ('231-502', '05 35 23.16', '-05 25 02.19', '231-502', 'i', 'B')
         ('231-838', '05 35 23.10', '-05 28 37.34', '231-838', 'i', 'J')
         ('232-453', '05 35 23.22', '-05 24 52.79', '232-453', 'i', '0')
         ('234-853', '05 35 23.40', '-05 28 53.19', '0', 'i', '0')
         ('236-527', '05 35 23.59', '-05 25 26.54', '236-527', 'i', '0')
         ('237-627', '05 35 23.66', '-05 26 27.15', '237-627', 'i', '0')
         ('238-334', '05 35 23.80', '-05 23 34.30', '238-334', 'i', 'B')
         ('239-334', '05 35 23.86', '-05 23 34.05', '0', 'd', 'EO,B')
         ('239-510', '05 35 23.98', '-05 25 09.94', '239-510', 'i', '0')
         ('240-314', '05 35 24.02', '-05 23 13.85', '240-314', 'i', 'B')
         ('242-519', '05 35 24.22', '-05 25 18.79', '242-519', 'i', '0')
         ('244-440', '05 35 24.38', '-05 24 39.74', '244-440', 'i', '0')
         ('245-632', '05 35 24.45', '-05 26 31.55', '245-632', 'i', 'B')
         ('245-1910', '05 35 24.48', '-05 19 09.84', '0', 'i', 'RN,B')
         ('245-502', '05 35 24.51', '-05 25 01.59', '245-502', 'i', '0')
         ('247-436', '05 35 24.69', '-05 24 35.74', '247-436', 'i', 'J')
         ('250-439', '05 35 25.02', '-05 24 38.49', '250-439', 'i', '0')
         ('252-457', '05 35 25.21', '-05 24 57.34', '252-457', 'i', '0')
         ('253-1536', '05 35 25.30', '-05 15 35.54', '0', 'd', 'J,RN,B')
         ('254-412', '05 35 25.37', '-05 24 11.50', '254-412', 'i', '0')
         ('255-512', '05 35 25.52', '-05 25 11.84', '0', 'i', '0')
         ('262-521', '05 35 26.18', '-05 25 20.49', '262-521', 'i', '0')
         ('264-532', '05 35 26.42', '-05 25 31.69', '264-532', 'i', '0')
         ('266-558', '05 35 26.62', '-05 25 57.84', '0', 'i', '0')
         ('280-931', '05 35 27.96', '-05 29 31.15', '0', 'i', '0')
         ('280-1720', '05 35 28.05', '-05 17 20.33', '0', 'd', 'FO')
         ('281-306', '05 35 28.13', '-05 23 06.45', '0', 'd', 'FO')
         ('282-458', '05 35 28.20', '-05 24 58.19', '282-458', 'i', 'J')
         ('282-614', '05 35 28.20', '-05 26 14.20', '0', 'i', '0')
         ('284-439', '05 35 28.40', '-05 24 38.69', '0', 'i', '0')
         ('294-757', '05 35 29.43', '-05 37 56.60', '0', 'rn', '0')
         ('294-606', '05 35 29.48', '-05 26 06.63', '0', 'd', 'RN')
         ('297-025', '05 35 29.67', '-05 30 24.75', '0', 'i', '0')
         ('304-539', '05 35 30.41', '-05 25 38.63', '304-539', 'i', '0')
         ('307-1807', '05 35 30.70', '-05 18 07.24', '307-1807', 'i', '0')
         ('314-816', '05 35 31.40', '-05 28 16.48', '0', 'i', '0')
         ('321-602', '05 35 32.10', '-05 26 01.94', '321-602', 'd', 'EO')
         ('332-405', '05 35 33.19', '-05 24 04.74', '0', 'd', '0')
         ('332-1605', '05 35 33.20', '-05 16 05.38', '332-1605', 'i', '0')
         ('346-1553', '05 35 34.62', '-05 15 52.92', '0', 'd', 'FO')
         ('347-1535', '05 35 34.67', '-05 15 34.88', '347-1535', 'd', 'J')
         ('351-3349', '05 35 35.13', '-05 33 49.18', '0', 'i', 'J')
         ('353-130', '05 35 35.32', '-05 21 29.59', '0', 'j', 'J,B')
         ('473-245', '05 35 47.34', '-05 22 44.82', '0', 'd', 'EO')],
                     mask = [(False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)
         (False, False, False, False, False, False)],
               fill\_value = ('N/A', 'N/A', 'N/A', 'N/A', 'N/', 'N/A'),
                    dtype = [('Name', '<U8'), ('RAJ2000', '<U11'), ('DEJ2000', '<U12'), ('[OW94]', '<U8'), ('Type', '<U2'), ('Note', '<U6')])
\end{Verbatim}

    Bright proplyds have \texttt{i} in the \texttt{Type} column.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}10}]:} \PY{n}{m} \PY{o}{=} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{l+s}{\PYZsq{}}\PY{l+s}{i}\PY{l+s}{\PYZsq{}}
         \PY{n}{md} \PY{o}{=} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{l+s}{\PYZsq{}}\PY{l+s}{d}\PY{l+s}{\PYZsq{}}
         \PY{n}{mj} \PY{o}{=} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{l+s}{\PYZsq{}}\PY{l+s}{j}\PY{l+s}{\PYZsq{}}
         \PY{n}{mr} \PY{o}{=} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{l+s}{\PYZsq{}}\PY{l+s}{rn}\PY{l+s}{\PYZsq{}}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}11}]:} \PY{n}{rdata}\PY{p}{[}\PY{n}{m}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}11}]:} <Table rows=178 names=('Name','RAJ2000','DEJ2000','[OW94]','Type','Note')>
         masked\_array(data = [('4468-605', '05 34 46.76', '-05 26 04.79', '0', 'i', 'J')
          ('4596-400', '05 34 59.56', '-05 24 00.19', '4596-400', 'i', '0')
          ('4582-635', '05 34 58.16', '-05 26 35.13', '0', 'i', '0')
          ('005-514', '05 35 00.47', '-05 25 14.34', '005-514', 'i', '0')
          ('038-627', '05 35 04.19', '-05 26 27.89', '038-627', 'i', '0')
          ('044-527', '05 35 04.42', '-05 25 27.40', '044-527', 'i', '0')
          ('046-245', '05 35 04.63', '-05 22 44.85', '0', 'i', '0')
          ('049-143', '05 35 04.94', '-05 21 42.99', '0', 'i', '0')
          ('057-419', '05 35 05.73', '-05 24 18.55', '057-419', 'i', '0')
          ('061-401', '05 35 06.09', '-05 24 00.60', '061-401', 'i', '0')
          ('064-3335', '05 35 06.44', '-05 33 35.25', '0', 'i', '0')
          ('066-3251', '05 35 06.57', '-05 32 51.49', '0', 'i', '0')
          ('066-652', '05 35 06.59', '-05 26 51.99', '066-652', 'i', 'B')
          ('069-601', '05 35 06.91', '-05 26 00.60', '069-601', 'i', '0')
          ('072-135', '05 35 07.21', '-05 21 34.43', '072-135', 'i', 'EO')
          ('073-227', '05 35 07.27', '-05 22 26.56', '073-227', 'i', '0')
          ('093-822', '05 35 09.59', '-05 28 22.92', '093-822', 'i', '0')
          ('099-339', '05 35 09.89', '-05 23 38.50', '0', 'i', 'J')
          ('102-233', '05 35 10.13', '-05 22 32.74', '102-233', 'i', '0')
          ('102-021', '05 35 10.19', '-05 20 20.99', '102-021', 'i', '0')
          ('102-322', '05 35 10.20', '-05 23 21.56', '102-322', 'i', '0')
          ('106-417', '05 35 10.54', '-05 24 16.70', '106-417', 'i', '0')
          ('106-156', '05 35 10.58', '-05 21 56.24', '106-156', 'i', '0')
          ('109-246', '05 35 10.90', '-05 22 46.36', '109-246', 'i', '0')
          ('109-327', '05 35 10.95', '-05 23 26.45', '109-327', 'i', 'J')
          ('117-421', '05 35 11.65', '-05 24 21.50', '117-421', 'i', '0')
          ('117-352', '05 35 11.73', '-05 23 51.70', '0', 'i', '0')
          ('119-340', '05 35 11.90', '-05 23 39.70', '119-340', 'i', '0')
          ('121-434', '05 35 12.12', '-05 24 33.80', '121-434', 'i', '0')
          ('124-132', '05 35 12.38', '-05 21 31.39', '124-132', 'i', 'J,EO,B')
          ('131-046', '05 35 13.05', '-05 20 45.79', '131-046', 'i', '0')
          ('131-247', '05 35 13.11', '-05 22 47.11', '131-247', 'i', 'J')
          ('132-042', '05 35 13.24', '-05 20 41.94', '132-042', 'i', 'J,EO')
          ('133-353', '05 35 13.30', '-05 23 53.05', '133-353', 'i', 'B')
          ('135-220', '05 35 13.51', '-05 22 19.49', '135-220', 'i', '0')
          ('138-207', '05 35 13.78', '-05 22 07.39', '138-207', 'i', '0')
          ('139-320', '05 35 13.92', '-05 23 20.16', '0', 'i', '0')
          ('141-520', '05 35 14.05', '-05 25 20.50', '141-520', 'i', 'FO')
          ('142-301', '05 35 14.15', '-05 23 00.91', '142-301', 'i', '0')
          ('143-425', '05 35 14.27', '-05 24 24.55', '143-425', 'i', '0')
          ('144-522', '05 35 14.34', '-05 25 22.30', '144-522', 'i', '0')
          ('146-201', '05 35 14.61', '-05 22 00.94', '0', 'i', '0')
          ('147-323', '05 35 14.72', '-05 23 23.01', '0', 'i', '0')
          ('148-305', '05 35 14.80', '-05 23 04.76', '148-305', 'i', 'B')
          ('149-329', '05 35 14.92', '-05 23 29.05', '149-329', 'i', '0')
          ('150-147', '05 35 15.00', '-05 21 47.34', '0', 'i', '0')
          ('150-231', '05 35 15.02', '-05 22 31.11', '150-231', 'i', 'B')
          ('152-319', '05 35 15.20', '-05 23 18.81', '152-319', 'i', '0')
          ('152-738', '05 35 15.21', '-05 27 37.85', '152-738', 'i', '0')
          ('154-324', '05 35 15.35', '-05 23 24.11', '154-324', 'i', 'B')
          ('154-225', '05 35 15.37', '-05 22 25.35', '154-225', 'i', 'B')
          ('154-240', '05 35 15.38', '-05 22 39.85', '0', 'i', '0')
          ('155-338', '05 35 15.51', '-05 23 37.45', '155-338', 'i', '0')
          ('157-323', '05 35 15.72', '-05 23 22.59', '157-323', 'i', 'B')
          ('158-323', '05 35 15.83', '-05 23 22.59', '158-323', 'i', 'B')
          ('158-327', '05 35 15.79', '-05 23 26.51', '158-327', 'i', 'B')
          ('158-326', '05 35 15.81', '-05 23 25.51', '158-326', 'i', 'B')
          ('159-338', '05 35 15.90', '-05 23 38.00', '159-338', 'i', 'B')
          ('159-418', '05 35 15.90', '-05 24 17.85', '159-418', 'i', '0')
          ('159-350', '05 35 15.96', '-05 23 50.30', '159-350', 'i', 'B')
          ('160-353', '05 35 16.01', '-05 23 53.00', '160-353', 'i', 'J')
          ('161-324', '05 35 16.05', '-05 23 24.35', '161-324', 'i', '0')
          ('161-328', '05 35 16.07', '-05 23 27.81', '161-328', 'i', '0')
          ('161-314', '05 35 16.10', '-05 23 14.05', '161-314', 'i', '0')
          ('162-133', '05 35 16.19', '-05 21 32.39', '162-133', 'i', '0')
          ('163-210', '05 35 16.27', '-05 22 10.45', '163-210', 'i', 'B')
          ('163-317', '05 35 16.27', '-05 23 16.51', '163-317', 'i', '0')
          ('163-222', '05 35 16.30', '-05 22 21.50', '163-222', 'i', 'B,FO')
          ('163-249', '05 35 16.33', '-05 22 49.01', '163-249', 'i', 'B')
          ('164-511', '05 35 16.35', '-05 25 09.60', '164-511', 'i', '0')
          ('165-235', '05 35 16.48', '-05 22 35.16', '165-235', 'i', '0')
          ('166-316', '05 35 16.61', '-05 23 16.19', '166-315', 'i', '0')
          ('166-406', '05 35 16.57', '-05 24 06.00', '166-406', 'i', '0')
          ('166-250', '05 35 16.59', '-05 22 50.36', '166-250', 'i', '0')
          ('167-317', '05 35 16.74', '-05 23 16.51', '167-317', 'i', '0')
          ('168-235', '05 35 16.81', '-05 22 34.71', '168-235', 'i', '0')
          ('168-328', '05 35 16.77', '-05 23 28.06', '168-328', 'i', 'B')
          ('168-326', '05 35 16.83', '-05 23 25.91', '168-326', 'i', 'B')
          ('169-338', '05 35 16.88', '-05 23 38.10', '169-338', 'i', 'B')
          ('170-301', '05 35 16.95', '-05 23 00.91', '170-301', 'i', '0')
          ('170-249', '05 35 16.96', '-05 22 48.51', '170-249', 'i', 'B')
          ('170-337', '05 35 16.97', '-05 23 37.15', '170-337', 'i', 'B')
          ('171-340', '05 35 17.04', '-05 23 39.75', '171-340', 'i', 'B')
          ('171-434', '05 35 17.11', '-05 24 34.40', '171-434', 'i', 'B')
          ('173-341', '05 35 17.32', '-05 23 41.40', '173-341', 'i', 'B')
          ('173-236', '05 35 17.34', '-05 22 35.81', '173-236', 'i', '0')
          ('174-305', '05 35 17.37', '-05 23 04.86', '174-305', 'i', '0')
          ('174-414', '05 35 17.38', '-05 24 13.90', '174-414', 'i', '0')
          ('175-251', '05 35 17.47', '-05 22 51.26', '175-251', 'i', 'B')
          ('175-355', '05 35 17.54', '-05 23 55.05', '175-355', 'i', '0')
          ('175-543', '05 35 17.54', '-05 25 42.89', '175-543', 'i', 'J,EO,B')
          ('176-325', '05 35 17.55', '-05 23 24.96', '176-325', 'i', '0')
          ('176-252', '05 35 17.64', '-05 22 51.66', '176-252', 'i', '0')
          ('177-341W', '05 35 17.66', '-05 23 41.00', '177-341', 'i', 'B')
          ('177-454', '05 35 17.69', '-05 24 54.10', '177-454', 'i', '0')
          ('177-541', '05 35 17.71', '-05 25 40.76', '0', 'i', 'EO,B')
          ('177-444', '05 35 17.73', '-05 24 43.75', '177-444', 'i', '0')
          ('177-341E', '05 35 17.73', '-05 23 41.10', '177-341', 'i', 'B')
          ('178-441', '05 35 17.81', '-05 24 41.05', '0', 'i', '0')
          ('178-258', '05 35 17.84', '-05 22 58.15', '0', 'i', '0')
          ('179-056', '05 35 17.92', '-05 20 55.44', '179-056', 'i', 'B')
          ('179-354', '05 35 17.96', '-05 23 53.50', '179-354', 'i', '0')
          ('180-331', '05 35 18.03', '-05 23 30.80', '180-331', 'i', 'B')
          ('181-247', '05 35 18.08', '-05 22 47.10', '181-247', 'i', 'B')
          ('181-825', '05 35 18.10', '-05 28 25.04', '0', 'i', 'RN')
          ('182-413', '05 35 18.22', '-05 24 13.45', '182-413', 'i', '0')
          ('183-439', '05 35 18.28', '-05 24 38.85', '183-439', 'i', 'B')
          ('183-419', '05 35 18.31', '-05 24 18.85', '183-419', 'i', '0')
          ('184-427', '05 35 18.35', '-05 24 26.85', '184-427', 'i', 'B')
          ('184-520', '05 35 18.44', '-05 25 19.29', '184-520', 'i', '0')
          ('187-314', '05 35 18.68', '-05 23 14.01', '187-314', 'i', 'B')
          ('189-329', '05 35 18.87', '-05 23 28.85', '189-329', 'i', '0')
          ('190-251', '05 35 19.03', '-05 22 50.65', '0', 'i', 'B')
          ('191-350', '05 35 19.06', '-05 23 49.50', '191-350', 'i', 'J')
          ('197-427', '05 35 19.65', '-05 24 26.70', '197-427', 'i', 'RN')
          ('198-222', '05 35 19.82', '-05 22 21.55', '198-222', 'i', '0')
          ('198-448', '05 35 19.83', '-05 24 47.95', '198-448', 'i', '0')
          ('199-1508', '05 35 19.89', '-05 15 08.25', '0', 'i', 'B')
          ('200-106', '05 35 20.04', '-05 21 05.99', '200-106', 'i', '0')
          ('201-534', '05 35 20.14', '-05 25 33.84', '201-534', 'i', '0')
          ('202-228', '05 35 20.15', '-05 22 28.30', '202-228', 'i', 'B')
          ('203-504', '05 35 20.26', '-05 25 04.05', '203-504', 'i', 'B')
          ('205-330', '05 35 20.45', '-05 23 29.96', '205-330', 'i', 'B')
          ('205-052', '05 35 20.52', '-05 20 52.05', '205-052', 'i', '0')
          ('205-421', '05 35 20.53', '-05 24 21.00', '205-421', 'i', 'FO')
          ('206-446', '05 35 20.62', '-05 24 46.45', '206-446', 'i', '0')
          ('209-151', '05 35 21.00', '-05 21 52.30', '209-151', 'i', 'B')
          ('210-225', '05 35 21.03', '-05 22 25.20', '0', 'i', '0')
          ('212-557', '05 35 21.15', '-05 25 57.04', '212-557', 'i', '0')
          ('212-400', '05 35 21.19', '-05 24 00.20', '0', 'i', '0')
          ('212-260', '05 35 21.24', '-05 22 59.51', '212-260', 'i', '0')
          ('213-533', '05 35 21.28', '-05 25 33.11', '0', 'i', 'B')
          ('213-346', '05 35 21.30', '-05 23 46.10', '0', 'i', 'B')
          ('215-652', '05 35 21.45', '-05 26 52.40', '0', 'i', '0')
          ('215-317', '05 35 21.49', '-05 23 16.71', '215-317', 'i', '0')
          ('215-106', '05 35 21.55', '-05 21 05.60', '215-106', 'i', 'J')
          ('216-541', '05 35 21.60', '-05 25 40.70', '0', 'i', '0')
          ('216-715', '05 35 21.62', '-05 27 14.65', '216-715', 'i', '0')
          ('218-339', '05 35 21.77', '-05 23 39.30', '218-339', 'i', '0')
          ('218-529', '05 35 21.82', '-05 25 28.46', '0', 'i', 'B')
          ('218-306', '05 35 21.84', '-05 23 06.46', '0', 'i', 'B')
          ('221-433', '05 35 22.08', '-05 24 32.95', '221-433', 'i', '0')
          ('223-414', '05 35 22.31', '-05 24 14.25', '223-414', 'i', 'B')
          ('224-728', '05 35 22.37', '-05 27 28.40', '224-728', 'i', '0')
          ('228-548', '05 35 22.83', '-05 25 47.69', '228-548', 'i', '0')
          ('231-460', '05 35 23.05', '-05 24 59.86', '231-460', 'i', '0')
          ('231-502', '05 35 23.16', '-05 25 02.19', '231-502', 'i', 'B')
          ('231-838', '05 35 23.10', '-05 28 37.34', '231-838', 'i', 'J')
          ('232-453', '05 35 23.22', '-05 24 52.79', '232-453', 'i', '0')
          ('234-853', '05 35 23.40', '-05 28 53.19', '0', 'i', '0')
          ('236-527', '05 35 23.59', '-05 25 26.54', '236-527', 'i', '0')
          ('237-627', '05 35 23.66', '-05 26 27.15', '237-627', 'i', '0')
          ('238-334', '05 35 23.80', '-05 23 34.30', '238-334', 'i', 'B')
          ('239-510', '05 35 23.98', '-05 25 09.94', '239-510', 'i', '0')
          ('240-314', '05 35 24.02', '-05 23 13.85', '240-314', 'i', 'B')
          ('242-519', '05 35 24.22', '-05 25 18.79', '242-519', 'i', '0')
          ('244-440', '05 35 24.38', '-05 24 39.74', '244-440', 'i', '0')
          ('245-632', '05 35 24.45', '-05 26 31.55', '245-632', 'i', 'B')
          ('245-1910', '05 35 24.48', '-05 19 09.84', '0', 'i', 'RN,B')
          ('245-502', '05 35 24.51', '-05 25 01.59', '245-502', 'i', '0')
          ('247-436', '05 35 24.69', '-05 24 35.74', '247-436', 'i', 'J')
          ('250-439', '05 35 25.02', '-05 24 38.49', '250-439', 'i', '0')
          ('252-457', '05 35 25.21', '-05 24 57.34', '252-457', 'i', '0')
          ('254-412', '05 35 25.37', '-05 24 11.50', '254-412', 'i', '0')
          ('255-512', '05 35 25.52', '-05 25 11.84', '0', 'i', '0')
          ('262-521', '05 35 26.18', '-05 25 20.49', '262-521', 'i', '0')
          ('264-532', '05 35 26.42', '-05 25 31.69', '264-532', 'i', '0')
          ('266-558', '05 35 26.62', '-05 25 57.84', '0', 'i', '0')
          ('280-931', '05 35 27.96', '-05 29 31.15', '0', 'i', '0')
          ('282-458', '05 35 28.20', '-05 24 58.19', '282-458', 'i', 'J')
          ('282-614', '05 35 28.20', '-05 26 14.20', '0', 'i', '0')
          ('284-439', '05 35 28.40', '-05 24 38.69', '0', 'i', '0')
          ('297-025', '05 35 29.67', '-05 30 24.75', '0', 'i', '0')
          ('304-539', '05 35 30.41', '-05 25 38.63', '304-539', 'i', '0')
          ('307-1807', '05 35 30.70', '-05 18 07.24', '307-1807', 'i', '0')
          ('314-816', '05 35 31.40', '-05 28 16.48', '0', 'i', '0')
          ('332-1605', '05 35 33.20', '-05 16 05.38', '332-1605', 'i', '0')
          ('351-3349', '05 35 35.13', '-05 33 49.18', '0', 'i', 'J')],
                      mask = [(False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)
          (False, False, False, False, False, False)],
                fill\_value = ('N/A', 'N/A', 'N/A', 'N/A', 'N/', 'N/A'),
                     dtype = [('Name', '<U8'), ('RAJ2000', '<U11'), ('DEJ2000', '<U12'), ('[OW94]', '<U8'), ('Type', '<U2'), ('Note', '<U6')])
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}12}]:} \PY{k}{print}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Number of bright proplyds:}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n+nb}{len}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of bright proplyds: 178
    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}13}]:} \PY{k+kn}{from} \PY{n+nn}{astropy} \PY{k+kn}{import} \PY{n}{coordinates} \PY{k}{as} \PY{n}{coord}
         \PY{k+kn}{import} \PY{n+nn}{astropy.units} \PY{k+kn}{as} \PY{n+nn}{u}
\end{Verbatim}

    Try out the new coordinates interface.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}14}]:} \PY{n}{c} \PY{o}{=} \PY{n}{coord}\PY{o}{.}\PY{n}{SkyCoord}\PY{p}{(}\PY{n}{ra}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{05 35 33.20}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{dec}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZhy{}05 16 05.38}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{hourangle}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{deg}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
         \PY{n}{c}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}14}]:} <SkyCoord (ICRS): ra=83.88833333333332 deg, dec=-5.268161111111111 deg>
\end{Verbatim}

    Add a column with an astropy \texttt{SkyCoord} instance for each object

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}15}]:} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coord}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{n}{coord}\PY{o}{.}\PY{n}{SkyCoord}\PY{p}{(}\PY{n}{ra}\PY{o}{=}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{RAJ2000}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{dec}\PY{o}{=}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{DEJ2000}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{hourangle}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{deg}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    Find the coordinates of $\theta^1$ Ori C:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}16}]:} \PY{n}{c0} \PY{o}{=} \PY{n}{coord}\PY{o}{.}\PY{n}{get\PYZus{}icrs\PYZus{}coordinates}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{tet01 ori c}\PY{l+s}{\PYZdq{}}\PY{p}{)}
         \PY{n}{c0}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}16}]:} <SkyCoord (ICRS): ra=83.818598977 deg, dec=-5.389680154 deg>
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}17}]:} \PY{n}{c0}\PY{o}{.}\PY{n}{separation}\PY{p}{(}\PY{n}{c}\PY{p}{)}\PY{o}{.}\PY{n}{arcsec}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}17}]:} 503.84327222379954
\end{Verbatim}

    Add another column with the projected separation in arcsec:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{c0}\PY{o}{.}\PY{n}{separation}\PY{p}{(}\PY{n}{c}\PY{p}{)}\PY{o}{.}\PY{n}{arcsec} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coord}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{]}
\end{Verbatim}

    Make a cumulative histogram to compare with the HA98 sample:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}19}]:} (685.54604284372397, 932.10782801757205)
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}257}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{800.0}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{4}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Henney \PYZam{} Arthur 1998}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{md}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dark disks}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{mr}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{g}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Reflec nebs}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{mj}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{m}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Bare jets}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of proplyds with projected distance \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Cumulative distribution of proplyds vs distance: Both samples}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{savefig}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{proplyd\PYZhy{}distance\PYZhy{}distribution.pdf}\PY{l+s}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_47_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    Try it again, but non-cumulative. If the cumulative distribution is
linear in $D'$ then the non-cumulative one should be constant.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}256}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{800.0}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{20}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Henney \PYZam{} Arthur 1998}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{md}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dark disks}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{mr}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{g}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Reflec nebs}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{mj}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{m}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Bare jets}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of proplyds with projected distance \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Distribution of proplyds vs distance: Both samples}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper right}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{12}\PY{p}{,} \PY{l+m+mi}{6}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_49_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    The ultimate tool for plotting a distribution is \texttt{distplot}. This
can show the following if we turn on all the options: 1. A rugplot of
the individual data points 2. A histogram of the distribution 3. The KDE
of the distribution 4. A fit to the distribution of any function from
\texttt{scipy.stats}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}387}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} 
                       \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} 
                       \PY{n}{fit}\PY{o}{=}\PY{n}{stats}\PY{o}{.}\PY{n}{expon}\PY{p}{,} 
                       \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{clip}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{800.0}\PY{p}{)}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{kernel}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{gau}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Gaussian KDE}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{rug\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{alpha}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+m+mf}{0.3}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{fit\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Exponential fit}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{800}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{25}\PY{p}{,}
                       \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Histogram (25 arcsec bins)}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{axlabel}\PY{o}{=}\PY{l+s}{r\PYZdq{}}\PY{l+s}{Projected distance, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{800.0}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Distribution of projected distances for all bright proplyds from Ricci et al. (2008) sample}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n+nb+bp}{None}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_51_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    What I don't like about this is that the KDE is affected by the fact
that there are no points with $D' < 0$. That is why it drops towards
zero. To fix this, we could reflect the dataset about zero and add a
negative mirrored dataset.

Note that \texttt{stats.laplace} is actually a 2-sided explonential. And
it doesn't fit very well. On the other hand, the KDE now looks much
nicer.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}546}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{r\PYZus{}}\PY{p}{[}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{o}{\PYZhy{}}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{]}\PY{p}{,} 
                       \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} 
                       \PY{n}{fit}\PY{o}{=}\PY{n}{stats}\PY{o}{.}\PY{n}{logistic}\PY{p}{,} 
                       \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{kernel}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{gau}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{KDE}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{rug\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{alpha}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+m+mf}{0.3}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{fit\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Sech\PYZhy{}squared fit}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{2}\PY{o}{*}\PY{l+m+mi}{800}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{25}\PY{p}{,}
                       \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Histogram (25 arcsec bins)}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{axlabel}\PY{o}{=}\PY{l+s}{r\PYZdq{}}\PY{l+s}{Projected distance, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{800.0}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Distribution of projected distances for all bright proplyds from Ricci et al. (2008) sample}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n+nb+bp}{None}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_53_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    So now, we will try the same trick on the joint distribution of $D'$ and
$r_0$. This is in a previous section.

    Zooming in on the central part, which is relevant to the bowshocks.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}531}]:} \PY{n}{Dmax} \PY{o}{=} \PY{l+m+mf}{110.0}
          \PY{n}{Dmaxx} \PY{o}{=} \PY{l+m+mf}{800.0}
          \PY{n}{mzoom} \PY{o}{=} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{\PYZlt{}} \PY{n}{Dmax}
          \PY{n}{dataset} \PY{o}{=} \PY{n}{mirrored}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m} \PY{o}{\PYZam{}} \PY{n}{mzoom}\PY{p}{]}\PY{p}{)}\PY{p}{)}
          \PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{(}\PY{n}{dataset}\PY{p}{,}
                       \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} 
                       \PY{n}{fit}\PY{o}{=}\PY{n}{stats}\PY{o}{.}\PY{n}{uniform}\PY{p}{,} 
                       \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{kernel}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{gau}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Gaussian KDE}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{rug\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{alpha}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+m+mf}{0.3}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{fit\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Constant fit}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{hist\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{range}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{Dmaxx}\PY{p}{,} \PY{n}{Dmaxx}\PY{p}{)}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{Dmaxx}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{10}\PY{p}{,}
                       \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Histogram (10 arcsec bins)}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{axlabel}\PY{o}{=}\PY{l+s}{r\PYZdq{}}\PY{l+s}{Projected distance, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{100.0}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Distribution of projected distances for all bright proplyds from Ricci et al. (2008) sample}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{;}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_56_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    So this suggests that at scales $< 100''$ the proplyd distribution is
uniform (implying density $\sim D^{-2}$.

Whereas at larger scales it does fall off.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}532}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{kdeplot}\PY{err}{?}
\end{Verbatim}

    \subsubsection{What about the stars?}\label{what-about-the-stars}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}21}]:} \PY{n}{sdata} \PY{o}{=} \PY{n}{Table}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd\PYZhy{}Datasets/Robberto2013/table5.dat}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{format}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{ascii}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}22}]:} \PY{n}{sdata}\PY{o}{.}\PY{n}{colnames}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}22}]:} ['Seq',
          'oncacs',
          'RAh',
          'RAm',
          'RAs',
          'DE-',
          'DEd',
          'DEm',
          'DEs',
          'visit',
          'CCD',
          'x435',
          'x555',
          'x658',
          'x775',
          'x850',
          'y435',
          'y555',
          'y658',
          'y775',
          'y850',
          'F435mag',
          'e\_F435mag',
          'f\_F435mag',
          'F555mag',
          'e\_F555mag',
          'f\_F555mag',
          'F658mag',
          'e\_F658mag',
          'f\_F658mag',
          'F775mag',
          'e\_F775mag',
          'f\_F775mag',
          'F850mag',
          'e\_F850mag',
          'f\_F850mag',
          'rad435',
          'rad555',
          'rad658',
          'rad775',
          'rad850',
          'csky435',
          'csky555',
          'csky658',
          'csky775',
          'csky850',
          'e\_csky435',
          'e\_csky555',
          'e\_csky658',
          'e\_csky775',
          'e\_csky850',
          'isky435',
          'isky555',
          'isky658',
          'isky775',
          'isky850',
          'osky435',
          'osky555',
          'osky658',
          'osky775',
          'osky850',
          'max435',
          'max555',
          'max658',
          'max775',
          'max850',
          'pixsat435',
          'pixsat555',
          'pixsat658',
          'pixsat775',
          'pixsat850',
          'radsat435',
          'radsat555',
          'radsat658',
          'radsat775',
          'radsat850',
          'type',
          'strip',
          'xstrip',
          'ystrip',
          'F435smag',
          'F555smag',
          'F658smag',
          'F775smag',
          'F850smag',
          'e\_F435smag',
          'e\_F555smag',
          'e\_F658smag',
          'e\_F775smag',
          'e\_F850smag',
          'rad435s',
          'rad555s',
          'rad658s',
          'rad775s',
          'rad850s',
          'sky435s',
          'sky555s',
          'sky658s',
          'sky775s',
          'sky850s',
          'dsky435s',
          'dksy555s',
          'dsky658s',
          'dksy775s',
          'dsky850s',
          'Date',
          'time']
\end{Verbatim}

    We first need to restrict the table to unique sources, since it contains
multiple observations of the same source. We can do this by comparing
the first two columns:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}23}]:} \PY{n}{m\PYZus{}uniq} \PY{o}{=} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Seq}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{oncacs}\PY{l+s}{\PYZsq{}}\PY{p}{]}
\end{Verbatim}

    Then winnowing down the table:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}24}]:} \PY{n}{sdata} \PY{o}{=} \PY{n}{sdata}\PY{p}{[}\PY{n}{m\PYZus{}uniq}\PY{p}{]}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}24}]:} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}24}]:} 
\end{Verbatim}

    Description of the \texttt{type} column from notes to Table 5:

\begin{verbatim}
Source type, from visual inspection: (0) not measured; (1) detected in at least one filter and unresolved; (2) double (companion closer than ≈3 pixels, one entry for both sources); (3) wide double (companion further than ≈3 pixel, one entry for each source); (5) silhouette disk; (6) photoionized (proplyd or with other evidence of photoionization); (7) galaxy; (8) Herbig-Haro.
\end{verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}25}]:} \PY{n}{source\PYZus{}types} \PY{o}{=} \PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{not measured}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{single}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{close double}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{wide double}\PY{l+s}{\PYZsq{}}\PY{p}{,} 
                         \PY{l+s}{\PYZsq{}}\PY{l+s}{???}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{disk}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{ionized}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{galaxy}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{herbig haro}\PY{l+s}{\PYZsq{}}\PY{p}{]}
         \PY{n}{count\PYZus{}table} \PY{o}{=} \PY{n}{Table}\PY{p}{(}\PY{n}{names}\PY{o}{=}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Code}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{Type}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{Number}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{,} 
                             \PY{n}{dtype}\PY{o}{=}\PY{p}{[}\PY{n+nb}{int}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{S12}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n+nb}{int}\PY{p}{]}\PY{p}{)}
         \PY{k}{for} \PY{n}{itype}\PY{p}{,} \PY{n}{label} \PY{o+ow}{in} \PY{n+nb}{enumerate}\PY{p}{(}\PY{n}{source\PYZus{}types}\PY{p}{)}\PY{p}{:}
             \PY{n}{count\PYZus{}table}\PY{o}{.}\PY{n}{add\PYZus{}row}\PY{p}{(}\PY{p}{[}\PY{n}{itype}\PY{p}{,} \PY{n}{label}\PY{p}{,} \PY{n}{np}\PY{o}{.}\PY{n}{sum}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{n}{itype}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{n}{count\PYZus{}table}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}25}]:} <Table rows=9 names=('Code','Type','Number')>
         array([(0, b'not measured', 2), (1, b'single', 2912),
                (2, b'close double', 47), (3, b'wide double', 154), (4, b'???', 0),
                (5, b'disk', 36), (6, b'ionized', 184), (7, b'galaxy', 59),
                (8, b'herbig haro', 5)], 
               dtype=[('Code', '<i8'), ('Type', 'S12'), ('Number', '<i8')])
\end{Verbatim}

    The \texttt{ionized} type is ``\emph{proplyd or with other evidence of
photoionization}'' and there are 184 of them, compared with 178 in the
Ricci catalog. This is close enough for me.

    Next job is to winnow out types 0, 7, and 8, which we don't want.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}26}]:} \PY{n}{sdata} \PY{o}{=} \PY{n}{sdata}\PY{p}{[}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{\PYZam{}} \PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{\PYZlt{}} \PY{l+m+mi}{7}\PY{p}{)}\PY{p}{]}
\end{Verbatim}

    And now create a mask to select out the \texttt{ionized} sources (mainly
proplyds).

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}27}]:} \PY{n}{m\PYZus{}rob\PYZus{}ionized} \PY{o}{=} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{type}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{l+m+mi}{6}
\end{Verbatim}

    Now we combine the 6 columns used for coordinates into a single RA-Dec
string:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}28}]:} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coordstring}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZob{}\PYZcb{} \PYZob{}\PYZcb{} \PYZob{}\PYZcb{} \PYZhy{}\PYZob{}\PYZcb{} \PYZob{}\PYZcb{} \PYZob{}\PYZcb{}}\PY{l+s}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{o}{*}\PY{n}{args}\PY{p}{)}
                           \PY{k}{for} \PY{n}{args} \PY{o+ow}{in} \PY{n+nb}{zip}\PY{p}{(}\PY{o}{*}\PY{p}{[}\PY{n}{sdata}\PY{p}{[}\PY{n}{col}\PY{p}{]} \PY{k}{for} \PY{n}{col} \PY{o+ow}{in} \PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{RAh}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{RAm}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{RAs}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{DEd}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{DEm}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{DEs}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{]}\PY{p}{)}\PY{p}{]}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}29}]:} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coordstring}\PY{l+s}{\PYZdq{}}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}29}]:} <MaskedColumn name='coordstring' unit=None format=None description=None>
         masked\_BaseColumn(data = ['5 34 9.889 -5 22 26.26' '5 34 10.25 -5 21 52.29'
          '5 34 11.111 -5 22 54.46' \ldots, '5 35 52.472 -5 38 7.85'
          '5 35 53.093 -5 30 10.38' '5 35 53.504 -5 39 32.88'],
                           mask = [False False False \ldots, False False False],
                     fill\_value = N/A)
\end{Verbatim}

    Then that string can be used to initialize an
\texttt{astropy.coordinates.SkyCoord} instance for each source.

\textbf{Warning:} The following cell takes a couple of minutes to run.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}30}]:} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coord}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{n}{coord}\PY{o}{.}\PY{n}{SkyCoord}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coordstring}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{hourangle}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{deg}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}31}]:} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coord}\PY{l+s}{\PYZdq{}}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}31}]:} <MaskedColumn name='coord' unit=None format=None description=None>
         masked\_BaseColumn(data = [<SkyCoord (ICRS): ra=83.54120416666666 deg, dec=-5.373961111111111 deg>
          <SkyCoord (ICRS): ra=83.54270833333332 deg, dec=-5.3645249999999995 deg>
          <SkyCoord (ICRS): ra=83.54629583333332 deg, dec=-5.381794444444444 deg>
          \ldots,
          <SkyCoord (ICRS): ra=83.96863333333332 deg, dec=-5.635513888888888 deg>
          <SkyCoord (ICRS): ra=83.97122083333332 deg, dec=-5.502883333333333 deg>
          <SkyCoord (ICRS): ra=83.97293333333332 deg, dec=-5.659133333333334 deg>],
                           mask = [False False False \ldots, False False False],
                     fill\_value = ?)
\end{Verbatim}

    And that in turn can be used to find the separation of each source from
$\theta^1$ C.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}32}]:} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{c0}\PY{o}{.}\PY{n}{separation}\PY{p}{(}\PY{n}{c}\PY{p}{)}\PY{o}{.}\PY{n}{arcsec} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{coord}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{]}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}33}]:} \PY{n+nb}{len}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}33}]:} 3333
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}258}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{1200.0}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{4}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ionized, Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Proplyds, Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of stars with projected distance \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Cumulative distribution of stars vs distance: Robberto ACS sample}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_84_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}259}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{1200.0}
          \PY{n}{binsize} \PY{o}{=} \PY{l+m+mi}{25}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}\PY{o}{/}\PY{o}{/}\PY{n}{binsize}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ionized, Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Proplyds, Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of stars with projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ (25 arcsec bins)}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Distribution of stars vs distance: Robberto ACS sample}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper right}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_85_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}554}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{1200.0}
          \PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{(}\PY{n}{mirrored}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,} 
                       \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} 
                       \PY{n}{fit}\PY{o}{=}\PY{n}{stats}\PY{o}{.}\PY{n}{semicircular}\PY{p}{,} 
                       \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{kernel}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{gau}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{KDE}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{rug\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{alpha}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+m+mf}{0.03}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{fit\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Semi\PYZhy{}circular fit}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{rmax}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{25}\PY{p}{,}
                       \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Histogram (25 arcsec bins)}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{axlabel}\PY{o}{=}\PY{l+s}{r\PYZdq{}}\PY{l+s}{Projected distance, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{1200.0}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Distribution of projected distances for all stars from Robberto et al. (2013) sample}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n+nb+bp}{None}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_86_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    Zoom in on inner 200''

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}260}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{200.0}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ionized, Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Proplyds, Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of stars with projected distance \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Cumulative distribution of stars vs distance: Robberto ACS sample}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_88_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    Zoom in on inner 30''

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}261}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{30.0}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ionized, Robberto 2013}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.7}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Proplyds, Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of stars with projected distance \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Cumulative distribution of stars vs distance: Robberto ACS sample}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_90_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsection{Maps of different source
samples}\label{maps-of-different-source-samples}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}51}]:} \PY{n}{rob\PYZus{}ra} \PY{o}{=} \PY{p}{[}\PY{n}{c}\PY{o}{.}\PY{n}{ra}\PY{o}{.}\PY{n}{deg} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{coord}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}
         \PY{n}{rob\PYZus{}dec} \PY{o}{=} \PY{p}{[}\PY{n}{c}\PY{o}{.}\PY{n}{dec}\PY{o}{.}\PY{n}{deg} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{sdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{coord}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}56}]:} \PY{n}{rob\PYZus{}ra} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{rob\PYZus{}ra}\PY{p}{)}
         \PY{n}{rob\PYZus{}dec} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{rob\PYZus{}dec}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}74}]:} \PY{n}{ricci\PYZus{}ra} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{c}\PY{o}{.}\PY{n}{ra}\PY{o}{.}\PY{n}{deg} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{coord}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}\PY{p}{)}
         \PY{n}{ricci\PYZus{}dec} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{c}\PY{o}{.}\PY{n}{dec}\PY{o}{.}\PY{n}{deg} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{coord}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}38}]:} \PY{k+kn}{import} \PY{n+nn}{aplpy}
         \PY{k+kn}{import} \PY{n+nn}{os}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}41}]:} \PY{k+kn}{from} \PY{n+nn}{imp} \PY{k+kn}{import} \PY{n+nb}{reload}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}39}]:} \PY{n}{aplpy}\PY{o}{.}\PY{n}{\PYZus{}\PYZus{}version\PYZus{}\PYZus{}}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}39}]:} '0.9.13.dev310'
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}40}]:} \PY{n}{hstdir} \PY{o}{=} \PY{n}{os}\PY{o}{.}\PY{n}{path}\PY{o}{.}\PY{n}{expanduser}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZti{}/Dropbox/JorgeBowshocks/HST}\PY{l+s}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}105}]:} \PY{n}{fig} \PY{o}{=} \PY{n}{aplpy}\PY{o}{.}\PY{n}{FITSFigure}\PY{p}{(}\PY{n}{os}\PY{o}{.}\PY{n}{path}\PY{o}{.}\PY{n}{join}\PY{p}{(}\PY{n}{hstdir}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{mosaicf656\PYZhy{}fixw\PYZhy{}align.fits}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
          \PY{n}{fig}\PY{o}{.}\PY{n}{show\PYZus{}grayscale}\PY{p}{(}\PY{n}{vmin}\PY{o}{=}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{n}{vmax}\PY{o}{=}\PY{l+m+mf}{5.e3}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
WARNING: Cannot determine equinox. Assuming J2000. [aplpy.wcs\_util]
WARNING:astropy:Cannot determine equinox. Assuming J2000.
WARNING: Cannot determine equinox. Assuming J2000. [aplpy.wcs\_util]
WARNING:astropy:Cannot determine equinox. Assuming J2000.
    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_99_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}108}]:} \PY{n}{fig}\PY{o}{.}\PY{n}{\PYZus{}figure}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{18}\PY{p}{)}
          \PY{n}{fig}\PY{o}{.}\PY{n}{show\PYZus{}markers}\PY{p}{(}\PY{n}{ricci\PYZus{}ra}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{ricci\PYZus{}dec}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{layer}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ricci proplyds}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{edgecolor}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{c}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{lw}\PY{o}{=}\PY{l+m+mi}{3}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.8}\PY{p}{)}
          \PY{n}{fig}\PY{o}{.}\PY{n}{show\PYZus{}markers}\PY{p}{(}\PY{n}{rob\PYZus{}ra}\PY{p}{[}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{rob\PYZus{}dec}\PY{p}{[}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{layer}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Robb proplyds}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{edgecolor}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{orange}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{fig}\PY{o}{.}\PY{n}{show\PYZus{}markers}\PY{p}{(}\PY{n}{rob\PYZus{}ra}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{rob\PYZus{}dec}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{m\PYZus{}rob\PYZus{}ionized}\PY{p}{]}\PY{p}{,} \PY{n}{layer}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Robb non\PYZhy{}proplyds}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{edgecolor}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{*}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{fig}\PY{o}{.}\PY{n}{recenter}\PY{p}{(}\PY{n}{c0}\PY{o}{.}\PY{n}{ra}\PY{o}{.}\PY{n}{deg}\PY{p}{,} \PY{n}{c0}\PY{o}{.}\PY{n}{dec}\PY{o}{.}\PY{n}{deg}\PY{p}{,} \PY{n}{radius}\PY{o}{=}\PY{l+m+mi}{60}\PY{o}{/}\PY{l+m+mi}{3600}\PY{p}{)}
          \PY{n}{ax} \PY{o}{=} \PY{n}{fig}\PY{o}{.}\PY{n}{\PYZus{}figure}\PY{o}{.}\PY{n}{axes}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
          \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{A title}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{fig}\PY{o}{.}\PY{n}{\PYZus{}figure}
\end{Verbatim}
\texttt{\color{outcolor}Out[{\color{outcolor}108}]:}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_100_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    So the conclusion of this section is that the Ricci proplyd catalog
(shown by blue circles on the image above) is more reliable than the
Robberto \texttt{ionized} catalog (shown by orange circles) for the
close-in proplyds. Robberto is missing a lot of obvious proplyds, and
furthermore has a few sources that don't seem to correspond to anything,
although some might be bowshocks or jet knots.

The Ricci catalog is only missing a very few, such as the one very close
to th1c.

    \subsection{Monte Carlo simulations}\label{monte-carlo-simulations}

Assume power law distribution in radius.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}562}]:} \PY{k}{class} \PY{n+nc}{SourcePopulation}\PY{p}{(}\PY{n+nb}{object}\PY{p}{)}\PY{p}{:}

              \PY{k}{def} \PY{n+nf}{\PYZus{}\PYZus{}init\PYZus{}\PYZus{}}\PY{p}{(}\PY{n+nb+bp}{self}\PY{p}{,} \PY{n}{N}\PY{p}{,} \PY{n}{Dmin}\PY{o}{=}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{n}{Dmax}\PY{o}{=}\PY{l+m+mf}{800.0}\PY{p}{,} \PY{n}{m}\PY{o}{=}\PY{l+m+mf}{2.6}\PY{p}{)}\PY{p}{:}
                  \PY{l+s+sd}{\PYZdq{}\PYZdq{}\PYZdq{}Return `N` samples of sources drawn from a radial distribution with density \PYZti{} D\PYZca{}\PYZhy{}m}
          \PY{l+s+sd}{        Maximum and minimum radii can be specified with `Dmin` and `Dmax`. }
          \PY{l+s+sd}{        If `Dmin = 0` then `m \PYZlt{} 3` is required.\PYZdq{}\PYZdq{}\PYZdq{}}
                  \PY{k}{assert}\PY{p}{(}\PY{n}{m} \PY{o}{\PYZlt{}} \PY{l+m+mi}{3}\PY{p}{)}

                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{N} \PY{o}{=} \PY{n}{N}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{m} \PY{o}{=} \PY{n}{m}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{Dmin} \PY{o}{=} \PY{n}{Dmin}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{Dmax} \PY{o}{=} \PY{n}{Dmax}

                  \PY{c}{\PYZsh{} Radial distances from center}
                  \PY{n}{xi} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{random\PYZus{}sample}\PY{p}{(}\PY{p}{(}\PY{n}{N}\PY{p}{,}\PY{p}{)}\PY{p}{)}
                  \PY{n}{x0} \PY{o}{=} \PY{n}{Dmin}\PY{o}{/}\PY{n}{Dmax}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{D} \PY{o}{=} \PY{n}{Dmax}\PY{o}{*}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{1} \PY{o}{\PYZhy{}} \PY{n}{x0}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{l+m+mf}{3.0} \PY{o}{\PYZhy{}} \PY{n}{m}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{xi} \PY{o}{+} \PY{n}{x0}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{l+m+mf}{3.0} \PY{o}{\PYZhy{}} \PY{n}{m}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{l+m+mf}{1.0}\PY{o}{/}\PY{p}{(}\PY{l+m+mf}{3.0} \PY{o}{\PYZhy{}} \PY{n}{m}\PY{p}{)}\PY{p}{)}
                  \PY{c}{\PYZsh{} Angle cosine with LOS}
                  \PY{n}{xi} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{random\PYZus{}sample}\PY{p}{(}\PY{p}{(}\PY{n}{N}\PY{p}{,}\PY{p}{)}\PY{p}{)}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{mu} \PY{o}{=} \PY{l+m+mi}{2}\PY{o}{*}\PY{n}{xi} \PY{o}{\PYZhy{}} \PY{l+m+mf}{1.0}
                  \PY{c}{\PYZsh{} Position angle}
                  \PY{n}{xi} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{random\PYZus{}sample}\PY{p}{(}\PY{p}{(}\PY{n}{N}\PY{p}{,}\PY{p}{)}\PY{p}{)}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{PA} \PY{o}{=} \PY{l+m+mf}{360.0}\PY{o}{*}\PY{n}{xi}

                  \PY{c}{\PYZsh{} Inclination to plane of sky inc = [\PYZhy{}90:90]}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{inc} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{degrees}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{arcsin}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{mu}\PY{p}{)}\PY{p}{)}

                  \PY{c}{\PYZsh{} Projected distance}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{Dprime} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{D}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{l+m+mf}{1.0} \PY{o}{\PYZhy{}} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{mu}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}

                  \PY{c}{\PYZsh{} Plane\PYZhy{}of\PYZhy{}sky coords}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{Dec} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{Dprime}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{cos}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{radians}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{PA}\PY{p}{)}\PY{p}{)}
                  \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{RA} \PY{o}{=} \PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{Dprime}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sin}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{radians}\PY{p}{(}\PY{n+nb+bp}{self}\PY{o}{.}\PY{n}{PA}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}662}]:} \PY{n}{p} \PY{o}{=} \PY{n}{SourcePopulation}\PY{p}{(}\PY{l+m+mi}{150}\PY{p}{,} \PY{n}{m}\PY{o}{=}\PY{l+m+mf}{2.1}\PY{p}{,} \PY{n}{Dmin}\PY{o}{=}\PY{l+m+mf}{5.0}\PY{p}{,} \PY{n}{Dmax}\PY{o}{=}\PY{l+m+mf}{250.0}\PY{p}{)}
          \PY{n}{p2} \PY{o}{=} \PY{n}{SourcePopulation}\PY{p}{(}\PY{l+m+mi}{30}\PY{p}{,} \PY{n}{m}\PY{o}{=}\PY{l+m+mf}{2.5}\PY{p}{,} \PY{n}{Dmin}\PY{o}{=}\PY{l+m+mf}{150.0}\PY{p}{,} \PY{n}{Dmax}\PY{o}{=}\PY{l+m+mf}{800.0}\PY{p}{)}
          \PY{n}{Dprimes} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{r\PYZus{}}\PY{p}{[}\PY{n}{p}\PY{o}{.}\PY{n}{Dprime}\PY{p}{,} \PY{n}{p2}\PY{o}{.}\PY{n}{Dprime}\PY{p}{]}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}663}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{800.0}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{4}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{Dprimes}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{Fake sample}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{c}{\PYZsh{} \PYZus{} = plt.hist(p.Dprime, bins=nbins, range=(0, rmax), cumulative=True, color=\PYZsq{}g\PYZsq{}, alpha=0.3, label=\PYZsq{}p\PYZsq{})}
          \PY{c}{\PYZsh{} \PYZus{} = plt.hist(p2.Dprime, bins=nbins, range=(0, rmax), cumulative=True, color=\PYZsq{}y\PYZsq{}, alpha=0.8, label=\PYZsq{}p2\PYZsq{})}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of proplyds with projected distance \PYZlt{} D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Cumulative distribution of proplyds vs distance: Both samples}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_105_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}250}]:} \PY{k+kn}{import} \PY{n+nn}{seaborn}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}251}]:} \PY{n}{cmap} \PY{o}{=} \PY{n}{seaborn}\PY{o}{.}\PY{n}{palettes}\PY{o}{.}\PY{n}{dark\PYZus{}palette}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{red}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{as\PYZus{}cmap}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}664}]:} \PY{n}{rmax} \PY{o}{=} \PY{l+m+mf}{800.0}
          \PY{n}{nbins} \PY{o}{=} \PY{n}{rmax}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{25}
          \PY{n}{datasets} \PY{o}{=} \PY{p}{[}\PY{n}{rdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{[}\PY{n}{m}\PY{p}{]}\PY{p}{,} \PY{n}{Dprimes}\PY{p}{,} \PY{n}{p}\PY{o}{.}\PY{n}{Dprime}\PY{p}{,} \PY{n}{p2}\PY{o}{.}\PY{n}{Dprime}\PY{p}{]}
          \PY{n}{colors} \PY{o}{=} \PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{g}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{y}\PY{l+s}{\PYZsq{}}\PY{p}{]}
          \PY{n}{labels} \PY{o}{=} \PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Ricci 2008}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{Fake sample}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{p}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{p2}\PY{l+s}{\PYZsq{}}\PY{p}{]}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{datasets}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{3}\PY{p}{]}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{n}{nbins}\PY{p}{,} \PY{n+nb}{range}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n}{rmax}\PY{p}{)}\PY{p}{,} \PY{n}{cumulative}\PY{o}{=}\PY{n+nb+bp}{False}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n+nb+bp}{None}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{n}{labels}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{3}\PY{p}{]}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Projected distance D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{, arcsec}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZsh{} of proplyds with projected distance = D}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s}{ (bin width 25 arcsec)}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Distribution of proplyds vs distance: Both samples}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{upper right}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{gcf}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{set\PYZus{}size\PYZus{}inches}\PY{p}{(}\PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{8}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_108_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}665}]:} \PY{n}{Dmax} \PY{o}{=} \PY{l+m+mf}{110.0}
          \PY{n}{Dmaxx} \PY{o}{=} \PY{l+m+mf}{800.0}
          \PY{n}{mzoom} \PY{o}{=} \PY{n}{Dprimes} \PY{o}{\PYZlt{}} \PY{n}{Dmax}
          \PY{n}{dataset} \PY{o}{=} \PY{n}{mirrored}\PY{p}{(}\PY{n}{Dprimes}\PY{p}{[}\PY{n}{mzoom}\PY{p}{]}\PY{p}{)}
          \PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{(}\PY{n}{dataset}\PY{p}{,}
                       \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} 
                       \PY{n}{fit}\PY{o}{=}\PY{n}{stats}\PY{o}{.}\PY{n}{uniform}\PY{p}{,} 
                       \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{kernel}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{gau}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Gaussian KDE}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,} 
                       \PY{n}{rug\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{alpha}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+m+mf}{0.3}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{fit\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{label}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{l+s}{\PYZdq{}}\PY{l+s}{Constant fit}\PY{l+s}{\PYZdq{}}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{hist\PYZus{}kws}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{range}\PY{l+s}{\PYZdq{}}\PY{p}{:} \PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{Dmaxx}\PY{p}{,} \PY{n}{Dmaxx}\PY{p}{)}\PY{p}{\PYZcb{}}\PY{p}{,}
                       \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{Dmaxx}\PY{o}{/}\PY{o}{/}\PY{l+m+mi}{10}\PY{p}{,}
                       \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Histogram (10 arcsec bins)}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{axlabel}\PY{o}{=}\PY{l+s}{r\PYZdq{}}\PY{l+s}{Projected distance, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{100.0}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Distribution of projected distances from Monta Carlo fake sample}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{;}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_109_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsubsection{Compare the projected separation and the inclination for
the inner 30 arcsec of the MC
sample}\label{compare-the-projected-separation-and-the-inclination-for-the-inner-30-arcsec-of-the-mc-sample}

Assume that the inner wind shock lies at about $D = 26''$. Only proplyds
that are physically clser than this will have Type I bowshocks. These
are shown by orange points in the figure. Physically more distant
proplyds are shown by gray points. We also show contours of physical
separation every $10''$ from $D = 10''$ to $D = 200''$.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}674}]:} \PY{n}{color} \PY{o}{=} \PY{l+s}{\PYZdq{}}\PY{l+s}{.5}\PY{l+s}{\PYZdq{}}
          \PY{n}{m30} \PY{o}{=} \PY{n}{p}\PY{o}{.}\PY{n}{Dprime} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{l+m+mf}{30.0}
          \PY{n}{Dmax} \PY{o}{=} \PY{l+m+mf}{26.0}
          \PY{n}{mwind} \PY{o}{=} \PY{n}{p}\PY{o}{.}\PY{n}{D} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{Dmax}
          \PY{n}{g} \PY{o}{=} \PY{n}{sns}\PY{o}{.}\PY{n}{JointGrid}\PY{p}{(}\PY{n}{mirrored}\PY{p}{(}\PY{n}{p}\PY{o}{.}\PY{n}{Dprime}\PY{p}{[}\PY{n}{m30}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{np}\PY{o}{.}\PY{n}{r\PYZus{}}\PY{p}{[}\PY{n}{p}\PY{o}{.}\PY{n}{inc}\PY{p}{[}\PY{n}{m30}\PY{p}{]}\PY{p}{,} \PY{n}{p}\PY{o}{.}\PY{n}{inc}\PY{p}{[}\PY{n}{m30}\PY{p}{]}\PY{p}{]}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{9}\PY{p}{,} \PY{n}{xlim}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{30}\PY{p}{)}\PY{p}{,} \PY{n}{ylim}\PY{o}{=}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{90}\PY{p}{,} \PY{l+m+mi}{90}\PY{p}{)}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{plot\PYZus{}marginals}\PY{p}{(}\PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{,} \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} 
                           \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{n+nb}{dict}\PY{p}{(}\PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{KDE}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{bw}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{silverman}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{cut}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}\PY{p}{)}
          \PY{c}{\PYZsh{}g.plot\PYZus{}joint(sns.regplot, color=color, fit\PYZus{}reg=False, scatter\PYZus{}kws=dict(s=50))}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{p}\PY{o}{.}\PY{n}{Dprime}\PY{p}{[}\PY{n}{mwind}\PY{p}{]}\PY{p}{,} \PY{n}{p}\PY{o}{.}\PY{n}{inc}\PY{p}{[}\PY{n}{mwind}\PY{p}{]}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{o}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{c}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{orange}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{50}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{D \PYZlt{} \PYZob{}\PYZcb{}}\PY{l+s}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{Dmax}\PY{p}{)}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{p}\PY{o}{.}\PY{n}{Dprime}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{mwind}\PY{p}{]}\PY{p}{,} \PY{n}{p}\PY{o}{.}\PY{n}{inc}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{mwind}\PY{p}{]}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{o}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{c}\PY{o}{=}\PY{n}{color}\PY{p}{,} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{50}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{D \PYZgt{} \PYZob{}\PYZcb{}}\PY{l+s}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{Dmax}\PY{p}{)}\PY{p}{)}
          \PY{n}{inc\PYZus{}pts} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mf}{90.0}\PY{p}{,} \PY{l+m+mf}{90.0}\PY{p}{)}
          \PY{n}{Dprime\PYZus{}pts} \PY{o}{=} \PY{n}{Dmax}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{cos}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{radians}\PY{p}{(}\PY{n}{inc\PYZus{}pts}\PY{p}{)}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{Dprime\PYZus{}pts}\PY{p}{,} \PY{n}{inc\PYZus{}pts}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZhy{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{k}{for} \PY{n}{D} \PY{o+ow}{in} \PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{l+m+mi}{10}\PY{p}{,} \PY{l+m+mi}{200}\PY{p}{,} \PY{l+m+mi}{10}\PY{p}{)}\PY{p}{:}
              \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{Dprime\PYZus{}pts}\PY{o}{*}\PY{n}{D}\PY{o}{/}\PY{n}{Dmax}\PY{p}{,} \PY{n}{inc\PYZus{}pts}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZhy{}}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{k}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{lw}\PY{o}{=}\PY{l+m+mf}{0.5}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.3}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper center}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{frameon}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{shadow}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Projected separation, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Inclination, degrees}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}marg\PYZus{}x}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper right}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}marg\PYZus{}y}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{best}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{fig}\PY{o}{.}\PY{n}{tight\PYZus{}layout}\PY{p}{(}\PY{p}{)}
          \PY{c}{\PYZsh{}g.fig.savefig(\PYZdq{}proplyd\PYZhy{}joint\PYZhy{}separation\PYZhy{}size.pdf\PYZdq{});}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_111_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsubsection{Distribution of sizes}\label{distribution-of-sizes}

    Read in the size table that I converted from the DS9 regions.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}874}]:} \PY{n}{sizedata} \PY{o}{=} \PY{n}{Table}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd\PYZhy{}Datasets/proplyd\PYZhy{}chords\PYZhy{}D60.dat}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{format}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{ascii.commented\PYZus{}header}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{sizedata}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{4}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}874}]:} <Table rows=4 names=('ID','RA1','DEC1','RA2','DEC2')>
          array([('154-240', '5:35:15.394', '-5:22:39.61', '5:35:15.354', '-5:22:39.71'),
                 ('163-249', '5:35:16.340', '-5:22:48.79', '5:35:16.324', '-5:22:48.80'),
                 ('165-235S', '5:35:16.487', '-5:22:35.29', '5:35:16.458', '-5:22:35.22'),
                 ('165-235N', '5:35:16.488', '-5:22:34.97', '5:35:16.479', '-5:22:34.97')], 
                dtype=[('ID', '<U8'), ('RA1', '<U11'), ('DEC1', '<U11'), ('RA2', '<U11'), ('DEC2', '<U11')])
\end{Verbatim}

    Create \texttt{coord.SkyCoord} objects for the two ends of the chord
that I measured at the back of each proplyd's head. Then use those to
find the chord diameter in arcsec (\texttt{Chord} column), and then
convert to a radius in units of $10^{14}$ cm (\texttt{r14} column).

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}875}]:} \PY{n}{coords1} \PY{o}{=} \PY{n}{coord}\PY{o}{.}\PY{n}{SkyCoord}\PY{p}{(}\PY{n}{ra}\PY{o}{=}\PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{RA1}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{dec}\PY{o}{=}\PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{DEC1}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{hourangle}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{deg}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
          \PY{n}{coords2} \PY{o}{=} \PY{n}{coord}\PY{o}{.}\PY{n}{SkyCoord}\PY{p}{(}\PY{n}{ra}\PY{o}{=}\PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{RA2}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{dec}\PY{o}{=}\PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{DEC2}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{hourangle}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{deg}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
          \PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Chord}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{c1}\PY{o}{.}\PY{n}{separation}\PY{p}{(}\PY{n}{c2}\PY{p}{)}\PY{o}{.}\PY{n}{arcsec} \PY{k}{for} \PY{n}{c1}\PY{p}{,} \PY{n}{c2} \PY{o+ow}{in} \PY{n+nb}{zip}\PY{p}{(}\PY{n}{coords1}\PY{p}{,} \PY{n}{coords2}\PY{p}{)}\PY{p}{]}
          \PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{l+m+mf}{0.5} \PY{o}{*} \PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Chord}\PY{l+s}{\PYZdq{}}\PY{p}{]} \PY{o}{*} \PY{l+m+mi}{430}\PY{o}{*}\PY{n}{u}\PY{o}{.}\PY{n}{AU}\PY{o}{.}\PY{n}{in\PYZus{}units}\PY{p}{(}\PY{n}{u}\PY{o}{.}\PY{n}{cm}\PY{p}{)}\PY{o}{/}\PY{l+m+mf}{1.e14}
          \PY{n}{sizedata}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{4}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}875}]:} <Table rows=4 names=('ID','RA1','DEC1','RA2','DEC2','Chord','r14')>
          array([ ('154-240', '5:35:15.394', '-5:22:39.61', '5:35:15.354', '-5:22:39.71', 0.6056714671056789, 19.48053979189225),
                 ('163-249', '5:35:16.340', '-5:22:48.79', '5:35:16.324', '-5:22:48.80', 0.23915181790427623, 7.691969587490479),
                 ('165-235S', '5:35:16.487', '-5:22:35.29', '5:35:16.458', '-5:22:35.22', 0.4387068370843108, 14.11036586820911),
                 ('165-235N', '5:35:16.488', '-5:22:34.97', '5:35:16.479', '-5:22:34.97', 0.13440609108383775, 4.322975982579263)], 
                dtype=[('ID', '<U8'), ('RA1', '<U11'), ('DEC1', '<U11'), ('RA2', '<U11'), ('DEC2', '<U11'), ('Chord', '<f8'), ('r14', '<f8')])
\end{Verbatim}

    Take the average of the RA and DEC components of the two ends of the
chord to get an average coordinate (\texttt{coords0}) for each source.
\textbf{Note: This will not quite be the center of the proplyd, but it
is close enough.}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}876}]:} \PY{n}{coords0} \PY{o}{=} \PY{n}{coord}\PY{o}{.}\PY{n}{SkyCoord}\PY{p}{(}\PY{n}{ra}\PY{o}{=}\PY{l+m+mf}{0.5}\PY{o}{*}\PY{p}{(}\PY{n}{coords1}\PY{o}{.}\PY{n}{ra} \PY{o}{+} \PY{n}{coords2}\PY{o}{.}\PY{n}{ra}\PY{p}{)}\PY{p}{,} \PY{n}{dec}\PY{o}{=}\PY{l+m+mf}{0.5}\PY{o}{*}\PY{p}{(}\PY{n}{coords1}\PY{o}{.}\PY{n}{dec} \PY{o}{+} \PY{n}{coords2}\PY{o}{.}\PY{n}{dec}\PY{p}{)}\PY{p}{)}
          \PY{n}{coords0}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{4}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}876}]:} <SkyCoord (ICRS): (ra, dec) in deg
              [(83.81405833333332, -5.377683333333333),
               (83.81804999999999, -5.380220833333333),
               (83.81863541666667, -5.376459722222222),
               (83.81868124999998, -5.3763805555555555)]>
\end{Verbatim}

    Remove the columns with the chord end coordinates because we don't need
them any more.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}877}]:} \PY{n}{sizedata}\PY{o}{.}\PY{n}{remove\PYZus{}columns}\PY{p}{(}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{RA1}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{RA2}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{DEC1}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{l+s}{\PYZdq{}}\PY{l+s}{DEC2}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{)}
          \PY{n}{sizedata}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{4}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}877}]:} <Table rows=4 names=('ID','Chord','r14')>
          array([('154-240', 0.6056714671056789, 19.48053979189225),
                 ('163-249', 0.23915181790427623, 7.691969587490479),
                 ('165-235S', 0.4387068370843108, 14.11036586820911),
                 ('165-235N', 0.13440609108383775, 4.322975982579263)], 
                dtype=[('ID', '<U8'), ('Chord', '<f8'), ('r14', '<f8')])
\end{Verbatim}

    Add some more columns:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{RA} and \texttt{Dec} corresponding to \texttt{coords0}
\item
  Projected distance \texttt{Dprime} from th1C (in arcsec)
\item
  Position angle \texttt{PA} from th1C (in degrees).
\end{itemize}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}878}]:} \PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{RA}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{coords0}\PY{o}{.}\PY{n}{ra}\PY{o}{.}\PY{n}{to\PYZus{}string}\PY{p}{(}\PY{n}{unit}\PY{o}{=}\PY{n}{u}\PY{o}{.}\PY{n}{hourangle}\PY{p}{,} \PY{n}{sep}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{:}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dec}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{coords0}\PY{o}{.}\PY{n}{dec}\PY{o}{.}\PY{n}{to\PYZus{}string}\PY{p}{(}\PY{n}{sep}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{:}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{c0}\PY{o}{.}\PY{n}{separation}\PY{p}{(}\PY{n}{coords0}\PY{p}{)}\PY{o}{.}\PY{n}{arcsec}
          \PY{n}{sizedata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{PA}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{c0}\PY{o}{.}\PY{n}{position\PYZus{}angle}\PY{p}{(}\PY{n}{coords0}\PY{p}{)}\PY{o}{.}\PY{n}{deg}
          \PY{n}{sizedata}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{4}\PY{p}{:}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}878}]:} <Table rows=4 names=('ID','Chord','r14','RA','Dec','Dprime','PA')>
          array([ ('163-323', 0.1011089261716131, 3.2520212137679168, '5:35:16.3125', '-5:23:22.6', 2.272420836013117, 276.2794710623649),
                 ('153-321', 0.08000000000590013, 2.573083376229769, '5:35:15.342', '-5:23:21.31', 16.82243690794256, 275.2472980493684),
                 ('167-231', 0.32854879080509697, 10.567292897982984, '5:35:16.728', '-5:22:31.18', 51.8190317547333, 4.367559662217565),
                 ('171-334', 0.20948633602138664, 6.737822609051992, '5:35:17.0625', '-5:23:34.115', 14.383406373150356, 141.56334754726322)], 
                dtype=[('ID', '<U8'), ('Chord', '<f8'), ('r14', '<f8'), ('RA', 'O'), ('Dec', 'O'), ('Dprime', '<f8'), ('PA', '<f8')])
\end{Verbatim}

    \begin{center}\rule{3in}{0.4pt}\end{center}

Now we try and merge in the HA98 table.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}747}]:} \PY{k+kn}{from} \PY{n+nn}{astropy.table} \PY{k+kn}{import} \PY{n}{join}\PY{p}{,} \PY{n}{Column}
\end{Verbatim}

    First naive attempt was a straight outer join on the \texttt{ID} column.
This gave some objects that are in the HA98 table but not in the new
data. Of these, 244-440 is OK, since it is outside our distance cut-off,
but the others need fixing. 177-341 (not in Ricci catalog) is just a
matter of the name, which should be 177-341W. There were also two really
missing: 171-334 and 154-324 (my typo).

So we need to fix things up. First make the \texttt{ID} field in the
HA98 table wider and fix the name of 177-341W.

\emph{This took much longer than it should have done. It turns out that
you can't change the dtype of a column without making a new table}.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}798}]:} \PY{n}{data} \PY{o}{=} \PY{n}{Table}\PY{p}{(}\PY{n}{data}\PY{p}{,} \PY{n}{names}\PY{o}{=}\PY{n}{data}\PY{o}{.}\PY{n}{colnames}\PY{p}{,} \PY{n}{dtype}\PY{o}{=}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZlt{}U12}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZlt{}f8}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZlt{}f8}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZlt{}f8}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
          \PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{Column}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{dtype}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZlt{}U12}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{irow} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{argmax}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{l+s}{\PYZsq{}}\PY{l+s}{177\PYZhy{}341}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{irow}\PY{p}{]} \PY{o}{=} \PY{l+s}{\PYZsq{}}\PY{l+s}{177\PYZhy{}341W}\PY{l+s}{\PYZsq{}}
\end{Verbatim}

    So now we can do the join properly:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}917}]:} \PY{n}{jdata} \PY{o}{=} \PY{n}{join}\PY{p}{(}\PY{n}{sizedata}\PY{p}{,} \PY{n}{data}\PY{p}{,} \PY{n}{join\PYZus{}type}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{outer}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{keys}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    And the only one missing is 244-440:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}918}]:} \PY{n}{jdata}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14\PYZus{}2}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{mask} \PY{o}{\PYZam{}} \PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14\PYZus{}1}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{mask}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}918}]:} <Table rows=1 names=('ID','Chord','r14\_1','RA','Dec','Dprime','PA','d','r14\_2','VicR14')>
          masked\_array(data = [('244-440', --, --, --, --, --, --, 142.3, 104.0, 180.6)],
                       mask = [(False, True, True, True, True, True, True, False, False, False)],
                 fill\_value = ('N/A', 1e+20, 1e+20, '?', '?', 1e+20, 1e+20, 1e+20, 1e+20, 1e+20),
                      dtype = [('ID', '<U12'), ('Chord', '<f8'), ('r14\_1', '<f8'), ('RA', 'O'), ('Dec', 'O'), ('Dprime', '<f8'), ('PA', '<f8'), ('d', '<f8'), ('r14\_2', '<f8'), ('VicR14', '<f8')])
\end{Verbatim}

    Now we tidy up some of the column names:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}919}]:} \PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14\PYZus{}1}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{name} \PY{o}{=} \PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}
          \PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14\PYZus{}2}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{name} \PY{o}{=} \PY{l+s}{\PYZdq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZdq{}}
          \PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{d}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{name} \PY{o}{=} \PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime\PYZus{}HA}\PY{l+s}{\PYZdq{}}
\end{Verbatim}

    Look at the rows that are in both datasets:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}920}]:} \PY{n}{overlap} \PY{o}{=} \PY{o}{\PYZti{}}\PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{mask} \PY{o}{\PYZam{}} \PY{o}{\PYZti{}}\PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{mask}
          \PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}920}]:} <Table rows=27 names=('ID','Chord','r14','RA','Dec','Dprime','PA','Dprime\_HA','r14\_HA','VicR14')>
          masked\_array(data = [ ('152-319', 0.4021371270602539, 12.934154456590305, '5:35:15.197', '-5:23:18.66', 19.37548214448735, 282.4844035826249, 19.16, 18.2, 14.8)
           ('153-321', 0.08000000000590013, 2.573083376229769, '5:35:15.342', '-5:23:21.31', 16.82243690794256, 275.2472980493684, 16.97, 1.2, 8.4)
           ('154-324', 0.09999999999592658, 3.216354219918985, '5:35:15.342', '-5:23:24.06', 16.79566852896244, 265.8635327222988, 16.63, 3.2, 10.3)
           ('155-338', 0.4026223646938783, 12.949761417696655, '5:35:15.505', '-5:23:37.455', 20.453470258425444, 224.42783197907104, 20.48, 17.0, 29.7)
           ('157-323', 0.1000000000016516, 3.2163542201031214, '5:35:15.705', '-5:23:22.45', 11.338007448530387, 272.01433163356654, 10.97, 2.5, 18.4)
           ('158-323', 0.1706546658700654, 5.488858547424075, '5:35:15.8045', '-5:23:22.455', 9.852961584895814, 272.2890310719733, 9.42, 6.3, 30.6)
           ('158-326', 0.23232597535592958, 7.472426312632764, '5:35:15.8285', '-5:23:25.54', 9.86108732117705, 254.1608255382134, 9.6, 11.3, 31.6)
           ('158-327', 0.4002366670401905, 12.873028930534636, '5:35:15.7755', '-5:23:26.585', 10.936257012268827, 250.02202328035557, 10.6, 16.6, 35.5)
           ('159-338', 0.19157551869142098, 6.161747280014195, '5:35:15.886', '-5:23:38.08', 17.50539471231517, 209.52961366072773, 17.2, 5.0, 13.5)
           ('159-350', 0.625922271425744, 20.13187739123473, '5:35:15.9375', '-5:23:50.125', 28.386023025109218, 196.07260600961948, 28.35, 20.1, 44.5)
           ('161-314', 0.18604946713139633, 5.9840098874612035, '5:35:16.095', '-5:23:14.055', 10.375560591839491, 327.9434914814732, 10.24, 5.3, 17.1)
           ('161-324', 0.10110892444353344, 3.252021158186754, '5:35:16.0435', '-5:23:24.31', 6.443858510726929, 256.8913668901656, 6.05, 3.5, 25.8)
           ('161-328', 0.19956873670361883, 6.418837484867318, '5:35:16.0625', '-5:23:27.805', 7.7764272710109426, 230.4040876150403, 7.74, 9.1, 20.0)
           ('163-317', 0.18169847973921033, 5.844066720858787, '5:35:16.27', '-5:23:16.325', 7.136451814769168, 336.08065007739856, 6.91, 5.0, 27.1)
           ('163-323', 0.1011089261716131, 3.2520212137679168, '5:35:16.3125', '-5:23:22.6', 2.272420836013117, 276.2794710623649, 2.14, 2.2, 19.4)
           ('166-316', 0.11587838074598988, 3.7270591892492524, '5:35:16.6065', '-5:23:15.955', 7.215630357963379, 17.183402450357246, 7.01, 2.5, 14.8)
           ('167-317', 0.24955691955806011, 8.026634513632452, '5:35:16.7455', '-5:23:16.245', 7.830071974020209, 32.50361387175205, 7.83, 7.9, 35.8)
           ('168-328', 0.1269980216773827, 4.084706229600512, '5:35:16.76', '-5:23:28.155', 6.908720522453734, 140.1817864462777, 6.64, 2.8, 21.0)
           ('169-338', 0.09449034060536078, 3.03914405760014, '5:35:16.883', '-5:23:38.095', 16.48188238894839, 157.67488234452193, 16.47, 2.8, 16.1)
           ('170-337', 0.4162404272647277, 13.38776654788322, '5:35:16.98', '-5:23:37.205', 16.295481457204364, 151.7642697781941, 16.2, 12.2, 36.8)
           ('171-334', 0.20948633602138664, 6.737822609051992, '5:35:17.0625', '-5:23:34.115', 14.383406373150356, 141.56334754726322, 14.29, 4.7, 22.9)
           ('171-340', 0.5462728212701063, 17.57006893990726, '5:35:17.0555', '-5:23:39.805', 19.120982071000434, 152.47369841097154, 19.11, 23.3, 23.2)
           ('173-341', 0.16941402292211163, 5.448955075611812, '5:35:17.327', '-5:23:41.42', 22.607217547181378, 145.23369658054506, 22.48, 4.1, 18.1)
           ('176-325', 0.2699999999970833, 8.684156394041189, '5:35:17.569', '-5:23:24.785', 16.618585154414777, 96.69168720243154, 16.38, 6.9, 23.5)
           ('177-341W', 0.6072973409169007, 19.532833652832174, '5:35:17.684', '-5:23:41.095', 25.78757452887539, 135.03756966648623, 25.84, 20.4, 51.6)
           ('180-331', 0.3261921659047774, 10.491495493550804, '5:35:18.057', '-5:23:30.745', 25.069100775623742, 108.3603522626762, 25.12, 12.2, 29.3)
           ('182-413', 0.9989495547792666, 32.12975616131363, '5:35:18.2155', '-5:24:13.155', 56.70157842265729, 152.52558854406146, 56.7, 36.9, 48.7)],
                       mask = [(False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)
           (False, False, False, False, False, False, False, False, False, False)],
                 fill\_value = ('N/A', 1e+20, 1e+20, '?', '?', 1e+20, 1e+20, 1e+20, 1e+20, 1e+20),
                      dtype = [('ID', '<U12'), ('Chord', '<f8'), ('r14', '<f8'), ('RA', 'O'), ('Dec', 'O'), ('Dprime', '<f8'), ('PA', '<f8'), ('Dprime\_HA', '<f8'), ('r14\_HA', '<f8'), ('VicR14', '<f8')])
\end{Verbatim}

    \begin{center}\rule{3in}{0.4pt}\end{center}

Check that the two estimates of the proplyd sizes are not too different.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}895}]:} \PY{n}{x}\PY{p}{,} \PY{n}{y} \PY{o}{=} \PY{p}{[}\PY{n}{np}\PY{o}{.}\PY{n}{log10}\PY{p}{(}\PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{n}{colname}\PY{p}{]}\PY{p}{)} \PY{k}{for} \PY{n}{colname} \PY{o+ow}{in} \PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}
          \PY{n}{g} \PY{o}{=} \PY{n}{sns}\PY{o}{.}\PY{n}{jointplot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{8}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZhy{}w}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{zorder}\PY{o}{=}\PY{o}{\PYZhy{}}\PY{l+m+mi}{100}\PY{p}{,} \PY{n}{lw}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{2.0}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{;}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_136_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    So it doesn't look too bad. Here are the cases where HA98 got
\textgreater{}30\% larger sizes. These are mainly large sized.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}884}]:} \PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1.3}\PY{o}{*}\PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}884}]:} <Table rows=5 names=('ID','r14','r14\_HA')>
          masked\_array(data = [('152-319', 12.934154456590305, 18.2)
           ('155-338', 12.949761417696655, 17.0) ('158-326', 7.472426312632764, 11.3)
           ('161-328', 6.418837484867318, 9.1) ('171-340', 17.57006893990726, 23.3)],
                       mask = [(False, False, False) (False, False, False) (False, False, False)
           (False, False, False) (False, False, False)],
                 fill\_value = ('N/A', 1e+20, 1e+20),
                      dtype = [('ID', '<U12'), ('r14', '<f8'), ('r14\_HA', '<f8')])
\end{Verbatim}

    And here are the cases where HA98 sizes were more than 30\% smaller.
These are mainly small sized. In this case, I think that the current
results are more reliable because in HA98 we did not remove the central
stars and so overestimated the compactness of some of the small
proplyds.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}887}]:} \PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1.3}\PY{o}{*}\PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}887}]:} <Table rows=6 names=('ID','r14','r14\_HA')>
          masked\_array(data = [('153-321', 2.573083376229769, 1.2) ('163-323', 3.2520212137679168, 2.2)
           ('166-316', 3.7270591892492524, 2.5) ('168-328', 4.084706229600512, 2.8)
           ('171-334', 6.737822609051992, 4.7) ('173-341', 5.448955075611812, 4.1)],
                       mask = [(False, False, False) (False, False, False) (False, False, False)
           (False, False, False) (False, False, False) (False, False, False)],
                 fill\_value = ('N/A', 1e+20, 1e+20),
                      dtype = [('ID', '<U12'), ('r14', '<f8'), ('r14\_HA', '<f8')])
\end{Verbatim}

    If we look at the distribution of ratios, then it seems we have
agreement to a level of about 30\%. This is not bad, given that the
sizes range over an order of magnitude.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}898}]:} \PY{n}{ratio} \PY{o}{=} \PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{o}{/}\PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{]}
          \PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{(}\PY{n}{ratio}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{,} \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{fit}\PY{o}{=}\PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{p}{,} \PY{n}{axlabel}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{r14 / r14\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{)}
          \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Current vs HA98 estimates of proplyd size:}\PY{l+s}{\PYZsq{}}
                    \PY{l+s}{\PYZsq{}}\PY{l+s}{ ratio = \PYZob{}:.3f\PYZcb{} +/\PYZhy{} \PYZob{}:.3f\PYZcb{}}\PY{l+s}{\PYZsq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{ratio}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{,} 
                                                           \PY{n}{ratio}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}898}]:} <matplotlib.text.Text at 0x1575874d0>
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_142_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    We can do the same thing for the separations. This shows a much tighter
correlation, as one would expect

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}900}]:} \PY{n}{x}\PY{p}{,} \PY{n}{y} \PY{o}{=} \PY{p}{[}\PY{n}{np}\PY{o}{.}\PY{n}{log10}\PY{p}{(}\PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{n}{colname}\PY{p}{]}\PY{p}{)} \PY{k}{for} \PY{n}{colname} \PY{o+ow}{in} \PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{Dprime\PYZus{}HA}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}
          \PY{n}{g} \PY{o}{=} \PY{n}{sns}\PY{o}{.}\PY{n}{jointplot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{8}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZhy{}w}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{zorder}\PY{o}{=}\PY{o}{\PYZhy{}}\PY{l+m+mi}{100}\PY{p}{,} \PY{n}{lw}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{2.0}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{;}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_144_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    And just for fun, here is the same plot for the Vicente \& Alves (2005)
sizes.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}896}]:} \PY{n}{x}\PY{p}{,} \PY{n}{y} \PY{o}{=} \PY{p}{[}\PY{n}{np}\PY{o}{.}\PY{n}{log10}\PY{p}{(}\PY{n}{jdata}\PY{p}{[}\PY{n}{overlap}\PY{p}{]}\PY{p}{[}\PY{n}{colname}\PY{p}{]}\PY{p}{)} \PY{k}{for} \PY{n}{colname} \PY{o+ow}{in} \PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{VicR14}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r14}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{]}
          \PY{n}{g} \PY{o}{=} \PY{n}{sns}\PY{o}{.}\PY{n}{jointplot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{brown}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{8}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZhy{}w}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{zorder}\PY{o}{=}\PY{o}{\PYZhy{}}\PY{l+m+mi}{100}\PY{p}{,} \PY{n}{lw}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{2.0}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{l+m+mf}{0.0}\PY{p}{,} \PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{;}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_146_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{center}\rule{3in}{0.4pt}\end{center}

Finally, we can go back to the size-distance relationship:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}923}]:} \PY{n}{jdata}\PY{o}{.}\PY{n}{filled}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{nan}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}923}]:} <Table rows=70 names=('ID','Chord','r14','RA','Dec','Dprime','PA','Dprime\_HA','r14\_HA','VicR14')>
          array([ ('133-353', 0.19956810372609624, 6.418817126068057, '5:35:13.2955', '-5:23:53.055', 56.13363987705124, 237.44385762445836, nan, nan, nan),
                 ('139-320', 0.15074155191820304, 4.848382266489986, '5:35:13.9075', '-5:23:20.045', 38.277129043789, 274.1998097040322, nan, nan, nan),
                 ('142-301', 0.9679778688332578, 31.13359703336854, '5:35:14.1165', '-5:23:00.71', 41.459036843045375, 302.27472634362283, nan, nan, nan),
                 ('147-323', 0.3103594930344309, 9.982260651538704, '5:35:14.7055', '-5:23:22.775', 26.25731935056034, 270.16015831371493, nan, nan, nan),
                 ('148-305', 0.14187554655648482, 4.563220128888503, '5:35:14.79', '-5:23:04.565', 30.96868722101388, 306.18424926889605, nan, nan, nan),
                 ('149-329', 0.0948264445804458, 3.049954351986543, '5:35:14.914', '-5:23:28.995', 23.945790120512257, 255.12644132749037, nan, nan, nan),
                 ('150-231', 0.19822035630358525, 6.37546879496851, '5:35:15.0175', '-5:22:30.83', 56.32415700268409, 337.45143636973563, nan, nan, nan),
                 ('152-319', 0.4021371270602539, 12.934154456590305, '5:35:15.197', '-5:23:18.66', 19.37548214448735, 282.4844035826249, 19.16, 18.2, 14.8),
                 ('153-321', 0.08000000000590013, 2.573083376229769, '5:35:15.342', '-5:23:21.31', 16.82243690794256, 275.2472980493684, 16.97, 1.2, 8.4),
                 ('154-225', 0.1803214866471138, 5.799777745431342, '5:35:15.362', '-5:22:25.15', 59.998665326323156, 344.08361682405405, nan, nan, nan),
                 ('154-240', 0.6056714671056789, 19.48053979189225, '5:35:15.374', '-5:22:39.66', 46.153018460637284, 339.35249280337854, nan, nan, nan),
                 ('154-324', 0.09999999999592658, 3.216354219918985, '5:35:15.342', '-5:23:24.06', 16.79566852896244, 265.8635327222988, 16.63, 3.2, 10.3),
                 ('155-338', 0.4026223646938783, 12.949761417696655, '5:35:15.505', '-5:23:37.455', 20.453470258425444, 224.42783197907104, 20.48, 17.0, 29.7),
                 ('157-323', 0.1000000000016516, 3.2163542201031214, '5:35:15.705', '-5:23:22.45', 11.338007448530387, 272.01433163356654, 10.97, 2.5, 18.4),
                 ('158-323', 0.1706546658700654, 5.488858547424075, '5:35:15.8045', '-5:23:22.455', 9.852961584895814, 272.2890310719733, 9.42, 6.3, 30.6),
                 ('158-326', 0.23232597535592958, 7.472426312632764, '5:35:15.8285', '-5:23:25.54', 9.86108732117705, 254.1608255382134, 9.6, 11.3, 31.6),
                 ('158-327', 0.4002366670401905, 12.873028930534636, '5:35:15.7755', '-5:23:26.585', 10.936257012268827, 250.02202328035557, 10.6, 16.6, 35.5),
                 ('159-338', 0.19157551869142098, 6.161747280014195, '5:35:15.886', '-5:23:38.08', 17.50539471231517, 209.52961366072773, 17.2, 5.0, 13.5),
                 ('159-350', 0.625922271425744, 20.13187739123473, '5:35:15.9375', '-5:23:50.125', 28.386023025109218, 196.07260600961948, 28.35, 20.1, 44.5),
                 ('159-418', 0.3142365584879447, 10.106960809866894, '5:35:15.8965', '-5:24:17.87', 55.669730359443506, 188.7524133614498, nan, nan, nan),
                 ('160-350', 0.18361197284160802, 5.905611437008119, '5:35:15.958', '-5:23:49.7', 27.89343785153164, 195.7100452719107, nan, nan, nan),
                 ('161-314', 0.18604946713139633, 5.9840098874612035, '5:35:16.095', '-5:23:14.055', 10.375560591839491, 327.9434914814732, 10.24, 5.3, 17.1),
                 ('161-324', 0.10110892444353344, 3.252021158186754, '5:35:16.0435', '-5:23:24.31', 6.443858510726929, 256.8913668901656, 6.05, 3.5, 25.8),
                 ('161-328', 0.19956873670361883, 6.418837484867318, '5:35:16.0625', '-5:23:27.805', 7.7764272710109426, 230.4040876150403, 7.74, 9.1, 20.0),
                 ('163-249', 0.23915181790427623, 7.691969587490479, '5:35:16.332', '-5:22:48.795', 34.11035029756079, 356.6931333118622, nan, nan, nan),
                 ('163-317', 0.18169847973921033, 5.844066720858787, '5:35:16.27', '-5:23:16.325', 7.136451814769168, 336.08065007739856, 6.91, 5.0, 27.1),
                 ('163-323', 0.1011089261716131, 3.2520212137679168, '5:35:16.3125', '-5:23:22.6', 2.272420836013117, 276.2794710623649, 2.14, 2.2, 19.4),
                 ('165-235N', 0.13440609108383775, 4.322975982579263, '5:35:16.4835', '-5:22:34.97', 47.87946244086696, 0.352875196377189, nan, nan, nan),
                 ('165-235S', 0.4387068370843108, 14.11036586820911, '5:35:16.4725', '-5:22:35.255', 47.59373359902839, 0.15723000502306675, nan, nan, nan),
                 ('166-250', 0.1493390719216531, 4.803273541935594, '5:35:16.586', '-5:22:50.07', 32.82935280918948, 3.187798038848313, nan, nan, nan),
                 ('166-316', 0.11587838074598988, 3.7270591892492524, '5:35:16.6065', '-5:23:15.955', 7.215630357963379, 17.183402450357246, 7.01, 2.5, 14.8),
                 ('166-406', 0.18361065843219077, 5.905569160945359, '5:35:16.569', '-5:24:06.1', 43.27999247683998, 177.9189001606502, nan, nan, nan),
                 ('167-231', 0.32854879080509697, 10.567292897982984, '5:35:16.728', '-5:22:31.18', 51.8190317547333, 4.367559662217565, nan, nan, nan),
                 ('167-317', 0.24955691955806011, 8.026634513632452, '5:35:16.7455', '-5:23:16.245', 7.830071974020209, 32.50361387175205, 7.83, 7.9, 35.8),
                 ('168-326E', 0.2435727716841236, 7.834163120955061, '5:35:16.8425', '-5:23:26.36', 6.657422789500048, 121.83327500978822, nan, nan, nan),
                 ('168-326W', 0.1005342149006856, 3.2335364635523374, '5:35:16.8225', '-5:23:25.985', 6.207970631425778, 120.34661250624949, nan, nan, nan),
                 ('168-328', 0.1269980216773827, 4.084706229600512, '5:35:16.76', '-5:23:28.155', 6.908720522453734, 140.1817864462777, 6.64, 2.8, 21.0),
                 ('168-404', 0.3001709084357675, 9.654559680836229, '5:35:16.758', '-5:24:04.305', 41.68867041110204, 173.94964873867485, nan, nan, nan),
                 ('169-338', 0.09449034060536078, 3.03914405760014, '5:35:16.883', '-5:23:38.095', 16.48188238894839, 157.67488234452193, 16.47, 2.8, 16.1),
                 ('170-249', 0.4937316418995504, 15.880158499958343, '5:35:16.9675', '-5:22:48.135', 35.519345688540575, 12.227689559813806, nan, nan, nan),
                 ('170-301', 0.16698907149310396, 5.370960047990761, '5:35:16.9735', '-5:23:00.685', 23.434419846272746, 18.955929422072533, nan, nan, nan),
                 ('170-337', 0.4162404272647277, 13.38776654788322, '5:35:16.98', '-5:23:37.205', 16.295481457204364, 151.7642697781941, 16.2, 12.2, 36.8),
                 ('170-400', 0.2947976834595547, 9.48173773256103, '5:35:16.9535', '-5:23:59.55', 37.42306087593395, 168.73016693660202, nan, nan, nan),
                 ('171-334', 0.20948633602138664, 6.737822609051992, '5:35:17.0625', '-5:23:34.115', 14.383406373150356, 141.56334754726322, 14.29, 4.7, 22.9),
                 ('171-340', 0.5462728212701063, 17.57006893990726, '5:35:17.0555', '-5:23:39.805', 19.120982071000434, 152.47369841097154, 19.11, 23.3, 23.2),
                 ('173-236', 0.521743596411042, 16.78112218100719, '5:35:17.349', '-5:22:35.5', 49.15950733797618, 15.600358889696293, nan, nan, nan),
                 ('173-341', 0.16941402292211163, 5.448955075611812, '5:35:17.327', '-5:23:41.42', 22.607217547181378, 145.23369658054506, 22.48, 4.1, 18.1),
                 ('174-305', 0.07789927861626998, 2.505516735162907, '5:35:17.368', '-5:23:04.715', 22.609238452630468, 36.674651861161394, nan, nan, nan),
                 ('174-400', 0.2947975908462822, 9.48173475379013, '5:35:17.3775', '-5:24:00.29', 39.85047911040879, 159.9759979965743, nan, nan, nan),
                 ('174-414', 0.26954302964271354, 8.66945860876404, '5:35:17.385', '-5:24:13.97', 52.94024013769274, 164.9380024540518, nan, nan, nan),
                 ('175-251', 0.19821860324606935, 6.375412410429117, '5:35:17.4775', '-5:22:51.03', 35.236510725236485, 25.445004768609063, nan, nan, nan),
                 ('175-355', 0.22822885465100226, 7.340648397939293, '5:35:17.5345', '-5:23:54.97', 35.88132097887825, 153.53608556029468, nan, nan, nan),
                 ('176-252', 0.11947118063428656, 3.8426163600744343, '5:35:17.641', '-5:22:51.48', 35.95926243531263, 29.26900271056063, nan, nan, nan),
                 ('176-325', 0.2699999999970833, 8.684156394041189, '5:35:17.569', '-5:23:24.785', 16.618585154414777, 96.69168720243154, 16.38, 6.9, 23.5),
                 ('177-341E', 0.042332549361707744, 1.3615647378500364, '5:35:17.736', '-5:23:41.065', 26.321279121121652, 133.7952787598883, nan, nan, nan),
                 ('177-341W', 0.6072973409169007, 19.532833652832174, '5:35:17.684', '-5:23:41.095', 25.78757452887539, 135.03756966648623, 25.84, 20.4, 51.6),
                 ('178-258', 0.6506124739054455, 20.9260017606295, '5:35:17.8295', '-5:22:57.93', 32.20124304201232, 39.3004420700999, nan, nan, nan),
                 ('179-354', 0.12011790445720019, 3.8634172890447855, '5:35:17.965', '-5:23:53.53', 37.9994898856793, 143.8446508426508, nan, nan, nan),
                 ('180-331', 0.3261921659047774, 10.491495493550804, '5:35:18.057', '-5:23:30.745', 25.069100775623742, 108.3603522626762, 25.12, 12.2, 29.3),
                 ('181-247', 0.30308283098129235, 9.748217424513806, '5:35:18.084', '-5:22:46.9', 43.3331964236521, 33.94422218032231, nan, nan, nan),
                 ('181-401', 0.13588072788920955, 4.3704055256992485, '5:35:18.0645', '-5:24:01.23', 45.216983977869724, 148.08474600353034, nan, nan, nan),
                 ('182-316', 0.2245153617232573, 7.221209311446509, '5:35:18.2485', '-5:23:15.48', 27.652686160939773, 74.54615273372958, nan, nan, nan),
                 ('182-316', 0.2283166074842956, 7.343470839896137, '5:35:18.187', '-5:23:31.455', 27.135360773050742, 108.49203085401089, nan, nan, nan),
                 ('182-413', 0.9989495547792666, 32.12975616131363, '5:35:18.2155', '-5:24:13.155', 56.70157842265729, 152.52558854406146, 56.7, 36.9, 48.7),
                 ('189-329', 0.14079422461206662, 4.52844098489688, '5:35:18.8795', '-5:23:28.82', 36.5668000502415, 99.39910341888888, nan, nan, nan),
                 ('190-251', 0.13794221136562448, 4.4367101364885535, '5:35:19.0345', '-5:22:50.465', 50.22511576873447, 49.85220926340271, nan, nan, nan),
                 ('191-350', 0.5153676065060261, 16.576047760627247, '5:35:19.075', '-5:23:49.68', 47.33453201276577, 124.5311720003038, nan, nan, nan),
                 ('204-330', 0.10999999999952767, 3.537989642039808, '5:35:20.42', '-5:23:29.655', 59.47200193070507, 96.57255594388522, nan, nan, nan),
                 ('205-330', 0.31035949075157415, 9.982260578113944, '5:35:20.4725', '-5:23:29.725', 60.25888129615085, 96.55337000935337, nan, nan, nan),
                 ('244-440', nan, nan, nan, nan, nan, nan, 142.3, 104.0, 180.6)], 
                dtype=[('ID', '<U12'), ('Chord', '<f8'), ('r14', '<f8'), ('RA', 'O'), ('Dec', 'O'), ('Dprime', '<f8'), ('PA', '<f8'), ('Dprime\_HA', '<f8'), ('r14\_HA', '<f8'), ('VicR14', '<f8')])
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}931}]:} \PY{n}{color} \PY{o}{=} \PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsh{}774499}\PY{l+s}{\PYZdq{}}
          \PY{c}{\PYZsh{} g = sns.JointGrid(mirrored(jdata[\PYZdq{}Dprime\PYZdq{}].filled(0.0)), doubled(jdata[\PYZdq{}r14\PYZdq{}].filled(0.0)), }
          \PY{n}{g} \PY{o}{=} \PY{n}{sns}\PY{o}{.}\PY{n}{JointGrid}\PY{p}{(}\PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{Dprime}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} \PY{n}{jdata}\PY{p}{[}\PY{l+s}{\PYZdq{}}\PY{l+s}{r14}\PY{l+s}{\PYZdq{}}\PY{p}{]}\PY{p}{,} 
                            \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{9}\PY{p}{,} \PY{n}{xlim}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{60}\PY{p}{)}\PY{p}{,} \PY{n}{ylim}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{35}\PY{p}{)}\PY{p}{)}
          \PY{c}{\PYZsh{} g.plot(sns.regplot, sns.distplot, stats.pearsonr);}
          \PY{n}{g}\PY{o}{.}\PY{n}{plot\PYZus{}marginals}\PY{p}{(}\PY{n}{sns}\PY{o}{.}\PY{n}{distplot}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{10}\PY{p}{,} \PY{n}{rug}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{,} \PY{n}{kde\PYZus{}kws}\PY{o}{=}\PY{n+nb}{dict}\PY{p}{(}\PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{KDE}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{plot\PYZus{}joint}\PY{p}{(}\PY{n}{sns}\PY{o}{.}\PY{n}{regplot}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{,} \PY{n}{ci}\PY{o}{=}\PY{l+m+mi}{99}\PY{p}{,} \PY{n}{order}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Quadratic regression fit with 99}\PY{l+s+si}{\PYZpc{} c}\PY{l+s}{onfidence bounds}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper left}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Projected separation, \PYZdl{}D}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdl{}}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}joint}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Proplyd radius \PYZdl{}r\PYZus{}0\PYZdl{}, \PYZdl{}10\PYZca{}\PYZob{}14\PYZcb{}\PYZdl{} cm}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}marg\PYZus{}x}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{upper right}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{ax\PYZus{}marg\PYZus{}y}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{loc}\PY{o}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{best}\PY{l+s}{\PYZdq{}}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{fig}\PY{o}{.}\PY{n}{tight\PYZus{}layout}\PY{p}{(}\PY{p}{)}
          \PY{n}{g}\PY{o}{.}\PY{n}{fig}\PY{o}{.}\PY{n}{savefig}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{proplyd\PYZhy{}joint\PYZhy{}separation\PYZhy{}size\PYZhy{}new.pdf}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{;}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Proplyd distribution_files/Proplyd distribution_149_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}743}]:} \PY{n}{data}\PY{p}{[}\PY{n}{data}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{==} \PY{l+s}{\PYZsq{}}\PY{l+s}{177\PYZhy{}341}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{ID}\PY{l+s}{\PYZsq{}}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}743}]:} <Column name='ID' unit=None format=None description=None>
          array(['177-341'], 
                dtype='<U7')
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}897}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{jointplot}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}729}]:} \PY{n}{sizedata}\PY{p}{[}\PY{p}{:}\PY{p}{:}\PY{l+m+mi}{10}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}729}]:} <Table rows=7 names=('ID','Chord','r14','RA','Dec','Dprime','PA')>
          array([ ('154-240', 0.6056714671056789, 19.48053979189225, '5:35:15.374', '-5:22:39.66', 46.153018460637284, 339.35249280337854),
                 ('174-305', 0.07789927861626998, 2.505516735162907, '5:35:17.368', '-5:23:04.715', 22.609238452630468, 36.674651861161394),
                 ('149-329', 0.0948264445804458, 3.049954351986543, '5:35:14.914', '-5:23:28.995', 23.945790120512257, 255.12644132749037),
                 ('177-341E', 0.042332549361707744, 1.3615647378500364, '5:35:17.736', '-5:23:41.065', 26.321279121121652, 133.7952787598883),
                 ('190-251', 0.13794221136562448, 4.4367101364885535, '5:35:19.0345', '-5:22:50.465', 50.22511576873447, 49.85220926340271),
                 ('158-326', 0.1726037583473396, 5.551548265569561, '5:35:15.824', '-5:23:25.565', 9.932562348684426, 254.12789181523758),
                 ('174-414', 0.26954302964271354, 8.66945860876404, '5:35:17.385', '-5:24:13.97', 52.94024013769274, 164.9380024540518)], 
                dtype=[('ID', '<U8'), ('Chord', '<f8'), ('r14', '<f8'), ('RA', 'O'), ('Dec', 'O'), ('Dprime', '<f8'), ('PA', '<f8')])
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    \begin{center}\rule{3in}{0.4pt}\end{center}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}719}]:} \PY{n}{coord}\PY{o}{.}\PY{n}{SkyCoord}\PY{o}{.}\PY{n}{to\PYZus{}string}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}720}]:} \PY{n}{coords0}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{4}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}string}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{hmsdms}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}720}]:} ['05h35m15.374s -05d22m39.66s',
           '05h35m16.332s -05d22m48.795s',
           '05h35m16.4725s -05d22m35.255s',
           '05h35m16.4835s -05d22m34.97s']
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}721}]:} \PY{n}{coord}\PY{o}{.}\PY{n}{Angle}\PY{o}{.}\PY{n}{to\PYZus{}string}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}723}]:} \PY{n}{coords0}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{4}\PY{p}{]}\PY{o}{.}\PY{n}{ra}\PY{o}{.}\PY{n}{to\PYZus{}string}\PY{p}{(}\PY{n}{unit}\PY{o}{=}\PY{n}{u}\PY{o}{.}\PY{n}{hourangle}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}723}]:} array(['5h35m15.374s', '5h35m16.332s', '5h35m16.4725s', '5h35m16.4835s'], dtype=object)
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}588}]:} \PY{n}{plt}\PY{o}{.}\PY{n}{scatter}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}672}]:} \PY{n}{sns}\PY{o}{.}\PY{n}{kdeplot}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}79}]:} \PY{k+kn}{import} \PY{n+nn}{matplotlib}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}583}]:} \PY{n}{matplotlib}\PY{o}{.}\PY{n}{markers}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}600}]:} \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{err}{?}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}93}]:} \PY{n}{f}\PY{o}{.}\PY{n}{axes}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]} \PY{o}{==} \PY{n}{fig}\PY{o}{.}\PY{n}{\PYZus{}ax1}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}93}]:} True
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}242}]:} \PY{n}{r} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{RandomState}\PY{p}{(}\PY{l+m+mi}{5}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}243}]:} \PY{n}{r}\PY{o}{.}\PY{n}{random\PYZus{}sample}\PY{p}{(}\PY{l+m+mi}{10}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}243}]:} array([ 0.22199317,  0.87073231,  0.20671916,  0.91861091,  0.48841119,
                  0.61174386,  0.76590786,  0.51841799,  0.2968005 ,  0.18772123])
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}182}]:} \PY{n}{np}\PY{o}{.}\PY{n}{r\PYZus{}}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{3}\PY{p}{]}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]}\PY{p}{]}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}182}]:} array([1, 2, 3, 0, 0, 1, 2])
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}244}]:} \PY{k+kn}{import} \PY{n+nn}{seaborn}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}249}]:} \PY{n}{seaborn}\PY{o}{.}\PY{n}{palettes}\PY{o}{.}\PY{n}{dark\PYZus{}palette}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{red}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{as\PYZus{}cmap}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
\end{Verbatim}

            \begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}249}]:} <matplotlib.colors.LinearSegmentedColormap at 0x111cb7490>
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}}]:} 
\end{Verbatim}

    % Add a bibliography block to the postdoc

    \end{document}

### 2015-06-18 papers/Paper1/sec-application.tex
New start on Jorge's paper

\section{Application to proplyd bowshocks}
\label{sec:application}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

### 2015-06-19 papers/Paper1/sec-projection.tex
New start on Jorge's paper
First draft paragraphs to the projection section

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
+\section{Projection onto the plane of the sky}
+\label{sec:projection}
 
@@
 %%% End:
+
+In this section we calculate the apparent shape of a limb brightened  border of a generic bow shock with cilindrical geometry, observed in the
+plane of the sky.
+
+\subsection{Frames of reference}
+
+We can specify the shell's position in cartesian coordinates $(x,y,z)$, where the x axis points towards the symetry axis of the system.
+Since the shell is cilindrically symetric, we can describe it's shape fully with the function $R(\theta)$, such that:
+
+\begin{equation}
+\left(\begin{array}
+x \\ y \\ z
+\end{array}
+\right) = R(\theta)\left(\begin{array}
+\cos\theta \\
+\sin\theta\cos\phi \\
+\sin\theta\sin\phi
+\end{array}\right)
+\end{equation}
+
+Where $\theta$ is the polar angle and $\phi$ the azimutal angle from spherical coordinates
+
+The observer's reference frame is denotated with primes, and is rotated respect y axis by an angle $i$. The transformation between the shell frame and the observed
+frame is given by:
+
+\begin{equation}
+\left(\begin{array}
+x' \\ y' \\ z'
+\end{array}
+\right) = \left(\begin{array}
+x\cos i - z\sin i\\
+y \\
+z\cos i + x\sin i
+\end{array}\right)
+\end{equation}
+
+\subsection{Tangent line}
+
+The normal and tangent vectors to the shell's border in the shell's frame are given by:
+
+\begin{align}
+\hat{t} = \left(\begin{array}
+\end{array}\right)\\
+\hat{n} = \left(\begin{array}
+\end{array}\right)
+\end{align}
+
+Then we apply the transformation to the observer's frame to obtain:
+
+\begin{align}
+\end{align}
+
+In the thin shell case, the limb brightened border of the shell is such that $\hat{n}'\cdot \hat{z}'$.

### 2015-06-19 papers/Paper1/sec-projection.tex
Update of 19/06/2015. Development almost done

@@
 
+%Note: I'm aware that some of this material should be moved to an appendix, but I think it will be a future edition.
 \subsection{Frames of reference}
@@
 \begin{equation}
-\left(\begin{array}
+\left(\begin{array}{c}
 x \\ y \\ z
 \end{array}
-\right) = R(\theta)\left(\begin{array}
+\right) = R(\theta)\left(\begin{array}{c}
 \cos\theta \\
@@
 \begin{equation}
-\left(\begin{array}
+\left(\begin{array}{c}
 x' \\ y' \\ z'
 \end{array}
-\right) = \left(\begin{array}
+\right) = \left(\begin{array}{c}
 x\cos i - z\sin i\\
@@
 \end{array}\right)
+\label{eq:Trans}
 \end{equation}
@@
 \begin{align}
-\hat{t} = \left(\begin{array}
+\hat{t} = \left(\begin{array}{c}
+-\cos\alpha \\
+\sin\alpha\cos\phi\\
+\sin\alpha\sin\phi
 \end{array}\right)\\
-\hat{n} = \left(\begin{array}
+\hat{n} = \left(\begin{array}{c}
+\sin\alpha \\
+\cos\alpha\cos\phi \\
+\cos\alpha\sin\phi
 \end{array}\right)
@@
 
-Then we apply the transformation to the observer's frame to obtain:
+Where:
 
 \begin{align}
+\tan\alpha = -\left\frac{dy}{dx}\right|_{R(\theta)} \\
 \end{align}
 
+Then we apply the transformation (\ref{eq:Trans}) to the normal and tangent vectors to obtain:
+
+\begin{align}
+\hat{n}' &= \left(\begin{array}{c}
+(\cos\theta+\omega\sin\theta)\cos i -(\sin\theta-\omega\cos\theta)\sin i \sin\phi\\
+(\sin\theta-\omega\cos\theta)\cos\phi \\
+()\sin i + ()\sin\phi\cos i
+\end{array}\right)\\
+\hat{t}' &= \left(\begin{array}{c}
+-()\cos i - ()\sin\phi\sin i \\
+()\cos\phi \\
+-()\sin i + ()\sin\phi\cos i
+\end{array}\right)
+\end{align}
+
+Where $\omega = \frac{1}{R}\frac{dR}{d\theta}$
+
 In the thin shell case, the limb brightened border of the shell is such that $\hat{n}'\cdot \hat{z}'$. 
+The values for $\phi$ that satisfy this relation for each inclination $i$ are given by:
+
+\begin{equation}
+\sin\phi_t = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
+\end{equation}
+
+With this, the coordinates of the limb brightened shell are given by:
+
+\begin{equation}
+\left(\begin{array}{c}
+x'_t \\ y'_t \\ z'_t
+\end{array}\right)= R(\theta)\left(\begin{array}{c}
+\cos\theta\cos i - \sin\theta\sin\phi_t \sin i \\
+\sin\theta(1-\sin^2\phi_t)^{1/2} \\
+\cos\theta\sin i +\sin\theta\sin\phi_t\cos i
+\end{array}\right)
+\end{equation}

### 2015-06-23 papers/Paper1/sec-projection.tex
Paper1 - fix {array} envs and untrack .log, .pdf
23/06/15 update. Main content written.

@@
 \label{sec:projection}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "proplyd-bowshocks"
-%%% End:
 
@@
 \sin\phi_t = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
+\label{eq:tanphi}
 \end{equation}
@@
 \end{array}\right)
+\label{eq:tangential}
 \end{equation}
+
+It is important to note that the equation (\ref{eq:tanphi}) does not have a solution for arbitrary values for $\theta$ and $i$, since
+it's required that $|\sin\phi_t|<1$. If $i\neq 0$, then, the  allowed values for $\theta$ are such that $\theta > \theta_\parallel$, where
+$\theta_\parallel$ is given implicitly by:
+
+\begin{align}
+\tan\theta_\parallel = \frac{|\tan i| + \omega(\theta_\parallel)}{1-\omega(\theta_\parallel |\tan i|)}
+\label{eq:thetapar}
+\end{align}
+
+\subsection{Parallel and perpendicular projected shell radii}
+
+Considering further applications to bow shocks, we will consider open shells. In order to compare the shell shape given by $R(\theta)$ with observations,
+it is convenient to define the following apparent radii in the observer frame: $R'_\parallel$ and $R'_\perp$. These are projected distances of the shell tangent line
+from the origin. The first is measured in the direction of the symetry axis, and the second in a perpendicular direction. More concretely $R'_\parallel = x'_t(y'_t=0)$
+and $R'_\perp = y'_t(x'_t=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:
+
+\begin{align}
+R'_\parallel = R(\theta_\parallel)\cos(\theta + i) \label{eq:Rpar} 
+\end{align}
+
+Where $\theta_\parallel$ is the solution of equation (\ref{eq:thetapar}), and
+
+\begin{align}
+R'_\perp = R(\theta_\perp)\sin\theta_\perp\left(1-\sin^2(\phi_t(\theta_\perp))\right)^{1/2}
+\end{align}
+
+Where $\theta_\perp$ is the solution of the next implicit equation:
+
+\begin{align}
+\cot\theta_\perp = \frac{1-\left(1+\omega(\theta_\perp)^2\sin^22i\right)^{1/2}}{2\omega(\theta_\perp\cos^2 i)}
+\end{align}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "proplyd-bowshocks"
+%%% End:

### 2015-06-24 papers/Paper1/sec-conic.tex
New start on Jorge's paper
24/06/15 update. First attempt to work in this section

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
+\section{Conic section approximation to bow shock shapes}
+\label{sec:conic}
 
@@
 %%% End:
+
+In this section we will analyze the case where the resultant shape is a conic curve (circle, ellipse, parabola or hyperbola).
+These curves are mathematical simple to model and give us a good reference to understand the effects of the projection effects
+described in the last section on other bowshocks. Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
+$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates thethe given curve is a closed one, i.e
+an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary
+
+\subsection{Characteristic radii}
+
+\subsection{Projection onto the plane of sky}

### 2015-06-25 papers/Paper1/sec-conic.tex
25/06/15 Procedure description

@@
 
-\subsection{Characteristic radii}
+Due to the similitudes between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
+
+\begin{align}
+x = au_c(t)-x_0 \\ 
+y = bv_c(t)
+\end{align}
+
+where:
+\begin{align}
+u_c(t) = \left\lbrace \begin{array}{c}
+\cos t ~\mathrm{if~ellipse} \\
+\cosh t ~mathrm{if~hyperbola}
+\end{array}\right
+\end{align}\\
+v_c(t) = \left\lbrace \begin{array}{c}
+\sin t ~\mathrm{if~ellipse} \\
+\sinh t ~mathrm{if~hyperbola}
+\end{array}\right \\
+-\pi < t < \pi \\
+R_0 = a - x_0 
+\end{align}
 
 \subsection{Projection onto the plane of sky}
+
+Once the parametrization is done, we can find the apparent shape of the shell in the observer's frame, following the procedure explained in section \ref{sec:projection}.
+
+First of all, the intrinsic 3D shape of the shell is given by:
+
+\begin{align}
+x = au_c(t)-x_0 \\ 
+y = bv_c(t)\cos\phi \\
+z =  bv_c(t)\sin\phi
+\end{align}
+
+The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:tanalpha}), then:
+
+\begin{align}
+\tan\phi &= \frac{b}{a}w_c(t) 
+\end{align}
+where:
+
+\begin{align}
+w_c(t) = \left\lbrace \begin{array}{c}
+\cot t ~\mathrm{if~ellipse} \\
+-\coth t ~mathrm{if~hyperbola}
+\end{array}\right
+\end{align}
+\subsection{Characteristic radii}

### 2015-06-29 papers/Paper1/sec-intro.tex
New start on Jorge's paper
Paper1: Add bibliography and make start on intro
All references should go in bowshocks-biblio.bib

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
+\section{Introduction}
+\label{sec:intro}
+
+%%
+%% Circumstances when bowshocks arise
+%%
+
+The archetypical bow shock is formed when a solid body moves
+supersonically through a compressible fluid.  Terrestrial examples
+include the atmospheric re-entry of a space capsule, or the sonic boom
+produced by a supersonic jet \citep{van-Dyke:1982a}.  In astrophysics
+the term bow shock is employed more widely, to refer to many different
+types of curved shocks that have approximate cylindrical symmetry.
+
+%%
+%% Examples of astrophysical bowshocks
+%%
+
+%% 
+%% Restriction to cylindrical symmetry
+%%
+
+For simplicity, the current paper is restricted to cylindrically
+symmetric bowshock shapes.
 

### 2015-06-29 papers/Paper1/sec-conic.tex
Fix some math-mode errors
Move emacs local variable section to end of file
Add short title and author list
Also, define commands for the cos/cosh terms in the conic section
equations.  Try out using cursive upper case letters, but we may change
those later
29/06/15 Some advances in conic section.
At this point there might be some mathematical inconsistencies, but still working on it

@@
 
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "proplyd-bowshocks"
-%%% End:
+\newcommand\Sin{\ensuremath{\mathcal{S}}}
+\newcommand\Cos{\ensuremath{\mathcal{C}}}
+\newcommand\Cot{\ensuremath{\mathcal{T}}}
 
@@
 \begin{align}
-x = au_c(t)-x_0 \\ 
-y = bv_c(t)
+x = a\Cos(t)-x_0 \\ 
+y = b\Sin(t)
 \end{align}
@@
 \begin{align}
-u_c(t) = \left\lbrace \begin{array}{c}
+\Cos(t) = \left\lbrace \begin{array}{c}
 \cos t ~\mathrm{if~ellipse} \\
-\cosh t ~mathrm{if~hyperbola}
-\end{array}\right
-\end{align}\\
-v_c(t) = \left\lbrace \begin{array}{c}
+\cosh t ~\mathrm{if~hyperbola}
+\end{array}\right.\\
+\Sin(t) = \left\lbrace \begin{array}{c}
 \sin t ~\mathrm{if~ellipse} \\
-\sinh t ~mathrm{if~hyperbola}
-\end{array}\right \\
+\sinh t ~\mathrm{if~hyperbola}
+\end{array}\right. \\
 -\pi < t < \pi \\
@@
 \begin{align}
-x = au_c(t)-x_0 \\ 
-y = bv_c(t)\cos\phi \\
-z =  bv_c(t)\sin\phi
+x = a\Cos(t)-x_0 \\ 
+y = b\Sin(t)\cos\phi \\
+z =  b\Sin(t)\sin\phi
 \end{align}
@@
 \begin{align}
-\tan\phi &= \frac{b}{a}w_c(t) 
+\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
 \end{align}
@@
 \begin{align}
-w_c(t) = \left\lbrace \begin{array}{c}
+\Cot(t) = \left\lbrace \begin{array}{c}
 \cot t ~\mathrm{if~ellipse} \\
--\coth t ~mathrm{if~hyperbola}
-\end{array}\right
+-\coth t ~\mathrm{if~hyperbola}
+\end{array}\right.
 \end{align}
-\subsection{Characteristic radii}
+
+We could work in another frame   where the origin is located at the conic's center: $(X,Y)$, where $X=x-X_0$ and $Y=y$.
+
+In this frame,  we use the transformations (\ref{eq:Trans})  to obtain the apparent shape of the shell:
+
+\begin{align}
+X' = \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
+Y'= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot(t)\right)^{1/2}
+\label{eq:conic-projected-y}
+\end{align}
+
+We must show that the apparent shape of the shell in the observer's frame is still the same conic. To do that, we can write equations
+(\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:
+
+\begin{align}
+X' = a'\Cos t' \label{eq:conic-projected-x-2} \\
+Y' = b'\Sin t' \label{eq:conic-projected-y-2}
+\end{align}
+
+Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y}) we find that
+
+\begin{align}
+a' = a^2\cos^2 i \pm b^2\sin^2 i \\
+\Cos t' = \frac{\Cos(t)}{a\cos i} \\
+b' = b
+\end{align}
+
+Which proves that effectively the projection of a given conic is the same conic. With this knowledge, we can obtain the characteristic radii in
+the observer's frame.
+
+The minimum value of $t$ is such that $1-\frac{b^2}{a^2}\tan^2 i T^2(t_\parallel) =0$, where:
+
+\begin{align}
+X'(t_\parallel) = R'_0 \\
+\Cot t = \frac{a^2}{b^2}\tan i
+\end{align}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "proplyd-bowshocks"
+%%% End:

### 2015-06-30 papers/Paper1/sec-conic.tex
30/06/15 New advances to conics section.

@@
 
-In this section we will analyze the case where the resultant shape is a conic curve (circle, ellipse, parabola or hyperbola).
+In this section we will analyze the case where the resultant shape  of the bow shock is a conic curve (circle, ellipse, parabola or hyperbola).
 These curves are mathematical simple to model and give us a good reference to understand the effects of the projection effects
-described in the last section on other bowshocks. Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
-$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates thethe given curve is a closed one, i.e
-an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary
+described in the last section on other bow shocks. The source of the inner wind is located at the origin, and the center of the conic is located at
+a distance $x_0$ from the source.
+%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
+%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates thethe given curve is a closed one, i.e
+%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary
 
@@
 -\pi < t < \pi \\
-R_0 = a - x_0 
+R_0 = a - x_0 \\
+a<0 ~ \mathrm{for~hyperbola}
 \end{align}
@@
 \begin{align}
-a' = a^2\cos^2 i \pm b^2\sin^2 i \\
+a' = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
 \Cos t' = \frac{\Cos(t)}{a\cos i} \\
@@
 
-The minimum value of $t$ is such that $1-\frac{b^2}{a^2}\tan^2 i T^2(t_\parallel) =0$, where:
+\begin{align}
+D' = D\cos i \\
+R'_0 = a' - (a-R_0)\cos i \\
+R'_0 = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
+\end{align}
+
+With $\tan\theta_c\equiv \frac{b}{a}$,  $f(i;\theta_c)\equiv\left(1-\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
+radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:
 
 \begin{align}
-X'(t_\parallel) = R'_0 \\
-\Cot t = \frac{a^2}{b^2}\tan i
+\frac{R'_0}{D'}={R_0}{D}\left(1-A\cot^2\theta_c(f(i;\theta_c)-1) \right)
 \end{align}
 
+Where $A\equiv \frac{R_c}{R_0}$
 %%% Local Variables:

### 2015-06-30 papers/Paper1/sec-generic-model.tex
New start on Jorge's paper
30/06/15 First attempt to write something in this section

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
+\section{Generic bow shock model}
+\label{sec:generic-model}
 
+The bow shocks we consider are originated by a source located at the origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a terminal
+(supersonic) velocity $v_w$. This wind interacts with another wind originated by another source located at a distance $D$ from the first one. 
+The mass loss rate of the second source is $\dot{M}_{w1}$ and the terminal velocity is $v_{w1}$. The momentum of the wind of the second source is
+higher than the momentum of the first one, and the resultant bow shock is stationary due to pressure balance.
 %%% Local Variables:

### 2015-07-02 papers/Paper1/sec-conic.tex
01/07/15 Last advance to conic section until edition.

@@
 
-With $\tan\theta_c\equiv \frac{b}{a}$,  $f(i;\theta_c)\equiv\left(1-\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
+With $\tan\theta_c\equiv \frac{b}{a}$,  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
 radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:
@@
 \begin{align}
-\frac{R'_0}{D'}={R_0}{D}\left(1-A\cot^2\theta_c(f(i;\theta_c)-1) \right)
+\frac{R'_0}{D'}={R_0}{D}\left(1+A\cot^2\theta_c(f(i;\theta_c)-1) \right)
 \end{align}
@@
 Where $A\equiv \frac{R_c}{R_0}$
+
+The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'^2}$. Then:
+
+\begin{align}
+\frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\thet_c)\frac{q'}{q}}
+\end{align}
+
+Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
+%Insert figures where needed
+
 %%% Local Variables:

### 2015-07-02 papers/Paper1/sec-intro.tex
Wrote something about bow shocks for intro

@@
 
-The archetypical bow shock is formed when a solid body moves
+The archetypal bow shock is formed when a solid body moves
 supersonically through a compressible fluid.  Terrestrial examples
@@
 types of curved shocks that have approximate cylindrical symmetry.
+Instead of a solid body, astrophysical examples usually involve the
+interaction of \emph{two} supersonic flows, such as the situation of a
+stellar wind emitted by a star that moves supersonically through the
+interstellar medium \citep{}.  In such cases, two shocks are generally
+produced, one in each flow, and technically speaking only the shock in
+the ambient medium is a ``bow shock'', whereas the other is the ``wind
+shock'' or ``termination shock''.  However,
 
@@
 
+%%
+%% Effects of instabilities
+%%
+
 %%% Local Variables:

### 2015-07-30 papers/Paper1/sec-application.tex
First attempt of writing

@@
 
+Proplyds are comet-like structures observed in HII regions like Orion Nebula Cluster (ONC). 
+These objects are interpreted as a D-type Ionization Front of a photoevaporated flow 
+originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
+The presure of the surrounding gas is not enough to confine this flow, thus accelerates as a 
+supersonic wind slowly until $M \sim 3$. In the particular case of the ONC, the ``Classic'' proplyds
+discovered by Laques \& Vidal \citep{Laques:1979}, which are spatially nearby $\theta^1~C~Ori$, an stationary bowshock
+may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of $\theta^1~C~Ori$.
 %%% Local Variables:

### 2015-07-30 papers/Paper1/sec-conic.tex
Correct typo in equation
02/66/15 Found more typographic errors
give more importance to the \theta_c parameter

--- 2015-06-30 papers/Paper1/sec-conic.tex
@@
 a distance $x_0$ from the source.
+
 %Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
-%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates thethe given curve is a closed one, i.e
+%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
 %an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary
@@
 \end{align}
+We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
+(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
+a parabola.
 
@@
 a' = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
-\Cos t' = \frac{\Cos(t)}{a\cos i} \\
+\Cos(t') = \frac{\Cos(t)}{a\cos i} \\
 b' = b
@@
 
-With $\tan\theta_c\equiv \frac{b}{a}$,  $f(i;\theta_c)\equiv\left(1-\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
+With  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
 radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:
@@
 \begin{align}
-\frac{R'_0}{D'}={R_0}{D}\left(1-A\cot^2\theta_c(f(i;\theta_c)-1) \right)
+\frac{R'_0}{D'}=\frac{R_0}{D}\left(1+A\cot^2\theta_c(f(i;\theta_c)-1) \right)
 \end{align}
@@
 Where $A\equiv \frac{R_c}{R_0}$
+
+The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
+
+\begin{align}
+\frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
+\end{align}
+
+Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
+%Insert figures where needed
+
 %%% Local Variables:

### 2015-08-01 papers/Paper1/sec-application.tex
Enhance a bit the description of the proplyd model

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
 
+Proplyds are comet-like structures observed in HII regions like Orion Nebula Cluster (ONC). 
+These objects are interpreted as a D-type Ionization Front (IF) of a photoevaporated flow 
+originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
+The presure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
+may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of $\theta^1~C~Ori$, which is highly supersonic $(M \sim 100)$.
+
+The density distribution of the photoevaporated flow can be determined using the steady state continuity equation and assuming that almost all ionizing photons are absorbed at the IF \citep{HA:1998} and ignoring dust absorption, can be found that
+
+\begin{align}
+N(r_{IF},\theta) = N_0 \cos^{0.5}\theta
+\end{align}
+
+This scenario can be described with the algebraic formalism of \citep{Canto:1996}.
 %%% Local Variables:

### 2015-08-07 papers/Paper1/sec-application.tex
07/08/15 Output of the last few days

@@
 N(r_{IF},\theta) = N_0 \cos^{0.5}\theta
+\label{eq:nprop}
 \end{align}
 
-This scenario can be described with the algebraic formalism of \citep{Canto:1996}.
+This scenario can be described with the formalism of \citep{Canto:1996}, who proposes an algebraic solution for the two winds interaction problem in the thin shell approximation. See figure.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{2winds-scheme}
+\caption{Schematic representation of the two winds problem. Any point in the shell is located with the coordinates
+$(R,\theta)$, and $\theta_1$ is measured from the external wind position}
+\label{fig:2-winds}
+\end{figure}
+
+ Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, as shown in figure (add figure later). Also we can
+obtain a relation between $\theta$ and $\theta_1$
+
+\begin{align}
+\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
+\label{eq:th1th}
+\end{align}
+
+\subsection{Characteristic Radii}
+
+$R_0$ is obtained directly from equation () of \citep{Canto:1996} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
+
+Combinig equation (23) from \citep{Canto:1996} and  (\ref{eq:th1th}) evaluated at $\theta=\frac{\pi}{2}$, we can obtain $R_{90}$
+
+\begin{align}
+R_{90} \simeq \frac{\left(2.4\beta\right)^{1/2}}{1-0.8\beta}
+\label{eq:r90}
+\end{align}
 %%% Local Variables:

### 2015-08-19 papers/Paper1/sec-conic.tex
included new figures in conic section

@@
 %an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
-
+\begin{figure}
+\begin{tabular}{cc}
+\includegraphics[width=0.4\linewidth]{ellipse} &
+\includegraphics[width=0.4\linewidth]{hiperbola}
+\end{tabular}
+\label{fig:conics}
+\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola The center of the conic is located at a distance $x_0$ from the origin at the $x$ axis. The shell position is 
+described either by cartesian coordinates $(x,y)$ or polar coordinates $(R,\theta)$. In this section is more convenient to use cartesian coordinates, as their parametrization is quite easy.}
+\end{figure}
 Due to the similitudes between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
@@
 a parabola.
-
+\begin{figure}
+\includegraphics[width=\linewidth]{conic1}
+\caption{A whole set of conics with the same radius of curvature. The parameter $\theta_c$ is used as the equivalent of the excentricity. This angle is defined as positive for closed curves
+and negative forthe opened ones. An special case is $\theta_c=0$, which describes a parabola.}
+\label{fig:conics-family}
+\end{figure}
 \subsection{Projection onto the plane of sky}

### 2015-08-28 papers/Paper1/sec-application.tex
Move first figure to section 2
Insert new figures and correct typographics errors

--- 2015-08-01 papers/Paper1/sec-application.tex
@@
 N(r_{IF},\theta) = N_0 \cos^{0.5}\theta
+\label{eq:nprop}
 \end{align}
 
-This scenario can be described with the algebraic formalism of \citep{Canto:1996}.
+This scenario can be described with the formalism of \citep{Canto:1996}, who proposes an algebraic solution for the two winds interaction problem in the thin shell approximation, in terms of a free parameter $\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$,
+the winds momentum ratio, which the quantities with subindex 1 corresponds to the strongest wind, therefore $\beta<=1$.
+
+ Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, which gives us the shell's shape. Also we can
+obtain a relation between $\theta$ and $\theta_1$
+
+\begin{align}
+\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
+\label{eq:th1th}
+\end{align}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{r-beta}
+\caption{Bowshock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with  $D$
+to avoid dependances with this parameter. }
+\end{figure}
+
+\subsection{Characteristic Radii}
+
+$R_0$ is obtained directly from equation (27) of \citep{Canto:1996} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
+
+Combinig equation (23) from \citep{Canto:1996} and  (\ref{eq:th1th}) evaluated at $\theta=\frac{\pi}{2}$, we can obtain $R_{90}$
+
+\begin{align}
+R_{90} \simeq \frac{\left(2.4\beta\right)^{1/2}}{1-0.8\beta}
+\label{eq:r90}
+\end{align}
+
 %%% Local Variables:

### 2015-08-31 papers/Paper1/sec-generic-model.tex
Move first figure to section 2
Insert characteristic radii figure

@@
 \label{sec:generic-model}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{2winds-scheme}
+\caption{Schematic representation of the two winds problem. Any point in the shell is located with the coordinates
+$(R,\theta)$, and $\theta_1$ is measured from the external wind position}
+\label{fig:2-winds}
+\end{figure}
 
@@
 higher than the momentum of the first one, and the resultant bow shock is stationary due to pressure balance.
+
+\subsection{Characteristic Radii}
+
+In order to contrast different bowshock models, we  derive a set of measurable radii. Each model used should predict them and these predictions can be
+compared with observations.
+
+\begin{itemize}
+\item Radius at axis of symemtry. Denoted as $R_0$. 
+\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
+\item Radius at the  perpendicular direction to the symmetry axis. Denoted as $R_{90}$
+\item For open bow shocks, the assymptotic angle. Denoted as $\theta_\infty$
+\end{itemize}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{ch-radii_ed}
+\caption{Schematic representation of the characteristic radii $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis $R_c$}
+\end{figure}
+
 %%% Local Variables:

### 2015-09-02 papers/Paper1/sec-conic.tex
Insert new figures and correct typographics errors
New figure for conic section

@@
 Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
-%Insert figures where needed
+\begin{figure}
+\includegraphics[width=\linewidth]{conic2}
+\label{fig:conic2}
+\caption{Graphic example of the increasing of the projected radius of curvature with inclination}
+\end{figure}
 
+\begin{figure}
+\includegraphics[width=\linewidth]{annotated}
+\caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
+the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
+an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
+\end{figure}
 %%% Local Variables:

### 2015-09-11 papers/Paper1/conic_fig.py
Editing some figures and text in conics section

@@ -25,10 +25,13 @@ if flag:
         trange = c.make_t_array()
         plt.plot(c.x(trange),c.y(trange),label =r"$\theta_c={:.0f}^\circ$".format(t))
 
-    plt.legend(loc="center left", fontsize='small')
+    plt.plot([0],[0],"b*")
+    plt.legend(loc="upper right", fontsize='x-small')
     plt.xlim(-5,2.1)
     plt.gca().set_aspect("equal",adjustable="box") #Trick to set equal axes found in stackoverflow.com
     plt.ylim(-4.1,4.1)
+    plt.axhline(xmin=0.05,xmax=0.95,color="black",lw=1.5,alpha=0.7)
+    plt.axvline(ymin=0.05,ymax=0.95,color="black",lw=1.5,alpha=0.7)
     plt.xlabel(r"$x/R_0$")
     plt.ylabel(r"$y/R_0$")
     plt.savefig("conic1.pdf")
@@ -51,8 +54,10 @@ else:
         ax.plot(ch.xt(i,t)/(ch.g(i)*np.cos(np.radians(i))),ch.yt(i,t)/(ch.g(i)*np.cos(np.radians(i))))
         Ap = ch.Aprime(i)
         ax.plot(Ap*np.cos(t)-Ap+1,Ap*np.sin(t),label=r"A'={:.2f}".format(Ap))
+        ax.plot([0],[0],"b*")
         ax.legend(loc="best",fontsize="small")
-        ax.grid()
+        plt.axhline(xmin=0.05,xmax=0.95,color="black",lw=1.5,alpha=0.7)
+        plt.axvline(ymin=0.05,ymax=0.95,color="black",lw=1.5,alpha=0.7)
         ax.set_xlabel(r"x'/R'_0")
         ax.set_ylabel(r"y'/R'_0")
         ax.set_xlim(-3,1.5)

### 2016-01-08 papers/Paper1/sec-application.tex
Insert Radius of curvature description for proplyd model
Advance in section 5

@@
 
+Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta$
+
 \begin{figure}
@@
 
+Expanding (\ref{eq:th1th}) until order 3th around $\theta=0$, we found for $\theta \ll 1$ that $\theta_1\simeq \beta^{1/2}\theta$.
+
+Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:
+
+\begin{align}
+R \simeq R_0 \left(1+\frac{1+2\beta^{1/2}}{6}\theta^2\right)
+\label{eq:R_approx}
+\end{align}
+
+Which lead us to derive the radius of curvature at the symmetry axis:
+
+\begin{equation}
+R_c = \frac{3}{2}R_0\left(1-\beta^{1/2}\right)^{-1}
+\label{eq:Rcurv}
+\end{equation}
+
+Equations (\ref{eq:r90}),  (\ref{eq:Rcurv}) and (27) from \citep{Canto:1996} are labeled as ``analytic i=0'' in figure (\ref{fig:rad-beta}).
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{rad-vs-beta}
+\caption{$R_0$, $R_c$ and $R_{90}$ vsersus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \citep{Canto:1996}
+are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}
+\label{fig:rad-beta}
+\end{figure*}
+
+Observationally, we can measure the projected radii. In order toestimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
+easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:radii-r0})
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{radii-vs-r0}
+\label{fig:radii-r0}
+\caption{Left: $R_c$ normalized with $R_0$ vs $R_0$ normalized with $D$. Right:$R_{90}$ normalized with $R_0$ vs $R_0$ normalized with $D$. Since the bow shock brightness decays 
+at the wings, it is more difficult to measure $R_{90}$. Along every single curve, $\beta$ is constant. The marks in the curves represents jumps of $15^\circ$ in inclination, and the most left 
+mark in each curve represent $i=0^\circ$}
+\end{figure*}
 %%% Local Variables:

### 2016-01-19 papers/Paper1/sec-application.tex
Minor corrections to article

@@
 originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
-The presure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
+The pressure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
 may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of $\theta^1~C~Ori$, which is highly supersonic $(M \sim 100)$.
@@
 \includegraphics[width=\linewidth]{r-beta}
-\caption{Bowshock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with  $D$
-to avoid dependances with this parameter. }
+\caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
+to avoid dependency with this parameter.}
 \end{figure}
@@
 
-Combinig equation (23) from \citep{Canto:1996} and  (\ref{eq:th1th}) evaluated at $\theta=\frac{\pi}{2}$, we can obtain $R_{90}$
+Combining equation (23) from \citep{Canto:1996} and  (\ref{eq:th1th}) evaluated at $\theta=\frac{\pi}{2}$, we can obtain $R_{90}$
 
@@
 \begin{figure*}
-\includegraphics[width=\linewidth]{rad-vs-beta}
+\begin{tabular}{ccc}
+\includegraphics[width=0.35\linewidth]{R0-b}&
+\includegraphics[width=0.35\linewidth]{Rc-b} &
+\includegraphics[width=0.35\linewidth]{R90-b}
+\end{tabular}
 \caption{$R_0$, $R_c$ and $R_{90}$ vsersus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \citep{Canto:1996}
@@
 
-Observationally, we can measure the projected radii. In order toestimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
+Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
 easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:radii-r0})
@@
 \begin{figure*}
-\includegraphics[width=\linewidth]{radii-vs-r0}
+\begin{tabular}{cc}
+\includegraphics[width=0.5\linewidth]{R90-R0-b}&
+\includegraphics[width=0.5\linewidth]{Rc-R0-b}
+\end{tabular}
 \label{fig:radii-r0}

### 2016-01-19 papers/Paper1/sec-conic.tex
Editing some figures and text in conics section
Make some figures 2-column using figure* environment
Minor corrections to article

@@
 \end{figure}
-Due to the similitudes between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
+Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
 
@@
 \caption{A whole set of conics with the same radius of curvature. The parameter $\theta_c$ is used as the equivalent of the excentricity. This angle is defined as positive for closed curves
-and negative forthe opened ones. An special case is $\theta_c=0$, which describes a parabola.}
+and negative for the opened ones. An special case is $\theta_c=0$, which describes a parabola.}
 \label{fig:conics-family}
@@
 Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
-\begin{figure}
-\includegraphics[width=\linewidth]{conic2}
+\begin{figure*}
+\includegraphics[width=0.8\linewidth]{conic2}
 \label{fig:conic2}
 \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
-\includegraphics[width=\linewidth]{annotated}
+The space parameter $A'$ vs $q'$ can be seen in figure (\ref{fig:Apqp}). In this figure is assumed that we know the intrinsic Radius of curvature and $R_0$, which is not the case with
+real observations.
+
+\begin{figure*}
+\includegraphics[width=0.9\linewidth]{annotated}
 \caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
@@
 an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
-\end{figure}
+\label{fig:Apqp}
+\end{figure*}
+
 %%% Local Variables:

### 2016-01-29 papers/Paper1/sec-application.tex
Last edit to application section

@@
 
- Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, which gives us the shell's shape. Also we can
-obtain a relation between $\theta$ and $\theta_1$
+If we apply the \citep{Canto:1996} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:
 
 \begin{align}
-\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
-\label{eq:th1th}
+\dot{M}_w &= \frac{\dot{M}_w^0}{3}\left(1-\cos^{3/2}\theta\right) \label{eq:dotprop} \\
+\dot{\Pi}_z &= \frac{1}{5}v_w \dot{M}_w^0\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
+\dot{\Pi}_r &= \frac{1}{2}v_w\dot{M}_w^0\left(\frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta\right) \label{eq:piz}\\
+\dot{J}_w = 0 \label{eq:jdot}
 \end{align}  
+The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \citep{Canto:1996}
+numerically in python code, we can obtain the bow shock shape $R(\theta)$, as illustred in figure (\ref{fig:r-beta}).
 
-Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta$
+% Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, which gives us the shell's shape. Also we can
+%obtain a relation between $\theta$ and $\theta_1$
+
+%\begin{align}
+%\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
+%\label{eq:th1th}
+%\end{align}
+
+%Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta$. The solution of this integral is an incomplete elliptical integral of the second kind:
+
+%\begin{align}
+%\int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta = \frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta
+%\end{align}
 
@@
 to avoid dependency with this parameter.}
+\label{fig:r-beta}
 \end{figure}
@@
 
+In order to find an analytic form of the characteristic radii $(R_0,R_c,R_{90})$, we may combine equations (\ref{eq:dotprop}) to (\ref{eq:jdot}) with (6) and (23) from \citep{Canto:1996}
+and obtain the following relation:
+
+\begin{align}
+\theta_1\cot\theta_1 -1 =  \frac{8}{5}\beta E\left(\frac{\theta}{2}|2\right)\cot\theta - \frac{4}{5}\beta
+\label{eq:th1th}
+\end{align}
+
 $R_0$ is obtained directly from equation (27) of \citep{Canto:1996} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
 
-Combining equation (23) from \citep{Canto:1996} and  (\ref{eq:th1th}) evaluated at $\theta=\frac{\pi}{2}$, we can obtain $R_{90}$
+We can obtain $R_{90}$ by the following process:
+Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:
 
 \begin{align}
-R_{90} \simeq \frac{\left(2.4\beta\right)^{1/2}}{1-0.8\beta}
+R_{90} &= D\tan\theta_{1,90} \\
+\theta_{1,90}\cot\theta_{1,90} &= 1-\frac{4}{5}\beta \label{eq:th190}
+\end{align}
+Where $\theta_{1,90}\equiv \theta_º(\frac{\pi}{2})$. Combining both equations we have:
+
+\begin{align}
+R_{90} &= D\frac{\theta_{1,90}}{1-\frac{4}{5}\beta} 
+\end{align}
+
+Expanding (\ref{eq:th190}) until 3rd order and solving for $\theta_{1,90}$:
+\begin{align}
+\theta_{1,90} \simeq \left(\frac{2.4\beta}{1-0.8\beta}\right)^{1/2} \\
+R_{90} \simeq \left(\frac{2.4\beta}{(1-0.8\beta)^3}\right)^{1/2}
 \label{eq:r90}
 \end{align}
+%%%% Here we go in edition
 
-Expanding (\ref{eq:th1th}) until order 3th around $\theta=0$, we found for $\theta \ll 1$ that $\theta_1\simeq \beta^{1/2}\theta$.
+Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 2nd order for small $\theta$ values to find that for such values
+$\theta_1 = \beta^{1/2}\theta$
 

### 2016-02-01 papers/Paper1/sec-application.tex
Advance in section writing

@@
 Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
-easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:radii-r0})
+easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure %(\ref{fig:radii-r0})
 
-\begin{figure*}
-\begin{tabular}{cc}
-\includegraphics[width=0.5\linewidth]{R90-R0-b}&
-\includegraphics[width=0.5\linewidth]{Rc-R0-b}
-\end{tabular}
-\label{fig:radii-r0}
-\caption{Left: $R_c$ normalized with $R_0$ vs $R_0$ normalized with $D$. Right:$R_{90}$ normalized with $R_0$ vs $R_0$ normalized with $D$. Since the bow shock brightness decays 
-at the wings, it is more difficult to measure $R_{90}$. Along every single curve, $\beta$ is constant. The marks in the curves represents jumps of $15^\circ$ in inclination, and the most left 
-mark in each curve represent $i=0^\circ$}
-\end{figure*}
+\subsection{Observational work}
+
+We measured the Characteristic radii in Orion Nebula proplyds from observations in [OIII] from the Hubble Space Telescope (HST).
+
+\subsubsection{Metodology}
+
+Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
+bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
+is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
+this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions.
+The figure ()
+shows a representation ofthe metodology described.
+
+%\begin{figure}
+%\end{figure}
+
+%\begin{figure*}
+%\begin{tabular}{cc}
+%\includegraphics[width=0.5\linewidth]{R90-R0-b}&
+%\includegraphics[width=0.5\linewidth]{Rc-R0-b}
+%\end{tabular}
+%\label{fig:radii-r0}
+%\caption{Left: $R_c$ normalized with $R_0$ vs $R_0$ normalized with $D$. Right:$R_{90}$ normalized with $R_0$ vs $R_0$ normalized with $D$. Since the bow shock brightness decays 
+%at the wings, it is more difficult to measure $R_{90}$. Along every single curve, $\beta$ is constant. The marks in the curves represents jumps of $15^\circ$ in inclination, and the most left 
+%mark in each curve represent $i=0^\circ$}
+%\end{figure*}
+
 %%% Local Variables:

### 2016-02-01 papers/Paper1/proplyds-table.tex
table with observations. still incomplete

\begin{table}
\begin{tabular}{|c|c|c|c|c|c|c|}
Proplyd & $R_0/D$ (1) & $R_0/D $ (2) & $R_0/D$ &$R_c/D$ (1) & $R_c/D $ (2)  & $R_c/D$  & $R_c/R_0$ \hline \\
LV2 & & & & & & & 
\end{tabular}
\end{table}

### 2016-02-02 papers/Paper1/proplyds-table.tex
Advance in completion

@@
 \begin{table}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-Proplyd & $R_0/D$ (1) & $R_0/D $ (2) & $R_0/D$ &$R_c/D$ (1) & $R_c/D $ (2)  & $R_c/D$  & $R_c/R_0$ \hline \\
-LV2 & & & & & & & 
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+Proplyd & $R_0/D$ (1) & $R_0/D $ (2) & $R_0/D$ & $R_c/D$ (1) & $R_c/D $ (2)  & $R_c/D$  & $R_c/R_0$ \\
+LV2     &   0.30  & 0.4  & 0.35  $\pm$ 0.05    & & & & \\
+LV3     &   0.58  & 0.55 & 0.565 $\pm$ 0.015   & & & & \\
+LV4     &   0.35  & 0.37 & 0.36  $\pm$ 0.01    & & & & \\
+LV5     &   0.41  & 0.33 & 0.37  $\pm$ 0.04    & & & & \\
+177-341 &   0.17  & 0.2  & 0.185 $\pm$ 0.015   & & & & \\
+167-328 &   0.15  & 0.14 & 0.145 $\pm$ 0.005   & & & & 
 \end{tabular}

### 2016-02-02 papers/Paper1/sec-application.tex
Insert proplyds measurements table
Change \include to \input
\include is only useful for including whole chapters in a very large
document - see
http://tex.stackexchange.com/questions/246/when-should-i-use-input-vs-include
Added references to introduction

@@
 We can obtain $R_{90}$ by the following process:
-Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:
+Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{Canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:
 
@@
 The figure ()
-shows a representation ofthe metodology described.
+shows a representation of the metodology described.
 
+\input{proplyds-table}
 %\begin{figure}

### 2016-02-02 papers/Paper1/sec-intro.tex
Added references to introduction

--- 2015-06-29 papers/Paper1/sec-intro.tex
@@
 types of curved shocks that have approximate cylindrical symmetry.
+Instead of a solid body, astrophysical examples usually involve the
+interaction of \emph{two} supersonic flows, such as the situation of a
+stellar wind emitted by a star that moves supersonically through the
+interstellar medium \citep{van-Buren:1988a, Kobulnicky:2010a,
+  van-Marle:2011a, Mackey:2012b, Mackey:2015a}.  In such cases, two
+shocks are generally produced, one in each flow.  Sometimes,
+especially in heliospheric studies \citep{Zank:1999a, Scherer:2014a}, the
+term ``bow shock'' is reserved for the shock in the ambient medium,
+with the other being called the ``wind shock'' or ``termination
+shock''.  However, in other contexts such as colliding wind binaries
+\citep{Stevens:1992a, Gayley:2009a} such a distinction is not so
+useful.  In this paper we use the term ``bow shock'' in a more general
+sense to refer to either of the two shocks, or to the shocked gas in
+between them.
 

### 2016-02-04 papers/Paper1/proplyds-table.tex
Added references to introduction
Finished and transposed table

--- 2016-02-01 papers/Paper1/proplyds-table.tex
@@
-\begin{table}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-Proplyd & $R_0/D$ (1) & $R_0/D $ (2) & $R_0/D$ &$R_c/D$ (1) & $R_c/D $ (2)  & $R_c/D$  & $R_c/R_0$ \hline \\
-LV2 & & & & & & & 
+ \begin{table*}
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+Proplyd & LV2 & LV3 & LV4  & LV5 & 177-341 & 167-328 \\
+$R_c/D$ (1) & 0.30 & 0.58  & 0.35 & 0.41 & 0.17 & 0.15 \\
+$R_c/D$ (2) & 0.4 & 0.55 & 0.37 & 0.33 & 0.2 & 0.14    \\
+$R_c/D$     & 0.35 $\pm$ 0.05 & 0.565 $\pm$ 0.015 & 0.36  $\pm$ 0.01  & 0.37 $\pm$ 0.04 & 0.185 $\pm$ 0.015 & 0.145 $\pm$ 0.005 \\
+$R_0/D$ (1) & 0.24 & 0.34 & 0.19 & 0.21 & 0.13 & 0.1 \\
+$R_0/D$ (2) & 0.235 & 0.348  & 0.184 & 0.206 & 0.129 & 0.097 \\
+$R_0/D$     & 0.238 $\pm$ 0.003 & 0.344 $\pm$ 0.004 & 0.187 $\pm$ 0.003 & 0.208 $\pm$ 0.002 & 0.130 $\pm$ $5\times 10^{-4}$ & 0.099 $\pm$ 0.002 \\
+$R_c/R_0$ & 1.471 $\pm$ 0.211 & 1.642 $\pm$ 0.048 & 1.925 $\pm$ 0.062 & 1.779 $\pm$ 0.193 & 1.423 $\pm$ 0.116 & 1.465 $\pm$ 0.059
 \end{tabular}
-\end{table}
+\caption{Characteristic Radii measurements for a sample of proplyds. The (1) mark refers to the fit restricting
+the center of the circle to be in the symmetry axis, while (2) refers to the fit without any restriction. The
+measurements without any mark were calculated as the mean of the two fits.}
+\end{table*}

### 2016-02-04 papers/Paper1/sec-application.tex
advance on section writing

--- 2016-02-01 papers/Paper1/sec-application.tex
@@
 
-We measured the Characteristic radii in Orion Nebula proplyds from observations in [OIII] from the Hubble Space Telescope (HST).
+We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$.
+The observations
 

### 2016-02-05 papers/Paper1/sec-application.tex
Advance in section 5 writing.

@@
 We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$.
-The observations
+The proposal for these observations were done by  Jogee, S.
+in 2004 with calibration purposes but (he never published anything using expliciyly these observations).
+% We must check if this phrase should be included
+Neverthless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.
 
@@
 this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions.
-The figure ()
-shows a representation of the metodology described.
+The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described.
+Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lessim theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.
+Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure ()).
+
+\begin{figure*}
+\begin{tabular}{cc}
+\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
+\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4}
+\end{tabular}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{177-341-will-anota}
+\caption{Schematic example of the observational measures used. We don't use $R_\theta$ any longer, but instead the radius of curvature}
+\label{fig:radii-measures-example}
+\end{figure}
 
 \input{proplyds-table}
+
 %\begin{figure}

### 2016-02-06 papers/Paper1/sec-application.tex
Including circle fit figures to paper

@@
 The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described.
-Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lessim theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.
-Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure ()).
+Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.
+Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure (\ref{fig:char-radii-obs})).
 
@@
 \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
-\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4}
+\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4} \\
+\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV5} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV5} \\
+\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-167-328} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-167-328} \\
+\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-502epositions-177-341} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-177-341}
 \end{tabular}
+\label{fig:char-radii-obs}
+\caption{Fits to the shell's shapes.
+In the left side we have the fits without any restrictions.
+In the right side we have the fits restricting the center of the circle to be in $y=0$.
+This data is summarized in table (\ref{tab:proplyds})}
 \end{figure*}

### 2016-02-08 papers/Paper1/sec-application.tex
Fixed typo and cross-ref and citation errors
Please check that document compiles cleanly before each commit

@@
 % We must check if this phrase should be included
-Neverthless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.
+Nevertheless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.
 

### 2016-02-08 papers/Paper1/proplyds-table.tex
Fixed typo and cross-ref and citation errors
Please check that document compiles cleanly before each commit
Edit table's apperarance

--- 2016-02-01 papers/Paper1/proplyds-table.tex
@@
-\begin{table}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-Proplyd & $R_0/D$ (1) & $R_0/D $ (2) & $R_0/D$ &$R_c/D$ (1) & $R_c/D $ (2)  & $R_c/D$  & $R_c/R_0$ \hline \\
-LV2 & & & & & & & 
+ \begin{table*}
+\begin{tabular}{c|cccccc}\hline
+Proplyd & LV2 & LV3 & LV4  & LV5 & 177-341 & 167-328 \\\hline
+$R_c/D$ (1) & 0.30 & 0.58  & 0.35 & 0.41 & 0.17 & 0.15 \\
+$R_c/D$ (2) & 0.4 & 0.55 & 0.37 & 0.33 & 0.2 & 0.14    \\
+$R_c/D$     & 0.35 $\pm$ 0.05 & 0.565 $\pm$ 0.015 & 0.36  $\pm$ 0.01  & 0.37 $\pm$ 0.04 & 0.185 $\pm$ 0.015 & 0.145 $\pm$ 0.005 \\
+$R_0/D$ (1) & 0.24 & 0.34 & 0.19 & 0.21 & 0.13 & 0.1 \\
+$R_0/D$ (2) & 0.235 & 0.348  & 0.184 & 0.206 & 0.129 & 0.097 \\
+$R_0/D$     & 0.238 $\pm$ 0.003 & 0.344 $\pm$ 0.004 & 0.187 $\pm$ 0.003 & 0.208 $\pm$ 0.002 & 0.130 $\pm$ $5\times 10^{-4}$ & 0.099 $\pm$ 0.002 \\
+$R_c/R_0$ & 1.471 $\pm$ 0.211 & 1.642 $\pm$ 0.048 & 1.925 $\pm$ 0.062 & 1.779 $\pm$ 0.193 & 1.423 $\pm$ 0.116 & 1.465 $\pm$ 0.059 
 \end{tabular}
-\end{table}
+\caption{Characteristic Radii measurements for a sample of proplyds. The (1) mark refers to the fit restricting
+the center of the circle to be in the symmetry axis, while (2) refers to the fit without any restriction. The
+measurements without any mark were calculated as the mean of the two fits.}
+\label{tab:proplyds}
+\end{table*}

### 2016-02-11 papers/Paper1/sec-intro.tex
More on bow shocks for intro
Mention jet-driven bow shocks.  Add a lot of references. Also first para
of abstract

@@
 shocks are generally produced, one in each flow.  Sometimes,
-especially in heliospheric studies \citep{Zank:1999a, Scherer:2014a}, the
-term ``bow shock'' is reserved for the shock in the ambient medium,
-with the other being called the ``wind shock'' or ``termination
-shock''.  However, in other contexts such as colliding wind binaries
-\citep{Stevens:1992a, Gayley:2009a} such a distinction is not so
-useful.  In this paper we use the term ``bow shock'' in a more general
-sense to refer to either of the two shocks, or to the shocked gas in
-between them.
+especially in heliospheric studies \citep{Zank:1999a, Scherer:2014a},
+the term ``bow shock'' is reserved for the shock in the ambient
+medium, with the other being called the ``wind shock'' or
+``termination shock''.  However, in other contexts such as colliding
+wind binaries \citep{Stevens:1992a, Gayley:2009a} such a distinction
+is not so useful.
 
@@
 %%
+
+A further class of astrophysical bow shock is driven by highly
+collimated, supersonic jets of material, such as the Herbig Haro
+objects \citep{Schwartz:1978b, Hartigan:1987a} that are powered by
+jets from young stars or protostars.  Additional examples are seen in
+planetary nebulae \citep{Phillips:2010a, Meaburn:2013a}, active
+galaxies \citep{Wilson:1987a}, and in galaxy clusters
+\citep{Markevitch:2002a}.  In the jet-driven case, the term ``working
+surface'' is often applied to the entire structure comprising the two
+shocks plus the shocked gas in between them, separated by a
+\textit{contact discontinuity}.  The working surface may be due to the
+interaction of the jet with a relatively quiescent medium, or may be an
+``internal working surface'' within the jet that is due to
+supersonic temporal variations in the flow velocity
+\citep{Raga:1990a}.
+
+In empirical studies the relationship between these theoretical
+constructs and the observed emission structures is not always clear.
+In such cases the term ``bow shock'' is often used in a more general
+sense to refer to the entire arc of emission.
+
+Bow shocks from pulsars and neutron stars
+\citep{Cordes:1993a, Brownsberger:2014a}.
+
+Terminology: head, wings, nose, apex, limb, etc.
+
+Radiative versus non-radiative shocks.
 

### 2016-02-12 papers/Paper1/sec-application.tex
Split figure with proplyds fits into two

@@
 \end{tabular}
-\caption{$R_0$, $R_c$ and $R_{90}$ vsersus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \citep{Canto:1996}
+\caption{$R_0$, $R_c$ and $R_{90}$ versus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \citep{Canto:1996}
 are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}
@@
 The proposal for these observations were done by  Jogee, S.
-in 2004 with calibration purposes but (he never published anything using expliciyly these observations).
+in 2004 with calibration purposes but (he never published anything using explicitly these observations).
 % We must check if this phrase should be included
@@
 \subsubsection{Metodology}
-
 Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
@@
 \begin{tabular}{cc}
-\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
-\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4} \\
-\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV5} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV5} \\
-\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-167-328} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-167-328} \\
-\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-502epositions-177-341} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-177-341}
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-502epositions-LV2} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-LV2} \\
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4}
 \end{tabular}
@@
 This data is summarized in table (\ref{tab:proplyds})}
+\end{figure*}
+
+\begin{figure*}
+\begin{tabular}{cc}
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV5} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV5} \\
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-502epositions-177-341} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-177-341}\\
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-167-328} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-167-328}
+\end{tabular}
+\label{fig:char-radii-obs-2}
+\caption{Continuation of figure (\ref{fig:char-radii-obs})}
 \end{figure*}

### 2016-02-16 papers/Paper1/sec-application.tex
Enhance metodology description.
Include (Robberto 2005) comparison

@@
 The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described.
-Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.
+Our first goal was comparing measurements of $(R_0,R_{90})$ of the LV group of proplyds in mid infrared by \citep{Robberto:2005} against observations in [OIII] with better angular resolution but less contrast against
+the background.
+In \citep{Robberto:2005} they compare their observations with shells obtained with the \citep{Canto:1996} two winds interactions formalism.
+They found no concordance between the model and observations.
+We attempted to redo the measurements with better resolution observations.
+We found quickly that we cannot measure $R_{90}$ in a reliable way since the shell's brightness decays toward the wings.
+Also, we are using a more sophisticated model where the proplyd's wind density decays as $n \propto \cos {1/2}\theta$ instead of an isotropic wind.
+A better replacement of $R_{90}$ is the radius of curvature, defined as the radius of the circle that fits the observations, because always is measurable.
+Figures (\ref{fig:char-radii-obs}) and (\ref{fig:char-radii-obs-2}) show our measurements of the radius of curvature for the LV group, with exception of LV1, which actually is a binary proplyd, thus our model is not adequate in this case.
+Also we include the proplyds 167-328 and 177-341 (HST1) which are close enough to $\theta^1~\mathrm{C~Ori}$ to be influenced by it stellar wind.
+Our results show a better concordance (but still not perfect) between models and observations, as shown in figure (\ref{fig:prop-shell-err}).
+A possible cause of the discrepancy may be that the \citep{Canto:1996} model assumes that the interacting winds are hypersonic in such way that the shocked gas can be considered as a bidimensional surface.
+In practice, the bow shock has a finite width, which can afect the apparent shape due to projection effects
+
+\begin{figure}
+\includegraphics[width=0.6\linewidth]{proplyd-shell-R0-Rc-errors-1}
+\label{fig:prop-shell-err}
+\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$.
+The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$.
+The dots represent separations in inclination of $15^{\circ}$.
+The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$.
+Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite.}
+\end{figure}
+%Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.
 Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure (\ref{fig:char-radii-obs})).

### 2016-02-19 papers/Paper1/sec-application.tex
Make Figure 9 much bigger
Insert new figure

@@
 
-\begin{figure}
-\includegraphics[width=0.6\linewidth]{proplyd-shell-R0-Rc-errors-1}
+\begin{figure*}
+\begin{tabular}{cc}
+\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-1} &
+\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-new}
+\end{tabular}
 \label{fig:prop-shell-err}
@@
 The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$.
-Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite.}
-\end{figure}
+Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite.
+Right side: The same}
+\end{figure*}
 %Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.

### 2016-03-03 papers/Paper1/sec-application.tex
Inserting new figures in article

@@
 \end{align}
-%%%% Here we go in edition
 
@@
 this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions.
-The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described.
+$R_0$ is calculated as the distance between the proplyd position and the bow shock in a line which is also included the
+center of curvature. The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described. 
 Our first goal was comparing measurements of $(R_0,R_{90})$ of the LV group of proplyds in mid infrared by \citep{Robberto:2005} against observations in [OIII] with better angular resolution but less contrast against
@@
 Figures (\ref{fig:char-radii-obs}) and (\ref{fig:char-radii-obs-2}) show our measurements of the radius of curvature for the LV group, with exception of LV1, which actually is a binary proplyd, thus our model is not adequate in this case.
-Also we include the proplyds 167-328 and 177-341 (HST1) which are close enough to $\theta^1~\mathrm{C~Ori}$ to be influenced by it stellar wind.
+Also we include the proplyds 167-328, 169-338, 177-341 (HST1), 189-339 and 180-331 which are close enough to $\theta^1~\mathrm{C~Ori}$ to be influenced by it stellar wind.
 Our results show a better concordance (but still not perfect) between models and observations, as shown in figure (\ref{fig:prop-shell-err}).
@@
 \includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-1} &
-\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-new}
+\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-new}
 \end{tabular}
@@
 
+\begin{figure*}
+\begin{tabular}{cc}
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3b-169-338} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3b-169-338} \\
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3b-189-329} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3b-189-329}\\
+\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-180-331} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-180-331}
+\end{tabular}
+\label{fig:char-radii-obs-3}
+\caption{Continuation of figure (\ref{fig:char-radii-obs}), (new sample)}
+\end{figure*}
+
 \begin{figure}

### 2016-03-31 papers/Paper1/proplyds-table.tex
Updated methodology section. Table updated

--- 2016-02-02 papers/Paper1/proplyds-table.tex
@@
-\begin{table}
-\begin{tabular}{|c|c|c|c|c|c|c|c|}
-Proplyd & $R_0/D$ (1) & $R_0/D $ (2) & $R_0/D$ & $R_c/D$ (1) & $R_c/D $ (2)  & $R_c/D$  & $R_c/R_0$ \\
-LV2     &   0.30  & 0.4  & 0.35  $\pm$ 0.05    & & & & \\
-LV3     &   0.58  & 0.55 & 0.565 $\pm$ 0.015   & & & & \\
-LV4     &   0.35  & 0.37 & 0.36  $\pm$ 0.01    & & & & \\
-LV5     &   0.41  & 0.33 & 0.37  $\pm$ 0.04    & & & & \\
-177-341 &   0.17  & 0.2  & 0.185 $\pm$ 0.015   & & & & \\
-167-328 &   0.15  & 0.14 & 0.145 $\pm$ 0.005   & & & & 
+ \begin{table*}
+\begin{tabular}{c|ccccccccc}\hline
+Proplyd & LV2 & LV2b & LV3 & LV4  & LV5 & 177-341 & 168-328 & 169-338 & 180-331\\\hline
+$D (\")$ &7.76 & 7.21 &6.89 & 6.2 & 9.55 & 25.65 & 6.83 & 16.43 & 25.07 \\
+$R_c/D$  & 0.23  & 0.19& 0.61  & 0.5  & 0.34  & 0.18  & 0.22 & 0.09 & 0.09\\
+$R_0/D$  & 0.32 & 0.1 & 0.34 & 0.19 & 0.21 & 0.14 & 0.15 & 0.06 & 0.07\\
+$R_c/R_0$ & 0.73 & 2.00 & 1.83 & 2.68  & 1.57 & 1.22 & 1.47 & 1.46 & 1.30  
 \end{tabular}
-\end{table}
+\caption{Characteristic Radii measurements for a sample of proplyds. %Enhance description when more rows were included
+}
+
+\label{tab:proplyds}
+\end{table*}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "proplyd-bowshocks.tex"
+%%% End:

### 2016-03-31 papers/Paper1/sec-application.tex
Updated methodology section. Table updated

--- 2016-02-19 papers/Paper1/sec-application.tex
@@
 
-\subsection{Observational work}
+\subsection{Observational data}
 
-We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$.
+%We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$.
 The proposal for these observations were done by  Jogee, S.
@@
 % We must check if this phrase should be included
-Nevertheless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.
+%Nevertheless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.
 
 \subsubsection{Metodology}
-Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
-bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
-is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
-this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions.
-The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described.
-Our first goal was comparing measurements of $(R_0,R_{90})$ of the LV group of proplyds in mid infrared by \citep{Robberto:2005} against observations in [OIII] with better angular resolution but less contrast against
-the background.
-In \citep{Robberto:2005} they compare their observations with shells obtained with the \citep{Canto:1996} two winds interactions formalism.
+Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta^1 ~C$.
+For the shell's position, the marks were placed in the outer border of each shock.
+The number of marks used in each shell varies with shell's size, and with our confidence with our measurements.
+Thus, we used few points in small bow shocks and/our the bow shock's outer shell is not well defined.
+The distance $D$ is measured as the distance between the position of $\theta^1 ~C~Ori$ and each proplyd's position.
+The radius of curvature $R_c$ is measured as the radius of the
+best circle fit of all the data points taken for each proplyd's shell.
+Finally, we measure $R_0$ as the distance between the proplyd's position and the circle's border in the line which include the center of curvature.
+To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, adn made 10 sets of randomly chosen removed marks, and made the measurements again to see how much these ``variations'' deviates from the original data.
+The results are summarized and explained
+in figure (\ref{fig:prop-shell-rad})
+%is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
+%this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions.
+$R_0$ is calculated as the distance between the proplyd position and the bow shock in a line which is also included the
+%center of curvature. The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described. 
+%Our first goal was comparing measurements of $(R_0,R_{90})$ of the LV group of proplyds in mid infrared by \citep{Robberto:2005} against observations in [OIII] with better angular resolution but less contrast against
+%the background.
+%In \citep{Robberto:2005} they compare their observations with shells obtained with the \citep{Canto:1996} two winds interactions formalism.
 They found no concordance between the model and observations.
@@
 Also, we are using a more sophisticated model where the proplyd's wind density decays as $n \propto \cos {1/2}\theta$ instead of an isotropic wind.
-A better replacement of $R_{90}$ is the radius of curvature, defined as the radius of the circle that fits the observations, because always is measurable.
+%A better replacement of $R_{90}$ is the radius of curvature, defined as the radius of the circle that fits the observations, because always is measurable.
 Figures (\ref{fig:char-radii-obs}) and (\ref{fig:char-radii-obs-2}) show our measurements of the radius of curvature for the LV group, with exception of LV1, which actually is a binary proplyd, thus our model is not adequate in this case.
-Also we include the proplyds 167-328 and 177-341 (HST1) which are close enough to $\theta^1~\mathrm{C~Ori}$ to be influenced by it stellar wind.
-Our results show a better concordance (but still not perfect) between models and observations, as shown in figure (\ref{fig:prop-shell-err}).
+Also we include the proplyds 167-328, 169-338, 177-341 (HST1), 189-339 and 180-331 which are close enough to $\theta^1~\mathrm{C~Ori}$ to be influenced by it stellar wind.
+%Our results show a better concordance (but still not perfect) between models and observations, as shown in figure (\ref{fig:prop-shell-err}).
 A possible cause of the discrepancy may be that the \citep{Canto:1996} model assumes that the interacting winds are hypersonic in such way that the shocked gas can be considered as a bidimensional surface.
@@
 \includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-1} &
-\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-new}
 \end{tabular}
-\label{fig:prop-shell-err}
+\label{fig:prop-shell-rad}
 \caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$.
@@
 
-\begin{figure*}
-\begin{tabular}{cc}
-\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-502epositions-LV2} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-LV2} \\
-\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
-\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4}
-\end{tabular}
-\label{fig:char-radii-obs}
-\caption{Fits to the shell's shapes.
+%\begin{figure*}
+%\begin{tabular}{cc}
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-502epositions-LV2} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-LV2} \\
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4}
+%\end{tabular}
+%\label{fig:char-radii-obs}
+%\caption{Fits to the shell's shapes.
 In the left side we have the fits without any restrictions.
@@
 This data is summarized in table (\ref{tab:proplyds})}
-\end{figure*}
+%\end{figure*}
 
-\begin{figure*}
-\begin{tabular}{cc}
-\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV5} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV5} \\
-\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-502epositions-177-341} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-177-341}\\
-\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-167-328} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-167-328}
-\end{tabular}
-\label{fig:char-radii-obs-2}
-\caption{Continuation of figure (\ref{fig:char-radii-obs})}
-\end{figure*}
+%\begin{figure*}
+%\begin{tabular}{cc}
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV5} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV5} \\
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-502epositions-177-341} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-177-341}\\
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-167-328} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-167-328}
+%\end{tabular}
+%\label{fig:char-radii-obs-2}
+%\caption{Continuation of figure (\ref{fig:char-radii-obs})}
+%\end{figure*}
+%
+%\begin{figure*}
+%\begin{tabular}{cc}
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3b-169-338} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3b-169-338} \\
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3b-189-329} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3b-189-329}\\
+%\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-180-331} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-180-331}
+%\end{tabular}
+%\label{fig:char-radii-obs-3}
+%\caption{Continuation of figure (\ref{fig:char-radii-obs}), (new sample)}
+%\end{figure*}
 
-\begin{figure}
-\includegraphics[width=\linewidth]{177-341-will-anota}
-\caption{Schematic example of the observational measures used. We don't use $R_\theta$ any longer, but instead the radius of curvature}
-\label{fig:radii-measures-example}
-\end{figure}
+%\begin{figure}
+%\includegraphics[width=\linewidth]{177-341-will-anota}
+%\caption{Schematic example of the observational measures used. We don't use $R_\theta$ any longer, but instead the radius of curvature}
+%\label{fig:radii-measures-example}
+%\end{figure}
 

### 2016-04-01 papers/Paper1/proplyds-table.tex
Update to table. Update to applications section

@@
 Proplyd & LV2 & LV2b & LV3 & LV4  & LV5 & 177-341 & 168-328 & 169-338 & 180-331\\\hline
-$D (\")$ &7.76 & 7.21 &6.89 & 6.2 & 9.55 & 25.65 & 6.83 & 16.43 & 25.07 \\
+$D (\arcsec)$ &7.76 & 7.21 &6.89 & 6.2 & 9.55 & 25.65 & 6.83 & 16.43 & 25.07 \\
 $R_c/D$  & 0.23  & 0.19& 0.61  & 0.5  & 0.34  & 0.18  & 0.22 & 0.09 & 0.09\\

### 2016-04-01 papers/Paper1/sec-application.tex
Update to table. Update to applications section

@@
 
-\subsubsection{Metodology}
-Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta^1 ~C$.
-For the shell's position, the marks were placed in the outer border of each shock.
+\subsubsection{Methodology}
+Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta^1 ~C$. For the shell's position, the marks were placed in the outer border of each shock. 
 The number of marks used in each shell varies with shell's size, and with our confidence with our measurements.
-Thus, we used few points in small bow shocks and/our the bow shock's outer shell is not well defined.
-The distance $D$ is measured as the distance between the position of $\theta^1 ~C~Ori$ and each proplyd's position.
-The radius of curvature $R_c$ is measured as the radius of the
-best circle fit of all the data points taken for each proplyd's shell.
-Finally, we measure $R_0$ as the distance between the proplyd's position and the circle's border in the line which include the center of curvature.
-To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, adn made 10 sets of randomly chosen removed marks, and made the measurements again to see how much these ``variations'' deviates from the original data.
-The results are summarized and explained
-in figure (\ref{fig:prop-shell-rad})
+Thus, we used few points in small bow shocks and/our the bow shock's outer shell is not well defined. The distance $D$ is measured as the distance between the position of $\theta^1 ~C~Ori$ 
+and each proplyd's position. The radius of curvature $R_c$ is measured as the radius of the 
+best circle fit of all the data points taken for each proplyd's shell. Finally, we measure $R_0$ as the distance between the proplyd's position and the circle's border in the line which 
+include the center of curvature.
+To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, adn made 10 sets of randomly chosen removed marks, and made the measurements again to 
+see how much these ``variations'' deviates from the original data. The results are summarized and explained in figure (\ref{fig:prop-shell-rad})
 %is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
@@
 \begin{figure*}
-\begin{tabular}{cc}
-\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-1} &
-\end{tabular}
+\includegraphics[width=\linewidth]{LV-full-field-annotated.png}
+\caption{DS9 shell marks over ONC. The circles mark each proplys position, while the cyan crosses delineate each bow shock and the red X marks the position of $\theta^1 ~C~Ori$. 
+The black circles only schematize a circle fit to each shell but they actually are not the real measurements.}
+\label{fig:radii-measures-example}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.45\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
 \label{fig:prop-shell-rad}
-\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$.
-The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$.
-The dots represent separations in inclination of $15^{\circ}$.
-The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$.
-Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite.
-Right side: The same}
+\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. 
+The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
+curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
+with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
+%Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same
+}
 \end{figure*}
@@
 
-%\begin{figure}
-%\includegraphics[width=\linewidth]{177-341-will-anota}
-%\caption{Schematic example of the observational measures used. We don't use $R_\theta$ any longer, but instead the radius of curvature}
-%\label{fig:radii-measures-example}
-%\end{figure}
-
 \input{proplyds-table}

### 2016-04-05 papers/Paper1/sec-application.tex
Add figures for individual fits for three sources
and two variations

@@
 
+\begin{figure*}
+\begin{tabular}{ccc}
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV5} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV5} &
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV5} \\
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
+\end{tabular}
+\label{fig:char-radii-obs}
+\caption{Examples of shell's circle fit for three sources:177-341, LV5 and 168-328.
+In the left side, for each source, the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing a
+fraction of the marks, but always keeping at least four points.
+177-341 is an example where the measurementsonly change very slightly from one variation to other.
+While with 168-328 the changes are more noticeable.
+LV5 is an intermediate case.}
+\end{figure*}
+
 \input{proplyds-table}

### 2016-04-08 papers/Paper1/sec-application.tex
Adjust size of proplyd figure

@@
 Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
-easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure %(\ref{fig:radii-r0})
+easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
+
+Although there is an analytical form for the radius of curvature, for $i\ne 0$ there is not an intuitive form for  $R'_c$.
+Plus, in practice, we are working with discret arrays, so, when transforming the shell's coordinates to the primed system, we almost certainly will miss the $\theta'=0$ point, which
+should allow us to estimate the radii $(R'_0,R'_c)$, the first with equation (\ref{eq:Rpar}) and the second with the mathematical definition of the radius of curvature using the primed coordinates.
+Insted, we estimate $R'_0$ as the projected radius with the value of $\theta'$ closest to zero, and
+$R'_c$ doing a least square fit to the points such as $\theta' \leq 45^\circ$.
+This restriction allows to obtain the best estimation of the radius of curvature at the nos of the shell.
+A lower cuttoff may undestimate $R'_c$ while higher cutoffs might be unaccurate, too.
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.45\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
+\begin{figure}
+\includegraphics[width=\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
 \label{fig:prop-shell-rad}
@@
 }
-\end{figure*}
+\end{figure}
 %Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.
@@
   \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV5} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV5} &
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV5} \\
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV4} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV4} &
+  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV4} \\
   \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
@@
 177-341 is an example where the measurementsonly change very slightly from one variation to other.
-While with 168-328 the changes are more noticeable.
-LV5 is an intermediate case.}
+While with 168-328 the changes are a little more noticeable.
+LV4 is a case where the most external points are crucial
+in the determination of the radius of curvature}
 \end{figure*}

### 2016-04-08 papers/Paper1/sec-application.tex
Re-running program to generate variant fits

@@
 \begin{figure*}
-\begin{tabular}{ccc}
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV4} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV4} &
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV4} \\
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
-  \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[width=0.3\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
+\begin{tabular}{@{}c@{}c@{}c@{}}
+  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
+  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
+  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV5} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV5} &
+  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV5} \\
+  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
+  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
 \end{tabular}

### 2016-04-08 papers/Paper1/sec-application.tex
Improve figure and caption for circle fit vars

@@
 \begin{figure*}
+  \setkeys{Gin}{width=0.33\linewidth, trim=10 30 55 62.5}
 \begin{tabular}{@{}c@{}c@{}c@{}}
-  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
-  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
-  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV5} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV5} &
-  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV5} \\
-  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
-  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
+
+All points & First sub-sample & Second sub-sample \\ \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
+  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
+  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV4} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp05/LV-bowshocks-xyfancy-positionssamp05-LV4} &
+  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV4} \\
+  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
+  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
 \end{tabular}
 \label{fig:char-radii-obs}
-\caption{Examples of shell's circle fit for three sources:177-341, LV5 and 168-328.
-In the left side, for each source, the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing a
-fraction of the marks, but always keeping at least four points.
-177-341 is an example where the measurementsonly change very slightly from one variation to other.
-While with 168-328 the changes are a little more noticeable.
-LV4 is a case where the most external points are crucial
-in the determination of the radius of curvature}
+\caption{Examples of systematic uncertainties in the circle fits to
+  the shell shapes for three sources (top to bottom rows): 177-341,
+  LV4 and 168-328.  The left hand column shows the fit to all of the
+  points identified on the shell border, where the number and spacing
+  of the points is a subjective measure of our confidence in tracing
+  the edge of each shell. The remaining two columns show fits to
+  randomly selected sub-samples of 2/3 of the points for each shell.}
 \end{figure*}
+
+In the better observed shells such as 177-341 (top row), the circle
+fits are relatively robust to removing points, resulting in little
+variation between the subsamples.
+
+In the left side, for each source, the fit is done using all the ds9
+marks, while in the middle and the right we show two variations
+removing a fraction of the marks, but always keeping at least four
+points. 177-341 is an example where the measurements only change very
+slightly from one variation to other. While with 168-328 the changes
+are a little more noticeable. LV4 is a case where the most external
+points are crucial in the determination of the radius of curvature.
 

### 2016-04-12 papers/Paper1/sec-application.tex
Reaccomodation of text and comments

@@
 include the center of curvature.
-To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, adn made 10 sets of randomly chosen removed marks, and made the measurements again to 
-see how much these ``variations'' deviates from the original data. The results are summarized and explained in figure (\ref{fig:prop-shell-rad})
+To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, and made 10 sets of randomly chosen removed marks, and made the measurements again to 
+see how much these ``variations'' deviates from the original data. The results are summarized and explained in figure (\ref{fig:prop-shell-rad}).  In this figure, in the left side, for each source, 
+the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing 2/3 of the marks, but always keeping at least four points. 
+In the better observed shells such as 177-341 (top row), the circle
+fits are relatively robust to removing points, resulting in little variation between the subsamples. But also there are cases where the variations are more noticeable.
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{LV-full-field-annotated.png}
+\caption{DS9 shell marks over ONC. The circles mark each proplys position, while the cyan crosses delineate each bow shock and the red X marks the position of $\theta^1 ~C~Ori$. 
+The black circles only schematize a circle fit to each shell but they actually are not the real measurements.}
+\label{fig:radii-measures-example}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
+\label{fig:prop-shell-rad}
+\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. 
+The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
+curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
+with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
+%Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same
+}
+\end{figure}
+
+\begin{figure*}
+  \setkeys{Gin}{width=0.33\linewidth, trim=10 30 55 62.5}
+\begin{tabular}{@{}c@{}c@{}c@{}}
+
+All points & First sub-sample & Second sub-sample \\ \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
+  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
+  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV4} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp05/LV-bowshocks-xyfancy-positionssamp05-LV4} &
+  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV4} \\
+  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
+  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
+\end{tabular}
+\label{fig:char-radii-obs}
+\caption{Examples of systematic uncertainties in the circle fits to
+  the shell shapes for three sources (top to bottom rows): 177-341,
+  LV4 and 168-328.  The left hand column shows the fit to all of the
+  points identified on the shell border, where the number and spacing
+  of the points is a subjective measure of our confidence in tracing
+  the edge of each shell. The remaining two columns show fits to
+  randomly selected sub-samples of 2/3 of the points for each shell.}
+\end{figure*}
+
+\input{proplyds-table}
+
+%\begin{figure}
+%\end{figure}
+
+%\begin{figure*}
+%\begin{tabular}{cc}
+%\includegraphics[width=0.5\linewidth]{R90-R0-b}&
+%\includegraphics[width=0.5\linewidth]{Rc-R0-b}
+%\end{tabular}
+%\label{fig:radii-r0}
+%\caption{Left: $R_c$ normalized with $R_0$ vs $R_0$ normalized with $D$. Right:$R_{90}$ normalized with $R_0$ vs $R_0$ normalized with $D$. Since the bow shock brightness decays 
+%at the wings, it is more difficult to measure $R_{90}$. Along every single curve, $\beta$ is constant. The marks in the curves represents jumps of $15^\circ$ in inclination, and the most left 
+%mark in each curve represent $i=0^\circ$}
+%\end{figure*}
+
 %is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
@@
 
-\begin{figure*}
-\includegraphics[width=\linewidth]{LV-full-field-annotated.png}
-\caption{DS9 shell marks over ONC. The circles mark each proplys position, while the cyan crosses delineate each bow shock and the red X marks the position of $\theta^1 ~C~Ori$. 
-The black circles only schematize a circle fit to each shell but they actually are not the real measurements.}
-\label{fig:radii-measures-example}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[width=\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
-\label{fig:prop-shell-rad}
-\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. 
-The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
-curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
-with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
-%Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same
-}
-\end{figure}
 %Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$.
@@
 
-\begin{figure*}
-  \setkeys{Gin}{width=0.33\linewidth, trim=10 30 55 62.5}
-\begin{tabular}{@{}c@{}c@{}c@{}}
-
-All points & First sub-sample & Second sub-sample \\ \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
-  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
-  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV4} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp05/LV-bowshocks-xyfancy-positionssamp05-LV4} &
-  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV4} \\
-  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
-  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
-\end{tabular}
-\label{fig:char-radii-obs}
-\caption{Examples of systematic uncertainties in the circle fits to
-  the shell shapes for three sources (top to bottom rows): 177-341,
-  LV4 and 168-328.  The left hand column shows the fit to all of the
-  points identified on the shell border, where the number and spacing
-  of the points is a subjective measure of our confidence in tracing
-  the edge of each shell. The remaining two columns show fits to
-  randomly selected sub-samples of 2/3 of the points for each shell.}
-\end{figure*}
-
-In the better observed shells such as 177-341 (top row), the circle
-fits are relatively robust to removing points, resulting in little
-variation between the subsamples.
-
-In the left side, for each source, the fit is done using all the ds9
-marks, while in the middle and the right we show two variations
-removing a fraction of the marks, but always keeping at least four
-points. 177-341 is an example where the measurements only change very
-slightly from one variation to other. While with 168-328 the changes
-are a little more noticeable. LV4 is a case where the most external
-points are crucial in the determination of the radius of curvature.
-
-\input{proplyds-table}
-
-%\begin{figure}
-%\end{figure}
-
-%\begin{figure*}
-%\begin{tabular}{cc}
-%\includegraphics[width=0.5\linewidth]{R90-R0-b}&
-%\includegraphics[width=0.5\linewidth]{Rc-R0-b}
-%\end{tabular}
-%\label{fig:radii-r0}
-%\caption{Left: $R_c$ normalized with $R_0$ vs $R_0$ normalized with $D$. Right:$R_{90}$ normalized with $R_0$ vs $R_0$ normalized with $D$. Since the bow shock brightness decays 
-%at the wings, it is more difficult to measure $R_{90}$. Along every single curve, $\beta$ is constant. The marks in the curves represents jumps of $15^\circ$ in inclination, and the most left 
-%mark in each curve represent $i=0^\circ$}
-%\end{figure*}
-
 %%% Local Variables:

### 2016-04-15 papers/Paper1/sec-application.tex
Week's changes in figures 2, 7 and respective sections

@@
 \caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
-to avoid dependency with this parameter.}
+to avoid dependency with this parameter. In dashed lines, the \citep{Canto:1996} solution for two 
+spherical, isotropic  interacting winds is shown, while in continuos lines we show the solution where the
+weakest wind has a density distribution given by (\ref{eq:nprop})}
 \label{fig:r-beta}

### 2016-04-15 papers/Paper1/sec-application.tex
Work on Fig 7 caption and accompanying text

--- 2016-04-12 papers/Paper1/sec-application.tex
@@
 \label{sec:application}
+
+\defcitealias{Canto:1996}{CRW}
+\newcommand\CRW{\citetalias{Canto:1996}}
 
@@
 
-This scenario can be described with the formalism of \citep{Canto:1996}, who proposes an algebraic solution for the two winds interaction problem in the thin shell approximation, in terms of a free parameter $\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$,
-the winds momentum ratio, which the quantities with subindex 1 corresponds to the strongest wind, therefore $\beta<=1$.
+This scenario can be described with the formalism of
+\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
+solution for the two winds interaction problem in the thin shell
+approximation, in terms of a free parameter
+$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
+momentum ratio, which the quantities with subindex 1 corresponds to
+the strongest wind, therefore $\beta<=1$.
 
-If we apply the \citep{Canto:1996} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:
+If we apply the \CRW{} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:
 
@@
 \end{align}  
-The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \citep{Canto:1996}
+The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}
 numerically in python code, we can obtain the bow shock shape $R(\theta)$, as illustred in figure (\ref{fig:r-beta}).
@@
 \includegraphics[width=\linewidth]{r-beta}
-\caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
-to avoid dependency with this parameter.}
+\caption{Bow shock shapes for interacting winds in the thin-shell
+  approximation. Coordinates are normalized by $D$, the distance
+  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
+  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
+  different values of the wind momentum ratio, \(\beta\), and for the
+  case where the weaker wind is isotropic (dashed lines) or an
+  anisotropic proplyd photoevaporation flow (solid lines).}
 \label{fig:r-beta}
@@
 
-In order to find an analytic form of the characteristic radii $(R_0,R_c,R_{90})$, we may combine equations (\ref{eq:dotprop}) to (\ref{eq:jdot}) with (6) and (23) from \citep{Canto:1996}
+In order to find an analytic form of the characteristic radii $(R_0,R_c,R_{90})$, we may combine equations (\ref{eq:dotprop}) to (\ref{eq:jdot}) with (6) and (23) from \CRW{}
 and obtain the following relation:
@@
 
-$R_0$ is obtained directly from equation (27) of \citep{Canto:1996} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
+$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
 
 We can obtain $R_{90}$ by the following process:
-Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{Canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:
+Evaluating equations  (\ref{eq:th1th}) and (23) from \CRW{} at $\theta=\frac{\pi}{2}$ we obtain the following:
 
@@
 \end{tabular}
-\caption{$R_0$, $R_c$ and $R_{90}$ versus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \citep{Canto:1996}
+\caption{$R_0$, $R_c$ and $R_{90}$ versus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \CRW{}
 are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}

### 2016-04-22 papers/Paper1/sec-application.tex
Found a relation between wind's index and \xi parameter.

@@
 
+Neverthless, we should not restrict to the 0.5 index in equation (\ref{eq:nprop}). We may generalize this relation as follows:
+
+\begin{align}
+n(r_{IF},\theta) = n_0 \cos^{k}\theta
+\label{eq:ngen}
+\end{align}
+
+Where $k >0$ implies that the wind's density decays towards wings, when $k<0$ the wind's density incresases towards the wings and $k=0$ implies that the wind is isotropic.
+
+\subsection{\CRW{} Scenario}
 This scenario can be described with the formalism of
@@
 
-If we apply the \CRW{} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:
+If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}), we find that the solutions for equations (8) - (11) of \CRW{} are the following:
 
 \begin{align}
-\dot{M}_w &= \frac{\dot{M}_w^0}{3}\left(1-\cos^{3/2}\theta\right) \label{eq:dotprop} \\
-\dot{\Pi}_z &= \frac{1}{5}v_w \dot{M}_w^0\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
-\dot{\Pi}_r &= \frac{1}{2}v_w\dot{M}_w^0\left(\frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta\right) \label{eq:piz}\\
+\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
+\mathrm{where} & M^0_w \equiv 4\piv_w r^2_{IF} n_0 \bar{m}\\
+\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
+\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w V_w I_k (\theta) \label{eq:piz}\\
+I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta
 \dot{J}_w = 0 \label{eq:jdot}
 \end{align}  
-The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}
-numerically in python code, we can obtain the bow shock shape $R(\theta)$, as illustred in figure (\ref{fig:r-beta}).
+Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}  we can obtain the bow shock shape $R(\theta)$. Actually, we work with two different scenarios:
+% as illustred in figure (\ref{fig:r-beta}), where we show the resulting bow shock shapes for two scenarios:
+$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison betwwen both solutions is shown in figure (\ref{fig:r-beta}).
 
@@
 \begin{align}
-\theta_1\cot\theta_1 -1 =  \frac{8}{5}\beta E\left(\frac{\theta}{2}|2\right)\cot\theta - \frac{4}{5}\beta
+\theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
 \label{eq:th1th}
@@
 R_{90} &= D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} &= 1-\frac{4}{5}\beta \label{eq:th190}
+\theta_{1,90}\cot\theta_{1,90} &= 1-\frac{2\beta}{k+2} \label{eq:th190}
 \end{align}
-Where $\theta_{1,90}\equiv \theta_º(\frac{\pi}{2})$. Combining both equations we have:
+Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing the parameter 
+$\xi\equiv \frac{2}{k+2}$ we have:
 
 \begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\frac{4}{5}\beta} 
+R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
 \end{align}
 
-Expanding (\ref{eq:th190}) until 3rd order and solving for $\theta_{1,90}$:
+Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}) we find that:
+
 \begin{align}
-\theta_{1,90} \simeq \left(\frac{2.4\beta}{1-0.8\beta}\right)^{1/2} \\
-R_{90} \simeq \left(\frac{2.4\beta}{(1-0.8\beta)^3}\right)^{1/2}
-\label{eq:r90}
+\theta_{1,90} \simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
+\label{eq:th190sol}
+\end{align}
+
+With this, we have a solution for $B \equiv \frac{R_{90}}{R_0}$:
+
+\begin{align}
+B = \frac{\sqrt(\xi\beta)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
+\label{eq:B}
 \end{align}
@@
 
+\subsection{Conic Scenario}
+
+Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$. Continue edition from here...
+
 \input{proplyds-table}

### 2016-04-26 papers/Paper1/sec-application.tex
Use slightly higher N0 values
Reducing the HA98 values by factor of 2 was too extreme - changed it to
factor of 1.5 instead.  This means that we generally need lower
inclinations in order to match the ionizing flux
Fixed some typing errors.Enhanced conics scenario.

@@
 \dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
-\mathrm{where} & M^0_w \equiv 4\piv_w r^2_{IF} n_0 \bar{m}\\
+\mathrm{where} & M^0_w \equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
 \dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
 \dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w V_w I_k (\theta) \label{eq:piz}\\
-I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta
+I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \\
 \dot{J}_w = 0 \label{eq:jdot}
@@
 
-Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}) we find that:
+Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}), using a small angle  approximation, we find that:
 
@@
 \begin{align}
-B = \frac{\sqrt(\xi\beta)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
+B = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
 \label{eq:B}
@@
 $\theta_1 = \beta^{1/2}\theta$
+
+This expansion is valid when k is integer or multiple of 1/2.
 
@@
 
+--- Rethink if should be included on paper ---
 Equations (\ref{eq:r90}),  (\ref{eq:Rcurv}) and (27) from \citep{Canto:1996} are labeled as ``analytic i=0'' in figure (\ref{fig:rad-beta}).
@@
 
+--- Finished rethinking ---
 Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
@@
 
-Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$. Continue edition from here...
+Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (make it in conics section)
+
+\begin{align}
+\tan^2\theta_c &= 3\left| \frac{\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{1}{\left(1-\beta^{1/2}\right)}\right| 
+\end{align}
+
+With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds momenta and different density distributions.
+In figure () we show
+the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$
 

### 2016-04-28 papers/Paper1/sec-application.tex
Insert conic xi figures

@@
 With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds momenta and different density distributions. 
-In figure () we show
-the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$
+In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well with a elliptic-like conic shape.
+LV4 is a special case which fits better with an hyperbola
+
+\begin{figure*}
+\begin{tabular}{cc}
+\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-10} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-08} \\
+\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-06} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-04} 
+\end{tabular}
+\label{fig:conic-xi}
+\caption{Comparison of projected radii for conic models against with the observed proplyds. A fixed value of $\xi$, which describes the anisotropy of the inner wind, is used
+in each graph. Models with $\theta_c > 0$ correspond to elliptical-like shapes, while $\theta_c<0$ describes hyperbolic-like shapes.}
+\end{figure*}
 

### 2016-05-06 papers/Paper1/sec-application.tex
Update conic-xi* figures and enhanced analysis

--- 2016-04-26 papers/Paper1/sec-application.tex
@@
   case where the weaker wind is isotropic (dashed lines) or an
-  anisotropic proplyd photoevaporation flow (solid lines).}
+  anisotropic photoevaporation flow. The solid lines shows a wind with a
+  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
+  And the dooted lines show a wind with extreme anisotropy degree $(k=8)$.}
 \label{fig:r-beta}
@@
 In the better observed shells such as 177-341 (top row), the circle
-fits are relatively robust to removing points, resulting in little variation between the subsamples. But also there are cases where the variations are more noticeable.
+fits are relatively robust to removing points, resulting in little variation between the subsamples. 
+But also there are cases where the variations are more noticeable.
+
+Beneath the error margins, our measurements are consistent with \citet{Robberto:2005} for $R'_0/D$. From figure (\ref{fig:conic-xi}), we also
+note that the LV4 measurements fits better with models where its photoevaporated flow is isotropic.
+The same is true with \citet{Robberto:2005} data.The rest of the proplyds fit better with more anisotropic winds, which may explain why \citet{Robberto:2005} did not find a match between models
+and data, since they only showed models where the interacting winds are isotropic.
 
@@
 
-\begin{figure}
-\includegraphics[width=\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
-\label{fig:prop-shell-rad}
-\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. 
-The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
-curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
-with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
+%\begin{figure}
+%\includegraphics[width=\linewidth]{../../read-shapes/proplyd-shell-R0-Rc-cloud} 
+%\label{fig:prop-shell-rad}
+%\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. 
+%The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
+%curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
+%with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
 %Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same
-}
-\end{figure}
+%}
+%\end{figure}
 
@@
 
-With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds momenta and different density distributions.
-In figure () we show
-the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$
+With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
+momenta and different density distributions. 
+In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well 
+with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
+LV4 is a special case which fits better with an hyperbola and isotropic wind.
+
+\begin{figure*}
+\begin{tabular}{cc}
+\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-10} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-08} \\
+\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-04} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-02} 
+\end{tabular}
+\label{fig:conic-xi}
+\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a conic-like bow shock with 
+fixed momentum ratio $\beta$ and the derived value of $\theta_c$ is also shown.The dots along each curve represent separation in inclination of 
+$15^\circ$. The measurements of each proplyd are accompained with the set of variations represented as colored radial lines. In 
+each graph we use a different degree of the weaker wind anisotropy, starting from an isotropic wind $(\xi=1)$, to the most anisotropic wind
+$(\xi=0.2)$.}
+\end{figure*}
+%Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with fixed wind's momentum ratio $\beta$. 
+%The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
+%curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
+%with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
 

### 2016-05-06 papers/Paper1/sec-conic.tex
Improve R90 description. Unfinished
Corrections to allow paper to compile
Tidy up the conic section of paper
Remove an unwanted figure and rearrange the others.  Remove extraneous
blank lines in latex file

@@
-\section{Conic section approximation to bow shock shapes}
+\section{Conic section approximation}
 \label{sec:conic}
@@
 \begin{figure}
+\setlength\tabcolsep{0pt}
 \begin{tabular}{cc}
-\includegraphics[width=0.4\linewidth]{ellipse} &
-\includegraphics[width=0.4\linewidth]{hiperbola}
+\includegraphics[height=0.44\linewidth, trim=30 0 30 0, clip]{ellipse_py_lab} &
+\includegraphics[height=0.44\linewidth, trim=60 0 70 0, clip]{hyperbola_py}
 \end{tabular}
@@
 \end{figure}
+\begin{figure}
+\includegraphics[width=\linewidth]{conic1}
+\caption{A whole set of conics with the same radius of curvature. The parameter $\theta_c$ is used as the equivalent of the excentricity. This angle is defined as positive for closed curves
+and negative for the opened ones. An special case is $\theta_c=0$, which describes a parabola.}
+\label{fig:conics-family}
+\end{figure}
+
 Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
-
 \begin{align}
-x = a\Cos(t)-x_0 \\ 
-y = b\Sin(t)
+x = a\Cos(t)-x_0 \label{eq:par-x}\\ 
+y = b\Sin(t) \label{eq:par-y}
 \end{align}
-
 where:
@@
 a parabola.
-\begin{figure}
-\includegraphics[width=\linewidth]{conic1}
-\caption{A whole set of conics with the same radius of curvature. The parameter $\theta_c$ is used as the equivalent of the excentricity. This angle is defined as positive for closed curves
-and negative for the opened ones. An special case is $\theta_c=0$, which describes a parabola.}
-\label{fig:conics-family}
-\end{figure}
-\subsection{Projection onto the plane of sky}
 
-Once the parametrization is done, we can find the apparent shape of the shell in the observer's frame, following the procedure explained in section \ref{sec:projection}.
+\subsection{Plane-of-sky projection of conic sections} 
+\begin{figure*}
+\includegraphics[width=0.9\linewidth]{annotated}
+\caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
+the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
+an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
+\label{fig:Apqp}
+\end{figure*}
 
-First of all, the intrinsic 3D shape of the shell is given by:
-
+Once the parametrization is done, we can find the apparent shape of
+the shell in the observer's frame, following the procedure explained
+in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
 \begin{align}
@@
 \end{align}
-
 The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:tanalpha}), then:
-
 \begin{align}
@@
 where:
-
 \begin{align}
@@
 We could work in another frame where the origin is located at the conic's center: $(X,Y)$, where $X=x-X_0$ and $Y=y$.
-
 In this frame,  we use the transformations (\ref{eq:Trans})  to obtain the apparent shape of the shell:
-
 \begin{align}
@@
 (\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:
-
 \begin{align}
 X' = a'\Cos t' \label{eq:conic-projected-x-2} \\
-Y' = b'\Sin t' \label{eq:conic-projected-y-2}
+Y' = b'\Sin t' \label{eq:conic-projected-y-2} . 
 \end{align}
@@
 Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y}) we find that
-
 \begin{align}
@@
 \end{align} 
-
 Which proves that effectively the projection of a given conic is the same conic. With this knowledge, we can obtain the characteristic radii in
 the observer's frame.
-
 \begin{align}
@@
 radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:
-
 \begin{align}
@@
 \end{align}
-
 Where $A\equiv \frac{R_c}{R_0}$
@@
 The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
-
 \begin{align}
@@
 \end{align}
-
-Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
-\begin{figure*}
-\includegraphics[width=0.8\linewidth]{conic2}
-\label{fig:conic2}
-\caption{Graphic example of the increasing of the projected radius of curvature with inclination}
-\end{figure*}
+where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$. 
+% \begin{figure*}
+% \includegraphics[width=0.8\linewidth]{conic2}
+% \label{fig:conic2}
+% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
+% \end{figure*}
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.9\linewidth]{annotated}
-\caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
-the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
-an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
-\label{fig:Apqp}
-\end{figure*}
+Finally, we need to obtain $R_{90}$ using equations (\ref{eq:par-x}) and (\ref{eq:par-y}):
+\begin{align}
+x_{90} = a - R_0 = a\Cos(t_{90}) \\
+y_{90} = R_{90} = b\Sin(t_{90})
+\end{align}
+With this we find that:
+\begin{align}
+R_{90} = b\left(1 \mp \frac{(R_0-a)^2}{a^2}\right)
+\end{align}
 

### 2016-05-09 papers/Paper1/sec-application.tex
Analysis of Rc completed

@@
 
-Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 2nd order for small $\theta$ values to find that for such values
-$\theta_1 = \beta^{1/2}\theta$
+Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 4th order for small $\theta$ values to find that for such values
 
-This expansion is valid when k is integer or multiple of 1/2.
-
+\begin{align}
+\theta_1^2 &\simeq \beta\theta^2\left[1+ \left(A_k-\frac{\beta}{15}\right)\theta^2\right] \\
+\mathrm{where:~} & A_k = \frac{1}{15}-\frac{k}{20}
+\end{align}
 Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:
@@
 \begin{align}
-R \simeq R_0 \left(1+\frac{1+2\beta^{1/2}}{6}\theta^2\right)
+R &\simeq R_0 \left(1+\gamma\theta^2\right)
 \label{eq:R_approx}
+\mathrm{where:~} & \gamma = \frac{1}{6} + \frac{\beta^{1/2}}{3}\left[1+\frac{1-\beta^{1/2}}{10}-\frac{3}{40}\frac{k}{1+\beta^{1/2}}\right]
 \end{align}
@@
 \begin{equation}
-R_c = \frac{3}{2}R_0\left(1-\beta^{1/2}\right)^{-1}
+R_c = R_0\left(1-2\gamma\right)^{-1}
 \label{eq:Rcurv}

### 2016-05-12 papers/Paper1/sec-application.tex
Tidy up the text (a bit) and inserted new figures

@@
 
---- Rethink if should be included on paper ---
-Equations (\ref{eq:r90}),  (\ref{eq:Rcurv}) and (27) from \citep{Canto:1996} are labeled as ``analytic i=0'' in figure (\ref{fig:rad-beta}).
+finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (make it in conics section)
+
+\begin{align}
+\tan^2\theta_c &= 3\left| \frac{\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{1}{\left(1-\beta^{1/2}\right)}\right| 
+\end{align}
 
@@
 \begin{tabular}{ccc}
-\includegraphics[width=0.35\linewidth]{R0-b}&
-\includegraphics[width=0.35\linewidth]{Rc-b} &
-\includegraphics[width=0.35\linewidth]{R90-b}
+\includegraphics[width=0.35\linewidth]{A-beta}&
+\includegraphics[width=0.35\linewidth]{B-beta} &
+\includegraphics[width=0.35\linewidth]{thc-beta}
 \end{tabular}
-\caption{$R_0$, $R_c$ and $R_{90}$ versus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \CRW{}
-are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}
+\caption{$\theta_c$, $R_c$ and $R_{90}$ versus $\beta$ for different anisotropy degrees, represented with the $\xi$ paramenter.}
 \label{fig:rad-beta}
@@
 
---- Finished rethinking ---
-Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
-easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
+%Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
+%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
 
-Although there is an analytical form for the radius of curvature, for $i\ne 0$ there is not an intuitive form for  $R'_c$.
+With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
+momenta and different density distributions.
+
+In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well 
+with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
+LV4 is a special case which fits better with an hyperbola and isotropic wind.
+
+%Although there is an analytical form for the radius of curvature, for $i\ne 0$ there is not an intuitive form for  $R'_c$.
 Plus, in practice, we are working with discret arrays, so, when transforming the shell's coordinates to the primed system, we almost certainly will miss the $\theta'=0$ point, which
-should allow us to estimate the radii $(R'_0,R'_c)$, the first with equation (\ref{eq:Rpar}) and the second with the mathematical definition of the radius of curvature using the primed coordinates.
+%should allow us to estimate the radii $(R'_0,R'_c)$, the first with equation (\ref{eq:Rpar}) and the second with the mathematical definition of the radius of curvature using the primed coordinates.
 Insted, we estimate $R'_0$ as the projected radius with the value of $\theta'$ closest to zero, and
-$R'_c$ doing a least square fit to the points such as $\theta' \leq 45^\circ$.
+%$R'_c$ doing a least square fit to the points such as $\theta' \leq 45^\circ$.
 This restriction allows to obtain the best estimation of the radius of curvature at the nos of the shell.
@@
 
-\subsection{Conic Scenario}
-
-Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (make it in conics section)
-
-\begin{align}
-\tan^2\theta_c &= 3\left| \frac{\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{1}{\left(1-\beta^{1/2}\right)}\right| 
-\end{align}
-
-With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
-momenta and different density distributions. 
-In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well 
-with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
-LV4 is a special case which fits better with an hyperbola and isotropic wind.
+%\subsection{Conic Scenario}
 

### 2016-05-17 papers/Paper1/sec-conic.tex
Rearranging equations for non projected radii
Now the equation for non projected radii are placed before
the projection of conics subsection

@@
 \includegraphics[height=0.44\linewidth, trim=30 0 30 0, clip]{ellipse_py_lab} &
-\includegraphics[height=0.44\linewidth, trim=60 0 70 0, clip]{hyperbola_py}
+\includegraphics[height=0.44\linewidth, trim=60 0 70 0, clip]{hyperbola_py_lab}
 \end{tabular}
 \label{fig:conics}
-\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola The center of the conic is located at a distance $x_0$ from the origin at the $x$ axis. The shell position is 
-described either by cartesian coordinates $(x,y)$ or polar coordinates $(R,\theta)$. In this section is more convenient to use cartesian coordinates, as their parametrization is quite easy.}
+\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola The center of the conic is located at a distance $x_0=R_0-a$ from the origin at the $x$ axis. 
+The radius of curvature at the axis is $R_c$, and $R_{90}$ is t he radius of the conic in the perpendicular direction to $R_0$.
+}
 \end{figure}
@@
 a parabola.
-
+To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,$\theta_c$)$
+could be derived from the former. The transformation betwwen the conic parameters and the characteristic radii are given by:
+\begin{align}
+\frac{R_c}{D} &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
+\frac{R_{90}}{D} &= b\left(1 \mp \frac{(R_0-a)^2}{a^2}\right)
+\end{align}
+The inverse transformation is given by:
+\begin{align}
+a &= (not finished) \label{eq:a-conic}\\
+b &= \left(aR_c\right)^{1/2}\\
+\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} 
+\end{align}
+From equations (\ref{eq:a-conic}) we can see that for $R^2_{90} > 2 R_c$, the conic parameter $a$ is negative, so in this case the resulting conic is an hyperbola, and we must take the negative root
+in equation (\ref{eq:thc-conic}). The opposite applies for ellipses.
+will be an ellipse
 \subsection{Plane-of-sky projection of conic sections} 
@@
 
-Finally, we need to obtain $R_{90}$ using equations (\ref{eq:par-x}) and (\ref{eq:par-y}):
-\begin{align}
-x_{90} = a - R_0 = a\Cos(t_{90}) \\
-y_{90} = R_{90} = b\Sin(t_{90})
-\end{align}
-With this we find that:
-\begin{align}
-R_{90} = b\left(1 \mp \frac{(R_0-a)^2}{a^2}\right)
-\end{align}
-
 %%% Local Variables:

### 2016-05-17 papers/Paper1/sec-application.tex
Inserted pressure figure and add a little discussion

@@
 
+Using the data from figure \ref{fig:conic-xi}, we estimate for each source the parameters $(\beta,i,\xi)$.
+With this, is possible to estimate the non projected distances $(R_0,D)$, from which we can estimate the stagnation pressure at the bow shock's position,
+and compare it with the expected pressure from the stellar wind at the distance $D$.
+Since we expect equilibrium pressure in the bow shock surface, both pressures should be the same.
+In figure \ref{fig:pressure} we compare the estimated flux and
+pressure to balance ionization in the photoevaporated flow and pressure balance, respectively.
+For the farthest proplyds, we can see that the estimated pressure is greater than the stellar wind pressure, even with the best fits.
+This suggests that at large distances, another source rather than the
+stellar wind is the reponsible for mantaining the stationary bow shocks.
+
 \begin{figure*}
@@
 \end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{../../proplyd-wind-figs/plot-wind-fits}
+\label{fig:pressure}
+\caption{Up: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd.
+The gray line represents the stellar flux at the distance $D$.
+Down: In colored lines, estiamted stagnation pressure for each proplyd.
+The gray solid line represent the stellar wind at the distance $D$.
+in both cases, the big dots represent the variations which have more agreement with ionization balance and pressure balance, respectively.}
+\end{figure*}
 %Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with fixed wind's momentum ratio $\beta$. 
@@
 
-\input{proplyds-table}
+%\input{proplyds-table}
 

### 2016-05-17 papers/Paper1/sec-application.tex
Add table to paper of arc parameters from fits

@@
 \label{sec:application}
-
+\newcommand\thC{\(\theta^1\)\,Ori~C}
 \defcitealias{Canto:1996}{CRW}
@@
 \subsection{\CRW{} Scenario}
+\label{sec:crw-scenario}
 This scenario can be described with the formalism of
@@
 \subsubsection{Methodology}
+\label{sec:methodology}
 Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta^1 ~C$. For the shell's position, the marks were placed in the outer border of each shock. 
@@
 
-\begin{figure*}
+\begin{figure}
 \includegraphics[width=\linewidth]{../../proplyd-wind-figs/plot-wind-fits}
@@
 in both cases, the big dots represent the variations which have more agreement with ionization balance and pressure balance, respectively.}
-\end{figure*}
+\end{figure}
+
+\begin{table*}
+  \caption{Fitted arc parameters for proplyd bowshocks}
+  \label{tab:arc-fits} 
+\newcommand\C[1]{\multicolumn{1}{c}{#1}}
+\begin{tabular}{llrllllrlll}\toprule
+             &          & \multicolumn{3}{c}{\dotfill Observed \dotfill}              & \multicolumn{6}{c}{\dotfill Model fits \dotfill} \\ 
+  \C{OW}     & \C{Name} & \(D'\) &\C{ \(R_0'/D'\) }&\C{ \((R_c'/R_0')_{\mathrm{shape}}\) }&\C{ \((R_c'/R_0')_{\mathrm{flux}}\) }&\C{ \(\beta\) }&\C{ \(\xi\) }&\C{ \(|i|\) }&\C{ \(D\) }&\C{ \(R_0/D\)}\\
+  \C{(1)}& \C{ (2) }&\C{ (3)    }&\C{    (4)      }&\C{              (5)           }&\C{           (6)             }&\C{     (7)   }&\C{   (8)   }&\C{   (9) }&\C{  (10) }&\C{   (11)} \\
+\midrule     
+168-328  &     & 6.8 & \(0.152 \pm 0.001\) & \(1.42 \pm 0.09\) & \(1.45 \pm 0.05\) & \(0.018 \pm 0.003\) & 0.4--0.6 & \(33 \pm 3\) & \(0.017 \pm 0.001\) & \(0.115 \pm 0.005\)\\
+169-338  &     & 16.5 & \(0.059 \pm 0.001\) & \(1.76 \pm 0.48\) & \(1.50 \pm 0.05\) & \(0.002 \pm 0.001\) & 0.8--0.8 & \(43 \pm 8\) & \(0.049 \pm 0.006\) & \(0.035 \pm 0.005\)\\
+177-341  & HST1& 25.6 & \(0.144 \pm 0.001\) & \(1.21 \pm 0.02\) & \(1.21 \pm 0.02\) & \(0.018 \pm 0.003\) & 0.1--0.2 & \(30 \pm 5\) & \(0.064 \pm 0.003\) & \(0.115 \pm 0.005\)\\
+180-331  &     & 25.1 & \(0.061 \pm 0.007\) & \(1.30 \pm 0.04\) & \(1.27 \pm 0.05\) & \(0.003 \pm 0.001\) & 0.4--0.4 & \(35 \pm 7\) & \(0.067 \pm 0.007\) & \(0.047 \pm 0.005\)\\
+167-317  & LV2 & 7.8 & \(0.305 \pm 0.025\) & \(0.81 \pm 0.28\) & \(1.50 \pm 0.1\) & \(0.085 \pm 0.015\) & 0.1--0.2 & \(13 \pm 13\) & \(0.018 \pm 0.001\) & \(0.225 \pm 0.005\)\\
+         & LV2b& 7.0 & \(0.097 \pm 0.002\) & \(2.00 \pm 0.62\) & \(1.63 \pm 0.08\) & \(0.008 \pm 0.003\) & 0.8--0.8 & \(28 \pm 13\) & \(0.018 \pm 0.002\) & \(0.078 \pm 0.012\)\\
+163-317  & LV3 & 6.9 & \(0.334 \pm 0.002\) & \(1.81 \pm 0.11\) & \(1.81 \pm 0.15\) & \(0.075 \pm 0.025\) & 0.6--0.8 & \(35 \pm 5\) & \(0.018 \pm 0.001\) & \(0.205 \pm 0.025\)\\
+161-324  & LV4 & 6.2 & \(0.186 \pm 0.002\) & \(2.59 \pm 0.24\) & \(2.05 \pm 0.07\) & \(0.040 \pm 0.014\) & 0.8--1.0 & \(18 \pm 12\) & \(0.014 \pm 0.001\) & \(0.160 \pm 0.028\)\\
+168-323  & LV5 & 9.4 & \(0.213 \pm 0.002\) & \(1.57 \pm 0.07\) & \(1.60 \pm 0.07\) & \(0.055 \pm 0.005\) & 0.2--0.4 & \(20 \pm 5\) & \(0.022 \pm 0.001\) & \(0.190 \pm 0.010\)\\
+\bottomrule
+\end{tabular}
+\begin{minipage}{0.95\linewidth}
+  Notes --
+%
+  Col.~(1): Source ID \citep{ODell:1994a}.
+%
+  Col.~(2): Alternative name of source.
+% 
+  Col.~(3): Projected distance from \thC{}, arcseconds.
+%
+  Col.~(4): Apparent shell outer radius along axis, normalized to
+  projected distance, with \(\pm 1\sigma\) uncertainties, determined
+  from circle fits described in \S~\ref{sec:methodology}.
+% 
+  Col.~(5): Apparent shell radius of curvature, normalized to radius
+  along axis, with \(\pm 1\sigma\) uncertainties, determined from
+  circle fits described in \S~\ref{sec:methodology}.
+% 
+  Col.~(6): As Col.~(5) but applying the additional requirement that
+  the proplyd surface brightness from model fits should agree with the
+  theoretical prediction.
+%
+  Col.~(7): Proplyd-to-O~star wind momentum ratio (see \S~\ref{sec:crw-scenario}). 
+% 
+  Col.~(8): Proplyd wind anisotropy factor.
+% 
+  Col.~(9): Inclination to plane of sky, degrees.
+% 
+  Col.~(10): True distance from \thC{}, parsecs.
+%
+  Col.~(11): True shell radius along axis, normalized to distance.
+
+\end{minipage}
+\end{table*}
 %Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with fixed wind's momentum ratio $\beta$. 

### 2016-05-20 papers/Paper1/sec-application.tex
Tidy up a bit the redaction. Add some new references to new table

@@
 The pressure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
-may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of $\theta^1~C~Ori$, which is highly supersonic $(M \sim 100)$.
+may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of \thC{}, which is highly supersonic $(M \sim 100)$.
 
-The density distribution of the photoevaporated flow can be determined using the steady state continuity equation and assuming that almost all ionizing photons are absorbed at the IF \citep{HA:1998} and ignoring dust absorption, can be found that
+The density distribution of the photoevaporated flow can be determined using the steady state continuity equation and assuming that almost all ionizing photons are absorbed at the IF 
+\citep{HA:1998} and ignoring dust absorption, can be found that
 
@@
 
-finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (make it in conics section)
+finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:thc-conic})
 
 \begin{align}
-\tan^2\theta_c &= 3\left| \frac{\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{1}{\left(1-\beta^{1/2}\right)}\right| 
+\tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
+\label{eq:thc-CRW}
 \end{align}
@@
 With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
-momenta and different density distributions.
-
-In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well 
-with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
-LV4 is a special case which fits better with an hyperbola and isotropic wind.
+momenta and different density distributions. Figure \ref{fig:rad-beta} shows  eqautions  ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
 
@@
 \label{sec:methodology}
-Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta^1 ~C$. For the shell's position, the marks were placed in the outer border of each shock. 
+Using the DS9 SAO image tools, we marked the positions of the proplyds and \thC{}. For the shell's position, the marks were placed in the outer border of each shock. 
 The number of marks used in each shell varies with shell's size, and with our confidence with our measurements.
-Thus, we used few points in small bow shocks and/our the bow shock's outer shell is not well defined. The distance $D$ is measured as the distance between the position of $\theta^1 ~C~Ori$ 
+Thus, we used few points in small bow shocks and/our the bow shock's outer shell is not well defined. The distance $D$ is measured as the distance between the position of \thC{} 
 and each proplyd's position. The radius of curvature $R_c$ is measured as the radius of the 
@@
 To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, and made 10 sets of randomly chosen removed marks, and made the measurements again to 
-see how much these ``variations'' deviates from the original data. The results are summarized and explained in figure (\ref{fig:prop-shell-rad}).  In this figure, in the left side, for each source, 
-the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing 2/3 of the marks, but always keeping at least four points. 
+see how much these ``variations'' deviates from the original data. Some examples are shown  in figure (\ref{fig:char-radii-obs}).  In the left side, for each source, 
+the fit is done using all the shell points, while in the middle and the right we show two variations removing 2/3 of thepoints, but always keeping at least four. 
 In the better observed shells such as 177-341 (top row), the circle
 fits are relatively robust to removing points, resulting in little variation between the subsamples. 
-But also there are cases where the variations are more noticeable.
+But also there are cases where the variations are more noticeable. Colums 3, 4 and 5 of table (\ref{tab:arc-fits}) represent the summary of all the measurements done. In colums 4 and 5, 
+the radii $(R_0,R_c)$ are measured as the average of all subsamples, and the uncertainty as the standard deviation.
+
+In figure (\ref{fig:conic-xi}) we show the theoretical conic curves. Most of the proplyds fit well 
+with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
 
 Beneath the error margins, our measurements are consistent with \citet{Robberto:2005} for $R'_0/D$. From figure (\ref{fig:conic-xi}), we also
-note that the LV4 measurements fits better with models where its photoevaporated flow is isotropic.
-The same is true with \citet{Robberto:2005} data.The rest of the proplyds fit better with more anisotropic winds, which may explain why \citet{Robberto:2005} did not find a match between models
+note that the LV4 measurements fits better with models where its photoevaporated flow is isotropic. The same is true with \citet{Robberto:2005} data.
+The rest of the proplyds fit better with more anisotropic winds, which may explain why \citet{Robberto:2005} did not find a match between models
 and data, since they only showed models where the interacting winds are isotropic.
 
-Using the data from figure \ref{fig:conic-xi}, we estimate for each source the parameters $(\beta,i,\xi)$.
-With this, is possible to estimate the non projected distances $(R_0,D)$, from which we can estimate the stagnation pressure at the bow shock's position,
-and compare it with the expected pressure from the stellar wind at the distance $D$.
-Since we expect equilibrium pressure in the bow shock surface, both pressures should be the same.
-In figure \ref{fig:pressure} we compare the estimated flux and
-pressure to balance ionization in the photoevaporated flow and pressure balance, respectively.
+Using the data from figure \ref{fig:conic-xi}, we estimate for each source the parameters $(\beta,i,\xi)$. With this, is possible to estimate the non projected distances $(R_0,D)$, 
+from which we can estimate the stagnation pressure at the bow shock's position, 
+and compare it with the expected pressure from the stellar wind at the distance $D$. Since we expect equilibrium pressure in the bow shock surface, both pressures should be the same. 
+In figure \ref{fig:pressure} we compare the estimated flux and pressure to balance ionization in the photoevaporated flow and pressure balance, respectively. In column 6 of table \ref{tab:arc-fits}
+we selected some subsamples where the measurements of $R_c'$ lead to a better approach to ionization balance and pressure balance. 
 For the farthest proplyds, we can see that the estimated pressure is greater than the stellar wind pressure, even with the best fits.
@@
 \label{fig:pressure}
-\caption{Up: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd.
-The gray line represents the stellar flux at the distance $D$.
-Down: In colored lines, estiamted stagnation pressure for each proplyd.
+\caption{Top: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd. The gray line represents the stellar flux at the distance $D$. 
+Bottom: In colored lines, estiamted stagnation pressure for each proplyd. 
 The gray solid line represent the stellar wind at the distance $D$.

### 2016-05-26 papers/Paper1/sec-application.tex
Update text in sections 4 and 5
In conics section, just corrected a typo which prevents compiling
In applications section. Included a brief description about observations

@@
 
-%We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$.
-The proposal for these observations were done by  Jogee, S.
-in 2004 with calibration purposes but (he never published anything using explicitly these observations).
-% We must check if this phrase should be included
-%Nevertheless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.
+We measured the Characteristic radii in Orion Nebula proplyds from observations with the WPC2 camera from the Hubble Space Telescope (HST) using the narrow [OIII] filter.
+The original proposal were done by John Bally (The proposal ID is 5469).
+In figure \ref{fig:radii-measures-example}, we show the field where our proplyds sample lies with the measurements of each bow shock shape we made.
 

### 2016-05-26 papers/Paper1/sec-conic.tex
Rearrange of some equations and introducing new
The idea is to derive R90 and theta_c from characteristic radii
more naturally
Update text in sections 4 and 5
In conics section, just corrected a typo which prevents compiling
In applications section. Included a brief description about observations

@@
 a parabola.
-To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,$\theta_c$)$
-could be derived from the former. The transformation betwwen the conic parameters and the characteristic radii are given by:
+To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
+could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
 \begin{align}
@@
 \begin{align}
-a &= (not finished) \label{eq:a-conic}\\
+a &= \frac{R_c}{2A-B^2} \label{eq:a-conic}\\
 b &= \left(aR_c\right)^{1/2}\\
-\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} 
+\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} \\
+\mathrm{where:}& B\equiv \frac{R_{90}}{R_0} \\
+A \equiv \frac{R_c}{R_0}
 \end{align}
@@
 in equation (\ref{eq:thc-conic}). The opposite applies for ellipses.
-will be an ellipse
 \subsection{Plane-of-sky projection of conic sections} 

### 2016-05-30 papers/Paper1/sec-application.tex
Improve graphs for Fig 7
* Combine the graph for Rc and R90
* Make the text bigger
* Label different conic on the theta_c graph
update applications sections with new figures.
Also updated next files with new D' measurements:
- wind-fits.tab
- plot-wind-fits.pdf
- arc-fit-table-for-paper.tab
- transpose-table.org (org mode command for transposing table does not
  available in my emacs)

@@
 
-\begin{figure*}
-\begin{tabular}{ccc}
-\includegraphics[width=0.35\linewidth]{A-beta}&
-\includegraphics[width=0.35\linewidth]{B-beta} &
-\includegraphics[width=0.35\linewidth]{thc-beta}
+\begin{figure}
+\begin{tabular}{c}
+\includegraphics[width=\linewidth]{AB-beta} \\
+\includegraphics[width=\linewidth]{thc-beta}
 \end{tabular}
-\caption{$\theta_c$, $R_c$ and $R_{90}$ versus $\beta$ for different anisotropy degrees, represented with the $\xi$ paramenter.}
+\caption{Top:Characteristic radii, normalized with $R_0$ vs $\beta$. In solid line we plot the radius of curvature, while in dashed line we plot $R_{90}$. Bottom: $\theta_c$ vs $\beta$. For
+highly anisotropic shells $\xi <0.4$, the resulting shell has shape of an oblate spheroid, while for the isotropic case, the resulting shell is an hyperbola.
+the proplyd case is noticeable because it has
+a transition from spheroidal shapes to hyperbola.
+%$\theta_c$, $R_c$ and $R_{90}$ versus $\beta$ for different anisotropy degrees, represented with the $\xi$ paramenter.}
+}
 \label{fig:rad-beta}
-\end{figure*}
+\end{figure}
 
@@
 \end{tabular}
-\label{fig:char-radii-obs}
 \caption{Examples of systematic uncertainties in the circle fits to
@@
   randomly selected sub-samples of 2/3 of the points for each shell.}
+\label{fig:char-radii-obs}
 \end{figure*}
@@
 \end{tabular}
-\label{fig:conic-xi}
 \caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a conic-like bow shock with 
@@
 $(\xi=0.2)$.}
+\label{fig:conic-xi}
 \end{figure*}
@@
 \includegraphics[width=\linewidth]{../../proplyd-wind-figs/plot-wind-fits}
-\label{fig:pressure}
 \caption{Top: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd. The gray line represents the stellar flux at the distance $D$. 
@@
 in both cases, the big dots represent the variations which have more agreement with ionization balance and pressure balance, respectively.}
+\label{fig:pressure}
 \end{figure}

### 2016-05-31 papers/Paper1/sec-application.tex
Updated table in paper

@@
 \midrule     
-168-328  &     & 6.8 & \(0.152 \pm 0.001\) & \(1.42 \pm 0.09\) & \(1.45 \pm 0.05\) & \(0.018 \pm 0.003\) & 0.4--0.6 & \(33 \pm 3\) & \(0.017 \pm 0.001\) & \(0.115 \pm 0.005\)\\
-169-338  &     & 16.5 & \(0.059 \pm 0.001\) & \(1.76 \pm 0.48\) & \(1.50 \pm 0.05\) & \(0.002 \pm 0.001\) & 0.8--0.8 & \(43 \pm 8\) & \(0.049 \pm 0.006\) & \(0.035 \pm 0.005\)\\
-177-341  & HST1& 25.6 & \(0.144 \pm 0.001\) & \(1.21 \pm 0.02\) & \(1.21 \pm 0.02\) & \(0.018 \pm 0.003\) & 0.1--0.2 & \(30 \pm 5\) & \(0.064 \pm 0.003\) & \(0.115 \pm 0.005\)\\
-180-331  &     & 25.1 & \(0.061 \pm 0.007\) & \(1.30 \pm 0.04\) & \(1.27 \pm 0.05\) & \(0.003 \pm 0.001\) & 0.4--0.4 & \(35 \pm 7\) & \(0.067 \pm 0.007\) & \(0.047 \pm 0.005\)\\
-167-317  & LV2 & 7.8 & \(0.305 \pm 0.025\) & \(0.81 \pm 0.28\) & \(1.50 \pm 0.1\) & \(0.085 \pm 0.015\) & 0.1--0.2 & \(13 \pm 13\) & \(0.018 \pm 0.001\) & \(0.225 \pm 0.005\)\\
-         & LV2b& 7.0 & \(0.097 \pm 0.002\) & \(2.00 \pm 0.62\) & \(1.63 \pm 0.08\) & \(0.008 \pm 0.003\) & 0.8--0.8 & \(28 \pm 13\) & \(0.018 \pm 0.002\) & \(0.078 \pm 0.012\)\\
-163-317  & LV3 & 6.9 & \(0.334 \pm 0.002\) & \(1.81 \pm 0.11\) & \(1.81 \pm 0.15\) & \(0.075 \pm 0.025\) & 0.6--0.8 & \(35 \pm 5\) & \(0.018 \pm 0.001\) & \(0.205 \pm 0.025\)\\
-161-324  & LV4 & 6.2 & \(0.186 \pm 0.002\) & \(2.59 \pm 0.24\) & \(2.05 \pm 0.07\) & \(0.040 \pm 0.014\) & 0.8--1.0 & \(18 \pm 12\) & \(0.014 \pm 0.001\) & \(0.160 \pm 0.028\)\\
-168-323  & LV5 & 9.4 & \(0.213 \pm 0.002\) & \(1.57 \pm 0.07\) & \(1.60 \pm 0.07\) & \(0.055 \pm 0.005\) & 0.2--0.4 & \(20 \pm 5\) & \(0.022 \pm 0.001\) & \(0.190 \pm 0.010\)\\
+ 168-328  &            &    6.8  &  $0.152 \pm 0.001$  &  $1.42 \pm 0.09$   &  $1.45 \pm 0.05$     &  $0.018 \pm 0.003$  &  0.4 -- 0.6  &  $33 \pm 3$   &  $0.017 \pm 0.001$  &  $0.115 \pm 0.005$  \\
+ 169-338  &            &  16.4  &  $0.059 \pm 0.001$  &  $1.76 \pm 0.48$   &  $1.50 \pm 0.05$     &  $0.002 \pm 0.001$  &  0.8 -- 0.8  &  $43 \pm 8$   &  $0.049 \pm 0.006$  &  $0.035 \pm 0.005$  \\
+ 177-341  & HST1   & 25.6  &  $0.144 \pm 0.001$  &  $1.21 \pm 0.02$   &  $1.25 \pm 0.02$     &  $0.018 \pm 0.003$  &  0.1 -- 0.2  &  $30 \pm 5$   &  $0.064 \pm 0.003$  &  $0.115 \pm 0.005$  \\
+ 180-331  &             &  25.1  &  $0.061 \pm 0.007$  &  $1.30 \pm 0.05$   &  $1.27 \pm 0.05$     &  $0.003 \pm 0.001$  &  0.4 -- 0.4  &  $35 \pm 7$   &  $0.066 \pm 0.007$  &  $0.047 \pm 0.005$  \\
+ 167-317  &  LV2     &    7.8  &  $0.305 \pm 0.025$  &  $0.81 \pm 0.28$   &  $1.50 \pm 0.1$      &  $0.085 \pm 0.015$  &  0.1 -- 0.2  &  $13 \pm 13$  &  $0.017 \pm 0.001$  &  $0.225 \pm 0.005$  \\
+               & LV2b    &   7.2  &  $0.097 \pm 0.002$  &  $2.00 \pm 0.62$   &  $1.63 \pm 0.08$     &  $0.008 \pm 0.003$  &  0.8 -- 0.8  &  $28 \pm 13$  &  $0.018 \pm 0.002$  &  $0.078 \pm 0.013$  \\
+ 163-317  & LV3      &   6.9  &  $0.334 \pm 0.002$  &  $1.81 \pm 0.12$   &  $1.85 \pm 0.15$     &  $0.075 \pm 0.025$  &  0.6 -- 0.8  &  $35 \pm 5$   &  $0.018 \pm 0.001$  &  $0.205 \pm 0.025$  \\
+ 161-324  & LV4      &   6.2  &  $0.186 \pm 0.002$  &  $2.59 \pm 0.24$   &  $2.05 \pm 0.07$     &  $0.040 \pm 0.014$  &  0.8 -- 1.0  &  $18 \pm 12$  &  $0.014 \pm 0.001$  &  $0.160 \pm 0.028$  \\
+ 168-323  & LV5      &   9.6  &  $0.213 \pm 0.002$  &  $1.57 \pm 0.07$   &  $1.60 \pm 0.07$     &  $0.055 \pm 0.005$  &  0.2 -- 0.4  &  $20 \pm 5$   &  $0.022 \pm 0.001$  &  $0.190 \pm 0.010$  \\
 \bottomrule

### 2016-06-07 papers/Paper1/sec-projection.tex
24/06/15 update. Completed the remaining equations
25/06/15 Slight changes
Fix some math-mode errors
Insert new figures and correct typographics errors
Add new figures for section 2

@@
 We can specify the shell's position in cartesian coordinates $(x,y,z)$, where the x axis points towards the symetry axis of the system.
-Since the shell is cilindrically symetric, we can describe it's shape fully with the function $R(\theta)$, such that:
-
+Since the shell is cylindrically symmetric, we can describe it's shape fully with the function $R(\theta)$, such that:
 \begin{equation}
@@
 \end{equation} 
-
-Where $\theta$ is the polar angle and $\phi$ the azimutal angle from spherical coordinates
+where $\theta$ is the polar angle and $\phi$ the azimutal angle from spherical coordinates
 
@@
 frame is given by:
-
 \begin{equation}
@@
 \begin{align}
-\tan\alpha = -\left\frac{dy}{dx}\right|_{R(\theta)} \\
+\tan\alpha = -\left.\frac{dy}{dx}\right|_{R(\theta)} \\
+\label{eq:tanalpha}
 \end{align}
@@
 (\sin\theta-\omega\cos\theta)\cos\phi \\
-()\sin i + ()\sin\phi\cos i
+(\cos\theta+\omega\sin\theta)\sin i + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
 \end{array}\right)\\
 \hat{t}' &= \left(\begin{array}{c}
--()\cos i - ()\sin\phi\sin i \\
-()\cos\phi \\
--()\sin i + ()\sin\phi\cos i
+-(\sin\theta-\omega\cos\theta)\cos i - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
+(\cos\theta+\omega\sin\theta)\cos\phi \\
+-(\cos\theta+\omega\sin\theta)\sin i + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
 \end{array}\right)
@@
 \begin{equation}
-\sin\phi_t = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
+\sin\phi_t = \tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
 \label{eq:tanphi}
@@
 \begin{align}
-\tan\theta_\parallel = \frac{|\tan i| + \omega(\theta_\parallel)}{1-\omega(\theta_\parallel |\tan i|)}
+\tan\theta_\parallel = \frac{|\tan i| + \omega(\theta_\parallel)}{1-\omega(\theta_\parallel) |\tan i|}
 \label{eq:thetapar}

### 2016-06-07 papers/Paper1/sec-application.tex
Include results subsection.
Enhance pressure figure description in text

@@
 R &\simeq R_0 \left(1+\gamma\theta^2\right)
-\label{eq:R_approx}
+\label{eq:R_approx} \\
 \mathrm{where:~} & \gamma = \frac{1}{6} + \frac{\beta^{1/2}}{3}\left[1+\frac{1-\beta^{1/2}}{10}-\frac{3}{40}\frac{k}{1+\beta^{1/2}}\right]
@@
 With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
-momenta and different density distributions. Figure \ref{fig:rad-beta} shows  eqautions  ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
+momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
 
@@
 
-\subsubsection{Methodology}
+\subsection{Methodology}
 \label{sec:methodology}
@@
 see how much these ``variations'' deviates from the original data. Some examples are shown  in figure (\ref{fig:char-radii-obs}).  In the left side, for each source, 
-the fit is done using all the shell points, while in the middle and the right we show two variations removing 2/3 of thepoints, but always keeping at least four. 
+the fit is done using all the shell points, while in the middle and the right we show two variations removing 2/3 of the points, but always keeping at least four. 
 In the better observed shells such as 177-341 (top row), the circle
@@
 the radii $(R_0,R_c)$ are measured as the average of all subsamples, and the uncertainty as the standard deviation.
-
+\subsection{Results}
+\label{sec:results}
 In figure (\ref{fig:conic-xi}) we show the theoretical conic curves. Most of the proplyds fit well 
@@
 
-Using the data from figure \ref{fig:conic-xi}, we estimate for each source the parameters $(\beta,i,\xi)$. With this, is possible to estimate the non projected distances $(R_0,D)$, 
-from which we can estimate the stagnation pressure at the bow shock's position, 
-and compare it with the expected pressure from the stellar wind at the distance $D$. Since we expect equilibrium pressure in the bow shock surface, both pressures should be the same. 
-In figure \ref{fig:pressure} we compare the estimated flux and pressure to balance ionization in the photoevaporated flow and pressure balance, respectively. In column 6 of table \ref{tab:arc-fits}
-we selected some subsamples where the measurements of $R_c'$ lead to a better approach to ionization balance and pressure balance. 
+Using the data from figure \ref{fig:conic-xi}, we estimate for each source the parameters $(\beta,i,\xi)$ (columns 7, 8 and 9 from table \ref{tab:arc-fits}).
+With this, is possible to estimate the non projected distances $(R_0,D)$ (columns 10 and 11).
+
+Using the data from table \ref{tab:arc-fits} along with the ionization front radius and photoevaporation flow density obtained from \citet{HA:1998} we measured the stagnation pressure at the bow shock's position,
+and compare it with the expected pressure from the stellar wind at the distance $D$.
+Since we expect equilibrium pressure in the bow shock surface, both pressures should be the same.
+The comparison is done in figure \ref{fig:pressure} (bottom).
+
+We also expect the stellar ionizing flux should be the required to balance the photoevaporated flux. We do
+the comparison in figure \ref{fig:pressure} (top). In both cases, the highlighted points represent the variations which have better agree with ionization balance and pressure balance, respctively.
+
 For the farthest proplyds, we can see that the estimated pressure is greater than the stellar wind pressure, even with the best fits.
@@
 \caption{Top: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd. The gray line represents the stellar flux at the distance $D$. 
-Bottom: In colored lines, estiamted stagnation pressure for each proplyd. 
+Bottom: In colored lines, estimated stagnation pressure for each proplyd. 
 The gray solid line represent the stellar wind at the distance $D$.

### 2016-06-07 papers/Paper1/sec-generic-model.tex
Minor corrections to article
Week's changes in figures 2, 7 and respective sections
Add new figures for section 2
Final version (?) of Fig 1

@@
 \begin{figure}
-\includegraphics[width=\linewidth]{2winds-scheme}
-\caption{Schematic representation of the two winds problem. Any point in the shell is located with the coordinates
-$(R,\theta)$, and $\theta_1$ is measured from the external wind position}
+% \includegraphics[width=\linewidth]{2winds-scheme}
+\includegraphics[width=\linewidth]{figs/generic-bowshock}
+\caption{Quasi-stationary bow shock structure formed by the
+  interaction of two supersonic winds.  Lower-left inset box shows the
+  case where the inner wind is anisotropic.   
+  % the two winds problem. Any point in the shell is located with the
+  % coordinates $(R,\theta)$, and $\theta_1$ is measured from the
+  % external wind position
+}
 \label{fig:2-winds}
 \end{figure}
+
+The general case of a two-wind interaction bow shock is illustrated in
+Figure~\ref{fig:2-winds}.  If the winds are isotropic, then the bow
+shock pattern wraps around the weaker of the two sources, in
 
@@
 
-In order to contrast different bowshock models, we  derive a set of measurable radii. Each model used should predict them and these predictions can be
+In order to contrast different bow shock models, we  derive a set of measurable radii. Each model used should predict them and these predictions can be
 compared with observations.
@@
 \begin{itemize}
-\item Radius at axis of symemtry. Denoted as $R_0$. 
+\item Radius at axis of symmetry. Denoted as $R_0$. 
 \item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
 \item Radius at the  perpendicular direction to the symmetry axis. Denoted as $R_{90}$
-\item For open bow shocks, the assymptotic angle. Denoted as $\theta_\infty$
+\item For open bow shocks, the asymptotic angle. Denoted as $\theta_\infty$
 \end{itemize}
@@
 \begin{figure}
-\includegraphics[width=\linewidth]{ch-radii_ed}
+\includegraphics[width=\linewidth]{ch-radii_ed2}
 \caption{Schematic representation of the characteristic radii $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis $R_c$}

### 2016-06-10 papers/Paper1/proplyd-bowshocks.tex
New start on Jorge's paper
Paper1 - fix {array} envs and untrack .log, .pdf
Paper1: Add bibliography and make start on intro
All references should go in bowshocks-biblio.bib
Add short title and author list
Also, define commands for the cos/cosh terms in the conic section
equations.  Try out using cursive upper case letters, but we may change
those later
More on bow shocks for intro
Mention jet-driven bow shocks.  Add a lot of references. Also first para
of abstract
Add table to paper of arc parameters from fits
Change CRyA to IRya

@@
+\RequirePackage{amsmath}
 \documentclass[useAMS,usenatbib]{mn2e}
@@
 \usepackage{fixltx2e}
+\usepackage{booktabs}
 \usepackage{hyperref}
@@
 
-\title{Photoionized bow shock shells.  I. Wind-wind interactions in the Orion proplyds}
+\title[Bowshock shapes]{True versus apparent shapes of astrophysical bow shocks}
 
-\newcommand\AddressCRyA{Centro de Radioastronom\'{\i}a y Astrof\'{\i}sica,
+\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
   Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
   58090 Morelia, Michoac\'an, M\'exico}
-\author{
+\author[Tarango Yong \& Henney]{
   Jorge A. Tarango Yong \& William J. Henney\\
@@
 \begin{abstract}
-
+  We develop a general framework for the effects of viewing angle on
+  the apparent shape of a limb-brightened, cylindrically symmetric
+  curved shock (bow shock).  
 \end{abstract}
 
-\section{Introduction}
-\label{sec:intro}
+\input{sec-intro}
+\input{sec-generic-model}
+\input{sec-projection}
+\input{sec-conic}
+\input{sec-application}
+\input{sec-conclusions}
 
-\section{Conclusions}
-\label{sec:conc}
+%% TODO Investigate newer versions of BST file from
+%% https://github.com/timj/mn2e-bst
+\bibliographystyle{mn2e}
+%% All references should be put in the BibTeX file bowshocks-biblio.bib
+\bibliography{bowshocks-biblio}
 
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2016-06-14 papers/Paper1/sec-conclusions.tex
New start on Jorge's paper
Start writting conclusions

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
+\section{Conclusions}
+\label{sec:conc}
+
+\newcommand\thC{\(\theta^1\)\,Ori~C}
+\defcitealias{Canto:1996}{CRW}
+
+We developed a method to estimate the shape of a generic bow shock product of the
+interaction of two winds and was applies to the proplyds in the core of the ONC.
+We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
+sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
+on \CRW{} work to estimate the intrinsic bow shock shape and get the stagnation pressure.
+Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
+distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
+while LV2 has the most anisotropic flow.
 

### 2016-06-15 papers/Paper1/sec-conic.tex
New figure with plane-of-sky projection

@@
-\section{Conic section approximation}
+\section{Quadrics of revolution}
 \label{sec:conic}
@@
 
+For an arbitrary surface of revolution, application of
+equations~(\ref{eq:tanphi}, \ref{eq:tangential}) to determine the
+projected shape of the tangent line is not straightforward and in
+general requires numerical techniques.  However, analytical results
+can be found for the important class of surfaces known as
+\textit{quadrics of revolution} \citep{Goldman:1983a, Gfrerrer:2009a},
+which are formed by rotating a conic section plane curve about its
+symmetry axis.  Examples are the sphere, spheroids (oblate and
+prolate), and right circular paraboloids and hyperboloids.\footnote{We
+  consider only the case of a single sheet of a 2-sheet hyperboloid or
+  paraboloid.}  We ignore the degenerate cases of cylinders, cones,
+and pairs of parallel planes.  While mathematically simple, these
+quadrics are sufficiently flexible that they can provide a useful
+approximation to more complex bow shock shapes.
+
+The 
 In this section we will analyze the case where the resultant shape  of the bow shock is a conic curve (circle, ellipse, parabola or hyperbola).
@@
 \begin{tabular}{cc}
-\includegraphics[height=0.44\linewidth, trim=30 0 30 0, clip]{ellipse_py_lab} &
-\includegraphics[height=0.44\linewidth, trim=60 0 70 0, clip]{hyperbola_py_lab}
+\includegraphics[height=0.54\linewidth, trim=30 0 30 0, clip]{ellipse_py_lab} &
+\includegraphics[height=0.54\linewidth, trim=60 0 70 0, clip]{hyperbola_py_lab}
 \end{tabular}
@@
 in equation (\ref{eq:thc-conic}). The opposite applies for ellipses.
-\subsection{Plane-of-sky projection of conic sections} 
+\subsection{Plane-of-sky projection of quadric surfaces} 
 \begin{figure*}

### 2016-06-15 papers/Paper1/sec-projection.tex
New figure with plane-of-sky projection

@@
 
-In this section we calculate the apparent shape of a limb brightened  border of a generic bow shock with cilindrical geometry, observed in the
-plane of the sky.
+In this section we calculate the apparent shape on the plane of the
+sky of the limb brightened border of a shock or shell that is
+idealized as as arbitrary cylindrically symmetric surface.
 
@@
 
-We can specify the shell's position in cartesian coordinates $(x,y,z)$, where the x axis points towards the symetry axis of the system.
-Since the shell is cylindrically symmetric, we can describe it's shape fully with the function $R(\theta)$, such that:
+Consider body-frame cartesian coordinates $(x,y,z)$, where \(x\) is
+the symmetry axis, and spherical polar coordinates
+\((R, \theta, \phi)\), where \(\theta\) is the polar angle and
+\(\phi\) the azimuthal angle.  Since the surface is cylindrically
+symmetric, it is can be specified as $R = R(\theta)$, so that
+cartesian coordinates on the surface are:
 \begin{equation}
@@
 \sin\theta\sin\phi
-\end{array}\right)
+\end{array}\right).
 \end{equation} 
-where $\theta$ is the polar angle and $\phi$ the azimutal angle from spherical coordinates
-
-The observer's reference frame is denotated with primes, and is rotated respect y axis by an angle $i$. The transformation between the shell frame and the observed
-frame is given by:
+Suppose that the viewing direction makes an angle \(i\) with the \(z\)
+axis, so that we can define observer-frame coordinates
+\((x', y', z')\), which are given by the rotating the body-frame
+coordinates:
 \begin{equation}
@@
 z\cos i + x\sin i
-\end{array}\right)
+\end{array}\right).
 \label{eq:Trans}
 \end{equation} 
+In what follows, all quantities in the observer's frame are denoted by
+attaching a prime to the equivalent quantity in the body frame.  The
+coordinates \(x'\) and \(y'\) are in the plane of the sky, with \(x'\)
+being the projected symmetry axis of the surface, while the line of
+sight lies along \(-z'\).  The inclination angle \(i\) is defined so
+that \(i = 0^\circ\) when the surface is viewed perpendicular to its
+axis (\textit{side on}) and \(i = 90^\circ\) when it is viewed along
+its axis (\textit{end on}).
 
@@
 The normal and tangent vectors to the shell's border in the shell's frame are given by:
-
 \begin{align}
@@
 \end{align}
-
 Where:
-
 \begin{align}
@@
 \end{align}
-
 Then we apply the transformation (\ref{eq:Trans}) to the normal and tangent vectors to obtain:
-
 \begin{align}
@@
 \end{align}
-
 Where $\omega = \frac{1}{R}\frac{dR}{d\theta}$
@@
 The values for $\phi$ that satisfy this relation for each inclination $i$ are given by:
-
 \begin{equation}
@@
 \end{equation}
-
 With this, the coordinates of the limb brightened shell are given by:
-
 \begin{equation}
@@
 $\theta_\parallel$ is given implicitly by:
-
 \begin{align}
@@
 and $R'_\perp = y'_t(x'_t=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:
-
 \begin{align}
@@
 \end{align}
-
 Where $\theta_\parallel$ is the solution of equation (\ref{eq:thetapar}), and
-
 \begin{align}
@@
 \end{align}
-
 Where $\theta_\perp$ is the solution of the next implicit equation:
-
 \begin{align}

### 2016-06-15 papers/Paper1/sec-projection.tex
Include POS projection figure in section 3
And brief discussion in text

@@
 \end{equation} 
-In what follows, all quantities in the observer's frame are denoted by
-attaching a prime to the equivalent quantity in the body frame.  The
-coordinates \(x'\) and \(y'\) are in the plane of the sky, with \(x'\)
-being the projected symmetry axis of the surface, while the line of
-sight lies along \(-z'\).  The inclination angle \(i\) is defined so
-that \(i = 0^\circ\) when the surface is viewed perpendicular to its
-axis (\textit{side on}) and \(i = 90^\circ\) when it is viewed along
-its axis (\textit{end on}).
+The relationship between the two frames is illustrated in
+Figure~\ref{fig:projection-pos}.  All quantities in the observer's
+frame are denoted by attaching a prime to the equivalent quantity in
+the body frame.  The celestial coordinates on the ``plane of the sky''
+are given by \((x', y')\) with \(x'\) being the projected symmetry
+axis of the surface, while the line of sight lies along \(-z'\).  The
+inclination angle \(i\) is defined so that \(i = 0^\circ\) when the
+surface is viewed perpendicular to its axis (\textit{side on}) and
+\(i = 90^\circ\) when it is viewed along its axis (\textit{end on}).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/projection-pos}
+  \caption{Relationship between body frame (unprimed coordinates) and
+    observer frame (primed coordinates).}
+  \label{fig:projection-pos}
+\end{figure}
 

### 2016-06-16 papers/Paper1/sec-projection.tex
Lots of improvements to section 3
Also, upgrade to the latest version of MNRAS macros: mnras.cls

@@
+\newenvironment{Vector}{\left(\begin{array}{c}}{\end{array}\right)}
+\newcommand\uvec[1]{\bm{\hat{#1}}}
+\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+
 \section{Projection onto the plane of the sky}
@@
 sky of the limb brightened border of a shock or shell that is
-idealized as as arbitrary cylindrically symmetric surface.
+idealized as an arbitrary cylindrically symmetric surface.
 
@@
 \begin{equation}
-\left(\begin{array}{c}
+  \begin{Vector}
     x \\ y \\ z
-\end{array}
-\right) = R(\theta)\left(\begin{array}{c}
+  \end{Vector} 
+  = R(\theta)
+  \begin{Vector}
     \cos\theta \\
@@
     \sin\theta\sin\phi
-\end{array}\right).
+  \end{Vector}.
+  \label{eq:body-frame}
 \end{equation} 
-Suppose that the viewing direction makes an angle \(i\) with the \(z\)
-axis, so that we can define observer-frame coordinates
-\((x', y', z')\), which are given by the rotating the body-frame
-coordinates:
+Suppose that the viewing direction makes an angle \(i\) with the
+\(z\)~axis, so that we can define observer-frame coordinates
+\((x', y', z')\), which are found by rotating the body-frame
+coordinates about the \(y\)~axis:
 \begin{equation}
-\left(\begin{array}{c}
+  \begin{Vector}
     x' \\ y' \\ z'
-\end{array}
-\right) = \left(\begin{array}{c}
+  \end{Vector}
+  = 
+  \begin{Vector}
     x\cos i - z\sin i\\
@@
     z\cos i + x\sin i
-\end{array}\right).
+  \end{Vector}.
   \label{eq:Trans}
@@
 
+\subsection{Unit vectors normal and tangential to the surface}
+\label{sec:unit-vectors-normal}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/bowshock-unit-vectors}
+  \caption{Normal and tangential unit vectors}
+  \label{fig:unitvec}
+\end{figure}
+We define unit vectors \(\uvec{n}, \uvec{t}\), such that \(\uvec{n}\) is normal to the surface, while \(\uvec{t}\) is tangent to the surface in a plane of constant \(\phi\).
+For \(\phi = 0\) the surface lies in the \(xy\) plane and it is straightforward to show (Fig.~\ref{fig:unitvec}) that in this case the unit vectors are given by
+\begin{equation}
+  \label{eq:uvec-phi0}
+  \uvec{t}_0 =
+  \begin{Vector}
+    -\cos\alpha \\ \sin\alpha \\ 0
+  \end{Vector}
+  \quad \mathrm{and} \quad
+  \uvec{n}_0 =
+  \begin{Vector}
+    \sin\alpha \\ \cos\alpha \\ 0
+  \end{Vector}, 
+\end{equation}
+where
+\begin{equation}
+  \label{eq:alpha}
+  \tan\alpha = -\left.\frac{dy}{dx}\right\vert_{R(\theta)} 
+  = \frac{1 + \omega \tan\theta}{\tan\theta - \omega}
+\end{equation}
+and 
+\begin{equation}
+  \label{eq:omega}
+  \omega(\theta) = \frac{1}{R} \frac{dR}{d\theta} . 
+\end{equation}
+For general \(\phi\), \(\uvec{n}\) and \(\uvec{t}\) can be found by rotating equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, which can then be converted to the observer frame by use of equation~(\ref{eq:Trans}) to give
+\begin{gather}
+  \label{eq:nprime}
+  \begin{split}
+    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
+    & \times 
+      \begin{Vector}
+        (\cos\theta+\omega\sin\theta)\cos i 
+        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
+        (\sin\theta-\omega\cos\theta)\cos\phi \\
+        (\cos\theta+\omega\sin\theta)\sin i 
+        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
+      \end{Vector}\\
+  \end{split}\\
+  \label{eq:tprime}
+  \begin{split}
+    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
+    & \times 
+      \begin{Vector}
+        -(\sin\theta-\omega\cos\theta)\cos i
+        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
+        (\cos\theta+\omega\sin\theta)\cos\phi \\
+        -(\cos\theta+\omega\sin\theta)\sin i 
+        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
+      \end{Vector}
+  \end{split}
+  \end{gather}
+
 \subsection{Tangent line}
 
-The normal and tangent vectors to the shell's border in the shell's frame are given by:
-\begin{align}
-\hat{t} = \left(\begin{array}{c}
--\cos\alpha \\
-\sin\alpha\cos\phi\\
-\sin\alpha\sin\phi
-\end{array}\right)\\
-\hat{n} = \left(\begin{array}{c}
-\sin\alpha \\
-\cos\alpha\cos\phi \\
-\cos\alpha\sin\phi
-\end{array}\right)
-\end{align}
-Where:
-\begin{align}
-\tan\alpha = -\left.\frac{dy}{dx}\right|_{R(\theta)} \\
-\label{eq:tanalpha}
-\end{align}
-Then we apply the transformation (\ref{eq:Trans}) to the normal and tangent vectors to obtain:
-\begin{align}
-\hat{n}' &= \left(\begin{array}{c}
-(\cos\theta+\omega\sin\theta)\cos i -(\sin\theta-\omega\cos\theta)\sin i \sin\phi\\
-(\sin\theta-\omega\cos\theta)\cos\phi \\
-(\cos\theta+\omega\sin\theta)\sin i + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-\end{array}\right)\\
-\hat{t}' &= \left(\begin{array}{c}
--(\sin\theta-\omega\cos\theta)\cos i - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
-(\cos\theta+\omega\sin\theta)\cos\phi \\
--(\cos\theta+\omega\sin\theta)\sin i + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-\end{array}\right)
-\end{align}
-Where $\omega = \frac{1}{R}\frac{dR}{d\theta}$
+% For optically thin emission with isotropic emissivity \(j\), the observed
+% surface brightness for any line of sight that intersects the shell is
+% \(S = \int j \, dz' / 4\pi\).
 
-In the thin shell case, the limb brightened border of the shell is such that $\hat{n}'\cdot \hat{z}'$. 
-The values for $\phi$ that satisfy this relation for each inclination $i$ are given by:
+% If the shell thickness is \(h(\theta)\) and emissivity is
+% \(j(\theta)\), then for optically thin emission the observed
+% surface brightness for any line of sight that intersects the shell is
+% \(S = j s / 4\pi\), where \(s\)
+
+% in the limit \(h \ll R\) and
+% \(\mu\) is
+% the cosine of the angle between the line of sight and the local normal
+% to the shell surface at the point of intersection:
+% \begin{equation}
+%   \label{eq:2}
+%   \mu = \uvec{n} \cdot \uvec{z}'
+% \end{equation}
+
+The boundary on the plane of the sky of the projected surface is the
+locus of those lines of sight that graze the surface tangentially.
+This corresponds to a curved line on the surface itself, which we
+denote the \textit{tangent line}, and which is defined by the
+condition 
 \begin{equation}
-\sin\phi_t = \tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
+  \label{eq:tangent-line-condition}
+  \uvec{n}'\cdot \uvec{z}' = 0.
+\end{equation}
+We denote by \(\phi\T\) that value of $\phi$ that satisfies this
+relation for a given inclination, \(i\), and polar angle, \(\theta\):
+\begin{equation}
+\sin\phi\T = \tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
 \label{eq:tanphi}
 \end{equation}
-With this, the coordinates of the limb brightened shell are given by:
+From equations~(\ref{eq:body-frame}, \ref{eq:Trans}) it follows that
+the observer-frame coordinates of the tangent line are given by
 \begin{equation}
 \left(\begin{array}{c}
-x'_t \\ y'_t \\ z'_t
+x'\T \\ y'\T \\ z'\T
 \end{array}\right)= R(\theta)\left(\begin{array}{c}
-\cos\theta\cos i - \sin\theta\sin\phi_t \sin i \\
-\sin\theta(1-\sin^2\phi_t)^{1/2} \\
-\cos\theta\sin i +\sin\theta\sin\phi_t\cos i
-\end{array}\right)
+\cos\theta\cos i - \sin\theta\sin\phi\T \sin i \\
+\sin\theta(1-\sin^2\phi\T)^{1/2} \\
+\cos\theta\sin i +\sin\theta\sin\phi\T\cos i
+\end{array}\right).
 \label{eq:tangential}
 \end{equation} 
+Note that, in general, \(z'\T\) is not a linear function of \(x'\T\)
+and \(y'\T\), so that the tangent line is not a plane curve.
 
-It is important to note that the equation (\ref{eq:tanphi}) does not have a solution for arbitrary values for $\theta$ and $i$, since
-it's required that $|\sin\phi_t|<1$. If $i\neq 0$, then, the  allowed values for $\theta$ are such that $\theta > \theta_\parallel$, where
-$\theta_\parallel$ is given implicitly by:
+The apparent shape \((x'\T, y'\T)\) of the tangent line on the plane
+of the sky can also be described in polar form as \(R'(\theta')\),
+where
+\begin{equation}
+  \label{eq:R-prime-theta-prime}
+  R' = (x'^2\T+ y'^2\T)^{1/2} 
+  \quad \text{and} \quad
+  \tan\theta' = y'\T / x'\T.
+\end{equation}
+It is important to note that equation~(\ref{eq:tanphi}) does not have
+a solution for arbitrary values of $\theta$ and $i$, but only when
+$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent
+line only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is
+given implicitly by
 \begin{align}
-\tan\theta_\parallel = \frac{|\tan i| + \omega(\theta_\parallel)}{1-\omega(\theta_\parallel) |\tan i|}
+\tan\theta_{0} = \frac{|\tan i| + \omega(\theta_{0})}{1-\omega(\theta_{0}) |\tan i|} . 
 \label{eq:thetapar}
 \end{align}
+In addition, if the surface is sufficiently ``open''
+(\(\alpha > \alpha_{\mathrm{min}} > 0\) for all \(\theta\)), then for
+those inclinations with
+\(\vert i\vert > (90^\circ - \alpha_{\mathrm{min}}) \) the tangent
+line does not exist for any value of \(\theta\).  In other words, when
+the viewing angle is sufficiently close to face-on, the projected
+surface has no ``edge'' and will no longer appear to be a bow shock.
 
@@
 Considering further applications to bow shocks, we will consider open shells. In order to compare the shell shape given by $R(\theta)$ with observations,
-it is convenient to define the following apparent radii in the observer frame: $R'_\parallel$ and $R'_\perp$. These are projected distances of the shell tangent line
-from the origin. The first is measured in the direction of the symetry axis, and the second in a perpendicular direction. More concretely $R'_\parallel = x'_t(y'_t=0)$
-and $R'_\perp = y'_t(x'_t=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:
+it is convenient to define the following apparent radii in the observer frame: $R'_{0}$ and $R'_{90}$. These are projected distances of the shell tangent line
+from the origin. The first is measured in the direction of the symetry axis, and the second in a perpendicular direction. More concretely $R'_{0} = x'\T(y'\T=0)$
+and $R'_{90} = y'\T(x'\T=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:
 \begin{align}
-R'_\parallel = R(\theta_\parallel)\cos(\theta + i) \label{eq:Rpar} 
+R'_{0} = R(\theta_{0})\cos(\theta + i) \label{eq:Rpar} 
 \end{align}
-Where $\theta_\parallel$ is the solution of equation (\ref{eq:thetapar}), and
+Where $\theta_{0}$ is the solution of equation (\ref{eq:thetapar}), and
 \begin{align}
-R'_\perp = R(\theta_\perp)\sin\theta_\perp\left(1-\sin^2(\phi_t(\theta_\perp))\right)^{1/2}
+R'_{90} = R(\theta_{90})\sin\theta_{90}\left(1-\sin^2(\phi\T(\theta_{90}))\right)^{1/2}
 \end{align}
-Where $\theta_\perp$ is the solution of the next implicit equation:
+Where $\theta_{90}$ is the solution of the next implicit equation:
 \begin{align}
-\cot\theta_\perp = \frac{1-\left(1+\omega(\theta_\perp)^2\sin^22i\right)^{1/2}}{2\omega(\theta_\perp\cos^2 i)}
+\cot\theta_{90} = \frac{1-\left(1+\omega(\theta_{90})^2\sin^22i\right)^{1/2}}{2\omega(\theta_{90})\cos^2 i}
 \end{align}
+
+  \subsection{Line-of-sight velocities on the tangent line}
+  \label{sec:line-sight-veloc}
+  Motions in a thin shocked shell will be predominantly tangential to the shell surface.
+In addition, for the particular case of wind-wind bowshocks, the flow in each azimuthal slice can be shown to be independent \citep{Wilkin:2000a}, which implies that the shell velocity is parallel to \(\uvec{t}\).
+The projected line-of-sight shell velocity is therefore
+  \begin{equation}
+    \label{eq:vlos}
+    v_{\mathrm{los}} = (\uvec{t}' \cdot -\uvec{z}') \, v_{\parallel}(\theta) = \frac{v_{\parallel}(\theta) (1+\omega^2)^{1/2} \sin i }{\sin\theta - \omega\cos\theta} ,
+  \end{equation}
+  where \( v_{\parallel}(\theta)\) is the gas velocity along the shell and the standard sign convention has been adopted such that velocities away from the observer are deemed positive.
 

### 2016-06-21 papers/Paper1/sec-projection.tex
Minor changes to unit vector figure
New version of Figure 2
Next, I will move this from sec 2 to sec 3
Move characteristic radii fig to sec 3

@@
 
+\subsection{Characteristic radii}
+\label{sec:characteristic-radii}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/characteristic-radii}
+  \caption{Characteristic radii in the body frame.}
+  \label{fig:characteristic-radii}
+\end{figure}
+
 \subsection{Unit vectors normal and tangential to the surface}
@@
   \includegraphics[width=\linewidth]{figs/bowshock-unit-vectors}
-  \caption{Normal and tangential unit vectors}
+  \caption{Unit vectors in the body frame that are normal and
+    tangential to the surface \(R(\theta)\) in a plane of constant
+    azimuth, \(\phi\).}
   \label{fig:unitvec}
@@
 
-\subsection{Parallel and perpendicular projected shell radii}
+\subsection{Characteristic radii on the plane of the sky}
 

### 2016-06-21 papers/Paper1/sec-application.tex
Add to paper new version of characterstic radii

@@
 \begin{tabular}{c}
-\includegraphics[width=\linewidth]{AB-beta} \\
-\includegraphics[width=\linewidth]{thc-beta}
+\includegraphics[width=\linewidth]{figs/AB-beta-log} \\
+\includegraphics[width=\linewidth]{figs/thc-beta-log}
 \end{tabular}
-\caption{Top:Characteristic radii, normalized with $R_0$ vs $\beta$. In solid line we plot the radius of curvature, while in dashed line we plot $R_{90}$. Bottom: $\theta_c$ vs $\beta$. For
-highly anisotropic shells $\xi <0.4$, the resulting shell has shape of an oblate spheroid, while for the isotropic case, the resulting shell is an hyperbola.
-the proplyd case is noticeable because it has
-a transition from spheroidal shapes to hyperbola.
-%$\theta_c$, $R_c$ and $R_{90}$ versus $\beta$ for different anisotropy degrees, represented with the $\xi$ paramenter.}
-}
+\caption{Top: Characteristic radii, $A = R_c/R_0$ (solid lines) and $B
+  = R_{90}/R_0$ (dashed lines)
+  vs $\beta$, calculated from quadric fits to the generalized CRW
+  solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
+  angle $\theta_c$ vs $\beta$ for the bow 
+  shock head (solid lines) and the bow shock tail (dashed lines).}
 \label{fig:rad-beta}

### 2016-06-28 papers/Paper1/sec-application.tex
Corrected/updated some equations.
+ Corrected bad written equations in sections 4,5
+ Updated equation for radius of curvature

@@
 
-Where $k >0$ implies that the wind's density decays towards wings, when $k<0$ the wind's density incresases towards the wings and $k=0$ implies that the wind is isotropic.
+Where $k >0$ implies that the wind's density decays towards wings, when $k<0$ the wind's density incresases towards the wings and $k=0$
+implies that the wind is isotropic.
+In this generalization we are assuming that the inner wind is hemispheric, i.e. the density of the photoevaporated flow behind the source is zero, since equation
+(\ref{eq:ngen}) leads to non realistic values for density when $\theta > \frac{\pi}{2}$
 
@@
 
-If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}), we find that the solutions for equations (8) - (11) of \CRW{} are the following:
+%If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}),
+%we find that the solutions for equations (8) - (11) of \CRW{} are the following:
+
+If we apply the \CRW{} formalism for a generalized photoevaporated flow with density given by equation (\ref{eq:ngen}),
+the shell shape $R(\theta)$ may be calculated from equation (6) of CRW{}:
 
 \begin{align}
+  R = \frac{\dot{J}_w + \dot{J}_{w1}}{\left(\dot{\Pi}_{wr}+\dot{\Pi}_{wr1}\right)\cos\theta-\left(\dot{\Pi}_{wz1}+\dot{\Pi}_{wz1}\right)\sin\theta}
+  \label{eq:Rmom}
+\end{align}
+
+Where:
+
+\begin{align}
+\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
+\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w v_w I_k (\theta) \label{eq:piz}\\
+I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \\
+\dot{J}_w = 0 \label{eq:jdot} \\
 \dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
-\mathrm{where} & M^0_w \equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
-\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
-\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w V_w I_k (\theta) \label{eq:piz}\\
-I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \\
-\dot{J}_w = 0 \label{eq:jdot}
+M^0_w &\equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
+\dot{\Pi}_{wz1} & = -\frac{\dot{M}^0_{w1}v_{w1}}{4}\sin^2\theta_1\\
+\dot{\Pi}_{wr1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
+\dot{J}_{w1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \label{eq:jdot1}
 \end{align}  
-Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}  we can obtain the bow shock shape $R(\theta)$. Actually, we work with two different scenarios:
-% as illustred in figure (\ref{fig:r-beta}), where we show the resulting bow shock shapes for two scenarios:
-$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison betwwen both solutions is shown in figure (\ref{fig:r-beta}).
+Combining equations  (\ref{eq:pir}) to (\ref{eq:jdot1}) we can obtain the bow shock shape $R(\theta)$ from equation (\ref{eq:Rmom}).
+The most notable scenarios, since they have astrophysical relevance are the following:
+$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
+is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
 
@@
 
-In order to find an analytic form of the characteristic radii $(R_0,R_c,R_{90})$, we may combine equations (\ref{eq:dotprop}) to (\ref{eq:jdot}) with (6) and (23) from \CRW{}
-and obtain the following relation:
+%Here goes a little introduction
 
@@
 \begin{align}
-R_{90} &= D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} &= 1-\frac{2\beta}{k+2} \label{eq:th190}
+R_{90} = D\tan\theta_{1,90} \\
+\theta_{1,90}\cot\theta_{1,90} = 1-\frac{2\beta}{k+2} \label{eq:th190}
 \end{align}
@@
 \begin{align}
-\theta_{1,90} \simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
+\theta_{1,90} &\simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
 \label{eq:th190sol}
@@
 \begin{align}
-\theta_1^2 &\simeq \beta\theta^2\left[1+ \left(A_k-\frac{\beta}{15}\right)\theta^2\right] \\
-\mathrm{where:~} & A_k = \frac{1}{15}-\frac{k}{20}
+\theta_1^2 &\simeq \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right] \\
+\mathrm{where:~} & C_{k\beta} \equiv \frac{1}{30}\left(1-\beta-\frac{9}{4}k\right)
 \end{align}
@@
 \label{eq:R_approx} \\
-\mathrm{where:~} & \gamma = \frac{1}{6} + \frac{\beta^{1/2}}{3}\left[1+\frac{1-\beta^{1/2}}{10}-\frac{3}{40}\frac{k}{1+\beta^{1/2}}\right]
+\mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
 \end{align}

### 2016-06-30 papers/Paper1/sec-conic.tex
Corrected/updated some equations.
+ Corrected bad written equations in sections 4,5
+ Updated equation for radius of curvature
Found and corrected more typos in quadrics section
Improve Fig 7 (family of conics)

@@
 \includegraphics[width=\linewidth]{conic1}
-\caption{A whole set of conics with the same radius of curvature. The parameter $\theta_c$ is used as the equivalent of the excentricity. This angle is defined as positive for closed curves
-and negative for the opened ones. An special case is $\theta_c=0$, which describes a parabola.}
+\caption{Example of a family of conic sections, all with the same
+  radius of curvature at their apex (marked by white dot) on the
+  \(x\)~axis: \(R_c = 2 R_0\). The parameter
+  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
+  values corresponding to hyperbolae.}
 \label{fig:conics-family}
@@
 \frac{R_c}{D} &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
-\frac{R_{90}}{D} &= b\left(1 \mp \frac{(R_0-a)^2}{a^2}\right)
+\frac{R_{90}}{D} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}
 \end{align}
@@
 \begin{align}
-a &= \frac{R_c}{2A-B^2} \label{eq:a-conic}\\
-b &= \left(aR_c\right)^{1/2}\\
-\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} \\
+\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
+\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|}\\
+\tan\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} \\
 \mathrm{where:}& B\equiv \frac{R_{90}}{R_0} \\
@@
 X' = \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
-Y'= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot(t)\right)^{1/2}
+Y'= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot^2(t)\right)^{1/2}
 \label{eq:conic-projected-y}
@@
 a' = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
-\Cos(t') = \frac{\Cos(t)}{a\cos i} \\
+\Cos(t') = \frac{a'\Cos(t)}{a\cos i} \\
 b' = b
@@
 
-With  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
-radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:
+With  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
 \begin{align}

### 2016-09-09 read-shapes/thetaC_vs_Obs.py
Add max inclination for theoretcal curves
Also modified in applications tex file the sections order
to convert CRW scenario in a section and put it before the applications
section

@@ -8,7 +8,8 @@ sys.path.insert(0,"../conic-projection")
 from conproj_utils import Conic
 import glob
 import json
-
+from scipy.optimize import fsolve
+from scipy.special import gamma as gamma_func
 # Contrast  conic curves against observations
 
 
@@ -35,36 +36,72 @@ def theta_c(beta,xi=1.0):
     return np.sign(arg)*np.arctan(np.sqrt(np.abs(arg)))
 
 def q(b):
+    """
+    Returns the radius on axis normalized with D
+    """
     return np.sqrt(b)/(1.+np.sqrt(b))
+
+def theta_infty(beta,xi,CRW=False):
+    """
+    Asymptotic angle of bowshock. If choose CRW as True then use
+    CRW solution for th_infty
+    """
+    def f_infty(th,beta,xi):
+        """
+        Function to be zeroed
+        """
+        k = 2./xi-2
+        C = (k+2*(1-beta))/(k+2)
+        I = np.sqrt(np.pi)*gamma_func(0.5*(k+1))/(4*gamma_func(0.5*k+2))
+        D = np.pi + 2*beta*I
+        return th-C*np.tan(th) - D
+    def f_CRW(th,beta):
+        """
+        CRW implicit equation for th_infty
+        """
+        return th -np.tan(th) - np.pi/(1.0-beta)
+
+    th_init = 91.0
+    if CRW:
+        th_inf, infodict, ier, mesg = fsolve(f_CRW,th_init,args=(beta),full_output=True)
+    else:
+        th_inf, infodict, ier, mesg = fsolve(f_infty,th_init,args=(beta,xi),full_output=True)
+    return th_inf
+
 #Step 1 Define command variables
 
 parser = argparse.ArgumentParser(description="Command line options")
 parser.add_argument("--xi",type=float,default=1.0,help="inner wind parameter")
-
+parser.add_argument("CRW",action="store_true",help="use CRW solution")
 args = parser.parse_args()
 Xi = args.xi
-
+CRW = args.CRW
+if CRW:
+    Xi = 1.0
+    
 #Step 2: Initialize arrays
 
 
 beta = [5e-4, 0.001, 0.002, 0.005, 0.01, 0.02, 0.05, 0.1]
 sns.set_style("ticks")
 colors = sns.color_palette('Blues', len(beta))
-
 inc = np.linspace(0,75,100)
[…]

### 2016-09-09 read-shapes/thetaC_vs_Obs.py
Correct issues in program which creates A' vs q' graphs
Added the new figures. No visible changes detected.

Results subsection becomes section

@@ -61,7 +61,7 @@ def theta_infty(beta,xi,CRW=False):
         """
         return th -np.tan(th) - np.pi/(1.0-beta)
 
-    th_init = 91.0
+    th_init = np.radians(91.0)
     if CRW:
         th_inf, infodict, ier, mesg = fsolve(f_CRW,th_init,args=(beta),full_output=True)
     else:
@@ -72,7 +72,7 @@ def theta_infty(beta,xi,CRW=False):
 
 parser = argparse.ArgumentParser(description="Command line options")
 parser.add_argument("--xi",type=float,default=1.0,help="inner wind parameter")
-parser.add_argument("CRW",action="store_true",help="use CRW solution")
+parser.add_argument("--CRW",action="store_true",help="use CRW solution")
 args = parser.parse_args()
 Xi = args.xi
 CRW = args.CRW
@@ -81,7 +81,7 @@ if CRW:
     
 #Step 2: Initialize arrays
 
-
+print(CRW)
 beta = [5e-4, 0.001, 0.002, 0.005, 0.01, 0.02, 0.05, 0.1]
 sns.set_style("ticks")
 colors = sns.color_palette('Blues', len(beta))
@@ -94,7 +94,7 @@ for b, c in zip(beta, colors):
     imax = np.degrees(np.arctan(-1./np.tan(th_inf)))
     imask = inc <=imax
     conic = Conic(A=A(b, Xi),th_conic=np.degrees(theta_c(b,Xi)))
-    print(r"$\beta={}$".format(b))
+    print(r"$\beta={}$".format(b),imax)
     q_prime = q(b)*conic.g(inc[imask])
     A_prime = conic.Aprime(inc[imask])
     plt.plot(q_prime,A_prime, linestyle="-", linewidth=2.0, color=c,

### 2016-09-13 papers/Paper1/sec-application.tex
Add max inclination for theoretcal curves
Also modified in applications tex file the sections order
to convert CRW scenario in a section and put it before the applications
section
Correct issues in program which creates A' vs q' graphs
Added the new figures. No visible changes detected.

Results subsection becomes section
Updated desciption on pressure graph on text.
Warning: The LaTeX document doesn't compile in my
desktop machine, maybe due to utdated LaTeX packages

@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
 \newcommand\thC{\(\theta^1\)\,Ori~C}
@@
 
-Proplyds are comet-like structures observed in HII regions like Orion Nebula Cluster (ONC). 
-These objects are interpreted as a D-type Ionization Front (IF) of a photoevaporated flow 
-originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
-The pressure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
-may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of \thC{}, which is highly supersonic $(M \sim 100)$.
-
-The density distribution of the photoevaporated flow can be determined using the steady state continuity equation and assuming that almost all ionizing photons are absorbed at the IF 
-\citep{HA:1998} and ignoring dust absorption, can be found that
-
-\begin{align}
-N(r_{IF},\theta) = N_0 \cos^{0.5}\theta
-\label{eq:nprop}
-\end{align}
-
-Neverthless, we should not restrict to the 0.5 index in equation (\ref{eq:nprop}). We may generalize this relation as follows:
-
-\begin{align}
-n(r_{IF},\theta) = n_0 \cos^{k}\theta
-\label{eq:ngen}
-\end{align}
-
-Where $k >0$ implies that the wind's density decays towards wings, when $k<0$ the wind's density incresases towards the wings and $k=0$
-implies that the wind is isotropic.
-In this generalization we are assuming that the inner wind is hemispheric, i.e. the density of the photoevaporated flow behind the source is zero, since equation
-(\ref{eq:ngen}) leads to non realistic values for density when $\theta > \frac{\pi}{2}$
-
-\subsection{\CRW{} Scenario}
+\section{Hypersonic thin shell approximation}
 \label{sec:crw-scenario}
@@
 is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
-
-% Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, which gives us the shell's shape. Also we can
-%obtain a relation between $\theta$ and $\theta_1$
-
-%\begin{align}
-%\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
-%\label{eq:th1th}
-%\end{align}
-
-%Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta$. The solution of this integral is an incomplete elliptical integral of the second kind:
-
-%\begin{align}
-%\int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta = \frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta
-%\end{align}
-
-\begin{figure}
-\includegraphics[width=\linewidth]{r-beta}
-\caption{Bow shock shapes for interacting winds in the thin-shell
-  approximation. Coordinates are normalized by $D$, the distance
-  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
-  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
-  different values of the wind momentum ratio, \(\beta\), and for the
-  case where the weaker wind is isotropic (dashed lines) or an
-  anisotropic photoevaporation flow. The solid lines shows a wind with a
-  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
-  And the dooted lines show a wind with extreme anisotropy degree $(k=8)$.}
-\label{fig:r-beta}
-\end{figure}
 
@@
 
+\section{Application to proplyd bowshocks}
+\label{sec:application}
+
+Proplyds are comet-like structures observed in HII regions like Orion Nebula Cluster (ONC). 
+These objects are interpreted as a D-type Ionization Front (IF) of a photoevaporated flow 
+originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
+The pressure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
+may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of \thC{}, which is highly supersonic $(M \sim 100)$.
+
+The density distribution of the photoevaporated flow can be determined using the steady state continuity equation and assuming that almost all ionizing photons are absorbed at the IF 
+\citep{HA:1998} and ignoring dust absorption, can be found that
+
+\begin{align}
+N(r_{IF},\theta) = N_0 \cos^{0.5}\theta
+\label{eq:nprop}
+\end{align}
+
+Neverthless, we should not restrict to the 0.5 index in equation (\ref{eq:nprop}). We may generalize this relation as follows:
+
+\begin{align}
+n(r_{IF},\theta) = n_0 \cos^{k}\theta
+\label{eq:ngen}
+\end{align}
+
+Where $k >0$ implies that the wind's density decays towards wings, when $k<0$ the wind's density incresases towards the wings and $k=0$
+implies that the wind is isotropic.
+In this generalization we are assuming that the inner wind is hemispheric, i.e. the density of the photoevaporated flow behind the source is zero, since equation
+(\ref{eq:ngen}) leads to non realistic values for density when $\theta > \frac{\pi}{2}$
+
+% Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, which gives us the shell's shape. Also we can
+%obtain a relation between $\theta$ and $\theta_1$
+
+%\begin{align}
+%\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
+%\label{eq:th1th}
+%\end{align}
+
+%Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta$. The solution of this integral is an incomplete elliptical integral of the second kind:
+
+%\begin{align}
+%\int^\theta_0 \cos^{1/2}\theta\sin^2\theta~d\theta = \frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta
+%\end{align}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{r-beta}
+\caption{Bow shock shapes for interacting winds in the thin-shell
+  approximation. Coordinates are normalized by $D$, the distance
+  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
+  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
+  different values of the wind momentum ratio, \(\beta\), and for the
+  case where the weaker wind is isotropic (dashed lines) or an
+  anisotropic photoevaporation flow. The solid lines shows a wind with a
+  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
+  And the dooted lines show a wind with extreme anisotropy degree $(k=8)$.}
+\label{fig:r-beta}
+\end{figure}
+
 %Although there is an analytical form for the radius of curvature, for $i\ne 0$ there is not an intuitive form for  $R'_c$.
@@
 To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, and made 10 sets of randomly chosen removed marks, and made the measurements again to 
-see how much these ``variations'' deviates from the original data. Some examples are shown  in figure (\ref{fig:char-radii-obs}).  In the left side, for each source, 
+see how much these subsamples deviates from the original data. Some examples are shown  in figure (\ref{fig:char-radii-obs}).  In the left side, for each source, 
 the fit is done using all the shell points, while in the middle and the right we show two variations removing 2/3 of the points, but always keeping at least four. 
@@
 fits are relatively robust to removing points, resulting in little variation between the subsamples. 
-But also there are cases where the variations are more noticeable. Colums 3, 4 and 5 of table (\ref{tab:arc-fits}) represent the summary of all the measurements done. In colums 4 and 5, 
+But also there are cases where the variations between subsamples are more noticeable.
+Colums 3, 4 and 5 of table (\ref{tab:arc-fits}) represent the summary of all the measurements done.
+In colums 4 and 5,
 the radii $(R_0,R_c)$ are measured as the average of all subsamples, and the uncertainty as the standard deviation.
-\subsection{Results}
+
+\section{Results}
 \label{sec:results}
@@
 
-Using the data from figure \ref{fig:conic-xi}, we estimate for each source the parameters $(\beta,i,\xi)$ (columns 7, 8 and 9 from table \ref{tab:arc-fits}).
+With the data from figure \ref{fig:conic-xi}, we derived a set of models which assumes a given set of bow shock parameters $(\beta, i,\xi)$ and have agreement with the measurements of each proplyd.
+A given model predicts the no projected
+distance $D$ for the proplyd and the non projected radius $R_0$. We summarize the results of the models in table \ref{tab:arc-fits}.
+
+From this models also we can estimate the stellar ionizing flux required to have ionization balance with the photoevaporated flow.
+To do this estimation we used the measured ionization front radius and the photoevaporated flow density for each proplyd
+and incorporated them into the models. The result is shown in figure \ref{fig:pressure} at top. We highlight the models which have agreement with ionization balance.
+Also we can estimate the stagnation pressure of the photoevaporated flow. The result is shown in figure \ref{fig:pressure} at bottom. 
+From this figures we can see that our models predict that for the farthest proplyds (169-338, 177-341 and 180-331) the stellar wind pressure is weaker than the estimated stagnation pressure.
+Since these bow shocks are stationary, we expect pressure
+balance, so the stellar wind is not enough to guarantee pressure balance far from \thC{}
+
+%Using the data from figure \ref{fig:conic-xi}, we estimate for each source the parameters $(\beta,i,\xi)$ (columns 7, 8 and 9 from table \ref{tab:arc-fits}).
 With this, is possible to estimate the non projected distances $(R_0,D)$ (columns 10 and 11).
 
-Using the data from table \ref{tab:arc-fits} along with the ionization front radius and photoevaporation flow density obtained from \citet{HA:1998} we measured the stagnation pressure at the bow shock's position,
-and compare it with the expected pressure from the stellar wind at the distance $D$.
-Since we expect equilibrium pressure in the bow shock surface, both pressures should be the same.
-The comparison is done in figure \ref{fig:pressure} (bottom).
+%Using the data from table \ref{tab:arc-fits} along with the ionization front radius and photoevaporation flow density obtained from \citet{HA:1998} we measured the stagnation pressure at the bow shock's position,
+%and compare it with the expected pressure from the stellar wind at the distance $D$. 
+%Since we expect equilibrium pressure in the bow shock surface, both pressures should be the same. The comparison is done in figure \ref{fig:pressure} (bottom).
 
-We also expect the stellar ionizing flux should be the required to balance the photoevaporated flux. We do
-the comparison in figure \ref{fig:pressure} (top). In both cases, the highlighted points represent the variations which have better agree with ionization balance and pressure balance, respctively.
+%We also expect the stellar ionizing flux should be the required to balance the photoevaporated flux. We do
+%the comparison in figure \ref{fig:pressure} (top). In both cases, the highlighted points represent the variations which have better agree with ionization balance and pressure balance, respctively.
 
-For the farthest proplyds, we can see that the estimated pressure is greater than the stellar wind pressure, even with the best fits.
+%For the farthest proplyds, we can see that the estimated pressure is greater than the stellar wind pressure, even with the best fits.
 This suggests that at large distances, another source rather than the
-stellar wind is the reponsible for mantaining the stationary bow shocks.
+%stellar wind is the reponsible for mantaining the stationary bow shocks.
 
@@
 \includegraphics[width=\linewidth]{../../proplyd-wind-figs/plot-wind-fits}
-\caption{Top: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd. The gray line represents the stellar flux at the distance $D$. 
-Bottom: In colored lines, estimated stagnation pressure for each proplyd. 
-The gray solid line represent the stellar wind at the distance $D$.
+\caption{Top: In colored lines, we show the ionizing flux required to balance the photoevaporated flow for some models which agree with the observed radii for each proplyd compared against the stellar ionizing
+flux at the distance D.
+Bottom: The estimated stagnation pressure for the same models as above compared against the stellar wind pressure.
+In both graphs, the big dots represent th models which show agreement with ionization balance.}
+%\caption{Top: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd. The gray line represents the stellar flux at the distance $D$. 
+%Bottom: In colored lines, estimated stagnation pressure for each proplyd. 
+%The gray solid line represent the stellar wind at the distance $D$.
 in both cases, the big dots represent the variations which have more agreement with ionization balance and pressure balance, respectively.}

### 2016-09-26 papers/Paper1/sec-application.tex
Move definitions to match re-ordered sections
Split the paper into two parts!
* The theoretical paper is now called quadrics-bowshock.tex
* The applications paper has the original name: proplyd-bowshock.tex

@@
-\newcommand\thC{\(\theta^1\)\,Ori~C}
-\defcitealias{Canto:1996}{CRW}
-\newcommand\CRW{\citetalias{Canto:1996}}
-
-\section{Hypersonic thin shell approximation}
-\label{sec:crw-scenario}
-This scenario can be described with the formalism of
-\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
-solution for the two winds interaction problem in the thin shell
-approximation, in terms of a free parameter
-$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
-momentum ratio, which the quantities with subindex 1 corresponds to
-the strongest wind, therefore $\beta<=1$.
-
-%If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}),
-%we find that the solutions for equations (8) - (11) of \CRW{} are the following:
-
-If we apply the \CRW{} formalism for a generalized photoevaporated flow with density given by equation (\ref{eq:ngen}),
-the shell shape $R(\theta)$ may be calculated from equation (6) of CRW{}:
-
-\begin{align}
-  R = \frac{\dot{J}_w + \dot{J}_{w1}}{\left(\dot{\Pi}_{wr}+\dot{\Pi}_{wr1}\right)\cos\theta-\left(\dot{\Pi}_{wz1}+\dot{\Pi}_{wz1}\right)\sin\theta}
-  \label{eq:Rmom}
-\end{align}
-
-Where:
-
-\begin{align}
-\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
-\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w v_w I_k (\theta) \label{eq:piz}\\
-I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \\
-\dot{J}_w = 0 \label{eq:jdot} \\
-\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
-M^0_w &\equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
-\dot{\Pi}_{wz1} & = -\frac{\dot{M}^0_{w1}v_{w1}}{4}\sin^2\theta_1\\
-\dot{\Pi}_{wr1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
-\dot{J}_{w1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \label{eq:jdot1}
-\end{align}  
-Combining equations  (\ref{eq:pir}) to (\ref{eq:jdot1}) we can obtain the bow shock shape $R(\theta)$ from equation (\ref{eq:Rmom}).
-The most notable scenarios, since they have astrophysical relevance are the following:
-$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
-is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
-
-\subsection{Characteristic Radii}
-
-%Here goes a little introduction
-
-\begin{align}
-\theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
-\label{eq:th1th}
-\end{align}
-
-$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
-
-We can obtain $R_{90}$ by the following process:
-Evaluating equations  (\ref{eq:th1th}) and (23) from \CRW{} at $\theta=\frac{\pi}{2}$ we obtain the following:
-
-\begin{align}
-R_{90} = D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} = 1-\frac{2\beta}{k+2} \label{eq:th190}
-\end{align}
-Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing the parameter 
-$\xi\equiv \frac{2}{k+2}$ we have:
-
-\begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
-\end{align}
-
-Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}), using a small angle  approximation, we find that:
-
-\begin{align}
-\theta_{1,90} &\simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
-\label{eq:th190sol}
-\end{align}
-
-With this, we have a solution for $B \equiv \frac{R_{90}}{R_0}$:
-
-\begin{align}
-B = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
-\label{eq:B}
-\end{align}
-
-Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 4th order for small $\theta$ values to find that for such values
-
-\begin{align}
-\theta_1^2 &\simeq \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right] \\
-\mathrm{where:~} & C_{k\beta} \equiv \frac{1}{30}\left(1-\beta-\frac{9}{4}k\right)
-\end{align}
-Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:
-
-\begin{align}
-R &\simeq R_0 \left(1+\gamma\theta^2\right)
-\label{eq:R_approx} \\
-\mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
-\end{align}
-
-Which lead us to derive the radius of curvature at the symmetry axis:
-
-\begin{equation}
-R_c = R_0\left(1-2\gamma\right)^{-1}
-\label{eq:Rcurv}
-\end{equation}
-
-finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:thc-conic})
-
-\begin{align}
-\tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
-\label{eq:thc-CRW}
-\end{align}
-
-\begin{figure}
-\begin{tabular}{c}
-\includegraphics[width=\linewidth]{figs/AB-beta-log} \\
-\includegraphics[width=\linewidth]{figs/thc-beta-log}
-\end{tabular}
-\caption{Top: Characteristic radii, $A = R_c/R_0$ (solid lines) and $B
-  = R_{90}/R_0$ (dashed lines)
-  vs $\beta$, calculated from quadric fits to the generalized CRW
-  solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
-  angle $\theta_c$ vs $\beta$ for the bow 
-  shock head (solid lines) and the bow shock tail (dashed lines).}
-\label{fig:rad-beta}
-\end{figure}
-
-%Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
-%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
-
-With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
-momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
-
 \section{Application to proplyd bowshocks}
 \label{sec:application}
-
-Proplyds are comet-like structures observed in HII regions like Orion Nebula Cluster (ONC). 
-These objects are interpreted as a D-type Ionization Front (IF) of a photoevaporated flow 
-originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
-The pressure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
-may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of \thC{}, which is highly supersonic $(M \sim 100)$.
 
@@
 %\end{align}
-
-\begin{figure}
-\includegraphics[width=\linewidth]{r-beta}
-\caption{Bow shock shapes for interacting winds in the thin-shell
-  approximation. Coordinates are normalized by $D$, the distance
-  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
-  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
-  different values of the wind momentum ratio, \(\beta\), and for the
-  case where the weaker wind is isotropic (dashed lines) or an
-  anisotropic photoevaporation flow. The solid lines shows a wind with a
-  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
-  And the dooted lines show a wind with extreme anisotropy degree $(k=8)$.}
-\label{fig:r-beta}
-\end{figure}
 

### 2016-09-26 papers/Paper1/sec-conclusions-proplyd.tex
Split the paper into two parts!
* The theoretical paper is now called quadrics-bowshock.tex
* The applications paper has the original name: proplyd-bowshock.tex

\section{Conclusions}
\label{sec:conclusions-proplyd}

Evidence for the leaky sieve model for channeling the stellar wind
momentum.

Alternative would be nebular champagne flow from Orion S.  We need to
work out the numbers for that. But the orientation seems too close to
radial for that to be plausible.

We also need to show that radiation pressure cannot be important.

Make sure we analyse the distribution of inclinations, taking into
account there is a maximum inclination above which a bowshock will not
be seen.

### 2016-09-26 papers/Paper1/sec-intro-proplyd.tex
Split the paper into two parts!
* The theoretical paper is now called quadrics-bowshock.tex
* The applications paper has the original name: proplyd-bowshock.tex

\section{Introduction}
\label{sec:introduction-proplyd}

Proplyds are comet-like structures observed in HII regions like Orion Nebula Cluster (ONC). 
These objects are interpreted as a D-type Ionization Front (IF) of a photoevaporated flow 
originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
The pressure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of \thC{}, which is highly supersonic $(M \sim 100)$.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

### 2016-09-26 papers/Paper1/sec-thin-shell.tex
Split the paper into two parts!
* The theoretical paper is now called quadrics-bowshock.tex
* The applications paper has the original name: proplyd-bowshock.tex

\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}
\newcommand\CRW{\citetalias{Canto:1996}}

\section{Hypersonic thin shell model}
\label{sec:crw-scenario}
This scenario can be described with the formalism of
\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
solution for the two winds interaction problem in the thin shell
approximation, in terms of a free parameter
$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
momentum ratio, which the quantities with subindex 1 corresponds to
the strongest wind, therefore $\beta<=1$.

%If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}),
%we find that the solutions for equations (8) - (11) of \CRW{} are the following:

If we apply the \CRW{} formalism for a generalized photoevaporated flow with density given by equation (\ref{eq:ngen}),
the shell shape $R(\theta)$ may be calculated from equation (6) of CRW{}:

\begin{align}
  R = \frac{\dot{J}_w + \dot{J}_{w1}}{\left(\dot{\Pi}_{wr}+\dot{\Pi}_{wr1}\right)\cos\theta-\left(\dot{\Pi}_{wz1}+\dot{\Pi}_{wz1}\right)\sin\theta}
  \label{eq:Rmom}
\end{align}

Where:

\begin{align}
\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w v_w I_k (\theta) \label{eq:piz}\\
I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \\
\dot{J}_w = 0 \label{eq:jdot} \\
\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
M^0_w &\equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
\dot{\Pi}_{wz1} & = -\frac{\dot{M}^0_{w1}v_{w1}}{4}\sin^2\theta_1\\
\dot{\Pi}_{wr1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
\dot{J}_{w1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \label{eq:jdot1}
\end{align}  
Combining equations  (\ref{eq:pir}) to (\ref{eq:jdot1}) we can obtain the bow shock shape $R(\theta)$ from equation (\ref{eq:Rmom}).
The most notable scenarios, since they have astrophysical relevance are the following:
$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes for interacting winds in the thin-shell
  approximation. Coordinates are normalized by $D$, the distance
  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
  different values of the wind momentum ratio, \(\beta\), and for the
  case where the weaker wind is isotropic (dashed lines) or an
  anisotropic photoevaporation flow. The solid lines shows a wind with a
  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
  And the dooted lines show a wind with extreme anisotropy degree $(k=8)$.}
\label{fig:r-beta}
\end{figure}

\subsection{Characteristic Radii}

%Here goes a little introduction

\begin{align}
\theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
\label{eq:th1th}
\end{align}

$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.

We can obtain $R_{90}$ by the following process:
Evaluating equations  (\ref{eq:th1th}) and (23) from \CRW{} at $\theta=\frac{\pi}{2}$ we obtain the following:

\begin{align}
R_{90} = D\tan\theta_{1,90} \\
\theta_{1,90}\cot\theta_{1,90} = 1-\frac{2\beta}{k+2} \label{eq:th190}
\end{align}
Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing the parameter 
$\xi\equiv \frac{2}{k+2}$ we have:

\begin{align}
R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
\end{align}

Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}), using a small angle  approximation, we find that:

\begin{align}
\theta_{1,90} &\simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
\label{eq:th190sol}
\end{align}

With this, we have a solution for $B \equiv \frac{R_{90}}{R_0}$:

\begin{align}
B = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
\label{eq:B}
\end{align}

Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 4th order for small $\theta$ values to find that for such values

\begin{align}
\theta_1^2 &\simeq \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right] \\
\mathrm{where:~} & C_{k\beta} \equiv \frac{1}{30}\left(1-\beta-\frac{9}{4}k\right)
\end{align}
Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:

\begin{align}
R &\simeq R_0 \left(1+\gamma\theta^2\right)
\label{eq:R_approx} \\
\mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
\end{align}

Which lead us to derive the radius of curvature at the symmetry axis:

\begin{equation}
R_c = R_0\left(1-2\gamma\right)^{-1}
\label{eq:Rcurv}
\end{equation}

finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:thc-conic})

\begin{align}
\tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
\label{eq:thc-CRW}
\end{align}

\begin{figure}
\begin{tabular}{c}
\includegraphics[width=\linewidth]{figs/AB-beta-log} \\
\includegraphics[width=\linewidth]{figs/thc-beta-log}
\end{tabular}
\caption{Top: Characteristic radii, $A = R_c/R_0$ (solid lines) and $B
  = R_{90}/R_0$ (dashed lines)
  vs $\beta$, calculated from quadric fits to the generalized CRW
  solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
  angle $\theta_c$ vs $\beta$ for the bow 
  shock head (solid lines) and the bow shock tail (dashed lines).}
\label{fig:rad-beta}
\end{figure}

%Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

### 2016-09-29 papers/Paper1/sec-application.tex
Edit applications section, enhance apperance of proplyd's shell circle fit

--- 2016-09-13 papers/Paper1/sec-application.tex
@@
 
-With the data from figure \ref{fig:conic-xi}, we derived a set of models which assumes a given set of bow shock parameters $(\beta, i,\xi)$ and have agreement with the measurements of each proplyd.
-A given model predicts the no projected
-distance $D$ for the proplyd and the non projected radius $R_0$. We summarize the results of the models in table \ref{tab:arc-fits}.
+With the data from figure \ref{fig:conic-xi}, we derived a set of models which assumes a given set of bow shock parameters $(\beta, i,\xi)$ which have agreement with the measurements of 
+each proplyd. A given model predicts the non projected distance $D$ for the proplyd and the non projected radius $R_0$. 
+We summarize the results of the models in table \ref{tab:arc-fits}.
 
 From this models also we can estimate the stellar ionizing flux required to have ionization balance with the photoevaporated flow. 
-To do this estimation we used the measured ionization front radius and the photoevaporated flow density for each proplyd
+To do this estimation we used the ionization front radius and the photoevaporated flow density measured in \citet{HA:1998} for each proplyd
 and incorporated them into the models. The result is shown in figure \ref{fig:pressure} at top. We highlight the models which have agreement with ionization balance.
@@
 \begin{figure*}
-  \setkeys{Gin}{width=0.33\linewidth, trim=10 30 55 62.5}
+  \setkeys{Gin}{width=0.33\linewidth}%, trim=10 30 55 62.5}
 \begin{tabular}{@{}c@{}c@{}c@{}}

### 2016-09-29 papers/Paper1/sec-conclusions.tex
Include POS projection figure in section 3
And brief discussion in text
Edit applications section, enhance apperance of proplyd's shell circle fit

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
+\section{Conclusions}
+\label{sec:conc}
+
+%\newcommand\thC{\(\theta^1\)\,Ori~C}
+\defcitealias{Canto:1996}{CRW}
+
+We developed a method to estimate the shape of a generic bow shock product of the
+interaction of two winds and was applied to the proplyds in the core of the ONC.
+We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
+sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
+on \CRW{} work to estimate the intrinsic bow shock shape and get the ionizing flux for ionization balance 
+and the stagnation pressure for our sample of proplyds.
+Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
+distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
+while LV2 has the most anisotropic flow. And for the 177-341, 169-348 and 180-331 we found out that 
+the stellar wind is not enough to keep their bow socks stationary.
 

### 2016-10-14 papers/Paper1/sec-conclusions.tex
Improvement of quadrics-bowshock paper.
Correct references.
Solve coherence issues.
Corrected wrong written equations
Rewrite conclusions according to the content of this paper

--- 2015-06-18 papers/Paper1/sec-application.tex
@@
-\section{Application to proplyd bowshocks}
-\label{sec:application}
+\section{Conclusions}
+\label{sec:conc}
+
+\newcommand\thC{\(\theta^1\)\,Ori~C}
+\defcitealias{Canto:1996}{CRW}
+
+We developed a method to estimate the shape of a generic bow shock product of the
+interaction of two winds as well as it apparent shape due to it orientation relative to the line of sight, asuuming
+the bow shock is geometrically and optically thin.
+
+In the general case we require numerical techniques, but is possible to handle analytically the apparent shape of
+the quadrics of revolution.
+
+Also we made a generalization of \CRW{} work where the weakest interacing wind is hemispherical and anisotropic where its
+density follows a power law of $\cos\theta$. Altrough other models also may be used.
+
+In any case we developed a form to derive a set of measurable radii which are used as comparison between the \CRW{} model, the quadrics
+of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
+(ONC) due to the interaction of the photoevaporated wind from proplyds and the stallar wind of \thC{}
+
+%and was applied to the proplyds in the core of the ONC.
+%We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
+%sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
+%on \CRW{} work to estimate the intrinsic bow shock shape and get the ionizing flux for ionization balance 
+%and the stagnation pressure for our sample of proplyds.
+%Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
+%distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
+%while LV2 has the most anisotropic flow. And for the 177-341, 169-348 and 180-331 we found out that 
+%the stellar wind is not enough to keep their bow socks stationary.
 

### 2016-10-14 papers/Paper1/sec-conic.tex
Improvement of quadrics-bowshock paper.
Correct references.
Solve coherence issues.
Corrected wrong written equations
Rewrite conclusions according to the content of this paper

@@
 
-The 
-In this section we will analyze the case where the resultant shape  of the bow shock is a conic curve (circle, ellipse, parabola or hyperbola).
-These curves are mathematical simple to model and give us a good reference to understand the effects of the projection effects
-described in the last section on other bow shocks. The source of the inner wind is located at the origin, and the center of the conic is located at
-a distance $x_0$ from the source.
+%The 
+%In this section we will analyze the case where the resultant shape  of the bow shock is a conic curve (circle, ellipse, parabola or hyperbola).
+%These curves are mathematical simple to model and give us a good reference to understand the effects of the projection effects
+%described in the last section on other bow shocks. The source of the inner wind is located at the origin, and the center of the conic is located at
+%a distance $x_0$ from the source.
 
@@
 \begin{align}
-\frac{R_c}{D} &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
-\frac{R_{90}}{D} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}
+R_c &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
+R_{90} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
 \end{align}
-The inverse transformation is given by:
+In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric. The inverse transformation of (\ref{eq:Rc-conic})
+and (\ref{eq:r90-conic}) is given by:
 \begin{align}
 \frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
-\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|}\\
-\tan\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} \\
-\mathrm{where:}& B\equiv \frac{R_{90}}{R_0} \\
+\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
+\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
+\mathrm{where:~}& B\equiv \frac{R_{90}}{R_0} \\
 A \equiv \frac{R_c}{R_0}
 \end{align}
-From equations (\ref{eq:a-conic}) we can see that for $R^2_{90} > 2 R_c$, the conic parameter $a$ is negative, so in this case the resulting conic is an hyperbola, and we must take the negative root
-in equation (\ref{eq:thc-conic}). The opposite applies for ellipses.
+
 \subsection{Plane-of-sky projection of quadric surfaces} 
@@
 the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
-an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
+an asymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
 \label{fig:Apqp}
@@
 \end{align}
-The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:tanalpha}), then:
+The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
 \begin{align}
@@
 
-Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y}) we find that
+Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y-2}) we find that
 \begin{align}
@@
 \end{align}
-Where $A\equiv \frac{R_c}{R_0}$
+%Where $A\equiv \frac{R_c}{R_0}$
 
@@
 
-The space parameter $A'$ vs $q'$ can be seen in figure (\ref{fig:Apqp}). In this figure is assumed that we know the intrinsic Radius of curvature and $R_0$, which is not the case with
-real observations.
+Using a space of parameters like figure \ref{fig:Apqp} we can compare models with observations of real bowshocks.
+
+%The space parameter $A'$ vs $q'$ can be seen in figure (\ref{fig:Apqp}).%In this figure is assumed that we know the intrinsic Radius of curvature and $R_0$, which is not the case with
+%real observations.
 

### 2016-10-14 papers/Paper1/sec-thin-shell.tex
Improvement of quadrics-bowshock paper.
Correct references.
Solve coherence issues.
Corrected wrong written equations
Rewrite conclusions according to the content of this paper

@@
 momentum ratio, which the quantities with subindex 1 corresponds to
-the strongest wind, therefore $\beta<=1$.
+the strongest wind, therefore $\beta<=1$. In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
+with the following density distribution:
 
+\begin{align}
+  n(\theta) = n_0\cos^k\theta
+\end{align}  
+The index $k$ gives the anisotropy degree. We are interested in winds where $k \geq 0$ for further applications. By the other side, we keep the strongest
+wind as isotropic.
+
+The shape of the resultant bow shock is given by:
 %If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}),
@@
 
-If we apply the \CRW{} formalism for a generalized photoevaporated flow with density given by equation (\ref{eq:ngen}),
-the shell shape $R(\theta)$ may be calculated from equation (6) of CRW{}:
-
+%If we apply the \CRW{} formalism for a generalized photoevaporated flow with density given by equation (\ref{eq:ngen}),
+%the shell shape $R(\theta)$ may be calculated from equation (6) of CRW{}:
 \begin{align}
@@
 \begin{align}
-\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
+\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{k+2}\theta\right)  \label{eq:pir}\\
 \dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w v_w I_k (\theta) \label{eq:piz}\\
@@
 \end{align}
-Combining equations  (\ref{eq:pir}) to (\ref{eq:jdot1}) we can obtain the bow shock shape $R(\theta)$ from equation (\ref{eq:Rmom}).
-The most notable scenarios, since they have astrophysical relevance are the following:
-$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
-is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
+
+Combining equations  (\ref{eq:pir}) to (\ref{eq:jdot1}) we can obtain numerically the bow shock shape $R(\theta)$ from equation (\ref{eq:Rmom}).
+To find the projected shape in the plane of sky, we fit $R(\theta)$ into a quadric curve which has the same characteristic radii $(R_0,R_c,R_{90})$. 
+%The most notable scenarios, since they have astrophysical relevance are the following:
+%$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
+%is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
 
@@
 \subsection{Characteristic Radii}
-
+$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
 %Here goes a little introduction
+For the rest of the radii we need a relation between $\theta$ and $\theta_1$ as follows:
 
@@
 
-$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
-
+Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
 We can obtain $R_{90}$ by the following process:

### 2016-10-21 papers/Paper1/appendix-quadrics.tex
Appendix for quadrics paper

--- 2016-06-15 papers/Paper1/sec-projection.tex
@@
-\section{Projection onto the plane of the sky}
-\label{sec:projection}
+\appendix
+\appendixpage
+\addappheadtotoc
+\section{Unit vectors normal and tangential to the surface}
+\label{app:unit-vectors-normal}
 
-In this section we calculate the apparent shape on the plane of the
-sky of the limb brightened border of a shock or shell that is
-idealized as as arbitrary cylindrically symmetric surface.
-
-%Note: I'm aware that some of this material should be moved to an appendix, but I think it will be a future edition.
-\subsection{Frames of reference}
-
-Consider body-frame cartesian coordinates $(x,y,z)$, where \(x\) is
-the symmetry axis, and spherical polar coordinates
-\((R, \theta, \phi)\), where \(\theta\) is the polar angle and
-\(\phi\) the azimuthal angle.  Since the surface is cylindrically
-symmetric, it is can be specified as $R = R(\theta)$, so that
-cartesian coordinates on the surface are:
+We define unit vectors \(\uvec{n}, \uvec{t}\), such that \(\uvec{n}\) is normal to the surface, while \(\uvec{t}\) is tangent to the surface in a plane of constant \(\phi\).
+For \(\phi = 0\) the surface lies in the \(xy\) plane and it is straightforward to show (Fig.~\ref{fig:unitvec}) that in this case the unit vectors are given by
 \begin{equation}
-\left(\begin{array}{c}
-x \\ y \\ z
-\end{array}
-\right) = R(\theta)\left(\begin{array}{c}
-\cos\theta \\
-\sin\theta\cos\phi \\
-\sin\theta\sin\phi
-\end{array}\right).
+  \label{eq:uvec-phi0}
+  \uvec{t}_0 =
+  \begin{Vector}
+    -\cos\alpha \\ \sin\alpha \\ 0
+  \end{Vector}
+  \quad \mathrm{and} \quad
+  \uvec{n}_0 =
+  \begin{Vector}
+    \sin\alpha \\ \cos\alpha \\ 0
+  \end{Vector}, 
 \end{equation}
-Suppose that the viewing direction makes an angle \(i\) with the \(z\)
-axis, so that we can define observer-frame coordinates
-\((x', y', z')\), which are given by the rotating the body-frame
-coordinates:
+where
 \begin{equation}
-\left(\begin{array}{c}
-x' \\ y' \\ z'
-\end{array}
-\right) = \left(\begin{array}{c}
-x\cos i - z\sin i\\
-y \\
-z\cos i + x\sin i
-\end{array}\right).
-\label{eq:Trans}
+  \label{eq:alpha}
+  \tan\alpha = -\left.\frac{dy}{dx}\right\vert_{R(\theta)} 
+  = \frac{1 + \omega \tan\theta}{\tan\theta - \omega}
 \end{equation}
-The relationship between the two frames is illustrated in
-Figure~\ref{fig:projection-pos}.  All quantities in the observer's
-frame are denoted by attaching a prime to the equivalent quantity in
-the body frame.  The celestial coordinates on the ``plane of the sky''
-are given by \((x', y')\) with \(x'\) being the projected symmetry
-axis of the surface, while the line of sight lies along \(-z'\).  The
-inclination angle \(i\) is defined so that \(i = 0^\circ\) when the
-surface is viewed perpendicular to its axis (\textit{side on}) and
-\(i = 90^\circ\) when it is viewed along its axis (\textit{end on}).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/projection-pos}
-  \caption{Relationship between body frame (unprimed coordinates) and
-    observer frame (primed coordinates).}
-  \label{fig:projection-pos}
-\end{figure}
-
-\subsection{Tangent line}
-
-The normal and tangent vectors to the shell's border in the shell's frame are given by:
-\begin{align}
-\hat{t} = \left(\begin{array}{c}
--\cos\alpha \\
-\sin\alpha\cos\phi\\
-\sin\alpha\sin\phi
-\end{array}\right)\\
-\hat{n} = \left(\begin{array}{c}
-\sin\alpha \\
-\cos\alpha\cos\phi \\
-\cos\alpha\sin\phi
-\end{array}\right)
-\end{align}
-Where:
-\begin{align}
-\tan\alpha = -\left.\frac{dy}{dx}\right|_{R(\theta)} \\
-\label{eq:tanalpha}
-\end{align}
-Then we apply the transformation (\ref{eq:Trans}) to the normal and tangent vectors to obtain:
-\begin{align}
-\hat{n}' &= \left(\begin{array}{c}
-(\cos\theta+\omega\sin\theta)\cos i -(\sin\theta-\omega\cos\theta)\sin i \sin\phi\\
+and 
+\begin{equation}
+  \label{eq:omega}
+  \omega(\theta) = \frac{1}{R} \frac{dR}{d\theta} . 
+\end{equation}
+For general \(\phi\), \(\uvec{n}\) and \(\uvec{t}\) can be found by rotating equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, which can then be converted to the observer frame by use of equation~(\ref{eq:Trans}) to give
+\begin{gather}
+  \label{eq:nprime}
+  \begin{split}
+    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
+    & \times 
+      \begin{Vector}
+        (\cos\theta+\omega\sin\theta)\cos i 
+        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
         (\sin\theta-\omega\cos\theta)\cos\phi \\
-(\cos\theta+\omega\sin\theta)\sin i + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-\end{array}\right)\\
-\hat{t}' &= \left(\begin{array}{c}
--(\sin\theta-\omega\cos\theta)\cos i - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
+        (\cos\theta+\omega\sin\theta)\sin i 
+        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
+      \end{Vector}\\
+  \end{split}\\
+  \label{eq:tprime}
+  \begin{split}
+    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
+    & \times 
+      \begin{Vector}
+        -(\sin\theta-\omega\cos\theta)\cos i
+        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
         (\cos\theta+\omega\sin\theta)\cos\phi \\
--(\cos\theta+\omega\sin\theta)\sin i + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-\end{array}\right)
-\end{align}
-Where $\omega = \frac{1}{R}\frac{dR}{d\theta}$
-
-In the thin shell case, the limb brightened border of the shell is such that $\hat{n}'\cdot \hat{z}'$. 
-The values for $\phi$ that satisfy this relation for each inclination $i$ are given by:
-\begin{equation}
-\sin\phi_t = \tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
-\label{eq:tanphi}
-\end{equation}
-With this, the coordinates of the limb brightened shell are given by:
-\begin{equation}
-\left(\begin{array}{c}
-x'_t \\ y'_t \\ z'_t
-\end{array}\right)= R(\theta)\left(\begin{array}{c}
-\cos\theta\cos i - \sin\theta\sin\phi_t \sin i \\
-\sin\theta(1-\sin^2\phi_t)^{1/2} \\
-\cos\theta\sin i +\sin\theta\sin\phi_t\cos i
-\end{array}\right)
-\label{eq:tangential}
-\end{equation}
-
-It is important to note that the equation (\ref{eq:tanphi}) does not have a solution for arbitrary values for $\theta$ and $i$, since
-it's required that $|\sin\phi_t|<1$. If $i\neq 0$, then, the  allowed values for $\theta$ are such that $\theta > \theta_\parallel$, where
-$\theta_\parallel$ is given implicitly by:
-\begin{align}
-\tan\theta_\parallel = \frac{|\tan i| + \omega(\theta_\parallel)}{1-\omega(\theta_\parallel) |\tan i|}
-\label{eq:thetapar}
-\end{align}
-
-\subsection{Parallel and perpendicular projected shell radii}
-
-Considering further applications to bow shocks, we will consider open shells. In order to compare the shell shape given by $R(\theta)$ with observations,
-it is convenient to define the following apparent radii in the observer frame: $R'_\parallel$ and $R'_\perp$. These are projected distances of the shell tangent line
-from the origin. The first is measured in the direction of the symetry axis, and the second in a perpendicular direction. More concretely $R'_\parallel = x'_t(y'_t=0)$
-and $R'_\perp = y'_t(x'_t=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:
-\begin{align}
-R'_\parallel = R(\theta_\parallel)\cos(\theta + i) \label{eq:Rpar} 
-\end{align}
-Where $\theta_\parallel$ is the solution of equation (\ref{eq:thetapar}), and
-\begin{align}
-R'_\perp = R(\theta_\perp)\sin\theta_\perp\left(1-\sin^2(\phi_t(\theta_\perp))\right)^{1/2}
-\end{align}
-Where $\theta_\perp$ is the solution of the next implicit equation:
-\begin{align}
-\cot\theta_\perp = \frac{1-\left(1+\omega(\theta_\perp)^2\sin^22i\right)^{1/2}}{2\omega(\theta_\perp\cos^2 i)}
-\end{align}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "proplyd-bowshocks"
-%%% End:
+        -(\cos\theta+\omega\sin\theta)\sin i 
+        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
+      \end{Vector}
+  \end{split}
+  \end{gather}

### 2016-10-21 papers/Paper1/proplyd-bowshocks.tex
Lots of improvements to section 3
Also, upgrade to the latest version of MNRAS macros: mnras.cls
Incorporate appendix into both papers

@@
 \RequirePackage{amsmath}
-\documentclass[useAMS,usenatbib]{mn2e}
+\documentclass[useAMS, usenatbib]{mnras}
 
@@
 % REMOVE if your LaTeX uses A4 paper by default
-\addtolength\topmargin{-1.8cm}
+%\addtolength\topmargin{-1.8cm}
 
 % Standard LaTeX packages
-\usepackage[varg]{txfonts}
-% \usepackage[varg]{newtxmath}
-% \usepackage{newtxtext}
+% \usepackage[varg]{txfonts}
+\usepackage[varg]{newtxmath}
+\usepackage{newtxtext}
 \usepackage{graphicx}
@@
 \usepackage{color}
+\usepackage{appendix}
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
@@
 
+%% Bold italic
+\newcommand\hmmax{0}            % we don't need heavy fonts
+\newcommand\bmmax{1}            % reduce use of math alphabets for bold
+\usepackage{bm}
+
 %% Bundled custom packages
 \usepackage{aastex-compat}
-\usepackage{astrojournals}
+%\usepackage{astrojournals}
 
-\title[Bowshock shapes]{True versus apparent shapes of astrophysical bow shocks}
+\title[Proplyd bowshocks]{What is confining the proplyd bow shocks in Orion?}
 
@@
 \begin{abstract}
-  We develop a general framework for the effects of viewing angle on
-  the apparent shape of a limb-brightened, cylindrically symmetric
-  curved shock (bow shock).  
+  We analyze the projected shapes of bowshocks associated with
+  photoevaporating disks (proplyds) in the inner Orion Nebula.  We
+  show that the photoevaporation flows must be anisotropic in order to
+  reproduce the observed shapes.  The stagnation pressures of the
+  shocked shells within 0.02~pc of the dominant high-mass star are
+  consistent with an interaction with its unshocked stellar wind, but
+  the more distant shells require a confining pressure that is an
+  order of magnitude higher than can be provided by the unmodified
+  wind.  We show that these outer objects may be proplyds that are
+  interacting with the conical wake generated by the wind-wind
+  interaction in the inner proplyds. 
 \end{abstract}
 
-\input{sec-intro}
-\input{sec-generic-model}
-\input{sec-projection}
-\input{sec-conic}
+\newcommand\thC{\(\theta^1\)\,Ori~C}
+\defcitealias{Canto:1996}{CRW}
+\newcommand\CRW{\citetalias{Canto:1996}}
+
+\input{sec-intro-proplyd}
 \input{sec-application}
-\input{sec-conclusions}
+\input{sec-conclusions-proplyd}
 
-%% TODO Investigate newer versions of BST file from
-%% https://github.com/timj/mn2e-bst
-\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 %% All references should be put in the BibTeX file bowshocks-biblio.bib

### 2016-10-21 papers/Paper1/sec-conic.tex
Enhance appareance of figure 6 using seaborn
Incorporate appendix into both papers

@@
 \begin{tabular}{cc}
-\includegraphics[height=0.54\linewidth, trim=30 0 30 0, clip]{ellipse_py_lab} &
-\includegraphics[height=0.54\linewidth, trim=60 0 70 0, clip]{hyperbola_py_lab}
+\includegraphics[height=0.54\linewidth, trim=30 0 30 0, clip]{ellipse_py} &
+\includegraphics[height=0.54\linewidth, trim=60 0 70 0, clip]{hyperbola_py}
 \end{tabular}
@@
 \begin{align}
-x = a\Cos(t)-x_0 \label{eq:par-x}\\ 
-y = b\Sin(t) \label{eq:par-y}
+x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
+y &= b\Sin(t) \label{eq:par-y}
 \end{align}
@@
 \begin{align}
-\Cos(t) = \left\lbrace \begin{array}{c}
+\Cos(t) &= \left\lbrace \begin{array}{c}
 \cos t ~\mathrm{if~ellipse} \\
@@
 \end{array}\right.\\
-\Sin(t) = \left\lbrace \begin{array}{c}
+\Sin(t) &= \left\lbrace \begin{array}{c}
 \sin t ~\mathrm{if~ellipse} \\
@@
 -\pi < t < \pi \\
-R_0 = a - x_0 \\
+R_0 &= a - x_0 \\
 a<0 ~ \mathrm{for~hyperbola}
@@
 \tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
-\mathrm{where:~}& B\equiv \frac{R_{90}}{R_0} \\
-A \equiv \frac{R_c}{R_0}
+\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
+A &\equiv \frac{R_c}{R_0}
 \end{align}
@@
 \begin{align}
-x = a\Cos(t)-x_0 \\ 
-y = b\Sin(t)\cos\phi \\
-z =  b\Sin(t)\sin\phi
+x &= a\Cos(t)-x_0 \\ 
+y &= b\Sin(t)\cos\phi \\
+z &=  b\Sin(t)\sin\phi
 \end{align}
@@
 \begin{align}
-X' = \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
-Y'= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot^2(t)\right)^{1/2}
+X' &= \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
+Y' &= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot^2(t)\right)^{1/2}
 \label{eq:conic-projected-y}
@@
 \begin{align}
-X' = a'\Cos t' \label{eq:conic-projected-x-2} \\
-Y' = b'\Sin t' \label{eq:conic-projected-y-2} . 
+X' &= a'\Cos t' \label{eq:conic-projected-x-2} \\
+Y' &= b'\Sin t' \label{eq:conic-projected-y-2} . 
 \end{align}
@@
 \begin{align}
-a' = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
-\Cos(t') = \frac{a'\Cos(t)}{a\cos i} \\
-b' = b
+a' &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
+\Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \\
+b' &= b
 \end{align} 
@@
 \begin{align}
-D' = D\cos i \\
-R'_0 = a' - (a-R_0)\cos i \\
-R'_0 = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
+D' &= D\cos i \\
+R'_0 &= a' - (a-R_0)\cos i \\
+R'_0 &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
 \end{align}

### 2016-10-21 papers/Paper1/sec-projection.tex
Incorporate appendix into both papers

@@
 \subsection{Frames of reference}
+\label{sec:ref-frames}
 
@@
 
-\subsection{Characteristic radii}
-\label{sec:characteristic-radii}
+%\subsection{Characteristic radii}
+%\label{sec:characteristic-radii}
 \begin{figure}
@@
 
-\subsection{Unit vectors normal and tangential to the surface}
-\label{sec:unit-vectors-normal}
+\subsection{Tangent line}
+
 \begin{figure}
@@
 \end{figure}
-We define unit vectors \(\uvec{n}, \uvec{t}\), such that \(\uvec{n}\) is normal to the surface, while \(\uvec{t}\) is tangent to the surface in a plane of constant \(\phi\).
-For \(\phi = 0\) the surface lies in the \(xy\) plane and it is straightforward to show (Fig.~\ref{fig:unitvec}) that in this case the unit vectors are given by
-\begin{equation}
-  \label{eq:uvec-phi0}
-  \uvec{t}_0 =
-  \begin{Vector}
-    -\cos\alpha \\ \sin\alpha \\ 0
-  \end{Vector}
-  \quad \mathrm{and} \quad
-  \uvec{n}_0 =
-  \begin{Vector}
-    \sin\alpha \\ \cos\alpha \\ 0
-  \end{Vector}, 
-\end{equation}
-where
-\begin{equation}
-  \label{eq:alpha}
-  \tan\alpha = -\left.\frac{dy}{dx}\right\vert_{R(\theta)} 
-  = \frac{1 + \omega \tan\theta}{\tan\theta - \omega}
-\end{equation}
-and 
-\begin{equation}
-  \label{eq:omega}
-  \omega(\theta) = \frac{1}{R} \frac{dR}{d\theta} . 
-\end{equation}
-For general \(\phi\), \(\uvec{n}\) and \(\uvec{t}\) can be found by rotating equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, which can then be converted to the observer frame by use of equation~(\ref{eq:Trans}) to give
-\begin{gather}
-  \label{eq:nprime}
-  \begin{split}
-    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
-    & \times 
-      \begin{Vector}
-        (\cos\theta+\omega\sin\theta)\cos i 
-        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
-        (\sin\theta-\omega\cos\theta)\cos\phi \\
-        (\cos\theta+\omega\sin\theta)\sin i 
-        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-      \end{Vector}\\
-  \end{split}\\
-  \label{eq:tprime}
-  \begin{split}
-    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
-    & \times 
-      \begin{Vector}
-        -(\sin\theta-\omega\cos\theta)\cos i
-        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
-        (\cos\theta+\omega\sin\theta)\cos\phi \\
-        -(\cos\theta+\omega\sin\theta)\sin i 
-        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-      \end{Vector}
-  \end{split}
-  \end{gather}
-
-\subsection{Tangent line}
 
@@
 \end{equation}
+See appendix \ref{app:unit-vectors-normal} for more information.
+
 We denote by \(\phi\T\) that value of $\phi$ that satisfies this

### 2016-10-21 papers/Paper1/sec-conic.tex
Incorporate appendix into both papers

@@
 \label{fig:conics}
-\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola The center of the conic is located at a distance $x_0=R_0-a$ from the origin at the $x$ axis. 
-The radius of curvature at the axis is $R_c$, and $R_{90}$ is t he radius of the conic in the perpendicular direction to $R_0$.
+\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola.
+  The center of the conic is located at a distance $x_0=R_0-a$ from the origin at the $x$ axis 
+  The radius of curvature at the axis is $R_c$, and $R_{90}$ is t he radius of the conic in the
+  perpendicular direction to $R_0$.
 }
@@
 
-Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
+Due to the similarities between the parametrization of the ellipse and the hyperbola, we can
+do the following parametrization\footnote{The wholee formalism descripted in this section does
+  not apply for paraboloids ($\theta_c=0$ case). This case is developed in appendix
+  \ref{app:parabola}}:
 \begin{align}
@@
 \Cot(t) = \left\lbrace \begin{array}{c}
-\cot t ~\mathrm{if~ellipse} \\
--\coth t ~\mathrm{if~hyperbola}
+-\cot t ~\mathrm{if~ellipse} \\
+\coth t ~\mathrm{if~hyperbola}
 \end{array}\right.
@@
 
-We must show that the apparent shape of the shell in the observer's frame is still the same conic. To do that, we can write equations
-(\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:
+If the apparent shape of the shell in the observer's frame is still the same conic, then, we
+can write equations(\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:
 \begin{align}
-X' &= a'\Cos t' \label{eq:conic-projected-x-2} \\
-Y' &= b'\Sin t' \label{eq:conic-projected-y-2} . 
+X' = a'\Cos( t') \label{eq:conic-projected-x-2} \\
+Y' = b'\Sin (t') \label{eq:conic-projected-y-2} . 
 \end{align}
@@
 \end{align}
-Which proves that effectively the projection of a given conic is the same conic. With this knowledge, we can obtain the characteristic radii in
-the observer's frame.
+
 \begin{align}
@@
 \begin{align}
-\frac{R'_0}{D'}=\frac{R_0}{D}\left(1+A\cot^2\theta_c(f(i;\theta_c)-1) \right)
+\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
 \end{align}

### 2016-10-21 papers/Paper1/sec-thin-shell.tex
Incorporate appendix into both papers

@@
 
-\section{Hypersonic thin shell model}
+\section{Application to the hypersonic thin shell solution}
 \label{sec:crw-scenario}
-This scenario can be described with the formalism of
-\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
-solution for the two winds interaction problem in the thin shell
-approximation, in terms of a free parameter
-$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
-momentum ratio, which the quantities with subindex 1 corresponds to
-the strongest wind, therefore $\beta<=1$. In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
+As an example application of the ideas of this paper, we consider a
+generalization of the thin-shell solution presented in
+\citet[][hereafter \CRW{}]{Canto:1996}, for the interaction of two
+hypersonic, constant velocity stellar winds.  It is assumed that the
+two shocks are highly radiative and that the post-shock flows are
+perfectly mixed to form a single shell of negligible thickness.  In
+this approximation, the shape of the shell was found algebraically by
+\CRW{} from considering conservation of linear and angular momentum,
+following an approach first outlined in \citet{Wilkin:1996a}.  The
+shape of the bow shock shell is uniquely determined by the parameter
+\(\beta\), defined as the momentum-loss ratio of the two winds:
+\begin{equation}
+  \label{eq:beta-definition}
+  \beta \equiv \frac{\dot{M}_w V_w}{\dot{M}_{w1} V_{w1}} . 
+\end{equation}
+In this definition we use the terminology of \CRW{}, in which
+\(\dot{M}_w\) and \(V_w\) are the mass-loss rate and velocity,
+respectively, of the wind with source at the origin, while
+\(\dot{M}_{w1}\) and \(V_{w1}\) are the mass-loss rate and velocity of
+the second wind, located at a distance \(D\) along their \(z\) axis.
+Note that \CRW{}'s \(z\) and \(r\) correspond to \(x\) and \(y\) in
+sections~\ref{sec:generic-model} to \ref{sec:conic} of the current
+paper.  By always placing the weaker of the two winds at the origin,
+it is only necessary to consider \(\beta \le 1\).
+
+In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
 with the following density distribution:
@@
 Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing the parameter 
-$\xi\equiv \frac{2}{k+2}$ we have:
+<$\xi\equiv \frac{2}{k+2}$ we have:
 
@@
 
+\subsection{Fits to the tail}
+\label{sec:fits-tail}
+
+For the hyperbola ``center''
+\begin{multline}
+  \label{eq:tail-analytic-x0}
+  x_{0,\mathrm{t}} = 0.7 \beta^{-0.55} \biggl[
+    C_3 \bigl(\log_{10}\beta\bigr)^3 + C_2 \bigl(\log_{10}\beta\bigr)^2 
+  \\ + C_1 \log_{10}\beta + C_0
+  \biggr]
+\end{multline}
+\begin{equation}
+  \label{eq:tail-analytic-x0-minus-a}
+  (x_{0,\mathrm{t}} - a_{\mathrm{t}}) = D_2 (\log_{10}\beta)^2 + D_1 \log_{10}\beta + D_0
+\end{equation}
+where
+\begin{alignat}{2}
+  C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
+  D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\} \\
+  \label{eq:tail-analytic-coeffs}
+\end{alignat}
+
+\newcommand\iso{\ensuremath{^{\mathrm{iso}}}}
+
+\begin{table}
+  \caption{Coefficients for hyperbola fit to bowshock tails}
+  \label{tab:tail-fit-coeffs}
+  \begin{align*}
+  C\iso_0 & = {0.123}  & c_{0,0} & = {0.123} & c_{1,0} & = {0.123} & c_{2,0} & = {0.123} \\
+  C\iso_1 & = {0.123}  & c_{0,1} & = {0.123} & c_{1,1} & = {0.123} & c_{2,1} & = {0.123} \\
+  C\iso_2 & = {0.123}  & c_{0,2} & = {0.123} & c_{1,2} & = {0.123} & c_{2,2} & = {0.123} \\
+  C\iso_3 & = {0.123}  & c_{0,3} & = {0.123} & c_{1,3} & = {0.123} & c_{2,3} & = {0.123} \\
+  D\iso_0 & = {0.123}  & d_{0,0} & = {0.123} & d_{1,0} & = {0.123} & d_{2,0} & = {0.123} \\
+  D\iso_1 & = {0.123}  & d_{0,1} & = {0.123} & d_{1,1} & = {0.123} & d_{2,1} & = {0.123} \\
+  D\iso_2 & = {0.123}  & d_{0,2} & = {0.123} & d_{1,2} & = {0.123} & d_{2,2} & = {0.123} \\
+  \end{align*}
+\end{table}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/conic-head-tail-fit}
+  \caption{Double quadric fits to thin shell
+    solutions. \textit{Replace these with a version that uses analytic
+    fit to tail hyperbola parameters}}
+  \label{fig:head-tail}
+\end{figure*}
+
 %%% Local Variables:

### 2016-12-06 papers/Paper1/quadrics-appendix.tex
incorporate appendix

\appendix
\appendixpage
\addappheadtotoc
\section{Parabola of Revolution}
\label{app:parabola}

For the sake of completness, in this section we develop the particular case of the parabola.
The parametrization is given by:

\begin{align}
x &= - \frac{1}{2}R_ct^2 + R_0 \\
y &= R_c t
\end{align}
Where $R_c$ is the radius of curvature and $R_0$ is the distance of the parabola nose to the
origin.
The respective tridimensional shape is given by:
\begin{align}
x &= -\frac{1}{2}R_ct^2 + R_0 \label{eq:x-par-a}\\
y &= R_c t \cos\phi  \label{eq:y-par-a}\\
z &= R_c t \sin\phi  \label{eq:z-par-a}
\end{align}
The azimutal angle where the surface is tangent to the line of sight in this case is given by:
\begin{align}
\sin\phi_t = -\frac{\tan i}{t} \label{eq:sin-tan-a} 
\end{align}

Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and (\ref{eq:z-par-a}) we find that:

\begin{align}
x' &= -\frac{R_c(\frac{1}{2}t^2 \cos^2 i -\sin^2 i)}{\cos i}+R_0\cos i \\
y' &= R_c\left(t^2-\tan^2 i\right)^{1/2} 
\end{align}

The projected radius $R'_0$ can be computed as $x'(y'=0)$. The value of $t$ which fullfill this condition is $t_\parallel$, so:

\begin{align}
t_\parallel &= \tan i \\
\frac{R'_0}{D'} &= \frac{R_0}{D}\left(1-\frac{1}{2}A\tan^2 i\right)  
\end{align}

### 2016-12-06 papers/Paper1/sec-conclusions.tex

@@
 of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
-(ONC) due to the interaction of the photoevaporated wind from proplyds and the stallar wind of \thC{}
+(ONC) due to the interaction of the photoevaporated wind from proplyds and the stallar wind of \thC{}.
 

### 2016-12-09 papers/Paper1/sec-conic.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote

--- 2016-10-21 papers/Paper1/sec-conic.tex
@@
 
-Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
+Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization
+\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
+  projected shape are developed in appendix \ref{app:parabola}}:
 \begin{align}
@@
 \Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \\
-b' &= b
+b' &= b \label{eq:b-prime}
 \end{align} 

### 2016-12-09 papers/Paper1/quadrics-appendix.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote

@@
 
-For the sake of completness, in this section we develop the particular case of the parabola.
+In this section we develop the particular case of the parabola.
 The parametrization is given by:
@@
 
-Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and (\ref{eq:z-par-a}) we find that:
+Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and (\ref{eq:z-par-a}) we find the apparent shape
+of the paraboloid:
 
@@
 
-The projected radius $R'_0$ can be computed as $x'(y'=0)$. The value of $t$ which fullfill this condition is $t_\parallel$, so:
+Taking the limit of eqautions () and () when $\theta_c$ tends to zero we find that:
 
 \begin{align}
-t_\parallel &= \tan i \\
-\frac{R'_0}{D'} &= \frac{R_0}{D}\left(1-\frac{1}{2}A\tan^2 i\right)  
+\left(\frac{q'}{q}\right)_{parabola} &= 1+\frac{A\tan^2 i}{2}\\
+\left(A'\right)_{parabola} &= \frac{A}{\cos^2 i + \frac{A}{2}\sin^2 i}
 \end{align}

### 2016-12-09 papers/Paper1/sec-conic.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote

--- 2016-10-21 papers/Paper1/sec-conic.tex
@@
 
-Due to the similarities between the parametrization of the ellipse and the hyperbola, we can
-do the following parametrization\footnote{The wholee formalism descripted in this section does
-  not apply for paraboloids ($\theta_c=0$ case). This case is developed in appendix
-  \ref{app:parabola}}:
+Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization
+\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
+  projected shape are developed in appendix \ref{app:parabola}}:
 \begin{align}
@@
 \Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \\
-b' &= b
+b' &= b \label{eq:b-prime}
 \end{align}

### 2017-01-25 papers/Paper1/quadrics-appendix.tex
Update some references in appendix
Include derivation of Rc of thin shell model in appendix
* Still need to be completed

@@
 
-Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and (\ref{eq:z-par-a}) we find the apparent shape
+Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and
+(\ref{eq:z-par-a}) we find the apparent shape
 of the paraboloid:
@@
 
-Taking the limit of eqautions () and () when $\theta_c$ tends to zero we find that:
+Taking the limit of equations (\ref{eq:qprime}) and (\ref{eq:Aprime}) when $\theta_c$ tends to zero we find that:
 
@@
 \end{align}
+
+\section{Analytic derivation of the raius of curvature in the Thin Shell model}
+\label{app:rc-r90-analytic}
+
+For small $\theta$ we may do a polynomial expansion for the shell shape such as:
+
+\begin{align}
+R \simeq R_0\left(1+\gamma\theta^2 + \Gamma\theta^4\right) \label{eq:R-exp}
+\end{align}
+
+With this, the radius of curvature at the axis for $R$ is given by equation (\ref{eq:Rcurv}).
+
+The coefficient gamma may be derived by an expansion at small angles of equation
+(\ref{eq:th1th}), as follows:
+
+From the first term of the right side we get:
+
+\begin{align}
+\cot\theta &\simeq \theta^{-1}\left[1-\frac{1}{3}\theta^2\right] \\
+\cos^k\theta\sin^2\theta &\simeq \theta^2 - \left(\frac{1}{3} + \frac{k}{2}\right)\theta^4 \\
+\implies I_k(\theta) &\simeq \frac{1}{3}\theta^3\left[ 1 - \frac{1}{10}(3k+2)\theta^2\right]\\
+\implies 2\beta I_k(\theta)\cot\theta &\simeq \frac{2}{3}\beta\theta^2\left[1-\frac{1}{30}
+(9k+16)\theta^2\right]\label{eq:AR1} 
+\end{align}
+
+For the second term we get:
+
+\begin{align}
+-\frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right) & \simeq -\beta\theta^2\left[1-\frac{1}{12}
+(3k+4)\theta^2\right] \label{eq:AR2}
+\end{align}
+
+For the left side we use equation (25) from \CRW{}. Then, equation (\ref{eq:th1th}) results
+as follows:
+
+\begin{align}
+\theta_1^2\left(1+\frac{1}{15}\theta_1^2\right) = \beta\theta^2\left[1+\frac{1}{60}(4-9k)
+\theta^2\right] \label{eq:th1th-app}
+\end{align}
+
+And we can use the approximation $\theta_1 \approx \beta\theta^2$ for the correction term in
+the left side of (\ref{eq:th1th-app}):
+
+\begin{align}
+\theta_1^2 &= \beta\theta^2\left[1+\frac{1}{60}(4-9k)\theta^2\right]
+\left(1-\frac{\beta}{15}\theta^2\right) \\
+\implies \theta_1^2 &= \beta\theta^2\left[1+ \left(A_k-\frac{\beta}{15}\right)\theta^2\right]\\
+\mathrm{where:~} A_k &\equiv \frac{1}{15}-\frac{3k}{20}
+\end{align}

### 2017-01-26 papers/Paper1/quadrics-appendix.tex
Finish derivation of Rc in thin shell model. Derivation of R90 unfinished

@@
 
-\section{Analytic derivation of the raius of curvature in the Thin Shell model}
-\label{app:rc-r90-analytic}
+\section{Analytic derivation of the radius of curvature in the Thin Shell model}
+\label{app:rc-analytic}
 
@@
 \left(1-\frac{\beta}{15}\theta^2\right) \\
-\implies \theta_1^2 &= \beta\theta^2\left[1+ \left(A_k-\frac{\beta}{15}\right)\theta^2\right]\\
-\mathrm{where:~} A_k &\equiv \frac{1}{15}-\frac{3k}{20}
+\implies \theta_1^2 &= \beta\theta^2\left[1+ 2c_k\theta^2\right] \label{eq:th1th-small}\\
+\mathrm{where:~} c_k &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
+A_k &\equiv \frac{1}{15}-\frac{3k}{20}
 \end{align}
+
+Now, using equation (23) from \CRW{} we may estimate $R$ at low angles. To do this, we need to
+expand each term as follows (neglecting terms of order four or higher):
+
+\begin{align}
+\theta_1 = &= \beta^{1/2}\theta\left[1+ 2c_k\theta^2\right]^{1/2} \\
+\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2c_k\theta^2\right)\right]\\
+\sin\theta_1 &= \theta_1\left[1-\frac{\theta_1^2}{6}\right] \\
+ &= \beta^{1/2}\theta\left[1+\left(c_k-\frac{1}{6}\beta\right)\theta^2\right] \\
+ \sin(\theta+\theta_1) &= \left[\theta+\theta_1\right]\left[1-\frac{\left(\theta+\theta_1
+ \right)^2}{6}\right] \\
+ &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{c_k\beta^{1/2}}{1+\beta^{1/2}}
+ -\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
+\end{align}
+
+So, combining these terms with equation (23) from \CRW{} we found the final expression for $R$:
+
+\begin{align}
+\frac{R}{D}\equiv \frac{\sin\theta_1}{\sin(\theta+\theta_1)} = \frac{\beta^1/2}{1+\beta^{1/2}}
+\left\lbrace 1 + \theta^2\left[\frac{c_k}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
+\right)\right] \right\rbrace \label{eq:r-small-theta}
+\end{align}
+
+Returning to equation (\ref{eq:R-exp}) we see the following:
+
+\begin{align}
+R_0 &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
+\gamma &= \frac{c_k}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right) \label{eq:app-gamma}
+\end{align}
+
+We recover equation (27) of \CRW{} for $R_0$ and equation (\ref{eq:app-gamma}) is the
+needed term to calculate the radius of curvature at the axis.
+
+\section{Analytic derivation of $R_{90}$ in the Thin Shell model}
+\label{app:r90-analytic}
+
+To derive $R_{90}$ we need to evaluate equations (23) from \CRW{} and (\ref{eq:th1th})
+at $\theta=\frac{\pi}{2}$:
+
+\begin{align}
+R_{90} = D\tan\theta_{1,90} \\
+\theta_{1,90}\cot\theta_{1,90} -1 = -\frac{2\beta}{k+2} \label{eq:th190}
+\end{align}
+Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing
+the parameter $\xi\equiv \frac{2}{k+2}$ we have:
+\begin{align}
+R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
+\end{align}
+
+Expanding the left side of (\ref{eq:th190}) until fourth order, equation (\ref{eq:th190})
+becomes:
+
+\begin{align}
+\theta_{1,90}^2\left(1+\frac{\theta_{1,90}^2}{15}\right) \simeq 3\xi\beta
+\end{align}

### 2017-01-26 papers/Paper1/quadrics-appendix.tex
Finished R90 derivation in thin shel model.
Coupling thin shell section with appendix

@@
 
-With this, the radius of curvature at the axis for $R$ is given by equation (\ref{eq:Rcurv}).
+The radius of curvature at the axis for $R$ is given by:
+
+\begin{align}
+R_c = R_0\left(1-2\gamma\right)^{-1}
+\end{align}
 
@@
 \left(1-\frac{\beta}{15}\theta^2\right) \\
-\implies \theta_1^2 &= \beta\theta^2\left[1+ 2c_k\theta^2\right] \label{eq:th1th-small}\\
-\mathrm{where:~} c_k &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
+\implies \theta_1^2 &= \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right]
+\label{eq:th1th-small}\\
+\mathrm{where:~} C_{k\beta} &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
 A_k &\equiv \frac{1}{15}-\frac{3k}{20}
@@
 \begin{align}
-\theta_1 = &= \beta^{1/2}\theta\left[1+ 2c_k\theta^2\right]^{1/2} \\
-\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2c_k\theta^2\right)\right]\\
+\theta_1 = &= \beta^{1/2}\theta\left[1+ 2C_{k\beta}\theta^2\right]^{1/2} \\
+\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2C_{k\beta}\theta^2\right)\right]\\
 \sin\theta_1 &= \theta_1\left[1-\frac{\theta_1^2}{6}\right] \\
- &= \beta^{1/2}\theta\left[1+\left(c_k-\frac{1}{6}\beta\right)\theta^2\right] \\
+ &= \beta^{1/2}\theta\left[1+\left(C_{k\beta}-\frac{1}{6}\beta\right)\theta^2\right] \\
  \sin(\theta+\theta_1) &= \left[\theta+\theta_1\right]\left[1-\frac{\left(\theta+\theta_1
  \right)^2}{6}\right] \\
- &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{c_k\beta^{1/2}}{1+\beta^{1/2}}
- -\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
+ &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{C_{k\beta}\beta^{1/2}}
+ {1+\beta^{1/2}}-\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
 \end{align}
@@
 \frac{R}{D}\equiv \frac{\sin\theta_1}{\sin(\theta+\theta_1)} = \frac{\beta^1/2}{1+\beta^{1/2}}
-\left\lbrace 1 + \theta^2\left[\frac{c_k}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
+\left\lbrace 1 + \theta^2\left[\frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
 \right)\right] \right\rbrace \label{eq:r-small-theta}
@@
 R_0 &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
-\gamma &= \frac{c_k}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right) \label{eq:app-gamma}
+\gamma &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right)
+\label{eq:app-gamma}
 \end{align}
@@
 \begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
+R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} \label{eq:r90-incomplete}
 \end{align}
@@
 \end{align}
+
+Applying the approximation $\theta_1^2 \approx 3\xi\beta$ we found a solution
+for $\theta_{1,90}$:
+
+\begin{align}
+\theta_{1,90} = \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2}
+\end{align}
+
+And substituting into (\ref{eq:r90-incomplete}) we find the solution for $R_{90}$:
+
+\begin{align}
+R_{90} &= \frac{\left(3\xi\beta\right)^{1/2}}{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}
+\left(1-\xi\beta\right)} \\
+\implies B &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
+{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
+\end{align}

### 2017-01-26 papers/Paper1/sec-thin-shell.tex
Include head/tail figure in paper
Rewrite intro to sec 5 of paper on CRW model
Make a start on writing in paper about about fits to tails
Include derivation of Rc of thin shell model in appendix
* Still need to be completed
Finished R90 derivation in thin shel model.
Coupling thin shell section with appendix

--- 2016-10-14 papers/Paper1/sec-thin-shell.tex
@@
 \dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w v_w I_k (\theta) \label{eq:piz}\\
-I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \\
+I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \label{eq:Ik}\\
 \dot{J}_w = 0 \label{eq:jdot} \\
@@
 Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
-We can obtain $R_{90}$ by the following process:
-Evaluating equations  (\ref{eq:th1th}) and (23) from \CRW{} at $\theta=\frac{\pi}{2}$ we obtain the following:
-
-\begin{align}
-R_{90} = D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} = 1-\frac{2\beta}{k+2} \label{eq:th190}
-\end{align}
-Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing the parameter 
-$\xi\equiv \frac{2}{k+2}$ we have:
-
-\begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
-\end{align}
-
-Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}), using a small angle  approximation, we find that:
-
-\begin{align}
-\theta_{1,90} &\simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
-\label{eq:th190sol}
-\end{align}
-
-With this, we have a solution for $B \equiv \frac{R_{90}}{R_0}$:
+We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
+which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:
 
@@
 
-Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 4th order for small $\theta$ values to find that for such values
+Now, the solution for $R_c$ is explained in appendix \ref{app:rc-analytic},
+which lead us to derive the radius of curvature at the symmetry axis:
 
 \begin{align}
-\theta_1^2 &\simeq \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right] \\
-\mathrm{where:~} & C_{k\beta} \equiv \frac{1}{30}\left(1-\beta-\frac{9}{4}k\right)
-\end{align}
-Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:
-
-\begin{align}
-R &\simeq R_0 \left(1+\gamma\theta^2\right)
-\label{eq:R_approx} \\
+R_c &= R_0\left(1-2\gamma\right)^{-1} \label{eq:Rcurv} \\
 \mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
@@
 
-Which lead us to derive the radius of curvature at the symmetry axis:
-
-\begin{equation}
-R_c = R_0\left(1-2\gamma\right)^{-1}
-\label{eq:Rcurv}
-\end{equation}
-
-finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:thc-conic})
+Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
+conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:thc-conic})
 

### 2017-01-29 papers/Paper1/sec-thin-shell.tex

--- 2016-10-21 papers/Paper1/sec-thin-shell.tex
@@
 Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
-We can obtain $R_{90}$ by the following process:
-Evaluating equations  (\ref{eq:th1th}) and (23) from \CRW{} at $\theta=\frac{\pi}{2}$ we obtain the following:
-
-\begin{align}
-R_{90} = D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} = 1-\frac{2\beta}{k+2} \label{eq:th190}
-\end{align}
-Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing the parameter 
-<$\xi\equiv \frac{2}{k+2}$ we have:
-
-\begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
-\end{align}
-
-Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}), using a small angle  approximation, we find that:
-
-\begin{align}
-\theta_{1,90} &\simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
-\label{eq:th190sol}
-\end{align}
-
-With this, we have a solution for $B \equiv \frac{R_{90}}{R_0}$:
+We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
+which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:
 

### 2017-01-30 papers/Paper1/sec-conic.tex
Update some references in appendix
Figure 5 is now in one column
Finish improvements to Fig 5

@@
 %an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
-\begin{figure}
+\begin{figure*}
 \setlength\tabcolsep{0pt}
-\begin{tabular}{cc}
-\includegraphics[height=0.54\linewidth, trim=30 0 30 0, clip]{ellipse_py} &
-\includegraphics[height=0.54\linewidth, trim=60 0 70 0, clip]{hyperbola_py}
+\begin{tabular}{ll}
+  (a) & (b) \\
+  \includegraphics[height=0.45\linewidth]{figs/ellipse_py}
+      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_py}
 \end{tabular}
 \label{fig:conics}
-\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola.
-  The center of the conic is located at a distance $x_0=R_0-a$ from the origin at the $x$ axis 
-  The radius of curvature at the axis is $R_c$, and $R_{90}$ is t he radius of the conic in the
-  perpendicular direction to $R_0$.
-}
-\end{figure}
+\caption{Example off-center conic sections that can form quadrics of
+  revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
+  between the conic section parameters \(a\), \(b\), \(\theta_c\) and
+  the bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
+  defined in Fig.~\ref{fig:characteristic-radii}. The center of the
+  conic is located at a distance $x_0=R_0-a$ from the origin along the
+  $x$ axis.  }
+\end{figure*}
 \begin{figure}
@@
 \frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
+\label{eq:qprime}
 \end{align}
@@
   \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
+  \label{eq:Aprime}
 \end{align}
@@
 %%% mode: latex
-%%% TeX-master: "proplyd-bowshocks"
+%%% TeX-master: "quadrics-bowshock"
 %%% End:

### 2017-02-01 papers/Paper1/shape_beta.py
Incorporate isotropic case to figure 9.
Other changes:
- Resize figure 8 and relocated in figs folder.

@@ -51,9 +51,12 @@ if flag:
     plt.ylabel(r"$r/D$",fontsize=fontsize)
     plt.tick_params(axis='both', which='major', labelsize=ticksize)
     plt.gca().set_aspect("equal",adjustable="box")
+    fig = plt.gcf()
+    fig.set_size_inches(7, 4.5)
     plt.xlim(-0.4,1)
     plt.ylim(0,1)
-    plt.savefig("r-beta.pdf")
+    plt.tight_layout()
+    fig.savefig("figs/r-beta.pdf")
 
 ####### Figure 2 #################
 

### 2017-02-02 papers/Paper1/sec-thin-shell.tex
Automatically generate data for table of tail coefficients
This is done in Rc-revisited-2016.org in the section "Write LaTeX
version of the tail analytic fit for paper".  The results are then
pasted into the latex file.
Incorporate isotropic case to figure 9.
Other changes:
- Resize figure 8 and relocated in figs folder.
Improve Fig 10

@@
 \begin{figure}
-\includegraphics[width=\linewidth]{r-beta}
+\includegraphics[width=\linewidth]{figs/r-beta}
 \caption{Bow shock shapes for interacting winds in the thin-shell
@@
 \begin{alignat}{2}
+  \label{eq:tail-analytic-coeffs-c}
   C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
-  D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\} \\
-  \label{eq:tail-analytic-coeffs}
+  \label{eq:tail-analytic-coeffs-d}
+  D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\}
 \end{alignat}
@@
   \label{tab:tail-fit-coeffs}
-  \begin{align*}
-  C\iso_0 & = {0.123}  & c_{0,0} & = {0.123} & c_{1,0} & = {0.123} & c_{2,0} & = {0.123} \\
-  C\iso_1 & = {0.123}  & c_{0,1} & = {0.123} & c_{1,1} & = {0.123} & c_{2,1} & = {0.123} \\
-  C\iso_2 & = {0.123}  & c_{0,2} & = {0.123} & c_{1,2} & = {0.123} & c_{2,2} & = {0.123} \\
-  C\iso_3 & = {0.123}  & c_{0,3} & = {0.123} & c_{1,3} & = {0.123} & c_{2,3} & = {0.123} \\
-  D\iso_0 & = {0.123}  & d_{0,0} & = {0.123} & d_{1,0} & = {0.123} & d_{2,0} & = {0.123} \\
-  D\iso_1 & = {0.123}  & d_{0,1} & = {0.123} & d_{1,1} & = {0.123} & d_{2,1} & = {0.123} \\
-  D\iso_2 & = {0.123}  & d_{0,2} & = {0.123} & d_{1,2} & = {0.123} & d_{2,2} & = {0.123} \\
-  \end{align*}
+  \renewcommand\arraystretch{1.2}
+  \setlength\tabcolsep{0.5\tabcolsep}
+  \begin{tabular}{@{}llll@{}}
+    \toprule
+    Equation~(\ref{eq:tail-analytic-x0}) & 
+    \multicolumn{3}{l}{
+    Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
+    } \\ \midrule
+    \( C\iso_0 = +1.3195     \)    
+    & \( c_{0,0} = +2.0758   \)  
+    & \( c_{1,0} = -0.2309   \)  
+    & \( c_{2,0} = -0.2532   \)\\
+      \( C\iso_1 = +0.4229     \)    
+    & \( c_{0,1} = +0.9571   \)  
+    & \( c_{1,1} = -0.1530   \)  
+    & \( c_{2,1} = -0.2487   \)\\
+      \( C\iso_2 = +0.1092     \)    
+    & \( c_{0,2} = +0.2528   \)  
+    & \( c_{1,2} = -0.0360   \)  
+    & \( c_{2,2} = -0.0794   \)\\
+      \( C\iso_3 = +0.0051     \)    
+    & \( c_{0,3} = +0.0171   \)  
+    & \( c_{1,3} = -0.0010   \)  
+    & \( c_{2,3} = -0.0095   \)\\ \midrule
+    Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
+    \multicolumn{3}{l}{
+    Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
+    } \\ \midrule
+    \( D\iso_0 = +0.7962   \)    
+    & \( d_{0,0} = +0.8516 \)  
+    & \( d_{1,0} = -0.0907 \)  
+    & \( d_{2,0} = -0.2002 \)\\
+      \( D\iso_1 = -0.2363   \)    
+    & \( d_{0,1} = -0.7620 \)  
+    & \( d_{1,1} = +0.1411 \)  
+    & \( d_{2,1} = -0.0295 \)\\
+      \( D\iso_2 = -0.0126   \)    
+    & \( d_{0,2} = -0.0683 \)  
+    & \( d_{1,2} = +0.0390 \)  
+    & \( d_{2,2} = -0.0236 \)\\
+    \bottomrule
+  \end{tabular}
 \end{table}
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/conic-head-tail-fit}
+  \includegraphics[height=0.85\textheight]{figs/conic-head-tail-analytic}
   \caption{Double quadric fits to thin shell
-    solutions. \textit{Replace these with a version that uses analytic
-    fit to tail hyperbola parameters}}
+    solutions.}
   \label{fig:head-tail}

### 2017-02-02 CRW-shapes/conic-head-tail-analytic.py

@@ -94,22 +94,23 @@ for j, xi in enumerate(XI_LIST):
         else:
             text = r'Anisotropic, $\xi = {:.1f}$'.format(xi)
         text += '\n' + r'$\beta = {:.4f}$'.format(beta)
-        text += ', ' + r'$D = {:.1f}$'.format(ht.D)
-        text += '\n' + r'$x_t = {:.1f}$'.format(ht.x0_t)
-        text += ', ' + r'$x_t - a_t = {:.1f}$'.format(ht.x0_t - ht.a_t)
-        text += ', ' + r"$\theta_t = {:.1f}$".format(np.degrees(-ht.theta_t))
-        text += '\n' + r'$x_h = {:.1f}$'.format(ht.x0_h)
-        text += ', ' + r"$\theta_h = {:.1f}$".format(np.degrees(ht.theta_h))
+        # text += ', ' + r'$D = {:.1f}$'.format(ht.D)
+        # text += '\n' + r'$x_t = {:.1f}$'.format(ht.x0_t)
+        # text += ', ' + r'$x_t - a_t = {:.1f}$'.format(ht.x0_t - ht.a_t)
+        # text += ', ' + r"$\theta_t = {:.1f}$".format(np.degrees(-ht.theta_t))
+        # text += '\n' + r'$x_h = {:.1f}$'.format(ht.x0_h)
+        # text += ', ' + r"$\theta_h = {:.1f}$".format(np.degrees(ht.theta_h))
         ax.text(xright, ytop, text,
                 ha='right', va='top', bbox=whitebox, fontsize='small')
 
 # Put axis labels on lower left panel only
 axes[-1, 0].set(
     xlim=[xmin, xmax], ylim=[ymin, ymax],
+    xticks=[-4, -2, 0],
     xlabel=r'$x / r_{0}$', ylabel=r'$y / r_{0}$',
 )
 
-fig.set_size_inches(3*nbeta, 3*nxi)
+fig.set_size_inches(2*nbeta, 2*nxi)
 fig.tight_layout()
 fig.savefig(figfilename)
-print(figfilename)
+print(figfilename, end='')

### 2017-02-06 papers/Paper1/sec-conic.tex
Rewrote Section 4 of paper to solve consistency issues.
- The conic parameters (a,b) are both defined as positive to avoid
conflicts with equation for Rc.
- THe rest of the section needs a revision.

@@
   defined in Fig.~\ref{fig:characteristic-radii}. The center of the
-  conic is located at a distance $x_0=R_0-a$ from the origin along the
-  $x$ axis.  }
+  conic is located at a distance $x_0=a \mp R_0$ from the origin along the
+  $x$ axis. Where the minus sign on $R_0$ correspond to ellipses and the plus
+  sign to hyperbolas}
 \end{figure*}
@@
 \cos t ~\mathrm{if~ellipse} \\
-\cosh t ~\mathrm{if~hyperbola}
+-\cosh t ~\mathrm{if~hyperbola}
 \end{array}\right.\\
@@
 \end{array}\right. \\
--\pi < t < \pi \\
+-\pi &< t < \pi \\
 R_0 &= a - x_0 \\
-a<0 ~ \mathrm{for~hyperbola}
 \end{align}
-We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
-(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
-a parabola.
-To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
-could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
+Where $a$ and $b$ are real, positive numbers.
+
+We have set a whole family of curves with a singular parameter denoted as:
 \begin{align}
-R_c &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
-R_{90} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
+  \tan\theta_c \equiv \pm\frac{b}{a}\label{eq:Thc}
 \end{align}
-In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric. The inverse transformation of (\ref{eq:Rc-conic})
-and (\ref{eq:r90-conic}) is given by:
+Positive values of this parameter describe closed curves (i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas).
+Particular cases are $\theta_c =\frac{\pi}{4}$,
+which describes a circle and $\theta_c=0$, which describes a parabola.
+To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic
+parameters $(a,b,\theta_c)$ could be derived from the former. Either way, the radius of curvature can be computed as:
+
 \begin{align}
-\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
-\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
-\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
-\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
-A &\equiv \frac{R_c}{R_0}
+R_c = \frac{b^2}{a} \label{eq:Rc-conic}
 \end{align}
+
+For the rest of the parameters, the equation for ellipses and hyperbolas are very similar, except for a sign in some terms. In all cases, the upper sign will
+correspond to ellipses and the lower sign for hyperbolas:
+
+\begin{align}
+R_{90} = b\left[\pm \left(1-\left(a\mp R_0\right)^2\right)\right]^{1/2}\label{eq:conic-R90}
+\end{align}
+
+Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
+But first is useful to define the quantities $A \equiv \frac{R_c}{R_0}$ and $B\equiv \frac{R_{90}}{R_0}$ for simplification purposes.
+
+\begin{align}
+  \frac{a}{R_0} &= \frac{A}{\pm\left(2A-B^2\right)} \label{eq:a-con}\\
+  \frac{b}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}} \label{eq:b-con}
+\end{align}
+
+Dividing equations (\ref{eq:a-con}) and (\ref{eq:b-con}) and substituting into equation (\ref{eq:Thc}) we get:
+
+\begin{align}
+\tan\theta_c = \frac{2A-B^2}{\left|2A-B^2\right|^{1/2}} \label{eq:th_c}
+\end{align}
+
+Note that the term $2A-B^2$ acts as a discriminant which determine the quadric we are working with.
+
+%The transformation between the conic parameters and the characteristic radii are given by:
+%\begin{align}
+%R_c &= \frac{b^2}{a} \\
+%R_{90} &= b\left[\pm\left(1 - \frac{(a \mp R_0)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
+%\end{align}ut 
+%In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric.
+%The inverse transformation of (\ref{eq:Rc-conic}) and (\ref{eq:r90-conic}) is given by:
+%\begin{align}
+%\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
+%\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
+%\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
+%\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
+%#A &\equiv \frac{R_c}{R_0}
+%\end{align}
 

### 2017-02-06 papers/Paper1/sec-conic.tex
Final hand-improvements to Fig 5

@@
 \begin{figure*}
-\setlength\tabcolsep{0pt}
+\setlength\tabcolsep{2em}
 \begin{tabular}{ll}
   (a) & (b) \\
-  \includegraphics[height=0.45\linewidth]{figs/ellipse_py}
-      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_py}
+  \includegraphics[height=0.45\linewidth]{figs/ellipse_edited}
+      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_edited}
 \end{tabular}
@@
   revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
-  between the conic section parameters \(a\), \(b\), \(\theta_c\) and
-  the bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
-  defined in Fig.~\ref{fig:characteristic-radii}. The center of the
-  conic is located at a distance $x_0=a \mp R_0$ from the origin along the
-  $x$ axis. Where the minus sign on $R_0$ correspond to ellipses and the plus
-  sign to hyperbolas}
+  between the conic section parameters \(a\), \(b\), \(\theta_c\) and the
+  bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
+  defined in Fig.~\ref{fig:characteristic-radii}. The origin (center
+  of the weaker flow) is indicated by a red star, the center of
+  curvature of the apex of the bow shock is indicated by a green dot,
+  and the geometric center of the conic section is indicated by a blue
+  cross.  }
 \end{figure*}

### 2017-02-07 papers/Paper1/sec-thin-shell.tex
Final hand-improvements to Fig 5
Add figure of residuals to head-tail fits

@@
 
+In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with
+
+We therefore 
+We carry out three-level nested fits to determine the
+
 For the hyperbola ``center''
@@
   \centering
-  \includegraphics[height=0.85\textheight]{figs/conic-head-tail-analytic}
+  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
   \caption{Double quadric fits to thin shell
@@
   \label{fig:head-tail}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
+  \caption[]{Residuals of double quadric fits to thin shell solutions.
+    Residuals are expressed as the fractional error in the
+    complementary angle \(\theta_1\) for the same parameters as are shown
+    in Fig.~\ref{fig:head-tail}.}
+  \label{fig:head-tail-residuals}
 \end{figure*}

### 2017-02-07 CRW-shapes/conic-head-tail-residuals.py

@@ -1,0 +1,127 @@
+import sys
+import numpy as np
+import astropy.modeling.fitting
+from matplotlib import pyplot as plt
+import seaborn as sns
+from scipy.interpolate import interp1d
+import equation6
+import conic_parameters
+import theta_ratio_fit 
+sys.path.append('../conic-projection')
+from conproj_utils import Conic
+
+XI_LIST = [None, 1.0, 0.8, 0.4]
+BETA_LIST = [0.1, 0.01, 0.0001]
+nxi, nbeta = len(XI_LIST), len(BETA_LIST)
+
+ntheta = 100
+theta = np.linspace(0.0, np.pi, ntheta)
+
+figfilename = sys.argv[0].replace('.py', '.pdf')
+
+sns.set_style('whitegrid')
+sns.set_color_codes('dark')
+
+NROWS = 2
+fig, axes = plt.subplots(nxi, nbeta, sharex=True, sharey=True)
+
+xmin, xmax = -5.0, 2.1
+ymin, ymax = -0.1, 7.0
+# xmin, xmax = -7.0, 4.1
+# ymin, ymax = -0.1, 11.0
+
+ytop = ymin + 0.98*(ymax - ymin)
+xright = xmin + 0.98*(xmax - xmin)
+whitebox = {'edgecolor': 'none', 'facecolor': 'white',
+            'alpha': 0.7, 'boxstyle': 'round,pad=0.1'}
+
+
+# x-data for tail asymptote
+xa = np.linspace(xmin, xmax, 2)
+
+# Set up fitter for fitting the tail
+fit = astropy.modeling.fitting.LevMarLSQFitter()
+
+for j, xi in enumerate(XI_LIST):
+    for i, beta in enumerate(BETA_LIST[::-1]):
+        ax = axes[j, i]
+
+        # The exact solution to the shell
+        if xi is None:
+            shell = equation6.Shell(innertype='isotropic', beta=beta)
+        else:
+            shell = equation6.Shell(innertype='anisotropic', beta=beta, xi=xi)
+        R, theta1 = shell.radius(theta, full=True)
+        ratio = theta1/theta
+        R_crw = R/shell.R0
+        x_crw = R_crw*np.cos(theta)
+        y_crw = R_crw*np.sin(theta)
+
+        # Fit to head and analytic fit to fit to tail
+        ht = conic_parameters.HeadTail(beta, xi=xi,
+				       xmin=0.0, method='analytic fit')
+
[…]

### 2017-02-08 papers/Paper1/sec-thin-shell.tex
Add a figure to illustrate the CRW two-wind interaction problem
Add new figure to show anisotropic wind patterns

@@
 \newcommand\CRW{\citetalias{Canto:1996}}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
+  \caption[]{Schematic diagram of two-wind interaction problem,
+    following \citet{Canto:1996}.}
+  \label{fig:crw-schema}
+\end{figure}
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/anisotropic-arrows}
+  \caption[]{Schematic diagram of wind flow patterns in isotropic and
+    non-isotropic cases.  Arrows represent the wind momentum loss rate
+    per solid angle.}
+  \label{fig:crw-schema}
+\end{figure}
 In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
 with the following density distribution:
-
 \begin{align}

### 2017-02-09 papers/Paper1/sec-projection.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote
Minor changes:
* Exchange Figures 2 and 3/
* subindices of eqautions A9 and A10 converted to \mathrm
Minor corrections to secs 3.3 and 3.4

--- 2016-06-21 papers/Paper1/sec-projection.tex
@@
 
-%Note: I'm aware that some of this material should be moved to an appendix, but I think it will be a future edition.
+% Note: I'm aware that some of this material should be moved to an appendix, but I think it will be a future edition.
+
 \subsection{Frames of reference}
+\label{sec:ref-frames}
 
@@
   \centering
+  \includegraphics[width=\linewidth]{figs/characteristic-radii}
+  \caption{Characteristic radii in the body frame.}
+  \label{fig:characteristic-radii}
+\end{figure}
+
+\begin{figure}
+  \centering
   \includegraphics[width=\linewidth]{figs/projection-pos}
@@
   \label{fig:projection-pos}
-\end{figure}
-
-\subsection{Characteristic radii}
-\label{sec:characteristic-radii}
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/characteristic-radii}
-  \caption{Characteristic radii in the body frame.}
-  \label{fig:characteristic-radii}
 \end{figure}
@@
   \end{gather}
-
 \subsection{Tangent line}
@@
 \end{equation}
+
 We denote by \(\phi\T\) that value of $\phi$ that satisfies this
@@
 \end{equation}
-It is important to note that equation~(\ref{eq:tanphi}) does not have
+Note that equation~(\ref{eq:tanphi}) will not have
 a solution for arbitrary values of $\theta$ and $i$, but only when
 $|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent
-line only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is
+line only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of \(\theta\) on the tangent line's projected symmetry axis (\(\theta' = 0\)), 
 given implicitly by
@@
 In addition, if the surface is sufficiently ``open''
-(\(\alpha > \alpha_{\mathrm{min}} > 0\) for all \(\theta\)), then for
-those inclinations with
-\(\vert i\vert > (90^\circ - \alpha_{\mathrm{min}}) \) the tangent
-line does not exist for any value of \(\theta\).  In other words, when
-the viewing angle is sufficiently close to face-on, the projected
-surface has no ``edge'' and will no longer appear to be a bow shock.
+(\(\alpha \ge \alpha_{\mathrm{min}} > 0\) for all \(\theta\)), then for those
+inclinations with
+\(\vert i\vert > (90^\circ - \alpha_{\mathrm{min}}) \) the tangent line does not exist
+for any value of \(\theta\).  In other words, when the viewing angle is
+sufficiently close to face-on, the projected surface has no ``edge''
+and will no longer look like a bow shock to the observer.
 
@@
 
-Considering further applications to bow shocks, we will consider open shells. In order to compare the shell shape given by $R(\theta)$ with observations,
+% Considering further applications to bow shocks, we will consider open shells.
+In order to compare the shell shape given by $R(\theta)$ with observations,
 it is convenient to define the following apparent radii in the observer frame: $R'_{0}$ and $R'_{90}$. These are projected distances of the shell tangent line
-from the origin. The first is measured in the direction of the symetry axis, and the second in a perpendicular direction. More concretely $R'_{0} = x'\T(y'\T=0)$
+from the origin. The first is measured in the direction of the symmetry axis, and the second in a perpendicular direction. More concretely $R'_{0} = x'\T(y'\T=0)$
 and $R'_{90} = y'\T(x'\T=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:
 \begin{align}
-R'_{0} = R(\theta_{0})\cos(\theta + i) \label{eq:Rpar} 
+R'_{0} = R(\theta_{0})\cos(\theta_{0} + i) \label{eq:Rpar} 
 \end{align}
@@
 \begin{align}
-R'_{90} = R(\theta_{90})\sin\theta_{90}\left(1-\sin^2(\phi\T(\theta_{90}))\right)^{1/2}
+R'_{90} = R(\theta_{90})\sin\theta_{90}\left(1-\sin^2\bigl(\phi\T(\theta_{90})\bigr)\right)^{1/2}
 \end{align}

### 2017-02-10 papers/Paper1/sec-conic.tex
Solved more mathematical inconsistencies in conics section

@@
 
-Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization
+Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization, using the convention
+that if a dual sign appears, the upper sign correspond to the elliptical quadrics, and the lower sign to the hyperbolic quadrics
 \footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
@@
 -\pi &< t < \pi \\
-R_0 &= a - x_0 \\
+x_0 &= \pm a - R_0 \label{eq:x0}\\
 \end{align}
@@
 
-For the rest of the parameters, the equation for ellipses and hyperbolas are very similar, except for a sign in some terms. In all cases, the upper sign will
-correspond to ellipses and the lower sign for hyperbolas:
+For the rest of the parameters, the equation for ellipses and hyperbolas are very similar:
 
 \begin{align}
-R_{90} = b\left[\pm \left(1-\left(a\mp R_0\right)^2\right)\right]^{1/2}\label{eq:conic-R90}
+R_{90} = b\left[\pm \left(1-\frac{x_0^2}{a^2}\right)\right]^{1/2}\label{eq:conic-R90}
 \end{align}
@@
 \Cot(t) = \left\lbrace \begin{array}{c}
--\cot t ~\mathrm{if~ellipse} \\
+\cot t ~\mathrm{if~ellipse} \\
 \coth t ~\mathrm{if~hyperbola}
@@
 
+Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:
+
 \begin{align}
-D' &= D\cos i \\
-R'_0 &= a' - (a-R_0)\cos i \\
-R'_0 &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
+R'_0 &= \pm a' - x_0\cos i \\
+R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (\pm a-R_0)\cos i
 \end{align}
 
-With  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
+Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
 \begin{align}
@@
 %Where $A\equiv \frac{R_c}{R_0}$
-
 The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
 \begin{align}
-  \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
+A'\equiv  \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
   \label{eq:Aprime}

### 2017-02-15 papers/Paper1/sec-conic.tex
Insert equations for \theta'_c and R'_90 and use of tilded variables

@@
 \begin{align}
-R_{90} = b\left[\pm \left(1-\frac{x_0^2}{a^2}\right)\right]^{1/2}\label{eq:conic-R90}
+R_{90} = \tan\theta_c\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
 \end{align}
@@
 Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
-But first is useful to define the quantities $A \equiv \frac{R_c}{R_0}$ and $B\equiv \frac{R_{90}}{R_0}$ for simplification purposes.
+%But first is useful to define the quantities $\tilde{R}_c \equiv \frac{R_c}{R_0}$ and $\equiv \frac{\tilde{R}_{90}}{R_0}$ for simplification purposes.
+Hereafter is useful to denote with a tilde quantities which are normalized with $R_0$:
 
 \begin{align}
-  \frac{a}{R_0} &= \frac{A}{\pm\left(2A-B^2\right)} \label{eq:a-con}\\
-  \frac{b}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}} \label{eq:b-con}
+  \tilde{a}\equiv \frac{a}{R_0} &= \pm\frac{\tilde{R}_c}{\left(2\tilde{R}_c-\tilde{R}_{90}^2\right)} \label{eq:a-con}\\
+  \tilde{b}\equiv \frac{b}{R_0} &= \frac{\tilde{R}_c}{\left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2}} \label{eq:b-con}
 \end{align}
@@
 \begin{align}
-\tan\theta_c = \frac{2A-B^2}{\left|2A-B^2\right|^{1/2}} \label{eq:th_c}
+\tan\theta_c = \pm \left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2} \label{eq:th_c}
 \end{align}
 
-Note that the term $2A-B^2$ acts as a discriminant which determine the quadric we are working with.
+Note that the term $2\tilde{R}_c-\tilde{R}_{90}^2$ acts as a discriminant which determine the quadric we are working with.
 
@@
 \begin{align}
-\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
+\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
 \label{eq:qprime}
@@
 \begin{align}
-A'\equiv  \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
-  \label{eq:Aprime}
+  \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
+  \label{eq:Aprime}\\
+  \tan\theta_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
+  \tilde{R}'_{90} &= \frac{\left[2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q})\right]^{1/2}}{\cos i f(i;\theta_c)\frac{q'}{q}}
 \end{align}
 where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.
+
 % \begin{figure*}

### 2017-02-16 papers/Paper1/sec-thin-shell.tex
Create new figures. Move figure 8 to section 2.
- ~R'c vs inclination
- ~R'90 vs inclination
- T'c vs ~R'c

@@
 \newcommand\CRW{\citetalias{Canto:1996}}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
-  \caption[]{Schematic diagram of two-wind interaction problem,
-    following \citet{Canto:1996}.}
-  \label{fig:crw-schema}
-\end{figure}
 
@@
   moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
-  And the dooted lines show a wind with extreme anisotropy degree $(k=8)$.}
+  And the dotted lines show a wind with extreme anisotropy degree $(k=8)$.}
 \label{fig:r-beta}
@@
 \begin{align}
-B = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
+\tilde{R}_{90} = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
 \label{eq:B}
@@
 \end{tabular}
-\caption{Top: Characteristic radii, $A = R_c/R_0$ (solid lines) and $B
+\caption{Top: Characteristic radii, $\tilde{R}_c = R_c/R_0$ (solid lines) and $\tilde{R}_{90}
   = R_{90}/R_0$ (dashed lines)

### 2017-02-16 papers/Paper1/sec-conic.tex
Make new graphs of projected conics

@@
 \caption{Example of a family of conic sections, all with the same
-  radius of curvature at their apex (marked by white dot) on the
-  \(x\)~axis: \(R_c = 2 R_0\). The parameter
-  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
-  values corresponding to hyperbolae.}
+  normalized radius of curvature at their apex (marked by white dot):
+  \(\widetilde{R}_c = R_c/R_0 = 2 \). The parameter
+  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative values
+  corresponding to hyperbolae.  Differerent values of
+  \(\widetilde{R}_c\) can be achieved by moving the origin along the
+  \(x\)-axis while keeping the apex fixed at \(\tilde{x} = 1\).)}
 \label{fig:conics-family}

### 2017-02-16 Quadric-shapes/projected-R0-vs-i.py

@@ -1,0 +1,55 @@
+import sys
+import numpy as np
+from matplotlib import pyplot as plt
+import seaborn as sns
+
+plotfile = sys.argv[0].replace('.py', '.pdf')
+
+sns.set_style('white')
+fig, ax = plt.subplots(figsize=(5, 5))
+
+inc = np.linspace(0.0, 0.5*np.pi, 5000)
+inc_deg = np.degrees(inc)
+
+Rcs = [1.0, 2.0, 4.0, 8.0]
+Tcs = [-2.0, -1.0, -0.5, 1e-3, 0.5, 1.0]
+
+n_Rc = len(Rcs)
+n_Tc = len(Tcs)
+
+lws = np.linspace(1.0, 2.0, n_Rc)
+alphas = np.linspace(1.0, 0.2, n_Rc)
+cols = sns.color_palette('magma', n_colors=n_Tc)
+lss = ['-', '--', ':', '-.']
+
+
+def qratio(inc, Tc, Rc):
+    f = np.sqrt(1.0 + Tc*np.tan(inc)**2)
+    return 1.0 + Rc*(f - 1.0) / Tc
+
+for Rc, lw, alpha, ls in list(zip(Rcs, lws, alphas, lss))[::-1]:
+    for Tc, col in list(zip(Tcs, cols))[::-1]:
+        if Rc == 1.0:
+            label = fr'$T_c = {Tc:.1f}$'
+        else:
+            label = None
+        ax.plot(inc_deg, qratio(inc, Tc, Rc),
+                c=col, ls=ls, label=label)
+
+i25, i50, i75 = [90.0 - np.degrees(np.arccos(_)) for _ in [0.25, 0.5, 0.75]]
+
+ax.fill_betweenx([0.0, 100.0], [0.0]*2, [i25]*2, alpha=0.2, color='g')
+ax.fill_betweenx([0.0, 100.0], [i50]*2, [i75]*2, alpha=0.2, color='g')
+
+ax.legend(ncol=1, fontsize='xx-small', frameon=True)
+ax.set(
+    yscale='linear',
+    xlim=[0.0, 90.0],
+    ylim=[0.0, 7.0],
+    xlabel=r'Inclination, degrees',
+    ylabel=r"Projected boost in apex ratio: $(R_{0}' / D') / (R_{0} / D)$",
+    xticks=[15, 30, 45, 60, 75, 90],
+)        
+fig.tight_layout()
+fig.savefig(plotfile)
+print(plotfile, end='')

### 2017-02-16 Quadric-shapes/projected-Rc-vs-i.py

@@ -1,0 +1,64 @@
+import sys
+import numpy as np
+from matplotlib import pyplot as plt
+import matplotlib.ticker
+import seaborn as sns
+
+plotfile = sys.argv[0].replace('.py', '.pdf')
+
+sns.set_style('white')
+fig, ax = plt.subplots(figsize=(5, 5))
+
+inc = np.linspace(0.0, 0.5*np.pi, 500)
+inc_deg = np.degrees(inc)
+
+Rcs = [1.0, 2.0, 4.0, 8.0]
+Tcs = [-2.0, -1.0, -0.5, 1e-3, 0.5, 1.0, 2.0]
+
+n_Rc = len(Rcs)
+n_Tc = len(Tcs)
+
+lws = np.linspace(1.0, 2.0, n_Rc)
+lss = ['-', '--', ':', '-.']
+alphas = np.linspace(1.0, 0.2, n_Rc)
+cols = sns.color_palette('magma', n_colors=n_Tc)
+
+
+def Rc_dash(inc, Tc, Rc):
+    f = np.sqrt(1.0 + Tc*np.tan(inc)**2)
+    return Rc * (1 + np.tan(inc)**2) / f / (1.0 + Rc*(f - 1.0) / Tc)
+
+for Rc, lw, alpha, ls in list(zip(Rcs, lws, alphas, lss))[::-1]:
+    for Tc, col in list(zip(Tcs, cols))[::-1]:
+        if Rc == 1.0:
+            label = fr'$T_c = {Tc:.1f}$'
+        else:
+            label = None
+        ax.plot(inc_deg, Rc_dash(inc, Tc, Rc),
+                c=col, ls=ls, label=label)
+
+i25, i50, i75 = [90.0 - np.degrees(np.arccos(_)) for _ in [0.25, 0.5, 0.75]]
+
+ax.fill_betweenx([0.0, 100.0], [0.0]*2, [i25]*2, alpha=0.2, color='g')
+ax.fill_betweenx([0.0, 100.0], [i50]*2, [i75]*2, alpha=0.2, color='g')
+ax.legend(ncol=1, fontsize='xx-small', frameon=True)
+ax.set(
+    yscale='linear',
+    xlim=[0.0, 90.0],
+    ylim=[0.0, 10.0],
+    # yticks=[1.0, 2.0, 5.0, 10.0],
+    # yticklabels=['1', '2', '5', '10'],
+    xlabel=r'Inclination, degrees',
[…]

### 2017-02-16 papers/Paper1/sec-conic.tex
Incorporate new figs into paper

@@
 \subsection{Plane-of-sky projection of quadric surfaces}
+
 \begin{figure*}
-\includegraphics[width=0.9\linewidth]{annotated}
-\caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
-the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
-an asymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
-\label{fig:Apqp}
+  \centering
+  \setkeys{Gin}{width=0.45\linewidth}
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics{figs/projected-Rc-vs-i}
+        & \includegraphics{figs/projected-R0-vs-i} \\
+  \end{tabular}
+  \caption[]{Effects of projection on quadrics of revolution.
+    Variation with inclination of characteristic radii.}
+  \label{fig:quadric-projection}
 \end{figure*}
-
 Once the parametrization is done, we can find the apparent shape of

### 2017-02-17 Quadric-shapes/projected-Tc-Rc-snapshots.py
Add the new quadric projection figs to paper

@@ -4,7 +4,7 @@ from matplotlib import pyplot as plt
 import matplotlib.ticker
 import seaborn as sns
 
-plotfile = sys.argv[0].replace('.py', '.pdf')
+plotfile = sys.argv[0].replace('.py', '.png')
 
 sns.set_style('white')
 fig, axes = plt.subplots(3, 3, figsize=(9, 9), sharex=True, sharey=True)
@@ -52,5 +52,5 @@ axes[-1, 0].set(
 )        
 
 fig.tight_layout()
-fig.savefig(plotfile)
+fig.savefig(plotfile, dpi=300)
 print(plotfile, end='')

### 2017-02-23 CRW-shapes/two-quadric-R90-Rc-snapshots.py
Add the new figures into the quadrics section (sec 4)

@@ -32,7 +32,7 @@ for ax, inc_deg in zip(axes.flat, incs_deg):
     ax.axhline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
     ax.axvline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
     ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
-    for xi, col in list(zip(XI_LIST, cols))[::-1]:
+    for xi, col in list(zip(XI_LIST, cols)):
         for beta in betas:
             # Fit to head and analytic fit to fit to tail
             ht = conic_parameters.HeadTail(beta, xi=xi, xmin=0.0, method='analytic fit')

### 2017-02-23 papers/Paper1/sec-thin-shell.tex
Add the new figures to the thin shell section (sec 5)

@@
 
+\subsection{Projection effects in the thin shell model}
+\label{sec:proj-effects-thin}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/two-quadric-R90-vs-Rc}
+  \caption{Diagnostic diagram for thin shell models}
+  \label{fig:thin-shell-R90-Rc}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figs/two-quadric-R90-Rc-snapshots}
+  \caption{Variation with inclination angle of radii diagnostics}
+  \label{fig:thin-shell-R90-Rc-snapshots}
+\end{figure*}
+
 %%% Local Variables:

### 2017-02-23 CRW-shapes/two-quadric-R90-vs-Rc.py

@@ -16,8 +16,13 @@ Rc_grid = np.linspace(0.0, 10.0, 2000)
 R90_T0_grid = np.sqrt(2*Rc_grid)
 R90_T1_grid = np.sqrt(2*Rc_grid - 1.0)
 R90_T1_grid[~np.isfinite(R90_T1_grid)] = 0.0 
-ax.fill_between(Rc_grid, R90_T1_grid, R90_T0_grid, alpha=0.2)
-ax.plot([0.0, 10.0], [0.0, 10.0], ':', c='k')
+
+ax.fill_between(Rc_grid, R90_T1_grid, R90_T0_grid, color='k', alpha=0.2)
+ax.fill_between(Rc_grid, R90_T0_grid, color='k', alpha=0.1)
+ax.plot(Rc_grid, R90_T0_grid, c='k', lw=0.5)
+ax.axhline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
+ax.axvline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
+ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
 
 inc = np.linspace(0.0, 0.5*np.pi, 500, endpoint=False)
 inc_deg = np.degrees(inc)

### 2017-02-24 papers/Paper1/sec-quadrics-observations.tex
Make a start on a new observations section for the paper

\section{Comparison with observations}
\label{sec:comp-with-observ}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figs/annotated-ll-arcs}
  \caption[]{Stationary bow shock arcs in the Orion Nebula}
  \label{fig:ll-arcs}
\end{figure*}

Placing various classes of objects on the \(R_{90}\)--\(R_c\) plane:
\begin{itemize}
\item LL arcs
\item runaway O stars
\item AGB stars
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock.tex"
%%% End:

### 2017-03-06 papers/Paper1/quadrics-appendix.tex
Move appendices to after references
Automatically generate data for table of tail coefficients
This is done in Rc-revisited-2016.org in the section "Write LaTeX
version of the tail analytic fit for paper".  The results are then
pasted into the latex file.
Minor changes:
* Exchange Figures 2 and 3/
* subindices of eqautions A9 and A10 converted to \mathrm
Missing exchanges to tilded Rc and R90
Add a subsection about Wilkin solution section 5

@@
 \appendix
-\appendixpage
-\addappheadtotoc
+% \appendixpage
+% \addappheadtotoc
 \section{Parabola of Revolution}
@@
 \begin{align}
-\left(\frac{q'}{q}\right)_{parabola} &= 1+\frac{A\tan^2 i}{2}\\
-\left(A'\right)_{parabola} &= \frac{A}{\cos^2 i + \frac{A}{2}\sin^2 i}
+\left(\frac{q'}{q}\right)_{\mathrm{parabola}} &= 1+\frac{\tilde{R}_c\tan^2 i}{2}\\
+\left(\tilde{R}'_c\right)_{\mathrm{parabola}} &= \frac{\tilde{R}_c}{\cos^2 i + \frac{\tilde{R}_c}{2}\sin^2 i}
 \end{align}
@@
 
-\section{Analytic derivation of $R_{90}$ in the Thin Shell model}
+\section{Analytic derivation of \texorpdfstring{\boldmath $R_{90}$}{R\_90} in the thin shell model}
 \label{app:r90-analytic}
@@
 \left(1-\xi\beta\right)} \\
-\implies B &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
+\implies \tilde{R}_{90} &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
 {\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
 \end{align}
+
+\section{Derivation of Characteristic Radii in Isotropic Wind/Parallel interaction Problem}
+\label{app:ch-rad-Wilkin}
+
+$\tilde{R}_{90}$ is obtained by simply evaluating equation (\ref{eq:R-Wilkin}) at $\theta=\frac{\pi}{2}$.
+For the Radius of curvature we follow a similar procedure than the Wind/Wind interaction, but using equation
+(\ref{eq:R-Wilkin}) for $R(\theta)$ and inserting the cosecant into the square root.
+
+Expanding the terms of $R(\theta)$ we find the following:
+
+\begin{align}
+  \csc^2\theta &\simeq \theta^{-2}\left[1+\frac{\theta^2}{3}\left(1+\frac{\theta^2}{5}\right)\right] \\
+  1-\theta\cot\theta &\simeq \frac{\theta^2}{3}\left[1 + \frac{\theta^2}{15}\left(1+\frac{2\theta^2}{21}\right)\right] \\
+  \implies \tilde{R}(\theta) \simeq 1 + \frac{\theta^2}{5} + O\left[\theta^4\right]
+\end{align}
+
+From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: quadrics-bowshock
+%%% End:

### 2017-03-06 papers/Paper1/sec-thin-shell.tex
Add a subsection about Wilkin solution section 5

@@
 Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
-conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:thc-conic})
+conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})
 
@@
 
-%Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
+% Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
+%being $R_0$ the
 %easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
@@
 momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
+
+\subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}
+
+This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:
+
+\begin{align}
+  R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
+\end{align}
+Where:
+\begin{align}
+  R_0 = \left(\frac{\dot{M}⁰_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
+\end{align}
+And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
+The characteristic radii are given by:
+\begin{align}
+  \tilde{R}_{90} &= \sqrt{3} \\
+  \tilde{R}_c &= \frac{5}{3}
+\end{align}
+The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}
 

### 2017-03-20 papers/Paper1/sec-quadrics-observations.tex
Initial outline of MIPSGAL section of paper
Just figures so far

@@
 \label{sec:comp-with-observ}
+
+Placing various classes of objects on the \(R_{90}\)--\(R_c\) plane:
+\begin{itemize}
+\item LL arcs
+\item runaway O stars
+\item AGB stars
+\end{itemize}
+
+\subsection{Mid-infrared arcs around early-type stars}
+\label{sec:mid-infrared-arcs}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/mipsgal-r0-r0}
+  \caption[]{Comparison of the bow sock sizes determined from our fits
+    with those given by Kobulnicky for the MIPSGAL sources.}
+  \label{fig:mipsgal-sizes}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
+  \end{tabular}
+  \caption[]{MIPSGAL sources on the bow shock shape diagnostic
+    diagram.  (a) Individual sources.  (b) Kernel density estimate of
+    the distribution.}
+  \label{fig:mipsgal-shapes}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figs/mipsgal-pairplot}
+  \caption[]{Correlations between non-shape parameters of MIPSGAL sources.}
+  \label{fig:mipsgal-pairplot}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
+  \end{tabular}
+  \caption[]{Significant correlation of bow shock shape with (a) bow
+    shock angular size, and (b) extinction-corrected magnitude of
+    stellar source.}
+  \label{fig:mipsgal-correlated}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
+  \end{tabular}
+  \caption[]{Lack of significant correlation of bow shock shape with
+    (a) environment, and (b) uncertainty in stellar source
+    identification.}
+  \label{fig:mipsgal-uncorrelated}
+\end{figure*}
+
+\subsection{Far-infrared arcs around late-type stars}
+\label{sec:far-infrared-arcs}
+
+\subsection{Stationary emission line arcs in M42}
+\label{sec:stat-emiss-line}
 
@@
 
-Placing various classes of objects on the \(R_{90}\)--\(R_c\) plane:
-\begin{itemize}
-\item LL arcs
-\item runaway O stars
-\item AGB stars
-\end{itemize}
-
 %%% Local Variables:

### 2017-03-21 papers/Paper1/sec-quadrics-observations.tex
Add figures for arc fits to MIPSGAL sources

@@
 \begin{figure}
+  (a)\\
+  \includegraphics[width=\linewidth]{figs/0510-3-star}
+  (b)\\
+  \includegraphics[width=\linewidth]{figs/0506-4-star}
+  (c)\\
+  \includegraphics[width=\linewidth]{figs/0517-5-star}
+  \caption[]{Examples of fits to the bow shock shapes of MIPSGAL sources.}
+  \label{fig:mipsgal-examples}
+\end{figure}
+
+\begin{figure}
   \centering
   \includegraphics[width=\linewidth]{figs/mipsgal-r0-r0}
-  \caption[]{Comparison of the bow sock sizes determined from our fits
+  \caption[]{Comparison of the bow shock sizes determined from our fits
     with those given by Kobulnicky for the MIPSGAL sources.}

### 2017-03-21 LL-shapes-2017/new-observed-R90-vs-Rc.py
Compare LL arcs with OB arcs

@@ -23,7 +23,7 @@ Rcols = [_ for _ in cols if _.startswith('R')]
 
 for table in table_LL, table_RSG:
     for col in Rcols:
-        if col in table:
+        if col in table.colnames:
             m = table[col] < 0.0
             table[col][m] = np.nan
 
@@ -32,6 +32,9 @@ for table in table_LL, table_RSG:
     table['R90'] = np.nanmean(R90stack, axis=0)
     table['dR90'] = np.nanstd(R90stack, axis=0)
     table.remove_columns(['R90 out', 'Rm90 out'])
+
+table_LL.write('ll-arcs-radii.tab', overwrite=True, format='ascii.tab')
+table_RSG.write('rsg-arcs-radii.tab', overwrite=True, format='ascii.tab')
 
 plotfile = sys.argv[0].replace('.py', '.pdf')
 

### 2017-03-21 papers/Paper1/quadrics-appendix.tex
Add Herschel comparison figure and p-value test

@@
 
+\section{Distribution of p-values for all correlations tested}
+\label{sec:distr-p-values}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/p-value-histogram}
+  \caption{Histogram of \(p\)-values for all Anderson--Darling
+    non-parametric 2-sample tests performed during the analysis of
+    section~\ref{sec:comp-with-observ}.  The vertical dashed line
+    shows the traditional threshold value for significance:
+    \(p = 0.05\). The red solid line shows the expected distribution
+    of \(p\)-values that would be obtained if no significant
+    correlations existed.}
+  \label{fig:histo-p-values}
+\end{figure}
+
+All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).
+It is therefore important to guard against the ``multiple comparisons problem'', whereby seemingly significant correlations are found where none really exist, simply by virtue of the large number of tests that were carried out.
+
+Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: quadrics-bowshock
+%%% TeX-master: "quadrics-bowshock.tex"
 %%% End:

### 2017-03-21 papers/Paper1/sec-quadrics-observations.tex
Compare LL arcs with OB arcs
Add Herschel comparison figure and p-value test

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
+  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.}
+  \label{fig:herschel-compare-mipsgal}
+\end{figure}
+
 \subsection{Stationary emission line arcs in M42}
@@
   \includegraphics[width=\textwidth]{figs/annotated-ll-arcs}
-  \caption[]{Stationary bow shock arcs in the Orion Nebula}
+  \caption[]{Stationary bow shock arcs in the Orion Nebula.}
   \label{fig:ll-arcs}
 \end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
+  \caption[]{Comparison of Orion with OB stars.}
+  \label{fig:ll-compare-mipsgal}
+\end{figure}
 

### 2017-03-24 papers/Paper1/sec-quadrics-observations.tex
Start empirical description of OB star bow shocks
Finish figure caption.  Describe data set.  Add the delta PA histogram
as an inset to the R0-R0 plot

@@
+\newcommand\hii{\ion{H}{ii}}
+
 \section{Comparison with observations}
@@
 
-\begin{figure}
-  (a)\\
-  \includegraphics[width=\linewidth]{figs/0510-3-star}
-  (b)\\
-  \includegraphics[width=\linewidth]{figs/0506-4-star}
-  (c)\\
-  \includegraphics[width=\linewidth]{figs/0517-5-star}
-  \caption[]{Examples of fits to the bow shock shapes of MIPSGAL sources.}
+The most extensive sample of stellar bow shock nebulae to date is a
+catalog of 709 arcs \citep{Kobulnicky:2016a} detected in mid-infrared
+surveys of the Galactic Plane by the \textit{Spitzer Space Telescope}
+(\textit{SST}, \citealp{Werner:2004a}) and \textit{Wide-field Infrared
+  Survey Explorer} (\textit{WISE}, \citealp{Wright:2010a}).  These
+sources are believed to be powered by the winds of early-type stars,
+which are either moving supersonically through the interstellar medium
+(runaway stars), or are interacting with a local bulk flow, such as
+the champagne flow from a nearby \hii{} region.
+
+\begin{figure*}
+  \setlength\tabcolsep{0pt}
+  \begin{tabular}{ll}
+    (a)
+    & (b) \\
+    \includegraphics
+    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0510-3-star}
+    & \includegraphics
+      [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0506-4-star} \\
+    (c)
+    & (d) \\
+    \includegraphics
+    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0517-5-star}
+    & \multicolumn{1}{c}
+      {\includegraphics[width=0.35\linewidth, trim=20 20 60 60]
+      {figs/mipsgal-r0-r0-plus-dPA-edited}}
+  \end{tabular}
+  \caption[]{Examples of typical fits to the bow shock shapes of
+    MIPSGAL sources with different star ratings: (a) K510, 3-star
+    rating; (b) K506, 4-star rating; (c) K517, 5-star rating.  Right
+    panels of parts (a)--(c) show a 4\('\) square \SI{24}{\um} image,
+    centered on each source.  Contours are ten linearly spaced levels
+    between the median brightness of the entire image and the maximum
+    brightness of the bow shock arc. Grids of galactic coordinates
+    (light blue lines, parallel to the box sides) and equatorial
+    coordinates (tilted magenta lines) are shown.  The stellar source
+    and the bow shock axis, as determined by \citet{Kobulnicky:2016a}
+    are indicated by an orange star and an orange line, respectively,
+    where the line extends from \(-2 R_0\) to \(+2 R_0\).  The
+    automatically traced arc shapes using the ``mean'' and ``peak''
+    methods (see text) are shown by blue and red dots, respectively.
+    The magenta circle shows the fit to the arc points within
+    \(\pm 45^\circ\) of the nominal bowshock axis, with the magenta dot
+    showing the center of curvature and the magenta line showing the
+    fitted bow shock axis, which is the line passing through the
+    source and the center of curvature.  Left panels of parts (a)--(c)
+    show the radius measured from the source (upper panel) and
+    brightness (lower panel) of the arc points, plotted as a function
+    of angle \(\theta\) from the nominal bow shock axis, and with the same
+    color coding as used on the image. Angular ranges of
+    \(\theta = \pm 45\degr\) and \(\pm 90\degr\) are shown by gray shaded
+    boxes In the upper panel, the \(R_0\) value tabulated by
+    \citet{Kobulnicky:2016a} is shown by a horizontal blue line. (d)
+    Comparison of the bow shock sizes (scatter plot) and position
+    angles (inset histograms) determined from our fits with those
+    tabulated by \citet{Kobulnicky:2016a} for the MIPSGAL sources.}
   \label{fig:mipsgal-examples}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/mipsgal-r0-r0}
-  \caption[]{Comparison of the bow shock sizes determined from our fits
-    with those given by Kobulnicky for the MIPSGAL sources.}
-  \label{fig:mipsgal-sizes}
-\end{figure}
+\end{figure*}
 
@@
   \end{tabular}
-  \caption[]{Significant correlation of bow shock shape with (a) bow
-    shock angular size, and (b) extinction-corrected magnitude of
-    stellar source.}
+  \caption[]{Comparison between the distribution of bowshock shapes
+    when the sources are divided into two sub-samples according to the
+    value of another parameter. (a)~Bow shock angular size, \(R_0\).
+    (b)~Extinction-corrected \(H\)-band magnitude of the stellar
+    source.}
   \label{fig:mipsgal-correlated}

### 2017-03-24 papers/Paper1/sec-quadrics-observations.tex
Describe bow shock tracing algorithm

@@
 the champagne flow from a nearby \hii{} region.
+
+In order to study the shapes of these bow shocks, we downloaded data
+from the NASA/IPAC Infrared Science Archive archive\footnote{
+  \url{http://irsa.ipac.caltech.edu/docs/program_interface/api_images.html}}
+and extracted 4\arcmin{} square images in the \SI{24}{\um} bandpass of
+the Multiband Imaging Photometer for \textit{Spitzer} (MIPS) centered
+on each of the 471 \citet{Kobulnicky:2016a} sources that are covered
+by the MIPSGAL \citep{Carey:2009a} survey, which includes most of the
+sources with Galactic longitude within \(\pm 60\degr\) of the Galactic
+center.
+
+We developed a methodology for automatically tracing the arcs as follows:
+\begin{enumerate}[1.]
+\item Calculate arrays of celestial coordinates, \(C\), for each pixel
+  of the image.
+\item Using the central source coordinates, \(C_0\) and nominal
+  bowshock radius, \(R_0\) from \citet{Kobulnicky:2016a}, construct a
+  pixel mask that includes only those pixels with separations
+  \(|C - C_0|\) from the source that lie between \(0.5 R_0\) and
+  \(3 R_0\).  This mask will be used for all subsequent operations,
+  which serves to help avoid confusion from the star itself and other
+  bright sources in the field of view.
+\item Define a ``step-back'' point, \(C_1\), which is located at a
+  separation \(2 R_0\) from the source, but in the opposite direction
+  from the apex of the bow shock. That is, along a position angle
+  180\degr{} from the nominal position angle, \(\text{PA}_0\), of
+  the bow shock axis.
+\item Looping over a grid of 50 position angles, \(\text{PA}_k\), within
+  \(\pm 60\degr\) of \(\text{PA}_0\), estimate the location of the
+  arc along each PA from the step-back point via two different methods:
+  \begin{enumerate}[(a)]
+  \item The pixel with the maximum brightness, with coordinates
+    \(C_{k,\text{peak}}\) (red dots in
+    Fig.~\ref{fig:mipsgal-examples}).
+  \item The mean brightness-weighted separation from \(C_1\), with
+    coordinates \(C_{k,\text{mean}}\) (light blue dots in
+    Fig.~\ref{fig:mipsgal-examples}).
+  \end{enumerate}
+  For each \(\text{PA}_k\) in the grid, the calculation is performed
+  over only those pixels that satisfy
+  \(|\text{PA}(C, C_1) - \text{PA}_k| < \frac12 \delta\theta\), where
+  \(\delta\theta = 120/50 = 2.4\degr\), which defines a thin radial wedge from
+  \(C_1\).
+\item For each of the points \(C_{k,\text{peak}}\) and \(C_{k,\text{mean}}\), determine the separation from the central source, \(R_k = |C_k - C_0|\) and the angle from the bow shock axis about the central source \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\)
+
+\end{enumerate}
 

### 2017-03-27 papers/Paper1/sec-quadrics-observations.tex
Add a couple of \clearpage commands
Before observation section and before conclusion, so that the figures
stay closer to the text that describes them.  We can remove them again
later when we have some more text

@@
   \(C_1\).
-\item For each of the points \(C_{k,\text{peak}}\) and \(C_{k,\text{mean}}\), determine the separation from the central source, \(R_k = |C_k - C_0|\) and the angle from the bow shock axis about the central source \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\)
+\item For each of the points \(C_{k,\text{peak}}\) and \(C_{k,\text{mean}}\), determine the radial separation from the central source, \(R_k = |C_k - C_0|\) and the angle from the bow shock axis about the central source \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\).
+These are plotted in the upper left panels of  Figure~\ref{fig:mipsgal-examples}.
 

### 2017-03-27 papers/Paper1/sec-quadrics-observations.tex
Describe star rating system

@@
 
-The most extensive sample of stellar bow shock nebulae to date is a
-catalog of 709 arcs \citep{Kobulnicky:2016a} detected in mid-infrared
-surveys of the Galactic Plane by the \textit{Spitzer Space Telescope}
-(\textit{SST}, \citealp{Werner:2004a}) and \textit{Wide-field Infrared
-  Survey Explorer} (\textit{WISE}, \citealp{Wright:2010a}).  These
-sources are believed to be powered by the winds of early-type stars,
-which are either moving supersonically through the interstellar medium
-(runaway stars), or are interacting with a local bulk flow, such as
-the champagne flow from a nearby \hii{} region.
+The most extensive observational sample of stellar bow shock nebulae
+to date is a catalog of 709 arcs \citep{Kobulnicky:2016a} detected in
+mid-infrared surveys of the Galactic Plane by the \textit{Spitzer
+  Space Telescope} (\textit{SST}, \citealp{Werner:2004a}) and
+\textit{Wide-field Infrared Survey Explorer} (\textit{WISE},
+\citealp{Wright:2010a}).  These sources are believed to be powered by
+the winds of early-type stars, which are either moving supersonically
+through the interstellar medium (runaway stars), or are interacting
+with a local bulk flow, such as the champagne flow from a nearby
+\hii{} region.
 
@@
   bowshock radius, \(R_0\) from \citet{Kobulnicky:2016a}, construct a
-  pixel mask that includes only those pixels with separations
-  \(|C - C_0|\) from the source that lie between \(0.5 R_0\) and
-  \(3 R_0\).  This mask will be used for all subsequent operations,
-  which serves to help avoid confusion from the star itself and other
-  bright sources in the field of view.
+  pixel mask that includes only those pixels with separations from the
+  source that satisfy \(\frac12 R_0 \le |C - C_0| \le 3 R_0\).  This mask
+  will be used for all subsequent operations, which serves to help
+  avoid confusion from the star itself and other bright sources in the
+  field of view.
 \item Define a ``step-back'' point, \(C_1\), which is located at a
@@
   \(\delta\theta = 120/50 = 2.4\degr\), which defines a thin radial wedge from
-  \(C_1\).
-\item For each of the points \(C_{k,\text{peak}}\) and \(C_{k,\text{mean}}\), determine the radial separation from the central source, \(R_k = |C_k - C_0|\) and the angle from the bow shock axis about the central source \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\).
-These are plotted in the upper left panels of  Figure~\ref{fig:mipsgal-examples}.
+  \(C_1\).  The results are shown as red and blue dots superimposed
+  on the images in Figure~\ref{fig:mipsgal-examples}. Each of the two
+  methods, ``peak'' and ``mean'', works better in some objects and
+  worse in others (according to the subjective judgment of
+  ``correctly'' tracing the bow shock shape).  We therefore take the
+  average by amalgamating all the \(C_{k,\text{peak}}\) and
+  \(C_{k,\text{mean}}\) points into a single set, \(C_{k}\), for
+  subsequent analysis.
+\item For each of the points \(C_{k}\), determine the radial
+  separation from the central source, \(R_k = |C_k - C_0|\) and the
+  angle from the bow shock axis about the central source
+  \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\).  These are plotted in
+  the upper left panels of Figure~\ref{fig:mipsgal-examples}.
+\item Make our own estimate of the axial size, \(R_0\), of the bow
+  shock by calculating the mean and standard deviation of \(R_k\) over
+  all points \(C_k\) with \(|\theta_k| \le 10\degr\).  Note that this is
+  distinct from the nominal value of \(R_0\) given in the
+  \citet{Kobulnicky:2016a} catalog, which was ``measured by eye''.
+\item Estimate the radius of curvature, \(R_c\), by fitting a circle
+  to all those points within \(\pm 45\degr\) of the nominal axis
+  (\(|\theta_k| < 45\degr\)), but after excluding any point with
+  \(R_k < \frac12 R_m\) or \(R_k > 2 R_m\), where \(R_m\) is the median
+  \(R_k\) for \(|\theta_k| < 45\degr\).
+\item Determine two separate estimates, \(R_{90+}\) and \(R_{90-}\),
+  of the perpendicular radius, \(R_{90}\), by taking the mean and
+  standard deviation of \(R_k\) over all points \(C_k\) with
+  \(|\theta_k - 90\degr| \le 10\degr\) for \(R_{90+}\), and with
+  \(|\theta_k + 90\degr| \le 10\degr\) for \(R_{90-}\).
+\end{enumerate}
 
-\end{enumerate}
+After these automatic steps, we subjectively evaluate the results by giving a star rating to each source:
+
+\paragraph*{0 stars} The fitting algorithm failed for some reason.
+
+\paragraph*{1 star} The fit was formally successful, but the results
+for \(R_c\) or \(R_{90}\) are far removed from what a human would
+predict by looking at the image.  For example, in the smallest
+bowshocks, which are only marginally resolved by Spitzer's 6\arcsec{}
+beam, the dispersion in \(R_k\) can be a significant fraction of
+\(R_0\), in which case our algorithm tends to erroneously favor
+\(R_c < R_0\).
+
+\paragraph*{2 stars} The fit results are not totally outlandish, but
+nonetheless some problem is apparent that casts doubt on the
+reliability of the results.  For example, a double-shell structure to
+the bow shock that leads to large differences between the ``peak'' and
+``mean'' methods, or point sources near to the bow shock that
+interfere with the tracing procedure.
+
+\paragraph*{3 stars} A good fit, but where the dispersion in \(R_k\)
+and/or the asymmetry in the bow shock reduces the precision in the
+determination of \(R_c\) and \(R_{90}\), giving subjectively estimated
+uncertainties around the 20\% level.  An example of a 3-star fit is
+shown in Figure~\ref{fig:mipsgal-examples}a.
+
+\paragraph*{4 stars} A high quality fit, with subjectively estimated
+uncertainties in \(R_c\) and \(R_{90}\) around the 10\% level. An
+example of a 4-star fit is shown in
+Figure~\ref{fig:mipsgal-examples}b.
+
+\paragraph*{5 stars} The highest-quality fit, usually corresponding to
+large, sharply defined bow shocks, whose shape is determined with high
+precision. An example of a 5-star fit is shown in
+Figure~\ref{fig:mipsgal-examples}c.
+
+\bigskip
+Only sources with a 3-star or higher rating are used in the following analysis, which amount to approximately half (227 out of 471) of all the MIPSGAL arc sources.
 

### 2017-03-27 papers/Paper1/sec-quadrics-observations.tex
Add citations for runaways and weather vanes

@@
 the winds of early-type stars, which are either moving supersonically
-through the interstellar medium (runaway stars), or are interacting
-with a local bulk flow, such as the champagne flow from a nearby
-\hii{} region.
+through the interstellar medium (runaway stars,
+\citealp{Gvaramadze:2008a}), or are interacting with a local bulk
+flow, such as the champagne flow from a nearby \hii{} region (weather
+vanes, \citealp{Povich:2008a}).
 
@@
 \paragraph*{2 stars} The fit results are not totally outlandish, but
-nonetheless some problem is apparent that casts doubt on the
-reliability of the results.  For example, a double-shell structure to
-the bow shock that leads to large differences between the ``peak'' and
-``mean'' methods, or point sources near to the bow shock that
-interfere with the tracing procedure.
+nonetheless some problem is apparent that casts doubt on their
+reliability.  For example, a double-shell structure to the bow shock
+that leads to large differences between the ``peak'' and ``mean''
+methods, or point sources near to the bow shock that interfere with
+the tracing procedure.
 

### 2017-03-28 papers/Paper1/sec-quadrics-observations.tex
Add 1 and 2 star sources to R0-R0 graph

@@
 \bigskip
-Only sources with a 3-star or higher rating are used in the following analysis, which amount to approximately half (227 out of 471) of all the MIPSGAL arc sources.
+Only sources with a 3-star or higher rating are used in the following analysis, which comprise approximately half (227 out of 471) of all the MIPSGAL arc sources.
+In some cases of poor and failed fits, there is nothing apparently ``wrong'' with the source itself, and it is likely that minor tweaks to the methodology would improve matters.
+But we have elected not to do so, in order to maintain a uniform methodology across all sources.
+
+Figure~\ref{fig:mipsgal-examples}d compares the bow shock size,
+\(R_0\), determined by our fits (vertical axis) with the corresponding
+value given in the \citet{Kobulnicky:2016a} catalog (horizontal axis).
+For most sources with 3-star or higher rating, the two estimates agree
+to within \(\pm 20\%\), but there are a small number of sources with a
+discrepancy of more than a factor of two.  In all cases that we
+checked, we believe that our estimates of \(R_0\) are more accurate
+than those in the catalog.
 

### 2017-03-28 papers/Paper1/sec-quadrics-observations.tex
Cleaning up star rating description

@@
 \label{sec:mid-infrared-arcs}
+
+\begin{figure*}
+  \setlength\tabcolsep{0pt}
+  \begin{tabular}{ll}
+    (a)
+    & (b) \\
+    \includegraphics
+    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0510-3-star}
+    & \includegraphics
+      [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0506-4-star} \\
+    (c)
+    & (d) \\
+    \includegraphics
+    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0517-5-star}
+    & \multicolumn{1}{c}
+      {\includegraphics[width=0.35\linewidth, trim=20 20 20 20]
+      {figs/mipsgal-r0-r0-plus-dPA-edited}}
+  \end{tabular}
+  \caption[]{Examples of typical fits to the bow shock shapes of
+    MIPSGAL sources with different star ratings: (a) K510, 3-star
+    rating; (b) K506, 4-star rating; (c) K517, 5-star rating.  Right
+    panels of parts (a)--(c) show a 4\('\) square \SI{24}{\um} image,
+    centered on each source.  Contours are ten linearly spaced levels
+    between the median brightness of the entire image and the maximum
+    brightness of the bow shock arc. Grids of galactic coordinates
+    (light blue lines, parallel to the box sides) and equatorial
+    coordinates (tilted magenta lines) are shown.  The stellar source
+    and the bow shock axis, as determined by \citet{Kobulnicky:2016a}
+    are indicated by an orange star and an orange line, respectively,
+    where the line extends from \(-2 R_0\) to \(+2 R_0\).  The
+    automatically traced arc shapes using the ``mean'' and ``peak''
+    methods (see text) are shown by blue and red dots, respectively.
+    The magenta circle shows the fit to the arc points within
+    \(\pm 45^\circ\) of the nominal bowshock axis, with the magenta dot
+    showing the center of curvature and the magenta line showing the
+    fitted bow shock axis, which is the line passing through the
+    source and the center of curvature.  Left panels of parts (a)--(c)
+    show the radius measured from the source (upper panel) and
+    brightness (lower panel) of the arc points, plotted as a function
+    of angle \(\theta\) from the nominal bow shock axis, and with the same
+    color coding as used on the image. Angular ranges of
+    \(\theta = \pm 45\degr\) and \(\pm 90\degr\) are shown by gray shaded
+    boxes In the upper panel, the \(R_0\) value tabulated by
+    \citet{Kobulnicky:2016a} is shown by a horizontal blue line. (d)
+    Comparison of the bow shock sizes (scatter plot) and position
+    angles (inset histograms) determined from our fits with those
+    tabulated by \citet{Kobulnicky:2016a} for the MIPSGAL sources.}
+  \label{fig:mipsgal-examples}
+\end{figure*}
 
@@
   from the apex of the bow shock. That is, along a position angle
-  180\degr{} from the nominal position angle, \(\text{PA}_0\), of
-  the bow shock axis.
-\item Looping over a grid of 50 position angles, \(\text{PA}_k\), within
-  \(\pm 60\degr\) of \(\text{PA}_0\), estimate the location of the
-  arc along each PA from the step-back point via two different methods:
+  180\degr{} from the nominal position angle, \(\text{PA}_0\), of the
+  bow shock axis.  This point is at one end of the orange line shown
+  superimposed on the bow shock images in
+  Figure~\ref{fig:mipsgal-examples}.
+\item Looping over a grid of 50 position angles, \(\text{PA}_k\),
+  within \(\pm 60\degr\) of \(\text{PA}_0\), estimate the location of
+  the arc along rays cast from the step-back point, using two
+  different methods:
   \begin{enumerate}[(a)]
-  \item The pixel with the maximum brightness, with coordinates
+  \item The pixel with the peak brightness, with coordinates
     \(C_{k,\text{peak}}\) (red dots in
@@
   \(C_{k,\text{mean}}\) points into a single set, \(C_{k}\), for
-  subsequent analysis.
+  the following steps.
 \item For each of the points \(C_{k}\), determine the radial
@@
   \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\).  These are plotted in
-  the upper left panels of Figure~\ref{fig:mipsgal-examples}.
+  the upper left panels of Figure~\ref{fig:mipsgal-examples}.  Note
+  that, even though the rays are cast from the step-back point \(C_1\)
+  within \(\pm 60\degr\) of \(\text{PA}_0\), the angles \(\theta_k\) are
+  measured from the source, \(C_0\), which is closer to the bow shock
+  than \(C_1\) and therefore \(|\theta_k|\) can be much larger than
+  \(60\degr\).
 \item Make our own estimate of the axial size, \(R_0\), of the bow
@@
 \bigskip
-Only sources with a 3-star or higher rating are used in the following analysis, which comprise approximately half (227 out of 471) of all the MIPSGAL arc sources.
-In some cases of poor and failed fits, there is nothing apparently ``wrong'' with the source itself, and it is likely that minor tweaks to the methodology would improve matters.
-But we have elected not to do so, in order to maintain a uniform methodology across all sources.
-
+%
 Figure~\ref{fig:mipsgal-examples}d compares the bow shock size,
@@
 checked, we believe that our estimates of \(R_0\) are more accurate
-than those in the catalog.
+than those in the catalog.  It is apparent that the star ratings are
+correlated with the bow shock size, with larger bow shocks tending to
+receive higher ratings, although there is considerable overlap.  In
+particular, most of the 1- and 2-star sources are close to the
+resolution limit of the MIPSGAL \SI{24}{\um} images (\(6\arcsec\),
+indicated by the dotted horizontal line in te figure).
 
-\begin{figure*}
-  \setlength\tabcolsep{0pt}
-  \begin{tabular}{ll}
-    (a)
-    & (b) \\
-    \includegraphics
-    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0510-3-star}
-    & \includegraphics
-      [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0506-4-star} \\
-    (c)
-    & (d) \\
-    \includegraphics
-    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0517-5-star}
-    & \multicolumn{1}{c}
-      {\includegraphics[width=0.35\linewidth, trim=20 20 60 60]
-      {figs/mipsgal-r0-r0-plus-dPA-edited}}
-  \end{tabular}
-  \caption[]{Examples of typical fits to the bow shock shapes of
-    MIPSGAL sources with different star ratings: (a) K510, 3-star
-    rating; (b) K506, 4-star rating; (c) K517, 5-star rating.  Right
-    panels of parts (a)--(c) show a 4\('\) square \SI{24}{\um} image,
-    centered on each source.  Contours are ten linearly spaced levels
-    between the median brightness of the entire image and the maximum
-    brightness of the bow shock arc. Grids of galactic coordinates
-    (light blue lines, parallel to the box sides) and equatorial
-    coordinates (tilted magenta lines) are shown.  The stellar source
-    and the bow shock axis, as determined by \citet{Kobulnicky:2016a}
-    are indicated by an orange star and an orange line, respectively,
-    where the line extends from \(-2 R_0\) to \(+2 R_0\).  The
-    automatically traced arc shapes using the ``mean'' and ``peak''
-    methods (see text) are shown by blue and red dots, respectively.
-    The magenta circle shows the fit to the arc points within
-    \(\pm 45^\circ\) of the nominal bowshock axis, with the magenta dot
-    showing the center of curvature and the magenta line showing the
-    fitted bow shock axis, which is the line passing through the
-    source and the center of curvature.  Left panels of parts (a)--(c)
-    show the radius measured from the source (upper panel) and
-    brightness (lower panel) of the arc points, plotted as a function
-    of angle \(\theta\) from the nominal bow shock axis, and with the same
-    color coding as used on the image. Angular ranges of
-    \(\theta = \pm 45\degr\) and \(\pm 90\degr\) are shown by gray shaded
-    boxes In the upper panel, the \(R_0\) value tabulated by
-    \citet{Kobulnicky:2016a} is shown by a horizontal blue line. (d)
-    Comparison of the bow shock sizes (scatter plot) and position
-    angles (inset histograms) determined from our fits with those
-    tabulated by \citet{Kobulnicky:2016a} for the MIPSGAL sources.}
-  \label{fig:mipsgal-examples}
-\end{figure*}
+In the following analysis, only those sources with a 3-star or higher
+rating are used.  These comprise approximately half (227 out of 471)
+of all the MIPSGAL arc sources.  In some cases of poor and failed
+fits, there is nothing apparently ``wrong'' with the source itself,
+and it is likely that minor tweaks to the methodology would improve
+matters, but we have elected not to do so, in order to maintain a
+uniform methodology across all sources.
+
+The inset of Figure~\ref{fig:mipsgal-examples}d shows histograms of the difference between the position angle determined by our fits and that listed in \citet{Kobulnicky:2016a}.
 

### 2017-03-28 papers/Paper1/sec-quadrics-observations.tex
Finish documenting the OB arc tracing, fitting, and rating

@@
     angles (inset histograms) determined from our fits with those
-    tabulated by \citet{Kobulnicky:2016a} for the MIPSGAL sources.}
+    tabulated by \citet{Kobulnicky:2016a} for the MIPSGAL sources.
+    The horizontal dotted line on the main plot shows the MIPS
+    \SI{24}{\um} point spread function FWHM of \(5.5\arcsec\).  The
+    standard deviation (s.d.) of the position angle differences is
+    shown on each inset histogram.}
   \label{fig:mipsgal-examples}
@@
 
-The inset of Figure~\ref{fig:mipsgal-examples}d shows histograms of the difference between the position angle determined by our fits and that listed in \citet{Kobulnicky:2016a}.
+The inset of Figure~\ref{fig:mipsgal-examples}d shows histograms of
+the difference between the position angle, \(\text{PA}_0\) determined
+by our fits and that listed in \citet{Kobulnicky:2016a}.  Although
+observational uncertainties undoubtedly contribute in part, the
+differences are mainly due to real asymmetries in the bow shocks,
+especially for the 4- and 5-star sources.  The
+\citeauthor{Kobulnicky:2016a} catalog \(\text{PA}_0\) values are
+mostly sensitive to the orientation of the bow shock wings, whereas
+our fitted \(\text{PA}_0\) values are determined by the point in the
+bow shock head that is closest to the stellar source.  For this
+reason, we use the catalog \(\text{PA}_0\) values for defining the
+axis when measuring \(R_{90+}\) and \(R_{90-}\). On the other hand,
+the fitted values of \(\text{PA}_0\) are better correlated with the
+position of the bow shock's brightness peak, as is apparent in the
+lower left panels of Figure~\ref{fig:mipsgal-examples}a and c.
 

### 2017-03-28 papers/Paper1/sec-quadrics-observations.tex
Finish Figure 19 and caption: Rc-R90 plane for OB bow shocks

@@
     (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom-annotated} &
     \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
   \end{tabular}
-  \caption[]{MIPSGAL sources on the bow shock shape diagnostic
-    diagram.  (a) Individual sources.  (b) Kernel density estimate of
-    the distribution.}
+  \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
+    of dimensionless radius of curvature versus perpendicular radius.
+    (a) Individual sources with bow shock fit quality rating of 3-star
+    or above.  All 5-star sources plus those 4-star sources with
+    \(R_c/R_0 < 1\) are labelled with their \cite{Kobulnicky:2016a}
+    catalog number.  Horizontal error bars do not directly reflect the
+    uncertainty in \(R_c/R_0\) but are instead simply the standard
+    deviation from the circle fit of bowshock points \(R_k\) within
+    \(\pm 45\degr\) of the axis.  Values on the vertical axis
+    represent the average of \(R_{90+}\) and \(R_{90-}\), with thin
+    vertical error bars showing the difference between \(R_{90+}\) and
+    \(R_{90-}\), and thick vertical error bars showing the rms
+    dispersion of \(R_k\) about these values for bow shock points
+    within \(\pm 10\degr\) of the \(+90\degr\) and \(-90\degr\)
+    directions.  (b) Kernel density estimate of the distribution for
+    3-star sources (blue, filled contours) and 4- plus 5-star sources
+    (orange/brown, unfilled contours).  Images of representative 4-
+    and 5-star sources at different points on the \(R_c\)--\(R_{90}\)
+    plane are also shown.}
   \label{fig:mipsgal-shapes}

### 2017-03-30 papers/Paper1/sec-quadrics-observations.tex
Discussion of Figure 19

@@
 
+\begin{figure*}
+  \centering
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom-annotated} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
+  \end{tabular}
+  \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
+    of dimensionless radius of curvature versus perpendicular radius.
+    The regions corresponding to different classes of cuadrics are
+    shown by shading (see \S~\ref{sec:conic}): oblate spheroids (light
+    gray background); prolate spheroids (darker gray background);
+    paraboloids (curved black line); hyperboloids (white background).
+    (a) Individual sources with bow shock fit quality rating of 3-star
+    or above.  All 5-star sources plus those 4-star sources with
+    \(R_c/R_0 < 1\) are labelled with their \cite{Kobulnicky:2016a}
+    catalog number.  Horizontal error bars do not directly reflect the
+    uncertainty in \(R_c/R_0\) but are instead simply the standard
+    deviation from the circle fit of bowshock points \(R_k\) within
+    \(\pm 45\degr\) of the axis.  Values on the vertical axis
+    represent the average of \(R_{90+}\) and \(R_{90-}\), with thin
+    vertical error bars showing the difference between \(R_{90+}\) and
+    \(R_{90-}\), and thick vertical error bars showing the rms
+    dispersion of \(R_k\) about these values for bow shock points
+    within \(\pm 10\degr\) of the \(+90\degr\) and \(-90\degr\)
+    directions.  (b) Kernel density estimator (KDE) of the
+    distribution for 3-star sources (blue, filled contours) and 4-
+    plus 5-star sources (orange/brown, unfilled contours).  The KDE
+    uses an anisotropic gaussian kernel with bandwidths of
+    \(0.18 \times 0.12\). Images of representative 4- and 5-star sources at
+    different points on the \(R_c\)--\(R_{90}\) plane are also shown.}
+  \label{fig:mipsgal-shapes}
+\end{figure*}
+
 In the following analysis, only those sources with a 3-star or higher
@@
 
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom-annotated} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
-  \end{tabular}
-  \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
-    of dimensionless radius of curvature versus perpendicular radius.
-    (a) Individual sources with bow shock fit quality rating of 3-star
-    or above.  All 5-star sources plus those 4-star sources with
-    \(R_c/R_0 < 1\) are labelled with their \cite{Kobulnicky:2016a}
-    catalog number.  Horizontal error bars do not directly reflect the
-    uncertainty in \(R_c/R_0\) but are instead simply the standard
-    deviation from the circle fit of bowshock points \(R_k\) within
-    \(\pm 45\degr\) of the axis.  Values on the vertical axis
-    represent the average of \(R_{90+}\) and \(R_{90-}\), with thin
-    vertical error bars showing the difference between \(R_{90+}\) and
-    \(R_{90-}\), and thick vertical error bars showing the rms
-    dispersion of \(R_k\) about these values for bow shock points
-    within \(\pm 10\degr\) of the \(+90\degr\) and \(-90\degr\)
-    directions.  (b) Kernel density estimate of the distribution for
-    3-star sources (blue, filled contours) and 4- plus 5-star sources
-    (orange/brown, unfilled contours).  Images of representative 4-
-    and 5-star sources at different points on the \(R_c\)--\(R_{90}\)
-    plane are also shown.}
-  \label{fig:mipsgal-shapes}
-\end{figure*}
+The derived bowshock shapes of all the 3-, 4-, and 5-star sources are
+shown in Figure~\ref{fig:mipsgal-shapes} on the plane of \(R_c/R_0\)
+versus \(R_{90} / R_0\).  Panel a shows the individual points
+superimposed on the theoretical results for quadrics of revolution
+(see figure caption and \S~\ref{sec:conic}), while panel b shows
+contours of the kernel density estimator (KDE, see
+\citealp{Leiva-Murillo:2012a, Scott:2015a}) of the two-dimensional
+distribution of points on the \(R_c\)--\(R_{90}\) plane.  The
+horizontal axis corresponds to the shape of the head of the bow shock
+near its apex, ranging from sharper, pointier shapes with
+\(R_c/R_0 < 1\) to flatter, snubber shapes with \(R_c/R_0 \gg 1\), where
+it must be understood that all judgments of sharpness/flatness are
+with respect to the axial separation, \(R_0\), between the source and
+the bow shock apex.  The vertical axis corresponds to the shape of the
+bow shock wings, ranging from closed ``C'' shapes for smaller values
+of \(R_{90} / R_0\) to open ``V'' shapes for larger values of
+\(R_{90} / R_0\).  The boundary between closed and open corresponds to
+the paraboloids, and is shown by the solid curved line that divides
+the shaded from the unshaded regions of the graph.
+
+The KDE contours in Figure~\ref{fig:mipsgal-shapes}b show that the
+distribution of 3-star sources is very similar to that of 4- and
+5-star sources, although the higher-rated sources are shifted slightly
+to the upper right.  This is probably due to higher-rated sources
+being on average bigger, as will be discussed further below.  The bulk
+of the sources are concentrated around the paraboloid line, with
+\(1 < R_c/R_0 < 2.5\), and \(1.2 < R_{90}/R_0 < 2\).  But significant
+minorities are found in three other regions: (1)~a clump with
+\(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\) at
+\(R_c/R_0 \approx 2\); (3)~a broad horizontal tail towards higher
+\(R_c\) at \(R_{90}/R_0 \la 2\).
 

### 2017-03-30 papers/Paper1/sec-quadrics-observations.tex
Finish caption for Fig 20 - pair plot of non-shape parameters

@@
     (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom-annotated} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
+    \includegraphics[width=0.45\textwidth, trim=0 0 30 0]
+    {figs/mipsgal-Rc-R90-zoom-annotated}
+        & \includegraphics[width=0.45\textwidth, trim=0 0 30 0]
+          {figs/mipsgal-Rc-R90-thumbnails} 
   \end{tabular}
@@
 \(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\) at
-\(R_c/R_0 \approx 2\); (3)~a broad horizontal tail towards higher
+\(R_c/R_0 \approx 2\); and (3)~a broad horizontal tail towards higher
 \(R_c\) at \(R_{90}/R_0 \la 2\).
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/mipsgal-pairplot}
-  \caption[]{Correlations between non-shape parameters of MIPSGAL sources.}
+  \includegraphics[width=0.8\textwidth]{figs/mipsgal-pairplot}
+  \caption[]{Matrix of pair plots that illustrate distributions of and
+    correlations between the non-shape parameters of all MIPSGAL bow
+    shock sources from \citet{Kobulnicky:2016a}.  Plots on the leading
+    diagonal show histograms of the following parameters: bow shock
+    angular size, \(\log_{10} R_0\); Galactic latitude,
+    \(\log_{10}|b|\); Galactic longitude, \(\cos \ell\);
+    extinction-corrected \(H\)-band magnitud of the stellar source,
+    \(H_0\); \(K\)-band extinction, \(A_K\).  Scatter plots in the
+    upper triangle show the joint distribution of each pair of
+    parameters.  These are repeated in the lower triangle but showing
+    the KDEs of the joint distributions, which are annotated with the
+    Pearson linear correlation coefficient, \(r\), for each pair. The
+    straight lines shown superimposed on the plots of stellar magnitud
+    versus bowshock size correspond to model results for the same star
+    at a sequence of distances (dashed lines) and a sequence of
+    stellar luminosities at a fixed distance (dotted lines).  See text
+    for details. }
   \label{fig:mipsgal-pairplot}

### 2017-03-30 papers/Paper1/sec-quadrics-observations.tex
Discussion of extinction to bow shock sources

@@
 
+In Figure~\ref{fig:mipsgal-pairplot} we show the distributions over
+all MIPSGAL bow shock sources of the bow shock size, Galactic
+coordinates, extinction-corrected stellar source magnitude, and dust
+extinction.  For the bow shock size, \(R_0\), we use the results from
+our model fitting rather than the values given in the
+\citet{Kobulnicky:2016a} catalog, but the distribution is very
+similar, as can be seen by comparing the top-left plot of
+Figure~\ref{fig:mipsgal-pairplot} with \citeauthor{Kobulnicky:2016a}'s
+Figure~8.
+
+The catalog gives the \(K\)-band extinction, \(A_K\), derived using
+the method of \citet{Majewski:2011a}, but that assumes an intrinsic
+color of \((H - [\SI{4.5}{\um}])_0 = +0.08\) magnitudes, which is too
+red if the sources are assumed to be OB stars.  We therefore re-derive
+\(A_K\) from the catalog magnitudes combined with the
+\citet{Indebetouw:2005a} reddening law, but assuming
+\((H - [\SI{4.5}{\um}])_0 = -0.1\) magnitudes, which is more typical
+of early type stars.  This does not make very much difference (compare
+the top-right plot of our Fig.~\ref{fig:mipsgal-pairplot} with
+\citeauthor{Kobulnicky:2016a}'s Fig.~9), but it does eliminate some of
+the apparent negative extinctions that are found in the catalog.
+
 \begin{figure*}

### 2017-03-30 papers/Paper1/sec-quadrics-observations.tex
Start to discuss correlations of size with other parameters

@@
 
+\subsubsection{Automatic tracing and fitting of bow shocks}
+\label{sec:autom-trac-fitt}
+
 In order to study the shapes of these bow shocks, we downloaded data
@@
 \end{enumerate}
+
+\subsubsection{Subjective evaluation of the fit quality}
+\label{sec:subj-eval-fit}
 
@@
 
+\subsubsection{OB bow shock shapes on the diagnostic plane}
+\label{sec:ob-shapes}
+
 The derived bowshock shapes of all the 3-, 4-, and 5-star sources are
@@
     \(\log_{10}|b|\); Galactic longitude, \(\cos \ell\);
-    extinction-corrected \(H\)-band magnitud of the stellar source,
+    extinction-corrected \(H\)-band magnitude of the stellar source,
     \(H_0\); \(K\)-band extinction, \(A_K\).  Scatter plots in the
@@
 \end{figure*}
+
+\subsubsection{Correlation between bow shock size and other parameters}
+\label{sec:corr-size}
 
@@
 \citeauthor{Kobulnicky:2016a}'s Fig.~9), but it does eliminate some of
-the apparent negative extinctions that are found in the catalog.
+the apparent negative extinctions that are found in the catalog.  The
+same reddening law gives \(A_H = 1.55 A_K\), and this is used to
+derive extinction-corrected \(H\)-band apparent magnitudes, \(H_0\).
+
+The most significant linear correlation between any pair of parameters
+in Figure~\ref{fig:mipsgal-pairplot} is that between bow shock size
+and stellar source brightness: \(H_0\) versus \(\log_{10} R_0\), with
+correlation coefficient \(r = -0.43\).  The distribution of \(H_0\)
+depends on the absolute magnitude, \(M_H\), and the distance, \(d\),
+to the source.  It is likely that variation in \(d\) is the more
+important of the two because \(M_H\) changes relatively little for
+main-sequence OB stars, ranging from \(M_H \approx -4\) (early-O) to
+\(M_H \approx -1.5\) (mid-B).  This is because part of the increase in
+bolometric luminosity, \(L\), is offset by an increase in the
+effective temperature, \(T_{\text{eff}}\), which shifts the peak of
+the stellar spectrum farther away from the \(H\)~band, resulting in
+\(L_H \propto L / T_{\text{eff}}^3 \sim L^{0.53}\), where the last step uses
+the upper main-sequence mass--luminosity and mass--radius scalings from
+\citet{Eker:2015a}. It is true that evolved OB supergiants can be much
+brighter, reaching \(M_H \approx -7\), but such stars are expected to be
+rare.  Assuming a B2V star (\(M_H = -2\)), then the observed range
+\(H_0 = 5\)--\(12\) corresponds to distances
+\(d = 100\)--\SI{6300}{pc}, and the histogram peak at
+\(H_0 \approx 9.5\) corresponds to \(d \approx \SI{2000}{pc}\), which is all
+perfectly reasonable.
+
+Turning now to the distribution of bow shock angular size, \(R_0\),
+this may be affected by various factors:
+\begin{enumerate}[1.]
+\item Distance, \(d\), since for a constant physical size the angular
+  size will vary as \(R_0 \propto d\).
+\item Momentum-loss ratio, \(\beta\), between the two flows that form the
+  bow shock.  All other things being equal, we have
+  \(R_0 \propto \beta^{1/2}\).  If the environment flow is constant and the OB
+  star wind has mass-loss rate \(\dot{M}\) and terminal velocity
+  \(V_\infty\), then \(\beta \propto \dot{M}{V_\infty}\).  Empirical and theoretical
+  studies of hot star winds (e.g., \citealp{Puls:1996a}) imply
+  \(\dot{M}{V_\infty} \sim L^{1.88} R^{-1/2} \sim L^{1.80}\), where the final
+  step applies only to main-sequence stars and again uses the
+  relations of \citet{Eker:2015a}.  
+\end{enumerate}
+
+\subsubsection{Correlation between bow shock shape and other parameters}
+\label{sec:corr-shape}
 
@@
 
+Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.
+
 %%% Local Variables:

### 2017-03-31 papers/Paper1/sec-quadrics-observations.tex
Size vs distance and size vs luminosity

@@
 
+\subsubsection{Correlation between bow shock size and other parameters}
+\label{sec:corr-size}
+
 \begin{figure*}
@@
     Pearson linear correlation coefficient, \(r\), for each pair. The
-    straight lines shown superimposed on the plots of stellar magnitud
-    versus bowshock size correspond to model results for the same star
+    straight lines shown superimposed on the plots of stellar magnitude
+    versus bowshock size correspond to toy model results for the same star
     at a sequence of distances (dashed lines) and a sequence of
@@
 \end{figure*}
-
-\subsubsection{Correlation between bow shock size and other parameters}
-\label{sec:corr-size}
 
@@
 \(M_H \approx -1.5\) (mid-B).  This is because part of the increase in
-bolometric luminosity, \(L\), is offset by an increase in the
-effective temperature, \(T_{\text{eff}}\), which shifts the peak of
-the stellar spectrum farther away from the \(H\)~band, resulting in
+bolometric luminosity, \(L\), as one ascends the main sequence is
+offset by an increase in the effective temperature,
+\(T_{\text{eff}}\), which shifts the peak of the stellar spectrum
+farther away from the \(H\)~band, resulting in
 \(L_H \propto L / T_{\text{eff}}^3 \sim L^{0.53}\), where the last step uses
@@
 Turning now to the distribution of bow shock angular size, \(R_0\),
-this may be affected by various factors:
-\begin{enumerate}[1.]
-\item Distance, \(d\), since for a constant physical size the angular
-  size will vary as \(R_0 \propto d\).
-\item Momentum-loss ratio, \(\beta\), between the two flows that form the
-  bow shock.  All other things being equal, we have
-  \(R_0 \propto \beta^{1/2}\).  If the environment flow is constant and the OB
-  star wind has mass-loss rate \(\dot{M}\) and terminal velocity
-  \(V_\infty\), then \(\beta \propto \dot{M}{V_\infty}\).  Empirical and theoretical
-  studies of hot star winds (e.g., \citealp{Puls:1996a}) imply
-  \(\dot{M}{V_\infty} \sim L^{1.88} R^{-1/2} \sim L^{1.80}\), where the final
-  step applies only to main-sequence stars and again uses the
-  relations of \citet{Eker:2015a}.  
-\end{enumerate}
+this will also be affected by distance to at least some degree, since
+for a constant physical size the angular size will vary as
+\(R_0 \propto d^{-1}\).  For instance, if we assume that the physical size
+of all bow shocks is \SI{0.1}{pc} and the absolute magnitude of all
+stars is \(M_H = -2\), as above, then we find the relation
+\(H_0 = 14.57 - 5 \log_{10} R_0\) if \(R_0\) is measured in
+arcseconds. This is shown as a dashed line on the relevant panels of
+Figure~\ref{fig:mipsgal-pairplot} for values of \(R_0\) that
+correspond to \(d = \SI{300}{pc}\) to \SI{8000}{pc}.  It can be seen
+that this relation is in excellent agreement with the linear trend in
+the data. On the other hand, the correlation coefficient of
+\(r = -0.43\) means in broad terms that only a fraction
+\(r^2 \approx 20\%\) of the total variance in \(H_0\) is ``explained'' by
+changes in \(R_0\), and vice~versa, implying that one or both of
+\(H_0\) and \(R_0\) is only a very imperfect proxy for \(d\).  We have
+already seen that the spread in \(H_0\) probably \emph{is} mostly due
+to a spread in distance, rather than a spread in \(H\)-band stellar
+luminosity.  If this is true, it follows that it is \(R_0\) that
+depends only weakly on \(d\) and is more influenced by other factors.
+
+One such factor is the stellar/environmental momentum-loss ratio,
+\(\beta\), between the two supersonic flows that form the bow shock.  All
+other things being equal, we have \(R_0 \propto \beta^{1/2}\) for
+\(\beta \ll 1\), as is typically the case.  If the environment flow is
+constant and the OB star wind has mass-loss rate \(\dot{M}\) and
+terminal velocity \(V_\infty\), then
+\(\beta \propto \dot{M}{V_\infty}\).  Empirical and theoretical studies of hot star
+winds (e.g., \citealp{Puls:1996a}) imply
+\(\dot{M}{V_\infty} \sim L^{1.88} R^{-1/2} \sim L^{1.80} \sim L_H^{3.40}\), where
+the final two steps apply only to main-sequence stars and again use
+the relations of \citet{Eker:2015a}.  If we assume as above that a B2V
+star with \(M_H = -2\) has a bow shock physical size of \SI{0.1}{pc},
+and consider a sequence of stars with varying \(H\)-band luminosities
+but all at a fixed distance of \(d = \SI{2000}{pc}\), then we find the
+relation \(H_0 = 8.02 - 1.49 \log_{10} R_0\).  This is shown as a
+dotted line in the relevant panels of
+Figure~\ref{fig:mipsgal-pairplot} for the absolute magnitude range
+\(M_H = -3.6\) (O6V) to \(M_H = -1.5\) (B5V).  It can be seen that
+this relation does not match the linear trend in the data, and
+predicts a much larger spread in \(R_0\) over a narrow range in
+\(H_0\) than is observed.  This could mean one of two things: first,
+it may be that the range of stellar luminosities is significantly
+narrower than we have supposed, implying that B stars vastly outnumber
+O stars among the sources.  Alternatively, there may be a positive
+correlation between the stellar luminosity and the momentum of the
+environmental flow, with the result that \(\beta\) varies less steeply
+with \(L_H\) than we have supposed.  This would arise if more luminous
+stars were preferentially found in denser environments, or, in the
+case of runaways, if more luminous stars tended to be faster moving.
+
+A third factor that may influence \(R_0\) is the inclination, \(i\),
+of the bow shock axis with respect to the plane of the sky.
 

### 2017-03-31 papers/Paper1/sec-quadrics-observations.tex
Add symbol size variation with R0'/R0 to Fig 10

@@
 environmental flow, with the result that \(\beta\) varies less steeply
-with \(L_H\) than we have supposed.  This would arise if more luminous
+with \(L_H\) than we have assumed.  That could arise if more luminous
 stars were preferentially found in denser environments, or, in the

### 2017-03-31 Quadric-shapes/projected-R90-Rc-snapshots.py

@@ -32,6 +32,11 @@ def Tc_prime(inc, Tc):
 def R90_prime(inc, Tc, Rc):
     return np.sqrt(2*Rc_prime(inc, Tc, Rc) - Tc_prime(inc, Tc))
 
+def qratio(inc, Tc, Rc):
+    f = np.sqrt(1.0 + Tc*np.tan(inc)**2)
+    return (1.0 + Rc*(f - 1.0) / Tc)*np.cos(inc)
+
+
 for ax, inc_deg in zip(axes.flat, incs_deg):
 
     Rc_grid2 = np.linspace(0.0, 10.0, 2000)
@@ -48,10 +53,12 @@ for ax, inc_deg in zip(axes.flat, incs_deg):
     inc = np.radians(inc_deg)
     Rcp = Rc_prime(inc, Tc_grid, Rc_grid).ravel()
     R90p = R90_prime(inc, Tc_grid, Rc_grid).ravel()
-    ax.scatter(Rcp, R90p, c=Tc_grid.ravel(),
+    R0p = qratio(inc, Tc_grid, Rc_grid).ravel()
+
+    ax.scatter(Rcp, R90p, c=Tc_grid.ravel(), s=15*R0p,
 	       vmin=Tc_grid.min(), vmax=Tc_grid.max(),
 	       edgecolors='none',
-	       cmap='magma', marker='.', s=15, alpha=0.8)
+	       cmap='magma', marker='.', alpha=0.8)
     # ax.axhspan(0.0, 10.0, alpha=0.1, facecolor='k', zorder=-1)
     # ax.axhline(1.0, ls='--', lw=0.5, c='k', zorder=0)
     # ax.axvline(1.0, ls='--', lw=0.5, c='k', zorder=0)

### 2017-04-02 papers/Paper1/sec-quadrics-observations.tex
Start write up of A-D tests

@@
 
+\begin{figure*}
+  \centering
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
+  \end{tabular}
+  \caption[]{Comparison between the distribution of bowshock shapes
+    when the sources are divided into two sub-samples according to the
+    value of another parameter. (a)~Bow shock angular size, \(R_0\).
+    (b)~Extinction-corrected \(H\)-band magnitude of the stellar
+    source.}
+  \label{fig:mipsgal-correlated}
+\end{figure*}
+
 Turning now to the distribution of bow shock angular size, \(R_0\),
@@
 of the bow shock axis with respect to the plane of the sky.
+Figure~\ref{fig:quadric-projection}b shows that for \(R_c > 1\), then
+the projected \(R_0'\) becomes larger than the true \(R_0\) as \(|i|\)
+increases.  This is further illustrated in
+Figure~\ref{fig:projected-R90-Rc-snapshots} for simple quadric shapes
+(spheroids, paraboloids, hyperboloids) and in
+Figure~\ref{fig:thin-shell-R90-Rc-snapshots} for the carawilkinoids
+and ancarawilkinoids.  It can be seen that the effect is relatively
+modest for bow shocks with projected shapes falling in the range
+\(1 < R_c/R_0 < 3\) and \(R_{90}/R_0 < 3\), as the vast majority of
+our observed sources do.  The increase in \(R_0\) is no more than a
+factor of 2 to 3 for moderate inclinations of \(30\) to \(60\degr\),
+although it can reach a factor of 5 to 10 for some shapes at more
+extreme inclinations.
+
+%% Maybe talk about the other correlations later if we have time
 
@@
 \label{sec:corr-shape}
-
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
-  \end{tabular}
-  \caption[]{Comparison between the distribution of bowshock shapes
-    when the sources are divided into two sub-samples according to the
-    value of another parameter. (a)~Bow shock angular size, \(R_0\).
-    (b)~Extinction-corrected \(H\)-band magnitude of the stellar
-    source.}
-  \label{fig:mipsgal-correlated}
-\end{figure*}
 
@@
 \end{figure*}
+
+We now investigate if the bow shock shapes of the MIPSGAL sources are
+correlated with any other parameters via the following methodology:
+\begin{enumerate}[1.]
+\item For each of the parameters in the \citet{Kobulnicky:2016a}
+  catalog, we divide the sources into two or more sub-samples,
+  according to the value of the parameter.  For quantitative
+  parameters, such as those discussed in the previous section, we use
+  two sub-samples of equal size, with membership determined by whether
+  the parameter is larger or smaller than the median value.  But we
+  also use categorical parameters, such as the type of bow shock
+  environment, or the presence/absence of \SI{8}{\um} emission, in
+  which case the sub-samples are of unequal size.
+\item We plot the KDEs of the two sub-samples separately on the
+  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
+  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
+  differences.
+\item We test if there is any statistically significant difference
+  between the shape distributions of the sub-samples by applying the
+  2-sample Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a} to the
+  \(R_c/R_0\) and \(R_{90}/R_0\) distributions separately.  This is a
+  non-parametric test of the \textit{null hypothesis} that the two
+  sub-samples are drawn from the same distribution.
+
+\end{enumerate}
 

### 2017-04-02 Quadric-shapes/projected-R90-Rc-snapshots.py

@@ -11,9 +11,9 @@ fig, axes = plt.subplots(3, 3, figsize=(9, 9), sharex=True, sharey=True)
 
 incs_deg = 10.0*np.arange(9)
 
-ny, nx = 35, 35
-Rcs = np.linspace(0.5, 5.0, nx)
-R90s = np.linspace(0.5, 5.0, ny)[::-1]
+ny, nx = 55, 55
+Rcs = np.linspace(0.5, 7.0, nx)
+R90s = np.linspace(0.5, 7.0, ny)[::-1]
 Rc_grid = Rcs[None, :]*np.ones_like(R90s[:, None])
 R90_grid = R90s[:, None]*np.ones_like(Rcs[None, :])
 Tc_grid = 2*Rc_grid - R90_grid**2

### 2017-04-03 papers/Paper1/quadrics-appendix.tex
Discussion of extinction to bow shock sources
Write more on interpretation of p-values

@@
     non-parametric 2-sample tests performed during the analysis of
-    section~\ref{sec:comp-with-observ}.  The vertical dashed line
-    shows the traditional threshold value for significance:
-    \(p = 0.05\). The red solid line shows the expected distribution
-    of \(p\)-values that would be obtained if no significant
-    correlations existed.}
+    section~\ref{sec:comp-with-observ}.  The vertical dashed lines
+    shows the traditional threshold values for significance:
+    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
+    expected uniform distribution of \(p\)-values that would be
+    expected if the null hypothesis were always true, that is, if no
+    significant correlations existed.}
   \label{fig:histo-p-values}
 \end{figure}
+
+The \(p\)-values are the probability of finding a difference between
+two populations as large as (or larger than) what is observed,
+\emph{given} that there is no difference in the underlying
+distribution from which the two populations are drawn (that is, given
+that the null hypothesis is true).  However, what we really want to
+know is something else: the probability that the null hypothesis is
+true, \emph{given} the observations.  That is, the probability,
+\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
+  error rate}.  The common mistake of conflating these two definitions
+is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
+error of the transposed conditional'', as discussed in detail by
+\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
+\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
+requires an estimate of the prior probability of the null hypothesis,
+independent of the observations.  Alternatively, it is also possible to find a lower bound on \(\alpha\) from a frequentist approach \citep{Sellke:2001a}:
+\begin{equation}
+  \label{eq:type-I}
+  \alpha(p) \ge \bigg[ 1 - \big(e p \ln p\big)^{-1} \bigg]^{-1}
+\end{equation}
+
+\begin{table}
+  \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
+  \label{tab:type-I}
+  \centering
+  \begin{tabular}{lrr} \toprule
+    Correlation & \(p\) & \(\alpha\) \\
+    \midrule
+    \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
+    \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
+    \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
+    \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
+    \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
+    \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
+    \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
+    \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
+    \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
+    \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
+    \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
+    \midrule
+    \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
+    \(R_c\) vs Facing & 0.71 & 1 \\
+    \(R_c\) vs H II & 0.50 & 1 \\
+    \(R_{90}\) vs Facing & 0.60 & 1 \\
+    \(R_{90}\) vs H II & 0.52 & 1 \\
+    \(R_c\) vs Multiple & 1.00 & 1 \\
+    \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
+    \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
+    \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
+    \midrule
+    \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
+    \(R_c\) vs Herschel & 0.074 & 0.3437 \\
+    \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
+    \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
+    \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 
+The p-curve \citep{Head:2015a}
+
 %%% Local Variables:

### 2017-04-03 papers/Paper1/sec-quadrics-observations.tex
Write more on interpretation of p-values

@@
 \item We test if there is any statistically significant difference
-  between the shape distributions of the sub-samples by applying the
-  2-sample Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a} to the
-  \(R_c/R_0\) and \(R_{90}/R_0\) distributions separately.  This is a
+  between the bow shock shapes of the sub-samples by applying the
+  2-sample Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a}
+  to \(R_c/R_0\) and \(R_{90}/R_0\) separately.  This is a
   non-parametric test of the \textit{null hypothesis} that the two
-  sub-samples are drawn from the same distribution.
-
+  sub-samples are drawn from the same distribution.  It returns a
+  \(p\)-value, which is the estimated probability that the observed
+  difference between the two sub-samples would be as large as it is
+  purely by chance if they were all were drawn from the same
+  distribution.  We adopt a threshold of \(p < 0.001\) in order to
+  confidently reject the null hypothesis and declare a ``significant''
+  difference between the two sub-samples, but we also consider the
+  less strict threshold of \(p < 0.05\) as an indicator of
+  ``probable'' difference (see Appendix~\ref{sec:distr-p-values} for
+  details).
 \end{enumerate}

### 2017-04-03 papers/Paper1/quadrics-appendix.tex
Started discussion of false negative rate, beta
Wrote a bit about effect sizes

@@
 
-The \(p\)-values are the probability of finding a difference between
-two populations as large as (or larger than) what is observed,
-\emph{given} that there is no difference in the underlying
-distribution from which the two populations are drawn (that is, given
-that the null hypothesis is true).  However, what we really want to
-know is something else: the probability that the null hypothesis is
-true, \emph{given} the observations.  That is, the probability,
-\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
-  error rate}.  The common mistake of conflating these two definitions
-is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
-error of the transposed conditional'', as discussed in detail by
-\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
-\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
-requires an estimate of the prior probability of the null hypothesis,
-independent of the observations.  Alternatively, it is also possible to find a lower bound on \(\alpha\) from a frequentist approach \citep{Sellke:2001a}:
-\begin{equation}
-  \label{eq:type-I}
-  \alpha(p) \ge \bigg[ 1 - \big(e p \ln p\big)^{-1} \bigg]^{-1}
-\end{equation}
-
 \begin{table}
@@
 
+The \(p\)-values are the probability of finding a difference between
+two populations as large as (or larger than) what is observed,
+\emph{given} that there is no difference in the underlying
+distribution from which the two populations are drawn (that is, given
+that the null hypothesis is true).  However, what we really want to
+know is something else: the probability that the null hypothesis is
+true, \emph{given} the observations.  That is, the probability,
+\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
+  error rate}.  The common mistake of conflating these two definitions
+is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
+error of the transposed conditional'', as discussed in detail by
+\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
+\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
+requires an estimate of the prior probability of the null hypothesis,
+independent of the observations.  Alternatively, it is also possible
+to find a lower bound on \(\alpha\) from a frequentist approach
+\citep{Sellke:2001a}:
+\begin{equation}
+  \label{eq:type-I}
+  \alpha(p) \ge \bigg[ 1 - \big(e\, p \ln p\big)^{-1} \bigg]^{-1}
+  \quad \text{valid for } p < 1/e.
+\end{equation}
+This is the approach we adopt here, which also numerically coincides
+with the Bayesian approach for the case where the prior probability of
+the null hypothesis is 0.5.  The reason that this is only a lower
+limit for \(\alpha\) is that if we have overwhelming a priori evidence that
+the null hypothesis is true (for instance, from previous empirical
+studies, or because it follows from a well-supported theory), then a
+Bayesian calculation would give a much higher value of \(\alpha\) than
+\eqref{eq:type-I} does.  In our case, however, we have no strong
+reasons for favoring any of the null hypotheses, so it is reasonable
+to assume \(\alpha\) is close to the lower limit of \eqref{eq:type-I}.
+
+In order to choose a threshold \(p\)-value that counts as a
+``significant'' result, one then needs to balance the risks of false
+positives against the risks of \textit{false negatives}.  The false
+negative probability, \(\beta\), also known as \textit{Type II error
+  rate}, is the probability of failing to reject an untrue null
+hypothesis.  That is, in the context of this paper, it is the
+probability of failing to detect a real difference between two
+sub-samples, or a real correlation between two variables.  The
+complementary probability, \(1 - \beta\), is known as the
+\textit{statistical power} or sensitivity of the test.  The value of
+\(\beta\) depends on three factors:
+\begin{enumerate}[1.]
+\item The \textit{effect size}, which is a measure of the magnitude of
+  the difference in a dependent variable between two sub-samples, or
+  the degree of correlation between two continuous variables.  For the
+  two sub-sample case, it is common to use a standardised mean
+  difference, such as Cohen's \(d\) statistic \citep{Cohen:1988a}:
+  \(d = (\bar{X}_A - \bar{X}_B) / s\), where \(\bar{X}_A\),
+  \(\bar{X}_B\) are the means of the dependent variable \(X\) for
+  samples A and B, while \(s\) is the pooled standard deviation of
+  \(X\).  For the case of two continuous variables, the Pearson linear
+  correlation coefficient, \(r\), can be used.  In both cases, rules
+  of thumb have been developed \citep{Ruscio:2008a} for classifying an
+  effect as ``large'' (\(d > 0.8\), \(r > 0.4\)) or ``small''
+  (\(d < 0.2\), \(r < 0.1\)).  Alternatively, non-parametric
+  statistics can be used, such as the \(A\) measure of stochastic
+  superiority \citep{Delaney:2002a}.
+\end{enumerate}
+
+Obviously, this depends on the \textit{effect size}, which is the
+
 All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).

### 2017-04-04 papers/Paper1/quadrics-appendix.tex
Add p-values to the pairwise correlation plots

@@
 reasons for favoring any of the null hypotheses, so it is reasonable
-to assume \(\alpha\) is close to the lower limit of \eqref{eq:type-I}.
+to assume \(\alpha\) is close to the lower limit given in \eqref{eq:type-I}.
 

### 2017-04-05 papers/Paper1/sec-quadrics-observations.tex
Fix an error with the median split on R0 correlations

--- 2017-04-02 papers/Paper1/sec-quadrics-observations.tex
@@
 
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
-  \end{tabular}
-  \caption[]{Comparison between the distribution of bowshock shapes
-    when the sources are divided into two sub-samples according to the
-    value of another parameter. (a)~Bow shock angular size, \(R_0\).
-    (b)~Extinction-corrected \(H\)-band magnitude of the stellar
-    source.}
-  \label{fig:mipsgal-correlated}
-\end{figure*}
-
 Turning now to the distribution of bow shock angular size, \(R_0\),
@@
 depends only weakly on \(d\) and is more influenced by other factors.
+
+\begin{figure*}
+  \centering
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
+  \end{tabular}
+  \caption[]{Lack of significant correlation of bow shock shape with
+    (a) environment, and (b) uncertainty in stellar source
+    identification.}
+  \label{fig:mipsgal-uncorrelated}
+\end{figure*}
 
@@
 \label{sec:corr-shape}
-
 \begin{figure*}
@@
     (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
   \end{tabular}
-  \caption[]{Lack of significant correlation of bow shock shape with
-    (a) environment, and (b) uncertainty in stellar source
-    identification.}
-  \label{fig:mipsgal-uncorrelated}
+  \caption[]{Comparison between the distribution of bowshock shapes
+    when the sources are divided into two sub-samples according to the
+    value of another parameter. (a)~Bow shock angular size, \(R_0\).
+    (b)~Extinction-corrected \(H\)-band magnitude of the stellar
+    source.}
+  \label{fig:mipsgal-correlated}
 \end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
+  \caption{Box plots of the distributions of bow shock shape
+    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), as a function of bow
+    shock size, \(R_0\).  All 3-, 4-, and 5-star sources are sorted
+    according to \(R_0\) and divided into 5 non-overlapping
+    sub-samples of roughly equal size, each labelled by their median
+    value of \(R_0\) in arcseconds, as illustrated in the lower panel.
+    The colored boxes show the interquartile range, with the median
+    indicated by a horizontal line, the 1st-to-9th interdecile range
+    by error bars, and outliers by diamonds.  It is apparent that the
+    dispersion in \(R_{90} / R_0\) (upper panel) increases
+    systematically with \(R_0\), although the central value is roughly
+    constant.  No clear systematic changes are apparent in
+    \(R_c / R_{90}\) (middle panel).}
+  \label{fig:mipsgal-boxplot}
+\end{figure}
 
@@
 \item We test if there is any statistically significant difference
-  between the shape distributions of the sub-samples by applying the
-  2-sample Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a} to the
-  \(R_c/R_0\) and \(R_{90}/R_0\) distributions separately.  This is a
-  non-parametric test of the \textit{null hypothesis} that the two
-  sub-samples are drawn from the same distribution.
-
+  between the bow shock shapes of the sub-samples by applying the
+  two-sample Anderson--Darling test \citep{Anderson:1952a,
+    Scholz:1987a, Makarov:2017a} to \(R_c/R_0\) and \(R_{90}/R_0\)
+  separately.  This is a non-parametric test of the \textit{null
+    hypothesis} that the two sub-samples are drawn from the same
+  distribution.  It returns a \(p\)-value, which is the estimated
+  probability that the observed difference between the two sub-samples
+  would be as large as it is purely by chance if they were all were
+  drawn from the same distribution.  We adopt a threshold of
+  \(p < 0.001\) in order to confidently reject the null hypothesis and
+  declare a ``significant'' difference between the two sub-samples,
+  but we also consider the less strict threshold of \(p < 0.05\) as an
+  indicator of ``probable'' difference (see
+  Appendix~\ref{sec:distr-p-values} for details).
 \end{enumerate}

### 2017-04-05 papers/Paper1/sec-quadrics-observations.tex
Add the plot with 5-sample partitioning on H0

@@
   \centering
-  \includegraphics[width=0.7\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
-  \caption{Box plots of the distributions of bow shock shape
-    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), as a function of bow
-    shock size, \(R_0\).  All 3-, 4-, and 5-star sources are sorted
-    according to \(R_0\) and divided into 5 non-overlapping
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
+    \includegraphics[height=0.8\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
+    & \includegraphics[height=0.8\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-H0}
+  \end{tabular}
+  \caption{(a) Box plots of the distributions of bow shock shape
+    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), after partitioning
+    on the bow shock size, \(R_0\).  All 3-, 4-, and 5-star sources
+    are sorted according to \(R_0\) and divided into 5 non-overlapping
     sub-samples of roughly equal size, each labelled by their median
@@
     constant.  No clear systematic changes are apparent in
-    \(R_c / R_{90}\) (middle panel).}
+    \(R_c / R_{90}\) (middle panel).  (b)~As (a), but partitioning on
+    the extinction-corrected \(H\)-band magnitude, \(H_0\).  Note that
+    sub-samples are plotted in order of \textit{decreasing} magnitude
+    to allow comparison between (a) and (b), given the negative
+    correlation between \(H_0\) and \(R_0\) (see
+    Fig.~\ref{fig:mipsgal-pairplot}).}
   \label{fig:mipsgal-boxplot}

### 2017-04-05 papers/Paper1/sec-quadrics-observations.tex
Add asymmetry measure and A-D tests to 5-sample figure

--- 2017-04-05 papers/Paper1/sec-quadrics-observations.tex
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
-  \caption{Box plots of the distributions of bow shock shape
-    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), as a function of bow
-    shock size, \(R_0\).  All 3-, 4-, and 5-star sources are sorted
-    according to \(R_0\) and divided into 5 non-overlapping
-    sub-samples of roughly equal size, each labelled by their median
-    value of \(R_0\) in arcseconds, as illustrated in the lower panel.
-    The colored boxes show the interquartile range, with the median
-    indicated by a horizontal line, the 1st-to-9th interdecile range
-    by error bars, and outliers by diamonds.  It is apparent that the
-    dispersion in \(R_{90} / R_0\) (upper panel) increases
-    systematically with \(R_0\), although the central value is roughly
-    constant.  No clear systematic changes are apparent in
-    \(R_c / R_{90}\) (middle panel).}
+  \setlength\tabcolsep{0pt}
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[height=1.167\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
+    & \includegraphics[height=1.167\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-H0}
+  \end{tabular}
+  \caption{(a) Box plots of the distributions of bow shock shape
+    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), together with a
+    measure of the tail asymmetry, \(|R_{90+} - R_{90-}| / R_{90}\),
+    after partitioning on the bow shock size, \(R_0\).  All 3-, 4-,
+    and 5-star sources are sorted according to \(R_0\) and divided
+    into 5 non-overlapping sub-samples of roughly equal size, each
+    labelled by their median value of \(R_0\) in arcseconds, as
+    illustrated in the lower panel.  The colored boxes show the
+    interquartile range, with the median indicated by a horizontal
+    line, the 1st-to-9th interdecile range by error bars, and outliers
+    by diamonds.  A 5-sample Anderson--Darling test is performed for
+    each dependent variable, with resultant \(p\)-value given at the
+    bottom of each panel.  It is apparent that the dispersion in
+    \(R_{90} / R_0\) (upper panel) increases systematically with
+    \(R_0\), although the central value is roughly constant.  No clear
+    systematic changes are apparent in \(R_c / R_{90}\) (middle
+    panel).  (b)~As (a), but partitioning on the extinction-corrected
+    \(H\)-band magnitude, \(H_0\).  Note that sub-samples are plotted
+    in order of \textit{decreasing} magnitude to allow comparison
+    between (a) and (b), given the negative correlation between
+    \(H_0\) and \(R_0\) (see Fig.~\ref{fig:mipsgal-pairplot}).}
   \label{fig:mipsgal-boxplot}

### 2017-04-06 papers/Paper1/sec-quadrics-observations.tex
New figure showing R90 dispersion versus R0

@@
     (a) & (b) \\
-    \includegraphics[height=1.167\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-R0}
-    & \includegraphics[height=1.167\linewidth]{figs/mipsgal-boxplot-Rc-R90-versus-H0}
+    \includegraphics[height=1.167\linewidth]
+    {figs/mipsgal-boxplot-Rc-R90-versus-R0}
+        & \includegraphics[height=1.167\linewidth]
+          {figs/mipsgal-boxplot-Rc-R90-versus-H0}
   \end{tabular}
@@
   \label{fig:mipsgal-boxplot}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/mipsgal-R90-ratio-versus-R0-heteroscedastic}
+  \caption{Heteroscedastic}
+  \label{fig:mipsgal-heteroscedastic}
 \end{figure}

### 2017-04-06 papers/Paper1/sec-quadrics-observations.tex
Finish the regression analysis of R90 vs R0

@@
   \includegraphics[width=\linewidth]{figs/mipsgal-R90-ratio-versus-R0-heteroscedastic}
-  \caption{Heteroscedastic}
+  \caption{Regression analysis of bow shock wings shape versus size.
+    The top panel shows a linear fit to \(R_{90}/R_0\) versus
+    \(\log_{10} R_0\), which is essentially flat and is consistent
+    with no correlation between the two quantities.  On the other
+    hand, in the central panel, which shows the absolute values of the
+    residuals from this fit, it is apparent that the dispersion about
+    the average value of the bow shock shape parameter \(R_{90}/R_0\)
+    increases with bow shock size.  A linear fit to all the data is
+    shown by the blue dotted line, while a locally weighted regression
+    (LOWESS; \citealp{Cleveland:1979a, Cleveland:1988a}) is shown by
+    the heavy green dashed line.  The negative curvature of the LOWESS
+    curve suggests that the slope of the linear fit is a compromise
+    between a steeper slope for smaller bow shocks and a flat (or
+    negative) slope for the largest bow shocks.  We therefore repeat
+    the linear fit, but after excluding sources with
+    \(\log_{10} R_0 > 1.4\), with results shown by the red dotted
+    line.  The bottom panel shows the bow shock wings asymmetry
+    parameter, \(|R_{90+} - R_{90-}| / R_{90}\), together with a
+    linear fit.}
   \label{fig:mipsgal-heteroscedastic}

### 2017-04-17 papers/Paper1/quadrics-appendix.tex
Include the linear p-value graph too, and redo fig caption

@@
 \begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/p-value-histogram}
-  \caption{Histogram of \(p\)-values for all Anderson--Darling
-    non-parametric 2-sample tests performed during the analysis of
-    section~\ref{sec:comp-with-observ}.  The vertical dashed lines
-    shows the traditional threshold values for significance:
+  (a)\\
+  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
+  (b)\\
+  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
+  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
+    tests performed during the analysis of
+    section~\ref{sec:comp-with-observ}. (a)~Uniformly spaced linear
+    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
+    bins and logarithmic vertical axis, with all values
+    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
+    lines shows the traditional threshold values for significance:
     \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
-    expected uniform distribution of \(p\)-values that would be
-    expected if the null hypothesis were always true, that is, if no
-    significant correlations existed.}
+    uniform distribution of \(p\)-values that would be expected if the
+    null hypothesis were always true, that is, if no significant
+    correlations existed.}
   \label{fig:histo-p-values}

### 2017-04-18 papers/Paper1/quadrics-appendix.tex
Add big table of stats tests to paper - still needs fixing
Finish tweaks to big table of p-values

@@
 From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
+\clearpage
+\sisetup{detect-weight=true, detect-shape=true, detect-inline-weight=math}
+\sisetup{round-mode=figures, round-precision=2}
+\begin{landscape}
+\begin{table}
+  \setlength\tabcolsep{2pt}
+  \caption{Big table of \(p\)-values}
+  \begin{tabular}{@{} ll @{\ } S[round-mode=places]S[round-mode=places] S[round-mode=places]S[round-mode=places] SS SS @{\quad\quad\quad} SSS @{\quad} S@{}S@{}S @{}}\toprule
+     & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\
+    {Comparison} & {Variable} & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)} & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)} & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)} & {\((\sigma/\!\sqrt n)_{\text{A}}\)} & {\((\sigma/\!\sqrt n)_{\text{B}}\)} & {\(r_b\)} & {\(d_C\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)} & \multicolumn{1}{c}{Anderson--Darling} & \multicolumn{1}{c}{Rank biserial} &  \multicolumn{1}{c}{Brown--Forsythe}\\
+\midrule
+    \multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\
+    \addlinespace
+    Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.030 & \bfseries 0.174 & \bfseries -0.308 & 0.851 & \bfseries 0.0215 & \bfseries 0.0235 & 0.125\\
+\(H\) magnitude  & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &  &  & 0.015 & 0.015 & 0.070 & -0.093 & 0.987 & 0.538 & 0.365 & 0.761\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & -0.303 & \bfseries 0.604 & 0.123 & 0.111 & \bfseries 0.0335\\
+\addlinespace
+Low/high  & \(R_{90}\) & 1.707 & 1.739 & 0.250 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & -0.110 & \bfseries 0.745 & \bfseries 0.0281 & 0.428 & \bfseries 0.00139\\
+\(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &  &  & 0.015 & 0.015 & 0.091 & -0.176 & 0.948 & 0.103 & 0.238 & 0.193\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.100 & -0.043 & 1.291 & 0.228 & 0.192 & 0.599\\
+\addlinespace
+Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.030 & 0.040 & -0.132 & 0.824 & 0.554 & 0.602 & 0.123\\
+extinction & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &  &  & 0.013 & 0.017 & -0.039 & -0.057 & 0.754 & 0.301 & 0.61 & 0.112\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\)  & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & -0.139 & 0.896 & 0.219 & 0.285 & 0.982\\
+\addlinespace
+Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.020 & -0.008 & 1.256 & 0.308 & 0.795 & 0.0534\\
+\(\vert{}b\vert\)  & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &  &  & 0.015 & 0.015 & 0.009 & -0.021 & 0.995 & 0.964 & 0.907 & 0.694\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & -0.181 & 0.736 & 0.19 & 0.368 & 0.0842\\
+\addlinespace
+High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & 0.093 & 0.868 & 0.361 & 0.532 & 0.159\\
+\(\cos \ell\)  & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &  &  & 0.013 & 0.018 & 0.054 & -0.122 & 0.909 & 0.604 & 0.491 & 0.365\\
+\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.090 & 0.084 & 0.081 & 0.078 & -0.000 & 0.064 & 1.274 & 1.03 & 0.999 & 0.549\\
+\midrule
+    \multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\
+    \addlinespace
+Environment:  & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.070 & 0.142 & 0.838 & 0.603 & 0.49 & 0.392\\
+Facing & \(\Delta R_{90}\) & 0.190 & 0.195 & 0.161 & 0.172 &  &  & 0.012 & 0.027 & -0.019 & -0.034 & 0.938 & 0.507 & 0.85 & 0.438\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.140 & 0.042 & -0.110 & 0.950 & 0.713 & 0.676 & 0.377\\
+\addlinespace
+Environment:  & \(R_{90}\) & 1.735 & 1.680 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.130 & 0.193 & 0.916 & 0.518 & 0.391 & 0.782\\
+\hii & \(\Delta R_{90}\) & 0.190 & 0.175 & 0.161 & 0.138 &  &  & 0.012 & 0.034 & -0.048 & 0.095 & 1.170 & 0.932 & 0.754 & 0.799\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & -0.174 & 0.894 & 0.496 & 0.875 & 0.255\\
+\addlinespace
+Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.230 & 0.243 & 0.022 & 0.041 & 0.074 & -0.177 & 0.917 & 0.342 & 0.396 & 0.338\\
+source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.160 &  &  & 0.013 & 0.021 & 0.093 & -0.136 & 1.013 & 0.421 & 0.284 & 0.97\\
+\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.090 & 0.080 & 0.064 & 0.128 & 0.027 & -0.076 & 0.835 & 0.999 & 0.756 & 0.605\\
+\addlinespace
+With/without  & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & 0.044 & 0.970 & 0.595 & 0.667 & 0.563\\
+\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &  &  & 0.031 & 0.011 & 0.021 & 0.106 & 1.377 & 0.765 & 0.826 & 0.219\\
+\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & -0.101 & 0.646 & 0.824 & 0.904 & 0.2\\
+\midrule
+    \multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Intercomparison with other datasets \dotfill}\\
+    \addlinespace
+MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &  &  & 0.020 & 0.191 & \bfseries 0.700 & \bfseries -1.928 & \bfseries 0.366 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
+ & \(\Delta R_{90}\) & 0.190 & 0.506 & 0.162 & 0.551 &  &  & 0.011 & 0.130 & 0.220 & -1.468 & \bfseries 0.294 & \bfseries 3.6e-05 & 0.121 & \bfseries 4.03e-14\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &  &  & 0.058 & 0.307 & \bfseries 0.516 & \bfseries -0.940 & 0.669 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\
+\addlinespace
+MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &  &  & 0.020 & 0.046 & \bfseries -0.756 & \bfseries 1.152 & 2.425 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
+ & \(\Delta R_{90}\) & 0.190 & 0.197 & 0.162 & 0.296 &  &  & 0.011 & 0.112 & -0.242 & -0.045 & 0.546 & 0.156 & 0.276 & 0.397\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &  &  & 0.058 & 0.030 & -0.201 & 0.418 & 10.969 & 0.0742 & 0.367 & 0.0505\\
+\bottomrule
+\end{tabular}
+\end{table}
+\end{landscape}
 

### 2017-04-19 Stellar-Bowshocks-2017/mipsgal-summary-stats-table-body.tex
Yet more fiddling with big p-value table
I decided to reverse the sign of Cohen's d for consistency with the
rank biserial correlation coefficient.  Also turn the sig/tau value
upside down so that it is usually bigger than one.  The table is now
generated automatically from the JSON file, so any further adjustments
will be easy.

%%% MIPSGAL summary statistics
%%% Table automatically generated from mipsgal-summary-stats.tab
%%% 2017-04-19 13:16:10.731012
%%%
% \Width is used to align number under col header in first column
	\newlength\Width\settowidth\Width{Comparison}
	\begin{tabular}{@{} ll @{\quad } S[round-mode=places]S[round-mode=places] S[round-mode=places]S[round-mode=places] SS SS @{\quad\quad\quad} SSS[round-mode=places] @{\quad} S@{}S@{}S @{}}\toprule
	  & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\ 
	  {Comparison} & {Variable} & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)} & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)} & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)} & {\((\sigma/\!\sqrt n)_{\text{A}}\)} & {\((\sigma/\!\sqrt n)_{\text{B}}\)} & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)} & \multicolumn{1}{c}{Anderson--Darling} & \multicolumn{1}{c}{Rank biserial} &  \multicolumn{1}{c}{Brown--Forsythe}\\
	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)} & {(3)} & {(4)} & {(5)} & {(6)} & {(7)} & {(8)} & {(9)} & {(10)}  & {(11)} & {(12)} & {(13)} & {(14)} & {(15)} & {(16)} \\  
	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\
\addlinespace
Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
\(H\) magnitude & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\
\addlinespace
Low/high & \(R_{90}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & \itshape 0.428 & \bfseries 0.00139\\
bow shock size, \(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\
\addlinespace
Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
extinction, \(A_K\) & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\
\addlinespace
Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
\(\vert{}b\vert\) & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\
\addlinespace
High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
\(\cos \ell\) & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\
\midrule
\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\
\addlinespace
Environment: & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
Isolated vs Facing & \(\Delta R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\
\addlinespace
Environment: & \(R_{90}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
Isolated vs \hii & \(\Delta R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\
\addlinespace
Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\
\addlinespace
With/without & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\
\midrule
\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Intercomparison with other datasets \dotfill}\\
\addlinespace
MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
 & \(\Delta R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\
\addlinespace
MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
 & \(\Delta R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505
\\
\bottomrule
\end{tabular}

### 2017-04-19 papers/Paper1/quadrics-appendix.tex
Yet more fiddling with big p-value table
I decided to reverse the sign of Cohen's d for consistency with the
rank biserial correlation coefficient.  Also turn the sig/tau value
upside down so that it is usually bigger than one.  The table is now
generated automatically from the JSON file, so any further adjustments
will be easy.

--- 2017-04-17 papers/Paper1/quadrics-appendix.tex
@@
 From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
+\clearpage
+
+% Landscape table needs to go on its own page, so we need to manually
+% adjust the section counter so that it will ``belong'' to the next
+% section
+\addtocounter{section}{1}
+\sisetup{detect-all=true, detect-inline-weight=math}
+\sisetup{round-mode=figures, round-precision=2}
+\begin{landscape}
+\begin{table}
+  \setlength\tabcolsep{3pt}
+  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
+Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
+  \label{tab:big-p}
+  \input{figs/mipsgal-summary-stats-table-body.tex}
+\end{table}
+\end{landscape}
+\addtocounter{section}{-1}
 
@@
   \caption{Histogram of \(p\)-values for all non-parametric 2-sample
-    tests performed during the analysis of
-    section~\ref{sec:comp-with-observ}. (a)~Uniformly spaced linear
+    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
     bins and linear vertical axis. (b)~Uniformly spaced logarithmic
@@
 \end{figure}
+
+Results from all the statistical tests discussed in \S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
 

### 2017-04-25 papers/Paper1/quadrics-appendix.tex
Column descriptions for Table E1

@@
 \end{landscape}
+\begin{table}
+  \contcaption{Results of all statistical tests performed on observed
+    bow shock shape parameters.}
+  \begin{tabular}{p{0.9\linewidth}}
+    \toprule
+    \textit{Description of columns:}
+    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
+    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
+    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
+    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
+    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
+    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
+    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
+It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
+    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
+    (Col.~13)~Ratio of standard deviations between the two sub-samples.
+    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
+    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
+    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
+    (Col.~16)~Brown--Forsythe test for dispersion
+    \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \addtocounter{section}{-1}
@@
 \label{sec:distr-p-values}
+\addtocounter{table}{1}
 

### 2017-04-26 papers/Paper1/sec-conic.tex
Add the new quadric projection figs to paper
Minor change: update x0 to be negative for Ellipses
(and positive for hyperbolas)
Add the new figures into the quadrics section (sec 4)
Last changes:
+ Implement Parabolic fit for Projection
+ Thoughts about Wilkin solution for bowshocks (most useless)
+ Correct some equations in quadrics section

@@
 \begin{align}
-x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
+x &= a\Cos(t)+x_0 \label{eq:par-x}\\ 
 y &= b\Sin(t) \label{eq:par-y}
@@
 -\pi &< t < \pi \\
-x_0 &= \pm a - R_0 \label{eq:x0}\\
+x_0 &=  R_0 \mp a \label{eq:x0}\\
 \end{align}
@@
 \begin{align}
-R_{90} = \tan\theta_c\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
+R_{90} = \left|\tan\theta_c\right|\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
 \end{align}
@@
 \end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/projected-R90-vs-Rc}
+  \caption{Diagnostic diagram for projected quadric parameters}
+  \label{fig:projected-R90-vs-Rc}
+\end{figure}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
+  \caption{Variation with inclination angle of projected quadric parameters}
+  \label{fig:projected-R90-Rc-snapshots}
+\end{figure*}
 Once the parametrization is done, we can find the apparent shape of
@@
 \begin{align}
-x &= a\Cos(t)-x_0 \\ 
+x &= a\Cos(t)+x_0 \\ 
 y &= b\Sin(t)\cos\phi \\
@@
 \begin{align}
-R'_0 &= \pm a' - x_0\cos i \\
-R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (\pm a-R_0)\cos i
+R'_0 &= \pm a' + x_0\cos i \\
+R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} +  (R_0 \mp a)\cos i
 \end{align}
@@
   \label{eq:Aprime}\\
-  \tan\theta_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
-  \tilde{R}'_{90} &= \frac{\left[2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q})\right]^{1/2}}{\cos i f(i;\theta_c)\frac{q'}{q}}
+  \tan\theta'_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
+  \tilde{R}'_{90} &= \left(\frac{2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q}}{\frac{q'}{q}}\right)^{1/2}\frac{\sec i}{f(i;\theta_c)}
 \end{align}
@@
 
-% \begin{figure*}
-% \includegraphics[width=0.8\linewidth]{conic2}
-% \label{fig:conic2}
-% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
-% \end{figure*}
-
-Using a space of parameters like figure \ref{fig:Apqp} we can compare models with observations of real bowshocks.
-
-%The space parameter $A'$ vs $q'$ can be seen in figure (\ref{fig:Apqp}).%In this figure is assumed that we know the intrinsic Radius of curvature and $R_0$, which is not the case with
-%real observations.
+When $R'_{90}$ is measurable, diagnostic diagrams like figure (\ref{fig:projected-R90-vs-Rc}) can be used to compare with observations.
 

### 2017-05-08 papers/Paper1/quadrics-bowshock.tex
Split the paper into two parts!
* The theoretical paper is now called quadrics-bowshock.tex
* The applications paper has the original name: proplyd-bowshock.tex
Incorporate appendix into both papers
incorporate appendix
Move appendices to after references
Automatically generate data for table of tail coefficients
This is done in Rc-revisited-2016.org in the section "Write LaTeX
version of the tail analytic fit for paper".  The results are then
pasted into the latex file.
Make a start on a new observations section for the paper
Describe bow shock tracing algorithm
Add a couple of \clearpage com

--- 2016-06-10 papers/Paper1/proplyd-bowshocks.tex
@@
-\RequirePackage{amsmath}
-\documentclass[useAMS,usenatbib]{mn2e}
+%\RequirePackage{amsmath}
+\documentclass[useAMS, usenatbib, a4paper]{mnras}
+\pdfsuppresswarningpagegroup=1
 
@@
 \usepackage{booktabs}
-\usepackage{hyperref}
 \usepackage{siunitx}
 \usepackage{color}
+\usepackage{enumerate}
+\usepackage{pdflscape}
+\usepackage{rotating}
+\usepackage{hyperref}
+
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
@@
 
+\usepackage{etoolbox}
+\robustify\bfseries
+\robustify\itshape
+
+%% Bold italic
+\newcommand\hmmax{0}            % we don't need heavy fonts
+\newcommand\bmmax{1}            % reduce use of math alphabets for bold
+\usepackage{bm}
+
 %% Bundled custom packages
 \usepackage{aastex-compat}
-\usepackage{astrojournals}
+
+% Definitions needed in abstract
+\newcommand\hii{\ion{H}{ii}}
 
@@
 \begin{abstract}
-  We develop a general framework for the effects of viewing angle on
-  the apparent shape of a limb-brightened, cylindrically symmetric
-  curved shock (bow shock).  
+  Stellar bow shocks are the result of the supersonic interaction
+  between a stellar wind and its environment.  Some of these are
+  "runaways": high-velocity stars that have been ejected from a star
+  cluster.  Others are "weather vanes", where it is the local
+  interstellar medium itself that is moving, perhaps as the result of
+  a champagne flow of ionized gas from a nearby \hii{} region.  We
+  present a new two-dimensional classification scheme for the shape of
+  such bow shocks, which accounts for both the apex (pointy versus
+  flat) and the wings (open versus closed).  For different theoretical
+  bow shock models, we show how variations in the true shape can be
+  disentangled from projection effects due to variations in the
+  inclination angle.  We apply our classification scheme to three
+  different observational datasets: mid-infrared arcs around hot
+  main-sequence stars (\(N = 227\)), far-infrared arcs around luminous
+  cool stars (\(N = 7\)), and emission-line arcs around proplyds and other
+  young stars in the Orion Nebula (\(N = 18\)).  We find significant
+  differences between the three datasets: cool star bow shocks have
+  markedly more closed wings than hot star bow shocks, while
+  differences in the shape of the apex region are only marginally
+  significant.  The Orion Nebula arcs, on the other hand, have both
+  significantly more open wings and significantly flatter apices than
+  the OhotB star bow shocks.  We discuss the implications of these
+  differences for understanding the physics of the bow shock
+  interaction in the three classes of sources.
 \end{abstract}
@@
 \input{sec-conic}
-\input{sec-application}
+\input{sec-thin-shell}
+\clearpage
+\input{sec-quadrics-observations}
 \input{sec-conclusions}
-
-%% TODO Investigate newer versions of BST file from
-%% https://github.com/timj/mn2e-bst
-\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 %% All references should be put in the BibTeX file bowshocks-biblio.bib
 \bibliography{bowshocks-biblio}
+\clearpage
+\input{quadrics-appendix}
 

### 2017-05-23 papers/Paper1/sec-quadrics-observations.tex
Add a better abstract to the quadrics paper
This was originally written for the Grazyna Puebla conference
Change significance levels in p-value histogram fig
Lower value is now p=0.003, corresponding to approx 3-sigma

@@
-\newcommand\hii{\ion{H}{ii}}
-
 \section{Comparison with observations}
@@
   differences.
-\item We test if there is any statistically significant difference
-  between the bow shock shapes of the sub-samples by applying the
-  two-sample Anderson--Darling test \citep{Anderson:1952a,
-    Scholz:1987a, Makarov:2017a} to \(R_c/R_0\) and \(R_{90}/R_0\)
-  separately.  This is a non-parametric test of the \textit{null
+\item We check if there is any statistically significant difference
+  between the bow shock shapes of the sub-samples by applying three
+  different non-parametric tests to \(R_c/R_0\) and \(R_{90}/R_0\)
+  separately.  The principal test used is the two-sample
+  Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a,
+    Makarov:2017a}, which is a general test of the \textit{null
     hypothesis} that the two sub-samples are drawn from the same
@@
   would be as large as it is purely by chance if they were all were
-  drawn from the same distribution.  We adopt a threshold of
-  \(p < 0.001\) in order to confidently reject the null hypothesis and
-  declare a ``significant'' difference between the two sub-samples,
-  but we also consider the less strict threshold of \(p < 0.05\) as an
-  indicator of ``probable'' difference (see
+  drawn from the same distribution.  We consider two different
+  thresholds for significance: \(p < 0.05\) (approximately
+  2-\(\sigma\) for a normal distribution) and \(p < 0.003\) (approximately
+  3-\(\sigma\)).  We show in Appendix~\ref{sec:distr-p-values} that the
+  more stringent \(p < 0.003\) condition is required in order to
+  confidently reject the null hypothesis and declare a ``significant''
+  difference between the two sub-samples, but we also consider the
+  less strict threshold of \(p < 0.05\) as an indicator of
+  ``possible'' difference.  We supplement the general-purpose
+  Anderson--Darling test with two tests that probe specific features of
+  the sample distributions: the Mann--Whitney--Wilcoxon \(U\) test
+  \citep{Mann:1947a}, which is sensitive to differences in the central
+  value (e.g., median) and the Brown--Forsythe test
+  \citep{Brown:1974a}, which is sensitive to differences in the
+  variance, or width, of the distribution (see
   Appendix~\ref{sec:distr-p-values} for details).

### 2017-05-24 papers/Paper1/sec-quadrics-observations.tex
Discussion in text of Fig 21
Also checked the statistics with environment if we break out the FB
and FH categories instead of combining them. It turns out to make no
difference. Results in mipsgal-Rc-R90-alt-environment.pdf

@@
 
+As shown in detail in Table~\ref{tab:big-p}, there is remarkably
+little variation in the bow shock shape distributions as a function of
+most of the other parameters.  Two examples in which there is
+\textit{no} significant shape difference between the sub-samples are
+shown in Figure~\ref{fig:mipsgal-uncorrelated}.  This lack of
+difference is interesting because in both examples there are a priori
+grounds to suspect that differences might exist.  The first example (Fig.~\ref{fig:mipsgal-uncorrelated}a) is
+the bow shock environment, which was categorized in
+\citet{Kobulnicky:2016a} as ``Isolated'' (I), ``Facing a large \hii{}
+region'' (FH), ``Facing a \SI{8}{\um} bright-rimmed cloud'' (FB), and
+``Within a giant \hii{} region'' (H), and where we have merged the FH
+and FB categories, labelled ``Facing'' in the figure.\footnote{Similar
+  results are also found for the FB and FH categories separately.}
+The shapes might be expected to vary with environment because the FB
+and FH categories should be associated with ``weather vane''
+interactions \citep{Povich:2008a} between the stellar wind and a
+divergent photoevaporation flow.  This is expected to give a more open
+bow shock than in the ``runaway'' case of interaction of a moving star
+with a static environment.  In the thin-shell approximation, the
+predicted shapes are a carawilkinoid for weather vanes and a wilkinoid
+for runaways, see \S~\ref{sec:crw-scenario}.  The fact that no such
+difference is detected could be explained in one of two ways: (i)~the
+momentum ratio \(\beta\) for the weather vanes could be small, since the
+carawilkinoid becomes indistinguishable from the wilkinoid as
+\(\beta \to 0\), or (ii)~many of the bow shocks classified as ``Isolated''
+might also be weather vanes rather than runaways.
+
+The second example (Fig.~\ref{fig:mipsgal-uncorrelated}b) divides the
+sources according to whether or not \citet{Kobulnicky:2016a} judged
+there to be multiple candidates for identity of the central star that
+drives the bow shock.  If the central star were to be misidentified,
+then the measured value of \(R_0\) would be erroneous, which would
+increase the dispersion in both \(R_c/R_0\) and \(R_{90}/R_0\).  The
+fact that no significant difference is seen in the shape distributions
+between sources with/without multiple candidates implies that such
+mistakes in identification of the central star must be rare.
+
 \subsection{Far-infrared arcs around late-type stars}

### 2017-05-25 papers/Paper1/quadrics-appendix.tex
Make table of equivalence between p-values and number of sigmas
Add the 3-star vs 4+5-star statistics
And lots of minor changes to the tables and figures.

@@
     (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
-    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
-    (Col.~16)~Brown--Forsythe test for dispersion
+    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive 
+    (Col.~16)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
     \\
@@
     bins and logarithmic vertical axis, with all values
-    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
-    lines shows the traditional threshold values for significance:
-    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
-    uniform distribution of \(p\)-values that would be expected if the
-    null hypothesis were always true, that is, if no significant
+    \(p \le 10^{-6}\) included in the leftmost bin.  Short thin vertical
+    lines above the horizontal axis show the individual value.  The
+    thick vertical dashed lines shows the traditional threshold values
+    for significance: \(p = 0.003\) (\(\approx 3 \sigma\)) and
+    \(p = 0.05\) (\(\approx 2 \sigma\)). The red solid line shows the uniform
+    distribution of \(p\)-values that would be expected if the null
+    hypothesis were always true, that is, if no significant
     correlations existed.}

### 2017-05-25 papers/Paper1/sec-quadrics-observations.tex
Add the 3-star vs 4+5-star statistics
And lots of minor changes to the tables and figures.

@@
 5-star sources, although the higher-rated sources are shifted slightly
-to the upper right.  This is probably due to higher-rated sources
-being on average bigger, as will be discussed further below.  The bulk
-of the sources are concentrated around the paraboloid line, with
-\(1 < R_c/R_0 < 2.5\), and \(1.2 < R_{90}/R_0 < 2\).  But significant
-minorities are found in three other regions: (1)~a clump with
-\(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\) at
-\(R_c/R_0 \approx 2\); and (3)~a broad horizontal tail towards higher
+to the upper right.  Possible reasons for this are discussed in
+\S~\ref{sec:corr-shape} below.
+% This is probably due to higher-rated sources
+% being on average bigger, as will be discussed further below.
+The bulk of the sources are concentrated around the paraboloid line,
+with \(1 < R_c/R_0 < 2.5\), and \(1.2 < R_{90}/R_0 < 2\).  But
+significant minorities are found in three other regions: (1)~a clump
+with \(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\)
+at \(R_c/R_0 \approx 2\); and (3)~a broad horizontal tail towards higher
 \(R_c\) at \(R_{90}/R_0 \la 2\).
@@
 sources according to whether or not \citet{Kobulnicky:2016a} judged
-there to be multiple candidates for identity of the central star that
-drives the bow shock.  If the central star were to be misidentified,
-then the measured value of \(R_0\) would be erroneous, which would
-increase the dispersion in both \(R_c/R_0\) and \(R_{90}/R_0\).  The
+there to be multiple candidates for the identity of the central star
+that drives the bow shock.  If the central star were to be
+misidentified in a significant number of sources, then the measured
+value of \(R_0\) for those sources would be erroneous, which would
+increase the scatter in both \(R_c/R_0\) and \(R_{90}/R_0\).  The
 fact that no significant difference is seen in the shape distributions
@@
 mistakes in identification of the central star must be rare.
+
+We also tested all the other source parameters listed in
+\citeauthor{Kobulnicky:2016a}'s catalog, finding no significant shape
+differences for sources with/without \SI{8}{\um} emission, with
+low/high extinction, closer/farther from the Galactic plane, or
+closer/farther from the Galactic center. Details are given in
+Table~\ref{tab:big-p}.  In all these cases, differences in mean or
+median \(R_{90}/R_0\) less than \(0.06\) and in \(R_c/R_0\) less than
+\(0.16\) are found, which are not significant even at the 2-\(\sigma\)
+level.
+
+The only parameters that \emph{do} show a possible correlation with
+the bowshock shape are the bow shock angular size, \(R_0\), and the
+extinction-corrected magnitude of the central star, \(H_0\), which are
+illustrated
+
+As mentioned in \S~\ref{sec:ob-shapes} there is also a shape
+difference between the 3-star sources and the 4/5-star sources (see
+Fig.~\ref{fig:mipsgal-shapes}b).  The \(p\)-values of statistical
+tests (see Table~\ref{tab:big-p}) indicate that this is much more
+significant than any correlation with the other parameters discussed
+in this section (\(p < 10^{-4}\) for \(R_{90}/R_0\) and
+\(p < 10^{-5}\) for \(R_c/R_0\)).  This means that it cannot be simply
+due to the tendency of the higher-rated sources to have larger angular
+sizes.  However, the subjective nature of the star ratings makes this
+hard to interpret.
 

### 2017-05-25 papers/Paper1/sec-quadrics-observations.tex
Improve captions for figs 21 and 22

@@
 
+\begin{figure*}
+  \centering
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
+    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
+  \end{tabular}
+  \caption[]{Example comparisons between the distribution of bowshock
+    shapes when the sources are divided into two or more sub-samples
+    according to the value of a categorical parameter.  Contours show
+    the KDE of the distribution of each sub-sample for all 3-, 4-, and
+    5-star sources, while filled circles show 5-star sources
+    only. Inset histograms show the marginal distributions on the two
+    shape axes. (a)~Source environment, divided into three
+    sub-samples: ``Isolated'' (purple symbols and purple filled
+    contours), ``Facing \hii{} region or \SI{8}{\um} bright-rimmed
+    cloud'' (orange symbols and orange-brown hollow continuous
+    contours), and ``Within \hii{} region'' (green symbols and green
+    hollow dashed contours). (b)~Uncertainty in stellar source
+    identification, divided into two sub-samples: ``Multiple
+    candidates for stellar source'' (green symbols and green filled
+    contours) and ``Single candidate for stellar source'' (orange
+    symbols and orange-brown hollow continuous contours).}
+  \label{fig:mipsgal-uncorrelated}
+\end{figure*}
+
 The most significant linear correlation between any pair of parameters
@@
 depends only weakly on \(d\) and is more influenced by other factors.
-
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
-  \end{tabular}
-  \caption[]{Lack of significant correlation of bow shock shape with
-    (a) environment, and (b) uncertainty in stellar source
-    identification.}
-  \label{fig:mipsgal-uncorrelated}
-\end{figure*}
 
@@
   \end{tabular}
-  \caption[]{Comparison between the distribution of bowshock shapes
-    when the sources are divided into two sub-samples according to the
-    value of another parameter. (a)~Bow shock angular size, \(R_0\).
-    (b)~Extinction-corrected \(H\)-band magnitude of the stellar
-    source.}
+  \caption[]{As Fig.~\ref{fig:mipsgal-uncorrelated} but for median
+    splits of continuous parameters. (a)~Bow shock angular size,
+    \(R_0\), divided into two equal-sized sub-samples: large (blue
+    symbols and blue filled contours) and small (red symbols and red
+    hollow contours).  (b)~Extinction-corrected \(H\)-band magnitude
+    of the stellar source, divided into two equal-sized sub-samples:
+    bright (red symbols and orange filled contours) and faint (green
+    symbols and green hollow contours).}
   \label{fig:mipsgal-correlated}
@@
 extinction-corrected magnitude of the central star, \(H_0\), which are
-illustrated
+illustrated in Figure~\ref{fig:mipsgal-correlated}.
 
@@
 sizes.  However, the subjective nature of the star ratings makes this
-hard to interpret.
+result hard to interpret.
 

### 2017-05-26 Stellar-Bowshocks-2017/mipsgal-summary-stats-table-body.tex
Discussion and tweaking of box plot figure

@@
 %%% Table automatically generated from mipsgal-summary-stats.tab
-%%% 2017-04-19 13:16:10.731012
+%%% 2017-05-26 13:27:55.244997
 %%%
@@
 	\begin{tabular}{@{} ll @{\quad } S[round-mode=places]S[round-mode=places] S[round-mode=places]S[round-mode=places] SS SS @{\quad\quad\quad} SSS[round-mode=places] @{\quad} S@{}S@{}S @{}}\toprule
-	  & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\
+	  & {Dependent} & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\
 	  {Comparison} & {Variable} & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)} & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)} & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)} & {\((\sigma/\!\sqrt n)_{\text{A}}\)} & {\((\sigma/\!\sqrt n)_{\text{B}}\)} & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)} & \multicolumn{1}{c}{Anderson--Darling} & \multicolumn{1}{c}{Rank biserial} &  \multicolumn{1}{c}{Brown--Forsythe}\\
 	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)} & {(3)} & {(4)} & {(5)} & {(6)} & {(7)} & {(8)} & {(9)} & {(10)}  & {(11)} & {(12)} & {(13)} & {(14)} & {(15)} & {(16)} \\  
-	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\
+	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous independent variables \dotfill}\\
 \addlinespace
-Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
-\(H\) magnitude & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\
+Faint/bright & \(R_{90} / R_{0}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
+\(H\) magnitude & \(\Delta R_{90} / R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & \itshape 0.428 & \bfseries 0.00139\\
-bow shock size, \(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\
+Low/high & \(R_{90} / R_{0}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & 0.428 & \bfseries 0.00139\\
+bow shock size, \(R_0\) & \(\Delta R_{90} / R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
-extinction, \(A_K\) & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\
+Low/high & \(R_{90} / R_{0}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
+extinction, \(A_K\) & \(\Delta R_{90} / R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
-\(\vert{}b\vert\) & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\
+Low/high & \(R_{90} / R_{0}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
+\(\vert{}b\vert\) & \(\Delta R_{90} / R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\
 \addlinespace
-High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
-\(\cos \ell\) & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
-\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\
+High/low & \(R_{90} / R_{0}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
+\(\cos \ell\) & \(\Delta R_{90} / R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
+\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c} / R_{0}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\
 \midrule
-\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\
+\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical independent variables \dotfill}\\
 \addlinespace
-Environment: & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
-Isolated vs Facing & \(\Delta R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\
+Environment: & \(R_{90} / R_{0}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
+Isolated vs Facing & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c} / R_{0}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\
 \addlinespace
-Environment: & \(R_{90}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
-Isolated vs \hii & \(\Delta R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\
+Environment: & \(R_{90} / R_{0}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
+Isolated vs \hii & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c} / R_{0}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\
 \addlinespace
-Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
-source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
-\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\
+Single/multiple & \(R_{90} / R_{0}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
+source candidate & \(\Delta R_{90} / R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
+\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c} / R_{0}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\
 \addlinespace
-With/without & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
-\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
-\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\
+With/without & \(R_{90} / R_{0}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
+\SI{8}{\um} emission & \(\Delta R_{90} / R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
+\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c} / R_{0}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\
+\addlinespace
+3-star vs (4+5)-star & \(R_{90} / R_{0}\) & 1.661 & 1.812 & 0.288 & 0.286 & 0.247 & 0.216 & 0.025 & 0.029 & \bfseries 0.328 & \bfseries 0.525 & 0.99 & \bfseries 8.23e-05 & \bfseries 2.63e-05 & 0.403\\
+ & \(\Delta R_{90} / R_{90}\) & 0.189 & 0.19 & 0.162 & 0.161 &   &   & 0.014 & 0.017 & -0.007 & 0.009 & 0.994 & 0.809 & 0.927 & 0.561\\
+\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(R_{c} / R_{0}\) & 1.632 & 2.0 & 0.91 & 0.764 & 0.106 & 0.061 & 0.079 & 0.079 & \bfseries 0.386 & \bfseries 0.431 & 0.84 & \bfseries 1.47e-05 & \bfseries 7.66e-07 & 0.762\\
 \midrule
@@
 \addlinespace
-MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
- & \(\Delta R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\
+MIPS vs Orion & \(R_{90} / R_{0}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
+ & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c} / R_{0}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\
 \addlinespace
-MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
- & \(\Delta R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505
+MIPS vs RSG & \(R_{90} / R_{0}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
+ & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c} / R_{0}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505
 \\

### 2017-05-26 papers/Paper1/quadrics-appendix.tex
Discussion and tweaking of box plot figure

@@
     (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
-    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
+    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source, as in steps~\ref{step:R0} and \ref{step:R90} of \S~\ref{sec:autom-trac-fitt}.
+Note that in the case of \(R_c\), this is \(\epsilon(R_0)\), and so is not a direct measure of the observational uncertainty in \(R_c\).
     (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 

### 2017-05-26 papers/Paper1/sec-quadrics-observations.tex
Discussion and tweaking of box plot figure

@@
 \item Make our own estimate of the axial size, \(R_0\), of the bow
-  shock by calculating the mean and standard deviation of \(R_k\) over
-  all points \(C_k\) with \(|\theta_k| \le 10\degr\).  Note that this is
-  distinct from the nominal value of \(R_0\) given in the
-  \citet{Kobulnicky:2016a} catalog, which was ``measured by eye''.
+  shock by calculating the mean of \(R_k\) over all points \(C_k\)
+  with \(|\theta_k| \le 10\degr\).  Note that this is distinct from the
+  nominal value of \(R_0\) given in the \citet{Kobulnicky:2016a}
+  catalog, which was ``measured by eye''.  We denote by
+  \(\epsilon(R_0)\) the standard deviation of the \(R_k\) that go into
+  calculating \(R_0\).\label{step:R0}
 \item Estimate the radius of curvature, \(R_c\), by fitting a circle
@@
 \item Determine two separate estimates, \(R_{90+}\) and \(R_{90-}\),
-  of the perpendicular radius, \(R_{90}\), by taking the mean and
-  standard deviation of \(R_k\) over all points \(C_k\) with
+  of the perpendicular radius, \(R_{90}\), by taking the mean of
+  \(R_k\) over all points \(C_k\) with
   \(|\theta_k - 90\degr| \le 10\degr\) for \(R_{90+}\), and with
-  \(|\theta_k + 90\degr| \le 10\degr\) for \(R_{90-}\).
+  \(|\theta_k + 90\degr| \le 10\degr\) for \(R_{90-}\).  The average of the
+  two standard deviations of the \(R_k\) that contribute to
+  \(R_{90+}\) and \(R_{90-}\) is denoted by \(\epsilon(R_{90})\).\label{step:R90}
 \end{enumerate}
@@
     uses an anisotropic gaussian kernel with bandwidths of
-    \(0.18 \times 0.12\). Images of representative 4- and 5-star sources at
-    different points on the \(R_c\)--\(R_{90}\) plane are also shown.}
+    \(0.18 \times 0.12\). Thumbnail images of representative 4- and 5-star
+    sources at different points on the \(R_c\)--\(R_{90}\) plane are
+    also shown. The angular scale of each image is indicated by a
+    yellow circle of diameter \(7.5''\), centered on the stellar
+    source.}
   \label{fig:mipsgal-shapes}
@@
     the KDE of the distribution of each sub-sample for all 3-, 4-, and
-    5-star sources, while filled circles show 5-star sources
+    5-star sources, while filled circle symbols show 5-star sources
     only. Inset histograms show the marginal distributions on the two
@@
     line, the 1st-to-9th interdecile range by error bars, and outliers
-    by diamonds.  A 5-sample Anderson--Darling test is performed for
-    each dependent variable, with resultant \(p\)-value given at the
-    bottom of each panel.  It is apparent that the dispersion in
-    \(R_{90} / R_0\) (upper panel) increases systematically with
-    \(R_0\), although the central value is roughly constant.  No clear
-    systematic changes are apparent in \(R_c / R_{90}\) (middle
-    panel).  (b)~As (a), but partitioning on the extinction-corrected
-    \(H\)-band magnitude, \(H_0\).  Note that sub-samples are plotted
-    in order of \textit{decreasing} magnitude to allow comparison
-    between (a) and (b), given the negative correlation between
-    \(H_0\) and \(R_0\) (see Fig.~\ref{fig:mipsgal-pairplot}).}
+    by diamonds.  A 5-sample Anderson--Darling test and Brown--Forsythe
+    test is performed for each dependent variable, with resultant
+    \(p\)-value given at the bottom of each panel.   It is apparent
+    that the dispersion in \(R_{90} / R_0\) (upper panel) increases
+    systematically with \(R_0\), although the central value is roughly
+    constant.  No clear systematic changes are apparent in
+    \(R_c / R_{90}\) (middle panel).  (b)~As (a), but partitioning on
+    the extinction-corrected \(H\)-band magnitude, \(H_0\).  Note that
+    sub-samples are plotted in order of \textit{decreasing} magnitude
+    to allow comparison between (a) and (b), given the negative
+    correlation between \(H_0\) and \(R_0\) (see
+    Fig.~\ref{fig:mipsgal-pairplot}).}
   \label{fig:mipsgal-boxplot}
@@
 median \(R_{90}/R_0\) less than \(0.06\) and in \(R_c/R_0\) less than
-\(0.16\) are found, which are not significant even at the 2-\(\sigma\)
-level.
+\(0.16\) are found, corresponding to rank biserial correlation
+coefficients (a non-parametric dimensionless measure of the difference
+between two samples, see Appendix~\ref{sec:distr-p-values}) of
+\(r_b < 0.15\), which are not significant even at the 2-\(\sigma\) level.
 
@@
 extinction-corrected magnitude of the central star, \(H_0\), which are
-illustrated in Figure~\ref{fig:mipsgal-correlated}.
+illustrated in Figure~\ref{fig:mipsgal-correlated}.  In both cases,
+the general purpose Anderson--Darling test indicates differences in the
+sub-sample distributions of \(R_{90} / R_0\) at the 2-\(\sigma\) level.  It
+is apparent from the histograms shown in the right-hand inset graphs
+of Figure~\ref{fig:mipsgal-correlated}a that in the case of the
+small/large \(R_0\) sub-samples it is the width rather than the
+central tendency of the distributions that is different, which is
+confirmed by the more specific Brown--Forsythe test, which indicates a
+difference between the sub-sample dispersions at the 3-\(\sigma\) level.
+In the case of the faint/bright \(H_0\) sub-samples
+(Fig.~\ref{fig:mipsgal-heteroscedastic}b), it is less clear what
+feature of the distributions differ.
+
+In order to investigate these effects in more detail and look for
+systematic trends, we divide the independent parameter (\(R_0\) or
+\(H_0\)) into 5 rather than 2 equal-sized sub-samples, with results
+shown as box plots in Figure~\ref{fig:mipsgal-boxplot}.  A systematic
+increase with \(R_0\) in the dispersion of \(R_{90}/R_0\) (upper panel
+of Fig.~\ref{fig:mipsgal-boxplot}a) is apparent from both the
+interquartile range (colored boxes) and interdecile range (error
+bars).  As a check on whether observational uncertainties might be
+contributing to this trend, the third and fourth rows of box plots
+show the statistics for, respectively, the fractional asymmetry of the
+bowshock wings and the standard deviation, \(\epsilon(R_{90})\), of the
+individual points on the bow shock that go into determining \(R_{90}\)
+(see step~\ref{step:R90} of the tracing/fitting methodology described
+in \S~\ref{sec:autom-trac-fitt}).  It can be seen that neither of
+these quantities tends to increase with \(R_0\), and in fact there is
+a significant \emph{decrease} in \(\epsilon(R_{90})\) with \(R_0\).  This
+implies that the increase with angular size of the diversity of bow
+shock wing shapes is real, and not due to observational uncertainties.  
+On the other hand, the fact that no clear trends are evident as a
+function of source magnitude \(H_0\) (Fig.~\ref{fig:mipsgal-boxplot}b)
+leads us to suspect that the \(p < 0.05\) result obtained for the
+2-sample Anderson--Darling test was a \emph{false positive}, which is
+also supported by the analysis in Appendix~\ref{sec:distr-p-values}
+and Figure~\ref{fig:histo-p-values}.
+
+So, the only correlation that survives scrutiny is the increase in
+dispersion of \(R_{90}/R_0\) with increasing \(R_0\), which is finally
+presented in the greatest detail in
+Figure~\ref{fig:mipsgal-heteroscedastic}, where eschew any binning and
+perform linear regressions of the individual sources as a function of
+\(\log_{10} R_0\).  As expected from the previous 2-sample and
+5-sample analyses, the regression of \(R_{90}/R_0\) is almost flat,
+with a low correlation coefficient.
 

### 2017-05-29 papers/Paper1/sec-quadrics-observations.tex
Finish description of OB stellar bow shocks

@@
     negative) slope for the largest bow shocks.  We therefore repeat
-    the linear fit, but after excluding sources with
-    \(\log_{10} R_0 > 1.4\), with results shown by the red dotted
-    line.  The bottom panel shows the bow shock wings asymmetry
-    parameter, \(|R_{90+} - R_{90-}| / R_{90}\), together with a
-    linear fit.}
+    the linear fit, but after excluding sources with \(R_0 > 25''\),
+    with results shown by the red dotted line.  The bottom panel shows
+    the bow shock wings asymmetry parameter,
+    \(|R_{90+} - R_{90-}| / R_{90}\), together with a linear fit.
+    Symbol size indicates the star rating of each source, from 3-star
+    (smallest) to 5-star (largest).}
   \label{fig:mipsgal-heteroscedastic}
@@
 presented in the greatest detail in
-Figure~\ref{fig:mipsgal-heteroscedastic}, where eschew any binning and
-perform linear regressions of the individual sources as a function of
-\(\log_{10} R_0\).  As expected from the previous 2-sample and
+Figure~\ref{fig:mipsgal-heteroscedastic}, where we eschew any binning
+and perform linear regressions of the individual sources as a function
+of \(\log_{10} R_0\).  As expected from the previous 2-sample and
 5-sample analyses, the regression of \(R_{90}/R_0\) is almost flat,
-with a low correlation coefficient.
+with a low correlation coefficient, whereas a regression of the
+absolute residuals to this fit against \(\log_{10} R_0\) shows a
+significant positive slope.  This increase in dispersion of shape with
+angular size is only evident for \(R_0 < 30''\), becoming flat at the
+largest sizes (see middle panel of
+Fig.~\ref{fig:mipsgal-heteroscedastic}).
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \label{fig:herschel-compare-mipsgal}
-\end{figure}
+\end{figure*}
 
@@
   \label{fig:ll-compare-mipsgal}
-\end{figure}
+\end{figure*}
 

### 2017-06-08 LL-shapes-2017/new-observed-R90-vs-Rc.py
Add Herschel material to paper
And add KDE for Herschel and Orion arcs in the figures

@@ -1,5 +1,5 @@
 T=[["073-227", "147.26", "0.65", "6.47", "-999.00", "3.12", "1.09", "3.20", "-999.00", "5.22"], ["109-246", "89.67", "1.34", "27.23", "1.83", "-999.00", "2.11", "6.22", "2.65", "-999.00"], ["000-400", "254.03", "0.31", "3.37", "2.46", "2.34", "0.58", "2.21", "2.59", "2.25"], ["005-514", "262.64", "0.44", "2.76", "-999.00", "-999.00", "0.61", "1.71", "1.50", "-999.00"], ["012-407", "231.47", "-999.00", "-999.00", "-999.00", "-999.00", "0.99", "1.86", "-999.00", "1.92"], ["030-524", "234.09", "0.16", "1.99", "2.33", "2.91", "0.27", "3.84", "2.17", "3.10"], ["042-628", "259.60", "0.69", "2.77", "1.67", "-999.00", "1.19", "1.87", "1.58", "2.32"], ["LL1", "198.63", "0.96", "2.61", "3.05", "2.05", "1.54", "2.46", "2.14", "2.28"], ["069-601", "212.20", "0.21", "2.90", "2.42", "3.39", "0.42", "2.05", "2.13", "2.09"], ["4285-458", "721.18", "-999.00", "-999.00", "-999.00", "-999.00", "0.27", "2.56", "1.68", "2.44"], ["LL3", "566.33", "0.26", "2.35", "-999.00", "-999.00", "0.55", "1.94", "1.54", "2.41"], ["LL4", "593.14", "0.24", "5.81", "4.67", "3.35", "0.43", "2.35", "2.69", "2.93"], ["4468-605", "471.31", "0.28", "2.47", "1.35", "1.52", "0.53", "1.80", "2.58", "1.58"], ["116-3101", "463.92", "0.22", "1.41", "1.72", "1.74", "0.31", "1.42", "1.52", "1.84"], ["266-558", "218.16", "0.51", "1.79", "-999.00", "1.25", "0.94", "1.92", "1.98", "2.94"], ["308-3036", "484.14", "0.29", "1.35", "-999.00", "1.05", "0.52", "1.50", "1.49", "2.08"], ["LL5", "369.55", "0.40", "2.63", "1.59", "2.69", "0.78", "3.03", "2.22", "4.40"], ["LL6", "485.83", "0.33", "6.01", "3.77", "4.3
[…]

### 2017-06-14 papers/Paper1/sec-quadrics-observations.tex
Add Herschel material to paper
And add KDE for Herschel and Orion arcs in the figures
Finish caption for Figure 25

@@
   \centering
+  \setkeys{Gin}{width=0.48\linewidth}
+  \includegraphics[trim=10 0 60 30, clip]{figs/alphaori-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/rhya-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/uuaur-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
+  \caption{RSG and AGB shells observed with Herschel.  Selected
+    Class~I sources (``fermata-like'') from the MESS survey
+    \citet{Cox:2012a}.  Left panels show PACS \SI{70}{\um} surface
+    brightness (blue) and \SI{160}{\um} (orange).  Right panels show
+    tracing of the bow shock arc (red symbols) and circle fit (magenta
+    lines and symbols) superimposed on a low-contrast image of the
+    \SI{70}{\um} surface brightness.}
+  \label{fig:herschel-arc-fits}
+\end{figure*}
+
+\begin{figure*}
+  \centering
   \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
-  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.}
+  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.  }
   \label{fig:herschel-compare-mipsgal}

### 2017-07-05 papers/Paper1/sec-quadrics-observations.tex
Description of Cox's Herschel source classes I-IV

@@
 
+We obtain a second sample of bow shocks from a far-infrared survey
+\citep{Cox:2012a} of circumstellar shells around asymptotic giant
+branch (AGB) stars and cool supergiants, obtained as part of the
+\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
+\citep{Groenewegen:2011a}.  The survey sources were divided into four
+classes, according to the overall shape of the extended emission at
+\SI{70}{\um}: ``fermata~\textfermata'', or arcs (Class~I);
+``eyes~\eye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
+``irregular'' (Class~IV).  Of these, only the Class~I sources clearly
+correspond to bow shocks, which represent 22 out of 50 total sources.
+
 \subsection{Stationary emission line arcs in M42}

### 2017-07-05 papers/Paper1/sec-quadrics-observations.tex
Use more whacky symbols

@@
 \SI{70}{\um}: ``fermata~\textfermata'', or arcs (Class~I);
-``eyes~\eye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
-``irregular'' (Class~IV).  Of these, only the Class~I sources clearly
+``eyes~\faEye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
+``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I sources clearly
 correspond to bow shocks, which represent 22 out of 50 total sources.

### 2017-07-05 papers/Paper1/sec-quadrics-observations.tex
Choose 9 additional Herschel sources to analyse
The actual data is excluded from the repo, but it can be automatically
downloaded by the scripts in Stellar-Bowshocks-2017/RSG/wget-scripts

@@
 ``eyes~\faEye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
-``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I sources clearly
-correspond to bow shocks, which represent 22 out of 50 total sources.
+``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I
+sources clearly correspond to bow shocks, which represent 23 out of 50
+total sources detected with extended emission.  For our sample, we
+select the 7 Class~I sources where the shape parameters can be
+unambiguously measured, and which are shown in
+Figure~\ref{fig:herschel-arc-fits}.  For some of the remaining Class~I
+sources (Fig.~1 of \citealp{Cox:2012a}), the bow shock becomes too
+diffuse around the ``sides'', so that \(R_{90}\) cannot be reliably
+determined (examples include \(\theta\)~Aps and )
 

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/CWLEO_wget_data.sh

@@ -1,0 +1,13 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/CWLEO-1_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/CWLeo-160_10_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/CWLEO-all_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/CWLeo-70_3_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/CWLEO_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/CWLEO_100_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/CWLEO_160_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/EPAQR_wget_data.sh

@@ -1,0 +1,10 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/EPAQR_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/EPAqr-160_4_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/EPAqr-70_3_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/EPAQR_70_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/KHICYG_wget_data.sh

@@ -1,0 +1,8 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/KHICYG_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/KHICYG_70_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/OMICET_wget_data.sh

@@ -1,0 +1,10 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/OmiCet-160_5_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/OmiCet-70_4_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/OMICET_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/OMICET_160_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/RCAS_wget_data.sh

@@ -1,0 +1,12 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RCAS_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RCAS_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RCAS-1_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RCAS-all_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RCAS-1_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RCAS-all_70_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/RTVIR_wget_data.sh

@@ -1,0 +1,12 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RTVIR-1_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RTVIR-all_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RTVIR-1_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RTVIR_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RTVIR_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/RTVIR-all_70_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/WAQL_wget_data.sh

@@ -1,0 +1,14 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAql-70_5_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAQL_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAQL-1_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAQL-all_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAQL-all_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAQL-1_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAql-160_7_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WAQL_70_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/WPIC_wget_data.sh

@@ -1,0 +1,12 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WPIC-all_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WPIC-1_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WPIC_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WPIC-1_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WPIC_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/WPIC-all_160_pixfrac10.0.mod.fits"

### 2017-07-05 Stellar-Bowshocks-2017/RSG/wget-scripts/XHER_wget_data.sh

@@ -1,0 +1,10 @@
+#!/bin/sh
+#
+# To run as an executable on a unix platform, do the following:
+# chmod 775 wget_data.bat
+# ./wget_data.bat
+#
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/XHER_70_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/XHer-160_7_AFGL190.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/XHER_160_pixfrac10.0.mod.fits"
+wget -x "https://irsa.ipac.caltech.edu:443/data/Herschel/MESS/images/XHer-70_3_AFGL190.mod.fits"

### 2017-07-06 papers/Paper1/sec-quadrics-observations.tex
Add second batch image figure to the paper

@@
   \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/rcas-imageplot}
   \caption{RSG and AGB shells observed with Herschel.  Selected
     Class~I sources (``fermata-like'') from the MESS survey
-    \citet{Cox:2012a}.  Left panels show PACS \SI{70}{\um} surface
+    \citet{Cox:2012a}, where the arc structure is particularly clear
+    and symmetrical.  Left panels show PACS \SI{70}{\um} surface
     brightness (blue) and \SI{160}{\um} (orange).  Right panels show
@@
   \centering
+  \setkeys{Gin}{width=0.48\linewidth}
+  \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
+  \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
+  \caption{As Fig~\ref{fig:herschel-arc-fits}, but for a further 8
+    Class~I sources from \citet{Cox:2012a} where the arc structure is
+    more diffuse, weak, and/or asymmetric. For CW~Leo only (top-left),
+    the right-hand panel shows a grayscale image of the \SI{160}{\um}
+    rather than \SI{80}{\um} emission.}
+  \label{fig:herschel-arc-fits-poor}
+\end{figure*}
+
+\begin{figure*}
+  \centering
   \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
-  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.  }
+  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.}
   \label{fig:herschel-compare-mipsgal}

### 2017-07-06 papers/Paper1/sec-quadrics-observations.tex
Update description of Cox sources in text

@@
     the right-hand panel shows a grayscale image of the \SI{160}{\um}
-    rather than \SI{80}{\um} emission.}
+    rather than \SI{70}{\um} emission.}
   \label{fig:herschel-arc-fits-poor}
@@
 \citep{Groenewegen:2011a}.  The survey sources were divided into four
-classes, according to the overall shape of the extended emission at
-\SI{70}{\um}: ``fermata~\textfermata'', or arcs (Class~I);
-``eyes~\faEye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
-``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I
-sources clearly correspond to bow shocks, which represent 23 out of 50
-total sources detected with extended emission.  For our sample, we
-select the 7 Class~I sources where the shape parameters can be
-unambiguously measured, and which are shown in
-Figure~\ref{fig:herschel-arc-fits}.  For some of the remaining Class~I
-sources (Fig.~1 of \citealp{Cox:2012a}), the bow shock becomes too
-diffuse around the ``sides'', so that \(R_{90}\) cannot be reliably
-determined (examples include \(\theta\)~Aps and )
+classes by \citeauthor{Cox:2012a}, according to the overall shape of
+the extended emission at \SI{70}{\um}: ``fermata~\textfermata'', or
+arcs (Class~I); ``eyes~\faEye'' (Class~II); ``rings~{\Large
+  \(\odot\)}'' (Class~III), and ``irregular~\staveXXV'' (Class~IV).  Of
+these, only the Class~I sources clearly correspond to bow shocks,
+which represent 22 out of 50 total sources detected with extended
+emission.  For our sample, we select the 16 Class~I sources where the
+shape parameters can be reliably measured, and which are shown in
+Figures~\ref{fig:herschel-arc-fits}
+and~\ref{fig:herschel-compare-mipsgal}.  In most sources, the bow
+shock shell is most clearly visible in the \SI{70}{\um} band, with the
+exception being CW~Leo where the \SI{180}{\um} band is used instead.
+
+The remaining six Class~I sources (Fig.~1 of \citealp{Cox:2012a}) are
+too asymmetrical or irregular to reliably determine \(R_{c}\) and
+\(R_{90}\), and are therefore excluded from our sample.
 

### 2017-08-08 papers/Paper1/sec-quadrics-observations.tex
Finally get back into writing. Describe fits to Herschel arcs

@@
   \setkeys{Gin}{width=0.48\linewidth}
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/alphaori-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}\\
+    (c) & (d) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/rhya-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}\\
+    (e) & (f) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/uuaur-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}\\
+    (g) & (h) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/rcas-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/rcas-imageplot}
+  \end{tabular}
   \caption{RSG and AGB shells observed with Herschel.  Selected
@@
     lines and symbols) superimposed on a low-contrast image of the
-    \SI{70}{\um} surface brightness.}
+    \SI{70}{\um} surface brightness. (a)~\(\alpha\)~Ori. (b)~\(\mu\)~Cep.
+    (c)~R~Hya. (d)~R~Leo. (e)~UU~Aur. (f)~V1934~Sgr. (g)~X~Pav.
+    (h)~R~Cas.}
   \label{fig:herschel-arc-fits}
@@
   \setkeys{Gin}{width=0.48\linewidth}
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot} \\
+    (c) & (d) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot} \\
+    (e) & (f) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot} \\
+    (g) & (h) \\
     \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
-  \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
+    & \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
+  \end{tabular}
   \caption{As Fig~\ref{fig:herschel-arc-fits}, but for a further 8
     Class~I sources from \citet{Cox:2012a} where the arc structure is
-    more diffuse, weak, and/or asymmetric. For CW~Leo only (top-left),
-    the right-hand panel shows a grayscale image of the \SI{160}{\um}
-    rather than \SI{70}{\um} emission.}
+    more diffuse, weak, and/or asymmetric. (a)~CW~Leo. For this source
+    only, the right-hand panel shows a grayscale image of the
+    \SI{160}{\um} rather than \SI{70}{\um}
+    emission. (b)~EP~Aqr. (c)~\(\chi\)~Cyg. (d)~RT~Vir. (e)~W~Aql. (f)~W~Pic. (g)~R~Scl.
+    (h)~\(\theta\)~Aps.}
   \label{fig:herschel-arc-fits-poor}
@@
 Figures~\ref{fig:herschel-arc-fits}
-and~\ref{fig:herschel-compare-mipsgal}.  In most sources, the bow
-shock shell is most clearly visible in the \SI{70}{\um} band, with the
-exception being CW~Leo where the \SI{180}{\um} band is used instead.
+and~\ref{fig:herschel-arc-fits-poor}. The remaining six Class~I
+sources (Fig.~1 of \citealp{Cox:2012a}) are too asymmetrical or
+irregular to reliably determine \(R_{c}\) and \(R_{90}\), and are
+therefore excluded from our sample.
 
-The remaining six Class~I sources (Fig.~1 of \citealp{Cox:2012a}) are
-too asymmetrical or irregular to reliably determine \(R_{c}\) and
-\(R_{90}\), and are therefore excluded from our sample.
+In most sources, the bow shock shell is most clearly visible in the
+\SI{70}{\um} band, with the exception being CW~Leo where the
+\SI{180}{\um} band is used instead.  In several sources, the shell is
+split into multiple filaments, with the clearest example being
+\(\alpha\)~Ori (Betelgeuse), shown in
+Figure~\ref{fig:herschel-arc-fits}(a).  For such sources, we take the
+outer envelope of the filaments as the bow shock arc.  Given this
+complication, and the fact that the angular resolution relative to the
+bow shock size is much better than in the MIPSGAL sources, we judge
+that the arc tracing is best performed by eye and this is carried out
+using the SAOImage~DS9 FITS viewer \citep{Joye:2003a}, with results
+shown as small red open circles in Figures~\ref{fig:herschel-arc-fits}
+and~\ref{fig:herschel-arc-fits-poor}.  Subsequently, the bow shock
+parameters \(R_0\), \(R_{90}\), and \(R_c\) are determined by circle
+fits, as in steps 5--8 of \S~\ref{sec:autom-trac-fitt}, with results
+shown in magenta on the figures.
 

### 2017-08-09 papers/Paper1/sec-quadrics-observations.tex
Finish description of MIPS/Herschel comparison

@@
   \centering
-  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
-  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.}
+  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
+  \caption[]{Comparison of bow shock shapes between Herschel RSG/AGB
+    arcs (large red symbols and hollow red contours) and MIPSGAL OB
+    star arcs (small purple symbols and filled purple contours).
+    Other details of the plots are as in
+    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
+    except that the diagnostic plots are zoomed in slightly to show
+    more detail, and a smaller KDE smoothing bandwidth of
+    \(0.12 \times 0.08\) is used.}
   \label{fig:herschel-compare-mipsgal}
@@
 
+Figure~\ref{fig:herschel-compare-mipsgal} compares the distributions
+of bow shock shapes between the Herschel (RSG/AGB) and MIGSGAL (OB
+star) samples.  The Anderson--Darling test gives a highly significant
+difference between the \(R_{90}/R_0\) ratio distributions of the two
+samples, but only a marginally significant difference between the
+\(R_c/R_0\) ratio distributions (detailed results are shown in
+Table~\ref{tab:big-p}).  The Herschel sources show considerably
+smaller \(R_{90}\) ratio (median \(R_{90}/R_0 \approx 1.4\), implying bow
+shock wings that are more closed than in the MIPSGAL sources (median
+\(R_{90}/R_0 \approx 1.7\)).  For the radius of curvature ratio, there is
+only a slight difference in average values: median
+\(R_c/R_0 \approx 1.5\) for Herschel versus \(\approx 1.6\) for MIPSGAL, which is
+not statistically significant (rank biserial \(p = 0.29\)).  On the
+other hand, the dispersion in \(R_c/R_0\) is four times smaller for
+the Herschel sample, which is marginally significant (Brown--Forsythe
+\(p = 0.015\)).  In particular, the MIPSGAL sample shows a significant
+minority of very flat-nosed shapes (\(R_c/R_0 > 2\)), but these are
+absent in the Herschel sample.  The same can be seen directly by
+comparing the RSG/AGB bow shock shapes in
+Figures~\ref{fig:herschel-arc-fits}
+and~\ref{fig:herschel-arc-fits-poor} with the representative OB bow
+shocks of Figure~\ref{fig:mipsgal-shapes}b.  The MIPSGAL sources K489
+and K123 have shapes that are similar to specific Herschel sources
+(UU~Aur and R~Hya, respectively), while sources such as K447 (extreme
+flat head) or K517 (extreme open wings) have no analog among the
+Herschel sources.
+
 \subsection{Stationary emission line arcs in M42}
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/annotated-ll-arcs}
+  \includegraphics[width=\linewidth]{figs/annotated-ll-arcs}
   \caption[]{Stationary bow shock arcs in the Orion Nebula.}
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
-  \caption[]{Comparison of Orion with OB stars.}
+  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
+  \caption[]{Comparison of Orion with OB stars.  Other details of the
+    plots are as in Figs.~\ref{fig:mipsgal-shapes}
+    and~\ref{fig:mipsgal-uncorrelated}, except that the diagnostic
+    plots are zoomed out to encompass larger ratio values, and a
+    larger KDE smoothing bandwidth of \(0.3 \times 0.2\) is used.}
   \label{fig:ll-compare-mipsgal}

### 2017-09-12 papers/Paper1/sec-conclusions.tex
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote
Improve Fig 8 on projection of quadrics
Now with 4 panels (incorporates what was in Fig 9 previously).  Use
better color scheme: a diverging set of 7 colors around
T=0 (black). Get rid of the varying line types and use varying
thickness instead. Additional panel showing R90' versus i.

--- 2016-10-14 papers/Paper1/sec-conclusions.tex
@@
 
-\newcommand\thC{\(\theta^1\)\,Ori~C}
+%\newcommand\thC{\(\theta^1\)\,Ori~C}
 \defcitealias{Canto:1996}{CRW}
@@
 Also we made a generalization of \CRW{} work where the weakest interacing wind is hemispherical and anisotropic where its
-density follows a power law of $\cos\theta$. Altrough other models also may be used.
+density follows a power law of $\cos\theta$. Although other models also may be used.
 
@@
 of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
-(ONC) due to the interaction of the photoevaporated wind from proplyds and the stallar wind of \thC{}
+(ONC) due to the interaction of the photoevaporated wind from proplyds and the stellar wind of \thC{}.
 

### 2017-09-12 papers/Paper1/sec-conic.tex
Improve Fig 8 on projection of quadrics
Now with 4 panels (incorporates what was in Fig 9 previously).  Use
better color scheme: a diverging set of 7 colors around
T=0 (black). Get rid of the varying line types and use varying
thickness instead. Additional panel showing R90' versus i.

@@
   \centering
-  \setkeys{Gin}{width=0.45\linewidth}
-  \begin{tabular}{ll}
+  \setkeys{Gin}{width=0.48\linewidth}
+  \begin{tabular}{@{}ll@{}}
     (a) & (b) \\
@@
         & \includegraphics{figs/projected-R0-vs-i} \\
+    (c) & (d) \\
+    \includegraphics{figs/projected-R90-vs-i}
+    & \includegraphics{figs/projected-R90-vs-Rc}
   \end{tabular}
-  \caption[]{Effects of projection on quadrics of revolution.
-    Variation with inclination of characteristic radii.}
+  \caption[]{Effects of projection on quadrics of revolution:
+    variation with inclination of characteristic radii. In panels
+    (a)--(c), vertical rectangles show quartiles of \(|\sin i|\), which
+    will be equally populated for an isotropic distribution of
+    orientations. (a)~Projected radius of curvature, normalized by
+    projected stand-off distance: \( \tilde{R}_c' = R'_c /
+    R'_0\). (b)~Projected stand-off distance: \(R_0' / R_0\).
+    (c)~Projected perpendicular radius, normalized by projected
+    stand-off distance: \( \tilde{R}_{90}' = R'_{90} /
+    R'_0\). (d)~Diagnostic diagram for dimensionless projected radii:
+    \(\tilde{R}_{90}'\) versus \(\tilde{R}_c'\). }
   \label{fig:quadric-projection}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/projected-R90-vs-Rc}
-  \caption{Diagnostic diagram for projected quadric parameters}
-  \label{fig:projected-R90-vs-Rc}
-\end{figure}
 \begin{figure*}

### 2017-09-12 Quadric-shapes/projected-R0-vs-i.py

@@ -1,25 +1,30 @@
 import sys
 import numpy as np
 from matplotlib import pyplot as plt
+from matplotlib.ticker import FormatStrFormatter
 import seaborn as sns
 
 plotfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('white')
+sns.set_color_codes(palette='deep')
 fig, ax = plt.subplots(figsize=(5, 5))
 
 inc = np.linspace(0.0, 0.5*np.pi, 5000)
 inc_deg = np.degrees(inc)
 
 Rcs = [0.5, 1.0, 2.0, 4.0, 8.0]
+thlabs = [44, 50, 42, 33, 22]
 Tcs = [-2.0, -1.0, -0.5, 1e-3, 0.5, 1.0, 2.0]
+shapes =  ['Hyperbola']*3 + ['Parabola', 'Prolate', 'Sphere', 'Oblate', ]
 
 n_Rc = len(Rcs)
 n_Tc = len(Tcs)
 
-lws = np.linspace(1.0, 2.0, n_Rc)
-alphas = np.linspace(1.0, 0.2, n_Rc)
+lws = np.linspace(0.5, 2.0, n_Rc)
+alphas = np.linspace(1.0, 1.0, n_Rc)**1.5
 cols = sns.color_palette('magma', n_colors=n_Tc)
+cols = 'cgbkmry'
 lss = ['-.', '-', '--', ':', '-.']
 
 dash_solid = []
@@ -34,19 +39,25 @@ def qratio(inc, Tc, Rc):
     f = np.sqrt(1.0 + Tc*np.tan(inc)**2)
     return (1.0 + Rc*(f - 1.0) / Tc)*np.cos(inc)
 
-for Rc, lw, alpha, ls, dash in list(zip(Rcs, lws, alphas, lss, dashes))[::-1]:
-    for Tc, col in list(zip(Tcs, cols))[::-1]:
+for Rc, lw, alpha, ls, dash, thlab in list(zip(Rcs, lws, alphas, lss, dashes, thlabs))[::-1]:
+    for Tc, col, shape in list(zip(Tcs, cols, shapes))[::-1]:
         if Rc == 1.0:
-            label = fr'$T_c = {Tc:.1f}$'
+            label = fr'{shape}: $T_c = {Tc:.1f}$'
         else:
             label = None
         ax.plot(inc_deg, qratio(inc, Tc, Rc),
-                c=col, dashes=dash, label=label)
+                c=col, lw=lw, alpha=alpha, label=label)
[…]

### 2017-09-12 Quadric-shapes/projected-R90-vs-Rc.py

@@ -7,6 +7,7 @@ import seaborn as sns
 plotfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('white')
+sns.set_color_codes(palette='deep')
 fig, ax = plt.subplots(figsize=(5, 5))
 
 Rc_grid = np.linspace(0.0, 10.0, 2000)
@@ -27,11 +28,12 @@ inc_deg = np.degrees(inc)
 
 Rcs = [0.5, 1.0, 2.0, 4.0, 8.0]
 Tcs = [-2.0, -1.0, -0.5, 1e-8, 0.5, 1.0, 2.0]
+shapes =  ['Hyperbola']*3 + ['Parabola', 'Prolate', 'Sphere', 'Oblate', ]
 
 n_Rc = len(Rcs)
 n_Tc = len(Tcs)
 
-lws = np.linspace(1.0, 2.0, n_Rc)
+lws = np.linspace(0.5, 2.0, n_Rc)
 dash_solid = []
 dash_dashed = [3, 2]
 dash_dotted = [1, 2]
@@ -43,6 +45,7 @@ dashes = [dash_triple_dot_dashed, dash_solid,
 lss = ['-.', '-', '--', ':', '-.']
 alphas = np.linspace(1.0, 0.2, n_Rc)
 cols = sns.color_palette('magma', n_colors=n_Tc)
+cols = 'cgbkmry'
 
 
 def Rc_prime(inc, Tc, Rc):
@@ -58,18 +61,18 @@ def R90_prime(inc, Tc, Rc):
 
 
 for Rc, lw, alpha, dash in list(zip(Rcs, lws, alphas, dashes))[::-1]:
-    for Tc, col in list(zip(Tcs, cols))[::-1]:
+    for Tc, col, shape in list(zip(Tcs, cols, shapes))[::-1]:
         if Rc == 1.0:
-            label = fr'$T_c = {Tc:.1f}$'
+            label = fr'{shape}: $T_c = {Tc:.1f}$'
         else:
             label = None
         ax.plot(Rc_prime(inc, Tc, Rc), R90_prime(inc, Tc, Rc),
-                c=col, dashes=dash, label=label)
+                c=col, lw=lw, label=label)
         # ax.plot(Rc_dash(inc, Tc, Rc), Tc_dash(inc, Tc), '.', alpha=0.1, ms=4,
         #         c=col, label=label)
[…]

### 2017-09-21 papers/Paper1/sec-conic.tex
Expand some fig captions and move figures between sections

@@
   \caption[]{Effects of projection on quadrics of revolution:
-    variation with inclination of characteristic radii. In panels
-    (a)--(c), vertical rectangles show quartiles of \(|\sin i|\), which
-    will be equally populated for an isotropic distribution of
+    variation with inclination of characteristic radii.  Different
+    line colors correspond to different quadric shapes (see key),
+    while variation in line width corresponds to variation in the
+    ``true'' dimensionless radius of curvature, \(\tilde{R}_c\), at
+    the apex. Vertical gray rectangles show quartiles of \(|\sin i|\),
+    which will be equally populated for an isotropic distribution of
     orientations. (a)~Projected radius of curvature, normalized by
@@
     R'_0\). (d)~Diagnostic diagram for dimensionless projected radii:
-    \(\tilde{R}_{90}'\) versus \(\tilde{R}_c'\). }
+    \(\tilde{R}_{90}'\) versus \(\tilde{R}_c'\).  Shading indicates
+    different classes of quadrics: hyperboloids (white), prolate
+    spheroids (dark gray), and oblate spheroids (light gray), with the
+    limiting case of paraboloids shown by the thin black line.}
   \label{fig:quadric-projection}

### 2017-09-21 papers/Paper1/sec-generic-model.tex
Include POS projection figure in section 3
And brief discussion in text
Correct errors in latex file
Remove repeated figure
Incorporated A' and q' results in  parabola appendix.
Restored projection section.
Correct errors and footnote
Create new figures. Move figure 8 to section 2.
- ~R'c vs inclination
- ~R'90 vs inclination
- T'c vs ~R'c
Expand some fig captions and move figures between sections

@@
-\section{Generic bow shock model}
+\section{Generic two-wind bow shock model}
 \label{sec:generic-model}
@@
   \caption{Quasi-stationary bow shock structure formed by the
-  interaction of two supersonic winds.  Lower-left inset box shows the
-  case where the inner wind is anisotropic.   
-  % the two winds problem. Any point in the shell is located with the
-  % coordinates $(R,\theta)$, and $\theta_1$ is measured from the
-  % external wind position
-}
+    interaction of two supersonic winds.  Lower-left inset box shows
+    the case where the inner wind is anisotropic. The streamlines
+    (thin lines) are drawn so as to be qualitatively realistic: they
+    are straight in regions of hypersonic flow, but curved in subsonic
+    regions, responding to pressure gradients in the shocked shells.}
 \label{fig:2-winds}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
+  \caption[]{Schematic diagram of two-wind interaction problem,
+    following \citet{Canto:1996}.}
+  \label{fig:crw-schema}
 \end{figure}
@@
 
-The bow shocks we consider are originated by a source located at the origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a terminal
-(supersonic) velocity $v_w$. This wind interacts with another wind originated by another source located at a distance $D$ from the first one. 
-The mass loss rate of the second source is $\dot{M}_{w1}$ and the terminal velocity is $v_{w1}$. The momentum of the wind of the second source is
-higher than the momentum of the first one, and the resultant bow shock is stationary due to pressure balance.
+The bow shocks we consider are originated by a source located at the
+origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a
+terminal (supersonic) velocity $v_w$. This wind interacts with another
+wind originated by another source located at a distance $D$ from the
+first one.  The mass loss rate of the second source is $\dot{M}_{w1}$
+and the terminal velocity is $v_{w1}$. The momentum of the wind of the
+second source is higher than the momentum of the first one, and the
+resultant bow shock is stationary due to pressure balance.
 
 \subsection{Characteristic Radii}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/characteristic-radii}
+  \caption{Characteristic radii in the body frame.}
+  \label{fig:characteristic-radii}
+\end{figure}
 
-In order to contrast different bow shock models, we  derive a set of measurable radii. Each model used should predict them and these predictions can be
-compared with observations.
-
+In order to contrast different bow shock models, we derive a set of
+measurable radii. Each model used should predict them and these
+predictions can be compared with observations.
 \begin{itemize}
@@
 \item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
-\item Radius at the  perpendicular direction to the symmetry axis. Denoted as $R_{90}$
-\item For open bow shocks, the asymptotic angle. Denoted as $\theta_\infty$
+\item Radius at the perpendicular direction to the symmetry
+  axis. Denoted as $R_{90}$
+\item For open bow shocks, the asymptotic angle. Denoted as
+  $\theta_\infty$
 \end{itemize}
 
-\begin{figure}
-\includegraphics[width=\linewidth]{ch-radii_ed2}
-\caption{Schematic representation of the characteristic radii $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis $R_c$}
-\end{figure}
+% \begin{figure}
+%   \includegraphics[width=\linewidth]{ch-radii_ed2}
+%   \caption{Schematic representation of the characteristic radii
+%   $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis
+%   $R_c$}
+% \end{figure}
 

### 2017-09-28 papers/Paper1/sec-generic-model.tex
Add figure showing th90 versus inclination

@@
     the case where the inner wind is anisotropic. The streamlines
-    (thin lines) are drawn so as to be qualitatively realistic: they
+    (thin lines) are drawn to be qualitatively realistic: they
     are straight in regions of hypersonic flow, but curved in subsonic
@@
 \end{figure}
-
+can't doesn;t 
 \begin{figure}

### 2017-09-28 papers/Paper1/sec-thin-shell.tex
Last changes:
+ Implement Parabolic fit for Projection
+ Thoughts about Wilkin solution for bowshocks (most useless)
+ Correct some equations in quadrics section
Add figure showing th90 versus inclination

@@
 I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \label{eq:Ik}\\
-\dot{J}_w = 0 \label{eq:jdot} \\
+\dot{J}_w &= 0 \label{eq:jdot} \\
 \dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/projected-th90-vs-i}
+  \caption{Variation with inclination of the body-frame polar angle
+    \(\theta_{90}\) that corresponds to the projected perpendicular radius
+    \(R’_{90}\).  Line colors and thicknesses represent different
+    quadrics of revolution, as in
+    Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
+    important because the quadric fits to the bow shock shape must be
+    accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
+    for \(R’_{90}\).}
+  \label{fig:projected-th90}
+\end{figure}
+
 \begin{figure*}
@@
     Residuals are expressed as the fractional error in the
-    complementary angle \(\theta_1\) for the same parameters as are shown
-    in Fig.~\ref{fig:head-tail}.}
+    complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
+    the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
   \label{fig:head-tail-residuals}

### 2017-09-28 CRW-shapes/two-quadric-R90-vs-Rc.py
Revamped Fig 16 with the [[an]cara]wilkinoids on Rc-R90 diagram
Split into two panels for clarity.  Annotated with i* where we switch
over from the head to the tail for R90

@@ -5,11 +5,20 @@ import matplotlib.ticker
 import seaborn as sns
 import conic_parameters
 
-plotfile = sys.argv[0].replace('.py', '.pdf')
+try: 
+    xiset = sys.argv[1]
+    plotfile = sys.argv[0].replace('.py', f'-{xiset}.pdf')
+    assert xiset in 'ab'
+    istart = -2 if xiset == 'a' else -1
+except:
+    sys.exit(f"Usage: {sys.argv[0]} a|b")
 
 sns.set_style('white')
 fig, ax = plt.subplots(figsize=(5, 5))
 
+
+left_annotate_pars = dict(xytext=(-5, 5), ha='right', va='bottom')
+right_annotate_pars = dict(xytext=(5, -5), ha='left', va='top')
 
 
 Rc_grid = np.linspace(0.0, 10.0, 2000)
@@ -29,12 +38,13 @@ inc_deg = np.degrees(inc)
 
 
 XI_LIST = [None, 1.0, 0.8, 0.4]
-BETA_LIST = [0.2, 0.1, 0.05, 0.02, 0.01, 0.001, 0.0001, 0.00001]
+BETA_LIST = [0.2, 0.1, 0.05, 0.02, 0.005, 1e-6]
 nxi, nbeta = len(XI_LIST), len(BETA_LIST)
 
 cols = sns.color_palette('magma', n_colors=nxi)
+annot_pars_list = [left_annotate_pars]*2 + [right_annotate_pars]*2 
 for beta in BETA_LIST[::-1]:
-    for xi, col in list(zip(XI_LIST, cols))[::-1]:
+    for xi, col, annot_pars in list(zip(XI_LIST, cols, annot_pars_list))[istart::-2]:
 
         # Fit to head and analytic fit to fit to tail
         ht = conic_parameters.HeadTail(beta, xi=xi, xmin=0.0, method='analytic fit')
@@ -102,21 +112,31 @@ for beta in BETA_LIST[::-1]:
 
 
         # Masks for high and low inclinations (overlapping range)
-        mlo = inc_deg <= inc_deg[i0]
-        mhi = inc_deg >= inc_deg[i0]
+        overlap_deg = 0.0
+        mlo = inc_deg <= inc_deg[i0] + overlap_deg
+        mhi = inc_deg >= inc_deg[i0] - overlap_deg
+        # mlo = inc_deg <= 40.0
+        # mhi = inc_deg >= 30.0
+
         # Ensure that LOS is not inside the tail cone
[…]

### 2017-09-29 papers/Paper1/app-dust-wave.tex
Start appendix on dust wave
Finish figure and caption.  Also re-arrange appendices into separate
files.

\section{Shape of a dusty radiative bow wave}
\label{sec:shape-dust-wave}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/dust-trajectories}
  \caption[Dust grain trajectories]{Dust grain trajectories under
    influence of a repulsive central \(r^{-2}\) radiative force.  Dust
    grains approach from the right at a uniform velocity and with a
    variety of impact parameters (initial \(y\)-coordinate). The
    central source is marked by a red star at the origin, and its
    radiative force deflects the trajectories into a hyperbolic shape,
    each of which reaches a minimum radius marked by a small black
    square.  The incoming hyperbolic trajectories are traced in gray
    and the outgoing trajectories are traced in red.  The locus of
    closest approach of the outgoing trajectories is parabolic in
    shape (traced by the thick, light gray line) and this constitutes
    the inner edge of the bow wave. }
  \label{fig:dust-trajectories}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

### 2017-09-29 papers/Paper1/app-p-values.tex
Start appendix on dust wave
Finish figure and caption.  Also re-arrange appendices into separate
files.

--- 2017-05-26 papers/Paper1/quadrics-appendix.tex
@@
-\appendix
-% \appendixpage
-% \addappheadtotoc
-\section{Parabola of Revolution}
-\label{app:parabola}
-
-In this section we develop the particular case of the parabola.
-The parametrization is given by:
-
-\begin{align}
-x &= - \frac{1}{2}R_ct^2 + R_0 \\
-y &= R_c t
-\end{align}
-Where $R_c$ is the radius of curvature and $R_0$ is the distance of the parabola nose to the
-origin.
-The respective tridimensional shape is given by:
-\begin{align}
-x &= -\frac{1}{2}R_ct^2 + R_0 \label{eq:x-par-a}\\
-y &= R_c t \cos\phi  \label{eq:y-par-a}\\
-z &= R_c t \sin\phi  \label{eq:z-par-a}
-\end{align}
-The azimutal angle where the surface is tangent to the line of sight in this case is given by:
-\begin{align}
-\sin\phi_t = -\frac{\tan i}{t} \label{eq:sin-tan-a} 
-\end{align}
-
-Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and
-(\ref{eq:z-par-a}) we find the apparent shape
-of the paraboloid:
-
-\begin{align}
-x' &= -\frac{R_c(\frac{1}{2}t^2 \cos^2 i -\sin^2 i)}{\cos i}+R_0\cos i \\
-y' &= R_c\left(t^2-\tan^2 i\right)^{1/2} 
-\end{align}
-
-Taking the limit of equations (\ref{eq:qprime}) and (\ref{eq:Aprime}) when $\theta_c$ tends to zero we find that:
-
-\begin{align}
-\left(\frac{q'}{q}\right)_{\mathrm{parabola}} &= 1+\frac{\tilde{R}_c\tan^2 i}{2}\\
-\left(\tilde{R}'_c\right)_{\mathrm{parabola}} &= \frac{\tilde{R}_c}{\cos^2 i + \frac{\tilde{R}_c}{2}\sin^2 i}
-\end{align}
-
-\section{Analytic derivation of the radius of curvature in the Thin Shell model}
-\label{app:rc-analytic}
-
-For small $\theta$ we may do a polynomial expansion for the shell shape such as:
-
-\begin{align}
-R \simeq R_0\left(1+\gamma\theta^2 + \Gamma\theta^4\right) \label{eq:R-exp}
-\end{align}
-
-The radius of curvature at the axis for $R$ is given by:
-
-\begin{align}
-R_c = R_0\left(1-2\gamma\right)^{-1}
-\end{align}
-
-The coefficient gamma may be derived by an expansion at small angles of equation
-(\ref{eq:th1th}), as follows:
-
-From the first term of the right side we get:
-
-\begin{align}
-\cot\theta &\simeq \theta^{-1}\left[1-\frac{1}{3}\theta^2\right] \\
-\cos^k\theta\sin^2\theta &\simeq \theta^2 - \left(\frac{1}{3} + \frac{k}{2}\right)\theta^4 \\
-\implies I_k(\theta) &\simeq \frac{1}{3}\theta^3\left[ 1 - \frac{1}{10}(3k+2)\theta^2\right]\\
-\implies 2\beta I_k(\theta)\cot\theta &\simeq \frac{2}{3}\beta\theta^2\left[1-\frac{1}{30}
-(9k+16)\theta^2\right]\label{eq:AR1} 
-\end{align}
-
-For the second term we get:
-
-\begin{align}
--\frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right) & \simeq -\beta\theta^2\left[1-\frac{1}{12}
-(3k+4)\theta^2\right] \label{eq:AR2}
-\end{align}
-
-For the left side we use equation (25) from \CRW{}. Then, equation (\ref{eq:th1th}) results
-as follows:
-
-\begin{align}
-\theta_1^2\left(1+\frac{1}{15}\theta_1^2\right) = \beta\theta^2\left[1+\frac{1}{60}(4-9k)
-\theta^2\right] \label{eq:th1th-app}
-\end{align}
-
-And we can use the approximation $\theta_1 \approx \beta\theta^2$ for the correction term in
-the left side of (\ref{eq:th1th-app}):
-
-\begin{align}
-\theta_1^2 &= \beta\theta^2\left[1+\frac{1}{60}(4-9k)\theta^2\right]
-\left(1-\frac{\beta}{15}\theta^2\right) \\
-\implies \theta_1^2 &= \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right]
-\label{eq:th1th-small}\\
-\mathrm{where:~} C_{k\beta} &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
-A_k &\equiv \frac{1}{15}-\frac{3k}{20}
-\end{align}
-
-Now, using equation (23) from \CRW{} we may estimate $R$ at low angles. To do this, we need to
-expand each term as follows (neglecting terms of order four or higher):
-
-\begin{align}
-\theta_1 = &= \beta^{1/2}\theta\left[1+ 2C_{k\beta}\theta^2\right]^{1/2} \\
-\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2C_{k\beta}\theta^2\right)\right]\\
-\sin\theta_1 &= \theta_1\left[1-\frac{\theta_1^2}{6}\right] \\
- &= \beta^{1/2}\theta\left[1+\left(C_{k\beta}-\frac{1}{6}\beta\right)\theta^2\right] \\
- \sin(\theta+\theta_1) &= \left[\theta+\theta_1\right]\left[1-\frac{\left(\theta+\theta_1
- \right)^2}{6}\right] \\
- &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{C_{k\beta}\beta^{1/2}}
- {1+\beta^{1/2}}-\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
-\end{align}
-
-So, combining these terms with equation (23) from \CRW{} we found the final expression for $R$:
-
-\begin{align}
-\frac{R}{D}\equiv \frac{\sin\theta_1}{\sin(\theta+\theta_1)} = \frac{\beta^1/2}{1+\beta^{1/2}}
-\left\lbrace 1 + \theta^2\left[\frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
-\right)\right] \right\rbrace \label{eq:r-small-theta}
-\end{align}
-
-Returning to equation (\ref{eq:R-exp}) we see the following:
-
-\begin{align}
-R_0 &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
-\gamma &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right)
-\label{eq:app-gamma}
-\end{align}
-
-We recover equation (27) of \CRW{} for $R_0$ and equation (\ref{eq:app-gamma}) is the
-needed term to calculate the radius of curvature at the axis.
-
-\section{Analytic derivation of \texorpdfstring{\boldmath $R_{90}$}{R\_90} in the thin shell model}
-\label{app:r90-analytic}
-
-To derive $R_{90}$ we need to evaluate equations (23) from \CRW{} and (\ref{eq:th1th})
-at $\theta=\frac{\pi}{2}$:
-
-\begin{align}
-R_{90} = D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} -1 = -\frac{2\beta}{k+2} \label{eq:th190}
-\end{align}
-Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing
-the parameter $\xi\equiv \frac{2}{k+2}$ we have:
-\begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} \label{eq:r90-incomplete}
-\end{align}
-
-Expanding the left side of (\ref{eq:th190}) until fourth order, equation (\ref{eq:th190})
-becomes:
-
-\begin{align}
-\theta_{1,90}^2\left(1+\frac{\theta_{1,90}^2}{15}\right) \simeq 3\xi\beta
-\end{align}
-
-Applying the approximation $\theta_1^2 \approx 3\xi\beta$ we found a solution
-for $\theta_{1,90}$:
-
-\begin{align}
-\theta_{1,90} = \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2}
-\end{align}
-
-And substituting into (\ref{eq:r90-incomplete}) we find the solution for $R_{90}$:
-
-\begin{align}
-R_{90} &= \frac{\left(3\xi\beta\right)^{1/2}}{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}
-\left(1-\xi\beta\right)} \\
-\implies \tilde{R}_{90} &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
-{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
-\end{align}
-
-\section{Derivation of Characteristic Radii in Isotropic Wind/Parallel interaction Problem}
-\label{app:ch-rad-Wilkin}
-
-$\tilde{R}_{90}$ is obtained by simply evaluating equation (\ref{eq:R-Wilkin}) at $\theta=\frac{\pi}{2}$.
-For the Radius of curvature we follow a similar procedure than the Wind/Wind interaction, but using equation
-(\ref{eq:R-Wilkin}) for $R(\theta)$ and inserting the cosecant into the square root.
-
-Expanding the terms of $R(\theta)$ we find the following:
-
-\begin{align}
-  \csc^2\theta &\simeq \theta^{-2}\left[1+\frac{\theta^2}{3}\left(1+\frac{\theta^2}{5}\right)\right] \\
-  1-\theta\cot\theta &\simeq \frac{\theta^2}{3}\left[1 + \frac{\theta^2}{15}\left(1+\frac{2\theta^2}{21}\right)\right] \\
-  \implies \tilde{R}(\theta) \simeq 1 + \frac{\theta^2}{5} + O\left[\theta^4\right]
-\end{align}
-
-From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
 \clearpage
@@
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock.tex"
+%%% TeX-master: "quadrics-bowshock"
 %%% End:

### 2017-09-29 papers/Paper1/app-parabola.tex
Start appendix on dust wave
Finish figure and caption.  Also re-arrange appendices into separate
files.

--- 2017-04-25 papers/Paper1/quadrics-appendix.tex
@@
-\appendix
-% \appendixpage
-% \addappheadtotoc
 \section{Parabola of Revolution}
@@
 
-\section{Analytic derivation of the radius of curvature in the Thin Shell model}
-\label{app:rc-analytic}
-
-For small $\theta$ we may do a polynomial expansion for the shell shape such as:
-
-\begin{align}
-R \simeq R_0\left(1+\gamma\theta^2 + \Gamma\theta^4\right) \label{eq:R-exp}
-\end{align}
-
-The radius of curvature at the axis for $R$ is given by:
-
-\begin{align}
-R_c = R_0\left(1-2\gamma\right)^{-1}
-\end{align}
-
-The coefficient gamma may be derived by an expansion at small angles of equation
-(\ref{eq:th1th}), as follows:
-
-From the first term of the right side we get:
-
-\begin{align}
-\cot\theta &\simeq \theta^{-1}\left[1-\frac{1}{3}\theta^2\right] \\
-\cos^k\theta\sin^2\theta &\simeq \theta^2 - \left(\frac{1}{3} + \frac{k}{2}\right)\theta^4 \\
-\implies I_k(\theta) &\simeq \frac{1}{3}\theta^3\left[ 1 - \frac{1}{10}(3k+2)\theta^2\right]\\
-\implies 2\beta I_k(\theta)\cot\theta &\simeq \frac{2}{3}\beta\theta^2\left[1-\frac{1}{30}
-(9k+16)\theta^2\right]\label{eq:AR1} 
-\end{align}
-
-For the second term we get:
-
-\begin{align}
--\frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right) & \simeq -\beta\theta^2\left[1-\frac{1}{12}
-(3k+4)\theta^2\right] \label{eq:AR2}
-\end{align}
-
-For the left side we use equation (25) from \CRW{}. Then, equation (\ref{eq:th1th}) results
-as follows:
-
-\begin{align}
-\theta_1^2\left(1+\frac{1}{15}\theta_1^2\right) = \beta\theta^2\left[1+\frac{1}{60}(4-9k)
-\theta^2\right] \label{eq:th1th-app}
-\end{align}
-
-And we can use the approximation $\theta_1 \approx \beta\theta^2$ for the correction term in
-the left side of (\ref{eq:th1th-app}):
-
-\begin{align}
-\theta_1^2 &= \beta\theta^2\left[1+\frac{1}{60}(4-9k)\theta^2\right]
-\left(1-\frac{\beta}{15}\theta^2\right) \\
-\implies \theta_1^2 &= \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right]
-\label{eq:th1th-small}\\
-\mathrm{where:~} C_{k\beta} &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
-A_k &\equiv \frac{1}{15}-\frac{3k}{20}
-\end{align}
-
-Now, using equation (23) from \CRW{} we may estimate $R$ at low angles. To do this, we need to
-expand each term as follows (neglecting terms of order four or higher):
-
-\begin{align}
-\theta_1 = &= \beta^{1/2}\theta\left[1+ 2C_{k\beta}\theta^2\right]^{1/2} \\
-\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2C_{k\beta}\theta^2\right)\right]\\
-\sin\theta_1 &= \theta_1\left[1-\frac{\theta_1^2}{6}\right] \\
- &= \beta^{1/2}\theta\left[1+\left(C_{k\beta}-\frac{1}{6}\beta\right)\theta^2\right] \\
- \sin(\theta+\theta_1) &= \left[\theta+\theta_1\right]\left[1-\frac{\left(\theta+\theta_1
- \right)^2}{6}\right] \\
- &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{C_{k\beta}\beta^{1/2}}
- {1+\beta^{1/2}}-\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
-\end{align}
-
-So, combining these terms with equation (23) from \CRW{} we found the final expression for $R$:
-
-\begin{align}
-\frac{R}{D}\equiv \frac{\sin\theta_1}{\sin(\theta+\theta_1)} = \frac{\beta^1/2}{1+\beta^{1/2}}
-\left\lbrace 1 + \theta^2\left[\frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
-\right)\right] \right\rbrace \label{eq:r-small-theta}
-\end{align}
-
-Returning to equation (\ref{eq:R-exp}) we see the following:
-
-\begin{align}
-R_0 &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
-\gamma &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right)
-\label{eq:app-gamma}
-\end{align}
-
-We recover equation (27) of \CRW{} for $R_0$ and equation (\ref{eq:app-gamma}) is the
-needed term to calculate the radius of curvature at the axis.
-
-\section{Analytic derivation of \texorpdfstring{\boldmath $R_{90}$}{R\_90} in the thin shell model}
-\label{app:r90-analytic}
-
-To derive $R_{90}$ we need to evaluate equations (23) from \CRW{} and (\ref{eq:th1th})
-at $\theta=\frac{\pi}{2}$:
-
-\begin{align}
-R_{90} = D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} -1 = -\frac{2\beta}{k+2} \label{eq:th190}
-\end{align}
-Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing
-the parameter $\xi\equiv \frac{2}{k+2}$ we have:
-\begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} \label{eq:r90-incomplete}
-\end{align}
-
-Expanding the left side of (\ref{eq:th190}) until fourth order, equation (\ref{eq:th190})
-becomes:
-
-\begin{align}
-\theta_{1,90}^2\left(1+\frac{\theta_{1,90}^2}{15}\right) \simeq 3\xi\beta
-\end{align}
-
-Applying the approximation $\theta_1^2 \approx 3\xi\beta$ we found a solution
-for $\theta_{1,90}$:
-
-\begin{align}
-\theta_{1,90} = \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2}
-\end{align}
-
-And substituting into (\ref{eq:r90-incomplete}) we find the solution for $R_{90}$:
-
-\begin{align}
-R_{90} &= \frac{\left(3\xi\beta\right)^{1/2}}{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}
-\left(1-\xi\beta\right)} \\
-\implies \tilde{R}_{90} &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
-{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
-\end{align}
-
-\section{Derivation of Characteristic Radii in Isotropic Wind/Parallel interaction Problem}
-\label{app:ch-rad-Wilkin}
-
-$\tilde{R}_{90}$ is obtained by simply evaluating equation (\ref{eq:R-Wilkin}) at $\theta=\frac{\pi}{2}$.
-For the Radius of curvature we follow a similar procedure than the Wind/Wind interaction, but using equation
-(\ref{eq:R-Wilkin}) for $R(\theta)$ and inserting the cosecant into the square root.
-
-Expanding the terms of $R(\theta)$ we find the following:
-
-\begin{align}
-  \csc^2\theta &\simeq \theta^{-2}\left[1+\frac{\theta^2}{3}\left(1+\frac{\theta^2}{5}\right)\right] \\
-  1-\theta\cot\theta &\simeq \frac{\theta^2}{3}\left[1 + \frac{\theta^2}{15}\left(1+\frac{2\theta^2}{21}\right)\right] \\
-  \implies \tilde{R}(\theta) \simeq 1 + \frac{\theta^2}{5} + O\left[\theta^4\right]
-\end{align}
-
-From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
-\clearpage
-
-% Landscape table needs to go on its own page, so we need to manually
-% adjust the section counter so that it will ``belong'' to the next
-% section
-\addtocounter{section}{1}
-\sisetup{detect-all=true, detect-inline-weight=math}
-\sisetup{round-mode=figures, round-precision=2}
-\begin{landscape}
-\begin{table}
-  \setlength\tabcolsep{3pt}
-  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
-Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
-  \label{tab:big-p}
-  \input{figs/mipsgal-summary-stats-table-body.tex}
-\end{table}
-\end{landscape}
-\begin{table}
-  \contcaption{Results of all statistical tests performed on observed
-    bow shock shape parameters.}
-  \begin{tabular}{p{0.9\linewidth}}
-    \toprule
-    \textit{Description of columns:}
-    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
-    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
-    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
-    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
-    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
-    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
-    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
-It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
-    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
-    (Col.~13)~Ratio of standard deviations between the two sub-samples.
-    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
-    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
-    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
-    (Col.~16)~Brown--Forsythe test for dispersion
-    \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\addtocounter{section}{-1}
-
-\section{Distribution of p-values for all correlations tested}
-\label{sec:distr-p-values}
-\addtocounter{table}{1}
-
-\begin{figure}
-  (a)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
-  (b)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
-  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
-    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
-    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
-    bins and logarithmic vertical axis, with all values
-    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
-    lines shows the traditional threshold values for significance:
-    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
-    uniform distribution of \(p\)-values that would be expected if the
-    null hypothesis were always true, that is, if no significant
-    correlations existed.}
-  \label{fig:histo-p-values}
-\end{figure}
-
-Results from all the statistical tests discussed in \S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
-
-\begin{table}
-  \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
-  \label{tab:type-I}
-  \centering
-  \begin{tabular}{lrr} \toprule
-    Correlation & \(p\) & \(\alpha\) \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
-    \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
-    \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
-    \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
-    \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
-    \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
-    \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
-    \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
-    \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
-    \(R_c\) vs Facing & 0.71 & 1 \\
-    \(R_c\) vs H II & 0.50 & 1 \\
-    \(R_{90}\) vs Facing & 0.60 & 1 \\
-    \(R_{90}\) vs H II & 0.52 & 1 \\
-    \(R_c\) vs Multiple & 1.00 & 1 \\
-    \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
-    \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
-    \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
-    \(R_c\) vs Herschel & 0.074 & 0.3437 \\
-    \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
-    \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
-    \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The \(p\)-values are the probability of finding a difference between
-two populations as large as (or larger than) what is observed,
-\emph{given} that there is no difference in the underlying
-distribution from which the two populations are drawn (that is, given
-that the null hypothesis is true).  However, what we really want to
-know is something else: the probability that the null hypothesis is
-true, \emph{given} the observations.  That is, the probability,
-\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
-  error rate}.  The common mistake of conflating these two definitions
-is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
-error of the transposed conditional'', as discussed in detail by
-\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
-\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
-requires an estimate of the prior probability of the null hypothesis,
-independent of the observations.  Alternatively, it is also possible
-to find a lower bound on \(\alpha\) from a frequentist approach
-\citep{Sellke:2001a}:
-\begin{equation}
-  \label{eq:type-I}
-  \alpha(p) \ge \bigg[ 1 - \big(e\, p \ln p\big)^{-1} \bigg]^{-1}
-  \quad \text{valid for } p < 1/e.
-\end{equation}
-This is the approach we adopt here, which also numerically coincides
-with the Bayesian approach for the case where the prior probability of
-the null hypothesis is 0.5.  The reason that this is only a lower
-limit for \(\alpha\) is that if we have overwhelming a priori evidence that
-the null hypothesis is true (for instance, from previous empirical
-studies, or because it follows from a well-supported theory), then a
-Bayesian calculation would give a much higher value of \(\alpha\) than
-\eqref{eq:type-I} does.  In our case, however, we have no strong
-reasons for favoring any of the null hypotheses, so it is reasonable
-to assume \(\alpha\) is close to the lower limit given in \eqref{eq:type-I}.
-
-In order to choose a threshold \(p\)-value that counts as a
-``significant'' result, one then needs to balance the risks of false
-positives against the risks of \textit{false negatives}.  The false
-negative probability, \(\beta\), also known as \textit{Type II error
-  rate}, is the probability of failing to reject an untrue null
-hypothesis.  That is, in the context of this paper, it is the
-probability of failing to detect a real difference between two
-sub-samples, or a real correlation between two variables.  The
-complementary probability, \(1 - \beta\), is known as the
-\textit{statistical power} or sensitivity of the test.  The value of
-\(\beta\) depends on three factors:
-\begin{enumerate}[1.]
-\item The \textit{effect size}, which is a measure of the magnitude of
-  the difference in a dependent variable between two sub-samples, or
-  the degree of correlation between two continuous variables.  For the
-  two sub-sample case, it is common to use a standardised mean
-  difference, such as Cohen's \(d\) statistic \citep{Cohen:1988a}:
-  \(d = (\bar{X}_A - \bar{X}_B) / s\), where \(\bar{X}_A\),
-  \(\bar{X}_B\) are the means of the dependent variable \(X\) for
-  samples A and B, while \(s\) is the pooled standard deviation of
-  \(X\).  For the case of two continuous variables, the Pearson linear
-  correlation coefficient, \(r\), can be used.  In both cases, rules
-  of thumb have been developed \citep{Ruscio:2008a} for classifying an
-  effect as ``large'' (\(d > 0.8\), \(r > 0.4\)) or ``small''
-  (\(d < 0.2\), \(r < 0.1\)).  Alternatively, non-parametric
-  statistics can be used, such as the \(A\) measure of stochastic
-  superiority \citep{Delaney:2002a}.
-\end{enumerate}
-
-Obviously, this depends on the \textit{effect size}, which is the
-
-All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).
-It is therefore important to guard against the ``multiple comparisons problem'', whereby seemingly significant correlations are found where none really exist, simply by virtue of the large number of tests that were carried out.
-
-Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.
-
-The p-curve \citep{Head:2015a}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock.tex"
+%%% TeX-master: "quadrics-bowshock"
 %%% End:

### 2017-09-29 papers/Paper1/app-rcurv.tex
Start appendix on dust wave
Finish figure and caption.  Also re-arrange appendices into separate
files.

--- 2017-04-25 papers/Paper1/quadrics-appendix.tex
@@
-\appendix
-% \appendixpage
-% \addappheadtotoc
-\section{Parabola of Revolution}
-\label{app:parabola}
-
-In this section we develop the particular case of the parabola.
-The parametrization is given by:
-
-\begin{align}
-x &= - \frac{1}{2}R_ct^2 + R_0 \\
-y &= R_c t
-\end{align}
-Where $R_c$ is the radius of curvature and $R_0$ is the distance of the parabola nose to the
-origin.
-The respective tridimensional shape is given by:
-\begin{align}
-x &= -\frac{1}{2}R_ct^2 + R_0 \label{eq:x-par-a}\\
-y &= R_c t \cos\phi  \label{eq:y-par-a}\\
-z &= R_c t \sin\phi  \label{eq:z-par-a}
-\end{align}
-The azimutal angle where the surface is tangent to the line of sight in this case is given by:
-\begin{align}
-\sin\phi_t = -\frac{\tan i}{t} \label{eq:sin-tan-a} 
-\end{align}
-
-Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and
-(\ref{eq:z-par-a}) we find the apparent shape
-of the paraboloid:
-
-\begin{align}
-x' &= -\frac{R_c(\frac{1}{2}t^2 \cos^2 i -\sin^2 i)}{\cos i}+R_0\cos i \\
-y' &= R_c\left(t^2-\tan^2 i\right)^{1/2} 
-\end{align}
-
-Taking the limit of equations (\ref{eq:qprime}) and (\ref{eq:Aprime}) when $\theta_c$ tends to zero we find that:
-
-\begin{align}
-\left(\frac{q'}{q}\right)_{\mathrm{parabola}} &= 1+\frac{\tilde{R}_c\tan^2 i}{2}\\
-\left(\tilde{R}'_c\right)_{\mathrm{parabola}} &= \frac{\tilde{R}_c}{\cos^2 i + \frac{\tilde{R}_c}{2}\sin^2 i}
-\end{align}
-
 \section{Analytic derivation of the radius of curvature in the Thin Shell model}
@@
 
-\section{Analytic derivation of \texorpdfstring{\boldmath $R_{90}$}{R\_90} in the thin shell model}
-\label{app:r90-analytic}
-
-To derive $R_{90}$ we need to evaluate equations (23) from \CRW{} and (\ref{eq:th1th})
-at $\theta=\frac{\pi}{2}$:
-
-\begin{align}
-R_{90} = D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} -1 = -\frac{2\beta}{k+2} \label{eq:th190}
-\end{align}
-Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing
-the parameter $\xi\equiv \frac{2}{k+2}$ we have:
-\begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} \label{eq:r90-incomplete}
-\end{align}
-
-Expanding the left side of (\ref{eq:th190}) until fourth order, equation (\ref{eq:th190})
-becomes:
-
-\begin{align}
-\theta_{1,90}^2\left(1+\frac{\theta_{1,90}^2}{15}\right) \simeq 3\xi\beta
-\end{align}
-
-Applying the approximation $\theta_1^2 \approx 3\xi\beta$ we found a solution
-for $\theta_{1,90}$:
-
-\begin{align}
-\theta_{1,90} = \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2}
-\end{align}
-
-And substituting into (\ref{eq:r90-incomplete}) we find the solution for $R_{90}$:
-
-\begin{align}
-R_{90} &= \frac{\left(3\xi\beta\right)^{1/2}}{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}
-\left(1-\xi\beta\right)} \\
-\implies \tilde{R}_{90} &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
-{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
-\end{align}
-
-\section{Derivation of Characteristic Radii in Isotropic Wind/Parallel interaction Problem}
-\label{app:ch-rad-Wilkin}
-
-$\tilde{R}_{90}$ is obtained by simply evaluating equation (\ref{eq:R-Wilkin}) at $\theta=\frac{\pi}{2}$.
-For the Radius of curvature we follow a similar procedure than the Wind/Wind interaction, but using equation
-(\ref{eq:R-Wilkin}) for $R(\theta)$ and inserting the cosecant into the square root.
-
-Expanding the terms of $R(\theta)$ we find the following:
-
-\begin{align}
-  \csc^2\theta &\simeq \theta^{-2}\left[1+\frac{\theta^2}{3}\left(1+\frac{\theta^2}{5}\right)\right] \\
-  1-\theta\cot\theta &\simeq \frac{\theta^2}{3}\left[1 + \frac{\theta^2}{15}\left(1+\frac{2\theta^2}{21}\right)\right] \\
-  \implies \tilde{R}(\theta) \simeq 1 + \frac{\theta^2}{5} + O\left[\theta^4\right]
-\end{align}
-
-From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
-\clearpage
-
-% Landscape table needs to go on its own page, so we need to manually
-% adjust the section counter so that it will ``belong'' to the next
-% section
-\addtocounter{section}{1}
-\sisetup{detect-all=true, detect-inline-weight=math}
-\sisetup{round-mode=figures, round-precision=2}
-\begin{landscape}
-\begin{table}
-  \setlength\tabcolsep{3pt}
-  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
-Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
-  \label{tab:big-p}
-  \input{figs/mipsgal-summary-stats-table-body.tex}
-\end{table}
-\end{landscape}
-\begin{table}
-  \contcaption{Results of all statistical tests performed on observed
-    bow shock shape parameters.}
-  \begin{tabular}{p{0.9\linewidth}}
-    \toprule
-    \textit{Description of columns:}
-    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
-    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
-    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
-    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
-    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
-    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
-    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
-It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
-    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
-    (Col.~13)~Ratio of standard deviations between the two sub-samples.
-    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
-    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
-    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
-    (Col.~16)~Brown--Forsythe test for dispersion
-    \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\addtocounter{section}{-1}
-
-\section{Distribution of p-values for all correlations tested}
-\label{sec:distr-p-values}
-\addtocounter{table}{1}
-
-\begin{figure}
-  (a)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
-  (b)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
-  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
-    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
-    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
-    bins and logarithmic vertical axis, with all values
-    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
-    lines shows the traditional threshold values for significance:
-    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
-    uniform distribution of \(p\)-values that would be expected if the
-    null hypothesis were always true, that is, if no significant
-    correlations existed.}
-  \label{fig:histo-p-values}
-\end{figure}
-
-Results from all the statistical tests discussed in \S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
-
-\begin{table}
-  \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
-  \label{tab:type-I}
-  \centering
-  \begin{tabular}{lrr} \toprule
-    Correlation & \(p\) & \(\alpha\) \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
-    \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
-    \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
-    \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
-    \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
-    \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
-    \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
-    \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
-    \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
-    \(R_c\) vs Facing & 0.71 & 1 \\
-    \(R_c\) vs H II & 0.50 & 1 \\
-    \(R_{90}\) vs Facing & 0.60 & 1 \\
-    \(R_{90}\) vs H II & 0.52 & 1 \\
-    \(R_c\) vs Multiple & 1.00 & 1 \\
-    \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
-    \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
-    \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
-    \(R_c\) vs Herschel & 0.074 & 0.3437 \\
-    \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
-    \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
-    \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The \(p\)-values are the probability of finding a difference between
-two populations as large as (or larger than) what is observed,
-\emph{given} that there is no difference in the underlying
-distribution from which the two populations are drawn (that is, given
-that the null hypothesis is true).  However, what we really want to
-know is something else: the probability that the null hypothesis is
-true, \emph{given} the observations.  That is, the probability,
-\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
-  error rate}.  The common mistake of conflating these two definitions
-is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
-error of the transposed conditional'', as discussed in detail by
-\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
-\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
-requires an estimate of the prior probability of the null hypothesis,
-independent of the observations.  Alternatively, it is also possible
-to find a lower bound on \(\alpha\) from a frequentist approach
-\citep{Sellke:2001a}:
-\begin{equation}
-  \label{eq:type-I}
-  \alpha(p) \ge \bigg[ 1 - \big(e\, p \ln p\big)^{-1} \bigg]^{-1}
-  \quad \text{valid for } p < 1/e.
-\end{equation}
-This is the approach we adopt here, which also numerically coincides
-with the Bayesian approach for the case where the prior probability of
-the null hypothesis is 0.5.  The reason that this is only a lower
-limit for \(\alpha\) is that if we have overwhelming a priori evidence that
-the null hypothesis is true (for instance, from previous empirical
-studies, or because it follows from a well-supported theory), then a
-Bayesian calculation would give a much higher value of \(\alpha\) than
-\eqref{eq:type-I} does.  In our case, however, we have no strong
-reasons for favoring any of the null hypotheses, so it is reasonable
-to assume \(\alpha\) is close to the lower limit given in \eqref{eq:type-I}.
-
-In order to choose a threshold \(p\)-value that counts as a
-``significant'' result, one then needs to balance the risks of false
-positives against the risks of \textit{false negatives}.  The false
-negative probability, \(\beta\), also known as \textit{Type II error
-  rate}, is the probability of failing to reject an untrue null
-hypothesis.  That is, in the context of this paper, it is the
-probability of failing to detect a real difference between two
-sub-samples, or a real correlation between two variables.  The
-complementary probability, \(1 - \beta\), is known as the
-\textit{statistical power} or sensitivity of the test.  The value of
-\(\beta\) depends on three factors:
-\begin{enumerate}[1.]
-\item The \textit{effect size}, which is a measure of the magnitude of
-  the difference in a dependent variable between two sub-samples, or
-  the degree of correlation between two continuous variables.  For the
-  two sub-sample case, it is common to use a standardised mean
-  difference, such as Cohen's \(d\) statistic \citep{Cohen:1988a}:
-  \(d = (\bar{X}_A - \bar{X}_B) / s\), where \(\bar{X}_A\),
-  \(\bar{X}_B\) are the means of the dependent variable \(X\) for
-  samples A and B, while \(s\) is the pooled standard deviation of
-  \(X\).  For the case of two continuous variables, the Pearson linear
-  correlation coefficient, \(r\), can be used.  In both cases, rules
-  of thumb have been developed \citep{Ruscio:2008a} for classifying an
-  effect as ``large'' (\(d > 0.8\), \(r > 0.4\)) or ``small''
-  (\(d < 0.2\), \(r < 0.1\)).  Alternatively, non-parametric
-  statistics can be used, such as the \(A\) measure of stochastic
-  superiority \citep{Delaney:2002a}.
-\end{enumerate}
-
-Obviously, this depends on the \textit{effect size}, which is the
-
-All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).
-It is therefore important to guard against the ``multiple comparisons problem'', whereby seemingly significant correlations are found where none really exist, simply by virtue of the large number of tests that were carried out.
-
-Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.
-
-The p-curve \citep{Head:2015a}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock.tex"
+%%% TeX-master: "quadrics-bowshock"
 %%% End:

### 2017-09-29 papers/Paper1/app-wilkinoid.tex
Start appendix on dust wave
Finish figure and caption.  Also re-arrange appendices into separate
files.

--- 2017-04-25 papers/Paper1/quadrics-appendix.tex
@@
-\appendix
-% \appendixpage
-% \addappheadtotoc
-\section{Parabola of Revolution}
-\label{app:parabola}
-
-In this section we develop the particular case of the parabola.
-The parametrization is given by:
-
-\begin{align}
-x &= - \frac{1}{2}R_ct^2 + R_0 \\
-y &= R_c t
-\end{align}
-Where $R_c$ is the radius of curvature and $R_0$ is the distance of the parabola nose to the
-origin.
-The respective tridimensional shape is given by:
-\begin{align}
-x &= -\frac{1}{2}R_ct^2 + R_0 \label{eq:x-par-a}\\
-y &= R_c t \cos\phi  \label{eq:y-par-a}\\
-z &= R_c t \sin\phi  \label{eq:z-par-a}
-\end{align}
-The azimutal angle where the surface is tangent to the line of sight in this case is given by:
-\begin{align}
-\sin\phi_t = -\frac{\tan i}{t} \label{eq:sin-tan-a} 
-\end{align}
-
-Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and
-(\ref{eq:z-par-a}) we find the apparent shape
-of the paraboloid:
-
-\begin{align}
-x' &= -\frac{R_c(\frac{1}{2}t^2 \cos^2 i -\sin^2 i)}{\cos i}+R_0\cos i \\
-y' &= R_c\left(t^2-\tan^2 i\right)^{1/2} 
-\end{align}
-
-Taking the limit of equations (\ref{eq:qprime}) and (\ref{eq:Aprime}) when $\theta_c$ tends to zero we find that:
-
-\begin{align}
-\left(\frac{q'}{q}\right)_{\mathrm{parabola}} &= 1+\frac{\tilde{R}_c\tan^2 i}{2}\\
-\left(\tilde{R}'_c\right)_{\mathrm{parabola}} &= \frac{\tilde{R}_c}{\cos^2 i + \frac{\tilde{R}_c}{2}\sin^2 i}
-\end{align}
-
-\section{Analytic derivation of the radius of curvature in the Thin Shell model}
-\label{app:rc-analytic}
-
-For small $\theta$ we may do a polynomial expansion for the shell shape such as:
-
-\begin{align}
-R \simeq R_0\left(1+\gamma\theta^2 + \Gamma\theta^4\right) \label{eq:R-exp}
-\end{align}
-
-The radius of curvature at the axis for $R$ is given by:
-
-\begin{align}
-R_c = R_0\left(1-2\gamma\right)^{-1}
-\end{align}
-
-The coefficient gamma may be derived by an expansion at small angles of equation
-(\ref{eq:th1th}), as follows:
-
-From the first term of the right side we get:
-
-\begin{align}
-\cot\theta &\simeq \theta^{-1}\left[1-\frac{1}{3}\theta^2\right] \\
-\cos^k\theta\sin^2\theta &\simeq \theta^2 - \left(\frac{1}{3} + \frac{k}{2}\right)\theta^4 \\
-\implies I_k(\theta) &\simeq \frac{1}{3}\theta^3\left[ 1 - \frac{1}{10}(3k+2)\theta^2\right]\\
-\implies 2\beta I_k(\theta)\cot\theta &\simeq \frac{2}{3}\beta\theta^2\left[1-\frac{1}{30}
-(9k+16)\theta^2\right]\label{eq:AR1} 
-\end{align}
-
-For the second term we get:
-
-\begin{align}
--\frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right) & \simeq -\beta\theta^2\left[1-\frac{1}{12}
-(3k+4)\theta^2\right] \label{eq:AR2}
-\end{align}
-
-For the left side we use equation (25) from \CRW{}. Then, equation (\ref{eq:th1th}) results
-as follows:
-
-\begin{align}
-\theta_1^2\left(1+\frac{1}{15}\theta_1^2\right) = \beta\theta^2\left[1+\frac{1}{60}(4-9k)
-\theta^2\right] \label{eq:th1th-app}
-\end{align}
-
-And we can use the approximation $\theta_1 \approx \beta\theta^2$ for the correction term in
-the left side of (\ref{eq:th1th-app}):
-
-\begin{align}
-\theta_1^2 &= \beta\theta^2\left[1+\frac{1}{60}(4-9k)\theta^2\right]
-\left(1-\frac{\beta}{15}\theta^2\right) \\
-\implies \theta_1^2 &= \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right]
-\label{eq:th1th-small}\\
-\mathrm{where:~} C_{k\beta} &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
-A_k &\equiv \frac{1}{15}-\frac{3k}{20}
-\end{align}
-
-Now, using equation (23) from \CRW{} we may estimate $R$ at low angles. To do this, we need to
-expand each term as follows (neglecting terms of order four or higher):
-
-\begin{align}
-\theta_1 = &= \beta^{1/2}\theta\left[1+ 2C_{k\beta}\theta^2\right]^{1/2} \\
-\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2C_{k\beta}\theta^2\right)\right]\\
-\sin\theta_1 &= \theta_1\left[1-\frac{\theta_1^2}{6}\right] \\
- &= \beta^{1/2}\theta\left[1+\left(C_{k\beta}-\frac{1}{6}\beta\right)\theta^2\right] \\
- \sin(\theta+\theta_1) &= \left[\theta+\theta_1\right]\left[1-\frac{\left(\theta+\theta_1
- \right)^2}{6}\right] \\
- &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{C_{k\beta}\beta^{1/2}}
- {1+\beta^{1/2}}-\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
-\end{align}
-
-So, combining these terms with equation (23) from \CRW{} we found the final expression for $R$:
-
-\begin{align}
-\frac{R}{D}\equiv \frac{\sin\theta_1}{\sin(\theta+\theta_1)} = \frac{\beta^1/2}{1+\beta^{1/2}}
-\left\lbrace 1 + \theta^2\left[\frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
-\right)\right] \right\rbrace \label{eq:r-small-theta}
-\end{align}
-
-Returning to equation (\ref{eq:R-exp}) we see the following:
-
-\begin{align}
-R_0 &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
-\gamma &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right)
-\label{eq:app-gamma}
-\end{align}
-
-We recover equation (27) of \CRW{} for $R_0$ and equation (\ref{eq:app-gamma}) is the
-needed term to calculate the radius of curvature at the axis.
-
-\section{Analytic derivation of \texorpdfstring{\boldmath $R_{90}$}{R\_90} in the thin shell model}
-\label{app:r90-analytic}
-
-To derive $R_{90}$ we need to evaluate equations (23) from \CRW{} and (\ref{eq:th1th})
-at $\theta=\frac{\pi}{2}$:
-
-\begin{align}
-R_{90} = D\tan\theta_{1,90} \\
-\theta_{1,90}\cot\theta_{1,90} -1 = -\frac{2\beta}{k+2} \label{eq:th190}
-\end{align}
-Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing
-the parameter $\xi\equiv \frac{2}{k+2}$ we have:
-\begin{align}
-R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} \label{eq:r90-incomplete}
-\end{align}
-
-Expanding the left side of (\ref{eq:th190}) until fourth order, equation (\ref{eq:th190})
-becomes:
-
-\begin{align}
-\theta_{1,90}^2\left(1+\frac{\theta_{1,90}^2}{15}\right) \simeq 3\xi\beta
-\end{align}
-
-Applying the approximation $\theta_1^2 \approx 3\xi\beta$ we found a solution
-for $\theta_{1,90}$:
-
-\begin{align}
-\theta_{1,90} = \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2}
-\end{align}
-
-And substituting into (\ref{eq:r90-incomplete}) we find the solution for $R_{90}$:
-
-\begin{align}
-R_{90} &= \frac{\left(3\xi\beta\right)^{1/2}}{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}
-\left(1-\xi\beta\right)} \\
-\implies \tilde{R}_{90} &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
-{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
-\end{align}
-
 \section{Derivation of Characteristic Radii in Isotropic Wind/Parallel interaction Problem}
@@
 From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
-\clearpage
-
-% Landscape table needs to go on its own page, so we need to manually
-% adjust the section counter so that it will ``belong'' to the next
-% section
-\addtocounter{section}{1}
-\sisetup{detect-all=true, detect-inline-weight=math}
-\sisetup{round-mode=figures, round-precision=2}
-\begin{landscape}
-\begin{table}
-  \setlength\tabcolsep{3pt}
-  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
-Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
-  \label{tab:big-p}
-  \input{figs/mipsgal-summary-stats-table-body.tex}
-\end{table}
-\end{landscape}
-\begin{table}
-  \contcaption{Results of all statistical tests performed on observed
-    bow shock shape parameters.}
-  \begin{tabular}{p{0.9\linewidth}}
-    \toprule
-    \textit{Description of columns:}
-    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
-    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
-    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
-    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
-    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
-    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
-    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
-It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
-    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
-    (Col.~13)~Ratio of standard deviations between the two sub-samples.
-    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
-    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
-    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
-    (Col.~16)~Brown--Forsythe test for dispersion
-    \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\addtocounter{section}{-1}
-
-\section{Distribution of p-values for all correlations tested}
-\label{sec:distr-p-values}
-\addtocounter{table}{1}
-
-\begin{figure}
-  (a)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
-  (b)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
-  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
-    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
-    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
-    bins and logarithmic vertical axis, with all values
-    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
-    lines shows the traditional threshold values for significance:
-    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
-    uniform distribution of \(p\)-values that would be expected if the
-    null hypothesis were always true, that is, if no significant
-    correlations existed.}
-  \label{fig:histo-p-values}
-\end{figure}
-
-Results from all the statistical tests discussed in \S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
-
-\begin{table}
-  \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
-  \label{tab:type-I}
-  \centering
-  \begin{tabular}{lrr} \toprule
-    Correlation & \(p\) & \(\alpha\) \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
-    \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
-    \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
-    \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
-    \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
-    \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
-    \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
-    \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
-    \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
-    \(R_c\) vs Facing & 0.71 & 1 \\
-    \(R_c\) vs H II & 0.50 & 1 \\
-    \(R_{90}\) vs Facing & 0.60 & 1 \\
-    \(R_{90}\) vs H II & 0.52 & 1 \\
-    \(R_c\) vs Multiple & 1.00 & 1 \\
-    \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
-    \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
-    \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
-    \(R_c\) vs Herschel & 0.074 & 0.3437 \\
-    \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
-    \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
-    \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The \(p\)-values are the probability of finding a difference between
-two populations as large as (or larger than) what is observed,
-\emph{given} that there is no difference in the underlying
-distribution from which the two populations are drawn (that is, given
-that the null hypothesis is true).  However, what we really want to
-know is something else: the probability that the null hypothesis is
-true, \emph{given} the observations.  That is, the probability,
-\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
-  error rate}.  The common mistake of conflating these two definitions
-is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
-error of the transposed conditional'', as discussed in detail by
-\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
-\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
-requires an estimate of the prior probability of the null hypothesis,
-independent of the observations.  Alternatively, it is also possible
-to find a lower bound on \(\alpha\) from a frequentist approach
-\citep{Sellke:2001a}:
-\begin{equation}
-  \label{eq:type-I}
-  \alpha(p) \ge \bigg[ 1 - \big(e\, p \ln p\big)^{-1} \bigg]^{-1}
-  \quad \text{valid for } p < 1/e.
-\end{equation}
-This is the approach we adopt here, which also numerically coincides
-with the Bayesian approach for the case where the prior probability of
-the null hypothesis is 0.5.  The reason that this is only a lower
-limit for \(\alpha\) is that if we have overwhelming a priori evidence that
-the null hypothesis is true (for instance, from previous empirical
-studies, or because it follows from a well-supported theory), then a
-Bayesian calculation would give a much higher value of \(\alpha\) than
-\eqref{eq:type-I} does.  In our case, however, we have no strong
-reasons for favoring any of the null hypotheses, so it is reasonable
-to assume \(\alpha\) is close to the lower limit given in \eqref{eq:type-I}.
-
-In order to choose a threshold \(p\)-value that counts as a
-``significant'' result, one then needs to balance the risks of false
-positives against the risks of \textit{false negatives}.  The false
-negative probability, \(\beta\), also known as \textit{Type II error
-  rate}, is the probability of failing to reject an untrue null
-hypothesis.  That is, in the context of this paper, it is the
-probability of failing to detect a real difference between two
-sub-samples, or a real correlation between two variables.  The
-complementary probability, \(1 - \beta\), is known as the
-\textit{statistical power} or sensitivity of the test.  The value of
-\(\beta\) depends on three factors:
-\begin{enumerate}[1.]
-\item The \textit{effect size}, which is a measure of the magnitude of
-  the difference in a dependent variable between two sub-samples, or
-  the degree of correlation between two continuous variables.  For the
-  two sub-sample case, it is common to use a standardised mean
-  difference, such as Cohen's \(d\) statistic \citep{Cohen:1988a}:
-  \(d = (\bar{X}_A - \bar{X}_B) / s\), where \(\bar{X}_A\),
-  \(\bar{X}_B\) are the means of the dependent variable \(X\) for
-  samples A and B, while \(s\) is the pooled standard deviation of
-  \(X\).  For the case of two continuous variables, the Pearson linear
-  correlation coefficient, \(r\), can be used.  In both cases, rules
-  of thumb have been developed \citep{Ruscio:2008a} for classifying an
-  effect as ``large'' (\(d > 0.8\), \(r > 0.4\)) or ``small''
-  (\(d < 0.2\), \(r < 0.1\)).  Alternatively, non-parametric
-  statistics can be used, such as the \(A\) measure of stochastic
-  superiority \citep{Delaney:2002a}.
-\end{enumerate}
-
-Obviously, this depends on the \textit{effect size}, which is the
-
-All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).
-It is therefore important to guard against the ``multiple comparisons problem'', whereby seemingly significant correlations are found where none really exist, simply by virtue of the large number of tests that were carried out.
-
-Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.
-
-The p-curve \citep{Head:2015a}
 

### 2017-09-29 Quadric-shapes/dust-trajectories.py

@@ -34,5 +34,6 @@ ax.set(xlim=[-3, 3], ylim=[-0.1, 5.9],
        xlabel="$x / R_0$",
        ylabel="$y / R_0$")
 sns.despine()
+fig.tight_layout()
 fig.savefig(figfile)
 print(figfile, end='')

### 2017-10-04 papers/Paper1/app-dust-wave.tex
Musings on grain-gas coupling
Include new dust wave figure in paper

@@
 \label{sec:shape-dust-wave}
+
+As an alternative to hydrodynamic or magnetohydrodynamic bow shocks,
+it is possible that some observed emission arcs may be bow waves due
+to the action of radiation pressure on dust grains.
 
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/dust-couple-stream-annotate}
+  \caption{Dust grain trajectories under influence of gas drag in
+    addition a repulsive central radiative force.  The dust
+    streamlines are shown in blue and the dust density as a linear
+    color scale, with maximum (white-yellow) of twice the ambient dust
+    density.  Results are shown for four values of the drag parameter
+    (see text): \(\alpha_\text{drag} = 0.25\), \(0.5\), \(1.0\), and
+    \(2.0\). The shape of the bow wave for the drag-free case
+    (Fig.~\ref{fig:dust-trajectories}) is shown by the thick dotted
+    line.}
+  \label{fig:dust-wave-coupling}
+\end{figure*}
+
 %%% Local Variables:

### 2017-10-06 papers/Paper1/sec-quadrics-observations.tex
Small progress on various small things

@@
 (spheroids, paraboloids, hyperboloids) and in
-Figure~\ref{fig:thin-shell-R90-Rc-snapshots} for the carawilkinoids
-and ancarawilkinoids.  It can be seen that the effect is relatively
-modest for bow shocks with projected shapes falling in the range
-\(1 < R_c/R_0 < 3\) and \(R_{90}/R_0 < 3\), as the vast majority of
-our observed sources do.  The increase in \(R_0\) is no more than a
+Figure~\ref{fig:thin-shell-R90-Rc-snapshots} for the wilkinoid,
+cantoids, and ancantoids.  It can be seen that the effect is
+relatively modest for bow shocks with projected shapes falling in the
+range \(1 < R_c/R_0 < 3\) and \(R_{90}/R_0 < 3\), as the vast majority
+of our observed sources do.  The increase in \(R_0\) is no more than a
 factor of 2 to 3 for moderate inclinations of \(30\) to \(60\degr\),
@@
 with a static environment.  In the thin-shell approximation, the
-predicted shapes are a carawilkinoid for weather vanes and a wilkinoid
+predicted shapes are a cantoid for weather vanes and a wilkinoid
 for runaways, see \S~\ref{sec:crw-scenario}.  The fact that no such
@@
 momentum ratio \(\beta\) for the weather vanes could be small, since the
-carawilkinoid becomes indistinguishable from the wilkinoid as
+cantoid becomes indistinguishable from the wilkinoid as
 \(\beta \to 0\), or (ii)~many of the bow shocks classified as ``Isolated''

### 2017-10-06 CRW-shapes/conic-head-tail-analytic.py

@@ -28,7 +28,7 @@ theta = np.linspace(0.0, np.pi, ntheta)
 
 figfilename = sys.argv[0].replace('.py', '.pdf')
 
-sns.set_style('whitegrid')
+sns.set_style('white')
 sns.set_color_codes('dark')
 
 NROWS = 2
@@ -110,6 +110,7 @@ axes[-1, 0].set(
     xlabel=r'$x / r_{0}$', ylabel=r'$y / r_{0}$',
 )
 
+sns.despine(bottom=True)
 fig.set_size_inches(2*nbeta, 2*nxi)
 fig.tight_layout()
 fig.savefig(figfilename)

### 2017-10-06 Dust-wave/dust-wave-Rc-R90.py

@@ -70,7 +70,7 @@ for alpha, ax, eax in zip(alphas, axes.flat, eaxes.flat):
     # Save the parameters for the head fit
     fitdata['head'] = {'Rc': Rc,
                        'R90': R90,
-                       'T': head_conic.b_a}
+                       'T': head_conic.b_a**2}
 
     # Now find a tail-fit conic
     # We only fit the tail between xswitch and xfar
@@ -93,7 +93,7 @@ for alpha, ax, eax in zip(alphas, axes.flat, eaxes.flat):
                        'a': best_model.a.value,
                        'b': best_model.b.value,
                        'r0': best_model.a.value + best_model.x0.value,
-                       'T': best_model.b.value/best_model.a.value}
+                       'T': (best_model.b.value/best_model.a.value)**2}
 
     # Finally, a third fit to the far tail with a hyperbola
     # model2 = conic_y_x(x0=15.0, a=30.0, b=1.0)
@@ -109,7 +109,7 @@ for alpha, ax, eax in zip(alphas, axes.flat, eaxes.flat):
                       'a': best_model2.a.value,
                       'b': best_model2.b.value,
                       'r0': best_model2.a.value + best_model2.x0.value,
-                      'T': best_model2.b.value/best_model2.a.value}
+                      'T': (best_model2.b.value/best_model2.a.value)**2}
 
     # Stash the fit data in the big dict
     alldata[alpha] = fitdata

### 2017-10-06 Dust-wave/three-quadric-dragoid-R90-vs-Rc.py

@@ -1,0 +1,77 @@
+import sys
+import json
+import numpy as np
+from matplotlib import pyplot as plt
+import matplotlib.ticker
+import seaborn as sns
+
+def Rc_prime(inc, Tc, Rc):
+    f = np.sqrt(1.0 + Tc*np.tan(inc)**2)
+    return Rc * (1 + np.tan(inc)**2) / f / (1.0 + Rc*(f - 1.0) / Tc)
+
+def Tc_prime(inc, Tc):
+    fsquared = 1.0 + Tc*np.tan(inc)**2
+    return Tc * (1.0 + np.tan(inc)**2) / fsquared
+
+def R90_prime(inc, Tc, Rc):
+    return np.sqrt(2*Rc_prime(inc, Tc, Rc) - Tc_prime(inc, Tc))
+
+plotfile = sys.argv[0].replace('.py', '.pdf')
+
+alldata = json.load(open('dust-wave-fitdata.json'))
+
+
+sns.set_style('white')
+sns.set_color_codes('dark')
+
+fig, ax = plt.subplots(figsize=(5, 5))
+
+
+left_annotate_pars = dict(xytext=(-5, 5), ha='right', va='bottom')
+right_annotate_pars = dict(xytext=(5, -5), ha='left', va='top')
+
+
+Rc_grid = np.linspace(0.0, 10.0, 2000)
+R90_T0_grid = np.sqrt(2*Rc_grid)
+R90_T1_grid = np.sqrt(2*Rc_grid - 1.0)
+R90_T1_grid[~np.isfinite(R90_T1_grid)] = 0.0 
+
+ax.fill_between(Rc_grid, R90_T1_grid, R90_T0_grid, color='k', alpha=0.2)
+ax.fill_between(Rc_grid, R90_T0_grid, color='k', alpha=0.1)
+ax.plot(Rc_grid, R90_T0_grid, c='k', lw=0.5)
+ax.axhline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
+ax.axvline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
+ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
+
+inc = np.linspace(0.0, 0.5*np.pi, 500, endpoint=False)
+inc_deg = np.degrees(inc)
+
+colors = 'bmgr'
+
+for (alpha, data), color in zip(alldata.items(), colors):
+    # Parameters for head conic
[…]

### 2017-10-13 papers/Paper1/obs-bowshocks.tex
Split observational material into its own paper !!!!!!!

--- 2017-05-08 papers/Paper1/quadrics-bowshock.tex
@@
 
+% Define a fermata symbol for use inline with text
+% 04 Jul 2017 WJH
+% Based on info in Secs 18.4.1 and 24.1 of musixdoc.pdf
+\usepackage{musixtex}
+\makeatletter
+\newcommand\textfermata{%
+  {\let\extractline\relax
+    \setlines10\smallmusicsize \nobarnumbers \nostartrule
+    \staffbotmarg0pt \setclefsymbol1\empty \global\clef@skip0pt
+    \raisebox{0ex}[0ex][0ex]{
+      \startextract\addspace{-\afterruleskip}%
+      \notes\fermataup{-2}\en
+      \zendextract}}}
+\makeatother
+
+% % The \eye command is in the dingbat package, but we need to take care
+% % of a naming conflict with the AMS package
+% \usepackage{savesym}
+% \savesymbol{checkmark}
+% \usepackage{dingbat}
+
+% The "eye" symbol is drawn with the \faEye command of the fontawesome
+% package
+\usepackage{fontawesome}
+% The ``irregular'' symbol is drawn from the Icelandic Sorcery and Witchcraft 
+\usepackage{staves}
+
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
@@
 
-\title[Bowshock shapes]{True versus apparent shapes of astrophysical bow shocks}
+\title[Stellar bow shocks]{Weather vanes and runaways: Bow
+  shocks across the HR diagram}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Tarango Yong \& Henney]{
-  Jorge A. Tarango Yong \& William J. Henney\\
+\author[Henney \& Tarango Yong]{
+  William J. Henney \& Jorge A. Tarango Yong \\
   \AddressCRyA
@@
   interstellar medium itself that is moving, perhaps as the result of
-  a champagne flow of ionized gas from a nearby \hii{} region.  We
-  present a new two-dimensional classification scheme for the shape of
-  such bow shocks, which accounts for both the apex (pointy versus
-  flat) and the wings (open versus closed).  For different theoretical
-  bow shock models, we show how variations in the true shape can be
-  disentangled from projection effects due to variations in the
-  inclination angle.  We apply our classification scheme to three
-  different observational datasets: mid-infrared arcs around hot
-  main-sequence stars (\(N = 227\)), far-infrared arcs around luminous
-  cool stars (\(N = 7\)), and emission-line arcs around proplyds and other
-  young stars in the Orion Nebula (\(N = 18\)).  We find significant
-  differences between the three datasets: cool star bow shocks have
-  markedly more closed wings than hot star bow shocks, while
-  differences in the shape of the apex region are only marginally
-  significant.  The Orion Nebula arcs, on the other hand, have both
-  significantly more open wings and significantly flatter apices than
-  the OhotB star bow shocks.  We discuss the implications of these
-  differences for understanding the physics of the bow shock
-  interaction in the three classes of sources.
+  a champagne flow of ionized gas from a nearby \hii{} region.
+  We recently proposed a new two-dimensional classification scheme for
+  the shape of such bow shocks, which we here apply to three very
+  different observational datasets.  These are: (1)~mid-infrared arcs
+  around hot main-sequence stars (\(N = 227\)); (2)~far-infrared arcs
+  around luminous cool stars (\(N = 7\)); and (3)~emission-line arcs
+  around proplyds and other young stars in the Orion Nebula
+  (\(N = 18\)).  We find significant differences between the three
+  datasets: cool star bow shocks have markedly more closed wings than
+  hot star bow shocks, while differences in the shape of the apex
+  region are only marginally significant.  The Orion Nebula arcs, on
+  the other hand, have both significantly more open wings and
+  significantly flatter apices than the hot star bow shocks.  We
+  discuss the implications of these differences for understanding the
+  physics of the bow shock interaction in the three classes of
+  sources.
 \end{abstract}
 
-\input{sec-intro}
-\input{sec-generic-model}
-\input{sec-projection}
-\input{sec-conic}
-\input{sec-thin-shell}
+\input{sec-obs-intro}
 \clearpage
 \input{sec-quadrics-observations}
-\input{sec-conclusions}
+\input{sec-obs-conclusions}
+\clearpage
 \bibliographystyle{mnras}
@@
 \bibliography{bowshocks-biblio}
-\clearpage
-\input{quadrics-appendix}
+\appendix
+\input{app-p-values}
 

### 2017-10-13 papers/Paper1/sec-obs-conclusions.tex
Split observational material into its own paper !!!!!!!

--- 2016-10-14 papers/Paper1/sec-conclusions.tex
@@
 \section{Conclusions}
-\label{sec:conc}
-
-\newcommand\thC{\(\theta^1\)\,Ori~C}
-\defcitealias{Canto:1996}{CRW}
-
-We developed a method to estimate the shape of a generic bow shock product of the
-interaction of two winds as well as it apparent shape due to it orientation relative to the line of sight, asuuming
-the bow shock is geometrically and optically thin.
-
-In the general case we require numerical techniques, but is possible to handle analytically the apparent shape of
-the quadrics of revolution.
-
-Also we made a generalization of \CRW{} work where the weakest interacing wind is hemispherical and anisotropic where its
-density follows a power law of $\cos\theta$. Altrough other models also may be used.
-
-In any case we developed a form to derive a set of measurable radii which are used as comparison between the \CRW{} model, the quadrics
-of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
-(ONC) due to the interaction of the photoevaporated wind from proplyds and the stallar wind of \thC{}
-
-%and was applied to the proplyds in the core of the ONC.
-%We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
-%sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
-%on \CRW{} work to estimate the intrinsic bow shock shape and get the ionizing flux for ionization balance 
-%and the stagnation pressure for our sample of proplyds.
-%Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
-%distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
-%while LV2 has the most anisotropic flow. And for the 177-341, 169-348 and 180-331 we found out that 
-%the stellar wind is not enough to keep their bow socks stationary.
+\label{sec:conclusion}
 
@@
 %%% mode: latex
-%%% TeX-master: "proplyd-bowshocks"
+%%% TeX-master: "obs-bowshocks"
 %%% End:

### 2017-10-13 papers/Paper1/quadrics-bowshock.tex
Description of Cox's Herschel source classes I-IV
Use more whacky symbols
Finally get back into writing. Describe fits to Herschel arcs
Add figure showing th90 versus inclination
Start appendix on dust wave
Finish figure and caption.  Also re-arrange appendices into separate
files.
Remove observational sections from theory paper and rework abstract
The abstract still needs a bit more

--- 2016-06-10 papers/Paper1/proplyd-bowshocks.tex
@@
 \usepackage{booktabs}
-\usepackage{hyperref}
 \usepackage{siunitx}
 \usepackage{color}
+\usepackage{enumerate}
+\usepackage{pdflscape}
+\usepackage{rotating}
+\usepackage{hyperref}
+
+% Define a fermata symbol for use inline with text
+% 04 Jul 2017 WJH
+% Based on info in Secs 18.4.1 and 24.1 of musixdoc.pdf
+\usepackage{musixtex}
+\makeatletter
+\newcommand\textfermata{%
+  {\let\extractline\relax
+    \setlines10\smallmusicsize \nobarnumbers \nostartrule
+    \staffbotmarg0pt \setclefsymbol1\empty \global\clef@skip0pt
+    \raisebox{0ex}[0ex][0ex]{
+      \startextract\addspace{-\afterruleskip}%
+      \notes\fermataup{-2}\en
+      \zendextract}}}
+\makeatother
+
+% % The \eye command is in the dingbat package, but we need to take care
+% % of a naming conflict with the AMS package
+% \usepackage{savesym}
+% \savesymbol{checkmark}
+% \usepackage{dingbat}
+
+% The "eye" symbol is drawn with the \faEye command of the fontawesome
+% package
+\usepackage{fontawesome}
+% The ``irregular'' symbol is drawn from the Icelandic Sorcery and Witchcraft 
+\usepackage{staves}
+
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
@@
 
+\usepackage{etoolbox}
+\robustify\bfseries
+\robustify\itshape
+
+%% Bold italic
+\newcommand\hmmax{0}            % we don't need heavy fonts
+\newcommand\bmmax{1}            % reduce use of math alphabets for bold
+\usepackage{bm}
+
 %% Bundled custom packages
 \usepackage{aastex-compat}
-\usepackage{astrojournals}
 
-\title[Bowshock shapes]{True versus apparent shapes of astrophysical bow shocks}
+% Definitions needed in abstract
+\newcommand\hii{\ion{H}{ii}}
+
+\title[Bowshock shapes]{True versus apparent shapes of bow shocks and bow waves}
 
@@
 \begin{abstract}
-  We develop a general framework for the effects of viewing angle on
-  the apparent shape of a limb-brightened, cylindrically symmetric
-  curved shock (bow shock).  
+  Astrophysical bow shocks are a common result of the interaction
+  between supersonic plasma flows, such as winds or jets from stars or
+  active galaxies.  Similarly shaped radiation bow waves are produced
+  by the relative motion between dust grains and a luminous source.
+  For cylindrically symmetric bow shocks and waves, we develop a
+  general theory of the effects of inclination angle, and propose a
+  new two-dimensional classification scheme for bow shapes, which is
+  based on dimensionless geometric ratios that can be estimated from
+  observational images.  The two ratios are related to the
+  ``snubness'' of the bow's apex and the ``openness'' of its wings.
+
+  ADD MORE
 \end{abstract}
@@
 \input{sec-conic}
-\input{sec-application}
+\input{sec-thin-shell}
 \input{sec-conclusions}
-
-%% TODO Investigate newer versions of BST file from
-%% https://github.com/timj/mn2e-bst
-\bibliographystyle{mn2e}
+\clearpage
+\bibliographystyle{mnras}
 %% All references should be put in the BibTeX file bowshocks-biblio.bib
 \bibliography{bowshocks-biblio}
+\appendix
+\input{app-parabola}
+\input{app-rcurv}
+\input{app-r90}
+\input{app-wilkinoid}
+\input{app-dust-wave}
 

### 2017-10-14 papers/Paper1/sec-thin-shell.tex
Revamped Fig 16 with the [[an]cara]wilkinoids on Rc-R90 diagram
Split into two panels for clarity.  Annotated with i* where we switch
over from the head to the tail for R90
Add new figures to cantoid section and remove unwanted ones

--- 2017-03-06 papers/Paper1/sec-thin-shell.tex
@@
 
-\newcommand\iso{\ensuremath{^{\mathrm{iso}}}}
+% \newcommand\iso{\ensuremath{^{\mathrm{iso}}}}
 
-\begin{table}
-  \caption{Coefficients for hyperbola fit to bowshock tails}
-  \label{tab:tail-fit-coeffs}
-  \renewcommand\arraystretch{1.2}
-  \setlength\tabcolsep{0.5\tabcolsep}
-  \begin{tabular}{@{}llll@{}}
-    \toprule
-    Equation~(\ref{eq:tail-analytic-x0}) & 
-    \multicolumn{3}{l}{
-    Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
-    } \\ \midrule
-    \( C\iso_0 = +1.3195     \)    
-    & \( c_{0,0} = +2.0758   \)  
-    & \( c_{1,0} = -0.2309   \)  
-    & \( c_{2,0} = -0.2532   \)\\
-      \( C\iso_1 = +0.4229     \)    
-    & \( c_{0,1} = +0.9571   \)  
-    & \( c_{1,1} = -0.1530   \)  
-    & \( c_{2,1} = -0.2487   \)\\
-      \( C\iso_2 = +0.1092     \)    
-    & \( c_{0,2} = +0.2528   \)  
-    & \( c_{1,2} = -0.0360   \)  
-    & \( c_{2,2} = -0.0794   \)\\
-      \( C\iso_3 = +0.0051     \)    
-    & \( c_{0,3} = +0.0171   \)  
-    & \( c_{1,3} = -0.0010   \)  
-    & \( c_{2,3} = -0.0095   \)\\ \midrule
-    Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
-    \multicolumn{3}{l}{
-    Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
-    } \\ \midrule
-    \( D\iso_0 = +0.7962   \)    
-    & \( d_{0,0} = +0.8516 \)  
-    & \( d_{1,0} = -0.0907 \)  
-    & \( d_{2,0} = -0.2002 \)\\
-      \( D\iso_1 = -0.2363   \)    
-    & \( d_{0,1} = -0.7620 \)  
-    & \( d_{1,1} = +0.1411 \)  
-    & \( d_{2,1} = -0.0295 \)\\
-      \( D\iso_2 = -0.0126   \)    
-    & \( d_{0,2} = -0.0683 \)  
-    & \( d_{1,2} = +0.0390 \)  
-    & \( d_{2,2} = -0.0236 \)\\
-    \bottomrule
-  \end{tabular}
-\end{table}
+% \begin{table}
+%   \caption{Coefficients for hyperbola fit to bowshock tails}
+%   \label{tab:tail-fit-coeffs}
+%   \renewcommand\arraystretch{1.2}
+%   \setlength\tabcolsep{0.5\tabcolsep}
+%   \begin{tabular}{@{}llll@{}}
+%     \toprule
+%     Equation~(\ref{eq:tail-analytic-x0}) & 
+%     \multicolumn{3}{l}{
+%     Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
+%     } \\ \midrule
+%     \( C\iso_0 = +1.3195     \)    
+%     & \( c_{0,0} = +2.0758   \)  
+%     & \( c_{1,0} = -0.2309   \)  
+%     & \( c_{2,0} = -0.2532   \)\\
+%       \( C\iso_1 = +0.4229     \)    
+%     & \( c_{0,1} = +0.9571   \)  
+%     & \( c_{1,1} = -0.1530   \)  
+%     & \( c_{2,1} = -0.2487   \)\\
+%       \( C\iso_2 = +0.1092     \)    
+%     & \( c_{0,2} = +0.2528   \)  
+%     & \( c_{1,2} = -0.0360   \)  
+%     & \( c_{2,2} = -0.0794   \)\\
+%       \( C\iso_3 = +0.0051     \)    
+%     & \( c_{0,3} = +0.0171   \)  
+%     & \( c_{1,3} = -0.0010   \)  
+%     & \( c_{2,3} = -0.0095   \)\\ \midrule
+%     Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
+%     \multicolumn{3}{l}{
+%     Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
+%     } \\ \midrule
+%     \( D\iso_0 = +0.7962   \)    
+%     & \( d_{0,0} = +0.8516 \)  
+%     & \( d_{1,0} = -0.0907 \)  
+%     & \( d_{2,0} = -0.2002 \)\\
+%       \( D\iso_1 = -0.2363   \)    
+%     & \( d_{0,1} = -0.7620 \)  
+%     & \( d_{1,1} = +0.1411 \)  
+%     & \( d_{2,1} = -0.0295 \)\\
+%       \( D\iso_2 = -0.0126   \)    
+%     & \( d_{0,2} = -0.0683 \)  
+%     & \( d_{1,2} = +0.0390 \)  
+%     & \( d_{2,2} = -0.0236 \)\\
+%     \bottomrule
+%   \end{tabular}
+% \end{table}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
-  \caption{Double quadric fits to thin shell
-    solutions.}
-  \label{fig:head-tail}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
+%   \caption{Double quadric fits to thin shell
+%     solutions.}
+%   \label{fig:head-tail}
+% \end{figure*}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figs/two-quadric-th90-vs-i}
+%   \caption{Variation with inclination of the body-frame polar angle
+%     \(\theta_{90}\) that corresponds to the projected perpendicular radius
+%     \(R’_{90}\).  Line colors and thicknesses represent different
+%     quadrics of revolution, as in
+%     Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
+%     important because the quadric fits to the bow shock shape must be
+%     accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
+%     for \(R’_{90}\).}
+%   \label{fig:projected-th90}
+% \end{figure}
 
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/two-quadric-R90-vs-Rc}
+  \includegraphics[width=\linewidth]{figs/test_xyprime}
+  \caption{Apparent bow shapes as a function of inclination angle for
+    isotropic thin shell models. (a)~Confocal paraboloid for
+    comparison (shape independent of inclination).
+    (b)~Wilkinoid. (c)~Cantoid, \(\beta = 0.001\). (d)~Cantoid,
+    \(\beta = 0.01\). }
+  \label{fig:xyprime}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/test_xyprime_ancantoid}
+  \caption{Further apparent bow shapes as a function of inclination
+    angle for anisotropic thin shell models (ancantoids).
+    (a)~\(\beta = 0.001\), \(\xi =.8\); (b) (a)~\(\beta = 0.1\),
+    \(\xi =.8\); (c)~\(\beta = 0.001\) \(\xi =0.4\); (d)
+    \(\beta = 0.1\) \(\xi =0.4\).}
+  \label{fig:xyprime-anacantoid}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \setkeys{Gin}{width=0.48\linewidth}
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
+    \includegraphics{figs/ancantoid-R90-vs-Rc-a}
+        & \includegraphics{figs/ancantoid-R90-vs-Rc-b} \\
+  \end{tabular}
   \caption{Diagnostic diagram for thin shell models}
   \label{fig:thin-shell-R90-Rc}
-\end{figure}
+\end{figure*}
 

### 2017-10-15 papers/Paper1/sec-standing-wave.tex
Add section on standing waves

\section{Perturbed bows}
\label{sec:perturbed-bows}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/compare_xyprime_wave-wilkinoid}
  \caption{Small-amplitude standing wave perturbations to bow shapes.}
  \label{fig:perturb-shapes}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]
  {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
  \caption{Plane-of-sky projections of perturbed bow shapes}
  \label{fig:perturb-xy-prime}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]
  {figs/wilkinoid-R90-vs-Rc-wave-A010-N10}
  \includegraphics[width=\linewidth]
  {figs/wilkinoid-R90-vs-Rc-wave-A005-N20}
  \caption{Diagnostic diagram for perturbed shapes}
  \label{fig:perturb-Rc-R90}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

### 2017-10-16 papers/Paper1/sec-standing-wave.tex
Start write-up of standing wave perturbations

@@
   \label{fig:perturb-shapes}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \label{fig:perturb-xy-prime}
-\end{figure}
+\end{figure*}
+
+The bow shock models that we have considered so far have been
+steady-state: although material is moving throughout the bow, the
+pattern of its structure does not vary with time.  In this section, we
+consider small, time-varying perturbations to such a steady-state
+structure.  These may be due to periodic variations in the
+momentum-loss rate of one of the winds, or due to dynamical
+instabilities in the shocked shell.
+
+For simplicity, we consider standing waves with an amplitude that
+multiplies the bow shock radius \(R\) and a pattern that is periodic
+in the axial angle \(\theta\): \(R(\theta) \to (1 + \Delta) R(\theta)\), where
+\begin{equation}
+  \label{eq:standing-wave}
+  \Delta = A \cos(N \theta) \cos(2\pi \varphi)
+\end{equation}
 
@@
   \includegraphics[width=\linewidth]
-  {figs/wilkinoid-R90-vs-Rc-wave-A010-N10}
+  {figs/wave-R90-vs-Rc-A010-N10}
   \includegraphics[width=\linewidth]
-  {figs/wilkinoid-R90-vs-Rc-wave-A005-N20}
+  {figs/wave-R90-vs-Rc-A005-N20}
   \caption{Diagnostic diagram for perturbed shapes}

### 2017-10-16 papers/Paper1/quadrics-bowshock.tex
Add section on standing waves
Write about the standing wave perturbations
Finish fig captions for shapes and projected shapes.  Finish text
about shapes.

@@
 % \usepackage[varg]{txfonts}
-\usepackage[varg]{newtxmath}
-\usepackage{newtxtext}
 \usepackage{graphicx}
@@
 \usepackage{hyperref}
+
+\usepackage[T1]{fontenc} 
+\usepackage[utf8]{inputenc}
 
@@
 
+% Fonts 
+\usepackage{newtxtext}
+% Note: newtxmath must come AFTER newtxtext
+\usepackage[varg]{newtxmath}
+
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
@@
 
-\title[Bowshock shapes]{True versus apparent shapes of bow shocks and bow waves}
+\title[Bow shock shapes]{True versus apparent shapes of bow shocks and bow waves}
 
@@
   observational images.  The two ratios are related to the
-  ``snubness'' of the bow's apex and the ``openness'' of its wings.
+  ``flatness'' of the bow's apex and the ``openness'' of its wings.
 
@@
 \input{sec-thin-shell}
+\clearpage
+\input{app-dust-wave}
+\clearpage
+\input{sec-standing-wave}
 \input{sec-conclusions}
@@
 \input{app-wilkinoid}
-\input{app-dust-wave}
 

### 2017-10-16 papers/Paper1/sec-standing-wave.tex
Write about the standing wave perturbations
Finish fig captions for shapes and projected shapes.  Finish text
about shapes.

@@
-\section{Perturbed bows}
-\label{sec:perturbed-bows}
-
-\begin{figure*}
+\begin{figure*}[t!]
   \centering
   \includegraphics[width=\linewidth]{figs/compare_xyprime_wave-wilkinoid}
-  \caption{Small-amplitude standing wave perturbations to bow shapes.}
+  \caption{Small-amplitude standing wave perturbations to wilkinoid
+    bow shapes.  The maximum deviations from the base shape are seen
+    at phases \(\phi = 0\) (blue line) and \(\phi = 0.5\) (red line), while
+    the perturbation is zero at \(\phi = 0.25\) and \(0.75\) (black
+    line).  Results are shown left to right for increasing wave
+    numbers \(N\) and decreasing amplitudes \(A\): (a)~\(A = 0.1\),
+    \(N = 1.0\), (b)~\(A = 0.05\), \(N = 2.0\), (a)~\(A = 0.02\),
+    \(N = 5.0\).}
   \label{fig:perturb-shapes}
@@
   {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
-  \caption{Plane-of-sky projections of perturbed bow shapes}
+  \caption{Plane-of-sky projections of perturbed bow shapes.  In all
+    cases, the base bow shape is ancantoid with \(\xi = 0.8\),
+    \(\beta = 0.005\) and the perturbation is the same as in the central
+    panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
+    \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
+    inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
+    color and thickness, see key) and for different fractional phases
+    of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
+    (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
+    the spatial coordinates are normalized to the instantaneous
+    projected apex radius \(R_0'\) at each phase.}.
   \label{fig:perturb-xy-prime}
 \end{figure*}
+
+\section{Perturbed bows}
+\label{sec:perturbed-bows}
 
@@
 
-For simplicity, we consider standing waves with an amplitude that
-multiplies the bow shock radius \(R\) and a pattern that is periodic
-in the axial angle \(\theta\): \(R(\theta) \to (1 + \Delta) R(\theta)\), where
+We consider fractional perturbations \(\Delta(\theta, t)\) of a base shape
+\(R(\theta)\), such that
+\(R(\theta) \to [1 + \Delta(\theta, t)] R(\theta)\).  For simplicity,
+\(\Delta(\theta, t)\) is a standing wave of constant amplitude \(A\), which is
+periodic in \(\theta\), with wave number \(N\).  In cylindrical symmetry
+\(\Delta(\theta, t)\) must be even in \(\theta\), so can be expressed as
 \begin{equation}
   \label{eq:standing-wave}
-  \Delta = A \cos(N \theta) \cos(2\pi \varphi)
+  \Delta(\theta, t) = A \cos(N \theta) \cos(2\pi \varphi) . 
 \end{equation}
+For waves with period \(P\), the fractional phase \(\varphi\) will
+vary with time \(t\) as
+\begin{equation}
+  \label{eq:fractional-phase}
+  \varphi(t) = (\varphi_0 + t/P) \bmod 1.0\ ,
+\end{equation}
+where \(\varphi_0\) is an arbitrary reference phase.
+
+Example oscillations with wave numbers \(N = 1.0\), \(2.0\), and
+\(5.0\) superimposed on a wilkinoid base shape are shown in
+Figure~\ref{fig:perturb-shapes}.  There are \(N\) nodes of the
+oscillation between \(\theta = 0 \to \pi\), always with an antinode at the apex
+(\(\theta = 0\)), as required by symmetry.  So, with \(N = 1.0\) there is a
+node (fixed point) in the near wing at \(\theta = \pi/2\), but an antinode in
+the far wing at \(\theta = \pi\), which is in antiphase with the oscillation
+of the apex, giving rise to a large-scale ``breathing'' mode of
+oscillation.  With \(N = 2.0\), there are nodes at \(\theta = \pi/4\) and
+\(3\pi/4\), while the antiphase antinode has moved to the near wing at
+\(\theta = \pi/2\).  There is still an antinode in the far wing at
+\(\theta = \pi\) but it is now in phase with the apex, giving rise to a
+``curling-up/straightening-out'' mode of oscillation.  With
+\(N = 5.0\), there are many more nodes and antinodes, giving a
+``ringing'' mode of oscillation.  Note that all our examples have
+\(A \propto 1/N\) in order to keep the local curvature relatively low.  If
+the product \(A N\) is not small compared to unity, then the local
+curvature can be so extreme as to reverse the concave shape of the
+base bow shape, producing locally convex regions.
 

### 2017-10-17 papers/Paper1/sec-standing-wave.tex
Text description of projection effects in perturbed bows

@@
     the spatial coordinates are normalized to the instantaneous
-    projected apex radius \(R_0'\) at each phase.}.
+    projected apex radius \(R_0'\) at each phase, so the apex does not
+    appear to move.}.
   \label{fig:perturb-xy-prime}
@@
 Figure~\ref{fig:perturb-shapes}.  There are \(N\) nodes of the
-oscillation between \(\theta = 0 \to \pi\), always with an antinode at the apex
+oscillation between \(\theta = [0, \pi]\), always with an antinode at the apex
 (\(\theta = 0\)), as required by symmetry.  So, with \(N = 1.0\) there is a
@@
 
+If the bow shape is viewed at different inclinations, then the effect
+of the oscillations on the projected shape will vary.  In particular,
+the apex-to-wing interval in body-frame angle changes from
+\(\theta = [0, \pi/2]\) at \(i = 0\) to
+\(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see
+equations~\eqref{eq:thetapar} and \eqref{eq:th90}.  The difference
+\(\theta_{90} - \theta_0\) is always a declining function of \(|i|\), so the
+oscillations of the tangent line become increasingly stretched out as
+the inclination increases.  This effect can be seen in
+Figure~\ref{fig:perturb-xy-prime}, which shows an example of the
+variation in projected perturbed shape with inclination angle for 3
+different phases, this time for an ancantoid base shape and the
+\(N = 2.0\) perturbation shown in Figure~\ref{fig:perturb-shapes}b.
+The most marked changes with phase are seen for low inclinations,
+whereas the changes are smaller, although still noticeable, for
+\(|i| \ge 45^\circ\). If \(A N\) exceeds about 0.5, then the local curvature
+of the perturbations is so extreme that multiple tangent lines exist
+at intermediate inclinations, which produces the appearance of
+additional incomplete bright arcs inside the main arc of the bow.
+
 \begin{figure}

### 2017-10-19 papers/Paper1/quadrics-bowshock.tex
Text description of projection effects in perturbed bows
Invent two new words: planitude and alatude
Planitude was already a word it seems.  I am co-opting it for R_c/R_0

Alatude is a complete neologism, it means R_90/R_0c

@@
 % Note: newtxmath must come AFTER newtxtext
-\usepackage[varg]{newtxmath}
+\usepackage[varvw,smallerops]{newtxmath}
 
@@
   For cylindrically symmetric bow shocks and waves, we develop a
-  general theory of the effects of inclination angle, and propose a
-  new two-dimensional classification scheme for bow shapes, which is
-  based on dimensionless geometric ratios that can be estimated from
-  observational images.  The two ratios are related to the
-  ``flatness'' of the bow's apex and the ``openness'' of its wings.
+  general theory for the effects of inclination angle on the apparent
+  shape. We propose a new two-dimensional classification scheme for
+  bow shapes, which is based on dimensionless geometric ratios that
+  can be estimated from observational images.  The two ratios are
+  related to the ``flatness'' of the bow's apex, which we term
+  \textit{planitude} and the ``openness'' of its wings, which we term
+  \textit{alatude}.
 

### 2017-11-01 papers/Paper1/quadrics-bowshock.tex
Add figure with empirical terminology to theory paper
Also, finish abstract and add keywords

@@
 }
+
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2017}
+
 \begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \maketitle
@@
   can be estimated from observational images.  The two ratios are
-  related to the ``flatness'' of the bow's apex, which we term
-  \textit{planitude} and the ``openness'' of its wings, which we term
-  \textit{alatude}.
+  related to the flatness of the bow's apex, which we term
+  \textit{planitude} and the openness of its wings, which we term
+  \textit{alatude}.  We calculate the expected distribution on the
+  planitude--alatude diagram for a variety of simple geometrical and
+  physical models: quadrics of revolution, wilkinoids, cantoids,
+  ancantoids, and dragoids.  We further show how these are modified in
+  the presence of small-amplitude standing-wave oscillations of the
+  basic shape, as may be produced by hydrodynamic instabilities or a
+  time-varying source.
+\end{abstract}
 
-  ADD MORE
-\end{abstract}
+\begin{keywords}
+  hydrodynamics -- stars: winds, outflows
+\end{keywords}
 
@@
 
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}

### 2017-11-01 papers/Paper1/sec-generic-model.tex
Add figure with empirical terminology to theory paper
Also, finish abstract and add keywords

--- 2017-09-21 papers/Paper1/sec-generic-model.tex
@@
 \label{sec:generic-model}
-
-\begin{figure}
-  % \includegraphics[width=\linewidth]{2winds-scheme}
-  \includegraphics[width=\linewidth]{figs/generic-bowshock}
-  \caption{Quasi-stationary bow shock structure formed by the
-    interaction of two supersonic winds.  Lower-left inset box shows
-    the case where the inner wind is anisotropic. The streamlines
-    (thin lines) are drawn so as to be qualitatively realistic: they
-    are straight in regions of hypersonic flow, but curved in subsonic
-    regions, responding to pressure gradients in the shocked shells.}
-\label{fig:2-winds}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
-  \caption[]{Schematic diagram of two-wind interaction problem,
-    following \citet{Canto:1996}.}
-  \label{fig:crw-schema}
-\end{figure}
-
-The general case of a two-wind interaction bow shock is illustrated in
-Figure~\ref{fig:2-winds}.  If the winds are isotropic, then the bow
-shock pattern wraps around the weaker of the two sources, in
-
-The bow shocks we consider are originated by a source located at the
-origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a
-terminal (supersonic) velocity $v_w$. This wind interacts with another
-wind originated by another source located at a distance $D$ from the
-first one.  The mass loss rate of the second source is $\dot{M}_{w1}$
-and the terminal velocity is $v_{w1}$. The momentum of the wind of the
-second source is higher than the momentum of the first one, and the
-resultant bow shock is stationary due to pressure balance.
-
-\subsection{Characteristic Radii}
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/characteristic-radii}
-  \caption{Characteristic radii in the body frame.}
-  \label{fig:characteristic-radii}
-\end{figure}
-
-In order to contrast different bow shock models, we derive a set of
-measurable radii. Each model used should predict them and these
-predictions can be compared with observations.
-\begin{itemize}
-\item Radius at axis of symmetry. Denoted as $R_0$.
-\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
-\item Radius at the perpendicular direction to the symmetry
-  axis. Denoted as $R_{90}$
-\item For open bow shocks, the asymptotic angle. Denoted as
-  $\theta_\infty$
-\end{itemize}
 

### 2017-11-01 papers/Paper1/sec-intro.tex
Add figure showing th90 versus inclination
Add figure with empirical terminology to theory paper
Also, finish abstract and add keywords

@@
 %% 
-%% Examples of astrophysical bowshocks
+%% Examples of astrophysical bow shocks
 %%
 
+\begin{figure}
+  \centering
+  \bigskip
+  \includegraphics[width=0.9\linewidth]{figs/bow-terminology}
+  \caption{Descriptive terminology for a stellar bow shock.  The apex
+    is the closest approach of the bow to the star, while the wings
+    are the parts of the bow that curve back past the star.}
+  \label{fig:bow-terminology}
+\end{figure}
 A further class of astrophysical bow shock is driven by highly
@@
 In such cases the term ``bow shock'' is often used in a more general
-sense to refer to the entire arc of emission.
+sense to refer to the entire arc of emission.  In this paper, we will
+concentrate on \textit{stellar bow shocks}, in which the position of
+the star can serve as a useful reference point for describing the bow
+shape.  The empirical terminology that we will employ is illustrated
+in Figure~\ref{fig:bow-terminology}.  The \textit{apex} is the point
+of closest approach of the bow to the star, which lies on the
+approximate symmetry axis, and the region around the apex is sometimes
+referred to as the \textit{head} of the bow.  The \textit{wings} are
+the swept-back sides of the bow, which lie in a direction from the
+star that is orthogonal to the axis, with the \textit{far wings} being
+the wing region farthest from the apex. Finally, the \textit{tail} is
+the region near the axis but in the opposite direction from the apex.
 
@@
 
+\begin{figure}
+  % \includegraphics[width=\linewidth]{2winds-scheme}
+  \includegraphics[width=\linewidth]{figs/generic-bowshock}
+  \caption{Quasi-stationary bow shock structure formed by the
+    interaction of two supersonic winds.  Lower-left inset box shows
+    the case where the inner wind is anisotropic. The streamlines
+    (thin lines) are drawn to be qualitatively realistic: they
+    are straight in regions of hypersonic flow, but curved in subsonic
+    regions, responding to pressure gradients in the shocked shells.}
+\label{fig:2-winds}
+\end{figure}
+can't doesn;t 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
+  \caption[]{Schematic diagram of two-wind interaction problem,
+    following \citet{Canto:1996}.}
+  \label{fig:crw-schema}
+\end{figure}
+
+The general case of a two-wind interaction bow shock is illustrated in
+Figure~\ref{fig:2-winds}.  If the winds are isotropic, then the bow
+shock pattern wraps around the weaker of the two sources, in
+
+The bow shocks we consider are originated by a source located at the
+origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a
+terminal (supersonic) velocity $v_w$. This wind interacts with another
+wind originated by another source located at a distance $D$ from the
+first one.  The mass loss rate of the second source is $\dot{M}_{w1}$
+and the terminal velocity is $v_{w1}$. The momentum of the wind of the
+second source is higher than the momentum of the first one, and the
+resultant bow shock is stationary due to pressure balance.
+
+\subsection{Characteristic Radii}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/characteristic-radii}
+  \caption{Characteristic radii in the body frame.}
+  \label{fig:characteristic-radii}
+\end{figure}
+
+In order to contrast different bow shock models, we derive a set of
+measurable radii. Each model used should predict them and these
+predictions can be compared with observations.
+\begin{itemize}
+\item Radius at axis of symmetry. Denoted as $R_0$.
+\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
+\item Radius at the perpendicular direction to the symmetry
+  axis. Denoted as $R_{90}$
+\item For open bow shocks, the asymptotic angle. Denoted as
+  $\theta_\infty$
+\end{itemize}
+
 %% 
@@
 For simplicity, the current paper is restricted to cylindrically
-symmetric bowshock shapes.
+symmetric bow shock shapes.
 

### 2017-11-01 papers/Paper1/sec-intro.tex
Nearly finish intro to theory paper

@@
 
-Bow shocks from pulsars and neutron stars
-\citep{Cordes:1993a, Brownsberger:2014a}.
-
-Terminology: head, wings, nose, apex, limb, etc.
-
-Radiative versus non-radiative shocks.
-
 \begin{figure}
@@
     the case where the inner wind is anisotropic. The streamlines
-    (thin lines) are drawn to be qualitatively realistic: they
-    are straight in regions of hypersonic flow, but curved in subsonic
-    regions, responding to pressure gradients in the shocked shells.}
+    (thin lines) are drawn to be qualitatively realistic: they are
+    straight in regions of hypersonic flow, but curved in subsonic
+    regions, responding to pressure gradients in the shocked
+    shells. Streamline slopes are discontinuous across oblique
+    shocks.}
 \label{fig:2-winds}
 \end{figure}
-can't doesn;t 
+\newcommand\Mach{\ensuremath{\mathcal{M}}} Figure~\ref{fig:2-winds}
+shows an idealized schematic of how a double bow-shock shell is formed
+from the interaction of two supersonic streams: an \textit{inner wind}
+and an \textit{outer wind}, with the inner wind being the weaker of
+the two (in terms of momentum), so that the shell curves back around
+the inner source.  The outer wind may be from another star, or may be
+a larger scale flow of the interstellar medium, such as the
+\textit{champagne flow} produced by the expansion of an \hii{} region
+away from a molecular cloud \cite{Tenorio-Tagle:1979a, Shu:2002a,
+  Medina:2014a}.  Alternatively, it may be due to the supersonic
+motion of the inner source through a relatively static medium, in
+which case the outer wind will not be divergent as shown in the figure
+but rather plane-parallel.  The thickness of the shocked shells at the
+apex depends on the Mach number, \Mach{}, of the flows and the
+efficiency of the post-shock cooling.  For sufficiently strong
+cooling, the post-shock cooling zone thickness is negligible and the
+shock can be considered isothermal.  In this case, the shell thickness
+is of order \(\Mach^{-2}\) times the source-apex separation
+\citep{Henney:2002a}, which can become very small for high Mach
+numbers.  The shell thickness will tend to increase towards the wings,
+due to the increasing shock obliqueness, which reduces the
+perpendicular Mach number.
+
 \begin{figure}
@@
   \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
-  \caption[]{Schematic diagram of two-wind interaction problem,
-    following \citet{Canto:1996}.}
+  \caption[]{Schematic diagram of cylindrically symmetric two-wind
+    interaction problem in the thin-shell limit, following
+    \citet{Canto:1996}.}
   \label{fig:crw-schema}
 \end{figure}
+In the extreme thin-shell limit, the entire bow structure can be
+treated as a surface.  The bow radius measured from the inner source
+(star) is \(R(\theta, \phi)\), where \(\theta\) is the polar angle, measured from
+the star-apex axis, and \(\phi\) is the azimuthal angle, measured around
+that axis.  Assuming cylindrical symmetry about the axis, this reduces
+to \(R(\theta)\), which is illustrated in Figure~\ref{fig:crw-schema},
+following \citet{Canto:1996}.  The separation between the two sources
+is \(D\) and the complementary angle, as measured at the position of
+the outer source, is \(\theta_1\).  The minimum value of \(R(\theta)\) is the
+stagnation radius, \(R_0\), which occurs at the apex (\(\theta = 0\)).  In
+a steady state, ram-pressure balance on the axis implies that
+\begin{equation}
+  \label{eq:stagnation-radius}
+  \frac{R_0} {D} = \frac{\beta^{1/2}} {1 + \beta^{1/2}} ,
+\end{equation}
+where \(\beta\) is the momentum ratio between the two winds.  If the inner
+wind has mass-loss rate \(\dot{M}_w\) and terminal velocity \(V_w\),
+while the outer wind has corresponding values \(\dot{M}_{w1}\) and
+\(V_{w1}\), then the momentum ratio is
+\begin{equation}
+  \label{eq:beta-definition}
+  \beta = \frac{\dot{M}_w V_w} {\dot{M}_{w1} V_{w1}} .
+\end{equation}
+The case where the outer wind is a parallel stream
+\citep{Wilkin:1996a} corresponds to the limit \(\beta \to 0\), in which case
+\(D\) is no longer a meaningful parameter.
 
-The general case of a two-wind interaction bow shock is illustrated in
-Figure~\ref{fig:2-winds}.  If the winds are isotropic, then the bow
-shock pattern wraps around the weaker of the two sources, in
+Bow shocks from pulsars and neutron stars
+\citep{Cordes:1993a, Brownsberger:2014a}.
 
-The bow shocks we consider are originated by a source located at the
-origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a
-terminal (supersonic) velocity $v_w$. This wind interacts with another
-wind originated by another source located at a distance $D$ from the
-first one.  The mass loss rate of the second source is $\dot{M}_{w1}$
-and the terminal velocity is $v_{w1}$. The momentum of the wind of the
-second source is higher than the momentum of the first one, and the
-resultant bow shock is stationary due to pressure balance.
+% The bow shocks we consider are originated by a source located at the
+% origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a
+% terminal (supersonic) velocity $v_w$. This wind interacts with another
+% wind originated by another source located at a distance $D$ from the
+% first one.  The mass loss rate of the second source is $\dot{M}_{w1}$
+% and the terminal velocity is $v_{w1}$. The momentum of the wind of the
+% second source is higher than the momentum of the first one, and the
+% resultant bow shock is stationary due to pressure balance.
 
-\subsection{Characteristic Radii}
+\subsection{Parameters to characterize a bow shape}
+
 \begin{figure}
@@
 \end{figure}
+
+The stagnation radius \(R_0\) describes the linear scale of the bow
+shock, but in order to characterize its shape more parameters are
+required.  To efficiently capture the diversity of bow shapes, we propose the parameters shown in Figure~\ref{fig:characteristic-radii}.
+
+\(R_{90}\) has been used before \citep{Robberto:2005, Meyer:2016a}, but as far as we know \(R_c\) hasn't.
 

### 2017-11-02 papers/Paper1/sec-intro.tex
Finish section 2 of theory paper

@@
 
+Radiation bow waves \citep{van-Marle:2011a}
+
 % The bow shocks we consider are originated by a source located at the
@@
 
-\subsection{Parameters to characterize a bow shape}
+\section{Planitude and alatude of bow shapes}
 
@@
   \includegraphics[width=\linewidth]{figs/characteristic-radii}
-  \caption{Characteristic radii in the body frame.}
+  \caption{Parameters for characterizing a bow shape.  Bow radius from
+    the star, measured parallel (\(R_0\)) and perpendicular
+    (\(R_{90}\)) to the symmetry axis, together with radius of
+    curvature (\(R_c\)) at apex and asymptotic opening angle
+    (\(\theta_\infty\)) of the far wings. }
   \label{fig:characteristic-radii}
@@
 shock, but in order to characterize its shape more parameters are
-required.  To efficiently capture the diversity of bow shapes, we propose the parameters shown in Figure~\ref{fig:characteristic-radii}.
+required.  To efficiently capture the diversity of bow shapes, we
+propose the parameters shown in Figure~\ref{fig:characteristic-radii}.
+The perpendicular radius \(R_{90}\) is the value of \(R(\theta)\) at
+\(\theta = 90^\circ\), whereas \(R_c\) is the radius of curvature of the bow at
+the apex (\(\theta = 0\)), which in cylindrical symmetry simplifies to
+\begin{equation}
+  \label{eq:radius-curvature}
+  R_c 
+  % = R_0 \Biggl[ 1
+  % - \frac{1} {R_0} \left.\frac{d^2\! R} {d\,\theta^2}\right|_{\theta = 0} \Biggr]^{-1}
+  = \frac{R_0^2}{R_0 - R_0''} \ , 
+\end{equation}
+where \(R_0''\) is \(d^2 \!R / d\theta^2\) evaluated at \(\theta = 0\).
 
-\(R_{90}\) has been used before \citep{Robberto:2005, Meyer:2016a}, but as far as we know \(R_c\) hasn't.
+A fourth parameter is the asymptotic opening angle of the far wings,
+\(\theta_\infty\), which is useful in the case that the wings are asymptotically
+conical.  However, in many bow shocks the wings tend towards the
+asymptotic angle only slowly, making \(\theta_\infty\) difficult to measure,
+especially since the emission from the far wings is often weak at
+best.  In contrast, the three radii, \(R_0\), \(R_{90}\), and
+\(R_c\). are straightforward to determine from observations.  One
+simple method to estimate the radius of curvature is to make use of
+the Taylor expansion\footnote{%
+  This method assumes both that \(R(\theta)\) is even (true for a
+  cylindrically symmetric bow) and that the orientation of the axis is
+  already known.  Generalization to cases where these assumptions do
+  not hold is discussed in \citet{Henney:2017a}.} %
+of \(R(\theta)\) about the apex (with \(\theta\) in
+radians):
+\begin{equation}
+  \label{eq:taylor-R-theta}
+  R(\theta) = R_0 + \frac12 R_0'' \theta^2 + \mathcal{O}(\theta^4) \ ,
+\end{equation}
+so that fitting a polynomial in \(\theta^2\) to \(R(\theta)\) for
+\(|\theta| < \Delta\theta \) yields \(R_0\) and \(R_0''\) from the first two
+coefficients, and hence \(R_c\) from
+equation~\eqref{eq:radius-curvature}.  Experience has shown that
+\(\Delta\theta = 30^\circ\) and three terms in the polynomial are good choices,
+where the third term is used only as a monitor (if the co-efficient of
+\(\theta^4\) is not small compared with \(R_0\), then it may indicate a
+problem with the fit).
 
-In order to contrast different bow shock models, we derive a set of
-measurable radii. Each model used should predict them and these
-predictions can be compared with observations.
-\begin{itemize}
-\item Radius at axis of symmetry. Denoted as $R_0$.
-\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
-\item Radius at the perpendicular direction to the symmetry
-  axis. Denoted as $R_{90}$
-\item For open bow shocks, the asymptotic angle. Denoted as
-  $\theta_\infty$
-\end{itemize}
+Since we have three radii, we can construct two dimensionless
+parameters:
+\begin{align}
+  \label{eq:planitude}
+  \text{Planitude} \quad \Pi & \equiv  \frac{R_c} {R_0} \\
+  \label{eq:alatude}
+  \text{Alatude} \quad \Lambda & \equiv  \frac{R_{90}} {R_0}
+\end{align}
+and these will be the principal shape parameters that we will use in
+the remainder of the paper.  The \textit{planitude}, \(\Pi\), is a
+measure of the flatness of the head of the bow around the apex, while
+the \textit{alatude}, \(\Lambda\), is a measure of the openness of the bow
+wings.  Although ``planitude'' can be found in the dictionary,
+``alatude'' is a new word that we introduce here, derived from the latin
+\textit{ala} for ``wing''.
+
+Several previous studies have discussed the relation between
+\(R_{90}\) and \(R_0\) as a diagnostic of bow shape (for example
+\citealp{Robberto:2005, Cox:2012a, Meyer:2016a}), but as far as we
+know, we are the first to include \(R_c\).  \citet{Robberto:2005} use
+the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd bow shapes
+in the Trapezium cluster in the center of the Orion Nebula
+\citep{Hayward:1994a, Garcia-Arredondo:2001a, Smith:2005a}.  In that
+case, the source of the outer wind is known, and so \(D\) is
+well-determined (at least, in projection), but for many bow shocks
+\(D\) is not known, and is not even defined for the moving-star or
+parallel-stream case. \citet{Cox:2012a} \S~4.1 use \(A\) and \(B\)
+for the projected values of \(R_0\) and \(R_{90}\), respectively (see
+next section for discussion of projection effects).
+\citet{Meyer:2016a} analyze the distribution of \(R_0 / R_{90}\),
+which is the reciproical of our \(\Lambda\), for numerical hydrodynamic
+simulations of bow shocks.
+
+% In order to contrast different bow shock models, we derive a set of
+% measurable radii. Each model used should predict them and these
+% predictions can be compared with observations.
+% \begin{itemize}
+% \item Radius at axis of symmetry. Denoted as $R_0$.
+% \item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
+% \item Radius at the perpendicular direction to the symmetry
+%   axis. Denoted as $R_{90}$
+% \item For open bow shocks, the asymptotic angle. Denoted as
+%   $\theta_\infty$
+% \end{itemize}
 

### 2017-11-03 papers/Paper1/sec-intro.tex
Add plan of paper to intro of theory paper

@@
 
+The paper is organized as follows.
+%
+In \S~\ref{sec:plan-alat-bow} we outline the geometric parameters that
+are necessary for describing bow shapes and introduce two
+dimensionless ratios: planitude and alatude.
+%
+In \S~\ref{sec:projection} we derive general results for the
+projection of bow shapes on to the plane of the sky.
+%
+In \S~\ref{sec:conic} we apply the results to the simplest possible
+class of geometric bow models: the quadrics of revolution, which
+comprise spheroids, paraboloids, and hyperboloids, each of which
+occupies a disjoint region of the planitude--alatude plane.
+%
+In \S~\ref{sec:crw-scenario} we consider thin-shell hydrodynamic
+models for the parallel-stream case (wilkinoids) and wind-wind case
+(cantoids), including extension to an anisotropic inner wind
+(ancantoids).  We calculate the location of the models in the
+planitude--alatude plane as a function of the inclination of the bow
+shock axis to the plane of the sky.
+%
+In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
+dusty radiation bow wave (dragoids), including the effects of
+gas-grain drag.
+%
+In \S~\ref{sec:perturbed-bows} we investigate the effects on the
+planitude--alatude plane of small-amplitude perturbations to the bow
+shape.
+%
+In \S~\ref{sec:conc} we summarise our results and outline how
+following papers will apply these ideas to observations and numerical
+simulations.
+
 % The bow shocks we consider are originated by a source located at the
@@
 \section{Planitude and alatude of bow shapes}
+\label{sec:plan-alat-bow}
 
@@
 
-Since we have three radii, we can construct two dimensionless
-parameters:
+Since we have three radii, we can construct two independent
+dimensionless parameters:
 \begin{align}
@@
 the \textit{alatude}, \(\Lambda\), is a measure of the openness of the bow
-wings.  Although ``planitude'' can be found in the dictionary,
-``alatude'' is a new word that we introduce here, derived from the latin
-\textit{ala} for ``wing''.
+wings.  Although ``planitude'' can be found in English dictionaries,
+``alatude'' is a new word that we introduce here, derived from the
+latin \textit{ala} for ``wing''.
 
@@
 \citealp{Robberto:2005, Cox:2012a, Meyer:2016a}), but as far as we
-know, we are the first to include \(R_c\).  \citet{Robberto:2005} use
-the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd bow shapes
-in the Trapezium cluster in the center of the Orion Nebula
+know, we are the first to include \(R_c\).  \citet{Robberto:2005}
+\S~4.2 use the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd
+bow shapes in the Trapezium cluster in the center of the Orion Nebula
 \citep{Hayward:1994a, Garcia-Arredondo:2001a, Smith:2005a}.  In that
@@
 \(D\) is not known, and is not even defined for the moving-star or
-parallel-stream case. \citet{Cox:2012a} \S~4.1 use \(A\) and \(B\)
-for the projected values of \(R_0\) and \(R_{90}\), respectively (see
-next section for discussion of projection effects).
-\citet{Meyer:2016a} analyze the distribution of \(R_0 / R_{90}\),
-which is the reciproical of our \(\Lambda\), for numerical hydrodynamic
-simulations of bow shocks.
+parallel-stream case. \citet{Cox:2012a} \S~4.1 compare the observed
+shapes of bow shocks around cool giant stars with an analytic model,
+and use \(A\) and \(B\) for the projected values of \(R_0\) and
+\(R_{90}\), respectively (see next section for discussion of
+projection effects).  \citet{Meyer:2016a} \S~3.2 analyze the
+distribution of \(R_0 / R_{90}\) (the reciprocal of our \(\Lambda\)) for
+hydrodynamic simulations of bow shocks around runaway OB stars.
 
@@
 
-For simplicity, the current paper is restricted to cylindrically
-symmetric bow shock shapes.
+% For simplicity, the current paper is restricted to cylindrically
+% symmetric bow shock shapes.
 

### 2017-11-03 papers/Paper1/sec-intro.tex
Tidy up projection section (3) of theory paper

@@
 \textit{champagne flow} produced by the expansion of an \hii{} region
-away from a molecular cloud \cite{Tenorio-Tagle:1979a, Shu:2002a,
+away from a molecular cloud \citep{Tenorio-Tagle:1979a, Shu:2002a,
   Medina:2014a}.  Alternatively, it may be due to the supersonic
@@
   % - \frac{1} {R_0} \left.\frac{d^2\! R} {d\,\theta^2}\right|_{\theta = 0} \Biggr]^{-1}
-  = \frac{R_0^2}{R_0 - R_0''} \ , 
+  = \frac{R_0^2}{R_0 - R_{\theta\theta,0}} \ , 
 \end{equation}
-where \(R_0''\) is \(d^2 \!R / d\theta^2\) evaluated at \(\theta = 0\).
+where \(R_{\theta\theta,0}\) is \(d^2 \!R / d\theta^2\) evaluated at \(\theta = 0\).
 
@@
   \label{eq:taylor-R-theta}
-  R(\theta) = R_0 + \frac12 R_0'' \theta^2 + \mathcal{O}(\theta^4) \ ,
+  R(\theta) = R_0 + \frac12 R_{\theta\theta,0} \,\theta^2 + \mathcal{O}(\theta^4) \ ,
 \end{equation}
 so that fitting a polynomial in \(\theta^2\) to \(R(\theta)\) for
-\(|\theta| < \Delta\theta \) yields \(R_0\) and \(R_0''\) from the first two
+\(|\theta| < \Delta\theta \) yields \(R_0\) and \(R_{\theta\theta,0}\) from the first two
 coefficients, and hence \(R_c\) from

### 2017-11-03 papers/Paper1/sec-projection.tex
Expand some fig captions and move figures between sections
Text description of projection effects in perturbed bows
Tidy up projection section (3) of theory paper

@@
 In this section we calculate the apparent shape on the plane of the
-sky of the limb brightened border of a shock or shell that is
+sky of the limb-brightened border of a shock or shell that is
 idealized as an arbitrary cylindrically symmetric surface.
@@
 \(i = 90^\circ\) when it is viewed along its axis (\textit{end on}).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/characteristic-radii}
-  \caption{Characteristic radii in the body frame.}
-  \label{fig:characteristic-radii}
-\end{figure}
 
@@
 \end{equation}
-
 We denote by \(\phi\T\) that value of $\phi$ that satisfies this
@@
 In order to compare the shell shape given by $R(\theta)$ with observations,
-it is convenient to define the following apparent radii in the observer frame: $R'_{0}$ and $R'_{90}$. These are projected distances of the shell tangent line
-from the origin. The first is measured in the direction of the symmetry axis, and the second in a perpendicular direction. More concretely $R'_{0} = x'\T(y'\T=0)$
-and $R'_{90} = y'\T(x'\T=0)$. From equations (\ref{eq:tanphi}) and (\ref{eq:tangential}) we find that:
+it is convenient to define the following apparent radii in the
+observer frame: $R'_{0}$ and $R'_{90}$. These are projected distances
+of the shell tangent line from the origin. The first is measured in
+the direction of the symmetry axis, and the second in a perpendicular
+direction. More concretely $R'_{0} = x'\T(y'\T=0)$ and
+$R'_{90} = y'\T(x'\T=0)$. From equations (\ref{eq:tanphi}) and
+(\ref{eq:tangential}) we find that:
 \begin{align}
@@
 \begin{align}
+  \label{eq:R90prime}
 R'_{90} = R(\theta_{90})\sin\theta_{90}\left(1-\sin^2\bigl(\phi\T(\theta_{90})\bigr)\right)^{1/2}
 \end{align}
-Where $\theta_{90}$ is the solution of the next implicit equation:
+Where $\theta_{90}$ is the solution of the implicit equation:
 \begin{align}
+  \label{eq:th90}
 \cot\theta_{90} = \frac{1-\left(1+\omega(\theta_{90})^2\sin^22i\right)^{1/2}}{2\omega(\theta_{90})\cos^2 i}
 \end{align}
+The projected alatude (see \S~\ref{sec:plan-alat-bow}) is then given
+by \(\Lambda' = R_{90}' / R_0'\).
+
+Similarly, the projected planitude is \(\Pi' = R_c' / R_0'\), where
+\(R_c'\) is found by applying the equivalent of equation
+\eqref{eq:radius-curvature} for primed quantities:
+\begin{equation}
+  \label{eq:projected-radius-curvature}
+  R_c' 
+  = \frac{(R_0')^2}{R_0' - R_{\theta'\theta',0}'} \ .
+\end{equation}
 
@@
 \label{sec:line-sight-veloc}
-  Motions in a thin shocked shell will be predominantly tangential to the shell surface.
-In addition, for the particular case of wind-wind bowshocks, the flow in each azimuthal slice can be shown to be independent \citep{Wilkin:2000a}, which implies that the shell velocity is parallel to \(\uvec{t}\).
-The projected line-of-sight shell velocity is therefore
+Motions in a thin shocked shell will be predominantly tangential to
+the shell surface. In addition, for the particular case of wind-wind
+bowshocks, the flow in each azimuthal slice can be shown to be
+independent \citep{Wilkin:2000a}, which implies that the shell
+velocity is parallel to \(\uvec{t}\). The projected line-of-sight
+shell velocity is therefore
   \begin{equation}

### 2017-11-03 papers/Paper1/sec-conic.tex
Convert first part of quadrics section to planitude-alatude notation

@@
   consider only the case of a single sheet of a 2-sheet hyperboloid or
-  paraboloid.}  We ignore the degenerate cases of cylinders, cones,
-and pairs of parallel planes.  While mathematically simple, these
-quadrics are sufficiently flexible that they can provide a useful
-approximation to more complex bow shock shapes.
+  paraboloid, since these are the versions that resemble a bow,
+  whereas the 1-sheet versions resemble the waist of an hourglass.}
+We ignore the degenerate cases of cylinders, cones, and pairs of
+parallel planes.  While mathematically simple, these quadrics are
+sufficiently flexible that they can provide a useful approximation to
+more complex bow shock shapes.
 
@@
 
-Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization, using the convention
-that if a dual sign appears, the upper sign correspond to the elliptical quadrics, and the lower sign to the hyperbolic quadrics
-\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
-  projected shape are developed in appendix \ref{app:parabola}}:
+The shape of the quadric curves in the \(xy\) plane (\(\phi = 0\)) are
+shown in Figure~\ref{fig:conics}(a) and (b) for the ellipse and
+hyperbola case, respectively.  The conic section itself is fully
+described by two lengths, \(a\) and \(b\), which are the
+semi-axes.\footnote{Note that we do not require that \(a > b\), so
+  either \(a\) or \(b\) may be the semi-major axis.}  However, the
+curve can be translated along the \(x\) axis to an arbitrary point
+with respect to the star, so that the apex distance \(R_0\) has no
+necessary relation to \(a\) or \(b\) and therefore the star/bow
+combination requires \emph{three} independent lengths for its
+specification.  The displacement \(x_0\) from the star to the
+``center'' of the conic section is
+\begin{equation}
+  \label{eq:conic-x0}
+  x_0 = R_0 - \sigma a
+  \quad \text{with} \quad
+  \sigma = \begin{cases}
+    +1 & \text{ellipse}\\
+    -1 & \text{hyperbola}
+  \end{cases} \ .
+\end{equation}
+For hyperbolas the center is ``outside'' of the bow and \(x_0\) is
+always positive, whereas for ellipses the center is ``inside'' the bow
+and \(x_0\) is usually negative, except when \(a < R_0\) (see
+Figure~\ref{fig:conics}).
+
+A general parametric form\footnote{%
+  The special case of the parabola needs to be treated differently,
+  see Appendix~\ref{app:parabola}.} %
+for the \(xy\) coordinates of the quadrics (in the \(\phi = 0\)plane, and
+with the star at the origin) as a function of \(t = [0, \pi]\) is then
+\begin{gather}
+  \label{eq:par-xy}
+  \begin{aligned}
+    x &= x_0 + \sigma a \Cos(t) \\ 
+    y &= b\Sin(t) 
+  \end{aligned}
+\end{gather}
+where
+\begin{equation}
+  \label{eq:sin-sinh-etc}
+  \Sin(t), \Cos(t) = \begin{cases}
+    \sin(t), \cos(t) & \text{ellipse}\\
+    \sinh(t), \cosh(t) & \text{hyperbola}
+  \end{cases}
+\end{equation}
+Except for the circle case (\(\sigma = +1\), \(a = b\)), the parametric
+variable \(t\) is not actually an angle in physical space.  Instead,
+the polar form of the bow shape \(R(\theta)\) must be found by substituting
+equations~\eqref{eq:par-xy} into \(\theta = \tan^{-1} y/x\) and
+\(R = (x^2 + y^2)^{1/2}\).
+
+The ``type'' of quadric surface can be characterized by the
+\textit{quadric parameter}:
+\begin{equation}
+  \label{eq:Tq}
+  T_q \equiv \sigma \frac{b} {a} \ , 
+\end{equation}
+where \(T_q < 0\) corresponds to open surfaces (hyperboloids) and
+\(T_q > 0\) corresponds to closed surfaces (oblate spheroids with
+\(T_q > 1\) and prolate spheroids with \(T_q < 1\)).  Special cases
+are the sphere (\(T_q = 1\)) and the paraboloid (\(T_q = 0\)).  The
+set of parameters \((T_q, a, x_0)\) are then sufficient to
+characterize the star/bow combination, where \(a\) is the quadric
+scale and \(x_0\) is its center displacement from the star.
+
+But, we can also characterize the star/bow by \((R_0, \Pi, \Lambda)\), where
+\(\Pi\) and \(\Lambda\) are the planitude and alatude, see
+\S~\ref{sec:plan-alat-bow}.  We now derive the relationship between
+these two descriptions.  The apex radius of curvature for a conic
+section is
+\begin{equation}
+  \label{eq:Rc-conic}
+  R_c = \frac{b^2}{a} \ ,
+\end{equation}
+whereas the perpendicular radius, \(R_{90}\), is the value of \(y\)
+when \(x = 0\), which can be found from equations (\ref{eq:conic-x0},
+\ref{eq:par-xy}) as
+\begin{equation}
+  \label{eq:conic-R90}
+  R_{90} = \left|T_q\right|
+  \left(2aR_0 - \sigma R_0^2\right)^{1/2} \ .
+\end{equation}
+Combining equations (\ref{eq:planitude}, \ref{eq:alatude},
+\ref{eq:conic-x0}, \ref{eq:Tq}--\ref{eq:conic-R90}) yields
 \begin{align}
-x &= a\Cos(t)+x_0 \label{eq:par-x}\\ 
-y &= b\Sin(t) \label{eq:par-y}
+  \label{eq:Tq-from-Pi-Lambda}
+  T_q &= \sigma \left| 2 \Pi - \Lambda^2 \right|^{1/2} \\
+  \label{eq:a-from-R0-Pi-Lambda}
+  a &= R_0 \frac{ \Pi  } { \left|  2 \Pi - \Lambda^2\right| } \\
+  x_0 &= R_0 \frac{\Pi - \Lambda^2} {2 \Pi - \Lambda^2}
 \end{align}
-where:
-\begin{align}
-\Cos(t) &= \left\lbrace \begin{array}{c}
-\cos t ~\mathrm{if~ellipse} \\
--\cosh t ~\mathrm{if~hyperbola}
-\end{array}\right.\\
-\Sin(t) &= \left\lbrace \begin{array}{c}
-\sin t ~\mathrm{if~ellipse} \\
-\sinh t ~\mathrm{if~hyperbola}
-\end{array}\right. \\
--\pi &< t < \pi \\
-x_0 &=  R_0 \mp a \label{eq:x0}\\
-\end{align}
-Where $a$ and $b$ are real, positive numbers.
+From these we see that it is the sign of \(2 \Pi - \Lambda^2\) that determines
+\(\sigma\) and thus whether a quadric is a spheroid or a hyperboloid.  For
+example, for a constant planitude, \(\Pi\), we can have a family of
+different quadric types, with varying alatude, \(\Lambda\), that increases
+from oblate to prolate to hyperboloid, as illustrated in
+Figure~\ref{fig:conics-family}.
 
-We have set a whole family of curves with a singular parameter denoted as:
-\begin{align}
-  \tan\theta_c \equiv \pm\frac{b}{a}\label{eq:Thc}
-\end{align}
-Positive values of this parameter describe closed curves (i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas).
-Particular cases are $\theta_c =\frac{\pi}{4}$,
-which describes a circle and $\theta_c=0$, which describes a parabola.
-To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic
-parameters $(a,b,\theta_c)$ could be derived from the former. Either way, the radius of curvature can be computed as:
+% We have set a whole family of curves with a singular parameter denoted as:
+% \begin{align}
+%   \tan\theta_c \equiv \pm\frac{b}{a}\label{eq:Thc}
+% \end{align}
+% Positive values of this parameter describe closed curves (i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas).
+% Particular cases are $\theta_c =\frac{\pi}{4}$,
+% which describes a circle and $\theta_c=0$, which describes a parabola.
+% To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic
+% parameters $(a,b,\theta_c)$ could be derived from the former. Either way, the radius of curvature can be computed as:
 
-\begin{align}
-R_c = \frac{b^2}{a} \label{eq:Rc-conic}
-\end{align}
+% \begin{align}
+% R_c = \frac{b^2}{a} \label{eq:Rc-conic}
+% \end{align}
 
-For the rest of the parameters, the equation for ellipses and hyperbolas are very similar:
+% For the rest of the parameters, the equation for ellipses and hyperbolas are very similar:
 
-\begin{align}
-R_{90} = \left|\tan\theta_c\right|\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
-\end{align}
+% \begin{align}
+% R_{90} = \left|\tan\theta_c\right|\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
+% \end{align}
 
-Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
-%But first is useful to define the quantities $\tilde{R}_c \equiv \frac{R_c}{R_0}$ and $\equiv \frac{\tilde{R}_{90}}{R_0}$ for simplification purposes.
-Hereafter is useful to denote with a tilde quantities which are normalized with $R_0$:
+% Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
+% %But first is useful to define the quantities $\tilde{R}_c \equiv \frac{R_c}{R_0}$ and $\equiv \frac{\tilde{R}_{90}}{R_0}$ for simplification purposes.
+% Hereafter is useful to denote with a tilde quantities which are normalized with $R_0$:
 
-\begin{align}
-  \tilde{a}\equiv \frac{a}{R_0} &= \pm\frac{\tilde{R}_c}{\left(2\tilde{R}_c-\tilde{R}_{90}^2\right)} \label{eq:a-con}\\
-  \tilde{b}\equiv \frac{b}{R_0} &= \frac{\tilde{R}_c}{\left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2}} \label{eq:b-con}
-\end{align}
+% \begin{align}
+%   \tilde{a}\equiv \frac{a}{R_0} &= \pm\frac{\tilde{R}_c}{\left(2\tilde{R}_c-\tilde{R}_{90}^2\right)} \label{eq:a-con}\\
+%   \tilde{b}\equiv \frac{b}{R_0} &= \frac{\tilde{R}_c}{\left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2}} \label{eq:b-con}
+% \end{align}
 
-Dividing equations (\ref{eq:a-con}) and (\ref{eq:b-con}) and substituting into equation (\ref{eq:Thc}) we get:
+% Dividing equations (\ref{eq:a-con}) and (\ref{eq:b-con}) and substituting into equation (\ref{eq:Thc}) we get:
 
-\begin{align}
-\tan\theta_c = \pm \left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2} \label{eq:th_c}
-\end{align}
+% \begin{align}
+% \tan\theta_c = \pm \left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2} \label{eq:th_c}
+% \end{align}
 
-Note that the term $2\tilde{R}_c-\tilde{R}_{90}^2$ acts as a discriminant which determine the quadric we are working with.
+% Note that the term $2\tilde{R}_c-\tilde{R}_{90}^2$ acts as a discriminant which determine the quadric we are working with.
 

### 2017-11-03 papers/Paper1/sec-conic.tex
Port the conic figures to the new notation

@@
+\begin{figure*}
+  \setlength\tabcolsep{2em}
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[height=0.45\linewidth]{figs/ellipse_edited}
+        & \includegraphics[height=0.45\linewidth]{figs/hyperbola_edited}
+  \end{tabular}
+  \caption{Example off-center conic sections that can form quadrics of
+    revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
+    between the conic section parameters \(a\), \(b\), \(\theta_q\) and the
+    bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
+    defined in Fig.~\ref{fig:characteristic-radii}. The origin (center
+    of the weaker flow) is indicated by a red star, the center of
+    curvature of the apex of the bow shock is indicated by a green
+    dot, and the geometric center of the conic section is indicated by
+    a blue cross, which is offset by \(x_0\) from the origin.  Note
+    that \(R_0\), \(R_{90}\), \(R_c\), \(a\), and \(b\) are all
+    \emph{lengths} and are always positive, whereas \(x_0\) is a
+    \emph{displacement} and may be positive or negative.}
+  \label{fig:conics}
+\end{figure*}
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/conic1}
+  \caption{Example of a family of conic sections, all with the same
+    planitude (flatness at apex, marked by white dot):
+    \(\Pi = R_c/R_0 = 2 \). The quadric angle,
+    \(\theta_q = \tan^{-1} T_q\), varies over the family (see text), with
+    lower values of \(\theta_q\) giving larger values of the alatude,
+    \(\Lambda = R_{90}/R_0 \), meaning more open wings.  Different values of
+    \(\Pi\) can be achieved for the same quadrics by sliding them along
+    the \(x\)-axis, which will also change the axis scales since these
+    are normalized by \(R_0\).}
+  \label{fig:conics-family}
+\end{figure}
+
 \section{Quadrics of revolution}
 \label{sec:conic}
-
-\newcommand\Sin{\ensuremath{\mathcal{S}}}
-\newcommand\Cos{\ensuremath{\mathcal{C}}}
-\newcommand\Cot{\ensuremath{\mathcal{T}}}
 
@@
 %an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary
-\begin{figure*}
-\setlength\tabcolsep{2em}
-\begin{tabular}{ll}
-  (a) & (b) \\
-  \includegraphics[height=0.45\linewidth]{figs/ellipse_edited}
-      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_edited}
-\end{tabular}
-\label{fig:conics}
-\caption{Example off-center conic sections that can form quadrics of
-  revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
-  between the conic section parameters \(a\), \(b\), \(\theta_c\) and the
-  bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
-  defined in Fig.~\ref{fig:characteristic-radii}. The origin (center
-  of the weaker flow) is indicated by a red star, the center of
-  curvature of the apex of the bow shock is indicated by a green dot,
-  and the geometric center of the conic section is indicated by a blue
-  cross.  }
-\end{figure*}
-\begin{figure}
-\includegraphics[width=\linewidth]{conic1}
-\caption{Example of a family of conic sections, all with the same
-  normalized radius of curvature at their apex (marked by white dot):
-  \(\widetilde{R}_c = R_c/R_0 = 2 \). The parameter
-  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative values
-  corresponding to hyperbolae.  Differerent values of
-  \(\widetilde{R}_c\) can be achieved by moving the origin along the
-  \(x\)-axis while keeping the apex fixed at \(\tilde{x} = 1\).)}
-\label{fig:conics-family}
-\end{figure}
 
@@
   see Appendix~\ref{app:parabola}.} %
-for the \(xy\) coordinates of the quadrics (in the \(\phi = 0\)plane, and
-with the star at the origin) as a function of \(t = [0, \pi]\) is then
+for the \(xy\) coordinates of the quadrics (in the \(\phi = 0\) plane,
+and with the star at the origin) as a function of \(t = [0, \pi]\) is
+then
 \begin{gather}
@@
   \label{eq:sin-sinh-etc}
-  \Sin(t), \Cos(t) = \begin{cases}
-    \sin(t), \cos(t) & \text{ellipse}\\
-    \sinh(t), \cosh(t) & \text{hyperbola}
+  \Sin{}, \Cos = \begin{cases}
+    \sin{}, \cos & \text{ellipse}\\
+    \sinh{}, \cosh & \text{hyperbola}
   \end{cases}
@@
 
-The ``type'' of quadric surface can be characterized by the
+The type of quadric surface can be characterized by the
 \textit{quadric parameter}:
@@
 \(T_q > 1\) and prolate spheroids with \(T_q < 1\)).  Special cases
-are the sphere (\(T_q = 1\)) and the paraboloid (\(T_q = 0\)).  The
-set of parameters \((T_q, a, x_0)\) are then sufficient to
+are the sphere (\(T_q = 1\)) and the paraboloid (\(T_q = 0\)).
+Alternatively, one can define a \textit{quadric angle}:
+\(\theta_q = \tan^{-1} T_q\), which is marked in Figure~\ref{fig:conics}.
+In the case of hyperboloids, the asymptotic opening angle of the wings
+(\S~\ref{sec:plan-alat-bow} and Fig.~\ref{fig:characteristic-radii})
+is \(\theta_\infty = \pi + \theta_q\) (note that \(\theta_q < 0\) in this case).
+
+The set of parameters \((T_q, a, x_0)\) are then sufficient to
 characterize the star/bow combination, where \(a\) is the quadric
-scale and \(x_0\) is its center displacement from the star.
-
-But, we can also characterize the star/bow by \((R_0, \Pi, \Lambda)\), where
+scale and \(x_0\) is its center displacement from the star.  However,
+we can also characterize the star/bow by \((R_0, \Pi, \Lambda)\), where
 \(\Pi\) and \(\Lambda\) are the planitude and alatude, see
@@
 different quadric types, with varying alatude, \(\Lambda\), that increases
-from oblate to prolate to hyperboloid, as illustrated in
-Figure~\ref{fig:conics-family}.
+from oblate, through prolate and paraboloid, to hyperboloid, as
+illustrated in Figure~\ref{fig:conics-family}.
 
@@
 \end{figure*}
+We now apply the machinery of \S~\ref{sec:projection} to find the projected shape of a quadric bow on the plane of the sky.
+
 Once the parametrization is done, we can find the apparent shape of
 the shell in the observer's frame, following the procedure explained
-in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
+in section.  First of all, the intrinsic 3D shape of the shell is given by:
 \begin{align}

### 2017-11-03 papers/Paper1/conic_fig.py

@@ -18,8 +18,8 @@ flag= args.fig <= 0
 ############## Variying  \theta_c with unitary radius of curvature ####################
 
 # Figure style
-sns.set_style('whitegrid')
-sns.set_context('talk')
+sns.set_style('ticks')
+#sns.set_context('talk')
 sns.set_color_codes('dark')
 
 
@@ -41,7 +41,7 @@ if flag:
         c  = conproj.Conic(A=2.0,th_conic = t)
         trange = c.make_t_array()
         ax.plot(c.x(trange), c.y(trange), lw=3, alpha=0.8,
-                label =r"{}: $\theta_c={:.0f}^\circ$".format(s, t))
+                label =r"{}: $\theta_q={:.0f}^\circ$".format(s, t))
 
     # Star at origin
     ax.plot([0],[0], "w*", ms=17, alpha=0.9)
@@ -60,8 +60,9 @@ if flag:
     ax.set_ylim(-4.1,4.1)
     ax.set_xlabel(r"$x/R_0$")
     ax.set_ylabel(r"$y/R_0$")
-    fig.set_size_inches(6, 6)
+    fig.set_size_inches(5, 5)
     fig.tight_layout()
+    sns.despine()
     fig.savefig("conic1.pdf")
 
 ##########  Show same conic at different inclinations (hyperbola example) #############

### 2017-11-03 papers/Paper1/sec-conic.tex
First half of revision of projection of quadrics

@@
     \(\Lambda = R_{90}/R_0 \), meaning more open wings.  Different values of
-    \(\Pi\) can be achieved for the same quadrics by sliding them along
-    the \(x\)-axis, which will also change the axis scales since these
-    are normalized by \(R_0\).}
+    \(\Pi\) can be achieved for the exact same quadrics by sliding them
+    along the \(x\)-axis, which will also change the axis scales since
+    these are normalized by \(R_0\).}
   \label{fig:conics-family}
@@
 
+We now apply the machinery of \S~\ref{sec:projection} to find the
+projected shape of a quadric bow on the plane of the sky.  The
+intrinsic 3D shape of the shell is given by rotating
+equations~\eqref{eq:par-xy} about the \(x\)-axis, but it is more
+convenient to first transform to a reference frame where the origin is
+at the center of the conic section:
+\begin{equation}
+  \label{eq:xyz-XYZ}
+  (X, Y, Z) = (x - X_0, y, z) . 
+\end{equation}
+In this new frame, the quadric shape is
+\begin{gather}
+  \label{eq:quadric-XYZ}
+  \begin{aligned}
+    X &= a\Cos(t) \\ 
+    Y &= b \Sin(t)\cos\phi \\
+    Z &= b \Sin(t)\sin\phi
+  \end{aligned}
+\end{gather}
+The azimuth of the tangent line as a function of inclination and
+parametric variable is then found from equations (\ref{eq:alpha},
+\ref{eq:tanphi}) to be
+\begin{equation}
+  \label{eq:phit-quadric}
+  \sin\phi_{\T} = \frac{b \Cos(t)} {a \Sin(t)} \tan i \ .
+\end{equation}
+Combining equations~(\ref{eq:Trans}, \ref{eq:quadric-XYZ},
+\ref{eq:phit-quadric}) gives the observer-frame cartesian
+plane-of-sky coordinates of the tangent line:
+\begin{gather}
+  \label{eq:conic-projected-XY}
+  \begin{aligned}
+    X_{\T}' & = \frac{\Cos(t)}{a\cos i}
+    \left(a^2\cos^2 i + \sigma b^2\sin^2 i\right)
+    \\
+    Y_{\T}' &= b\Sin(t)
+    \left(
+      1 - \frac{b^2 \Cos^2(t)}{a^2 \Sin^2(t)}
+      \tan^2 i\right)^{1/2}
+  \end{aligned}
+\end{gather}
+
+We now show that the projected shape is a conic section of the same
+variety (ellipse or hyperbola) as the one that generated the original
+quadric.  If this were true, then it should be possible to write the
+plane-of-sky coordinates as
+\begin{gather}
+  \begin{aligned}
+    X_{\T}' = a'\Cos( t')  \\
+    Y_{\T}' = b'\Sin (t')  . 
+  \end{aligned}\label{eq:conic-projected-XY-conic}
+\end{gather}
+Comparing equations (\ref{eq:conic-projected-XY}) and
+(\ref{eq:conic-projected-XY-conic}), we find after some algebra that
+\begin{align}
+  a' &= \left(a^2\cos^2 i + \sigma b^2\sin^2 i\right)^{1/2} \\
+  b' &= b \label{eq:b-prime} \\
+  \Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \ , 
+\end{align} 
+thus demonstrating the claim.
+
+Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:
+
+\begin{align}
+R'_0 &= \pm a' + x_0\cos i \\
+R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} +  (R_0 \mp a)\cos i
+\end{align}
+
+Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
+\begin{align}
+\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
+\label{eq:qprime}
+\end{align}
+%Where $A\equiv \frac{R_c}{R_0}$
+The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
+\begin{align}
+  \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
+  \label{eq:Aprime}\\
+  \tan\theta'_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
+  \tilde{R}'_{90} &= \left(\frac{2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q}}{\frac{q'}{q}}\right)^{1/2}\frac{\sec i}{f(i;\theta_c)}
+\end{align}
+where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.
+
+When $R'_{90}$ is measurable, diagnostic diagrams like figure (\ref{fig:projected-R90-vs-Rc}) can be used to compare with observations.  
 \begin{figure*}
@@
 \end{figure*}
-We now apply the machinery of \S~\ref{sec:projection} to find the projected shape of a quadric bow on the plane of the sky.
-
-Once the parametrization is done, we can find the apparent shape of
-the shell in the observer's frame, following the procedure explained
-in section.  First of all, the intrinsic 3D shape of the shell is given by:
-\begin{align}
-x &= a\Cos(t)+x_0 \\ 
-y &= b\Sin(t)\cos\phi \\
-z &=  b\Sin(t)\sin\phi
-\end{align}
-The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
-\begin{align}
-\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
-\end{align}
-where:
-\begin{align}
-\Cot(t) = \left\lbrace \begin{array}{c}
-\cot t ~\mathrm{if~ellipse} \\
-\coth t ~\mathrm{if~hyperbola}
-\end{array}\right.
-\end{align}
-
-We could work in another frame where the origin is located at the conic's center: $(X,Y)$, where $X=x-X_0$ and $Y=y$.
-In this frame, we use the transformations (\ref{eq:Trans})  to obtain the apparent shape of the shell:
-\begin{align}
-X' &= \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
-Y' &= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot^2(t)\right)^{1/2}
-\label{eq:conic-projected-y}
-\end{align}
-
-If the apparent shape of the shell in the observer's frame is still the same conic, then, we
-can write equations(\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:
-\begin{align}
-X' = a'\Cos( t') \label{eq:conic-projected-x-2} \\
-Y' = b'\Sin (t') \label{eq:conic-projected-y-2} . 
-\end{align}
-
-Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y-2}) we find that
-\begin{align}
-a' &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
-\Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \\
-b' &= b \label{eq:b-prime}
-\end{align}
-
-Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:
-
-\begin{align}
-R'_0 &= \pm a' + x_0\cos i \\
-R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} +  (R_0 \mp a)\cos i
-\end{align}
-
-Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
-\begin{align}
-\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
-\label{eq:qprime}
-\end{align}
-%Where $A\equiv \frac{R_c}{R_0}$
-The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
-\begin{align}
-  \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
-  \label{eq:Aprime}\\
-  \tan\theta'_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
-  \tilde{R}'_{90} &= \left(\frac{2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q}}{\frac{q'}{q}}\right)^{1/2}\frac{\sec i}{f(i;\theta_c)}
-\end{align}
-where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.
-
-When $R'_{90}$ is measurable, diagnostic diagrams like figure (\ref{fig:projected-R90-vs-Rc}) can be used to compare with observations.
 

### 2017-11-05 papers/Paper1/sec-conic.tex
More simplification of the conic section description

@@
+\newcommand{\Q}{\ensuremath{\mathcal{Q}}}
+\newcommand{\thetaQ}{\ensuremath{\theta_{\scriptscriptstyle \Q}}}
+
 \begin{figure*}
@@
     revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
-    between the conic section parameters \(a\), \(b\), \(\theta_q\) and the
+    between the conic section parameters \(a\), \(b\), \(\thetaQ\) and the
     bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
@@
     planitude (flatness at apex, marked by white dot):
-    \(\Pi = R_c/R_0 = 2 \). The quadric angle,
-    \(\theta_q = \tan^{-1} T_q\), varies over the family (see text), with
-    lower values of \(\theta_q\) giving larger values of the alatude,
-    \(\Lambda = R_{90}/R_0 \), meaning more open wings.  Different values of
-    \(\Pi\) can be achieved for the exact same quadrics by sliding them
-    along the \(x\)-axis, which will also change the axis scales since
-    these are normalized by \(R_0\).}
+    \(\Pi = R_c/R_0 = 2 \). The quadric angle, \(\thetaQ\), varies over
+    the family (see text), with lower values of \(\thetaQ\) giving
+    larger values of the alatude, \(\Lambda = R_{90}/R_0 \), meaning more
+    open wings.  Different values of \(\Pi\) can be achieved for the
+    exact same quadrics by sliding them along the \(x\)-axis, which
+    will also change the axis scales since these are normalized by
+    \(R_0\).}
   \label{fig:conics-family}
@@
   \label{eq:Tq}
-  T_q \equiv \sigma \frac{b} {a} \ , 
+  \Q \equiv \sigma \frac{b^2} {a^2} \ , 
 \end{equation}
-where \(T_q < 0\) corresponds to open surfaces (hyperboloids) and
-\(T_q > 0\) corresponds to closed surfaces (oblate spheroids with
-\(T_q > 1\) and prolate spheroids with \(T_q < 1\)).  Special cases
-are the sphere (\(T_q = 1\)) and the paraboloid (\(T_q = 0\)).
+where \(\Q < 0\) corresponds to open surfaces (hyperboloids) and
+\(\Q > 0\) corresponds to closed surfaces (oblate spheroids with
+\(\Q > 1\) and prolate spheroids with \(\Q < 1\)).  Special cases
+are the sphere (\(\Q = 1\)) and the paraboloid (\(\Q = 0\)).
 Alternatively, one can define a \textit{quadric angle}:
-\(\theta_q = \tan^{-1} T_q\), which is marked in Figure~\ref{fig:conics}.
-In the case of hyperboloids, the asymptotic opening angle of the wings
-(\S~\ref{sec:plan-alat-bow} and Fig.~\ref{fig:characteristic-radii})
-is \(\theta_\infty = \pi + \theta_q\) (note that \(\theta_q < 0\) in this case).
+\(\thetaQ = \sigma \tan^{-1} (b/a)\), which is marked in
+Figure~\ref{fig:conics}.  In the case of hyperboloids, the asymptotic
+opening angle of the wings (\S~\ref{sec:plan-alat-bow} and
+Fig.~\ref{fig:characteristic-radii}) is
+\(\theta_\infty = \pi + \thetaQ\) (note that \(\thetaQ < 0\) in this case).
 
-The set of parameters \((T_q, a, x_0)\) are then sufficient to
+The set of parameters \((\Q, a, x_0)\) are then sufficient to
 characterize the star/bow combination, where \(a\) is the quadric
@@
 we can also characterize the star/bow by \((R_0, \Pi, \Lambda)\), where
-\(\Pi\) and \(\Lambda\) are the planitude and alatude, see
-\S~\ref{sec:plan-alat-bow}.  We now derive the relationship between
-these two descriptions.  The apex radius of curvature for a conic
-section is
+\(R_0\) is the star-apex distance, and \(\Pi\) and \(\Lambda\) are the
+planitude and alatude, see \S~\ref{sec:plan-alat-bow}.  We now derive
+the equivalences between these two descriptions.  The apex radius of
+curvature for a conic section is
 \begin{equation}
   \label{eq:Rc-conic}
-  R_c = \frac{b^2}{a} \ ,
+  R_c = \frac{b^2}{a} = a |\Q|\ ,
 \end{equation}
@@
   \label{eq:conic-R90}
-  R_{90} = \left|T_q\right|
-  \left(2aR_0 - \sigma R_0^2\right)^{1/2} \ .
+  R_{90}^2 = \Q \left(\sigma a^2 - x_0^2\right) \ .
 \end{equation}
@@
 \begin{align}
+  \label{eq:R0-from-Q-a-x0}
+  R_0 &= x_0 + \sigma a  \\
+  \label{eq:Pi-from-Q-a-x0}
+  \Pi &= \frac{a \Q}{a + \sigma x_0} \\
+  \label{eq:Lambda-from-Q-a-x0}
+  \Lambda &= \left( \Q \frac{a - \sigma x_0} {a + \sigma x_0}  \right)^{1/2}
+\end{align}
+with \(\sigma = \sgn Q\).  It also follows that the quadric parameter in
+terms of the planitude and alatude is
+\begin{equation}
   \label{eq:Tq-from-Pi-Lambda}
-  T_q &= \sigma \left| 2 \Pi - \Lambda^2 \right|^{1/2} \\
-  \label{eq:a-from-R0-Pi-Lambda}
-  a &= R_0 \frac{ \Pi  } { \left|  2 \Pi - \Lambda^2\right| } \\
-  x_0 &= R_0 \frac{\Pi - \Lambda^2} {2 \Pi - \Lambda^2}
-\end{align}
-From these we see that it is the sign of \(2 \Pi - \Lambda^2\) that determines
-\(\sigma\) and thus whether a quadric is a spheroid or a hyperboloid.  For
+  \Q = 2 \Pi - \Lambda^2 
+\end{equation}
+% \begin{align}
+%   \label{eq:a-from-R0-Pi-Lambda}
+%   a &= R_0 \frac{ \Pi  } { \left|  2 \Pi - \Lambda^2\right| } \\
+%   x_0 &= R_0 \frac{\Pi - \Lambda^2} {2 \Pi - \Lambda^2}
+% \end{align}
+Hence, it is the sign of \(2 \Pi - \Lambda^2\) that determines
+\(\sigma\) and whether a quadric is a spheroid or a hyperboloid.  For
 example, for a constant planitude, \(\Pi\), we can have a family of
@@
   \label{eq:xyz-XYZ}
-  (X, Y, Z) = (x - X_0, y, z) . 
+  (X, Y, Z) = (x - x_0, y, z) . 
 \end{equation}
@@
 \end{gather}
-
-We now show that the projected shape is a conic section of the same
-variety (ellipse or hyperbola) as the one that generated the original
-quadric.  If this were true, then it should be possible to write the
-plane-of-sky coordinates as
+We wish to show that the projected shape is a conic section of the
+same variety (ellipse or hyperbola) as the one that generated the
+original quadric.  If this \emph{were} true, then it would be possible
+to write the plane-of-sky coordinates as
 \begin{gather}
   \begin{aligned}
-    X_{\T}' = a'\Cos( t')  \\
-    Y_{\T}' = b'\Sin (t')  . 
+    X_{\T}' &= a'\Cos( t')  \\
+    Y_{\T}' &= b'\Sin (t')  . 
   \end{aligned}\label{eq:conic-projected-XY-conic}
@@
 (\ref{eq:conic-projected-XY-conic}), we find after some algebra that
+the two forms for \((X_{\T}', Y_{\T}')\) are indeed consistent, with
+the equivalences:
+%
+\newcommand\fQi{\ensuremath{f_{\scriptscriptstyle \Q,i}}}
 \begin{align}
-  a' &= \left(a^2\cos^2 i + \sigma b^2\sin^2 i\right)^{1/2} \\
-  b' &= b \label{eq:b-prime} \\
-  \Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \ , 
+  \label{eq:a-prime}
+  a' &= a \fQi \cos i  \\
+  \label{eq:b-prime}
+  b' &= b \\
+  t' &= \Cos^{-1} \left[ \fQi \Cos(t) \right]  \ ,
+  % t' &= \Cos^{-1} \left[  \frac{a'\Cos(t)}{a\cos i}\right] \ .
 \end{align}
-thus demonstrating the claim.
+where for convenience we define the quadric projection factor:
+\begin{equation}
+  \label{eq:fQi-factor}
+  \fQi = \left( 1 + \Q \tan^2 i \right)^{1/2} \ .
+\end{equation}
+This demonstrates the original claim that the projected shape is also
+a conic section, which means that we can re-use the previous
+equations~(\ref{eq:R0-from-Q-a-x0}--\ref{eq:Tq-from-Pi-Lambda}) with
+primed quantities substituted for unprimed ones.  From
+equations~(\ref{eq:Tq}, \ref{eq:a-prime}, \ref{eq:b-prime}) it follows
+that the quadric parameter of the projected shape is
+\begin{equation}
+  \label{eq:Q-prime}
+  \Q' = \frac{ \Q } { \fQi^2 \cos^2 i} \ .
+\end{equation}
+Finally, we transform the projected reference frame back to be
+centered on the star again:
+\begin{equation}
+  \label{eq:XYZ-xyz-prime}
+  (x_{\T}', y_{\T}') = (X_{\T}' + x_0', Y_{\T}') \ , 
+\end{equation}
+where the projected quadric displacement \(x_0'\) follows from simple
+foreshortening:
+\begin{equation}
+  \label{eq:x0-prime}
+  x_0' = x_0 \cos i \ .
+\end{equation}
 

### 2017-11-05 papers/Paper1/sec-conic.tex
Redo projected quadrics figures with new notation

@@
 %\end{align}
+\begin{figure*}
+  \centering
+  \setkeys{Gin}{width=0.48\linewidth}
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
+    \includegraphics{figs/projected-Rc-vs-i}
+        & \includegraphics{figs/projected-R0-vs-i} \\
+    (c) & (d) \\
+    \includegraphics{figs/projected-R90-vs-i}
+    & \includegraphics{figs/projected-R90-vs-Rc}
+  \end{tabular}
+  \caption[]{Effects of projection on quadrics of revolution:
+    variation with inclination of bow size and shape.  Different line
+    colors correspond to varying quadric parameter, \(\Q\), (see key),
+    while variation in line width corresponds to variation in the
+    ``true'' planitude, \(\Pi\), or apex radius of curvature. Vertical
+    gray rectangles show quartiles of \(|\sin i|\), which will be
+    equally populated for an isotropic distribution of
+    orientations. (a)~Projected planitude: \(\Pi'\). (b)~Projected/true
+    star-apex distance: \(R_0' / R_0\).  (c)~Projected alatude:
+    \(\Lambda'\). (d)~Diagnostic diagram for
+    dimensionless projected radii: \(\tilde{R}_{90}'\) versus
+    \(\tilde{R}_c'\).  Shading indicates different classes of
+    quadrics: hyperboloids (white), prolate spheroids (dark gray), and
+    oblate spheroids (light gray), with the limiting case of
+    paraboloids shown by the thin black line.}
+  \label{fig:quadric-projection}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
+  \caption{Variation with inclination angle of projected quadric parameters}
+  \label{fig:projected-R90-Rc-snapshots}
+\end{figure*}
 
@@
 \end{gather}
-We wish to show that the projected shape is a conic section of the
+We wish to show that this projected shape is a conic section of the
 same variety (ellipse or hyperbola) as the one that generated the
@@
 
-Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:
-
+The projection of the apex distance then follows from the primed
+version of equation~\eqref{eq:R0-from-Q-a-x0} as
+\begin{equation}
+  \label{eq:R0-prime}
+  \frac{R_0'}{R_0} =
+  \cos i \left[ 1 + \frac{\Pi} {\Q} \bigl(\fQi - 1\bigr) \right]
+\end{equation}
+and the projected planitude and alatude can be calculated as
 \begin{align}
-R'_0 &= \pm a' + x_0\cos i \\
-R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} +  (R_0 \mp a)\cos i
+  \label{eq:Pi-prime}
+  \Pi' &= \frac{\Pi}{(R_0'/R_0)\, \fQi \cos i } \\
+  \label{eq:Lambda-prime}
+  \Lambda' &= \left( 2 \Pi' - \Q' \right)^{1/2} \ .
 \end{align}
 
-Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
-\begin{align}
-\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
-\label{eq:qprime}
-\end{align}
-%Where $A\equiv \frac{R_c}{R_0}$
-The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
-\begin{align}
-  \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
-  \label{eq:Aprime}\\
-  \tan\theta'_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
-  \tilde{R}'_{90} &= \left(\frac{2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q}}{\frac{q'}{q}}\right)^{1/2}\frac{\sec i}{f(i;\theta_c)}
-\end{align}
-where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.
+% Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:
 
-When $R'_{90}$ is measurable, diagnostic diagrams like figure (\ref{fig:projected-R90-vs-Rc}) can be used to compare with observations.  
-\begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
-    (a) & (b) \\
-    \includegraphics{figs/projected-Rc-vs-i}
-        & \includegraphics{figs/projected-R0-vs-i} \\
-    (c) & (d) \\
-    \includegraphics{figs/projected-R90-vs-i}
-    & \includegraphics{figs/projected-R90-vs-Rc}
-  \end{tabular}
-  \caption[]{Effects of projection on quadrics of revolution:
-    variation with inclination of characteristic radii.  Different
-    line colors correspond to different quadric shapes (see key),
-    while variation in line width corresponds to variation in the
-    ``true'' dimensionless radius of curvature, \(\tilde{R}_c\), at
-    the apex. Vertical gray rectangles show quartiles of \(|\sin i|\),
-    which will be equally populated for an isotropic distribution of
-    orientations. (a)~Projected radius of curvature, normalized by
-    projected stand-off distance: \( \tilde{R}_c' = R'_c /
-    R'_0\). (b)~Projected stand-off distance: \(R_0' / R_0\).
-    (c)~Projected perpendicular radius, normalized by projected
-    stand-off distance: \( \tilde{R}_{90}' = R'_{90} /
-    R'_0\). (d)~Diagnostic diagram for dimensionless projected radii:
-    \(\tilde{R}_{90}'\) versus \(\tilde{R}_c'\).  Shading indicates
-    different classes of quadrics: hyperboloids (white), prolate
-    spheroids (dark gray), and oblate spheroids (light gray), with the
-    limiting case of paraboloids shown by the thin black line.}
-  \label{fig:quadric-projection}
-\end{figure*}
+% \begin{align}
+% R'_0 &= \pm a' + x_0\cos i \\
+% R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} +  (R_0 \mp a)\cos i
+% \end{align}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
-  \caption{Variation with inclination angle of projected quadric parameters}
-  \label{fig:projected-R90-Rc-snapshots}
-\end{figure*}
+% Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
+% \begin{align}
+% \frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
+% \label{eq:qprime}
+% \end{align}
+% %Where $A\equiv \frac{R_c}{R_0}$
+% The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
+% \begin{align}
+%   \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
+%   \label{eq:Aprime}\\
+%   \tan\theta'_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
+%   \tilde{R}'_{90} &= \left(\frac{2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q}}{\frac{q'}{q}}\right)^{1/2}\frac{\sec i}{f(i;\theta_c)}
+% \end{align}
+% where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.
+
+% When $R'_{90}$ is measurable, diagnostic diagrams like figure (\ref{fig:projected-R90-vs-Rc}) can be used to compare with observations.
 

### 2017-11-05 Quadric-shapes/projected-R0-vs-i.py

@@ -42,7 +42,7 @@ def qratio(inc, Tc, Rc):
 for Rc, lw, alpha, ls, dash, thlab in list(zip(Rcs, lws, alphas, lss, dashes, thlabs))[::-1]:
     for Tc, col, shape in list(zip(Tcs, cols, shapes))[::-1]:
         if Rc == 1.0:
-            label = fr'{shape}: $T_c = {Tc:.1f}$'
+            label = fr'{shape}: $\mathcal{{Q}} = {Tc:.1f}$'
         else:
             label = None
         ax.plot(inc_deg, qratio(inc, Tc, Rc),
@@ -50,7 +50,7 @@ for Rc, lw, alpha, ls, dash, thlab in list(zip(Rcs, lws, alphas, lss, dashes, th
         # ax.plot(inc_deg, qratio(inc, Tc, Rc),
         #         c=col, dashes=dash, label=label)
     ax.text(thlab, qratio(np.radians(thlab), 0.5, Rc),
-            r'$\widetilde{R}_{c}{} = ' + f'{Rc:.1f}$',
+            r'$\Pi = ' + f'{Rc:.1f}$',
             ha='center', va='center', fontsize='x-small',
             bbox={'facecolor': 'white', 'alpha': 0.7, 'pad': 0.05, 'ec': 'none'})
 
@@ -74,7 +74,7 @@ ax.set(
     # ylim=[0.0, 5.5],
     ylim=[0.05, 50],
     xlabel=r'Inclination, degrees',
-    ylabel=r"Variation in projected stand-off distance: $R_{0}' / R_{0}$",
+    ylabel=r"Variation in projected star-apex separation: $R_{0}' / R_{0}$",
     xticks=[15, 30, 45, 60, 75, 90],
 )
 ax.yaxis.set_major_formatter( FormatStrFormatter('%.1f') )

### 2017-11-05 Quadric-shapes/projected-R90-Rc-snapshots.py

@@ -6,7 +6,7 @@ import seaborn as sns
 
 plotfile = sys.argv[0].replace('.py', '.pdf')
 
-sns.set_style('white')
+sns.set_style('ticks')
 fig, axes = plt.subplots(3, 3, figsize=(9, 9), sharex=True, sharey=True)
 
 incs_deg = 10.0*np.arange(9)
@@ -70,10 +70,13 @@ axes[-1, 0].set(
     yscale='linear',
     xlim=[0.0, 8.1],
     ylim=[0.0, 8.1],
-    xlabel=r"$\widetilde{R}_{c}{}'$",
-    ylabel=r"$\widetilde{R}_{90}{}'$",
+    xticks=range(9),
+    yticks=range(9),
+    xlabel=r"$\Pi'$",
+    ylabel=r"$\Lambda'$",
 )        
 
+sns.despine()
 fig.tight_layout()
 fig.savefig(plotfile, dpi=300)
 print(plotfile, end='')

### 2017-11-05 Quadric-shapes/projected-R90-vs-Rc.py

@@ -54,7 +54,7 @@ def R90_prime(inc, Tc, Rc):
 for Rc, lw, alpha in list(zip(Rcs, lws, alphas))[::-1]:
     for Tc, col, shape in list(zip(Tcs, cols, shapes))[::-1]:
         if Rc == 1.0:
-            label = fr'{shape}: $T_c = {Tc:.1f}$'
+            label = fr'{shape}: $\mathcal{{Q}} = {Tc:.1f}$'
         else:
             label = None
         ax.plot(Rc_prime(inc, Tc, Rc), R90_prime(inc, Tc, Rc),
@@ -68,8 +68,8 @@ ax.set(
     yscale='linear',
     xlim=[0.0, 8.1],
     ylim=[0.0, 8.1],
-    xlabel=r"Projected dimensionless radius of curvature: $\widetilde{R}_{c}{}'$",
-    ylabel=r"Projected dimensionless perpendicular radius: $\widetilde{R}_{90}{}'$",
+    xlabel=r"Projected planitude: $\Pi'$",
+    ylabel=r"Projected alatude: $\Lambda'$",
 )        
 sns.despine()
 fig.tight_layout()

### 2017-11-05 Quadric-shapes/projected-Rc-vs-i.py

@@ -41,7 +41,7 @@ def Rc_dash(inc, Tc, Rc):
 for Rc, lw, alpha, ls, dash in list(zip(Rcs, lws, alphas, lss, dashes))[::-1]:
     for Tc, col, shape in list(zip(Tcs, cols, shapes))[::-1]:
         if Rc == 1.0:
-            label = fr'{shape}: $T_c = {Tc:.1f}$'
+            label = fr'{shape}: $\mathcal{{Q}} = {Tc:.1f}$'
         else:
             label = None
         ax.plot(inc_deg, Rc_dash(inc, Tc, Rc),
@@ -59,7 +59,7 @@ ax.set(
     # yticks=[1.0, 2.0, 5.0, 10.0],
     # yticklabels=['1', '2', '5', '10'],
     xlabel=r'Inclination, degrees',
-    ylabel=r"Projected dimensionless radius of curvature: $\widetilde{R}_{c}{}'$",
+    ylabel=r"Projected planitude: $\Pi' = R_{c}'/R_{0}'$",
     xticks=[15, 30, 45, 60, 75, 90],
 )        
 yaxis = ax.get_yaxis()

### 2017-11-05 papers/Paper1/sec-conic.tex
Make start on describing projected quadric figures

@@
     \includegraphics{figs/projected-Rc-vs-i}
-        & \includegraphics{figs/projected-R0-vs-i} \\
-    (c) & (d) \\
-    \includegraphics{figs/projected-R90-vs-i}
-    & \includegraphics{figs/projected-R90-vs-Rc}
+        & \includegraphics{figs/projected-R0-vs-i}
   \end{tabular}
@@
     orientations. (a)~Projected planitude: \(\Pi'\). (b)~Projected/true
-    star-apex distance: \(R_0' / R_0\).  (c)~Projected alatude:
-    \(\Lambda'\). (d)~Diagnostic diagram for
-    dimensionless projected radii: \(\tilde{R}_{90}'\) versus
-    \(\tilde{R}_c'\).  Shading indicates different classes of
-    quadrics: hyperboloids (white), prolate spheroids (dark gray), and
-    oblate spheroids (light gray), with the limiting case of
-    paraboloids shown by the thin black line.}
+    star-apex distance: \(R_0' / R_0\). }
   \label{fig:quadric-projection}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
-  \caption{Variation with inclination angle of projected quadric parameters}
-  \label{fig:projected-R90-Rc-snapshots}
 \end{figure*}
@@
 
+\begin{figure*}
+  \centering
+  \setkeys{Gin}{width=0.48\linewidth}
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
+    \includegraphics{figs/projected-R90-vs-i}
+    & \includegraphics{figs/projected-R90-vs-Rc}
+  \end{tabular}
+  \caption[]{As Figure~\ref{fig:quadric-projection}, but (a)~projected
+    alatude, \(\Lambda'\), versus inclination, \(i\), and (b)~diagnostic
+    planitude--alatude diagram: \(\Lambda'\) versus \(\Pi'\).  Shading
+    indicates different classes of quadrics: hyperboloids (white),
+    prolate spheroids (dark gray), and oblate spheroids (light gray),
+    with the limiting case of paraboloids shown by the thin black
+    line.}
+  \label{fig:quadric-projection-continued}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
+  \caption{Variation with inclination angle of the apparent shape of
+    quadric bows.  Upper left panel shows a set of quadrics at zero
+    inclination, uniformly distributed in planitude and alatude in the
+    ranges \(\Pi = [\frac12, 7]\), \(\Lambda = [\frac12, 7]\).  Subsequent
+    panels show the effect of projection on the apparent
+    \((\Pi', \Lambda')\) as the inclination is increased from
+    \(0^\circ\) to \(80^\circ\) in \(10^\circ\) steps.}
+  \label{fig:projected-R90-Rc-snapshots}
+\end{figure*}
+
 The projection of the apex distance then follows from the primed
@@
 \end{align}
+These are all shown in Figures~\ref{fig:quadric-projection}
+and~\ref{fig:quadric-projection-continued} for a variety of quadric
+parameter \(Q\) (line color) and true planitude \(\Pi\) (line
+thickness).  The projected planitude and alatude
+(Figs~\ref{fig:quadric-projection}a and
+\ref{fig:quadric-projection-continued}a) behave in a qualitatively
+similar fashion.  Whatever the true values of \(\Pi\) and \(\Lambda\), all
+spheroids (\(\Q > 0\)) tend towards \(\Pi' = 1\) and \(\Lambda' = 1\) as the
+inclination increases towards \(90^\circ\).  This is because when the
+spheroid is oriented edge-on, we see its circular cross-section.
+Hyperboloids, on the other hand,
+
+Paraboloids (\(\Q = 0\)), on the other hand,
 

### 2017-11-05 papers/Paper1/sec-conic.tex
Lots more discussion of projected quadric figures

@@
 \(\Q > 0\) corresponds to closed surfaces (oblate spheroids with
-\(\Q > 1\) and prolate spheroids with \(\Q < 1\)).  Special cases
-are the sphere (\(\Q = 1\)) and the paraboloid (\(\Q = 0\)).
+\(\Q > 1\) and prolate spheroids with \(\Q < 1\)).  Special cases are
+the sphere (\(\Q = 1\)) and the paraboloid (\(\Q = 0\)).
 Alternatively, one can define a \textit{quadric angle}:
@@
 Fig.~\ref{fig:characteristic-radii}) is
-\(\theta_\infty = \pi + \thetaQ\) (note that \(\thetaQ < 0\) in this case).
+\(\theta_\infty = \pi + \thetaQ\) (note that \(\thetaQ < 0\) in this case), and
+the minimum slope angle is \(\alpha_{\mathrm{min}} = |\thetaQ|\), see
+discussion following equation~\eqref{eq:thetapar}.
+
+\begin{figure*}
+  \centering
+  \setkeys{Gin}{width=0.48\linewidth}
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
+    \includegraphics{figs/projected-Rc-vs-i}
+        & \includegraphics{figs/projected-R90-vs-i}
+  \end{tabular}
+  \caption[]{Effects of projection on quadrics of revolution:
+    variation with inclination, \(|i|\), of bow size and shape.
+    Different line colors correspond to varying quadric parameter,
+    \(\Q\), (see key), while variation in line width corresponds to
+    variation in the ``true'' planitude, \(\Pi\), or apex radius of
+    curvature. Vertical gray rectangles show quartiles of
+    \(|\sin i|\), which will be equally populated for an isotropic
+    distribution of orientations. (a)~Projected planitude:
+    \(\Pi'\). (b)~Projected alatude, \(\Lambda'\).}
+  \label{fig:quadric-projection}
+\end{figure*}
 
@@
 %\end{align}
-\begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
-    (a) & (b) \\
-    \includegraphics{figs/projected-Rc-vs-i}
-        & \includegraphics{figs/projected-R0-vs-i}
-  \end{tabular}
-  \caption[]{Effects of projection on quadrics of revolution:
-    variation with inclination of bow size and shape.  Different line
-    colors correspond to varying quadric parameter, \(\Q\), (see key),
-    while variation in line width corresponds to variation in the
-    ``true'' planitude, \(\Pi\), or apex radius of curvature. Vertical
-    gray rectangles show quartiles of \(|\sin i|\), which will be
-    equally populated for an isotropic distribution of
-    orientations. (a)~Projected planitude: \(\Pi'\). (b)~Projected/true
-    star-apex distance: \(R_0' / R_0\). }
-  \label{fig:quadric-projection}
-\end{figure*}
 
@@
     (a) & (b) \\
-    \includegraphics{figs/projected-R90-vs-i}
+    \includegraphics{figs/projected-R0-vs-i}
     & \includegraphics{figs/projected-R90-vs-Rc}
   \end{tabular}
-  \caption[]{As Figure~\ref{fig:quadric-projection}, but (a)~projected
-    alatude, \(\Lambda'\), versus inclination, \(i\), and (b)~diagnostic
-    planitude--alatude diagram: \(\Lambda'\) versus \(\Pi'\).  Shading
-    indicates different classes of quadrics: hyperboloids (white),
-    prolate spheroids (dark gray), and oblate spheroids (light gray),
-    with the limiting case of paraboloids shown by the thin black
-    line.}
+  \caption[]{As Figure~\ref{fig:quadric-projection}, but
+    (a)~projected/true star-apex distance: \(R_0' / R_0\), \(i\), and
+    (b)~diagnostic planitude--alatude diagram: \(\Lambda'\) versus
+    \(\Pi'\).  Shading indicates different classes of quadrics:
+    hyperboloids (white), prolate spheroids (dark gray), and oblate
+    spheroids (light gray), with the limiting case of paraboloids
+    shown by the thin black line.}
   \label{fig:quadric-projection-continued}
@@
 thickness).  The projected planitude and alatude
-(Figs~\ref{fig:quadric-projection}a and
-\ref{fig:quadric-projection-continued}a) behave in a qualitatively
-similar fashion.  Whatever the true values of \(\Pi\) and \(\Lambda\), all
-spheroids (\(\Q > 0\)) tend towards \(\Pi' = 1\) and \(\Lambda' = 1\) as the
-inclination increases towards \(90^\circ\).  This is because when the
-spheroid is oriented edge-on, we see its circular cross-section.
-Hyperboloids, on the other hand,
+(Fig.~\ref{fig:quadric-projection}) behave in a qualitatively similar
+fashion.  Whatever the true values of \(\Pi\) and \(\Lambda\), all spheroids
+(\(\Q > 0\)) tend towards \(\Pi' = 1\) and \(\Lambda' = 1\) as the inclination
+increases towards \(90^\circ\).  This is because when the spheroid is
+oriented edge-on, we see its circular cross-section.  Hyperboloids
+behave differently: although \(\Pi'\) and \(\Lambda'\) initially decrease with
+increasing inclination (for true \(\Pi > 2\)), they turn around and
+increases again as \(|i|\) approaches the critical value
+\(i_{\mathrm{crit}} = 90^\circ - |\thetaQ|\).  For
+\(|i| > i_{\mathrm{crit}}\) the tangent line does not exist (see
+\S~\ref{sec:tangent-line}) because the line of sight is ``inside'' the
+asymptotic cone of the far wings (with opening half angle
+\(\alpha_{\mathrm{min}} = |\thetaQ|\)), and so no limb-brightened shell
+would be visible.\footnote{%
+  As illustrated in Figure~8 of \citet{Graham:2002a}, the isophotal
+  emission contours are elliptical in such a case (assuming
+  cylindrical symmetry) and no curved bow shape is apparent.
+  Deviations from cylindrical symmetry \emph{can} result in a curved
+  emission arc, even for this no-tangent case
+  (\citeauthor{Graham:2002a}'s Fig.~9), but that is beyond the scope
+  of this paper.} For paraboloids and spheroids,
+\(\alpha_{\mathrm{min}} = 0\), which means that the tangent line exists for
+all viewing angles.
 
-Paraboloids (\(\Q = 0\)), on the other hand,
+Figure~\ref{fig:quadric-projection-continued}a shows how the apparent
+star-apex separation varies with inclination.  For moderate
+inclinations, \(|i| < 30^\circ\), this depends primarily on the true
+planitude \(\Pi\), with very little influence of the quadric parameter
+\(\Q\).  For \(\Pi > 1\), the separation increases with \(|i|\), whereas
+for \(\Pi < 1\) it decreases slightly.  Note, however, that for cases
+where the projected distance to the source of the external flow,
+\(D'\), can be measured, then \(R_0'/D'\) is always an increasing
+function of \(|i|\).  For larger inclinations, \(|i| > 30^\circ\), the
+strands for different \(\Q\) begin to separate, with hyperbolae
+showing the strongest increase of \(R_0'\) with \(|i|\).
 

### 2017-11-05 papers/Paper1/sec-projection.tex
Lots more discussion of projected quadric figures

@@
 \end{equation}
-where
+where \(\alpha\) is the \textit{slope angle}, given by
 \begin{equation}
@@
 \end{equation}
-and 
+and \(\omega\) is a dimensionless \textit{local growth factor}:
 \begin{equation}
@@
 \end{equation}
-For general \(\phi\), \(\uvec{n}\) and \(\uvec{t}\) can be found by rotating equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, which can then be converted to the observer frame by use of equation~(\ref{eq:Trans}) to give
+For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
+equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, and then
+converting to the observer frame by use of equation~(\ref{eq:Trans})
+to give
 \begin{gather}
@@
 \subsection{Tangent line}
+\label{sec:tangent-line}
 

### 2017-11-05 papers/Paper1/sec-conic.tex
Finish discussion of Pi'-Lambda' plane

@@
     (a) & (b) \\
-    \includegraphics{figs/projected-R0-vs-i}
-    & \includegraphics{figs/projected-R90-vs-Rc}
+    \includegraphics{figs/projected-R90-vs-Rc}
+    & \includegraphics{figs/projected-R0-vs-i}
   \end{tabular}
-  \caption[]{As Figure~\ref{fig:quadric-projection}, but
-    (a)~projected/true star-apex distance: \(R_0' / R_0\), \(i\), and
-    (b)~diagnostic planitude--alatude diagram: \(\Lambda'\) versus
-    \(\Pi'\).  Shading indicates different classes of quadrics:
+  \caption[]{ As Figure~\ref{fig:quadric-projection}, but %
+    (a)~diagnostic planitude--alatude diagram: \(\Lambda'\) versus
+    \(\Pi'\), and %
+    (b)~projected/true star-apex distance: \(R_0' / R_0\) versus
+    \(|i|\). %
+    In (a), shading indicates different classes of quadrics:
     hyperboloids (white), prolate spheroids (dark gray), and oblate
@@
 
-Figure~\ref{fig:quadric-projection-continued}a shows how the apparent
+In Figure~\ref{fig:quadric-projection-continued}a, we show the
+inclination-dependent tracks of the quadrics in the diagnostic
+\(\Pi'\)--\(\Lambda'\) plane of projected alatude versus projected planitude.
+The true planitude and alatude, which are seen for an edge-on viewing
+angle \(i = 0^\circ\), are marked by filled circles.  The zones
+corresponding to each class of quadric (oblate spheroid, prolate
+spheroid, or hyperboloid) are marked by gray shading, and it can be
+seen that the tracks never cross from one zone to another. The
+convergence of all the spheroid tracks on the point
+\((\Pi', \Lambda') = (1, 1)\) is apparent, as is the divergence of the
+hyperboloid tracks towards \((\Pi', \Lambda') = (+\infty, +\infty)\).  The paraboloids,
+by contrast, converge on the point \((\Pi', \Lambda') = (2, 2)\), and the
+special case of the confocal paraboloid,\footnote{So named because the
+  star is at the focus of the parabola.} with true planitude and
+alatude \((\Pi, \Lambda) = (2, 2)\), is the only quadric whose apparent shape
+remains identical for all inclination angles.
+
+Figure~\ref{fig:quadric-projection-continued}b shows how the apparent
 star-apex separation varies with inclination.  For moderate

### 2017-11-06 papers/Paper1/app-p-values.tex
Finish the quadrics section from the theory paper!

@@
     (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
-    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive 
+    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive to differences in the central value of the distributions.
     (Col.~16)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}

### 2017-11-06 papers/Paper1/sec-conic.tex
Finish the quadrics section from the theory paper!

@@
   \caption{Variation with inclination angle of the apparent shape of
-    quadric bows.  Upper left panel shows a set of quadrics at zero
-    inclination, uniformly distributed in planitude and alatude in the
-    ranges \(\Pi = [\frac12, 7]\), \(\Lambda = [\frac12, 7]\).  Subsequent
-    panels show the effect of projection on the apparent
-    \((\Pi', \Lambda')\) as the inclination is increased from
-    \(0^\circ\) to \(80^\circ\) in \(10^\circ\) steps.}
+    quadric bows with true planitude and alatude that are uniformly
+    distributed over the ranges \(\Pi = [0.5, 4.5]\),
+    \(\Lambda = [0.5, 4.5]\).  Panels show the apparent
+    \((\Pi', \Lambda')\) as the inclination is increased through uniform
+    intervals in \(|sin i|\).  Symbol color represents the quadric
+    parameter, \(\Q\), increasing from dark blue, through orange, to
+    yellow. Symbol size is proportional to the increase in apparent
+    star--apex distance, \(R_0'/R_0\).}
   \label{fig:projected-R90-Rc-snapshots}
@@
 
+A complementary view of the effects of projection is shown in
+Figure~\ref{fig:projected-R90-Rc-snapshots}, which shows ``snapshots''
+of \((\Pi', \Lambda')\) for a sequence of 6 values of the inclination, equally
+spaced in \(\vert\sin {i}\vert\), so that each panel is equally likely for an
+isotropic distribution of orientations.  The distribution of the true
+\(\Pi\) and \(\Lambda\) are each assumed to be uniform on the range
+\([0.5, 4.5]\), giving a uniformly filled square of values for
+\(|i| = 0\), which becomes increasingly distorted as \(|i|\)
+increases.  The color scale represents \(\Q\) and the symbol size is
+proportional to \(R_0'/R_0\).  It can be seen that the points tend to
+cluster closer and closer to the diagonal, \(\Lambda' = \Pi'\), as the
+inclination increases, and that the points just below this line tend
+to have the largest values of \(R_0'/R_0\).  The green shaded region
+shows the zone of true \(\Lambda, \Pi\) for hyperboloids where the tangent
+lines till exists for that value of \(|i|\).  This becomes smaller and
+smaller as \(|i|\) increases, which explains why the hyperboloid zone
+becomes increasingly depopulated.  This figure is purely illustrative
+of the qualitative effects of projection, since in reality there is no
+particular reason to expect a uniform distribution in \(\Pi\) and \(\Lambda\).
+
 % Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:

### 2017-11-06 Quadric-shapes/projected-R90-Rc-snapshots.py

@@ -7,13 +7,16 @@ import seaborn as sns
 plotfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
-fig, axes = plt.subplots(3, 3, figsize=(9, 9), sharex=True, sharey=True)
+fig, axes = plt.subplots(2, 3, figsize=(9, 6), sharex=True, sharey=True)
 
-incs_deg = 10.0*np.arange(9)
 
-ny, nx = 55, 55
-Rcs = np.linspace(0.5, 7.0, nx)
-R90s = np.linspace(0.5, 7.0, ny)[::-1]
+sin_inc_edges = np.linspace(0.0, 1.0, len(axes.flat)+1)
+sin_incs = 0.5*(sin_inc_edges[:-1] + sin_inc_edges[1:])
+incs_deg = np.degrees(np.arcsin(sin_incs))
+
+ny, nx = 41, 41
+Rcs = np.linspace(0.5, 4.5, nx)
+R90s = np.linspace(0.5, 4.5, ny)[::-1]
 Rc_grid = Rcs[None, :]*np.ones_like(R90s[:, None])
 R90_grid = R90s[:, None]*np.ones_like(Rcs[None, :])
 Tc_grid = 2*Rc_grid - R90_grid**2
@@ -51,27 +54,35 @@ for ax, inc_deg in zip(axes.flat, incs_deg):
     ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
 
     inc = np.radians(inc_deg)
+
+    thetaQ = 0.5*np.pi - inc
+    Tc_crit = -np.tan(thetaQ)**2
+    R90_Tcrit_grid = np.sqrt(2*Rc_grid2 - Tc_crit)
+    ax.fill_between(Rc_grid2, R90_T0_grid, R90_Tcrit_grid, color='g', alpha=0.1)
+
     Rcp = Rc_prime(inc, Tc_grid, Rc_grid).ravel()
     R90p = R90_prime(inc, Tc_grid, Rc_grid).ravel()
     R0p = qratio(inc, Tc_grid, Rc_grid).ravel()
 
     ax.scatter(Rcp, R90p, c=Tc_grid.ravel(), s=15*R0p,
-	       vmin=Tc_grid.min(), vmax=Tc_grid.max(),
-	       edgecolors='none',
-	       cmap='magma', marker='.', alpha=0.8)
[…]

### 2017-11-07 papers/Paper1/app-parabola.tex
Rewrite appendix A on parabola with new notation

@@
-\section{Parabola of Revolution}
+\section{Paraboloids and their plane-of-sky projection}
 \label{app:parabola}
 
-In this section we develop the particular case of the parabola.
-The parametrization is given by:
+Equation~\eqref{eq:par-xy} for the \(xy\) coordinates of a quadric in the \(\phi = 0\) plane cannot be used in the case of a paraboloid (\(\Q = 0\)).  Instead, a convenient parametrization is
+\begin{gather}
+  \label{eq:parabola-xy}
+  \begin{aligned}
+    x &= R_0 \left(1  - \tfrac{1}{2} \Pi\, t^2\right) \\
+    y &= R_0\, \Pi\, t \ ,
+  \end{aligned}
+\end{gather}
+where we have ``baked in'' knowledge of the planitude,
+\(\Pi = R_c/R_0\) (see \S~\ref{sec:plan-alat-bow}). The projected
+plane-of-sky coordinates of the tangent line follow from
+equation~\eqref{eq:Trans} as
+\begin{gather}
+  \label{eq:parabola-xy-prime-phi}
+  \begin{aligned}
+    x_{\T}' / R_0 &= \left(1 - \tfrac{1}{2} \Pi\, t^2\right) \cos i
+      + \Pi\, t \sin\phi_{\T} \sin i\\
+    y_{\T}' / R_0 &= \Pi\, t \cos\phi_{\T}\ ,
+  \end{aligned}
+\end{gather}
+The azimuth of the tangent line is found from
+equations~(\ref{eq:alpha}, \ref{eq:tanphi}) as
+\(\sin\phi_{\T} = -t^{-1} \tan i \), so that
+\begin{gather}
+  \label{eq:parabola-xy-prime-final}
+  \begin{aligned}
+    x_{\T}' / R_0 &= \cos i \left[ 1 + \tfrac{1}{2} \Pi \tan^2 i -
+      \tfrac{1}{2} \Pi \left( t^2 - \tan^2 i \right) \right]\\
+    y_{\T}' / R_0 &= \Pi \left( t^2 - \tan^2 i \right)^{1/2} \ .
+  \end{aligned}
+\end{gather}
+The projected star--apex distance, \(R_0'\), is the value of
+\(x_{\T}'\) when \(y_{\T}' = 0\), yielding
+\begin{equation}
+  \label{eq:parabola-R0-prime}
+  R_0' / R_0 = \cos i \left( 1 + \tfrac{1}{2} \Pi \tan^2 i  \right) \ . 
+\end{equation}
+Note that this same result can be obtained from a Taylor expansion of
+equation~\eqref{eq:fQi-factor} substituted into~\eqref{eq:R0-prime} in
+the limit \(\Q \to 0\).
 
+Equation~\eqref{eq:parabola-xy-prime-final} can be rewritten in the
+form
+\begin{gather}
+  \label{eq:parabola-xy-all-primes}
+  \begin{aligned}
+    x_{\T}' &= R_0' \left(1  - \tfrac{1}{2} \Pi' t'^2\right) \\
+    y_{\T}' &= R_0' \Pi' t' \ ,
+  \end{aligned}
+\end{gather}
+where
 \begin{align}
-x &= - \frac{1}{2}R_ct^2 + R_0 \\
-y &= R_c t
+  \label{eq:parabola-Pi-prime}
+  \Pi' &= \frac{2 \Pi} {2 \cos^2 i + \Pi \sin^2 i} \\
+  \label{eq:parabola-t-prime}
+  t' &= \cos i \left(t^2 - \tan^2 i\right)^{1/2} \ ,
 \end{align}
-Where $R_c$ is the radius of curvature and $R_0$ is the distance of the parabola nose to the
-origin.
-The respective tridimensional shape is given by:
-\begin{align}
-x &= -\frac{1}{2}R_ct^2 + R_0 \label{eq:x-par-a}\\
-y &= R_c t \cos\phi  \label{eq:y-par-a}\\
-z &= R_c t \sin\phi  \label{eq:z-par-a}
-\end{align}
-The azimutal angle where the surface is tangent to the line of sight in this case is given by:
-\begin{align}
-\sin\phi_t = -\frac{\tan i}{t} \label{eq:sin-tan-a} 
-\end{align}
-
-Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and
-(\ref{eq:z-par-a}) we find the apparent shape
-of the paraboloid:
-
-\begin{align}
-x' &= -\frac{R_c(\frac{1}{2}t^2 \cos^2 i -\sin^2 i)}{\cos i}+R_0\cos i \\
-y' &= R_c\left(t^2-\tan^2 i\right)^{1/2} 
-\end{align}
-
-Taking the limit of equations (\ref{eq:qprime}) and (\ref{eq:Aprime}) when $\theta_c$ tends to zero we find that:
-
-\begin{align}
-\left(\frac{q'}{q}\right)_{\mathrm{parabola}} &= 1+\frac{\tilde{R}_c\tan^2 i}{2}\\
-\left(\tilde{R}'_c\right)_{\mathrm{parabola}} &= \frac{\tilde{R}_c}{\cos^2 i + \frac{\tilde{R}_c}{2}\sin^2 i}
-\end{align}
-
+which demonstrates that the projected shape is also a parabola. It is
+apparent from \eqref{eq:parabola-Pi-prime} that the projected
+planitude obeys
+\begin{equation*}
+\lim_{i \to 90^\circ} \Pi' = 2 \ ,
+\end{equation*}
+for all values of the true planitude \(\Pi\), as can be seen in
+Figure~\ref{fig:quadric-projection}a.  Finally, the projected alatude
+can be found as
+\begin{equation}
+  \label{eq:parabola-Lambda-prime}
+  \Lambda' = \left( 2 \Pi' \right)^{1/2} \ .
+\end{equation}
 %%% Local Variables:

### 2017-11-07 papers/Paper1/sec-conic.tex
Rewrite appendix A on parabola with new notation

@@
 \end{equation}
-and the projected planitude and alatude can be calculated as
+and the projected planitude and alatude can be calculated from
+equations~(\ref{eq:Pi-from-Q-a-x0}, \ref{eq:Tq-from-Pi-Lambda},
+\ref{eq:a-prime}, \ref{eq:Q-prime}) as
 \begin{align}
@@
 shows the zone of true \(\Lambda, \Pi\) for hyperboloids where the tangent
-lines till exists for that value of \(|i|\).  This becomes smaller and
-smaller as \(|i|\) increases, which explains why the hyperboloid zone
-becomes increasingly depopulated.  This figure is purely illustrative
-of the qualitative effects of projection, since in reality there is no
+lines still exists for that value of \(|i|\).  This becomes smaller
+and smaller as \(|i|\) increases, which explains why the hyperboloid
+zone becomes increasingly depopulated: all quadrics that lay above
+this region when \(i = 0^\circ\) will no longer be visible as bow for this
+value of \(|i|\).  Note that this figure is merely illustrative of the
+qualitative effects of projection, since in reality there is no
 particular reason to expect a uniform distribution in \(\Pi\) and \(\Lambda\).

### 2017-11-07 papers/Paper1/app-parabola.tex
Rewrite first paragraph of thin-shell section

@@
 \end{equation*}
-for all values of the true planitude \(\Pi\), as can be seen in
-Figure~\ref{fig:quadric-projection}a.  Finally, the projected alatude
-can be found as
+for all values of the true planitude \(\Pi\), as is shown by the black
+lines in Figure~\ref{fig:quadric-projection}a.  Also, for the special
+case of the confocal paraboloid, \(\Pi = 2\), we have \(\Pi' = \Pi\) by
+equation~\eqref{eq:parabola-Pi-prime} for all inclinations, so its
+shape is unaffected by projection. Finally, the projected alatude can
+be found as
 \begin{equation}

### 2017-11-07 papers/Paper1/sec-thin-shell.tex
Write about the standing wave perturbations
Finish fig captions for shapes and projected shapes.  Finish text
about shapes.
Nearly finish intro to theory paper
Rewrite appendix A on parabola with new notation
Rewrite first paragraph of thin-shell section

@@
 
-\section{Application to the hypersonic thin shell solution}
+\section{Thin-shell hydrodynamic bow shock models}
 \label{sec:crw-scenario}
-As an example application of the ideas of this paper, we consider a
-generalization of the thin-shell solution presented in
-\citet[][hereafter \CRW{}]{Canto:1996}, for the interaction of two
-hypersonic, constant velocity stellar winds.  It is assumed that the
-two shocks are highly radiative and that the post-shock flows are
-perfectly mixed to form a single shell of negligible thickness.  In
-this approximation, the shape of the shell was found algebraically by
-\CRW{} from considering conservation of linear and angular momentum,
-following an approach first outlined in \citet{Wilkin:1996a}.  The
-shape of the bow shock shell is uniquely determined by the parameter
-\(\beta\), defined as the momentum-loss ratio of the two winds:
+
+More physically realistic examples of bow shapes are provided by
+steady-state hydrodynamic models for the interaction of hypersonic
+flows in the thin-shell limit.  The classic examples are the solutions
+for the wind--parallel stream and wind--wind problems (see
+\S~\ref{sec:intro}) of \citet[][hereafter \CRW{}]{Canto:1996}, where
+it is assumed that the two shocks are highly radiative and that the
+post-shock flows are perfectly mixed to form a single shell of
+negligible thickness. In this approximation, the shape of the shell is
+found algebraically by \CRW{} from conservation of linear and angular
+momentum, following an approach first outlined in
+\citet{Wilkin:1996a}.  For the wind--stream case, the resulting bow
+shape was dubbed \textit{wilkinoid} by \citet{Cox:2012a} and has the
+form:
 \begin{equation}
-  \label{eq:beta-definition}
-  \beta \equiv \frac{\dot{M}_w V_w}{\dot{M}_{w1} V_{w1}} . 
+  \label{eq:wilkinoid-R-theta}
+  R(\theta) = R_0\csc\theta\left( 3(1-\theta\cot\theta) \right)^{1/2} \ .
 \end{equation}
-In this definition we use the terminology of \CRW{}, in which
-\(\dot{M}_w\) and \(V_w\) are the mass-loss rate and velocity,
-respectively, of the wind with source at the origin, while
-\(\dot{M}_{w1}\) and \(V_{w1}\) are the mass-loss rate and velocity of
-the second wind, located at a distance \(D\) along their \(z\) axis.
-Note that \CRW{}'s \(z\) and \(r\) correspond to \(x\) and \(y\) in
-sections~\ref{sec:generic-model} to \ref{sec:conic} of the current
+For the wind--wind case, a family of solutions are found, depending on
+the value of \(\beta\), the wind momentum ratio, see
+Figure~\ref{fig:crw-schema}, equations~(\ref{eq:stagnation-radius},
+\ref{eq:beta-definition}), and surrounding discussion in
+\S~\ref{sec:intro}.  We propose that these shapes be called
+\textit{cantoids}.  The exact solution for the cantoid shapes
+(eqs.~[23, 24] of \CRW{}) is only obtainable in implicit form, but an
+approximate explicit solution (eq.~[26] of \CRW{}) is very accurate
+for \(\beta \le 0.1\).  The wilkinoid shape corresponds to the
+\(\beta \to 0\) limit of the cantoids.  Note that \CRW{}'s \(z\) and
+\(r\) axes, which we use in our Figure~\ref{fig:crw-schema},
+correspond respectively to the \(x\) and \(y\) axes in
+sections~\ref{sec:projection} and \ref{sec:conic} of the current
 paper.  By always placing the weaker of the two winds at the origin,
@@
     per solid angle.}
-  \label{fig:crw-schema}
+  \label{fig:anisotropic-arrows}
 \end{figure}
@@
 \begin{align}
-  R_0 = \left(\frac{\dot{M}⁰_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
+  R_0 = \left(\frac{\dot{M}_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
 \end{align}
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/test_xyprime}
+  \includegraphics[width=0.8\linewidth]{figs/test_xyprime}
   \caption{Apparent bow shapes as a function of inclination angle for
@@
   \label{fig:xyprime}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/test_xyprime_ancantoid}
+  \includegraphics[width=0.8\linewidth]{figs/test_xyprime_ancantoid}
   \caption{Further apparent bow shapes as a function of inclination
@@
   \label{fig:xyprime-anacantoid}
-\end{figure}
+\end{figure*}
 

### 2017-11-07 papers/Paper1/app-ancantoid.tex
Move the ancantoid derivation to an appendix

--- 2017-09-28 papers/Paper1/sec-thin-shell.tex
@@
-\newcommand\thC{\(\theta^1\)\,Ori~C}
-\defcitealias{Canto:1996}{CRW}
-\newcommand\CRW{\citetalias{Canto:1996}}
-
-\section{Application to the hypersonic thin shell solution}
-\label{sec:crw-scenario}
-As an example application of the ideas of this paper, we consider a
-generalization of the thin-shell solution presented in
-\citet[][hereafter \CRW{}]{Canto:1996}, for the interaction of two
-hypersonic, constant velocity stellar winds.  It is assumed that the
-two shocks are highly radiative and that the post-shock flows are
-perfectly mixed to form a single shell of negligible thickness.  In
-this approximation, the shape of the shell was found algebraically by
-\CRW{} from considering conservation of linear and angular momentum,
-following an approach first outlined in \citet{Wilkin:1996a}.  The
-shape of the bow shock shell is uniquely determined by the parameter
-\(\beta\), defined as the momentum-loss ratio of the two winds:
-\begin{equation}
-  \label{eq:beta-definition}
-  \beta \equiv \frac{\dot{M}_w V_w}{\dot{M}_{w1} V_{w1}} . 
-\end{equation}
-In this definition we use the terminology of \CRW{}, in which
-\(\dot{M}_w\) and \(V_w\) are the mass-loss rate and velocity,
-respectively, of the wind with source at the origin, while
-\(\dot{M}_{w1}\) and \(V_{w1}\) are the mass-loss rate and velocity of
-the second wind, located at a distance \(D\) along their \(z\) axis.
-Note that \CRW{}'s \(z\) and \(r\) correspond to \(x\) and \(y\) in
-sections~\ref{sec:generic-model} to \ref{sec:conic} of the current
-paper.  By always placing the weaker of the two winds at the origin,
-it is only necessary to consider \(\beta \le 1\).
-
+\section{Bow shocks from anisotropic wind--wind interactions}
+\label{app:ancantoid}
 \begin{figure}
@@
   \caption[]{Schematic diagram of wind flow patterns in isotropic and
-    non-isotropic cases.  Arrows represent the wind momentum loss rate
-    per solid angle.}
-  \label{fig:crw-schema}
+    non-isotropic cases for different values of the anisotropy index,
+    \(k\).  Arrow length represents the wind momentum loss rate per
+    solid angle.}
+  \label{fig:anisotropic-arrows}
 \end{figure}
+
+We wish to generalize the results of \citet[\CRW{}]{Canto:1996} to the case where the inner wind is no longer isotropic, but instead has a density that falls off with angle away from the symmetry axis.
+Specifically, at some fiducial radius, \(r_0\), from the origin, the wind mass density is given by
+\begin{equation}
+  \label{eq:ancantoid-density}
+  \rho(r_0, \theta) =
+  \begin{cases}
+    \rho_0 \cos^k \theta & \text{for \(\theta \le 90^\circ\)} \\
+    0 & \text{for \(\theta > 90^\circ\)}
+  \end{cases}
+  \ ,
+\end{equation}
+where \(k \ge 0\) is an anisotropy index.  The wind velocity is still
+assumed to be constant and the wind streamlines to be radial, so the
+radial variation of density at each angle is
+\(\rho(r, \theta) = \rho(r_0, \theta)\, (r/r_0)^{-2}\) and the wind momentum loss rate
+per solid angle has the same \(\cos^k\theta\) dependence as the density.
+
 In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
@@
 
-\begin{figure}
-\includegraphics[width=\linewidth]{figs/r-beta}
-\caption{Bow shock shapes for interacting winds in the thin-shell
-  approximation. Coordinates are normalized by $D$, the distance
-  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
-  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
-  different values of the wind momentum ratio, \(\beta\), and for the
-  case where the weaker wind is isotropic (dashed lines) or an
-  anisotropic photoevaporation flow. The solid lines shows a wind with a
-  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
-  And the dotted lines show a wind with extreme anisotropy degree $(k=8)$.}
-\label{fig:r-beta}
-\end{figure}
-
-\subsection{Characteristic Radii}
-$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
-%Here goes a little introduction
-For the rest of the radii we need a relation between $\theta$ and $\theta_1$ as follows:
-
-\begin{align}
-\theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
-\label{eq:th1th}
-\end{align}
-
-Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
-We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
-which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:
-
-\begin{align}
-\tilde{R}_{90} = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
-\label{eq:B}
-\end{align}
-
-Now, the solution for $R_c$ is explained in appendix \ref{app:rc-analytic},
-which lead us to derive the radius of curvature at the symmetry axis:
-
-\begin{align}
-R_c &= R_0\left(1-2\gamma\right)^{-1} \label{eq:Rcurv} \\
-\mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
-\end{align}
-
-Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
-conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})
-
-\begin{align}
-\tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
-\label{eq:thc-CRW}
-\end{align}
-
-\begin{figure}
-\begin{tabular}{c}
-\includegraphics[width=\linewidth]{figs/AB-beta-log} \\
-\includegraphics[width=\linewidth]{figs/thc-beta-log}
-\end{tabular}
-\caption{Top: Characteristic radii, $\tilde{R}_c = R_c/R_0$ (solid lines) and $\tilde{R}_{90}
-  = R_{90}/R_0$ (dashed lines)
-  vs $\beta$, calculated from quadric fits to the generalized CRW
-  solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
-  angle $\theta_c$ vs $\beta$ for the bow 
-  shock head (solid lines) and the bow shock tail (dashed lines).}
-\label{fig:rad-beta}
-\end{figure}
-
-% Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
-%being $R_0$ the
-%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
-
-With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
-momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
-
-\subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}
-
-This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:
-
-\begin{align}
-  R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
-\end{align}
-Where:
-\begin{align}
-  R_0 = \left(\frac{\dot{M}⁰_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
-\end{align}
-And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
-The characteristic radii are given by:
-\begin{align}
-  \tilde{R}_{90} &= \sqrt{3} \\
-  \tilde{R}_c &= \frac{5}{3}
-\end{align}
-The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}
-
-\subsection{Fits to the tail}
-\label{sec:fits-tail}
-
-In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with
-
-We therefore 
-We carry out three-level nested fits to determine the
-
-For the hyperbola ``center''
-\begin{multline}
-  \label{eq:tail-analytic-x0}
-  x_{0,\mathrm{t}} = 0.7 \beta^{-0.55} \biggl[
-    C_3 \bigl(\log_{10}\beta\bigr)^3 + C_2 \bigl(\log_{10}\beta\bigr)^2 
-  \\ + C_1 \log_{10}\beta + C_0
-  \biggr]
-\end{multline}
-\begin{equation}
-  \label{eq:tail-analytic-x0-minus-a}
-  (x_{0,\mathrm{t}} - a_{\mathrm{t}}) = D_2 (\log_{10}\beta)^2 + D_1 \log_{10}\beta + D_0
-\end{equation}
-where
-\begin{alignat}{2}
-  \label{eq:tail-analytic-coeffs-c}
-  C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
-  \label{eq:tail-analytic-coeffs-d}
-  D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\}
-\end{alignat}
-
-\newcommand\iso{\ensuremath{^{\mathrm{iso}}}}
-
-\begin{table}
-  \caption{Coefficients for hyperbola fit to bowshock tails}
-  \label{tab:tail-fit-coeffs}
-  \renewcommand\arraystretch{1.2}
-  \setlength\tabcolsep{0.5\tabcolsep}
-  \begin{tabular}{@{}llll@{}}
-    \toprule
-    Equation~(\ref{eq:tail-analytic-x0}) & 
-    \multicolumn{3}{l}{
-    Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
-    } \\ \midrule
-    \( C\iso_0 = +1.3195     \)    
-    & \( c_{0,0} = +2.0758   \)  
-    & \( c_{1,0} = -0.2309   \)  
-    & \( c_{2,0} = -0.2532   \)\\
-      \( C\iso_1 = +0.4229     \)    
-    & \( c_{0,1} = +0.9571   \)  
-    & \( c_{1,1} = -0.1530   \)  
-    & \( c_{2,1} = -0.2487   \)\\
-      \( C\iso_2 = +0.1092     \)    
-    & \( c_{0,2} = +0.2528   \)  
-    & \( c_{1,2} = -0.0360   \)  
-    & \( c_{2,2} = -0.0794   \)\\
-      \( C\iso_3 = +0.0051     \)    
-    & \( c_{0,3} = +0.0171   \)  
-    & \( c_{1,3} = -0.0010   \)  
-    & \( c_{2,3} = -0.0095   \)\\ \midrule
-    Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
-    \multicolumn{3}{l}{
-    Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
-    } \\ \midrule
-    \( D\iso_0 = +0.7962   \)    
-    & \( d_{0,0} = +0.8516 \)  
-    & \( d_{1,0} = -0.0907 \)  
-    & \( d_{2,0} = -0.2002 \)\\
-      \( D\iso_1 = -0.2363   \)    
-    & \( d_{0,1} = -0.7620 \)  
-    & \( d_{1,1} = +0.1411 \)  
-    & \( d_{2,1} = -0.0295 \)\\
-      \( D\iso_2 = -0.0126   \)    
-    & \( d_{0,2} = -0.0683 \)  
-    & \( d_{1,2} = +0.0390 \)  
-    & \( d_{2,2} = -0.0236 \)\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
-  \caption{Double quadric fits to thin shell
-    solutions.}
-  \label{fig:head-tail}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/projected-th90-vs-i}
-  \caption{Variation with inclination of the body-frame polar angle
-    \(\theta_{90}\) that corresponds to the projected perpendicular radius
-    \(R’_{90}\).  Line colors and thicknesses represent different
-    quadrics of revolution, as in
-    Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
-    important because the quadric fits to the bow shock shape must be
-    accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
-    for \(R’_{90}\).}
-  \label{fig:projected-th90}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
-  \caption[]{Residuals of double quadric fits to thin shell solutions.
-    Residuals are expressed as the fractional error in the
-    complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
-    the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
-  \label{fig:head-tail-residuals}
-\end{figure*}
-
-\subsection{Projection effects in the thin shell model}
-\label{sec:proj-effects-thin}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/two-quadric-R90-vs-Rc}
-  \caption{Diagnostic diagram for thin shell models}
-  \label{fig:thin-shell-R90-Rc}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/two-quadric-R90-Rc-snapshots}
-  \caption{Variation with inclination angle of radii diagnostics}
-  \label{fig:thin-shell-R90-Rc-snapshots}
-\end{figure*}
-
 %%% Local Variables:

### 2017-11-07 papers/Paper1/sec-thin-shell.tex
Move the ancantoid derivation to an appendix

@@
 it is only necessary to consider \(\beta \le 1\).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/anisotropic-arrows}
-  \caption[]{Schematic diagram of wind flow patterns in isotropic and
-    non-isotropic cases.  Arrows represent the wind momentum loss rate
-    per solid angle.}
-  \label{fig:anisotropic-arrows}
-\end{figure}
-In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
-with the following density distribution:
-\begin{align}
-  n(\theta) = n_0\cos^k\theta
-\end{align}  
-The index $k$ gives the anisotropy degree. We are interested in winds where $k \geq 0$ for further applications. By the other side, we keep the strongest
-wind as isotropic.
-
-The shape of the resultant bow shock is given by:
-%If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}),
-%we find that the solutions for equations (8) - (11) of \CRW{} are the following:
-
-%If we apply the \CRW{} formalism for a generalized photoevaporated flow with density given by equation (\ref{eq:ngen}),
-%the shell shape $R(\theta)$ may be calculated from equation (6) of CRW{}:
-\begin{align}
-  R = \frac{\dot{J}_w + \dot{J}_{w1}}{\left(\dot{\Pi}_{wr}+\dot{\Pi}_{wr1}\right)\cos\theta-\left(\dot{\Pi}_{wz1}+\dot{\Pi}_{wz1}\right)\sin\theta}
-  \label{eq:Rmom}
-\end{align}
-
-Where:
-
-\begin{align}
-\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{k+2}\theta\right)  \label{eq:pir}\\
-\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w v_w I_k (\theta) \label{eq:piz}\\
-I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \label{eq:Ik}\\
-\dot{J}_w &= 0 \label{eq:jdot} \\
-\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
-M^0_w &\equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
-\dot{\Pi}_{wz1} & = -\frac{\dot{M}^0_{w1}v_{w1}}{4}\sin^2\theta_1\\
-\dot{\Pi}_{wr1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
-\dot{J}_{w1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \label{eq:jdot1}
-\end{align}
-
-Combining equations  (\ref{eq:pir}) to (\ref{eq:jdot1}) we can obtain numerically the bow shock shape $R(\theta)$ from equation (\ref{eq:Rmom}).
-To find the projected shape in the plane of sky, we fit $R(\theta)$ into a quadric curve which has the same characteristic radii $(R_0,R_c,R_{90})$. 
-%The most notable scenarios, since they have astrophysical relevance are the following:
-%$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
-%is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
 

### 2017-11-07 papers/Paper1/app-ancantoid.tex
Finish Appendix B on ancantoids!

@@
 
-We wish to generalize the results of \citet[\CRW{}]{Canto:1996} to the case where the inner wind is no longer isotropic, but instead has a density that falls off with angle away from the symmetry axis.
-Specifically, at some fiducial radius, \(r_0\), from the origin, the wind mass density is given by
+We wish to generalize the results of \citet[\CRW{}]{Canto:1996} to the
+case where the inner wind is no longer isotropic, but instead has a
+density that falls off with angle, \(\theta\), away from the symmetry axis.
+Specifically, at some fiducial radius, \(r_0\), from the origin, the
+wind mass density is given by
 \begin{equation}
@@
 \end{equation}
-where \(k \ge 0\) is an anisotropy index.  The wind velocity is still
-assumed to be constant and the wind streamlines to be radial, so the
-radial variation of density at each angle is
-\(\rho(r, \theta) = \rho(r_0, \theta)\, (r/r_0)^{-2}\) and the wind momentum loss rate
-per solid angle has the same \(\cos^k\theta\) dependence as the density.
+where \(\rho_0\) is the density on the symmetry axis and \(k \ge 0\) is an
+\textit{anisotropy index}.  The wind velocity is still assumed to be
+constant and the wind streamlines to be radial, so the radial
+variation of density at each angle is
+\(\rho(r, \theta) = \rho(r_0, \theta)\, (r/r_0)^{-2}\) and the wind mass loss rate and
+momentum loss rate per solid angle both have the same \(\cos^k\theta\)
+dependence as the density.  Examples are shown in
+Figure~\ref{fig:anisotropic-arrows} for a variety of different values
+of \(k\).  As \(k\) increases, the wind becomes increasingly jet-like.
 
-In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
-with the following density distribution:
-\begin{align}
-  n(\theta) = n_0\cos^k\theta
-\end{align}  
-The index $k$ gives the anisotropy degree. We are interested in winds where $k \geq 0$ for further applications. By the other side, we keep the strongest
-wind as isotropic.
+Our primary motivation for considering such an anisotropic wind is the
+case of the Orion Nebula proplyds and their interaction with the
+stellar wind of the massive star \thC{}
+\citep{Garcia-Arredondo:2001a}.  The inner ``wind'' in this case is
+the transonic photoevaporation flow away from a roughly hemispherical
+ionization front, where photoionization equilibrium, together with
+monodirectional illumination of the front, implies that the ionized
+hydrogen density, \(n\), satisfies \(n^2 \propto \cos \theta\), which is
+equivalent to \(k = 0.5\) in equation~\eqref{eq:ancantoid-density}.
+Since the primary source of ionizing photons is the same star that is
+the source of the outer wind, it is natural that the inner wind's axis
+should be aligned with the star--star axis in this case.  For other
+potential causes of wind anisotropy (for instance, bipolar flow from
+an accretion disk), there is no particular reason for the axes to be
+aligned, so cylindrical symmetry would be broken.  Nevertheless, we
+calculate results for general \(k\) with aligned axes, so as to
+provide a richer variety of cylindrically symmetric bow shock shapes
+than are seen in the cantoids.
 
-The shape of the resultant bow shock is given by:
-%If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}),
-%we find that the solutions for equations (8) - (11) of \CRW{} are the following:
+The general solution for the bow shock shape, \(R(\theta)\), in the \CRW{}
+formalism is
+\begin{equation}
+  R(\theta) = \frac {\dot{J}_{\w} + \dot{J}_{\w{}1}}
+  {\left(\dot{\Pi}_{\w{}r}+\dot{\Pi}_{\w{}r1}\right)\cos\theta
+    - \left(\dot{\Pi}_{\w{}z}+\dot{\Pi}_{\w{}z1}\right)\sin\theta}
+  \label{eq:Rmom}
+\end{equation}
+where \(\dot{\Pi}_{\w{}r}\), \(\dot{\Pi}_{\w{}z}\), \(\dot{J}_{\w}\) are
+the accumulated linear radial momentum, linear axial momentum, and
+angular momentum, respectively, due to the inner wind emitted between
+the axis and \(\theta\). The equivalent quantities for the outer wind have
+subscripts appended with ``1''.  The inner wind momenta for our
+anisotropic case (replacing \CRW{}'s eqs.~[9, 10]) are:
+\begin{gather}
+  \label{eq:ancantoid-momenta}
+  \begin{aligned}
+    \dot{\Pi}_{\w{}z} &= \frac{k + 1}{2(k+2)}\, \dot{M}_{\w}^0 V_{\w}
+    \left(1-\cos^{k+2}\theta\right) \\
+    \dot{\Pi}_{\w{}r} &= (k + 1)\, \dot{M}^0_{\w} V_{\w}\, I_k (\theta) 
+  \end{aligned}
+\end{gather}
+where
+\begin{equation}
+  \label{eq:ancantoid-mass-loss}
+  \dot{M}^0_{\w} = \frac{2 \pi} {k + 1} r_0^2 \rho_0 V_{\w}
+\end{equation}
+is the total mass-loss rate of the inner wind. The integral
+\begin{equation}
+  \label{eq:ancantoid-I-integral}
+  I_k(\theta) = \int^\theta_0 \cos^k \theta \sin^2\theta \,d\theta 
+\end{equation}
+has an analytic solution in terms of the hypergeometric function,
+\({}_2 F_1(-\tfrac12; \tfrac{1+k}2; \tfrac{3+k}2; \cos^2 \theta)\), but is
+more straightforwardly calculated by numerical quadrature.  The
+angular momentum of the inner wind about the origin is
+\(\dot{J}_{\w} = 0\) because it is purely radial.  The outer wind
+momenta are unchanged from the \CRW{} case, but are given here for
+completeness:
+\begin{gather}
+  \label{eq:ancantoid-momenta-outer}
+  \begin{aligned}
+    \dot{\Pi}_{\w{}z1} & =
+    -\frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\sin^2\theta_1\\
+    \dot{\Pi}_{\w{}r1} & =
+    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
+    \dot{J}_{\w{}1} & =
+    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \ .
+  \end{aligned} 
+\end{gather}
 
-%If we apply the \CRW{} formalism for a generalized photoevaporated flow with density given by equation (\ref{eq:ngen}),
-%the shell shape $R(\theta)$ may be calculated from equation (6) of CRW{}:
-\begin{align}
-  R = \frac{\dot{J}_w + \dot{J}_{w1}}{\left(\dot{\Pi}_{wr}+\dot{\Pi}_{wr1}\right)\cos\theta-\left(\dot{\Pi}_{wz1}+\dot{\Pi}_{wz1}\right)\sin\theta}
-  \label{eq:Rmom}
-\end{align}
+We define \(\beta\) in this case as the momentum ratio \emph{on the symmetry axis}, which means that 
+\begin{equation}
+  \label{eq:ancantoid-momentum-ratio}
+  \dot{M}^0_{\w{}1}V_{\w{}1} = 2 (k + 1)\, \beta\, \dot{M}^0_{\w} V_{\w} \ . 
+\end{equation}
+Substituting
+equations~(\ref{eq:ancantoid-momenta}--\ref{eq:ancantoid-momentum-ratio})
+into equation~\eqref{eq:Rmom} and making use of the geometric relation
+between the interior angles of the triangle shown in
+Figure~\ref{fig:crw-schema}:
+\begin{equation}
+  \label{eq:crw-angles}
+  R \sin(\theta + \theta_1) = D \sin \theta_1 \ , 
+\end{equation}
+yields
+\begin{equation}
+  \label{eq:ancantoid-theta-theta1-implicit}
+  \theta_1 \cot \theta_1 = 1 +
+  2 \beta \left(
+    I_k(\theta) \cot \theta
+    - \frac{1 - \cos^{k+2} \theta} {k + 2} \right)   \ , 
+\end{equation}
+which is the generalization of \CRW{}'s equation~(24) to the
+anisotropic case.  Equation~\eqref{eq:ancantoid-theta-theta1-implicit}
+is solved numerically to give \(\theta_1(\theta)\), which is then combined with
+equations~(\ref{eq:crw-angles}) and (\ref{eq:stagnation-radius}) to
+give the dimensionless bow shape, \(R(\theta; \beta, k)/R_0\), where we now
+explicitly indicate the dependence of the solution on two parameters:
+axial momentum ratio, \(\beta\), and anisotropy index, \(k\).  We refer to
+the resultant bow shapes as \textit{ancantoids}.
 
-Where:
-
-\begin{align}
-\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{k+2}\theta\right)  \label{eq:pir}\\
-\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w v_w I_k (\theta) \label{eq:piz}\\
-I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \label{eq:Ik}\\
-\dot{J}_w &= 0 \label{eq:jdot} \\
-\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
-M^0_w &\equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
-\dot{\Pi}_{wz1} & = -\frac{\dot{M}^0_{w1}v_{w1}}{4}\sin^2\theta_1\\
-\dot{\Pi}_{wr1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
-\dot{J}_{w1} & = \frac{\dot{M}^0_{w1}v_{w1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \label{eq:jdot1}
-\end{align}
-
-Combining equations  (\ref{eq:pir}) to (\ref{eq:jdot1}) we can obtain numerically the bow shock shape $R(\theta)$ from equation (\ref{eq:Rmom}).
-To find the projected shape in the plane of sky, we fit $R(\theta)$ into a quadric curve which has the same characteristic radii $(R_0,R_c,R_{90})$. 
 %The most notable scenarios, since they have astrophysical relevance are the following:

### 2017-11-07 papers/Paper1/sec-conclusions.tex
Finish Appendix B on ancantoids!

@@
 
+How different regions of the \(\Pi\)--\(\Lambda\) plane are populated.
+Bottom-right quadrant hard to get to (except for standing wave
+oscillations), but may be due to finite shell thickness, which (for
+low Mach number) will be more apparent in the wings, which might
+decrease \(\Lambda\) more than \(\Pi\).  Fact that thin-shell solutions should
+trace the contact discontinuity, but in some cases it may be only the
+inner or the outer shell that is visible.
+
 %and was applied to the proplyds in the core of the ONC.

### 2017-11-07 papers/Paper1/sec-intro.tex
Finish Appendix B on ancantoids!

@@
 \end{equation}
-where \(\beta\) is the momentum ratio between the two winds.  If the inner
-wind has mass-loss rate \(\dot{M}_w\) and terminal velocity \(V_w\),
-while the outer wind has corresponding values \(\dot{M}_{w1}\) and
-\(V_{w1}\), then the momentum ratio is
+where \(\beta\) is the momentum ratio between the two winds.  If the winds
+are isotropic, with inner wind mass-loss rate \(\dot{M}_{\w}\) and
+terminal velocity \(V_{\w}\), while the outer wind has corresponding
+values \(\dot{M}_{\w1}\) and \(V_{\w1}\), then the momentum ratio is
 \begin{equation}
   \label{eq:beta-definition}
-  \beta = \frac{\dot{M}_w V_w} {\dot{M}_{w1} V_{w1}} .
+  \beta = \frac{\dot{M}_{\w} V_{\w}} {\dot{M}_{\w1} V_{\w1}} .
 \end{equation}
@@
 % The bow shocks we consider are originated by a source located at the
-% origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a
-% terminal (supersonic) velocity $v_w$. This wind interacts with another
+% origin, emitting a wind with a mass loss rate of $\dot{M}_{\w}$ and a
+% terminal (supersonic) velocity $v_{\w}$. This wind interacts with another
 % wind originated by another source located at a distance $D$ from the
-% first one.  The mass loss rate of the second source is $\dot{M}_{w1}$
-% and the terminal velocity is $v_{w1}$. The momentum of the wind of the
+% first one.  The mass loss rate of the second source is $\dot{M}_{\w1}$
+% and the terminal velocity is $v_{\w1}$. The momentum of the wind of the
 % second source is higher than the momentum of the first one, and the
@@
     (\(R_{90}\)) to the symmetry axis, together with radius of
-    curvature (\(R_c\)) at apex and asymptotic opening angle
+    curvature (\(R_{\C}\)) at apex and asymptotic opening angle
     (\(\theta_\infty\)) of the far wings. }
@@
 The perpendicular radius \(R_{90}\) is the value of \(R(\theta)\) at
-\(\theta = 90^\circ\), whereas \(R_c\) is the radius of curvature of the bow at
+\(\theta = 90^\circ\), whereas \(R_{\C}\) is the radius of curvature of the bow at
 the apex (\(\theta = 0\)), which in cylindrical symmetry simplifies to
@@
   \label{eq:radius-curvature}
-  R_c 
+  R_{\C} 
   % = R_0 \Biggl[ 1
@@
 best.  In contrast, the three radii, \(R_0\), \(R_{90}\), and
-\(R_c\). are straightforward to determine from observations.  One
+\(R_{\C}\). are straightforward to determine from observations.  One
 simple method to estimate the radius of curvature is to make use of
@@
 \(|\theta| < \Delta\theta \) yields \(R_0\) and \(R_{\theta\theta,0}\) from the first two
-coefficients, and hence \(R_c\) from
+coefficients, and hence \(R_{\C}\) from
 equation~\eqref{eq:radius-curvature}.  Experience has shown that
@@
   \label{eq:planitude}
-  \text{Planitude} \quad \Pi & \equiv  \frac{R_c} {R_0} \\
+  \text{Planitude} \quad \Pi & \equiv  \frac{R_{\C}} {R_0} \\
   \label{eq:alatude}
@@
 \citealp{Robberto:2005, Cox:2012a, Meyer:2016a}), but as far as we
-know, we are the first to include \(R_c\).  \citet{Robberto:2005}
+know, we are the first to include \(R_{\C}\).  \citet{Robberto:2005}
 \S~4.2 use the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd
@@
 % \item Radius at axis of symmetry. Denoted as $R_0$.
-% \item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
+% \item Radius of Curvature at the axis of symmetry. Denoted as $R_{\C}$
 % \item Radius at the perpendicular direction to the symmetry

### 2017-11-08 papers/Paper1/app-shape-parameters.tex
Re-write derivation of planitude for ancantoids
Note that C_{k\beta} is now 2 x what it was before

\section{Planitude and alatude of thin-shell bow shapes}
\label{sec:thin-shell-shapes}

In this appendix, we provide analytic calculations of the planitude
(exact) and alatude (approximate) for the wilkinoid, cantoids, and
ancantoids.  We first consider the most general case of the
ancantoids, and then show how results for cantoids and the wilkinoid
follow as special cases.

From equations~\eqref{eq:radius-curvature} and~\eqref{eq:planitude},
the planitude depends on the apex second derivative,
\(R_{\theta\theta,0}\), as
\begin{equation}
  \label{eq:planitude-from-2nd-derivative}
  \Pi = \left(  1 - R_{\theta\theta,0} / R_0\right)^{-1} \ .
\end{equation}
From equation~\eqref{eq:taylor-R-theta}, the second derivative can be
found from the coefficient of \(\theta^2\) in the Taylor expansion
of \(R(\theta)\).  Since we do not have \(R(\theta)\) in explicit analytic form,
we proceed via a Taylor expansion of the implicit
equations~\eqref{eq:crw-angles}
and~\eqref{eq:ancantoid-theta-theta1-implicit}, retaining terms up to
\(\theta^4\) to obtain from
equation~\eqref{eq:ancantoid-theta-theta1-implicit}:
\begin{equation}
  \label{eq:taylor-expansion-implicit}
  \theta_1^2 = \beta \theta^2 \left( 1 + C_{k\beta} \theta^2\right) + \mathcal{O}(\theta^6)\ , 
\end{equation}
with the coefficient \(C_{k\beta}\) given by
\begin{equation}
  \label{eq:C-k-beta}
  C_{k\beta} = \frac{1}{15} - \frac{3k}{20} - \frac{\beta}{15}  \ .
\end{equation}
Then, from equation~\eqref{eq:crw-angles} we find
\begin{align}
  \label{eq:taylor-R-over-D}
  \frac{R}{D} & = \frac{\sin \theta_1} {\sin (\theta + \theta_1)} \nonumber \\
              & = \frac{\beta^{1/2}}{1+\beta^{1/2}}
                \left\lbrace 1 + \theta^2
                \left[ \frac{C_{k\beta}} {2 \left(1+\beta^{1/2}\right)}
                + \frac{1}{6} \left(1+2\beta^{1/2} \right)
                \right]
                \right\rbrace + \mathcal{O}(\theta^4) \ ,
\end{align}
where in the second line we have carried out a Taylor expansion of the
two \(\sin\) terms and substituted
\eqref{eq:taylor-expansion-implicit}.  Comparing coefficients of unity
and \(\theta^2\) between equations~\eqref{eq:taylor-R-theta} and
\eqref{eq:taylor-R-over-D} we find
\begin{align}
  \label{eq:again-R0-over-D}
  \frac{R_0} {D} &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
  \label{eq:final-second-derivative}
  \frac{R_{\theta\theta,0}} {R_0} &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{3}\left(1+2\beta^{1/2}\right) \ ,
\end{align}
so that the final result for the planitude, from~\eqref{eq:planitude-from-2nd-derivative}, is
\begin{equation}
  \label{eq:final-planitude}
  \Pi = \left[ {1 - \frac{C_{k\beta}}{1+\beta^{1/2}} - \frac{1}{3}\left(1+2\beta^{1/2}\right)}
  \right]^{-1} \ .
\end{equation}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

### 2017-11-08 papers/Paper1/sec-thin-shell.tex
Re-write derivation of planitude for ancantoids
Note that C_{k\beta} is now 2 x what it was before

@@
 \end{equation}
-For the wind--wind case, a family of solutions are found, depending on
+
+For the wind--wind case, a family of solutions are found that depend on
 the value of \(\beta\), the wind momentum ratio, see
@@
 it is only necessary to consider \(\beta \le 1\).
+
+A generalization of the cantoids to the case of an
+anisotropic\footnote{Note that the wind anisotropy axis must be
+  aligned with the star--star axis to maintain cylindrical symmetry.}
+inner wind is developed in Appendix~\ref{app:ancantoid}, giving rise
+to what we call \textit{ancantoids}, which depend on an anisotropy
+index, \(k\), in addition to \(\beta\).
 

### 2017-11-08 papers/Paper1/app-shape-parameters.tex
Re-write derivation of alatude for ancantoids

@@
 \end{equation}
-Then, from equation~\eqref{eq:crw-angles} we find
+Note that it is necessary to include the \(\theta^4\) term in the expansion
+of \(\theta_1^2\) so that \(\theta_1/\theta\) is accurate to order
+\(\theta^2\).  Then, from equation~\eqref{eq:crw-angles} we find
 \begin{align}
@@
 
+To find the alatude, \(\Lambda = R_{90} / R_0\), we use equation~\eqref{eq:crw-angles} at \(\theta = 90^\circ\) to write
+\begin{equation}
+  \label{eq:Lambda-from-theta-1-90}
+  \Lambda = \frac{D} {R_0} \tan \theta_{1,90} \ , 
+\end{equation}
+where \(\theta_{1,90} = \theta_1(\theta = 90^\circ)\), which, following
+equation~\eqref{eq:ancantoid-theta-theta1-implicit}, must satisfy
+\begin{equation}
+  \label{eq:theta-1-90-implicit}
+  \theta_{1,90} \cot \theta_{1,90}  = 1 - \frac{2 \beta}{k + 2} \ . 
+\end{equation}
+Combining \eqref{eq:Lambda-from-theta-1-90} and
+\eqref{eq:theta-1-90-implicit} with \eqref{eq:again-R0-over-D} yields
+\begin{equation}
+  \label{eq:Lambda-beta-xi-theta-1-90}
+  \Lambda = \frac{ \left(1 + \beta^{1/2}\right) \,\theta_{1,90}} {\beta^{1/2} \left(1 - \xi_k \beta\right)} \ ,
+\end{equation}
+where
+\begin{equation}
+  \label{eq:xi-k}
+  \xi_k = \frac{2} {k +2} \ .
+\end{equation}
+We now take the Taylor expansion of equation~\eqref{eq:theta-1-90-implicit} to find
+\begin{equation}
+  \label{eq:theta-1-90-Taylor}
+  \theta_{1,90}^2 + \tfrac{1}{15}  \theta_{1,90}^4 + \mathcal{O}(\theta_{1,90}^6)
+  = 3 \xi_k \beta \ , 
+\end{equation}
+which, if \(\theta_{1,90}\) is small, has the approximate solution
+\begin{equation}
+  \label{eq:theta-1-90-approx}
+  \theta_{1,90} \approx \left( \frac{3 \xi_k \beta} {1 + \tfrac15 \xi_k \beta} \right) \ .
+\end{equation}
+Substituting back into equation~\eqref{eq:Lambda-from-theta-1-90} yields an approximate value for the alatude of
+\begin{equation}
+  \label{eq:Lambda-approx}
+  \Lambda \approx \frac {(3 \xi_k)^{1/2} \left( 1 + \beta^{1/2} \right)}
+  { \left( 1 + \tfrac15 \xi_k \beta \right)^{1/2} \left( 1 - \xi_k \beta \right)} \ ,
+\end{equation}
+which has a relative error of order \((6 \beta / (k +2))^2\), so the approximation should be accurate for \(\beta < 0.1\).
+
 %%% Local Variables:

### 2017-11-09 papers/Paper1/sec-conic.tex
Re-do the ancantoid shape graphs

@@
 \(\theta_\infty = \pi + \thetaQ\) (note that \(\thetaQ < 0\) in this case), and
-the minimum slope angle is \(\alpha_{\mathrm{min}} = |\thetaQ|\), see
+the minimum slope angle is \(\alpha_{\mathrm{min}} = \abs{\thetaQ}\), see
 discussion following equation~\eqref{eq:thetapar}.
@@
   \caption[]{Effects of projection on quadrics of revolution:
-    variation with inclination, \(|i|\), of bow size and shape.
+    variation with inclination, \(\abs{i}\), of bow size and shape.
     Different line colors correspond to varying quadric parameter,
@@
     curvature. Vertical gray rectangles show quartiles of
-    \(|\sin i|\), which will be equally populated for an isotropic
+    \(\abs{\sin i}\), which will be equally populated for an isotropic
     distribution of orientations. (a)~Projected planitude:
@@
   \label{eq:Rc-conic}
-  R_c = \frac{b^2}{a} = a |\Q|\ ,
+  R_c = \frac{b^2}{a} = a \abs{\Q}\ ,
 \end{equation}
@@
     (b)~projected/true star-apex distance: \(R_0' / R_0\) versus
-    \(|i|\). %
+    \(\abs{i}\). %
     In (a), shading indicates different classes of quadrics:
@@
     \((\Pi', \Lambda')\) as the inclination is increased through uniform
-    intervals in \(|sin i|\).  Symbol color represents the quadric
+    intervals in \(\abs{sin i}\).  Symbol color represents the quadric
     parameter, \(\Q\), increasing from dark blue, through orange, to
@@
 increasing inclination (for true \(\Pi > 2\)), they turn around and
-increases again as \(|i|\) approaches the critical value
-\(i_{\mathrm{crit}} = 90^\circ - |\thetaQ|\).  For
-\(|i| > i_{\mathrm{crit}}\) the tangent line does not exist (see
+increases again as \(\abs{i}\) approaches the critical value
+\(i_{\mathrm{crit}} = 90^\circ - \abs{\thetaQ}\).  For
+\(\abs{i} > i_{\mathrm{crit}}\) the tangent line does not exist (see
 \S~\ref{sec:tangent-line}) because the line of sight is ``inside'' the
 asymptotic cone of the far wings (with opening half angle
-\(\alpha_{\mathrm{min}} = |\thetaQ|\)), and so no limb-brightened shell
+\(\alpha_{\mathrm{min}} = \abs{\thetaQ}\)), and so no limb-brightened shell
 would be visible.\footnote{%
@@
 star-apex separation varies with inclination.  For moderate
-inclinations, \(|i| < 30^\circ\), this depends primarily on the true
+inclinations, \(\abs{i} < 30^\circ\), this depends primarily on the true
 planitude \(\Pi\), with very little influence of the quadric parameter
-\(\Q\).  For \(\Pi > 1\), the separation increases with \(|i|\), whereas
+\(\Q\).  For \(\Pi > 1\), the separation increases with \(\abs{i}\), whereas
 for \(\Pi < 1\) it decreases slightly.  Note, however, that for cases
@@
 \(D'\), can be measured, then \(R_0'/D'\) is always an increasing
-function of \(|i|\).  For larger inclinations, \(|i| > 30^\circ\), the
+function of \(\abs{i}\).  For larger inclinations, \(\abs{i} > 30^\circ\), the
 strands for different \(\Q\) begin to separate, with hyperbolae
-showing the strongest increase of \(R_0'\) with \(|i|\).
+showing the strongest increase of \(R_0'\) with \(\abs{i}\).
 
@@
 of \((\Pi', \Lambda')\) for a sequence of 6 values of the inclination, equally
-spaced in \(\vert\sin {i}\vert\), so that each panel is equally likely for an
+spaced in \(\abs{\sin {i}}\), so that each panel is equally likely for an
 isotropic distribution of orientations.  The distribution of the true
@@
 \([0.5, 4.5]\), giving a uniformly filled square of values for
-\(|i| = 0\), which becomes increasingly distorted as \(|i|\)
+\(\abs{i} = 0\), which becomes increasingly distorted as \(\abs{i}\)
 increases.  The color scale represents \(\Q\) and the symbol size is
@@
 shows the zone of true \(\Lambda, \Pi\) for hyperboloids where the tangent
-lines still exists for that value of \(|i|\).  This becomes smaller
-and smaller as \(|i|\) increases, which explains why the hyperboloid
+lines still exists for that value of \(\abs{i}\).  This becomes smaller
+and smaller as \(\abs{i}\) increases, which explains why the hyperboloid
 zone becomes increasingly depopulated: all quadrics that lay above
 this region when \(i = 0^\circ\) will no longer be visible as bow for this
-value of \(|i|\).  Note that this figure is merely illustrative of the
+value of \(\abs{i}\).  Note that this figure is merely illustrative of the
 qualitative effects of projection, since in reality there is no

### 2017-11-09 CRW-shapes/ancantoid-shape.py

@@ -1,0 +1,52 @@
+import sys
+import numpy as np
+from matplotlib import pyplot as plt
+import matplotlib.ticker
+import seaborn as sns
+import conic_parameters
+from equation6 import Shell
+
+plotfile = sys.argv[0].replace('.py', '.pdf')
+
+sns.set_style('ticks')
+sns.set_color_codes(palette='deep')
+fig, ax = plt.subplots(figsize=(6, 5))
+
+ks = [None, 0.5, 3.0, 8.0]
+colors = 'krmb'
+betas = [0.01, 0.1, 0.5]
+lws = [2, 1.5, 1]
+theta = np.linspace(0,0.99*np.pi)
+
+for k, color in zip(ks, colors):
+    for beta, lw in zip(betas, lws):
+        if k is None:
+            shell = Shell(beta=beta, innertype="isotropic")
+            label = fr"Cantoid, $\beta = {beta:.2f}$"
+        else:
+            xi = 2.0 / (k + 2.0)
+            shell = Shell(beta=beta, innertype="anisotropic", xi=xi)
+            label = fr"Ancantoid, $k = {k:.1f}$, $\beta = {beta:.2f}$"
+
+        R = shell.radius(theta)
+        R[R < 0.0] = np.nan
+
+        ax.plot(R*np.cos(theta), R*np.sin(theta), color=color, lw=lw, label=label)
+        ax.plot(R*np.cos(theta), -R*np.sin(theta), color=color, lw=lw, label="_nolabel_")
+
+ax.axhline(0.0, color='k', ls='--')
+ax.plot([0.0, 1.0], [0.0, 0.0], 'o', color='k')
+ax.legend(ncol=1, fontsize='small', frameon=True,
+          labelspacing=0.8, loc='upper right', title='Shape')
+ax.set(
+    yscale='linear',
+    xlim=[-0.45, 1.18],
+    ylim=[-0.25, 1.05],
+    xlabel=r"$z / D$",
+    ylabel=r"$r / D$",
+)
+ax.set_aspect('equal')
+sns.despine(trim=True)
+fig.tight_layout()
+fig.savefig(plotfile)
+print(plotfile, end='')

### 2017-11-10 papers/Paper1/app-shape-parameters.tex
Re-do the ancantoid shape graphs
Finish reorganization/expansion of Appendix C

@@
-\section{Planitude and alatude of thin-shell bow shapes}
+\section{Analytic derivation of thin-shell bow shapes}
 \label{sec:thin-shell-shapes}
@@
 follow as special cases.
+
+\subsection{Planitude of ancantoids}
+\label{sec:ancantoid-planitude}
 
@@
   \label{eq:final-planitude}
+  \text{ancantoid} \quad
   \Pi = \left[ {1 - \frac{C_{k\beta}}{1+\beta^{1/2}} - \frac{1}{3}\left(1+2\beta^{1/2}\right)}
@@
 \end{equation}
+
+\subsection{Alatude of ancantoids}
+\label{sec:ancantoid-alatude}
 
@@
   \label{eq:Lambda-approx}
+  \text{ancantoid} \quad
   \Lambda \approx \frac {(3 \xi_k)^{1/2} \left( 1 + \beta^{1/2} \right)}
@@
 \end{equation}
-which has a relative error of order \((6 \beta / (k +2))^2\), so the approximation should be accurate for \(\beta < 0.1\).
+which has a relative error of order \((3 \xi_k \beta)^2\), so the
+approximation should be accurate for \(\beta < 0.1\).
 
+\subsection{Planitude and alatude of cantoids and wilkinoid}
+\label{sec:cantoid-wilkinoid-shapes}
+
+Since \(\Pi\) and \(\Lambda\) depend on only that portion of the inner wind
+emitted in the forward hemisphere, \(\theta \le 90^\circ\), the results for the
+cantoids can be found by taking \(k = 0\), in which case
+equations~(\ref{eq:C-k-beta}, \ref{eq:final-planitude}, \ref{eq:xi-k},
+\ref{eq:Lambda-approx}) yield
+\begin{gather}
+  \label{eq:cantoid-Pi-Lambda}
+  \text{cantoid} \quad
+  \begin{cases}
+    \quad \Pi &= \dfrac {5} {3 \left( 1 - \beta^{1/2} \right)}\\[12pt]
+    \quad \Lambda &= \dfrac { \sqrt 3} {\left( 1 + \tfrac15 \beta \right)^{1/2} \left( 1 - \beta^{1/2} \right)} \ .
+  \end{cases}
+\end{gather}
+The wilkinoid shape is equal to the \(\beta \to 0\) limit of the cantoid, so
+its planitude and alatude are given by:
+\begin{gather}
+  \label{eq:wilkinoid-Pi-Lambda}
+  \text{wilkinoid} \quad
+  \begin{cases}
+    \quad \Pi &= \dfrac {5} {3}\\[10pt]
+    \quad \Lambda &= \sqrt 3 \ .
+  \end{cases}
+\end{gather}
+
+\subsection{Asymptotic opening angle}
+\label{sec:asympt-open-angle}
+
+The asymptotic opening angle
+of the far wings, \(\theta_\infty\), can be found from
+equation~\eqref{eq:ancantoid-theta-theta1-implicit} for the
+ancantoids, together with the condition that
+\(\theta_\infty + \theta_{1\infty} = \pi\).  These yield the implicit equation
+\begin{equation}
+  \label{eq:anacantoid-theta-inf}
+  \theta_\infty - \left( \frac {k + 2 (1 - \beta)} {k + 2} \right) \tan \theta_\infty
+  = \pi + 2 \beta I_k(\pi/2) \ ,                                                                                                                                          
+\end{equation}
+where
+\begin{equation}
+  I_k(\pi/2) = \frac{\sqrt \pi}{4} \,
+      \frac{  \GammaFunc\left( \frac{k+1}{2} \right)} {\GammaFunc\left(\frac{k+4}{2}\right)}
+\end{equation}
+and \(\GammaFunc\) is the usual Gamma function.  This can be compared with the equivalent result obtained by \CRW{} for the cantoids:
+\begin{equation}
+  \label{eq:cantoid-theta-inf}
+  \theta_\infty - \tan \theta_\infty = \frac{\pi}{1 - \beta} \ .
+\end{equation}
+Note that, unlike the case for \(\Pi\) and \(\Lambda\),
+equation~\eqref{eq:anacantoid-theta-inf} does \emph{not} reduce to
+equation~\eqref{eq:cantoid-theta-inf} in the limit \(k \to 0\).  This is
+because, for \(\theta > 90^\circ\), the \(k = 0\) ancantoid differs from the
+cantoid since there is no wind in the backward hemisphere (see
+Figure~\ref{fig:anisotropic-arrows}).  Therefore there is less inner
+support for the far wings of the bow, and so \(\theta_\infty\) is smaller than
+in the cantoid case.  The wilkinoid result again follows from
+\(beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that
+the far wings are asymptotically parallel to the symmetry axis, as is
+the case for the paraboloid (App.~\ref{app:parabola}).  In the case of
+the wilkinoid, however, the behavior is cubic in the wings,
+\(z \sim r^3\), as opposed to quadratic as in the paraboloid.
 %%% Local Variables:

### 2017-11-10 papers/Paper1/sec-thin-shell.tex
Re-do the ancantoid shape graphs
Finish reorganization/expansion of Appendix C

@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{figs/ancantoid-shape}
+\caption{Bow shock shapes for interacting winds in the thin-shell
+  approximation: cantoids and ancantoids. Coordinates are normalized
+  by $D$, the distance between the two wind sources, which are
+  indicated by black dots on the axis.  The weaker source is at
+  \((0.0, 0.0)\) and the stronger source is at \((1.0, 0.0)\).
+  Results are shown for different values of the wind momentum ratio,
+  \(\beta\) (different line widths), and for the case where the weaker
+  wind is isotropic (black lines) or anisotropic (colored lines).}
+\label{fig:r-beta}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
+  \caption{Shapes of cantoids and ancantoids in the
+    \(\Pi\)--\(\Lambda\) plane.  Line colors correspond to different anisotropy
+    indices, and match the values if Fig.~\ref{fig:r-beta}. Circle
+    symbols mark particular \(\beta\) values: \(0, 0.01, 0.1\), from
+    largest to smallest circle.  Square symbols mark \(\beta = 0.5\), but
+    with \(\Lambda\) calculated exactly, instead of using the approximation
+    of equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
+    the result for the wilkinoid:
+    \((\Pi, \Lambda) = (\frac53, \sqrt{3})\).  Background shading indicates
+    the domains of different quadric classes: hyperboloids (white),
+    prolate spheroids (darg gray), and oblate spheroids (light gray).}
+  \label{fig:ancantoid-Pi-lambda-true}
+\end{figure}
+
 A generalization of the cantoids to the case of an
@@
 to what we call \textit{ancantoids}, which depend on an anisotropy
-index, \(k\), in addition to \(\beta\).
-
-\begin{figure}
-\includegraphics[width=\linewidth]{figs/r-beta}
-\caption{Bow shock shapes for interacting winds in the thin-shell
-  approximation. Coordinates are normalized by $D$, the distance
-  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
-  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
-  different values of the wind momentum ratio, \(\beta\), and for the
-  case where the weaker wind is isotropic (dashed lines) or an
-  anisotropic photoevaporation flow. The solid lines shows a wind with a
-  moderate degree of anisotropy $(k=0.5)$, which is expected for the proplyds.
-  And the dotted lines show a wind with extreme anisotropy degree $(k=8)$.}
-\label{fig:r-beta}
-\end{figure}
+index, \(k\), in addition to \(\beta\).  The resulting shapes are shown in
+Figure~\ref{fig:r-beta} for three different values of \(\beta\).  There is
+a general tendency for the bows to be flatter and more open with
+increasing \(\beta\), but at a given \(\beta\) it is the cantoid (black lines) that is most open
 

### 2017-11-10 papers/Paper1/app-shape-parameters.tex
Many small edits after complete read-through

@@
-\section{Analytic derivation of thin-shell bow shapes}
+\section{Analytic derivation of thin-shell bow shape parameters}
 \label{sec:thin-shell-shapes}
 
-In this appendix, we provide analytic calculations of the planitude
-(exact) and alatude (approximate) for the wilkinoid, cantoids, and
+In this appendix, we provide analytic calculations of the planitude,
+alatude, and asymptotic opening angle for the wilkinoid, cantoids, and
 ancantoids.  We first consider the most general case of the
@@
 \end{equation}
-Substituting back into equation~\eqref{eq:Lambda-from-theta-1-90} yields an approximate value for the alatude of
+Substituting back into equation~\eqref{eq:Lambda-from-theta-1-90}
+yields an approximate value for the alatude of
 \begin{equation}
@@
   \Lambda \approx \frac {(3 \xi_k)^{1/2} \left( 1 + \beta^{1/2} \right)}
-  { \left( 1 + \tfrac15 \xi_k \beta \right)^{1/2} \left( 1 - \xi_k \beta \right)} \ ,
+  { \left( 1 + \tfrac15 \xi_k \beta \right)^{1/2} \left( 1 - \xi_k \beta \right)} \ .
 \end{equation}
-which has a relative error of order \((3 \xi_k \beta)^2\), so the
-approximation should be accurate for \(\beta < 0.1\).
+This approximation is surprisingly accurate, with a relative error of
+order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).  The
+leading term in the relative error scales as \((\beta / (k + 2))^2\), so the
+approximation is even better for smaller \(\beta\) and larger \(k\).
 
@@
 \end{gather}
+The same results can also be obtained directly from
+equation~\eqref{eq:wilkinoid-R-theta}, and in the case of \(\Lambda\) this
+has already been noted by several authors \citep{Cox:2012a,
+  Meyer:2016a}.
 
@@
 \end{equation}
-Note that, unlike the case for \(\Pi\) and \(\Lambda\),
+Note that, unlike in the cases of \(\Pi\) and \(\Lambda\),
 equation~\eqref{eq:anacantoid-theta-inf} does \emph{not} reduce to
@@
 because, for \(\theta > 90^\circ\), the \(k = 0\) ancantoid differs from the
-cantoid since there is no wind in the backward hemisphere (see
+cantoid since the former has no wind in the backward hemisphere (see
 Figure~\ref{fig:anisotropic-arrows}).  Therefore there is less inner
@@
 in the cantoid case.  The wilkinoid result again follows from
-\(beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that
-the far wings are asymptotically parallel to the symmetry axis, as is
-the case for the paraboloid (App.~\ref{app:parabola}).  In the case of
-the wilkinoid, however, the behavior is cubic in the wings,
+\(\beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that the far
+wings are asymptotically parallel to the symmetry axis, as is the case
+for the paraboloid (App.~\ref{app:parabola}).  In the case of the
+wilkinoid, however, the behavior is cubic in the wings,
 \(z \sim r^3\), as opposed to quadratic as in the paraboloid.

### 2017-11-10 papers/Paper1/sec-conic.tex
Many small edits after complete read-through

@@
 of \((\Pi', \Lambda')\) for a sequence of 6 values of the inclination, equally
-spaced in \(\abs{\sin {i}}\), so that each panel is equally likely for an
-isotropic distribution of orientations.  The distribution of the true
-\(\Pi\) and \(\Lambda\) are each assumed to be uniform on the range
+spaced in \(\abs{\sin {i}}\), so that each panel is equally likely for
+an isotropic distribution of orientations.  The distribution of the
+true \(\Pi\) and \(\Lambda\) are each assumed to be uniform on the range
 \([0.5, 4.5]\), giving a uniformly filled square of values for
@@
 shows the zone of true \(\Lambda, \Pi\) for hyperboloids where the tangent
-lines still exists for that value of \(\abs{i}\).  This becomes smaller
-and smaller as \(\abs{i}\) increases, which explains why the hyperboloid
-zone becomes increasingly depopulated: all quadrics that lay above
-this region when \(i = 0^\circ\) will no longer be visible as bow for this
-value of \(\abs{i}\).  Note that this figure is merely illustrative of the
-qualitative effects of projection, since in reality there is no
-particular reason to expect a uniform distribution in \(\Pi\) and \(\Lambda\).
+lines still exists for that value of \(\abs{i}\).  This becomes
+smaller and smaller as \(\abs{i}\) increases, which explains why the
+hyperboloid zone becomes increasingly depopulated: all quadrics that
+lay above this region when \(i = 0^\circ\) will no longer be visible as a
+bow for this value of \(\abs{i}\).  Note that this figure is merely
+illustrative of the qualitative effects of projection, since in
+reality there is no particular reason to expect a uniform distribution
+in true \(\Pi\) and \(\Lambda\).
 

### 2017-11-10 papers/Paper1/sec-thin-shell.tex
Many small edits after complete read-through

@@
 a general tendency for the bows to be flatter and more open with
-increasing \(\beta\), but at a given \(\beta\) it is the cantoid (black lines) that is most open
+increasing \(\beta\), while at a given \(\beta\) it is the cantoid (black
+lines) that is most open
 

### 2017-11-11 papers/Paper1/sec-thin-shell.tex
Improve ancantoid figures

@@
 
-\section{Thin-shell hydrodynamic bow shock models}
+\section{Thin-shell bow shock models}
 \label{sec:crw-scenario}
@@
 For the wind--wind case, a family of solutions are found that depend on
-the value of \(\beta\), the wind momentum ratio, see
-Figure~\ref{fig:crw-schema}, equations~(\ref{eq:stagnation-radius},
-\ref{eq:beta-definition}), and surrounding discussion in
-\S~\ref{sec:intro}.  We propose that these shapes be called
-\textit{cantoids}.  The exact solution for the cantoid shapes
-(eqs.~[23, 24] of \CRW{}) is only obtainable in implicit form, but an
-approximate explicit solution (eq.~[26] of \CRW{}) is very accurate
-for \(\beta \le 0.1\).  The wilkinoid shape corresponds to the
-\(\beta \to 0\) limit of the cantoids.  Note that \CRW{}'s \(z\) and
-\(r\) axes, which we use in our Figure~\ref{fig:crw-schema},
-correspond respectively to the \(x\) and \(y\) axes in
+the value of \(\beta\), the wind momentum ratio,\footnote{%
+  By always placing the weaker of the two winds at the origin, it is
+  only necessary to consider \(\beta \le 1\).  } %
+see Figure~\ref{fig:crw-schema},
+equations~(\ref{eq:stagnation-radius}, \ref{eq:beta-definition}), and
+surrounding discussion in \S~\ref{sec:intro}.  We propose that these
+shapes be called \textit{cantoids}.  The exact solution for the
+cantoid shapes (eqs.~[23, 24] of \CRW{}) is only obtainable in
+implicit form, but an approximate explicit solution (eq.~[26] of
+\CRW{}) is very accurate for \(\beta \le 0.1\).  The wilkinoid shape
+corresponds to the \(\beta \to 0\) limit of the cantoids.  Note that \CRW{}
+employ cylindrical polar coordinates, \(z\) and \(r\), see our
+Figure~\ref{fig:crw-schema}, and we follow this usage for the
+thin-shell models discussed in this section.  \CRW{}'s \(z\) axis
+corresponds to the cartesian \(x\) axis used in
 sections~\ref{sec:projection} and \ref{sec:conic} of the current
-paper.  By always placing the weaker of the two winds at the origin,
-it is only necessary to consider \(\beta \le 1\).
+paper, while the \(r\) axis corresponds to \(y\) when \(\phi = 0\).
+
+A generalization of the cantoids to the case of an
+anisotropic\footnote{Note that the wind anisotropy axis must be
+  aligned with the star--star axis to maintain cylindrical symmetry.}
+inner wind is developed next, giving rise
+to what we call \textit{ancantoids}, which depend on an anisotropy
+index, \(k\), in addition to \(\beta\).
+
+\subsection{Bow shocks from anisotropic wind--wind interactions}
+\label{sec:ancantoid}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/anisotropic-arrows}
+  \caption[]{Schematic diagram of wind flow patterns in isotropic and
+    non-isotropic cases for different values of the anisotropy index,
+    \(k\).  Arrow length represents the wind momentum loss rate per
+    solid angle.}
+  \label{fig:anisotropic-arrows}
+\end{figure}
+
+We wish to generalize the results of \citet[\CRW{}]{Canto:1996} to the
+case where the inner wind is no longer isotropic, but instead has a
+density that falls off with angle, \(\theta\), away from the symmetry axis.
+Specifically, at some fiducial spherical radius, \(R_0\), from the
+origin, the wind mass density is given by
+\begin{equation}
+  \label{eq:ancantoid-density}
+  \rho(R_0, \theta) =
+  \begin{cases}
+    \rho_0 \cos^k \theta & \text{for \(\theta \le 90^\circ\)} \\
+    0 & \text{for \(\theta > 90^\circ\)}
+  \end{cases}
+  \ ,
+\end{equation}
+where \(\rho_0\) is the density on the symmetry axis and \(k \ge 0\) is an
+\textit{anisotropy index}.  The wind velocity is still assumed to be
+constant and the wind streamlines to be radial, so the radial
+variation of density at each angle is
+\(\rho(R, \theta) = \rho(R_0, \theta)\, (R/R_0)^{-2}\) and the wind mass loss rate and
+momentum loss rate per solid angle both have the same \(\cos^k\theta\)
+dependence as the density.  Examples are shown in
+Figure~\ref{fig:anisotropic-arrows} for a variety of different values
+of \(k\).  As \(k\) increases, the wind becomes increasingly jet-like.
+
+Our primary motivation for considering such an anisotropic wind is the
+case of the Orion Nebula proplyds and their interaction with the
+stellar wind of the massive star \thC{}
+\citep{Garcia-Arredondo:2001a}.  The inner ``wind'' in this case is
+the transonic photoevaporation flow away from a roughly hemispherical
+ionization front, where photoionization equilibrium, together with
+monodirectional illumination of the front, implies that the ionized
+hydrogen density, \(n\), satisfies \(n^2 \propto \cos \theta\), which is
+equivalent to \(k = 0.5\) in equation~\eqref{eq:ancantoid-density}.
+Since the primary source of ionizing photons is the same star that is
+the source of the outer wind, it is natural that the inner wind's axis
+should be aligned with the star--star axis in this case.  For other
+potential causes of wind anisotropy (for instance, bipolar flow from
+an accretion disk), there is no particular reason for the axes to be
+aligned, so cylindrical symmetry would be broken.  Nevertheless, we
+calculate results for general \(k\) with aligned axes, so as to
+provide a richer variety of cylindrically symmetric bow shock shapes
+than are seen in the cantoids.
+
+The general solution for the bow shock shape, \(R(\theta)\), in the \CRW{}
+formalism is
+\begin{equation}
+  R(\theta) = \frac {\dot{J}_{\w} + \dot{J}_{\w{}1}}
+  {\left(\dot{\Pi}_{\w{}r}+\dot{\Pi}_{\w{}r1}\right)\cos\theta
+    - \left(\dot{\Pi}_{\w{}z}+\dot{\Pi}_{\w{}z1}\right)\sin\theta}
+  \label{eq:Rmom}
+\end{equation}
+where \(\dot{\Pi}_{\w{}r}\), \(\dot{\Pi}_{\w{}z}\), \(\dot{J}_{\w}\) are
+the accumulated linear radial momentum, linear axial momentum, and
+angular momentum, respectively, due to the inner wind emitted between
+the axis and \(\theta\). The equivalent quantities for the outer wind have
+subscripts appended with ``1''.  The inner wind momenta for our
+anisotropic case (replacing \CRW{}'s eqs.~[9, 10]) are:
+\begin{gather}
+  \label{eq:ancantoid-momenta}
+  \begin{aligned}
+    \dot{\Pi}_{\w{}z} &= \frac{k + 1}{2(k+2)}\, \dot{M}_{\w}^0 V_{\w}
+    \max\left[\bigl(1- \cos^{k+2} \theta\bigr), 1 \right] \\
+    \dot{\Pi}_{\w{}r} &= (k + 1)\, \dot{M}^0_{\w} V_{\w}\, I_k (\theta) 
+  \end{aligned}
+\end{gather}
+where
+\begin{equation}
+  \label{eq:ancantoid-mass-loss}
+  \dot{M}^0_{\w} = \frac{2 \pi} {k + 1} r_0^2 \rho_0 V_{\w}
+\end{equation}
+is the total mass-loss rate of the inner wind. The integral
+\begin{equation}
+  \label{eq:ancantoid-I-integral}
+  I_k(\theta) = \int^{\max(\theta, \pi/2)}_0 \cos^k \theta \sin^2\theta \,d\theta 
+\end{equation}
+has an analytic solution in terms of the hypergeometric function,
+\({}_2 F_1(-\tfrac12; \tfrac{1+k}2; \tfrac{3+k}2; \cos^2 \theta)\), but is
+more straightforwardly calculated by numerical quadrature.  The
+angular momentum of the inner wind about the origin is
+\(\dot{J}_{\w} = 0\) because it is purely radial.  The outer wind
+momenta are unchanged from the \CRW{} case, but are given here for
+completeness:
+\begin{gather}
+  \label{eq:ancantoid-momenta-outer}
+  \begin{aligned}
+    \dot{\Pi}_{\w{}z1} & =
+    -\frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\sin^2\theta_1\\
+    \dot{\Pi}_{\w{}r1} & =
+    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
+    \dot{J}_{\w{}1} & =
+    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \ .
+  \end{aligned} 
+\end{gather}
+
+We define \(\beta\) in this case as the momentum ratio \emph{on the symmetry axis}, which means that 
+\begin{equation}
+  \label{eq:ancantoid-momentum-ratio}
+  \dot{M}^0_{\w{}1}V_{\w{}1} = 2 (k + 1)\, \beta\, \dot{M}^0_{\w} V_{\w} \ . 
+\end{equation}
+Substituting
+equations~(\ref{eq:ancantoid-momenta}--\ref{eq:ancantoid-momentum-ratio})
+into equation~\eqref{eq:Rmom} and making use of the geometric relation
+between the interior angles of the triangle shown in
+Figure~\ref{fig:crw-schema}:
+\begin{equation}
+  \label{eq:crw-angles}
+  R \sin(\theta + \theta_1) = D \sin \theta_1 \ , 
+\end{equation}
+yields
+\begin{equation}
+  \label{eq:ancantoid-theta-theta1-implicit}
+  \theta_1 \cot \theta_1 = 1 +
+  2 \beta \left(
+    I_k(\theta) \cot \theta
+    - \frac{1 - \cos^{k+2} \theta} {k + 2} \right)   \ , 
+\end{equation}
+which is the generalization of \CRW{}'s equation~(24) to the
+anisotropic case.  Equation~\eqref{eq:ancantoid-theta-theta1-implicit}
+is solved numerically to give \(\theta_1(\theta)\), which is then combined with
+equations~(\ref{eq:crw-angles}) and (\ref{eq:stagnation-radius}) to
+give the dimensionless bow shape, \(R(\theta; \beta, k)/R_0\), where we now
+explicitly indicate the dependence of the solution on two parameters:
+axial momentum ratio, \(\beta\), and anisotropy index, \(k\).  We refer to
+the resultant bow shapes as \textit{ancantoids}.
+
+%The most notable scenarios, since they have astrophysical relevance are the following:
+%$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
+%is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "quadrics-bowshock"
+%%% End:
 
@@
 
-A generalization of the cantoids to the case of an
-anisotropic\footnote{Note that the wind anisotropy axis must be
-  aligned with the star--star axis to maintain cylindrical symmetry.}
-inner wind is developed in Appendix~\ref{app:ancantoid}, giving rise
-to what we call \textit{ancantoids}, which depend on an anisotropy
-index, \(k\), in addition to \(\beta\).  The resulting shapes are shown in
+\subsection{True shapes of cantoids and ancantoids}
+\label{sec:true-cantoids-ancantoids}
+
+The resulting shapes are shown in
 Figure~\ref{fig:r-beta} for three different values of \(\beta\).  There is
@@
 
-\subsection{Characteristic Radii}
-$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
-%Here goes a little introduction
-For the rest of the radii we need a relation between $\theta$ and $\theta_1$ as follows:
-
-\begin{align}
-\theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
-\label{eq:th1th}
-\end{align}
-
-Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
-We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
-which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:
-
-\begin{align}
-\tilde{R}_{90} = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
-\label{eq:B}
-\end{align}
-
-Now, the solution for $R_c$ is explained in appendix \ref{app:rc-analytic},
-which lead us to derive the radius of curvature at the symmetry axis:
-
-\begin{align}
-R_c &= R_0\left(1-2\gamma\right)^{-1} \label{eq:Rcurv} \\
-\mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
-\end{align}
-
-Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
-conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})
-
-\begin{align}
-\tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
-\label{eq:thc-CRW}
-\end{align}
-
 \begin{figure}
-\begin{tabular}{c}
-\includegraphics[width=\linewidth]{figs/AB-beta-log} \\
-\includegraphics[width=\linewidth]{figs/thc-beta-log}
-\end{tabular}
-\caption{Top: Characteristic radii, $\tilde{R}_c = R_c/R_0$ (solid lines) and $\tilde{R}_{90}
-  = R_{90}/R_0$ (dashed lines)
-  vs $\beta$, calculated from quadric fits to the generalized CRW
-  solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
-  angle $\theta_c$ vs $\beta$ for the bow 
-  shock head (solid lines) and the bow shock tail (dashed lines).}
-\label{fig:rad-beta}
+  \centering
+  \includegraphics[width=\linewidth]{figs/ancantoid-angles}
+  \caption{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
+    cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
+    \((\Pi, \Lambda)\), which is representative of the shape of the head,
+    while dashed lines show \(\theta_{\Q}\) calculated from
+    \(\theta_\infty\), which is representative of the tail.  Dot-dashed line
+    shows the result for cantoids, which differ from the \(k=0\)
+    ancantoids in \(\theta_\infty\), but not in \((\Pi, \Lambda)\). Gray shading and
+    line colors have the same meaning as in
+    Fig.~\ref{fig:ancantoid-Pi-lambda-true}. }
+  \label{fig:ancantoid-angles}
 \end{figure}
 
-% Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
-%being $R_0$ the
-%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
+% \subsection{Characteristic Radii}
+% $R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
+% %Here goes a little introduction
+% For the rest of the radii we need a relation between $\theta$ and $\theta_1$ as follows:
 
-With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
-momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
+% \begin{align}
+% \theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
+% \label{eq:th1th}
+% \end{align}
 
-\subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}
+% Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
+% We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
+% which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:
 
-This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:
+% \begin{align}
+% \tilde{R}_{90} = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
+% \label{eq:B}
+% \end{align}
 
-\begin{align}
-  R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
-\end{align}
-Where:
-\begin{align}
-  R_0 = \left(\frac{\dot{M}_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
-\end{align}
-And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
-The characteristic radii are given by:
-\begin{align}
-  \tilde{R}_{90} &= \sqrt{3} \\
-  \tilde{R}_c &= \frac{5}{3}
-\end{align}
-The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}
+% Now, the solution for $R_c$ is explained in appendix \ref{app:rc-analytic},
+% which lead us to derive the radius of curvature at the symmetry axis:
 
-\subsection{Fits to the tail}
-\label{sec:fits-tail}
+% \begin{align}
+% R_c &= R_0\left(1-2\gamma\right)^{-1} \label{eq:Rcurv} \\
+% \mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
+% \end{align}
 
-In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with
+% Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
+% conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})
 
-We therefore 
-We carry out three-level nested fits to determine the
+% \begin{align}
+% \tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
+% \label{eq:thc-CRW}
+% \end{align}
 
-For the hyperbola ``center''
-\begin{multline}
-  \label{eq:tail-analytic-x0}
-  x_{0,\mathrm{t}} = 0.7 \beta^{-0.55} \biggl[
-    C_3 \bigl(\log_{10}\beta\bigr)^3 + C_2 \bigl(\log_{10}\beta\bigr)^2 
-  \\ + C_1 \log_{10}\beta + C_0
-  \biggr]
-\end{multline}
-\begin{equation}
-  \label{eq:tail-analytic-x0-minus-a}
-  (x_{0,\mathrm{t}} - a_{\mathrm{t}}) = D_2 (\log_{10}\beta)^2 + D_1 \log_{10}\beta + D_0
-\end{equation}
-where
-\begin{alignat}{2}
-  \label{eq:tail-analytic-coeffs-c}
-  C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
-  \label{eq:tail-analytic-coeffs-d}
-  D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\}
-\end{alignat}
+% \begin{figure}
+% \begin{tabular}{c}
+% \includegraphics[width=\linewidth]{figs/AB-beta-log} \\
+% \includegraphics[width=\linewidth]{figs/thc-beta-log}
+% \end{tabular}
+% \caption{Top: Characteristic radii, $\tilde{R}_c = R_c/R_0$ (solid lines) and $\tilde{R}_{90}
+%   = R_{90}/R_0$ (dashed lines)
+%   vs $\beta$, calculated from quadric fits to the generalized CRW
+%   solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
+%   angle $\theta_c$ vs $\beta$ for the bow 
+%   shock head (solid lines) and the bow shock tail (dashed lines).}
+% \label{fig:rad-beta}
+% \end{figure}
 
-% \newcommand\iso{\ensuremath{^{\mathrm{iso}}}}
+% % Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
+% %being $R_0$ the
+% %easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).
 
-% \begin{table}
-%   \caption{Coefficients for hyperbola fit to bowshock tails}
-%   \label{tab:tail-fit-coeffs}
-%   \renewcommand\arraystretch{1.2}
-%   \setlength\tabcolsep{0.5\tabcolsep}
-%   \begin{tabular}{@{}llll@{}}
-%     \toprule
-%     Equation~(\ref{eq:tail-analytic-x0}) & 
-%     \multicolumn{3}{l}{
-%     Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
-%     } \\ \midrule
-%     \( C\iso_0 = +1.3195     \)    
-%     & \( c_{0,0} = +2.0758   \)  
-%     & \( c_{1,0} = -0.2309   \)  
-%     & \( c_{2,0} = -0.2532   \)\\
-%       \( C\iso_1 = +0.4229     \)    
-%     & \( c_{0,1} = +0.9571   \)  
-%     & \( c_{1,1} = -0.1530   \)  
-%     & \( c_{2,1} = -0.2487   \)\\
-%       \( C\iso_2 = +0.1092     \)    
-%     & \( c_{0,2} = +0.2528   \)  
-%     & \( c_{1,2} = -0.0360   \)  
-%     & \( c_{2,2} = -0.0794   \)\\
-%       \( C\iso_3 = +0.0051     \)    
-%     & \( c_{0,3} = +0.0171   \)  
-%     & \( c_{1,3} = -0.0010   \)  
-%     & \( c_{2,3} = -0.0095   \)\\ \midrule
-%     Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
-%     \multicolumn{3}{l}{
-%     Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
-%     } \\ \midrule
-%     \( D\iso_0 = +0.7962   \)    
-%     & \( d_{0,0} = +0.8516 \)  
-%     & \( d_{1,0} = -0.0907 \)  
-%     & \( d_{2,0} = -0.2002 \)\\
-%       \( D\iso_1 = -0.2363   \)    
-%     & \( d_{0,1} = -0.7620 \)  
-%     & \( d_{1,1} = +0.1411 \)  
-%     & \( d_{2,1} = -0.0295 \)\\
-%       \( D\iso_2 = -0.0126   \)    
-%     & \( d_{0,2} = -0.0683 \)  
-%     & \( d_{1,2} = +0.0390 \)  
-%     & \( d_{2,2} = -0.0236 \)\\
-%     \bottomrule
-%   \end{tabular}
-% \end{table}
+% With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
+% momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.
+
+% \subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}
+
+% This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:
+
+% \begin{align}
+%   R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
+% \end{align}
+% Where:
+% \begin{align}
+%   R_0 = \left(\frac{\dot{M}_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
+% \end{align}
+% And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
+% The characteristic radii are given by:
+% \begin{align}
+%   \tilde{R}_{90} &= \sqrt{3} \\
+%   \tilde{R}_c &= \frac{5}{3}
+% \end{align}
+% The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}
+
+% \subsection{Fits to the tail}
+% \label{sec:fits-tail}
+
+% In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with
+
+% We therefore 
+% We carry out three-level nested fits to determine the
+
+% For the hyperbola ``center''
+% \begin{multline}
+%   \label{eq:tail-analytic-x0}
+%   x_{0,\mathrm{t}} = 0.7 \beta^{-0.55} \biggl[
+%     C_3 \bigl(\log_{10}\beta\bigr)^3 + C_2 \bigl(\log_{10}\beta\bigr)^2 
+%   \\ + C_1 \log_{10}\beta + C_0
+%   \biggr]
+% \end{multline}
+% \begin{equation}
+%   \label{eq:tail-analytic-x0-minus-a}
+%   (x_{0,\mathrm{t}} - a_{\mathrm{t}}) = D_2 (\log_{10}\beta)^2 + D_1 \log_{10}\beta + D_0
+% \end{equation}
+% where
+% \begin{alignat}{2}
+%   \label{eq:tail-analytic-coeffs-c}
+%   C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
+%   \label{eq:tail-analytic-coeffs-d}
+%   D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\}
+% \end{alignat}
+
+% % \newcommand\iso{\ensuremath{^{\mathrm{iso}}}}
+
+% % \begin{table}
+% %   \caption{Coefficients for hyperbola fit to bowshock tails}
+% %   \label{tab:tail-fit-coeffs}
+% %   \renewcommand\arraystretch{1.2}
+% %   \setlength\tabcolsep{0.5\tabcolsep}
+% %   \begin{tabular}{@{}llll@{}}
+% %     \toprule
+% %     Equation~(\ref{eq:tail-analytic-x0}) & 
+% %     \multicolumn{3}{l}{
+% %     Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
+% %     } \\ \midrule
+% %     \( C\iso_0 = +1.3195     \)    
+% %     & \( c_{0,0} = +2.0758   \)  
+% %     & \( c_{1,0} = -0.2309   \)  
+% %     & \( c_{2,0} = -0.2532   \)\\
+% %       \( C\iso_1 = +0.4229     \)    
+% %     & \( c_{0,1} = +0.9571   \)  
+% %     & \( c_{1,1} = -0.1530   \)  
+% %     & \( c_{2,1} = -0.2487   \)\\
+% %       \( C\iso_2 = +0.1092     \)    
+% %     & \( c_{0,2} = +0.2528   \)  
+% %     & \( c_{1,2} = -0.0360   \)  
+% %     & \( c_{2,2} = -0.0794   \)\\
+% %       \( C\iso_3 = +0.0051     \)    
+% %     & \( c_{0,3} = +0.0171   \)  
+% %     & \( c_{1,3} = -0.0010   \)  
+% %     & \( c_{2,3} = -0.0095   \)\\ \midrule
+% %     Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
+% %     \multicolumn{3}{l}{
+% %     Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
+% %     } \\ \midrule
+% %     \( D\iso_0 = +0.7962   \)    
+% %     & \( d_{0,0} = +0.8516 \)  
+% %     & \( d_{1,0} = -0.0907 \)  
+% %     & \( d_{2,0} = -0.2002 \)\\
+% %       \( D\iso_1 = -0.2363   \)    
+% %     & \( d_{0,1} = -0.7620 \)  
+% %     & \( d_{1,1} = +0.1411 \)  
+% %     & \( d_{2,1} = -0.0295 \)\\
+% %       \( D\iso_2 = -0.0126   \)    
+% %     & \( d_{0,2} = -0.0683 \)  
+% %     & \( d_{1,2} = +0.0390 \)  
+% %     & \( d_{2,2} = -0.0236 \)\\
+% %     \bottomrule
+% %   \end{tabular}
+% % \end{table}
+
+% % \begin{figure*}
+% %   \centering
+% %   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
+% %   \caption{Double quadric fits to thin shell
+% %     solutions.}
+% %   \label{fig:head-tail}
+% % \end{figure*}
+
+% % \begin{figure}
+% %   \centering
+% %   \includegraphics[width=\linewidth]{figs/two-quadric-th90-vs-i}
+% %   \caption{Variation with inclination of the body-frame polar angle
+% %     \(\theta_{90}\) that corresponds to the projected perpendicular radius
+% %     \(R’_{90}\).  Line colors and thicknesses represent different
+% %     quadrics of revolution, as in
+% %     Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
+% %     important because the quadric fits to the bow shock shape must be
+% %     accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
+% %     for \(R’_{90}\).}
+% %   \label{fig:projected-th90}
+% % \end{figure}
 
@@
 %   \centering
-%   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
-%   \caption{Double quadric fits to thin shell
-%     solutions.}
-%   \label{fig:head-tail}
+%   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
+%   \caption[]{Residuals of double quadric fits to thin shell solutions.
+%     Residuals are expressed as the fractional error in the
+%     complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
+%     the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
+%   \label{fig:head-tail-residuals}
 % \end{figure*}
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=\linewidth]{figs/two-quadric-th90-vs-i}
-%   \caption{Variation with inclination of the body-frame polar angle
-%     \(\theta_{90}\) that corresponds to the projected perpendicular radius
-%     \(R’_{90}\).  Line colors and thicknesses represent different
-%     quadrics of revolution, as in
-%     Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
-%     important because the quadric fits to the bow shock shape must be
-%     accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
-%     for \(R’_{90}\).}
-%   \label{fig:projected-th90}
-% \end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
-  \caption[]{Residuals of double quadric fits to thin shell solutions.
-    Residuals are expressed as the fractional error in the
-    complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
-    the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
-  \label{fig:head-tail-residuals}
-\end{figure*}
-
-\subsection{Projection effects in the thin shell model}
-\label{sec:proj-effects-thin}
+% \subsection{Projection effects in the thin shell model}
+% \label{sec:proj-effects-thin}
 

### 2017-11-11 CRW-shapes/ancantoid-Pi-Lambda-true.py

@@ -9,7 +9,7 @@ plotfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
 sns.set_color_codes(palette='deep')
-fig, ax = plt.subplots(figsize=(5, 5))
+fig, ax = plt.subplots(figsize=(4, 4))
 
 Rc_grid = np.linspace(0.0, 10.0, 2000)
 R90_T0_grid = np.sqrt(2*Rc_grid)
@@ -31,6 +31,7 @@ labels = ["Cantoid"] + [f"Ancantoid, $k = {k:.1f}$" for k in ks[1:]]
 bbetas = [1e-8, 0.01, 0.1]
 mss = [6, 4, 3]
 colors = 'krmb'
+ax.plot(5./3., np.sqrt(3.0), '+', color='0.8', mew=2, ms=13)
 ax.plot(5./3., np.sqrt(3.0), '+', color='white', ms=12)
 for k, color, label in zip(ks, colors, labels):
     xi = 2.0 / (k + 2.0)

### 2017-11-11 CRW-shapes/ancantoid-angles.py

@@ -21,7 +21,7 @@ plotfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
 sns.set_color_codes(palette='deep')
-fig, ax = plt.subplots(figsize=(6, 5))
+fig, ax = plt.subplots(figsize=(4, 5))
 
 ks = [0.0, 0.5, 3.0, 8.0]
 colors = 'krmb'
@@ -59,7 +59,7 @@ thct_crw = np.degrees(-theta_tail(beta, None, f=conic_parameters.finf_CRW))
 ax.plot(beta, thct_crw, linestyle="-.", color="k", label="_nolabel_")
 
 i0 = len(beta)//2
-ax.annotate("Cantoid", xy=(beta[i0], thct_crw[i0]),
+ax.annotate("Cantoids", xy=(beta[i0], thct_crw[i0]),
             xytext=(-30, -30), textcoords='offset points',
             arrowprops=dict(arrowstyle="->", connectionstyle="arc3,rad=.2"))
 
@@ -71,14 +71,14 @@ ellipse_tail = Ellipse(xy_tail, 1e-4, 20, **ellipse_props)
 ax.add_patch(ellipse_head)
 ax.add_patch(ellipse_tail)
 ax.annotate(r"$\theta_{\mathcal{Q}}$ from $\Pi$, $\Lambda$", xy=xy_head,
-            xytext=(30, 30), textcoords='offset points',
+            xytext=(15, 30), textcoords='offset points',
             arrowprops=dict(arrowstyle="simple,tail_width=0.1",
                             fc="0.2", ec="none",
                             patchB=ellipse_head, shrinkB=17,
                             connectionstyle="angle3,angleA=-10,angleB=-90"),
 )
 ax.annotate(r"$\theta_{\mathcal{Q}}$ from $\theta_\infty$", xy=xy_tail,
-            xytext=(20, -40), textcoords='offset points',
+            xytext=(10, -40), textcoords='offset points',
             arrowprops=dict(arrowstyle="simple,tail_width=0.1",
                             fc="0.2", ec="none",
                             patchB=ellipse_tail, shrinkB=17,

### 2017-11-11 CRW-shapes/ancantoid-shape.py

@@ -10,40 +10,52 @@ plotfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
 sns.set_color_codes(palette='deep')
-fig, ax = plt.subplots(figsize=(6, 5))
+fig, ax = plt.subplots(figsize=(4, 5))
 
-ks = [None, 0.5, 3.0, 8.0]
-colors = 'krmb'
+ks = [None, 0.0, 0.5, 3.0, 8.0]
+colors = 'kkrmb'
+linestyles = ['--'] + ['-']*4
 betas = [0.01, 0.1, 0.5]
-lws = [2, 1.5, 1]
+lws = [2.0, 1.5, 1.0]
 theta = np.linspace(0,0.99*np.pi)
 
-for k, color in zip(ks, colors):
+for k, color, ls in zip(ks, colors, linestyles):
     for beta, lw in zip(betas, lws):
         if k is None:
             shell = Shell(beta=beta, innertype="isotropic")
-            label = fr"Cantoid, $\beta = {beta:.2f}$"
+            label = fr"Cantoid"
         else:
             xi = 2.0 / (k + 2.0)
             shell = Shell(beta=beta, innertype="anisotropic", xi=xi)
-            label = fr"Ancantoid, $k = {k:.1f}$, $\beta = {beta:.2f}$"
+            label = fr"Ancantoid, $k = {k:.1f}$"
+        if lw < 2.0:
+            label = "_nolabel_"
 
         R = shell.radius(theta)
         R[R < 0.0] = np.nan
 
-        ax.plot(R*np.cos(theta), R*np.sin(theta), color=color, lw=lw, label=label)
-        ax.plot(R*np.cos(theta), -R*np.sin(theta), color=color, lw=lw, label="_nolabel_")
+        ax.plot(R*np.cos(theta), R*np.sin(theta),
+                ls=ls, color=color, lw=lw, label=label)
+        ax.plot(R*np.cos(theta), -R*np.sin(theta),
+                ls=ls, color=color, lw=lw, label="_nolabel_")
 
-ax.axhline(0.0, color='k', ls='--')
+ax.axhline(0.0, color='k', ls=':')
+ax.axvline(0.0, color='k', ls=':')
 ax.plot([0.0, 1.0], [0.0, 0.0], 'o', color='k')
+
[…]

### 2017-11-11 papers/Paper1/sec-thin-shell.tex
Start to describe Figs 13, 14 on true ancantoid shapes

@@
 
-The resulting shapes are shown in
-Figure~\ref{fig:r-beta} for three different values of \(\beta\).  There is
-a general tendency for the bows to be flatter and more open with
-increasing \(\beta\), while at a given \(\beta\) it is the cantoid (black
-lines) that is most open
+The shapes of the ancantoid bow shocks are shown in
+Figure~\ref{fig:r-beta} for three different values of \(\beta\), and are
+compared with the \CRW{} results for cantoids (dashed curves).  The
+location of these shapes in the planitude--alatude plane is shown in
+Figure~\ref{fig:ancantoid-Pi-lambda-true}, where the gray background
+shading indicates the zones of different quadric classes, as in
+\S~\ref{sec:conic}, Figures~\ref{fig:quadric-projection-continued}
+and~\ref{fig:projected-R90-Rc-snapshots}.  The \(k=0\) ancantoid is
+identical to the cantoid for \(\theta \le 90^\circ\) (\(z > 0\)), but is slightly
+more swept back in the far wings.\footnote{%
+  Due to the discontinuity in the inner wind density at
+  \(theta = 90^\circ\) (see Fig.~\ref{fig:anisotropic-arrows}), there is a
+  discontinuity in the second derivative of the bow shape.} %
+Since the true planitude and alatude depend on \(R(\theta)\) only in the
+range \(\theta = [0, 90^\circ]\), the cantoid and the \(k = 0\) ancantoid
+behave identically in Figure~\ref{fig:ancantoid-Pi-lambda-true}.
+
+There is a general tendency for the bows to be flatter and more open
+with increasing \(\beta\) and decreasing \(k\), with the cantoid being
+most open at a given \(\beta\).  All the models cluster close to the
+diagonal \(\Lambda \simeq \Pi\) in the planitude--alatude plane, but with a tendency
+for \(\Lambda > \Pi\) at higher anisotropy.  There is therefore a degeneracy
+between \(\beta\) and \(k\) for higher values of \(\beta\).  The wilkinoid
+shape, which corresponds to the \(\beta \to 0\) limit of the cantoids is
+marked by a white plus symbol in
+Figure~\ref{fig:ancantoid-Pi-lambda-true}, which lies in the prolate
+ellipsoid region of the plane.
 

### 2017-11-11 papers/Paper1/sec-conic.tex
Finish sec 5.2 on true shapes of cantoids and ancantoids

@@
 Alternatively, one can define a \textit{quadric angle}:
-\(\thetaQ = \sigma \tan^{-1} (b/a)\), which is marked in
-Figure~\ref{fig:conics}.  In the case of hyperboloids, the asymptotic
-opening angle of the wings (\S~\ref{sec:plan-alat-bow} and
-Fig.~\ref{fig:characteristic-radii}) is
-\(\theta_\infty = \pi + \thetaQ\) (note that \(\thetaQ < 0\) in this case), and
+\begin{equation}
+  \label{eq:thetaQ}
+  \thetaQ = \sigma \tan^{-1} (b/a) \ ,
+\end{equation}
+which is marked in Figure~\ref{fig:conics}.  In the case of
+hyperboloids, the asymptotic opening angle of the wings
+(\S~\ref{sec:plan-alat-bow} and Fig.~\ref{fig:characteristic-radii})
+is \(\theta_\infty = \pi + \thetaQ\) (note that \(\thetaQ < 0\) in this case), and
 the minimum slope angle is \(\alpha_{\mathrm{min}} = \abs{\thetaQ}\), see

### 2017-11-11 papers/Paper1/sec-thin-shell.tex
Finish sec 5.2 on true shapes of cantoids and ancantoids

@@
   \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
-  \caption{Shapes of cantoids and ancantoids in the
-    \(\Pi\)--\(\Lambda\) plane.  Line colors correspond to different anisotropy
-    indices, and match the values if Fig.~\ref{fig:r-beta}. Circle
-    symbols mark particular \(\beta\) values: \(0, 0.01, 0.1\), from
-    largest to smallest circle.  Square symbols mark \(\beta = 0.5\), but
-    with \(\Lambda\) calculated exactly, instead of using the approximation
-    of equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
+  \caption{True shapes of cantoids and ancantoids in the
+    \(\Pi\)--\(\Lambda\) plane, calculated according to results of
+    App.~\ref{sec:thin-shell-shapes}.  For each line, \(\beta\) varies
+    over the range \([0, 1]\) from lower left to upper right (although
+    the black and red lines are truncated on the upper right), and
+    line colors correspond to different anisotropy indices, matching
+    those used in Fig.~\ref{fig:r-beta}. Circle symbols mark
+    particular \(\beta\) values: \(0, 0.01, 0.1\), from largest to
+    smallest circle.  Square symbols mark \(\beta = 0.5\), but with
+    \(\Lambda\) calculated exactly, instead of using the approximation of
+    equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
     the result for the wilkinoid:
@@
     the domains of different quadric classes: hyperboloids (white),
-    prolate spheroids (darg gray), and oblate spheroids (light gray).}
+    prolate spheroids (dark gray), and oblate spheroids (light gray).}
   \label{fig:ancantoid-Pi-lambda-true}
@@
 \S~\ref{sec:conic}, Figures~\ref{fig:quadric-projection-continued}
-and~\ref{fig:projected-R90-Rc-snapshots}.  The \(k=0\) ancantoid is
-identical to the cantoid for \(\theta \le 90^\circ\) (\(z > 0\)), but is slightly
+and~\ref{fig:projected-R90-Rc-snapshots}.  Values of \(\Pi\) and
+\(\Lambda\) are calculated via the analytic expressions derived in
+Appendix~\ref{sec:ancantoid-planitude} and
+\ref{sec:ancantoid-alatude}, respectively, which are only approximate
+in the case of \(\Lambda\).  However, the filled square symbols show the
+exact results for \(\beta = 0.5\), which can be seen to lie extremely close
+to the approximate results, even for the worst case of \(k = 0\). The
+leading term in the relative error of
+equation~\eqref{eq:Lambda-approx} scales as \((\beta / (k + 2))^2\), so
+the approximation is even better for smaller \(\beta\) and larger \(k\).
+
+It is apparent from Figure~\ref{fig:r-beta} that the \(k=0\) ancantoid
+is identical to the cantoid for \(\theta \le 90^\circ\) (\(z > 0\), to the right
+of vertical dotted line in Fig.~\ref{fig:r-beta}), but is slightly
 more swept back in the far wings.\footnote{%
   Due to the discontinuity in the inner wind density at
-  \(theta = 90^\circ\) (see Fig.~\ref{fig:anisotropic-arrows}), there is a
+  \(\theta = 90^\circ\) (see Fig.~\ref{fig:anisotropic-arrows}), there is a
   discontinuity in the second derivative of the bow shape.} %
@@
 behave identically in Figure~\ref{fig:ancantoid-Pi-lambda-true}.
-
 There is a general tendency for the bows to be flatter and more open
@@
 between \(\beta\) and \(k\) for higher values of \(\beta\).  The wilkinoid
-shape, which corresponds to the \(\beta \to 0\) limit of the cantoids is
+shape, which corresponds to the \(\beta \to 0\) limit of the cantoids, is
 marked by a white plus symbol in
-Figure~\ref{fig:ancantoid-Pi-lambda-true}, which lies in the prolate
-ellipsoid region of the plane.
+Figure~\ref{fig:ancantoid-Pi-lambda-true}, and lies in the prolate
+spheroid region of the plane.  Cantoids lie either in the prolate
+spheroid or hyperboloid regions, according to whether \(\beta\) is less
+than or greater than about \(0.01\).  For ancantoids of increasing
+\(k\), this dividing point moves to higher values of \(\beta\), until
+almost the entire range of models with \(k = 8\) are within the
+prolate spheroid zone.
 
@@
 \end{figure}
+
+However, the true planitude and alatude, which are what would be
+observed for a side-on viewing angle (\(i = 0\)), are not at all
+sensitive to the behavior of the far wings of the bow shock, which has
+a rather different implication as to which variety of quadric best
+approximates each shape.  We illustrate this is
+Figure~\ref{fig:ancantoid-angles}, which shows two different ways of
+estimating the quadric angle, \(\theta_{\Q}\) (see \S~\ref{sec:conic}).
+The first is from \((\Pi, \Lambda)\), as in
+Figure~\ref{fig:ancantoid-Pi-lambda-true}:
+\newcommand\head{^{\text{head}}}
+\newcommand\tail{^{\text{tail}}}
+\begin{equation}
+  \label{eq:thetaQ-head}
+  \theta_{\Q}\head =
+  \sgn{\bigl(2 \Pi - \Lambda^2\bigr)} \;
+  \tan^{-1} \Abs{2\Pi - \Lambda^2}^{1/2} \ ,
+\end{equation}
+which follows from equations~\eqref{eq:Tq}, \eqref{eq:thetaQ}, and
+\eqref{eq:Tq-from-Pi-Lambda}.  The second is from the asymptotic
+opening angle of the wings, \(\theta_\infty\) (Fig.~\ref{fig:characteristic-radii}):
+\begin{equation}
+  \label{eq:thetaQ-tail}
+  \theta_{\Q}\tail = \theta_\infty - 180^\circ \ , 
+\end{equation}
+where \(\theta_\infty\) is calculated from
+equation~\eqref{eq:anacantoid-theta-inf} for ancantoids, or
+\eqref{eq:cantoid-theta-inf} for cantoids.  If the bow shock shape
+were truly a quadric, then these two definitions would agree.
+However, as seen in Figure~\ref{fig:ancantoid-angles}, this is not the
+case for the cantoids and ancantoids.  While
+\(\smash[b]{\theta_{\Q}\head}\) generally corresponds to a prolate spheroid
+(except for the largest values of \(\beta\)),
+\(\smash[b]{\theta_{\Q}\tail}\) always corresponds to a hyperbola.  This
+has important implications for the projected shapes (as we will see in
+the next section), since the far wings influence the projected
+planitude and alatude when the inclination is large.
 
@@
 
+\subsection{Apparent shapes of projected cantoids and ancantoids}
+\label{sec:proj-shap-cant}
+
 \begin{figure*}

### 2017-11-11 CRW-shapes/ancantoid-Pi-Lambda-true.py

@@ -25,7 +25,7 @@ ax.axvline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
 ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
 
 # Plot our curves
-betas = np.logspace(-5.0, np.log10(0.5), 100)
+betas = np.logspace(-5.0, np.log10(1.0), 100)
 ks = [0.0, 0.5, 3.0, 8.0]
 labels = ["Cantoid"] + [f"Ancantoid, $k = {k:.1f}$" for k in ks[1:]]
 bbetas = [1e-8, 0.01, 0.1]

### 2017-11-12 papers/Paper1/app-shape-parameters.tex
Finish sec 5.2 on true shapes of cantoids and ancantoids
Re-do the projected ancantoid fig and start describing it

@@
 This approximation is surprisingly accurate, with a relative error of
-order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).  The
-leading term in the relative error scales as \((\beta / (k + 2))^2\), so the
-approximation is even better for smaller \(\beta\) and larger \(k\).
+order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).
 
@@
 \begin{equation}
-  \label{eq:anacantoid-theta-inf}
+  \label{eq:ancantoid-theta-inf}
   \theta_\infty - \left( \frac {k + 2 (1 - \beta)} {k + 2} \right) \tan \theta_\infty
@@
 Note that, unlike in the cases of \(\Pi\) and \(\Lambda\),
-equation~\eqref{eq:anacantoid-theta-inf} does \emph{not} reduce to
+equation~\eqref{eq:ancantoid-theta-inf} does \emph{not} reduce to
 equation~\eqref{eq:cantoid-theta-inf} in the limit \(k \to 0\).  This is

### 2017-11-12 papers/Paper1/sec-thin-shell.tex
Re-do the projected ancantoid fig and start describing it

@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{figs/ancantoid-shape}
+\caption{Bow shock shapes for interacting winds in the thin-shell
+  approximation: cantoids and ancantoids. Coordinates are normalized
+  by $D$, the distance between the two wind sources, which are
+  indicated by black dots on the axis.  The weaker source is at
+  \((0.0, 0.0)\) and the stronger source is at \((1.0, 0.0)\).
+  Results are shown for different values of the wind momentum ratio,
+  \(\beta\) (different line widths), and for the case where the weaker
+  wind is isotropic (black lines) or anisotropic (colored lines).}
+\label{fig:r-beta}
+\end{figure}
+
 The general solution for the bow shock shape, \(R(\theta)\), in the \CRW{}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
+  \caption{True shapes of cantoids and ancantoids in the
+    \(\Pi\)--\(\Lambda\) plane, calculated according to results of
+    App.~\ref{sec:thin-shell-shapes}.  For each line, \(\beta\) varies
+    over the range \([0, 1]\) from lower left to upper right (although
+    the black and red lines are truncated on the upper right), and
+    line colors correspond to different anisotropy indices, matching
+    those used in Fig.~\ref{fig:r-beta}. Circle symbols mark
+    particular \(\beta\) values: \(0, 0.01, 0.1\), from largest to
+    smallest circle.  Square symbols mark \(\beta = 0.5\), but with
+    \(\Lambda\) calculated exactly, instead of using the approximation of
+    equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
+    the result for the wilkinoid:
+    \((\Pi, \Lambda) = (\frac53, \sqrt{3})\).  Background shading indicates
+    the domains of different quadric classes: hyperboloids (white),
+    prolate spheroids (dark gray), and oblate spheroids (light gray).}
+  \label{fig:ancantoid-Pi-lambda-true}
+\end{figure}
+
 We define \(\beta\) in this case as the momentum ratio \emph{on the symmetry axis}, which means that 
@@
 
-%The most notable scenarios, since they have astrophysical relevance are the following:
-%$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison between both solutions
-%is shown in figure (\ref{fig:r-beta}), along with an extreme anisotropy case.
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "quadrics-bowshock"
-%%% End:
-
 \begin{figure}
-\includegraphics[width=\linewidth]{figs/ancantoid-shape}
-\caption{Bow shock shapes for interacting winds in the thin-shell
-  approximation: cantoids and ancantoids. Coordinates are normalized
-  by $D$, the distance between the two wind sources, which are
-  indicated by black dots on the axis.  The weaker source is at
-  \((0.0, 0.0)\) and the stronger source is at \((1.0, 0.0)\).
-  Results are shown for different values of the wind momentum ratio,
-  \(\beta\) (different line widths), and for the case where the weaker
-  wind is isotropic (black lines) or anisotropic (colored lines).}
-\label{fig:r-beta}
+  \centering
+  \includegraphics[width=\linewidth]{figs/ancantoid-angles}
+  \caption{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
+    cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
+    \((\Pi, \Lambda)\), which is representative of the shape of the head,
+    while dashed lines show \(\theta_{\Q}\) calculated from
+    \(\theta_\infty\), which is representative of the tail.  Dot-dashed line
+    shows the result for cantoids, which differ from the \(k=0\)
+    ancantoids in \(\theta_\infty\), but not in \((\Pi, \Lambda)\). Gray shading and
+    line colors have the same meaning as in
+    Fig.~\ref{fig:ancantoid-Pi-lambda-true}. }
+  \label{fig:ancantoid-angles}
 \end{figure}
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
-  \caption{True shapes of cantoids and ancantoids in the
-    \(\Pi\)--\(\Lambda\) plane, calculated according to results of
-    App.~\ref{sec:thin-shell-shapes}.  For each line, \(\beta\) varies
-    over the range \([0, 1]\) from lower left to upper right (although
-    the black and red lines are truncated on the upper right), and
-    line colors correspond to different anisotropy indices, matching
-    those used in Fig.~\ref{fig:r-beta}. Circle symbols mark
-    particular \(\beta\) values: \(0, 0.01, 0.1\), from largest to
-    smallest circle.  Square symbols mark \(\beta = 0.5\), but with
-    \(\Lambda\) calculated exactly, instead of using the approximation of
-    equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
-    the result for the wilkinoid:
-    \((\Pi, \Lambda) = (\frac53, \sqrt{3})\).  Background shading indicates
-    the domains of different quadric classes: hyperboloids (white),
-    prolate spheroids (dark gray), and oblate spheroids (light gray).}
-  \label{fig:ancantoid-Pi-lambda-true}
-\end{figure}
+  \includegraphics[width=0.9\linewidth]{figs/test_xyprime}
+  \caption{Apparent bow shapes as a function of inclination angle for
+    isotropic thin shell models. (a)~Confocal paraboloid for
+    comparison (shape independent of inclination).
+    (b)~Wilkinoid. (c)~Cantoid, \(\beta = 0.001\). (d)~Cantoid,
+    \(\beta = 0.01\). }
+  \label{fig:xyprime}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.9\linewidth]{figs/test_xyprime_ancantoid}
+  \caption{Further apparent bow shapes as a function of inclination
+    angle for anisotropic thin shell models (ancantoids).
+    (a)~\(\beta = 0.001\), \(k = 0.5\); (b) (a)~\(\beta = 0.1\),
+    \(k = 0.5\); (c)~\(\beta = 0.001\) \(k = 3\); (d)
+    \(\beta = 0.1\) \(k = 3\).}
+  \label{fig:xyprime-ancantoid}
+\end{figure*}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/ancantoid-angles}
-  \caption{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
-    cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
-    \((\Pi, \Lambda)\), which is representative of the shape of the head,
-    while dashed lines show \(\theta_{\Q}\) calculated from
-    \(\theta_\infty\), which is representative of the tail.  Dot-dashed line
-    shows the result for cantoids, which differ from the \(k=0\)
-    ancantoids in \(\theta_\infty\), but not in \((\Pi, \Lambda)\). Gray shading and
-    line colors have the same meaning as in
-    Fig.~\ref{fig:ancantoid-Pi-lambda-true}. }
-  \label{fig:ancantoid-angles}
-\end{figure}
-
 However, the true planitude and alatude, which are what would be
@@
 where \(\theta_\infty\) is calculated from
-equation~\eqref{eq:anacantoid-theta-inf} for ancantoids, or
+equation~\eqref{eq:ancantoid-theta-inf} for ancantoids, or
 \eqref{eq:cantoid-theta-inf} for cantoids.  If the bow shock shape
@@
 \(\smash[b]{\theta_{\Q}\tail}\) always corresponds to a hyperbola.  This
+tension between the shape of the head and the shape of the far wings
 has important implications for the projected shapes (as we will see in
@@
 
+\begin{figure}
+  \centering
+  \setkeys{Gin}{width=\linewidth}
+  \begin{tabular}{@{}l@{}}
+    (a) \\
+    \includegraphics{figs/ancantoid-R90-vs-Rc-a} \\
+    (b) \\
+    \includegraphics{figs/ancantoid-R90-vs-Rc-b}
+  \end{tabular}
+  \caption{Apparent projected shapes of wilkinoid, cantoids and
+    ancantoids in the \(\Pi'\)--\(\Lambda'\) plane.  Colored dots indicate the
+    \(\abs{i} = 0\) position (as shown in
+    Fig.~\ref{fig:ancantoid-Pi-lambda-true}).}
+  \label{fig:thin-shell-R90-Rc}
+\end{figure}
+
 \subsection{Apparent shapes of projected cantoids and ancantoids}
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{figs/test_xyprime}
-  \caption{Apparent bow shapes as a function of inclination angle for
-    isotropic thin shell models. (a)~Confocal paraboloid for
-    comparison (shape independent of inclination).
-    (b)~Wilkinoid. (c)~Cantoid, \(\beta = 0.001\). (d)~Cantoid,
-    \(\beta = 0.01\). }
-  \label{fig:xyprime}
-\end{figure*}
+Figures~\ref{fig:xyprime} and~\ref{fig:xyprime-ancantoid} show the
+apparent bow shapes of various thin shell models (wilkinoid, cantoids,
+ancantoids) for different inclination angles \(\abs{i}\).  For
+comparison, Figure~\ref{fig:xyprime}a shows the confocal paraboloid,
+whose apparent shape is independent of inclination (see
+Appendix~\ref{app:parabola}).  The wilkinoid (Fig.~\ref{fig:xyprime}b)
+shows only subtle changes, with the wings becoming slightly more swept
+back as the inclination increases.  The cantoids
+(Fig.~\ref{fig:xyprime}c and d) behave in the opposite way, with the
+wings becoming markedly more open once \(\abs{i}\) exceeds
+\(60^\circ\) (for \(\beta = 0.001\)), or \(45^\circ\) (for
+\(\beta = 0.01\)).  The ancantoids (Fig.~\ref{fig:xyprime-ancantoid}) can
+show more complex behavior.  For instance, in the \(k = 0.5\),
+\(\beta = 0.001\) ancantoid (Fig.~\ref{fig:xyprime-ancantoid}a) the near
+wings begin to become more closed with increasing inclination up to
+\(\abs{i} = 60^\circ\), at which point they open up again.
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{figs/test_xyprime_ancantoid}
-  \caption{Further apparent bow shapes as a function of inclination
-    angle for anisotropic thin shell models (ancantoids).
-    (a)~\(\beta = 0.001\), \(\xi =.8\); (b) (a)~\(\beta = 0.1\),
-    \(\xi =.8\); (c)~\(\beta = 0.001\) \(\xi =0.4\); (d)
-    \(\beta = 0.1\) \(\xi =0.4\).}
-  \label{fig:xyprime-anacantoid}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
-    (a) & (b) \\
-    \includegraphics{figs/ancantoid-R90-vs-Rc-a}
-        & \includegraphics{figs/ancantoid-R90-vs-Rc-b} \\
-  \end{tabular}
-  \caption{Diagnostic diagram for thin shell models}
-  \label{fig:thin-shell-R90-Rc}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/two-quadric-R90-Rc-snapshots}
-  \caption{Variation with inclination angle of radii diagnostics}
-  \label{fig:thin-shell-R90-Rc-snapshots}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.8\textwidth]{figs/two-quadric-R90-Rc-snapshots}
+%   \caption{Variation with inclination angle of radii diagnostics}
+%   \label{fig:thin-shell-R90-Rc-snapshots}
+% \end{figure*}
 

### 2017-11-12 Dust-wave/ancantoid-R90-vs-Rc.py

@@ -60,9 +60,9 @@ cols = sns.color_palette('magma', n_colors=nxi)
 annot_pars_list = [right_annotate_pars]*2 + [left_annotate_pars]*2 
 for beta in BETA_LIST[::-1]:
     for xi, col, annot_pars in list(zip(XI_LIST, cols, annot_pars_list))[istart::-2]:
-
+        k = None if xi is None else 2/xi - 2
         if beta == BETA_LIST[0]:
-            label = "Cantoid" if xi is None else fr"Ancantoid $\xi = {xi:.1f}$"
+            label = "Cantoid" if k is None else fr"Ancantoid $k = {k:.1f}$"
         else:
             label = "_nolabel_"
 
@@ -97,8 +97,8 @@ ax.set(
     xlim=[0.0, 5.1],
     ylim=[0.0, 5.1],
 #    ylim=[-3.0, 1.1],
-    xlabel=r"Projected dimensionless radius of curvature: $\widetilde{R}_{c}{}'$",
-    ylabel=r"Projected dimensionless perpendicular radius: $\widetilde{R}_{90}{}'$",
+    xlabel=r"Projected planitude: $\Pi'$",
+    ylabel=r"Projected alatude: $\Lambda'$",
 )        
 
 sns.despine()

### 2017-11-12 papers/Paper1/sec-thin-shell.tex
Re-do figs for projected ancantoid shapes to reduce white space
Now they can be put in a single column

@@
 
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=0.9\linewidth]{figs/test_xyprime}
+  \includegraphics[width=\linewidth]{figs/test_xyprime}
   \caption{Apparent bow shapes as a function of inclination angle for
@@
   \label{fig:xyprime}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=0.9\linewidth]{figs/test_xyprime_ancantoid}
+  \includegraphics[width=\linewidth]{figs/test_xyprime_ancantoid}
   \caption{Further apparent bow shapes as a function of inclination
@@
   \label{fig:xyprime-ancantoid}
-\end{figure*}
+\end{figure}
 
@@
 wings begin to become more closed with increasing inclination up to
-\(\abs{i} = 60^\circ\), at which point they open up again.
+\(\abs{i} = 60^\circ\), at which point they open up again, whereas the
+opening angle of the far wings increases monotonically with
+\(\abs{i}\).
+
+The paths that are traced in the projected planitude--alatude plane
+with changing inclination are shown in
+Figure~\ref{fig:thin-shell-R90-Rc}.
 

### 2017-11-12 Dust-wave/test_xyprime.py

@@ -9,7 +9,7 @@ from bow_projection import (xyprime_t, theta_infinity, theta_0_90,
 figfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
-fig, axes = plt.subplots(2, 2, figsize=(8, 8))
+fig, axes = plt.subplots(2, 2, figsize=(6, 6), sharex=True, sharey=True)
 
 inclinations = [0, 15, 30, 45, 60.1, 75]
 linewidths = [2.4, 2.0, 1.6, 1.2, 0.8, 0.4]
@@ -18,8 +18,8 @@ colors = sns.color_palette('magma_r', n_colors=len(inclinations))
 for shape_name, ax, R_theta, extra_pars in [
         ["Paraboloid", axes[0, 0], paraboloid_R_theta, ()],
         ["Wilkinoid", axes[0, 1], wilkinoid_R_theta, ()],
-        [r"Cantoid $\beta = 0.001$", axes[1, 0], cantoid_R_theta, (0.001,)],
-        [r"Cantoid $\beta = 0.01$", axes[1, 1], cantoid_R_theta, (0.01,)],
+        ["Cantoid\n" r"$\beta = 0.001$", axes[1, 0], cantoid_R_theta, (0.001,)],
+        ["Cantoid\n" r"$\beta = 0.01$", axes[1, 1], cantoid_R_theta, (0.01,)],
 ]:
     th_inf = theta_infinity(R_theta, *extra_pars)
     for inc_dg, color, lw in zip(inclinations, colors, linewidths):
@@ -38,16 +38,18 @@ for shape_name, ax, R_theta, extra_pars in [
 
     ax.plot([0], [0], 'o', color='k')
 
-    ax.legend(title=shape_name, ncol=2, loc="center left")
-    ax.set(
-        xlabel=r"$x' / R_0'$",
-        ylabel=r"$y' / R_0'$",
-        xlim=[-7, 3],
-        ylim=[-5, 5],
-    )
-    ax.set_aspect('equal', adjustable='box')
+    ax.legend(title=shape_name, ncol=2, fontsize='small',
+              handlelength=1.0, handletextpad=0.5, columnspacing=0.3,
+              loc="center left")
+    ax.set_aspect('equal', adjustable='box-forced')
 
+axes[-1,0].set(
+    xlabel=r"$x' / R_0'$",
[…]

### 2017-11-12 Dust-wave/test_xyprime_ancantoid.py

@@ -9,7 +9,7 @@ from ancantoid_shape import Ancantoid
 figfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
-fig, axes = plt.subplots(2, 2, figsize=(8, 8))
+fig, axes = plt.subplots(2, 2, figsize=(6, 6), sharex=True, sharey=True)
 
 inclinations = [0, 15, 30, 45, 60, 75]
 linewidths = [2.4, 2.0, 1.6, 1.2, 0.8, 0.4]
@@ -20,7 +20,7 @@ for xi, beta, ax in [[0.8, 0.001, axes[0, 0]],
                      [0.4, 0.001, axes[1, 0]],
                      [0.4, 0.1, axes[1, 1]],]:
 
-    label = fr"Ancantoid $\beta = {beta:.3f}$, $\xi = {xi:.1f}$"
+    label = "Ancantoid\n" fr"$\beta = {beta:.3f}$, $k = {2/xi - 2:.1f}$"
     shape = Ancantoid(xi=xi, beta=beta)
     th_inf = theta_infinity(shape)
     for inc_dg, color, lw in zip(inclinations, colors, linewidths):
@@ -42,16 +42,18 @@ for xi, beta, ax in [[0.8, 0.001, axes[0, 0]],
 
     ax.plot([0], [0], 'o', color='k')
 
-    ax.legend(title=label, ncol=2, loc="center left")
-    ax.set(
-        xlabel=r"$x' / R_0'$",
-        ylabel=r"$y' / R_0'$",
-        xlim=[-7, 3],
-        ylim=[-5, 5],
-    )
-    ax.set_aspect('equal', adjustable='box')
+    ax.legend(title=label, ncol=2, fontsize='small',
+              handlelength=1.0, handletextpad=0.5, columnspacing=0.3,
+              loc="center left")
+    ax.set_aspect('equal', adjustable='box-forced')
 
+axes[-1,0].set(
+    xlabel=r"$x' / R_0'$",
+    ylabel=r"$y' / R_0'$",
+    xlim=[-7, 3],
+    ylim=[-5, 5],
+)
 sns.despine()
-fig.tight_layout()
+fig.tight_layout(pad=0.3, h_pad=0.1, w_pad=0.1)
 fig.savefig(figfile)
 print(figfile, end='')

### 2017-11-12 papers/Paper1/app-shape-parameters.tex
Redo fig 18 with ancantoid tracks on Pi-Lambda plane

@@
 \end{gather}
-The same results can also be obtained directly from
+The wilkinoid results can also be obtained directly from
 equation~\eqref{eq:wilkinoid-R-theta}, and in the case of \(\Lambda\) this

### 2017-11-12 papers/Paper1/sec-conic.tex
Redo fig 18 with ancantoid tracks on Pi-Lambda plane

@@
 strands for different \(\Q\) begin to separate, with hyperbolae
-showing the strongest increase of \(R_0'\) with \(\abs{i}\).
+showing the strongest increase of \(R_0'\) with~\(\abs{i}\).
 

### 2017-11-12 Dust-wave/ancantoid-R90-vs-Rc.py

@@ -16,7 +16,7 @@ except:
     sys.exit(f"Usage: {sys.argv[0]} a|b")
 
 sns.set_style('ticks')
-fig, ax = plt.subplots(figsize=(5, 5))
+fig, ax = plt.subplots(figsize=(4, 4))
 
 bp.N_NEIGHBORHOOD = 50
 bp.DEGREE_POLY_NEIGHBORHOOD = 2
@@ -41,7 +41,7 @@ ax.axvline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
 ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
 
 XI_LIST = [None, 1.0, 0.8, 0.4]
-BETA_LIST = [0.2, 0.1, 0.05, 0.02, 0.005, 1e-3]
+BETA_LIST = [0.3, 0.1, 0.03, 0.01, 1e-3]
 nxi, nbeta = len(XI_LIST), len(BETA_LIST)
 
 # Put a cross at the Wilkinoid coordinates: [5/3, sqrt(3)]
@@ -53,7 +53,13 @@ inc = np.linspace(0.0, th_inf - np.pi/2, 50)
 tab = bow_diagnostic.parameter_table(inc, shape)
 Rc, R90 = tab['tilde R_c prime'], tab['tilde R_90 prime']
 ax.plot(Rc, R90, '-', c='w', label="_nolabel_", lw=0.6, alpha=0.9)
-ax.plot(Rc, R90, 'x', ms=0.2, c='w', label="_nolabel_", alpha=0.5)
+sini = np.linspace(0.0, 1.0, 10)
+inc_e = np.arcsin(sini)
+tab_e = bow_diagnostic.parameter_table(inc_e, shape)
+Rc_e, R90_e = tab_e['tilde R_c prime'], tab_e['tilde R_90 prime']
+ax.scatter(Rc_e, R90_e, marker='|', s=3**2,
+           linewidths=0.1, edgecolors='none',
+           c='w', alpha=0.5, label="_nolabel_")
 
 
 cols = sns.color_palette('magma', n_colors=nxi)
@@ -75,19 +81,30 @@ for beta in BETA_LIST[::-1]:
             shape = ancantoid_shape.Ancantoid(xi=xi, beta=beta, n=301)
 
         th_inf = bp.theta_infinity(shape)
-        inc = np.linspace(0.0, th_inf - np.pi/2, 50)
[…]

### 2017-11-13 papers/Paper1/sec-thin-shell.tex
Redo fig 18 with ancantoid tracks on Pi-Lambda plane
Finish section 5!  Discuss new zoomed graph

@@
 more swept back in the far wings.\footnote{%
+  \label{fn:discontinuity}
   Due to the discontinuity in the inner wind density at
@@
   \caption{Apparent projected shapes of wilkinoid, cantoids and
-    ancantoids in the \(\Pi'\)--\(\Lambda'\) plane.  Colored dots indicate the
-    \(\abs{i} = 0\) position (as shown in
-    Fig.~\ref{fig:ancantoid-Pi-lambda-true}).}
+    ancantoids in the \(\Pi'\)--\(\Lambda'\) plane.  Colored symbols indicate
+    the \(\abs{i} = 0\) position for \(\beta = 0.001\), \(0.003\),
+    \(0.01\), \(0.03\), \(0.1\), \(0.3\).  Thin lines show the
+    inclination-dependent tracks of each model, with tick marks along
+    each track for 20 equal-spaced values of \(\abs{\sin i}\).  Gray
+    shaded regions are as in
+    Fig.~\ref{fig:quadric-projection-continued}a.  The wilkinoid track
+    is shown in white. (a)~Isotropic wind model (cantoid) and
+    proplyd-like model (ancantoid, \(k = 0.5\)). (b)~Hemispheric wind
+    model (ancantoid, \(k = 0\)) and jet-like model (ancantoid,
+    \(k = 3\)).}
   \label{fig:thin-shell-R90-Rc}
@@
 
-The paths that are traced in the projected planitude--alatude plane
-with changing inclination are shown in
-Figure~\ref{fig:thin-shell-R90-Rc}.
+The inclination-dependent tracks that are traced by the thin-shell
+models in the projected planitude--alatude plane are shown in
+Figure~\ref{fig:thin-shell-R90-Rc}.  The behavior is qualitatively
+different from the quadric shapes shown in
+Figure~\ref{fig:quadric-projection-continued}a in that the tracks are
+no longer confined within the borders of the region of a single type
+of quadric (hyperboloid or spheroid). At low inclinations, many of the
+models behave like the prolate spheroids, but then transition to a
+hyperboloid behavior at higher inclinations, which is due to the
+tension between the shape of the head and the shape of the far wings,
+as discussed in the previous section. This can be seen most clearly in
+the \(\beta = 0.001\), \(k = 0.5\) ancantoid (lowest red line in
+Fig.~\ref{fig:thin-shell-R90-Rc}a, see also zoomed version in
+Fig.~\ref{fig:convergence-cantoid-wilkinoid}). The track begins
+heading towards \((\Pi', \Gamma') = (1, 1)\), as expected for a spheroid, but
+then turns around and crosses the paraboloid line to head out on a
+hyperboloid-like track.
+
+Ancantoids with different degrees of inner-wind anisotropy are shown
+in Figure~\ref{fig:thin-shell-R90-Rc}b.  In all cases, the tracks
+follow hyperboloid-like behavior at high inclinations, tending to
+populate the region just above the diagonal \(\Lambda' = \Pi'\).  The
+\(k = 0\) ancantoids show a kink in their tracks at the point where
+the projected apex passes through \(\theta = 90^\circ\), due to the
+discontinuity in the second derivative of \(R(\theta)\) there (see
+footnote~\ref{fn:discontinuity}).  The wilkinoid has a much less
+interesting track, most clearly seen in the zoomed
+Figure~\ref{fig:convergence-cantoid-wilkinoid}, simply moving the
+short distance from \((\tfrac53, \sqrt3)\) to
+\((\tfrac32, \mathbf{???})\).  Despite its location in the ellipsoid
+region of the plane, the fact that it has \(\theta_\infty = 180^\circ\) means that it
+behaves more like a parabola at high inclination, but converges on
+\((\tfrac32, \mathbf{???})\) instead of \((2, 2)\) since the far wings
+are asymptotically cubic, rather than quadratic.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/ancantoid-R90-vs-Rc-lobeta-a}
+  \caption{As Fig.~\ref{fig:thin-shell-R90-Rc}a but zoomed in to show
+    the wilkinoid track (white) and the convergence of the cantoid
+    tracks (purple) to this as \(\beta \to 0\).}
+  \label{fig:convergence-cantoid-wilkinoid}
+\end{figure}
+
+The local density of tick marks gives an indication of how likely it
+would be to observe each portion of the track, assuming an isotropic
+distribution of viewing angles.  It can be seen that the ticks tend to
+be concentrated towards the beginning of each track, near the
+\(\abs{i} = 0\) point, so the hyperboloid-like portions of the tracks
+would be observed for only a relatively narrow range of inclinations.
+This concentration becomes more marked as \(\beta\) becomes smaller, which
+helps to resolve the apparent paradox that the wilkinoid corresponds
+to the \(\beta \to 0\) limit of the cantoids, and yet follows a
+qualitatively different track.  The detailed behavior of the
+small-\(\beta\) cantoid models is shown in
+Figure~\ref{fig:convergence-cantoid-wilkinoid}, which zooms in on the
+region around the wilkinoid track.  It can be seen that for
+\(\beta < 0.001\) the cantoid tracks begin to develop a downward hook,
+similar to the \(k = 0.5\) ancantoids discussed above.  For
+\(\beta < 10^{-4}\) this begins to approach the wilkinoid track and the
+high inclination, upward portion of the track becomes less and less
+important as \(\beta\) decreases.
 

### 2017-11-13 Dust-wave/ancantoid-R90-vs-Rc-lobeta.py

@@ -99,7 +99,7 @@ for beta in BETA_LIST[::-1]:
         # Put a dot at the i=0 case
         ax.plot(Rc[0:1], R90[0:1], 'o', mec='none', c=col, label="_nolabel_", alpha=0.7)
         # Label the dot with the cross-over inclination
-        beta_label = rf'$\beta = \mathrm{{{beta:g}}}$'
+        beta_label = rf'$\beta = 10^{{{int(np.log10(beta)):d}}}$'
         # But only for some of them
         ax.annotate(beta_label, xy=(Rc[0], R90[0]),
                     textcoords='offset points',

### 2017-11-14 papers/Paper1/app-dust-wave.tex
Add figure for dragoid R_c-R_90 diagram
Add figure for plane-of-sky shapes of dragoids
Description of dust wave in the no-drag case

@@
 
+\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
+\newcommand{\grain}{\ensuremath{_{\text{g}}}}
+\newcommand{\xsec}{\ensuremath{\sigma\grain}}
+\newcommand\frad{\ensuremath{f_{\text{rad}}}}
+\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
+A dust grain of geometrical cross-section \(\xsec\) situated a
+distance \(R\) from a point source of radiation with luminosity \(L\)
+will experience a repulsive, radially directed radiative force
+\citep[e.g.,][]{Spitzer:1978a}
+\begin{equation}
+  \label{eq:dust-rad-force}
+  \frad = \frac{\xsec \Qp L} {4 \pi R^2 c} e^{-\tau}
+\end{equation}
+where \Qp{} is the frequency-averaged\footnote{%
+  Frequency averages of any quantity \(x\) should be understood as
+  weighted by the attenuated source spectrum:
+  \(\langle x \rangle_\nu = (L \, e^{-\tau})^{-1} \int_0^\infty x(\nu)\, L_\nu \, e^{-\tau_\nu} \, d\nu
+  \).  } %
+radiation pressure efficiency\footnote{%
+  For absorption efficiency \(Q_{\text{abs}}\), scattering efficiency
+  \(Q_{\text{scat}}\), and asymmetry parameter (mean scattering
+  cosine) \(g\), we have
+  \(\Qp = Q_{\text{abs}} + (1 - g) Q_{\text{scat}}\).  } %
+of the grain, \(c\) is the speed of light, and \(\tau\) is the
+frequency-averaged optical depth between the source and the grain.
+For simplicity, we will consider only the optically thin case,
+\(\tau \to 0\).
+
+If \(\frad\) is the only force experienced by the grain, then it will
+move on a \textit{ballistic} trajectory, determined by its initial
+speed at large distance, \(u_\infty\), and its impact parameter, \(b\).
+For \(b = 0\), the grain radially approaches the source with initial
+radial velocity \(-u_\infty\), which is decelerated to zero at the distance
+of closest approach, \(R_0\), given by energy conservation:
+\begin{equation}
+  \label{eq:dust-r0}
+  R_0 = \frac{\xsec \Qp L} {2 \pi c m\grain u_\infty^2} \ ,
+\end{equation}
+where \(m\grain\) is the grain mass.  The grain then turns round and
+recedes from the source along the same radius, reaching a velocity of
+\(+u_\infty\) at large distance.  For \(b > 0\), the trajectory,
+\(R(\theta)\), is readily found\footnote{%
+  The problem is formally identical to that of Rutherford scattering,
+  or (modulo a change of sign) planetary orbits.  The method of
+  solution (via introduction of a centrifugal potential term and
+  reduction to a 1-dimensional problem) can be found in any classical
+  mechanics text \citep[e.g.,][\S~14]{Landau:1976a}. } in polar
+coordinates as
+\begin{equation}
+  \label{eq:dust-r-theta}
+  \frac{R\grain(\theta; b)} {R_0} = 
+  \frac{ \tfrac12 \bigl( \varepsilon^2 - 1 \bigr)} {\varepsilon \cos(\theta - \thm) - 1}
+\end{equation}
+where \(\varepsilon^2 = 1 + 4 b^2 / R_0^2\) and
+\(\thm = \cos^{-1} \varepsilon\) is the polar angle of closest approach along
+the trajectory (see Fig.~\ref{fig:dust-trajectories}).  If the
+incoming dust grains initially travel along parallel trajectories with
+varying \(b\), but the same \(u_\infty\), then the deflection of the
+trajectories by the radiative force will form a bow wave around the
+radiation source, as shown in Figure~\ref{fig:dust-trajectories}.
+However, the inner edge of the bow wave, \(R_{\text{in}}(\theta)\) is not
+given by the closest approach along individual trajectories,
+\(R\grain(\thm; b)\), but instead must found by minimizing
+\(R\grain(\theta; b)\) over all \(b\) for each value of \(\theta\), which yields
+\begin{equation}
+  \label{eq:dust-r-in}
+  \frac{R_{\text{in}}(\theta)} {R_0} = \frac{2}{1 + \cos\theta} \ .
+\end{equation}
+This is the polar form of the equation for the confocal parabola,
+which we have already discussed in detail in \S~\ref{sec:conic} and
+Appendix~\ref{app:parabola}.
+
 \begin{figure*}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/test_xyprime_dragoid}
+  \caption{Plane-of-sky shapes for dragoids.}
+  \label{fig:dragoid-xy-prime}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/dragoid-R90-vs-Rc}
+  \caption{Diagnostic diagram for dragoids}
+  \label{fig:dragoid-Rc-R90}
+\end{figure}
+
 %%% Local Variables:

### 2017-11-14 papers/Paper1/app-dust-wave.tex
Improve ballistic dust trajectories description

--- 2017-10-04 papers/Paper1/app-dust-wave.tex
@@
 
+\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
+\newcommand{\grain}{\ensuremath{_{\text{g}}}}
+\newcommand{\xsec}{\ensuremath{\sigma\grain}}
+\newcommand\frad{\ensuremath{f_{\text{rad}}}}
+\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
+A dust grain of geometrical cross-section \(\xsec\) situated a
+distance \(R\) from a point source of radiation with luminosity \(L\)
+will experience a repulsive, radially directed radiative force
+\citep[e.g.,][]{Spitzer:1978a}
+\begin{equation}
+  \label{eq:dust-rad-force}
+  \frad = \frac{\xsec \Qp L} {4 \pi R^2 c} e^{-\tau}
+\end{equation}
+where \Qp{} is the frequency-averaged\footnote{%
+  Frequency averages of any quantity \(x\) should be understood as
+  weighted by the attenuated source spectrum:
+  \(\langle x \rangle_\nu = (L \, e^{-\tau})^{-1} \int_0^\infty x(\nu)\, L_\nu \, e^{-\tau_\nu} \, d\nu
+  \).  } %
+radiation pressure efficiency\footnote{%
+  For absorption efficiency \(Q_{\text{abs}}\), scattering efficiency
+  \(Q_{\text{scat}}\), and asymmetry parameter (mean scattering
+  cosine) \(g\), we have
+  \(\Qp = Q_{\text{abs}} + (1 - g) Q_{\text{scat}}\)
+  \citep[e.g., \S~4.5 of][]{Bohren:1983a}.} %
+of the grain, \(c\) is the speed of light, and \(\tau\) is the
+frequency-averaged optical depth between the source and the grain.
+For simplicity, we will consider only the optically thin case,
+\(\tau \to 0\).
+
+If \(\frad\) is the only force experienced by the grain, then it will
+move on a \textit{ballistic} trajectory, determined by its initial
+speed at large distance, \(v_\infty\), and its impact parameter, \(b\).
+For \(b = 0\), the grain radially approaches the source with initial
+radial velocity \(-v_\infty\), which is decelerated to zero at the distance
+of closest approach, \(R_0\), given by energy conservation:
+\begin{equation}
+  \label{eq:dust-r0}
+  R_0 = \frac{\xsec \Qp L} {2 \pi c m\grain v_\infty^2} \ ,
+\end{equation}
+where \(m\grain\) is the grain mass.  The grain then turns round and
+recedes from the source along the same radius, reaching a velocity of
+\(+v_\infty\) at large distance.  For \(b > 0\), the trajectory,
+\(R\grain(\theta; b)\), is found\footnote{%
+  The problem is formally identical to that of Rutherford scattering,
+  or (modulo a change of sign) planetary orbits.  The method of
+  solution (via introduction of a centrifugal potential term and
+  reduction to a 1-dimensional problem) can be found in any classical
+  mechanics text \citep[e.g.,][\S~14]{Landau:1976a}.} %
+to be hyperbolic, characterized by an eccentricity,
+\(\varepsilon = \bigl( 1 + 4 b^2 / R_0^2\bigr)^{1/2}\), and polar angle of
+closest approach, \(\thm = \cos^{-1} \varepsilon^{-1}\).  The trajectory is
+symmetrical about \(\thm\) and can be written as
+\begin{equation}
+  \label{eq:dust-r-theta}
+  \frac{R\grain(\theta; b)} {R_0} = 
+  \frac{ \tfrac12 \bigl( \varepsilon^2 - 1 \bigr)} {\varepsilon \cos(\theta - \thm) - 1} \ , 
+\end{equation}
+with a total deflection angle of \(2 \thm\), which is equal to
+\(90^\circ\) when \(b = 0.5 R_0\).  If the incoming dust grains initially
+travel along parallel trajectories with varying \(b\), but the same
+\(v_\infty\), then deflection by the radiative force will form a bow wave
+around the radiation source, as shown in
+Figure~\ref{fig:dust-trajectories}.  However, the inner edge of the
+bow wave, \(R_{\text{in}}(\theta)\) is not given by the closest approach
+along individual trajectories, \(R\grain(\thm; b)\), but instead must
+found by minimizing \(R\grain(\theta; b)\) over all \(b\) for each value of
+\(\theta\), which yields
+\begin{equation}
+  \label{eq:dust-r-in}
+  \frac{R_{\text{in}}(\theta)} {R_0} = \frac{2}{1 + \cos\theta} \ .
+\end{equation}
+This is the polar form of the equation for the confocal parabola,
+which we have already discussed in detail in \S~\ref{sec:conic} and
+Appendix~\ref{app:parabola}.
+
+The length scale, \(R_0\), of the bow wave depends on the grain
+properties via the combination \(\xsec \Qp / m\grain\).  For grains of
+size \(a\grain\) and internal density \(\rho\grain\), we have
+\(\xsec / m\grain \approx (a\grain \rho\grain)^{-1}\).  For radiation with
+wavelength smaller than the grain size, \(\lambda < a\grain\), the
+efficiency is \(\Qp \sim 1\), whereas for \(\lambda > a\grain\) it is
+\(\Qp \sim a\grain/\lambda\).  Therefore, we would expect \(R_0\) to be almost
+independent of grain size for small grains, but to vary as
+\(R_0 \propto a\grain^{-1}\) for large grains, where small/large is relative
+to the peak wavelength of the radiation source.
+
 \begin{figure*}

### 2017-11-14 papers/Paper1/app-dust-wave.tex
Make start on gas-grain drag description

@@
 \newcommand\Qp{\ensuremath{Q_{\text{p}}}}
-\newcommand{\grain}{\ensuremath{_{\text{g}}}}
+\newcommand{\grain}{\ensuremath{_{\text{d}}}}
 \newcommand{\xsec}{\ensuremath{\sigma\grain}}
@@
 \(R_0 \propto a\grain^{-1}\) for large grains, where small/large is relative
-to the peak wavelength of the radiation source.
+to the peak wavelength of the radiation source.  In principle, a
+polydisperse population of grains could produce a blurring of the
+observed bow wave, but only if large grains contribute significantly
+to the dust emission.
 
@@
 \end{figure*}
+
+\newcommand\fdrag{\ensuremath{f_{\text{drag}}}}
+\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
+\newcommand\Qdrag{\ensuremath{Q_{\text{drag}}}}
+\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
+
+More realistically, a grain will also be subject to a drag force,
+\(\fdrag\), due to its relative motion with respect to gas or plasma
+particles. If the gas density, velocity, and sound speed are
+\(\rho\gas\), \(v\gas\), and \(\soundspeed\), then a grain with velocity
+\(v\grain\) will experience a drag force
+\begin{equation}
+  \label{eq:dust-fdrag}
+  \fdrag \approx \Qdrag \xsec \rho\gas (v\grain - v\gas)^2 
+\end{equation}
+so long as the relative speed, \(w = v\grain - v\gas\), is supersonic:
+\(\abs{w} > \soundspeed\).  If the grain is charged and immersed in an
+ionized plasma, then the interaction cross section is boosted by a
+factor \(\Qdrag\) with respect to the geometric one due to long-range
+Coulomb interactions \citep{Draine:1979a}.  We neglect the back
+reaction of the dust on the gas motion and assume a uniform background
+gas flow with \(v\gas = -v_\infty\).  We can define a characteristic
+asymptotic drift speed, \(w_0\), to be the value of \(w\) that gives
+\(\fdrag = \frad\) at \(R = R_0\), so that
+\begin{equation}
+  \label{eq:dust-w0}
+  w_0 = \left( \frac{\Qp L} {4\pi c \Qdrag \rho\gas R_0^2} \right)^{1/2}
+\end{equation}
 

### 2017-11-15 papers/Paper1/app-dust-wave.tex
Add figure with on-axis grain trajectories

--- 2017-11-14 papers/Paper1/app-dust-wave.tex
@@
 \(\tau \to 0\).
+
+\subsection{Gas-free bow wave}
+\label{sec:gas-free-bow}
 
@@
 
-The length scale, \(R_0\), of the bow wave depends on the grain
-properties via the combination \(\xsec \Qp / m\grain\).  For grains of
-size \(a\grain\) and internal density \(\rho\grain\), we have
+The apex stagnation radius, \(R_0\), of the bow wave depends on the
+grain properties via the combination \(\xsec \Qp / m\grain\).  For
+grains of size \(a\grain\) and internal density \(\rho\grain\), we have
 \(\xsec / m\grain \approx (a\grain \rho\grain)^{-1}\).  For radiation with
@@
 \(R_0 \propto a\grain^{-1}\) for large grains, where small/large is relative
-to the peak wavelength of the radiation source.
+to the peak wavelength of the radiation source.  In principle, a
+polydisperse population of grains could produce a blurring of the
+observed bow wave, but only if large grains contribute significantly
+to the dust emission.
+
+\newcommand\drag{\ensuremath{_{\text{drag}}}}
+\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
+\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
+\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/dust-coupling-1d}
+  \caption{Dust-gas coupling for an on-axis (purely radial) trajectory
+    with \(\alpha\drag = 0.5\). (a)~Grain velocity (in units of
+    \(v_\infty\)) and radius (in units of \(R_0\)) versus time. (b)~Phase
+    space trajectory. Grain spirals in on point
+    \((x, u) = (\alpha\drag^{-1}, 0)\).}
+  \label{fig:dust-coupling-1d}
+\end{figure}
 
@@
 \end{figure*}
+
+\subsection{Bow wave with gas drag}
+\label{sec:bow-wave-drag}
+
+More realistically, a grain will also be subject to a drag force,
+\(f\drag\), due to its relative motion with respect to gas or plasma
+particles. If the gas density, velocity, and sound speed are
+\(\rho\gas\), \(v\gas\), and \(\soundspeed\), then a grain with velocity
+\(v\grain\) will experience a drag force that is directed opposite to
+the relative velocity, \(w = v\grain - v\gas\).  In the supersonic
+limit, \(\abs{w} \gg \soundspeed\), the magnitude of the force is
+\begin{equation}
+  \label{eq:dust-fdrag}
+  \abs{f\drag} \approx Q\drag \xsec \rho\gas w^2 \ ,
+\end{equation}
+where \(Q\drag\) is a boost factor to account for the increase in
+cross section due to the Coulomb force when a charged grain interacts
+with an ionized plasma \citep{Draine:1979a}.  We neglect the back
+reaction of the dust on the gas motion and assume a uniform background
+gas flow with \(v\gas = -v_\infty\).
+
+Considering the incoming flow on the symmetry axis, at each radius
+there is an asymptotic gas--grain drift speed, \(w\drift\), for which
+the radiative and drag forces exactly cancel, \(f\drag = -\frad\),
+yielding
+\begin{equation}
+  \label{eq:dust-wdrift}
+  w\drift = \left( \frac{\Qp L} {4\pi c Q\drag \rho\gas R^2} \right)^{1/2} \ .
+\end{equation}
+Any deviation of \(w\) from \(w\drift\) produces unbalanced forces
+that tend to restore \(w \to w\drift\).  We define a dimensionless
+coupling coefficient, \(\alpha\drag\), to be the speed of the incoming
+stream in units of the drift velocity at the radiative stagnation
+radius:
+\begin{equation}
+  \label{eq:dust-alpha}
+  \alpha\drag \equiv \frac{v_\infty} {w\drift(R_0)} = \left(
+    Q\drag \frac{R_0 / a\grain} {\rho\grain / \rho\gas}
+  \right)^{1/2} \ ,
+\end{equation}
+where we have used equation~\eqref{eq:dust-r0} and suppressed a
+grain-shape dependent geometric factor of order unity.  If
+\(\alpha\drag \ll 1\), then \(w\drift \gg v_\infty\) out to several times the
+stagnation radius, so the radiation field has no difficulty in
+effectively decoupling the grain from the gas and producing the
+velocity difference, \(w = 2 v_\infty\), that is required to turn the grain
+around and expel it towards the direction whence it came.  However,
+for non-zero \(\alpha\drag\) the \(R^{-1}\) dependence of \(w\drift\)
+(eq.~\eqref{eq:dust-wdrift}) means that the grain will
+\textit{re-couple} to the inflowing gas stream around a radius
+\(\approx R_0 / \alpha\drag \) and be swept in again for another try.  This
+behavior is illustrated in Figure~\ref{fig:dust-coupling-1d}, where it can be seen that
 

### 2017-11-15 papers/Paper1/app-dust-wave.tex
Finish 1-d on-axis dust drag description

@@
   \includegraphics[width=\linewidth]{figs/dust-coupling-1d}
-  \caption{Dust-gas coupling for an on-axis (purely radial) trajectory
-    with \(\alpha\drag = 0.5\). (a)~Grain velocity (in units of
-    \(v_\infty\)) and radius (in units of \(R_0\)) versus time. (b)~Phase
-    space trajectory. Grain spirals in on point
+  \caption{Dust-gas coupling for an on-axis (purely radial)
+    trajectory.  (a)~Grain radial position, \(R/R_0\), gas--grain
+    velocity difference, \(w/v_\infty\), and local asymptotic drift
+    velocity, \(w\drift/v_\infty\), versus time for
+    \(\alpha\drag = 0.5\).  (b)~Phase space (position, velocity)
+    trajectories for \(\alpha\drag = 0\), 0.5, and 2. For
+    \(\alpha\drag > 0\), the grain spirals in on the point
     \((x, u) = (\alpha\drag^{-1}, 0)\).}
@@
 \textit{re-couple} to the inflowing gas stream around a radius
-\(\approx R_0 / \alpha\drag \) and be swept in again for another try.  This
-behavior is illustrated in Figure~\ref{fig:dust-coupling-1d}, where it can be seen that
+\(\approx R_0 / \alpha\drag \) and be swept in again for another try.  A further
+effect of increasing \(\alpha\drag\) is that the grain penetrates closer to
+the star on its initial approach, thanks to the tail wind provided by
+the gas flow.  Both these behaviors are illustrated in
+Figure~\ref{fig:dust-coupling-1d}, where it can be seen that the grain
+inertia means that \(w\) lags behind the changes in \(w\drift\) and
+the phase space trajectory is spiral, converging on the point
+\((R, v) = (R_0 / \alpha\drag, 0)\).
 

### 2017-11-15 Dust-wave/dust-coupling-1d.py

@@ -22,6 +22,7 @@ alpha = 1.0/2.0
 # Time grid
 t = np.linspace(0.0, 60.0, 501)
 soln = odeint(dydt, y0, t, args=(alpha,))
+t0 = t[np.argmin(soln[:, 0])]
 
 # Slippage velocity
 w = 1.0 + soln[:, 1]
@@ -31,14 +32,14 @@ wdrift = 1.0 / alpha / soln[:, 0]
 sns.set_style('ticks')
 sns.set_color_codes('dark')
 fig, (ax, axp) = plt.subplots(2, 1, figsize=(4, 6))
-ax.plot(t, soln[:, 0], label='$x$')
-ax.plot(t, w, label='$w$')
-ax.plot(t, wdrift, ls='--', label='$w_\mathrm{drift}$')
+ax.plot(t - t0, soln[:, 0], label='$R/R_{0}$')
+ax.plot(t - t0, w, label='$w / v_{\infty}$')
+ax.plot(t - t0, wdrift, ls='--', label='$w_\mathrm{drift} / v_{\infty}$')
 
 ax.axhline(1.0/alpha, ls=':', color='k', lw=0.8)
 ax.axhspan(0.0, 1.0, color='k', alpha=0.1)
 ax.legend(title=r"$\alpha_\mathrm{drag} = 0.5$")
-ax.set(xlabel='Time', ylim=[None, 4])
+ax.set(xlabel=r'Time / $(R_{0} / v_{\infty})$', ylim=[-0.3, 4.3])
 t2 = np.linspace(0.0, 20.0, 201)
 soln2 = odeint(dydt, y0, t2, args=(2.0,))
 soln0 = odeint(dydt, y0, t2, args=(0.0,))
@@ -47,11 +48,13 @@ axp.plot(soln0[:, 0], soln0[:, 1], label=r"$\alpha_\mathrm{drag} = 0$")
 axp.plot(soln[:, 0], soln[:, 1], label=r"$\alpha_\mathrm{drag} = 0.5$")
 axp.plot(soln2[:, 0], soln2[:, 1], label=r"$\alpha_\mathrm{drag} = 2$")
 axp.axhline(0, xmax=0.55, color='k', lw=0.5)
-axp.legend(title='Phase space')
-axp.set(xlabel='$x$', ylabel='$u$',
-        xlim=[0, 7], ylim=[-1, 1], yticks=[-1.0, -0.5, 0., 0.5, 1.0])
[…]

### 2017-11-15 Dust-wave/dust-coupling-2d.py
Redo 2-d dust drag figure as grayscale

@@ -7,7 +7,7 @@ figfile = sys.argv[0].replace('.py', '.pdf')
 
 # Impact parameter
 b = 0.001
-stream = streamline(Y0=b, alpha=1.0/2.0)
+stream = streamline(Y0=b, alpha=1.0/2.0, tstop=90, X0=15., n=501)
 sns.set_style('white')
 sns.set_color_codes()
 fig, (ax, axp) = plt.subplots(2, 1, figsize=(4, 6))
@@ -25,9 +25,9 @@ axp.plot(stream['y'], stream['v'], label='$(y, v)$')
 axp.axhline(0, color='k', lw=0.5)
 axp.legend(title='Phase space')
 axp.set(xlabel='$x$, $y$', ylabel='$u$, $v$',
-        xlim=[-3, 5], ylim=[-1.1, 1.1])
+        xlim=[-13, 15], ylim=[-1.1, 1.1])
 
-sns.despine()
+sns.despine(trim=True)
 fig.tight_layout()
 fig.savefig(figfile)
 print(figfile, end='')

### 2017-11-16 papers/Paper1/app-dust-wave.tex
Redo 2-d dust drag figure as grayscale
Describe divergent case and 2d drag trajectories

@@
 \begin{figure}
-  \centering
+  (a)\\
   \includegraphics[width=\linewidth]{figs/dust-trajectories}
+  (b)\\
+  \includegraphics[width=\linewidth]{figs/dust-divergent}
   \caption[Dust grain trajectories]{Dust grain trajectories under
-    influence of a repulsive central \(r^{-2}\) radiative force.  Dust
-    grains approach from the right at a uniform velocity and with a
-    variety of impact parameters (initial \(y\)-coordinate). The
-    central source is marked by a red star at the origin, and its
-    radiative force deflects the trajectories into a hyperbolic shape,
-    each of which reaches a minimum radius marked by a small black
-    square.  The incoming hyperbolic trajectories are traced in gray
-    and the outgoing trajectories are traced in red.  The locus of
-    closest approach of the outgoing trajectories is parabolic in
-    shape (traced by the thick, light gray line) and this constitutes
-    the inner edge of the bow wave. }
+    influence of a repulsive central \(r^{-2}\) radiative force.
+    (a)~A parallel stream of dust grains approach from the right at a
+    uniform velocity and with a variety of impact parameters (initial
+    \(y\)-coordinate). The central source is marked by a red star at
+    the origin, and its radiative force deflects the trajectories into
+    a hyperbolic shape, each of which reaches a minimum radius marked
+    by a small black square.  The incoming hyperbolic trajectories are
+    traced in gray and the outgoing trajectories are traced in red.
+    The locus of closest approach of the outgoing trajectories is
+    parabolic in shape (traced by the thick, light gray line) and this
+    constitutes the inner edge of the bow wave.  (b)~The same but for
+    a divergent stream of dust grains that originates from a source on
+    the \(x\) axis at a distance \(D = 10 R_0\) from the origin.  In
+    this case, the inner edge of the bow wave is hyperbolic and the
+    parallel stream result is also shown for comparison.}
   \label{fig:dust-trajectories}
@@
 with a total deflection angle of \(2 \thm\), which is equal to
-\(90^\circ\) when \(b = 0.5 R_0\).  If the incoming dust grains initially
-travel along parallel trajectories with varying \(b\), but the same
-\(v_\infty\), then deflection by the radiative force will form a bow wave
-around the radiation source, as shown in
-Figure~\ref{fig:dust-trajectories}.  However, the inner edge of the
-bow wave, \(R_{\text{in}}(\theta)\) is not given by the closest approach
-along individual trajectories, \(R\grain(\thm; b)\), but instead must
-found by minimizing \(R\grain(\theta; b)\) over all \(b\) for each value of
-\(\theta\), which yields
+\(90^\circ\) when \(b = 0.5 R_0\).
+
+\subsubsection{Parallel dust stream}
+\label{sec:dust-parallel}
+
+If the incoming dust grains initially travel along parallel
+trajectories with varying \(b\), but the same \(v_\infty\), then deflection
+by the radiative force will form a bow wave around the radiation
+source, as shown in Figure~\ref{fig:dust-trajectories}.  However, the
+inner edge of the bow wave, \(R_{\text{in}}(\theta)\) is not given by the
+closest approach along individual trajectories, \(R\grain(\thm; b)\),
+but instead must found by minimizing \(R\grain(\theta; b)\) over all
+\(b\) for each value of \(\theta\), which yields
 \begin{equation}
@@
 
-The apex stagnation radius, \(R_0\), of the bow wave depends on the
+The apex turn-around radius, \(R_0\), of the bow wave depends on the
 grain properties via the combination \(\xsec \Qp / m\grain\).  For
@@
 to the dust emission.
+
+\subsubsection{Divergent dust stream}
+\label{sec:dust-divergent}
+
+If the dust grains are assumed to originate from a second point
+source, located at a distance \(D\) from the radiation source, then
+the incoming stream will be divergent instead of plane parallel.  The
+individual streamlines are not affected by this change and are still
+described by equation~\eqref{eq:dust-r-theta}, except that the
+trajectory axes for \(b > 0\) are no longer aligned with the global
+symmetry axis, so we must make the substitution
+\(\theta \to \theta + \theta_1(b)\), where \(\sin \theta_1 = b / D\) (see
+Fig.~\ref{fig:crw-schema}). We parametrize the degree of divergence as
+\(\mu = R_0 / D\) and, as before, \(R\grain(\theta + \theta_1(b, \mu); b)\) is
+minimized over all trajectories to find the shape of the bow wave's
+inner edge.  This time, the result is a confocal hyperbola:
+\begin{equation}
+  \label{eq:dust-divergent-r-in}
+  \frac{R_{\text{in}}(\theta; \mu)} {R_0} = \frac{1 + \varepsilon_\mu}{1 + \varepsilon_\mu\cos\theta} \ ,
+\end{equation}
+where the eccentricity is (to first order in \(\mu\))
+\( \varepsilon_\mu = (1 - 2\mu)^{-1}\).  An example is shown in
+Figure~\ref{fig:dust-trajectories} for \(\mu = 0.1\).  Unsurprisingly,
+the resulting bow shape is more open than in the parallel stream case,
+increasingly so with increasing \(\mu\).  The planitude and alatude are
+both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\).
 
@@
     \(\alpha\drag = 0.5\).  (b)~Phase space (position, velocity)
-    trajectories for \(\alpha\drag = 0\), 0.5, and 2. For
-    \(\alpha\drag > 0\), the grain spirals in on the point
+    trajectories for \(\alpha\drag = 0\), 0.5, and 2. All trajectories
+    begin in the lower right corner and evolve in a clockwise
+    direction. For \(\alpha\drag > 0\), the grain spirals in on the point
     \((x, u) = (\alpha\drag^{-1}, 0)\).}
@@
     (Fig.~\ref{fig:dust-trajectories}) is shown by the thick dotted
-    line.}
+    line.  Faint patterns visible in the density are numerical
+    aliasing artefacts caused by sparse sampling of the streamlines in
+    the low density regions.}
   \label{fig:dust-wave-coupling}
@@
 reaction of the dust on the gas motion and assume a uniform background
-gas flow with \(v\gas = -v_\infty\).
+gas flow that is perfectly coupled to the incoming dust stream at
+large radii.  So, for the parallel stream case, we have
+\(v\gas = -v_\infty \uvec{x}\) everywhere.
 
@@
 coupling coefficient, \(\alpha\drag\), to be the speed of the incoming
-stream in units of the drift velocity at the radiative stagnation
+stream in units of the drift velocity at the radiative turn-around
 radius:
@@
 \(\alpha\drag \ll 1\), then \(w\drift \gg v_\infty\) out to several times the
-stagnation radius, so the radiation field has no difficulty in
+turn-around radius, so the radiation field has no difficulty in
 effectively decoupling the grain from the gas and producing the
@@
 inertia means that \(w\) lags behind the changes in \(w\drift\) and
-the phase space trajectory is spiral, converging on the point
-\((R, v) = (R_0 / \alpha\drag, 0)\).
+the phase space trajectory is spiral, converging on the stagnation
+point \((R, v) = (R_0 / \alpha\drag, 0)\).
+
+However, this description only applies to grains with impact
+parameter, \(b\), that is exactly zero.  Even a very small finite
+\(b\) means that \(\frad\) has a component perpendicular to the axis,
+which pushes the grain to the side and means that, after re-coupling,
+its second approach is at a much larger impact parameter than its
+first, so it is dragged around the wings of the bow wave before it can
+bounce in and out more than twice.  This is illustrated in
+Figure~\ref{fig:dust-wave-coupling}, which shows grain trajectories
+and the resulting dust density structure, calculated from numerical
+integration of equations~\eqref{eq:dust-rad-force}
+and~\eqref{eq:dust-fdrag} in 2-D cylindrical coordinates.  Results are
+shown for a range of coupling parameters, \(\alpha\drag\).  The
+\(\alpha\drag = 0.25\) case appears qualitatively similar to the no-gas
+case shown in Figure~\ref{fig:dust-trajectories}a, except that the
+inner edge of the bow wave has been shifted to a smaller radius.  The
+\(\alpha\drag = 0.5\) case shows the oscillating trajectories discussed
+above for those grains that come in with a small initial impact
+parameter.  In the \(\alpha\drag = 1.0\) case, the oscillating trajectories
+are more confined, forming a thick shell around \(R_0\).  In the
+\(\alpha\drag = 2.0\) case, the shell is much thinner and concentrated at
+the inner rim.  As \(\alpha\drag\) increases, the oscillations are damped
+further so that the stagnation radius \(R_0 / \alpha\drag\) becomes a good
+approximation to the apex radius of the density wave.  All the cases
+illustrated are for a parallel incident stream, but a divergent stream
+gives qualitatively similar behavior.
 

### 2017-11-16 Dust-wave/dust-divergent.py

@@ -6,9 +6,9 @@ import seaborn as sns
 figfile = sys.argv[0].replace('.py', '.pdf')
 NTH = 4001
 MU = 1./10.
-sns.set_style('white')
+sns.set_style('ticks')
 sns.set_color_codes('dark')
-fig, ax = plt.subplots(figsize=(7, 3))
+fig, ax = plt.subplots(figsize=(4, 4))
 blist = np.linspace(0.0, 6.0) + 0.01
 thmlist = np.arccos(1./np.sqrt(1.0 + 4.0*blist**2))
 for thm, b in zip(thmlist, blist):
@@ -28,16 +28,22 @@ for thm, b in zip(thmlist, blist):
     ax.plot(x[m_out], y[m_out], '-', color='r', alpha=0.8, lw=0.5)
 thm_grid = np.linspace(0.0, np.pi, 200)
 rm = 2.0/(1.0 + np.cos(thm_grid))
+ecc = 1.0/(1.0 - (3/2)*MU)**(4/3)
+rmh = (1.0 + ecc)/(1.0 + ecc*np.cos(thm_grid))
+rmh[rmh < 0.0] = np.nan
 xlocus = rm*np.cos(thm_grid)
 ylocus = rm*np.sin(thm_grid)
 ax.plot(xlocus, ylocus, '-', color='k', alpha=0.2, lw=3)
+xlocus = rmh*np.cos(thm_grid)
+ylocus = rmh*np.sin(thm_grid)
+ax.plot(xlocus, ylocus, '-', color='k', alpha=0.2, lw=3)
 
 ax.plot([0.0], [0.0], '*', color='r')
-ax.set(xlim=[-3, 11], ylim=[-0.1, 5.9],
+ax.set(xlim=[-3.1, 3.9], ylim=[-0.1, 6.9],
        xlabel="$x / R_0$",
        ylabel="$y / R_0$")
 ax.set_aspect('equal')
-sns.despine()
+sns.despine(trim=True)
 fig.tight_layout()
 fig.savefig(figfile)
 print(figfile, end='')

### 2017-11-16 Quadric-shapes/dust-trajectories.py

@@ -5,9 +5,9 @@ import seaborn as sns
 
 figfile = sys.argv[0].replace('.py', '.pdf')
 NTH = 4001
-sns.set_style('white')
+sns.set_style('ticks')
 sns.set_color_codes('dark')
-fig, ax = plt.subplots(figsize=(5, 5))
+fig, ax = plt.subplots(figsize=(4, 4))
 blist = np.linspace(0.0, 6.0) + 0.01
 thmlist = np.arccos(1./np.sqrt(1.0 + 4.0*blist**2))
 for thm in thmlist:
@@ -30,10 +30,10 @@ ylocus = rm*np.sin(thm_grid)
 ax.plot(xlocus, ylocus, '-', color='k', alpha=0.2, lw=3)
 
 ax.plot([0.0], [0.0], '*', color='r')
-ax.set(xlim=[-3, 3], ylim=[-0.1, 5.9],
+ax.set(xlim=[-3.1, 3.9], ylim=[-0.1, 6.9],
        xlabel="$x / R_0$",
        ylabel="$y / R_0$")
-sns.despine()
+sns.despine(trim=True)
 fig.tight_layout()
 fig.savefig(figfile)
 print(figfile, end='')

### 2017-11-17 papers/Paper1/app-dust-wave.tex
Re-organize the dust wave section a bit

@@
 which we have already discussed in detail in \S~\ref{sec:conic} and
-Appendix~\ref{app:parabola}.
-
-The apex turn-around radius, \(R_0\), of the bow wave depends on the
-grain properties via the combination \(\xsec \Qp / m\grain\).  For
-grains of size \(a\grain\) and internal density \(\rho\grain\), we have
-\(\xsec / m\grain \approx (a\grain \rho\grain)^{-1}\).  For radiation with
-wavelength smaller than the grain size, \(\lambda < a\grain\), the
-efficiency is \(\Qp \sim 1\), whereas for \(\lambda > a\grain\) it is
-\(\Qp \sim a\grain/\lambda\).  Therefore, we would expect \(R_0\) to be almost
-independent of grain size for small grains, but to vary as
-\(R_0 \propto a\grain^{-1}\) for large grains, where small/large is relative
-to the peak wavelength of the radiation source.  In principle, a
-polydisperse population of grains could produce a blurring of the
-observed bow wave, but only if large grains contribute significantly
-to the dust emission.
+Appendix~\ref{app:parabola}.  Its planitude and alatude are
+\(\Gamma = \Lambda = 2\) and these are unchanged under projection at any
+inclination.
 
@@
     velocity, \(w\drift/v_\infty\), versus time for
-    \(\alpha\drag = 0.5\).  (b)~Phase space (position, velocity)
+    \(\alpha\drag = 0.5\).  The behavior is typical of the dynamics of a
+    damped harmonic oscillator. (b)~Phase space (position, velocity)
     trajectories for \(\alpha\drag = 0\), 0.5, and 2. All trajectories
@@
   \caption{Dust grain trajectories under influence of gas drag in
-    addition a repulsive central radiative force.  The dust
-    streamlines are shown in blue and the dust density as a linear
-    color scale, with maximum (white-yellow) of twice the ambient dust
-    density.  Results are shown for four values of the drag parameter
-    (see text): \(\alpha_\text{drag} = 0.25\), \(0.5\), \(1.0\), and
-    \(2.0\). The shape of the bow wave for the drag-free case
-    (Fig.~\ref{fig:dust-trajectories}) is shown by the thick dotted
-    line.  Faint patterns visible in the density are numerical
-    aliasing artefacts caused by sparse sampling of the streamlines in
-    the low density regions.}
+    addition to a repulsive central radiative force.  The dust
+    streamlines are shown as black lines with arrows and the dust
+    density as a linear gray scale, with maximum (black) of twice the
+    ambient dust density.  Results are shown for four values of the
+    drag parameter (see text): \(\alpha_\text{drag} = 0.25\), \(0.5\),
+    \(1.0\), and \(2.0\). The shape of the bow wave for the drag-free
+    case (Fig.~\ref{fig:dust-trajectories}) is shown by the thick
+    dotted line.  Faint patterns visible in the density away from the
+    bow wave are numerical aliasing artefacts caused by sparse
+    sampling of the streamlines in the low density regions.}
   \label{fig:dust-wave-coupling}
@@
 \(v\grain\) will experience a drag force that is directed opposite to
-the relative velocity, \(w = v\grain - v\gas\).  In the supersonic
-limit, \(\abs{w} \gg \soundspeed\), the magnitude of the force is
+the relative velocity, \(\bm{w} = \bm{v}\grain - \bm{v}\gas\).  In the
+supersonic limit, \(w \equiv \abs{\bm{w}} \gg \soundspeed\), the magnitude of
+the force is
 \begin{equation}
@@
 \end{equation}
-where \(Q\drag\) is a boost factor to account for the increase in
-cross section due to the Coulomb force when a charged grain interacts
-with an ionized plasma \citep{Draine:1979a}.  We neglect the back
-reaction of the dust on the gas motion and assume a uniform background
-gas flow that is perfectly coupled to the incoming dust stream at
-large radii.  So, for the parallel stream case, we have
-\(v\gas = -v_\infty \uvec{x}\) everywhere.
+where \(Q\drag\) is an efficiency factor (which may be smaller or
+greater than unity) that accounts for details such as sticking
+probability and the boost in cross section due to the Coulomb force
+when a charged grain interacts with an ionized plasma
+\citep{Draine:1979a}.  We neglect the back reaction of the dust on the
+gas motion and assume a uniform background gas flow that is perfectly
+coupled to the incoming dust stream at large radii.  So, for the
+parallel stream case, we have \(\bm{v}\gas = -v_\infty \uvec{x}\) everywhere.
 
@@
 Any deviation of \(w\) from \(w\drift\) produces unbalanced forces
-that tend to restore \(w \to w\drift\).  We define a dimensionless
-coupling coefficient, \(\alpha\drag\), to be the speed of the incoming
-stream in units of the drift velocity at the radiative turn-around
-radius:
+that tend to restore \(w \to w\drift\), although the grain inertia means
+that this will not happen instantaneously, so that if \(w\drift\)
+varies rapidly along a streamline, then changes in \(w\) will lag
+behind.  We define a dimensionless coupling coefficient,
+\(\alpha\drag\), to be the speed of the incoming stream in units of the
+drift velocity at the radiative turn-around radius:
 \begin{equation}
@@
 effectively decoupling the grain from the gas and producing the
-velocity difference, \(w = 2 v_\infty\), that is required to turn the grain
-around and expel it towards the direction whence it came.  However,
-for non-zero \(\alpha\drag\) the \(R^{-1}\) dependence of \(w\drift\)
-(eq.~\eqref{eq:dust-wdrift}) means that the grain will
+velocity difference that is required to turn the grain around and
+expel it towards the direction whence it came (\(w = 2 v_\infty\)).
+However, for non-zero \(\alpha\drag\) the \(R^{-1}\) dependence of
+\(w\drift\) (eq.~\eqref{eq:dust-wdrift}) means that the grain will
 \textit{re-couple} to the inflowing gas stream around a radius
-\(\approx R_0 / \alpha\drag \) and be swept in again for another try.  A further
-effect of increasing \(\alpha\drag\) is that the grain penetrates closer to
-the star on its initial approach, thanks to the tail wind provided by
-the gas flow.  Both these behaviors are illustrated in
-Figure~\ref{fig:dust-coupling-1d}, where it can be seen that the grain
-inertia means that \(w\) lags behind the changes in \(w\drift\) and
-the phase space trajectory is spiral, converging on the stagnation
-point \((R, v) = (R_0 / \alpha\drag, 0)\).
+\(\approx R_0 / \alpha\drag \) and be swept back in again for another approach to
+the source.  A further effect of increasing \(\alpha\drag\) is that the
+grain penetrates closer to the star on its initial approach, thanks to
+the tail wind provided by the gas flow.  Both these behaviors are
+illustrated in Figure~\ref{fig:dust-coupling-1d}, where the inertial
+lag of \(w\) behind \(w\drift\) means that the phase space trajectory
+(panel b) is a spiral, which converges on the stagnation point
+\((R, v) = (R_0 / \alpha\drag, 0)\). The cases \(\alpha\drag = 0.5\) and
+\(\alpha\drag = 2\) are shown, and it can be seen that with larger
+\(\alpha\drag\) the oscillations about the stagnation radius are
+significantly damped.
 
@@
 shown for a range of coupling parameters, \(\alpha\drag\).  The
-\(\alpha\drag = 0.25\) case appears qualitatively similar to the no-gas
+\(\alpha\drag = 0.25\) case appears qualitatively similar to the no-drag
 case shown in Figure~\ref{fig:dust-trajectories}a, except that the
-inner edge of the bow wave has been shifted to a smaller radius.  The
+inner edge of the bow wave has been shifted to a smaller radius.
+Recoupling of the outgoing streamlines to the gas flow does occur
+eventually, but on length scales larger than shown in the figure. The
 \(\alpha\drag = 0.5\) case shows the oscillating trajectories discussed
@@
 illustrated are for a parallel incident stream, but a divergent stream
-gives qualitatively similar behavior.
+gives qualitatively similar behavior.  We propose the term
+\textit{dragoid} for the 3-dimensional shapes of the bow waves, found
+by rotating results such as Figure~\ref{fig:dust-wave-coupling} about
+the symmetry axis.
+
+\subsection{Applicability of the bow wave models}
+\label{sec:dust-applicability}
+
+The apex turn-around radius, \(R_0\), of the bow wave depends on the
+grain properties via the combination \(\xsec \Qp / m\grain\).  For
+grains of size \(a\grain\) and internal density \(\rho\grain\), we have
+\(\xsec / m\grain \approx (a\grain \rho\grain)^{-1}\).  For radiation with
+wavelength smaller than the grain size, \(\lambda < a\grain\), the
+efficiency is \(\Qp \sim 1\), whereas for \(\lambda > a\grain\) it is
+\(\Qp \sim a\grain/\lambda\).  Therefore, we would expect \(R_0\) to be almost
+independent of grain size for small grains, but to vary as
+\(R_0 \propto a\grain^{-1}\) for large grains, where small/large is relative
+to the peak wavelength of the radiation source.  In principle, a
+polydisperse population of grains could produce a blurring of the
+observed bow wave, but only if large grains contribute significantly
+to the dust emission.
+
+\TODO{Variation of \(\alpha\drag\) with grain size, charged grains.}
+
+\TODO{Lorentz force, Larmor radius}
+
+\TODO{Back-reaction on gas, \(\alpha\drag \to \infty\), recovery of drag-free
+  results but with increased effective grain mass.}
+
+\section{Apparent shapes of projected dragoids}
+\label{sec:dust-wave-apparent}
 

### 2017-11-17 papers/Paper1/app-parabola.tex
Finish Appendix B on ancantoids!
Re-organize the dust wave section a bit

@@
 where we have ``baked in'' knowledge of the planitude,
-\(\Pi = R_c/R_0\) (see \S~\ref{sec:plan-alat-bow}). The projected
+\(\Pi = R_{\C}/R_0\) (see \S~\ref{sec:plan-alat-bow}). The projected
 plane-of-sky coordinates of the tangent line follow from
@@
 for all values of the true planitude \(\Pi\), as is shown by the black
-lines in Figure~\ref{fig:quadric-projection}a.  Also, for the special
-case of the confocal paraboloid, \(\Pi = 2\), we have \(\Pi' = \Pi\) by
-equation~\eqref{eq:parabola-Pi-prime} for all inclinations, so its
-shape is unaffected by projection. Finally, the projected alatude can
+lines in Figure~\ref{fig:quadric-projection}a. The projected alatude can
 be found as
@@
 \end{equation}
+For the special case of the confocal paraboloid,
+\(\Pi = \Lambda = 2\), we have \(\Pi' = \Pi\) and
+\(\Lambda' = \Lambda\) by equations~\eqref{eq:parabola-Pi-prime}
+and~\eqref{eq:parabola-Lambda-prime} for all inclinations, so its
+shape is unaffected by projection.
 %%% Local Variables:

### 2017-11-17 papers/Paper1/sec-thin-shell.tex
Re-organize the dust wave section a bit

@@
     the wilkinoid track (white) and the convergence of the cantoid
-    tracks (purple) to this as \(\beta \to 0\).}
+    tracks (purple) to the wilkinoid as \(\beta \to 0\).}
   \label{fig:convergence-cantoid-wilkinoid}

### 2017-11-17 papers/Paper1/app-dust-equations.tex
New appendix on the dust grain dynamics equations in 2D

\section{Equations of motion for grains with radiation and gas drag}
\label{sec:equat-moti-grains}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/dust-couple-div-stream}
  \caption{Divergent dragoids}
  \label{fig:divergent-dragoids}
\end{figure}

To find the dust grain trajectories \(R\grain(\theta)\) in the presence of
radiation and drag forces (\S~\ref{sec:bow-wave-drag}), we numerically
integrate the equations of motion. We define dimensionless cylindrical
polar coordinates,
\begin{equation}
  \label{eq:dust-XY}
  (X, Y) = \left(\frac{R\grain(\theta) \cos\theta } {R_0}, \ 
    \frac{R\grain(\theta) \sin\theta } {R_0}\right)
  \ ,
\end{equation}
and dust grain velocities,
\begin{equation}
  \label{eq:dust-UV}
  (U, V) = \left( \frac{\bm{v}\grain \cdot \uvec{x}} {v_\infty}, \ 
  \frac{\bm{v}\grain \cdot \uvec{y}} {v_\infty}\right) \ ,
\end{equation}
where \(\uvec{x}\) and \(\uvec{y}\) are unit vectors along the \(X\)
and \(Y\) axes (parallel and perpendicular, respectively, to the
symmetry axis).  The grain equation of motion then follows from
equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0},
\ref{eq:dust-fdrag}--\ref{eq:dust-alpha}) as the following set of
coupled differential equations:
\begin{gather}
  \label{eq:dust-motion}
  \begin{aligned}
    \frac{d X}{d t} &= U \quad\quad
    \frac{d Y}{d t} = V \\
    \frac{d U}{d t} &= \frac12 \left[  
      X \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 \left(U - U_1\right)
    \right] \\
    \frac{d V}{d t} &= \frac12 \left[  
      Y \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 \left(V - V_1\right)
    \right] \ ,
  \end{aligned}
\end{gather}
where \((U_1, V_1)\) are the components of the gas velocity (assumed
fixed), given by
\begin{equation}
  \label{eq:dust-gas-velocities}
  (U_1, V_1) = 
  \begin{cases}
    \text{parallel stream} & (-1, 0)\\
    \text{divergent stream} &
    \left( \dfrac{X - \mu^{-1}}{R_1},\ \dfrac{Y}{R_1}\right) \ ,
  \end{cases}
\end{equation}
where
\begin{equation}
  \label{eq:dust-R1}
  R_1 = \left( \bigl(X - \mu^{-1}\bigr)^2 + Y^2 \right)^{1/2}
\end{equation}
is the distance from the second source, located at
\((X, Y) = (\mu^{-1}, 0)\).

Equations~\eqref{eq:dust-motion} are integrated

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

### 2017-11-17 Dust-wave/dragoid_shape.py
Try to get projection working for divergent dragoids
But it doesn't work at the moment.

@@ -4,10 +4,19 @@ from astropy.table import Table
 from bow_projection import Spline_R_theta_from_grid
 
 class Dragoid(object):
-    def __init__(self, alpha):
-        astring = f'-alpha{int(100*alpha):03d}.tab'
+    def __init__(self, alpha, mu=None):
+        if mu is None:
+            astring = 'dust-couple-stream'
+        else:
+            astring = 'dust-couple-div-stream'
+        astring += f'-alpha{int(100*alpha):03d}'
+        if mu is not None:
+            astring += f'-mu{int(100*mu):03d}'
+        astring += '.tab'
         self.label = fr"$\alpha_\mathrm{{drag}} =  {alpha:.02f}$"
-        t = Table.read('dust-couple-stream' + astring, format='ascii.tab')
+        if mu is not None:
+            self.label += '\n' + fr"$\mu =  {mu:.02f}$"
+        t = Table.read(astring, format='ascii.tab')
         dth = np.pi/len(t)
         self.thgrid = t['theta'] + 0.5*dth
         self.Rgrid = t['R']/t['R'][0]

### 2017-11-17 Dust-wave/test_xyprime_div_dragoid.py

@@ -1,0 +1,55 @@
+import sys
+import numpy as np
+from matplotlib import pyplot as plt
+import seaborn as sns
+from bow_projection import (xyprime_t, theta_infinity, theta_0_90,
+                            characteristic_radii_projected)
+from dragoid_shape import Dragoid
+
+figfile = sys.argv[0].replace('.py', '.pdf')
+
+sns.set_style('ticks')
+fig, axes = plt.subplots(2, 2, figsize=(8, 8))
+
+# For some reason, exactly 30.0 had problems with R0p
+inclinations = [0.0, 15.0, 30.01, 45.0, 60.0, 75.01]
+linewidths = [2.4, 2.0, 1.6, 1.2, 0.8, 0.4]
+colors = sns.color_palette('magma_r', n_colors=len(inclinations))
+
+alphas = [1.0, 1.0, 4.0, 4.0]
+mus = [0.05, 0.2, 0.05, 0.2]
+for alpha, mu, ax in zip(alphas, mus, axes.flat):
+    shape = Dragoid(alpha=alpha, mu=mu)
+    th_inf = theta_infinity(shape)
+    for inc_dg, color, lw in zip(inclinations, colors, linewidths):
+        inc = np.radians(inc_dg)
+        th0, th90 = theta_0_90(inc, shape)
+        th = np.linspace(th0, th_inf, 301)
+        xp, yp = xyprime_t(th, inc, shape)
+        m = np.isfinite(xp) & np.isfinite(yp)
+        if m.sum() == 0:
+            # Case of no tangent line at all at this inclination
+            continue
+        xxp = np.concatenate((xp[m][::-1], xp[m]))
+        yyp = np.concatenate((-yp[m][::-1], yp[m]))
+        radii = characteristic_radii_projected(inc, shape)        
+        R0p = radii['R_0 prime']
+        ax.plot(xxp/R0p, yyp/R0p,
+                label=fr"$i = {inc_dg:.0f}^\circ$",
+                color=color, lw=1.5*lw)
+
+    ax.plot([0], [0], 'o', color='k')
+
+    ax.legend(title="Dragoid " + shape.label, ncol=2, loc="center left")
+    ax.set(
+        xlabel=r"$x' / R_0'$",
+        ylabel=r"$y' / R_0'$",
+        xlim=[-7, 3],
+        ylim=[-5, 5],
+    )
+    ax.set_aspect('equal', adjustable='box')
+
+sns.despine()
[…]

### 2017-11-18 papers/Paper1/app-dust-equations.tex
Try to get projection working for divergent dragoids
But it doesn't work at the moment.
Re-run the dragoid dynamic models with much higher resolution
This now looks a lot better.  Also, use lowess smoothing on the
inclination tracks for dragoids

@@
 
-Equations~\eqref{eq:dust-motion} are integrated
+Equations~\eqref{eq:dust-motion} are integrated using the python
+wrapper \texttt{scipy.integrate.odeint} to the Fortran ODEPACK library
+\citep{Hindmarsh:1983a, Jones:2001a}, with results shown in
+Figure~\ref{fig:dust-wave-coupling} for parallel-stream cases and
+Figure~\ref{fig:divergent-dragoids} for divergent-stream cases.
 

### 2017-11-18 papers/Paper1/app-dust-wave.tex
Try to get projection working for divergent dragoids
But it doesn't work at the moment.
Re-run the dragoid dynamic models with much higher resolution
This now looks a lot better.  Also, use lowess smoothing on the
inclination tracks for dragoids

@@
 illustrated are for a parallel incident stream, but a divergent stream
-gives qualitatively similar behavior.  We propose the term
+gives qualitatively similar behavior, as shown in
+Appendix~\ref{sec:equat-moti-grains}.  We propose the term
 \textit{dragoid} for the 3-dimensional shapes of the bow waves, found
@@
 
-\section{Apparent shapes of projected dragoids}
+\subsection{Apparent shapes of projected dragoids}
 \label{sec:dust-wave-apparent}
@@
   \includegraphics[width=\linewidth]{figs/test_xyprime_dragoid}
-  \caption{Plane-of-sky shapes for dragoids.}
+  \caption{Plane-of-sky shapes for parallel-stream dragoids.}
   \label{fig:dragoid-xy-prime}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/test_xyprime_div_dragoid}
+  \caption{Plane-of-sky shapes for divergent-stream dragoids.}
+  \label{fig:dragoid-div-xy-prime}
 \end{figure}

### 2017-11-18 Dust-wave/dragoid-R90-vs-Rc.py

@@ -1,5 +1,7 @@
 import sys
 import numpy as np
+from scipy.interpolate import interp1d
+import statsmodels.api as sm
 from matplotlib import pyplot as plt
 import matplotlib.ticker
 import seaborn as sns
@@ -7,16 +9,11 @@ import bow_projection as bp
 import dragoid_shape
 import bow_diagnostic
 
-bp.N_NEIGHBORHOOD = 50
-bp.DEGREE_POLY_NEIGHBORHOOD = 2
-bp.SCALE_NEIGHBORHOOD = 0.2
-bp.DEGREE_POLY_NEIGHBORHOOD_90 = 2
-bp.SCALE_NEIGHBORHOOD_90 = 0.01
 
 plotfile = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
-fig, ax = plt.subplots(figsize=(5, 5))
+fig, ax = plt.subplots(figsize=(4, 4))
 
 Rc_grid = np.linspace(0.0, 10.0, 2000)
 R90_T0_grid = np.sqrt(2*Rc_grid)
@@ -33,44 +30,74 @@ ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
 # Put a cross at the Wilkinoid coordinates: [5/3, sqrt(3)]
 ax.plot([5./3.], [np.sqrt(3.0)], '+', c='w', ms=10, alpha=1.0)
 # And plot the projected wilkinoids 
+bp.N_NEIGHBORHOOD = 50
+bp.DEGREE_POLY_NEIGHBORHOOD = 2
+bp.SCALE_NEIGHBORHOOD = 0.03
+bp.DEGREE_POLY_NEIGHBORHOOD_90 = 2
+bp.SCALE_NEIGHBORHOOD_90 = 0.01
 shape = bp.wilkinoid_R_theta
 th_inf = bp.theta_infinity(shape)
 inc = np.linspace(0.0, th_inf - np.pi/2, 50)
 tab = bow_diagnostic.parameter_table(inc, shape)
 Rc, R90 = tab['tilde R_c prime'], tab['tilde R_90 prime']
 ax.plot(Rc, R90, '-', c='w', label="_nolabel_", lw=0.6, alpha=0.9)
-ax.plot(Rc, R90, 'x', ms=0.2, c='w', label="_nolabel_", alpha=0.5)
[…]

### 2017-11-18 Dust-wave/dragoid_shape.py

@@ -1,10 +1,11 @@
 import sys
 import numpy as np
 from astropy.table import Table
+import statsmodels.api as sm
 from bow_projection import Spline_R_theta_from_grid
 
 class Dragoid(object):
-    def __init__(self, alpha, mu=None):
+    def __init__(self, alpha, mu=None, lowess_frac=None):
         if mu is None:
             astring = 'dust-couple-stream'
         else:
@@ -22,6 +23,11 @@ class Dragoid(object):
         self.Rgrid = t['R']/t['R'][0]
         self.thgrid = np.concatenate([-self.thgrid[::-1], self.thgrid])
         self.Rgrid = np.concatenate([self.Rgrid[::-1], self.Rgrid])
+        if lowess_frac is not None:
+            # Optionally smooth the shape before fitting spline
+            self.Rgrid = sm.nonparametric.lowess(
+                self.Rgrid, self.thgrid, frac=lowess_frac,
+                is_sorted=True, return_sorted=False)
         self.splinefit = Spline_R_theta_from_grid(
               theta_grid=self.thgrid, R_grid=self.Rgrid)
 
@@ -46,7 +52,7 @@ if __name__ == "__main__":
     alphas = [0.25, 0.5, 1.0, 2.0] + [4.0, 4.0]
     mus = [None]*4 + [0.2, 0.8]
     for alpha, mu in zip(alphas, mus):
-        shape = Dragoid(alpha=alpha, mu=mu)
+        shape = Dragoid(alpha=alpha, mu=mu, lowess_frac=None)
         ax.plot(np.degrees(shape.thgrid), shape.Rgrid,
                 color='b', alpha=0.2, lw=2, label='_nolabel_')
         ax.plot(th_dg, shape(th), lw=0.8, label=shape.label)

### 2017-11-18 Dust-wave/dust-couple-div-stream.py

@@ -12,9 +12,9 @@ sns.set_color_codes()
 fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(6, 4))
 alphas = [1.0, 1.0, 4.0, 4.0]
 mus = [0.05, 0.2, 0.2, 0.8]
-nb = 501
-bgrid = 0.001 + np.linspace(0.0, 5.0, 1001)
-ibspecial = [5, 20, 50, 100, 200, 300]
+nb = 25*200 + 1
+bgrid = 0.001 + np.linspace(0.0, 5.0, nb)
+ibspecial = 25*np.array([1, 4, 10, 20, 40, 60])
 nth = 200
 thm_grid = np.linspace(0.0, np.pi, nth)
 dth = np.pi/nth
@@ -32,7 +32,7 @@ for alpha, mu, ax in zip(alphas, mus, axes.flat):
     # Launch grains on a uniform grid of th1
     # Make sure it fills the plot
     th1max = np.arctan2(ymax/zoom, 1.0/mu - xmax/zoom)
-    th1grid = 0.001*mu + np.linspace(0.0, th1max, 1001)
+    th1grid = 0.001*mu + np.linspace(0.0, th1max, nb)
     bgrid = np.sin(th1grid)/mu
 
     # Hyperbola solution for drag-free case, but scaling mu by alpha
@@ -50,7 +50,7 @@ for alpha, mu, ax in zip(alphas, mus, axes.flat):
         assert Rlaunch > 0.0
         X0 = 1./mu - Rlaunch*np.cos(th1)
         Y0 = Rlaunch*np.sin(th1)
-        s = streamline(X0=X0, Y0=Y0, tstop=30, alpha=alpha, mu=mu, n=10001)
+        s = streamline(X0=X0, Y0=Y0, tstop=30, alpha=alpha, mu=mu, n=30001)
         # ax.plot(s['x'], s['y'], color='k', lw=0.5)
         # Accumulate (x, y) points in a long list
         xx.extend(s['x'])

### 2017-11-18 Dust-wave/dust-couple-stream.py

@@ -11,9 +11,9 @@ sns.set_style('white')
 sns.set_color_codes()
 fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(6, 4))
 alphas = [1.0/4.0, 1.0/2.0, 1.0, 2.0]
-nb = 501
-bgrid = 0.001 + np.linspace(0.0, 5.0, 1001)
-ibspecial = [5, 20, 50, 100, 200, 300]
+nb = 25*200 + 1
+bgrid = 0.001 + np.linspace(0.0, 5.0, nb)
+ibspecial = 25*np.array([1, 4, 10, 20, 40, 60])
 nth = 200
 thm_grid = np.linspace(0.0, np.pi, nth)
 dth = np.pi/nth
@@ -27,7 +27,7 @@ for alpha, ax in zip(alphas, axes.flat):
     xx, yy, ww = [], [], []
     xs, ys = [], []
     for ib, b in enumerate(bgrid):
-        s = streamline(X0=5, Y0=b, tstop=30, alpha=alpha, n=10001)
+        s = streamline(X0=5, Y0=b, tstop=30, alpha=alpha, n=30001)
         # ax.plot(s['x'], s['y'], color='k', lw=0.5)
         # Accumulate (x, y) points in a long list
         xx.extend(s['x'])

### 2017-11-18 papers/Paper1/app-dust-wave.tex
Fill out figure captions for dragoid projections

@@
   \includegraphics[width=\linewidth]{figs/test_xyprime_dragoid}
-  \caption{Plane-of-sky shapes for parallel-stream dragoids.}
+  \caption{Apparent bow shapes in the plane of the sky for
+    parallel-stream dragoids as a function of inclination angle.  Drag
+    coefficient, \(\alpha\drag\) increases from top-left to bottom-right.
+    Inlination \(\abs{i}\) is shown in \(15^\circ\) increments, indicated
+    by line color and thickness (see key).}
   \label{fig:dragoid-xy-prime}
@@
   \includegraphics[width=\linewidth]{figs/test_xyprime_div_dragoid}
-  \caption{Plane-of-sky shapes for divergent-stream dragoids.}
+  \caption{As Fig.~\ref{fig:dragoid-xy-prime} but for divergent stream
+    dragoids.  Drag coefficient increases from top to bottom, while
+    degree of divergence increases from left to right. }
   \label{fig:dragoid-div-xy-prime}
@@
   \includegraphics[width=\linewidth]{figs/dragoid-R90-vs-Rc}
-  \caption{Diagnostic diagram for dragoids}
+  \caption{Apparent projected shapes of dragoids in the
+    \(\Pi'\)--\(\Lambda'\) plane. Colored symbols indicate the
+    \(\abs{i} = 0\) position for selected models (see key).  Thin
+    lines show the inclination-dependent tracks of each model, with
+    tick marks along each track for 20 equal-spaced values of
+    \(\abs{\sin i}\). Gray shaded regions are as in
+    Fig.~\ref{fig:quadric-projection-continued}a.  The wilkinoid track
+    is shown in white. }
   \label{fig:dragoid-Rc-R90}

### 2017-11-19 papers/Paper1/app-dust-wave.tex
Split up the paper again!  Now there are two theory papers

@@
 \label{sec:bow-wave-drag}
-
 More realistically, a grain will also be subject to a drag force,
@@
 \TODO{Back-reaction on gas, \(\alpha\drag \to \infty\), recovery of drag-free
-  results but with increased effective grain mass.}
+  result for \(R_0\) but with increased effective grain mass.}
 
@@
     coefficient, \(\alpha\drag\) increases from top-left to bottom-right.
-    Inlination \(\abs{i}\) is shown in \(15^\circ\) increments, indicated
+    Inclination \(\abs{i}\) is shown in \(15^\circ\) increments, indicated
     by line color and thickness (see key).}

### 2017-11-19 papers/Paper1/dusty-bow-wave.tex
Split up the paper again!  Now there are two theory papers

--- 2017-10-16 papers/Paper1/quadrics-bowshock.tex
@@
-%\RequirePackage{amsmath}
 \documentclass[useAMS, usenatbib, a4paper]{mnras}
@@
 
-% The following is needed to fix the margins if using Letter-size paper
-% REMOVE if your LaTeX uses A4 paper by default
-%\addtolength\topmargin{-1.8cm}
-
-% Standard LaTeX packages
-% \usepackage[varg]{txfonts}
 \usepackage{graphicx}
@@
 
-% Define a fermata symbol for use inline with text
-% 04 Jul 2017 WJH
-% Based on info in Secs 18.4.1 and 24.1 of musixdoc.pdf
-\usepackage{musixtex}
-\makeatletter
-\newcommand\textfermata{%
-  {\let\extractline\relax
-    \setlines10\smallmusicsize \nobarnumbers \nostartrule
-    \staffbotmarg0pt \setclefsymbol1\empty \global\clef@skip0pt
-    \raisebox{0ex}[0ex][0ex]{
-      \startextract\addspace{-\afterruleskip}%
-      \notes\fermataup{-2}\en
-      \zendextract}}}
-\makeatother
-
-% % The \eye command is in the dingbat package, but we need to take care
-% % of a naming conflict with the AMS package
-% \usepackage{savesym}
-% \savesymbol{checkmark}
-% \usepackage{dingbat}
-
-% The "eye" symbol is drawn with the \faEye command of the fontawesome
-% package
-\usepackage{fontawesome}
-% The ``irregular'' symbol is drawn from the Icelandic Sorcery and Witchcraft 
-\usepackage{staves}
-
 % Fonts 
@@
 
-% Definitions needed in abstract
-\newcommand\hii{\ion{H}{ii}}
-
-\title[Bow shock shapes]{True versus apparent shapes of bow shocks and bow waves}
+\title[Bow wave shapes]{True versus apparent shapes of dusty radiative bow waves}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Tarango Yong \& Henney]{
-  Jorge A. Tarango Yong \& William J. Henney\\
+\author[Henney \& Tarango Yong]{
+  William J. Henney \& Jorge A. Tarango Yong\\
   \AddressCRyA
 }
+
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2017}
+\DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\Sin}{\mathcal{S}}
+\DeclareMathOperator{\Cos}{\mathcal{C}}
+\DeclareMathOperator{\Cot}{\mathcal{T}}
+\DeclareMathOperator{\GammaFunc}{\Gamma}
+\newcommand\w{\ensuremath{\mathrm{w}}}
+\newcommand\C{\ensuremath{\mathrm{c}}}
+\providecommand{\abs}[1]{\lvert#1\rvert}
+\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
+\newcommand\TODO[1]{%
+  \begin{center}
+    \framebox{\parbox{0.8\linewidth}{
+        \texttt{\footnotesize\color{red} #1}}}
+  \end{center}}
+
+\newcommand\uvec[1]{\bm{\hat{#1}}}
+\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+
 \begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \maketitle
 \begin{abstract}
-  Astrophysical bow shocks are a common result of the interaction
-  between supersonic plasma flows, such as winds or jets from stars or
-  active galaxies.  Similarly shaped radiation bow waves are produced
-  by the relative motion between dust grains and a luminous source.
-  For cylindrically symmetric bow shocks and waves, we develop a
-  general theory of the effects of inclination angle, and propose a
-  new two-dimensional classification scheme for bow shapes, which is
-  based on dimensionless geometric ratios that can be estimated from
-  observational images.  The two ratios are related to the
-  ``flatness'' of the bow's apex and the ``openness'' of its wings.
-
-  ADD MORE
+  Dusty stellar bow waves result from the action of a star's radiation
+  pressure on a stream of dust grains that is flowing past it.  They
+  are an alternative mechanism to hydrodynamic bow shocks for
+  explaining the curved arcs of infrared emission seen around some
+  stars.  We develop simple cylindrically symmetric models for the
+  dust grain dynamics under the influence of radiation and gas--grain
+  drag forces, which produce bow shapes that we call dragoids.  Using
+  our recently developed two-dimensional classification scheme for
+  projected bow shapes, we then analyze the inclination-dependent
+  tracks of the dragoids in the planitude--alatude plane, finding
+  interesting differences from the wilkinoid, cantoid, and ancantoid
+  shapes of hydrodynamic bow shock models.  We analyze the prospects
+  of using shape analysis of observational datasets to discriminate
+  between different bow models, finding that sample sizes of order 100
+  are required.
 \end{abstract}
 
-\input{sec-intro}
-\input{sec-generic-model}
-\input{sec-projection}
-\input{sec-conic}
-\input{sec-thin-shell}
-\clearpage
+\begin{keywords}
+  hydrodynamics -- stars: winds, outflows
+\end{keywords}
+
+\input{sec-dust-bow-intro}
 \input{app-dust-wave}
-\clearpage
 \input{sec-standing-wave}
-\input{sec-conclusions}
-\clearpage
 \bibliographystyle{mnras}
-%% All references should be put in the BibTeX file bowshocks-biblio.bib
 \bibliography{bowshocks-biblio}
 \appendix
-\input{app-parabola}
-\input{app-rcurv}
-\input{app-r90}
-\input{app-wilkinoid}
+\input{app-dust-equations}
 
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}

### 2017-11-19 papers/Paper1/sec-dust-bow-intro.tex
Split up the paper again!  Now there are two theory papers

--- 2016-09-26 papers/Paper1/sec-intro-proplyd.tex
@@
 \section{Introduction}
-\label{sec:introduction-proplyd}
-
-Proplyds are comet-like structures observed in HII regions like Orion Nebula Cluster (ONC). 
-These objects are interpreted as a D-type Ionization Front (IF) of a photoevaporated flow 
-originated in the protoplanetary disk of a nearby low mass YSO \citep{Johnstone:1998}.
-The pressure of the surrounding gas is not enough to confine this flow \citep{HA:1998}
-may be formed by the interaction of the photoevaporated wind of the proplyds with the stellar wind of \thC{}, which is highly supersonic $(M \sim 100)$.
+\label{sec:introduction}
 
@@
 %%% mode: latex
-%%% TeX-master: "proplyd-bowshocks"
+%%% TeX-master: t
 %%% End:

### 2017-11-20 papers/Paper1/quadrics-bowshock.tex
Add plan of paper to intro of theory paper
Convert first part of quadrics section to planitude-alatude notation
Port the conic figures to the new notation
Move the ancantoid derivation to an appendix
Finish Appendix B on ancantoids!
Re-write derivation of planitude for ancantoids
Note that C_{k\beta} is now 2 x what it was before
Re-write derivation of alatude for ancantoids
Re-do the ancantoid shape graphs
Finish reorganization/expansion of Appendix C
Finish sec 5.2 on true shapes of cantoids and ancantoids
Re-do the projected ancantoid fig and start describing it
Re-organize the dust wave se

@@
 
-\title[Bow shock shapes]{True versus apparent shapes of bow shocks and bow waves}
+\title[Bow shock shapes]{True versus apparent shapes of bow shocks}
 
@@
 \pubyear{2017}
+
+\DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\Sin}{\mathcal{S}}
+\DeclareMathOperator{\Cos}{\mathcal{C}}
+\DeclareMathOperator{\Cot}{\mathcal{T}}
+\DeclareMathOperator{\GammaFunc}{\Gamma}
+\newcommand\w{\ensuremath{\mathrm{w}}}
+\newcommand\C{\ensuremath{\mathrm{c}}}
+\providecommand{\abs}[1]{\lvert#1\rvert}
+\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
+\newcommand\TODO[1]{%
+  \begin{center}
+    \framebox{\parbox{0.8\linewidth}{
+        \texttt{\footnotesize\color{red} #1}}}
+  \end{center}}
 
@@
   physical models: quadrics of revolution, wilkinoids, cantoids,
-  ancantoids, and dragoids.  We further show how these are modified in
-  the presence of small-amplitude standing-wave oscillations of the
-  basic shape, as may be produced by hydrodynamic instabilities or a
-  time-varying source.
+  and ancantoids.  
 \end{abstract}
@@
 \input{sec-intro}
-\input{sec-generic-model}
+% \input{sec-generic-model}
 \input{sec-projection}
@@
 \input{sec-thin-shell}
-\clearpage
-\input{app-dust-wave}
-\clearpage
-\input{sec-standing-wave}
+% \input{app-dust-wave}
+% \input{sec-standing-wave}
 \input{sec-conclusions}
@@
 \input{app-parabola}
-\input{app-rcurv}
-\input{app-r90}
-\input{app-wilkinoid}
+\input{app-ancantoid}
+\input{app-shape-parameters}
+% \input{app-dust-equations}
 

### 2017-11-20 papers/Paper1/sec-conclusions.tex
Write first half of conclusions for Paper I

@@
 
-%\newcommand\thC{\(\theta^1\)\,Ori~C}
-\defcitealias{Canto:1996}{CRW}
+We have shown that the shapes of stellar bow shocks can be usefully
+characterized by two dimensionless numbers: the \textit{planitude},
+\(\Pi\), or flatness of the bow's apex, and the \textit{alatude},
+\(\Lambda\), or openness of the bow's wings.  The planitude and alatude can
+be estimated from ratios of lengths that can be straightforwardly
+measured from observations or theoretical models.  We develop a
+general theory for the projected shape, \((\Pi', \Lambda')\), of a bow shock's
+limb-brightened edge, or \textit{tangent line}, as a function of
+inclination angle, \(i\), where the emission shell is idealized as a
+cylindrically symmetric surface.
+
+We first apply this theory to find inclination-dependent tracks on the
+projected planitude--alatude plane for the special case of
+\textit{quadric} surfaces, such as hyperboloids, paraboloids, and
+spheroids, where the tangent line is a conic section.  The spheroids
+and hyperboloids occupy distinct regions of the plane, with the
+paraboloids defining the boundary between the two.  As the inclination
+is increased from \(\abs{i} = 0\) (side-on) to \(\abs{i} = 90^\circ\)
+(end-on), the tracks first tend to approach the diagonal
+\(\Lambda' = \Pi'\), corresponding to confocal conics, always remaining within
+their own region.  At the highest inclinations, the spheroids all
+converge at \(\abs{i} = 90^\circ\) on the point
+\((\Pi', \Lambda') = (1, 1)\) and the paraboloids on the point
+\((\Pi', \Lambda') = (2, 2)\).  The hyperboloids, on the other hand diverge as
+\((\Pi', \Lambda') \to (\infty, \infty)\) for a finite
+\(i_{\mathrm{crit}}\), which depends on the hyperbolic eccentricity.
+For \(\abs{i} > i_{\mathrm{crit}}\), the tangent line no longer exists
+for the hyperbola, and it no longer would appear to be a bow shock.
+
+We have presented a new two-dimensional classification scheme for the
+analysis of the shapes of stellar bow shocks, which
 

### 2017-11-20 papers/Paper1/sec-dust-bow-intro.tex
Write first half of conclusions for Paper I

@@
 \label{sec:introduction}
+
+The paper is organized as follows.
+%
+In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
+dusty radiation bow wave (dragoids), including the effects of
+gas-grain drag.
+%
+In \S~\ref{sec:perturbed-bows} we investigate the effects on the
+planitude--alatude plane of small-amplitude perturbations to the bow
+shape.
+%
 

### 2017-11-20 papers/Paper1/sec-intro.tex
Re-organize the dust wave section a bit
Write first half of conclusions for Paper I

@@
 
-Bow shocks from pulsars and neutron stars
-\citep{Cordes:1993a, Brownsberger:2014a}.
+\TODO{Bow shocks from pulsars and neutron stars
+  \citep{Cordes:1993a, Brownsberger:2014a}.}
 
-Radiation bow waves \citep{van-Marle:2011a}
+\TODO{Radiation bow waves \citep{van-Marle:2011a}.}
 
@@
 shock axis to the plane of the sky.
-%
-In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
-dusty radiation bow wave (dragoids), including the effects of
-gas-grain drag.
-%
-In \S~\ref{sec:perturbed-bows} we investigate the effects on the
-planitude--alatude plane of small-amplitude perturbations to the bow
-shape.
-%
 In \S~\ref{sec:conc} we summarise our results and outline how

### 2017-11-20 papers/Paper1/sec-conclusions.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))

@@
-\section{Conclusions}
+\section{Summary and discussion}
 \label{sec:conc}
@@
 measured from observations or theoretical models.  We develop a
-general theory for the projected shape, \((\Pi', \Lambda')\), of a bow shock's
-limb-brightened edge, or \textit{tangent line}, as a function of
-inclination angle, \(i\), where the emission shell is idealized as a
-cylindrically symmetric surface.
+general method for finding the projected shape,
+\((\Pi', \Lambda')\), of a bow shock's limb-brightened edge, or
+\textit{tangent line}, as a function of inclination angle, \(i\),
+where the emission shell is idealized as a cylindrically symmetric
+surface.
 
-We first apply this theory to find inclination-dependent tracks on the
-projected planitude--alatude plane for the special case of
+We first apply this method to find inclination-dependent tracks
+on the projected planitude--alatude plane for the special case of
 \textit{quadric} surfaces, such as hyperboloids, paraboloids, and
@@
 \((\Pi', \Lambda') \to (\infty, \infty)\) for a finite
-\(i_{\mathrm{crit}}\), which depends on the hyperbolic eccentricity.
-For \(\abs{i} > i_{\mathrm{crit}}\), the tangent line no longer exists
-for the hyperbola, and it no longer would appear to be a bow shock.
+\(i_{\mathrm{crit}}\), which depends on the asymptotic opening angle
+of the tail.  For \(\abs{i} > i_{\mathrm{crit}}\), the tangent line no
+longer exists for the hyperbola, and it no would longer appear to be a
+bow shock.
 
-We have presented a new two-dimensional classification scheme for the
-analysis of the shapes of stellar bow shocks, which
+We then apply the projection method to a set of thin-shell
+hydrodynamic models of bow shocks: the \textit{wilkinoid} from a
+wind-parallel stream interaction and the \textit{cantoids} from
+wind-wind interactions.  We generalize the latter to the
+\textit{ancantoids}, where one of the winds is anisotropic.  We find
+that the wilkinoid is confined to a small region of the
+\(\Pi'\)--\(\Lambda'\) plane, with projected planitude and alatude varying with
+inclination by \(< 15\%\).  The cantoids and ancantoids with
+sufficiently small values of \(\beta\), the wind momentum ratio, have more
+interesting behavior, with tracks that pass from the spheroid region
+at low inclinations to the hyperboloid region at high inclinations.
 
-We developed a method to estimate the shape of a generic bow shock product of the
-interaction of two winds as well as it apparent shape due to it orientation relative to the line of sight, asuuming
-the bow shock is geometrically and optically thin.
-
-In the general case we require numerical techniques, but is possible to handle analytically the apparent shape of
-the quadrics of revolution.
-
-Also we made a generalization of \CRW{} work where the weakest interacing wind is hemispherical and anisotropic where its
-density follows a power law of $\cos\theta$. Although other models also may be used.
-
-In any case we developed a form to derive a set of measurable radii which are used as comparison between the \CRW{} model, the quadrics
-of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
-(ONC) due to the interaction of the photoevaporated wind from proplyds and the stellar wind of \thC{}.
-
-How different regions of the \(\Pi\)--\(\Lambda\) plane are populated.
-Bottom-right quadrant hard to get to (except for standing wave
-oscillations), but may be due to finite shell thickness, which (for
-low Mach number) will be more apparent in the wings, which might
-decrease \(\Lambda\) more than \(\Pi\).  Fact that thin-shell solutions should
-trace the contact discontinuity, but in some cases it may be only the
-inner or the outer shell that is visible.
+This paper is the first of a series that will apply our shape analysis
+to a wide variety of models and observations of stellar bow shocks.
+In a second paper \citep{Henney:2018a}, we consider the alternative
+model of dusty radiation-driven bow wave, instead of a hydrodynamic
+bow shock, and also calculate the signature in the planitude--alatude
+plane of oscillations in the bow shape, which may be due to
+instabilities or a time-varying source.  In a third paper
+\citep{Henney:2018b}, we apply our techniques to observational
+datasets for three different classes of stellar bow shocks: OB stars,
+cool giants/supergiants, and young stars in the extended Orion Nebula.
+In a fourth paper \citep{Tarango-Yong:2018b}, we analyze the proplyd
+bow shocks in the core of the Orion Nebula.
 

### 2017-11-20 papers/Paper1/sec-conic.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))

@@
 increasing inclination (for true \(\Pi > 2\)), they turn around and
-increases again as \(\abs{i}\) approaches the critical value
+increase again as \(\abs{i}\) approaches the critical value
 \(i_{\mathrm{crit}} = 90^\circ - \abs{\thetaQ}\).  For

### 2017-11-20 papers/Paper1/sec-dust-bow-discuss.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))

\section{Summary and discussion}

How different regions of the \(\Pi\)--\(\Lambda\) plane are populated.
Bottom-right quadrant hard to get to (except for standing wave
oscillations), but may be due to finite shell thickness, which (for
low Mach number) will be more apparent in the wings, which might
decrease \(\Lambda\) more than \(\Pi\).  Fact that thin-shell solutions should
trace the contact discontinuity, but in some cases it may be only the
inner or the outer shell that is visible.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dusty-bow-wave"
%%% End:

### 2017-11-20 papers/Paper1/sec-intro.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))

@@
 
-\TODO{Bow shocks from pulsars and neutron stars
-  \citep{Cordes:1993a, Brownsberger:2014a}.}
-
-\TODO{Radiation bow waves \citep{van-Marle:2011a}.}
+% \TODO{Bow shocks from pulsars and neutron stars
+%   \citep{Cordes:1993a, Brownsberger:2014a}.}
 
@@
 shock axis to the plane of the sky.
+%
 In \S~\ref{sec:conc} we summarise our results and outline how
@@
   already known.  Generalization to cases where these assumptions do
-  not hold is discussed in \citet{Henney:2017a}.} %
+  not hold is discussed in \citet{Henney:2018b}.} %
 of \(R(\theta)\) about the apex (with \(\theta\) in

### 2017-11-20 papers/Paper1/sec-thin-shell.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))

@@
 Figure~\ref{fig:convergence-cantoid-wilkinoid}, simply moving the
-short distance from \((\tfrac53, \sqrt3)\) to
-\((\tfrac32, \mathbf{???})\).  Despite its location in the ellipsoid
-region of the plane, the fact that it has \(\theta_\infty = 180^\circ\) means that it
-behaves more like a parabola at high inclination, but converges on
-\((\tfrac32, \mathbf{???})\) instead of \((2, 2)\) since the far wings
-are asymptotically cubic, rather than quadratic.
+short distance from \((\nicefrac53, \sqrt3)\) to
+\((\nicefrac32, \smash{\sqrt{\nicefrac83}})\).  Despite its location
+in the ellipsoid region of the plane, the fact that it has
+\(\theta_\infty = 180^\circ\) means that it behaves more like a parabola at high
+inclination, but converges on
+\((\nicefrac32, \smash{\sqrt{\nicefrac83}})\) instead of \((2, 2)\)
+since the far wings are asymptotically cubic, rather than quadratic.
 

### 2017-11-21 papers/Paper1/app-dust-wave.tex
Finish first draft of introduction to Paper 2

@@
 This is the polar form of the equation for the confocal parabola,
-which we have already discussed in detail in \S~\ref{sec:conic} and
-Appendix~\ref{app:parabola}.  Its planitude and alatude are
-\(\Gamma = \Lambda = 2\) and these are unchanged under projection at any
-inclination.
+which we have already discussed in detail in \PaperI{}'s
+\S~\ref{Q-sec:conic} and Appendix~\ref{Q-app:parabola}.  Its planitude
+and alatude are \(\Gamma = \Lambda = 2\) and these are unchanged under projection
+at any inclination.
 
@@
 \(\theta \to \theta + \theta_1(b)\), where \(\sin \theta_1 = b / D\) (see
-Fig.~\ref{fig:crw-schema}). We parametrize the degree of divergence as
-\(\mu = R_0 / D\) and, as before, \(R\grain(\theta + \theta_1(b, \mu); b)\) is
-minimized over all trajectories to find the shape of the bow wave's
-inner edge.  This time, the result is a confocal hyperbola:
+Fig.~\ref{Q-fig:crw-schema} of \PaperI{}). We parametrize the degree
+of divergence as \(\mu = R_0 / D\) and, as before,
+\(R\grain(\theta + \theta_1(b, \mu); b)\) is minimized over all trajectories to
+find the shape of the bow wave's inner edge.  This time, the result is
+a confocal hyperbola:
 \begin{equation}
@@
     \(\abs{\sin i}\). Gray shaded regions are as in
-    Fig.~\ref{fig:quadric-projection-continued}a.  The wilkinoid track
-    is shown in white. }
+    Fig.~\ref{Q-fig:quadric-projection-continued}a of \PaperI{}.  The
+    wilkinoid track is shown in white. }
   \label{fig:dragoid-Rc-R90}
@@
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock"
+%%% TeX-master: "dusty-bow-wave"
 %%% End:

### 2017-11-21 papers/Paper1/dusty-bow-wave.tex
Write first half of conclusions for Paper I
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))
Finish first draft of introduction to Paper 2

@@
 \usepackage{rotating}
+\usepackage{xr-hyper}
 \usepackage{hyperref}
+\externaldocument[Q-]{quadrics-bowshock}
 
@@
 
-\title[Bow wave shapes]{True versus apparent shapes of dusty radiative bow waves}
+\title[Dusty bow wave shapes]
+{True versus apparent shapes of dusty radiative bow waves}
 
@@
   interesting differences from the wilkinoid, cantoid, and ancantoid
-  shapes of hydrodynamic bow shock models.  We analyze the prospects
-  of using shape analysis of observational datasets to discriminate
+  shapes of hydrodynamic bow shock models. We further show how these
+  are modified in the presence of small-amplitude standing-wave
+  oscillations of the basic shape, as may be produced by hydrodynamic
+  instabilities or a time-varying source.  We analyze the prospects of
+  using shape analysis of observational datasets to discriminate
   between different bow models, finding that sample sizes of order 100
@@
 \begin{keywords}
-  hydrodynamics -- stars: winds, outflows
+  circumstellar matter -- radiation: dynamics -- stars: winds, outflows
 \end{keywords}
@@
 \input{sec-standing-wave}
+\input{sec-dust-bow-discuss}
 \bibliographystyle{mnras}

### 2017-11-21 papers/Paper1/sec-conic.tex
Finish first draft of introduction to Paper 2

@@
   \end{tabular}
-  \caption{Example off-center conic sections that can form quadrics of
+  \caption[]{Example off-center conic sections that can form quadrics of
     revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
@@
   \includegraphics[width=\linewidth]{figs/conic1}
-  \caption{Example of a family of conic sections, all with the same
+  \caption[]{Example of a family of conic sections, all with the same
     planitude (flatness at apex, marked by white dot):
@@
   \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
-  \caption{Variation with inclination angle of the apparent shape of
+  \caption[]{Variation with inclination angle of the apparent shape of
     quadric bows with true planitude and alatude that are uniformly

### 2017-11-21 papers/Paper1/sec-dust-bow-intro.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))
Finish first draft of introduction to Paper 2

@@
+\defcitealias{Tarango-Yong:2018a}{Paper~I}
+\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
+
 \section{Introduction}
 \label{sec:introduction}
+\newcommand\hii{\ion{H}{ii}}
+
+Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
+often interpreted as bow shocks, due to a supersonic hydrodynamic
+interaction between the star's wind and an external stream. This
+stream may be due to the star's own motion or to an independent flow,
+such as an \hii{} region in the champagne phase
+\citep{Tenorio-Tagle:1979a}, or another star's wind
+\citep{Canto:1996}. However, an alternative interpretation in some
+cases may be a radiation-pressure driven bow wave, as first proposed
+by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
+emitted by the star are absorbed by dust grains in the incoming
+stream, with the resultant momentum transfer being sufficient to
+decelerate and deflect the grains within a certain distance from the
+star, forming a dust-free, bow-shaped cavity with an enhanced dust
+density at its edge.  Two regimes are possible, depending on the
+strength of coupling between the gas (or plasma) and the dust.  In the
+strong-coupling regime, gas--grain drag decelerates the gas along with
+the dust, forming a shocked gas shell in a similar fashion to the
+wind-driven bow shock case.  In the weak-coupling regime, the gas
+stream is relatively unaffected and the dust temporarily decouples to
+form a dust-only bow wave.  This second case has recently been studied
+in detail in the context of the interaction of late O-type stars
+(which have only weak stellar winds) with dusty photoevaporation flows
+inside \hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
+  Ochsendorf:2015a}.  More complex, hybrid scenarios are also
+possible, such as that studied by \citet{van-Marle:2011a}, where a
+hydrodynamic bow shock forms, but the larger dust grains that
+accompany the stellar wind pass right through the shocked shell due to
+weak gas--grain coupling, and form their own bow wave at a larger
+radius.
+
+In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
+new two-dimensional classification scheme for bow shapes: the
+projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
+measures the flatness of the bow's apex, while alatude measures the
+openness of the bow's wings.  Both are dimensionless ratios of lengths
+that can be estimated from observational images.  We have analyzed the
+inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
+geometric shapes (spheroids, paraboloids, hyperboloids) and for
+thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
+ancantoids).  In this paper, we will do the same for simple models of a
+dusty radiation bow wave in the weak coupling limit (dragoids).
 
@@
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "dusty-bow-wave"
 %%% End:

### 2017-11-21 papers/Paper1/sec-intro.tex
Finish first draft of introduction to Paper 2

@@
+% Force paper II to be before paper III in the reference list
+\nocite{Henney:2018a}
+
 \section{Introduction}
@@
 comprise spheroids, paraboloids, and hyperboloids, each of which
-occupies a disjoint region of the planitude--alatude plane.
+occupies a distinct region of the planitude--alatude plane.
 %
@@
   \includegraphics[width=\linewidth]{figs/characteristic-radii}
-  \caption{Parameters for characterizing a bow shape.  Bow radius from
-    the star, measured parallel (\(R_0\)) and perpendicular
+  \caption[]{Parameters for characterizing a bow shape.  Bow radius
+    from the star, measured parallel (\(R_0\)) and perpendicular
     (\(R_{90}\)) to the symmetry axis, together with radius of

### 2017-11-21 papers/Paper1/sec-thin-shell.tex
Finish first draft of introduction to Paper 2

@@
   \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
-  \caption{True shapes of cantoids and ancantoids in the
+  \caption[]{True shapes of cantoids and ancantoids in the
     \(\Pi\)--\(\Lambda\) plane, calculated according to results of
@@
   \includegraphics[width=\linewidth]{figs/ancantoid-angles}
-  \caption{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
+  \caption[]{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
     cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
@@
   \end{tabular}
-  \caption{Apparent projected shapes of wilkinoid, cantoids and
+  \caption[]{Apparent projected shapes of wilkinoid, cantoids and
     ancantoids in the \(\Pi'\)--\(\Lambda'\) plane.  Colored symbols indicate
@@
   \includegraphics[width=\linewidth]{figs/ancantoid-R90-vs-Rc-lobeta-a}
-  \caption{As Fig.~\ref{fig:thin-shell-R90-Rc}a but zoomed in to show
+  \caption[]{As Fig.~\ref{fig:thin-shell-R90-Rc}a but zoomed in to show
     the wilkinoid track (white) and the convergence of the cantoid

### 2017-11-23 papers/Paper1/dusty-bow-wave.tex
Change title and intro for paper 2

@@
 
-\title[Dusty bow wave shapes]
-{True versus apparent shapes of dusty radiative bow waves}
+\title[Dust waves, bow waves, bow shocks]
+{Shapes of dust waves, bow waves, and bow shocks}
 
@@
 \begin{abstract}
-  Dusty stellar bow waves result from the action of a star's radiation
-  pressure on a stream of dust grains that is flowing past it.  They
-  are an alternative mechanism to hydrodynamic bow shocks for
-  explaining the curved arcs of infrared emission seen around some
-  stars.  We develop simple cylindrically symmetric models for the
-  dust grain dynamics under the influence of radiation and gas--grain
-  drag forces, which produce bow shapes that we call dragoids.  Using
-  our recently developed two-dimensional classification scheme for
-  projected bow shapes, we then analyze the inclination-dependent
-  tracks of the dragoids in the planitude--alatude plane, finding
-  interesting differences from the wilkinoid, cantoid, and ancantoid
-  shapes of hydrodynamic bow shock models. We further show how these
-  are modified in the presence of small-amplitude standing-wave
-  oscillations of the basic shape, as may be produced by hydrodynamic
-  instabilities or a time-varying source.  We analyze the prospects of
-  using shape analysis of observational datasets to discriminate
-  between different bow models, finding that sample sizes of order 100
-  are required.
+  Dust waves and bow waves result from the action of a star's
+  radiation pressure on a stream of dust grains that is flowing past
+  it.  They are an alternative mechanism to hydrodynamic bow shocks
+  for explaining the curved arcs of infrared emission seen around some
+  stars.  We employ simple cylindrically symmetric models for the dust
+  grain dynamics under the influence of radiation and weak gas--grain
+  coupling, which produce bow shapes that we call dragoids.  We also
+  show how thin-shell hydrodynamic models can be modified to treat the
+  case of strong gas-grain coupling, producing bow shapes that we call
+  trapoids.  Using our recently developed two-dimensional
+  classification scheme for projected bow shapes, we then analyze the
+  inclination-dependent tracks of the dragoids and trapoids in the
+  planitude--alatude plane, finding interesting differences from the
+  wilkinoid, cantoid, and ancantoid shapes of hydrodynamic bow shock
+  models. We further show how these are modified in the presence of
+  small-amplitude standing-wave oscillations of the basic shape, as
+  may be produced by hydrodynamic instabilities or a time-varying
+  source.  We analyze the prospects of using shape analysis of
+  observational datasets to discriminate between different bow models,
+  finding that sample sizes of order 100 are required.
 \end{abstract}

### 2017-11-23 papers/Paper1/sec-dust-bow-intro.tex
Change title and intro for paper 2

@@
 Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
-often interpreted as bow shocks, due to a supersonic hydrodynamic
-interaction between the star's wind and an external stream. This
-stream may be due to the star's own motion or to an independent flow,
-such as an \hii{} region in the champagne phase
+often interpreted as \textit{bow shocks}, due to a supersonic
+hydrodynamic interaction between the star's wind and an external
+stream. This stream may be due to the star's own motion or to an
+independent flow, such as an \hii{} region in the champagne phase
 \citep{Tenorio-Tagle:1979a}, or another star's wind
@@
 stream is relatively unaffected and the dust temporarily decouples to
-form a dust-only bow wave.  This second case has recently been studied
-in detail in the context of the interaction of late O-type stars
-(which have only weak stellar winds) with dusty photoevaporation flows
-inside \hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
-  Ochsendorf:2015a}.  More complex, hybrid scenarios are also
-possible, such as that studied by \citet{van-Marle:2011a}, where a
-hydrodynamic bow shock forms, but the larger dust grains that
-accompany the stellar wind pass right through the shocked shell due to
-weak gas--grain coupling, and form their own bow wave at a larger
-radius.
+form a dust-only shell.  This second case has recently been studied in
+detail in the context of the interaction of late O-type stars (which
+have only weak stellar winds) with dusty photoevaporation flows inside
+\hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
+  Ochsendorf:2015a}.  We follow the nomenclature proposed by
+\citet{Ochsendorf:2014b}, in which \textit{dust wave} refers to the
+weak coupling case and \textit{bow wave} to the strong coupling case.
+More complex, hybrid scenarios are also possible, such as that studied
+by \citet{van-Marle:2011a}, where a hydrodynamic bow shock forms, but
+the larger dust grains that accompany the stellar wind pass right
+through the shocked gas shell, and form their own dust wave at a
+larger radius.
+
+\begin{figure}
+  \centering
+  \framebox{
+    \parbox[m][4cm]{0.8\linewidth}
+    {\centerline{\textbf{\dotfill TODO\dotfill}}}}
+  \caption{Bow shocks, bow waves, and dust waves}
+  \label{fig:3-types-bow}
+\end{figure}
 
@@
 thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
-ancantoids).  In this paper, we will do the same for simple models of a
-dusty radiation bow wave in the weak coupling limit (dragoids).
+ancantoids).  In this paper, we will do the same for simple models of
+radiation-driven dust waves (dragoids) and bow waves (trapoids).
 

### 2017-11-26 papers/Paper1/sec-conic.tex
Make graph of departure function for conics
And begin description of it in paper

@@
 illustrated in Figure~\ref{fig:conics-family}.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/conic-departure}
+  \caption[]{Parabolic departure function for conic sections.}
+  \label{fig:conic-departure}
+\end{figure}
+
+\subsection{Parabolic departure function}
+\label{sec:parab-depart-funct}
+
+The special case of confocal conic sections
+(\(\Lambda = \Pi\)) can be written in polar form as
+\begin{equation}
+  \label{eq:confocal-polar}
+  R(\theta) = R_0 \frac {1 + \ecc} {1 + \ecc \cos \theta}
+\end{equation}
+where \(\ecc = (1 - \Q)^{1/2}\) is the \textit{conic eccentricity}.
+For the confocal parabola (\(\ecc = 1\)), the dimensionless reciprocal
+radius is therefore \(R_0/R(\theta) = \tfrac12 (1 + \cos \theta)\), which
+suggests the following form for a \textit{departure function} that
+measures the difference between a given shape \(R(\theta)\) and the
+parabola:
+\begin{equation}
+  \label{eq:departure-function}
+  \Depart\bigl(\cos \theta\bigr) = \frac{R_0} {R(\theta)} - \tfrac12 \left( 1 + \cos \theta \right). 
+\end{equation}
+From equations~\eqref{eq:confocal-polar} and
+\eqref{eq:departure-function} it is clear that \(\Depart\) is a linear
+function of \(\cos \theta\) for other confocal conics, being positive for
+ellipses (\(\ecc < 1\)) and negative for hyperbolae (\(\ecc > 1\)).
 

### 2017-11-26 Quadric-shapes/conic-departure.py

@@ -1,0 +1,76 @@
+import sys
+import numpy as np
+from matplotlib import pyplot as plt
+import seaborn as sns
+
+plotfile = sys.argv[0].replace('.py', '.pdf')
+
+def departure(R, theta):
+    """Departure function of R(theta) from parabola"""
+    return 1.0/R - 0.5*(1 + np.cos(theta))
+
+
+def xy_conic_t(t, Pi, Lambda):
+    """Parametric equation for ellipse/hyperbola"""
+    Q = 2*Pi - Lambda**2
+    a = Pi / np.abs(Q)
+    b = a*np.sqrt(np.abs(Q))
+    sigma = np.sign(Q)
+    x0 = 1.0 - sigma*a
+    if sigma > 0:
+        C, S = np.cos, np.sin
+    else:
+        C, S = np.cosh, np.sinh
+    x = x0 + sigma*a*C(t)
+    y = b*S(t)
+    return x, y
+
+def R_th_from_xy(x, y):
+    R = np.hypot(x, y)
+    th = np.arctan2(y, x)
+    return R, th
+
+sns.set_style('ticks')
+sns.set_color_codes('deep')
+fig, ax = plt.subplots(figsize=(4, 4))
+
+# Show theta = 90 
+ax.axvline(0.0, ls=':', c='k', lw=0.5)
+
+t = np.linspace(0.0, np.pi, 500)
+colors = 'rky'
+lws = 0.5, 1.0, 1.5, 2.0
+Tudes = [1.5, 1.9999, 2.66]
+
+
+for Pi, color in zip(Tudes, colors):
+    for Lambda, lw in zip(Tudes, lws):
+        x, y = xy_conic_t(t, Pi, Lambda)
+        R, th =  R_th_from_xy(x, y)
+        Delta = departure(R, th)
+        label = fr'$\Pi = {Pi:.1f}$, $\Lambda = {Lambda:.1f}$'
+        ax.plot(np.cos(th), Delta, c=color, lw=lw, label=label)
+
+# Fill in forbidden zone
+# mugrid = np.linspace(-1.0, 1.0)
+# ax.fill_between(mugrid, -0.5*(1.0 + mugrid), -1.0, color='k', alpha=0.4)
+
+ax.annotate(r"$\Pi = \frac{3}{2}$", (0.8, 0.05), color='r', va='center')
[…]

### 2017-11-26 papers/Paper1/sec-conic.tex
Finish section on departure function for conics

@@
 
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/conic-departure}
+  \caption[]{Parabolic departure function, \(\Depart(\cos\theta)\), for
+    conic sections with different planitude and alatude, centered on
+    that of the confocal parabola, \((\Pi, \Lambda) = (2, 2)\), which has
+    \(\Depart(\cos\theta) = 0\).  Planitude (shown by different line
+    colors) determines the slope of \(\Depart\) at the apex,
+    \(\cos\theta = 1\).  Alatude (shown by different line widths)
+    determines the value of \(\Depart\) at \(\cos\theta = 0\).  All conics
+    with \(\Pi = \Lambda\) have departure functions that are straight lines.}
+  \label{fig:conic-departure}
+\end{figure}
+
 \begin{figure*}
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/conic-departure}
-  \caption[]{Parabolic departure function for conic sections.}
-  \label{fig:conic-departure}
-\end{figure}
-
 \subsection{Parabolic departure function}
@@
 ellipses (\(\ecc < 1\)) and negative for hyperbolae (\(\ecc > 1\)).
+Examples are shown in Figure~\ref{fig:conic-departure} for a grid of 9
+conics centered on the confocal parabola, with \((\Pi, \Lambda)\) ranging from
+\(3/4\) to \(4/3\) of \((2, 2)\).  The hyperbolae have negative values
+of \(\Depart\) in the far wings, with tracks that end at \(\cos \theta_\infty\).
+
+Strictly speaking, the departure function is redundant if one is
+interested in only conic sections, since they are fully determined by
+\(\Pi\) and \(\Lambda\).  Nonetheless, as we will show in following sections,
+it is a useful tool for studying general \(R(\theta)\), being very
+sensitive to small variations in the shape.
 

### 2017-11-27 papers/Paper1/sec-thin-shell.tex
Finish making departure function figure for ancantoids
Still need to write about it in text
Finish description in paper of departure function for ancantoids
Add another panel to graph with k=3 and k=8 results

@@
   \centering
+  \setkeys{Gin}{width=\linewidth}
+  \begin{tabular}{@{}l@{}}
+    (a) \\
+    \includegraphics{figs/crw-departure} \\
+    (b) \\
+    \includegraphics{figs/crw-departure-k38}
+  \end{tabular}
+  \caption[]{Parabolic departure function, \(\Depart(\cos\theta)\), for
+    ancantoids and cantoids.  Heavy lines show the \(\beta = 0\) parallel
+    stream case (Wilkinoid in the isotropic case).  Light lines show
+    increasing values of \(\beta = \num{e-4}\), \num{0.001}, \num{0.01},
+    \num{0.1}, as marked.  (a)~Cantoids (gray) and moderately
+    anisotropic ancantoids: hemispheric, \(k = 0\) (black), and
+    proplyd-like, \(k = 0.5\) (red). (b)~Cantoids (gray) and extremely
+    anisotropic, jet-like ancantoids: \(k = 3\) (purple) and \(k = 8\)
+    (blue).}
+  \label{fig:ancantoid-departure}
+\end{figure}
+
+\begin{figure}
+  \centering
   \includegraphics[width=\linewidth]{figs/test_xyprime}
@@
 planitude and alatude when the inclination is large.
+
+Figure~\ref{fig:ancantoid-departure} shows the parabolic departure
+function (see \S~\ref{sec:parab-depart-funct}) for the thin-shell
+models. This provides an alternative perspective on the resultant bow
+shapes, with two different types of behavior being apparent.  Models
+with high \(\beta\) and low anisotropy behave similarly to the
+hyperboloids, such as the
+\((\Pi, \Lambda) = (\nicefrac32, \nicefrac83)\), \((2, \nicefrac83)\),
+\((\nicefrac83, \nicefrac83)\), and \((\nicefrac32, 2)\) cases from
+Figure~\ref{fig:conic-departure}.  This is the case for the
+\(\beta \ge 0.01\) models in Figure~\ref{fig:ancantoid-departure}a, which
+all show departure functions that become negative in the far wings
+(more open than parabola) and terminate at a
+\(\theta_\infty < 180^\circ\).  The second type of behavior is shown by models with
+low \(\beta\) or high anisotropy, which behave like spheroids for positive
+and mildly negative values of \(\cos \theta\), but, unlike the spheroids,
+all tend towards \(\Depart = 0\) in the far tail as \(\cos\theta \to -1\).
 

### 2017-11-27 CRW-shapes/crw-departure-k38.py

@@ -32,8 +32,8 @@ ax.plot(mugrid, compensate(bp.wilkinoid_R_theta(thgrid), thgrid),
 
 betas = [0.1, 0.01, 0.001, 0.0001, 1e-7]
 
-ks = [None, 0.0, 0.5]
-colors = gray, 'k', 'r'
+ks = [None, 3.0, 8.0]
+colors = gray, 'm', 'b'
 
 # Plot cantoids
 for k, color in zip(ks, colors):
@@ -54,18 +54,19 @@ for k, color in zip(ks, colors):
 # Fill in forbidden zone
 #ax.fill_between(mugrid, -0.5*(1.0 + mugrid), -1.0, color='k', alpha=0.4)
 
-ax.annotate(r"$\beta = 0.1$", (-0.6, -0.15), fontsize='small', ha='right')
-ax.annotate(r"$\beta = 0.01$", (-0.63, -0.04), fontsize='small', ha='right')
-#ax.annotate(r"$\beta = 0.001$", (-0.6, -0.2), fontsize='small', ha='right')
+ax.annotate(r"$\beta = 0.1$", (0.1, 0.48), color='b', fontsize='small', ha='right')
+ax.annotate(r"$\beta = 0.01$", (0.0, 0.7),  color='b', fontsize='small', ha='right')
+ax.annotate(r"$\beta = 0$", (-0.1, 0.83),  color='b', fontsize='small', ha='right')
 
-ax.annotate(r"$\beta = 0$", (-0.48, 0.185), color='r', fontsize='small', ha='center')
-ax.annotate(r"$\beta = 0$", (-0.56, 0.12), fontsize='small', ha='center')
+ax.annotate(r"$\beta = 0.1$", (0.0, 0.18), color='m', fontsize='small', ha='right')
+ax.annotate(r"$\beta = 0.01$", (-0.1, 0.35),  color='m', fontsize='small', ha='right')
+ax.annotate(r"$\beta = 0$", (-0.4, 0.45),  color='m', fontsize='small', ha='right')
 
 ax.legend()
 
 ax.set(
     xlim=[-1.02, 1.02],
-    ylim=[-0.255, 0.255],
+    ylim=[-0.375, 0.9],
     xlabel=r"$\cos \,\theta$",
     ylabel=r"Departure function, $\Delta(\cos\theta)$",
 )

### 2017-11-30 papers/Paper1/sec-conclusions.tex
More about the simulations - develop plan for using Meyers 2017
Write fig caption for simulation departure function graphs

@@
+\section{More realistic bow shock models}
+\label{sec:more-realistic-bow}
+
+\begin{figure}
+  (a)\\
+  \includegraphics[width=\linewidth]
+  {figs/depart-cheby-M17-MHD2040-AllB7}\\[-\baselineskip]
+  (b)\\
+  \includegraphics[width=\linewidth]
+  {figs/depart-cheby-M17-HD2040}\\[-\baselineskip]
+  \caption{Departure function for the shape of the contact
+    discontinuity, measured from two numerical simulations of a
+    \(20\,M_\odot\) main-sequence star, moving at \SI{40}{km.s^{-1}}
+    through a uniform medium of density \SI{0.57}{cm^{-3}}
+    \citep{Meyer:2017a}. (a)~Magnetohydrodynamic simulation with
+    ambient magnetic field of strength \SI{7}{\micro G}, oriented
+    parallel to the stellar velocity. (b)~Hydrodynamic simulation with
+    zero magnetic field.  Blue dots show the measured shape, while the
+    thick, pale-red line shows a 12th-order Chebyshev polynomial fit.
+    The published shapes only extend to
+    \(\theta \approx 130\)--\(150^\circ\), so we extrapolate the shapes out to
+    \(\theta = 180^\circ\). Two different extrapolations are shown,
+    corresponding to bows that are asymptotically closed (dashed red
+    line) or open (solid red line).  For comparison, black lines show
+    the departure function for wilkinoid (thick line) and cantoids
+    (thin lines).}
+  \label{fig:sim-depart}
+\end{figure}
+
+The assumptions underlying the models of the previous section may
+break down in various ways.  To test whether
+
+Most importantly, the shocked shell may not be thin.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/test_xyprime_simulation}
+  \caption{Projected shapes of contact discontinuity from simulations.}
+  \label{fig:sim-xyp}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
+  \caption{Apparent projected shapes of simulations.}
+  \label{fig:sim-Pi-Lambda}
+\end{figure}
+
 \section{Summary and discussion}

### 2017-11-30 papers/Paper1/sec-obs-conclusions.tex
Get some screenshots together for Meyer (2016) simulations
Still need to measure arcs in ds9
Write fig caption for simulation departure function graphs

@@
 \label{sec:conclusion}
+
+Difference in SEDs between FIR and MIR samples?  \citet{Meyer:2016a}
+say emission peaks at 3--50 micron for O star bow shocks.
+
+Al other things being equal, larger bows will be at higher
+inclinations (we should estimate how much variation in size we should
+get due to inclination -- it will be more for flatter bows).  Higher
+inclinations means less variation from the standing wave oscillations,
+which goes against our result that larger bows have greater dispersion
+in \(\Lambda'\).  Although the standing waves mainly give dispersion in
+\(\Pi'\) anyhow.
 

### 2017-11-30 Simulation-Shapes/m17-planitude-alatude.py

@@ -60,6 +60,8 @@ ax.fill_between(Rc_grid, R90_T0_grid, 0.5, color='k', alpha=0.1)
 ax.plot(Rc_grid, R90_T0_grid, c='k', lw=0.5)
 ax.axhline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
 ax.axvline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
+ax.axhline(2.0, ls=':', lw=0.5, alpha=0.5, color='k', zorder=-1)
+ax.axvline(2.0, ls=':', lw=0.5, alpha=0.5, color='k', zorder=-1)
 ax.plot([0.9, 10.0], [0.9, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
 
 # Put a cross at the Wilkinoid coordinates: [5/3, sqrt(3)]
@@ -165,7 +167,7 @@ for model, label, color in zip(models, labels, colors):
 
 
 ax.legend(ncol=1, fontsize='small',
-          title='Simulations\n(Meyer et al. 2017)',
+          title='Simulation\ncontact discontinuity\n(Meyer et al. 2017)',
           frameon=True, loc="upper left").get_title().set_size('small')
 ax.set(
     xlim=[0.93, 6.1],

### 2017-12-01 papers/Paper1/sec-conclusions.tex
Finish caption for projected simulation shape figure
And improve spacing between panels

@@
   {figs/depart-cheby-M17-HD2040}\\[-\baselineskip]
-  \caption{Departure function for the shape of the contact
+  \caption[]{Departure function for the shape of the contact
     discontinuity, measured from two numerical simulations of a
@@
   \includegraphics[width=\linewidth]{figs/test_xyprime_simulation}
-  \caption{Projected shapes of contact discontinuity from simulations.}
+  \caption[]{Projected shapes of contact discontinuity from
+    simulations at different inclinations \(\abs{i}\) (varying line
+    color and thickness, see key).  Top row shows magnetized
+    simulation of Fig.~\ref{fig:sim-depart}a, bottom row shows
+    non-magnetized simulation of Fig.~\ref{fig:sim-depart}b.  Left
+    column shows asymptotically open extrapolation, right column shows
+    asymptotically closed extrapolation.  All shapes are normalized to
+    the projected apex distance, \(R_0'\) }
   \label{fig:sim-xyp}
@@
   \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
-  \caption{Apparent projected shapes of simulations.}
+  \caption[]{Apparent projected shapes of simulations.}
   \label{fig:sim-Pi-Lambda}

### 2017-12-01 Simulation-Shapes/test_xyprime_simulation.py

@@ -66,6 +66,8 @@ axes[-1,0].set(
 )
 
 sns.despine()
+for ax in axes.flat:
+    ax.label_outer()
 fig.tight_layout(pad=0.3, h_pad=0.1, w_pad=0.1)
 fig.savefig(figfile)
 print(figfile, end='')

### 2017-12-01 Simulation-Shapes/m17-planitude-alatude.py
Add a new figure of R0 prime for the simulations
This has an annoying discrepancy for the HD simulation dust emission.
I suspect that the Meyer (2017) paper has an error in the spatial
scales.

@@ -1,4 +1,4 @@
-T=[["Source", "R0/100", "Rc/R0", "R90/R0", "Rm90/R0"], ["M17-MHD2040-AllB7", "0.48", "3.57", "1.95", "1.92"], ["M17-MHD2040-AllB7-Halpha-i00", "0.62", "4.78", "2.21", "2.21"], ["M17-MHD2040-AllB7-60mic-i30", "0.20", "2.14", "1.74", "1.73"], ["M17-MHD2040-AllB7-60mic-i45", "0.23", "1.70", "1.59", "1.61"], ["M17-MHD2040-AllB7-60mic-i60", "0.27", "1.51", "1.47", "1.46"], ["M17-HD2040", "0.84", "1.78", "1.75", "1.75"], ["M17-HD2040-Halpha-i00-CD", "0.99", "1.96", "2.09", "2.08"], ["M17-HD2040-Halpha-i00-BS", "1.31", "2.15", "1.95", "1.96"], ["M17-HD2040-60mic-i30", "0.48", "1.89", "1.80", "1.79"], ["M17-HD2040-60mic-i45", "0.56", "1.87", "1.90", "1.59"], ["M17-HD2040-60mic-i60", "0.70", "1.66", "1.55", "1.59"]]
[…]

### 2017-12-01 Simulation-Shapes/m17-r0-prime.py

@@ -1,0 +1,133 @@
+T=[["Source", "R0/pc", "Rc/R0", "R90/R0", "Rm90/R0"], ["M17-MHD2040-AllB7", "0.38", "3.57", "1.95", "1.92"], ["M17-MHD2040-AllB7-Halpha-i00", "0.40", "2.83", "1.90", "1.89"], ["M17-MHD2040-AllB7-60mic-i30", "0.48", "2.14", "1.74", "1.73"], ["M17-MHD2040-AllB7-60mic-i45", "0.56", "1.70", "1.59", "1.61"], ["M17-MHD2040-AllB7-60mic-i60", "0.67", "1.51", "1.47", "1.46"], ["M17-HD2040", "0.66", "1.78", "1.75", "1.75"], ["M17-HD2040-Halpha-i00", "0.71", "2.33", "1.83", "1.85"], ["M17-HD2040-Halpha-i00-CD", "0.59", "1.68", "1.93", "1.93"], ["M17-HD2040-Halpha-i00-BS", "0.75", "1.91", "1.83", "1.83"], ["M17-HD2040-60mic-i30", "1.17", "1.89", "1.80", "1.79"], ["M17-HD2040-60mic-i45", "1.36", "1.87", "1.90", "1.59"], ["M17-HD2040-60mic-i60", "1.70", "1.66", "1.55", "1.59"], ["M17-MHD2040-AllB7-60mic-i90", 1.05, -999.0, -999.0, -999.0]]
+import sys
+import numpy as np
+from scipy.interpolate import interp1d
+import statsmodels.api as sm
+from astropy.table import Table
+from matplotlib import pyplot as plt
+import matplotlib.ticker
+import seaborn as sns
+from simulation_shape import Simulation
+sys.path.append("../Dust-wave")
+import bow_projection as bp
+import bow_diagnostic
+
+plotfile = sys.argv[0].replace('.py', '.pdf')
+
+sns.set_style('ticks')
+fig, ax = plt.subplots(figsize=(4, 4))
+
+
+table = Table(rows=T[1:], names=T[0], dtype=[str] + [float]*4)
+
+# Take average +/- std of the +ve and -ve R90
+R90stack = np.stack([table['R90/R0'], table['Rm90/R0']])
+table['R90'] = np.nanmean(R90stack, axis=0)
+table['dR90'] = np.nanstd(R90stack, axis=0)
+table.remove_columns(['R90/R0', 'Rm90/R0'])
+
+
+def select_marker_style(s):
[…]

### 2017-12-03 papers/Paper1/app-shape-parameters.tex
Write a big chunk of the description of the simulation CD shapes

@@
 
-To find the alatude, \(\Lambda = R_{90} / R_0\), we use equation~\eqref{eq:crw-angles} at \(\theta = 90^\circ\) to write
+To find the alatude, \(\Lambda = R_{90} / R_0\), we use
+equation~\eqref{eq:crw-angles} at \(\theta = \ang{90}\) to write
 \begin{equation}
@@
 \end{equation}
-where \(\theta_{1,90} = \theta_1(\theta = 90^\circ)\), which, following
+where \(\theta_{1,90} = \theta_1(\theta = \ang{90})\), which, following
 equation~\eqref{eq:ancantoid-theta-theta1-implicit}, must satisfy
@@
 Since \(\Pi\) and \(\Lambda\) depend on only that portion of the inner wind
-emitted in the forward hemisphere, \(\theta \le 90^\circ\), the results for the
+emitted in the forward hemisphere, \(\theta \le \ang{90}\), the results for the
 cantoids can be found by taking \(k = 0\), in which case
@@
 equation~\eqref{eq:cantoid-theta-inf} in the limit \(k \to 0\).  This is
-because, for \(\theta > 90^\circ\), the \(k = 0\) ancantoid differs from the
+because, for \(\theta > \ang{90}\), the \(k = 0\) ancantoid differs from the
 cantoid since the former has no wind in the backward hemisphere (see

### 2017-12-03 papers/Paper1/sec-conclusions.tex
Add a new figure of R0 prime for the simulations
This has an annoying discrepancy for the HD simulation dust emission.
I suspect that the Meyer (2017) paper has an error in the spatial
scales.
Write a big chunk of the description of the simulation CD shapes

@@
     discontinuity, measured from two numerical simulations of a
-    \(20\,M_\odot\) main-sequence star, moving at \SI{40}{km.s^{-1}}
+    \SI{20}{M_\odot} main-sequence star, moving at \SI{40}{km.s^{-1}}
     through a uniform medium of density \SI{0.57}{cm^{-3}}
@@
     The published shapes only extend to
-    \(\theta \approx 130\)--\(150^\circ\), so we extrapolate the shapes out to
-    \(\theta = 180^\circ\). Two different extrapolations are shown,
+    \(\theta \approx 130\)--\ang{150}, so we extrapolate the shapes out to
+    \(\theta = \ang{180}\). Two different extrapolations are shown,
     corresponding to bows that are asymptotically closed (dashed red
@@
 The assumptions underlying the models of the previous section may
-break down in various ways.  To test whether
+break down in various ways.  To test whether the planitude--alatude
+analysis is still useful in less ``ideal'' situations, we here apply
+it to more realistic simulations of stellar bow shocks.  We choose a
+pair of hydromagnetic (HD) and magnetohydrodynamic (MHD) moving-star
+simulations from \citet{Meyer:2017a}, in which the only difference is
+the presence (MHD case) or absence (HD case) of an ambient magnetic
+field with strength \(B = \SI{7}{\micro G}\), oriented parallel to the
+stellar velocity.  In each case, the inner wind comes from a
+\(20\,M_\odot\) main-sequence star, with mass loss rate and terminal
+velocity that are roughly constant with time at
+\(\dot{M}_{\w} \approx \SI{4e-7}{M_\odot.y^{-1}}\) and
+\(V_{\w} \approx \SI{1200}{km.s^{-1}}\), while the outer wind is a
+parallel stream due to the star's own motion at \SI{40}{km.s^{-1}}
+through a uniform medium of density \SI{0.57}{cm^{-3}}.
 
-Most importantly, the shocked shell may not be thin.
+For these parameters, the radiative cooling distance for shocked
+ambient gas in the bow is a significant fraction (\(\approx 10\%\)) of the
+bow shock size, \(R_0\), tending to increase towards the wings, and
+the radiative cooling in the shocked stellar wind is even less
+efficient.  This represents a gross violation of the assumptions
+behind the thin-shell models, since the total shocked shell thickness
+is of the same order as \(R_0\).  The parabolic departure function
+(see \S~\ref{sec:parab-depart-funct}) for the shape of the contact
+discontinuity\footnote{%
+  Note that, in the non-magnetic HD models, efficient thermal
+  conduction leads to a thick layer of hot, thermally evaporated
+  ambient material that separates the shocked stellar wind from the
+  cool, dense shell of shocked ambient gas \citep[see \S~3.3
+  of][]{Meyer:2014b}.  In this case, the contact discontinuity is
+  taken to be the boundary between hot and cold ambient gas, as
+  opposed to the \textit{material discontinuity} between shocked
+  ambient gas and shocked wind gas.  In the MHD models, the thermal
+  conduction is almost completely suppressed, so that the material and
+  contact discontinuities coincide. } %
+in the two models is shown in Figure~\ref{fig:sim-depart} as blue
+symbols.\footnote{%
+  Measured from Figure~3 of \citet{Meyer:2017a} by tracing the
+  \SI{0.4}{cm^{-3}} density contour.} %
+The MHD simulation shows a strongly negative dip in the departure
+function close to the apex (\(\cos \theta = 1\)), indicating a very flat
+shape.\footnote{%
+  \citet{Meyer:2017a} speculate that this flatness may be the
+  signature of the formation of a complex multiple-shock topology at
+  the apex \citep{de-Sterck:1999a}.  For our purposes, the reason does
+  not matter, merely that the magnetic and non-magnetic models predict
+  markedly different shapes. } %
+The HD simulation shows only a small negative dip in the departure
+function at the apex, but otherwise approximately follows the
+wilkinoid curve in the forward hemisphere.  In both cases the
+departure function is more positive than the wilkinoid in the far
+wings (\(\cos \theta < -0.5\)), but we do not have data for the full range
+of \(\theta\), and so two different extrapolations for
+\(\theta \to \ang{180}\) are shown.  In the first (dashed red line in
+figure), we fit a low-order polynomial of \(\cos \theta\) to the points
+with \(\cos \theta < -0.5\) and extend it to \(\cos \theta = -1\), which gives
+an asymptotically closed shape.  In the second extrapolation (solid
+red line in figure), we fit a polynomial that is multiplied by
+\((1 + \cos\theta)^{1/2}\), which forces the departure function to zero at
+\(\cos \theta = -1\), giving an asymptotically open shape, as with the
+wilkinoid.  In a true steady state, the far wings should be
+asymptotically open, but as \(\theta \to \ang{180}\) the flow times become
+longer and longer, so that a bow shock with a finite age will be
+closed.
 
@@
 
+Using a 12th-order Chebyshev fit to the traced shapes, we show the
+apparent shape of the contact discontinuity at a series of inclination
+angles, \(\abs{i}\), in Figure~\ref{fig:sim-xyp}.  The four panels
+show the two simulations for each of the two far-wing extrapolations.
+Comparison with Figures~\ref{fig:xyprime}
+and~\ref{fig:xyprime-ancantoid} shows the general tendency is the same
+as with the wilkinoid: that the apex becomes less flat and the wings
+less open as the inclination angle is increased.  There is no sign of
+the sudden increase in openness at high inclination, as seen in the
+cantoids and ancantoids that are asymptotically hyperbolic.  On the
+other hand, the projected shapes of both simulations vary much more
+strongly with \(\abs{i}\) than the wilkinoid does.  For the HD
+simulation, this is mainly apparent for \(\abs{i} > \ang{30}\), but
+for the MHD simulation it occurs at all angles.
+
 \begin{figure}
@@
   \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
-  \caption[]{Apparent projected shapes of simulations.}
+  \caption[]{Apparent projected shapes of simulations in the
+    \(\Pi'\)--\(\Lambda'\) plane.}
   \label{fig:sim-Pi-Lambda}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/m17-r0-prime}
+  \caption[]{Apparent projected apex distance of simulations.}
+  \label{fig:sim-R0-prime}
 \end{figure}
@@
 
-We first apply this method to find inclination-dependent tracks
-on the projected planitude--alatude plane for the special case of
+We first apply this method to find inclination-dependent tracks on the
+projected planitude--alatude plane for the special case of
 \textit{quadric} surfaces, such as hyperboloids, paraboloids, and
@@
 paraboloids defining the boundary between the two.  As the inclination
-is increased from \(\abs{i} = 0\) (side-on) to \(\abs{i} = 90^\circ\)
+is increased from \(\abs{i} = 0\) (side-on) to \(\abs{i} = \ang{90}\)
 (end-on), the tracks first tend to approach the diagonal
@@
 their own region.  At the highest inclinations, the spheroids all
-converge at \(\abs{i} = 90^\circ\) on the point
+converge at \(\abs{i} = \ang{90}\) on the point
 \((\Pi', \Lambda') = (1, 1)\) and the paraboloids on the point

### 2017-12-03 papers/Paper1/sec-projection.tex
Rewrite appendix A on parabola with new notation
Finish Appendix B on ancantoids!
Write a big chunk of the description of the simulation CD shapes

@@
 axis of the surface, while the line of sight lies along \(-z'\).  The
-inclination angle \(i\) is defined so that \(i = 0^\circ\) when the
+inclination angle \(i\) is defined so that \(i = \ang{0}\) when the
 surface is viewed perpendicular to its axis (\textit{side on}) and
-\(i = 90^\circ\) when it is viewed along its axis (\textit{end on}).
+\(i = \ang{90}\) when it is viewed along its axis (\textit{end on}).
 
@@
 \begin{equation}
-\sin\phi\T = \tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
+\sin\phi\T = -\tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
 \label{eq:tanphi}
@@
 inclinations with
-\(\vert i\vert > (90^\circ - \alpha_{\mathrm{min}}) \) the tangent line does not exist
+\(\vert i\vert > (\ang{90} - \alpha_{\mathrm{min}}) \) the tangent line does not exist
 for any value of \(\theta\).  In other words, when the viewing angle is
@@
 
-Similarly, the projected planitude is \(\Pi' = R_c' / R_0'\), where
-\(R_c'\) is found by applying the equivalent of equation
+Similarly, the projected planitude is \(\Pi' = R_{\C}' / R_0'\), where
+\(R_{\C}'\) is found by applying the equivalent of equation
 \eqref{eq:radius-curvature} for primed quantities:
@@
   \label{eq:projected-radius-curvature}
-  R_c' 
+  R_{\C}' 
   = \frac{(R_0')^2}{R_0' - R_{\theta'\theta',0}'} \ .

### 2017-12-03 papers/Paper1/sec-conclusions.tex
Finish fig caption for planitude-alatude tracks of simulations

@@
 simulation, this is mainly apparent for \(\abs{i} > \ang{30}\), but
-for the MHD simulation it occurs at all angles.
+for the MHD simulation it occurs at all inclinations.
 
@@
   \caption[]{Apparent projected shapes of simulations in the
-    \(\Pi'\)--\(\Lambda'\) plane.}
+    \(\Pi'\)--\(\Lambda'\) plane.  Thick solid lines show the predicted
+    inclination-dependent tracks of the traced contact discontinuity
+    shape, with tick marks indicating 20 equal intervals in
+    \(\abs{\sin i}\). Open square symbols show the shapes traced from
+    the dust emission maps at \SI{60}{\um} for inclinations of
+    (largest to smallest) \ang{30}, \ang{45}, and \ang{60}. For
+    comparison, the wilkinoid track is shown in white. Note that the
+    scales of both axes are logarithmic in this case.}
   \label{fig:sim-Pi-Lambda}
 \end{figure}
+
+The resultant inclination-dependent tracks in the planitude--alatude plane are shown in
 

### 2017-12-03 papers/Paper1/sec-conclusions.tex
Describe the simulation planitude-alatude tracks

@@
     shape, with tick marks indicating 20 equal intervals in
-    \(\abs{\sin i}\). Open square symbols show the shapes traced from
-    the dust emission maps at \SI{60}{\um} for inclinations of
+    \(\abs{\sin i}\). The true planitude and alatude are marked by
+    filled circle symbols.  Open square symbols show the shapes traced
+    from the dust emission maps at \SI{60}{\um} for inclinations of
     (largest to smallest) \ang{30}, \ang{45}, and \ang{60}. For
@@
 
-The resultant inclination-dependent tracks in the planitude--alatude plane are shown in
+The resultant inclination-dependent tracks in the planitude--alatude
+plane are shown in Figure~\ref{fig:sim-Pi-Lambda}.  These are compared
+with measurements\footnote{%
+  The shape measurements were performed by converting to contours the
+  \SI{60}{\um} images in \citet{Meyer:2017a}'s Fig.~10 and then
+  tracing around the bow the ridge of minimum radius of curvature of
+  the contours.} %
+from post-processed infrared dust continuum maps \citep[\S~4.3
+of][]{Meyer:2017a}, shown by open square symbols for \(i = \ang{30}\),
+\ang{45}, and \ang{60}.
 

### 2017-12-03 papers/Paper1/sec-conclusions.tex
Finish description of simulation shape tracks

@@
     inclination-dependent tracks of the traced contact discontinuity
-    shape, with tick marks indicating 20 equal intervals in
-    \(\abs{\sin i}\). The true planitude and alatude are marked by
+    shape for the asymptotically open extrapolation, with tick marks
+    indicating 20 equal intervals in \(\abs{\sin i}\). Thin solid
+    lines show the same for the asymptotically closed extrapolation,
+    which only deviates from the open case at the high-\(\abs{i}\) end
+    of the HD tracks.  The true planitude and alatude are marked by
     filled circle symbols.  Open square symbols show the shapes traced
@@
   \SI{60}{\um} images in \citet{Meyer:2017a}'s Fig.~10 and then
-  tracing around the bow the ridge of minimum radius of curvature of
-  the contours.} %
-from post-processed infrared dust continuum maps \citep[\S~4.3
-of][]{Meyer:2017a}, shown by open square symbols for \(i = \ang{30}\),
-\ang{45}, and \ang{60}.
+  tracing the ridge of minimum radius of curvature of the contours.
+  Identical results are found from using the \SI{100}{\um} maps
+  instead.  For the \SI{25}{\um} maps, although the same results are
+  found for low inclinations, in the maps with
+  \(\abs{i} \ge \ang{45}\) in the HD case it becomes impossible to trace
+  the limb-brightened rim because it becomes fainter than the emission
+  from the true apex of the bow.} %
+from post-processed infrared dust continuum maps at \SI{60}{\um}
+\citep[\S~4.3 of][]{Meyer:2017a}, shown by open square symbols for
+\(i = \ang{30}\), \ang{45}, and \ang{60}.  The agreement between the
+two is good.  In particular, the \SI{60}{\um}-derived shapes are
+always very close to the tracks derived from the contact discontinuity
+shape. Also, the ordering of the three inclinations along the tracks
+corresponds to what is predicted, although quantitatively there are
+some slight deviations.  This close agreement stems for the fact that
+the long-wavelength dust emission from hot-star bow shocks tends to be
+dominated by material just outside the contact discontinuity, as
+emphasized by \citet{Meyer:2014b}.
 

### 2017-12-04 papers/Paper1/sec-conclusions.tex
Find definitive correction to HD sim dust map scale in Meyer (2017)
The true apex does not lie!

@@
 dominated by material just outside the contact discontinuity, as
-emphasized by \citet{Meyer:2014b}.
+emphasized by \citet{Meyer:2014b}.  Note that there is almost no
+difference in the planitude--alatude tracks between the closed and open
+extrapolations.  This is because \(\Pi'\) and \(\Lambda'\) only depend on the
+portion of \(R(\theta)\) between \(\theta_0\) (eq.~[\ref{eq:thetapar}]) and
+\(\theta_{90}\) (eq.~[\ref{eq:th90}]), and these are both smaller than the
+\(\theta\) range where extrapolation is necessary, except for in the HD
+case at the highest inclinations.
 
@@
 \end{figure}
+
+Finally, Figure~\ref{fig:sim-R0-prime} shows the inclination
+dependence of the projected apex distance, \(R_0'\).  Again, the lines
+show the prediction based on the shape of the contact discontinuity,
+while the square symbols show the results from the \SI{60}{\um} dust continuum maps.
+In addition, triangle symbols show results from H\(\alpha\) optical emission line maps, which are given for \(i = 0\) in
 

### 2017-12-04 Simulation-Shapes/m17-r0-prime.py

@@ -1,4 +1,4 @@
-T=[["Source", "R0/pc", "Rc/R0", "R90/R0", "Rm90/R0"], ["M17-MHD2040-AllB7", "0.38", "3.57", "1.95", "1.92"], ["M17-MHD2040-AllB7-Halpha-i00", "0.40", "2.83", "1.90", "1.89"], ["M17-MHD2040-AllB7-60mic-i30", "0.48", "2.14", "1.74", "1.73"], ["M17-MHD2040-AllB7-60mic-i45", "0.56", "1.70", "1.59", "1.61"], ["M17-MHD2040-AllB7-60mic-i60", "0.67", "1.51", "1.47", "1.46"], ["M17-HD2040", "0.66", "1.78", "1.75", "1.75"], ["M17-HD2040-Halpha-i00", "0.71", "2.33", "1.83", "1.85"], ["M17-HD2040-Halpha-i00-CD", "0.59", "1.68", "1.93", "1.93"], ["M17-HD2040-Halpha-i00-BS", "0.75", "1.91", "1.83", "1.83"], ["M17-HD2040-60mic-i30", "1.17", "1.89", "1.80", "1.79"], ["M17-HD2040-60mic-i45", "1.36", "1.87", "1.90", "1.59"], ["M17-HD2040-60mic-i60", "1.70", "1.66", "1.55", "1.59"], ["M17-MHD2040-AllB7-60mic-i90", 1.05, -999.0, -999.0, -999.0]]
[…]

### 2017-12-04 papers/Paper1/sec-conclusions.tex
Finish the simulation section of theory paper
Just need to revisit discussion and abstract now

@@
 corresponds to what is predicted, although quantitatively there are
-some slight deviations.  This close agreement stems for the fact that
-the long-wavelength dust emission from hot-star bow shocks tends to be
-dominated by material just outside the contact discontinuity, as
-emphasized by \citet{Meyer:2014b}.  Note that there is almost no
+some slight deviations.  This close agreement stems from the fact,
+emphasized by \citet{Meyer:2014b}, that the long-wavelength dust
+emission from hot-star bow shocks tends to be dominated by material
+just outside the contact discontinuity.  Note that there is almost no
 difference in the planitude--alatude tracks between the closed and open
@@
   \includegraphics[width=\linewidth]{figs/m17-r0-prime}
-  \caption[]{Apparent projected apex distance of simulations.}
+  \caption[]{Apparent projected apex distance of simulations.  Line
+    and symbol meanings are as in Figure~\ref{fig:sim-Pi-Lambda}.  In
+    addition, triangle symbols at \(\abs{i} = \ang{0}\) denote radius
+    measured on H\(\alpha\) optical emission maps.}
   \label{fig:sim-R0-prime}
@@
 Finally, Figure~\ref{fig:sim-R0-prime} shows the inclination
-dependence of the projected apex distance, \(R_0'\).  Again, the lines
-show the prediction based on the shape of the contact discontinuity,
-while the square symbols show the results from the \SI{60}{\um} dust continuum maps.
-In addition, triangle symbols show results from H\(\alpha\) optical emission line maps, which are given for \(i = 0\) in
+dependence of the projected apex distance, \(R_0'\).  As in the
+previous figure, the lines show the prediction based on the shape of
+the contact discontinuity, while the square symbols show the results
+from the \SI{60}{\um} dust continuum maps.\footnote{%
+  There is an apparent error in the spatial scales for the HD
+  simulations in Figs.~10 and 11 of \citet{Meyer:2017a}, with the dust
+  emission peaks occurring at radii that are clearly too large.  The
+  stated apex distance for the contact discontinuity in this
+  simulation is \SI{0.69}{pc} from Table~2 of \citet{Meyer:2014b}, and
+  the position of the peak in dust column density is \SI{0.70}{pc}
+  from Fig.~17a of \citet{Meyer:2014b}.  These are consistent with
+  Figs.~3, 4, and 7 of \citet{Meyer:2017a}, but not with Figs.~10 and
+  11.  Luckily, the position of the true apex is clearly visible in
+  the \SI{25}{\um} maps of Fig.~10 at inclinations of \ang{45} and
+  \ang{60}.  The projected separation of the true apex is
+  \(R_0 \cos i\), independent of the bow shape, which allows a
+  correction factor of \num{0.65} to be found, assuming that the
+  on-axis peak in the \SI{25}{\um} emission coincides with the peak in
+  dust column density.  This correction has been applied to the blue
+  square symbols shown in our Fig.~\ref{fig:sim-R0-prime}.} %
+In addition, triangle symbols show results from H\(\alpha\) optical
+emission line maps, which are given for \(i = 0\) in Fig.~7 of
+\citet{Meyer:2017a}.  Again, the agreement is good between the values
+derived from the shape of the contact discontinuity and those derived
+from the surface brightness maps. The greatest discrepancy is seen
+with the H\(\alpha\) maps and the intermediate inclination dust maps, with
+\(R_0'\) being overestimated by a few percent in both cases.  The
+differences in behavior between the two simulation are much larger
+than this.  The larger true planitude of the MHD simulation means that
+the relative increase of \(R_0'\) with \(\abs{i}\) is much stronger
+than in the HD simulation for \(\abs{i} < \ang{45}\), as expected from
+Figure~\ref{fig:quadric-projection}b.
 

### 2017-12-04 Simulation-Shapes/m17-r0-prime.py

@@ -82,13 +82,19 @@ for model, label, color in zip(models, labels, colors):
     R0 = 0.378 if 'MHD' in model else 0.661
     ax.axhline(R0, ls=':', lw=0.5, color=color)
 
+    inc = np.linspace(0.0, np.pi/2, 100)
+
     # First do the "theoretical" tracks
     shape = Simulation(name=model, force_open=True, cheby_degree=12)
-    th_inf = bp.theta_infinity(shape)
-    inc = np.linspace(0.0, np.pi/2, 100)
     tab = bow_diagnostic.parameter_table(inc, shape)
     R0p = tab['R_0 prime']
     ax.plot(np.degrees(inc), R0*R0p, c=color, label=label, lw=2.5, alpha=0.5)
+
+    # Repeat for the closed shape, but with a thin line
+    shape = Simulation(name=model, force_open=False, cheby_degree=12)
+    tab = bow_diagnostic.parameter_table(inc, shape)
+    R0pp = tab['R_0 prime']
+    ax.plot(np.degrees(inc), R0*R0pp, '-', c=color, label="_nolabel_", lw=0.5, alpha=1.0)
 
     mask = [s.startswith(model) and not (s.endswith('BS') or s.endswith('CD')) 
             for s in table['Source']]

### 2017-12-04 papers/Paper1/quadrics-bowshock.tex
Paper 1 is finished!
Except I still need to finish the analytical calculation of the
wilkinoid projection at high inclination.  Currently I am just
guessing that it is (Pi-prime, Lambda-prime) = (3/2, sqrt(8/3))
Finish first draft of introduction to Paper 2
Make graph of departure function for conics
And begin description of it in paper
Finish section on departure function for conics
Finish revision of discussion and abstract

@@
 \usepackage{graphicx}
+\usepackage{dblfloatfix}
+%\usepackage[section, above, below]{placeins}
 \usepackage{microtype}
@@
 \usepackage{rotating}
-\usepackage{hyperref}
+\usepackage{nicefrac}
 
@@
 \usepackage[utf8]{inputenc}
-
-% Define a fermata symbol for use inline with text
-% 04 Jul 2017 WJH
-% Based on info in Secs 18.4.1 and 24.1 of musixdoc.pdf
-\usepackage{musixtex}
-\makeatletter
-\newcommand\textfermata{%
-  {\let\extractline\relax
-    \setlines10\smallmusicsize \nobarnumbers \nostartrule
-    \staffbotmarg0pt \setclefsymbol1\empty \global\clef@skip0pt
-    \raisebox{0ex}[0ex][0ex]{
-      \startextract\addspace{-\afterruleskip}%
-      \notes\fermataup{-2}\en
-      \zendextract}}}
-\makeatother
-
-% % The \eye command is in the dingbat package, but we need to take care
-% % of a naming conflict with the AMS package
-% \usepackage{savesym}
-% \savesymbol{checkmark}
-% \usepackage{dingbat}
-
-% The "eye" symbol is drawn with the \faEye command of the fontawesome
-% package
-\usepackage{fontawesome}
-% The ``irregular'' symbol is drawn from the Icelandic Sorcery and Witchcraft 
-\usepackage{staves}
 
@@
 \usepackage[varvw,smallerops]{newtxmath}
+
+\usepackage{hyperref}
+\usepackage{xr-hyper}
 
@@
 \DeclareMathOperator{\GammaFunc}{\Gamma}
+\DeclareMathOperator{\Depart}{\Delta}
+\newcommand\ecc{\ensuremath{e}}
 \newcommand\w{\ensuremath{\mathrm{w}}}
@@
   Astrophysical bow shocks are a common result of the interaction
-  between supersonic plasma flows, such as winds or jets from stars or
-  active galaxies.  Similarly shaped radiation bow waves are produced
-  by the relative motion between dust grains and a luminous source.
-  For cylindrically symmetric bow shocks and waves, we develop a
-  general theory for the effects of inclination angle on the apparent
-  shape. We propose a new two-dimensional classification scheme for
-  bow shapes, which is based on dimensionless geometric ratios that
-  can be estimated from observational images.  The two ratios are
-  related to the flatness of the bow's apex, which we term
-  \textit{planitude} and the openness of its wings, which we term
-  \textit{alatude}.  We calculate the expected distribution on the
-  planitude--alatude diagram for a variety of simple geometrical and
-  physical models: quadrics of revolution, wilkinoids, cantoids,
-  and ancantoids.  
+  between two supersonic plasma flows, such as winds or jets from
+  stars or active galaxies, or streams due to the relative motion
+  between a star and the interstellar medium.
+  % Similarly shaped radiation bow waves are produced
+  % by the relative motion between dust grains and a luminous source.
+  For cylindrically symmetric bow shocks, we develop a general theory
+  for the effects of inclination angle on the apparent shape. We
+  propose a new two-dimensional classification scheme for bow shapes,
+  which is based on dimensionless geometric ratios that can be
+  estimated from observational images.  The two ratios are related to
+  the flatness of the bow's apex, which we term \textit{planitude} and
+  the openness of its wings, which we term \textit{alatude}.  We
+  calculate the expected distribution in the planitude--alatude plane
+  for a variety of simple geometrical and physical models: quadrics of
+  revolution, wilkinoids, cantoids, and ancantoids.  We further test
+  our methods against numerical magnetohydrodynamical simulations of
+  stellar bow shocks and find that the apparent planitude and alatude
+  measured from infrared dust continuum maps serve as accurate
+  diagnostics of the shape of the contact discontinuity, which can be
+  used to discriminate between different physical models.
 \end{abstract}
@@
 \begin{keywords}
-  hydrodynamics -- stars: winds, outflows
+  circumstellar matter -- hydrodynamics -- stars: winds, outflows
 \end{keywords}
@@
 \input{sec-conclusions}
-\clearpage
 \bibliographystyle{mnras}
@@
 \input{app-parabola}
-\input{app-ancantoid}
+%\input{app-ancantoid}
 \input{app-shape-parameters}

### 2017-12-04 papers/Paper1/sec-conclusions.tex
Finish revision of discussion and abstract

@@
     addition, triangle symbols at \(\abs{i} = \ang{0}\) denote radius
-    measured on H\(\alpha\) optical emission maps.}
+    measured on H\(\alpha\) optical emission maps.  Note that the distances
+    for the blue square symbols have been adjusted for the correction
+    factor discussed in footnote~\ref{fn:meyer-correction}.}
   \label{fig:sim-R0-prime}
@@
 
-Finally, Figure~\ref{fig:sim-R0-prime} shows the inclination
+Figure~\ref{fig:sim-R0-prime} shows the inclination
 dependence of the projected apex distance, \(R_0'\).  As in the
@@
 from the \SI{60}{\um} dust continuum maps.\footnote{%
+  \label{fn:meyer-correction}
   There is an apparent error in the spatial scales for the HD
@@
 \(R_0'\) being overestimated by a few percent in both cases.  The
-differences in behavior between the two simulation are much larger
+differences in behavior between the two simulations are much larger
 than this.  The larger true planitude of the MHD simulation means that
@@
 Figure~\ref{fig:quadric-projection}b.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/m17-histograms}
+  \caption[]{Histograms of (top to bottom) projected planitude,
+    alatude, and bow shock size for the shape of the contact
+    discontinuity in the \citet{Meyer:2017a} simulations. The \(y\)
+    axis gives the probability density (per unit \(x\)-axis quantity),
+    assuming a uniform distribution of viewing directions.}
+  \label{fig:sim-histograms}
+\end{figure}
+
+The probability densities\footnote{%
+  The probability density is defined so that its integral over the
+  full range of the histogrammed variable is unity, making it
+  independent of the histogram bin widths.  This means that the
+  characteristic width of an approximately unimodal distribution is
+  one over the maximum probability density.} %
+of the apparent shape and size of the simulation bows (measured at the
+contact discontinuity) are shown in Figure~\ref{fig:sim-histograms},
+assuming that the viewing direction is uniformly distributed in solid
+angle.  The modal value of the projected planitude is similar at
+\(\Pi' \approx 1.8\) for both simulations, but the distribution is much
+broader in the MHD case, which has a low-level wing extending out to
+\(\Pi' \approx 6\).  The projected alatude distributions are both narrower
+than the planitude (note the different scale of the histogram axis),
+with the MHD case again being the broader of the two and peaking at a
+slightly lower value (\(\Lambda' \approx 1.7\) as opposed to
+\(\approx 1.8\) for the HD case).  Finally, the distribution of
+projected-over-true apex distance is also broader for the MHD case.
 
@@
 \(\Pi\), or flatness of the bow's apex, and the \textit{alatude},
-\(\Lambda\), or openness of the bow's wings.  The planitude and alatude can
-be estimated from ratios of lengths that can be straightforwardly
-measured from observations or theoretical models.  We develop a
-general method for finding the projected shape,
-\((\Pi', \Lambda')\), of a bow shock's limb-brightened edge, or
-\textit{tangent line}, as a function of inclination angle, \(i\),
-where the emission shell is idealized as a cylindrically symmetric
-surface.
+\(\Lambda\), or openness of the bow's wings (\S~\ref{sec:plan-alat-bow}).
+The planitude and alatude can be estimated from ratios of lengths that
+can be straightforwardly measured from observations or theoretical
+models.  We develop a general method (\S~\ref{sec:projection}) for
+finding the projected shape, \((\Pi', \Lambda')\), of a bow shock's
+limb-brightened edge, or \textit{tangent line}, as a function of
+inclination angle, \(i\), where the emission shell is idealized as a
+cylindrically symmetric surface.
 
@@
 projected planitude--alatude plane for the special case of
-\textit{quadric} surfaces, such as hyperboloids, paraboloids, and
-spheroids, where the tangent line is a conic section.  The spheroids
-and hyperboloids occupy distinct regions of the plane, with the
-paraboloids defining the boundary between the two.  As the inclination
-is increased from \(\abs{i} = 0\) (side-on) to \(\abs{i} = \ang{90}\)
-(end-on), the tracks first tend to approach the diagonal
-\(\Lambda' = \Pi'\), corresponding to confocal conics, always remaining within
-their own region.  At the highest inclinations, the spheroids all
-converge at \(\abs{i} = \ang{90}\) on the point
+\textit{quadric} surfaces (\S~\ref{sec:conic}), such as hyperboloids,
+paraboloids, and spheroids, where the tangent line is a conic section.
+The spheroids and hyperboloids occupy distinct regions of the plane,
+with the paraboloids defining the boundary between the two.  As the
+inclination is increased from \(\abs{i} = 0\) (side-on) to
+\(\abs{i} = \ang{90}\) (end-on), the tracks first tend to approach the
+diagonal \(\Lambda' = \Pi'\), corresponding to confocal conics, always
+remaining within their own region.  At the highest inclinations, the
+spheroids all converge at \(\abs{i} = \ang{90}\) on the point
 \((\Pi', \Lambda') = (1, 1)\) and the paraboloids on the point
@@
 of the tail.  For \(\abs{i} > i_{\mathrm{crit}}\), the tangent line no
-longer exists for the hyperbola, and it no would longer appear to be a
-bow shock.
+longer exists for the hyperboloid, and it would no longer appear to be
+a curved bow shock.  We introduce the parabolic departure function
+(\S~\ref{sec:parab-depart-funct}) as tool for visualizing differences
+in bow shapes, \(R(\theta)\), over the full range,
+\(\theta = [\ang{0}, \ang{180}]\).
 
 We then apply the projection method to a set of thin-shell
-hydrodynamic models of bow shocks: the \textit{wilkinoid} from a
-wind-parallel stream interaction and the \textit{cantoids} from
-wind-wind interactions.  We generalize the latter to the
-\textit{ancantoids}, where one of the winds is anisotropic.  We find
-that the wilkinoid is confined to a small region of the
-\(\Pi'\)--\(\Lambda'\) plane, with projected planitude and alatude varying with
-inclination by \(< 15\%\).  The cantoids and ancantoids with
-sufficiently small values of \(\beta\), the wind momentum ratio, have more
-interesting behavior, with tracks that pass from the spheroid region
-at low inclinations to the hyperboloid region at high inclinations.
+hydrodynamic models of bow shocks (\S~\ref{sec:crw-scenario}): the
+\textit{wilkinoid} from a wind-parallel stream interaction and the
+\textit{cantoids} from wind-wind interactions.  We generalize the
+latter to the \textit{ancantoids}, where one of the winds is
+anisotropic.  We find that the wilkinoid is confined to a small region
+of the \(\Pi'\)--\(\Lambda'\) plane, with projected planitude and alatude
+varying with inclination by \(< 15\%\).  The cantoids and ancantoids
+with sufficiently small values of \(\beta\), the wind momentum ratio, have
+more interesting behavior, with tracks that pass from the spheroid
+region at low inclinations to the hyperboloid region at high
+inclinations.
+
+Finally (\S~\ref{sec:more-realistic-bow}), we test the projected shape
+analysis methods against the results of computational fluid dynamic
+simulations of magnetized and non-magnetized bow shocks from
+\citet{Meyer:2017a} of a runaway OB main-sequence star.  We find that
+measurements made on maps of infrared dust emission can be accurate
+diagnostics of the projected shape of the contact discontinuity for
+this type of bow shock (Fig.~\ref{fig:sim-Pi-Lambda}).  The
+distributions of projected planitude and alatude for a population of
+randomly oriented bow shocks shows systematic differences between the
+different simulations.
 
@@
 to a wide variety of models and observations of stellar bow shocks.
-In a second paper \citep{Henney:2018a}, we consider the alternative
-model of dusty radiation-driven bow wave, instead of a hydrodynamic
-bow shock, and also calculate the signature in the planitude--alatude
-plane of oscillations in the bow shape, which may be due to
-instabilities or a time-varying source.  In a third paper
-\citep{Henney:2018b}, we apply our techniques to observational
-datasets for three different classes of stellar bow shocks: OB stars,
-cool giants/supergiants, and young stars in the extended Orion Nebula.
-In a fourth paper \citep{Tarango-Yong:2018b}, we analyze the proplyd
-bow shocks in the core of the Orion Nebula.
+In a second paper, % \citep{Henney:2018a}
+we consider the alternative model of dusty radiation-driven bow wave,
+instead of a hydrodynamic bow shock, and also calculate the signature
+in the planitude--alatude plane of oscillations in the bow shape, which
+may be due to instabilities or a time-varying source.  In a third
+paper, % \citep{Henney:2018b},
+we apply our techniques to observational datasets for three different
+classes of stellar bow shocks: OB stars, cool giants/supergiants, and
+young stars in the extended Orion Nebula.  In a fourth paper,
+% \citep{Tarango-Yong:2018b},
+we analyze the proplyd bow shocks in the core of the Orion Nebula.
 

### 2017-12-04 papers/Paper1/sec-intro.tex
Finish revision of discussion and abstract

@@
 % Force paper II to be before paper III in the reference list
-\nocite{Henney:2018a}
+%\nocite{Henney:2018a}
 
@@
 %
+In \S~\ref{sec:more-realistic-bow} we test our methods against the
+results of more realistic numerical simulations of bow shocks,
+including the derivation of the shape parameters from maps of infrared
+dust emission.
+%
 In \S~\ref{sec:conc} we summarise our results and outline how
-following papers will apply these ideas to observations and numerical
-simulations.
+following papers will apply these ideas to observations and to a more
+extensive set of models and numerical simulations.
 

### 2017-12-04 Simulation-Shapes/m17-histograms.py

@@ -49,13 +49,16 @@ axes[1].legend(ncol=1, fontsize='small',
 axes[0].set(
     xlabel=r"Projected planitude: $\Pi'$",
     yticks=[0, 1],
+    ylim=[-0.05, None],
 )
 axes[1].set(
     xlabel=r"Projected alatude: $\Lambda'$",
     ylabel="Probability density",
+    ylim=[-0.05*3, None],
 )
 axes[2].set(
     xlabel=r"Projected apex distance: $R_{0}'/R_{0}$",
+    ylim=[-0.05*2, None],
 )
 
 sns.despine(trim=True)

### 2017-12-05 papers/Paper1/sec-conclusions.tex
Add a new appendix on the circle fits

@@
 In a second paper, % \citep{Henney:2018a}
-we consider the alternative model of dusty radiation-driven bow wave,
-instead of a hydrodynamic bow shock, and also calculate the signature
-in the planitude--alatude plane of oscillations in the bow shape, which
-may be due to instabilities or a time-varying source.  In a third
-paper, % \citep{Henney:2018b},
+we consider the alternative model of dusty radiation-driven bow wave
+\citep{Ochsendorf:2014a}, instead of a hydrodynamic bow shock, and
+also calculate the signature in the planitude--alatude plane of
+oscillations in the bow shape, which may be due to instabilities or a
+time-varying source.  In a third paper, % \citep{Henney:2018b},
 we apply our techniques to observational datasets for three different
-classes of stellar bow shocks: OB stars, cool giants/supergiants, and
-young stars in the extended Orion Nebula.  In a fourth paper,
+classes of stellar bow shocks: OB stars \citep{Kobulnicky:2016a}, cool
+giants/supergiants \citep{Cox:2012a}, and young stars in the extended
+Orion Nebula \citep{Henney:2013a}.  In a fourth paper,
 % \citep{Tarango-Yong:2018b},
-we analyze the proplyd bow shocks in the core of the Orion Nebula.
+we analyze the proplyd bow shocks in the core of the Orion Nebula
+\citep{Garcia-Arredondo:2001a}.
 

### 2017-12-05 papers/Paper1/sec-intro.tex
Add a new appendix on the circle fits

@@
   already known.  Generalization to cases where these assumptions do
-  not hold is discussed in \citet{Henney:2018b}.} %
-of \(R(\theta)\) about the apex (with \(\theta\) in
-radians):
+  not hold is discussed in Appendix~\ref{app:rcurv-empirical}.} %
+of \(R(\theta)\) about the apex (with \(\theta\) in radians):
 \begin{equation}

### 2017-12-05 papers/Paper1/quadrics-bowshock.tex
Add a new appendix on the circle fits
Add acknowledgements and email addresses

@@
 \author[Tarango Yong \& Henney]{
-  Jorge A. Tarango Yong \& William J. Henney\\
+  Jorge A. Tarango Yong\thanks{E-mail: j.tarango@irya.unam.mx}
+  \& William J. Henney\thanks{E-mail: w.henney@irya.unam.mx}\\
   \AddressCRyA
@@
 \input{sec-conclusions}
+
+\section*{Acknowledgements}
+
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grant Programa de Apoyo a Proyectos de Investigación e
+Inovación Tecnológica IN111215.  JATY acknowledges support via a
+research studentship from Consejo Nacional de Ciencias y Tecnología,
+Mexico.
+
 \bibliographystyle{mnras}
@@
 % \input{app-dust-equations}
-
+\input{app-rcurv-empirical}
 % Don't change these lines

### 2017-12-05 papers/Paper1/sec-conclusions.tex
Add acknowledgements and email addresses

@@
     measured on H\(\alpha\) optical emission maps.  Note that the distances
-    for the blue square symbols have been adjusted for the correction
-    factor discussed in footnote~\ref{fn:meyer-correction}.}
+    for the blue square symbols have been adjusted according to the
+    correction factor discussed in
+    footnote~\ref{fn:meyer-correction}.}
   \label{fig:sim-R0-prime}

### 2017-12-06 papers/Papers1234/_region_.tex
Submitted first paper! To MNRAS and arxiv

--- 2017-11-12 papers/Paper1/app-shape-parameters.tex
@@
-\section{Analytic derivation of thin-shell bow shape parameters}
+\message{ !name(quadrics-bowshock.tex)}%\RequirePackage{amsmath}
+\documentclass[useAMS, usenatbib, a4paper]{mnras}
+\pdfsuppresswarningpagegroup=1
+
+% The following is needed to fix the margins if using Letter-size paper
+% REMOVE if your LaTeX uses A4 paper by default
+%\addtolength\topmargin{-1.8cm}
+
+% Standard LaTeX packages
+% \usepackage[varg]{txfonts}
+\usepackage{graphicx}
+\usepackage{microtype}
+\usepackage{xcolor}
+\usepackage{fixltx2e}
+\usepackage{booktabs}
+\usepackage{siunitx}
+\usepackage{color}
+\usepackage{enumerate}
+\usepackage{pdflscape}
+\usepackage{rotating}
+\usepackage{hyperref}
+
+\usepackage[T1]{fontenc} 
+\usepackage[utf8]{inputenc}
+
+% Define a fermata symbol for use inline with text
+% 04 Jul 2017 WJH
+% Based on info in Secs 18.4.1 and 24.1 of musixdoc.pdf
+\usepackage{musixtex}
+\makeatletter
+\newcommand\textfermata{%
+  {\let\extractline\relax
+    \setlines10\smallmusicsize \nobarnumbers \nostartrule
+    \staffbotmarg0pt \setclefsymbol1\empty \global\clef@skip0pt
+    \raisebox{0ex}[0ex][0ex]{
+      \startextract\addspace{-\afterruleskip}%
+      \notes\fermataup{-2}\en
+      \zendextract}}}
+\makeatother
+
+% % The \eye command is in the dingbat package, but we need to take care
+% % of a naming conflict with the AMS package
+% \usepackage{savesym}
+% \savesymbol{checkmark}
+% \usepackage{dingbat}
+
+% The "eye" symbol is drawn with the \faEye command of the fontawesome
+% package
+\usepackage{fontawesome}
+% The ``irregular'' symbol is drawn from the Icelandic Sorcery and Witchcraft 
+\usepackage{staves}
+
+% Fonts 
+\usepackage{newtxtext}
+% Note: newtxmath must come AFTER newtxtext
+\usepackage[varvw,smallerops]{newtxmath}
+
+\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
+  urlcolor=blue!50!black}
+
+\usepackage{etoolbox}
+\robustify\bfseries
+\robustify\itshape
+
+%% Bold italic
+\newcommand\hmmax{0}            % we don't need heavy fonts
+\newcommand\bmmax{1}            % reduce use of math alphabets for bold
+\usepackage{bm}
+
+%% Bundled custom packages
+\usepackage{aastex-compat}
+
+% Definitions needed in abstract
+\newcommand\hii{\ion{H}{ii}}
+
+\title[Bow shock shapes]{True versus apparent shapes of bow shocks and bow waves}
+
+\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
+  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
+  58090 Morelia, Michoac\'an, M\'exico}
+\author[Tarango Yong \& Henney]{
+  Jorge A. Tarango Yong \& William J. Henney\\
+  \AddressCRyA
+}
+
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2017}
+
+\DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\Sin}{\mathcal{S}}
+\DeclareMathOperator{\Cos}{\mathcal{C}}
+\DeclareMathOperator{\Cot}{\mathcal{T}}
+\DeclareMathOperator{\GammaFunc}{\Gamma}
+\newcommand\w{\ensuremath{\mathrm{w}}}
+\newcommand\C{\ensuremath{\mathrm{c}}}
+\providecommand{\abs}[1]{\lvert#1\rvert}
+
+\begin{document}
+
+\message{ !name(app-shape-parameters.tex) !offset(-107) }
+
+\section{Analytic derivation of thin-shell bow shapes}
 \label{sec:thin-shell-shapes}
 
-In this appendix, we provide analytic calculations of the planitude,
-alatude, and asymptotic opening angle for the wilkinoid, cantoids, and
+In this appendix, we provide analytic calculations of the planitude
+(exact) and alatude (approximate) for the wilkinoid, cantoids, and
 ancantoids.  We first consider the most general case of the
@@
 This approximation is surprisingly accurate, with a relative error of
-order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).
+order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).  The
+leading term in the relative error scales as \((\beta / (k + 2))^2\), so the
+approximation is even better for smaller \(\beta\) and larger \(k\).
 
@@
 \end{gather}
-The same results can also be obtained directly from
-equation~\eqref{eq:wilkinoid-R-theta}, and in the case of \(\Lambda\) this
-has already been noted by several authors \citep{Cox:2012a,
-  Meyer:2016a}.
 
@@
 \begin{equation}
-  \label{eq:ancantoid-theta-inf}
+  \label{eq:anacantoid-theta-inf}
   \theta_\infty - \left( \frac {k + 2 (1 - \beta)} {k + 2} \right) \tan \theta_\infty
@@
 \end{equation}
-Note that, unlike in the cases of \(\Pi\) and \(\Lambda\),
-equation~\eqref{eq:ancantoid-theta-inf} does \emph{not} reduce to
+Note that, unlike the case for \(\Pi\) and \(\Lambda\),
+equation~\eqref{eq:anacantoid-theta-inf} does \emph{not} reduce to
 equation~\eqref{eq:cantoid-theta-inf} in the limit \(k \to 0\).  This is
 because, for \(\theta > 90^\circ\), the \(k = 0\) ancantoid differs from the
-cantoid since the former has no wind in the backward hemisphere (see
+cantoid since there is no wind in the backward hemisphere (see
 Figure~\ref{fig:anisotropic-arrows}).  Therefore there is less inner
@@
 in the cantoid case.  The wilkinoid result again follows from
-\(\beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that the far
-wings are asymptotically parallel to the symmetry axis, as is the case
-for the paraboloid (App.~\ref{app:parabola}).  In the case of the
-wilkinoid, however, the behavior is cubic in the wings,
+\(\beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that
+the far wings are asymptotically parallel to the symmetry axis, as is
+the case for the paraboloid (App.~\ref{app:parabola}).  In the case of
+the wilkinoid, however, the behavior is cubic in the wings,
 \(z \sim r^3\), as opposed to quadratic as in the paraboloid.
@@
 %%% End:
+
+\message{ !name(quadrics-bowshock.tex) !offset(-137) }
+
+\end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2017-12-06 papers/Papers1234/app-r90.tex
Submitted first paper! To MNRAS and arxiv

--- 2017-04-25 papers/Paper1/quadrics-appendix.tex
@@
-\appendix
-% \appendixpage
-% \addappheadtotoc
-\section{Parabola of Revolution}
-\label{app:parabola}
-
-In this section we develop the particular case of the parabola.
-The parametrization is given by:
-
-\begin{align}
-x &= - \frac{1}{2}R_ct^2 + R_0 \\
-y &= R_c t
-\end{align}
-Where $R_c$ is the radius of curvature and $R_0$ is the distance of the parabola nose to the
-origin.
-The respective tridimensional shape is given by:
-\begin{align}
-x &= -\frac{1}{2}R_ct^2 + R_0 \label{eq:x-par-a}\\
-y &= R_c t \cos\phi  \label{eq:y-par-a}\\
-z &= R_c t \sin\phi  \label{eq:z-par-a}
-\end{align}
-The azimutal angle where the surface is tangent to the line of sight in this case is given by:
-\begin{align}
-\sin\phi_t = -\frac{\tan i}{t} \label{eq:sin-tan-a} 
-\end{align}
-
-Subtituting (\ref{eq:sin-tan-a}) into (\ref{eq:x-par-a}), (\ref{eq:y-par-a}) and
-(\ref{eq:z-par-a}) we find the apparent shape
-of the paraboloid:
-
-\begin{align}
-x' &= -\frac{R_c(\frac{1}{2}t^2 \cos^2 i -\sin^2 i)}{\cos i}+R_0\cos i \\
-y' &= R_c\left(t^2-\tan^2 i\right)^{1/2} 
-\end{align}
-
-Taking the limit of equations (\ref{eq:qprime}) and (\ref{eq:Aprime}) when $\theta_c$ tends to zero we find that:
-
-\begin{align}
-\left(\frac{q'}{q}\right)_{\mathrm{parabola}} &= 1+\frac{\tilde{R}_c\tan^2 i}{2}\\
-\left(\tilde{R}'_c\right)_{\mathrm{parabola}} &= \frac{\tilde{R}_c}{\cos^2 i + \frac{\tilde{R}_c}{2}\sin^2 i}
-\end{align}
-
-\section{Analytic derivation of the radius of curvature in the Thin Shell model}
-\label{app:rc-analytic}
-
-For small $\theta$ we may do a polynomial expansion for the shell shape such as:
-
-\begin{align}
-R \simeq R_0\left(1+\gamma\theta^2 + \Gamma\theta^4\right) \label{eq:R-exp}
-\end{align}
-
-The radius of curvature at the axis for $R$ is given by:
-
-\begin{align}
-R_c = R_0\left(1-2\gamma\right)^{-1}
-\end{align}
-
-The coefficient gamma may be derived by an expansion at small angles of equation
-(\ref{eq:th1th}), as follows:
-
-From the first term of the right side we get:
-
-\begin{align}
-\cot\theta &\simeq \theta^{-1}\left[1-\frac{1}{3}\theta^2\right] \\
-\cos^k\theta\sin^2\theta &\simeq \theta^2 - \left(\frac{1}{3} + \frac{k}{2}\right)\theta^4 \\
-\implies I_k(\theta) &\simeq \frac{1}{3}\theta^3\left[ 1 - \frac{1}{10}(3k+2)\theta^2\right]\\
-\implies 2\beta I_k(\theta)\cot\theta &\simeq \frac{2}{3}\beta\theta^2\left[1-\frac{1}{30}
-(9k+16)\theta^2\right]\label{eq:AR1} 
-\end{align}
-
-For the second term we get:
-
-\begin{align}
--\frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right) & \simeq -\beta\theta^2\left[1-\frac{1}{12}
-(3k+4)\theta^2\right] \label{eq:AR2}
-\end{align}
-
-For the left side we use equation (25) from \CRW{}. Then, equation (\ref{eq:th1th}) results
-as follows:
-
-\begin{align}
-\theta_1^2\left(1+\frac{1}{15}\theta_1^2\right) = \beta\theta^2\left[1+\frac{1}{60}(4-9k)
-\theta^2\right] \label{eq:th1th-app}
-\end{align}
-
-And we can use the approximation $\theta_1 \approx \beta\theta^2$ for the correction term in
-the left side of (\ref{eq:th1th-app}):
-
-\begin{align}
-\theta_1^2 &= \beta\theta^2\left[1+\frac{1}{60}(4-9k)\theta^2\right]
-\left(1-\frac{\beta}{15}\theta^2\right) \\
-\implies \theta_1^2 &= \beta\theta^2\left[1+ 2C_{k\beta}\theta^2\right]
-\label{eq:th1th-small}\\
-\mathrm{where:~} C_{k\beta} &\equiv \frac{1}{2}\left(A_k-\frac{\beta}{15}\right) \\
-A_k &\equiv \frac{1}{15}-\frac{3k}{20}
-\end{align}
-
-Now, using equation (23) from \CRW{} we may estimate $R$ at low angles. To do this, we need to
-expand each term as follows (neglecting terms of order four or higher):
-
-\begin{align}
-\theta_1 = &= \beta^{1/2}\theta\left[1+ 2C_{k\beta}\theta^2\right]^{1/2} \\
-\theta + \theta_1 &= \theta\left[1+\beta^{1/2}\left(1+2C_{k\beta}\theta^2\right)\right]\\
-\sin\theta_1 &= \theta_1\left[1-\frac{\theta_1^2}{6}\right] \\
- &= \beta^{1/2}\theta\left[1+\left(C_{k\beta}-\frac{1}{6}\beta\right)\theta^2\right] \\
- \sin(\theta+\theta_1) &= \left[\theta+\theta_1\right]\left[1-\frac{\left(\theta+\theta_1
- \right)^2}{6}\right] \\
- &= \theta\left(1+\beta^{1/2}\right)\left\lbrace 1+\left[\frac{C_{k\beta}\beta^{1/2}}
- {1+\beta^{1/2}}-\frac{1}{6}\left(1+\beta^{1/2}\right)^2\right]\theta^2\right\rbrace
-\end{align}
-
-So, combining these terms with equation (23) from \CRW{} we found the final expression for $R$:
-
-\begin{align}
-\frac{R}{D}\equiv \frac{\sin\theta_1}{\sin(\theta+\theta_1)} = \frac{\beta^1/2}{1+\beta^{1/2}}
-\left\lbrace 1 + \theta^2\left[\frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}
-\right)\right] \right\rbrace \label{eq:r-small-theta}
-\end{align}
-
-Returning to equation (\ref{eq:R-exp}) we see the following:
-
-\begin{align}
-R_0 &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
-\gamma &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}\left(1+2\beta^{1/2}\right)
-\label{eq:app-gamma}
-\end{align}
-
-We recover equation (27) of \CRW{} for $R_0$ and equation (\ref{eq:app-gamma}) is the
-needed term to calculate the radius of curvature at the axis.
-
 \section{Analytic derivation of \texorpdfstring{\boldmath $R_{90}$}{R\_90} in the thin shell model}
@@
 
-\section{Derivation of Characteristic Radii in Isotropic Wind/Parallel interaction Problem}
-\label{app:ch-rad-Wilkin}
-
-$\tilde{R}_{90}$ is obtained by simply evaluating equation (\ref{eq:R-Wilkin}) at $\theta=\frac{\pi}{2}$.
-For the Radius of curvature we follow a similar procedure than the Wind/Wind interaction, but using equation
-(\ref{eq:R-Wilkin}) for $R(\theta)$ and inserting the cosecant into the square root.
-
-Expanding the terms of $R(\theta)$ we find the following:
-
-\begin{align}
-  \csc^2\theta &\simeq \theta^{-2}\left[1+\frac{\theta^2}{3}\left(1+\frac{\theta^2}{5}\right)\right] \\
-  1-\theta\cot\theta &\simeq \frac{\theta^2}{3}\left[1 + \frac{\theta^2}{15}\left(1+\frac{2\theta^2}{21}\right)\right] \\
-  \implies \tilde{R}(\theta) \simeq 1 + \frac{\theta^2}{5} + O\left[\theta^4\right]
-\end{align}
-
-From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$
-\clearpage
-
-% Landscape table needs to go on its own page, so we need to manually
-% adjust the section counter so that it will ``belong'' to the next
-% section
-\addtocounter{section}{1}
-\sisetup{detect-all=true, detect-inline-weight=math}
-\sisetup{round-mode=figures, round-precision=2}
-\begin{landscape}
-\begin{table}
-  \setlength\tabcolsep{3pt}
-  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
-Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
-  \label{tab:big-p}
-  \input{figs/mipsgal-summary-stats-table-body.tex}
-\end{table}
-\end{landscape}
-\begin{table}
-  \contcaption{Results of all statistical tests performed on observed
-    bow shock shape parameters.}
-  \begin{tabular}{p{0.9\linewidth}}
-    \toprule
-    \textit{Description of columns:}
-    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
-    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
-    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
-    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
-    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
-    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
-    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
-It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
-    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
-    (Col.~13)~Ratio of standard deviations between the two sub-samples.
-    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
-    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
-    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
-    (Col.~16)~Brown--Forsythe test for dispersion
-    \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\addtocounter{section}{-1}
-
-\section{Distribution of p-values for all correlations tested}
-\label{sec:distr-p-values}
-\addtocounter{table}{1}
-
-\begin{figure}
-  (a)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
-  (b)\\
-  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
-  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
-    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
-    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
-    bins and logarithmic vertical axis, with all values
-    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
-    lines shows the traditional threshold values for significance:
-    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
-    uniform distribution of \(p\)-values that would be expected if the
-    null hypothesis were always true, that is, if no significant
-    correlations existed.}
-  \label{fig:histo-p-values}
-\end{figure}
-
-Results from all the statistical tests discussed in \S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
-
-\begin{table}
-  \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
-  \label{tab:type-I}
-  \centering
-  \begin{tabular}{lrr} \toprule
-    Correlation & \(p\) & \(\alpha\) \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
-    \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
-    \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
-    \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
-    \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
-    \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
-    \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
-    \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
-    \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
-    \(R_c\) vs Facing & 0.71 & 1 \\
-    \(R_c\) vs H II & 0.50 & 1 \\
-    \(R_{90}\) vs Facing & 0.60 & 1 \\
-    \(R_{90}\) vs H II & 0.52 & 1 \\
-    \(R_c\) vs Multiple & 1.00 & 1 \\
-    \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
-    \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
-    \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
-    \(R_c\) vs Herschel & 0.074 & 0.3437 \\
-    \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
-    \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
-    \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The \(p\)-values are the probability of finding a difference between
-two populations as large as (or larger than) what is observed,
-\emph{given} that there is no difference in the underlying
-distribution from which the two populations are drawn (that is, given
-that the null hypothesis is true).  However, what we really want to
-know is something else: the probability that the null hypothesis is
-true, \emph{given} the observations.  That is, the probability,
-\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
-  error rate}.  The common mistake of conflating these two definitions
-is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
-error of the transposed conditional'', as discussed in detail by
-\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
-\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
-requires an estimate of the prior probability of the null hypothesis,
-independent of the observations.  Alternatively, it is also possible
-to find a lower bound on \(\alpha\) from a frequentist approach
-\citep{Sellke:2001a}:
-\begin{equation}
-  \label{eq:type-I}
-  \alpha(p) \ge \bigg[ 1 - \big(e\, p \ln p\big)^{-1} \bigg]^{-1}
-  \quad \text{valid for } p < 1/e.
-\end{equation}
-This is the approach we adopt here, which also numerically coincides
-with the Bayesian approach for the case where the prior probability of
-the null hypothesis is 0.5.  The reason that this is only a lower
-limit for \(\alpha\) is that if we have overwhelming a priori evidence that
-the null hypothesis is true (for instance, from previous empirical
-studies, or because it follows from a well-supported theory), then a
-Bayesian calculation would give a much higher value of \(\alpha\) than
-\eqref{eq:type-I} does.  In our case, however, we have no strong
-reasons for favoring any of the null hypotheses, so it is reasonable
-to assume \(\alpha\) is close to the lower limit given in \eqref{eq:type-I}.
-
-In order to choose a threshold \(p\)-value that counts as a
-``significant'' result, one then needs to balance the risks of false
-positives against the risks of \textit{false negatives}.  The false
-negative probability, \(\beta\), also known as \textit{Type II error
-  rate}, is the probability of failing to reject an untrue null
-hypothesis.  That is, in the context of this paper, it is the
-probability of failing to detect a real difference between two
-sub-samples, or a real correlation between two variables.  The
-complementary probability, \(1 - \beta\), is known as the
-\textit{statistical power} or sensitivity of the test.  The value of
-\(\beta\) depends on three factors:
-\begin{enumerate}[1.]
-\item The \textit{effect size}, which is a measure of the magnitude of
-  the difference in a dependent variable between two sub-samples, or
-  the degree of correlation between two continuous variables.  For the
-  two sub-sample case, it is common to use a standardised mean
-  difference, such as Cohen's \(d\) statistic \citep{Cohen:1988a}:
-  \(d = (\bar{X}_A - \bar{X}_B) / s\), where \(\bar{X}_A\),
-  \(\bar{X}_B\) are the means of the dependent variable \(X\) for
-  samples A and B, while \(s\) is the pooled standard deviation of
-  \(X\).  For the case of two continuous variables, the Pearson linear
-  correlation coefficient, \(r\), can be used.  In both cases, rules
-  of thumb have been developed \citep{Ruscio:2008a} for classifying an
-  effect as ``large'' (\(d > 0.8\), \(r > 0.4\)) or ``small''
-  (\(d < 0.2\), \(r < 0.1\)).  Alternatively, non-parametric
-  statistics can be used, such as the \(A\) measure of stochastic
-  superiority \citep{Delaney:2002a}.
-\end{enumerate}
-
-Obviously, this depends on the \textit{effect size}, which is the
-
-All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).
-It is therefore important to guard against the ``multiple comparisons problem'', whereby seemingly significant correlations are found where none really exist, simply by virtue of the large number of tests that were carried out.
-
-Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.
-
-The p-curve \citep{Head:2015a}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock.tex"
+%%% TeX-master: "quadrics-bowshock"
 %%% End:

### 2017-12-06 papers/Papers1234/app-rcurv-empirical.tex
Submitted first paper! To MNRAS and arxiv

\section{Empirical determination of radius of curvature for a bow shock of unknown orientation}
\label{app:rcurv-empirical}

Consider a set of \(N\) points on the plane of the sky, with Cartesian
coordinates \(\bm{r}_k = (x_k, y_k)\) for \(k = 1 \dots N\).  We wish
to estimate the radius of curvature of the smooth curve that the set
of points is presumed to be sampled from.  To do this, we fit a circle
to the points as follows.  The circle is defined by its center,
\(\bm{r}_{\C} = (x_{\C}, y_{\C})\), and radius, \(R_{\C}\).  For a
given circle, we define a mean radius of the set of points from the
circle center:
\begin{equation}
  \label{eq:rcurv-mean-radius}
  \bar{R}(x_{\C}, y_{\C}) = \frac{1}{N}  \sum_{k = 1}^{N} \Abs{\bm{r}_k - \bm{r}_{\C}}  \ .
\end{equation}
We then optimize\footnote{%
  For example, using a Levenberg-Marquardt algorithm, such as
  \texttt{astropy.modeling.fitting.LevMarLSQFitter} from the AstroPy
  library \citep{Astropy-Collaboration:2013a}.} %
to find best-fit values \((x_{\C}^*, y_{\C}^*)\), which minimize the
objective function
\begin{equation}
  \label{eq:rcurv-objective-function}
  f(x_{\C}, y_{\C}) = \sum_{k = 1}^{N} \left(
    \abs{\bm{r}_k - \bm{r}_{\C}}  - \bar{R} (x_{\C}, y_{\C}) \right)^2 \ .
\end{equation}
The best-fit radius of curvature is then given by
\(R_{\C}^* = \bar{R}(x_{\C}^*, y_{\C}^*)\).

If we also know the position, \(\bm{r}_0 = (x_0, y_0)\), of the bow's
central source, then we can find the unit vector in the direction of
the bow's projected axis as
\begin{equation}
  \label{eq:rcurv-axis-vector}
  \uvec{\xi} = \frac {\bm{r}_0 - \bm{r}_{\C}^*} { \abs{\bm{r}_0 - \bm{r}_{\C}^*}} \ , 
\end{equation}
and the apex distance from the source as\footnote{%
  This is only valid if the resultant \(R_0 < R_{\C}^*\), otherwise
  the opposite sign of \(\uvec{\xi}\) must be taken.}
\begin{equation}
  \label{eq:rcurv-apex-distance}
  R_0 = \Abs{\bm{r}_{\C}^* + R_{\C}^* \uvec{\xi} - \bm{r}_0} \ .
\end{equation}
A refinement of the method is then to repeat the circle fit after
restricting the set of points to those lying within a certain angle
\(\Delta\theta\) of the bow axis by requiring
\begin{equation}
  \label{eq:rcurv-delta-theta}
  \uvec{\xi} \cdot 
  {\left( \bm{r}_k - \bm{r}_{\C}^* \right) }
  \ge   {\Abs{\bm{r}_k - \bm{r}_{\C}^*}}
  \cos \Delta\theta \ ,
\end{equation}
where we find that best results are obtained with \(\Delta\theta \le \ang{30}\).

If quantitative estimates exist for the uncertainties, \(\epsilon_k\), in the
measurements of \(\bm{r}_k\), then it is appropriate to incorporate
weights of \(\epsilon_k^{-2}\) in the objective function.  In cases where the
bow shape is traced by eye, based on real or synthetic observations, a
more practical approach is to maintain uniform weighting but to place
a greater density of points \(\bm{r}_k\) in regions where the shape is
well-determined and to place them more sparsely in regions where the
shape is less certain.

Note that this method is not necessary if the orientation of the bow
axis is known a~priori, in which case the Taylor series method
described in \S~\ref{sec:plan-alat-bow} is more efficient and
accurate.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

### 2017-12-06 papers/Papers1234/obs-bowshocks.tex
Submitted first paper! To MNRAS and arxiv

--- 2017-10-13 papers/Paper1/obs-bowshocks.tex
@@
   the shape of such bow shocks, which we here apply to three very
-  different observational datasets.  These are: (1)~mid-infrared arcs
+  different observational datasets: (1)~mid-infrared arcs
   around hot main-sequence stars (\(N = 227\)); (2)~far-infrared arcs

### 2017-12-06 papers/Papers1234/proplyds-table.tex
Submitted first paper! To MNRAS and arxiv

 \begin{table*}
\begin{tabular}{c|ccccccccc}\hline
Proplyd & LV2 & LV2b & LV3 & LV4  & LV5 & 177-341 & 168-328 & 169-338 & 180-331\\\hline
$D' (\arcsec)$ &7.83 & 7.01 &6.91 & 6.05 & 9.42 & 25.84 & 6.64 & 16.47 & 25.12 \\
$R'_c/D'$ (central)  & 0.23  & 0.19& 0.61  & 0.5  & 0.34  & 0.18  & 0.22 & 0.09 & 0.09\\
$R'_c/D'$ (max)
$R'_c/D'$ (min)
$R'_0/D'$ (central) & 0.32 & 0.1 & 0.34 & 0.19 & 0.21 & 0.14 & 0.15 & 0.06 & 0.07\\
$R'_0/D'$ (max)&&&&&&&&& \\
$R'_0/D'$ (min)&&&&&&&&& \\
$\beta$ &&&&&&&&& \\
$\xi$ &&&&&&&&& \\
$i$ &&&&&&&&& \\
$D$ (arcsec) &&&&&&&&& \\
$R_0/D$ &&&&&&&&& \\
$r_0$ &&&&&&&&& \\
$N_6$ &&&&&&&&& \\
$P$ (in) &&&&&&&&& \\
$P$ (wind) &&&&&&&&& \\
$F$ (photo) &&&&&&&&& \\
$F$ (star)  &&&&&&&&& \\
\end{tabular}
\caption{Characteristic Radii measurements for a sample of proplyds. The ``central label'' refers to the ``main'' 
measurements of the radii. The ``max'' and ``min'' labels refer to the maximum and minimum measurements of the radii
obtained in all variations. In the $\beta$, $\xi$ and $i$ rows we show the parameteres which more approaches to the 
expected stagnation pressure and flux to mantain pressure balance and the photoevaporation flow.
}

\label{tab:proplyds}
\end{table*}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks.tex"
%%% End:

### 2017-12-06 papers/Papers1234/sec-conic.tex
Submitted first paper! To MNRAS and arxiv

--- 2017-11-26 papers/Paper1/sec-conic.tex
@@
   \label{fig:quadric-projection}
+  \bigskip
+  \bigskip
+  \begin{tabular}{@{}ll@{}}
+    (a) & (b) \\
+    \includegraphics{figs/projected-R90-vs-Rc}
+    & \includegraphics{figs/projected-R0-vs-i}
+  \end{tabular}
+  \caption[]{ As Figure~\ref{fig:quadric-projection}, but %
+    (a)~diagnostic planitude--alatude diagram: \(\Lambda'\) versus
+    \(\Pi'\), and %
+    (b)~projected/true star-apex distance: \(R_0' / R_0\) versus
+    \(\abs{i}\). %
+    In (a), shading indicates different classes of quadrics:
+    hyperboloids (white), prolate spheroids (dark gray), and oblate
+    spheroids (light gray), with the limiting case of paraboloids
+    shown by the thin black line.}
+  \label{fig:quadric-projection-continued}
 \end{figure*}
@@
 
-\begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
-    (a) & (b) \\
-    \includegraphics{figs/projected-R90-vs-Rc}
-    & \includegraphics{figs/projected-R0-vs-i}
-  \end{tabular}
-  \caption[]{ As Figure~\ref{fig:quadric-projection}, but %
-    (a)~diagnostic planitude--alatude diagram: \(\Lambda'\) versus
-    \(\Pi'\), and %
-    (b)~projected/true star-apex distance: \(R_0' / R_0\) versus
-    \(\abs{i}\). %
-    In (a), shading indicates different classes of quadrics:
-    hyperboloids (white), prolate spheroids (dark gray), and oblate
-    spheroids (light gray), with the limiting case of paraboloids
-    shown by the thin black line.}
-  \label{fig:quadric-projection-continued}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \setkeys{Gin}{width=0.48\linewidth}
+% \end{figure*}
 
@@
 (\(\Q > 0\)) tend towards \(\Pi' = 1\) and \(\Lambda' = 1\) as the inclination
-increases towards \(90^\circ\).  This is because when the spheroid is
+increases towards \(\ang{90}\).  This is because when the spheroid is
 oriented edge-on, we see its circular cross-section.  Hyperboloids
@@
 increase again as \(\abs{i}\) approaches the critical value
-\(i_{\mathrm{crit}} = 90^\circ - \abs{\thetaQ}\).  For
+\(i_{\mathrm{crit}} = \ang{90} - \abs{\thetaQ}\).  For
 \(\abs{i} > i_{\mathrm{crit}}\) the tangent line does not exist (see
@@
 The true planitude and alatude, which are seen for an edge-on viewing
-angle \(i = 0^\circ\), are marked by filled circles.  The zones
+angle \(i = \ang{0}\), are marked by filled circles.  The zones
 corresponding to each class of quadric (oblate spheroid, prolate
@@
 star-apex separation varies with inclination.  For moderate
-inclinations, \(\abs{i} < 30^\circ\), this depends primarily on the true
+inclinations, \(\abs{i} < \ang{30}\), this depends primarily on the true
 planitude \(\Pi\), with very little influence of the quadric parameter
@@
 \(D'\), can be measured, then \(R_0'/D'\) is always an increasing
-function of \(\abs{i}\).  For larger inclinations, \(\abs{i} > 30^\circ\), the
+function of \(\abs{i}\).  For larger inclinations, \(\abs{i} > \ang{30}\), the
 strands for different \(\Q\) begin to separate, with hyperbolae
@@
 hyperboloid zone becomes increasingly depopulated: all quadrics that
-lay above this region when \(i = 0^\circ\) will no longer be visible as a
+lay above this region when \(i = \ang{0}\) will no longer be visible as a
 bow for this value of \(\abs{i}\).  Note that this figure is merely

### 2017-12-06 papers/Papers1234/sec-intro-proplyd.tex
Submitted first paper! To MNRAS and arxiv

--- 2016-09-26 papers/Paper1/sec-intro-proplyd.tex
@@
 
+\begin{figure*}
+\includegraphics[width=0.9\linewidth]{annotated}
+\caption{\textit{Moved here from the other paper, but we probably want
+    to get rid of it completely at some point.} Projected Radius of
+  curvature vs projected $R_0$ for
+  $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
+  the same shape at a different inclination. Being the dark blue the
+  ones with the lower inclination and the red ones with the highest
+  value. For closed shapes, there is an asymptotic limit for the
+  projected radius of curvature at high inclinations, while for open
+  shapes there is an upper limit for inclination where a tangent line
+  can be observed.}
+\label{fig:Apqp}
+\end{figure*}
+
 %%% Local Variables:

### 2017-12-06 papers/Papers1234/sec-standing-wave.tex
Submitted first paper! To MNRAS and arxiv

--- 2017-10-17 papers/Paper1/sec-standing-wave.tex
@@
 \(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see
-equations~\eqref{eq:thetapar} and \eqref{eq:th90}.  The difference
-\(\theta_{90} - \theta_0\) is always a declining function of \(|i|\), so the
-oscillations of the tangent line become increasingly stretched out as
-the inclination increases.  This effect can be seen in
-Figure~\ref{fig:perturb-xy-prime}, which shows an example of the
+equations~\eqref{Q-eq:thetapar} and \eqref{Q-eq:th90} of \PaperI{}.
+The difference \(\theta_{90} - \theta_0\) is always a declining function of
+\(|i|\), so the oscillations of the tangent line become increasingly
+stretched out as the inclination increases.  This effect can be seen
+in Figure~\ref{fig:perturb-xy-prime}, which shows an example of the
 variation in projected perturbed shape with inclination angle for 3

### 2017-12-06 papers/Papers1234/sec-thin-shell.tex
Submitted first paper! To MNRAS and arxiv

--- 2017-11-27 papers/Paper1/sec-thin-shell.tex
@@
   \begin{cases}
-    \rho_0 \cos^k \theta & \text{for \(\theta \le 90^\circ\)} \\
-    0 & \text{for \(\theta > 90^\circ\)}
+    \rho_0 \cos^k \theta & \text{for \(\theta \le \ang{90}\)} \\
+    0 & \text{for \(\theta > \ang{90}\)}
   \end{cases}
@@
 It is apparent from Figure~\ref{fig:r-beta} that the \(k=0\) ancantoid
-is identical to the cantoid for \(\theta \le 90^\circ\) (\(z > 0\), to the right
+is identical to the cantoid for \(\theta \le \ang{90}\) (\(z > 0\), to the right
 of vertical dotted line in Fig.~\ref{fig:r-beta}), but is slightly
@@
   Due to the discontinuity in the inner wind density at
-  \(\theta = 90^\circ\) (see Fig.~\ref{fig:anisotropic-arrows}), there is a
+  \(\theta = \ang{90}\) (see Fig.~\ref{fig:anisotropic-arrows}), there is a
   discontinuity in the second derivative of the bow shape.} %
 Since the true planitude and alatude depend on \(R(\theta)\) only in the
-range \(\theta = [0, 90^\circ]\), the cantoid and the \(k = 0\) ancantoid
+range \(\theta = [0, \ang{90}]\), the cantoid and the \(k = 0\) ancantoid
 behave identically in Figure~\ref{fig:ancantoid-Pi-lambda-true}.
@@
   \label{eq:thetaQ-tail}
-  \theta_{\Q}\tail = \theta_\infty - 180^\circ \ , 
+  \theta_{\Q}\tail = \theta_\infty - \ang{180} \ , 
 \end{equation}
@@
 (more open than parabola) and terminate at a
-\(\theta_\infty < 180^\circ\).  The second type of behavior is shown by models with
+\(\theta_\infty < \ang{180}\).  The second type of behavior is shown by models with
 low \(\beta\) or high anisotropy, which behave like spheroids for positive
@@
 wings becoming markedly more open once \(\abs{i}\) exceeds
-\(60^\circ\) (for \(\beta = 0.001\)), or \(45^\circ\) (for
+\(\ang{60}\) (for \(\beta = 0.001\)), or \(\ang{45}\) (for
 \(\beta = 0.01\)).  The ancantoids (Fig.~\ref{fig:xyprime-ancantoid}) can
@@
 wings begin to become more closed with increasing inclination up to
-\(\abs{i} = 60^\circ\), at which point they open up again, whereas the
+\(\abs{i} = \ang{60}\), at which point they open up again, whereas the
 opening angle of the far wings increases monotonically with
@@
 \(k = 0\) ancantoids show a kink in their tracks at the point where
-the projected apex passes through \(\theta = 90^\circ\), due to the
+the projected apex passes through \(\theta = \ang{90}\), due to the
 discontinuity in the second derivative of \(R(\theta)\) there (see
@@
 in the ellipsoid region of the plane, the fact that it has
-\(\theta_\infty = 180^\circ\) means that it behaves more like a parabola at high
+\(\theta_\infty = \ang{180}\) means that it behaves more like a parabola at high
 inclination, but converges on

### 2017-12-06 papers/Paper1/conic_fig.py

@@ -1,96 +1,0 @@
-"""
-This scipt has been created for making some figures in section 4 
-"""
-from __future__ import print_function
-import numpy as np
-import sys
-sys.path.insert(0,"../../conic-projection")
-import conproj_utils as conproj
-import matplotlib.pyplot as plt
-import seaborn as sns
-import argparse
-
-
-parser = argparse.ArgumentParser(description="Choose the output figure")
-parser.add_argument("--fig",type=int,default = 0,choices=[0,1],help="Choose your figure output")
-args = parser.parse_args()
-flag= args.fig <= 0 
-############## Variying  \theta_c with unitary radius of curvature ####################
-
-# Figure style
-sns.set_style('ticks')
-#sns.set_context('talk')
-sns.set_color_codes('dark')
-
-
-#45: circle
-#30-15: ellipse
-# 0: parabola
-#-15- -45:hyperbola
-
-thc_list = [60, 45, 30, 0.0, -30,-45]
-conic_types = ['Oblate ellipse', 'Circle', 'Prolate ellipse',
-               'Parabola', 'Hyperbola', 'Hyperbola']
-
-if flag:
-    fig, ax = plt.subplots(1, 1)
-    ax.axhline(xmin=0.05,xmax=0.95,color="black",lw=1.5,alpha=0.7)
-    ax.axvline(ymin=0.05,ymax=0.95,color="black",lw=1.5,alpha=0.7)
-    
-    for t, s in reversed(list(zip(thc_list, conic_types))):
-        c  = conproj.Conic(A=2.0,th_conic = t)
-        trange = c.make_t_array()
-        ax.plot(c.x(trange), c.y(trange), lw=3, alpha=0.8,
-                label =r"{}: $\theta_q={:.0f}^\circ$".format(s, t))
-
-    # Star at origin
-    ax.plot([0],[0], "w*", ms=17, alpha=0.9)
-    ax.plot([0],[0], "b*", ms=15)
-    ax.plot([0],[0], "w*", ms=10, alpha=0.95)
-    # Circle at apex
-    ax.plot([1],[0], "wo", ms=7, alpha=0.9)
-    ax.plot([1],[0], "bo", ms=6)
-    ax.plot([1],[0], "wo", ms=4, alpha=0.95)
-
[…]

### 2017-12-06 papers/Paper1/json-plot.py

@@ -1,203 +1,0 @@
-"""
-Plot the ouputs from the program
-space-param-tab.py
-"""
-
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib
-import json
-import argparse
-import sys
-
-### Command line section ###
-
-parser = argparse.ArgumentParser(description="Plot output options")
-
-parser.add_argument("-x",type=str,default="i",choices=["i","I","R0","r0","beta","b"],help="x axis quantity")
-parser.add_argument("-y",type=str,default="Rc",choices=["Rc","rc","R0","r0","r90","R90"],help="y axis quantity")
-#the choices are made in a such way that does not distinguish between uppercases and lowercases, also beta and b
-#are equivalent choices
-
-args= parser.parse_args()
-
-inc_choice = (args.x == "i") or (args.x == "I")
-r0_choice_x = (args.x == "r0") or (args.x == "R0")
-r0_choice_y = (args.y == "r0") or (args.y == "R0")
-beta_choice = (args.x == "beta") or (args.x == "b")
-rc_choice = (args.y == "Rc") or (args.y == "rc")
-r90_choice = (args.y == "R90") or (args.y == "r90")
-print("You chose to plot {} vs {}".format(args.y,args.x))
-
-#print(r0_choice_x,"\n",r0_choice_y,"\n",inc_choice,"\n",beta_choice,"\n",rc_choice)
-#chosing R0 as x axis and y axis should lead to the identity function
-if r0_choice_x and r0_choice_y:
-    print("These choices don't lead to useful information")
-    sys.exit()
-
-### Open json file according to the x and y axis choices ###
-
-# RcVsR0.json has high resolution in inclinations
-# Rc-R0VsBeta.json has high resolution in beta
-
-# The potential plots we can do are the following:
-
-# Requires to open RcVsR0.json
-# - Rc vs R0 for a sample of beta values
-# - Rc vs inclination for a sample of beta values
-# - R0 vs inclination for a sample of beta values
-
-# Requires to open Rc-R0VsBeta.json
-# - Rc vs beta for a sample of inclinations
-# - R0 vs beta for a sample of inclinations
-# - Rc vs R0 for a sample of inclinations
-
-
[…]

### 2017-12-06 papers/Paper1/plot_log_fit.py

@@ -1,46 +1,0 @@
-import numpy as np
-import json
-import matplotlib.pyplot as plt
-from scipy.optimize import leastsq
-import argparse
-
-"""
-Attempt to fit log beta vs log [Rc,R0,R90]
-"""
-
-shelldata = json.load(open("Rc-R0VsBeta.json"))
-
-parser = argparse.ArgumentParser(description="choose y-axis to plot")
-parser.add_argument("--axis",type=str,default="Rc",choices=["Rc","R0","R90"],help="y-axis choice")
-parser.add_argument("--norm",action="store_true",help="Normalize with R0")
-
-cmd_args = parser.parse_args()
-b = np.logspace(-3,-1)
-y_arg = {"R0":"R0'","Rc": "Rc'_f","R90":"R90'"}
-y_lab = {"R0":"R'_0","Rc": "R'_c","R90":"R'_{90}"}
-y_a = {"R0":0.5*np.log10(b)-np.log10(1+np.sqrt(b)),"Rc":np.log10(1.5)+0.5*np.log10(b)-np.log10(1-b),
-       "R90":0.5*(np.log10(2.4)+np.log10(b)-3*np.log(1-0.8*b))}
-y_n = {"R0":0*b,"Rc":np.log10(1.5) - np.log10(1.-np.sqrt(b)) ,"R90":0.5*(np.log10(2.4)+2*np.log10(1+np.sqrt(b))-3*np.log(1-0.8*b))}
-for i,modeldata in shelldata.items():
-    beta = np.array(shelldata[i]["beta"])
-    y = np.array(shelldata[i][y_arg[cmd_args.axis]])
-    if cmd_args.norm:
-        R0 = np.array(shelldata[i]["R0'"])
-        Y = y/R0
-    else:
-        Y = y
-    plt.plot(np.log10(beta),np.log10(Y),":",label=i)
-
-if cmd_args.norm:
-    ylabel = r"$\log\left({}/R'_0\right)$".format(y_lab[cmd_args.axis])
-    fig_name = "log-beta-vs-log-{}-norm.pdf".format(y_lab[cmd_args.axis])
-    y_analytic = y_n[cmd_args.axis]
-else:
-    ylabel = r"$\log{}$".format(y_lab[cmd_args.axis])
-    fig_name = "log-beta-vs-log-{}.pdf".format(y_lab[cmd_args.axis])
-    y_analytic = y_a[cmd_args.axis]
[…]

### 2017-12-06 papers/Paper1/space-param-tab.py

@@ -1,118 +1,0 @@
-"""
-Create a json dictionary for one of the following figures
-0. Rc', R0' vs beta for i=0,15,30,45,60 degrees
-1. Json dictionary for Rc' vs R0' for beta = 0.001,0.01,0.05,0.08,0.1 if possible
-"""
-
-import numpy as np
-import sys
-sys.path.insert(0,"../..")
-from equation6 import Shell
-import toolbox as tool
-import matplotlib.pyplot as plt
-import argparse
-import json
-
-parser = argparse.ArgumentParser(description="Terminal options for script")
-parser.add_argument("--test",action="store_true",help="Run test for Rc accuracy")
-parser.add_argument("--fig",type=int,default=0,choices=[0,1],help="choose figure output")
-parser.add_argument("-N",type=int,default=30,help="Number of points of beta or inclination")
-args= parser.parse_args()
-
-theta = np.linspace(0,np.pi,500) #Looks like 500 points are a good enough resolution to
-                                 #obtain good results
-#Test Rc function accuracy
-
-if args.test:
-    shell = Shell(beta=0.01,innertype="proplyd")
-    R = shell.radius(theta)
-    R[R<=0]=np.nan
-    Rc,drc = tool.Rc(R,theta)
-    Rcfit = tool.Rc_fit(R,theta)
-    Rc_analytic = 1.5*R[0]/(1-np.sqrt(0.01))
-    print(Rc,Rc_analytic,Rcfit,Rc-Rc_analytic,Rcfit-Rc_analytic,drc)
-    print("Test finished")
-    sys.exit() #After running the test exit python
-
-if args.fig==0:
-    inc=[0,15,30,45,60]
-    beta = np.logspace(-3,-1,args.N)
-    shelldata = {}
-    R = [None]*len(beta)
-    shell = [None]*len(beta)
-    for i in inc:
-        print("Case i={}".format(i))
-        R0p = np.zeros_like(beta)*np.nan
-        dr0p = np.zeros_like(beta)*np.nan
-        Rcp = np.zeros_like(beta)*np.nan
-        drcp = np.zeros_like(beta)*np.nan
-        R90 = np.zeros_like(beta)*np.nan
-        Rcpf = np.zeros_like(beta)*np.nan
-        for j,b in enumerate(beta):
-            if i==0: #Avoid recalculate R for each iteration of inclination
[…]

### 2017-12-06 papers/Paper1/toolbox.py

@@ -1,112 +1,0 @@
-"""
-Set of functions to calculate
-tangent line, projected shapes, 
-characteristic radii, etc.
-"""
-
-import numpy as np
-from scipy.interpolate import interp1d
-from scipy.optimize import leastsq
-def omega(R,t):
-    """
-    Calculates the deivate of ln(R(theta))
-    """
-
-    return np.gradient(np.log(R))/np.gradient(t)
-
-def tangent_line(i,t,R):
-    """
-    sine of the azimutal angle of the tangent line
-    """
-    w = omega(R,t)
-    return  np.tan(np.radians(i))*(1+w*np.tan(t))/(w-np.tan(t))
-
-def projection(R,t,i):
-    """
-    Coordinates of the tangent line in the observer's
-    reference frame
-    """
-    sp = tangent_line(i,t,R)
-    xp = R*(np.cos(t)-np.sin(t)*sp*np.tan(np.radians(i)))
-    yp = R*(np.sin(t))*np.sqrt(1-sp**2)/np.cos(np.radians(i))
-    mask = np.isfinite(xp) & np.isfinite(yp)
-    return xp[mask],yp[mask]
-
-def theta_prime(xp,yp):
-    """
-    Polar angle of the projected shell. Enter x' & y'
-    """
-    return np.arctan2(yp,xp)
-
-def R_prime(xp,yp):
-    """
-    Returns projected radius of the shell. Enter x' and y'
-    """
-    return np.sqrt(xp**2+yp**2)
-
-def R0p(R,t):
-    """
-    Returns R'_0 and a uncertainty due to the first element of theta' is not
-    (almost sure) exactly 0 
-    """
-
-
-    r0p = R[0]
-    w = omega(R,t)
-    dr = np.abs(r0p*w[0]*t[0])
-    return r0p,dr
-
-def Rc(R,t):
-    """
-    Computes the radius of curvature at the shell's <<nose>> and the error margin.
-    This is a numeric approach, so, for i=0, the result will differ from the analytic 
-    result, but is accurate enough. Note: Enter projected R & theta
-    """
-    w = omega(R,t)
-    dw = np.gradient(w)/np.gradient(t) # Derivative of omega
-    rc = R[0]/np.abs(-dw[0]+1)
-    f = (w**2+1)**1.5/np.abs(w**2-dw+1)
-    df = np.gradient(f)/np.gradient(t)
-    drc = np.abs(R[0]*(df[0])*t[0])
-    return rc,drc
-
[…]

### 2017-12-06 papers/Papers1234/conic_fig.py

@@ -1,0 +1,96 @@
+"""
+This scipt has been created for making some figures in section 4 
+"""
+from __future__ import print_function
+import numpy as np
+import sys
+sys.path.insert(0,"../../conic-projection")
+import conproj_utils as conproj
+import matplotlib.pyplot as plt
+import seaborn as sns
+import argparse
+
+
+parser = argparse.ArgumentParser(description="Choose the output figure")
+parser.add_argument("--fig",type=int,default = 0,choices=[0,1],help="Choose your figure output")
+args = parser.parse_args()
+flag= args.fig <= 0 
+############## Variying  \theta_c with unitary radius of curvature ####################
+
+# Figure style
+sns.set_style('ticks')
+#sns.set_context('talk')
+sns.set_color_codes('dark')
+
+
+#45: circle
+#30-15: ellipse
+# 0: parabola
+#-15- -45:hyperbola
+
+thc_list = [60, 45, 30, 0.0, -30,-45]
+conic_types = ['Oblate ellipse', 'Circle', 'Prolate ellipse',
+               'Parabola', 'Hyperbola', 'Hyperbola']
+
+if flag:
+    fig, ax = plt.subplots(1, 1)
+    ax.axhline(xmin=0.05,xmax=0.95,color="black",lw=1.5,alpha=0.7)
+    ax.axvline(ymin=0.05,ymax=0.95,color="black",lw=1.5,alpha=0.7)
+    
+    for t, s in reversed(list(zip(thc_list, conic_types))):
+        c  = conproj.Conic(A=2.0,th_conic = t)
+        trange = c.make_t_array()
+        ax.plot(c.x(trange), c.y(trange), lw=3, alpha=0.8,
+                label =r"{}: $\theta_q={:.0f}^\circ$".format(s, t))
+
+    # Star at origin
+    ax.plot([0],[0], "w*", ms=17, alpha=0.9)
+    ax.plot([0],[0], "b*", ms=15)
+    ax.plot([0],[0], "w*", ms=10, alpha=0.95)
+    # Circle at apex
+    ax.plot([1],[0], "wo", ms=7, alpha=0.9)
+    ax.plot([1],[0], "bo", ms=6)
+    ax.plot([1],[0], "wo", ms=4, alpha=0.95)
+
[…]

### 2017-12-06 papers/Papers1234/json-plot.py

@@ -1,0 +1,203 @@
+"""
+Plot the ouputs from the program
+space-param-tab.py
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+import json
+import argparse
+import sys
+
+### Command line section ###
+
+parser = argparse.ArgumentParser(description="Plot output options")
+
+parser.add_argument("-x",type=str,default="i",choices=["i","I","R0","r0","beta","b"],help="x axis quantity")
+parser.add_argument("-y",type=str,default="Rc",choices=["Rc","rc","R0","r0","r90","R90"],help="y axis quantity")
+#the choices are made in a such way that does not distinguish between uppercases and lowercases, also beta and b
+#are equivalent choices
+
+args= parser.parse_args()
+
+inc_choice = (args.x == "i") or (args.x == "I")
+r0_choice_x = (args.x == "r0") or (args.x == "R0")
+r0_choice_y = (args.y == "r0") or (args.y == "R0")
+beta_choice = (args.x == "beta") or (args.x == "b")
+rc_choice = (args.y == "Rc") or (args.y == "rc")
+r90_choice = (args.y == "R90") or (args.y == "r90")
+print("You chose to plot {} vs {}".format(args.y,args.x))
+
+#print(r0_choice_x,"\n",r0_choice_y,"\n",inc_choice,"\n",beta_choice,"\n",rc_choice)
+#chosing R0 as x axis and y axis should lead to the identity function
+if r0_choice_x and r0_choice_y:
+    print("These choices don't lead to useful information")
+    sys.exit()
+
+### Open json file according to the x and y axis choices ###
+
+# RcVsR0.json has high resolution in inclinations
+# Rc-R0VsBeta.json has high resolution in beta
+
+# The potential plots we can do are the following:
+
+# Requires to open RcVsR0.json
+# - Rc vs R0 for a sample of beta values
+# - Rc vs inclination for a sample of beta values
+# - R0 vs inclination for a sample of beta values
+
+# Requires to open Rc-R0VsBeta.json
+# - Rc vs beta for a sample of inclinations
+# - R0 vs beta for a sample of inclinations
+# - Rc vs R0 for a sample of inclinations
+
+
[…]

### 2017-12-06 papers/Papers1234/shape_beta.py

@@ -1,0 +1,98 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+sys.path.insert(0,"../..")
+from equation6 import Shell
+import argparse
+import seaborn as sns
+###################################
+"""                              
+The objective of this program is 
+#to make a figure that illustrates
+how the shell shape changes with
+$\beta$ and if possible compare it
+with the result of other authors
+"""
+###################################
+
+############ Figure 1 #############
+# Shell shape vs $\beta$ ##########
+
+beta = [0.01,0.1,0.99]
+theta = np.linspace(0,0.99*np.pi)
+
+parser =argparse.ArgumentParser(description="choose figure output")
+parser.add_argument("--fig",type=int,default=0,choices=[0,1],help="figure output")
+args = parser.parse_args()
+flag = args.fig <= 0
+inner_list = ["isotropic","proplyd"]
+xi_list = [1.0,0.8,0.2]
+line_dict = {"isotropic":"--","proplyd":"-"}
+line_list = ["--","-",":",]
+color_list = ["r","g","b","m","c","k"]
+#label = {"isotropic":None,"proplyd":r"$\beta={}$".format(b)}
+sns.set_style("whitegrid")
+if flag:
+    for xi,line in zip(xi_list,line_list):
+        for b,col in zip(beta,color_list):
+            shell = Shell(beta=b,innertype="anisotropic",xi=xi)
+            R = shell.radius(theta)
+            R[R<=0] = np.nan
+            if xi==0.8:
+                label = r"$\beta={}$".format(b)
+            else:
+                label = None
+            plt.plot(R*np.cos(theta),R*np.sin(theta),color=col,linestyle=line,
+                     label=label)
+    fontsize = 15
+    ticksize = 14
+    plt.legend(fontsize="small")
+    plt.xlabel(r"$z/D$",fontsize=fontsize)
+    plt.ylabel(r"$r/D$",fontsize=fontsize)
+    plt.tick_params(axis='both', which='major', labelsize=ticksize)
+    plt.gca().set_aspect("equal",adjustable="box")
+    fig = plt.gcf()
+    fig.set_size_inches(7, 4.5)
[…]

### 2017-12-06 papers/Papers1234/space-param-tab.py

@@ -1,0 +1,118 @@
+"""
+Create a json dictionary for one of the following figures
+0. Rc', R0' vs beta for i=0,15,30,45,60 degrees
+1. Json dictionary for Rc' vs R0' for beta = 0.001,0.01,0.05,0.08,0.1 if possible
+"""
+
+import numpy as np
+import sys
+sys.path.insert(0,"../..")
+from equation6 import Shell
+import toolbox as tool
+import matplotlib.pyplot as plt
+import argparse
+import json
+
+parser = argparse.ArgumentParser(description="Terminal options for script")
+parser.add_argument("--test",action="store_true",help="Run test for Rc accuracy")
+parser.add_argument("--fig",type=int,default=0,choices=[0,1],help="choose figure output")
+parser.add_argument("-N",type=int,default=30,help="Number of points of beta or inclination")
+args= parser.parse_args()
+
+theta = np.linspace(0,np.pi,500) #Looks like 500 points are a good enough resolution to
+                                 #obtain good results
+#Test Rc function accuracy
+
+if args.test:
+    shell = Shell(beta=0.01,innertype="proplyd")
+    R = shell.radius(theta)
+    R[R<=0]=np.nan
+    Rc,drc = tool.Rc(R,theta)
+    Rcfit = tool.Rc_fit(R,theta)
+    Rc_analytic = 1.5*R[0]/(1-np.sqrt(0.01))
+    print(Rc,Rc_analytic,Rcfit,Rc-Rc_analytic,Rcfit-Rc_analytic,drc)
+    print("Test finished")
+    sys.exit() #After running the test exit python
+
+if args.fig==0:
+    inc=[0,15,30,45,60]
+    beta = np.logspace(-3,-1,args.N)
+    shelldata = {}
+    R = [None]*len(beta)
+    shell = [None]*len(beta)
+    for i in inc:
+        print("Case i={}".format(i))
+        R0p = np.zeros_like(beta)*np.nan
+        dr0p = np.zeros_like(beta)*np.nan
+        Rcp = np.zeros_like(beta)*np.nan
+        drcp = np.zeros_like(beta)*np.nan
+        R90 = np.zeros_like(beta)*np.nan
+        Rcpf = np.zeros_like(beta)*np.nan
+        for j,b in enumerate(beta):
+            if i==0: #Avoid recalculate R for each iteration of inclination
[…]

### 2017-12-15 papers/Papers1234/sec-dust-bow-intro.tex
Make a start on writing up the different dust regimes

--- 2017-11-23 papers/Paper1/sec-dust-bow-intro.tex
@@
 
+\section{Different types of bow}
+\label{sec:different-types-bow}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
+  \caption{Bow regimes of parameter space (\(v, n\)) of the external
+    stream for main-sequence OB stars of different masses:
+    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}. }
+  \label{fig:zones-v-n-plane}
+\end{figure*}
+
+We will mainly consider the canonical case of a bow around a star of
+bolometric luminosity, \(L\), with a radiatively driven
+wind,\footnote{In \S~\ref{sec:case-inside-out} we consider the case of
+  an external luminous source.} which is immersed in an external
+stream of gas and dust with density, \(\rho\), and velocity, \(v\).  The
+size and shape of the bow is determined by a generalized balance of
+pressure (or, equivalently, momentum) between internal and external
+sources.  We assume that the stream is supersonic and super-alfvenic,
+so that the external pressure is dominated by the ram pressure:
+\(\rho v^2\).
+
+\subsection{Imperfect coupling between gas and dust}
+\label{sec:imperf-coupl-betw}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
+  \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
+    gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
+  \label{fig:decouple-v-n-plane}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/decouple-v40-versus-n}
+  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
+    showing bow radius and different regimes for a fixed inflow
+    velocity of \SI{40}{km.s^{-1}}.}
+  \label{fig:decouple-v40-versus-n}
+\end{figure}
+
+\subsection{The case of inside-out bows with external illumination}
+\label{sec:case-inside-out}
+
 %%% Local Variables:

### 2017-12-15 Dust-wave/decouple-v-n-plane.py

@@ -8,11 +8,9 @@ figname = sys.argv[0].replace('.py', '.pdf')
 
 sns.set_style('ticks')
 sns.set_color_codes('dark')
-fig, axes = plt.subplots(1, 3, sharex=True, sharey=True, figsize=(8, 4))
+fig, ax = plt.subplots(1, 1, figsize=(3, 4))
 stardata = [
-    [10.0, 0.63, 0.0026, axes[0]],
-    [20.0, 5.5, 0.0446, axes[1]],
-    [40.0, 22.0, 0.1682, axes[2]],
+    [10.0, 0.63, 0.0026, ax],
 ]
 
 # Velocities in units of km/s (10 km/s -> 100 km/s)
@@ -96,19 +94,20 @@ for M, L4, eta, ax in stardata:
     if np.any(~m):
         alpha[m] = np.nan
         #ax.contourf(vv, nn, alpha, (0.5, 2.0), colors='m', alpha=0.2)
-        cs = ax.contour(vv, nn, alpha, (0.25, 0.5, 1.0, 2.0, 4.0, 20.0, 50.0),
+        cs = ax.contour(vv, nn, alpha, (0.5, 1.0, 2.0, 20.0, 80.0),
                         linewidths=0.3,
                         colors='m', alpha=0.5)
         ax.clabel(cs,
-                  fontsize='x-small', fmt=r"$\alpha = %.2f$",
-                  inline=True, inline_spacing=0.2, use_clabeltext=True)
+                  fontsize='xx-small', fmt=r"$\alpha = %.2f$",
+                  inline=True, inline_spacing=2, use_clabeltext=True)
     # ax.contour(vv, nn, tau, (eta/3, eta, 3*eta), colors='r')
     # ax.contour(vv, nn, tau, (1.0, 3.0), colors='m')
     cs = ax.contour(vv, nn, R0, R0s, linewidths=lws, colors='k')
     clevs = [level for level in clevs_to_label if level in cs.levels]
-    ax.clabel(cs, clevs,
+    ax.clabel(cs, (0.001, 0.01, 0.1, 1.0),
+              manual=((25, 5e5), (15, 3e3), (85, 1.2e-2), (20, 2e-3)),
               fontsize='xx-small', fmt=cformats,
-              inline=True, inline_spacing=0.2, use_clabeltext=True)
+              inline=True, inline_spacing=8, use_clabeltext=False)
 
 
[…]

### 2017-12-15 Dust-wave/zones-v-n-plane.py

@@ -46,6 +46,12 @@ RBW_label = r"Radiation bow wave, $\eta < \tau < 1$"
 RBS_label = r"Radiation bow shock, $\tau > 1$"
 WBS_label = r"Wind bow shock, $\tau < \eta$"
 
+# Miscellaneous panel-dependent plot params
+d = {
+    "trapped y": {10.0: 1.6e4, 20.0: 4.0e4, 40.0: 3.0e4},
+    "trapped bg": {10.0: '0.85', 20.0: 'w', 40.0: 'w'},
+}
+
 T0 = 8000
 for M, L4, eta, S49, ax in stardata:
     Mlabel = "\n".join([rf"$M = {M:.0f}\, M_\odot$",
@@ -65,17 +71,17 @@ for M, L4, eta, S49, ax in stardata:
     # Ionization fraction in shell
     ysh = 1.0 - 1.0/(3.5e5*Ush)
 
-    cs = ax.contour(vv, nn, ysh,
-                    (0.9, 0.99, 0.999, 0.9999, 0.99999),
-                    linewidths=1.0,
-                    colors='g', alpha=0.5)
-    ax.clabel(cs,
-              fontsize=5, colors='g', fmt='$%.5f$', 
-              inline=True, inline_spacing=1, use_clabeltext=True)
-    ax.text(75, 6e-3, fr"$y_\mathrm{{in}} = {ysh.max():.5f}$",
-            fontsize=5, color='g', alpha=0.5)
-    ax.text(12, 1.3e6, fr"$y_\mathrm{{in}} = {ysh.min():.5f}$",
-            fontsize=5, color='g', alpha=0.5)
+    # cs = ax.contour(vv, nn, ysh,
+    #                 (0.9, 0.99, 0.999, 0.9999, 0.99999),
+    #                 linewidths=1.0,
+    #                 colors='g', alpha=0.5)
+    # ax.clabel(cs,
+    #           fontsize=5, colors='g', fmt='$%.5f$', 
+    #           inline=True, inline_spacing=1, use_clabeltext=True)
+    # ax.text(75, 6e-3, fr"$y_\mathrm{{in}} = {ysh.max():.5f}$",
+    #         fontsize=5, color='g', alpha=0.5)
+    # ax.text(12, 1.3e6, fr"$y_\mathrm{{in}} = {ysh.min():.5f}$",
+    #         fontsize=5, color='g', alpha=0.5)
 
     # Fraction of ionizing photons absorbed in shell
[…]

### 2017-12-16 papers/Papers1234/sec-dust-bow-intro.tex
Get as far as Rstar in the write-up

@@
 
+The internal pressure is the sum of wind ram pressure and the
+effective radiation pressure that acts on the bow shell.  The
+radiative momentum loss rate of the star is \(L/c\) and the wind
+momentum loss rate can be expressed as
+\begin{equation}
+  \label{eq:wind-efficiency}
+  \dot{M} V = \eta L / c \ , 
+\end{equation}
+where \(\eta\) is the momentum efficiency of the wind, which is typically
+\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
+all of the stellar radiative momentum, emitted with rate \(L/c\), is
+trapped by the bow shell.  In the single scattering
+limit,\footnote{Why multiple scattering is not important.} and
+temporarily neglecting the wind, then pressure balance at the bow
+apex, a distance \(R\) along the symmetry axis from the star is given by
+\begin{equation}
+  \label{eq:2}
+  \frac{L}{4 \pi c R^2} = \rho v^2 \ ,
+\end{equation}
+which gives a fiducial bow shock radius in this limit as
+\begin{equation}
+  \label{eq:Rstar}
+  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
+\end{equation}
+
 \subsection{Imperfect coupling between gas and dust}

### 2017-12-19 papers/Papers1234/app-dust-wave.tex
Submitted first paper! To MNRAS and arxiv
Finish equations for different regimes in well-coupled case

--- 2017-11-21 papers/Paper1/app-dust-wave.tex
@@
 
-\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
-\newcommand{\grain}{\ensuremath{_{\text{d}}}}
-\newcommand{\xsec}{\ensuremath{\sigma\grain}}
-\newcommand\frad{\ensuremath{f_{\text{rad}}}}
-\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
 A dust grain of geometrical cross-section \(\xsec\) situated a
@@
 with a total deflection angle of \(2 \thm\), which is equal to
-\(90^\circ\) when \(b = 0.5 R_0\).
+\ang{90} when \(b = 0.5 R_0\).
 
@@
     coefficient, \(\alpha\drag\) increases from top-left to bottom-right.
-    Inclination \(\abs{i}\) is shown in \(15^\circ\) increments, indicated
+    Inclination \(\abs{i}\) is shown in \ang{15} increments, indicated
     by line color and thickness (see key).}

### 2017-12-19 papers/Papers1234/sec-dust-bow-intro.tex
Finish equations for different regimes in well-coupled case

@@
 so that the external pressure is dominated by the ram pressure:
-\(\rho v^2\).
+\(\rho v^2\). We first consider the case where the dust grains and gas
+are perfectly coupled by collisions (although this assumption is
+relaxed below in \S~\ref{sec:imperf-coupl-betw}).
 
@@
 temporarily neglecting the wind, then pressure balance at the bow
-apex, a distance \(R\) along the symmetry axis from the star is given by
+apex, a distance \(R_0\) along the symmetry axis from the star is given by
 \begin{equation}
-  \label{eq:2}
-  \frac{L}{4 \pi c R^2} = \rho v^2 \ ,
+  \label{eq:rad-press-balance-thick}
+  \frac{L}{4 \pi c R_0^2} = \rho v^2 \ ,
 \end{equation}
-which gives a fiducial bow shock radius in this limit as
+which gives a fiducial bow shock radius in this optically thick limit
+as
 \begin{equation}
@@
 \end{equation}
+
+We now consider the opposite, optically thin limit.  Although dust
+grains typically constitute only a small fraction
+\(Z\grain \sim 0.01\) of the mass of the external stream, they
+nevertheless dominate the broad-band opacity at FUV, optical and IR
+wavelengths if they are present.\footnote{%
+  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
+  dominates if the hydrogen neutral fraction is larger than
+  \(\approx 0.001\), see discussion of ionization front trapping
+  below.} %
+If the total opacity (gas plus dust) per total mass (gas plus dust) is
+\(\kappa\) (with units of \si{cm^2.g^{-1}}), then the radiative
+acceleration in the optically thin limit is
+\begin{equation}
+  \label{eq:rad-accel}
+  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ , 
+\end{equation}
+so that an incoming stream with initial velocity, \(v_\infty\), can be
+brought to rest by radiation alone\footnote{%
+  For simplicity, we here ignore the effects of pressure gradients and
+  shocks, which are important as the velocity approaches the sound
+  speed, \(\sound\). In \S~XX below, we show that the resultant
+  corrections to \(R_0\) are of order \(\sound / v_\infty\).} %
+at a distance \(R_0\) where
+\begin{equation}
+  \label{eq:rad-poten}
+  \int_{R_0}^\infty a_{\text{rad}} \, dr = \tfrac12 v^2 \ , 
+\end{equation}
+yielding
+\begin{equation}
+  \label{eq:rad:R0}
+  R_0 = \frac{\kappa L}{2\pi c v_\infty^2} \ .
+\end{equation}
+On the other hand, we can also employ a similar argument to the
+optically thick case above by approximating the bow shell as a
+surface, and balancing stellar radiation pressure against the ram
+pressure of the incoming stream.  The important difference when the
+shell is not optically thick is that only a fraction \(1 - e^{-\tau}\) of
+the radiative momentum is absorbed by the bow, so that equation~\eqref{eq:rad-press-balance-thick} is replaced with 
+\begin{equation}
+  \label{eq:rad-press-balance-tau}
+  \frac{L (1 - e^{-\tau})}{4 \pi c R_0^2} = \rho v^2 \ .
+\end{equation}
+In the optically thin limit, \(1 - e^{-\tau} \approx \tau\), so these two
+descriptions can be seen to agree so long as
+\(\tau = 2 \kappa \rho R_0\), which we will assume to be generally valid.
+
+Then, defining a fiducial optical depth, \(\tau_* = \rho \kappa R_*\), and adding
+in the stellar wind ram pressure\footnote{%
+  We implicitly assume that the interaction of the stellar wind with
+  the external stream can always be treated in the continuum limit.
+  This will be true if either the collisional mean free path or the
+  ion Larmor radius is much smaller than \(R_0\), which is almost
+  always the case.} %
+from equation~\eqref{eq:wind-efficiency}, we find that the general bow
+radius can be written in terms of the fiducial radius as
+\(R_0 = x R_*\), where \(x\) is the solution of
+\begin{equation}
+  \label{eq:rad-full-x}
+  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta = 0 \ .
+\end{equation}
+Since this is a transcendental equation, \(x\) must be found
+numerically, but we can write explicit expressions for three limiting
+cases:
+\begin{equation}
+  \label{eq:x-cases}
+  x \approx
+  \begin{cases}
+    \text{if \(\tau_* \gg 1\):} & (1 + \eta)^{1/2} \\
+    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta \bigr)^{1/2} \approx
+    \begin{cases}
+      \text{if \(\tau_*^2 \gg \eta\):} & 2 \tau_* \\
+      \text{if \(\tau_*^2 \ll \eta\):} & \eta^{1/2} 
+    \end{cases}
+  \end{cases}
+\end{equation}
+The first case, \(x \approx (1 + \eta)^{1/2}\), corresponds to a
+\textit{radiation bow shock}; the second case,
+\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave}; and the
+third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow shock}.
+The two bow shock cases are similar in that the external stream is
+oblivious to the presence of the star until it suddenly hits the bow
+shock shell, differing only in whether it is radiation or wind that is
+providing the internal pressure.  In the intermediate bow wave case,
+on the other hand, the external stream is gradually decelerated by
+absorption of photons as it approaches the bow.\footnote{A shock does
+  still form in this case, but shocked material constitutes a small
+  fraction of the total column density of the shell, see \S~XX.}
+
+We now consider the application to bow shocks around main sequence OB stars.
 

### 2017-12-19 papers/Papers1234/sec-dust-bow-intro.tex
Write up stellar parameters

@@
 
-We now consider the application to bow shocks around main sequence OB stars.
-
+We now consider the application to bow shocks around main sequence OB
+stars, expressing stellar and ambient parameters in terms of typical
+values as follows:
+\begin{gather*}
+  \label{eq:stellar-parameters}
+  \dot{M}_{-7} = \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
+  V_3 = V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
+  L_4 = L / \bigl(\SI{e4}{L_\odot}\bigr) \\
+  v_{10} = v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
+  n = (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
+  \kappa_{600} = \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
+\end{gather*}
+where \(\bar{m}\) is the mean mass per hydrogen nucleon
+(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
+abundances).  Note that \(\kappa = \SI{600}{cm^2.g^{-1}}\) corresponds to a
+cross section of \(\approx \SI{e-21}{cm^2}\) per hydrogen nucleon, which is
+typical for interstellar medium dust \citep{Bertoldi:1996a} at far
+ultraviolet wavelengths, where OB stars emit most of their radiation.
+In terms of these parameters, we can express the stellar wind momentum
+efficiency as
+\begin{equation}
+  \label{eq:wind-eta-typical}
+  \eta = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
+\end{equation}
+and the fiducial radius and optical depth as
+\begin{align}
+  \label{eq:fiducial-typical}
+  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
+  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1}
+\end{align}
 \subsection{Imperfect coupling between gas and dust}

### 2017-12-19 papers/Papers1234/sec-dust-bow-intro.tex
Added table of star parameters and reorganized a bit

@@
 
-We will mainly consider the canonical case of a bow around a star of
-bolometric luminosity, \(L\), with a radiatively driven
-wind,\footnote{In \S~\ref{sec:case-inside-out} we consider the case of
-  an external luminous source.} which is immersed in an external
-stream of gas and dust with density, \(\rho\), and velocity, \(v\).  The
-size and shape of the bow is determined by a generalized balance of
-pressure (or, equivalently, momentum) between internal and external
-sources.  We assume that the stream is supersonic and super-alfvenic,
-so that the external pressure is dominated by the ram pressure:
-\(\rho v^2\). We first consider the case where the dust grains and gas
-are perfectly coupled by collisions (although this assumption is
-relaxed below in \S~\ref{sec:imperf-coupl-betw}).
+In this section, we investigate the different types of bow interaction
+that will occur in different regions of parameter space. We will
+mainly treat the canonical case of a bow around a star of bolometric
+luminosity, \(L\), with a radiatively driven wind,\footnote{%
+  In \S~\ref{sec:case-inside-out} we consider the case of an external
+  luminous source.} %
+which is immersed in an external stream of gas and dust with density,
+\(\rho\), and velocity, \(v\).  The size and shape of the bow is
+determined by a generalized balance of pressure (or, equivalently,
+momentum) between internal and external sources.  We assume that the
+stream is supersonic and super-alfvenic, so that the external pressure
+is dominated by the ram pressure: \(\rho v^2\).
+
+\subsection{Strong gas-grain coupling}
+\label{sec:strong-gas-grain}
+
+We first consider the case where the dust grains and gas are perfectly
+coupled by collisions.\footnote{%
+  Cases where this assumption does not hold are investigated below in
+  \S~\ref{sec:imperf-coupl-betw}.} %
+Although dust grains typically constitute only a small fraction
+\(Z\grain \sim 0.01\) of the mass of the external stream, they
+nevertheless dominate the broad-band opacity at FUV, optical and IR
+wavelengths if they are present.\footnote{%
+  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
+  dominates if the hydrogen neutral fraction is larger than
+  \(\approx 0.001\), see discussion of ionization front trapping
+  below.} %
+The strong coupling assumption means that all the radiative forces
+applied to the dust grains are directly felt by the gas also.
 
@@
 all of the stellar radiative momentum, emitted with rate \(L/c\), is
-trapped by the bow shell.  In the single scattering
-limit,\footnote{Why multiple scattering is not important.} and
-temporarily neglecting the wind, then pressure balance at the bow
-apex, a distance \(R_0\) along the symmetry axis from the star is given by
+trapped by the bow shell.  In the single scattering limit,\footnote{%
+  Although it may seem inconsistent to assume single scattering in the
+  case of high optical depths, this is defensible for the following
+  reasons. (1)~The grain albedo is not that high (typically
+  \(\sim 0.5\) at ultraviolet through optical wavelengths). (2)~The
+  scattered radiation field is more isotropic than the stellar field,
+  leading to cancellation in the radiative
+  flux. (3)~Absorbed radiation is re-emitted at infrared
+  wavelengths, where the dust opacity is very much lower.} %
+and temporarily neglecting the wind, then pressure balance at the bow
+apex, a distance \(R_0\) along the symmetry axis from the star is
+given by
 \begin{equation}
@@
 \end{equation}
-which gives a fiducial bow shock radius in this optically thick limit
+which yields a fiducial bow shock radius in this optically thick limit
 as
@@
 
-We now consider the opposite, optically thin limit.  Although dust
-grains typically constitute only a small fraction
-\(Z\grain \sim 0.01\) of the mass of the external stream, they
-nevertheless dominate the broad-band opacity at FUV, optical and IR
-wavelengths if they are present.\footnote{%
-  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
-  dominates if the hydrogen neutral fraction is larger than
-  \(\approx 0.001\), see discussion of ionization front trapping
-  below.} %
-If the total opacity (gas plus dust) per total mass (gas plus dust) is
-\(\kappa\) (with units of \si{cm^2.g^{-1}}), then the radiative
-acceleration in the optically thin limit is
+We now consider the opposite, optically thin limit.  If the total
+opacity (gas plus dust) per total mass (gas plus dust) is \(\kappa\) (with
+units of \si{cm^2.g^{-1}}), then the radiative acceleration is
 \begin{equation}
@@
 shell is not optically thick is that only a fraction \(1 - e^{-\tau}\) of
-the radiative momentum is absorbed by the bow, so that equation~\eqref{eq:rad-press-balance-thick} is replaced with 
+the radiative momentum is absorbed by the bow, so that
+equation~\eqref{eq:rad-press-balance-thick} is replaced with
 \begin{equation}
@@
 descriptions can be seen to agree so long as
-\(\tau = 2 \kappa \rho R_0\), which we will assume to be generally valid.
+\(\tau = 2 \kappa \rho R_0\), which we will assume to hold generally.
 
@@
 
+\begin{table*}
+  \centering
+  \caption{Stellar parameters for main-sequence OB stars}
+  \label{tab:stars}
+  \begin{tabular}{l S S S S S S S S l}
+    \toprule
+    & {\(M / \si{M_\odot}\)} & {\(L_4\)}
+    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta \)}
+    & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
+    & {\(S_{49}\)} & Figures 
+    \\
+    \midrule
+    & 10 & 0.63 & 0.003 & 1.082 & 0.0026 & 25.2 & 0.115 & e-4
+                   & \ref{fig:zones-v-n-plane}a,
+                     \ref{fig:decouple-v-n-plane},
+                     \ref{fig:decouple-v40-versus-n} \\
+    Main-sequence OB stars
+    & 20 & 5.5 & 0.42 & 1.167 & 0.0446 & 33.9 & 0.086 & 0.1
+                   & \ref{fig:zones-v-n-plane}b\\
+    & 40 & 22 & 5.1 & 1.451 & 0.1682 & 42.5 & 0.068 & 1.0
+                   & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
+    Red supergiant star
+    & 20 & 15.6 & 100 & 0.015 & 0.0476 & 4 & 0.725 & 0
+                   & \\ 
+    \bottomrule
+  \end{tabular}
+\end{table*}
+
 We now consider the application to bow shocks around main sequence OB
@@
   R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
-  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1}
+  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
 \end{align}
+In Figure~\ref{fig:zones-v-n-plane}, we show results for the bow size
+(apex distance, \(R_0\)) as a function of the density, \(n\), and
+relative velocity, \(v_\infty\), of the external stream, with each panel
+corresponding to a particular star, with parameters as shown in
+Table~\ref{tab:stars}.
+
 \subsection{Imperfect coupling between gas and dust}

### 2017-12-19 papers/Papers1234/sec-dust-bow-intro.tex
Fix the wind velocities for the stars
Meyer had got it totally wrong

@@
 corresponding to a particular star, with parameters as shown in
-Table~\ref{tab:stars}.
+Table~\ref{tab:stars}.  To facilitate comparison with previous work,
+we choose to use the stellar parameters given in \citet{Meyer:2014b,
+  Meyer:2016a, Meyer:2017a}, based on stellar evolution tracks for
+stars of \SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and 
+theoretical wind prescriptions \citep{de-Jager:1988a, Vink:2000a}.
 

### 2017-12-19 papers/Papers1234/sec-dust-bow-intro.tex
Write more of inside-out section
Also, finish replacing the stellar data properly and re-doing the
figures for the new faster wind speeds.  And add Jane as an author,
since she has been helping with the stellar parameters.

@@
   \centering
-  \caption{Stellar parameters for main-sequence OB stars}
+  \caption{Stellar parameters for example stars}
   \label{tab:stars}
-  \begin{tabular}{l S S S S S S S S l}
+  \begin{tabular}{l S S S S S S S S S l}
     \toprule
@@
     & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta \)}
+    & {Sp.~Type} 
     & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
@@
     \midrule
-    & 10 & 0.63 & 0.003 & 1.082 & 0.0026 & 25.2 & 0.115 & e-4
+    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & e-4
                    & \ref{fig:zones-v-n-plane}a,
@@
     Main-sequence OB stars
-    & 20 & 5.5 & 0.42 & 1.167 & 0.0446 & 33.9 & 0.086 & 0.1
+    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.1
                    & \ref{fig:zones-v-n-plane}b\\
-    & 40 & 22 & 5.1 & 1.451 & 0.1682 & 42.5 & 0.068 & 1.0
+    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.0
                    & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
     Red supergiant star
-    & 20 & 15.6 & 100 & 0.015 & 0.0476 & 4 & 0.725 & 0
+    & 20 & 15.6 & 100 & 0.015 & 0.0476 & {M1\,Ia} & 3.6 & 0.805 & 0
                    & \\ 
@@
 
-\subsection{The case of inside-out bows with external illumination}
+\subsection{The case of inside-out bows}
 \label{sec:case-inside-out}
+
+So far, we have considered the case where the inner source dominates
+the radiation, while dust is present only in the outer stream, which
+applies to hot stars interacting with the ISM.  However, in the case
+of cool stars, the inner wind will also be dusty.  Examples are the
+red supergiant (RSG) phase of high-mass evolution, or the asymptotic
+giant branch (AGB) stage of low/intermediate-mass evolution.  In both
+these cases, it is still the inner source that provides the radiation
+field.  However, not all winds are radiatively driven and in those
+cases it is conceivable that it is the outer source that dominates the
+radiation field.  An example is the case of photoevaporating
+protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
+regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
+thermally driven photoevaporation flow \citep{HA:1998, Henney:1999a},
+while the outer stream is the stellar wind from an O~star
+\citep{Garcia-Arredondo:2001a}.
 

### 2017-12-19 Dust-wave/decouple-v-n-plane.py

@@ -10,7 +10,7 @@ sns.set_style('ticks')
 sns.set_color_codes('dark')
 fig, ax = plt.subplots(1, 1, figsize=(3, 4))
 stardata = [
-    [10.0, 0.63, 0.0026, ax],
+    [10.0, 0.63, 0.0066, ax],
 ]
 
 # Velocities in units of km/s (10 km/s -> 100 km/s)
@@ -74,7 +74,7 @@ for M, L4, eta, ax in stardata:
     Rwbs = eta**0.5 * Rs
 
     # Gas deceleration through dust wave Delta v/v
-    dv_v = 0.82*(1.0 + alpha)*Zd
+    dv_v = 0.75*(1.0 + alpha)*Zd
     # Inner bow shock radius inside a dust wave
     Ribs = eta**0.5 * rstar((1.0 - dv_v)*vv/10, nn, L4)
     # Don't let it be bigger than dust wave

### 2017-12-20 papers/Papers1234/sec-dust-bow-intro.tex
Finish long footnote on stellar wind models
And add a bit to a new section about observations of IR arcs in Carina

@@
 that will occur in different regions of parameter space. We will
-mainly treat the canonical case of a bow around a star of bolometric
-luminosity, \(L\), with a radiatively driven wind,\footnote{%
-  In \S~\ref{sec:case-inside-out} we consider the case of an external
-  luminous source.} %
-which is immersed in an external stream of gas and dust with density,
-\(\rho\), and velocity, \(v\).  The size and shape of the bow is
-determined by a generalized balance of pressure (or, equivalently,
-momentum) between internal and external sources.  We assume that the
-stream is supersonic and super-alfvenic, so that the external pressure
-is dominated by the ram pressure: \(\rho v^2\).
+mainly treat the canonical case\footnote{%
+  Variant cases with differing arrangements of dust and radiation
+  sources are treated in \S~\ref{sec:case-inside-out}.} %
+of a bow around a star of bolometric luminosity, \(L\), with a
+radiatively driven wind, which is immersed in an external stream of
+gas and dust with density, \(\rho\), and velocity, \(v\).  The size and
+shape of the bow is determined by a generalized balance of pressure
+(or, equivalently, momentum) between internal and external sources.
+We assume that the stream is supersonic and super-alfvenic, so that
+the external pressure is dominated by the ram pressure: \(\rho v^2\).
 
@@
 \end{equation}
-On the other hand, we can also employ a similar argument to the
-optically thick case above by approximating the bow shell as a
-surface, and balancing stellar radiation pressure against the ram
-pressure of the incoming stream.  The important difference when the
-shell is not optically thick is that only a fraction \(1 - e^{-\tau}\) of
-the radiative momentum is absorbed by the bow, so that
+On the other hand, we can also argue as in the optically thick case
+above by approximating the bow shell as a surface, and balancing
+stellar radiation pressure against the ram pressure of the incoming
+stream.  The important difference when the shell is not optically
+thick is that only a fraction \(1 - e^{-\tau}\) of the radiative momentum
+is absorbed by the bow, so that
 equation~\eqref{eq:rad-press-balance-thick} is replaced with
@@
   still form in this case, but shocked material constitutes a small
-  fraction of the total column density of the shell, see \S~XX.}
+  fraction of the total column density of the shell, see
+  \S~\ref{sec:shape-bow-wave}.}
 
@@
 Table~\ref{tab:stars}.  To facilitate comparison with previous work,
-we choose to use the stellar parameters given in \citet{Meyer:2014b,
-  Meyer:2016a, Meyer:2017a}, based on stellar evolution tracks for
-stars of \SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and 
-theoretical wind prescriptions \citep{de-Jager:1988a, Vink:2000a}.
+we choose stellar parameters similar to those used in the
+hydrodynamical simulations of \citet{Meyer:2014b, Meyer:2016a,
+  Meyer:2017a}, based on stellar evolution tracks for stars of
+\SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and theoretical wind
+prescriptions \citep{de-Jager:1988a, Vink:2000a}.  Although the
+stellar parameters do evolve with time, they change relatively little
+during the main-sequence lifetime of several million years.\footnote{%
+  \label{fn:meyer-velocities-too-low}
+  Note that we have recalculated the stellar wind terminal velocities,
+  since the values given in the \citeauthor{Meyer:2014b} papers are
+  troublingly low.  We have used the prescription
+  \(V = 2.6 V_{\text{esc}}\), where
+  \(V_{\text{esc}} = \left( 2 G M (1 - \Gamma_e)/ R \right)^{1/2}\) is the
+  photospheric escape velocity, which is appropriate for strong
+  line-driven winds with \(T_{\text{eff}} > \SI{21 000}{K}\)
+  \citep{Lamers:1995a}.  We find velocities of
+  \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
+  observations and theory \citep{Vink:1999a} for O~stars, but at least
+  two times higher than those cited by \citet{Meyer:2014b}. For
+  main-sequence B~stars, wind column densities are too low to reliably
+  measure the terminal velocity from near ultraviolet P~Cygni profiles
+  \citep{Prinja:1989a}, and so the values are theory-dependent
+  \citep{Krticka:2014a} and hence more uncertain.  A further
+  complication is the existence of a subset of OB stars with
+  anomalously weak winds \citep{Puls:2008a}, which in some cases is
+  related to the presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
+  \citep{Oskinova:2011b}.} %
 

### 2017-12-20 papers/Papers1234/sec-dust-case-studies.tex
Finish long footnote on stellar wind models
And add a bit to a new section about observations of IR arcs in Carina

\section{Case studies}
\label{sec:case-studies}

Carina mid-infrared bow shocks \citep{Sexton:2015b} are in a high
density environment, \SI{1000}{cm^{-3}}, so they may be bow waves.
There seems to be spectral types for most of them: B0 (but supergiant)
to O7.  Sizes are 3 to 12 arcsec, which at Carina (\SI{2.3}{kpc}) is
\SIrange{0.033}{0.134}{pc}.

Amazingly, the size/density combination gives regions that overlap
with the dust wave region for both the \SI{20}{M_\odot} and \SI{40}{M_\odot}
case.  And implying velocities of \SIrange{30}{50}{km.s^{-1}}.  This
is more believable than the \SI{10}{km.s^{-1}} that they quote, since
that would not give a shock at all.  This would imply
\(\tau > \eta \approx 0.1\), so the bow luminosity should be 10\% of the star
luminosity, so getting on for \SI{e4}{L_\odot}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dusty-bow-wave"
%%% End:

### 2017-12-20 papers/Papers1234/sec-dust-bow-intro.tex
Finish figure caption for regimes in v-n plane

@@
   \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
-  \caption{Bow regimes of parameter space (\(v, n\)) of the external
+  \caption{Bow regimes in parameter space (\(v, n\)) of the external
     stream for main-sequence OB stars of different masses:
-    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}. }
+    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}.  In all
+    cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
+    coupling is assumed. Solid black lines of varying width show the
+    bow size (star-apex separation, \(R_0\)), while gray shading shows
+    the radiation bow wave regime, with lower border \(\tau = \eta\) and
+    upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
+    depth through the bow.  For bows above the red solid line, the
+    ionization front is trapped inside the bow.  Blue lines delineate
+    different cooling regimes.  Above the thin blue line
+    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
+    forming a thin shocked shell.  Below the thick blue line
+    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
+    non-radiative.}
   \label{fig:zones-v-n-plane}
@@
   \citep{Oskinova:2011b}.} %
+The three examples are an early B~star (\SI{10}{M_\odot}), a late O~star
+(\SI{20}{M_\odot}), and an early O~star (\SI{40}{M_\odot}), which cover the
+range of luminosities and wind strengths expected from bow-producing
+hot main sequence stars.  The luminosity is a steep function of
+stellar mass (\(L \sim M^{2.5}\)) and the wind mass-loss rate is a steep
+function of luminosity (\(\dot{M} \sim L^{2.2}\)), which means that the
+wind momentum efficiency is also a steep function of mass
+(\(\eta \sim M^3\)), approaching unity for early O~stars, but falling to
+less than 1\% for B~stars.
 

### 2017-12-21 papers/Papers1234/sec-dust-bow-intro.tex
Revisit the ionization front trapping
Take into account hardening.  And calculate the dust and gas optical
depths separately for the shocked shell

@@
 
+\subsection{Radiative cooling lengths}
+\label{sec:radi-cool-lengths}
+
+\subsection{Ionization state of the bow shell}
+\label{sec:trapp-ioniz-front}
+
+\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
+\newcommand\shell{\ensuremath{_{\text{sh}}}}
+
+We wish to calculate whether the star is capable of photoionizing the
+entire bow shock shell, or whether the ionization front will be trapped
+within it.  The number of hydrogen recombinations per unit time per
+unit area in a fully ionized shell is \(\mathcal{R} = \alphaB n\shell^2 h\shell\),
+while the flux of ionizing photons incident on the inner edge of the
+shell is \(\mathcal{F} = S / 4 \pi R_0^2\).  Assuming photoionization equilibrium, the hydrogen photoabsorption optical depth of the shell is
+\begin{equation}
+  \label{eq:ion-tau-gas}
+  \tau\gas = - \ln(1 - \mathcal{R} / \mathcal{F}) \ .
+\end{equation}
+The column density of the shocked shell can be found, for example, from equations~(10) and~(12) of \citet{Wilkin:1996a} in the limit \(v/V \to 0\) (Wilkin's parameter \(\alpha\)) and \(\theta \to 0\).
+This yields
+\begin{equation}
+  \label{eq:shocked-shell-column}
+  n\shell h\shell = \tfrac34 n R_0 \ .
+\end{equation}
+
 \subsection{Imperfect coupling between gas and dust}

### 2017-12-21 Dust-wave/zones-v-n-plane.py

@@ -48,8 +48,11 @@ WBS_label = r"Wind bow shock, $\tau < \eta$"
 
 # Miscellaneous panel-dependent plot params
 d = {
-    "trapped y": {10.0: 1.6e4, 20.0: 4.0e4, 40.0: 3.0e4},
+    "RBW y": {10.0: 4000.0, 20.0: 5000.0, 40.0: 2500.0},
+    "trapped y": {10.0: 3.5e4, 20.0: 2.5e5, 40.0: 1.5e5},
     "trapped bg": {10.0: '0.85', 20.0: 'w', 40.0: 'w'},
+    "IF tau": {10.0: 0.2, 20.0: 3.7, 40.0: 6.4},
+    "IF tau gas": {10.0: 5.0, 20.0: 5.0, 40.0: 5.0},
 }
 
 T0 = 8000
@@ -84,13 +87,15 @@ for M, L4, eta, S49, ax in stardata:
     #         fontsize=5, color='g', alpha=0.5)
 
     # Fraction of ionizing photons absorbed in shell
-    absfrac = 2.56e-5 * (vv/10)**2 * nn**2 * R0**3 / S49
+    absfrac0 = 3*np.pi*(3.085677582e18)**3 * 2.6e-13 / 1e49
+    absfrac = absfrac0 * (vv/10)**2 * nn**2 * R0**3 / S49
     # Equivalent optical depth
     tau_gas = -np.log(1.0 - absfrac)
     #absfrac = 2.76e-4 * (vv/10)**-1 * nn**0.5 * (L4)**1.5 / S49
 
+    tau_dust = (3/8)*tau
     # Ionization parameter just outside the shell
-    Uout = U*np.exp(-(tau + tau_gas))
+    Uout = U*np.exp(-(tau_dust + tau_gas))
     Uout[~np.isfinite(Uout)] = 0.0
     Ushout = Uout/(vv/10)**2
 
@@ -112,12 +117,28 @@ for M, L4, eta, S49, ax in stardata:
     #           inline=True, inline_spacing=1, use_clabeltext=True)
 
     #ax.contour(vv, nn, 3.5e5*Uout, (0.5, 98.1), colors='r', alpha=0.5)
-    cs = ax.contour(vv, nn, 3.5e5*Ushout, (0.5,), linewidths=2, colors='r', alpha=0.5)
+    c_sig_over_alpha = 2.99792458e10*3e-18 / 2.6e-13
[…]

### 2017-12-21 papers/Papers1234/sec-dust-bow-intro.tex
More progress on i-front trapping

@@
 descriptions can be seen to agree so long as
-\(\tau = 2 \kappa \rho R_0\), which we will assume to hold generally.
+\begin{equation}
+  \label{eq:tau-thin}
+  \tau = 2 \kappa \rho R_0 \ ,
+\end{equation}
+which we will assume to hold generally.
 
@@
 absorption of photons as it approaches the bow.\footnote{A shock does
-  still form in this case, but shocked material constitutes a small
+  still form in this case, but shocked material constitutes only a
   fraction of the total column density of the shell, see
@@
 values as follows:
-\begin{gather*}
+\begin{align*}
   \label{eq:stellar-parameters}
-  \dot{M}_{-7} = \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
-  V_3 = V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
-  L_4 = L / \bigl(\SI{e4}{L_\odot}\bigr) \\
-  v_{10} = v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
-  n = (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
-  \kappa_{600} = \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
-\end{gather*}
+  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
+  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
+  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
+  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
+  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
+  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
+\end{align*}
 where \(\bar{m}\) is the mean mass per hydrogen nucleon
@@
 
-\subsection{Radiative cooling lengths}
-\label{sec:radi-cool-lengths}
-
 \subsection{Ionization state of the bow shell}
@@
 We wish to calculate whether the star is capable of photoionizing the
-entire bow shock shell, or whether the ionization front will be trapped
-within it.  The number of hydrogen recombinations per unit time per
-unit area in a fully ionized shell is \(\mathcal{R} = \alphaB n\shell^2 h\shell\),
-while the flux of ionizing photons incident on the inner edge of the
-shell is \(\mathcal{F} = S / 4 \pi R_0^2\).  Assuming photoionization equilibrium, the hydrogen photoabsorption optical depth of the shell is
+entire bow shock shell, or whether the ionization front will be
+trapped within it.  The number of hydrogen recombinations\footnote{%
+  The diffuse field is treated in the on-the-spot approximation,
+  assuming all emitted Lyman continuum photons are immediately
+  re-absorbed locally, so the case~B recombination co-efficient,
+  \(\alphaB = \num{2.6e-13}\, (T/\SI{e4}{K})\, \si{cm^3.s^{-1}}\), is
+  used.} %
+per unit time per unit area in a fully ionized shell is
+\(\mathcal{R} = \alphaB n\shell^2 h\shell\), while the flux of
+hydrogen-ionizing photons (\(h \nu > \SI{13.6}{eV}\)) incident on the
+inner edge of the shell is \(\mathcal{F} = S / 4 \pi R_0^2\), where
+\(S\) is the ionizing photon luminosity of the star.  Assuming
+photoionization equilibrium, the hydrogen photoabsorption optical
+depth of the shell is
 \begin{equation}
   \label{eq:ion-tau-gas}
-  \tau\gas = - \ln(1 - \mathcal{R} / \mathcal{F}) \ .
+  \tau\gas = - \ln(1 - \mathcal{R} / \mathcal{F}) \ ,
 \end{equation}
-The column density of the shocked shell can be found, for example, from equations~(10) and~(12) of \citet{Wilkin:1996a} in the limit \(v/V \to 0\) (Wilkin's parameter \(\alpha\)) and \(\theta \to 0\).
-This yields
+so long as \(\mathcal{R} < \mathcal{F}\).  The column density of the
+shocked shell can be found, for example, from equations~(10) and~(12)
+of \citet{Wilkin:1996a} in the limit \(v/V \to 0\) (Wilkin's parameter
+\(\alpha\)) and \(\theta \to 0\).  This yields
 \begin{equation}
@@
 \end{equation}
+Assuming strong cooling behind the shock,\footnote{%
+  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
+} %
+the shell density is \(n\shell = M_0^2 n\), where \(M_0 = v / \sound\)
+is the isothermal Mach number of the external stream.  We will assume
+a typical photoionized temperature of \SI{8000}{K}, so that
+\(\sound \approx \SI{10}{km.s^{-1}}\) and \(M_0 = v_{10}\), yielding
+\begin{equation}
+  \label{eq:ion-tau-gas-expanded}
+  \tau\gas = -\ln\bigl(1 -
+  \num{8.42e-6}\, v_{10}^2 n^2 R_{0,\text{pc}}^3 S_{49}^{-1}\bigr) \ , 
+\end{equation}
+where 
+\begin{align*}
+  R_{0,\text{pc}} &= R_0 / \bigl( \SI{1}{pc} \bigr) \\
+  S_{49} &= S / \bigl( \SI{e49}{s^{-1}} \bigr) \ . 
+\end{align*}
+Numerical values of \(S_{49}\) for our three example stars are given
+in Table~\ref{tab:stars}.  The dust opacity is approximately constant
+at FUV to EUV wavelengths, so the dust optical depth of the shocked
+shell to ionizing photons follows from equations~\eqref{eq:tau-thin}
+and~\eqref{eq:shocked-shell-column} as \(\tau\grain = \tfrac38 \tau\).
+
+The hydrogen ionization fraction, \(y\), at the outer edge of the shocked
+shell then follows as
+\begin{equation}
+  \label{eq:outer-shell-ionization-balance}
+  \frac{y^2}{1 - y} = \frac{\sigma \mathcal{F}}{\alphaB n} e^{-(\tau\grain + \tau\gas)} \ ,
+\end{equation}
+where \(\sigma\) is the effective hydrogen photoionization cross section.
+\begin{equation}
+  \label{eq:sigma-vs-tau}
+  \sigma = 0.5 \sigma_0 e^{-\tau\gas/3}
+\end{equation}
+where \(\sigma_0 = \SI{6e-18}{cm^2}\) is the threshold cross-section.
+
+\subsection{Radiative cooling lengths}
+\label{sec:radi-cool-lengths}
 

### 2017-12-21 Dust-wave/zones-v-n-plane.py

@@ -87,7 +87,8 @@ for M, L4, eta, S49, ax in stardata:
     #         fontsize=5, color='g', alpha=0.5)
 
     # Fraction of ionizing photons absorbed in shell
-    absfrac0 = 3*np.pi*(3.085677582e18)**3 * 2.6e-13 / 1e49
+    alphaB = 2.6e-13*(T0/1e4)**(-0.7)
+    absfrac0 = 3*np.pi*(3.085677582e18)**3 * alphaB / 1e49
     absfrac = absfrac0 * (vv/10)**2 * nn**2 * R0**3 / S49
     # Equivalent optical depth
     tau_gas = -np.log(1.0 - absfrac)
@@ -117,7 +118,7 @@ for M, L4, eta, S49, ax in stardata:
     #           inline=True, inline_spacing=1, use_clabeltext=True)
 
     #ax.contour(vv, nn, 3.5e5*Uout, (0.5, 98.1), colors='r', alpha=0.5)
-    c_sig_over_alpha = 2.99792458e10*3e-18 / 2.6e-13
+    c_sig_over_alpha = 2.99792458e10*3e-18 / alphaB
     c_sig_over_alpha *= (1 - absfrac)**(1./3.)
     y_IF = 0.5
     y1, y2 = 0.01, 0.99
@@ -135,7 +136,7 @@ for M, L4, eta, S49, ax in stardata:
     #            colors='y', linewidths=0.4)
     arrows = r"$\uparrow\!\!\!\!\uparrow$"
     ax.text(60, d["trapped y"][M],
-            rf"{arrows} Trapped i-front, $\tau = {tau_dust_IF:.1f}$, $\tau_\mathrm{{gas}} = {tau_gas_IF:.1f}$ {arrows}",
+            rf"{arrows} Trapped i-front, $\tau_\mathrm{{d}} = {tau_dust_IF:.1f}$, $\tau_\mathrm{{gas}} = {tau_gas_IF:.1f}$ {arrows}",
             ha='center', va='center',
             fontsize='xx-small', color='r', alpha=0.5, rotation=10,
             bbox=dict(fc=d["trapped bg"][M], ec='none', pad=0.1)

### 2017-12-22 papers/Papers1234/sec-dust-bow-intro.tex
Yet more work on the ionization trapping - still not finished!
I have managed to simplify things, but still have a bit of work to do

@@
 per unit time per unit area in a fully ionized shell is
-\(\mathcal{R} = \alphaB n\shell^2 h\shell\), while the flux of
-hydrogen-ionizing photons (\(h \nu > \SI{13.6}{eV}\)) incident on the
-inner edge of the shell is \(\mathcal{F} = S / 4 \pi R_0^2\), where
-\(S\) is the ionizing photon luminosity of the star.  Assuming
-photoionization equilibrium, the hydrogen photoabsorption optical
-depth of the shell is
+\begin{equation}
+  \label{eq:shell-recombination-rate}
+  \mathcal{R} = \alphaB n\shell^2 h\shell \ ,
+\end{equation}
+while the flux of hydrogen-ionizing photons
+(\(h \nu > \SI{13.6}{eV}\)) incident on the inner edge of the shell is
+\begin{equation}
+  \label{eq:shell-ionizing-flux}
+  \mathcal{F} = \frac{S} {4 \pi R_0^2} \ , 
+\end{equation}
+where \(S\) is the ionizing photon luminosity of the star.  Any shell
+with \(\mathcal{R} > \mathcal{F}\) cannot be entirely photoionized by
+the star, and so must have trapped the ionization front.  This simple
+criterion is shown by the dark red line in
+Figure~\ref{fig:zones-v-n-plane}.  If 
+\(n / v_{10}^2 > \text{\numrange{1000}{5000}}\), depending
+only weakly on the stellar parameters, then the outer parts of the
+shocked shell are neutral, instead of ionized.
+
+Assuming photoionization equilibrium, the
+hydrogen photoabsorption optical depth of the shell is
 \begin{equation}
@@
 shocked shell can be found, for example, from equations~(10) and~(12)
-of \citet{Wilkin:1996a} in the limit \(v/V \to 0\) (Wilkin's parameter
+of \citet{Wilkin:1996a} in the limit \(v_\infty/V \to 0\) (Wilkin's parameter
 \(\alpha\)) and \(\theta \to 0\).  This yields
@@
 \end{equation}
-where \(\sigma\) is the effective hydrogen photoionization cross section.
+where \(\sigma\) is the effective hydrogen photoionization cross section,
+averaged over the local ionizing spectrum.  Since the
+frequency-dependent cross section, \(\sigma_\nu \sim \nu^{-3}\), is strongly
+peaked at the threshold, the local EUV spectrum becomes harder with
+increasing \(\tau\gas\), as the lower frequency photons are selectively
+absorbed,\footnote{} leading to a reduction in the effective
+\(\sigma\).  An approximate fit to the results in Appendix~A of
+\citet{Henney:2005b} is
 \begin{equation}
@@
 where \(\sigma_0 = \SI{6e-18}{cm^2}\) is the threshold cross-section.
+Although this was derived for a particular ionizing spectrum (\SI{40
+  000}{K} black body), we adopt it for all our hot stars.
 

### 2017-12-22 Dust-wave/zones-v-n-plane.py

@@ -56,12 +56,13 @@ d = {
 }
 
 T0 = 8000
+kappa = 600.0
 for M, L4, eta, S49, ax in stardata:
     Mlabel = "\n".join([rf"$M = {M:.0f}\, M_\odot$",
                         rf"$L = {1e4*L4:.1e}\, L_\odot$".replace("e+0", r"\times 10^"),
                         rf"$\eta = {eta}$"])
     Rs = rstar(vv/10, nn, L4)
-    ts = taustar(vv/10, nn, L4)
+    ts = taustar(vv/10, nn, L4, kappa600=kappa/600.0)
     a, b = 0.0, 2*np.sqrt(1.0 + eta)
     x = chandrupatla(xfunc, a, b, args=(ts, eta))
     R0 = x*Rs
@@ -120,7 +121,7 @@ for M, L4, eta, S49, ax in stardata:
     #ax.contour(vv, nn, 3.5e5*Uout, (0.5, 98.1), colors='r', alpha=0.5)
     c_sig_over_alpha = 2.99792458e10*3e-18 / alphaB
     c_sig_over_alpha *= (1 - absfrac)**(1./3.)
-    y_IF = 0.5
+    y_IF = 0.1
     y1, y2 = 0.01, 0.99
     LHS_IF = y_IF**2 / (1 - y_IF)
     LHS1, LHS2 = y1**2/(1 - y1), y2**2/(1 - y2)
@@ -128,7 +129,8 @@ for M, L4, eta, S49, ax in stardata:
     m = (c_sig_over_alpha*Ushout >= LHS1) & (c_sig_over_alpha*Ushout <= LHS2)
     tau_gas_IF = np.nanmean(tau_gas[m])
     tau_dust_IF = np.nanmean(tau_dust[m])
-    cs = ax.contourf(vv, nn, tau_dust, (tau_dust[m].min(), tau_dust[m].max()), linewidths=2, colors='r', alpha=0.5)
+    cs = ax.contourf(vv, nn, tau_dust, (tau_dust[m].min(), tau_dust[m].max()), linewidths=2, colors='r', alpha=0.3)
+    ax.contour(vv, nn, absfrac, 1.0, linewidths=0.7, colors='r')
 
     # ax.contour(vv, nn, tau, tau_dust_IF,
     #            colors='k', linestyles='--', linewidths=0.8)

### 2017-12-24 papers/Papers1234/sec-dust-bow-intro.tex
Nearly finished the i-front trapping (simpler now)

@@
 
-Then, defining a fiducial optical depth, \(\tau_* = \rho \kappa R_*\), and adding
-in the stellar wind ram pressure\footnote{%
+Then, defining a fiducial optical depth,
+\begin{equation}
+  \label{eq:tau-star}
+  \tau_* = \rho \kappa R_* \ ,
+\end{equation}
+and adding in the stellar wind ram pressure\footnote{%
   We implicitly assume that the interaction of the stellar wind with
@@
   re-absorbed locally, so the case~B recombination co-efficient,
-  \(\alphaB = \num{2.6e-13}\, (T/\SI{e4}{K})\, \si{cm^3.s^{-1}}\), is
-  used.} %
+  \(\alphaB = \num{2.6e-13}\, T_4^{-0.7}\, \si{cm^3.s^{-1}}\), is
+  used, where \(T_4 = T/\SI{e4}{K}\).} %
 per unit time per unit area in a fully ionized shell is
@@
 with \(\mathcal{R} > \mathcal{F}\) cannot be entirely photoionized by
-the star, and so must have trapped the ionization front.  This simple
+the star, and so must have trapped the ionization front.  The column
+density of the shocked shell can be found, for example, from
+equations~(10) and~(12) of \citet{Wilkin:1996a} in the limit
+\(v_\infty/V \to 0\) (Wilkin's parameter \(\alpha\)) and \(\theta \to 0\).  This yields
+\begin{equation}
+  \label{eq:shocked-shell-column}
+  n\shell h\shell = \tfrac34 n R_0 \ .
+\end{equation}
+Assuming strong cooling behind the shock,\footnote{%
+  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
+} %
+the shell density is \(n\shell = \mathcal{M}_0^2 n\), where
+\(\mathcal{M}_0 = v_\infty / \sound\) is the isothermal Mach number of the
+external stream.\footnote{%
+  \label{fn:temperature-dependence}
+  The sound speed depends on the temperature and hydrogen and helium
+  ionization fractions, \(y\) and \(y_{\text{He}}\) as
+  \(\sound^2 = (1 + y + z_{\text{He}} y_{\text{He}}) (k T /
+  \bar{m})\), where \(z_{\text{He}}\) is the helium nucleon abundance
+  by number relative to hydrogen and
+  \(k = \SI{1.3806503e-16}{erg.K^{-1}}\) is Boltzmann's constant.  We
+  assume \(y = 1\), \(y_{\text{He}} = 0.5\), \(z_{\text{He}} = 0.09\),
+  so that \(\sound = \num{11.4}\, T_4^{1/2}\, \si{km.s^{-1}}\). } %
+Putting these together with equations~\eqref{eq:Rstar} and
+~\eqref{eq:tau-star}, one finds that \(\mathcal{R} > \mathcal{F}\)
+implies
+\begin{equation}
+  \label{eq:ifront-trap-x-cubed-taustar}
+  x^3 \tau_* > \frac{4 S c \sound \bar{m}^2 \kappa}{3 \alpha L} \ .
+\end{equation}
+From equation~\eqref{eq:rad-full-x}, it can be seen that \(x\) depends
+on the external stream parameters, \(n\), \(v_\infty\) only via
+\(\tau_*\), and so equation~\eqref{eq:ifront-trap-x-cubed-taustar} is a
+condition for \(\tau_*\).  In the radiation bow shock case,
+\(x = (1 + \eta)^{1/2}\), and the condition can be written:
+\begin{equation}
+  \label{eq:ifront-trap-taustar-bow-shock}
+  \tau_* > 145.0 \frac{S_{49} T_4^{1.7} \kappa_{600}}{L_4 (1 + \eta)^{3/2}} \ , 
+\end{equation}
+where
+\begin{equation*}
+  S_{49} = S / \bigl( \SI{e49}{s^{-1}} \bigr) \ .
+\end{equation*}
+Numerical values of \(S_{49}\) for our three example stars are given
+in Table~\ref{tab:stars}.  In the radiation bow wave case,
+\(x = 2\tau_*\), and the condition can be written:
+\begin{equation}
+  \label{eq:ifront-trap-taustar-bow-shock}
+  \tau_* > \left(  18.1 \frac{S_{49} T_4^{1.7} \kappa_{600}}{L_4}\right)^{1/4} \ , 
+\end{equation}
+
+\(\tau_* \sim n^{1/2} / v_\infty\) 
+This simple
 criterion is shown by the dark red line in
@@
 \end{equation}
-so long as \(\mathcal{R} < \mathcal{F}\).  The column density of the
-shocked shell can be found, for example, from equations~(10) and~(12)
-of \citet{Wilkin:1996a} in the limit \(v_\infty/V \to 0\) (Wilkin's parameter
-\(\alpha\)) and \(\theta \to 0\).  This yields
-\begin{equation}
-  \label{eq:shocked-shell-column}
-  n\shell h\shell = \tfrac34 n R_0 \ .
-\end{equation}
-Assuming strong cooling behind the shock,\footnote{%
-  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
-} %
-the shell density is \(n\shell = M_0^2 n\), where \(M_0 = v / \sound\)
-is the isothermal Mach number of the external stream.  We will assume
+so long as \(\mathcal{R} < \mathcal{F}\).
+
+We will assume
 a typical photoionized temperature of \SI{8000}{K}, so that
@@
 \begin{align*}
-  R_{0,\text{pc}} &= R_0 / \bigl( \SI{1}{pc} \bigr) \\
-  S_{49} &= S / \bigl( \SI{e49}{s^{-1}} \bigr) \ . 
+  R_{0,\text{pc}} &= R_0 / \bigl( \SI{1}{pc} \bigr)
 \end{align*}
-Numerical values of \(S_{49}\) for our three example stars are given
-in Table~\ref{tab:stars}.  The dust opacity is approximately constant
+The dust opacity is approximately constant
 at FUV to EUV wavelengths, so the dust optical depth of the shocked

### 2017-12-24 papers/Papers1234/app-dust-ifront-trap.tex
Further simplification of the i-front trapping
Move the complicated version to an appendix, which will probably be
dropped from the final version

--- 2017-12-24 papers/Papers1234/sec-dust-bow-intro.tex
@@
-\defcitealias{Tarango-Yong:2018a}{Paper~I}
-\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
+\section{Further details on ionization front trapping}
+\label{sec:furth-deta-ioniz}
 
-\section{Introduction}
-\label{sec:introduction}
-\newcommand\hii{\ion{H}{ii}}
-
-Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
-often interpreted as \textit{bow shocks}, due to a supersonic
-hydrodynamic interaction between the star's wind and an external
-stream. This stream may be due to the star's own motion or to an
-independent flow, such as an \hii{} region in the champagne phase
-\citep{Tenorio-Tagle:1979a}, or another star's wind
-\citep{Canto:1996}. However, an alternative interpretation in some
-cases may be a radiation-pressure driven bow wave, as first proposed
-by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
-emitted by the star are absorbed by dust grains in the incoming
-stream, with the resultant momentum transfer being sufficient to
-decelerate and deflect the grains within a certain distance from the
-star, forming a dust-free, bow-shaped cavity with an enhanced dust
-density at its edge.  Two regimes are possible, depending on the
-strength of coupling between the gas (or plasma) and the dust.  In the
-strong-coupling regime, gas--grain drag decelerates the gas along with
-the dust, forming a shocked gas shell in a similar fashion to the
-wind-driven bow shock case.  In the weak-coupling regime, the gas
-stream is relatively unaffected and the dust temporarily decouples to
-form a dust-only shell.  This second case has recently been studied in
-detail in the context of the interaction of late O-type stars (which
-have only weak stellar winds) with dusty photoevaporation flows inside
-\hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
-  Ochsendorf:2015a}.  We follow the nomenclature proposed by
-\citet{Ochsendorf:2014b}, in which \textit{dust wave} refers to the
-weak coupling case and \textit{bow wave} to the strong coupling case.
-More complex, hybrid scenarios are also possible, such as that studied
-by \citet{van-Marle:2011a}, where a hydrodynamic bow shock forms, but
-the larger dust grains that accompany the stellar wind pass right
-through the shocked gas shell, and form their own dust wave at a
-larger radius.
-
-\begin{figure}
-  \centering
-  \framebox{
-    \parbox[m][4cm]{0.8\linewidth}
-    {\centerline{\textbf{\dotfill TODO\dotfill}}}}
-  \caption{Bow shocks, bow waves, and dust waves}
-  \label{fig:3-types-bow}
-\end{figure}
-
-In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
-new two-dimensional classification scheme for bow shapes: the
-projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
-measures the flatness of the bow's apex, while alatude measures the
-openness of the bow's wings.  Both are dimensionless ratios of lengths
-that can be estimated from observational images.  We have analyzed the
-inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
-geometric shapes (spheroids, paraboloids, hyperboloids) and for
-thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
-ancantoids).  In this paper, we will do the same for simple models of
-radiation-driven dust waves (dragoids) and bow waves (trapoids).
-
-The paper is organized as follows.
-%
-In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
-dusty radiation bow wave (dragoids), including the effects of
-gas-grain drag.
-%
-In \S~\ref{sec:perturbed-bows} we investigate the effects on the
-planitude--alatude plane of small-amplitude perturbations to the bow
-shape.
-%
-
-\section{Different types of bow}
-\label{sec:different-types-bow}
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
-  \caption{Bow regimes in parameter space (\(v, n\)) of the external
-    stream for main-sequence OB stars of different masses:
-    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}.  In all
-    cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
-    coupling is assumed. Solid black lines of varying width show the
-    bow size (star-apex separation, \(R_0\)), while gray shading shows
-    the radiation bow wave regime, with lower border \(\tau = \eta\) and
-    upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
-    depth through the bow.  For bows above the red solid line, the
-    ionization front is trapped inside the bow.  Blue lines delineate
-    different cooling regimes.  Above the thin blue line
-    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
-    forming a thin shocked shell.  Below the thick blue line
-    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
-    non-radiative.}
-  \label{fig:zones-v-n-plane}
-\end{figure*}
-
-In this section, we investigate the different types of bow interaction
-that will occur in different regions of parameter space. We will
-mainly treat the canonical case\footnote{%
-  Variant cases with differing arrangements of dust and radiation
-  sources are treated in \S~\ref{sec:case-inside-out}.} %
-of a bow around a star of bolometric luminosity, \(L\), with a
-radiatively driven wind, which is immersed in an external stream of
-gas and dust with density, \(\rho\), and velocity, \(v\).  The size and
-shape of the bow is determined by a generalized balance of pressure
-(or, equivalently, momentum) between internal and external sources.
-We assume that the stream is supersonic and super-alfvenic, so that
-the external pressure is dominated by the ram pressure: \(\rho v^2\).
-
-\subsection{Strong gas-grain coupling}
-\label{sec:strong-gas-grain}
-
-We first consider the case where the dust grains and gas are perfectly
-coupled by collisions.\footnote{%
-  Cases where this assumption does not hold are investigated below in
-  \S~\ref{sec:imperf-coupl-betw}.} %
-Although dust grains typically constitute only a small fraction
-\(Z\grain \sim 0.01\) of the mass of the external stream, they
-nevertheless dominate the broad-band opacity at FUV, optical and IR
-wavelengths if they are present.\footnote{%
-  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
-  dominates if the hydrogen neutral fraction is larger than
-  \(\approx 0.001\), see discussion of ionization front trapping
-  below.} %
-The strong coupling assumption means that all the radiative forces
-applied to the dust grains are directly felt by the gas also.
-
-The internal pressure is the sum of wind ram pressure and the
-effective radiation pressure that acts on the bow shell.  The
-radiative momentum loss rate of the star is \(L/c\) and the wind
-momentum loss rate can be expressed as
-\begin{equation}
-  \label{eq:wind-efficiency}
-  \dot{M} V = \eta L / c \ , 
-\end{equation}
-where \(\eta\) is the momentum efficiency of the wind, which is typically
-\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
-all of the stellar radiative momentum, emitted with rate \(L/c\), is
-trapped by the bow shell.  In the single scattering limit,\footnote{%
-  Although it may seem inconsistent to assume single scattering in the
-  case of high optical depths, this is defensible for the following
-  reasons. (1)~The grain albedo is not that high (typically
-  \(\sim 0.5\) at ultraviolet through optical wavelengths). (2)~The
-  scattered radiation field is more isotropic than the stellar field,
-  leading to cancellation in the radiative
-  flux. (3)~Absorbed radiation is re-emitted at infrared
-  wavelengths, where the dust opacity is very much lower.} %
-and temporarily neglecting the wind, then pressure balance at the bow
-apex, a distance \(R_0\) along the symmetry axis from the star is
-given by
-\begin{equation}
-  \label{eq:rad-press-balance-thick}
-  \frac{L}{4 \pi c R_0^2} = \rho v^2 \ ,
-\end{equation}
-which yields a fiducial bow shock radius in this optically thick limit
-as
-\begin{equation}
-  \label{eq:Rstar}
-  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
-\end{equation}
-
-We now consider the opposite, optically thin limit.  If the total
-opacity (gas plus dust) per total mass (gas plus dust) is \(\kappa\) (with
-units of \si{cm^2.g^{-1}}), then the radiative acceleration is
-\begin{equation}
-  \label{eq:rad-accel}
-  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ , 
-\end{equation}
-so that an incoming stream with initial velocity, \(v_\infty\), can be
-brought to rest by radiation alone\footnote{%
-  For simplicity, we here ignore the effects of pressure gradients and
-  shocks, which are important as the velocity approaches the sound
-  speed, \(\sound\). In \S~XX below, we show that the resultant
-  corrections to \(R_0\) are of order \(\sound / v_\infty\).} %
-at a distance \(R_0\) where
-\begin{equation}
-  \label{eq:rad-poten}
-  \int_{R_0}^\infty a_{\text{rad}} \, dr = \tfrac12 v^2 \ , 
-\end{equation}
-yielding
-\begin{equation}
-  \label{eq:rad:R0}
-  R_0 = \frac{\kappa L}{2\pi c v_\infty^2} \ .
-\end{equation}
-On the other hand, we can also argue as in the optically thick case
-above by approximating the bow shell as a surface, and balancing
-stellar radiation pressure against the ram pressure of the incoming
-stream.  The important difference when the shell is not optically
-thick is that only a fraction \(1 - e^{-\tau}\) of the radiative momentum
-is absorbed by the bow, so that
-equation~\eqref{eq:rad-press-balance-thick} is replaced with
-\begin{equation}
-  \label{eq:rad-press-balance-tau}
-  \frac{L (1 - e^{-\tau})}{4 \pi c R_0^2} = \rho v^2 \ .
-\end{equation}
-In the optically thin limit, \(1 - e^{-\tau} \approx \tau\), so these two
-descriptions can be seen to agree so long as
-\begin{equation}
-  \label{eq:tau-thin}
-  \tau = 2 \kappa \rho R_0 \ ,
-\end{equation}
-which we will assume to hold generally.
-
-Then, defining a fiducial optical depth,
-\begin{equation}
-  \label{eq:tau-star}
-  \tau_* = \rho \kappa R_* \ ,
-\end{equation}
-and adding in the stellar wind ram pressure\footnote{%
-  We implicitly assume that the interaction of the stellar wind with
-  the external stream can always be treated in the continuum limit.
-  This will be true if either the collisional mean free path or the
-  ion Larmor radius is much smaller than \(R_0\), which is almost
-  always the case.} %
-from equation~\eqref{eq:wind-efficiency}, we find that the general bow
-radius can be written in terms of the fiducial radius as
-\(R_0 = x R_*\), where \(x\) is the solution of
-\begin{equation}
-  \label{eq:rad-full-x}
-  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta = 0 \ .
-\end{equation}
-Since this is a transcendental equation, \(x\) must be found
-numerically, but we can write explicit expressions for three limiting
-cases:
-\begin{equation}
-  \label{eq:x-cases}
-  x \approx
-  \begin{cases}
-    \text{if \(\tau_* \gg 1\):} & (1 + \eta)^{1/2}  \\
-    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta \bigr)^{1/2} \approx
-    \begin{cases}
-      \text{if \(\tau_*^2 \gg \eta\):} & 2 \tau_*  \\
-      \text{if \(\tau_*^2 \ll \eta\):} & \eta^{1/2} 
-    \end{cases}
-  \end{cases}
-\end{equation}
-The first case, \(x \approx (1 + \eta)^{1/2}\), corresponds to a
-\textit{radiation bow shock}; the second case,
-\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave}; and the
-third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow shock}.
-The two bow shock cases are similar in that the external stream is
-oblivious to the presence of the star until it suddenly hits the bow
-shock shell, differing only in whether it is radiation or wind that is
-providing the internal pressure.  In the intermediate bow wave case,
-on the other hand, the external stream is gradually decelerated by
-absorption of photons as it approaches the bow.\footnote{A shock does
-  still form in this case, but shocked material constitutes only a
-  fraction of the total column density of the shell, see
-  \S~\ref{sec:shape-bow-wave}.}
-
-\begin{table*}
-  \centering
-  \caption{Stellar parameters for example stars}
-  \label{tab:stars}
-  \begin{tabular}{l S S S S S S S S S l}
-    \toprule
-    & {\(M / \si{M_\odot}\)} & {\(L_4\)}
-    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta \)}
-    & {Sp.~Type} 
-    & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
-    & {\(S_{49}\)} & Figures 
-    \\
-    \midrule
-    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & e-4
-                   & \ref{fig:zones-v-n-plane}a,
-                     \ref{fig:decouple-v-n-plane},
-                     \ref{fig:decouple-v40-versus-n} \\
-    Main-sequence OB stars
-    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.1
-                   & \ref{fig:zones-v-n-plane}b\\
-    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.0
-                   & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
-    Red supergiant star
-    & 20 & 15.6 & 100 & 0.015 & 0.0476 & {M1\,Ia} & 3.6 & 0.805 & 0
-                   & \\ 
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-We now consider the application to bow shocks around main sequence OB
-stars, expressing stellar and ambient parameters in terms of typical
-values as follows:
-\begin{align*}
-  \label{eq:stellar-parameters}
-  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
-  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
-  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
-  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
-  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
-  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
-\end{align*}
-where \(\bar{m}\) is the mean mass per hydrogen nucleon
-(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
-abundances).  Note that \(\kappa = \SI{600}{cm^2.g^{-1}}\) corresponds to a
-cross section of \(\approx \SI{e-21}{cm^2}\) per hydrogen nucleon, which is
-typical for interstellar medium dust \citep{Bertoldi:1996a} at far
-ultraviolet wavelengths, where OB stars emit most of their radiation.
-In terms of these parameters, we can express the stellar wind momentum
-efficiency as
-\begin{equation}
-  \label{eq:wind-eta-typical}
-  \eta = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
-\end{equation}
-and the fiducial radius and optical depth as
-\begin{align}
-  \label{eq:fiducial-typical}
-  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
-  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
-\end{align}
-In Figure~\ref{fig:zones-v-n-plane}, we show results for the bow size
-(apex distance, \(R_0\)) as a function of the density, \(n\), and
-relative velocity, \(v_\infty\), of the external stream, with each panel
-corresponding to a particular star, with parameters as shown in
-Table~\ref{tab:stars}.  To facilitate comparison with previous work,
-we choose stellar parameters similar to those used in the
-hydrodynamical simulations of \citet{Meyer:2014b, Meyer:2016a,
-  Meyer:2017a}, based on stellar evolution tracks for stars of
-\SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and theoretical wind
-prescriptions \citep{de-Jager:1988a, Vink:2000a}.  Although the
-stellar parameters do evolve with time, they change relatively little
-during the main-sequence lifetime of several million years.\footnote{%
-  \label{fn:meyer-velocities-too-low}
-  Note that we have recalculated the stellar wind terminal velocities,
-  since the values given in the \citeauthor{Meyer:2014b} papers are
-  troublingly low.  We have used the prescription
-  \(V = 2.6 V_{\text{esc}}\), where
-  \(V_{\text{esc}} = \left( 2 G M (1 - \Gamma_e)/ R \right)^{1/2}\) is the
-  photospheric escape velocity, which is appropriate for strong
-  line-driven winds with \(T_{\text{eff}} > \SI{21 000}{K}\)
-  \citep{Lamers:1995a}.  We find velocities of
-  \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
-  observations and theory \citep{Vink:1999a} for O~stars, but at least
-  two times higher than those cited by \citet{Meyer:2014b}. For
-  main-sequence B~stars, wind column densities are too low to reliably
-  measure the terminal velocity from near ultraviolet P~Cygni profiles
-  \citep{Prinja:1989a}, and so the values are theory-dependent
-  \citep{Krticka:2014a} and hence more uncertain.  A further
-  complication is the existence of a subset of OB stars with
-  anomalously weak winds \citep{Puls:2008a}, which in some cases is
-  related to the presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
-  \citep{Oskinova:2011b}.} %
-The three examples are an early B~star (\SI{10}{M_\odot}), a late O~star
-(\SI{20}{M_\odot}), and an early O~star (\SI{40}{M_\odot}), which cover the
-range of luminosities and wind strengths expected from bow-producing
-hot main sequence stars.  The luminosity is a steep function of
-stellar mass (\(L \sim M^{2.5}\)) and the wind mass-loss rate is a steep
-function of luminosity (\(\dot{M} \sim L^{2.2}\)), which means that the
-wind momentum efficiency is also a steep function of mass
-(\(\eta \sim M^3\)), approaching unity for early O~stars, but falling to
-less than 1\% for B~stars.
-
-\subsection{Ionization state of the bow shell}
-\label{sec:trapp-ioniz-front}
-
-\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
-\newcommand\shell{\ensuremath{_{\text{sh}}}}
+This appendix will probably be dropped from the paper.  It contains
+details of the derivation of the ionization front trapping that I now
+think are too verbose to be included, given that this is not the main
+point of the paper.  They are collected here for completeness.
 
@@
 
-\subsection{Radiative cooling lengths}
-\label{sec:radi-cool-lengths}
-
-\subsection{Imperfect coupling between gas and dust}
-\label{sec:imperf-coupl-betw}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
-  \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
-    gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
-  \label{fig:decouple-v-n-plane}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/decouple-v40-versus-n}
-  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
-    showing bow radius and different regimes for a fixed inflow
-    velocity of \SI{40}{km.s^{-1}}.}
-  \label{fig:decouple-v40-versus-n}
-\end{figure}
-
-\subsection{The case of inside-out bows}
-\label{sec:case-inside-out}
-
-So far, we have considered the case where the inner source dominates
-the radiation, while dust is present only in the outer stream, which
-applies to hot stars interacting with the ISM.  However, in the case
-of cool stars, the inner wind will also be dusty.  Examples are the
-red supergiant (RSG) phase of high-mass evolution, or the asymptotic
-giant branch (AGB) stage of low/intermediate-mass evolution.  In both
-these cases, it is still the inner source that provides the radiation
-field.  However, not all winds are radiatively driven and in those
-cases it is conceivable that it is the outer source that dominates the
-radiation field.  An example is the case of photoevaporating
-protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
-regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
-thermally driven photoevaporation flow \citep{HA:1998, Henney:1999a},
-while the outer stream is the stellar wind from an O~star
-\citep{Garcia-Arredondo:2001a}.
-
 %%% Local Variables:

### 2017-12-24 papers/Papers1234/sec-dust-bow-intro.tex
Further simplification of the i-front trapping
Move the complicated version to an appendix, which will probably be
dropped from the final version

@@
 \begin{align}
-  \label{eq:fiducial-typical}
+  \label{eq:Rstar-typical}
   R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
+  \label{eq:taustar-typical}
   \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
@@
 \(\tau_*\), and so equation~\eqref{eq:ifront-trap-x-cubed-taustar} is a
-condition for \(\tau_*\).  In the radiation bow shock case,
+condition for \(\tau_*\), which, by using equation~\eqref{eq:taustar-typical}, becomes a condition on \(n / v_{10}^2\).  In the radiation bow shock case,
 \(x = (1 + \eta)^{1/2}\), and the condition can be written:
 \begin{equation}
-  \label{eq:ifront-trap-taustar-bow-shock}
-  \tau_* > 145.0 \frac{S_{49} T_4^{1.7} \kappa_{600}}{L_4 (1 + \eta)^{3/2}} \ , 
+  \label{eq:ifront-trap-density-RBS}
+  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta)^3} \ , 
 \end{equation}
@@
   \label{eq:ifront-trap-taustar-bow-shock}
-  \tau_* > \left(  18.1 \frac{S_{49} T_4^{1.7} \kappa_{600}}{L_4}\right)^{1/4} \ , 
+  \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ , 
 \end{equation}
-
-\(\tau_* \sim n^{1/2} / v_\infty\) 
-This simple
-criterion is shown by the dark red line in
-Figure~\ref{fig:zones-v-n-plane}.  If 
-\(n / v_{10}^2 > \text{\numrange{1000}{5000}}\), depending
-only weakly on the stellar parameters, then the outer parts of the
-shocked shell are neutral, instead of ionized.
-
-Assuming photoionization equilibrium, the
-hydrogen photoabsorption optical depth of the shell is
-\begin{equation}
-  \label{eq:ion-tau-gas}
-  \tau\gas = - \ln(1 - \mathcal{R} / \mathcal{F}) \ ,
-\end{equation}
-so long as \(\mathcal{R} < \mathcal{F}\).
-
-We will assume
-a typical photoionized temperature of \SI{8000}{K}, so that
-\(\sound \approx \SI{10}{km.s^{-1}}\) and \(M_0 = v_{10}\), yielding
-\begin{equation}
-  \label{eq:ion-tau-gas-expanded}
-  \tau\gas = -\ln\bigl(1 -
-  \num{8.42e-6}\, v_{10}^2 n^2 R_{0,\text{pc}}^3 S_{49}^{-1}\bigr) \ , 
-\end{equation}
-where 
-\begin{align*}
-  R_{0,\text{pc}} &= R_0 / \bigl( \SI{1}{pc} \bigr)
-\end{align*}
-The dust opacity is approximately constant
-at FUV to EUV wavelengths, so the dust optical depth of the shocked
-shell to ionizing photons follows from equations~\eqref{eq:tau-thin}
-and~\eqref{eq:shocked-shell-column} as \(\tau\grain = \tfrac38 \tau\).
-
-The hydrogen ionization fraction, \(y\), at the outer edge of the shocked
-shell then follows as
-\begin{equation}
-  \label{eq:outer-shell-ionization-balance}
-  \frac{y^2}{1 - y} = \frac{\sigma \mathcal{F}}{\alphaB n} e^{-(\tau\grain + \tau\gas)} \ ,
-\end{equation}
-where \(\sigma\) is the effective hydrogen photoionization cross section,
-averaged over the local ionizing spectrum.  Since the
-frequency-dependent cross section, \(\sigma_\nu \sim \nu^{-3}\), is strongly
-peaked at the threshold, the local EUV spectrum becomes harder with
-increasing \(\tau\gas\), as the lower frequency photons are selectively
-absorbed,\footnote{} leading to a reduction in the effective
-\(\sigma\).  An approximate fit to the results in Appendix~A of
-\citet{Henney:2005b} is
-\begin{equation}
-  \label{eq:sigma-vs-tau}
-  \sigma = 0.5 \sigma_0 e^{-\tau\gas/3}
-\end{equation}
-where \(\sigma_0 = \SI{6e-18}{cm^2}\) is the threshold cross-section.
-Although this was derived for a particular ionizing spectrum (\SI{40
-  000}{K} black body), we adopt it for all our hot stars.
 

### 2017-12-24 papers/Papers1234/sec-dust-bow-intro.tex
Make a start on the cooling length section - do shock jump

@@
 
-We wish to calculate whether the star is capable of photoionizing the
-entire bow shock shell, or whether the ionization front will be
-trapped within it.  The number of hydrogen recombinations\footnote{%
+In this section we calculate whether the star is capable of
+photoionizing the entire bow shock shell, or whether the ionization
+front will be trapped within it.  The number of hydrogen
+recombinations\footnote{%
   The diffuse field is treated in the on-the-spot approximation,
@@
 \begin{equation}
-  \label{eq:ifront-trap-taustar-bow-shock}
-  \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ , 
+  \label{eq:ifront-trap-taustar-RBW}
+  \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ . 
 \end{equation}
+In the wind bow shock case, the result is the same as
+equation~\eqref{eq:ifront-trap-density-RBS}, but changing the factor
+\((1 + \eta)^3\) to \(\eta^3\).  For the example hot stars in
+Table~\ref{tab:stars}, and assuming \(\kappa_{600} = 1\),
+\(T_4 = 0.8\), the resulting density threshold is
+\(n > (\text{\numrange{1000}{5000}})\, v_{10}^2\), depending only
+weakly on the stellar parameters, which is shown by the red lines in
+Figure~\ref{fig:zones-v-n-plane}.  For the \SI{10}{M_\odot} star, this is
+in the radiation bow wave regime, whereas for the higher mass stars it
+is in the radiation bow shock regime.  When the external stream is
+denser than this, then the outer parts of the shocked shell may be
+neutral instead of ionized, giving rise to a cometary compact \hii{}
+region \citep{Mac-Low:1991a, Arthur:2006a}.  This is only necessarily
+true, however, when the star is isolated.  If the star is in a cluster
+environment, then the contribution of other nearby massive stars to
+the ionizing radiation field must be considered.
 
@@
 \label{sec:radi-cool-lengths}
+\newcommand\M{\ensuremath{\mathcal{M}}}
+In this section, we calculate whether the radiative cooling is
+sufficiently rapid behind the bow shock to allow the formation of a
+thin, dense shell.  Since cooling is least efficient at low densities,
+we will assume that the wind bow shock regime applies unless otherwise
+specified. We label quantities just outside the shock by the subscript
+``0'', quantities just inside the shock (after thermalization, but
+before any radiative cooling) by the subscript ``1'', and quantities
+after the gas has cooled back to the photoionization equilibrium
+temperature by the subscript ``2''.  Assuming a ratio of specific
+heats, \(\gamma = 5/3\), the relation between the pre-shock and immediate
+post-shock quantities is
+\begin{align}
+  % \M_1 &= \left(\frac{\M_0^2 + 3} {5\M_0^2 - 1}\right)^{1/2} \\
+  \label{eq:shock-n-jump}
+  \frac{n_1}{n_0} &= \frac{4 \M_0^2} {\M_0^2 + 3} \\
+  \label{eq:shock-T-jump}
+  \frac{T_1}{T_0} &= \tfrac1{16} \bigl( 5\M_0^2 - 1 \bigr) \bigl( 1 + 3/\M_0^2 \bigr) \\
+  \label{eq:shock-v-jump}
+  \frac{v_1}{v_0} &= \left(\frac{n_1}{n_0}\right)^{-1} \ ,
+\end{align}
+where \(\M_0 = v_0 / \sound\).
 

### 2017-12-25 papers/Papers1234/sec-dust-bow-intro.tex
Add in heating as well as cooling and write up some more

@@
 \end{align}
-where \(\M_0 = v_0 / \sound\).
+where \(\M_0 = v_0 / \sound\).  The cooling length of the post-shock
+gas can be written as
+\newcommand\cool{\ensuremath{_{\text{cool}}}}
+\begin{equation}
+  \label{eq:dcool}
+  d\cool = \frac{P_1 v_1} { (\gamma - 1) \bigl(  \mathcal{L}_1 - \mathcal{G}_1 \bigr) }\ ,  
+\end{equation}
+where \(P_1\) is the thermal pressure and \(\mathcal{L}_1\),
+\(\mathcal{G}_1\) are the volumetric radiative cooling and heating
+rates.  For fully photoionized gas, we have
+\(P_1 \approx 2 n_1 k T_1\), \(\mathcal{L}_1 = n_1^2 \Lambda(T_1)\), and
+\(\mathcal{G}_1 = n_1^2 \Gamma(T_1)\), where \(\Lambda(T)\) is the cooling
+coefficient, which is dominated by metal emission lines that are
+excited by electron collisions, and \(\Gamma(T)\) is the heating
+coefficient, which is dominated by hydrogen photo-electrons
+\citep{Osterbrock:2006a}. The cooling coefficient has a maximum around
+\SI{e5}{K}, and for typical ISM abundances can be approximated as
+follows:
+\begin{align}
+  \label{eq:cooling-coefficient}
+  \Lambda_{\text{warm}} &= \num{3.3e-24} \, T_4^{2.3} \, \si{erg.cm^{-3}.s^{-1}}\\
+  \Lambda_{\text{hot}} &= \num{e-20} \, T_4^{-1}\, \si{erg.cm^{-3}.s^{-1}} \\
+  \Lambda &= \left( \Lambda_{\text{warm}}^{-k} +  \Lambda_{\text{hot}}^{-k} \right)^{-1/k}
+      \quad \text{with} \quad k = 3 \ ,
+\end{align}
+which is valid in the range \(0.7 < T_4 < 1000\).  We approximate the heating coefficient as
+\begin{equation}
+  \label{eq:heating-coefficient}
+  \Gamma = \num{1.77e-24} \, T_4^{-1/2} \, \si{erg.cm^{-3}.s^{-1}} \ ,
+\end{equation}
+where the coefficient is chosen so as to give \(\Gamma = \Lambda\) at
+an equilibrium temperature of \(T_4 = 0.8\).
+
+In Figure~\ref{fig:zones-v-n-plane} we show curves corresponding to
+\(d\cool = R_0\) and \(d\cool = h_0\), where \(h_0\) is the shell
+thickness in the efficient cooling case.
 

### 2017-12-25 Dust-wave/zones-v-n-plane.py

@@ -166,8 +166,10 @@ for M, L4, eta, S49, ax in stardata:
     #
     # Now do the cooling length
     #
+    # Sound speed:
+    cs = 11.4*np.sqrt(T0/1e4)
     # pre-shock Mach number
-    M0 = vv/10.0
+    M0 = vv/cs
     # post-shock Mach number
     M1 = np.sqrt((M0**2 + 3)/(5*M0**2 - 1))
     # post-shock temperature in units of T0
@@ -177,12 +179,19 @@ for M, L4, eta, S49, ax in stardata:
     # post-shock velocity
     v1 = vv*nn/n1
     # Cooling rate
-    Lam1 = 3.3e-24 * T1**2.3
-    Lam2 = 1e-20 / T1
+    Lam1 = 3.3e-24 * (T1*T0/1e4)**2.3
+    Lam2 = 1e-20 / (T1*T0/1e4)
+
     k = 3
     Lambda = (Lam1**(-k) + Lam2**(-k))**(-1/k)
+
+    # Heating rate
+    Gamma = (T0/1e4)**2.8 * 3.3e-24 /np.sqrt(T1*T0/1e4)
+
     # Cooling length in parsec
-    dcool = 3*(1e5*v1)*(1.3806503e-16 * T1*T0) / (n1*Lambda) / 3.085677582e18
+    dcool = 3*(1e5*v1)*(1.3806503e-16 * T1*T0) / (n1*(Lambda - Gamma)) / 3.085677582e18
+
+    dcool[vv < cs] = np.nan
 
     # Ratio with respect to adiabatic shell thickness
     h1 = 0.177*R0

### 2017-12-26 papers/Papers1234/sec-dust-bow-intro.tex
Finish the section on radiative cooling

@@
 } %
-the shell density is \(n\shell = \mathcal{M}_0^2 n\), where
+the shell density is
+\begin{equation}
+  \label{eq:isothermal-shell-density}
+  n\shell = \mathcal{M}_0^2 n \,
+\end{equation}
+where
 \(\mathcal{M}_0 = v_\infty / \sound\) is the isothermal Mach number of the
@@
 
-In Figure~\ref{fig:zones-v-n-plane} we show curves corresponding to
-\(d\cool = R_0\) and \(d\cool = h_0\), where \(h_0\) is the shell
-thickness in the efficient cooling case.
+In Figure~\ref{fig:zones-v-n-plane} we show curves calculated from
+equations~\eqref{eq:shock-n-jump} to~\eqref{eq:heating-coefficient},
+corresponding to \(d\cool = R_0\) (thick blue line) and
+\(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
+thickness in the efficient cooling case.  In this context, \(n_0 = n\)
+and \(n_2 = n\shell\), so that \(h_0\) follows from
+equations~\eqref{eq:shocked-shell-column}
+and~\eqref{eq:isothermal-shell-density} as
+\begin{equation}
+  \label{eq:strong-cooling-h0}
+  h_0 = \tfrac34 \M_0^{-2} R_0 \ .
+\end{equation}
+The bends in the curves at \(v \approx \SI{50}{km.s^{-1}}\) are due to the
+maximum in the cooling coefficient \(\Lambda(T)\) around
+\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
+blue line, radiative cooling is so efficient that the bow shock can be
+considered isothermal, and so the shell is dense and thin (at least,
+in the apex region).  It can be seen that the ionization front
+trapping always occurs at densities larger than this, which justifies
+the use of equation~\eqref{eq:isothermal-shell-density} in the
+previous section.  For bows with outer stream densities below the
+thick blue line, cooling is unimportant and the bow shock can be
+considered non-radiative.  In this case the shell is thicker than in
+the radiative case,
+\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
+  An approximate value can be found from
+  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
+  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
+  Consideration of the slight increase in density between the shock
+  and the contact discontinuity reduces this value by 5--10\%.} %
+For bows with outer stream densities between the two blue lines,
+cooling does occur, albeit inefficiently, so that the shell thickness
+is set by \(d\cool\) rather than \(h_0\).
 

### 2017-12-27 papers/Papers1234/sec-dust-bow-intro.tex
Add paragraph on i-front trapping effect on R0

@@
 
+In principle, when the ionization front trapping occurs in the bow
+wave regime, then the curves for \(R_0\) will be modified in the
+region above the red line because all of the ionizing radiation is
+trapped in the shell due to gas opacity, which is not included in
+equation~\eqref{eq:tau-thin}.  However, this only happens for our
+\SI{10}{M_\odot} star, which has a relatively soft spectrum.
+Table~\ref{tab:stars} gives the peak wavelength of the stellar
+spectrum for this star as \(\lambda_{\text{eff}} = \SI{0.115}{\um}\), which
+is significantly larger than the hydrogen ionization threshold at
+\SI{0.0912}{\um}, meaning that only a small fraction of the total
+stellar luminosity is in the EUV band and affected by the gas opacity.
+The effect on \(R_0\) is therefore small.  For the higher mass stars,
+\(\lambda_{\text{eff}} < \SI{0.0912}{\um}\), so the majority of the
+luminosity is in the EUV band, but in these cases the ionization front
+trapping occurs well inside the radiation bow shock zone, where the
+dust optical depth is already sufficient to trap all of the radiative
+momentum.
+
 \subsection{Radiative cooling lengths}
@@
   \label{eq:dcool}
-  d\cool = \frac{P_1 v_1} { (\gamma - 1) \bigl(  \mathcal{L}_1 - \mathcal{G}_1 \bigr) }\ ,  
+  d\cool = \frac{3 P_1 v_1} { 2 \bigl(  \mathcal{L}_1 - \mathcal{G}_1 \bigr) }\ ,  
 \end{equation}

### 2017-12-28 papers/Papers1234/sec-dust-bow-intro.tex
Add B supergiant to table and consider inner dust waves
The inner dust waves still need more work

@@
     \midrule
-    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & e-4
+    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
                    & \ref{fig:zones-v-n-plane}a,
@@
     Main-sequence OB stars
-    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.1
+    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
                    & \ref{fig:zones-v-n-plane}b\\
-    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.0
+    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
                    & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
+    Blue supergiant star
+    & 33 & 30.2 & 20.2 & 0.93 & 0.3079 & {B0.7\,Ia} & 23.5 & 0.123 & 0.016
+                   & \\[\smallskipamount]
     Red supergiant star
@@
 
-\subsection{Ionization state of the bow shell}
+\subsubsection{Ionization state of the bow shell}
 \label{sec:trapp-ioniz-front}
@@
 Numerical values of \(S_{49}\) for our three example stars are given
-in Table~\ref{tab:stars}.  In the radiation bow wave case,
+in Table~\ref{tab:stars}, taken from Figure~4 of
+\citet{Sternberg:2003a}.  In the radiation bow wave case,
 \(x = 2\tau_*\), and the condition can be written:
@@
 
-\subsection{Radiative cooling lengths}
+\subsubsection{Radiative cooling lengths}
 \label{sec:radi-cool-lengths}

### 2017-12-28 Dust-wave/decouple-v40-versus-n.py

@@ -77,10 +77,16 @@ Ribs = eta**0.5 * rstar((1.0 - dv_v)*vv/10, nn, L4)
 m = Ribs > Rdw
 Ribs[m] = Rdw[m]
 
-# Remove cases where dust wave will not exist
+# Make a copy for the inner dust wave
+Ridw = Rdw.copy()
+
+# Remove cases where dust wave is inside the bow shock
 m = Rdw < R0
 Rdw[m] = np.nan 
 Ribs[m] = np.nan 
+# Trim unphysical zones for inner dust wave
+Ridw[~m] = np.nan
+Ridw[nn > 10.0] = np.nan
 
 # Choose only the R0 where there is not also a dust wave
 ax.plot(nn[~m], R0[~m], color="k", lw=0.1)
@@ -94,6 +100,9 @@ m = (tau > eta) & (tau < 1.0)
 ax.plot(nn[m], R0[m], ls="-.", label="Bow wave")
 m = tau >= 1.0
 ax.plot(nn[m], R0[m], label="Radiation bow shock")
+
+# Go back and plot the internal dust wave
+ax.plot(nn, Ridw, ls="--", c="orange", lw=0.5, label="_nolabel_")
 
 m = nn < 10.0
 ax.plot(nn[m], Rstarstar[m], color='k', lw=0.1)

### 2017-12-29 papers/Papers1234/sec-dust-bow-intro.tex
Add in red supergiant case and discussion of RBW regime boundaries

@@
     & 33 & 30.2 & 20.2 & 0.93 & 0.3079 & {B0.7\,Ia} & 23.5 & 0.123 & 0.016
-                   & \\[\smallskipamount]
+                   & \ref{fig:B-supergiant} \\[\smallskipamount]
     Red supergiant star
     & 20 & 15.6 & 100 & 0.015 & 0.0476 & {M1\,Ia} & 3.6 & 0.805 & 0
-                   & \\ 
+                   & \ref{fig:M-supergiant} \\ 
     \bottomrule
@@
 
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-RSG}
+  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for a cool M-type
+    supergiant instead of hot main sequence stars.  A smaller dust
+    opacity is used, \(\kappa = \SI{60}{cm^2.g^{-1}}\), because of the
+    reduced extinction efficiency at the optical/infrared wavelengths
+    emitted by this star.}
+  \label{fig:M-supergiant}
+\end{figure}
+
+It can be seen from Figure~\ref{fig:zones-v-n-plane} that the onset of
+the radiation bow wave regime is very similar for the three
+main-sequence stars, occurring at
+\(n > \text{\numrange{20}{40}} \, v_{10}^2\).  An important
+difference, however, is that for the \SI{40}{M_\odot} star, which has a
+powerful wind, the radiation bow wave regime only occurs for a very
+narrow range of densities, whereas for the \SI{10}{M_\odot} star, with a
+much weaker wind, the regime is much broader, extending to
+\(n < \num{e4} \, v_{10}^2\).  Another difference is the size scale of
+the bows in this regime, which is
+\(R_0 = \text{\SIrange{0.001}{0.003}{pc}}\) for the \SI{10}{M_\odot} star
+if \(v_\infty = \SI{40}{km.s^{-1}}\), but \(R_0 \approx \SI{0.1}{pc}\) for the
+\SI{40}{M_\odot} star, assuming the same inflow velocity.
+
+Figure~\ref{fig:M-supergiant} shows results for a cool M-type
+super-giant star with stellar parameters inspired by Betelgeuse
+(\chemalpha~Orionis), as listed in Table~\ref{tab:stars}.  Unlike the
+UV-dominated spectrum of the hot stars, this star emits predominantly
+in the near-infrared, where the dust extinction efficiency is lower,
+so we adopt a lower opacity of \SI{60}{cm^2.g^{-1}}.  This has the
+effect of shifting the radiation bow wave regime to higher densities:
+\(n = \text{\numrange{1000}{30 000}}\, v_{10}^2\) in this case.
+
 \subsubsection{Ionization state of the bow shell}
@@
 \newcommand\shell{\ensuremath{_{\text{sh}}}}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-BSG}
+  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for an evolved
+    B-type supergiant instead of main sequence stars.  This is similar
+    to Fig.~\ref{fig:zones-v-n-plane} in all respects, except the
+    trapping of the ionization front, which occurs for much lower
+    outer stream densities.}
+  \label{fig:B-supergiant}
+\end{figure}
 

### 2017-12-29 Dust-wave/zones-v-n-plane-RSG.py

@@ -10,7 +10,7 @@ sns.set_style('ticks')
 sns.set_color_codes('dark')
 fig, axes = plt.subplots(1, 1, sharex=True, sharey=True, figsize=(3.3, 4))
 stardata = [
-    [33.0, 30.2, 0.3079, 0.016, axes],
+    [20.0, 15.6, 0.0476, 0.0, axes],
 ]
 
 # Velocities in units of km/s (10 km/s -> 100 km/s)
@@ -46,18 +46,18 @@ WBS_label = r"Wind bow shock, $\tau < \eta$"
 
 # Miscellaneous panel-dependent plot params
 d = {
-    "RBW y": {33.0: 1500.0, 20.0: 5000.0, 40.0: 2500.0},
+    "RBW y": {33.0: 1500.0, 20.0: 1e5, 40.0: 2500.0},
     "trapped y": {33.0: 250, 20.0: 2.5e5, 40.0: 1.5e5},
     "trapped bg": {33.0: 'w', 20.0: 'w', 40.0: 'w'},
     "IF tau": {33.0: 0.2, 20.0: 3.7, 40.0: 6.4},
     "IF tau gas": {33.0: 5.0, 20.0: 5.0, 40.0: 5.0},
 }
 
-T0 = 8000
-kappa = 600.0
+T0 = 1000
+kappa = 60.0
 for M, L4, eta, S49, ax in stardata:
     Mlabel = "\n".join([
-        "B supergiant", "",
+        "M supergiant", "",
         rf"$M = {M:.0f}\, M_\odot$",
         rf"$L = {1e4*L4:.1e}\, L_\odot$".replace("e+0", r"\times 10^"),
         rf"$\eta = {eta}$"])
@@ -68,88 +68,6 @@ for M, L4, eta, S49, ax in stardata:
     R0 = x*Rs
     tau = 2*x*ts
 
-    # Ionization parameter - fiducial
-    U = 2.789*S49 / (R0**2 * nn)
-    # Shell ionization parameter - assume compression by M^2
-    Ush = U/(vv/10)**2
-    # Ionization fraction in shell
-    ysh = 1.0 - 1.0/(3.5e5*Ush)
-
-    # cs = ax.contour(vv, nn, ysh,
-    #                 (0.9, 0.99, 0.999, 0.9999, 0.99999),
-    #                 linewidths=1.0,
-    #                 colors='g', alpha=0.5)
-    # ax.clabel(cs,
[…]

### 2017-12-29 Dust-wave/zones-v-n-plane.py

@@ -137,8 +137,9 @@ for M, L4, eta, S49, ax in stardata:
     # ax.contour(vv, nn, tau_gas, tau_gas_IF,
     #            colors='y', linewidths=0.4)
     arrows = r"$\uparrow\!\!\!\!\uparrow$"
+    trap_text = rf"{arrows} Trapped i-front {arrows}"
     ax.text(60, d["trapped y"][M],
-            rf"{arrows} Trapped i-front, $\tau_\mathrm{{d}} = {tau_dust_IF:.1f}$, $\tau_\mathrm{{gas}} = {tau_gas_IF:.1f}$ {arrows}",
+            trap_text,
             ha='center', va='center',
             fontsize='xx-small', color='r', alpha=0.5, rotation=10,
             bbox=dict(fc=d["trapped bg"][M], ec='none', pad=0.1)

### 2017-12-29 papers/Papers1234/sec-dust-bow-intro.tex
Add discussion of gravity and Eddington factor

@@
   \label{eq:rad-accel}
-  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ , 
+  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ .
 \end{equation}
-so that an incoming stream with initial velocity, \(v_\infty\), can be
+Therefore, an incoming stream with initial velocity, \(v_\infty\), can be
 brought to rest by radiation alone\footnote{%
-  For simplicity, we here ignore the effects of pressure gradients and
+  For simplicity, we here ignore the effects of gravity, which are
+  important for low ratios of \(\kappa L / M\), see
+  \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
   shocks, which are important as the velocity approaches the sound
-  speed, \(\sound\). In \S~XX below, we show that the resultant
-  corrections to \(R_0\) are of order \(\sound / v_\infty\).} %
+  speed, \(\sound\) (in \S~XX below, we show that the resultant
+  corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
 at a distance \(R_0\) where
@@
 \(n = \text{\numrange{1000}{30 000}}\, v_{10}^2\) in this case.
+
+\subsubsection{Effects of stellar gravity}
+\label{sec:effects-gravity}
+
+In principle, gravitational attraction from the star, of mass \(M\),
+will partially counteract the radiative acceleration.  This can be
+accounted for by replacing \(L\) with an effective luminosity
+\newcommand\Edd{\ensuremath{_{\text{E}}}}
+\begin{equation}
+  \label{eq:effective-luminosity}
+  L_{\text{eff}} = L \bigl(1 - \Gamma\Edd^{-1}\bigr) \ ,
+\end{equation}
+in which \(\Gamma\Edd\) is the Eddington factor:
+\begin{equation}
+  \label{eq:eddington-factor}
+  \Gamma\Edd = \frac{\kappa L}{4\pi c G M} = 458.5 \, \frac{\kappa_{600} L_4}{ M } \ ,
+\end{equation}
+where, in the last expression, \(M\) is measured in solar masses.  For
+the stars in Table~\ref{tab:stars}, we find
+\(\Gamma\Edd \approx \text{\numrange{30}{400}}\), so gravity can be safely
+ignored.  The only exception is when the optical depth of the bow is
+very large: \(\tau > \ln\Gamma\Edd \sim 5\), in which case gravity may be
+important in the outer parts of the shell (see
+\citealt{Rodriguez-Ramirez:2016b}).
 

### 2018-01-04 papers/Papers1234/sec-dust-bow-intro.tex
Add advection contribution to i-front trapping
And write about the B-type supergiant

@@
 \end{equation}
-while the flux of hydrogen-ionizing photons
+while the advective flux of hydrogen nuclei through the shock is 
+\begin{equation}
+  \label{eq:shell-advective-flux}
+  \mathcal{A} = n v \ ,
+\end{equation}
+and the flux of hydrogen-ionizing photons
 (\(h \nu > \SI{13.6}{eV}\)) incident on the inner edge of the shell is
@@
 where \(S\) is the ionizing photon luminosity of the star.  Any shell
-with \(\mathcal{R} > \mathcal{F}\) cannot be entirely photoionized by
-the star, and so must have trapped the ionization front.  The column
-density of the shocked shell can be found, for example, from
-equations~(10) and~(12) of \citet{Wilkin:1996a} in the limit
-\(v_\infty/V \to 0\) (Wilkin's parameter \(\alpha\)) and \(\theta \to 0\).  This yields
+with \(\mathcal{R} + \mathcal{A} > \mathcal{F}\) cannot be entirely
+photoionized by the star, and so must have trapped the ionization
+front.
+
+The ratio of advective particle flux to ionizing flux is, from equations~\eqref{eq:Rstar}, \eqref{eq:shell-advective-flux}, \eqref{eq:shell-ionizing-flux},
+\begin{equation}
+  \label{eq:advective-over-ionizing-flux}
+  \frac{\mathcal{A}}{\mathcal{F}} = \num{5.86e-5} \frac{x^2 L_4}{v_{10} S_{49}} \ , 
+\end{equation}
+which is nearly always small.  For clarity of exposition, we therefore
+ignore \(\mathcal{A}\) in the following discussion, although it is
+included in quantitative calculations.  The column density of the
+shocked shell can be found, for example, from equations~(10) and~(12)
+of \citet{Wilkin:1996a} in the limit \(v_\infty/V \to 0\) (Wilkin's parameter
+\(\alpha\)) and \(\theta \to 0\).  This yields
 \begin{equation}
@@
 the ionizing radiation field must be considered.
+
+Quite different results are obtained for a B-type supergiant star (see
+Tab.~\ref{tab:stars} and Fig.~\ref{fig:B-supergiant}), which has a
+similar bolometric luminosity and wind strength to the \SI{40}{M_\odot}
+main-sequence star, but a hundred times lower ionizing luminosity.
+This results in a far lower threshold for trapping the ionization
+front of \(n > 40 v_{10}^2\).  The advective flux, \(\mathcal{A}\), is
+relatively stronger for this star tan for the main-sequence stars, but
+even for \(v_{10} < 2\), where the effect is strongest, the change is
+only of order the width of the red line in
+Figure~\ref{fig:B-supergiant}.
 

### 2018-01-04 Dust-wave/zones-v-n-plane-BSG.py

@@ -91,6 +91,8 @@ for M, L4, eta, S49, ax in stardata:
     alphaB = 2.6e-13*(T0/1e4)**(-0.7)
     absfrac0 = 3*np.pi*(3.085677582e18)**3 * alphaB / 1e49
     absfrac = absfrac0 * (vv/10)**2 * nn**2 * R0**3 / S49
+    # Advection contribution
+    advecfrac = 4*np.pi*(3.085677582e18*R0)**2 *nn*vv*1e5 / (1e49*S49) 
     # Equivalent optical depth
     tau_gas = -np.log(1.0 - absfrac)
     #absfrac = 2.76e-4 * (vv/10)**-1 * nn**0.5 * (L4)**1.5 / S49
@@ -130,7 +132,7 @@ for M, L4, eta, S49, ax in stardata:
     tau_gas_IF = np.nanmean(tau_gas[m])
     tau_dust_IF = np.nanmean(tau_dust[m])
     cs = ax.contourf(vv, nn, tau_dust, (tau_dust[m].min(), tau_dust[m].max()), linewidths=2, colors='r', alpha=0.3)
-    ax.contour(vv, nn, absfrac, 1.0, linewidths=0.7, colors='r')
+    ax.contour(vv, nn, absfrac+advecfrac, 1.0, linewidths=0.7, colors='r')
 
     # ax.contour(vv, nn, tau, tau_dust_IF,
     #            colors='k', linestyles='--', linewidths=0.8)

### 2018-01-11 papers/Papers1234/app-dust-wave.tex
Finish long footnote on stellar wind models
And add a bit to a new section about observations of IR arcs in Carina
Finish duststream graph and figueres

@@
-\section{Shape of a dusty radiative bow wave}
+\section{Shape and structure of dust waves}
 \label{sec:shape-dust-wave}
@@
 
-\subsection{Gas-free bow wave}
+\subsection{Gas-free dust wave}
 \label{sec:gas-free-bow}
@@
 both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\).
-
-\newcommand\drag{\ensuremath{_{\text{drag}}}}
-\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
-\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
-\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
 
@@
 
+\subsection{Bow wave with magnetic field}
+\label{sec:bow-wave-with}
+
+\newcommand\Larmor{\ensuremath{_{\text{L}}}}
+
+First consider the limit of very small gyro-radius, which is the case
+when the Lorentz force is much larger than other forces acting on the
+grain. The grains will then follow tightly wound helical paths around
+the magnetic field lines, which can be decomposed into a circular
+motion of radius \(r\Larmor\) plus the motion if the \textit{guiding
+  center} along the field line.  The motion of the guiding center is
+explicitly followed by accounting for the components parallel to the
+field lines of the radiative and drag forces, whereas forces
+perpendicular to the field lines, which would only effect the circular
+motion are ignored in the first instance (but see \S~XXX below).
+
+\begin{figure}
+
+  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b15-z0000}
+  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b45-z0000}
+  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b75-z0000}
+  \caption{Grain trajectories for magnetised dust waves in the limit
+    of no gas drag and small gyro-radius. }
+  \label{fig:magnetic-dust-waves}
+\end{figure}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-15}
+  \caption{xxx}
+  \label{fig:projected-magnetic-dust-waves-15}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-45}
+  \caption{xxx}
+  \label{fig:projected-magnetic-dust-waves-45}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-75}
+  \caption{xxx}
+  \label{fig:projected-magnetic-dust-waves-75}
+\end{figure*}
+
 \subsection{Applicability of the bow wave models}
@@
 
+\section{Shape and structure of bow waves}
+\label{sec:shape-bow-wave}
+
 %%% Local Variables:

### 2018-01-11 Dust-wave/dust-bfield-stream.py

@@ -31,8 +31,11 @@ xmin, xmax = [-4.99, 4.99]
 ymin, ymax = [-4.99, 4.99]
 xx, yy, ww = [], [], []
 xs, ys = [], []
+nt = 3001
+tstop = 60
+X0 = 20
 for iy0, y0 in enumerate(y0grid):
-    s = streamline(X0=20, Y0=y0, Z0=Z0, thB=np.radians(thB_degrees), tstop=60, n=3001)
+    s = streamline(X0=X0, Y0=y0, Z0=Z0, thB=np.radians(thB_degrees), tstop=tstop, n=nt)
     # ax.plot(s['x'], s['y'], color='k', lw=0.5)
     # Accumulate (x, y) points in a long list
     xx.extend(s['x'])
@@ -57,9 +60,26 @@ rho_m = np.median(H)
 ax.imshow(H.T, origin='lower', extent=[xmin, xmax, ymin, ymax],
           vmin=0.0, vmax=20.0*rho_m, cmap='gray_r')
 # Plot the streamlines that we saved earlier
+x1s = [4, 2, 0, -2, -4]
+# Bespoke collection of colors for the scatter shot grains at each x1 position
+colors = [
+    # First batch at x=4 is separated from rest
+    # Pale yellow
+    (0.8, 0.8, 0.3, 1.0),
+    # Swing towards orange for next two at x=2 and x=0
+    (0.9, 0.7, 0.2, 1.0),
+    (1.0, 0.4, 0.1, 1.0),
+    # Now we need a contrast - go more purple
+    (0.7, 0.1, 0.4, 1.0),
+    # And finally, more blue
+    (0.2, 0.2, 0.5, 1.0)
+]
 for x, y in zip(xs, ys):
     ax.plot(x, y, '-', color='w', lw=0.8, alpha=0.5)
     ax.plot(x, y, '-', color='k', lw=0.5)
+    for x1, color in zip(x1s, colors):
+        itime = int((X0 - x1)*nt/tstop)
+        ax.plot(x[itime-10:itime+20:10], y[itime-10:itime+20:10], '.', ms=4.0, color=color, zorder=20-x1)
 ax.plot(xlocus, ylocus, ':', color='y', alpha=0.7, lw=2)
 ax.plot(xlocus, -ylocus, ':', color='y', alpha=0.7, lw=2)
 cthB = np.cos(np.radians(thB_degrees))

### 2018-01-14 Dust-wave/dust-lorentz-3d.py
Add in drag terms to magnetic dust waves

@@ -7,10 +7,11 @@ from dust_blorentz_ode import streamline
 figfile = sys.argv[0].replace('.py', '.pdf')
 
 # Impact parameter
-Y0 = -0.01
-Z0 = 0.5
-thB_degrees = 5
-stream = streamline(Y0=Y0, Z0=Z0, thB=np.radians(thB_degrees), tstop=150, X0=10., n=2001, LFAC=1.5)
+Y0 = 0.00
+Z0 = 0.00
+thB_degrees = 25
+MACH_ALFVEN = 4.0
+stream = streamline(Y0=Y0, Z0=Z0, thB=np.radians(thB_degrees), tstop=150, X0=10., n=2001, LFAC=10, ALPHA_DRAG=0.5, V_TURB_0=1.0/MACH_ALFVEN)
 sns.set_style('white')
 sns.set_color_codes()
 fig, (ax, axp) = plt.subplots(2, 1, figsize=(4, 6))
@@ -24,7 +25,7 @@ ax.axhspan(0.0, 1.0, color='k', alpha=0.1)
 label = fr"$\theta_B = {thB_degrees:.1f}^\circ$, "
 label += f"$y_0 = {Y0:.2f}$, $z_0 = {Z0:.2f}$"
 ax.legend(title=label, ncol=2)
-ax.set(xlabel='Time', ylim=[-8.5, 8.5], xlim=[0, 50])
+ax.set(xlabel='Time', ylim=[-2, 3], xlim=[0, 50])
 
 axp.plot(stream['x'], stream['u'], label='$(X, U)$')
 axp.plot(stream['y'], stream['v'], label='$(Y, V)$')
@@ -32,7 +33,7 @@ axp.plot(stream['z'], stream['w'], label='$(Z, W)$')
 axp.axhline(0, color='k', lw=0.5)
 axp.legend(title='Phase space')
 axp.set(xlabel='$X$, $Y$, $Z$', ylabel='$U$, $V$, $W$',
-        xlim=[-7, 9], ylim=[-1.1, 1.1])
+        xlim=[-3, 3], ylim=[-1.5, 1.5])
 
 sns.despine(trim=True)
 fig.tight_layout()

### 2018-01-14 Dust-wave/dust-lorentz-stream-3d-turb.py

@@ -13,11 +13,17 @@ try:
     LFAC = float(sys.argv[2])
     MACH_ALFVEN = float(sys.argv[3])
     ZPLANE = float(sys.argv[4])
+    try: 
+        ALPHA_DRAG = float(sys.argv[5])
+    except:
+        ALPHA_DRAG = 0.0
 except:
-    sys.exit(f"Usage: {sys.argv[0]} FIELD_ANGLE LORENTZ_FORCE MACH_ALFVEN ZPLANE")
+    sys.exit(f"Usage: {sys.argv[0]} FIELD_ANGLE LORENTZ_FORCE MACH_ALFVEN ZPLANE [ALPHA_DRAG]")
 
 
 suffix = f"b{int(thB_degrees):02d}-L{int(100*LFAC):04d}-Ma{int(10*MACH_ALFVEN):04d}-Z{int(100*ZPLANE):+04d}"
+if ALPHA_DRAG > 0.0:
+    suffix += f"-alpha{int(100*ALPHA_DRAG):04d}"
 figfile = sys.argv[0].replace('.py', f'-{suffix}.jpg')
 
 sns.set_style('white')
@@ -39,6 +45,22 @@ p = Rectangle((xmin, ymin), xmax - xmin, ymax - ymin,
 ax.add_patch(p)
 art3d.pathpatch_2d_to_3d(p, z=ZPLANE, zdir="z")
 
+# Put lines of B on the bottom z plane
+cthB = np.cos(np.radians(thB_degrees))
+sthB = np.sin(np.radians(thB_degrees))
+for xx in np.linspace(-15, 15, 31):
+    yy1, yy2 = -15, 15
+    x1 = -xx*sthB + yy1*cthB
+    x2 = -xx*sthB + yy2*cthB
+    y1 = xx*cthB + yy1*sthB
+    y2 = xx*cthB + yy2*sthB
+    x = np.linspace(x1, x2, 200)
+    y = np.linspace(y1, y2, 200)
+    m = (x >= xmin) & (y >= ymin) & (x <= xmax) & (y <= ymax)
+    x[~m] = np.nan
+    ax.plot(x, y, zs=zmin, zdir='z', lw=2, alpha=0.5, color='c')
+
+
 #nt = 3001
 nt = 3001
 tstop = 60
@@ -55,27 +77,10 @@ mu_p_max = 0.1
 # Find all the trajectories
 trajectories = []
 for y0 in y0grid:
-    # Pitch angle to field
[…]

### 2018-01-14 Dust-wave/dust-lorentz-stream-3d-turbz.py

@@ -22,7 +22,7 @@ figfile = sys.argv[0].replace('.py', f'-{suffix}.jpg')
 
 sns.set_style('white')
 sns.set_color_codes()
-fig, ax = plt.subplots(subplot_kw=dict(projection='3d'), figsize=(6, 3))
+fig, ax = plt.subplots(subplot_kw=dict(projection='3d'), figsize=(6, 3.3))
 
 
 ny0, nz0 = 31, 1
@@ -93,7 +93,7 @@ for y0 in y0grid:
     if ymin <= s['y'][it0] <= ymax:
         trajectories.append(s)
 
-# Sort according to y coordinate near the star
+# Sort according to z coordinate near the star
 trajectories.sort(key=lambda s: s['z'][it0], reverse=False)
 
 ycolors = sns.color_palette('magma_r', n_colors=len(trajectories))
@@ -106,7 +106,7 @@ for iy0, s in enumerate(trajectories):
     m = m & (y >= ymin) & (y <= ymax)
     m = m & (z >= zmin) & (z <= zmax)
     x[~m] = np.nan
-    # Draw the star before we get to the first negative y value
+    # Draw the star before we get to the first positive z value
     if s['z'][it0] > 0.0 and not star_done:
         ax.plot([0, 0], [0, 0], [zmin, zmax], '--', color='k', lw=0.3)
         ax.plot([xmin, xmax], [0, 0], [0, 0], '--', color='k', lw=0.3)
@@ -137,6 +137,6 @@ text = "$" + r" \quad\quad ".join([
     fr"\mathcal{{M}}_A = {MACH_ALFVEN:.1f}",
     fr"y_0 = {YPLANE:.4f}"]) + "$"
 fig.text(0.1, 0.9, text)
-fig.tight_layout(rect=[0, 0, 0.95, 1.0])
+fig.tight_layout(rect=[0, 0, 1.05, 1.0])
 fig.savefig(figfile, dpi=600)
 print(figfile, end='')

### 2018-01-14 Dust-wave/dust_blorentz_ode.py

@@ -1,7 +1,7 @@
 import numpy as np
 from scipy.integrate import odeint
 
-def dydt(y, t, thB, LORENTZ_FAC):
+def dydt(y, t, thB, LORENTZ_FAC, ALPHA_DRAG=0.0):
     """Derivatives for ODE: x'' = 0.5 (x^{-2} - alpha^2 (x' + 1))"""
     X, U, Y, V, Z, W = y
     dXdt = U
@@ -17,21 +17,52 @@ def dydt(y, t, thB, LORENTZ_FAC):
     Bx, By, Bz = np.cos(thB), np.sin(thB), 0.0
     # Lorentz acceleration vector
     alorentz = 0.5*LORENTZ_FAC * np.cross([U + 1.0, V, W], [Bx, By, Bz])
-    dUdt = arad[0] + alorentz[0]
-    dVdt = arad[1] + alorentz[1]
-    dWdt = arad[2] + alorentz[2]
+
+    # Drag acceleration vector (assume that gas velocity is [-1, 0, 0])
+    adrag = -0.5*ALPHA_DRAG**2 * np.array([U + 1.0, V, W])
+
+    dUdt = arad[0] + alorentz[0] + adrag[0] 
+    dVdt = arad[1] + alorentz[1] + adrag[1] 
+    dWdt = arad[2] + alorentz[2] + adrag[2] 
     return [dXdt, dUdt, dYdt, dVdt, dZdt, dWdt]
+
+
+def init_vturb(v_turb_0, mu_p_max, thB):
+    """Turbulent grain velocity at a high pitch angle"""
+    # Pitch angle to field
+    c_p = np.random.uniform(0.0, mu_p_max)
+    s_p = np.sqrt(1.0 - c_p**2) 
+    # Azimuth around field
+    phi_B = np.random.uniform(0.0, 2*np.pi)
+    spB, cpB = np.sin(phi_B), np.cos(phi_B) 
+    # Magnitude and sign
+    v_turb = np.random.normal(loc=0.0, scale=v_turb_0)
+    # Components in frame of B-field
+    vBx = v_turb*c_p
+    vBy = v_turb*s_p*cpB
+    vBz = v_turb*s_p*spB
+    # Now transform to flow frame
+    cthB, sthB = np.cos(thB), np.sin(thB)
+    u0 = vBx*cthB - vBy*sthB
+    v0 = vBx*sthB + vBy*cthB
+    w0 = vBz
[…]

### 2018-01-16 papers/Papers1234/sec-projection.tex
Intermediate steps in equation 13

--- 2017-12-03 papers/Paper1/sec-projection.tex
@@
 For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
-equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, and then
-converting to the observer frame by use of equation~(\ref{eq:Trans})
+equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, as follows:
+
+\begin{align}
+  \uvec{n} &= \mathcal{R}\uvec{n}_0 =
+  \begin{Vector}
+    \sin\alpha \\ \cos\alpha\cos\phi \\ \cos\alpha\sin\phi
+  \end{Vector} \\
+  \uvec{t} &= \mathcal{R}\uvec{t}_0 =
+  \begin{Vector}
+    -\cos\alpha \\ \sin\alpha\cos\phi \\ \sin\alpha\sin\phi
+  \end{Vector}
+\end{align}
+Where $\mathcal{R}$ is the rotation matrix around the $x$-axis:
+\begin{equation}
+  \mathcal{R} =
+  \begin{pmatrix}
+    1 & 0 & 0 \\
+    0 &\cos\phi & -\sin\phi \\
+    0 &\sin\phi & \cos\phi
+  \end{pmatrix}
+\end{equation}
+then converting to the observer frame by use of equation~(\ref{eq:Trans})
 to give

### 2018-01-17 papers/Papers1234/app-intermediate.tex
Add new appendixes to address referee points

%% \section{Derivation of selected results from \S\S~2 and 3}

\section{Radius of curvature}
\label{sec:radius-curvature}

The radius of curvature of a general curve can be written (e.g.,
eq.~[2-5] of \citealp{Guggenheimer:2012a}):
\begin{equation}
  \label{eq:Rcurv-general}
  R_{\C} \equiv \frac{1}{\abs{\kappa}} = \Abs{\frac{d s}{d \alpha}} \ ,  
\end{equation}
where \(\kappa\) is the \textit{curvature}, \(s\) is the path length along
the curve and \(\alpha\) is the tangent angle (see Fig.~\ref{fig:unitvec}).
In spherical polar coordinates, this becomes \citep{Weisstein:2018a}:
\begin{equation}
  \label{eq:Rcurv-polar}
  R_{\C} = \frac{\left( R^2 + R_\theta^2 \right)^{3/2}}
  {\Abs{R^2 + 2 R_\theta^2 - R R_{\theta\theta}}} \ , 
\end{equation}
where \(R_\theta = d R / d \theta\) and
\(R_{\theta\theta} = d^2 R / d \theta^2\).  At the apex,
\(R_\theta = 0\) by symmetry, which yields
equation~\eqref{eq:radius-curvature} of
\S~\ref{sec:plan-alat-bow}. Note that \(\theta\) is dimensionless and
should be measured in radians \citep{Mohr:2015a, Quincey:2017a}.

\section{Rotation matrices and plane of sky projection}
\label{sec:plane-sky-projection}

The transformation from the body frame (unprimed) to observer-frame
(primed) coordinates is a rotation about the \(y\) axis by an angle
\(i\), which is described by the rotation matrix:
\begin{equation}
  \label{eq:Rotation-matrix-y}
  \mathbfss{A}_y(i) = 
   \begin{pmatrix}
    \cos i & 0 & -\sin i \\
    0 & 1 & 0 \\
    \sin i & 0 &\cos i 
  \end{pmatrix} \ .
\end{equation}
This is used in equation~\eqref{eq:Trans}.

Since we are considering cylindrically symmetric bows, all azimuths
\(\phi\) are equivalent, so it is sufficient to work with two-dimensional
curves in the plane \(z = 0\) (which is also \(\phi = 0\)) and then find
the three-dimensional surface by rotating about the \(x\)-axis via the
rotation matrix:
\begin{equation}
  \label{eq:Rotation-matrix-x}
  \mathbfss{A}_x(\phi) = 
   \begin{pmatrix}
    1 & 0 & 0 \\
    0 &\cos\phi & -\sin\phi \\
    0 &\sin\phi & \cos\phi 
  \end{pmatrix} \ .
\end{equation}
This is used in \S~\ref{sec:unit-vectors-normal} to find the general
form of the body-frame normal and tangent unit vectors:
\begin{align}
  \uvec{n} &= \mathbfss{A}_x(\phi) \, \uvec{n}_0 =
  \begin{Vector}
    \sin\alpha \\ \cos\alpha\cos\phi \\ \cos\alpha\sin\phi
  \end{Vector} \\
  \uvec{t} &= \mathbfss{A}_x(\phi) \, \uvec{t}_0 =
  \begin{Vector}
    -\cos\alpha \\ \sin\alpha\cos\phi \\ \sin\alpha\sin\phi
  \end{Vector} \ . 
\end{align}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

### 2018-01-17 papers/Papers1234/sec-intro.tex
Partially address first point of referee - rad curvature
Add new appendixes to address referee points

--- 2017-12-05 papers/Paper1/sec-intro.tex
@@
 The perpendicular radius \(R_{90}\) is the value of \(R(\theta)\) at
-\(\theta = 90^\circ\), whereas \(R_{\C}\) is the radius of curvature of the bow at
-the apex (\(\theta = 0\)), which in cylindrical symmetry simplifies to
+\(\theta = 90^\circ\), whereas \(R_{\C}\) is the radius of curvature of the bow
+at the apex (\(\theta = 0\)).  For a cylindrically symmetric bow, we show
+in Appendix~\ref{sec:radius-curvature} that this is given by
 \begin{equation}
@@
   R_{\C} 
-  % = R_0 \Biggl[ 1
-  % - \frac{1} {R_0} \left.\frac{d^2\! R} {d\,\theta^2}\right|_{\theta = 0} \Biggr]^{-1}
   = \frac{R_0^2}{R_0 - R_{\theta\theta,0}} \ , 

### 2018-01-17 papers/Papers1234/sec-projection.tex
Add new appendixes to address referee points

--- 2017-12-03 papers/Paper1/sec-projection.tex
@@
-\newenvironment{Vector}{\left(\begin{array}{c}}{\end{array}\right)}
-\newcommand\uvec[1]{\bm{\hat{#1}}}
-\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
-
 \section{Projection onto the plane of the sky}
@@
 \begin{equation}
+  \bm{R} \equiv
   \begin{Vector}
@@
   \end{Vector} 
-  = R(\theta)
+  = 
   \begin{Vector}
-    \cos\theta \\
-    \sin\theta\cos\phi \\
-    \sin\theta\sin\phi
+    R(\theta)\, \cos\theta \\
+    R(\theta)\, \sin\theta\cos\phi \\
+    R(\theta)\, \sin\theta\sin\phi
   \end{Vector}.
@@
 \begin{equation}
+  \bm{R}' \equiv
   \begin{Vector}
@@
   \end{Vector}
+  = \mathbfss{A}_y(i)\, \bm{R}
   =
@@
     z\cos i + x\sin i
-  \end{Vector}.
+  \end{Vector} \ ,
   \label{eq:Trans}
 \end{equation}
+where the rotation matrix \(\mathbfss{A}_y(i)\) is given in Appendix~\ref{sec:plane-sky-projection}. 
 The relationship between the two frames is illustrated in
@@
 For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
-equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, and then
-converting to the observer frame by use of equation~(\ref{eq:Trans})
-to give
+equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis with the matrix
+\(\mathbfss{A}_x(\phi)\)(see Appendix~\ref{sec:plane-sky-projection}) and
+then converting to the observer frame by use of
+equation~(\ref{eq:Trans}) to give
 \begin{gather}
   \label{eq:nprime}
-  \begin{split}
-    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
+  \begin{aligned}
+    \uvec{n}' &= \mathbfss{A}_y(i)\, \uvec{n}
+    = \mathbfss{A}_y(i)\, \mathbfss{A}_x(\phi)\, \uvec{n}_0 \\
+    & =
+    \begin{aligned}[t]
+      & \frac{1}{(1+\omega^2)^{1/2}} \\
       & \times 
@@
         + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-      \end{Vector}\\
-  \end{split}\\
+      \end{Vector}
+    \end{aligned}
+  \end{aligned}\\
   \label{eq:tprime}
-  \begin{split}
-    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
+  \begin{aligned}
+    \uvec{t}' &= \mathbfss{A}_y(i)\, \uvec{t}
+    = \mathbfss{A}_y(i)\, \mathbfss{A}_x(\phi)\, \uvec{t}_0 \\
+    & =
+    \begin{aligned}[t]
+      & \frac{1}{(1+\omega^2)^{1/2}} \\
       & \times 
@@
         + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-      \end{Vector}
-  \end{split}
+      \end{Vector} \ .
+    \end{aligned}
+  \end{aligned}
 \end{gather}

### 2018-01-18 papers/Papers1234/sec-projection.tex
Explain about the plane of sky as a projective space

@@
 \begin{equation}
-  \bm{R} \equiv
+  \bm{r} \equiv
   \begin{Vector}
@@
 \begin{equation}
-  \bm{R}' \equiv
+  \bm{r}' \equiv
   \begin{Vector}
@@
   \end{Vector}
-  = \mathbfss{A}_y(i)\, \bm{R}
+  = \mathbfss{A}_y(i)\, \bm{r}
   =
@@
 \end{equation}
-where the rotation matrix \(\mathbfss{A}_y(i)\) is given in Appendix~\ref{sec:plane-sky-projection}. 
+where the rotation matrix \(\mathbfss{A}_y(i)\) is given in
+Appendix~\ref{sec:plane-sky-projection}.  The inclination angle \(i\)
+is defined so that \(i = \ang{0}\) when the surface is viewed
+perpendicular to its axis (\textit{side on}) and \(i = \ang{90}\) when
+it is viewed along its axis (\textit{end on}).
+
 The relationship between the two frames is illustrated in
@@
 frame are denoted by attaching a prime to the equivalent quantity in
-the body frame.  The celestial coordinates on the ``plane of the sky''
-are given by \((x', y')\) with \(x'\) being the projected symmetry
-axis of the surface, while the line of sight lies along \(-z'\).  The
-inclination angle \(i\) is defined so that \(i = \ang{0}\) when the
-surface is viewed perpendicular to its axis (\textit{side on}) and
-\(i = \ang{90}\) when it is viewed along its axis (\textit{end on}).
+the body frame. There are two ways of interpreting the primed
+coordinates. On the one hand, the 3-vector \((x', y', z')\) specifies
+a point in Euclidean space, \(\mathds{R}^3\), but an alternative
+interpretation is to take the 2-vector \((x', y')\) as specifying a
+point in a \textit{projective space}, \(\mathds{P}^2\) (see, for
+example, \S~15.6 of \citealp{Penrose:2004a}). Each ``point'' in
+\(\mathds{P}^2\) is equivalent to a line in \(\mathds{R}^3\),
+specifically: a line of sight that passes through the observer. Thus,
+\((x', y')\) gives the celestial coordinates on the \textit{plane of
+  the sky}, with \(x'\) being the projected symmetry axis of the
+surface.  We assume that the observer is located at a very large
+distance, relative to the size of the bow, so that all lines of sight
+are effectively parallel to the \(z'\) axis, with the observer at
+\(z' = -\infty\).  But, from the point of view of the plane of the sky, the
+\(z'\) coordinate is strictly irrelevant since it is a projective
+plane, and not a Euclidean plane.  In the following, we will switch
+between the \(\mathds{R}^3\) and \(\mathds{P}^2\) interpretations as
+convenient, resolving ambiguity where necessary via the adjectives
+``Euclidean'' for \(\mathds{R}^3\) and ``plane-of-sky'' or
+``projected'' for \(\mathds{P}^2\).
 
@@
   \caption{Relationship between body frame (unprimed coordinates) and
-    observer frame (primed coordinates).}
+    observer frame (primed coordinates).  Note that the plane of the
+    sky is a projective plane, not a geometric plane in Euclidean
+    3-space, see discussion in text.}
   \label{fig:projection-pos}
@@
 Note that, in general, \(z'\T\) is not a linear function of \(x'\T\)
-and \(y'\T\), so that the tangent line is not a plane curve.
-
-The apparent shape \((x'\T, y'\T)\) of the tangent line on the plane
-of the sky can also be described in polar form as \(R'(\theta')\),
-where
+and \(y'\T\), so that the tangent line \((x'\T, y'\T, z'\T)\) is not a
+plane curve in 3-dimensional Euclidean space, \(\mathds{R}^3\).
+However, for the projected shape \((x'\T, y'\T)\) of the tangent line
+on the plane of the sky, \(\mathds{P}^2\), the value of \(z'\T\) does
+not matter (see above).  The projected shape can also be described in
+polar form as \(R'(\theta')\), where
 \begin{equation}
@@
 \end{equation}
+
 Note that equation~(\ref{eq:tanphi}) will not have
@@
 
+Projective space \(\mathbb{RP}^2\) or \(\mathbbm{RP}^2\) or \(\mathds{RP}^2\)
+
 \subsection{Line-of-sight velocities on the tangent line}

### 2018-01-20 Simulation-Shapes/Meyer-2017-src/paper.tex
Start work on figure to explain fits to Meyer 2017 shapes

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[referee,useAMS]{mn2e}
%%\documentclass[referee,useAMS,usenatbib]{mn2e}

\usepackage{natbib}

\usepackage{latexsym,graphicx}%,natbib}
\usepackage{color}
\usepackage{fixltx2e}
\usepackage{verbatim}
\usepackage{float}
\usepackage{amsmath,amssymb}
\usepackage{times}
\usepackage{soul}
\usepackage{natbib}
%\usepackage{siunitx}

\usepackage{setspace}
%\doublespacing

% Definition for highlighting changes in red
%
\def\changed{}
% comment the following line to remove the highlighting
\def\changed{\color{red}}

%%%% units & names definitions
\newcommand\kms{{\rm\,km\,s^{-1}}}
\newcommand\msun{\rm\,M_\odot}
\newcommand\rsun{\rm\,R_\odot}
\newcommand\lsun{\rm\,L_\odot}
\newcommand{\MC}{\multicolumn}
\newcommand\hii{H\,{\sc ii} \,}
\newcommand\hi{H\,{\sc i} \,}
\newcommand\myr{\msun \, {\rm yr}^{-1}}

%%%% symbols definitions
\def\apgt{\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
\def\aplt{\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }

\newcommand{\degree}{\ensuremath{^\circ}}

\def\ion#1#2{\rm{#1}\,{\textsc {#2}}} 
\def\HII{\rm{H}\,{\textsc {ii}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\citestyle{mn2e}
% Bibliography and bibfile
\def\aj{AJ}%
     % Astronomical Journal
\def\araa{ARA\&A}%
     % Annual Review of Astron and Astrophys
\def\apj{ApJ}%
     % Astrophysical Journal
\def\apjl{ApJ}%
     % Astrophysical Journal, Letters
\def\apjs{ApJS}%
     % Astrophysical Journal, Supplement
\def\ao{Appl.~Opt.}%
     % Applied Optics
\def\apss{Ap\&SS}%
     % Astrophysics and Space Science
\def\aap{A\&A}%
     % Astronomy and Astrophysics
\def\aapr{A\&A~Rev.}%
     % Astronomy and Astrophysics Reviews
\def\aaps{A\&AS}%
     % Astronomy and Astrophysics, Supplement
\def\azh{AZh}%
     % Astronomicheskii Zhurnal
\def\baas{BAAS}%
     % Bulletin of the AAS
\def\jrasc{JRASC}%
     % Journal of the RAS of Canada
\def\memras{MmRAS}%
     % Memoirs of the RAS
\def\mnras{MNRAS}%
     % Monthly Notices of the RAS
\def\na{New~Ast.}%
     % New Astronomy
\def\pra{Phys.~Rev.~A}%
     % Physical Review A: General Physics
\def\prb{Phys.~Rev.~B}%
     % Physical Review B: Solid State
\def\prc{Phys.~Rev.~C}%
     % Physical Review C
\def\prd{Phys.~Rev.~D}%
     % Physical Review D
\def\pre{Phys.~Rev.~E}%
     % Physical Review E
\def\prl{Phys.~Rev.~Lett.}%
     % Physical Review Letters
\def\pasp{PASP}%
     % Publications of the ASP
\def\pasj{PASJ}%
     % Publications of the ASJ
\def\qjras{QJRAS}%
     % Publications of the RMXAA
\def\rmxaa{Rev.~Mex.~Ast.}%
     % Quarterly Journal of the RAS
\def\skytel{S\&T}%
     % Sky and Telescope
\def\solphys{Sol.~Phys.}%
     % Solar Physics
\def\sovast{Soviet~Ast.}%
     % Soviet Astronomy
\def\ssr{Space~Sci.~Rev.}%
     % Space Science Reviews
\def\zap{ZAp}%
     % Zeitschrift fuer Astrophysik
\def\nat{Nature}%
     % Nature
\def\iaucirc{IAU~Circ.}%
     % IAU Cirulars
\def\aplett{Astrophys.~Lett.}%
     % Astrophysics Letters
\def\apspr{Astrophys.~Space~Phys.~Res.}%
     % Astrophysics Space Physics Research
\def\bain{Bull.~Astron.~Inst.~Netherlands}%
     % Bulletin Astronomical Institute of the Netherlands
\def\fcp{Fund.~Cosmic~Phys.}%
     % Fundamental Cosmic Physics
\def\gca{Geochim.~Cosmochim.~Acta}%
     % Geochimica Cosmochimica Acta
\def\grl{Geophys.~Res.~Lett.}%
     % Geophysics Research Letters
\def\jcp{J.~Chem.~Phys.}%
     % Journal of Chemical Physics
\def\jgr{J.~Geophys.~Res.}%
     % Journal of Geophysics Research
\def\jqsrt{J.~Quant.~Spec.~Radiat.~Transf.}%
     % Journal of Quantitiative Spectroscopy and Radiative Trasfer
\def\memsai{Mem.~Soc.~Astron.~Italiana}%
     % Mem. Societa Astronomica Italiana
\def\nphysa{Nucl.~Phys.~A}%
     % Nuclear Physics A
\def\physrep{Phys.~Rep.}%
     % Physics Reports
\def\physscr{Phys.~Scr}%
     % Physica Scripta
\def\planss{Planet.~Space~Sci.}%
     % Planetary Space Science
\def\procspie{Proc.~SPIE}%
     % Proceedings of the SPIE
\let\astap=\aap
\let\apjlett=\apjl
\let\apjsupp=\apjs
\let\applopt=\ao

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Title
\title[Bow shock nebulae of hot massive stars in a magnetized medium]{Bow shock nebulae of hot massive stars in a magnetized medium}

\author[D. M.-A.~Meyer et al.]
       {D. M.-A.~Meyer,$^{1}$\thanks{E-mail: dominique.meyer@uni-tuebingen.de} A. Mignone,$^{2}$ R. Kuiper,$^{1}$ A. Raga$^{3}$ and W. Kley$^{1}$ 
       \\
       $^{1}$Institut f\" ur Astronomie und Astrophysik, Universit\" at T\" ubingen,  Auf der Morgenstelle 10, 72076 T\" ubingen, Germany \\
       $^{2}$Dipartimento di Fisica Generale Facolt\`a di Scienze M.F.N., Universit\`a degli Studi di Torino, Via Pietro Giuria 1, 10125 Torino, Italy \\ 
       $^{3}$Instituto de Ciencias Nucleares, Universidad Nacional Aut\' onoma de M\' exico, Ap. 70-543, 04510 D.F., M\' exico \\
       }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Date
\date{Received 2015; accepted 2015}

\maketitle

\label{firstpage}

\begin{abstract}

\textcolor{black}{
A significant fraction of OB-type, main-sequence massive stars are classified 
as {\it runaway} and move supersonically through the interstellar medium (ISM). 
Their strong stellar winds interact with their surroundings \textcolor{black}{where the} 
typical strength of the local ISM magnetic field is about $3.5$-$7\, \mu \rm G$, which 
can result in the formation of bow shock nebulae. 
%
We investigate the effects of such magnetic field\textcolor{black}{s}, aligned with the motion of 
the flow, on the formation and emission properties of these circumstellar structures. 
}
%
\textcolor{black}{
Our axisymmetric, magneto-hydrodynamical simulations with optically-thin radiative 
cooling, heating and anisotropic thermal conduction show that the  
presence of the background ISM magnetic field affects the projected optical emission our bow 
shocks at H$\alpha$ and [O{\sc iii}] $\lambda \, 5007$ 
which become fainter by about $1$-$2$ orders of magnitude, respectively. 
%
Radiative transfer calculations against dust opacity indicate that the magnetic 
field slightly diminishes their projected infrared emission and that our bow 
shocks emit brightly at $60\, \mu \rm m$. 
} 
%
This may explain why the bow shocks generated 
by ionizing runaway massive stars are often difficult to identify. 
Finally, we discuss our results in the context of the bow shock of $\zeta$ Ophiuchi and 
we support the interpretation of its imperfect morphology as an evidence of the presence 
of an ISM magnetic field not aligned with the motion of its driving star.

\end{abstract}

\begin{keywords}
methods: numerical -- MHD  -- circumstellar matter -- stars: massive.
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sect:introduction}

Massive star formation is a \textcolor{black}{rare} event that strongly impacts the whole
Galactic machinery. These stars can release strong winds and ionizing radiation
which \textcolor{black}{shape their close surroundings into} beautiful billows of swept-up and
irradiated interstellar gas, that, in the case of a static or a slowly-moving
star, can produce structures such as the Bubble Nebula (NGC 7635) in the
constellation of Orion~\citep{moore_aj_124_2002}. The detailed study of the
circumstellar medium of these massive stars provides us an insight into
their internal physics~\citep{langer_araa_50_2012}, \textcolor{black}{it provides information on} their
intrinsic rotation~\citep{langer_ApJ_520_1999}, their envelope's
(in)stability~\citep{yoon_apj_717_2012} and allows us to understand the
properties of their close surroundings throughout their 
evolution~\citep{vanmarle_aa_460_2006,chita_aa_488_2008} and after their 
death~\citep{orlando_apj_678_2008,chiotellis_aa_537_2012}. \textcolor{black}{This
information is relevant for evaluating their feedback}, i.e. the amount of energy,
momentum and metals that massive stars inject into the interstellar medium (ISM)
of the Galaxy~\citep{vink_asp_353_2006}.

\textcolor{black}{In particular}, the bow shocks that develop around some fast-moving massive stars
ejected from their parent stellar clusters provide an  
opportunity to constrain both their wind and local ISM
properties~\citep{huthoff_aa_383_2002,meyer_mnras_439_2014}. Over the past decades,
stellar wind bow shocks have first been serendipitously noticed as bright [O{\sc
iii}] $\lambda \, 5007$ spectral line arc-like shapes and/or distorted
bubbles surrounding some massive stars having a particularly large space
velocity with respect to their ambient medium.
As a textbook example of such a bow shock, we refer the reader, e.g. 
to $\zeta$ Ophiuchi~\citep[][see Fig.~\ref{fig:obs} below]{gull_apj_230_1979}.
Further infrared observations, e.g. with the {\it Infrared Astronomical
Satellite}~\citep[{\it IRAS},][]{neugebauer_278_apj_1984} and 
the {\it Wide-Field Infrared Satellite Explorer}~\citep[ {\it WISE}, ][]{wright_aj_140_2010} facilities have made possible the compilation 
of catalogues of dozens of these bow shock nebulae~\citep{buren_apj_329_1988,vanburen_aj_110_1995,
noriegacrespo_aj_113_1997} and have motivated early numerical simulations
devoted to the parsec-scale circumstellar medium of moving
stars~\citep{brighenti_mnras_277_1995, brighenti_mnras_273_1995}. Recently,
modern facilities led to the construction of multi-wavelengths databases, see e.g.
the E-BOSS catalog~\citep{peri_aa_538_2012,2015arXiv150404264P} 
\textcolor{black}{ or the recent study of~\citet{kobulnicky_2016}}. Moreover, a
connection with high-energy astrophysics has been established, showing that
stellar wind bow shocks produce cosmic rays in the same way as the expanding shock waves of
growing supernova remnants do~\citep{valle_mnras_448_2015}.

It is the \textcolor{black}{discovery of bow shocks} around the historical stars
Betelgeuse~\citep{noriegacrespo_aj_114_1997} and
Vela-X1~\citep{kaper_apj_475_1997} that revived the interest of the scientific
community \textcolor{black}{regarding such circumstellar} structures generated by massive stars. The
fundamental study of~\citet{comeron_aa_338_1998} demonstrates that complex
morphologies can arise from massive stars' wind-ISM interactions. Bow shocks are subject to a 
wide range of shear-like and non-linear instabilities~\citep{blondin_na_57_1998} 
producing severe distortions of their overall forms, \textcolor{black}{which can only be 
analytically approximated}~\citep{wilkin_459_apj_1996} in the particular
situations of either a star moving in a relatively dense 
ISM~\citep{comeron_aa_338_1998} or a high-mass star hypersonically moving 
through the Galactic plane~\citep[][hereafter Paper~I]{meyer_2014b}. Tayloring 
numerical models to runaway red supergiant stars allows us to constrain 
the mass loss and local ISM properties of 
Betelgeuse~\citep{vanmarle_apj_734_2011,cox_aa_537_2012,mackey_apjlett_751_2012} or
IRC$-$10414~\citep{Gvaramadze_2013,meyer_mnras_439_2014}. \textcolor{black}{For} the sake of simplicity, these
models neglect the magnetisation of the ISM.

\textcolor{black}{
However, magnetic fields are an essential component of the ISM of the Galaxy, 
e.g. its large scale component has a tendency to be aligned with the galactic 
spiral arms~\citep{gaensler_apj_493_1998}. If the strength of the ISM magnetic field 
can reach up to several tenths of Gauss in the center of our 
Galaxy~\citep[see][]{rand_apj_343_1989, 
ohno_mnras_262_1993,opher_natur_462_2009,
shabala_mnras_405_2010}, it can be even stronger in the cold 
phase of the ISM~\citep{crutcher_apj_515_1999}. In particular, radio polarization 
measures of the magnetic field in the context of Galactic ionized supershells are 
reported to be $2$-$6\, \mu \rm G$ in~\citet{harvey_apj_736_2011}. This value is 
in accordance with previous estimates of the field strength in the warm phase of the 
ISM~\citep{troland_301_apj_1986} and was supported by hydrodynamical 
simulations~\citep{fiedler_apj_415_1993}.  
Such a background magnetic field should therefore be included in realistic models of 
circumstellar nebulae around massive stars. 
}

Numerical studies of magneto-hydrodynamical flows around an obstacle is approximated 
in the \textcolor{black}{plane-parallel} approach in~\citet{sterck_phpl_1998,
sterck_aa_343_1999}. A significant number of circumstellar structures, such as
the vicinity of our Sun~\citep{pogolerov_aa_321_1997}, 
planetary nebulae developing in the vicinity of intermediate-mass
stars~\citep{heiligman_mnras_191_1980} or supernova
remnants~\citep{rozyczka_274_MNRAS_1995} have been studied in such a two-dimensional
approach~\citep[see also][]{soker_apj_484_1997,pogolerov_aa_354_2000}. The 
presence of a weak magnetic field can inhibit the \textcolor{black}{growth rate of
shear} instabilities in the bow shocks around cool stars such as the runaway 
red supergiant Betelgeuse in the constellation of
Orion~\citep{vanmarle_aa_561_2014}. \textcolor{black}{We place our work} in this context, focusing 
on bow shocks generated by hot, fast winds of main-sequence massive stars.

In this study, we continue our investigation of the circumstellar medium of
runaway massive stars moving within the plane of the Milky 
way~\citep[Paper~I,][]{meyer_mnras_450_2015,meyer_mnras_459_2016}. As a
logical extension of them, we present magneto-hydrodynamical
models of a sample of some \textcolor{black}{of} the most common main-sequence, runaway massive
stars~\citep{kroupa_mnras_322_2001} moving at the most probable space
velocities~\citep{eldridge_mnras_414_2011}. We ignore any intrinsic inhomogenity
or turbulence in the ISM. Particularly, we assume an axisymmetric magnetisation
of the ISM surrounding the bow shocks in the spirit of~\citet{vanmarle_aa_561_2014}. We concentrate our
efforts on an initially $20\, \rm M_{\odot}$ star, however, we also consider bow
shocks generated by lower and higher initial mass stars. This project
principally differs from Paper~I because \textcolor{black}{of} (i) the inclusion of an ISM background
\textcolor{black}{magnetic field leads to anisotropic heat conduction}~\citep[see, e.g.][]{balsara_mnras_386_2008} and (ii) our study does not
concentrate on the \textcolor{black}{secular} stellar wind evolution of our bow-shock-producing stars. Note that our
study introduces a reduced number of representative models due to the high
numerical cost of the magneto-hydrodynamical simulations.  
\textcolor{black}{
Following~\citet{acreman_mnras_456_2016}, we additionally appreciate the effects of the ISM magnetic field on the 
bow shocks with the help of radiative transfer calculations of dust continuum emission. 
}

This paper is organised as follows. We start in Section 2 with a review of the
physics included in our models for both the stellar wind and the ISM. We also
recall the adopted numerical methods. Our models of bow shocks generated by
main-sequence, runaway massive stars moving in a magnetised medium are presented
together with a discussion of their morphology and internal structure in Section
3. We detail the emission properties of our bow shocks and discuss their observational 
implications in Section 4. Finally, we formulate our conclusions in Section 5.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Method}
\label{sect:methods}

In the present section, we briefly summarise the numerical methods and
microphysics utilised to produce magneto-hydrodynamical bow shock models of
the circumstellar medium surrounding hot, runaway massive stars.

\subsection{Governing equations}
\label{sect:eq}

We consider a magnetised flow past a source of hot, \textcolor{black}{ionized and magnetized} stellar wind. 
The dynamics are described by the ideal equations of 
magneto-hydrodynamics and the dissipative character of the 
thermodynamics originates from the treatment of the gas with heating and losses 
by optically-thin radiation together with electronic heat conduction. 
These equations are,
%
\begin{equation}
	   \frac{\partial \rho}{\partial t}  + 
	   \bmath{\nabla}  \cdot \big(\rho\bmath{v}) =   0,
\label{eq:mhdeq_1}
\end{equation}
%
\begin{equation}
	   \frac{\partial \bmath{m} }{\partial t}  + 
           \bmath{\nabla} \cdot \Big( \bmath{m} \otimes \bmath{v}  + \bmath{B} \otimes \bmath{B} + \bmath{\hat{I}}p_{\rm t} \Big) 
            =   \bmath{0},
\label{eq:mhdeq_2}
\end{equation}
%
\begin{equation}
	  \frac{\partial E }{\partial t}   + 
	  \bmath{\nabla} \cdot \Big( (E+p_{\rm t})\bmath{v}-\bmath{B}(\bmath{v}\cdot\bmath{B}) \Big)  = \zeta(T,\rho,\mu),
\label{eq:mhdeq_3}
\end{equation}
%
and,
%
\begin{equation}
	  \frac{\partial \bmath{B} }{\partial t}   + 
	  \bmath{\nabla} \cdot \Big( \bmath{v}  \textcolor{black}{\otimes} \bmath{B} - \bmath{B} \textcolor{black}{\otimes} \bmath{v} \Big)  =
	  \bmath{0},
\label{eq:mhdeq_4}
\end{equation}
%
where $\rho$ and $\bmath{v}$ are the mass density and the velocity of the
plasma. In the relation of momentum conservation Eq.~(\ref{eq:mhdeq_2}), the
quantity $\bmath{m}=\rho\bmath{v}$ is the linear momentum of a gas element,
$\bmath{B}$ the magnetic field, $\bmath{\hat{I}}$ the \textcolor{black}{identity matrix} and,  
%
\begin{equation}
	  p_{\rm t}  =	p + \frac{ \bmath{B} \cdot \bmath{B} }{2},
\label{eq:pres}
\end{equation}
%
is the total pressure of the gas, i.e. the sum of its thermal component $p$ 
and its magnetic contribution $(\bmath{B} \cdot \bmath{B})/2$, respectively. 
Eq.~(\ref{eq:mhdeq_3}) describes the conservation of the total energy of the gas, 
%
\begin{equation}
	E = \frac{p}{(\gamma - 1)} + \frac{ \bmath{m} \cdot \bmath{m} }{2\rho} + \frac{ \bmath{B} \cdot \bmath{B} }{2},
\label{eq:energy}
\end{equation}
%
where $\gamma$ is the adiabatic index, \textcolor{black}{which is taken to be $5/3$}, i.e. we assume 
an ideal gas. The right-hand source term $\zeta(T,\rho,\mu)$ in
Eq.~(\ref{eq:mhdeq_3}) represents (i) the heating and the losses by
optically-thin radiative processes and (ii) the heat transfers by anisotropic
electronic thermal conduction (see Section~\ref{ssect:microphysics}). Finally,
Eq.~(\ref{eq:mhdeq_4}) is the induction equation and governs the time evolution
of the vector magnetic field $\bmath{B}$. The relation, 
%
\begin{equation}
	  c_{\rm s} = \sqrt{ \frac{\gamma p}{\rho} },
\label{eq:cs}
\end{equation}
%
closes the system Eq.(\ref{eq:mhdeq_1})$-$(\ref{eq:mhdeq_4}), where $c_{\rm
s}$ denotes the adiabatic speed of sound.

\subsection{Boundary conditions and numerical scheme}
\label{sect:scheme}

We solve the above described system of equations
Eqs.~(\ref{eq:mhdeq_1})$-$(\ref{eq:cs}) using the open-source {\sc pluto}
code\footnote{http://plutocode.ph.unito.it/}~\citep{mignone_apj_170_2007,
migmone_apjs_198_2012} on a uniform two-dimensional grid covering a rectangular
computational domain in a cylindrical frame of reference $(O; R, z)$ of origin
$O$ and symmetry axis about $R=0$. The grid $[O;R_{\rm max}]\times[-z_{\rm
min};z_{\rm max}]$ where $R_{\rm max}$, $-z_{\rm min}$ and $z_{\rm max}$ are the
upper and lower limits of the $OR$ and $Oz$ directions, respectively, which are
discretised with $N_{\rm R}=2N_{\rm z}=1000$ cells such that the grid resolution
is $\Delta_R=\Delta_z=R_{\rm max}/N_{\rm R}$. Learning from previous bow shock
models~\citep{comeron_aa_338_1998,vanmarle_aa_460_2006}, we impose inflow
boundary conditions corresponding to the stellar motion at $z=z_{\rm max}$
whereas outflow boundaries are set at $R=R_{\rm max}$ and $z=-z_{\rm min}$.
Moreover, the stellar wind is modelled setting inflow boundaries conditions
centered around the origin (see Section~\ref{sect:ism}).

We integrate the system of partial differential equations within the eight-wave
formulation of the magneto-hydrodynamical Eqs.~(\ref{eq:mhdeq_1})$-$(\ref{eq:cs}),
using a cell-centered representation consisting in evaluating $\rho$,
$\bmath{m}$, $E$ and $\bmath{B}$ using the barycenter of the cells (see
section 2 of Paper~I). This formulation, used together with the \textcolor{black}{Harten-Lax-van
Leer approximate Riemann solver~\citep{hll_ref}}, conserves the divergence-free condition
$\bmath{\nabla} \cdot \bmath{B} = \bmath{0}$. The method is a second order,
unsplit, time-marching algorithm scheme controlled by the Courant-Friedrich-Levy
parameter initially set to $C_{\rm cfl}=0.1$. The gas cooling and heating
rates are linearly interpolated from tabulated cooling curves (see
Section~\ref{ssect:microphysics}) and the corresponding rate of change is 
subtracted from the \textcolor{black}{total} energy $E$. The parabolic term of
heat conduction is integrated with the Super-Time-Stepping
algorithm~\citep{alexiades_cnme_12_1996}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Gas microphysics}
\label{ssect:microphysics}

The source term $\zeta(T,\rho,\mu)$ in Eq.~(\ref{eq:mhdeq_3}) represents the non-ideal 
thermodynamics processes that we take into account, and reads, 
%
\begin{equation}
      \zeta(T,\rho,\mu) = \itl{\Phi}(T,\rho) + \bmath{\nabla} \cdot \bmath{{F}_{\rm c}}
\label{eq:terms}
\end{equation}
%
where $\itl{\Phi}(T,\rho)$ is a function that stands for the processes by 
optically-thin radiation where, 
%
\begin{equation}
	T =  \mu \frac{ m_{\mathrm{H}} }{ k_{\rm{B}} } \frac{p}{\rho},
\label{eq:temperature}
\end{equation}
%
is the gas temperature, with $\mu=0.61$ the mean molecular 
weight of the gas, $k_{\rm{B}}$ the Boltzmann constant 
and $m_{\rm H}$ the proton mass, respectively. The gain and losses by optically-thin 
radiative processes are taken into account via the following law,
%
\begin{equation}  
	 \itl \Phi(T,\rho)  =  n_{\mathrm{H}}\itl{\Gamma}(T)   
		   		 -  n^{2}_{\mathrm{H}}\itl{\Lambda}(T),
\label{eq:dissipation}
\end{equation}
%
where $\itl{\Lambda}(T)$ and $\itl{\Gamma}(T)$ are the rate of change of the gas 
internal energy induced by heating and cooling as a function of $T$, respectively, 
and where $n_{\mathrm{H}}=\rho/\mu (1+\chi_{\rm He,Z}) m_{\mathrm{H}}$ is the 
hydrogen number density with $\chi_{\rm He,Z}$ the mass fraction of the coolants heavier 
than hydrogen. Details about the processes included into the cooling $\Lambda(T)$ 
and heating $\Gamma(T)$ laws are given in section 2 of Paper~I.

The divergence term in the source function in Eq.~(\ref{eq:terms}) represents 
the anisotropic heat flux, 
%
\begin{equation}
      \bmath{{F}_{\rm c}} = \kappa_{||} \hat{\bmath{b}} \Big(  \hat{\bmath{b}} \cdot \bmath{ \nabla } T  \Big) + \kappa_{\perp} \Big( \bmath{ \nabla } T  -  \hat{\bmath{b}} \cdot \bmath{ \nabla } T  \Big),
\label{eq:tc}
\end{equation}
%
where $\hat{\bmath{b}}=\bmath{B}/||\textcolor{black}{\bmath{B}}||$ is the magnetic field unit vector. It is
calculated through the interface of the nearest neighbouring cells in the whole
computational domain according to the temperature difference $\Delta T$ and to
the local field orientation $\hat{\bmath{b}}$~\citep[\textcolor{black}{see appendix of}][]{migmone_apjs_198_2012}.
The coefficients $\kappa_{||}$ and $\kappa_{\perp}$ are the heat coefficients
along the directions parallel and normal to the local magnetic field streamline,
respectively.   Along the direction of the local magnetic field, 
%
\begin{equation}
      \kappa_{||}=K_{||} T^{5/2},
      \label{fig:eq_kappa_par}
\end{equation}
%
with,
%
\begin{equation}
      K_{||} =  \frac{ 1.84 \times 10^{-5} }{ \ln( \mathcal{L} ) }\, \rm erg\, \rm s^{-1}\, \rm K^{-1}\, \rm cm^{-1},
      \label{fig:eq_kappa}
\end{equation}
%
where $\ln( \mathcal{L} ) = 29.7 + \ln ( T / 10^{6}\sqrt{n}) $ is the Coulomb
logarithm, with $n$ the gas total number density~\citep{spitzer_1962}. The heat
conduction coefficients satisfy $\kappa_{\perp}/\kappa_{||} \approx 10^{-16} \ll 1$ for the
densities that we
consider~\citep{parker_1963_book,velazquez_apj_601_2004,balsara_mnras_386_2008,
orlando_apj_678_2008}. The value of $\textcolor{black}{\bmath{{F}_{\rm c}}}$ varies between the
classical flux in Eq.~(\ref{eq:tc}) and the saturated conduction
regime~\citep{balsara_mnras_386_2008} which limits the heat flux to, 
%
\begin{equation}
    F_{\rm sat} = 5 \phi \rho c_{\rm iso}^{3},
    \label{fig:eq_sat}
\end{equation}
%
for very large temperature gradients (\textcolor{black}{$\ge\, 10^{6}\, \rm K\, \rm pc^{-1}$}), with 
$ c_{\rm iso} = p/\rho$ the isothermal speed of sound and $\phi<1$ a 
free parameter that we set to the typical value of $0.3$~\citep{cowie_apj_211_1977}.

\begin{table*}
	\centering
	\caption{
	\textcolor{black}{
	 Stellar wind parameters at the beginning of the simulations, at a time $t_{\rm start}$ 
	 after the beginning of the zero-age main-sequences of the star.
	 Parameter $M_{\star}$ (in $\rm M_{\odot}$) is the initial mass of the star, $L_{\star}$ 
	 the stellar luminosity (in $\rm L_{\odot}$), $\dot{M}$ 
	 its mass loss and $v_{\rm w}$ the wind velocity, see also table~1 of~\citet{meyer_mnras_459_2016}.
	 }   
	 }
	\begin{tabular}{ccccccc}
%	\hline
	\hline
	$M_{\star}\, (\rm M_{\odot})$  &  $t_{\mathrm{ start}}\, (\rm Myr)$
				   &   $\textcolor{black}{\log(L_{\star}/\rm L_{\odot})}$                              
			           &   $\log(\dot{M}/\rm M_{\odot}\, \rm yr^{-1})$
			           &   $v_{\rm w}\, (\mathrm{km}\, \mathrm{s}^{-1})$			           
			           &   $T_{\rm eff}\, (\mathrm{K})$
			\\ \hline   
	$10$ &  $5.0$  &  $3.80$ 		    &  $-9.52$   & $1082$ & $25200$         \\        
	$20$ &  $3.0$  &  $4.74$                    &  $-7.38$   & $1167$ & $33900$         \\        
  	$40$ &  $0.0$  &  $5.34$  	            &  $-6.29$   & $1451$ & $42500$         \\ 
	%    
	\hline 
	\end{tabular}
\label{tab:wind_para}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Setting up the stellar wind}
\label{sect:ism}

We impose the stellar wind at the surface of a sphere of 
radius $20\Delta z\, \rm pc$ centered into the origin $O$ with 
wind material. Its density is, 
%
\begin{equation}
	\rho_{w} = \frac{ \dot{M} }{ 4\pi r^{2} v_{\rm w} },
\label{eq:wind}
\end{equation}
%
where $\dot{M}$ is the star's mass-loss rate and $r$ the distance to the origin 
$O$. We interpolate the wind parameters from stellar evolution models of 
non-rotating massive stars with solar metallicity that we used for previous 
studies, see Paper~I. 
\textcolor{black}{
Our stellar wind models are have been generated with the stellar evolution code 
described in~\citet{heger_apj_626_2005} and subsequently updated 
by~\citet{yoon_443_aa_2005,petrovic_aa_435_2005} and~\citet{brott_aa_530_2011a}.
It utilises the mass-loss prescriptions 
of~\citet{kudritzki_aa_219_1989} for the main-sequence phase of our massive 
stars and of~\citet{dejager_aas_72_1988} for the red supergiant phase. 
Despite of the fact that our 
wind models report the marginal evolution of 
main-sequence winds, see Paper~I, they remain quasi-constant during the part of 
the stellar evolution that we follow. 
%Our stellar masses $M_{\star}$, 
%luminosities $L_{\star}$ and effective temperature $T_{\rm eff}$ are consistent 
%with~\citet{brott_aa_530_2011a} whereas the differences  concern (i) their duration 
%since ours include the star's evolution through the red supergiant phase that we 
%investigated in Paper~I and (ii) their stellar velocities, which are slightly lower.  
%partly because of a typo in the conversion factor between escape and wind velocity 
%$v_{\rm w}$ in Eq.~2 of~\citet{eldridge_mnras_367_2006}, where the $\beta(T)$ 
%factor should be squared. 
%Nevertheless, our values 
%of $v_{\rm w}$ still remain within the orders of magnitude of, e.g. late O 
%tars~\citep{martins_aa_468_2007} or weak-winded stars~\citep{comeron_aa_338_1998}. 
%urthermore, stellar evolution of massive stars 
%s governed by physical mechanisms neglected by~\citet{brott_aa_530_2011a} such as 
%the presence of low-mass companions~\citep{sana_sci_337_2012}, which in its turn 
%affect their properties~\citep{paxton_apjs_192_2011,marchant_aa_588_2016}. 
We refer the reader 
interested in a graphical representation of the utilised wind models to the fig~3 
of Paper~I, while we report the wind properties at the beginning of our simulations 
in our Table~\ref{tab:wind_para}.  
}
\textcolor{black}{
Note that our adopted values for the stellar wind velocity belong to the lower 
limit of the range of validity for stellar winds of OB stars (see below in 
Section~\ref{sect:physics33}).
}

Since we assume a spherically symmetric stellar wind density, thermal pressure and 
velocity profiles, we use the Parker prescription~\citep{parker_paj_128_1958} to model 
the magnetic field in the stellar wind. It consists of a radial component of the field, 
%
\begin{equation}
	B_{r} = B_{\star} \Big( \frac{R_{\star}}{r} \Big)^{2},
\label{eq:Bstellarfield_1}
\end{equation}
%
where $B_{\star}$ and $R_{\star}$ are the stellar surface magnetic field and the stellar radius, 
respectively, and of a toroidal component, which, in the case of a non-rotating star, this 
reduces to $B_{\phi} = 0$. The $\propto 1/r^{2}$ radial dependence of
Eq.~(\ref{eq:Bstellarfield_1}) makes the strength
of the stellar magnetic field almost negligible at the wind termination shock
that is typically about a few tenths of $\rm pc$ from the star that we study 
(Paper~I). However, imposing a null
magnetic field in the stellar wind region would let the direction of the heat
flux $\bmath{{F}_{\rm c}}$ undetermined in the region of (un)shocked wind 
material of the bow shock, see magnetic field unit vector $\hat{\bmath{b}}$ 
in the right-hand side of Eq.~(\ref{eq:tc}). Note that, given their analogous radial 
dependance on $r$, stellar wind and stellar magnetic field are 
similarly implemented into our axisymmetric simulations. 
In these simulations the stellar surface magnetic 
field is set to $B_{\star} \simeq 1.0\,\rm kG$~\citep{donati_mnras_333_2002} 
at $R_{\star}=3.66\, R_{\odot}$~\citep{brott_aa_530_2011a} where $R_{\odot}$ 
is the solar radius.

\subsection{Setting up the ISM}
\label{sect:medium}

Our runaway stars are moving through the warm ionised phase of the ISM, i.e.
we assume that they run in their own $\HII$ region inside \textcolor{black}{which the gas is considered 
as} homogeneous, laminar and fully ionised fluid. The ISM composition 
assumes solar metalicity~\citep{lodders_apj_591_2003}, with 
$n_{\rm H}=0.57\, \mathrm{cm}^{-3}$~\citep{wolfire_apj_587_2003} and
with $T_{\rm ISM}\approx 8000\, \rm K$, initially. 
The model is a moving star within an ISM at rest. We solve the equations 
of motion \textcolor{black}{in} the frame in which the star is at rest and, hence, 
the ISM moves with $v_{\mathrm{ISM}}=-v_{\star}$, 
where $v_{\star}$ is the bulk motion of the star. 
The gas in the computational domain is 
evaluated with the cooling curve for photoionised gas described in fig.~4a of Paper~I. 
\textcolor{black}{In particular}, our initial conditions neglect the possibility that a bow shock might trap the ionising front 
of the $\HII$ region (see section~2.4 of Paper~I for an extended discussion of 
the assumptions underlying our method for modelling bow shocks from hot massive stars). 
%
Additionally, an axisymmetric magnetic field $\bmath{B}=-B_{\rm ISM}\, \bmath{\hat{z}}$ field 
is imposed over the whole computational domain, with $B_{\rm ISM}>0$ its 
strength and $\bmath{\hat{z}}$ the unit vector along the $Oz$ direction. Finally, 
our simulations trace the respective proportions of ISM gas with respect to the 
wind material using a passive scalar tracer according to the advection equation,
%
\begin{equation}
	\frac{\partial (\rho Q) }{\partial t } +  \bmath{ \nabla } \cdot  ( \bmath{v} \rho Q) = 0,
\label{eq:tracer}
\end{equation}
%
where $Q$ is a passive tracer which initial value is $Q(\bmath{r})=1$ for the wind material and 
$Q(\bmath{r})=0$ for the ISM gas, respectively.

\subsection{Simulation ranges}
\label{sect:models}

We first focus on a baseline bow shock generated by an initially 
$20\, \rm M_{\odot}$ star moving with a velocity $v_{\star}=40\, \rm km\, \rm s^{-1}$ in
the Galactic plane of the Milky Way \textcolor{black}{whose magnetic field} is assumed to be $B_{\rm
ISM}=7\, \mu \rm G$~\citep{draine_piim_bool_2011}. Then, we consider models with velocity $v_{\star}=20$ to 
$70\, \rm km\, \rm s^{-1}$, \textcolor{black}{explore the effects of a magnetisation
of $B_{\rm ISM}=3.5\, \mu \rm G$}, and carry out simulations 
of initially $10$ and $40\, \rm M_{\odot}$ stars 
moving at velocities $v_{\star}=40$ and $70\, \rm km\, \rm s^{-1}$, respectively. 
We investigate the effects of the ISM magnetic field carrying out a couple of 
\textcolor{black}{additional purely hydrodynamical simulations}, as comparison runs. All our 
simulations are started at a time about $4.5\, \rm Myr$ 
after the zero-age main-sequence phase of our stars and are run at least 
four crossing times $|z_{\rm max}-z_{\rm min}|/v_{\star}$ of the gas through 
the computational domain, such that the system \textcolor{black}{reaches} a steady or quasi-stationary   
state in the case of a stable or unstable bow shock, respectively.

\textcolor{black}{We label our magneto-hydrodynamical simulations concatenating 
the values of the initial mass $M_{\star}$ of the moving
star (in $\rm M_{\odot}$), its bulk motion} $v_{\star}$ (in $\rm km\,
\rm s^{-1}$) and the included physics ``Ideal'' for dissipativeless simulations,
``Cool" if the model includes heating and losses by optically-thin radiative
processes, ``Heat" for heat conduction and ``All" if cooling, heating and heat 
conduction are taken into account together). Finally, the labels inform about the
strength of the ISM magnetic field. We distinguish our magneto-hydrodynamical runs
from our previously published hydrodynamical studies (Paper~I) adding the prefix 
``HD" and ``MHD" to the simulations labels of our hydrodynamical and 
magneto-hydrodynamical simulations, respectively. All the informations 
relative to our models are summarised in Table~\ref{tab:ms}.

\begin{table*}
	\centering
	\caption{
	 Nomenclature and grid parameters used in our (magneto-)hydrodynamical
simulations. The quantities $M_{\star}$ (in $M_{\odot}$) and
$v_{\star}$ (in $\mathrm{km}\, \mathrm{{s}^{-1}}$) are the initial mass of the
stars and their space velocity, respectively, whereas $B_{\rm ISM}$ (in $\mu \rm G$) is 
the strength of the ISM magnetic field. Parameters $\it \Delta$,
$z_{\mathrm{min}}$ and $R_{\mathrm{max}}$ are the resolution of the uniform grid
(in $\mathrm{pc}\, \mathrm{{cell}^{-1}}$) and the lower and upper limits of the 
domain along the $\rm R$-axis and $\rm z$-axis (in $\mathrm{pc}$), respectively.  The
last column contains the physics included in each simulation. Heat conduction (HC) 
refers to isotropic thermal conduction in the case of an hydrodynamical (HD) simulation and 
to anisotropic thermal conduction in the case of an magneto-hydrodynamical (MHD) simulation, 
respectively. 
	 }
	\begin{tabular}{lccccccc}
%	\hline
	\hline
	${\rm {Model}}$ &   $M_{\star}\, (M_{\odot})$                              
 			&   $v_{\star}\, (\mathrm{km}\, \mathrm{s}^{-1})$
			&   $B_{\rm ISM}\, (\mu \rm G)$ 
			&   $\itl{\Delta}\, ( 10^{-3}\, \mathrm{pc}\, \mathrm{cell}^{-1})$ 
			&   $z_{\mathrm{min}}\, (\mathrm{pc})$ 
			&   $R_{\mathrm{max}}\, (\mathrm{pc})$
			&   $\rm Included\, microphysics$
			\\ \hline   
	HD2040Ideal      &  $20$  &  $40$ & $-$   &  $8.0$   &  $-2.0$     &  $~8.0$      & HD, adiabatic  \\             
	HD2040Cool       &  $20$  &  $40$ & $-$   &  $8.0$   &  $-2.0$     &  $~8.0$      & HD, cooling, heating  \\        
	HD2040Heat       &  $20$  &  $40$ & $-$   &  $8.0$   &  $-2.0$     &  $~8.0$      & HD, HC  \\ 
	HD2040All        &  $20$  &  $40$ & $-$   &  $8.0$   &  $-2.0$     &  $~8.0$      & HD, cooling, heating, HC  \\             
	MHD2040IdealB7   &  $20$  &  $40$ & $7.0$   &  $8.0$   &  $-2.0$     &  $~8.0$   & MHD   \\        
	MHD2040CoolB7    &  $20$  &  $40$ & $7.0$   &  $8.0$   &  $-2.0$     &  $~8.0$   & MHD, cooling, heating  \\  
	MHD2040HeatB7    &  $20$  &  $40$ & $7.0$   &  $8.0$   &  $-2.0$     &  $~8.0$   & MHD, HC  \\         
	MHD2040AllB7     &  $20$  &  $40$ & $7.0$   &  $8.0$   &  $-2.0$     &  $~8.0$   & MHD, cooling, heating, HC  \\     
	% 
	MHD1040AllB7     &  $10$  &  $40$ & $7.0$   &  $3.0$   &  $-2.0$     &  $~6.0$   & MHD, cooling, heating, HC  \\         	
	MHD2020AllB7     &  $20$  &  $20$ & $7.0$   &  $6.0$   &  $-3.0$     &  $12.0$  & MHD, cooling, heating, HC  \\         
	MHD2040AllB3.5   &  $20$  &  $40$ & $3.5$   &  $8.0$   &  $-2.0$     &  $~8.0$   & MHD, cooling, heating, HC  \\  
	MHD2070AllB7     &  $20$  &  $70$ & $7.0$   &  $1.2$   &  $-1.0$     &  $~3.0$   & MHD, cooling, heating, HC  \\     
	MHD4070AllB7     &  $40$  &  $70$ & $7.0$   &  $1.6$   &  $-4.0$     &  $16.0$  & MHD, cooling, heating, HC  \\
	\hline    
%	\hline 
	\end{tabular}
\label{tab:ms}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results and discussion}
\label{sect:results}

This section presents the magneto-hydrodynamical simulations carried out in the
context of our Galactic, ionizing, runaway massive stars. We detail the
effects of the included microphysics on a baseline bow shock model,  
we discuss the morphological differences between our hydrodynamical and 
magneto-hydrodynamical simulations and we consider the 
effects of the adopted stellar wind models. 
Finally, review the limitations of the model.

\subsection{Bow shock thermodynamics}
\label{sect:physics1}

\subsubsection{Effects of the included physics: hydrodynamics}
\label{sect:physics1}

In Fig.~\ref{fig:physics}, we show the gas density field in a series of bow
shock models of our initially $20\, \rm M_{\odot}$ star moving with velocity
$40\, \rm km\, \rm s^{-1}$ through a medium of ISM background density $n_{\rm
H}=0.59\, \rm cm^{-3}$ and of magnetic field strength $B_{\rm ISM}=7\, \mu \rm
G$. The crosses indicate the position of the moving star. 
The figures correspond to a time about $5\, \rm Myr$ after the beginning of
the main-sequence phase of the star. The stellar wind and ISM properties are
the same for all figures, only the included physics is different for each models
(our Table~\ref{tab:ms}). Left-hand panels are hydrodynamical simulations whereas  
right-hand panels are magneto-hydrodynamical simulations, respectively. 
From top to bottom, the included thermodynamic processes are adiabatic (a), 
take into account optically-thin radiative processes of the gas (b), heat 
transfers (c) or both (d). The black dotted lines are the contours 
$Q(\bmath{r})=1/2$ which trace the discontinuity between the stellar wind 
and the ISM gas. The streamlines (a-c) and vector velocity field (d) 
highlight the penetration of the ISM gas into the different layers 
of the bow shock.

\begin{figure*}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_hdadia_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_mhdideal_legend.eps}
	\end{minipage} \\
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_hdcool_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_mhdcool_legend.eps}
	\end{minipage} \\
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_hdheat_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_mhdheat_legend.eps}
	\end{minipage} \\ 
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_hdall_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.48\textwidth}
 		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_mhdall_legend.eps}
	\end{minipage} \\ 	
	\caption{   
	Changes in the morphology of a stellar wind bow shock with variation of
the included physics. Figures show gas number density plotted with a density
range from $10^{-5}$ to $5\, \rm cm^{-3}$ in the logarithmic scale for an
initially $20\, \rm M_{\odot}$ star moving with velocity $40\, \rm km\, \rm
s^{-1}$. Left-hand panels are the hydrodynamical models whereas right-hand
panels are the magneto-hydrodynamical models with $B_{\rm ISM}=7\, \rm \mu G$.
The first line of panels shows adiabatic (a) and ideal magneto-hydrodynamical
(e) models, respectively. The second line of panels plots models with optically-thin 
radiative processes (b,f), the third line shows models including thermal (an-)isotropic
conduction (c,g) and the last line plots models models including cooling,
heating and (an-)isotropic thermal conduction (d,h). The nomenclature of the
models follows our Table~\ref{tab:ms}. For
each figure the dotted thick line traces the material discontinuity, i.e. 
the interface of the wind/ISM regions, $Q(\bmath{r})=1/2$. The right part of each figure overplots ISM flow
streamlines, except panel (d) which explicitly plots the velocity 
field as white arrows over the whole computational domain. 
The crosses mark the position of the star. 
\textcolor{black}{ The R-axis represents the radial direction and the z-axis 
the direction of stellar motion (in $\rm pc$).}
Only a fraction of the computational domain is shown.
		 }
	\label{fig:physics}  
\end{figure*}

The internal structure of the bow shocks can be understood \textcolor{black}{by} comparing the timescales
associated to the different physical processes at work. The dynamical 
timescale represents the time interval it takes the gas to advect  
through a given layer of our bow shocks, i.e. the region of shocked 
ISM or the layer of shocked wind. It is defined as, 
%
\begin{equation}
t_{\mathrm{dyn}}=\frac{ \Delta l }{ v }, 
\label{eq:time_dyn}
\end{equation}
%
where $\Delta l$ is the characteristic lengthscale of the region of the bow shock 
measured along the $Oz$ direction and where $v$ is the gas velocity in the post-shock 
region of the considered layers. According to the Rankine-Hugoniot relations and taking 
into account the non-ideal character of our model, we should have 
$v \simeq v_{\star}/4$ in the shocked ISM and $v \simeq v_{\rm w}/4$ in the post-region at the 
forward shock and at the reverse shock, respectively.

The cooling timescale is defined as,  
%
\begin{equation}
t_{\mathrm{cool}} =  \frac{E_{\rm int}}{\dot{E_{\rm int}}}  = \frac{p}{(\gamma-1)\itl{\Lambda}(T) n_{\rm H}^{2}},  
\label{eq:time_cool}
\end{equation}
%
where $\dot{E_{\rm int}}$ is the rate of change of internal energy $E_{\rm int}$~\citep{orlando_aa_444_2005}. 
The heat conduction timescale measures the rapidity of heat transfer into the 
bow shock, and is given by, 
%
\begin{equation}
  t_{\rm heat} = \frac{7pl^{2}}{2(\gamma-1)\kappa(T)T}, 
\label{eq:time_heat}
\end{equation}
%
where $l$ is a characteristic length of the bow shock along which heat transfers take 
place. Measuring the density, 
pressure and velocity fields in our simulations, we evaluate and compare those quantities 
defined in Eqs.~(\ref{eq:time_dyn})-(\ref{eq:time_heat}) at both 
the post-shock regions at the forward and reverse shocks. 
Results for both the layers of shocked wind and shocked 
ISM material are given in Table~\ref{tab:ts}.

\begin{table}
	\centering
	\caption{
	Characteristics dynamical timescale $t_{\rm dyn}$, cooling timescale $t_{\rm cool}$ and thermal
conduction timescale $t_{\rm heat}$ (in $\rm Myr$) measured along the $Oz$ direction from our simulations
of our initially $20\, \rm M_{\odot}$ star moving velocity $40\, \mathrm{km}\,
\mathrm{s}^{-1}$ (see Fig.~\ref{fig:physics}a-h). We estimate the various
timescales in both the post-shock region at the forward shock (FS) and the
reverse shock (RS) of our bow shocks. The black hyphen indicate that the
corresponding physical process is not included in the models (our
Table~\ref{tab:ms}).  
	}
	\begin{tabular}{lccccccccc}
%	\hline
	\hline
	${\rm {Model}}$ &   $t_{\rm dyn}\, (\rm Myr)$                              
 			 &   $t_{\rm cool}\, (\rm Myr)$
			 &   $t_{\rm heat}\, (\rm Myr)$ 
			\\ \hline     
	HD2040Ideal (FS)     &  $2.5\times 10^{-2}$  &  $-$  &  $-$    \\             
	HD2040Ideal (RS)     &  $4.7\times 10^{-3}$  &  $-$  &  $-$    \\             
	HD2040Cool (FS)      &  $1.0\times 10^{-2}$  &  $4.5\times 10^{-3}$  &  $-$    \\        
	HD2040Cool (RS)      &  $3.7\times 10^{-3}$  &  $3.5\times 10^{+3}$  &  $-$    \\        
	HD2040Heat (FS)      &  $6.5\times 10^{-2}$  &  $-$                  &  $1.2\times 10^{+3}$    \\ 
	HD2040Heat (RS)      &  $1.3\times 10^{-2}$  &  $-$                  &  $1.2\times 10^{-4}$    \\ 
	HD2020All (FS)       &  $9.0\times 10^{-3}$  &  $5.1\times 10^{-3}$  &  $8.7\times 10^{+5}$    \\             
	HD2020All (RS)       &  $1.1\times 10^{-2}$  &  $2.5\times 10^{+1}$  &  $4.0\times 10^{-3}$    \\             
	MHD2040IdealB7 (FS)  &  $1.8\times 10^{-2}$  &  $-$  		       &  $-$    \\        
	MHD2040IdealB7 (RS)  &  $4.3\times 10^{-3}$  &  $-$                  &  $-$    \\        
	MHD2040CoolB7 (FS)   &  $1.1\times 10^{-1}$  &  $4.3\times 10^{-2}$  &  $-$    \\ 
	MHD2040CoolB7 (RS)   &  $2.0\times 10^{-3}$  &  $1.0\times 10^{+3}$  &  $-$    \\  	
	MHD2040HeatB7 (FS)   &  $1.0\times 10^{-2}$  &  $-$                  &  $1.1\times 10^{+25}$    \\         
	MHD2040HeatB7 (RS)   &  $6.7\times 10^{-3}$  &  $-$                  &  $5.5\times 10^{+9}$    \\         
	MHD2040AllB7 (FS)    &  $3.0\times 10^{-1}$  &  $3.4\times 10^{-3}$  &  $1.4\times 10^{+18}$    \\   
	MHD2040AllB7 (RS)    &  $2.3\times 10^{-3}$  &  $3.0\times 10^{+4}$  &  $5.4\times 10^{+7}$    \\ 	
	\hline    
%	\hline 
	\end{tabular}
\label{tab:ts}
\end{table}

Our hydrodynamical, \textcolor{black}{dissipation-free} bow shock model HD2040Ideal has a morphology
governed by the gas dynamics only (Fig.~\ref{fig:physics}a). It has a contact
discontinuity separating the outer region of cold shocked ISM from the inner 
region of hot shocked stellar wind, which are themselves bordered by the forward and reverse shocks,
respectively. There is no advection of ISM material into the wind region (see
the ISM gas streamlines in Fig.~\ref{fig:physics}a). The model HD2040Cool including 
cooling by optically-thin radiation has a considerably reduced layer of dense, 
shocked ISM gas caused by the rapid losses of internal energy 
($t_{\rm dyn} \gg t_{\rm cool}$, see timescales in our 
Table~\ref{tab:ts}). Its thinness favours 
the growth of Kelvin-Helmholtz instabilities and allows large eddies
to develop in the shocked regions (Fig.~\ref{fig:physics}b). 
The layer of hot gas is isothermal because the regular wind 
momentum input at the reverse shock prevents it from cooling and 
it therefore conserves its hot temperature ($t_{\rm cool} \gg t_{\rm dyn}$) 
whereas the distance between the star and the contact discontinuity, 
%
\begin{equation}
	R(0) = \sqrt{ \frac{\dot{M}v_{\mathrm{w}}}{4\pi\rho_{\mathrm{ISM}}v_{\star}^{2} } },
\label{eq:Ro}
\end{equation}
%
does not evolve~\citep{wilkin_459_apj_1996}.

\textcolor{black}{
The model HD2040Heat takes into account thermal conduction which is isotropic in the 
case of the absence of magnetic field. The heat flux reads,} 
%
\begin{equation}
     \bmath{{F}_{\rm c}} = \kappa \bmath{ \nabla } T, 
\label{eq:tciso}
\end{equation}
%
and transports internal energy from the reverse shock to the contact
discontinuity ($t_{\rm dyn} \gg t_{\rm heat}$) which in its turn splits 
the dense region into a hot ($t_{\rm dyn} \gg t_{\rm heat}$) and a cold layer of shocked ISM
gas ($t_{\rm dyn} \ll t_{\rm heat}$), respectively. 
This modifies the penetration of ISM gas into the bow shock and
causes the region of shocked wind to shrink to a narrow layer of material close to the
\textcolor{black}{reverse shock} (Fig.~\ref{fig:physics}c). Not surprisingly, the
model with both cooling and conduction HD2040All (Fig.~\ref{fig:physics}d)
presents both the thermally split region of shocked ISM ($t_{\rm dyn} \ll t_{\rm heat}$, $t_{\rm dyn} \gg t_{\rm cool}$, 
$t_{\rm cool} \ll t_{\rm heat}$) and a reduced layer
of shocked wind material ($t_{\rm dyn} \gg t_{\rm heat}$, 
$t_{\rm dyn} \ll t_{\rm cool}$, $t_{\rm cool} \gg t_{\rm heat}$) that reorganises the internal structure of the bow
shock together with a dense shell of cool ISM gas (see the also discussion in Paper~I).  
For the sake of clarity Fig.~\ref{fig:physics}d overplots the gas velocity fields as white arrows 
which illustrate the penetration of ISM gas into the hot layer of the bow shock.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Effects of the included physics: magneto-hydrodynamics}
\label{sect:physics2}

We plot in the right-hand panels of Fig.~\ref{fig:physics} the ideal
magneto-hydrodynamical simulation of our initially $20\, \rm M_{\odot}$ star
moving with $v_{\star}=40\, \rm km\, \rm s^{-1}$ through a medium where the strength
of the magnetic field is $B_{\rm ISM}=7\, \mu \rm G$ (e) together with models
including cooling and heating by optically-thin radiation (f), anisotropic heat
conduction (g) and both (h). Despite of the fact that the overall morphology of
our magneto-hydrodynamical bow shock models is globally similar to the models
with $B_{\rm ISM}=0\, \mu \rm G$, a given number of significant changes relative
to both their shape and internal structure arise. Note that in the context of
our magneto-hydrodynamical models, $t_{\rm heat}$ represents the heat transfer
timescale normal to the fields lines.

\textcolor{black}{Our ideal magneto-hydrodynamical model has the typical structure 
of a stellar wind bow shock, with a region of shocked ISM gas surrounding the 
one of shocked wind gas. The contact discontinuity acts as a border between 
the two kind of material (Fig.~\ref{fig:physics}e). The model with cooling 
MHD2040CoolB7 has reduced but denser layer of ISM gas (Fig.~\ref{fig:physics}f) 
due to the rapid cooling time ($t_{\rm cool} \ll t_{\rm dyn}$). The magneto-hydrodynamical 
model with thermal conduction is similar to our model MHD2040IdealB7 since, due to  
his anisotropic character, heat transport are canceled across the magnetic field lines 
($t_{\rm heat} \ggg t_{\rm dyn}$). Note the boundary effect close to the apex 
along the $Oz$ direction as a result of the heat conduction along the 
direction of the ISM magnetic field lines (Fig.~\ref{fig:physics}g).  
Finally, our model with both processes has its dynamics governed by the cooling in the 
region of shocked ISM ($t_{\rm heat} \ggg t_{\rm dyn}$, $t_{\rm heat} \ggg t_{\rm cool}$, 
$t_{\rm cool} \ll t_{\rm dyn}$) and by the wind momentum in the region of shocked wind 
($t_{\rm heat} \ggg t_{\rm dyn}$, $t_{\rm heat} \ggg t_{\rm cool}$, $t_{\rm dyn} \ll t_{\rm cool}$).  
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Effects of the boundary conditions: stellar wind models}
\label{sect:physics33}

\textcolor{black}{
The shape of the bow shock generated around a runaway massive star in the warm 
phase of the ISM is a function of the respective strength of both the ISM ram 
pressure $\rho_{\rm ISM}v_{\star}^{2}$ and the stellar wind ram pressure 
$\rho_{\rm w}v_{\rm w}^{2}$, as seen in the frame of reference of the moving 
object~\citep[see explanations in][]{mohamed_aa_541_2012}. According to 
Eq.~(\ref{eq:wind}), $\rho_{w}=\dot{M} / 4\pi r^{2} v_{\rm w}$ which implies 
that $\rho_{\rm w}v_{\rm w}^{2} \propto \dot{M} v_{\rm w}$. In other words, in a 
given ambient medium and at a given peculiar velocity, the governing quantity 
in the shaping of such bow shock is $\dot{M}\rm v_{w}$ and its stand-off 
distance $R(0)$ goes as $\sqrt{ \dot{M} v_{w} }$, see Eq.~(\ref{eq:Ro}). 
Nevertheless, if the production of stellar evolution models depends on specific 
prescriptions relative to $\dot{M}$ that are consistently used through the 
calculations~\citep[in our case the recipe of][]{kudritzki_aa_219_1989}, 
the estimate of the wind velocity is posterior to the calculation of the 
stellar structure and it does not influence $\dot{M}$, $T_{\rm eff}$ or 
$L_{\star}$. 
}

\begin{figure}
	\begin{minipage}[b]{ 0.47\textwidth}
		\includegraphics[width=1.0\textwidth]{./plot_brott.eps}
	\end{minipage} \\ 	
	\caption{   
	\textcolor{black}{
	Comparison of the quantity $\dot{M}\rm v_{w}$ between our weak-winded 
	stars and the non-rotating Galactic models of~\citet{brott_aa_530_2011a}. 
	The grey zone of the plot corresponds to the mass regime of massive stars ($M_{\star}\ge8\,\rm M_{\odot}$). 
	Solid and dotted lines are lines of constant $\dot{M} v_{w}$ and $M_{\star}$, respectively.
	}
		 }
	\label{fig:brot}  
\end{figure}

\textcolor{black}{
The manner to calculate $\rm v_{w}$ is not unique~\citep{castor_apj_195_1975,kudritzki_aa_219_1989,kudritzki_aa_38_2000, 
eldridge_mnras_367_2006} and it can also be assumed to characteristic 
values for the concerned stars~\citep{comeron_aa_338_1998,vanmarle_aa_561_2014,vanmarle_2015,
acreman_mnras_456_2016}. In our study, the wind velocities are in the lower 
limit of the range of validity for the main-sequence massive stars that we 
consider, nonetheless, they still remain within the order 
of magnitude of, e.g. late O stars~\citep{martins_aa_468_2007} or weak-winded 
stars~\citep{comeron_aa_338_1998}. Furthermore, the evolution of massive stars 
are governed by physical mechanisms strongly influencing their feedback such 
as the presence of low-mass companions~\citep{sana_sci_337_2012}, \textcolor{black}{which 
are neglected in our stellar evolution models. Produced before their zero-age 
main-sequence phase, e.g. by fragmentation of the accretion disk that surrounds 
massive protostars~\citep{2016arXiv160903402M}, those dwarf stars entirely 
modify the evolution of massive stars and consequently affect their wind 
properties~\citep{demink_aa_467_2007,demink_aa_497_2009,paxton_apjs_192_2011,marchant_aa_588_2016}}. 
}

\textcolor{black}{
Using wind velocities faster by a factor $\alpha$ would 
enlarge the bow shocks by a factor $\sqrt{\alpha}$ and, eventually, in the 
hydrodynamical case, favorise the growth of \textcolor{black}{instabilities} (cf.~Fig.~\ref{fig:physics}b). 
However, the results of our numerical study would be similar in the sense 
that the presence of the field essentially stabilises the nebulae and inhibits 
the effects of heat conduction (cf.~Fig.~\ref{fig:physics}a,h), 
reduces their size (Section~\ref{sect:titi}) and modifies, e.g.  
their infrared emission accordingly (see Section~\ref{sect:infrared}). 
In Fig.~\ref{fig:brot}, we compare our values of $\dot{M} v_{w}$ 
(Table~\ref{tab:wind_para}) with the non-rotating stellar evolutionary models 
published in~\citet{brott_aa_530_2011a}. We conclude that the 
bow shocks generated with our initially $10$, $20$ and $40\, \rm M_{\odot}$ 
weak-winded stellar models correspond to nebulae produced by 
initially $\approx10$, $\approx18$ and $\approx32\, \rm M_{\odot}$ standard massive stars 
at Galactic metallicity, respectively. Therefore, our models have full validity 
for this study of magnetized bow shock nebulae, albeit of lower zero-age 
main-sequence mass in the case of our heaviest runaway star. 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Hydrodynamics versus magneto-hydrodynamics}
\label{sect:physics3}

\subsubsection{The effects of the magnetic pressure}
\label{sect:titi}

The ISM magnetic pressure, \textcolor{black}{proportional to $\vec{B}_{\rm ISM}^{2}$}, 
dynamically compresses the region of shocked ISM gas such that the density in the
post-shock region at the forward shock slightly increases. Similarly, the shape
of the bow shock's wings of shocked ISM are displaced sidewards compare to our
model with $B_{\rm ISM}=0\, \mu \rm G$ (Fig.~\ref{fig:physics}a,e). The size
of the layer of ISM gas diminishes along the direction of motion of the moving star and the position of
the termination shock \textcolor{black}{sets} at a distance from the star where the wind ram
pressure equals the ISM total pressure decreases as measured along the $Oz$
axis. The effects of the cooling is standard in the sense that it makes the
region of shocked ISM thinner and denser, i.e. the position of the forward shock
decreases, together with the bow shock volume. The effects of heat conduction
are canceled ($t_{\rm dyn} \ll t_{\rm heat}$) in the direction \textcolor{black}{perpendicular} to the
field lines, i.e. in the direction perpendicular to the streamline collinear 
to both the reverse shock and the contact discontinuity.

\subsubsection{Stagnation point morphology and discussion in the context of plasma physics studies}
\label{sect:}

The topology at the apex of our magneto-hydrodynamical bow shock
(Fig.~\ref{fig:physics}h) is different from the traditional single-front bow
shock morphology (Fig.~\ref{fig:physics}d). \textcolor{black}{This can be discussed at the light 
of plasma physics studies~\citep{sterck_phpl_1998,sterck_aa_343_1999}. These 
works explore the formation of exotic shocks and discontinuities that affect 
the particularly dimpled apex of bow shocks generated by field-aligned flows around a conducting 
cylinder~\citep{sterck_phpl_1998}. They extended this result to bow shocks 
produced around a conducting sphere and showed} that the inflow 
parameter space leading to such structures is similar to plasma $\beta$ and 
\textcolor{black}{Alfv\' enic} Mach number values allowing the formation of so-called switch-on 
shocks~\citep{sterck_aa_343_1999}.

\begin{figure}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_hdall_B0_legend.eps}
	\end{minipage} \\
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_mhdall_Blow_B3.5_legend.eps}
	\end{minipage} \\
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_mhdall_B7_legend.eps}
	\end{minipage} \\  	
	\caption{
		\textcolor{black}{Models of} stellar wind bow shocks of our initially $20\, \rm
M_{\odot}$ star moving with velocity $v_{\star}=40\, \rm km\, \rm s^{-1}$ represented as a function of its ISM 
magnetic field strength, with $B_{\rm ISM}=0$ (a), $3.5$ (b) and $7.0\, \rm \mu G$ (c).  
		 }
	\label{fig:bfieldstrength}  
\end{figure}

Switch-on shocks are allowed when plasma $\beta$ of the inflowing material,
i.e. the ratio of the gas and magnetic pressures, which read,
%
\begin{equation}
	\beta = \frac{8\pi n k_{\rm B} T }{\bmath{B}_{\rm ISM} \cdot \bmath{B}_{\rm ISM} },
\label{eq:beta}
\end{equation}
%
\textcolor{black}{and its \textcolor{black}{Alfv\' enic} Mach number,
%
\begin{equation}
	M_{\rm A} = \frac{ v  }{ v_{\rm A} },
\label{eq:Ma}
\end{equation}
%
where,
%
\begin{equation}
	v_{\rm A} = \frac{ |\bmath{B}_{\rm ISM}|  }{ \sqrt{ 4 \pi n m_{\rm H} } },
\label{eq:va}
\end{equation}
%
is the Alfv\' enic velocity, satisfy some particular conditions. 
Note that in Eq.~(\ref{eq:Ma}) the velocities are taken along the shock normal. }
On the one hand, the plasma beta must be such that,
%
\begin{equation}
	\beta < \frac{2}{\gamma},
\label{eq:cond1}
\end{equation}
%
whereas on the other hand, the \textcolor{black}{Alfv\' enic} Mach number verifies the following order 
relation,
%
\begin{equation}
	1 < M_{\rm A} < \sqrt{ \frac{\gamma(1-\beta)+1 }{\gamma-1} },
\label{eq:cond2}
\end{equation}
%
where $\gamma$ is the adiabatic index, \textcolor{black}{see Eq.~1 in~\citet{pogolerov_aa_354_2000}}. Numbers from our simulations indicate
that the ISM thermal pressure $n_{\rm ISM} k_{\rm B} T_{\rm ISM}\approx 8.62
\times 10^{-13}\, \rm dyne\, \rm s^{-2}$, \textcolor{black}{therefore we find 
$\beta > 2/\gamma \approx 1.2$ for $B_{\rm ISM} \le 3.5\, \mu \rm G$ 
(see bow shocks with normal morphologies in Fig.~\ref{fig:bfieldstrength}a,b)
but $\beta \approx
\textcolor{black}{0.44}< 2/\gamma \approx 1.2$ for $B_{\rm ISM}=7\, \mu \rm G$ 
(see dimpled bow shock in Fig.~\ref{fig:bfieldstrength}c).
The \textcolor{black}{Alfv\' enic} Mach number $M_{\rm A} =
v/v_{\rm A} \approx 40.0\, \rm  km\, \rm s^{-1}/17.2\, \rm  km\, \rm
s^{-1} \approx 2.33$ which is outside the range 
$1<M_{\rm A}<((\gamma(1-\beta)+1)/(\gamma-1))^{1/2} \approx \textcolor{black}{1.70}$. 
Similarly, the model with $v_{\star}=70\, \rm  km\, \rm s^{-1}$ is such that 
$M_{\rm A}>((\gamma(1-\beta)+1)/(\gamma-1))^{1/2}$ whereas our slower model with 
$v_{\star}=20\, \rm  km\, \rm s^{-1}$ gives 
$1<M_{\rm A}\approx 1.16<((\gamma(1-\beta)+1)/(\gamma-1))^{1/2}$, which 
is inside the range in Eq.~(\ref{eq:cond2}).  
We conclude that the upstream ISM conditions in our magneto-hydrodynamical 
simulations producing dimpled bow shocks have values consistent with the 
existence of switch-on shocks}, see also sketch of the ($\beta$,$M_{\rm A}$) 
plane in Fig.~3 of~\citet{sterck_aa_343_1999}.

\textcolor{black}{However, we can not affirm that the dimpled apex topology of our 
magneto-hydrodynamical bow shocks models is of origin similar to the ones 
in~\citet{sterck_phpl_1998,sterck_aa_343_1999}. Only their particular 
concave-inward form that differs from the classical shape of hydrodynamical 
bow shocks (Fig.~\ref{fig:physics}e) authorizes a comparison between the 
two studies. Nevertheless, we notice that our bow shocks are also generated 
in an ambient medium in which the plasma beta and the \textcolor{black}{Alfv\' enic} Mach number 
have parameter values consistent with the formation of switch-on shocks, 
which has been showed to be similar to the parameter values producing dimpled 
bow shocks around charged obstacles~\citep[see][and references therein]
{sterck_phpl_1998,sterck_aa_343_1999}.} Additional investigations, left for future studies, 
are required to assess the question of \textcolor{black}{the exact nature the 
various discontinuities affecting magneto-hydrodynamical bow shocks of OB stars. }

\begin{figure*}
	\begin{minipage}[b]{ 0.65\textwidth}
		\includegraphics[width=1.0\textwidth]{./cuts.eps}
	\end{minipage} \\  	
	\caption{
	         Number density (solid lines, in $\rm cm^{-3}$) and temperature 
	         (dotted lines, in $\rm K$) profiles in our hydrodynamical (thick blue lines) 
	         and magneto-hydrodynamical (thin red lines) 
	         bow shocks models of an initial $20\, \rm M_{\odot}$ star moving with velocity 
	         $v_{\star}=40\, \mathrm{km}\, \mathrm{s}^{-1}$. The profiles are measured along the 
	         symmetry axis Oz. 
		 }
	\label{fig:cuts}  
\end{figure*}

\subsubsection{Effects of the magnetic field strength}
\label{sect:}

Fig.~\ref{fig:bfieldstrength} is similar to Fig.~\ref{fig:physics} and displays
the effects of the ISM magnetic field strength $B_{\rm ISM}=0$ (a), $3.5$ (b)
and $7.0\, \rm \mu G$ (c) on the shape of the bow shocks produced by our
initially $20\, \rm M_{\odot}$ star moving with velocity $v_{\star}=40\, \rm
km\, \rm s^{-1}$. In Fig.~\ref{fig:cuts} we show density (solid lines) and
temperature (dotted lines) profiles from our hydrodynamical simulation (thick
blue lines) and magneto-hydrodynamical model (thin red lines) of the bow shocks
in Fig.~\ref{fig:bfieldstrength}. The profiles are taken along the symmetry axis
of the computational domain. The global structure of the bow shock is similar
for both simulations, i.e. it consists of a hot bubble ($T\approx\, 10^{7}\, \rm
K$) surrounded by a shell of dense ($n\approx\, 10\, \rm cm^{-3}$) shocked ISM
gas. The profiles in Fig.~\ref{fig:cuts} highlights the progressive compression 
of the bow shocks by the the ISM total pressure which magnetic component increases 
as $B_{\rm ISM}$ is larger. \textcolor{black}{Several mechanisms at work might be 
responsible for such discrepancy:
%
\begin{enumerate}
%
\item The magnetic pressure in the ISM. If one neglects the thermal pressures $nk_{\rm B}T$ 
      in both the supersonic stellar wind and the inflowing ISM, and omits the magnetic 
      pressure $\propto B_{\star}^{2} \propto r^{-4}$ at the wind termination shock,  
      then the pressure balance between ISM and stellar wind gas reads, 
%
\begin{equation}
	\rho_{\rm w} v_{\mathrm{w}}^{2} = \rho_{\rm ISM} v_{\star}^{2} + \frac{B_{\rm ISM}^{2}}{8\pi},
\label{eq:pressures}
\end{equation}
%
from which one can derive the bow shock stand-off distance in a planar-aligned field bow shock,
%
\begin{equation}
	R(0) = \Bigg( \frac{2\dot{M}v_{\mathrm{w}}}{ B_{\rm ISM}^{2} + 8\pi \rho_{\mathrm{ISM}}v_{\star}^{2} }\Bigg)^{1/2},
	\label{eq:Romag}
\end{equation}
%
that is slightly smaller from the one derived in a purely hydrodynamical context~\citep{wilkin_459_apj_1996}.  
%
\item The cooling by optically-thin radiative processes. Changes in the density at the 
      post-shock region at the forward shock influence the temperature in the shocked ISM gas, 
      which in their turn modify the cooling rate of the gas, itself affecting its thermal 
      pressure. This results in an increase of the density of the shell of ISM gas but also a decrease 
      of the temperature in the hot region of shocked stellar wind material that shrinks in order 
      to maintain its total pressure equal to $\rho_{\rm ISM} v_{\star}^{2}+B_{\rm ISM}^{2}/8\pi$. 
%
\item The magnetic field field lines inside the bow shock. The compression of the layer of shocked ISM gas 
      modifies the arrangement of the field lines in the post-shock region at the forward shock. 
      Thus, the term $B_{\rm ISM}^{2}/8\pi$ corresponding to the magnetic pressure increases and modifies 
      the effects of radiative cooling in the simulations (see above). 
%       
\item Symmetry effects. The solution may also be affected by the intrinsic two-dimensional nature of 
      our simulations, which may develop numerical artifices close to the symmetry axis. In the case 
      of magneto-hydrodynamical simulations of objects moving supersonically along the direction 
      of the ISM magnetic field, such effects are more complex than a simple accumulation of material 
      at the apex of the nebula, but might present artificial shocks, see also Section~\ref{sect:physics4}.       
%
\end{enumerate}
%
}

\textcolor{black}{
Appreciating in detail which of the above cited processes dominates the solution would 
require three-dimensional numerical simulations which are beyond the scope of this work. 
Moreover, establishing an analytic theory of the position of the contact 
discontinuity of a magnetized bow shock is a non-trivial task since the 
thin-shell limit~\citep{wilkin_459_apj_1996} is not applicable. 
}
%
In particular, the hot bubble loses about three quarter of its size along
the $Oz$ direction when the ISM magnetic field strength increases up to $B_{\rm
ISM}=7\, \mu \rm G$ (Fig.~\ref{fig:bfieldstrength}a,c). This modifies 
the volume of hot shocked ISM gas advected thanks to heat transfers towards the
inner part of the bow shock of our model HD2040All, reducing it to a narrow
layer made of shocked wind material since anisotropic thermal conduction forbids
the penetration of ISM gas in the hot region. The effects of the ISM
magnetisation on our optical and infrared bow shocks' emission properties are 
further discussed in Section~\ref{sect:discussion}.

%\subsubsection{Instabilities and comparison with analytical approximation}
%\subsubsection{Instabilities}
%\label{sect:instab}

All of our magneto-hydrodynamical simulations have a stable density field
(Fig.~\ref{fig:physics}e,f,g,h). \textcolor{black}{The simulations} with cooling but
without heat transfer (Fig.~\ref{fig:physics}b) show that the presence of the
magnetic field inhibits the growth of Kelvin-Helmholtz instabilities
(Fig.~\ref{fig:physics}f) that typically develops within the contact
discontinuity of the bow shocks because they are the interface of two plasma
moving in opposite
directions~\citep[][Paper~I]{comeron_aa_338_1998,vanmarle_aa_469_2007}. 
\textcolor{black}{The solution does} not change performing the simulation MHD2040AllB7 at double and
quadruple spatial resolution, and conclude that our results are consistent with both
numerical studies devoted to the growth and saturation of these instabilities in
the presence of a planar magnetic field~\citep[see,
e.g.][]{keppens_jplph_61_1999} and with results obtained for slow-winded, cool
runaway stars moving in a planar-aligned magnetic
field~\citep{vanmarle_aa_561_2014}. Note that detailed numerical studies
demonstrating the suppression of shear instabilities by the presence of a
background magnetic field also exist in the context of jets from
protostars~\citep{viallet_473_aa_2007}.

%\begin{figure}
%	\begin{minipage}[b]{ 0.48\textwidth}
%		\includegraphics[width=1.0\textwidth]{./density_map_40_Mo_20kms_PSN_legend.eps}
%	\end{minipage} \\  	
%	\caption{
%	         Same as Fig.~\ref{fig:physics} for our initially $40\, \rm
%M_{\odot}$ star moving with velocity $v_{\star}=70\, \mathrm{km}\, \mathrm{s}^{-1}$. 
%The left-hand part of the figure shows the hydrodynamical (HD) model MS4070 and 
%the right-hand our magneto-hydrodynamical (MHD) model MHD4070AllB7 of Paper~I. The 
%overplotted black lines represents the analytical solution of~\citet{wilkin_459_apj_1996}, 
%see Eq.~(\ref{eq:wilkin}).  
%		 }
%	\label{fig:mhd4070all}  
%\end{figure}

%Fig.~\ref{fig:mhd4070all} compares the density field of an initially $40\, \rm
%M_{\odot}$ star moving with velocity $v_{\star}=70\, \mathrm{km}\,
%\mathrm{s}^{-1}$ in a non-magnetised ISM (model MS4070, left-hand part) 
%and in a magnetised ISM with $B_{\ISM}=7\, \mu \rm G$ (model MHD4070AllB7, 
%right-hand part), respectively, and overplots the canonical analytical 
%solution of stellar wind bow shocks morphology defined as, 
%
%\begin{equation}
%	R({\theta}) = R(0) \mathrm{cosec}(\theta \frac{\pi}{180}) \sqrt{ 3(1-\theta \frac{\pi}{180} )\mathrm{cotan}(\theta \frac{\pi}{180} ) },
%\label{eq:wilkin}
%\end{equation}
%
%where $\theta$ is the angle with respect to the direction of motion of the 
%star~\citep{wilkin_459_apj_1996}. \textcolor{black}{Note that, given its shorter 
%lifetime, the models involving the initially $40\, \rm M_{\odot}$ star are 
%started at the zero-age main-sequence time. 
%}
%The density field in our hydrodynamical simulation 
%MS4070 (Paper~I) develops strong non-linear instabilities~\textcolor{black}{\citep{vishniac_apj_428_1994}} that dramatically distorts
%its overall shape~\citep[see also bottom panel of Fig.~8 in Paper~I and the discussion 
%concerning these instabilities in][]{comeron_aa_338_1998} whereas they are 
%absent from all our magneto-hydrodynamical model. \textcolor{black}{This is in accordance 
%with the two-dimensional magneto-hydrodynamical numerical analysis of the growth of 
%the thin-shell instability which can be suppressed when the field is parallel to the 
%flow~\citep{heitsch_apj_665_2007}}.

%Our simulation MHD4070AllB7 illustrates that the presence of \textcolor{black}{magnetic 
%field prevents these instabilities from growing since} it forbids the whole structure from
%developing a thin shell which in turn allows the seed of the non-linear
%instability to form at the apex of the bow shock~\citep{blondin_na_57_1998}. 
%\textcolor{black}{Consequently, this bow shock} does not present any Vishniac-related distortions (right-hand
%part of Fig.~\ref{fig:mhd4070all}). The superposition 
%of Wilkin's solution on the density fields in our simulations indicates that it
%is close to the contact discontinuity but does not represent the overall shape of
%the bow shock as in the hydrodynamical case (left-hand part of Fig.~\ref{fig:mhd4070all}).
%
%\textcolor{black}{Since the assumptions of Wilkin's model are not consistent with the  
%magneto-hydrodynamical simulations, we therefore should not expect this analytical 
%model to fit our models.}
%We conclude that the presence of a magnetic field makes the morphology of  
%Galactic bow shock from hot stars inconsistent with analytical approximations. 
%
%This is valid even for situations in which the purely hydrodynamical modelling 
%of the surroundings of the star produces has a thin-shell, e.g. in the case of an 
%initially high mass star moving with an hypersonic motion with respect to the ambient 
%ISM (Paper~I).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Effects of the star's bulk motion}
\label{sect:physics3}

%\subsubsection{Effects of the space velocity of the runaway star}
%\label{sect:vel}

\begin{figure}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_20kms_MS_legend.eps}
	\end{minipage} \\
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_40kms_MS_legend.eps}
	\end{minipage} \\
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./streamlines_map_20_Mo_70kms_MS_legend.eps}
	\end{minipage} \\  	
	\caption{
		Grid of stellar wind bow shocks from our initially $20\, \rm
M_{\odot}$ star represented as a function of its space velocity with respect to
the ISM, with velocity $v_{\star}=20$ (a), $40$ (b) and $70\, \mathrm{km}\,
\mathrm{s}^{-1}$ (c). The nomenclature of the models follows Table~\ref{tab:ms}.
The bow shocks are shown at about $5\, \rm Myr$ after the beginning of the
main-sequence phase of the central star's evolution. All our MHD models assume a
strength of the ISM magnetic field $B_{\rm ISM}=7\, \mu \rm G$. The gas number density
is shown with a density range from $10^{-5}$ to $5.0\, \mathrm{cm}^{-3}$ in the
logarithmic scale. The crosses mark the position of the star. The solid
black contour traces the boundary between wind and ISM material
$Q_{1}(\bmath{r})=1/2$. The
$R$-axis represents the radial direction and the $z$-axis the direction of
stellar motion (in $\mathrm{pc}$). Only part of the computational domain is
shown in the figures.  
		 }
	\label{fig:motion}  
\end{figure}

Fig.~\ref{fig:motion} is similar to Fig.~\ref{fig:bfieldstrength} and plots a grid of
density field of our initially $20\, \rm M_{\odot}$ star moving with velocity
$v_{\star}=20$ (a), $40$ (b), $70\, \mathrm{km}\, \mathrm{s}^{-1}$ (c). The
scaling effect of the bulk motion of the star on the bow shocks morphology is \textcolor{black}{similar
to} our hydrodynamical study (Paper~I). At a given strength of the ISM magnetic
field, the compression of the forward shock increases as the \textcolor{black}{spatial}
motion of the star increases because the ambient medium ram pressure is larger.
The relative thickness of the layers of ISM and wind behaves similarly as
described in Paper~I. Our model with $v_{\star}=20\, \rm km\, \rm s^{-1}$ has a
layer of shocked ISM larger than the layer of shocked wind because the
relatively small ISM ram pressure induces a weak forward shock
(Fig.~\ref{fig:motion}a). The shell of shocked ISM is thinner in our
simulation with $v_{\star}=70\, \rm km\, \rm s^{-1}$ because the strong forward
shock has a high post-shock temperature which allows an efficient cooling of the
plasma (Fig.~\ref{fig:motion}c).

\textcolor{black}{
The density field in our models with ISM inflow 
velocity similar to the \textcolor{black}{Alfv\' enic} speed ($v_{\star}=20 
~\simeq v_{\rm A}\approx 17.2\, \rm km\, \rm s^{-1}$) has the dimpled shape 
of its apex of the bow shock (Fig.~\ref{fig:motion}a). 
The model with $v_{\star}=70\, \rm km\, \rm s^{-1}$ has inflow ISM velocity 
larger than the \textcolor{black}{Alfv\' enic} speed and presents the classical single-front 
morphology (Fig.~\ref{fig:motion}c) typically produced by stellar wind bow 
shocks~\citep{brighenti_mnras_273_1995,brighenti_mnras_277_1995,comeron_aa_338_1998,meyer_mnras_459_2016}. 
A similar effect of the \textcolor{black}{Alfv\' enic} speed is discussed in, e.g. fig.4 of~\citet{sterck_aa_343_1999}. 
Again, exploring in detail whether the formation mechanisms of our dimpled bow shocks 
is identical to the ones obtained in calculations of 
bow shock flow over a conducting sphere is far beyond the scope of this work. }
Note the absence of instabilities in our magneto-hydrodynamical bow shocks simulations 
compare to our hydrodynamical models.

%\begin{figure}
%	\begin{minipage}[b]{ 0.48\textwidth}
%		\includegraphics[width=1.0\textwidth]{./streamlines_map_10_Mo_40kms_MS_legend.eps}
%	\end{minipage} \\  	
%	\caption{
%	         Same as Fig.~\ref{fig:motion} for our initially $10\, \rm
%M_{\odot}$ star moving with velocity $v_{\star}=40\, \mathrm{km}\, \mathrm{s}^{-1}$.  
%		 }
%	\label{fig:mhd1040all}  
%\end{figure}

%\subsubsection{Effects of the initial mass of the star}
%\label{sect:vel}

%In Fig.~\ref{fig:mhd1040all} we show the density field of our initially $10\,
%\rm M_{\odot}$ star moving with velocity $v_{\star}=40\, \mathrm{km}\,
%\mathrm{s}^{-1}$. \textcolor{black}{As described in Paper~I, the volume of a bow
%shock scales with the wind momentum strength, i.e. with the mass-loss, of the
%runaway stars. 
%If one neglects the thermal pressures $nk_{\rm B}T$ in both the
%supersonic stellar wind and the inflowing ISM, and omits the magnetic pressure
%$\propto B_{\star}^{2} \propto r^{-4}$ at the wind termination shock, therefore
%the pressure balance between ISM and stellar wind gas near the wind/ISM
%interface reads, 
%
%\begin{equation}
%	\rho_{\rm w} v_{\mathrm{w}}^{2} = \rho_{\rm ISM} v_{\star}^{2} + \frac{B_{\rm ISM}^{2}}{8\pi},
%\label{eq:pressures}
%\end{equation}
%
%from which one can derive the bow shock stand-off distance in a planar-aligned field bow shock,
%
%\begin{equation}
%	R(0) = \Bigg( \frac{2\dot{M}v_{\mathrm{w}}}{ B_{\rm ISM}^{2} + 8\pi \rho_{\mathrm{ISM}}v_{\star}^{2} }\Bigg)^{1/2},
%	\label{eq:Romag}
%\end{equation}
%
%that differs slightly from the one derived in a purely hydrodynamical context.
%Nonetheless, it conserves its $\propto \dot{M}^{1/2}$ dependence of its stand-off distance
%as predicted by Eq.~(\ref{eq:Ro}), see also in~\citet{wilkin_459_apj_1996}.

%\textcolor{black}{
%Interestingly, the volume of our magnetized bow shocks generated by massive
%runaway stars depends on the stellar wind properties. This is inconsistent with 
%the analytic solution of the general shape of an isothermal bow shock produced by 
%a solid obstacle}, 
%
%\begin{equation}
%	\sin(\theta) = \frac{c_{\rm s}}{v_{\star}} = \frac{1}{M},
%	\label{eq:landau}
%\end{equation}
%
%where $M$ is the ISM Mach number~\citep{1966hydr.book.....L}. Note that the
%non-validity of this law with respect to hydrodynamical simulations of bow
%shocks from brown dwarves, i.e. stars with quasi-null mass-losses, has already
%be noticed on the basis of simulations carried out with the code {\sc pluto}
%that we use in this study (D. Thun, private communication).

\subsection{Model limitation}
\label{sect:physics4}

\textcolor{black}{
First and above, our models suffer from their two-dimensional nature. If 
carrying out axi-symmetric models is advantageous in order to decrease the 
amount of computational ressources necessary to perform the simulations, however, 
it forbids the bow shocks from generating a structure which apex would be 
totally unaffected by symmetry-axis related phenomenons, common in this case of 
calculations~\citep{meyer_mnras_459_2016}. This prevents our simulations from being able 
to assess, e.g. the question of the relation between the seeds of the non-linear 
thin-shell instability at the tip of the structure and the growth of 
Kelvin-Helmholtz instabilities occuring later in the wings of the bow shocks. 
Only full 3D models of the same bow shocks could fix such problems and 
allow us to further discuss in detail the instability of bow shocks from OB stars.
We refer the reader to~\citet{vanmarle_2015} for a discussion of the dimension-dependence 
of numerical solutions concerning the interaction of magnetic fields with hydrodynamical 
instabilities. 
}

\textcolor{black}{
In particular, the selection of admissible shocks which is generally treated 
using artificial viscosity in purely hydrodynamical simulations is more 
complex in our magneto-hydrodynamical context~\citep[see 
discussion in][]{ pogolerov_aa_354_2000}. This can lead to additional 
fragilities of the solution, especially close to the symmetry axis of our 
cylindrically-symmetric models. Although the stability of these kinds of shocks 
is still under debate~\citep{desterck_aipc_537_2000,desterck_2001}, we will try 
to address these issues in future three-dimensional simulations. 
Moreover, such models would (i) allow us to explore the effects of a non-aligned 
ISM magnetic field on the morphology of the bow shocks and (ii) will make 
subsequent radiative transfer calculations meaningful, e.g. considering 
polarization maps using full anisotropic scattering of the photons on the dust 
particles in the bow shocks. The space of parameters investigated in our study is 
also limited, especially in terms of the explored range of space velocity 
$v_{\star}$ and ISM density $n_{\rm ISM}$ and will be extended in a follow-up 
project. Finally, other physical processes such as the presence of a 
surrounding $\HII$ region or the intrinsic viscous, granulous and turbulent 
character of the ISM are also neglected and deserve additional investigations. 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table*}
	\centering
	\caption{
	Maximum optical surface brightness of our magneto-hydrodynamical
simulations with $B_{\rm ISM}=7\, \mu G$. The second and third columns are the
quantities $\Sigma_{[\rm H\alpha]}^{\rm max}$ and $\Sigma_{[\rm O{\sc III}]}^{\rm
max}$ representing the maximum projected emission in [O{\sc iii}] $\lambda \,
5007$ and H$\alpha$ (in $\rm erg\, \rm cm^{-2}\, \rm s^{-1}\, \rm arcsec^{-2}$),
respectively. Models consisting of the hydrodynamical counterpart of our bow shocks 
models have their labels in italic in the first column (see description in Table~1 
in Paper~I). The surface brightnesses are measured along the direction of motion of 
the star at the apex of our bow shocks, close to the symmetry axis $Oz$. 
	}
	\begin{tabular}{cccc}
%	\hline
	\hline
	${\rm {Model}}$ &   $\Sigma_{[\rm H\alpha]}^{\rm max}\, (\rm erg\, \rm cm^{-2}\, \rm s^{-1}\, \rm arcsec^{-2})$                              
			&   $\Sigma_{[\rm O{\sc III}]}^{\rm max}\, (\rm erg\, \rm cm^{-2}\, \rm s^{-1}\, \rm arcsec^{-2})$    
			&   $\Sigma_{[\rm O{\sc III}]}^{\rm max}/\Sigma_{[\rm H\alpha]}^{\rm max}$
			\\ \hline   
	MHD1040AllB7    &  $2.5\times 10^{-19}$  &  $7.0\times 10^{-18}$ & $28.0$   \\ 
	{\it MS1040 }   &  $1.0\times 10^{-18}$  &  $2.5\times 10^{-17}$ & $25.0$   \\     		
	MHD2020AllB7    &  $1.7\times 10^{-17}$  &  $6.8\times 10^{-17}$ & $4.0$   \\   
	{\it MS2020 }   &  $6.0\times 10^{-17}$  &  $7.2\times 10^{-17}$ & $1.2$   \\     		
	MHD2040AllB7    &  $2.9\times 10^{-17}$  &  $1.6\times 10^{-16}$ & $5.5$   \\    
	MHD2040AllB3.5  &  $1.0\times 10^{-16}$  &  $3.2\times 10^{-16}$ & $3.2$   \\    	
	{\it MS2040 }   &  $1.2\times 10^{-16}$  &  $2.5\times 10^{-16}$ & $2.1$   \\    
	MHD2070AllB7    &  $8.0\times 10^{-18}$  &  $2.0\times 10^{-16}$ & $25.0$   \\  
	{\it MS2070 }   &  $1.5\times 10^{-16}$  &  $8.5\times 10^{-16}$ & $5.7$   \\  	
	MHD4070AllB7    &  $1.2\times 10^{-17}$  &  $5.5\times 10^{-16}$ & $45.8$   \\   
	{\it MS4070 }   &  $4.0\times 10^{-16}$  &  $1.0\times 10^{-15}$ & $2.5$   \\     			
	\hline    
%	\hline 
	\end{tabular}
\label{tab:sigma}
\end{table*}

\section{Comparison with observations and implications of our results}
\label{sect:discussion}

In this section, we extract observables from our simulations, compare them to observations 
and discuss their astrophysical implications. 
We first recall the used post-processing methods and then compare 
the emission by optically-thin radiation 
of our magneto-hydrodynamical bow shocks with hydrodynamical
models of the same star moving at the same \textcolor{black}{velocity}.
\textcolor{black}{Given the high temperature generated by collisional heating (Fig.~\ref{fig:temperature}), 
we particularly focus on the H$\alpha$ and [O{\sc iii}] $\lambda \, 5007$ optical emission.   
Moreover, stellar wind bow shocks from massive stars have been first detected at these 
spectral lines and hence constitute a natural observable. } 
\textcolor{black}{
We complete our analysis with infrared radiative transfer calculations and 
comment the observability of our bow shock nebulae. Last, we discuss our findings in the
context of the runaway massive star $\zeta$ Ophiuchi.   
}

\begin{figure}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./temperature_legend.eps}
	\end{minipage} \\  	
	\caption{
	         \textcolor{black}{Temperature field (in $\rm K$) in the models MS2040 and MHD2040AllB7. 
	         The cross-like structure in the  central region of freely-expanding 
	         stellar wind is a boundary effects caused by the pressure
	         }}
	\label{fig:temperature}  
\end{figure}

\subsection{Post-processing methods}
\label{sect:maps}

Fig.~\ref{fig:maps} plots the projected optical emission of our model of an initially
$20\, \rm M_{\odot}$ star moving at $40\, \rm km\, \rm s^{-1}$ in H$\alpha$ (a)
and [O{\sc iii}] $\lambda \, 5007$ (b) in $\mathrm{erg}\, \mathrm{s}^{-1}\, \mathrm{cm}^{-2}\,
\mathrm{arcsec}^{-2}$. Left-hand part of the panels correspond to the star
moving into an ISM with no background magnetic field (hydrodynamical model MS2040, Paper~I) whereas right-hand
parts correspond to $B_{\rm ISM}=7\, \rm \mu G$ (magneto-hydrodynamical model MHD2040AllB7). We take into
account the rotational symmetry about $R=0$ of our models and integrate the
emission rate assuming that our bow shocks lay in the plane of the sky, i.e. 
the star moves perpendicular to the observer’s line-of-sight. The
spectral lines emission coefficients are evaluated using the 
prescriptions for optical spectral line emission 
from~\citet{dopita_aa_29_1973} and~\citet{osterbrock_1989}, which read,
%
\begin{equation}
	j_{\rm [H\alpha]}(T) \approx 1.21\times 10^{-22} T^{-0.9} n_{\rm p}^{2}\, \rm erg\, s^{-1}\, cm^{-3}\, sr^{-1},
\label{eq:Ha}
\end{equation}
%
where $n_{\rm p}$ is the number of proton in the plasma, and,
%
\begin{equation}
	j_{\rm [O{\sc III}]}(T) \approx 3.23\times 10^{-21} \frac{ e^{-\frac{28737}{T}} }{4\pi\sqrt{T}} n_{\rm p}^{2}\, \rm erg\, s^{-1}\, cm^{-3}\, sr^{-1},
\label{eq:OIII}
\end{equation}
%
for the H$\alpha$ and [O{\sc iii}] $\lambda \, 5007$ spectral lines, respectively. 
Additionally, we assume solar oxygen abundances~\citep{lodders_apj_591_2003} and cease to
consider the oxygen as triply ionised at temperatures larger than $10^{6}\, \rm
K$~\citep[cf.][]{cox_mnras_250_1991}. 
%

\begin{figure}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./map_Ha.eps}
	\end{minipage} \\
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./map_OIII.eps}
	\end{minipage}	\\ 	
%	\begin{minipage}[b]{ 0.48\textwidth}
%		\includegraphics[width=1.0\textwidth]{./map_Ha.eps}
%	\end{minipage}	\\	
	\caption{
	         Surface brightness maps of H$\alpha$ (a), [O{\sc
iii}] (b) surface brightness (in $\mathrm{erg}\, \mathrm{s}^{-1}\,
\mathrm{cm}^{-2}\, \mathrm{arcsec}^{-2}$), respectively, of our bow shock model 
generated by our initially $20\, \rm M_{\odot}$ star moving with velocity
$v_{\star}=40\, \mathrm{km}\, \mathrm{s}^{-1}$. Quantities are calculated excluding the
undisturbed ISM and plotted in the linear scale. The left-hand part of the panels 
refers to the hydrodynamical model MS2040, the right-hand part to the 
magneto-hydrodynamical model \textcolor{black}{MHD2040AllB7}. The crosses mark the
position of the star. \textcolor{black}{For the sake of comparison, these optical maps 
are presented as in Paper~I}. 
		 }
	\label{fig:maps}  
\end{figure}

\begin{figure*}
	\begin{minipage}[b]{ 0.58\textwidth}
		\includegraphics[width=1.0\textwidth]{./luminosity_grid.eps}
	\end{minipage} 
	\caption{
	         \textcolor{black}{Bow shocks luminosities and feedback of our
magneto-hydrodynamical models. We separate the infrared reprocessed
starlight (red squares, in $\rm erg\, \rm s^{-1}$) and distinguish the total emission by
optically-thin radiation from the bow shock (dark-green triangles, in $\rm erg\,
\rm s^{-1}$) from the emission from the shocked wind material only (orange dots,
in $\rm erg\, \rm s^{-1}$). Additionally, we show the luminosity from $[\rm
O{\sc III}]$ $\lambda \, 5007$ emission (pale green losanges, in $\rm erg\, \rm
s^{-1}$), the luminosity from H$\alpha$ emission (blue crosses, in $\rm erg\,
\rm s^{-1}$) and the X-rays luminosity in both the soft and hard energy bands
$E>0.5\, \rm eV$ ($T>5.8\times10^{6}\, \rm K$). For the sake of comparison we
add the feedback of the hydrodynamical model HD2040 corresponding to $B_{\rm
ISM}=0\, \mu \rm G$ (originally published in Paper~I). The 
simulations labels are indicated under the corresponding values.} 
		 }
	\label{fig:feedback}  
\end{figure*}

The bow shocks luminosities $L$ are estimated integrating the emission rate,
%
\begin{equation}
	\itl{ L} = 2\pi \iint_{\mathcal D} \itl{\Lambda}(T) n_{\rm H}^{2} R dRdz,
\label{eq:bslum}
\end{equation}
%
where $\mathcal D$ represents its volume in the $z>0$ part of the 
computational domain~\citep[][Paper~I]{mohamed_aa_541_2012}. Similarly, we calulate
the momentum deposited by the bow shock \textcolor{black}{by}
subtracting the stellar motion from the ISM gas velocity field. 
We compute $L_{\rm H\alpha}$ and $L_{[\rm OIII]}$, the bow
shocks luminosity in [O{\sc iii}] $\lambda \,
5007$ and H$\alpha$, respectively. Furthermore, we
discriminate the total bow shock luminosity $L_{\rm total}$ from the shocked
wind emission $L_{\rm wind}$. For distinguishing the two kind 
of material, we make use of a passive scalar $Q$ that is advected with
the gas. We estimate the overall X-rays luminosity $L_{\rm X}$ with emission coefficients
generated with the {\sc xspec} program~\citep{arnaud_aspc_101_1996} with solar 
metalicity and chemical abundances from~\citet{asplund_araa_47_2009}. Moreover, 
the total infrared emission $L_{\rm IR}$ is estimated as a fraction of the 
starlight bolometric flux $L_{\star}$~\citep{brott_aa_530_2011a} intercepted by 
the ISM silicate dust grains in the bow shock,  
%
\begin{equation}
	\itl{ \Gamma}_{\star}^{\rm dust} = 
	\frac{L_{\star}}{ 4\pi d^{2} }n_{\rm d}\sigma_{\rm d}(1-A)\, \rm erg\, s^{-1}\, cm^{-3},
\label{eq:radlum}
\end{equation}
%
plus the collisional heating,
%
\begin{equation}
	\itl{\Gamma}_{\rm coll,photo}^{\rm dust}(T) = \frac{ 2^{5/2} f Q 
	n n_{\rm d} \sigma_{\rm d} }{ \sqrt{\pi m_{\rm p}} } \Big( k_{\rm B}T \Big)^{3/2} \, \rm erg\, s^{-1}\, cm^{-3},
\label{eq:dustheathot}
\end{equation}
%
where $a=5.0\, \rm nm$ is the dust grains radius, 
%
\begin{equation}
  \sigma_{\rm d}=\pi a^{2}\, \rm cm^{2},
  \label{eq:crosssection}
\end{equation}
%
is their geometrical cross-section, $d$ their distance from the star and 
$A=1/2$ their Albedo. Additionally,  $n_{\rm d}$ is the dust number density 
whereas $Q\, \simeq 1$ represents the grains electrical properties. More 
details regarding to the estimate of the bow shock infrared luminosity are given in 
Appendix B of Paper~I.

\textcolor{black}{
Last, infrared images are computed performing dust continuum calculations 
against dust opacity for the bow shock generated by our $20\, \rm M_{\odot}$ 
star moving with velocity $40\, \rm km\, \rm s^{-1}$,  using 
the radiative transfer code {\sc radmc-3d}\footnote{ 
\textcolor{black}{http://www.ita.uni-heidelberg.de/~dullemond/software/radmc-3d/} 
}~\citep{ dullemond_2012}. We map the dust mass density fields in our models 
onto a uniform spherical grid $[0;R_{\rm sph}]\times[0; \theta_{\rm max}]$, 
where $R_{\rm sph}=(R_{\rm max}^{2}+z_{\rm max}^{2})^{1/2}$ and $\theta_{\rm 
max}=180\degree$. We assume a dust-to-gas mass ratio of $1/200$. The 
dust density field is computed with the help of the passive 
scalar tracer $Q$ that allows us to separate the dust-free stellar wind of our 
hot OB stars with respect to the dust-enriched regions of the bow shock, made of 
shocked ISM gas. Additionally, we 
exclude the regions of ISM material that are strongly heated by the shocks 
or by electronic thermal conduction (Paper~I), and which are defined as much hotter 
than about a few $10^{4}\, \rm K$. {\sc radmc-3d} then self-consistently 
determines the dust temperature using the Monte-Carlo 
method of~\citet{bjorkman_paj_554_2001} and~\citet{lucy_aa_344_1999} that we use 
as input to the calculations of our synthetic observations.
}

\textcolor{black}{
The code solves the transfer equation by ray-tracing photons packages from the
stellar atmosphere that we model as a black body point source of temperature
$T_{\rm eff}$ (see our Table~\ref{tab:wind_para}) that is located at the origin of
the spherical grid. The dust is assumed to be composed of
silicates~\citep{draine_apj_285_1984} of mass density $3.3\, \rm g\, \rm
cm^{-3}$ that follow the canonical power-law distribution $n(a)\propto a^{-q}$
with $q=-3.3$~\citep{mathis_apj_217_1977} and where $a_{\rm min}=0.005\, \mu \rm m$
and $a_{\rm max}=0.25\, \mu \rm m$ the minimal and maximal dust
sizes~\citep{vanmarle_apj_734_2011}.  We generate the corresponding {\sc
radmc-3d} input files containing the dust scattering $\kappa_{\rm scat}$ and
absorption $\kappa_{\rm abs}$ opacities such that the total opacity $\kappa_{\rm
tot}=\kappa_{\rm scat}+\kappa_{\rm abs}$ (see Fig.~\ref{fig:dust}a) on the basis
of a run of the Mie code of Bohren and Huffman~\citep{bohren_book_1983} which is
available as a module of the {\sc
hyperion}\footnote{\textcolor{black}{http://www.hyperion-rt.org/}}
package~\citep{robitaille_aa_536_2011}. Our radiative transfer calculations 
produces spectral energy distributions (SEDs) and isophotal images of the bow
shocks at a desired wavelength, which we choose to be $\lambda=24$ and $60\, \mu
\rm m$ because they corresponds to the wavelengths at which stellar wind bow
shocks are typically observed, see~\citet{sexton_mnras_446_2015}
and~\citet{buren_apj_329_1988,vanburen_aj_110_1995, noriegacrespo_aj_113_1997},
respectively. Our SEDs and images are calibrated to such that we 
consider that the objects are located at a distance $1\, \rm pc$ from 
the observer. 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Results: optically-thin emission}
\label{sect:feedback}

In Table~\ref{tab:sigma} we report the maximum surface brightness measured along
the direction of motion of the stars in the synthetic emission maps build from
our models at both the H$\alpha$ and [O{\sc iii}] $\lambda \, 5007$ spectral
line emission. We find that the presence of an ISM magnetic field makes \textcolor{black}{the}
H$\alpha$ signatures fainter by about 1-2 orders of magnitudes whereas \textcolor{black}{the}
[O{\sc iii}]  $\lambda \, 5007$ emission maps are about 1 order of magnitude
fainter, respectively. \textcolor{black}{The luminosity of stellar wind bow shocks is a volume
integral (Paper~I) and this volume decreases when a large ISM magnetic pressure 
compresses the nebula} (Fig.~\ref{fig:physics}d,h). Thus, their
surface brightness is fainter despite of the fact that the density and
temperature of their shocked regions is similar (Fig.~\ref{fig:cuts}).

\begin{figure}
	\begin{minipage}[b]{ 0.50\textwidth}
		\includegraphics[width=0.98\textwidth]{./opacity.eps}
	\end{minipage} 	\\
	\begin{minipage}[b]{ 0.50\textwidth}
		\includegraphics[width=0.98\textwidth]{./plot_seds_mhd.eps}
	\end{minipage}	
	\caption{
	         \textcolor{black}{
	         Top panel: dust opacities used in this study, inspired from~\citet{acreman_mnras_456_2016}. 
	         The figure shows the total opacity 
	         $\kappa_{\rm tot}$ (blue solid thick line), the absorption opacity $\kappa_{\rm abs}$ (red dotted thin line) 
	         and the scattering opacity $\kappa_{\rm scat}$ (green dashed thin line).  
	         } 
	         \textcolor{black}{
	         Bottom panel: spectral energy distributions of our model involving a $20\, \rm M_{\odot}$ star 
	         moving with a velocity of $40\, \rm km\, \rm s^{-1}$, considered in the hydrodynamical 
	         (model MS2040 with $B_{\rm ISM}=0\, \mu \rm G$, solid blue line) and 
	         in the magneto-hydrodynamical contexts (model MHD2040AllB7 with $B_{\rm ISM}=7\, \mu \rm G$, dotted red line).
	         The plot shows the flux density $F_{\lambda}$ (in $\rm Jy$) as a function 
	         of the wavelength $\lambda$ (in $\mu$m) for an inclination angle $\phi=0\degree$ of the bow shock. 
	         }	         
		 }
	\label{fig:dust}  
\end{figure}

\begin{figure*}
		\centering
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_30deg_lambda25_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_30deg_lambda60_legend.eps}
	\end{minipage}		
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_30deg_lambda100_legend.eps}
	\end{minipage}	\\	
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_45deg_lambda25_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_45deg_lambda60_legend.eps}
	\end{minipage}		
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_45deg_lambda100_legend.eps}
	\end{minipage}	\\
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_60deg_lambda25_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_60deg_lambda60_legend.eps}
	\end{minipage}	
	\begin{minipage}[b]{ 0.32\textwidth}
	      \centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_60deg_lambda100_legend.eps}
	\end{minipage}	\\
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_90deg_lambda25_legend.eps}
	\end{minipage}
	\begin{minipage}[b]{ 0.32\textwidth}
			\centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_90deg_lambda60_legend.eps}
	\end{minipage}	
	\begin{minipage}[b]{ 0.32\textwidth}
	      \centering
	        \includegraphics[width=1.0\textwidth]{./map_2040_90deg_lambda100_legend.eps}
	\end{minipage}		
	\caption{
	         \textcolor{black}{
	         Isophotal infrared emission maps of our bow shock models MS2040 and MHD2040AllB7. 
	         It represents our initially $20\, \rm M_{\odot}$ star moving with velocity $40\, \rm km\, \rm
s^{-1}$ as seen at wavelengths $\lambda=25$ (a-d), $60\, \rm \mu m$ (e-h) and $100\, \rm \mu m$ (i-l). The projected
flux is in units of $\rm erg\, \rm s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$. 
The maps are generated with an inclination 
angle of $\phi=30$ (a,e,i), $45$ (b,f,j), $60$ (c,g,k) and $90\degree$ (d,h,l) with respect to 
the plane of the sky. For each panel, the surface brightness is plotted in the linear scale and 
its maximum corresponds to the maximum of the hydrodynamical (left) and 
magneto-hydrodynamical bow shock models (right). 
%The crosses mark the position of the star. 
		 } 
		 }
	\label{fig:maps1}  
\end{figure*}

%\begin{figure}
%	\begin{minipage}[b]{ 0.48\textwidth}
%		\includegraphics[width=1.0\textwidth]{./plot_seds_mhd.eps}
%	\end{minipage} 	
%	\caption{
%	         \textcolor{black}{
%	         Spectral energy distributions of our model involving a $20\, \rm M_{\odot}$ star 
%	         moving with a velocity of $40\, \rm km\, \rm s^{-1}$, considered in the hydrodynamical 
%	         (model MS2040, solid blue line) and in the magneto-hydrodynamical contexts (model MHD2040AllB7, dotted red line).
%	         The distributions show $\lambda F_{\lambda}$ (in $\rm W\, \rm m^{-2}$) as a function 
%	         of the wavelength $\lambda$ (in $\mu$m) in the interval $1\le\lambda\le\, 200\, \mu$m for 
%	         an inclination angle $\phi=0\degree$ of the bow shock. 
%	         } 
%		 }
%	\label{fig:feedback}  
%\end{figure}

The ratio of our bow shocks models' maximum [O{\sc iii}] and H$\alpha$ maximum
surface brightness increases \textcolor{black}{in} the presence of the magnetic field, e.g. the
hydrodynamical model MS2040 has $\Sigma_{[\rm O{\sc III}]]}^{\rm
max}/\Sigma_{[\rm H\alpha]}^{\rm max}\approx2.1$ whereas our model MHD2040AllB7 has
$\Sigma_{[\rm O{\sc III}]]}^{\rm max}/\Sigma_{[\rm H\alpha]}^{\rm
max}\approx5.5$ if $B_{\rm ISM}=7\, \mu \rm G$. We notice that the spectral line
ratio $\Sigma_{[\rm O{\sc III}]]}^{\rm max}/ \Sigma_{[\rm H\alpha]}^{\rm max}$
augments with the increasing space velocity of the star, e.g. our models
MHD2020B7, MHD2040AllB7 and MHD2070B7 have $\Sigma_{[\rm O{\sc III}]]}^{\rm
max}/\Sigma_{[\rm H\alpha]}^{\rm max}\approx4.0$, $5.5$ and $25.0$,
respectively. This difference between [O{\sc iii}] $\lambda \, 5007$ and 
H$\alpha$ emission is more pronounced in our magneto-hydrodynamical simulations.
As for our hydrodynamical study, the region of maximum emission peaks close to
the contact discontinuity in the layer of shocked ISM material, in the region of
the stagnation shock (Paper~I, see also Figs.~\ref{fig:maps}a,b).

\begin{figure}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./plot_comparison.eps}
	\end{minipage}  	
	\caption{
		\textcolor{black}{
		Cross-sections taken through the direction of motion of the bow shock 
of our initially $20\, \rm M_{\odot}$ star moving in a medium 
with velocity $v_{\star}=40\, \rm km\, \rm s^{-1}$, both in a medium with 
$B_{\rm ISM}=0$ and $7\, \mu\rm G$. The emission are shown for a viewing angle 
of $\phi=45\degree$ and at the waveband $\lambda=60\, \mu\rm m$ (dotted red curves)
and for $\phi=60\degree$ at $\lambda=100\, \mu\rm m$ (solid blue curves).  
The surface brightness (in $\rm erg\, \rm s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$) 
is plotted as a function of the distance to the star (in $\rm pc$). 
The position of the star is located at the origin.} 
		 }
	\label{fig:cuts_mhd}  
\end{figure}

The ISM magnetic field does not change the order relations we previously
established with hydrodynamical bow shocks generated by main-sequence stars 
(Fig.~13a in Paper~I), i.e. $L_{\rm wind} < L_{\rm H\alpha} < L_{\rm total} <
L_{\rm IR}$ (see orange dots, blue crosses of Saint-Andrew, dark green triangles
and black squares in Fig.~\ref{fig:feedback}a, respectively). Additionally, as
discussed above in the context of projected emission maps, we find that the 
optical spectral line emission that we consider are such that $L_{[\rm O{\sc III}]}
> L_{\rm H\alpha}$. This confirms and extend to magneto-hydrodynamical bow shocks 
a result previously obtained \textcolor{black}{by} integrating the optically-thin emission in the range
$8000 \le T \leq 10^{6}\, \rm K$ (Paper~I). Our magneto-hydrodynamical bow shock
models have H$\alpha$ and $[\rm O{\sc III}]$ emission originating from the shocked 
ISM gas and their emission from the wind material is negligible ($L_{\rm total}/L_{\rm
wind}\approx10^{-6}$). Moreover, we find that the bow shocks X-rays emission are
very small in all our simulations ($L_{\rm X}/L_{\rm wind}\approx10^{-1}$, see
black crosses in Fig.~\ref{fig:feedback}a).

%The bow shock momentum input rate to the ISM is 
%reported in Table.~\ref{table_feedback}. These quantity decreases as a function of
%the \textcolor{black}{velocity} of the runaway star (see our 
%models \textcolor{black}{MHD2020B7}, \textcolor{black}{MHD2040AllB7} and
%\textcolor{black}{MHD2070B7}) because they depend on the bow shock
%volume which shrinks as the star's bulk motion increases, see Paper~I 
%and Eq.~(\ref{eq:bslum}), or if the mass-loss of the moving star increases 
%at a given space velocity (see our models \textcolor{black}{MHD2070B7} and \textcolor{black}{MHD4070AllB7}).
%This suggests that bow shocks produced by high-mass stars of about $40\, \rm
%M_{\odot}$ and slowly-moving with velocities of about $20\, \rm km\, \rm s^{-1}$
%have the most important mass flux through their forward shocks and are
%consequently the principal momentum-depositer bow shocks in the Galactic plane.
%We note that, according to our models, the amount of momentum deposited into 
%the ISM is about $10^{39}$$-$$10^{40}\, \rm g\, \rm cm\, \rm s^{-1}$, i.e. about 
%2-3 orders of magnitude smaller that one of a cometary-like $\HII$ region surrounding a
%typical fast-moving OB star~\citep[see e.g.][]{mackey_sept_2014}. This suggests that 
%runaway massive star's feedback is not an important process in the replenishing 
%of the ISM in terms of linear momentum.

%\begin{table}
%	\centering
%	\caption{
%	\textcolor{black}{Bow shock linear momentum feedback (in $\rm g\, \rm cm\, \rm s^{-1}$)}. 
%	}
%	\begin{tabular}{cc}
%	\hline
%	\hline
%	Model        &  Momentum ($\rm g\, \rm cm\, \rm s^{-1}$)    \\ \hline   
%	MHD1020B7    &  $1.26\times 10^{36}$     \\ 
%	MHD2020B7    &  $8.73\times 10^{39}$     \\ 
%	HD2040       &  $2.98\times 10^{39}$     \\ 
%	MHD2040B3.5  &  $1.42\times 10^{39}$     \\ 
%	MHD2040AllB7    &  $1.37\times 10^{39}$     \\ 
%	MHD2070B7    &  $2.99\times 10^{38}$     \\ 
%	MHD4070AllB7    &  $3.93\times 10^{40}$     \\ 
%	\hline    
%	\hline 
%	\end{tabular}
%\label{table_feedback}
%\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Results: dust continuum infrared emission}
\label{sect:infrared}

%\subsubsection{\textcolor{black}{Calculation method}}
%\label{sect:infrared_method}

\subsubsection{Spectral energy distribution}
\label{sect:infrared_seds}

\textcolor{black}{
Fig.~\ref{fig:dust}b plots a comparison betwenn the SEDs of two bow shock models 
generated by our $20\, \rm M_{\odot}$ star moving with velocity $40\, \rm km\, 
\rm s^{-1}$,  either through an unmagnetized ISM (model 
MS2040, solid blue line) or in a medium with $B_{\rm ISM}=7\, \mu\rm G$ (model MHD2040AllB7, 
dotted red line) for a viewing angle of the nebulae of $\phi=0\degree$. The 
figure represents the flux density $F_{\lambda}$ (in $\rm Jy$) as a function of 
the wavelength $\lambda$ (in $\mu \rm m$) for the waveband including the 
$0.01\le \lambda \le 2000 \, \mu \rm m$. The star is 
responsible for the component in the range $0.01\le \lambda \le 10 \, \mu \rm m$ 
that corresponds to a black body spectrum of temperature $T_{\rm eff}=33900\, 
\rm K$ (see Table~\ref{tab:wind_para}) while the circumstellar dust produces 
the feature in the waveband $10\le \lambda \le 2000 \, \mu \rm m$.  
The bow shock's component is in the waveband including the wavelengths at which 
stellar wind bow shock are typically recorded, e.g. at $60\, \mu \rm m$~\citet{buren_apj_329_1988,
vanburen_aj_110_1995,noriegacrespo_aj_113_1997}. 
}

\textcolor{black}{
The SED of the magnetized bow shock has a slightly larger flux than the 
SED of the hydrodynamical bow shock in the waveband $10\le \lambda 
\le 30\, \mu \rm m$, because its smaller size makes the shell of dense ISM 
gas closer to the star, increasing therefore the dust temperature (Fig.~\ref{fig:dust}b). 
At $\lambda \approx 30\, \mu \rm m$, the hydrodynamical bow shock emits by slightly 
more than half an order of magnitude than the magnetized nebula, 
e.g. at $\lambda \approx 60\, \mu \rm m$ our model MS2040 has a density flux 
$F_{\lambda} \approx 3\times 10^{-1}\, \rm Jy$ whereas our model MHD2040AllB7 shows  
$F_{\lambda} \approx 1\times 10^{-1}\, \rm Jy$, respectively. This is consistent 
with the previously discussed reduction of the projected optical emission of 
our bow shocks. This relates to the changes in size of the nebulae induced by 
the inclusion of the magnetic field in our simulations, which reduces the mass of dust in 
the structure responsible for the reprocessing of the starlight, e.g. 
our models MS2040 and MHD2040AllB7 contain about 
$M_{\rm d}\approx3\times 10^{-2}\, \rm M_{\odot}$ and 
$M_{\rm d}\approx2\times 10^{-3}\, \rm M_{\odot}$, respectively, where 
$M_{\rm d}$ is the dust mass trapped into the nebulae. The reduced mass    
of dust into the magnetized bow shock absorbs a lesser amount of the stellar 
radiation and therefore re-emits a smaller quantity of energy,  
reducing $F_{\lambda}$ in the waveband $\lambda\ge\, 30\, \mu$m 
(Fig.~\ref{fig:dust}b). 
Note that the infrared 
surface brightness of a bow shock is also sensible to the density of its ambient 
medium, i.e. $F_{\lambda}$ is much larger in the situation of a runaway star moving 
in a medium with $n_{\rm ISM}\simeq 1000\, \rm cm^{-3}$~\citep{acreman_mnras_456_2016}.  
%
%Interestingly, those SEDs confirm that %the component of the SED corresponding 
%to the bow shock peaks in the $3 \le \lambda \le 50$ waveband, as 
%recently 
%conjectured n~\citet{meyer_mnras_459_2016}. Interestingly, this prediction 
%relative to the observability of circumstellar nebulae from moving massive 
%stars is also valid for magnetized bow shocks. 
}

\subsubsection{Synthetic infrared emission maps}
\label{sect:infrared_maps}

\textcolor{black}{
Our Fig.~\ref{fig:maps1} plots a series of synthetic infrared emission maps of our bow 
shock models produced by an initially $20\, \rm M_{\odot}$ star moving with 
velocity $40\, \rm km\, \rm s^{-1}$ in its purely hydrodynamical (MS2040) or 
magneto-hydrodynamical configuration (MHD2040AllB7) at the wavelengths 
corresponding to the central wavelengths of the {\it IRAS} facility's main 
broadband images~\citep{vanburen_apj_329_1988}, i.e. $\lambda=25\, \rm \mu m$ (left column 
of panels), $60\, \rm \mu m$ (middle column of panels) and $100\, \rm \mu m$ 
(right column of panels). The maps are represented with an inclination angle of 
$\phi=30\degree$ (Fig.~\ref{fig:maps1}a,e,i), $45\degree$ 
(Fig.~\ref{fig:maps1}b,f,j), $60\degree$ (Fig.~\ref{fig:maps1}c,g,k) and 
$90\degree$ (Fig.~\ref{fig:maps1}d,h,l) with respect to the plane of the 
sky and the projected flux is plotted in units of $\rm erg\, \rm s^{-1}\, \rm 
cm^{-2}\, \rm arcsec^{-2}$. As in the context of their optical emission 
(Fig.~\ref{fig:maps}), the overall size of the infrared magnetized bow shocks is 
smaller than in the hydrodynamical case because of the reduction of their 
stand-off distance $R(0)$, see, e.g. Fig.~\ref{fig:maps1}a,e,j. 
The global morphology of our infrared bow shock 
nebulae does not change significantly. It remains a single, bright arc at the 
front of an ovoid structure that is symmetric with respect to the direction of 
motion of the runaway star and extended to the trail ($z \le 0$) of the bow shocks 
due to the supersonic motion of the star~\citet{acreman_mnras_456_2016}. In the 
hydrodynamical case, the region of maximum emission is the region containing the 
ISM dust which temperature is smaller than a few $10^{4}\, \rm K$, i.e. 
between the contact discontinuity and the forward shock of the bow 
shock~\citep[Paper~I,][]{acreman_mnras_456_2016} whereas in the magnetized case, 
the maximum emission is reduced to a thin region close to the discontinuity 
between hot stellar wind and colder ISM. Both the shocked stellar wind and the 
shocked ISM of the bow shock do not contributes to these emission 
because the material is too hot. 
}

\textcolor{black}{
Fig.~\ref{fig:cuts_mhd} reports cross-sections taken along the direction of 
motion of the bow shock and comparing their surface brightesses at several 
wavebands $\lambda$ and viewing angles $\phi$. It illustrates that, as in the 
case of the optical emission, the presence of the ISM magnetic field makes the 
bow shocks slightly dimmer, e.g. for $\phi=45\degree$ our model has a maximal 
surface brighness of $\Sigma^{\rm max}_{100\,\mu\rm m} \approx 4.3\times 
10^{-17}\, \rm erg\, \rm s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$ whereas 
$\Sigma^{\rm max}_{100\,\mu\rm m} \approx 2.6\times 10^{-17}\, \rm erg\, \rm 
s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$ for $B_{\rm ISM}=0$ and $7\, \mu\rm G$, 
respectively. Fig.~\ref{fig:cuts} shows different cross-sections of the 
projected infrared emission the magnetized bow shock of our initially $20\, \rm 
M_{\odot}$ star moving with velocity $v_{\star}=40\, \rm km\, \rm s^{-1}$. The 
emission at $\lambda=60\, \mu\rm m$ is more important that at $\lambda=25\, 
\mu\rm m$ and at $\lambda=100\, \mu\rm m$, e.g. it peaks at $\Sigma^{\rm 
max}_{60\,\mu\rm m} \approx 8.2 \times 10^{-17}\, \rm erg\, \rm s^{-1}\, \rm 
cm^{-2}\, \rm arcsec^{-2}$ whereas $\Sigma^{\rm max}_{25\,\mu\rm m} \approx 2.6 
\times 10^{-17}\, \rm erg\, \rm s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$ and 
$\Sigma^{\rm max}_{100\,\mu\rm m} \approx 3.0 \times 10^{-17}\, \rm erg\, \rm 
s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$, respectively, at a distance of $0.55\, 
\rm pc$ from the star and assuming an inclination angle of the bow shock of 
$\phi=45\degree$ (Fig.~\ref{fig:cuts}a). All our models have similar behaviour 
of their infrared surface brightness as a function of $\lambda$ and $\phi$. Note 
also that the evolution of the position of the stand-off distance of the bow 
shock is consistent with the study of~\citet{acreman_mnras_456_2016} in the 
sense that it increases at larger $\phi$ (Fig.~\ref{fig:cuts}b). 
}

%\textcolor{black}{
%For $\lambda > 25\, \mu\rm m$ and for both the models MS2040 and 
%MHD2040AllB7, the brightness of our bow shocks decreases as a function 
%f the increasing wavelength, i.e. $\Sigma_{60} \approx 7.0\times 10^{-17}$ 
%hereas $\Sigma_{100} \approx 5.2\times 10^{-17}\, \rm erg\, 
%rm s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$ for $\phi=45\degree$, respectively, for the 
%ydrodynamical model with $\phi=45\degree$. This can be explained by the 
%onotonical decrease of $F_{\lambda}$ in the waveband $\lambda \ge \, 60\, \mu$, 
%ee Fig.~\ref{fig:feedback}. At similar $\lambda$ and $\phi$, our magneto-hydrodynamical 
%bow shocks are fainter than their hydrodynamical equivalent. All our models report such 
%trends concerning their isophotal infrared emission. This makes, under our 
%assumptions, the $\lambda=25\, \rm \mu m$ wavelength the ideal tool to observe 
%our stellar wind bow shocks in the Galactic plane. 
%The presence of the magnetic field therefore reduces $\Sigma_{60}$ and $\Sigma_{100}$ 
%by up to an order of magnitude, respectively. This difference 
%is less important in the case of our optical synthetic emission maps (see our 
%Table~\ref{tab:sigma} and Fig.~\ref{fig:maps}).
%}

\begin{figure*}
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./plot_wavelengths.eps}
	\end{minipage} 
	\begin{minipage}[b]{ 0.48\textwidth}
		\includegraphics[width=1.0\textwidth]{./plot_angles.eps}
	\end{minipage}  	
	\caption{
		\textcolor{black}{Cross-sections taken through the direction of motion of the bow shock 
of our initially $20\, \rm M_{\odot}$ star moving in a medium with $B_{\rm ISM}=7\, \mu\rm G$ 
with velocity $v_{\star}=40\, \rm km\, \rm s^{-1}$. The emission are shown for the principal 
broadband images of the $\it IRAS$ telescope for a viewing angle $\phi=45\degree$ (a) and for 
the wavelength $\lambda=60\, \mu\rm m$ as a function of different viewing angle $\phi$ (b).  
The surface brightness (in $\rm erg\, \rm s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$) is plotted as a 
function of the distance to the star (in $\rm pc$). The position of the star is located at the origin.} 
		 }
	\label{fig:cuts}  
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Implications of our results and discussion}
\label{sect:implication}

\subsubsection{Bow shocks H$\alpha$ and [OIII] observability}
\label{sect:observability}

The surface brightnesses at H$\alpha$ and $[\rm O{\sc III}]$ $\lambda \, 5007$
spectral line emission of our stellar wind bow shocks reported in
Table~\ref{sect:obs} indicate that (i) the presence of the ISM magnetic field makes their
projected emission $\Sigma_{\rm H \alpha}$ and $\Sigma_{[\rm OIII]}$ fainter by
two and 1$-$2 orders of magnitude and (ii) that this reduction of the nebulae's
emission is more important as the strength of the B field is larger.
Consequently, the emission signature of a purely hydrodynamical bow shock model
that is above the the diffuse emission sensitivity threshold of, e.g. the
SuperCOSMOS H-Alpha Survey (SHS) of $\Sigma_{\rm SHS}\approx1.1$-$2.8\times
10^{-17}\, \rm erg\, \rm s^{-1}\, \rm cm^{-2}\, \rm arcsec^{-2}$ \textcolor{black}{can drop down below it} 
once the ISM magnetic field is switched-on. As an example, our
hydrodynamical model of a $20\, M_{\odot}$ star moving with velocity
$v_{\star}=70\, \rm km\, \rm s^{-1}$ (Paper~I) could be observed since it has
$\Sigma_{\rm H \alpha}\approx 1.5\times 10^{-16} \ge \Sigma_{\rm SHS}$ whereas
our magneto-hydrodynamical model of the same runaway star has $\Sigma_{\rm H
\alpha}\approx 8.0\times 10^{-18} \ll \Sigma_{\rm SHS}$ and would be invisible
regarding to the SHS facility (our Table~\ref{tab:sigma}).

This may explain why not so many stellar wind bow shocks are discovered at 
H$\alpha$ around isolated, hot massive stars, despite of the fact the ionisation 
of their circumstellar medium must produce such 
emission~\citep{brown_aa_439_2005}. Since $\Sigma_{\rm H \alpha}\propto n^{2}$ 
(see Appendix A of Paper~I), it implies that the more diluted the ISM 
constituting the surrounding of an exiled star, i.e. the higher the runaway 
star's Galactic latitude, the smaller the probability to observe its bow shock 
at H$\alpha$. In other words, the search for bow shocks at this wavelength may 
work well within the Galactic plane or in relatively dense regions of the ISM. 
Note also that in the presence of the magnetic field, all models have 
$\Sigma_{[\rm OIII]}/\Sigma_{\rm H \alpha}>1$, which is consistent with the 
discovery of the first bow-shock-producing massive stars $\zeta$ Ophiuchi in 
$[\rm OIII]$ $\lambda \, 5007$ emission.

\subsubsection{Surrounding \hii region and dust composition}
\label{sect:hii_region}

\textcolor{black}{
Massive stars release huge amount of ultraviolet 
photons~\citep{diazmiller_apj_501_1998} that ionize the hydrogen constituting  
their surroundings~\citep{dyson_ass_35_1975}, giving birth to an \hii region 
overwhelming the stellar wind bubble of the 
star~\citep{weaver_apj_218_1977,vanmarle_phd_2006}. In the case of a runaway 
star, the stellar motion produces a bow shock surrounded by a cometary \hii 
region~\citep{raga_apj_300_1086,maclow_apj_369_1991,raga_rmxaa_33_1997, 
arthur_apjs_165_2006,zhu_apj_812_2015}, which presence in our study is simply 
taken into account assuming that the ambient medium of the star is fully 
ionized, however, we neglect its turbulent internal structure. The gas that is 
between the forward shock of the bow shock and the outer part of the \hii region 
is filled by ISM dust that emits infrared thermal emission by efficiently 
reprocessing the stellar radiation, i.e. it is brighter that the emission by 
gas cooling (Paper~I). 
}

\textcolor{black}{
While our study shows that our nebulae are brighter at $60\, \mu \rm m$ 
(Fig.~\ref{fig:cuts}), i.e. at the waveband at which catalogues of bow shocks 
from OB stars have been 
compiled~\citep{buren_apj_329_1988,vanburen_aj_110_1995,
noriegacrespo_aj_113_1997}, the study of~\citet{mackey_aa_586_2016} compared the 
respective brightnesses of the front of a distorted circumstellar bubble with 
the outer edge of its surrounding \hii region and find the $24\, \mu \rm m$ 
waveband to be ideal to observe the structure generated by the stellar wind. 
However, the presence of the ISM background magnetic field makes our infrared 
arc  smaller and slightly dimmer, i.e. more difficult to detect in the case of a 
distant runaway star which could explain why a large proportion of observed \hii 
regions do not contain dust-free cavities encircled with bright mid-infrared 
arcs~\citep{sharpless_apj_1959,churchwell_apj_649_2006,watcher_aj_139_2010,
simpson_mnras_424_2012}. Further radiation magneto-hydrodynamics simulations are 
required to fully assess the question of the infrared screening of stellar wind bow shocks by 
their own \hii regions, particularly for an ambient medium corresponding to the 
Galactic plane ($n_{\rm ISM}\simeq1\, \rm cm^{-3}$). 
}

\textcolor{black}{ 
Following~\citet{pavlyuchenkov_rep_57_2013}, we consider that the dust filling 
the \hii region and penetrating into the bow shock is similar of that of the 
ISM. Our radiative transfer calculations nevertheless suffer from uncertainties 
regarding to the composition of this ISM dust. Our mixture is made of 
Silicates~\citep{draine_apj_285_1984} which could be modified, e.g. changing the slope 
of the dust size distribution. Particularly, the inclusion of very small grains such as polycyclic 
aromatic hydrocarbon~\citep[PAHs, see][]{wood_apj_688_2008} may be an 
appropriate update of the dust mixture, as it have been shown to be necessary 
to fit observations of mid-infrared bow shocks around O stars in dense medium in 
M17 and RCW 49~\citep{povich_apj_689_2008}. Enlarging our work in a wider study, 
e.g. scanning the parameter space of the quantities governing the formation of 
Galactic stellar wind bow shocks ($v_{\star}$, $n_{\rm ISM}$, $M_{\star}$) in 
order to discuss both their SEDs and infrared images will be considered in a 
follow-up paper, e.g. performing a systematic post-processing of the grid of bow 
shock simulations of~\citet{meyer_mnras_459_2016} with {\sc radmc-3d}. Then, 
thorough comparison of numerical simulations with, e.g. the {\it IRAS} 
observations 
of~\citet{buren_apj_329_1988,vanburen_aj_110_1995,noriegacrespo_aj_113_1997}  
would be achievable.  
}

%\begin{figure}
%	\begin{minipage}[b]{ 0.48\textwidth}
%		\includegraphics[width=1.0\textwidth]{./cut.eps}
%	\end{minipage} 	
%	\caption{
%	         \textcolor{black}{
%	         Cross-sections taken along the direction of motion of the moving star in
%	         our model MHD2040AllB7, considered with an inclination angle of $\phi=0\degree$. 
%	         The position of the star is located at the origin. 
%	         } 
%		 }
%	\label{fig:cuts}  
%\end{figure}

%\begin{figure}
%		\centering
%	\begin{minipage}[b]{ 0.4\textwidth}
%		\centering
%		\includegraphics[width=1.0\textwidth]{./map_4070_60deg_60mm_legend.eps}
%	\end{minipage} \\	
%	\begin{minipage}[b]{ 0.4\textwidth}
%		\centering	
%		\includegraphics[width=1.0\textwidth]{./map_4070_45deg_60mm_legend.eps}
%	\end{minipage} \\
%	\begin{minipage}[b]{ 0.4\textwidth}
%		\centering
%		\includegraphics[width=1.0\textwidth]{./map_4070_30deg_60mm_legend.eps}
%	\end{minipage} 
%	\caption{
%	         \textcolor{black}{
%	         Same as Fig~\ref{fig:maps1} for our initially $40\, \rm M_{\odot}$ 
%	         star moving with velocity $70\, \rm km\, \rm s^{-1}$. The images are 
%	         computed at $\lambda=60\, \rm \mu m$. This illustrates the effects of the ISM 
%	         magnetic field on the dust continuum emission of a thin-shelled 
%	         bow shock. 
%		 }
%		 }
%	\label{fig:maps2}  
%\end{figure}

%\subsubsection{\textcolor{black}{Magnetized thin-shelled bow shocks and implications}}
%\label{sect:instatilities}

%\textcolor{black}{
%In Fig.~\ref{fig:maps2} we plot additional isophotal infrared emission maps at
%$\lambda=60\, \rm \mu m$ of the hydrodynamical bow shock model MS4070 that
%develops a thin shell and its corresponding magnetized model MHD4070AllB7, i.e. the only
%difference between those simulations is the absence/presence of the ISM
%background magnetic field. The maps are generated for the viewing
%angles $\phi=30$ (a), $45$ (b) and $60\degree$ (c). As previously discussed with
%respect to their density fields, the magnetisation of the ISM changes the
%overall stability of the bow shock and the arc-like nebulae around
%runaway stars having a thin-shell become stable because of the suppression of
%Kelvin-Helmholtz and Vishniac instabilities that affects their dense, rippled
%region of shocked ISM material (see Fig.~\ref{fig:mhd4070all}). Neverthess, the 
%size of (clumpy) filaments (see Fig.~\ref{fig:maps2}b,c) is largely resolvable 
%by, e.g. the about 2 arcsec resolution of some {\it Spitzer} surveys~\citep{povich_apjs_194_2011}. 
%The characteristic ring-like projection artefacts of an unstable bow shock (that
%would be a clumpy pattern in the case of a full tri-dimensional simulation)
%disappear in the magnetize case, whatever is the considered inclination angle of
%the bow shock (Fig.~\ref{fig:maps2}a-c), since the thin shell is replaced by a
%thicker layer of shocked ISM gas (Fig.~\ref{fig:mhd4070all}). 
%}

%\textcolor{black}{
%As an additional effect of projection, the ring-like artefacts may resemble 
%broken arcs if viewed from a specific angle ($\phi \le 45\degree$, see 
%Fig.~\ref{fig:maps2}a-b). Note that such may be produced if the star experiences 
%mass-loss pulsation, as discuss for red supergiant runaway stars in~\citet{2}. 
%In other words, it is very difficult to morphologically discriminate a smooth, 
%magnetized bow shock produced by a star that would generated a thin shell if it would be in a 
%%non-magnetized medium, from a non-magnetized bow shock without a thin shell 
%(which would also be smooth, albeit fainter, if it would be moving in a magnetized 
%environment), since both would look stable. 
%Furthermore, if one assumes that the ISM is always magnetized, this implies that
%thin-shelled bow shocks do not really exist, at least in the warm phase of 
%the ISM with $n_{\rm ISM}\approx1\, \rm
%cm^{-3}$. Nonetheless, this may not be correct in high density medium where the 
%ISM thermal and ram pressures are very important since Wilkin's analytic solution 
%has been shown to be accurate to fit $24\, \mu\rm m$ {\it Spitzer} infrared 
%bow shocks in the Carina nebula~\citep{sexton_mnras_446_2015}. 
%}

\subsubsection{Shaping of the circumstellar medium of runaway massive stars at the pre-supernova phase}
\label{sect:presn}

It has been shown in the context of Galactic, high-mass runaway stars, that the 
pre-shaped circumstellar medium in which these stars die and explode as a type 
II supernova is principally constituted of its own main-sequence wind bubble, 
distorted by the stellar motion. Further evolutionary phase(s) produce 
additional bubble(s) and/or shell(s) whose evolution is contained inside the 
initial bow shock~\citep{brighenti_mnras_270_1994, brighenti_mnras_277_1995}. 
The expansion   of the subsequent supernova shock wave is strongly impacted by 
the progenitor's pre-shaped circumstellar medium inside which it develops 
initially~\citep[see, e.g.][]{cox_mnras_250_1991}. Particularly, the more 
well-defined and stable the walls of the tunnel formed by the reverse shock of 
the bow shock are, the easier the channeling the supernovae ejecta inside 
it~\citep[see in particular Appendix A of][and references 
therein]{meyer_mnras_450_2015}.

Our study shows that the presence of background ISM magnetic field aligned with
the direction of motion of a main-sequence runaway star inhibits the growth of
both shear instabilities that typically affect these
circumstellar structures (Fig.~\ref{fig:physics}).
Consequently, a planar-aligned magnetic field would further shape the reverse
shock of moving stars' bow shocks as a smooth tube in which shocks waves could
be channeled as a jet-like extension, e.g. as in~\citet{cox_mnras_250_1991}.
Additionally, the shock wave outflowing out of the forward shock of circumstellar 
structures of runaway stars that are sufficiently dense to make their
subsequent supernova remnant asymmetric~\citep{meyer_mnras_450_2015} would be
more collimated along the direction of motion of its progenitor and/or ambient magnetic
field. \textcolor{black}{This may produce additional asymmetries to the elongated shape 
of supernovae remnants exploding in a magnetized ISM~\citep{rozyczka_274_MNRAS_1995}.}

\subsubsection{The case of the hot runaway star $\zeta$ Ophiuchi}
\label{sect:obs}

The O9.5 V star $\zeta$ Ophiuchi is the Earth's closest massive, main-sequence 
runaway star. Infrared observations, e.g. with the ${\it WISE}$ $3.4\, \mu m$ 
facility~\citep[band W1, ][see Fig.~\ref{fig:obs}\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky/}]{wright_aj_140_2010} highlighted the complex topology of its stellar wind bow 
shock, originally discovered in [O{\sc iii}] $\lambda \, 5007$ spectral 
line~\citep{gull_apj_230_1979} and further observed in the infrared 
waveband~\citep{vanburen_apj_329_1988}. The properties of the particular, 
\textcolor{black}{non-axisymmetric} shape of its circumstellar nebula which moves 
in the \hii region Sh 2-27~\citep{sharpless_apj_1959} is studied in a relatively 
large literature~\citep[see][and references therein]{mackey_mnras_2013}. The 
mass-loss of $\zeta$ Ophiuchi has been estimated in the range $\dot{M}_{\zeta} 
\approx 1.58 \times 10^{-9}$$-$ $1.43 \times 10^{-7}\, \rm M_{\odot}\, \rm 
yr^{-1}$~\citep{gvaramadze_mnras_427_2012}, which, according to 
Eq.~(\ref{eq:Ro}), taking $R(0)\approx\, 0.16\, \rm 
pc$~\citep{gvaramadze_mnras_427_2012}, adopting $v_{\star} \approx 26.5\, \rm 
km\, \rm s^{-1}$ and considering a typical OB star wind velocity of $v_{\rm 
w}\approx1500\, \rm km\, \rm s^{-1}$, constrains its ambient medium density to 
$n_{\zeta}\approx 3$-$4\, \rm cm^{-3}$~\citep[cf.][]{gull_apj_230_1979}.

\textcolor{black}{
Assuming (i) the magnetisation of the close surrounding of $\zeta$ Ophiuchi to be 
$B_{\rm ISM}=7\, \mu \rm G$~\citep{mackey_mnras_2013}, (ii) that the 
conditions for switch-on shocks to be permitted are fulfilled, i.e. plasma and Alfv\' enic 
velocities are normal to the shock, and (iii)} considering that its
ISM properties are, in addition to the above presented quantities, such that
$\gamma=1.67$, $T_{\rm ISM}=8000\, \rm  K$, it comes that \textcolor{black}{$\beta \ge 2/\gamma$} 
and $M_{\rm A}<1$. \textcolor{black}{This indictes that, under our hypothesises, 
the ambient medium of $\zeta$ Ophiuchi  
does not allow the existence of switch-on shocks. Consequently, the imperfect 
shape of its bow shock (Fig.~\ref{fig:obs}) may not be explained invoking the
particular double-front topology of bow shocks that can be produced in such regime, but 
rather by the presence of a background ISM magnetic field whose direction is
not aligned with respect to the motion of the star.} Further
tri-dimensional \textcolor{black}{magneto-hydrodynamical models are needed in order to
assess the question} of $\zeta$ Ophiuchi's background ISM magnetic field direction, the
position of its contact discontinuity and a more precise estimate of its stellar
wind mass-loss.

\subsubsection{The case of runaway cool stars}
\label{sect:coolstars}

Our results apply to bow shocks generated by hot, main-sequence OB stars that 
move through the hot ionized gas of their own \hii 
region~\citep{raga_rmxaa_33_1997} and archetype of which is the nebulae 
surrounding $\zeta$ Ophiuchi (see above discussion). Externally-photoionized 
cool runaway stars that move rapidly in the \hii region produced by an other 
source of ionizing radiation have particularly bright optical emission, see e.g. 
the cases of the red supergiant Betelgeuse~\citep{mohamed_aa_541_2012,2014Natur.512..282M} and 
IRC$-$10414~\citep{meyer_mnras_439_2014}. These circumstellar structures are 
themselves \textcolor{black}{sensitive} to the presence of even a weak ISM 
background magnetic field of a few $\mu \rm G$~\citep{vanmarle_aa_561_2014}. 
Consequently, one can expect that the inclusion of such a field in numerical 
models tailored to these objects would affect their associated synthetic 
emission maps and update the current estimate of their driving star's mass loss 
and/or ambient medium density~\citep{meyer_mnras_459_2016}.

\textcolor{black}{
According to the fact that the warm phase of the ISM is typically magnetized, the 
reduction of both optical and infrared surface brightnesses of circumstellar 
structures generated by massive stars should be a rather common phenomenon. In 
particular, it should also concern bow shocks of OB runaway stars once they have 
evolved through the red supergiant phase (Paper~I).
However, the proportion of red supergiant stars amongst the population of all 
runaway massive stars should be similar to the proportion of red supergiant 
with respect to the population of static OB stars, which is, to the best of 
our knowledge, contradicted by observations. The recent study of~\citet{vanmarle_aa_561_2014}
shows that a background ISM magnetic field can inhibits the growth of shear 
instabilities, i.e. forbids the development of potentially bright infrared 
knots, in the bow shock of Betelgeuse, and, this may participate in 
explaining why the scientific literature only reports 4 known runaway red 
superigant stars, amongst which only 3 have a detected bow shock, i.e. 
Betelgeuse~\citep{noriegacrespo_aj_114_1997}, 
IRC$-$10414~\citep{meyer_mnras_439_2014} and $\mu$ 
Cep~\citep{cox_aa_537_2012}. The extragalactic, hyperveloce red supergiant star 
J004330.06+405258.4 in M31 has all kinematic characteristics to generate a bow 
shock but it has not been observed so far~\citep{evans_aj_150_2015}. 
This remark is also valid for bow shocks generated by runaway massive stars 
experiencing other evolutionary stages such as the so-called blue supergiant 
phase~\citep[see, e.g.][]{kaper_apj_475_1997}. 
}

\subsubsection{Comparison with the bow shock around the Sun}
\label{sect:sun}

\textcolor{black}{
The Sun is moving into the warm phase of the ISM~\citep{mccomas_apj_801_2015} 
and the properties of its ambient surrounding, the so-called local interstellar 
medium (LISM) are similar to the ISM in which our runaway stars move, especially 
in terms of Alfv\' enic Mach number and plasma 
$\beta$~\citep{florinski_apj_604_2004,burlaga_apj_804_2015}. The study of the 
interaction between our Sun and the LISM led to a large literature, including, 
amongst other, numerical investigations of the bow shock formed by the solar 
wind~\citep[see, e.g.][and references 
therein]{pogorelov_JGR_103_1998,baranov_jgr_1993,zank_araa_53_2015}. If obvious similitudes between the 
bow shock of the Sun and those of our massive stars indicate that the physical 
processes governing the formation of circumstellar nebulae around OB stars such 
as electronic thermal conduction or the influence of the background local 
magnetic field have to be included in the modelling of those 
structures~\citep{zank_ssrv_146_2009}, nevertheless, the bow shock of the Sun 
is, partly due to the differences in terms of effective temperature and wind 
velocity, on a totally different scale. Further resemblances with bow-like 
nebulae from massive stars are therefore mostly morphological. 
}

\textcolor{black}{ 
As a low-mass star ($<8\, \rm M_{\odot}$), the Sun is much cooler ($T_{\rm eff}\approx 6000\, \rm K$) 
than the runaway OB stars considered in the present work ($T_{\rm eff} > 
20000\, \rm K$) and its mass-loss ($\dot{M}_{\odot}\approx 10^{-14}\, \rm M_{\odot}\, 
\rm yr^{-1}$) is much smaller than that of a main-sequence star with 
$M_{\star} \ge 20\, \rm M_{\odot}$ (our Table~\ref{tab:wind_para}), 
which makes its stellar luminosity fainter by several orders of magnitude 
($L_{\star}/L_{\odot} \ge 10^{3}$). Moreover, the solar wind velocity at 
1 $\rm AU$ is about $350\, \rm km\, \rm s^{-1}$~\citep{golub_1997} 
whereas our OB stars have larger wind velocities ($>1000\, \rm km\, 
\rm s^{-1}$, see Table~\ref{tab:wind_para}). 
Stellar winds from solar-like stars consequently develop a smaller ram pressure 
and expel less linear momentum than massive stars such as our $20\, \rm 
M_{\odot}$ star and their associated corresponding circumstellar structures, i.e. wind 
bubbles or bow shocks are scaled down to a few tens or hundreds of $\rm AU$. 
Note also that the Sun is too cool to produce ionizing radiations and generated 
an \hii region that is susceptible screen its optical/infrared wind bubble. In other 
words, if the numerical methods developed 
to study the bow shock surrounding the Sun are similar to the ones utilised in 
our study, the solar solutions are more appropriated to investigate the surroundings 
of cool, low-mass stars such as, asymptotic giant stars (AGB), see~\citep{wareing_apj_660_2007, 
WareingZijlstraOBrien_2007_MNRAS_382_1233_AGB_bowshocks,raga_apj_680_2008,
esquivel_apj_725_2010,villaver_apj_748_2012,chiotellis_mnras_547_2016}, 
or the trails let by planetesimals moving in stellar systems presenting a common 
envelope~\citep[see][and references therein]{thun_aa_589_2016}. 
}

\textcolor{black}{
Early two-dimensional numerical models of the solar neighbourhood were carried out assuming 
that the respective directions of both the Sun's motion and the LISM magnetic 
field are considered as parallel, as we hereby do with our massive 
stars~\citep{pogorelov_JGR_103_1998}. More sophisticated simulations have produced three-dimensional 
models in which the Sun moves obliquely through the LISM~\citep[see, 
e.g.][]{baranov_astl_22_1996,boley_apj_776_2013}. Such investigation is  observationally motivated 
by the perturbated and non-uniform appearance of the heliopause, e.g. the 
boundary between the interplanetary and interstellar 
medium~\citep{kawamura_2010} which revealed the need for 3D calculations,  able 
to report the non-stationary character of the trail of the bow shock of the 
Sun~\citep{washimi_ssrv_78_1996,linde_jgr_103_1998,ratkiewicz_aa_335_1998}. 
Those models are more complex than our simplistic two-dimensional simulations 
and investigate, e.g. the charges exchanges arising between the stellar wind 
and the LISM~\citep{fitzenreiter_jgr_95_1990}. These studies also 
highlighted the complexity and fragility of such models, e.g. regarding to the 
variety of instable MHD discontinuities that affects shock waves propagating 
through a magnetized flow and differentiating the shocks from purely 
hydrodynamical discontinuities described by the Rankine-Hugoniot~\citep[see 
also][]{sterck_phpl_1998,sterck_aa_343_1999}. Additionally, those solutions are 
affected by the spatial resolution of the calculations and the inclusion of 
numerical viscosity in the models~\citep[][and references 
therein]{lopez_angeo_29_2011,wang_jgra_119_2014}. 
}

\begin{figure*}
	\begin{minipage}[b]{ 0.76\textwidth}
		\includegraphics[width=1.0\textwidth]{./bs.eps}
	\end{minipage} 
	\caption{
	         ${\it WISE}$ $3.4\, \mu m$~\citep[band W1, ][]{wright_aj_140_2010} 
	         observation of the stellar wind bow shock surrounding the massive 
	         runaway O9.5 V star $\zeta$ Ophiuchi. \textcolor{black}{The image 
	         represents about $35\, \rm arcmin$ in the horizontal direction, 
	         which at a distance of $112\, \rm pc$ 
	         corresponds to about $1.12\, \rm pc$.} 
		 }
	\label{fig:obs}  
\end{figure*}

\textcolor{black}{
Finally, let mention an other obvious difference between bow shock of the Sun and 
the nebulae generated by the runaway OB stars that we model. The proximity of the Earth 
with the Sun makes it easier to be studied and analysed by means of, e.g. radio 
observations~\citep{baranov_sovastronlett_1_1975} while its innermost 
substructures are directly reachable with spacecrafts such as {\it Voyager 1} and 
{\it Voyager 2}\footnote{http://voyager.jpl.nasa.gov/mission/interstellar.html}. 
Their missions partly consisted in leaving the neighbourhood of our Sun in order 
to explore the heliosheath, i.e. the layer corresponding to the region of shocked solar wind 
that is between the contact discontinuity (the heliopause) and the 
reverse shock of the solar bow shock (the wind termination shock). The {\it Voyager} 
engines crossed the outermost edge of the solar system between 2004 and 2007 at a the expected 
distance of 94 and 84 AU from the Earth~\citep{linde_jgr_103_1998}, giving 
the first experimental data on 
the physics of the interstellar medium~\citep{chalov_mnras_455_2016}. Those 
measures proved the existence of the solar bow shock, but also highlighted the 
particular conditions of the outer space in terms of magnetic 
phenomenon~\citep{richardson_2016} and effects of cosmic 
rays~\citep{webber_2016}. In order to make our models more realistic, those 
physical processes should be taken into account into future simulations of bow 
shocks from runaway high-mass stars.  
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
\label{section:conclusion}

% Summarise the work
In this study, we present\textcolor{black}{ed} magneto-hydrodynamical models of the
circumstellar medium of runaway, main-sequence, massive stars moving
supersonically through the plane of the Galaxy. Our two-dimensional simulations first
investigate\textcolor{black}{d} the conjugated effects of optically-thin radiative cooling and
heating together with anisotropic thermal transfers on a field-aligned, 
magneto-hydrodynamical bow shock flow around an OB-type, fast-moving star. We
then explore\textcolor{black}{d} the effects of the stellar motion with respect to the bow shocks, 
focusing on an initially $20\, \rm M_{\odot}$ star moving with velocities
$v_{\star}=20$, $40$ and $70\, \rm km\, \rm s^{-1}$. We present\textcolor{black}{ed} additional
models of an initially $10\, \rm M_{\odot}$~\textcolor{black}{star} moving with velocities
$v_{\star}=40\, \rm km\, \rm s^{-1}$ and of an initially $40\, \rm M_{\odot}$~\textcolor{black}{star} 
moving with velocities $v_{\star}=70\, \rm km\, \rm s^{-1}$. The ISM magnetic
field strength is set to $B_{\rm ISM}=7\, \mu \rm G$. We also
consider\textcolor{black}{ed} bow shock nebulae produced within a weaker ISM magnetic field ($B_{\rm
ISM}=3.5\, \mu \rm G$). The other ISM properties are unchanged for each models.

% Here: governing processes, shape, luminosity and details, momentum feedback 
Our models show that although the magnetization of the ISM does not radically
change the global aspect of our bow shock nebulae, it slightly modifies their
internal organiation. Anisotropic thermal transfers do not split the region of
shocked ISM gas as in our hydrodynamical models (Paper~I), since the presence of
the magnetic field in the regions of shocked material \textcolor{black}{forbids heat 
conduction perpendicular to the magnetic field lines}. 
\textcolor{black}{The field lines, initially parallel to the direction of stellar
motion, are bent round by the bow shock into a sheath around
the fast stellar wind bubble.}
%They adopt the structure of a hot,
%low-density region of shocked wind surrounded by a cold, dense layer of shocked
%ISM gas. 
\textcolor{black}{As showed in~\citet{heitsch_apj_665_2007}}, the presence 
of the magnetic field stabilises \textcolor{black}{the} contact
discontinuities inhibiting the growth of the Kelvin-Helmholtz instabilities that typically
occur in pure hydrodynamical models at the interface between shocked ISM and shocked stellar wind.

%We also find that it prevents the bow shocks \textcolor{black}{of} fast-moving, high-mass stars from
%developing a thin shell \textcolor{black}{liable to the developement of} Vishniac-related
%instabilities, as it has been shown in the hydrodynamical
%context~\citep{blondin_na_57_1998}. 
%Note that due to Consequently, the analytical 
%solution regarding to their morphology given in~\citet{wilkin_459_apj_1996} 
%is not suitable to describe them.

% Emission maps and feedback
As in our previous hydrodynamical study (Paper~I), bow shocks are brighter
in infrared reprocessed starlight. Their emission by optically-thin radiation
mostly originates from the shocked ISM and their [O{\sc iii}] $\lambda \, 5007$
spectral line emission are higher than their H$\alpha$ emission. Notably, their 
X-rays emission are negligible compared to their optical luminosity and
therefore it does not constitute the best waveband to search for hot massive stars'
stellar wind bow shocks. We find that the presence of an ISM background 
magnetic field \textcolor{black}{has the effect of} reducing the optical 
synthetic emission maps of our models, 
making them fainter by one and two orders
of magnitude at [O{\sc iii}] $\lambda \, 5007$ and H$\alpha$, respectively. This
may explain why not so many of them are observed at these spectral lines. We
confirm that, under our assumptions and even in the presence of a magnetic field, 
circumstellar structures produced by high-mass, slowly-moving stars are the 
easiest observable bow shock nebulae in the warm neutral phase of the Milky Way.

% Infrared 
\textcolor{black}{
We performed dust continuum radiative transfer calculations of our bow 
shocks models~\citep[cf.][]{acreman_mnras_456_2016} and generated spectral 
energy distributions and isophotal emission maps for different wavelengths $25\, 
\le \lambda\, \le 100\, \mu\rm m$ and viewing angles $0\degree\, \le \phi\, \le 90\degree$. 
Consistently with the observation of~\citet{buren_apj_329_1988,vanburen_aj_110_1995,noriegacrespo_aj_113_1997}, 
the calculations show that our bow shocks are brighter at $60\, \mu\rm m$. 
The projected infrared emission can also be diminished the presence of the ISM magnetic field, 
in particular at wavelengths $\lambda\ge 60\, \mu\rm m$, since the amount of 
dust trapped into the bow shock is smaller. We also notice that 
the change in surface brightness of our emission maps as a function of 
the viewing angle of the bow shock is similar as in the optical waveband, i.e. it 
is brighter if $\phi=0\degree$ and fainter if $\phi=90\degree$~\citep[see][]{meyer_mnras_459_2016}. 
}

% Speak about $zeta$ Ophiuchi 
In future models, we would like to extend this pioneering study of 
massive stars' bow shocks within the magnetized ISM towards 
three-dimensional models in which the ISM magnetic field is unaligned with
respect to the motion of the star, as it has been done in order to appreciate
its influence on the morphology of the global
heliopause~\citep{pogorelov_JGR_103_1998}. Such simulations will help to
better understand the structure of the circumstellar nebulae forming
around hot, ionising, massive runaway stars and allow us to predict more
accurately, e.g. the optical emission signatures of these bow shocks.
Thorough comparison with particular hot, bow-shock-producing massive stars, 
e.g. $\zeta$ Ophiuchi, might then be feasible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgements}

The authors thank Tom Hartquist, for his kind help and very helpful advices 
when reviewing this paper and Richard Stancliffe for numerous 
grammatical comments when carefully reading the manuscript.
%
D.~M.-A.~Meyer gratefully thanks T. Robitaille and C. Dullemond for their 
support with the {\sc hyperion} and the {\sc radmc-3d} raditative 
transfer codes, respectively, as well as D. Thun for fruitful discussion concerning his master thesis.
%
Are also acknowledged Prof. R. Jalabert and G. Weick from the Institute of 
Physics and Chemistry of Materials of Strasbourg (IPCMS) for their kind help 
concerning the Mie theory. 
% 
This study was in parts conducted within the Emmy Noether research group on
"Accretion Flows and Feedback in Realistic Models of Massive Star Formation" 
funded by the German Research Foundation under grant no. KU 2849/3-1.  
%
\textcolor{black}{
The authors gratefully acknowledge the computing time provided on the 
supercomputer JUROPA at J\" ulich Supercomputing Centre (JSC) 
and on the bwGrid cluster T\" ubingen. 
}
%
This research has made use of ''Aladin sky atlas" and ``VizieR catalogue access 
tool" both developed at CDS, Strasbourg Observatory, France.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Bibliography style for the bibtex
\bibliographystyle{mn2e}

\footnotesize{
% Create the reference Section using BibTeX:
\bibliography{grid}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-20 papers/Papers1234/app-intermediate.tex
Transformation of basis vectors, but not sure this is right approach
Need to transform the points or the basis, but not both

@@
 \end{equation}
-This is used in equation~\eqref{eq:Trans}.
+This is used in equation~\eqref{eq:Trans}.  A further application is
+to find the observer-frame Cartesian basis vectors by rotating the
+body-frame basis:
+\begin{align}
+  \label{eq:xunit-prime}
+  \uvec{x}' &= \mathbfss{A}_y(i)\, \uvec{x}
+              =
+              \begin{Vector}
+              \cos i \\ 0 \\ \sin i  
+              \end{Vector}
+  \\
+  \label{eq:yunit-prime}
+  \uvec{y}' &= \mathbfss{A}_y(i)\, \uvec{y}
+              =
+              \begin{Vector}
+              0 \\ 1 \\ 0
+              \end{Vector}
+  \\
+  \label{eq:zunit-prime}
+  \uvec{z}' &= \mathbfss{A}_y(i)\, \uvec{z}
+              =
+              \begin{Vector}
+              -\sin i \\ 0 \\ \cos i  
+              \end{Vector}
+\end{align}
 
@@
 \end{align}
+These are then to the observer frame in equations~\eqref{eq:nprime}
+and \eqref{eq:tprime} by use of equation~\eqref{eq:Rotation-matrix-y}.
+
+The first equality in equation~\eqref{eq:tanphi} is found by
+substituting equations~\eqref{eq:nprime} and~\eqref{eq:zunit-prime}
+in~\eqref{eq:tangent-line-condition}, yielding
 

### 2018-01-20 papers/Papers1234/sec-projection.tex
Transformation of basis vectors, but not sure this is right approach
Need to transform the points or the basis, but not both

@@
 equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis with the matrix
-\(\mathbfss{A}_x(\phi)\)(see Appendix~\ref{sec:plane-sky-projection}) and
-then converting to the observer frame by use of
+\(\mathbfss{A}_x(\phi)\) and then rotating to the observer frame with
+\(\mathbfss{A}_y(i)\)
+
+by use of
 equation~(\ref{eq:Trans}) to give
-\begin{gather}
+\begin{equation}
   \label{eq:nprime}
@@
     \end{aligned}
-  \end{aligned}\\
+  \end{aligned}
+\end{equation}
+\begin{equation}
   \label{eq:tprime}
@@
   \end{aligned}
-\end{gather}
+\end{equation}
+
 \subsection{Tangent line}
@@
 
-Projective space \(\mathbb{RP}^2\) or \(\mathbbm{RP}^2\) or \(\mathds{RP}^2\)
-
 \subsection{Line-of-sight velocities on the tangent line}

### 2018-02-21 papers/Papers1234/sec-conclusions.tex
Finish Meyer tracing fig and write about it (unfinished)

--- 2017-12-05 papers/Paper1/sec-conclusions.tex
@@
 \label{sec:more-realistic-bow}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/M17-composite}
+  \caption[]{Procedure for tracing the contact discontinuity from the
+    \citet{Meyer:2017a} simulations.  The density maps from
+    \citeauthor{Meyer:2017a}'s Fig.~3 are converted to FITS format and
+    displayed using the software \textsc{SAOImage DS9}.  The density
+    contour at \SI{0.4}{cm^{-3}} is displayed (shown in green in the
+    figure) and this is traced by hand by placing ``point regions'' on
+    the image (shown by black ``x'' shapes in the figure).  The zoom
+    facility of the software allows the points to be placed with any
+    required accuracy.  The points are saved to a file in the DS9
+    region file format, which is then read by Python programs for
+    further processing.  For example, the yellow boxes show circle
+    fits and determination of the parameters \(R_0\), \(R_c\), and
+    \(R_{90}\).  In this example, only the points shown in orange
+    (within \ang{60} of axis) are used in the fits.}
+  \label{fig:meyer-trace}
+\end{figure}
 
@@
 the radiative cooling in the shocked stellar wind is even less
-efficient.  This represents a gross violation of the assumptions
+efficient.  This represents a significant violation of the assumptions
 behind the thin-shell models, since the total shocked shell thickness
-is of the same order as \(R_0\).  The parabolic departure function
+is of the same order as \(R_0\).
+
+We have traced the the shape of the contact discontinuity in the two
+models, using the procedure outlined in Figure~\ref{fig:meyer-trace}.
+
+The parabolic departure function
 (see \S~\ref{sec:parab-depart-funct}) for the shape of the contact

### 2018-02-22 papers/Papers1234/sec-conclusions.tex
Finish addressing ref point about Meyer comparison

@@
 behind the thin-shell models, since the total shocked shell thickness
-is of the same order as \(R_0\).
-
-We have traced the the shape of the contact discontinuity in the two
-models, using the procedure outlined in Figure~\ref{fig:meyer-trace}.
-
-The parabolic departure function
-(see \S~\ref{sec:parab-depart-funct}) for the shape of the contact
-discontinuity\footnote{%
+is of the same order as \(R_0\).  Nevertheless, the emissivity of
+several observationally important emission processes, such as
+mid-infrared thermal dust emission and the optical H\(\alpha\) emission
+line, is concentrated near the contact discontinuity,\footnote{%
   Note that, in the non-magnetic HD models, efficient thermal
@@
   contact discontinuities coincide. } %
-in the two models is shown in Figure~\ref{fig:sim-depart} as blue
-symbols.\footnote{%
-  Measured from Figure~3 of \citet{Meyer:2017a} by tracing the
-  \SI{0.4}{cm^{-3}} density contour.} %
-The MHD simulation shows a strongly negative dip in the departure
-function close to the apex (\(\cos \theta = 1\)), indicating a very flat
-shape.\footnote{%
+so it is reasonable to use this surface as a first approximation for
+the shape of the bow.
+
+We have traced the contact discontinuity in the two models, using the
+procedure outlined in Figure~\ref{fig:meyer-trace}, and show results
+for the parabolic departure function (see
+\S~\ref{sec:parab-depart-funct}) as blue symbols in
+Figure~\ref{fig:sim-depart}.  The MHD simulation shows a strongly
+negative dip in the departure function close to the apex
+(\(\cos \theta = 1\)), indicating a very flat shape.\footnote{%
   \citet{Meyer:2017a} speculate that this flatness may be the

### 2018-02-26 papers/Papers1234/app-rcurv-empirical.tex
Make multi-panel fig for new circle fits to 000-400
Make new section for 000-400 comparison

@@
 \end{equation}
-A refinement of the method is then to repeat the circle fit after
-restricting the set of points to those lying within a certain angle
-\(\Delta\theta\) of the bow axis by requiring
+A refinement of the method is then to iteratively repeat the circle
+fit after restricting the set of points to those lying within a
+certain angle \(\Delta\theta_\C\) of the bow axis by requiring
 \begin{equation}
@@
   \ge   {\Abs{\bm{r}_k - \bm{r}_{\C}^*}}
-  \cos \Delta\theta \ ,
+  \cos \Delta\theta_C \ ,
 \end{equation}
-where we find that best results are obtained with \(\Delta\theta \le \ang{30}\).
+where we find that best results are obtained with \(\Delta\theta_\C \approx \ang{30}\).
 

### 2018-02-26 papers/Papers1234/sec-conclusions.tex
Make new section for 000-400 comparison
Remove RA, Dec axes and add scale bar and compass

@@
 
+\section{Example application to observations}
+\label{sec:obs}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
+  \caption{Example empirical determination of planitude and alatude
+    for an observed bow shock.  An \textit{HST} H\(\alpha\) image (ACS
+    F658N filter) of M42~000-400 is shown in color scale and contours
+    \citep{Bally:2006a}.}
+  \label{fig:000-400-fit}
+\end{figure*}
+
+As an example of measuring the projected planitude and alatude of a
+real bow shock, we present an analysis of the H\(\alpha\) emission arc
+associated with the proplyd M42~000-400 in the west of the Orion
+Nebula \citep{Bally:2000a},\footnote{%
+  The same object is listed as 4596-400 in some catalogs, such as
+  \citet{Ricci:2008a}.  } %
+which was used as an archetype of the bow shape in
+Figure~\ref{fig:bow-terminology}.
+
 \section{Summary and discussion}

### 2018-02-26 papers/Papers1234/sec-conclusions.tex
Expand figure caption for 000-400 fits

@@
   \caption{Example empirical determination of planitude and alatude
-    for an observed bow shock.  An \textit{HST} H\(\alpha\) image (ACS
-    F658N filter) of M42~000-400 is shown in color scale and contours
-    \citep{Bally:2006a}.}
+    for an observed bow shock.  Color scale and contours show an
+    \textit{HST} H\(\alpha\) image (ACS F658N filter,
+    \citealp{Bally:2006a}) of M42~000-400. Three different bows have
+    been traced by hand on the image (red and white filled symbols):
+    (\textit{a})~outer edge, (\textit{b})~ridge of maximum emission,
+    and (\textit{c})~inner edge.  For each panel, the dark-colored
+    circle shows the initial fit to the full set of points (white and
+    red), using the algorithm described in
+    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
+    derived axis are shown by a small filled circle and dashed line in
+    the same color. Lighter colored circles show three subsequent
+    iterations where the fit is restricted to points within
+    \(\pm\ang{75}\) of the axis.  The subset of points used in the
+    final iteration is marked in red.  In panels \textit{b} and
+    \textit{c} the iterations converge immediately, but in panel
+    \textit{a} the iterations stably oscillate between two slightly
+    different solutions.  (\textit{d})~Location of the converged
+    circle fits in the projected planitude--alatude plane.  Each
+    solution has two values of the alatude \(\Lambda'\), corresponding to
+    \(R_{90}^+\) and \(R_{90}^-\).}
   \label{fig:000-400-fit}

### 2018-02-26 papers/Papers1234/app-rcurv-empirical.tex
Add material to appendix E on the circle fits to data

--- 2017-12-06 papers/Papers1234/app-rcurv-empirical.tex
@@
   \label{eq:rcurv-mean-radius}
-  \bar{R}(x_{\C}, y_{\C}) = \frac{1}{N}  \sum_{k = 1}^{N} \Abs{\bm{r}_k - \bm{r}_{\C}}  \ .
+  \bar{R}_\C(x_{\C}, y_{\C}) = \frac{1}{N}  \sum_{k = 1}^{N} \Abs{\bm{r}_k - \bm{r}_{\C}}  \ .
 \end{equation}
-We then optimize\footnote{%
-  For example, using a Levenberg-Marquardt algorithm, such as
-  \texttt{astropy.modeling.fitting.LevMarLSQFitter} from the AstroPy
-  library \citep{Astropy-Collaboration:2013a}.} %
+We then optimize
+% \footnote{%
+%   For example, using a Levenberg-Marquardt algorithm, such as
+%   \texttt{astropy.modeling.fitting.LevMarLSQFitter} from the AstroPy
+%   library \citep{Astropy-Collaboration:2013a}.} %
 to find best-fit values \((x_{\C}^*, y_{\C}^*)\), which minimize the
@@
   f(x_{\C}, y_{\C}) = \sum_{k = 1}^{N} \left(
-    \abs{\bm{r}_k - \bm{r}_{\C}}  - \bar{R} (x_{\C}, y_{\C}) \right)^2 \ .
+    \abs{\bm{r}_k - \bm{r}_{\C}}  - \bar{R}_\C (x_{\C}, y_{\C}) \right)^2 \ .
 \end{equation}
 The best-fit radius of curvature is then given by
-\(R_{\C}^* = \bar{R}(x_{\C}^*, y_{\C}^*)\).
+\(R_{\C}^* = \bar{R}_\C(x_{\C}^*, y_{\C}^*)\).
 
@@
 \end{equation}
-A refinement of the method is then to repeat the circle fit after
-restricting the set of points to those lying within a certain angle
-\(\Delta\theta\) of the bow axis by requiring
+A refinement of the method is then to iteratively repeat the circle
+fit after restricting the set of points to those lying within a
+certain angle \(\Delta\theta\) of the bow axis, where we find that best results
+are obtained with \(\Delta\theta \approx \ang{60}\) to \ang{75}.  That is, 
 \begin{equation}
   \label{eq:rcurv-delta-theta}
-  \uvec{\xi} \cdot 
-  {\left( \bm{r}_k - \bm{r}_{\C}^* \right) }
-  \ge   {\Abs{\bm{r}_k - \bm{r}_{\C}^*}}
-  \cos \Delta\theta \ ,
+  \Abs{\theta_k} < \Delta\theta \ , 
 \end{equation}
-where we find that best results are obtained with \(\Delta\theta \le \ang{30}\).
+where the angle \(\theta_k\) of each point from the axis, measured at the
+source position \(r_0\), can be calculated\footnote{%
+  Note that the cross product (\(\times\)) of the 2d vectors is assumed to
+  yield the (signed scalar) \(z\) component, also known as the
+  ``perpendicular dot product''.} %
+as
+\begin{equation}
+  \label{eq:rcurv-theta-k}
+  \theta_k = \arctan \left[  
+    \frac{\left( \bm{r}_k - \bm{r}_0 \right) \times \uvec{\xi}}
+    {\left( \bm{r}_k - \bm{r}_0 \right) \cdot \uvec{\xi}}
+  \right] \ .
+\end{equation}
+Two or three iterations are sufficient for convergence in most cases,
+although in some cases it is possible that the process will converge
+to a stable flip-flop oscillation between two different solutions.
+This is due to the dependence of the \(\theta_k\), via \(\uvec{\xi}\), on
+the \(\bm{r}_{\C}^*\) of the previous iteration, which can lead to
+points entering and leaving the fitted set.  We have not found this to
+be a serious problem in practice, since the two solutions tend to be
+very close to one another.  It could be mitigated by averaging
+\(\bm{r}_{\C}^*\) over two previous iterations.  The alternative of
+measuring the angle with respect to the center of curvature,
+\(\bm{r}_{\C}^*\), instead of the source, \(\bm{r}_0\), is found to be
+much less stable.
 
@@
 measurements of \(\bm{r}_k\), then it is appropriate to incorporate
-weights of \(\epsilon_k^{-2}\) in the objective function.  In cases where the
-bow shape is traced by eye, based on real or synthetic observations, a
-more practical approach is to maintain uniform weighting but to place
-a greater density of points \(\bm{r}_k\) in regions where the shape is
-well-determined and to place them more sparsely in regions where the
-shape is less certain.
+weights of \(\epsilon_k^{-2}\) in the objective function.  However, in cases
+where the bow shape is traced by eye, based on real or synthetic
+observations, a more practical approach is to maintain uniform
+weighting but to place a greater density of points \(\bm{r}_k\) in
+regions where the shape is well-determined and to place them more
+sparsely in regions where the shape is less certain.
 
-Note that this method is not necessary if the orientation of the bow
-axis is known a~priori, in which case the Taylor series method
-described in \S~\ref{sec:plan-alat-bow} is more efficient and
-accurate.
+Since there is no guarantee of symmetry about the axis \(\uvec{\xi}\),
+the perpendicular radius will in general be different in the two wings
+of the bow, with values \(R_{90}^+\) and \(R_{90}^-\).  These can be
+estimated by defining
+\begin{equation}
+  \label{eq:rcurv-R-k}
+  R_k = \Abs{\bm{r}_k - \bm{r}_0}
+\end{equation}
+and linearly interpolating between the points \((\theta_k, R_k)\) at
+\(\theta = \pm \ang{90}\).
+
+Our Python language implementation of this algorithm is freely
+available at \url{https://github.com/div-B-equals-0/circle-fit}.  An
+example application to real data is given in \S~\ref{sec:obs} and
+Figure~\ref{fig:000-400-fit}.  Note that this method is not necessary
+if the orientation of the bow axis is known a~priori, in which case
+the Taylor series method described in \S~\ref{sec:plan-alat-bow} is
+more efficient and accurate.
 

### 2018-02-27 papers/Papers1234/sec-conclusions.tex
Now we have two separate figures for the 000-400 fits

--- 2018-02-22 papers/Papers1234/sec-conclusions.tex
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
+  \caption[]{Example empirical determination of planitude and alatude
+    for an observed bow shock.  Color scale and contours show an
+    \textit{HST} H\(\alpha\) image (ACS F658N filter,
+    \citealp{Bally:2006a}) of M42~000-400. Three different bows have
+    been traced by hand on the image (red and white filled symbols):
+    (\textit{a})~inner edge, (\textit{b})~ridge of maximum emission,
+    and (\textit{c})~outer edge.  For each panel, the dark-colored
+    circle shows the initial fit to the full set of points (white and
+    red), using the algorithm described in
+    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
+    derived axis are shown by a small filled circle and dashed line in
+    the same color. Lighter colored circles show three subsequent
+    iterations where the fit is restricted to points within
+    \(\pm \Delta\theta = \ang{75}\) of the axis.  The subset of points used in
+    the final iteration is marked in red.  The perpendicular radii for
+    the final iteration are shown by dotted lines. In panels
+    \textit{b} and \textit{c} the iterations converge immediately, but
+    in panel \textit{a} the iterations stably oscillate between two
+    slightly different solutions. }
+  \label{fig:000-400-fit}
+\end{figure*}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/000-400-planitude-alatude}
+  \caption[]{Location in the projected planitude--alatude plane of the
+    converged circle fits to the M42~000-400 bow.  For each solution,
+    the two values of the alatude \(\Lambda'\), corresponding to
+    \(R_{90}^+\) and \(R_{90}^-\), are joined by a vertical
+    line. Large symbols show the results from the fits shown in
+    Figure~\ref{fig:000-400-fit}, while small symbols show results for
+    fits using \(\Delta\theta = \ang{60}\) instead of \ang{75}.}
+  \label{fig:000-400-planitude-alatude}
+\end{figure}
+
+\section{Example application to observations}
+\label{sec:obs}
+
+As an example of measuring the projected planitude and alatude of a
+real bow shock, in Figure~\ref{fig:000-400-fit} we present an analysis
+of the H\(\alpha\) emission arc associated with the proplyd M42~000-400 in
+the west of the Orion Nebula \citep{Bally:2000a},\footnote{%
+  The same object is listed as 4596-400 in some catalogs, such as
+  \citet{Ricci:2008a}.  } %
+which was used as an archetype of the bow shape in
+Figure~\ref{fig:bow-terminology}.  To give an idea of the systematic
+uncertainties and sensitivity to subjective choices, three different
+tracings of the bow shape are considered: the peak of the emission arc
+(``ridge''), and its inner and outer edges
+(Fig.~\ref{fig:000-400-fit}\textit{a}--\textit{c}).  In all three
+cases, we placed the points that define the bow by eye, using
+SAOImage~DS9 in a similar fashion to in Figure~\ref{fig:meyer-trace},
+and guided by the image contours.\footnote{%
+  In the case of the ``ridge'' method at least, it is possible to
+  automate this step, which we will discuss in detail in a following
+  paper. } %
+The principal hindrance to an accurate tracing of the bow shape in
+this object is the strong and variable nebular background emission,
+which particularly affects the far wing on the right hand side of the
+image, where a bright background filament is superimposed on the bow.
+
 \section{Summary and discussion}

### 2018-02-27 papers/Papers1234/app-rcurv-empirical.tex
More refinements of Appendix E
Now use "perp scalar product" instead of vector product

@@
 source position \(r_0\), can be calculated\footnote{%
-  Note that the cross product (\(\times\)) of the 2d vectors is assumed to
-  yield the (signed scalar) \(z\) component, also known as the
-  ``perpendicular dot product''.} %
+  In equation~\eqref{eq:rcurv-theta-k}, the ``perpendicular'' operator
+  (\(\perp\)) rotates its vector argument counter-clockwise by \ang{90},
+  so that \((x, y)^\perp = (-y, x)\).} %
 as
@@
   \theta_k = \arctan \left[  
-    \frac{\left( \bm{r}_k - \bm{r}_0 \right) \times \uvec{\xi}}
+    \frac{\left( \bm{r}_k - \bm{r}_0 \right) \cdot \uvec{\xi}^\perp}
     {\left( \bm{r}_k - \bm{r}_0 \right) \cdot \uvec{\xi}}
@@
 measurements of \(\bm{r}_k\), then it is appropriate to incorporate
-weights of \(\epsilon_k^{-2}\) in the objective function.  However, in cases
+weights of \(\epsilon_k^{-2}\) in the objective function.  However, it is
+rare for the \(\epsilon_k\) to be objectively quantifiable, since the
+uncertainties are often systematic and/or subjective.  In cases
 where the bow shape is traced by eye, based on real or synthetic

### 2018-02-27 papers/Papers1234/app-rcurv-empirical.tex
New figure of planitude versus Delta theta

@@
 \end{equation}
-where the angle \(\theta_k\) of each point from the axis, measured at the
-source position \(r_0\), can be calculated\footnote{%
-  In equation~\eqref{eq:rcurv-theta-k}, the ``perpendicular'' operator
-  (\(\perp\)) rotates its vector argument counter-clockwise by \ang{90},
-  so that \((x, y)^\perp = (-y, x)\).} %
-as
+where the signed angle \(\theta_k\) of each point from the
+axis,\footnote{%
+  Although the sign of \(\theta_k\) is not relevant to
+  equation~\eqref{eq:rcurv-delta-theta}, it is used below in
+  calculating the perpendicular radii.  } %
+measured at the source position \(r_0\), can be calculated as
 \begin{equation}
@@
 \end{equation}
+In the preceding equation, the ``perpendicular'' operator (\(\perp\))
+rotates its vector argument counter-clockwise by \ang{90}, so that
+\((x, y)^\perp = (-y, x)\).
+
 Two or three iterations are sufficient for convergence in most cases,

### 2018-02-27 LL-shapes-2017/000-400-Pi-vs-Dtheta.py

@@ -1,0 +1,31 @@
+INPUT=[["D theta", "Outer", "Ridge", "Inner"], [45, 1.775, 8.342, 3.312], [50, 1.775, 8.342, 2.771], [55, 2.153, 4.343, 3.163], [60, 2.186, 3.262, 3.163], [65, 2.395, 4.217, 2.692], [70, 2.478, 3.664, 2.911], [75, 2.749, 3.318, 2.721], [80, 2.749, 3.642, 2.858], ["Median", 2.291, 3.941, 2.885], ["MAD", 0.323, 0.513, 0.179]]
+import sys
+import numpy as np
+from astropy.table import Table
+from matplotlib import pyplot as plt
+import seaborn as sns
+
+tab = Table(rows=INPUT[1:9], names=INPUT[0])
+
+figfile = sys.argv[0].replace('.py', '.pdf')
+
+sns.set_color_codes()
+
+fig, ax = plt.subplots(figsize=(4, 4))
+arcs = "Inner", "Outer", "Ridge"
+colors = 'mcr'
+m = tab['D theta'] >= 60.0
+for arc, color in zip(arcs, colors):
+    mean = np.mean(tab[arc][m])
+    sigma = np.std(tab[arc][m])
+    label = fr"{arc}: ${mean:.1f} \pm {sigma:.1f}$"
+    ax.plot(tab['D theta'], tab[arc], 'o', color=color, label=label)
+ax.legend()
+ax.set(ylim=[0.0, 9.0],
+       xlabel=r"$\Delta \theta$, degrees",
+       xticks=tab['D theta'],
+       ylabel=r"Fitted $\Pi'$")
+sns.despine(trim=True)
+fig.tight_layout()
+fig.savefig(figfile)
+print(figfile, end='')

### 2018-02-27 papers/Papers1234/sec-conclusions.tex
Write more about the 000-400 fits in the text

@@
     the final iteration are shown by dotted lines. In panels
-    \textit{b} and \textit{c} the iterations converge immediately, but
-    in panel \textit{a} the iterations stably oscillate between two
+    \textit{a} and \textit{b} the iterations converge immediately, but
+    in panel \textit{c} the iterations stably oscillate between two
     slightly different solutions. }
@@
 
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/000-400-Pi-vs-Dtheta}
+  \caption[]{Sensitivity of fitted planitude to the parameter
+    \(\Delta\theta\), which controls how close a point must be to the axis in
+    order to be included in the circle fit. }
+  \label{fig:000-400-Delta-theta}
+\end{figure}
+
 \section{Example application to observations}
@@
 As an example of measuring the projected planitude and alatude of a
-real bow shock, in Figure~\ref{fig:000-400-fit} we present an analysis
-of the H\(\alpha\) emission arc associated with the proplyd M42~000-400 in
-the west of the Orion Nebula \citep{Bally:2000a},\footnote{%
+real bow shock, we present an analysis of the H\(\alpha\) emission arc
+associated with the proplyd M42~000-400 in the west of the Orion
+Nebula \citep{Bally:2000a},\footnote{%
   The same object is listed as 4596-400 in some catalogs, such as
@@
 uncertainties and sensitivity to subjective choices, three different
-tracings of the bow shape are considered: the peak of the emission arc
-(``ridge''), and its inner and outer edges
-(Fig.~\ref{fig:000-400-fit}\textit{a}--\textit{c}).  In all three
+tracings of the bow shape are considered (see
+Fig.~\ref{fig:000-400-fit}): the peak of the emission arc (``ridge''),
+and its inner and outer edges.  In all three
 cases, we placed the points that define the bow by eye, using
@@
 image, where a bright background filament is superimposed on the bow.
+
+We determine the planitude and alatude by fitting a circle to the
+traced points within \(\pm \Delta\theta = \ang{75}\) bow axis, using the
+iterative algorithm described in Appendix~\ref{app:rcurv-empirical}.
+The fitted circle, when combined with the position of the central
+source, yields the orientation of the bow axis, together with the apex
+distance, \(R_0\), radius of curvature, \(R_\C\), and two
+perpendicular radii (one for each wing), \(R_{90}^+\) and
+\(R_{90}^-\).  These are all indicated on the panels of
+Figure~\ref{fig:000-400-fit} by light-colored lines.\footnote{%
+  For conciseness, we drop the prime symbol from the radii in this
+  section and Appendix~\ref{app:rcurv-empirical}, even though all the
+  quantities are projected ones.} %
+The projected planitude and alatude then follow as \(\Pi = R_\C/R_0\),
+\(\Lambda^+ = R_{90}^+/R_0\), \(\Lambda^- = R_{90}^-/R_0\), which are shown in Figure~\ref{fig:000-400-planitude-alatude}.
+
+The planitude is found to have a moderate dependence on the choice of
+\(\Delta\theta\), as shown in Figure~~\ref{fig:000-400-Dtheta}. The fact that
+the radius of curvature is defined at a point (the projected apex)
+might seem to argue for making \(\Delta\theta\) as small as possible, but that
+leads to an extreme sensitivity of the circle fits to the exact
+positions of the few points that are included in the fit.  A reliable
+fit requires 4 or more points, which span a total separation
+\(\approx R_\C\).
 

### 2018-02-28 papers/Papers1234/sec-conclusions.tex
More on how results vary with Delta theta

@@
 The planitude is found to have a moderate dependence on the choice of
-\(\Delta\theta\), as shown in Figure~~\ref{fig:000-400-Dtheta}. The fact that
-the radius of curvature is defined at a point (the projected apex)
-might seem to argue for making \(\Delta\theta\) as small as possible, but that
-leads to an extreme sensitivity of the circle fits to the exact
-positions of the few points that are included in the fit.  A reliable
-fit requires 4 or more points, which span a total separation
-\(\approx R_\C\).
+\(\Delta\theta\), as shown in Figure~\ref{fig:000-400-Delta-theta}. The fact
+that the radius of curvature is defined at a point (the projected
+apex) might seem to argue for making \(\Delta\theta\) as small as possible, but
+that would lead to circle fits that were extremely sensitive to the
+exact positions of the few points included in the fit.  A reliable fit
+requires 4 or more points, ideally spanning a total separation that is
+a substantial fraction of \(R_\C\), which would argue for
+\(\Delta\theta\) larger than about \(\Pi/2\) radians, or \ang{60}--\ang{90}.  On
+the other hand, if \(\Delta\theta \ge \ang{90}\) then the planitude and alatude
+would no longer be independent since the bow would be forced to lie on
+the ``sphere'' line, \(\Lambda = (2 \Pi - 1)^{1/2}\) (see \S~\ref{sec:conic}).
+Balancing these two concerns suggests an optimal
+\(\Delta\theta = \ang{75}\), which is what is used in
+Figure~\ref{fig:000-400-fit}, but we also show results for both
+\ang{75} (thick lines) and \ang{60} (thin lines) in
+Figure~\ref{fig:000-400-planitude-alatude}.
+
+\(\Pi = 2.9 \pm 0.2 \pm 0.3\)
 

### 2018-02-28 papers/Papers1234/sec-conclusions.tex
Add 069-601 to the figure with images and circle fits

@@
   \centering
-  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
+  \includegraphics[width=\linewidth]{figs/new-two-arc-multi-fig}
   \caption[]{Example empirical determination of planitude and alatude
-    for an observed bow shock.  Color scale and contours show an
-    \textit{HST} H\(\alpha\) image (ACS F658N filter,
-    \citealp{Bally:2006a}) of M42~000-400. Three different bows have
-    been traced by hand on the image (red and white filled symbols):
-    (\textit{a})~inner edge, (\textit{b})~ridge of maximum emission,
-    and (\textit{c})~outer edge.  For each panel, the dark-colored
-    circle shows the initial fit to the full set of points (white and
-    red), using the algorithm described in
-    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
-    derived axis are shown by a small filled circle and dashed line in
-    the same color. Lighter colored circles show three subsequent
-    iterations where the fit is restricted to points within
+    for observed bow shocks associated with proplyds in the Orion
+    Nebula.  Color scale and contours show an \textit{HST} H\(\alpha\)
+    image (ACS F658N filter, \citealp{Bally:2006a}) of M42~000-400
+    (panels \textit{a--c}) and M42~069-601 (panels \textit{d--f}). Three
+    different bows have been traced by hand on the image (red and
+    white filled symbols): (\textit{a, d})~inner edge, (\textit{b,
+      e})~ridge of maximum emission, and (\textit{c, f})~outer edge.
+    For each panel, the dark-colored circle shows the initial fit to
+    the full set of points (white and red), using the algorithm
+    described in Appendix~\ref{app:rcurv-empirical}.  The center of
+    curvature and derived axis are shown by a small filled circle and
+    dashed line in the same color. Lighter colored circles show three
+    subsequent iterations where the fit is restricted to points within
     \(\pm \Delta\theta = \ang{75}\) of the axis.  The subset of points used in
@@
     the final iteration are shown by dotted lines. In panels
-    \textit{a} and \textit{b} the iterations converge immediately, but
-    in panel \textit{c} the iterations stably oscillate between two
+    \textit{a, b, d--f} the iterations converge immediately, but in
+    panel \textit{c} the iterations stably oscillate between two
     slightly different solutions. }
@@
 
-\begin{figure}
+\begin{figure*}
+  \begin{tabular}{p{0.45\linewidth} p{0.45\linewidth}}
+    (a) & (b) \\
     \includegraphics[width=\linewidth]{figs/000-400-planitude-alatude}
+    & \includegraphics[width=\linewidth]{figs/069-601-planitude-alatude}
+  \end{tabular}
   \caption[]{Location in the projected planitude--alatude plane of the
@@
   \label{fig:000-400-planitude-alatude}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
+  \begin{tabular}{p{0.45\linewidth} p{0.45\linewidth}}
+    (a) & (b) \\
     \includegraphics[width=\linewidth]{figs/000-400-Pi-vs-Dtheta}
+    & \includegraphics[width=\linewidth]{figs/069-601-Pi-vs-Dtheta}
+  \end{tabular}
   \caption[]{Sensitivity of fitted planitude to the parameter
@@
   \label{fig:000-400-Delta-theta}
-\end{figure}
+\end{figure*}
 

### 2018-02-28 LL-shapes-2017/new-000-400-circle-fit.py

@@ -1,0 +1,14 @@
+import sys 
+sys.path.append("/Users/will/Dropbox/circle-fit")
+import circle_fit
+
+for arc in "inner", "outer", "ridge":
+    for delta_theta in 45, 50, 55, 60, 65, 70, 75, 80:
+        plotfile = f"000-400-{arc}-{delta_theta:02d}.pdf"
+        print('#### '*10)
+        print("Creating", plotfile)
+        circle_fit.plot_solution(
+            f"new-w000-400-{arc}.reg",
+            "w000-400-Bally_09-extract.fits",
+            plotfile,
+            delta_theta=delta_theta)

### 2018-03-02 papers/Papers1234/app-rcurv-empirical.tex
Make table of the M42 bow fits

@@
 
-Consider a set of \(N\) points on the plane of the sky, with Cartesian
-coordinates \(\bm{r}_k = (x_k, y_k)\) for \(k = 1 \dots N\).  We wish
-to estimate the radius of curvature of the smooth curve that the set
-of points is presumed to be sampled from.  To do this, we fit a circle
-to the points as follows.  The circle is defined by its center,
-\(\bm{r}_{\C} = (x_{\C}, y_{\C})\), and radius, \(R_{\C}\).  For a
-given circle, we define a mean radius of the set of points from the
-circle center:
+Consider a set of \(N\) points on the plane of the sky,\footnote{%
+  In the main body of the paper, the prime symbol (\('\)) is used to
+  distinguish projected from ``true'' quantities.  In this Appendix,
+  for simplicity, we omit the primes since \emph{all} quantities are
+  projected.} %
+with Cartesian coordinates \(\bm{r}_k = (x_k, y_k)\) for
+\(k = 1 \dots N\).  We wish to estimate the radius of curvature of the
+smooth curve that the set of points is presumed to be sampled from.
+To do this, we fit a circle to the points as follows.  The circle is
+defined by its center, \(\bm{r}_{\C} = (x_{\C}, y_{\C})\), and radius,
+\(R_{\C}\).  For a given circle, we define a mean radius of the set of
+points from the circle center:
 \begin{equation}
@@
 the perpendicular radius will in general be different in the two wings
-of the bow, with values \(R_{90}^+\) and \(R_{90}^-\).  These can be
+of the bow, with values \(R_{90+}\) and \(R_{90-}\).  These can be
 estimated by defining

### 2018-03-02 papers/Papers1234/sec-conclusions.tex
Make table of the M42 bow fits

@@
     for observed bow shocks associated with proplyds in the Orion
-    Nebula.  Color scale and contours show an \textit{HST} H\(\alpha\)
-    image (ACS F658N filter, \citealp{Bally:2006a}) of M42~000-400
-    (panels \textit{a--c}) and M42~069-601 (panels \textit{d--f}). Three
-    different bows have been traced by hand on the image (red and
-    white filled symbols): (\textit{a, d})~inner edge, (\textit{b,
-      e})~ridge of maximum emission, and (\textit{c, f})~outer edge.
-    For each panel, the dark-colored circle shows the initial fit to
-    the full set of points (white and red), using the algorithm
-    described in Appendix~\ref{app:rcurv-empirical}.  The center of
-    curvature and derived axis are shown by a small filled circle and
-    dashed line in the same color. Lighter colored circles show three
-    subsequent iterations where the fit is restricted to points within
+    Nebula (M42).  Color scale and contours show an \textit{HST}
+    H\(\alpha\) image (ACS F658N filter, \citealp{Bally:2006a}) of
+    M42~000-400 (panels \textit{a--c}) and M42~069-601 (panels
+    \textit{d--f}).  The image scale and orientation are indicated on
+    panel~\textit{a} and are the same for all panels.  Three different
+    bows have been traced by eye on each object (red and white filled
+    symbols): (\textit{a, d})~inner edge, (\textit{b, e})~ridge of
+    maximum emission, and (\textit{c, f})~outer edge.  For each panel,
+    the dark-colored circle shows the initial fit to the full set of
+    points (white and red), using the algorithm described in
+    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
+    derived axis are shown by a small filled circle and dashed line in
+    the same color. Lighter colored circles show three subsequent
+    iterations where the fit is restricted to points within
     \(\pm \Delta\theta = \ang{75}\) of the axis.  The subset of points used in
@@
 \begin{figure*}
-  \begin{tabular}{p{0.45\linewidth} p{0.45\linewidth}}
+  \begin{tabular}{p{0.47\linewidth} p{0.47\linewidth}}
     (a) & (b) \\
@@
   \caption[]{Location in the projected planitude--alatude plane of the
-    converged circle fits to the M42~000-400 bow.  For each solution,
-    the two values of the alatude \(\Lambda'\), corresponding to
-    \(R_{90}^+\) and \(R_{90}^-\), are joined by a vertical
-    line. Large symbols show the results from the fits shown in
+    converged circle fits to the M42 bows: (\textit{a})~000-400,
+    (\textit{b})~069-601. For each solution, the two values of the
+    projected alatude, \(\Lambda_+'\) and \(\Lambda_-'\), corresponding to
+    \(R_{90+}\) and \(R_{90-}\), are joined by a vertical line. Large
+    symbols show the results from the fits shown in
     Figure~\ref{fig:000-400-fit}, while small symbols show results for
-    fits using \(\Delta\theta = \ang{60}\) instead of \ang{75}.}
+    fits using \(\Delta\theta = \ang{60}\) instead of \ang{75}. In panel
+    \textit{a}, two slightly different \(\Pi'\) values are shown for the
+    outer bow, since the fit does not converge to a single value (see
+    Fig.~\ref{fig:000-400-fit}\textit{c} and
+    App.~\ref{app:rcurv-empirical}).}
   \label{fig:000-400-planitude-alatude}
@@
   \end{tabular}
-  \caption[]{Sensitivity of fitted planitude to the parameter
-    \(\Delta\theta\), which controls how close a point must be to the axis in
-    order to be included in the circle fit. }
+  \caption[]{Variation of fitted planitude, \(\Pi'\), as a function of
+    the parameter \(\Delta\theta\), which controls how close a point must be to
+    the axis in order to be included in the circle
+    fit. (\textit{a})~M42 000-400, (\textit{b}) M42 069-601.  For the
+    three traced bows (inner, outer, and ridge) of each object, the
+    symbol key lists the mean and standard deviation of \(\Pi'\),
+    calculated over the ``stable'' range \(\Delta\theta = \ang{60}\) to
+    \ang{80}, which is indicated by light gray shading.}
   \label{fig:000-400-Delta-theta}
@@
 
-As an example of measuring the projected planitude and alatude of a
-real bow shock, we present an analysis of the H\(\alpha\) emission arc
-associated with the proplyd M42~000-400 in the west of the Orion
-Nebula \citep{Bally:2000a},\footnote{%
-  The same object is listed as 4596-400 in some catalogs, such as
-  \citet{Ricci:2008a}.  } %
-which was used as an archetype of the bow shape in
-Figure~\ref{fig:bow-terminology}.  To give an idea of the systematic
-uncertainties and sensitivity to subjective choices, three different
-tracings of the bow shape are considered (see
+As an example of measuring the projected planitude and alatude of real
+bow shocks, we present an analysis of M42~000-400 and M42~069-601,
+which are two H\(\alpha\) emission arcs \citep{Bally:2000a,
+  Gutierrez-Soto:2015a} associated with proplyds\footnote{%
+  The coordinate designation (see \citealp{ODell:1994a} for an
+  explanation of the nomenclature) of 000-400 is very imprecise in
+  right ascension, but we use it here for consistency with previous
+  papers. The associated proplyd is listed with the more correct
+  designation 4596-400 in catalogs such as \citet{Ricci:2008a}.  } %
+in the west of the Orion Nebula (M42).  An image of one of these arcs
+(M42~069-601) was used in the illustration of bow shock terminology in
+Figure~\ref{fig:bow-terminology}.
+
+We consider three different tracings of the bow shape (see
 Fig.~\ref{fig:000-400-fit}): the peak of the emission arc (``ridge''),
-and its inner and outer edges.  In all three
-cases, we placed the points that define the bow by eye, using
-SAOImage~DS9 in a similar fashion to in Figure~\ref{fig:meyer-trace},
-and guided by the image contours.\footnote{%
+and its inner and outer edges.  In all three cases, we placed by eye
+the points that define the bow, using SAOImage~DS9 in a similar
+fashion to in Figure~\ref{fig:meyer-trace}, and guided by the image
+contours.\footnote{%
   In the case of the ``ridge'' method at least, it is possible to
@@
   paper. } %
-The principal hindrance to an accurate tracing of the bow shape in
-this object is the strong and variable nebular background emission,
-which particularly affects the far wing on the right hand side of the
-image, where a bright background filament is superimposed on the bow.
 
@@
 distance, \(R_0\), radius of curvature, \(R_\C\), and two
-perpendicular radii (one for each wing), \(R_{90}^+\) and
-\(R_{90}^-\).  These are all indicated on the panels of
-Figure~\ref{fig:000-400-fit} by light-colored lines.\footnote{%
-  For conciseness, we drop the prime symbol from the radii in this
-  section and Appendix~\ref{app:rcurv-empirical}, even though all the
-  quantities are projected ones.} %
-The projected planitude and alatude then follow as \(\Pi = R_\C/R_0\),
-\(\Lambda^+ = R_{90}^+/R_0\), \(\Lambda^- = R_{90}^-/R_0\), which are shown in Figure~\ref{fig:000-400-planitude-alatude}.
+perpendicular radii (one for each wing), \(R_{90+}\) and \(R_{90-}\).
+These are all indicated on the panels of Figure~\ref{fig:000-400-fit}
+by light-colored lines.\footnote{%
+  For conciseness, we drop the prime symbol from the radii, both in
+  this section and in Appendix~\ref{app:rcurv-empirical}, even though
+  they are all projected quantities.} %
+The projected planitude and alatude then follow as \(\Pi' = R_\C/R_0\),
+\(\Lambda_+ = R_{90+}/R_0\), \(\Lambda_- = R_{90-}/R_0\), which are shown in
+Figure~\ref{fig:000-400-planitude-alatude}.
 
 The planitude is found to have a moderate dependence on the choice of
-\(\Delta\theta\), as shown in Figure~\ref{fig:000-400-Delta-theta}. The fact
-that the radius of curvature is defined at a point (the projected
-apex) might seem to argue for making \(\Delta\theta\) as small as possible, but
-that would lead to circle fits that were extremely sensitive to the
-exact positions of the few points included in the fit.  A reliable fit
-requires 4 or more points, ideally spanning a total separation that is
-a substantial fraction of \(R_\C\), which would argue for
-\(\Delta\theta\) larger than about \(\Pi/2\) radians, or \ang{60}--\ang{90}.  On
-the other hand, if \(\Delta\theta \ge \ang{90}\) then the planitude and alatude
-would no longer be independent since the bow would be forced to lie on
-the ``sphere'' line, \(\Lambda = (2 \Pi - 1)^{1/2}\) (see \S~\ref{sec:conic}).
-Balancing these two concerns suggests an optimal
-\(\Delta\theta = \ang{75}\), which is what is used in
-Figure~\ref{fig:000-400-fit}, but we also show results for both
-\ang{75} (thick lines) and \ang{60} (thin lines) in
-Figure~\ref{fig:000-400-planitude-alatude}.
+\(\Delta\theta\), as shown in Figure~\ref{fig:000-400-Delta-theta}, where it can
+be seen that, although the values of \(\Pi'\) are relatively stable for
+\(\Delta\theta \ge \ang{60}\) (light gray shaded region), they can show much
+larger variations for \(\Delta\theta < \ang{60}\).  The fact that the radius of
+curvature is defined at a point (the projected apex) might seem to
+argue for making \(\Delta\theta\) as small as possible, but that would lead to
+circle fits that were extremely sensitive to the exact positions of
+the few points included in the fit.  A reliable fit requires 4 or more
+points, ideally spanning a total separation that is a substantial
+fraction of \(R_\C\), which would argue for \(\Delta\theta\) larger than about
+\(\Pi'/2\) radians, or \ang{60}--\ang{90}.  On the other hand, if
+\(\Delta\theta \ge \ang{90}\) then the planitude and alatude would no longer be
+independent since the bow would be forced to lie on the ``sphere''
+line, \(\Lambda' = (2 \Pi' - 1)^{1/2}\) (see \S~\ref{sec:conic}).  Balancing
+these two concerns suggests an optimal \(\Delta\theta = \ang{75}\), which is
+shown in Figure~\ref{fig:000-400-fit}, whereas in
+Figure~\ref{fig:000-400-planitude-alatude} we show results for both
+\ang{75} (thick lines) and \ang{60} (thin lines).
 
-\(\Pi = 2.9 \pm 0.2 \pm 0.3\)
+\begin{table}
+  \caption[x]{Fitted planitude and alatude for M42 bows}
+  \label{tab:m42-fit}
+  \centering
+  \begin{tabular}{ll lll}
+    \toprule
+    Source & Bow & \(\Pi'\) & \(\Lambda'\)& \(\Delta\Lambda'\) \\
+    \midrule
+    000-400 & Inner & \(2.87 \pm 0.19\) & \(2.40 \pm 0.04\) & \(0.35 \pm 0.08\) \\
+           &  Ridge & \(3.62 \pm 0.38\) & \(2.73 \pm 0.02\) & \(0.51 \pm 0.10\) \\
+           & Outer & \(2.51 \pm 0.24\) & \(2.46 \pm 0.02\) & \(-0.06 \pm 0.02\) \\[\smallskipamount]
+           & All & \(3.00 \pm 0.54\) & \(2.53 \pm 0.15\) & \(0.16 \pm 0.16\) \\[\bigskipamount]
+    069-601 & Inner & \(3.81 \pm 0.23\) & \(2.90 \pm 0.01\) & \(0.44 \pm 0.05\) \\
+           & Ridge & \(2.43 \pm 0.13\) & \(2.17 \pm 0.01\) & \(0.07 \pm 0.02\) \\
+           & Outer & \(2.22 \pm 0.15\) & \(2.11 \pm 0.01\) & \(0.01 \pm 0.01\) \\[\smallskipamount]
+           & All & \(2.82 \pm 0.75\) & \(2.39 \pm 0.37\) & \(0.17 \pm 0.20\)\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\(\Pi' = 2.9 \pm 0.2 \pm 0.3\)
+
+The principal hindrance to an accurate tracing of the bow shape in
+this object is the strong and variable nebular background emission,
+which particularly affects the far wing on the right hand side of the
+image, where a bright background filament is superimposed on the bow.
+
+These give an idea of the systematic uncertainties and sensitivity to
+subjective choices,
 

### 2018-03-02 LL-shapes-2017/000-400-Pi-vs-Dtheta.py

@@ -21,10 +21,11 @@ for arc, color in zip(arcs, colors):
     label = fr"{arc}: ${mean:.1f} \pm {sigma:.1f}$"
     ax.plot(tab['D theta'], tab[arc], 'o', color=color, label=label)
 ax.legend(title="M42 000-400")
+ax.axvspan(60.0, 80.0, color='0.9')
 ax.set(ylim=[0.0, 9.0],
        xlabel=r"$\Delta \theta$, degrees",
        xticks=tab['D theta'],
-       ylabel=r"Fitted planitude $\Pi$")
+       ylabel=r"Fitted planitude $\Pi'$")
 sns.despine(trim=True)
 fig.tight_layout()
 fig.savefig(figfile)

### 2018-03-02 LL-shapes-2017/000-400-planitude-alatude.py

@@ -68,8 +68,8 @@ ax.set(
     xlim=[0., 5.1],
     ylim=[0., 5.1],
     #yticks=range(6),
-    xlabel=r"Fitted planitude: $\Pi$",
-    ylabel=r"Fitted alatude: $\Lambda$",
+    xlabel=r"Fitted planitude: $\Pi'$",
+    ylabel=r"Fitted alatude: $\Lambda'$",
 )        
 sns.despine()
 fig.tight_layout(pad=0.5)

### 2018-03-02 LL-shapes-2017/069-601-Pi-vs-Dtheta.py

@@ -21,10 +21,11 @@ for arc, color in zip(arcs, colors):
     label = fr"{arc}: ${mean:.1f} \pm {sigma:.1f}$"
     ax.plot(tab['D theta'], tab[arc], 'o', color=color, label=label)
 ax.legend(title="M42 069-601")
+ax.axvspan(60.0, 80.0, color='0.9')
 ax.set(ylim=[0.0, 9.0],
        xlabel=r"$\Delta \theta$, degrees",
        xticks=tab['D theta'],
-       ylabel=r"Fitted planitude, $\Pi$")
+       ylabel=r"Fitted planitude, $\Pi'$")
 sns.despine(trim=True)
 fig.tight_layout()
 fig.savefig(figfile)

### 2018-03-02 LL-shapes-2017/069-601-planitude-alatude.py

@@ -67,8 +67,8 @@ ax.set(
     xlim=[0., 5.1],
     ylim=[0., 5.1],
     #yticks=range(6),
-    xlabel=r"Fitted planitude: $\Pi$",
-    ylabel=r"Fitted alatude: $\Lambda$",
+    xlabel=r"Fitted planitude: $\Pi'$",
+    ylabel=r"Fitted alatude: $\Lambda'$",
 )        
 sns.despine()
 fig.tight_layout(pad=0.5)

### 2018-03-05 papers/Papers1234/sec-conclusions.tex
Start writing about the table

@@
 
+\begin{table}
+  \caption[]{Fitted planitude and alatude for M42 bows}
+  \label{tab:m42-fit}
+  \centering
+  \begin{tabular}{ll rrr}
+    \toprule
+    Source & Bow & \(\Pi'\) & \(\langle \Lambda' \rangle\)& \(\Delta\Lambda'\) \\
+    \midrule
+    000-400 & Inner & \(2.87 \pm 0.19\) & \(2.40 \pm 0.04\) & \(0.35 \pm 0.08\) \\
+           &  Ridge & \(3.62 \pm 0.38\) & \(2.73 \pm 0.02\) & \(0.51 \pm 0.10\) \\
+           & Outer & \(2.51 \pm 0.24\) & \(2.46 \pm 0.02\) & \(-0.06 \pm 0.02\) \\[\smallskipamount]
+           & All & \(3.00 \pm 0.54\) & \(2.53 \pm 0.15\) & \(0.16 \pm 0.16\) \\[\bigskipamount]
+    069-601 & Inner & \(3.81 \pm 0.23\) & \(2.90 \pm 0.01\) & \(0.44 \pm 0.05\) \\
+           & Ridge & \(2.43 \pm 0.13\) & \(2.17 \pm 0.01\) & \(0.07 \pm 0.02\) \\
+           & Outer & \(2.22 \pm 0.15\) & \(2.11 \pm 0.01\) & \(0.01 \pm 0.01\) \\[\smallskipamount]
+           & All & \(2.82 \pm 0.75\) & \(2.39 \pm 0.37\) & \(0.17 \pm 0.20\)\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \section{Example application to observations}
@@
 
-\begin{table}
-  \caption[x]{Fitted planitude and alatude for M42 bows}
-  \label{tab:m42-fit}
-  \centering
-  \begin{tabular}{ll lll}
-    \toprule
-    Source & Bow & \(\Pi'\) & \(\Lambda'\)& \(\Delta\Lambda'\) \\
-    \midrule
-    000-400 & Inner & \(2.87 \pm 0.19\) & \(2.40 \pm 0.04\) & \(0.35 \pm 0.08\) \\
-           &  Ridge & \(3.62 \pm 0.38\) & \(2.73 \pm 0.02\) & \(0.51 \pm 0.10\) \\
-           & Outer & \(2.51 \pm 0.24\) & \(2.46 \pm 0.02\) & \(-0.06 \pm 0.02\) \\[\smallskipamount]
-           & All & \(3.00 \pm 0.54\) & \(2.53 \pm 0.15\) & \(0.16 \pm 0.16\) \\[\bigskipamount]
-    069-601 & Inner & \(3.81 \pm 0.23\) & \(2.90 \pm 0.01\) & \(0.44 \pm 0.05\) \\
-           & Ridge & \(2.43 \pm 0.13\) & \(2.17 \pm 0.01\) & \(0.07 \pm 0.02\) \\
-           & Outer & \(2.22 \pm 0.15\) & \(2.11 \pm 0.01\) & \(0.01 \pm 0.01\) \\[\smallskipamount]
-           & All & \(2.82 \pm 0.75\) & \(2.39 \pm 0.37\) & \(0.17 \pm 0.20\)\\
-    \bottomrule
-  \end{tabular}
-\end{table}
+Unlike all the models considered in \S~\ref{sec:crw-scenario} and
+\S~\ref{sec:more-realistic-bow}, the observed bows are not necessarily
+symmetrical and so the alatude for the two wings, \(\Lambda_-'\) and
+\(\Lambda_+'\), may be different.  We calculate an average alatude,
+\(\langle\Lambda'\rangle\), and an alatude asymmetry, \(\Delta\Lambda'\):
+\begin{equation}
+  \label{eq:alatude-average-and-asym}
+  \langle\Lambda'\rangle = \tfrac12 \left( \Lambda_+' + \Lambda_-' \right)
+  \quad\quad \Delta\Lambda' = \tfrac12 \left( \Lambda_+' - \Lambda_-' \right)
+\end{equation}
+The results for these and the planitude are shown in Table~\ref{tab:m42-fit}
 

### 2018-03-05 papers/Papers1234/sec-conclusions.tex
Finish discussion of systematic uncertainties

@@
 
+\subsection{Empirical determination of bow shock shape}
+\label{sec:empir-determ-bow}
+
 We consider three different tracings of the bow shape (see
@@
 We determine the planitude and alatude by fitting a circle to the
-traced points within \(\pm \Delta\theta = \ang{75}\) bow axis, using the
+traced points within \(\pm \Delta\theta = \ang{75}\) of the bow axis, using the
 iterative algorithm described in Appendix~\ref{app:rcurv-empirical}.
@@
   they are all projected quantities.} %
-The projected planitude and alatude then follow as \(\Pi' = R_\C/R_0\),
-\(\Lambda_+ = R_{90+}/R_0\), \(\Lambda_- = R_{90-}/R_0\), which are shown in
+The projected planitude and alatude then follow as
+\(\Pi' = R_\C/R_0\), \(\Lambda_+ = R_{90+}/R_0\),
+\(\Lambda_- = R_{90-}/R_0\), which are shown in
 Figure~\ref{fig:000-400-planitude-alatude}.
+
+\subsection{Analysis of sources of systematic uncertainty}
+\label{sec:analys-sourc-syst}
 
@@
 fraction of \(R_\C\), which would argue for \(\Delta\theta\) larger than about
-\(\Pi'/2\) radians, or \ang{60}--\ang{90}.  On the other hand, if
+\(\Pi'/2\) radians, or \ang{60} to \ang{90}.  On the other hand, if
 \(\Delta\theta \ge \ang{90}\) then the planitude and alatude would no longer be
@@
 symmetrical and so the alatude for the two wings, \(\Lambda_-'\) and
-\(\Lambda_+'\), may be different.  We calculate an average alatude,
-\(\langle\Lambda'\rangle\), and an alatude asymmetry, \(\Delta\Lambda'\):
+\(\Lambda_+'\), may be different.  We therefore calculate an average
+alatude, \(\langle\Lambda'\rangle\), and an alatude asymmetry, \(\Delta\Lambda'\):
 \begin{equation}
@@
 \end{equation}
-The results for these and the planitude are shown in Table~\ref{tab:m42-fit}
+The results for these two quantities, together with the planitude, are
+shown in Table~\ref{tab:m42-fit}.  For each object and for each tracing
+(inner, ridge, outer, see Fig.~\ref{fig:000-400-fit}), the
+\(\text{mean} \pm \text{standard\ deviation}\) is listed for circle
+fits using \(\Delta\theta = \ang{60}\) to \ang{80} (see
+Fig.~\ref{fig:000-400-Delta-theta}).  Additionally, the row ``All''
+for each object gives the global mean and standard deviation over all
+three tracings.
 
-\(\Pi' = 2.9 \pm 0.2 \pm 0.3\)
+It can be seen from Table~\ref{tab:m42-fit} that the uncertainty in
+the fitted parameters is dominated by the variations between the
+different traced shapes.  For example, the one-sigma relative
+variation of planitude \(\Pi'\) is \(< 10\%\) within the individual
+tracings, but \(\approx 20\%\) between tracings.  For the mean alatude
+\(\langle\Lambda'\rangle\), the variation within individual tracings is extremely
+small\footnote{%
+  This is because the only way that variation in the circle fit
+  parameters affect the alatudes is through the axis orientation
+  vector, and changing the orientation induces roughly opposite
+  effects on \(\Lambda_+'\) and \(\Lambda_-'\), which cancel out in \(\langle\Lambda'\rangle\).
+} %
+at \(\approx 1\%\), but is \(\approx 10\%\) between tracings.  The alatude
+asymmetry, \(\Delta\Lambda'\), is best interpreted as a difference between the
+symmetry axis of the apex region and the symmetry axis of the wings.
+In relative terms, this is \(0\)--\(20\%\), but with large systematic
+variations between tracings (for instance, in both objects it is very
+small for the outer arcs).
+
+It could be argued that much of the between-tracing variations in
+\(\Pi'\) and \(\langle\Lambda'\rangle\) are due to real differences in the shape of the
+inner and outer boundaries of the emission arc.  Although this may be
+true, in the absence of a robust theory as to exactly what feature of
+the observed images constitutes \emph{the} bow shock, such variations
+nevertheless serve to limit the precision with which the bow shock
+shape can be measured.  We therefore conclude that conservative
+estimates of \(20\%\) precision for \(\Pi'\) and \(10\%\) precision for
+\(\Lambda'\) are appropriate when analyzing observations of a similar
+quality to those presented in Figure~\ref{fig:000-400-fit}.
+
+\subsection{Derived shape of M42 arcs}
+\label{sec:derived-shape-m42}
 

### 2018-03-06 papers/Papers1234/sec-conclusions.tex
Start discussing shape of M42 arcs

@@
     \citeauthor{Meyer:2017a}'s Fig.~3 are converted to FITS format and
-    displayed using the software \textsc{SAOImage DS9}.  The density
-    contour at \SI{0.4}{cm^{-3}} is displayed (shown in green in the
-    figure) and this is traced by hand by placing ``point regions'' on
-    the image (shown by black ``x'' shapes in the figure).  The zoom
-    facility of the software allows the points to be placed with any
-    required accuracy.  The points are saved to a file in the DS9
-    region file format, which is then read by Python programs for
-    further processing.  For example, the yellow boxes show circle
-    fits and determination of the parameters \(R_0\), \(R_c\), and
-    \(R_{90}\).  In this example, only the points shown in orange
-    (within \ang{60} of axis) are used in the fits.}
+    displayed using the software SAOImage~DS9 \citep{Joye:2003a}.  The
+    density contour at \SI{0.4}{cm^{-3}} is displayed (shown in green
+    in the figure) and this is traced by hand by placing ``point
+    regions'' on the image (shown by black ``x'' shapes in the
+    figure).  The zoom facility of the software allows the points to
+    be placed with any required accuracy.  The points are saved to a
+    file in the DS9 region file format, which is then read by Python
+    programs for further processing.  For example, the yellow boxes
+    show circle fits and determination of the parameters \(R_0\),
+    \(R_c\), and \(R_{90}\).  In this example, only the points shown
+    in orange (within \ang{60} of axis) are used in the fits.}
   \label{fig:meyer-trace}
@@
 and its inner and outer edges.  In all three cases, we placed by eye
-the points that define the bow, using SAOImage~DS9 in a similar
-fashion to in Figure~\ref{fig:meyer-trace}, and guided by the image
-contours.\footnote{%
+the points that define the bow, using SAOImage~DS9 \citep{Joye:2003a}
+in a similar fashion to in Figure~\ref{fig:meyer-trace}, and guided by
+the image contours.\footnote{%
   In the case of the ``ridge'' method at least, it is possible to
@@
 different traced shapes.  For example, the one-sigma relative
-variation of planitude \(\Pi'\) is \(< 10\%\) within the individual
-tracings, but \(\approx 20\%\) between tracings.  For the mean alatude
+variation of planitude, \(\Pi'\), is \(< 10\%\) within the individual
+tracings, but \(\approx 20\%\) between tracings.  For the mean alatude,
 \(\langle\Lambda'\rangle\), the variation within individual tracings is extremely
@@
   vector, and changing the orientation induces roughly opposite
-  effects on \(\Lambda_+'\) and \(\Lambda_-'\), which cancel out in \(\langle\Lambda'\rangle\).
-} %
+  effects on \(\Lambda_+'\) and \(\Lambda_-'\), which approximately cancel out in
+  \(\langle\Lambda'\rangle\).  } %
 at \(\approx 1\%\), but is \(\approx 10\%\) between tracings.  The alatude
@@
 estimates of \(20\%\) precision for \(\Pi'\) and \(10\%\) precision for
-\(\Lambda'\) are appropriate when analyzing observations of a similar
-quality to those presented in Figure~\ref{fig:000-400-fit}.
+\(\Lambda'\) are appropriate when analyzing observations of a similar or
+better quality\footnote{%
+  Since the uncertainties are systematic and due to unavoidably
+  subjective decisions, it is unlikely that better quality
+  observations would improve the situation, although poorer quality
+  observations could make things worse.  } %
+to those presented in Figure~\ref{fig:000-400-fit}.  This will be an
+important limitation when comparing the statistics of the shapes of
+different bow shock populations, as we will present in a following
+paper.
 
@@
 \label{sec:derived-shape-m42}
+
+From a casual inspection of Figure~\ref{fig:000-400-fit}, it is
+apparent that the shapes of the two M42 arcs are closely similar, and
+this is confirmed by the numbers in Table~\ref{tab:m42-fit}. Both
+000-400 and 069-601 are consistent with
+\((\Pi', \Lambda') \approx (3.0, 2.5)\), and if we take the absolute minimum over
+all the different tracings and reasonable variations in the
+\(\Delta\theta\) fit parameter, we find firm lower limits of
+\((\Pi', \Lambda') > (2.1, 2.1)\).  In the rest of this section
+
+If we compare th
 

### 2018-03-06 papers/Papers1234/quadrics-bowshock.tex
Submitted first paper! To MNRAS and arxiv
Add new appendixes to address referee points
Explain about the plane of sky as a projective space
Finish the new section on the observations

--- 2017-12-05 papers/Paper1/quadrics-bowshock.tex
@@
 \usepackage{nicefrac}
+
+% Alternative hollow blackboard bold fonts
+\usepackage{dsfont}
+\usepackage{bbm}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Tarango Yong \& Henney]{
-  Jorge A. Tarango Yong\thanks{E-mail: j.tarango@irya.unam.mx}
+\author[Tarango-Yong \& Henney]{
+  Jorge A. Tarango-Yong\thanks{E-mail: j.tarango@irya.unam.mx}
   \& William J. Henney\thanks{E-mail: w.henney@irya.unam.mx}\\
@@
 \providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
+\newenvironment{Vector}{\left(\begin{array}{c}}{\end{array}\right)}
+\newcommand\uvec[1]{\bm{\hat{#1}}}
+\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+
 \newcommand\TODO[1]{%
@@
   diagnostics of the shape of the contact discontinuity, which can be
-  used to discriminate between different physical models.
+  used to discriminate between different physical models.  We present
+  an algorithm that can determine the planitude and alatude from observed
+  bow shock emission maps with a precision of 10 to 20\%. 
 \end{abstract}
@@
 research studentship from Consejo Nacional de Ciencias y Tecnología,
-Mexico.
+Mexico.  This work has made extensive use of Python language libraries
+from the SciPy \citep{Jones:2001a} and AstroPy
+\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a}
+projects.
 
@@
 \appendix
+\input{app-intermediate}
 \input{app-parabola}

### 2018-03-06 papers/Papers1234/sec-conclusions.tex
Finish the new section on the observations

@@
   \caption[]{Example empirical determination of planitude and alatude
-    for observed bow shocks associated with proplyds in the Orion
-    Nebula (M42).  Color scale and contours show an \textit{HST}
+    for observed bow shocks associated with proplyds in the outer
+    Orion Nebula (M42).  Color scale and contours show an \textit{HST}
     H\(\alpha\) image (ACS F658N filter, \citealp{Bally:2006a}) of
@@
   designation 4596-400 in catalogs such as \citet{Ricci:2008a}.  } %
-in the west of the Orion Nebula (M42).  An image of one of these arcs
-(M42~069-601) was used in the illustration of bow shock terminology in
+in the west of the Orion Nebula (M42) at a distance of roughly
+\SI{0.5}{pc} from the high-mass Trapezium stars that ionize the
+nebula.  An image of one of these arcs (M42~069-601) was used in the
+illustration of bow shock terminology in
 Figure~\ref{fig:bow-terminology}.
@@
 The projected planitude and alatude then follow as
-\(\Pi' = R_\C/R_0\), \(\Lambda_+ = R_{90+}/R_0\),
-\(\Lambda_- = R_{90-}/R_0\), which are shown in
+\(\Pi' = R_\C/R_0\), \(\Lambda_+' = R_{90+}/R_0\),
+\(\Lambda_-' = R_{90-}/R_0\), which are shown in
 Figure~\ref{fig:000-400-planitude-alatude}.
@@
 It could be argued that much of the between-tracing variations in
-\(\Pi'\) and \(\langle\Lambda'\rangle\) are due to real differences in the shape of the
-inner and outer boundaries of the emission arc.  Although this may be
-true, in the absence of a robust theory as to exactly what feature of
-the observed images constitutes \emph{the} bow shock, such variations
-nevertheless serve to limit the precision with which the bow shock
-shape can be measured.  We therefore conclude that conservative
-estimates of \(20\%\) precision for \(\Pi'\) and \(10\%\) precision for
-\(\Lambda'\) are appropriate when analyzing observations of a similar or
-better quality\footnote{%
+\(\Pi'\) and \(\langle\Lambda'\rangle\) are due to real differences between the shapes of
+the inner and outer boundaries of the emission arc.  Although this may
+be true, in the absence of a robust theory as to exactly what feature
+of the observed images constitutes \emph{the} bow shock, such
+variations nevertheless serve to limit the precision with which the
+bow shock shape can be measured.  We therefore conclude that
+conservative estimates of \(20\%\) precision for \(\Pi'\) and \(10\%\)
+precision for \(\Lambda'\) are appropriate when analyzing observations of a
+similar or better quality\footnote{%
   Since the uncertainties are systematic and due to unavoidably
@@
 
-\subsection{Derived shape of M42 arcs}
+\subsection{Derived shape of the M42 arcs}
 \label{sec:derived-shape-m42}
@@
 all the different tracings and reasonable variations in the
-\(\Delta\theta\) fit parameter, we find firm lower limits of
-\((\Pi', \Lambda') > (2.1, 2.1)\).  In the rest of this section
+\(\Delta\theta\) fit parameter, we find unassailable lower limits of
+\((\Pi', \Lambda') > (2.1, 2.1)\).  In the rest of this section, we consider
+only these lower limits, since they are already sufficient for drawing
+interesting conclusions.
 
-If we compare th
-
-The principal hindrance to an accurate tracing of the bow shape in
-this object is the strong and variable nebular background emission,
-which particularly affects the far wing on the right hand side of the
-image, where a bright background filament is superimposed on the bow.
-
-These give an idea of the systematic uncertainties and sensitivity to
-subjective choices,
+Comparison with Figure~\ref{fig:sim-Pi-Lambda} shows that both the MHD
+and HD simulations of \citet{Meyer:2016a} are inconsistent with the
+observations.  Although \(\Pi' > 2.1\) can be satisfied,\footnote{%
+  Either by the MHD simulations at low inclinations
+  (\(\abs{i} = \ang{0}\)--\ang{20}) or by the HD simulation at
+  intermediate inclinations (\(\abs{i} = \ang{30}\)--\ang{40}).} %
+the simulations' projected alatude is \(\Lambda' < 1.9\) for all
+inclinations, which is significantly less than the observed lower
+limit of \(2.1\).  This is not particularly surprising since the
+simulations were not tailored to the situation of these proplyd bow
+shocks in M42, in which the mildly supersonic photoevaporation flow
+from an externally irradiated protoplanetary disk interacts with the
+mildly supersonic champagne flow from the core of the Orion Nebula.
+The proplyd case has at least four important differences from the
+runaway O-star case modeled by \citet{Meyer:2016a}: (1)~The velocity
+of the outer wind is \(\le \SI{20}{km.s^{-1}}\) instead of
+\SI{40}{km.s^{-1}}; (2)~The outer wind is slightly divergent, rather
+than plane-parallel; (3)~Both inner and outer shocks are strongly
+radiative, so both shells (see Fig.~\ref{fig:2-winds}) contribute to
+the observed emission; (4)~The inner wind is not isotropic, but
+instead corresponds to the \(k = 0.5\) case of
+equation~\eqref{eq:ancantoid-density}.  The ways in which these
+differences may account for the discrepancy with the observations will
+be explored in detail in a subsequent paper.
 
@@
 
-Finally (\S~\ref{sec:more-realistic-bow}), we test the projected shape
-analysis methods against the results of computational fluid dynamic
-simulations of magnetized and non-magnetized bow shocks from
-\citet{Meyer:2017a} of a runaway OB main-sequence star.  We find that
-measurements made on maps of infrared dust emission can be accurate
-diagnostics of the projected shape of the contact discontinuity for
-this type of bow shock (Fig.~\ref{fig:sim-Pi-Lambda}).  The
-distributions of projected planitude and alatude for a population of
-randomly oriented bow shocks shows systematic differences between the
-different simulations.
+In the following section (\S~\ref{sec:more-realistic-bow}), we test the
+projected shape analysis methods against the results of computational
+fluid dynamic simulations of magnetized and non-magnetized bow shocks
+from \citet{Meyer:2017a} of a runaway OB main-sequence star.  We find
+that measurements made on maps of infrared dust emission can be
+accurate diagnostics of the projected shape of the contact
+discontinuity for this type of bow shock
+(Fig.~\ref{fig:sim-Pi-Lambda}).  The distributions of projected
+planitude and alatude for a population of randomly oriented bow shocks
+shows systematic differences between the different simulations.
+
+Finally (\S~\ref{sec:obs}), we give an example of the application of
+our methods to observed emission maps of bow shocks, describing a
+robust algorithm for empirically determining the projected planitude
+and alatude from imperfect real data.  We investigate the sensitivity
+of the results to systematic errors due to both observational
+uncertainties and subjective choices in the application of the
+algorithm.  We find that the projected planitude and alatude can be
+determined with precisions of 20\% and 10\%, respectively.  For our
+illustrative observations, we show that this is more than sufficient
+to rule out certain models.
 

### 2018-03-07 papers/Papers1234/app-intermediate.tex
Finish final tweaks to derivation of equations in Sec 3 and App B

--- 2018-01-17 papers/Papers1234/app-intermediate.tex
@@
 \end{equation}
-This is used in equation~\eqref{eq:Trans}.
+This is used in equation~\eqref{eq:Trans}.  A further application is
+to express the observer-frame Cartesian basis vectors in terms of the
+body-frame basis:
+\begin{align}
+  \label{eq:xunit-prime}
+  \uvec{x}' &= \mathbfss{A}_y(-i)\, %\uvec{x}
+              \begin{Vector}
+              1 \\ 0 \\ 0  
+              \end{Vector}
+              =
+              \begin{Vector}
+              \cos i \\ 0 \\ -\sin i  
+              \end{Vector} \ ,
+  \\
+  \label{eq:yunit-prime}
+  \uvec{y}' &= \mathbfss{A}_y(-i)\, %\uvec{y}
+              \begin{Vector}
+              0 \\ 1 \\ 0  
+              \end{Vector}
+              =
+              \begin{Vector}
+              0 \\ 1 \\ 0
+              \end{Vector} \ , 
+  \\
+  \label{eq:zunit-prime}
+  \uvec{z}' &= \mathbfss{A}_y(-i)\, %\uvec{z}
+              \begin{Vector}
+              0 \\ 0 \\ 1  
+              \end{Vector}
+              =
+              \begin{Vector}
+              \sin i \\ 0 \\ \cos i  
+              \end{Vector} \ .
+\end{align}
+Note that in this case the sign of \(i\) is reversed because it is the
+inverse operation to that in equation~\eqref{eq:Trans}
 
@@
     0 &\sin\phi & \cos\phi 
-  \end{pmatrix} \ .
+  \end{pmatrix} \ ,
 \end{equation}
-This is used in \S~\ref{sec:unit-vectors-normal} to find the general
-form of the body-frame normal and tangent unit vectors:
-\begin{align}
-  \uvec{n} &= \mathbfss{A}_x(\phi) \, \uvec{n}_0 =
-  \begin{Vector}
-    \sin\alpha \\ \cos\alpha\cos\phi \\ \cos\alpha\sin\phi
-  \end{Vector} \\
-  \uvec{t} &= \mathbfss{A}_x(\phi) \, \uvec{t}_0 =
-  \begin{Vector}
-    -\cos\alpha \\ \sin\alpha\cos\phi \\ \sin\alpha\sin\phi
-  \end{Vector} \ . 
-\end{align}
+where \(\phi\) takes all values in the interval \([0, 2\pi]\).
 

### 2018-03-07 papers/Papers1234/sec-projection.tex
Finish final tweaks to derivation of equations in Sec 3 and App B

@@
 \((x', y', z')\), which are found by rotating the body-frame
-coordinates about the \(y\)~axis:
+coordinates about the \(y\)~axis.  The same vector, \(\bm{r}\), expressed in the observer frame is then 
 \begin{equation}
-  \bm{r}' \equiv
+  \bm{r} = 
   \begin{Vector}
@@
   \end{Vector}
-  = \mathbfss{A}_y(i)\, \bm{r}
+  = \mathbfss{A}_y(i)\,
+  \begin{Vector}
+    x \\ y \\ z
+  \end{Vector}
   =
@@
 is defined so that \(i = \ang{0}\) when the surface is viewed
-perpendicular to its axis (\textit{side on}) and \(i = \ang{90}\) when
-it is viewed along its axis (\textit{end on}).
+perpendicular to its axis (\textit{side on}) and \(i = \pm\ang{90}\)
+when it is viewed along its axis (\textit{end on}), with positive
+\(i\) when the apex points towards the observer.
 
@@
 \end{equation}
-For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
-equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis with the matrix
-\(\mathbfss{A}_x(\phi)\) and then rotating to the observer frame with
-\(\mathbfss{A}_y(i)\)
-
-by use of
-equation~(\ref{eq:Trans}) to give
-\begin{equation}
-  \label{eq:nprime}
-  \begin{aligned}
-    \uvec{n}' &= \mathbfss{A}_y(i)\, \uvec{n}
-    = \mathbfss{A}_y(i)\, \mathbfss{A}_x(\phi)\, \uvec{n}_0 \\
-    & =
-    \begin{aligned}[t]
-      & \frac{1}{(1+\omega^2)^{1/2}} \\
-      & \times 
+For general \(\phi \ne 0\), we find \(\uvec{n}\) and \(\uvec{t}\) by
+rotating equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis with the
+matrix \(\mathbfss{A}_x(\phi)\) (eq.~[\ref{eq:Rotation-matrix-x}]):
+\begin{align}
+  \label{eq:uvec-n-phi}
+  \uvec{n} &= \mathbfss{A}_x(\phi) \, \uvec{n}_0 =
   \begin{Vector}
-        (\cos\theta+\omega\sin\theta)\cos i 
-        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
-        (\sin\theta-\omega\cos\theta)\cos\phi \\
-        (\cos\theta+\omega\sin\theta)\sin i 
-        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-      \end{Vector}
-    \end{aligned}
-  \end{aligned}
-\end{equation}
-\begin{equation}
-  \label{eq:tprime}
-  \begin{aligned}
-    \uvec{t}' &= \mathbfss{A}_y(i)\, \uvec{t}
-    = \mathbfss{A}_y(i)\, \mathbfss{A}_x(\phi)\, \uvec{t}_0 \\
-    & =
-    \begin{aligned}[t]
-      & \frac{1}{(1+\omega^2)^{1/2}} \\
-      & \times 
+    \sin\alpha \\ \cos\alpha\cos\phi \\ \cos\alpha\sin\phi
+  \end{Vector}  \\
+  \label{eq:uvec-t-phi}
+  \uvec{t} &= \mathbfss{A}_x(\phi) \, \uvec{t}_0 =
   \begin{Vector}
-        -(\sin\theta-\omega\cos\theta)\cos i
-        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
-        (\cos\theta+\omega\sin\theta)\cos\phi \\
-        -(\cos\theta+\omega\sin\theta)\sin i 
-        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
+    -\cos\alpha \\ \sin\alpha\cos\phi \\ \sin\alpha\sin\phi
   \end{Vector} \ .
-    \end{aligned}
-  \end{aligned}
-\end{equation}
+\end{align}
 
@@
   \label{eq:tangent-line-condition}
-  \uvec{n}'\cdot \uvec{z}' = 0.
+  \uvec{n} \cdot \uvec{z}' = 0.
 \end{equation}
-We denote by \(\phi\T\) that value of $\phi$ that satisfies this
-relation for a given inclination, \(i\), and polar angle, \(\theta\):
+We denote by \(\phi\T\) that value of $\phi$ that satisfies this relation
+for a given inclination, \(i\), and polar angle, \(\theta\).  From
+equations~(\ref{eq:uvec-n-phi}, \ref{eq:tangent-line-condition},
+\ref{eq:zunit-prime}, \ref{eq:alpha}) this is
 \begin{equation}
-\sin\phi\T = -\tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
+\sin\phi\T = -\tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta} \ .
 \label{eq:tanphi}
@@
 
-Note that equation~(\ref{eq:tanphi}) will not have
-a solution for arbitrary values of $\theta$ and $i$, but only when
-$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent
-line only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of \(\theta\) on the tangent line's projected symmetry axis (\(\theta' = 0\)), 
-given implicitly by
+Note that equation~(\ref{eq:tanphi}) will not have a solution for
+arbitrary values of $\theta$ and $i$, but only when
+$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent line
+only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of
+\(\theta\) on the tangent line's projected symmetry axis
+(\(\theta' = 0\)).  From equations~(\ref{eq:tangential},
+\ref{eq:R-prime-theta-prime}) it follows that \(\sin^2\phi\T = 1\) at
+\(\theta = \theta_0\), which yields the implicit equation
 \begin{align}

### 2018-03-07 papers/Papers1234/sec-conic.tex
Include corrections from Jorge's email of 2018-01-31

@@
   \label{eq:conic-R90}
-  R_{90}^2 = \Q \left(\sigma a^2 - x_0^2\right) \ .
+  R_{90}^2 = \Q \left(a^2 - x_0^2\right) \ .
 \end{equation}
@@
 \((\Pi', \Lambda') = (1, 1)\) is apparent, as is the divergence of the
-hyperboloid tracks towards \((\Pi', \Lambda') = (+\infty, +\infty)\).  The paraboloids,
-by contrast, converge on the point \((\Pi', \Lambda') = (2, 2)\), and the
-special case of the confocal paraboloid,\footnote{So named because the
-  star is at the focus of the parabola.} with true planitude and
-alatude \((\Pi, \Lambda) = (2, 2)\), is the only quadric whose apparent shape
-remains identical for all inclination angles.
+hyperboloid tracks towards \((\Pi', \Lambda') = (+\infty, +\infty)\), whereas the
+paraboloids, by contrast, converge on the point
+\((\Pi', \Lambda') = (2, 2)\).  Two special cases are the confocal paraboloid
+and the concentric sphere,\footnote{So named because the star is at
+  the focus of the parabola, or the center of the sphere.} with true
+planitude and alatude \((\Pi, \Lambda) = (2, 2)\) and \((1, 1)\),
+respectively, which are the only quadrics whose apparent shape remains
+identical for all inclination angles.
 

### 2018-03-07 papers/paper1-submit/latexdiff/ms-bows01-expand.tex
Trial run with latexdiff

%\RequirePackage{amsmath}
\documentclass[useAMS, usenatbib, a4paper]{mnras}
\pdfsuppresswarningpagegroup=1

% The following is needed to fix the margins if using Letter-size paper
% REMOVE if your LaTeX uses A4 paper by default
%\addtolength\topmargin{-1.8cm}

% Standard LaTeX packages
% \usepackage[varg]{txfonts}
\usepackage{graphicx}
\usepackage{dblfloatfix}
%\usepackage[section, above, below]{placeins}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{nicefrac}

\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}

% Fonts 
\usepackage{newtxtext}
% Note: newtxmath must come AFTER newtxtext
\usepackage[varvw,smallerops]{newtxmath}

\usepackage{hyperref}
\usepackage{xr-hyper}

\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

%% Bold italic
\newcommand\hmmax{0}            % we don't need heavy fonts
\newcommand\bmmax{1}            % reduce use of math alphabets for bold
\usepackage{bm}

\makeatletter
%% Bundled custom packages
\newlength{\table@note@skip}
\setlength{\table@note@skip}{0.5ex}
\def\@eapj@cap@font{\bfseries}
\gdef\tblnote@list{}
\gdef\tblref@list{}
\newcommand\tablecomments[1]{\@tablecom{#1}}% 
\newcommand\tablerefs[1]{\@tableref{#1}}% 
\def\@tablecom#1{% 
 \vspace*{\table@note@skip}
\par 
{\parbox{\linewidth}{\hskip1em\rmfamily {\@eapj@cap@font Note}. --- #1}\par}% 
}% 
\def\@tableref#1{% 
 \vspace*{\table@note@skip}
\par 
{\parbox{\linewidth}{\hskip1em\rmfamily {\@eapj@cap@font References}. --- #1}\par}% 
}% 
\def\spew@tblnotes{% 
 \@ifx@empty\tblref@list{}{% 
  \@tablenotes{\tblref@list}%
  \vspace*{\table@note@skip}%
  \global\let\tblref@list\@empty 
 }% 
 \@ifx@empty\tblnote@list{}{% 
  \@tablenotes{\tblnote@list}% 
  \vspace*{\table@note@skip}%
  \global\let\tblnote@list\@empty
 }
 \the\DT@p@ftn%
}% 
\def\@tablenotes#1{% 
 \par 
% \footnoterule% 
 {\@table@type@size#1}% 
}%

\def\tabletypesize#1{\def\table@hook{#1}\gdef\@table@type@size{#1}}
\tabletypesize{\footnotesize}

\global\let\tablenotemark\relax
\global\def\tablenotemark#1{{\normalfont\textsuperscript{#1}}}
\global\let\tablenotetext\relax
% \global\def\tablenotetext#1#2{\footnotetext[#1]{\@table@type@size#2}} 
\global\def\tablenotetext#1#2{\noindent\textsuperscript{#1}{\@table@type@size#2}}

\newcommand\nodata{ ~$\cdots$~ }%

\newcommand\phn{\phantom{0}}% 
\newcommand\phd{\phantom{.}}% 
\newcommand\phs{\phantom{$-$}}% 
\newcommand\phm[1]{\phantom{#1}}%

\makeatother

% Definitions needed in abstract
\newcommand\hii{\ion{H}{ii}}

\title[Bow shock shapes]{True versus apparent shapes of bow shocks}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango-Yong \& Henney]{
  Jorge A. Tarango-Yong\thanks{E-mail: j.tarango@irya.unam.mx}
  \& William J. Henney\thanks{E-mail: w.henney@irya.unam.mx}\\
  \AddressCRyA
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2017}

\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Sin}{\mathcal{S}}
\DeclareMathOperator{\Cos}{\mathcal{C}}
\DeclareMathOperator{\Cot}{\mathcal{T}}
\DeclareMathOperator{\GammaFunc}{\Gamma}
\DeclareMathOperator{\Depart}{\Delta}
\newcommand\ecc{\ensuremath{e}}
\newcommand\w{\ensuremath{\mathrm{w}}}
\newcommand\C{\ensuremath{\mathrm{c}}}
\providecommand{\abs}[1]{\lvert#1\rvert}
\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
\newcommand\TODO[1]{%
  \begin{center}
    \framebox{\parbox{0.8\linewidth}{
        \texttt{\footnotesize\color{red} #1}}}
  \end{center}}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Astrophysical bow shocks are a common result of the interaction
  between two supersonic plasma flows, such as winds or jets from
  stars or active galaxies, or streams due to the relative motion
  between a star and the interstellar medium.
  % Similarly shaped radiation bow waves are produced
  % by the relative motion between dust grains and a luminous source.
  For cylindrically symmetric bow shocks, we develop a general theory
  for the effects of inclination angle on the apparent shape. We
  propose a new two-dimensional classification scheme for bow shapes,
  which is based on dimensionless geometric ratios that can be
  estimated from observational images.  The two ratios are related to
  the flatness of the bow's apex, which we term \textit{planitude} and
  the openness of its wings, which we term \textit{alatude}.  We
  calculate the expected distribution in the planitude--alatude plane
  for a variety of simple geometrical and physical models: quadrics of
  revolution, wilkinoids, cantoids, and ancantoids.  We further test
  our methods against numerical magnetohydrodynamical simulations of
  stellar bow shocks and find that the apparent planitude and alatude
  measured from infrared dust continuum maps serve as accurate
  diagnostics of the shape of the contact discontinuity, which can be
  used to discriminate between different physical models.
\end{abstract}

\begin{keywords}
  circumstellar matter -- hydrodynamics -- stars: winds, outflows
\end{keywords}

% start input ./sec-intro.tex
% Force paper II to be before paper III in the reference list
%\nocite{Henney:2018a}

\section{Introduction}
\label{sec:intro}

%%
%% Circumstances when bowshocks arise
%%

The archetypal bow shock is formed when a solid body moves
supersonically through a compressible fluid.  Terrestrial examples
include the atmospheric re-entry of a space capsule, or the sonic boom
produced by a supersonic jet \citep{van-Dyke:1982a}.  In astrophysics
the term bow shock is employed more widely, to refer to many different
types of curved shocks that have approximate cylindrical symmetry.
Instead of a solid body, astrophysical examples usually involve the
interaction of \emph{two} supersonic flows, such as the situation of a
stellar wind emitted by a star that moves supersonically through the
interstellar medium \citep{van-Buren:1988a, Kobulnicky:2010a,
  van-Marle:2011a, Mackey:2012b, Mackey:2015a}.  In such cases, two
shocks are generally produced, one in each flow.  Sometimes,
especially in heliospheric studies \citep{Zank:1999a, Scherer:2014a},
the term ``bow shock'' is reserved for the shock in the ambient
medium, with the other being called the ``wind shock'' or
``termination shock''.  However, in other contexts such as colliding
wind binaries \citep{Stevens:1992a, Gayley:2009a} such a distinction
is not so useful.

%% 
%% Examples of astrophysical bow shocks
%%

\begin{figure}
  \centering
  \bigskip
  \includegraphics[width=0.9\linewidth]{figs/bow-terminology}
  \caption{Descriptive terminology for a stellar bow shock.  The apex
    is the closest approach of the bow to the star, while the wings
    are the parts of the bow that curve back past the star.}
  \label{fig:bow-terminology}
\end{figure}
A further class of astrophysical bow shock is driven by highly
collimated, supersonic jets of material, such as the Herbig Haro
objects \citep{Schwartz:1978b, Hartigan:1987a} that are powered by
jets from young stars or protostars.  Additional examples are seen in
planetary nebulae \citep{Phillips:2010a, Meaburn:2013a}, active
galaxies \citep{Wilson:1987a}, and in galaxy clusters
\citep{Markevitch:2002a}.  In the jet-driven case, the term ``working
surface'' is often applied to the entire structure comprising the two
shocks plus the shocked gas in between them, separated by a
\textit{contact discontinuity}.  The working surface may be due to the
interaction of the jet with a relatively quiescent medium, or may be an
``internal working surface'' within the jet that is due to
supersonic temporal variations in the flow velocity
\citep{Raga:1990a}.

In empirical studies the relationship between these theoretical
constructs and the observed emission structures is not always clear.
In such cases the term ``bow shock'' is often used in a more general
sense to refer to the entire arc of emission.  In this paper, we will
concentrate on \textit{stellar bow shocks}, in which the position of
the star can serve as a useful reference point for describing the bow
shape.  The empirical terminology that we will employ is illustrated
in Figure~\ref{fig:bow-terminology}.  The \textit{apex} is the point
of closest approach of the bow to the star, which lies on the
approximate symmetry axis, and the region around the apex is sometimes
referred to as the \textit{head} of the bow.  The \textit{wings} are
the swept-back sides of the bow, which lie in a direction from the
star that is orthogonal to the axis, with the \textit{far wings} being
the wing region farthest from the apex. Finally, the \textit{tail} is
the region near the axis but in the opposite direction from the apex.

\begin{figure}
  % \includegraphics[width=\linewidth]{2winds-scheme}
  \includegraphics[width=\linewidth]{figs/generic-bowshock}
  \caption{Quasi-stationary bow shock structure formed by the
    interaction of two supersonic winds.  Lower-left inset box shows
    the case where the inner wind is anisotropic. The streamlines
    (thin lines) are drawn to be qualitatively realistic: they are
    straight in regions of hypersonic flow, but curved in subsonic
    regions, responding to pressure gradients in the shocked
    shells. Streamline slopes are discontinuous across oblique
    shocks.}
\label{fig:2-winds}
\end{figure}
\newcommand\Mach{\ensuremath{\mathcal{M}}} Figure~\ref{fig:2-winds}
shows an idealized schematic of how a double bow-shock shell is formed
from the interaction of two supersonic streams: an \textit{inner wind}
and an \textit{outer wind}, with the inner wind being the weaker of
the two (in terms of momentum), so that the shell curves back around
the inner source.  The outer wind may be from another star, or may be
a larger scale flow of the interstellar medium, such as the
\textit{champagne flow} produced by the expansion of an \hii{} region
away from a molecular cloud \citep{Tenorio-Tagle:1979a, Shu:2002a,
  Medina:2014a}.  Alternatively, it may be due to the supersonic
motion of the inner source through a relatively static medium, in
which case the outer wind will not be divergent as shown in the figure
but rather plane-parallel.  The thickness of the shocked shells at the
apex depends on the Mach number, \Mach{}, of the flows and the
efficiency of the post-shock cooling.  For sufficiently strong
cooling, the post-shock cooling zone thickness is negligible and the
shock can be considered isothermal.  In this case, the shell thickness
is of order \(\Mach^{-2}\) times the source-apex separation
\citep{Henney:2002a}, which can become very small for high Mach
numbers.  The shell thickness will tend to increase towards the wings,
due to the increasing shock obliqueness, which reduces the
perpendicular Mach number.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
  \caption[]{Schematic diagram of cylindrically symmetric two-wind
    interaction problem in the thin-shell limit, following
    \citet{Canto:1996}.}
  \label{fig:crw-schema}
\end{figure}
In the extreme thin-shell limit, the entire bow structure can be
treated as a surface.  The bow radius measured from the inner source
(star) is \(R(\theta, \phi)\), where \(\theta\) is the polar angle, measured from
the star-apex axis, and \(\phi\) is the azimuthal angle, measured around
that axis.  Assuming cylindrical symmetry about the axis, this reduces
to \(R(\theta)\), which is illustrated in Figure~\ref{fig:crw-schema},
following \citet{Canto:1996}.  The separation between the two sources
is \(D\) and the complementary angle, as measured at the position of
the outer source, is \(\theta_1\).  The minimum value of \(R(\theta)\) is the
stagnation radius, \(R_0\), which occurs at the apex (\(\theta = 0\)).  In
a steady state, ram-pressure balance on the axis implies that
\begin{equation}
  \label{eq:stagnation-radius}
  \frac{R_0} {D} = \frac{\beta^{1/2}} {1 + \beta^{1/2}} ,
\end{equation}
where \(\beta\) is the momentum ratio between the two winds.  If the winds
are isotropic, with inner wind mass-loss rate \(\dot{M}_{\w}\) and
terminal velocity \(V_{\w}\), while the outer wind has corresponding
values \(\dot{M}_{\w1}\) and \(V_{\w1}\), then the momentum ratio is
\begin{equation}
  \label{eq:beta-definition}
  \beta = \frac{\dot{M}_{\w} V_{\w}} {\dot{M}_{\w1} V_{\w1}} .
\end{equation}
The case where the outer wind is a parallel stream
\citep{Wilkin:1996a} corresponds to the limit \(\beta \to 0\), in which case
\(D\) is no longer a meaningful parameter.

% \TODO{Bow shocks from pulsars and neutron stars
%   \citep{Cordes:1993a, Brownsberger:2014a}.}

The paper is organized as follows.
%
In \S~\ref{sec:plan-alat-bow} we outline the geometric parameters that
are necessary for describing bow shapes and introduce two
dimensionless ratios: planitude and alatude.
%
In \S~\ref{sec:projection} we derive general results for the
projection of bow shapes on to the plane of the sky.
%
In \S~\ref{sec:conic} we apply the results to the simplest possible
class of geometric bow models: the quadrics of revolution, which
comprise spheroids, paraboloids, and hyperboloids, each of which
occupies a distinct region of the planitude--alatude plane.
%
In \S~\ref{sec:crw-scenario} we consider thin-shell hydrodynamic
models for the parallel-stream case (wilkinoids) and wind-wind case
(cantoids), including extension to an anisotropic inner wind
(ancantoids).  We calculate the location of the models in the
planitude--alatude plane as a function of the inclination of the bow
shock axis to the plane of the sky.
%
In \S~\ref{sec:more-realistic-bow} we test our methods against the
results of more realistic numerical simulations of bow shocks,
including the derivation of the shape parameters from maps of infrared
dust emission.
%
In \S~\ref{sec:conc} we summarise our results and outline how
following papers will apply these ideas to observations and to a more
extensive set of models and numerical simulations.

% The bow shocks we consider are originated by a source located at the
% origin, emitting a wind with a mass loss rate of $\dot{M}_{\w}$ and a
% terminal (supersonic) velocity $v_{\w}$. This wind interacts with another
% wind originated by another source located at a distance $D$ from the
% first one.  The mass loss rate of the second source is $\dot{M}_{\w1}$
% and the terminal velocity is $v_{\w1}$. The momentum of the wind of the
% second source is higher than the momentum of the first one, and the
% resultant bow shock is stationary due to pressure balance.

\section{Planitude and alatude of bow shapes}
\label{sec:plan-alat-bow}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/characteristic-radii}
  \caption[]{Parameters for characterizing a bow shape.  Bow radius
    from the star, measured parallel (\(R_0\)) and perpendicular
    (\(R_{90}\)) to the symmetry axis, together with radius of
    curvature (\(R_{\C}\)) at apex and asymptotic opening angle
    (\(\theta_\infty\)) of the far wings. }
  \label{fig:characteristic-radii}
\end{figure}

The stagnation radius \(R_0\) describes the linear scale of the bow
shock, but in order to characterize its shape more parameters are
required.  To efficiently capture the diversity of bow shapes, we
propose the parameters shown in Figure~\ref{fig:characteristic-radii}.
The perpendicular radius \(R_{90}\) is the value of \(R(\theta)\) at
\(\theta = 90^\circ\), whereas \(R_{\C}\) is the radius of curvature of the bow at
the apex (\(\theta = 0\)), which in cylindrical symmetry simplifies to
\begin{equation}
  \label{eq:radius-curvature}
  R_{\C} 
  % = R_0 \Biggl[ 1
  % - \frac{1} {R_0} \left.\frac{d^2\! R} {d\,\theta^2}\right|_{\theta = 0} \Biggr]^{-1}
  = \frac{R_0^2}{R_0 - R_{\theta\theta,0}} \ , 
\end{equation}
where \(R_{\theta\theta,0}\) is \(d^2 \!R / d\theta^2\) evaluated at \(\theta = 0\).

A fourth parameter is the asymptotic opening angle of the far wings,
\(\theta_\infty\), which is useful in the case that the wings are asymptotically
conical.  However, in many bow shocks the wings tend towards the
asymptotic angle only slowly, making \(\theta_\infty\) difficult to measure,
especially since the emission from the far wings is often weak at
best.  In contrast, the three radii, \(R_0\), \(R_{90}\), and
\(R_{\C}\). are straightforward to determine from observations.  One
simple method to estimate the radius of curvature is to make use of
the Taylor expansion\footnote{%
  This method assumes both that \(R(\theta)\) is even (true for a
  cylindrically symmetric bow) and that the orientation of the axis is
  already known.  Generalization to cases where these assumptions do
  not hold is discussed in Appendix~\ref{app:rcurv-empirical}.} %
of \(R(\theta)\) about the apex (with \(\theta\) in radians):
\begin{equation}
  \label{eq:taylor-R-theta}
  R(\theta) = R_0 + \frac12 R_{\theta\theta,0} \,\theta^2 + \mathcal{O}(\theta^4) \ ,
\end{equation}
so that fitting a polynomial in \(\theta^2\) to \(R(\theta)\) for
\(|\theta| < \Delta\theta \) yields \(R_0\) and \(R_{\theta\theta,0}\) from the first two
coefficients, and hence \(R_{\C}\) from
equation~\eqref{eq:radius-curvature}.  Experience has shown that
\(\Delta\theta = 30^\circ\) and three terms in the polynomial are good choices,
where the third term is used only as a monitor (if the co-efficient of
\(\theta^4\) is not small compared with \(R_0\), then it may indicate a
problem with the fit).

Since we have three radii, we can construct two independent
dimensionless parameters:
\begin{align}
  \label{eq:planitude}
  \text{Planitude} \quad \Pi & \equiv  \frac{R_{\C}} {R_0} \\
  \label{eq:alatude}
  \text{Alatude} \quad \Lambda & \equiv  \frac{R_{90}} {R_0}
\end{align}
and these will be the principal shape parameters that we will use in
the remainder of the paper.  The \textit{planitude}, \(\Pi\), is a
measure of the flatness of the head of the bow around the apex, while
the \textit{alatude}, \(\Lambda\), is a measure of the openness of the bow
wings.  Although ``planitude'' can be found in English dictionaries,
``alatude'' is a new word that we introduce here, derived from the
latin \textit{ala} for ``wing''.

Several previous studies have discussed the relation between
\(R_{90}\) and \(R_0\) as a diagnostic of bow shape (for example
\citealp{Robberto:2005, Cox:2012a, Meyer:2016a}), but as far as we
know, we are the first to include \(R_{\C}\).  \citet{Robberto:2005}
\S~4.2 use the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd
bow shapes in the Trapezium cluster in the center of the Orion Nebula
\citep{Hayward:1994a, Garcia-Arredondo:2001a, Smith:2005a}.  In that
case, the source of the outer wind is known, and so \(D\) is
well-determined (at least, in projection), but for many bow shocks
\(D\) is not known, and is not even defined for the moving-star or
parallel-stream case. \citet{Cox:2012a} \S~4.1 compare the observed
shapes of bow shocks around cool giant stars with an analytic model,
and use \(A\) and \(B\) for the projected values of \(R_0\) and
\(R_{90}\), respectively (see next section for discussion of
projection effects).  \citet{Meyer:2016a} \S~3.2 analyze the
distribution of \(R_0 / R_{90}\) (the reciprocal of our \(\Lambda\)) for
hydrodynamic simulations of bow shocks around runaway OB stars.

% In order to contrast different bow shock models, we derive a set of
% measurable radii. Each model used should predict them and these
% predictions can be compared with observations.
% \begin{itemize}
% \item Radius at axis of symmetry. Denoted as $R_0$.
% \item Radius of Curvature at the axis of symmetry. Denoted as $R_{\C}$
% \item Radius at the perpendicular direction to the symmetry
%   axis. Denoted as $R_{90}$
% \item For open bow shocks, the asymptotic angle. Denoted as
%   $\theta_\infty$
% \end{itemize}

%% 
%% Restriction to cylindrical symmetry
%%

% For simplicity, the current paper is restricted to cylindrically
% symmetric bow shock shapes.

%%
%% Effects of instabilities
%%

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
 % end input ./sec-intro.tex
 % \input{sec-generic-model}
% start input ./sec-projection.tex
\newenvironment{Vector}{\left(\begin{array}{c}}{\end{array}\right)}
\newcommand\uvec[1]{\bm{\hat{#1}}}
\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}

\section{Projection onto the plane of the sky}
\label{sec:projection}

In this section we calculate the apparent shape on the plane of the
sky of the limb-brightened border of a shock or shell that is
idealized as an arbitrary cylindrically symmetric surface.

% Note: I'm aware that some of this material should be moved to an appendix, but I think it will be a future edition.

\subsection{Frames of reference}
\label{sec:ref-frames}

Consider body-frame cartesian coordinates $(x,y,z)$, where \(x\) is
the symmetry axis, and spherical polar coordinates
\((R, \theta, \phi)\), where \(\theta\) is the polar angle and
\(\phi\) the azimuthal angle.  Since the surface is cylindrically
symmetric, it is can be specified as $R = R(\theta)$, so that
cartesian coordinates on the surface are:
\begin{equation}
  \begin{Vector}
    x \\ y \\ z
  \end{Vector} 
  = R(\theta)
  \begin{Vector}
    \cos\theta \\
    \sin\theta\cos\phi \\
    \sin\theta\sin\phi
  \end{Vector}.
  \label{eq:body-frame}
\end{equation} 
Suppose that the viewing direction makes an angle \(i\) with the
\(z\)~axis, so that we can define observer-frame coordinates
\((x', y', z')\), which are found by rotating the body-frame
coordinates about the \(y\)~axis:
\begin{equation}
  \begin{Vector}
    x' \\ y' \\ z'
  \end{Vector}
  = 
  \begin{Vector}
    x\cos i - z\sin i\\
    y \\
    z\cos i + x\sin i
  \end{Vector}.
  \label{eq:Trans}
\end{equation} 
The relationship between the two frames is illustrated in
Figure~\ref{fig:projection-pos}.  All quantities in the observer's
frame are denoted by attaching a prime to the equivalent quantity in
the body frame.  The celestial coordinates on the ``plane of the sky''
are given by \((x', y')\) with \(x'\) being the projected symmetry
axis of the surface, while the line of sight lies along \(-z'\).  The
inclination angle \(i\) is defined so that \(i = \ang{0}\) when the
surface is viewed perpendicular to its axis (\textit{side on}) and
\(i = \ang{90}\) when it is viewed along its axis (\textit{end on}).

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/projection-pos}
  \caption{Relationship between body frame (unprimed coordinates) and
    observer frame (primed coordinates).}
  \label{fig:projection-pos}
\end{figure}

\subsection{Unit vectors normal and tangential to the surface}
\label{sec:unit-vectors-normal}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-unit-vectors}
  \caption{Unit vectors in the body frame that are normal and
    tangential to the surface \(R(\theta)\) in a plane of constant
    azimuth, \(\phi\).}
  \label{fig:unitvec}
\end{figure}
We define unit vectors \(\uvec{n}, \uvec{t}\), such that \(\uvec{n}\) is normal to the surface, while \(\uvec{t}\) is tangent to the surface in a plane of constant \(\phi\). For \(\phi = 0\) the surface lies in the \(xy\) plane and it is straightforward to show (Fig.~\ref{fig:unitvec}) that in this case the unit vectors are given by 
\begin{equation}
  \label{eq:uvec-phi0}
  \uvec{t}_0 =
  \begin{Vector}
    -\cos\alpha \\ \sin\alpha \\ 0
  \end{Vector}
  \quad \mathrm{and} \quad
  \uvec{n}_0 =
  \begin{Vector}
    \sin\alpha \\ \cos\alpha \\ 0
  \end{Vector}, 
\end{equation}
where \(\alpha\) is the \textit{slope angle}, given by
\begin{equation}
  \label{eq:alpha}
  \tan\alpha = -\left.\frac{dy}{dx}\right\vert_{R(\theta)} 
  = \frac{1 + \omega \tan\theta}{\tan\theta - \omega}
\end{equation}
and \(\omega\) is a dimensionless \textit{local growth factor}:
\begin{equation}
  \label{eq:omega}
  \omega(\theta) = \frac{1}{R} \frac{dR}{d\theta} . 
\end{equation}
For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, and then
converting to the observer frame by use of equation~(\ref{eq:Trans})
to give
\begin{gather}
  \label{eq:nprime}
  \begin{split}
    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
    & \times 
      \begin{Vector}
        (\cos\theta+\omega\sin\theta)\cos i 
        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
        (\sin\theta-\omega\cos\theta)\cos\phi \\
        (\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector}\\
  \end{split}\\
  \label{eq:tprime}
  \begin{split}
    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
    & \times 
      \begin{Vector}
        -(\sin\theta-\omega\cos\theta)\cos i
        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
        (\cos\theta+\omega\sin\theta)\cos\phi \\
        -(\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector}
  \end{split}
  \end{gather}
\subsection{Tangent line}
\label{sec:tangent-line}

% For optically thin emission with isotropic emissivity \(j\), the observed
% surface brightness for any line of sight that intersects the shell is
% \(S = \int j \, dz' / 4\pi\).

% If the shell thickness is \(h(\theta)\) and emissivity is
% \(j(\theta)\), then for optically thin emission the observed
% surface brightness for any line of sight that intersects the shell is
% \(S = j s / 4\pi\), where \(s\)

% in the limit \(h \ll R\) and
% \(\mu\) is
% the cosine of the angle between the line of sight and the local normal
% to the shell surface at the point of intersection:
% \begin{equation}
%   \label{eq:2}
%   \mu = \uvec{n} \cdot \uvec{z}'
% \end{equation}

The boundary on the plane of the sky of the projected surface is the
locus of those lines of sight that graze the surface tangentially.
This corresponds to a curved line on the surface itself, which we
denote the \textit{tangent line}, and which is defined by the
condition  
\begin{equation}
  \label{eq:tangent-line-condition}
  \uvec{n}'\cdot \uvec{z}' = 0.
\end{equation}
We denote by \(\phi\T\) that value of $\phi$ that satisfies this
relation for a given inclination, \(i\), and polar angle, \(\theta\):
\begin{equation}
\sin\phi\T = -\tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
\label{eq:tanphi}
\end{equation}
From equations~(\ref{eq:body-frame}, \ref{eq:Trans}) it follows that
the observer-frame coordinates of the tangent line are given by
\begin{equation}
\left(\begin{array}{c}
x'\T \\ y'\T \\ z'\T
\end{array}\right)= R(\theta)\left(\begin{array}{c}
\cos\theta\cos i - \sin\theta\sin\phi\T \sin i \\
\sin\theta(1-\sin^2\phi\T)^{1/2} \\
\cos\theta\sin i +\sin\theta\sin\phi\T\cos i
\end{array}\right).
\label{eq:tangential}
\end{equation} 
Note that, in general, \(z'\T\) is not a linear function of \(x'\T\)
and \(y'\T\), so that the tangent line is not a plane curve.

The apparent shape \((x'\T, y'\T)\) of the tangent line on the plane
of the sky can also be described in polar form as \(R'(\theta')\),
where
\begin{equation}
  \label{eq:R-prime-theta-prime}
  R' = (x'^2\T+ y'^2\T)^{1/2} 
  \quad \text{and} \quad
  \tan\theta' = y'\T / x'\T.
\end{equation}
Note that equation~(\ref{eq:tanphi}) will not have
a solution for arbitrary values of $\theta$ and $i$, but only when
$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent
line only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of \(\theta\) on the tangent line's projected symmetry axis (\(\theta' = 0\)), 
given implicitly by
\begin{align}
\tan\theta_{0} = \frac{|\tan i| + \omega(\theta_{0})}{1-\omega(\theta_{0}) |\tan i|} . 
\label{eq:thetapar}
\end{align}
In addition, if the surface is sufficiently ``open''
(\(\alpha \ge \alpha_{\mathrm{min}} > 0\) for all \(\theta\)), then for those
inclinations with
\(\vert i\vert > (\ang{90} - \alpha_{\mathrm{min}}) \) the tangent line does not exist
for any value of \(\theta\).  In other words, when the viewing angle is
sufficiently close to face-on, the projected surface has no ``edge''
and will no longer look like a bow shock to the observer.

\subsection{Characteristic radii on the plane of the sky}

% Considering further applications to bow shocks, we will consider open shells.
In order to compare the shell shape given by $R(\theta)$ with observations,
it is convenient to define the following apparent radii in the
observer frame: $R'_{0}$ and $R'_{90}$. These are projected distances
of the shell tangent line from the origin. The first is measured in
the direction of the symmetry axis, and the second in a perpendicular
direction. More concretely $R'_{0} = x'\T(y'\T=0)$ and
$R'_{90} = y'\T(x'\T=0)$. From equations (\ref{eq:tanphi}) and
(\ref{eq:tangential}) we find that:
\begin{align}
R'_{0} = R(\theta_{0})\cos(\theta_{0} + i) \label{eq:Rpar} 
\end{align}
Where $\theta_{0}$ is the solution of equation (\ref{eq:thetapar}), and
\begin{align}
  \label{eq:R90prime}
R'_{90} = R(\theta_{90})\sin\theta_{90}\left(1-\sin^2\bigl(\phi\T(\theta_{90})\bigr)\right)^{1/2}
\end{align}
Where $\theta_{90}$ is the solution of the implicit equation:
\begin{align}
  \label{eq:th90}
\cot\theta_{90} = \frac{1-\left(1+\omega(\theta_{90})^2\sin^22i\right)^{1/2}}{2\omega(\theta_{90})\cos^2 i}
\end{align}
The projected alatude (see \S~\ref{sec:plan-alat-bow}) is then given
by \(\Lambda' = R_{90}' / R_0'\).

Similarly, the projected planitude is \(\Pi' = R_{\C}' / R_0'\), where
\(R_{\C}'\) is found by applying the equivalent of equation
\eqref{eq:radius-curvature} for primed quantities:
\begin{equation}
  \label{eq:projected-radius-curvature}
  R_{\C}' 
  = \frac{(R_0')^2}{R_0' - R_{\theta'\theta',0}'} \ .
\end{equation}

\subsection{Line-of-sight velocities on the tangent line}
\label{sec:line-sight-veloc}
Motions in a thin shocked shell will be predominantly tangential to
the shell surface. In addition, for the particular case of wind-wind
bowshocks, the flow in each azimuthal slice can be shown to be
independent \citep{Wilkin:2000a}, which implies that the shell
velocity is parallel to \(\uvec{t}\). The projected line-of-sight
shell velocity is therefore
  \begin{equation}
    \label{eq:vlos}
    v_{\mathrm{los}} = (\uvec{t}' \cdot -\uvec{z}') \, v_{\parallel}(\theta) = \frac{v_{\parallel}(\theta) (1+\omega^2)^{1/2} \sin i }{\sin\theta - \omega\cos\theta} ,
  \end{equation}
  where \( v_{\parallel}(\theta)\) is the gas velocity along the shell and the standard sign convention has been adopted such that velocities away from the observer are deemed positive.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

 % end input ./sec-projection.tex
 % start input ./sec-conic.tex
\newcommand{\Q}{\ensuremath{\mathcal{Q}}}
\newcommand{\thetaQ}{\ensuremath{\theta_{\scriptscriptstyle \Q}}}

\begin{figure*}
  \setlength\tabcolsep{2em}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[height=0.45\linewidth]{figs/ellipse_edited}
        & \includegraphics[height=0.45\linewidth]{figs/hyperbola_edited}
  \end{tabular}
  \caption[]{Example off-center conic sections that can form quadrics of
    revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
    between the conic section parameters \(a\), \(b\), \(\thetaQ\) and the
    bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
    defined in Fig.~\ref{fig:characteristic-radii}. The origin (center
    of the weaker flow) is indicated by a red star, the center of
    curvature of the apex of the bow shock is indicated by a green
    dot, and the geometric center of the conic section is indicated by
    a blue cross, which is offset by \(x_0\) from the origin.  Note
    that \(R_0\), \(R_{90}\), \(R_c\), \(a\), and \(b\) are all
    \emph{lengths} and are always positive, whereas \(x_0\) is a
    \emph{displacement} and may be positive or negative.}
  \label{fig:conics}
\end{figure*}
\begin{figure}
  \includegraphics[width=\linewidth]{figs/conic1}
  \caption[]{Example of a family of conic sections, all with the same
    planitude (flatness at apex, marked by white dot):
    \(\Pi = R_c/R_0 = 2 \). The quadric angle, \(\thetaQ\), varies over
    the family (see text), with lower values of \(\thetaQ\) giving
    larger values of the alatude, \(\Lambda = R_{90}/R_0 \), meaning more
    open wings.  Different values of \(\Pi\) can be achieved for the
    exact same quadrics by sliding them along the \(x\)-axis, which
    will also change the axis scales since these are normalized by
    \(R_0\).}
  \label{fig:conics-family}
\end{figure}

\section{Quadrics of revolution}
\label{sec:conic}

For an arbitrary surface of revolution, application of
equations~(\ref{eq:tanphi}, \ref{eq:tangential}) to determine the
projected shape of the tangent line is not straightforward and in
general requires numerical techniques.  However, analytical results
can be found for the important class of surfaces known as
\textit{quadrics of revolution} \citep{Goldman:1983a, Gfrerrer:2009a},
which are formed by rotating a conic section plane curve about its
symmetry axis.  Examples are the sphere, spheroids (oblate and
prolate), and right circular paraboloids and hyperboloids.\footnote{We
  consider only the case of a single sheet of a 2-sheet hyperboloid or
  paraboloid, since these are the versions that resemble a bow,
  whereas the 1-sheet versions resemble the waist of an hourglass.}
We ignore the degenerate cases of cylinders, cones, and pairs of
parallel planes.  While mathematically simple, these quadrics are
sufficiently flexible that they can provide a useful approximation to
more complex bow shock shapes.

%The 
%In this section we will analyze the case where the resultant shape  of the bow shock is a conic curve (circle, ellipse, parabola or hyperbola).
%These curves are mathematical simple to model and give us a good reference to understand the effects of the projection effects
%described in the last section on other bow shocks. The source of the inner wind is located at the origin, and the center of the conic is located at
%a distance $x_0$ from the source.

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary

The shape of the quadric curves in the \(xy\) plane (\(\phi = 0\)) are
shown in Figure~\ref{fig:conics}(a) and (b) for the ellipse and
hyperbola case, respectively.  The conic section itself is fully
described by two lengths, \(a\) and \(b\), which are the
semi-axes.\footnote{Note that we do not require that \(a > b\), so
  either \(a\) or \(b\) may be the semi-major axis.}  However, the
curve can be translated along the \(x\) axis to an arbitrary point
with respect to the star, so that the apex distance \(R_0\) has no
necessary relation to \(a\) or \(b\) and therefore the star/bow
combination requires \emph{three} independent lengths for its
specification.  The displacement \(x_0\) from the star to the
``center'' of the conic section is
\begin{equation}
  \label{eq:conic-x0}
  x_0 = R_0 - \sigma a
  \quad \text{with} \quad
  \sigma = \begin{cases}
    +1 & \text{ellipse}\\
    -1 & \text{hyperbola}
  \end{cases} \ .
\end{equation}
For hyperbolas the center is ``outside'' of the bow and \(x_0\) is
always positive, whereas for ellipses the center is ``inside'' the bow
and \(x_0\) is usually negative, except when \(a < R_0\) (see
Figure~\ref{fig:conics}).

A general parametric form\footnote{%
  The special case of the parabola needs to be treated differently,
  see Appendix~\ref{app:parabola}.} %
for the \(xy\) coordinates of the quadrics (in the \(\phi = 0\) plane,
and with the star at the origin) as a function of \(t = [0, \pi]\) is
then
\begin{gather}
  \label{eq:par-xy}
  \begin{aligned}
    x &= x_0 + \sigma a \Cos(t) \\ 
    y &= b\Sin(t) 
  \end{aligned}
\end{gather}
where
\begin{equation}
  \label{eq:sin-sinh-etc}
  \Sin{}, \Cos = \begin{cases}
    \sin{}, \cos & \text{ellipse}\\
    \sinh{}, \cosh & \text{hyperbola}
  \end{cases}
\end{equation}
Except for the circle case (\(\sigma = +1\), \(a = b\)), the parametric
variable \(t\) is not actually an angle in physical space.  Instead,
the polar form of the bow shape \(R(\theta)\) must be found by substituting
equations~\eqref{eq:par-xy} into \(\theta = \tan^{-1} y/x\) and
\(R = (x^2 + y^2)^{1/2}\).

The type of quadric surface can be characterized by the
\textit{quadric parameter}:
\begin{equation}
  \label{eq:Tq}
  \Q \equiv \sigma \frac{b^2} {a^2} \ , 
\end{equation}
where \(\Q < 0\) corresponds to open surfaces (hyperboloids) and
\(\Q > 0\) corresponds to closed surfaces (oblate spheroids with
\(\Q > 1\) and prolate spheroids with \(\Q < 1\)).  Special cases are
the sphere (\(\Q = 1\)) and the paraboloid (\(\Q = 0\)).
Alternatively, one can define a \textit{quadric angle}:
\begin{equation}
  \label{eq:thetaQ}
  \thetaQ = \sigma \tan^{-1} (b/a) \ ,
\end{equation}
which is marked in Figure~\ref{fig:conics}.  In the case of
hyperboloids, the asymptotic opening angle of the wings
(\S~\ref{sec:plan-alat-bow} and Fig.~\ref{fig:characteristic-radii})
is \(\theta_\infty = \pi + \thetaQ\) (note that \(\thetaQ < 0\) in this case), and
the minimum slope angle is \(\alpha_{\mathrm{min}} = \abs{\thetaQ}\), see
discussion following equation~\eqref{eq:thetapar}.

\begin{figure}
  \includegraphics[width=\linewidth]{figs/conic-departure}
  \caption[]{Parabolic departure function, \(\Depart(\cos\theta)\), for
    conic sections with different planitude and alatude, centered on
    that of the confocal parabola, \((\Pi, \Lambda) = (2, 2)\), which has
    \(\Depart(\cos\theta) = 0\).  Planitude (shown by different line
    colors) determines the slope of \(\Depart\) at the apex,
    \(\cos\theta = 1\).  Alatude (shown by different line widths)
    determines the value of \(\Depart\) at \(\cos\theta = 0\).  All conics
    with \(\Pi = \Lambda\) have departure functions that are straight lines.}
  \label{fig:conic-departure}
\end{figure}

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R90-vs-i}
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution:
    variation with inclination, \(\abs{i}\), of bow size and shape.
    Different line colors correspond to varying quadric parameter,
    \(\Q\), (see key), while variation in line width corresponds to
    variation in the ``true'' planitude, \(\Pi\), or apex radius of
    curvature. Vertical gray rectangles show quartiles of
    \(\abs{\sin i}\), which will be equally populated for an isotropic
    distribution of orientations. (a)~Projected planitude:
    \(\Pi'\). (b)~Projected alatude, \(\Lambda'\).}
  \label{fig:quadric-projection}
  \bigskip
  \bigskip
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-R90-vs-Rc}
    & \includegraphics{figs/projected-R0-vs-i}
  \end{tabular}
  \caption[]{ As Figure~\ref{fig:quadric-projection}, but %
    (a)~diagnostic planitude--alatude diagram: \(\Lambda'\) versus
    \(\Pi'\), and %
    (b)~projected/true star-apex distance: \(R_0' / R_0\) versus
    \(\abs{i}\). %
    In (a), shading indicates different classes of quadrics:
    hyperboloids (white), prolate spheroids (dark gray), and oblate
    spheroids (light gray), with the limiting case of paraboloids
    shown by the thin black line.}
  \label{fig:quadric-projection-continued}
\end{figure*}

The set of parameters \((\Q, a, x_0)\) are then sufficient to
characterize the star/bow combination, where \(a\) is the quadric
scale and \(x_0\) is its center displacement from the star.  However,
we can also characterize the star/bow by \((R_0, \Pi, \Lambda)\), where
\(R_0\) is the star-apex distance, and \(\Pi\) and \(\Lambda\) are the
planitude and alatude, see \S~\ref{sec:plan-alat-bow}.  We now derive
the equivalences between these two descriptions.  The apex radius of
curvature for a conic section is
\begin{equation}
  \label{eq:Rc-conic}
  R_c = \frac{b^2}{a} = a \abs{\Q}\ ,
\end{equation}
whereas the perpendicular radius, \(R_{90}\), is the value of \(y\)
when \(x = 0\), which can be found from equations (\ref{eq:conic-x0},
\ref{eq:par-xy}) as
\begin{equation}
  \label{eq:conic-R90}
  R_{90}^2 = \Q \left(\sigma a^2 - x_0^2\right) \ .
\end{equation}
Combining equations (\ref{eq:planitude}, \ref{eq:alatude},
\ref{eq:conic-x0}, \ref{eq:Tq}--\ref{eq:conic-R90}) yields
\begin{align}
  \label{eq:R0-from-Q-a-x0}
  R_0 &= x_0 + \sigma a  \\
  \label{eq:Pi-from-Q-a-x0}
  \Pi &= \frac{a \Q}{a + \sigma x_0} \\
  \label{eq:Lambda-from-Q-a-x0}
  \Lambda &= \left( \Q \frac{a - \sigma x_0} {a + \sigma x_0}  \right)^{1/2}
\end{align}
with \(\sigma = \sgn Q\).  It also follows that the quadric parameter in
terms of the planitude and alatude is
\begin{equation}
  \label{eq:Tq-from-Pi-Lambda}
  \Q = 2 \Pi - \Lambda^2 
\end{equation}
% \begin{align}
%   \label{eq:a-from-R0-Pi-Lambda}
%   a &= R_0 \frac{ \Pi  } { \left|  2 \Pi - \Lambda^2\right| } \\
%   x_0 &= R_0 \frac{\Pi - \Lambda^2} {2 \Pi - \Lambda^2}
% \end{align}
Hence, it is the sign of \(2 \Pi - \Lambda^2\) that determines
\(\sigma\) and whether a quadric is a spheroid or a hyperboloid.  For
example, for a constant planitude, \(\Pi\), we can have a family of
different quadric types, with varying alatude, \(\Lambda\), that increases
from oblate, through prolate and paraboloid, to hyperboloid, as
illustrated in Figure~\ref{fig:conics-family}.

\subsection{Parabolic departure function}
\label{sec:parab-depart-funct}

The special case of confocal conic sections
(\(\Lambda = \Pi\)) can be written in polar form as
\begin{equation}
  \label{eq:confocal-polar}
  R(\theta) = R_0 \frac {1 + \ecc} {1 + \ecc \cos \theta}
\end{equation}
where \(\ecc = (1 - \Q)^{1/2}\) is the \textit{conic eccentricity}.
For the confocal parabola (\(\ecc = 1\)), the dimensionless reciprocal
radius is therefore \(R_0/R(\theta) = \tfrac12 (1 + \cos \theta)\), which
suggests the following form for a \textit{departure function} that
measures the difference between a given shape \(R(\theta)\) and the
parabola:
\begin{equation}
  \label{eq:departure-function}
  \Depart\bigl(\cos \theta\bigr) = \frac{R_0} {R(\theta)} - \tfrac12 \left( 1 + \cos \theta \right). 
\end{equation}
From equations~\eqref{eq:confocal-polar} and
\eqref{eq:departure-function} it is clear that \(\Depart\) is a linear
function of \(\cos \theta\) for other confocal conics, being positive for
ellipses (\(\ecc < 1\)) and negative for hyperbolae (\(\ecc > 1\)).
Examples are shown in Figure~\ref{fig:conic-departure} for a grid of 9
conics centered on the confocal parabola, with \((\Pi, \Lambda)\) ranging from
\(3/4\) to \(4/3\) of \((2, 2)\).  The hyperbolae have negative values
of \(\Depart\) in the far wings, with tracks that end at \(\cos \theta_\infty\).

Strictly speaking, the departure function is redundant if one is
interested in only conic sections, since they are fully determined by
\(\Pi\) and \(\Lambda\).  Nonetheless, as we will show in following sections,
it is a useful tool for studying general \(R(\theta)\), being very
sensitive to small variations in the shape.

% We have set a whole family of curves with a singular parameter denoted as:
% \begin{align}
%   \tan\theta_c \equiv \pm\frac{b}{a}\label{eq:Thc}
% \end{align}
% Positive values of this parameter describe closed curves (i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas).
% Particular cases are $\theta_c =\frac{\pi}{4}$,
% which describes a circle and $\theta_c=0$, which describes a parabola.
% To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic
% parameters $(a,b,\theta_c)$ could be derived from the former. Either way, the radius of curvature can be computed as:

% \begin{align}
% R_c = \frac{b^2}{a} \label{eq:Rc-conic}
% \end{align}

% For the rest of the parameters, the equation for ellipses and hyperbolas are very similar:

% \begin{align}
% R_{90} = \left|\tan\theta_c\right|\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
% \end{align}

% Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
% %But first is useful to define the quantities $\tilde{R}_c \equiv \frac{R_c}{R_0}$ and $\equiv \frac{\tilde{R}_{90}}{R_0}$ for simplification purposes.
% Hereafter is useful to denote with a tilde quantities which are normalized with $R_0$:

% \begin{align}
%   \tilde{a}\equiv \frac{a}{R_0} &= \pm\frac{\tilde{R}_c}{\left(2\tilde{R}_c-\tilde{R}_{90}^2\right)} \label{eq:a-con}\\
%   \tilde{b}\equiv \frac{b}{R_0} &= \frac{\tilde{R}_c}{\left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2}} \label{eq:b-con}
% \end{align}

% Dividing equations (\ref{eq:a-con}) and (\ref{eq:b-con}) and substituting into equation (\ref{eq:Thc}) we get:

% \begin{align}
% \tan\theta_c = \pm \left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2} \label{eq:th_c}
% \end{align}

% Note that the term $2\tilde{R}_c-\tilde{R}_{90}^2$ acts as a discriminant which determine the quadric we are working with.

%The transformation between the conic parameters and the characteristic radii are given by:
%\begin{align}
%R_c &= \frac{b^2}{a} \\
%R_{90} &= b\left[\pm\left(1 - \frac{(a \mp R_0)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
%\end{align}ut 
%In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric.
%The inverse transformation of (\ref{eq:Rc-conic}) and (\ref{eq:r90-conic}) is given by:
%\begin{align}
%\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
%\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
%\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
%\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
%#A &\equiv \frac{R_c}{R_0}
%\end{align}

\subsection{Plane-of-sky projection of quadric surfaces}

We now apply the machinery of \S~\ref{sec:projection} to find the
projected shape of a quadric bow on the plane of the sky.  The
intrinsic 3D shape of the shell is given by rotating
equations~\eqref{eq:par-xy} about the \(x\)-axis, but it is more
convenient to first transform to a reference frame where the origin is
at the center of the conic section:
\begin{equation}
  \label{eq:xyz-XYZ}
  (X, Y, Z) = (x - x_0, y, z) . 
\end{equation}
In this new frame, the quadric shape is
\begin{gather}
  \label{eq:quadric-XYZ}
  \begin{aligned}
    X &= a\Cos(t) \\ 
    Y &= b \Sin(t)\cos\phi \\
    Z &= b \Sin(t)\sin\phi
  \end{aligned}
\end{gather}
The azimuth of the tangent line as a function of inclination and
parametric variable is then found from equations (\ref{eq:alpha},
\ref{eq:tanphi}) to be
\begin{equation}
  \label{eq:phit-quadric}
  \sin\phi_{\T} = \frac{b \Cos(t)} {a \Sin(t)} \tan i \ .
\end{equation}
Combining equations~(\ref{eq:Trans}, \ref{eq:quadric-XYZ},
\ref{eq:phit-quadric}) gives the observer-frame cartesian
plane-of-sky coordinates of the tangent line:
\begin{gather}
  \label{eq:conic-projected-XY}
  \begin{aligned}
    X_{\T}' & = \frac{\Cos(t)}{a\cos i}
    \left(a^2\cos^2 i + \sigma b^2\sin^2 i\right)
    \\
    Y_{\T}' &= b\Sin(t)
    \left(
      1 - \frac{b^2 \Cos^2(t)}{a^2 \Sin^2(t)}
      \tan^2 i\right)^{1/2}
  \end{aligned}
\end{gather}
We wish to show that this projected shape is a conic section of the
same variety (ellipse or hyperbola) as the one that generated the
original quadric.  If this \emph{were} true, then it would be possible
to write the plane-of-sky coordinates as
\begin{gather}
  \begin{aligned}
    X_{\T}' &= a'\Cos( t')  \\
    Y_{\T}' &= b'\Sin (t')  . 
  \end{aligned}\label{eq:conic-projected-XY-conic}
\end{gather}
Comparing equations (\ref{eq:conic-projected-XY}) and
(\ref{eq:conic-projected-XY-conic}), we find after some algebra that
the two forms for \((X_{\T}', Y_{\T}')\) are indeed consistent, with
the equivalences:
%
\newcommand\fQi{\ensuremath{f_{\scriptscriptstyle \Q,i}}}
\begin{align}
  \label{eq:a-prime}
  a' &= a \fQi \cos i  \\
  \label{eq:b-prime}
  b' &= b \\
  t' &= \Cos^{-1} \left[ \fQi \Cos(t) \right]  \ ,
  % t' &= \Cos^{-1} \left[  \frac{a'\Cos(t)}{a\cos i}\right] \ .
\end{align}
where for convenience we define the quadric projection factor:
\begin{equation}
  \label{eq:fQi-factor}
  \fQi = \left( 1 + \Q \tan^2 i \right)^{1/2} \ .
\end{equation}
This demonstrates the original claim that the projected shape is also
a conic section, which means that we can re-use the previous
equations~(\ref{eq:R0-from-Q-a-x0}--\ref{eq:Tq-from-Pi-Lambda}) with
primed quantities substituted for unprimed ones.  From
equations~(\ref{eq:Tq}, \ref{eq:a-prime}, \ref{eq:b-prime}) it follows
that the quadric parameter of the projected shape is
\begin{equation}
  \label{eq:Q-prime}
  \Q' = \frac{ \Q } { \fQi^2 \cos^2 i} \ .
\end{equation}
Finally, we transform the projected reference frame back to be
centered on the star again:
\begin{equation}
  \label{eq:XYZ-xyz-prime}
  (x_{\T}', y_{\T}') = (X_{\T}' + x_0', Y_{\T}') \ , 
\end{equation}
where the projected quadric displacement \(x_0'\) follows from simple
foreshortening:
\begin{equation}
  \label{eq:x0-prime}
  x_0' = x_0 \cos i \ .
\end{equation}

% \begin{figure*}
%   \centering
%   \setkeys{Gin}{width=0.48\linewidth}
% \end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption[]{Variation with inclination angle of the apparent shape of
    quadric bows with true planitude and alatude that are uniformly
    distributed over the ranges \(\Pi = [0.5, 4.5]\),
    \(\Lambda = [0.5, 4.5]\).  Panels show the apparent
    \((\Pi', \Lambda')\) as the inclination is increased through uniform
    intervals in \(\abs{sin i}\).  Symbol color represents the quadric
    parameter, \(\Q\), increasing from dark blue, through orange, to
    yellow. Symbol size is proportional to the increase in apparent
    star--apex distance, \(R_0'/R_0\).}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}

The projection of the apex distance then follows from the primed
version of equation~\eqref{eq:R0-from-Q-a-x0} as
\begin{equation}
  \label{eq:R0-prime}
  \frac{R_0'}{R_0} =
  \cos i \left[ 1 + \frac{\Pi} {\Q} \bigl(\fQi - 1\bigr) \right]
\end{equation}
and the projected planitude and alatude can be calculated from
equations~(\ref{eq:Pi-from-Q-a-x0}, \ref{eq:Tq-from-Pi-Lambda},
\ref{eq:a-prime}, \ref{eq:Q-prime}) as
\begin{align}
  \label{eq:Pi-prime}
  \Pi' &= \frac{\Pi}{(R_0'/R_0)\, \fQi \cos i } \\
  \label{eq:Lambda-prime}
  \Lambda' &= \left( 2 \Pi' - \Q' \right)^{1/2} \ .
\end{align}
These are all shown in Figures~\ref{fig:quadric-projection}
and~\ref{fig:quadric-projection-continued} for a variety of quadric
parameter \(Q\) (line color) and true planitude \(\Pi\) (line
thickness).  The projected planitude and alatude
(Fig.~\ref{fig:quadric-projection}) behave in a qualitatively similar
fashion.  Whatever the true values of \(\Pi\) and \(\Lambda\), all spheroids
(\(\Q > 0\)) tend towards \(\Pi' = 1\) and \(\Lambda' = 1\) as the inclination
increases towards \(\ang{90}\).  This is because when the spheroid is
oriented edge-on, we see its circular cross-section.  Hyperboloids
behave differently: although \(\Pi'\) and \(\Lambda'\) initially decrease with
increasing inclination (for true \(\Pi > 2\)), they turn around and
increase again as \(\abs{i}\) approaches the critical value
\(i_{\mathrm{crit}} = \ang{90} - \abs{\thetaQ}\).  For
\(\abs{i} > i_{\mathrm{crit}}\) the tangent line does not exist (see
\S~\ref{sec:tangent-line}) because the line of sight is ``inside'' the
asymptotic cone of the far wings (with opening half angle
\(\alpha_{\mathrm{min}} = \abs{\thetaQ}\)), and so no limb-brightened shell
would be visible.\footnote{%
  As illustrated in Figure~8 of \citet{Graham:2002a}, the isophotal
  emission contours are elliptical in such a case (assuming
  cylindrical symmetry) and no curved bow shape is apparent.
  Deviations from cylindrical symmetry \emph{can} result in a curved
  emission arc, even for this no-tangent case
  (\citeauthor{Graham:2002a}'s Fig.~9), but that is beyond the scope
  of this paper.} For paraboloids and spheroids,
\(\alpha_{\mathrm{min}} = 0\), which means that the tangent line exists for
all viewing angles.

In Figure~\ref{fig:quadric-projection-continued}a, we show the
inclination-dependent tracks of the quadrics in the diagnostic
\(\Pi'\)--\(\Lambda'\) plane of projected alatude versus projected planitude.
The true planitude and alatude, which are seen for an edge-on viewing
angle \(i = \ang{0}\), are marked by filled circles.  The zones
corresponding to each class of quadric (oblate spheroid, prolate
spheroid, or hyperboloid) are marked by gray shading, and it can be
seen that the tracks never cross from one zone to another. The
convergence of all the spheroid tracks on the point
\((\Pi', \Lambda') = (1, 1)\) is apparent, as is the divergence of the
hyperboloid tracks towards \((\Pi', \Lambda') = (+\infty, +\infty)\).  The paraboloids,
by contrast, converge on the point \((\Pi', \Lambda') = (2, 2)\), and the
special case of the confocal paraboloid,\footnote{So named because the
  star is at the focus of the parabola.} with true planitude and
alatude \((\Pi, \Lambda) = (2, 2)\), is the only quadric whose apparent shape
remains identical for all inclination angles.

Figure~\ref{fig:quadric-projection-continued}b shows how the apparent
star-apex separation varies with inclination.  For moderate
inclinations, \(\abs{i} < \ang{30}\), this depends primarily on the true
planitude \(\Pi\), with very little influence of the quadric parameter
\(\Q\).  For \(\Pi > 1\), the separation increases with \(\abs{i}\), whereas
for \(\Pi < 1\) it decreases slightly.  Note, however, that for cases
where the projected distance to the source of the external flow,
\(D'\), can be measured, then \(R_0'/D'\) is always an increasing
function of \(\abs{i}\).  For larger inclinations, \(\abs{i} > \ang{30}\), the
strands for different \(\Q\) begin to separate, with hyperbolae
showing the strongest increase of \(R_0'\) with~\(\abs{i}\).

A complementary view of the effects of projection is shown in
Figure~\ref{fig:projected-R90-Rc-snapshots}, which shows ``snapshots''
of \((\Pi', \Lambda')\) for a sequence of 6 values of the inclination, equally
spaced in \(\abs{\sin {i}}\), so that each panel is equally likely for
an isotropic distribution of orientations.  The distribution of the
true \(\Pi\) and \(\Lambda\) are each assumed to be uniform on the range
\([0.5, 4.5]\), giving a uniformly filled square of values for
\(\abs{i} = 0\), which becomes increasingly distorted as \(\abs{i}\)
increases.  The color scale represents \(\Q\) and the symbol size is
proportional to \(R_0'/R_0\).  It can be seen that the points tend to
cluster closer and closer to the diagonal, \(\Lambda' = \Pi'\), as the
inclination increases, and that the points just below this line tend
to have the largest values of \(R_0'/R_0\).  The green shaded region
shows the zone of true \(\Lambda, \Pi\) for hyperboloids where the tangent
lines still exists for that value of \(\abs{i}\).  This becomes
smaller and smaller as \(\abs{i}\) increases, which explains why the
hyperboloid zone becomes increasingly depopulated: all quadrics that
lay above this region when \(i = \ang{0}\) will no longer be visible as a
bow for this value of \(\abs{i}\).  Note that this figure is merely
illustrative of the qualitative effects of projection, since in
reality there is no particular reason to expect a uniform distribution
in true \(\Pi\) and \(\Lambda\).

% Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:

% \begin{align}
% R'_0 &= \pm a' + x_0\cos i \\
% R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} +  (R_0 \mp a)\cos i
% \end{align}

% Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
% \begin{align}
% \frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
% \label{eq:qprime}
% \end{align}
% %Where $A\equiv \frac{R_c}{R_0}$
% The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
% \begin{align}
%   \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
%   \label{eq:Aprime}\\
%   \tan\theta'_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
%   \tilde{R}'_{90} &= \left(\frac{2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q}}{\frac{q'}{q}}\right)^{1/2}\frac{\sec i}{f(i;\theta_c)}
% \end{align}
% where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.

% When $R'_{90}$ is measurable, diagnostic diagrams like figure (\ref{fig:projected-R90-vs-Rc}) can be used to compare with observations.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

 % end input ./sec-conic.tex
 % start input ./sec-thin-shell.tex
\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}
\newcommand\CRW{\citetalias{Canto:1996}}

\section{Thin-shell bow shock models}
\label{sec:crw-scenario}

More physically realistic examples of bow shapes are provided by
steady-state hydrodynamic models for the interaction of hypersonic
flows in the thin-shell limit.  The classic examples are the solutions
for the wind--parallel stream and wind--wind problems (see
\S~\ref{sec:intro}) of \citet[][hereafter \CRW{}]{Canto:1996}, where
it is assumed that the two shocks are highly radiative and that the
post-shock flows are perfectly mixed to form a single shell of
negligible thickness. In this approximation, the shape of the shell is
found algebraically by \CRW{} from conservation of linear and angular
momentum, following an approach first outlined in
\citet{Wilkin:1996a}.  For the wind--stream case, the resulting bow
shape was dubbed \textit{wilkinoid} by \citet{Cox:2012a} and has the
form:
\begin{equation}
  \label{eq:wilkinoid-R-theta}
  R(\theta) = R_0\csc\theta\left( 3(1-\theta\cot\theta) \right)^{1/2} \ .
\end{equation}

For the wind--wind case, a family of solutions are found that depend on
the value of \(\beta\), the wind momentum ratio,\footnote{%
  By always placing the weaker of the two winds at the origin, it is
  only necessary to consider \(\beta \le 1\).  } %
see Figure~\ref{fig:crw-schema},
equations~(\ref{eq:stagnation-radius}, \ref{eq:beta-definition}), and
surrounding discussion in \S~\ref{sec:intro}.  We propose that these
shapes be called \textit{cantoids}.  The exact solution for the
cantoid shapes (eqs.~[23, 24] of \CRW{}) is only obtainable in
implicit form, but an approximate explicit solution (eq.~[26] of
\CRW{}) is very accurate for \(\beta \le 0.1\).  The wilkinoid shape
corresponds to the \(\beta \to 0\) limit of the cantoids.  Note that \CRW{}
employ cylindrical polar coordinates, \(z\) and \(r\), see our
Figure~\ref{fig:crw-schema}, and we follow this usage for the
thin-shell models discussed in this section.  \CRW{}'s \(z\) axis
corresponds to the cartesian \(x\) axis used in
sections~\ref{sec:projection} and \ref{sec:conic} of the current
paper, while the \(r\) axis corresponds to \(y\) when \(\phi = 0\).

A generalization of the cantoids to the case of an
anisotropic\footnote{Note that the wind anisotropy axis must be
  aligned with the star--star axis to maintain cylindrical symmetry.}
inner wind is developed next, giving rise
to what we call \textit{ancantoids}, which depend on an anisotropy
index, \(k\), in addition to \(\beta\).

\subsection{Bow shocks from anisotropic wind--wind interactions}
\label{sec:ancantoid}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/anisotropic-arrows}
  \caption[]{Schematic diagram of wind flow patterns in isotropic and
    non-isotropic cases for different values of the anisotropy index,
    \(k\).  Arrow length represents the wind momentum loss rate per
    solid angle.}
  \label{fig:anisotropic-arrows}
\end{figure}

We wish to generalize the results of \citet[\CRW{}]{Canto:1996} to the
case where the inner wind is no longer isotropic, but instead has a
density that falls off with angle, \(\theta\), away from the symmetry axis.
Specifically, at some fiducial spherical radius, \(R_0\), from the
origin, the wind mass density is given by
\begin{equation}
  \label{eq:ancantoid-density}
  \rho(R_0, \theta) =
  \begin{cases}
    \rho_0 \cos^k \theta & \text{for \(\theta \le \ang{90}\)} \\
    0 & \text{for \(\theta > \ang{90}\)}
  \end{cases}
  \ ,
\end{equation}
where \(\rho_0\) is the density on the symmetry axis and \(k \ge 0\) is an
\textit{anisotropy index}.  The wind velocity is still assumed to be
constant and the wind streamlines to be radial, so the radial
variation of density at each angle is
\(\rho(R, \theta) = \rho(R_0, \theta)\, (R/R_0)^{-2}\) and the wind mass loss rate and
momentum loss rate per solid angle both have the same \(\cos^k\theta\)
dependence as the density.  Examples are shown in
Figure~\ref{fig:anisotropic-arrows} for a variety of different values
of \(k\).  As \(k\) increases, the wind becomes increasingly jet-like.

Our primary motivation for considering such an anisotropic wind is the
case of the Orion Nebula proplyds and their interaction with the
stellar wind of the massive star \thC{}
\citep{Garcia-Arredondo:2001a}.  The inner ``wind'' in this case is
the transonic photoevaporation flow away from a roughly hemispherical
ionization front, where photoionization equilibrium, together with
monodirectional illumination of the front, implies that the ionized
hydrogen density, \(n\), satisfies \(n^2 \propto \cos \theta\), which is
equivalent to \(k = 0.5\) in equation~\eqref{eq:ancantoid-density}.
Since the primary source of ionizing photons is the same star that is
the source of the outer wind, it is natural that the inner wind's axis
should be aligned with the star--star axis in this case.  For other
potential causes of wind anisotropy (for instance, bipolar flow from
an accretion disk), there is no particular reason for the axes to be
aligned, so cylindrical symmetry would be broken.  Nevertheless, we
calculate results for general \(k\) with aligned axes, so as to
provide a richer variety of cylindrically symmetric bow shock shapes
than are seen in the cantoids.

\begin{figure}
\includegraphics[width=\linewidth]{figs/ancantoid-shape}
\caption{Bow shock shapes for interacting winds in the thin-shell
  approximation: cantoids and ancantoids. Coordinates are normalized
  by $D$, the distance between the two wind sources, which are
  indicated by black dots on the axis.  The weaker source is at
  \((0.0, 0.0)\) and the stronger source is at \((1.0, 0.0)\).
  Results are shown for different values of the wind momentum ratio,
  \(\beta\) (different line widths), and for the case where the weaker
  wind is isotropic (black lines) or anisotropic (colored lines).}
\label{fig:r-beta}
\end{figure}

The general solution for the bow shock shape, \(R(\theta)\), in the \CRW{}
formalism is
\begin{equation}
  R(\theta) = \frac {\dot{J}_{\w} + \dot{J}_{\w{}1}}
  {\left(\dot{\Pi}_{\w{}r}+\dot{\Pi}_{\w{}r1}\right)\cos\theta
    - \left(\dot{\Pi}_{\w{}z}+\dot{\Pi}_{\w{}z1}\right)\sin\theta}
  \label{eq:Rmom}
\end{equation}
where \(\dot{\Pi}_{\w{}r}\), \(\dot{\Pi}_{\w{}z}\), \(\dot{J}_{\w}\) are
the accumulated linear radial momentum, linear axial momentum, and
angular momentum, respectively, due to the inner wind emitted between
the axis and \(\theta\). The equivalent quantities for the outer wind have
subscripts appended with ``1''.  The inner wind momenta for our
anisotropic case (replacing \CRW{}'s eqs.~[9, 10]) are:
\begin{gather}
  \label{eq:ancantoid-momenta}
  \begin{aligned}
    \dot{\Pi}_{\w{}z} &= \frac{k + 1}{2(k+2)}\, \dot{M}_{\w}^0 V_{\w}
    \max\left[\bigl(1- \cos^{k+2} \theta\bigr), 1 \right] \\
    \dot{\Pi}_{\w{}r} &= (k + 1)\, \dot{M}^0_{\w} V_{\w}\, I_k (\theta) 
  \end{aligned}
\end{gather}
where
\begin{equation}
  \label{eq:ancantoid-mass-loss}
  \dot{M}^0_{\w} = \frac{2 \pi} {k + 1} r_0^2 \rho_0 V_{\w}
\end{equation}
is the total mass-loss rate of the inner wind. The integral
\begin{equation}
  \label{eq:ancantoid-I-integral}
  I_k(\theta) = \int^{\max(\theta, \pi/2)}_0 \cos^k \theta \sin^2\theta \,d\theta 
\end{equation}
has an analytic solution in terms of the hypergeometric function,
\({}_2 F_1(-\tfrac12; \tfrac{1+k}2; \tfrac{3+k}2; \cos^2 \theta)\), but is
more straightforwardly calculated by numerical quadrature.  The
angular momentum of the inner wind about the origin is
\(\dot{J}_{\w} = 0\) because it is purely radial.  The outer wind
momenta are unchanged from the \CRW{} case, but are given here for
completeness:
\begin{gather}
  \label{eq:ancantoid-momenta-outer}
  \begin{aligned}
    \dot{\Pi}_{\w{}z1} & =
    -\frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\sin^2\theta_1\\
    \dot{\Pi}_{\w{}r1} & =
    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)\\
    \dot{J}_{\w{}1} & =
    \frac{\dot{M}^0_{\w{}1}V_{\w{}1}}{4}\left(\theta_1-\sin\theta_1\cos\theta_1\right)D \ .
  \end{aligned} 
\end{gather}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-Pi-lambda-true}
  \caption[]{True shapes of cantoids and ancantoids in the
    \(\Pi\)--\(\Lambda\) plane, calculated according to results of
    App.~\ref{sec:thin-shell-shapes}.  For each line, \(\beta\) varies
    over the range \([0, 1]\) from lower left to upper right (although
    the black and red lines are truncated on the upper right), and
    line colors correspond to different anisotropy indices, matching
    those used in Fig.~\ref{fig:r-beta}. Circle symbols mark
    particular \(\beta\) values: \(0, 0.01, 0.1\), from largest to
    smallest circle.  Square symbols mark \(\beta = 0.5\), but with
    \(\Lambda\) calculated exactly, instead of using the approximation of
    equation~\eqref{eq:Lambda-approx}.  The white plus symbol marks
    the result for the wilkinoid:
    \((\Pi, \Lambda) = (\frac53, \sqrt{3})\).  Background shading indicates
    the domains of different quadric classes: hyperboloids (white),
    prolate spheroids (dark gray), and oblate spheroids (light gray).}
  \label{fig:ancantoid-Pi-lambda-true}
\end{figure}

We define \(\beta\) in this case as the momentum ratio \emph{on the symmetry axis}, which means that 
\begin{equation}
  \label{eq:ancantoid-momentum-ratio}
  \dot{M}^0_{\w{}1}V_{\w{}1} = 2 (k + 1)\, \beta\, \dot{M}^0_{\w} V_{\w} \ . 
\end{equation}
Substituting
equations~(\ref{eq:ancantoid-momenta}--\ref{eq:ancantoid-momentum-ratio})
into equation~\eqref{eq:Rmom} and making use of the geometric relation
between the interior angles of the triangle shown in
Figure~\ref{fig:crw-schema}:
\begin{equation}
  \label{eq:crw-angles}
  R \sin(\theta + \theta_1) = D \sin \theta_1 \ , 
\end{equation}
yields
\begin{equation}
  \label{eq:ancantoid-theta-theta1-implicit}
  \theta_1 \cot \theta_1 = 1 +
  2 \beta \left(
    I_k(\theta) \cot \theta
    - \frac{1 - \cos^{k+2} \theta} {k + 2} \right)   \ , 
\end{equation}
which is the generalization of \CRW{}'s equation~(24) to the
anisotropic case.  Equation~\eqref{eq:ancantoid-theta-theta1-implicit}
is solved numerically to give \(\theta_1(\theta)\), which is then combined with
equations~(\ref{eq:crw-angles}) and (\ref{eq:stagnation-radius}) to
give the dimensionless bow shape, \(R(\theta; \beta, k)/R_0\), where we now
explicitly indicate the dependence of the solution on two parameters:
axial momentum ratio, \(\beta\), and anisotropy index, \(k\).  We refer to
the resultant bow shapes as \textit{ancantoids}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-angles}
  \caption[]{Equivalent quadric angles, \(\theta_{\Q}\), for ancantoids and
    cantoids.  Solid lines show values of \(\theta_{\Q}\) calculated from
    \((\Pi, \Lambda)\), which is representative of the shape of the head,
    while dashed lines show \(\theta_{\Q}\) calculated from
    \(\theta_\infty\), which is representative of the tail.  Dot-dashed line
    shows the result for cantoids, which differ from the \(k=0\)
    ancantoids in \(\theta_\infty\), but not in \((\Pi, \Lambda)\). Gray shading and
    line colors have the same meaning as in
    Fig.~\ref{fig:ancantoid-Pi-lambda-true}. }
  \label{fig:ancantoid-angles}
\end{figure}

\begin{figure}
  \centering
  \setkeys{Gin}{width=\linewidth}
  \begin{tabular}{@{}l@{}}
    (a) \\
    \includegraphics{figs/crw-departure} \\
    (b) \\
    \includegraphics{figs/crw-departure-k38}
  \end{tabular}
  \caption[]{Parabolic departure function, \(\Depart(\cos\theta)\), for
    ancantoids and cantoids.  Heavy lines show the \(\beta = 0\) parallel
    stream case (Wilkinoid in the isotropic case).  Light lines show
    increasing values of \(\beta = \num{e-4}\), \num{0.001}, \num{0.01},
    \num{0.1}, as marked.  (a)~Cantoids (gray) and moderately
    anisotropic ancantoids: hemispheric, \(k = 0\) (black), and
    proplyd-like, \(k = 0.5\) (red). (b)~Cantoids (gray) and extremely
    anisotropic, jet-like ancantoids: \(k = 3\) (purple) and \(k = 8\)
    (blue).}
  \label{fig:ancantoid-departure}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime}
  \caption{Apparent bow shapes as a function of inclination angle for
    isotropic thin shell models. (a)~Confocal paraboloid for
    comparison (shape independent of inclination).
    (b)~Wilkinoid. (c)~Cantoid, \(\beta = 0.001\). (d)~Cantoid,
    \(\beta = 0.01\). }
  \label{fig:xyprime}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_ancantoid}
  \caption{Further apparent bow shapes as a function of inclination
    angle for anisotropic thin shell models (ancantoids).
    (a)~\(\beta = 0.001\), \(k = 0.5\); (b) (a)~\(\beta = 0.1\),
    \(k = 0.5\); (c)~\(\beta = 0.001\) \(k = 3\); (d)
    \(\beta = 0.1\) \(k = 3\).}
  \label{fig:xyprime-ancantoid}
\end{figure}

\subsection{True shapes of cantoids and ancantoids}
\label{sec:true-cantoids-ancantoids}

The shapes of the ancantoid bow shocks are shown in
Figure~\ref{fig:r-beta} for three different values of \(\beta\), and are
compared with the \CRW{} results for cantoids (dashed curves).  The
location of these shapes in the planitude--alatude plane is shown in
Figure~\ref{fig:ancantoid-Pi-lambda-true}, where the gray background
shading indicates the zones of different quadric classes, as in
\S~\ref{sec:conic}, Figures~\ref{fig:quadric-projection-continued}
and~\ref{fig:projected-R90-Rc-snapshots}.  Values of \(\Pi\) and
\(\Lambda\) are calculated via the analytic expressions derived in
Appendix~\ref{sec:ancantoid-planitude} and
\ref{sec:ancantoid-alatude}, respectively, which are only approximate
in the case of \(\Lambda\).  However, the filled square symbols show the
exact results for \(\beta = 0.5\), which can be seen to lie extremely close
to the approximate results, even for the worst case of \(k = 0\). The
leading term in the relative error of
equation~\eqref{eq:Lambda-approx} scales as \((\beta / (k + 2))^2\), so
the approximation is even better for smaller \(\beta\) and larger \(k\).

It is apparent from Figure~\ref{fig:r-beta} that the \(k=0\) ancantoid
is identical to the cantoid for \(\theta \le \ang{90}\) (\(z > 0\), to the right
of vertical dotted line in Fig.~\ref{fig:r-beta}), but is slightly
more swept back in the far wings.\footnote{%
  \label{fn:discontinuity}
  Due to the discontinuity in the inner wind density at
  \(\theta = \ang{90}\) (see Fig.~\ref{fig:anisotropic-arrows}), there is a
  discontinuity in the second derivative of the bow shape.} %
Since the true planitude and alatude depend on \(R(\theta)\) only in the
range \(\theta = [0, \ang{90}]\), the cantoid and the \(k = 0\) ancantoid
behave identically in Figure~\ref{fig:ancantoid-Pi-lambda-true}.
There is a general tendency for the bows to be flatter and more open
with increasing \(\beta\) and decreasing \(k\), with the cantoid being
most open at a given \(\beta\).  All the models cluster close to the
diagonal \(\Lambda \simeq \Pi\) in the planitude--alatude plane, but with a tendency
for \(\Lambda > \Pi\) at higher anisotropy.  There is therefore a degeneracy
between \(\beta\) and \(k\) for higher values of \(\beta\).  The wilkinoid
shape, which corresponds to the \(\beta \to 0\) limit of the cantoids, is
marked by a white plus symbol in
Figure~\ref{fig:ancantoid-Pi-lambda-true}, and lies in the prolate
spheroid region of the plane.  Cantoids lie either in the prolate
spheroid or hyperboloid regions, according to whether \(\beta\) is less
than or greater than about \(0.01\).  For ancantoids of increasing
\(k\), this dividing point moves to higher values of \(\beta\), until
almost the entire range of models with \(k = 8\) are within the
prolate spheroid zone.

However, the true planitude and alatude, which are what would be
observed for a side-on viewing angle (\(i = 0\)), are not at all
sensitive to the behavior of the far wings of the bow shock, which has
a rather different implication as to which variety of quadric best
approximates each shape.  We illustrate this is
Figure~\ref{fig:ancantoid-angles}, which shows two different ways of
estimating the quadric angle, \(\theta_{\Q}\) (see \S~\ref{sec:conic}).
The first is from \((\Pi, \Lambda)\), as in
Figure~\ref{fig:ancantoid-Pi-lambda-true}:
\newcommand\head{^{\text{head}}}
\newcommand\tail{^{\text{tail}}}
\begin{equation}
  \label{eq:thetaQ-head}
  \theta_{\Q}\head =
  \sgn{\bigl(2 \Pi - \Lambda^2\bigr)} \;
  \tan^{-1} \Abs{2\Pi - \Lambda^2}^{1/2} \ ,
\end{equation}
which follows from equations~\eqref{eq:Tq}, \eqref{eq:thetaQ}, and
\eqref{eq:Tq-from-Pi-Lambda}.  The second is from the asymptotic
opening angle of the wings, \(\theta_\infty\) (Fig.~\ref{fig:characteristic-radii}):
\begin{equation}
  \label{eq:thetaQ-tail}
  \theta_{\Q}\tail = \theta_\infty - \ang{180} \ , 
\end{equation}
where \(\theta_\infty\) is calculated from
equation~\eqref{eq:ancantoid-theta-inf} for ancantoids, or
\eqref{eq:cantoid-theta-inf} for cantoids.  If the bow shock shape
were truly a quadric, then these two definitions would agree.
However, as seen in Figure~\ref{fig:ancantoid-angles}, this is not the
case for the cantoids and ancantoids.  While
\(\smash[b]{\theta_{\Q}\head}\) generally corresponds to a prolate spheroid
(except for the largest values of \(\beta\)),
\(\smash[b]{\theta_{\Q}\tail}\) always corresponds to a hyperbola.  This
tension between the shape of the head and the shape of the far wings
has important implications for the projected shapes (as we will see in
the next section), since the far wings influence the projected
planitude and alatude when the inclination is large.

Figure~\ref{fig:ancantoid-departure} shows the parabolic departure
function (see \S~\ref{sec:parab-depart-funct}) for the thin-shell
models. This provides an alternative perspective on the resultant bow
shapes, with two different types of behavior being apparent.  Models
with high \(\beta\) and low anisotropy behave similarly to the
hyperboloids, such as the
\((\Pi, \Lambda) = (\nicefrac32, \nicefrac83)\), \((2, \nicefrac83)\),
\((\nicefrac83, \nicefrac83)\), and \((\nicefrac32, 2)\) cases from
Figure~\ref{fig:conic-departure}.  This is the case for the
\(\beta \ge 0.01\) models in Figure~\ref{fig:ancantoid-departure}a, which
all show departure functions that become negative in the far wings
(more open than parabola) and terminate at a
\(\theta_\infty < \ang{180}\).  The second type of behavior is shown by models with
low \(\beta\) or high anisotropy, which behave like spheroids for positive
and mildly negative values of \(\cos \theta\), but, unlike the spheroids,
all tend towards \(\Depart = 0\) in the far tail as \(\cos\theta \to -1\).

% \subsection{Characteristic Radii}
% $R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.
% %Here goes a little introduction
% For the rest of the radii we need a relation between $\theta$ and $\theta_1$ as follows:

% \begin{align}
% \theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
% \label{eq:th1th}
% \end{align}

% Equation (\ref{eq:th1th}) is reduced to equation (24) of \CRW{} when $k=0$.
% We can obtain $R_{90}$ by following the process shown in appendix \ref{app:r90-analytic},
% which lead us to a solution for $B \equiv \frac{R_{90}}{R_0}$:

% \begin{align}
% \tilde{R}_{90} = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
% \label{eq:B}
% \end{align}

% Now, the solution for $R_c$ is explained in appendix \ref{app:rc-analytic},
% which lead us to derive the radius of curvature at the symmetry axis:

% \begin{align}
% R_c &= R_0\left(1-2\gamma\right)^{-1} \label{eq:Rcurv} \\
% \mathrm{where:~} & \gamma = \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{6}(1-2\beta^{1/2})
% \end{align}

% Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
% conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})

% \begin{align}
% \tan^2\theta_c &= \left| \frac{3\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{2}{\left(1-2\gamma\right)}\right| 
% \label{eq:thc-CRW}
% \end{align}

% \begin{figure}
% \begin{tabular}{c}
% \includegraphics[width=\linewidth]{figs/AB-beta-log} \\
% \includegraphics[width=\linewidth]{figs/thc-beta-log}
% \end{tabular}
% \caption{Top: Characteristic radii, $\tilde{R}_c = R_c/R_0$ (solid lines) and $\tilde{R}_{90}
%   = R_{90}/R_0$ (dashed lines)
%   vs $\beta$, calculated from quadric fits to the generalized CRW
%   solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
%   angle $\theta_c$ vs $\beta$ for the bow 
%   shock head (solid lines) and the bow shock tail (dashed lines).}
% \label{fig:rad-beta}
% \end{figure}

% % Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
% %being $R_0$ the
% %easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

% With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
% momenta and different density distributions. Figure \ref{fig:rad-beta} shows equations ( \ref{eq:B}), (\ref{eq:Rcurv}) and (\ref{eq:thc-CRW}) for different anisotropy indexes.

% \subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}

% This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:

% \begin{align}
%   R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
% \end{align}
% Where:
% \begin{align}
%   R_0 = \left(\frac{\dot{M}_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
% \end{align}
% And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
% The characteristic radii are given by:
% \begin{align}
%   \tilde{R}_{90} &= \sqrt{3} \\
%   \tilde{R}_c &= \frac{5}{3}
% \end{align}
% The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}

% \subsection{Fits to the tail}
% \label{sec:fits-tail}

% In most cases, the quadric fit to the head of the bowshock does a very poor job of representing the ``wings'' or ``tail''.  The bowshock tail in all cases is asymptotically hyperbolic, with

% We therefore 
% We carry out three-level nested fits to determine the

% For the hyperbola ``center''
% \begin{multline}
%   \label{eq:tail-analytic-x0}
%   x_{0,\mathrm{t}} = 0.7 \beta^{-0.55} \biggl[
%     C_3 \bigl(\log_{10}\beta\bigr)^3 + C_2 \bigl(\log_{10}\beta\bigr)^2 
%   \\ + C_1 \log_{10}\beta + C_0
%   \biggr]
% \end{multline}
% \begin{equation}
%   \label{eq:tail-analytic-x0-minus-a}
%   (x_{0,\mathrm{t}} - a_{\mathrm{t}}) = D_2 (\log_{10}\beta)^2 + D_1 \log_{10}\beta + D_0
% \end{equation}
% where
% \begin{alignat}{2}
%   \label{eq:tail-analytic-coeffs-c}
%   C_k &= c_{2,k} \xi^2 + c_{1,k} \xi + c_{0,k} &\quad \text{for\ } k &= \{0, 1, 2, 3\} \\
%   \label{eq:tail-analytic-coeffs-d}
%   D_k &= d_{2,k} \xi^2 + d_{1,k} \xi + d_{0,k} &\quad \text{for\ } k &= \{0, 1, 2\}
% \end{alignat}

% % \newcommand\iso{\ensuremath{^{\mathrm{iso}}}}

% % \begin{table}
% %   \caption{Coefficients for hyperbola fit to bowshock tails}
% %   \label{tab:tail-fit-coeffs}
% %   \renewcommand\arraystretch{1.2}
% %   \setlength\tabcolsep{0.5\tabcolsep}
% %   \begin{tabular}{@{}llll@{}}
% %     \toprule
% %     Equation~(\ref{eq:tail-analytic-x0}) & 
% %     \multicolumn{3}{l}{
% %     Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
% %     } \\ \midrule
% %     \( C\iso_0 = +1.3195     \)    
% %     & \( c_{0,0} = +2.0758   \)  
% %     & \( c_{1,0} = -0.2309   \)  
% %     & \( c_{2,0} = -0.2532   \)\\
% %       \( C\iso_1 = +0.4229     \)    
% %     & \( c_{0,1} = +0.9571   \)  
% %     & \( c_{1,1} = -0.1530   \)  
% %     & \( c_{2,1} = -0.2487   \)\\
% %       \( C\iso_2 = +0.1092     \)    
% %     & \( c_{0,2} = +0.2528   \)  
% %     & \( c_{1,2} = -0.0360   \)  
% %     & \( c_{2,2} = -0.0794   \)\\
% %       \( C\iso_3 = +0.0051     \)    
% %     & \( c_{0,3} = +0.0171   \)  
% %     & \( c_{1,3} = -0.0010   \)  
% %     & \( c_{2,3} = -0.0095   \)\\ \midrule
% %     Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
% %     \multicolumn{3}{l}{
% %     Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
% %     } \\ \midrule
% %     \( D\iso_0 = +0.7962   \)    
% %     & \( d_{0,0} = +0.8516 \)  
% %     & \( d_{1,0} = -0.0907 \)  
% %     & \( d_{2,0} = -0.2002 \)\\
% %       \( D\iso_1 = -0.2363   \)    
% %     & \( d_{0,1} = -0.7620 \)  
% %     & \( d_{1,1} = +0.1411 \)  
% %     & \( d_{2,1} = -0.0295 \)\\
% %       \( D\iso_2 = -0.0126   \)    
% %     & \( d_{0,2} = -0.0683 \)  
% %     & \( d_{1,2} = +0.0390 \)  
% %     & \( d_{2,2} = -0.0236 \)\\
% %     \bottomrule
% %   \end{tabular}
% % \end{table}

% % \begin{figure*}
% %   \centering
% %   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
% %   \caption{Double quadric fits to thin shell
% %     solutions.}
% %   \label{fig:head-tail}
% % \end{figure*}

% % \begin{figure}
% %   \centering
% %   \includegraphics[width=\linewidth]{figs/two-quadric-th90-vs-i}
% %   \caption{Variation with inclination of the body-frame polar angle
% %     \(\theta_{90}\) that corresponds to the projected perpendicular radius
% %     \(R’_{90}\).  Line colors and thicknesses represent different
% %     quadrics of revolution, as in
% %     Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
% %     important because the quadric fits to the bow shock shape must be
% %     accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
% %     for \(R’_{90}\).}
% %   \label{fig:projected-th90}
% % \end{figure}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
%   \caption[]{Residuals of double quadric fits to thin shell solutions.
%     Residuals are expressed as the fractional error in the
%     complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
%     the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
%   \label{fig:head-tail-residuals}
% \end{figure*}

% \subsection{Projection effects in the thin shell model}
% \label{sec:proj-effects-thin}

\begin{figure}
  \centering
  \setkeys{Gin}{width=\linewidth}
  \begin{tabular}{@{}l@{}}
    (a) \\
    \includegraphics{figs/ancantoid-R90-vs-Rc-a} \\
    (b) \\
    \includegraphics{figs/ancantoid-R90-vs-Rc-b}
  \end{tabular}
  \caption[]{Apparent projected shapes of wilkinoid, cantoids and
    ancantoids in the \(\Pi'\)--\(\Lambda'\) plane.  Colored symbols indicate
    the \(\abs{i} = 0\) position for \(\beta = 0.001\), \(0.003\),
    \(0.01\), \(0.03\), \(0.1\), \(0.3\).  Thin lines show the
    inclination-dependent tracks of each model, with tick marks along
    each track for 20 equal-spaced values of \(\abs{\sin i}\).  Gray
    shaded regions are as in
    Fig.~\ref{fig:quadric-projection-continued}a.  The wilkinoid track
    is shown in white. (a)~Isotropic wind model (cantoid) and
    proplyd-like model (ancantoid, \(k = 0.5\)). (b)~Hemispheric wind
    model (ancantoid, \(k = 0\)) and jet-like model (ancantoid,
    \(k = 3\)).}
  \label{fig:thin-shell-R90-Rc}
\end{figure}

\subsection{Apparent shapes of projected cantoids and ancantoids}
\label{sec:proj-shap-cant}

Figures~\ref{fig:xyprime} and~\ref{fig:xyprime-ancantoid} show the
apparent bow shapes of various thin shell models (wilkinoid, cantoids,
ancantoids) for different inclination angles \(\abs{i}\).  For
comparison, Figure~\ref{fig:xyprime}a shows the confocal paraboloid,
whose apparent shape is independent of inclination (see
Appendix~\ref{app:parabola}).  The wilkinoid (Fig.~\ref{fig:xyprime}b)
shows only subtle changes, with the wings becoming slightly more swept
back as the inclination increases.  The cantoids
(Fig.~\ref{fig:xyprime}c and d) behave in the opposite way, with the
wings becoming markedly more open once \(\abs{i}\) exceeds
\(\ang{60}\) (for \(\beta = 0.001\)), or \(\ang{45}\) (for
\(\beta = 0.01\)).  The ancantoids (Fig.~\ref{fig:xyprime-ancantoid}) can
show more complex behavior.  For instance, in the \(k = 0.5\),
\(\beta = 0.001\) ancantoid (Fig.~\ref{fig:xyprime-ancantoid}a) the near
wings begin to become more closed with increasing inclination up to
\(\abs{i} = \ang{60}\), at which point they open up again, whereas the
opening angle of the far wings increases monotonically with
\(\abs{i}\).

The inclination-dependent tracks that are traced by the thin-shell
models in the projected planitude--alatude plane are shown in
Figure~\ref{fig:thin-shell-R90-Rc}.  The behavior is qualitatively
different from the quadric shapes shown in
Figure~\ref{fig:quadric-projection-continued}a in that the tracks are
no longer confined within the borders of the region of a single type
of quadric (hyperboloid or spheroid). At low inclinations, many of the
models behave like the prolate spheroids, but then transition to a
hyperboloid behavior at higher inclinations, which is due to the
tension between the shape of the head and the shape of the far wings,
as discussed in the previous section. This can be seen most clearly in
the \(\beta = 0.001\), \(k = 0.5\) ancantoid (lowest red line in
Fig.~\ref{fig:thin-shell-R90-Rc}a, see also zoomed version in
Fig.~\ref{fig:convergence-cantoid-wilkinoid}). The track begins
heading towards \((\Pi', \Gamma') = (1, 1)\), as expected for a spheroid, but
then turns around and crosses the paraboloid line to head out on a
hyperboloid-like track.

Ancantoids with different degrees of inner-wind anisotropy are shown
in Figure~\ref{fig:thin-shell-R90-Rc}b.  In all cases, the tracks
follow hyperboloid-like behavior at high inclinations, tending to
populate the region just above the diagonal \(\Lambda' = \Pi'\).  The
\(k = 0\) ancantoids show a kink in their tracks at the point where
the projected apex passes through \(\theta = \ang{90}\), due to the
discontinuity in the second derivative of \(R(\theta)\) there (see
footnote~\ref{fn:discontinuity}).  The wilkinoid has a much less
interesting track, most clearly seen in the zoomed
Figure~\ref{fig:convergence-cantoid-wilkinoid}, simply moving the
short distance from \((\nicefrac53, \sqrt3)\) to
\((\nicefrac32, \smash{\sqrt{\nicefrac83}})\).  Despite its location
in the ellipsoid region of the plane, the fact that it has
\(\theta_\infty = \ang{180}\) means that it behaves more like a parabola at high
inclination, but converges on
\((\nicefrac32, \smash{\sqrt{\nicefrac83}})\) instead of \((2, 2)\)
since the far wings are asymptotically cubic, rather than quadratic.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ancantoid-R90-vs-Rc-lobeta-a}
  \caption[]{As Fig.~\ref{fig:thin-shell-R90-Rc}a but zoomed in to show
    the wilkinoid track (white) and the convergence of the cantoid
    tracks (purple) to the wilkinoid as \(\beta \to 0\).}
  \label{fig:convergence-cantoid-wilkinoid}
\end{figure}

The local density of tick marks gives an indication of how likely it
would be to observe each portion of the track, assuming an isotropic
distribution of viewing angles.  It can be seen that the ticks tend to
be concentrated towards the beginning of each track, near the
\(\abs{i} = 0\) point, so the hyperboloid-like portions of the tracks
would be observed for only a relatively narrow range of inclinations.
This concentration becomes more marked as \(\beta\) becomes smaller, which
helps to resolve the apparent paradox that the wilkinoid corresponds
to the \(\beta \to 0\) limit of the cantoids, and yet follows a
qualitatively different track.  The detailed behavior of the
small-\(\beta\) cantoid models is shown in
Figure~\ref{fig:convergence-cantoid-wilkinoid}, which zooms in on the
region around the wilkinoid track.  It can be seen that for
\(\beta < 0.001\) the cantoid tracks begin to develop a downward hook,
similar to the \(k = 0.5\) ancantoids discussed above.  For
\(\beta < 10^{-4}\) this begins to approach the wilkinoid track and the
high inclination, upward portion of the track becomes less and less
important as \(\beta\) decreases.

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\textwidth]{figs/two-quadric-R90-Rc-snapshots}
%   \caption{Variation with inclination angle of radii diagnostics}
%   \label{fig:thin-shell-R90-Rc-snapshots}
% \end{figure*}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
 % end input ./sec-thin-shell.tex
 % \input{app-dust-wave}
% \input{sec-standing-wave}
% start input ./sec-conclusions.tex
\section{More realistic bow shock models}
\label{sec:more-realistic-bow}

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-MHD2040-AllB7}\\[-\baselineskip]
  (b)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-HD2040}\\[-\baselineskip]
  \caption[]{Departure function for the shape of the contact
    discontinuity, measured from two numerical simulations of a
    \SI{20}{M_\odot} main-sequence star, moving at \SI{40}{km.s^{-1}}
    through a uniform medium of density \SI{0.57}{cm^{-3}}
    \citep{Meyer:2017a}. (a)~Magnetohydrodynamic simulation with
    ambient magnetic field of strength \SI{7}{\micro G}, oriented
    parallel to the stellar velocity. (b)~Hydrodynamic simulation with
    zero magnetic field.  Blue dots show the measured shape, while the
    thick, pale-red line shows a 12th-order Chebyshev polynomial fit.
    The published shapes only extend to
    \(\theta \approx 130\)--\ang{150}, so we extrapolate the shapes out to
    \(\theta = \ang{180}\). Two different extrapolations are shown,
    corresponding to bows that are asymptotically closed (dashed red
    line) or open (solid red line).  For comparison, black lines show
    the departure function for wilkinoid (thick line) and cantoids
    (thin lines).}
  \label{fig:sim-depart}
\end{figure}

The assumptions underlying the models of the previous section may
break down in various ways.  To test whether the planitude--alatude
analysis is still useful in less ``ideal'' situations, we here apply
it to more realistic simulations of stellar bow shocks.  We choose a
pair of hydromagnetic (HD) and magnetohydrodynamic (MHD) moving-star
simulations from \citet{Meyer:2017a}, in which the only difference is
the presence (MHD case) or absence (HD case) of an ambient magnetic
field with strength \(B = \SI{7}{\micro G}\), oriented parallel to the
stellar velocity.  In each case, the inner wind comes from a
\(20\,M_\odot\) main-sequence star, with mass loss rate and terminal
velocity that are roughly constant with time at
\(\dot{M}_{\w} \approx \SI{4e-7}{M_\odot.y^{-1}}\) and
\(V_{\w} \approx \SI{1200}{km.s^{-1}}\), while the outer wind is a
parallel stream due to the star's own motion at \SI{40}{km.s^{-1}}
through a uniform medium of density \SI{0.57}{cm^{-3}}.

For these parameters, the radiative cooling distance for shocked
ambient gas in the bow is a significant fraction (\(\approx 10\%\)) of the
bow shock size, \(R_0\), tending to increase towards the wings, and
the radiative cooling in the shocked stellar wind is even less
efficient.  This represents a gross violation of the assumptions
behind the thin-shell models, since the total shocked shell thickness
is of the same order as \(R_0\).  The parabolic departure function
(see \S~\ref{sec:parab-depart-funct}) for the shape of the contact
discontinuity\footnote{%
  Note that, in the non-magnetic HD models, efficient thermal
  conduction leads to a thick layer of hot, thermally evaporated
  ambient material that separates the shocked stellar wind from the
  cool, dense shell of shocked ambient gas \citep[see \S~3.3
  of][]{Meyer:2014b}.  In this case, the contact discontinuity is
  taken to be the boundary between hot and cold ambient gas, as
  opposed to the \textit{material discontinuity} between shocked
  ambient gas and shocked wind gas.  In the MHD models, the thermal
  conduction is almost completely suppressed, so that the material and
  contact discontinuities coincide. } %
in the two models is shown in Figure~\ref{fig:sim-depart} as blue
symbols.\footnote{%
  Measured from Figure~3 of \citet{Meyer:2017a} by tracing the
  \SI{0.4}{cm^{-3}} density contour.} %
The MHD simulation shows a strongly negative dip in the departure
function close to the apex (\(\cos \theta = 1\)), indicating a very flat
shape.\footnote{%
  \citet{Meyer:2017a} speculate that this flatness may be the
  signature of the formation of a complex multiple-shock topology at
  the apex \citep{de-Sterck:1999a}.  For our purposes, the reason does
  not matter, merely that the magnetic and non-magnetic models predict
  markedly different shapes. } %
The HD simulation shows only a small negative dip in the departure
function at the apex, but otherwise approximately follows the
wilkinoid curve in the forward hemisphere.  In both cases the
departure function is more positive than the wilkinoid in the far
wings (\(\cos \theta < -0.5\)), but we do not have data for the full range
of \(\theta\), and so two different extrapolations for
\(\theta \to \ang{180}\) are shown.  In the first (dashed red line in
figure), we fit a low-order polynomial of \(\cos \theta\) to the points
with \(\cos \theta < -0.5\) and extend it to \(\cos \theta = -1\), which gives
an asymptotically closed shape.  In the second extrapolation (solid
red line in figure), we fit a polynomial that is multiplied by
\((1 + \cos\theta)^{1/2}\), which forces the departure function to zero at
\(\cos \theta = -1\), giving an asymptotically open shape, as with the
wilkinoid.  In a true steady state, the far wings should be
asymptotically open, but as \(\theta \to \ang{180}\) the flow times become
longer and longer, so that a bow shock with a finite age will be
closed.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_simulation}
  \caption[]{Projected shapes of contact discontinuity from
    simulations at different inclinations \(\abs{i}\) (varying line
    color and thickness, see key).  Top row shows magnetized
    simulation of Fig.~\ref{fig:sim-depart}a, bottom row shows
    non-magnetized simulation of Fig.~\ref{fig:sim-depart}b.  Left
    column shows asymptotically open extrapolation, right column shows
    asymptotically closed extrapolation.  All shapes are normalized to
    the projected apex distance, \(R_0'\) }
  \label{fig:sim-xyp}
\end{figure}

Using a 12th-order Chebyshev fit to the traced shapes, we show the
apparent shape of the contact discontinuity at a series of inclination
angles, \(\abs{i}\), in Figure~\ref{fig:sim-xyp}.  The four panels
show the two simulations for each of the two far-wing extrapolations.
Comparison with Figures~\ref{fig:xyprime}
and~\ref{fig:xyprime-ancantoid} shows the general tendency is the same
as with the wilkinoid: that the apex becomes less flat and the wings
less open as the inclination angle is increased.  There is no sign of
the sudden increase in openness at high inclination, as seen in the
cantoids and ancantoids that are asymptotically hyperbolic.  On the
other hand, the projected shapes of both simulations vary much more
strongly with \(\abs{i}\) than the wilkinoid does.  For the HD
simulation, this is mainly apparent for \(\abs{i} > \ang{30}\), but
for the MHD simulation it occurs at all inclinations.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
  \caption[]{Apparent projected shapes of simulations in the
    \(\Pi'\)--\(\Lambda'\) plane.  Thick solid lines show the predicted
    inclination-dependent tracks of the traced contact discontinuity
    shape for the asymptotically open extrapolation, with tick marks
    indicating 20 equal intervals in \(\abs{\sin i}\). Thin solid
    lines show the same for the asymptotically closed extrapolation,
    which only deviates from the open case at the high-\(\abs{i}\) end
    of the HD tracks.  The true planitude and alatude are marked by
    filled circle symbols.  Open square symbols show the shapes traced
    from the dust emission maps at \SI{60}{\um} for inclinations of
    (largest to smallest) \ang{30}, \ang{45}, and \ang{60}. For
    comparison, the wilkinoid track is shown in white. Note that the
    scales of both axes are logarithmic in this case.}
  \label{fig:sim-Pi-Lambda}
\end{figure}

The resultant inclination-dependent tracks in the planitude--alatude
plane are shown in Figure~\ref{fig:sim-Pi-Lambda}.  These are compared
with measurements\footnote{%
  The shape measurements were performed by converting to contours the
  \SI{60}{\um} images in \citet{Meyer:2017a}'s Fig.~10 and then
  tracing the ridge of minimum radius of curvature of the contours.
  Identical results are found from using the \SI{100}{\um} maps
  instead.  For the \SI{25}{\um} maps, although the same results are
  found for low inclinations, in the maps with
  \(\abs{i} \ge \ang{45}\) in the HD case it becomes impossible to trace
  the limb-brightened rim because it becomes fainter than the emission
  from the true apex of the bow.} %
from post-processed infrared dust continuum maps at \SI{60}{\um}
\citep[\S~4.3 of][]{Meyer:2017a}, shown by open square symbols for
\(i = \ang{30}\), \ang{45}, and \ang{60}.  The agreement between the
two is good.  In particular, the \SI{60}{\um}-derived shapes are
always very close to the tracks derived from the contact discontinuity
shape. Also, the ordering of the three inclinations along the tracks
corresponds to what is predicted, although quantitatively there are
some slight deviations.  This close agreement stems from the fact,
emphasized by \citet{Meyer:2014b}, that the long-wavelength dust
emission from hot-star bow shocks tends to be dominated by material
just outside the contact discontinuity.  Note that there is almost no
difference in the planitude--alatude tracks between the closed and open
extrapolations.  This is because \(\Pi'\) and \(\Lambda'\) only depend on the
portion of \(R(\theta)\) between \(\theta_0\) (eq.~[\ref{eq:thetapar}]) and
\(\theta_{90}\) (eq.~[\ref{eq:th90}]), and these are both smaller than the
\(\theta\) range where extrapolation is necessary, except for in the HD
case at the highest inclinations.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-r0-prime}
  \caption[]{Apparent projected apex distance of simulations.  Line
    and symbol meanings are as in Figure~\ref{fig:sim-Pi-Lambda}.  In
    addition, triangle symbols at \(\abs{i} = \ang{0}\) denote radius
    measured on H\(\alpha\) optical emission maps.  Note that the distances
    for the blue square symbols have been adjusted according to the
    correction factor discussed in
    footnote~\ref{fn:meyer-correction}.}
  \label{fig:sim-R0-prime}
\end{figure}

Figure~\ref{fig:sim-R0-prime} shows the inclination
dependence of the projected apex distance, \(R_0'\).  As in the
previous figure, the lines show the prediction based on the shape of
the contact discontinuity, while the square symbols show the results
from the \SI{60}{\um} dust continuum maps.\footnote{%
  \label{fn:meyer-correction}
  There is an apparent error in the spatial scales for the HD
  simulations in Figs.~10 and 11 of \citet{Meyer:2017a}, with the dust
  emission peaks occurring at radii that are clearly too large.  The
  stated apex distance for the contact discontinuity in this
  simulation is \SI{0.69}{pc} from Table~2 of \citet{Meyer:2014b}, and
  the position of the peak in dust column density is \SI{0.70}{pc}
  from Fig.~17a of \citet{Meyer:2014b}.  These are consistent with
  Figs.~3, 4, and 7 of \citet{Meyer:2017a}, but not with Figs.~10 and
  11.  Luckily, the position of the true apex is clearly visible in
  the \SI{25}{\um} maps of Fig.~10 at inclinations of \ang{45} and
  \ang{60}.  The projected separation of the true apex is
  \(R_0 \cos i\), independent of the bow shape, which allows a
  correction factor of \num{0.65} to be found, assuming that the
  on-axis peak in the \SI{25}{\um} emission coincides with the peak in
  dust column density.  This correction has been applied to the blue
  square symbols shown in our Fig.~\ref{fig:sim-R0-prime}.} %
In addition, triangle symbols show results from H\(\alpha\) optical
emission line maps, which are given for \(i = 0\) in Fig.~7 of
\citet{Meyer:2017a}.  Again, the agreement is good between the values
derived from the shape of the contact discontinuity and those derived
from the surface brightness maps. The greatest discrepancy is seen
with the H\(\alpha\) maps and the intermediate inclination dust maps, with
\(R_0'\) being overestimated by a few percent in both cases.  The
differences in behavior between the two simulations are much larger
than this.  The larger true planitude of the MHD simulation means that
the relative increase of \(R_0'\) with \(\abs{i}\) is much stronger
than in the HD simulation for \(\abs{i} < \ang{45}\), as expected from
Figure~\ref{fig:quadric-projection}b.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-histograms}
  \caption[]{Histograms of (top to bottom) projected planitude,
    alatude, and bow shock size for the shape of the contact
    discontinuity in the \citet{Meyer:2017a} simulations. The \(y\)
    axis gives the probability density (per unit \(x\)-axis quantity),
    assuming a uniform distribution of viewing directions.}
  \label{fig:sim-histograms}
\end{figure}

The probability densities\footnote{%
  The probability density is defined so that its integral over the
  full range of the histogrammed variable is unity, making it
  independent of the histogram bin widths.  This means that the
  characteristic width of an approximately unimodal distribution is
  one over the maximum probability density.} %
of the apparent shape and size of the simulation bows (measured at the
contact discontinuity) are shown in Figure~\ref{fig:sim-histograms},
assuming that the viewing direction is uniformly distributed in solid
angle.  The modal value of the projected planitude is similar at
\(\Pi' \approx 1.8\) for both simulations, but the distribution is much
broader in the MHD case, which has a low-level wing extending out to
\(\Pi' \approx 6\).  The projected alatude distributions are both narrower
than the planitude (note the different scale of the histogram axis),
with the MHD case again being the broader of the two and peaking at a
slightly lower value (\(\Lambda' \approx 1.7\) as opposed to
\(\approx 1.8\) for the HD case).  Finally, the distribution of
projected-over-true apex distance is also broader for the MHD case.

\section{Summary and discussion}
\label{sec:conc}

We have shown that the shapes of stellar bow shocks can be usefully
characterized by two dimensionless numbers: the \textit{planitude},
\(\Pi\), or flatness of the bow's apex, and the \textit{alatude},
\(\Lambda\), or openness of the bow's wings (\S~\ref{sec:plan-alat-bow}).
The planitude and alatude can be estimated from ratios of lengths that
can be straightforwardly measured from observations or theoretical
models.  We develop a general method (\S~\ref{sec:projection}) for
finding the projected shape, \((\Pi', \Lambda')\), of a bow shock's
limb-brightened edge, or \textit{tangent line}, as a function of
inclination angle, \(i\), where the emission shell is idealized as a
cylindrically symmetric surface.

We first apply this method to find inclination-dependent tracks on the
projected planitude--alatude plane for the special case of
\textit{quadric} surfaces (\S~\ref{sec:conic}), such as hyperboloids,
paraboloids, and spheroids, where the tangent line is a conic section.
The spheroids and hyperboloids occupy distinct regions of the plane,
with the paraboloids defining the boundary between the two.  As the
inclination is increased from \(\abs{i} = 0\) (side-on) to
\(\abs{i} = \ang{90}\) (end-on), the tracks first tend to approach the
diagonal \(\Lambda' = \Pi'\), corresponding to confocal conics, always
remaining within their own region.  At the highest inclinations, the
spheroids all converge at \(\abs{i} = \ang{90}\) on the point
\((\Pi', \Lambda') = (1, 1)\) and the paraboloids on the point
\((\Pi', \Lambda') = (2, 2)\).  The hyperboloids, on the other hand diverge as
\((\Pi', \Lambda') \to (\infty, \infty)\) for a finite
\(i_{\mathrm{crit}}\), which depends on the asymptotic opening angle
of the tail.  For \(\abs{i} > i_{\mathrm{crit}}\), the tangent line no
longer exists for the hyperboloid, and it would no longer appear to be
a curved bow shock.  We introduce the parabolic departure function
(\S~\ref{sec:parab-depart-funct}) as tool for visualizing differences
in bow shapes, \(R(\theta)\), over the full range,
\(\theta = [\ang{0}, \ang{180}]\).

We then apply the projection method to a set of thin-shell
hydrodynamic models of bow shocks (\S~\ref{sec:crw-scenario}): the
\textit{wilkinoid} from a wind-parallel stream interaction and the
\textit{cantoids} from wind-wind interactions.  We generalize the
latter to the \textit{ancantoids}, where one of the winds is
anisotropic.  We find that the wilkinoid is confined to a small region
of the \(\Pi'\)--\(\Lambda'\) plane, with projected planitude and alatude
varying with inclination by \(< 15\%\).  The cantoids and ancantoids
with sufficiently small values of \(\beta\), the wind momentum ratio, have
more interesting behavior, with tracks that pass from the spheroid
region at low inclinations to the hyperboloid region at high
inclinations.

Finally (\S~\ref{sec:more-realistic-bow}), we test the projected shape
analysis methods against the results of computational fluid dynamic
simulations of magnetized and non-magnetized bow shocks from
\citet{Meyer:2017a} of a runaway OB main-sequence star.  We find that
measurements made on maps of infrared dust emission can be accurate
diagnostics of the projected shape of the contact discontinuity for
this type of bow shock (Fig.~\ref{fig:sim-Pi-Lambda}).  The
distributions of projected planitude and alatude for a population of
randomly oriented bow shocks shows systematic differences between the
different simulations.

This paper is the first of a series that will apply our shape analysis
to a wide variety of models and observations of stellar bow shocks.
In a second paper, % \citep{Henney:2018a}
we consider the alternative model of dusty radiation-driven bow wave
\citep{Ochsendorf:2014a}, instead of a hydrodynamic bow shock, and
also calculate the signature in the planitude--alatude plane of
oscillations in the bow shape, which may be due to instabilities or a
time-varying source.  In a third paper, % \citep{Henney:2018b},
we apply our techniques to observational datasets for three different
classes of stellar bow shocks: OB stars \citep{Kobulnicky:2016a}, cool
giants/supergiants \citep{Cox:2012a}, and young stars in the extended
Orion Nebula \citep{Henney:2013a}.  In a fourth paper,
% \citep{Tarango-Yong:2018b},
we analyze the proplyd bow shocks in the core of the Orion Nebula
\citep{Garcia-Arredondo:2001a}.

%and was applied to the proplyds in the core of the ONC.
%We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
%sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
%on \CRW{} work to estimate the intrinsic bow shock shape and get the ionizing flux for ionization balance 
%and the stagnation pressure for our sample of proplyds.
%Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
%distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
%while LV2 has the most anisotropic flow. And for the 177-341, 169-348 and 180-331 we found out that 
%the stellar wind is not enough to keep their bow socks stationary.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
 % end input ./sec-conclusions.tex

\section*{Acknowledgements}

We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN111215.  JATY acknowledges support via a
research studentship from Consejo Nacional de Ciencias y Tecnología,
Mexico.

\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
  Collaboration} et~al.}{2013}]{Astropy-Collaboration:2013a}
{Astropy Collaboration} et~al., 2013, \aap, 558, A33

\bibitem[\protect\citeauthoryear{{Canto}, {Raga}  \& {Wilkin}}{{Canto}
  et~al.}{1996}]{Canto:1996}
{Canto} J.,  {Raga} A.~C.,   {Wilkin} F.~P.,  1996, \mn@doi [\apj]
  {10.1086/177820}, \href {http://adsabs.harvard.edu/abs/1996ApJ...469..729C}
  {469, 729}

\bibitem[\protect\citeauthoryear{{Cox} et~al.,}{{Cox} et~al.}{2012}]{Cox:2012a}
{Cox} N.~L.~J.,  et~al., 2012, \aap, 537, A35

\bibitem[\protect\citeauthoryear{{Garc{\'{\i}}a-Arredondo}, {Henney}  \&
  {Arthur}}{{Garc{\'{\i}}a-Arredondo} et~al.}{2001}]{Garcia-Arredondo:2001a}
{Garc{\'{\i}}a-Arredondo} F.,  {Henney} W.~J.,   {Arthur} S.~J.,  2001, \apj,
  561, 830

\bibitem[\protect\citeauthoryear{{Gayley}}{{Gayley}}{2009}]{Gayley:2009a}
{Gayley} K.~G.,  2009, \apj, 703, 89

\bibitem[\protect\citeauthoryear{Gfrerrer \& Zsombor-Murray}{Gfrerrer \&
  Zsombor-Murray}{2009}]{Gfrerrer:2009a}
Gfrerrer A.,  Zsombor-Murray P.,  2009, Journal for Geometry and Graphics, 13,
  131

\bibitem[\protect\citeauthoryear{Goldman}{Goldman}{1983}]{Goldman:1983a}
Goldman R.,  1983, \mn@doi [IEEE Computer Graphics and Applications]
  {http://doi.ieeecomputersociety.org/10.1109/MCG.1983.263025}, 3, 68

\bibitem[\protect\citeauthoryear{{Graham}, {Meaburn}, {Garrington}, {O'Brien},
  {Henney}  \& {O'Dell}}{{Graham} et~al.}{2002}]{Graham:2002a}
{Graham} M.~F.,  {Meaburn} J.,  {Garrington} S.~T.,  {O'Brien} T.~J.,  {Henney}
  W.~J.,   {O'Dell} C.~R.,  2002, \apj, 570, 222

\bibitem[\protect\citeauthoryear{{Hartigan}, {Raymond}  \&
  {Hartmann}}{{Hartigan} et~al.}{1987}]{Hartigan:1987a}
{Hartigan} P.,  {Raymond} J.,   {Hartmann} L.,  1987, \apj, 316, 323

\bibitem[\protect\citeauthoryear{{Hayward}, {Houck}  \& {Miles}}{{Hayward}
  et~al.}{1994}]{Hayward:1994a}
{Hayward} T.~L.,  {Houck} J.~R.,   {Miles} J.~W.,  1994, \apj, 433, 157

\bibitem[\protect\citeauthoryear{{Henney}}{{Henney}}{2002}]{Henney:2002a}
{Henney} W.~J.,  2002, Revista Mexicana de Astronomia y Astrofisica, 38, 71

\bibitem[\protect\citeauthoryear{{Henney}, {Garc{\'{\i}}a-D{\'{\i}}az},
  {O'Dell}  \& {Rubin}}{{Henney} et~al.}{2013}]{Henney:2013a}
{Henney} W.~J.,  {Garc{\'{\i}}a-D{\'{\i}}az} M.~T.,  {O'Dell} C.~R.,   {Rubin}
  R.~H.,  2013, \mnras, 428, 691

\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Gilbert}  \&
  {Kiminki}}{{Kobulnicky} et~al.}{2010}]{Kobulnicky:2010a}
{Kobulnicky} H.~A.,  {Gilbert} I.~J.,   {Kiminki} D.~C.,  2010, \apj, 710, 549

\bibitem[\protect\citeauthoryear{{Kobulnicky} et~al.,}{{Kobulnicky}
  et~al.}{2016}]{Kobulnicky:2016a}
{Kobulnicky} H.~A.,  et~al., 2016, \apjs, 227, 18

\bibitem[\protect\citeauthoryear{{Mackey}, {Mohamed}, {Neilson}, {Langer}  \&
  {Meyer}}{{Mackey} et~al.}{2012}]{Mackey:2012b}
{Mackey} J.,  {Mohamed} S.,  {Neilson} H.~R.,  {Langer} N.,   {Meyer} D.~M.-A.,
   2012, \apjl, 751, L10

\bibitem[\protect\citeauthoryear{{Mackey}, {Gvaramadze}, {Mohamed}  \&
  {Langer}}{{Mackey} et~al.}{2015}]{Mackey:2015a}
{Mackey} J.,  {Gvaramadze} V.~V.,  {Mohamed} S.,   {Langer} N.,  2015, \aap,
  573, A10

\bibitem[\protect\citeauthoryear{{Markevitch}, {Gonzalez}, {David},
  {Vikhlinin}, {Murray}, {Forman}, {Jones}  \& {Tucker}}{{Markevitch}
  et~al.}{2002}]{Markevitch:2002a}
{Markevitch} M.,  {Gonzalez} A.~H.,  {David} L.,  {Vikhlinin} A.,  {Murray} S.,
   {Forman} W.,  {Jones} C.,   {Tucker} W.,  2002, \apjl, 567, L27

\bibitem[\protect\citeauthoryear{{Meaburn}, {Boumis}  \& {Akras}}{{Meaburn}
  et~al.}{2013}]{Meaburn:2013a}
{Meaburn} J.,  {Boumis} P.,   {Akras} S.,  2013, \mnras, 435, 3462

\bibitem[\protect\citeauthoryear{{Medina}, {Arthur}, {Henney}, {Mellema}  \&
  {Gazol}}{{Medina} et~al.}{2014}]{Medina:2014a}
{Medina} S.-N.~X.,  {Arthur} S.~J.,  {Henney} W.~J.,  {Mellema} G.,   {Gazol}
  A.,  2014, \mnras, 445, 1797

\bibitem[\protect\citeauthoryear{{Meyer}, {Mackey}, {Langer}, {Gvaramadze},
  {Mignone}, {Izzard}  \& {Kaper}}{{Meyer} et~al.}{2014}]{Meyer:2014b}
{Meyer} D.~M.-A.,  {Mackey} J.,  {Langer} N.,  {Gvaramadze} V.~V.,  {Mignone}
  A.,  {Izzard} R.~G.,   {Kaper} L.,  2014, \mnras, 444, 2754

\bibitem[\protect\citeauthoryear{{Meyer}, {van Marle}, {Kuiper}  \&
  {Kley}}{{Meyer} et~al.}{2016}]{Meyer:2016a}
{Meyer} D.~M.-A.,  {van Marle} A.-J.,  {Kuiper} R.,   {Kley} W.,  2016, \mnras,
  459, 1146

\bibitem[\protect\citeauthoryear{{Meyer}, {Mignone}, {Kuiper}, {Raga}  \&
  {Kley}}{{Meyer} et~al.}{2017}]{Meyer:2017a}
{Meyer} D.~M.-A.,  {Mignone} A.,  {Kuiper} R.,  {Raga} A.~C.,   {Kley} W.,
  2017, \mnras, 464, 3229

\bibitem[\protect\citeauthoryear{{Ochsendorf}, {Verdolini}, {Cox}, {Bern{\'e}},
  {Kaper}  \& {Tielens}}{{Ochsendorf} et~al.}{2014}]{Ochsendorf:2014a}
{Ochsendorf} B.~B.,  {Verdolini} S.,  {Cox} N.~L.~J.,  {Bern{\'e}} O.,  {Kaper}
  L.,   {Tielens} A.~G.~G.~M.,  2014, \aap, 566, A75

\bibitem[\protect\citeauthoryear{{Phillips}, {Cuesta}  \&
  {Ramos-Larios}}{{Phillips} et~al.}{2010}]{Phillips:2010a}
{Phillips} J.~P.,  {Cuesta} L.~C.,   {Ramos-Larios} G.,  2010, \mnras, 409, 881

\bibitem[\protect\citeauthoryear{{Raga}, {Binette}, {Canto}  \&
  {Calvet}}{{Raga} et~al.}{1990}]{Raga:1990a}
{Raga} A.~C.,  {Binette} L.,  {Canto} J.,   {Calvet} N.,  1990, \apj, 364, 601

\bibitem[\protect\citeauthoryear{{Robberto} et~al.,}{{Robberto}
  et~al.}{2005}]{Robberto:2005}
{Robberto} M.,  et~al., 2005, \mn@doi [\aj] {10.1086/428000}, \href
  {http://adsabs.harvard.edu/abs/2005AJ....129.1534R} {129, 1534}

\bibitem[\protect\citeauthoryear{{Scherer} \& {Fichtner}}{{Scherer} \&
  {Fichtner}}{2014}]{Scherer:2014a}
{Scherer} K.,  {Fichtner} H.,  2014, \apj, 782, 25

\bibitem[\protect\citeauthoryear{{Schwartz}}{{Schwartz}}{1978}]{Schwartz:1978b}
{Schwartz} R.~D.,  1978, \apj, 223, 884

\bibitem[\protect\citeauthoryear{{Shu}, {Lizano}, {Galli}, {Cant{\'o}}  \&
  {Laughlin}}{{Shu} et~al.}{2002}]{Shu:2002a}
{Shu} F.~H.,  {Lizano} S.,  {Galli} D.,  {Cant{\'o}} J.,   {Laughlin} G.,
  2002, \apj, 580, 969

\bibitem[\protect\citeauthoryear{{Smith}, {Bally}, {Shuping}, {Morris}  \&
  {Kassis}}{{Smith} et~al.}{2005}]{Smith:2005a}
{Smith} N.,  {Bally} J.,  {Shuping} R.~Y.,  {Morris} M.,   {Kassis} M.,  2005,
  \aj, 130, 1763

\bibitem[\protect\citeauthoryear{{Stevens}, {Blondin}  \& {Pollock}}{{Stevens}
  et~al.}{1992}]{Stevens:1992a}
{Stevens} I.~R.,  {Blondin} J.~M.,   {Pollock} A.~M.~T.,  1992, \apj, 386, 265

\bibitem[\protect\citeauthoryear{{Tenorio-Tagle}}{{Tenorio-Tagle}}{1979}]{Tenorio-Tagle:1979a}
{Tenorio-Tagle} G.,  1979, \aap, 71, 59

\bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{1996}]{Wilkin:1996a}
{Wilkin} F.~P.,  1996, \apjl, 459, L31

\bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{2000}]{Wilkin:2000a}
{Wilkin} F.~P.,  2000, \apj, 532, 400

\bibitem[\protect\citeauthoryear{{Wilson} \& {Ulvestad}}{{Wilson} \&
  {Ulvestad}}{1987}]{Wilson:1987a}
{Wilson} A.~S.,  {Ulvestad} J.~S.,  1987, \apj, 319, 105

\bibitem[\protect\citeauthoryear{{Zank}}{{Zank}}{1999}]{Zank:1999a}
{Zank} G.~P.,  1999, \ssr, 89, 413

\bibitem[\protect\citeauthoryear{{de Sterck} \& {Poedts}}{{de Sterck} \&
  {Poedts}}{1999}]{de-Sterck:1999a}
{de Sterck} H.,  {Poedts} S.,  1999, \aap, 343, 641

\bibitem[\protect\citeauthoryear{{van Buren} \& {McCray}}{{van Buren} \&
  {McCray}}{1988}]{van-Buren:1988a}
{van Buren} D.,  {McCray} R.,  1988, \apjl, 329, L93

\bibitem[\protect\citeauthoryear{{van Dyke}}{{van Dyke}}{1982}]{van-Dyke:1982a}
{van Dyke} M.,  1982, {An album of fluid motion}.
Parabolic Press, Stanford, CA

\bibitem[\protect\citeauthoryear{{van Marle}, {Meliani}, {Keppens}  \&
  {Decin}}{{van Marle} et~al.}{2011}]{van-Marle:2011a}
{van Marle} A.~J.,  {Meliani} Z.,  {Keppens} R.,   {Decin} L.,  2011, \apjl,
  734, L26

\makeatother
\end{thebibliography}

\appendix
% start input ./app-parabola.tex
\section{Paraboloids and their plane-of-sky projection}
\label{app:parabola}

Equation~\eqref{eq:par-xy} for the \(xy\) coordinates of a quadric in the \(\phi = 0\) plane cannot be used in the case of a paraboloid (\(\Q = 0\)).  Instead, a convenient parametrization is
\begin{gather}
  \label{eq:parabola-xy}
  \begin{aligned}
    x &= R_0 \left(1  - \tfrac{1}{2} \Pi\, t^2\right) \\
    y &= R_0\, \Pi\, t \ ,
  \end{aligned}
\end{gather}
where we have ``baked in'' knowledge of the planitude,
\(\Pi = R_{\C}/R_0\) (see \S~\ref{sec:plan-alat-bow}). The projected
plane-of-sky coordinates of the tangent line follow from
equation~\eqref{eq:Trans} as
\begin{gather}
  \label{eq:parabola-xy-prime-phi}
  \begin{aligned}
    x_{\T}' / R_0 &= \left(1 - \tfrac{1}{2} \Pi\, t^2\right) \cos i
      + \Pi\, t \sin\phi_{\T} \sin i\\
    y_{\T}' / R_0 &= \Pi\, t \cos\phi_{\T}\ ,
  \end{aligned}
\end{gather}
The azimuth of the tangent line is found from
equations~(\ref{eq:alpha}, \ref{eq:tanphi}) as
\(\sin\phi_{\T} = -t^{-1} \tan i \), so that
\begin{gather}
  \label{eq:parabola-xy-prime-final}
  \begin{aligned}
    x_{\T}' / R_0 &= \cos i \left[ 1 + \tfrac{1}{2} \Pi \tan^2 i -
      \tfrac{1}{2} \Pi \left( t^2 - \tan^2 i \right) \right]\\
    y_{\T}' / R_0 &= \Pi \left( t^2 - \tan^2 i \right)^{1/2} \ .
  \end{aligned}
\end{gather}
The projected star--apex distance, \(R_0'\), is the value of
\(x_{\T}'\) when \(y_{\T}' = 0\), yielding
\begin{equation}
  \label{eq:parabola-R0-prime}
  R_0' / R_0 = \cos i \left( 1 + \tfrac{1}{2} \Pi \tan^2 i  \right) \ . 
\end{equation}
Note that this same result can be obtained from a Taylor expansion of
equation~\eqref{eq:fQi-factor} substituted into~\eqref{eq:R0-prime} in
the limit \(\Q \to 0\).

Equation~\eqref{eq:parabola-xy-prime-final} can be rewritten in the
form
\begin{gather}
  \label{eq:parabola-xy-all-primes}
  \begin{aligned}
    x_{\T}' &= R_0' \left(1  - \tfrac{1}{2} \Pi' t'^2\right) \\
    y_{\T}' &= R_0' \Pi' t' \ ,
  \end{aligned}
\end{gather}
where
\begin{align}
  \label{eq:parabola-Pi-prime}
  \Pi' &= \frac{2 \Pi} {2 \cos^2 i + \Pi \sin^2 i} \\
  \label{eq:parabola-t-prime}
  t' &= \cos i \left(t^2 - \tan^2 i\right)^{1/2} \ ,
\end{align}
which demonstrates that the projected shape is also a parabola. It is
apparent from \eqref{eq:parabola-Pi-prime} that the projected
planitude obeys
\begin{equation*}
\lim_{i \to \ang{90}} \Pi' = 2 \ ,
\end{equation*}
for all values of the true planitude \(\Pi\), as is shown by the black
lines in Figure~\ref{fig:quadric-projection}a. The projected alatude can
be found as
\begin{equation}
  \label{eq:parabola-Lambda-prime}
  \Lambda' = \left( 2 \Pi' \right)^{1/2} \ .
\end{equation}
For the special case of the confocal paraboloid,
\(\Pi = \Lambda = 2\), we have \(\Pi' = \Pi\) and
\(\Lambda' = \Lambda\) by equations~\eqref{eq:parabola-Pi-prime}
and~\eqref{eq:parabola-Lambda-prime} for all inclinations, so its
shape is unaffected by projection.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
 % end input ./app-parabola.tex
 %\input{app-ancantoid}
% start input ./app-shape-parameters.tex
\section{Analytic derivation of thin-shell bow shape parameters}
\label{sec:thin-shell-shapes}

In this appendix, we provide analytic calculations of the planitude,
alatude, and asymptotic opening angle for the wilkinoid, cantoids, and
ancantoids.  We first consider the most general case of the
ancantoids, and then show how results for cantoids and the wilkinoid
follow as special cases.

\subsection{Planitude of ancantoids}
\label{sec:ancantoid-planitude}

From equations~\eqref{eq:radius-curvature} and~\eqref{eq:planitude},
the planitude depends on the apex second derivative,
\(R_{\theta\theta,0}\), as
\begin{equation}
  \label{eq:planitude-from-2nd-derivative}
  \Pi = \left(  1 - R_{\theta\theta,0} / R_0\right)^{-1} \ .
\end{equation}
From equation~\eqref{eq:taylor-R-theta}, the second derivative can be
found from the coefficient of \(\theta^2\) in the Taylor expansion
of \(R(\theta)\).  Since we do not have \(R(\theta)\) in explicit analytic form,
we proceed via a Taylor expansion of the implicit
equations~\eqref{eq:crw-angles}
and~\eqref{eq:ancantoid-theta-theta1-implicit}, retaining terms up to
\(\theta^4\) to obtain from
equation~\eqref{eq:ancantoid-theta-theta1-implicit}:
\begin{equation}
  \label{eq:taylor-expansion-implicit}
  \theta_1^2 = \beta \theta^2 \left( 1 + C_{k\beta} \theta^2\right) + \mathcal{O}(\theta^6)\ , 
\end{equation}
with the coefficient \(C_{k\beta}\) given by
\begin{equation}
  \label{eq:C-k-beta}
  C_{k\beta} = \frac{1}{15} - \frac{3k}{20} - \frac{\beta}{15}  \ .
\end{equation}
Note that it is necessary to include the \(\theta^4\) term in the expansion
of \(\theta_1^2\) so that \(\theta_1/\theta\) is accurate to order
\(\theta^2\).  Then, from equation~\eqref{eq:crw-angles} we find
\begin{align}
  \label{eq:taylor-R-over-D}
  \frac{R}{D} & = \frac{\sin \theta_1} {\sin (\theta + \theta_1)} \nonumber \\
              & = \frac{\beta^{1/2}}{1+\beta^{1/2}}
                \left\lbrace 1 + \theta^2
                \left[ \frac{C_{k\beta}} {2 \left(1+\beta^{1/2}\right)}
                + \frac{1}{6} \left(1+2\beta^{1/2} \right)
                \right]
                \right\rbrace + \mathcal{O}(\theta^4) \ ,
\end{align}
where in the second line we have carried out a Taylor expansion of the
two \(\sin\) terms and substituted
\eqref{eq:taylor-expansion-implicit}.  Comparing coefficients of unity
and \(\theta^2\) between equations~\eqref{eq:taylor-R-theta} and
\eqref{eq:taylor-R-over-D} we find
\begin{align}
  \label{eq:again-R0-over-D}
  \frac{R_0} {D} &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
  \label{eq:final-second-derivative}
  \frac{R_{\theta\theta,0}} {R_0} &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{3}\left(1+2\beta^{1/2}\right) \ ,
\end{align}
so that the final result for the planitude, from~\eqref{eq:planitude-from-2nd-derivative}, is
\begin{equation}
  \label{eq:final-planitude}
  \text{ancantoid} \quad
  \Pi = \left[ {1 - \frac{C_{k\beta}}{1+\beta^{1/2}} - \frac{1}{3}\left(1+2\beta^{1/2}\right)}
  \right]^{-1} \ .
\end{equation}

\subsection{Alatude of ancantoids}
\label{sec:ancantoid-alatude}

To find the alatude, \(\Lambda = R_{90} / R_0\), we use
equation~\eqref{eq:crw-angles} at \(\theta = \ang{90}\) to write
\begin{equation}
  \label{eq:Lambda-from-theta-1-90}
  \Lambda = \frac{D} {R_0} \tan \theta_{1,90} \ , 
\end{equation}
where \(\theta_{1,90} = \theta_1(\theta = \ang{90})\), which, following
equation~\eqref{eq:ancantoid-theta-theta1-implicit}, must satisfy
\begin{equation}
  \label{eq:theta-1-90-implicit}
  \theta_{1,90} \cot \theta_{1,90}  = 1 - \frac{2 \beta}{k + 2} \ . 
\end{equation}
Combining \eqref{eq:Lambda-from-theta-1-90} and
\eqref{eq:theta-1-90-implicit} with \eqref{eq:again-R0-over-D} yields
\begin{equation}
  \label{eq:Lambda-beta-xi-theta-1-90}
  \Lambda = \frac{ \left(1 + \beta^{1/2}\right) \,\theta_{1,90}} {\beta^{1/2} \left(1 - \xi_k \beta\right)} \ ,
\end{equation}
where
\begin{equation}
  \label{eq:xi-k}
  \xi_k = \frac{2} {k +2} \ .
\end{equation}
We now take the Taylor expansion of equation~\eqref{eq:theta-1-90-implicit} to find
\begin{equation}
  \label{eq:theta-1-90-Taylor}
  \theta_{1,90}^2 + \tfrac{1}{15}  \theta_{1,90}^4 + \mathcal{O}(\theta_{1,90}^6)
  = 3 \xi_k \beta \ , 
\end{equation}
which, if \(\theta_{1,90}\) is small, has the approximate solution
\begin{equation}
  \label{eq:theta-1-90-approx}
  \theta_{1,90} \approx \left( \frac{3 \xi_k \beta} {1 + \tfrac15 \xi_k \beta} \right) \ .
\end{equation}
Substituting back into equation~\eqref{eq:Lambda-from-theta-1-90}
yields an approximate value for the alatude of
\begin{equation}
  \label{eq:Lambda-approx}
  \text{ancantoid} \quad
  \Lambda \approx \frac {(3 \xi_k)^{1/2} \left( 1 + \beta^{1/2} \right)}
  { \left( 1 + \tfrac15 \xi_k \beta \right)^{1/2} \left( 1 - \xi_k \beta \right)} \ .
\end{equation}
This approximation is surprisingly accurate, with a relative error of
order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).

\subsection{Planitude and alatude of cantoids and wilkinoid}
\label{sec:cantoid-wilkinoid-shapes}

Since \(\Pi\) and \(\Lambda\) depend on only that portion of the inner wind
emitted in the forward hemisphere, \(\theta \le \ang{90}\), the results for the
cantoids can be found by taking \(k = 0\), in which case
equations~(\ref{eq:C-k-beta}, \ref{eq:final-planitude}, \ref{eq:xi-k},
\ref{eq:Lambda-approx}) yield
\begin{gather}
  \label{eq:cantoid-Pi-Lambda}
  \text{cantoid} \quad
  \begin{cases}
    \quad \Pi &= \dfrac {5} {3 \left( 1 - \beta^{1/2} \right)}\\[12pt]
    \quad \Lambda &= \dfrac { \sqrt 3} {\left( 1 + \tfrac15 \beta \right)^{1/2} \left( 1 - \beta^{1/2} \right)} \ .
  \end{cases}
\end{gather}
The wilkinoid shape is equal to the \(\beta \to 0\) limit of the cantoid, so
its planitude and alatude are given by:
\begin{gather}
  \label{eq:wilkinoid-Pi-Lambda}
  \text{wilkinoid} \quad
  \begin{cases}
    \quad \Pi &= \dfrac {5} {3}\\[10pt]
    \quad \Lambda &= \sqrt 3 \ .
  \end{cases}
\end{gather}
The wilkinoid results can also be obtained directly from
equation~\eqref{eq:wilkinoid-R-theta}, and in the case of \(\Lambda\) this
has already been noted by several authors \citep{Cox:2012a,
  Meyer:2016a}.

\subsection{Asymptotic opening angle}
\label{sec:asympt-open-angle}

The asymptotic opening angle
of the far wings, \(\theta_\infty\), can be found from
equation~\eqref{eq:ancantoid-theta-theta1-implicit} for the
ancantoids, together with the condition that
\(\theta_\infty + \theta_{1\infty} = \pi\).  These yield the implicit equation
\begin{equation}
  \label{eq:ancantoid-theta-inf}
  \theta_\infty - \left( \frac {k + 2 (1 - \beta)} {k + 2} \right) \tan \theta_\infty
  = \pi + 2 \beta I_k(\pi/2) \ ,
\end{equation}
where
\begin{equation}
  I_k(\pi/2) = \frac{\sqrt \pi}{4} \,
      \frac{  \GammaFunc\left( \frac{k+1}{2} \right)} {\GammaFunc\left(\frac{k+4}{2}\right)}
\end{equation}
and \(\GammaFunc\) is the usual Gamma function.  This can be compared with the equivalent result obtained by \CRW{} for the cantoids:
\begin{equation}
  \label{eq:cantoid-theta-inf}
  \theta_\infty - \tan \theta_\infty = \frac{\pi}{1 - \beta} \ .
\end{equation}
Note that, unlike in the cases of \(\Pi\) and \(\Lambda\),
equation~\eqref{eq:ancantoid-theta-inf} does \emph{not} reduce to
equation~\eqref{eq:cantoid-theta-inf} in the limit \(k \to 0\).  This is
because, for \(\theta > \ang{90}\), the \(k = 0\) ancantoid differs from the
cantoid since the former has no wind in the backward hemisphere (see
Figure~\ref{fig:anisotropic-arrows}).  Therefore there is less inner
support for the far wings of the bow, and so \(\theta_\infty\) is smaller than
in the cantoid case.  The wilkinoid result again follows from
\(\beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that the far
wings are asymptotically parallel to the symmetry axis, as is the case
for the paraboloid (App.~\ref{app:parabola}).  In the case of the
wilkinoid, however, the behavior is cubic in the wings,
\(z \sim r^3\), as opposed to quadratic as in the paraboloid.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
 % end input ./app-shape-parameters.tex
 % \input{app-dust-equations}
% start input ./app-rcurv-empirical.tex
\section{Empirical determination of radius of curvature for a bow shock of unknown orientation}
\label{app:rcurv-empirical}

Consider a set of \(N\) points on the plane of the sky, with Cartesian
coordinates \(\bm{r}_k = (x_k, y_k)\) for \(k = 1 \dots N\).  We wish
to estimate the radius of curvature of the smooth curve that the set
of points is presumed to be sampled from.  To do this, we fit a circle
to the points as follows.  The circle is defined by its center,
\(\bm{r}_{\C} = (x_{\C}, y_{\C})\), and radius, \(R_{\C}\).  For a
given circle, we define a mean radius of the set of points from the
circle center:
\begin{equation}
  \label{eq:rcurv-mean-radius}
  \bar{R}(x_{\C}, y_{\C}) = \frac{1}{N}  \sum_{k = 1}^{N} \Abs{\bm{r}_k - \bm{r}_{\C}}  \ .
\end{equation}
We then optimize\footnote{%
  For example, using a Levenberg-Marquardt algorithm, such as
  \texttt{astropy.modeling.fitting.LevMarLSQFitter} from the AstroPy
  library \citep{Astropy-Collaboration:2013a}.} %
to find best-fit values \((x_{\C}^*, y_{\C}^*)\), which minimize the
objective function
\begin{equation}
  \label{eq:rcurv-objective-function}
  f(x_{\C}, y_{\C}) = \sum_{k = 1}^{N} \left(
    \abs{\bm{r}_k - \bm{r}_{\C}}  - \bar{R} (x_{\C}, y_{\C}) \right)^2 \ .
\end{equation}
The best-fit radius of curvature is then given by
\(R_{\C}^* = \bar{R}(x_{\C}^*, y_{\C}^*)\).

If we also know the position, \(\bm{r}_0 = (x_0, y_0)\), of the bow's
central source, then we can find the unit vector in the direction of
the bow's projected axis as
\begin{equation}
  \label{eq:rcurv-axis-vector}
  \uvec{\xi} = \frac {\bm{r}_0 - \bm{r}_{\C}^*} { \abs{\bm{r}_0 - \bm{r}_{\C}^*}} \ , 
\end{equation}
and the apex distance from the source as\footnote{%
  This is only valid if the resultant \(R_0 < R_{\C}^*\), otherwise
  the opposite sign of \(\uvec{\xi}\) must be taken.}
\begin{equation}
  \label{eq:rcurv-apex-distance}
  R_0 = \Abs{\bm{r}_{\C}^* + R_{\C}^* \uvec{\xi} - \bm{r}_0} \ .
\end{equation}
A refinement of the method is then to repeat the circle fit after
restricting the set of points to those lying within a certain angle
\(\Delta\theta\) of the bow axis by requiring
\begin{equation}
  \label{eq:rcurv-delta-theta}
  \uvec{\xi} \cdot 
  {\left( \bm{r}_k - \bm{r}_{\C}^* \right) }
  \ge   {\Abs{\bm{r}_k - \bm{r}_{\C}^*}}
  \cos \Delta\theta \ ,
\end{equation}
where we find that best results are obtained with \(\Delta\theta \le \ang{30}\).

If quantitative estimates exist for the uncertainties, \(\epsilon_k\), in the
measurements of \(\bm{r}_k\), then it is appropriate to incorporate
weights of \(\epsilon_k^{-2}\) in the objective function.  In cases where the
bow shape is traced by eye, based on real or synthetic observations, a
more practical approach is to maintain uniform weighting but to place
a greater density of points \(\bm{r}_k\) in regions where the shape is
well-determined and to place them more sparsely in regions where the
shape is less certain.

Note that this method is not necessary if the orientation of the bow
axis is known a~priori, in which case the Taylor series method
described in \S~\ref{sec:plan-alat-bow} is more efficient and
accurate.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:
 % end input ./app-rcurv-empirical.tex
 % Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-03-07 papers/paper1-submit/latexdiff/ms-bows02-expand.tex
Trial run with latexdiff

--- 2018-03-07 papers/paper1-submit/latexdiff/ms-bows01-expand.tex
@@
 \newcommand\phm[1]{\phantom{#1}}% 
-
 \makeatother
@@
 % start input ./sec-projection.tex
-\newenvironment{Vector}{\left(\begin{array}{c}}{\end{array}\right)}
-\newcommand\uvec[1]{\bm{\hat{#1}}}
-\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
 
@@
 \begin{equation}
+  \bm{r} \equiv
   \begin{Vector}
@@
 \((x', y', z')\), which are found by rotating the body-frame
-coordinates about the \(y\)~axis:
-\begin{equation}
+coordinates about the \(y\)~axis.  The same vector, \(\bm{r}\), expressed in the observer frame is then 
+\begin{equation}
+  \bm{r} = 
   \begin{Vector}
     x' \\ y' \\ z'
+  \end{Vector}
+  = \mathbfss{A}_y(i)\,
+  \begin{Vector}
+    x \\ y \\ z
   \end{Vector}
@@
     z\cos i + x\sin i
-  \end{Vector}.
+  \end{Vector} \ ,
   \label{eq:Trans}
 \end{equation}
+where the rotation matrix \(\mathbfss{A}_y(i)\) is given in
+Appendix~\ref{sec:plane-sky-projection}.  The inclination angle \(i\)
+is defined so that \(i = \ang{0}\) when the surface is viewed
+perpendicular to its axis (\textit{side on}) and \(i = \pm\ang{90}\)
+when it is viewed along its axis (\textit{end on}), with positive
+\(i\) when the apex points towards the observer.
+
 The relationship between the two frames is illustrated in
@@
 \end{equation}
-For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
-equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, and then
-converting to the observer frame by use of equation~(\ref{eq:Trans})
-to give
-\begin{gather}
-  \label{eq:nprime}
-  \begin{split}
-    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
-    & \times 
+For general \(\phi \ne 0\), we find \(\uvec{n}\) and \(\uvec{t}\) by
+rotating equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis with the
+matrix \(\mathbfss{A}_x(\phi)\) (eq.~[\ref{eq:Rotation-matrix-x}]):
+\begin{align}
+  \label{eq:uvec-n-phi}
+  \uvec{n} &= \mathbfss{A}_x(\phi) \, \uvec{n}_0 =
   \begin{Vector}
-        (\cos\theta+\omega\sin\theta)\cos i 
-        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
-        (\sin\theta-\omega\cos\theta)\cos\phi \\
-        (\cos\theta+\omega\sin\theta)\sin i 
-        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-      \end{Vector}\\
-  \end{split}\\
-  \label{eq:tprime}
-  \begin{split}
-    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
-    & \times 
+    \sin\alpha \\ \cos\alpha\cos\phi \\ \cos\alpha\sin\phi
+  \end{Vector}  \\
+  \label{eq:uvec-t-phi}
+  \uvec{t} &= \mathbfss{A}_x(\phi) \, \uvec{t}_0 =
   \begin{Vector}
-        -(\sin\theta-\omega\cos\theta)\cos i
-        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
-        (\cos\theta+\omega\sin\theta)\cos\phi \\
-        -(\cos\theta+\omega\sin\theta)\sin i 
-        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
-      \end{Vector}
-  \end{split}
-  \end{gather}
+    -\cos\alpha \\ \sin\alpha\cos\phi \\ \sin\alpha\sin\phi
+  \end{Vector} \ .
+\end{align}
+
 \subsection{Tangent line}
@@
   \label{eq:tangent-line-condition}
-  \uvec{n}'\cdot \uvec{z}' = 0.
-\end{equation}
-We denote by \(\phi\T\) that value of $\phi$ that satisfies this
-relation for a given inclination, \(i\), and polar angle, \(\theta\):
-\begin{equation}
-\sin\phi\T = -\tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
+  \uvec{n} \cdot \uvec{z}' = 0.
+\end{equation}
+We denote by \(\phi\T\) that value of $\phi$ that satisfies this relation
+for a given inclination, \(i\), and polar angle, \(\theta\).  From
+equations~(\ref{eq:uvec-n-phi}, \ref{eq:tangent-line-condition},
+\ref{eq:zunit-prime}, \ref{eq:alpha}) this is
+\begin{equation}
+\sin\phi\T = -\tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta} \ .
 \label{eq:tanphi}
@@
 \end{equation}
-Note that equation~(\ref{eq:tanphi}) will not have
-a solution for arbitrary values of $\theta$ and $i$, but only when
-$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent
-line only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of \(\theta\) on the tangent line's projected symmetry axis (\(\theta' = 0\)), 
-given implicitly by
+
+Note that equation~(\ref{eq:tanphi}) will not have a solution for
+arbitrary values of $\theta$ and $i$, but only when
+$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent line
+only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of
+\(\theta\) on the tangent line's projected symmetry axis
+(\(\theta' = 0\)).  From equations~(\ref{eq:tangential},
+\ref{eq:R-prime-theta-prime}) it follows that \(\sin^2\phi\T = 1\) at
+\(\theta = \theta_0\), which yields the implicit equation
 \begin{align}
@@
 \begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/M17-composite}
+  \caption[]{Procedure for tracing the contact discontinuity from the
+    \citet{Meyer:2017a} simulations.  The density maps from
+    \citeauthor{Meyer:2017a}'s Fig.~3 are converted to FITS format and
+    displayed using the software SAOImage~DS9 \citep{Joye:2003a}.  The
+    density contour at \SI{0.4}{cm^{-3}} is displayed (shown in green
+    in the figure) and this is traced by hand by placing ``point
+    regions'' on the image (shown by black ``x'' shapes in the
+    figure).  The zoom facility of the software allows the points to
+    be placed with any required accuracy.  The points are saved to a
+    file in the DS9 region file format, which is then read by Python
+    programs for further processing.  For example, the yellow boxes
+    show circle fits and determination of the parameters \(R_0\),
+    \(R_c\), and \(R_{90}\).  In this example, only the points shown
+    in orange (within \ang{60} of axis) are used in the fits.}
+  \label{fig:meyer-trace}
+\end{figure}
+
+\begin{figure}
   (a)\\
@@
 the radiative cooling in the shocked stellar wind is even less
-efficient.  This represents a gross violation of the assumptions
+efficient.  This represents a significant violation of the assumptions
 behind the thin-shell models, since the total shocked shell thickness
-is of the same order as \(R_0\).  The parabolic departure function
-(see \S~\ref{sec:parab-depart-funct}) for the shape of the contact
-discontinuity\footnote{%
+is of the same order as \(R_0\).  Nevertheless, the emissivity of
+several observationally important emission processes, such as
+mid-infrared thermal dust emission and the optical H\(\alpha\) emission
+line, is concentrated near the contact discontinuity,\footnote{%
   Note that, in the non-magnetic HD models, efficient thermal
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/new-two-arc-multi-fig}
+  \caption[]{Example empirical determination of planitude and alatude
+    for observed bow shocks associated with proplyds in the outer
+    Orion Nebula (M42).  Color scale and contours show an \textit{HST}
+    H\(\alpha\) image (ACS F658N filter, \citealp{Bally:2006a}) of
+    M42~000-400 (panels \textit{a--c}) and M42~069-601 (panels
+    \textit{d--f}).  The image scale and orientation are indicated on
+    panel~\textit{a} and are the same for all panels.  Three different
+    bows have been traced by eye on each object (red and white filled
+    symbols): (\textit{a, d})~inner edge, (\textit{b, e})~ridge of
+    maximum emission, and (\textit{c, f})~outer edge.  For each panel,
+    the dark-colored circle shows the initial fit to the full set of
+    points (white and red), using the algorithm described in
+    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
+    derived axis are shown by a small filled circle and dashed line in
+    the same color. Lighter colored circles show three subsequent
+    iterations where the fit is restricted to points within
+    \(\pm \Delta\theta = \ang{75}\) of the axis.  The subset of points used in
+    the final iteration is marked in red.  The perpendicular radii for
+    the final iteration are shown by dotted lines. In panels
+    \textit{a, b, d--f} the iterations converge immediately, but in
+    panel \textit{c} the iterations stably oscillate between two
+    slightly different solutions. }
+  \label{fig:000-400-fit}
+\end{figure*}
+
+\begin{figure*}
+  \begin{tabular}{p{0.47\linewidth} p{0.47\linewidth}}
+    (a) & (b) \\
+    \includegraphics[width=\linewidth]{figs/000-400-planitude-alatude}
+    & \includegraphics[width=\linewidth]{figs/069-601-planitude-alatude}
+  \end{tabular}
+  \caption[]{Location in the projected planitude--alatude plane of the
+    converged circle fits to the M42 bows: (\textit{a})~000-400,
+    (\textit{b})~069-601. For each solution, the two values of the
+    projected alatude, \(\Lambda_+'\) and \(\Lambda_-'\), corresponding to
+    \(R_{90+}\) and \(R_{90-}\), are joined by a vertical line. Large
+    symbols show the results from the fits shown in
+    Figure~\ref{fig:000-400-fit}, while small symbols show results for
+    fits using \(\Delta\theta = \ang{60}\) instead of \ang{75}. In panel
+    \textit{a}, two slightly different \(\Pi'\) values are shown for the
+    outer bow, since the fit does not converge to a single value (see
+    Fig.~\ref{fig:000-400-fit}\textit{c} and
+    App.~\ref{app:rcurv-empirical}).}
+  \label{fig:000-400-planitude-alatude}
+\end{figure*}
+
+\begin{figure*}
+  \begin{tabular}{p{0.47\linewidth} p{0.47\linewidth}}
+    (a) & (b) \\
+    \includegraphics[width=\linewidth]{figs/000-400-Pi-vs-Dtheta}
+    & \includegraphics[width=\linewidth]{figs/069-601-Pi-vs-Dtheta}
+  \end{tabular}
+  \caption[]{Variation of fitted planitude, \(\Pi'\), as a function of
+    the parameter \(\Delta\theta\), which controls how close a point must be to
+    the axis in order to be included in the circle
+    fit. (\textit{a})~M42 000-400, (\textit{b}) M42 069-601.  For the
+    three traced bows (inner, outer, and ridge) of each object, the
+    symbol key lists the mean and standard deviation of \(\Pi'\),
+    calculated over the ``stable'' range \(\Delta\theta = \ang{60}\) to
+    \ang{80}, which is indicated by light gray shading.}
+  \label{fig:000-400-Delta-theta}
+\end{figure*}
+
+\begin{table}
+  \caption[]{Fitted planitude and alatude for M42 bows}
+  \label{tab:m42-fit}
+  \centering
+  \begin{tabular}{ll rrr}
+    \toprule
+    Source & Bow & \(\Pi'\) & \(\langle \Lambda' \rangle\)& \(\Delta\Lambda'\) \\
+    \midrule
+    000-400 & Inner & \(2.87 \pm 0.19\) & \(2.40 \pm 0.04\) & \(0.35 \pm 0.08\) \\
+           &  Ridge & \(3.62 \pm 0.38\) & \(2.73 \pm 0.02\) & \(0.51 \pm 0.10\) \\
+           & Outer & \(2.51 \pm 0.24\) & \(2.46 \pm 0.02\) & \(-0.06 \pm 0.02\) \\[\smallskipamount]
+           & All & \(3.00 \pm 0.54\) & \(2.53 \pm 0.15\) & \(0.16 \pm 0.16\) \\[\bigskipamount]
+    069-601 & Inner & \(3.81 \pm 0.23\) & \(2.90 \pm 0.01\) & \(0.44 \pm 0.05\) \\
+           & Ridge & \(2.43 \pm 0.13\) & \(2.17 \pm 0.01\) & \(0.07 \pm 0.02\) \\
+           & Outer & \(2.22 \pm 0.15\) & \(2.11 \pm 0.01\) & \(0.01 \pm 0.01\) \\[\smallskipamount]
+           & All & \(2.82 \pm 0.75\) & \(2.39 \pm 0.37\) & \(0.17 \pm 0.20\)\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\section{Example application to observations}
+\label{sec:obs}
+
+As an example of measuring the projected planitude and alatude of real
+bow shocks, we present an analysis of M42~000-400 and M42~069-601,
+which are two H\(\alpha\) emission arcs \citep{Bally:2000a,
+  Gutierrez-Soto:2015a} associated with proplyds\footnote{%
+  The coordinate designation (see \citealp{ODell:1994a} for an
+  explanation of the nomenclature) of 000-400 is very imprecise in
+  right ascension, but we use it here for consistency with previous
+  papers. The associated proplyd is listed with the more correct
+  designation 4596-400 in catalogs such as \citet{Ricci:2008a}.  } %
+in the west of the Orion Nebula (M42) at a distance of roughly
+\SI{0.5}{pc} from the high-mass Trapezium stars that ionize the
+nebula.  An image of one of these arcs (M42~069-601) was used in the
+illustration of bow shock terminology in
+Figure~\ref{fig:bow-terminology}.
+
+\subsection{Empirical determination of bow shock shape}
+\label{sec:empir-determ-bow}
+
+We consider three different tracings of the bow shape (see
+Fig.~\ref{fig:000-400-fit}): the peak of the emission arc (``ridge''),
+and its inner and outer edges.  In all three cases, we placed by eye
+the points that define the bow, using SAOImage~DS9 \citep{Joye:2003a}
+in a similar fashion to in Figure~\ref{fig:meyer-trace}, and guided by
+the image contours.\footnote{%
+  In the case of the ``ridge'' method at least, it is possible to
+  automate this step, which we will discuss in detail in a following
+  paper. } %
+
+We determine the planitude and alatude by fitting a circle to the
+traced points within \(\pm \Delta\theta = \ang{75}\) of the bow axis, using the
+iterative algorithm described in Appendix~\ref{app:rcurv-empirical}.
+The fitted circle, when combined with the position of the central
+source, yields the orientation of the bow axis, together with the apex
+distance, \(R_0\), radius of curvature, \(R_\C\), and two
+perpendicular radii (one for each wing), \(R_{90+}\) and \(R_{90-}\).
+These are all indicated on the panels of Figure~\ref{fig:000-400-fit}
+by light-colored lines.\footnote{%
+  For conciseness, we drop the prime symbol from the radii, both in
+  this section and in Appendix~\ref{app:rcurv-empirical}, even though
+  they are all projected quantities.} %
+The projected planitude and alatude then follow as
+\(\Pi' = R_\C/R_0\), \(\Lambda_+' = R_{90+}/R_0\),
+\(\Lambda_-' = R_{90-}/R_0\), which are shown in
+Figure~\ref{fig:000-400-planitude-alatude}.
+
+\subsection{Analysis of sources of systematic uncertainty}
+\label{sec:analys-sourc-syst}
+
+The planitude is found to have a moderate dependence on the choice of
+\(\Delta\theta\), as shown in Figure~\ref{fig:000-400-Delta-theta}, where it can
+be seen that, although the values of \(\Pi'\) are relatively stable for
+\(\Delta\theta \ge \ang{60}\) (light gray shaded region), they can show much
+larger variations for \(\Delta\theta < \ang{60}\).  The fact that the radius of
+curvature is defined at a point (the projected apex) might seem to
+argue for making \(\Delta\theta\) as small as possible, but that would lead to
+circle fits that were extremely sensitive to the exact positions of
+the few points included in the fit.  A reliable fit requires 4 or more
+points, ideally spanning a total separation that is a substantial
+fraction of \(R_\C\), which would argue for \(\Delta\theta\) larger than about
+\(\Pi'/2\) radians, or \ang{60} to \ang{90}.  On the other hand, if
+\(\Delta\theta \ge \ang{90}\) then the planitude and alatude would no longer be
+independent since the bow would be forced to lie on the ``sphere''
+line, \(\Lambda' = (2 \Pi' - 1)^{1/2}\) (see \S~\ref{sec:conic}).  Balancing
+these two concerns suggests an optimal \(\Delta\theta = \ang{75}\), which is
+shown in Figure~\ref{fig:000-400-fit}, whereas in
+Figure~\ref{fig:000-400-planitude-alatude} we show results for both
+\ang{75} (thick lines) and \ang{60} (thin lines).
+
+Unlike all the models considered in \S~\ref{sec:crw-scenario} and
+\S~\ref{sec:more-realistic-bow}, the observed bows are not necessarily
+symmetrical and so the alatude for the two wings, \(\Lambda_-'\) and
+\(\Lambda_+'\), may be different.  We therefore calculate an average
+alatude, \(\langle\Lambda'\rangle\), and an alatude asymmetry, \(\Delta\Lambda'\):
+\begin{equation}
+  \label{eq:alatude-average-and-asym}
+  \langle\Lambda'\rangle = \tfrac12 \left( \Lambda_+' + \Lambda_-' \right)
+  \quad\quad \Delta\Lambda' = \tfrac12 \left( \Lambda_+' - \Lambda_-' \right)
+\end{equation}
+The results for these two quantities, together with the planitude, are
+shown in Table~\ref{tab:m42-fit}.  For each object and for each tracing
+(inner, ridge, outer, see Fig.~\ref{fig:000-400-fit}), the
+\(\text{mean} \pm \text{standard\ deviation}\) is listed for circle
+fits using \(\Delta\theta = \ang{60}\) to \ang{80} (see
+Fig.~\ref{fig:000-400-Delta-theta}).  Additionally, the row ``All''
+for each object gives the global mean and standard deviation over all
+three tracings.
+
+It can be seen from Table~\ref{tab:m42-fit} that the uncertainty in
+the fitted parameters is dominated by the variations between the
+different traced shapes.  For example, the one-sigma relative
+variation of planitude, \(\Pi'\), is \(< 10\%\) within the individual
+tracings, but \(\approx 20\%\) between tracings.  For the mean alatude,
+\(\langle\Lambda'\rangle\), the variation within individual tracings is extremely
+small\footnote{%
+  This is because the only way that variation in the circle fit
+  parameters affect the alatudes is through the axis orientation
+  vector, and changing the orientation induces roughly opposite
+  effects on \(\Lambda_+'\) and \(\Lambda_-'\), which approximately cancel out in
+  \(\langle\Lambda'\rangle\).  } %
+at \(\approx 1\%\), but is \(\approx 10\%\) between tracings.  The alatude
+asymmetry, \(\Delta\Lambda'\), is best interpreted as a difference between the
+symmetry axis of the apex region and the symmetry axis of the wings.
+In relative terms, this is \(0\)--\(20\%\), but with large systematic
+variations between tracings (for instance, in both objects it is very
+small for the outer arcs).
+
+It could be argued that much of the between-tracing variations in
+\(\Pi'\) and \(\langle\Lambda'\rangle\) are due to real differences between the shapes of
+the inner and outer boundaries of the emission arc.  Although this may
+be true, in the absence of a robust theory as to exactly what feature
+of the observed images constitutes \emph{the} bow shock, such
+variations nevertheless serve to limit the precision with which the
+bow shock shape can be measured.  We therefore conclude that
+conservative estimates of \(20\%\) precision for \(\Pi'\) and \(10\%\)
+precision for \(\Lambda'\) are appropriate when analyzing observations of a
+similar or better quality\footnote{%
+  Since the uncertainties are systematic and due to unavoidably
+  subjective decisions, it is unlikely that better quality
+  observations would improve the situation, although poorer quality
+  observations could make things worse.  } %
+to those presented in Figure~\ref{fig:000-400-fit}.  This will be an
+important limitation when comparing the statistics of the shapes of
+different bow shock populations, as we will present in a following
+paper.
+
+\subsection{Derived shape of the M42 arcs}
+\label{sec:derived-shape-m42}
+
+From a casual inspection of Figure~\ref{fig:000-400-fit}, it is
+apparent that the shapes of the two M42 arcs are closely similar, and
+this is confirmed by the numbers in Table~\ref{tab:m42-fit}. Both
+000-400 and 069-601 are consistent with
+\((\Pi', \Lambda') \approx (3.0, 2.5)\), and if we take the absolute minimum over
+all the different tracings and reasonable variations in the
+\(\Delta\theta\) fit parameter, we find unassailable lower limits of
+\((\Pi', \Lambda') > (2.1, 2.1)\).  In the rest of this section, we consider
+only these lower limits, since they are already sufficient for drawing
+interesting conclusions.
+
+Comparison with Figure~\ref{fig:sim-Pi-Lambda} shows that both the MHD
+and HD simulations of \citet{Meyer:2016a} are inconsistent with the
+observations.  Although \(\Pi' > 2.1\) can be satisfied,\footnote{%
+  Either by the MHD simulations at low inclinations
+  (\(\abs{i} = \ang{0}\)--\ang{20}) or by the HD simulation at
+  intermediate inclinations (\(\abs{i} = \ang{30}\)--\ang{40}).} %
+the simulations' projected alatude is \(\Lambda' < 1.9\) for all
+inclinations, which is significantly less than the observed lower
+limit of \(2.1\).  This is not particularly surprising since the
+simulations were not tailored to the situation of these proplyd bow
+shocks in M42, in which the mildly supersonic photoevaporation flow
+from an externally irradiated protoplanetary disk interacts with the
+mildly supersonic champagne flow from the core of the Orion Nebula.
+The proplyd case has at least four important differences from the
+runaway O-star case modeled by \citet{Meyer:2016a}: (1)~The velocity
+of the outer wind is \(\le \SI{20}{km.s^{-1}}\) instead of
+\SI{40}{km.s^{-1}}; (2)~The outer wind is slightly divergent, rather
+than plane-parallel; (3)~Both inner and outer shocks are strongly
+radiative, so both shells (see Fig.~\ref{fig:2-winds}) contribute to
+the observed emission; (4)~The inner wind is not isotropic, but
+instead corresponds to the \(k = 0.5\) case of
+equation~\eqref{eq:ancantoid-density}.  The ways in which these
+differences may account for the discrepancy with the observations will
+be explored in detail in a subsequent paper.
+
 \section{Summary and discussion}
@@
 research studentship from Consejo Nacional de Ciencias y Tecnología,
-Mexico.
+Mexico.  This work has made extensive use of Python language libraries
+from the SciPy \citep{Jones:2001a} and AstroPy
+\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a}
+projects.  We appreciate the thoughtful comments of the anonymous
+referee, which were led us to clarify the presentation of our results
+and prompted the addition of \S~\ref{sec:obs}.
 
@@
 
+\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
+  Collaboration} et~al.}{2018}]{Astropy-Collaboration:2018a}
+{Astropy Collaboration} et~al., 2018, preprint, \href
+  {http://adsabs.harvard.edu/abs/2018arXiv180102634T} {} (\mn@eprint {arXiv}
+  {1801.02634})
+
+\bibitem[\protect\citeauthoryear{{Bally}, {O'Dell}  \& {McCaughrean}}{{Bally}
+  et~al.}{2000}]{Bally:2000a}
+{Bally} J.,  {O'Dell} C.~R.,   {McCaughrean} M.~J.,  2000, \aj, 119, 2919
+
+\bibitem[\protect\citeauthoryear{{Bally}, {Licht}, {Smith}  \&
+  {Walawender}}{{Bally} et~al.}{2006}]{Bally:2006a}
+{Bally} J.,  {Licht} D.,  {Smith} N.,   {Walawender} J.,  2006, \aj, 131, 473
+
 \bibitem[\protect\citeauthoryear{{Canto}, {Raga}  \& {Wilkin}}{{Canto}
@@
 
+\bibitem[\protect\citeauthoryear{Guggenheimer}{Guggenheimer}{2012}]{Guggenheimer:2012a}
+Guggenheimer H.,  2012, Differential Geometry.
+Dover Books on Mathematics, Dover Publications
+
+\bibitem[\protect\citeauthoryear{Guti{\'e}rrez-Soto}{Guti{\'e}rrez-Soto}{2015}]{Gutierrez-Soto:2015a}
+Guti{\'e}rrez-Soto L.~{\'A}.,  2015, Master's thesis, Universidad Nacional
+  Aut{\'o}noma de M{\'e}xico
+
 \bibitem[\protect\citeauthoryear{{Hartigan}, {Raymond}  \&
@@
   R.~H.,  2013, \mnras, 428, 691
+
+\bibitem[\protect\citeauthoryear{Jones, Oliphant, Peterson  et~al.}{Jones
+  et~al.}{2018}]{Jones:2001a}
+Jones E.,  Oliphant T.,  Peterson P.,   et~al., 2001--2018, {SciPy}: Open
+  source scientific tools for {Python}, \url {http://www.scipy.org/}
+
+\bibitem[\protect\citeauthoryear{{Joye} \& {Mandel}}{{Joye} \&
+  {Mandel}}{2003}]{Joye:2003a}
+{Joye} W.~A.,  {Mandel} E.,  2003, in {Payne} H.~E.,  {Jedrzejewski} R.~I.,
+  {Hook} R.~N.,  eds,  Astronomical Society of the Pacific Conference Series
+  Vol. 295, Astronomical Data Analysis Software and Systems XII. p.~489
 
@@
 
+\bibitem[\protect\citeauthoryear{Mohr \& Phillips}{Mohr \&
+  Phillips}{2015}]{Mohr:2015a}
+Mohr P.~J.,  Phillips W.~D.,  2015, Metrologia, 52, 40
+
+\bibitem[\protect\citeauthoryear{{O'Dell} \& {Wen}}{{O'Dell} \&
+  {Wen}}{1994}]{ODell:1994a}
+{O'Dell} C.~R.,  {Wen} Z.,  1994, \apj, 436, 194
+
 \bibitem[\protect\citeauthoryear{{Ochsendorf}, {Verdolini}, {Cox}, {Bern{\'e}},
@@
 
+\bibitem[\protect\citeauthoryear{{Penrose}}{{Penrose}}{2004}]{Penrose:2004a}
+{Penrose} R.,  2004, {The road to reality : a complete guide to the laws of the
+  universe}.
+Jonathan Cape, London
+
 \bibitem[\protect\citeauthoryear{{Phillips}, {Cuesta}  \&
@@
 
+\bibitem[\protect\citeauthoryear{Quincey \& Brown}{Quincey \&
+  Brown}{2017}]{Quincey:2017a}
+Quincey P.,  Brown R. J.~C.,  2017, Metrologia, 54, 454
+
 \bibitem[\protect\citeauthoryear{{Raga}, {Binette}, {Canto}  \&
@@
 {Raga} A.~C.,  {Binette} L.,  {Canto} J.,   {Calvet} N.,  1990, \apj, 364, 601
+
+\bibitem[\protect\citeauthoryear{{Ricci}, {Robberto}  \& {Soderblom}}{{Ricci}
+  et~al.}{2008}]{Ricci:2008a}
+{Ricci} L.,  {Robberto} M.,   {Soderblom} D.~R.,  2008, \aj, 136, 2136
 
@@
 
+\bibitem[\protect\citeauthoryear{Weisstein}{Weisstein}{2018}]{Weisstein:2018a}
+Weisstein E.~W.,  1999--2018, Radius of Curvature, From MathWorld -- A Wolfram
+  Web Resource., \url {http://mathworld.wolfram.com/RadiusofCurvature.html}
+
 \bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{1996}]{Wilkin:1996a}
@@
 \appendix
+% start input ./app-intermediate.tex
+%% \section{Derivation of selected results from \S\S~2 and 3}
+
+\section{Radius of curvature}
+\label{sec:radius-curvature}
+
+The radius of curvature of a general curve can be written (e.g.,
+eq.~[2-5] of \citealp{Guggenheimer:2012a}):
+\begin{equation}
+  \label{eq:Rcurv-general}
+  R_{\C} \equiv \frac{1}{\abs{\kappa}} = \Abs{\frac{d s}{d \alpha}} \ ,  
+\end{equation}
+where \(\kappa\) is the \textit{curvature}, \(s\) is the path length along
+the curve and \(\alpha\) is the tangent angle (see Fig.~\ref{fig:unitvec}).
+In spherical polar coordinates, this becomes \citep{Weisstein:2018a}:
+\begin{equation}
+  \label{eq:Rcurv-polar}
+  R_{\C} = \frac{\left( R^2 + R_\theta^2 \right)^{3/2}}
+  {\Abs{R^2 + 2 R_\theta^2 - R R_{\theta\theta}}} \ , 
+\end{equation}
+where \(R_\theta = d R / d \theta\) and
+\(R_{\theta\theta} = d^2 R / d \theta^2\).  At the apex,
+\(R_\theta = 0\) by symmetry, which yields
+equation~\eqref{eq:radius-curvature} of
+\S~\ref{sec:plan-alat-bow}. Note that \(\theta\) is dimensionless and
+should be measured in radians \citep{Mohr:2015a, Quincey:2017a}.
+
+\section{Rotation matrices and plane of sky projection}
+\label{sec:plane-sky-projection}
+
+The transformation from the body frame (unprimed) to observer-frame
+(primed) coordinates is a rotation about the \(y\) axis by an angle
+\(i\), which is described by the rotation matrix:
+\begin{equation}
+  \label{eq:Rotation-matrix-y}
+  \mathbfss{A}_y(i) = 
+   \begin{pmatrix}
+    \cos i & 0 & -\sin i \\
+    0 & 1 & 0 \\
+    \sin i & 0 &\cos i 
+  \end{pmatrix} \ .
+\end{equation}
+This is used in equation~\eqref{eq:Trans}.  A further application is
+to express the observer-frame Cartesian basis vectors in terms of the
+body-frame basis:
+\begin{align}
+  \label{eq:xunit-prime}
+  \uvec{x}' &= \mathbfss{A}_y(-i)\, %\uvec{x}
+              \begin{Vector}
+              1 \\ 0 \\ 0  
+              \end{Vector}
+              =
+              \begin{Vector}
+              \cos i \\ 0 \\ -\sin i  
+              \end{Vector} \ ,
+  \\
+  \label{eq:yunit-prime}
+  \uvec{y}' &= \mathbfss{A}_y(-i)\, %\uvec{y}
+              \begin{Vector}
+              0 \\ 1 \\ 0  
+              \end{Vector}
+              =
+              \begin{Vector}
+              0 \\ 1 \\ 0
+              \end{Vector} \ , 
+  \\
+  \label{eq:zunit-prime}
+  \uvec{z}' &= \mathbfss{A}_y(-i)\, %\uvec{z}
+              \begin{Vector}
+              0 \\ 0 \\ 1  
+              \end{Vector}
+              =
+              \begin{Vector}
+              \sin i \\ 0 \\ \cos i  
+              \end{Vector} \ .
+\end{align}
+Note that in this case the sign of \(i\) is reversed because it is the
+inverse operation to that in equation~\eqref{eq:Trans}
+
+Since we are considering cylindrically symmetric bows, all azimuths
+\(\phi\) are equivalent, so it is sufficient to work with two-dimensional
+curves in the plane \(z = 0\) (which is also \(\phi = 0\)) and then find
+the three-dimensional surface by rotating about the \(x\)-axis via the
+rotation matrix:
+\begin{equation}
+  \label{eq:Rotation-matrix-x}
+  \mathbfss{A}_x(\phi) = 
+   \begin{pmatrix}
+    1 & 0 & 0 \\
+    0 &\cos\phi & -\sin\phi \\
+    0 &\sin\phi & \cos\phi 
+  \end{pmatrix} \ ,
+\end{equation}
+where \(\phi\) takes all values in the interval \([0, 2\pi]\).
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "quadrics-bowshock"
+%%% End:
+ % end input ./app-intermediate.tex
  % start input ./app-parabola.tex
@@
   \label{eq:theta-1-90-approx}
-  \theta_{1,90} \approx \left( \frac{3 \xi_k \beta} {1 + \tfrac15 \xi_k \beta} \right) \ .
+  \theta_{1,90} \approx \left( \frac{3 \xi_k \beta} {1 + \tfrac15 \xi_k \beta} \right)^{1/2} \ .
 \end{equation}
@@
 
-Consider a set of \(N\) points on the plane of the sky, with Cartesian
-coordinates \(\bm{r}_k = (x_k, y_k)\) for \(k = 1 \dots N\).  We wish
-to estimate the radius of curvature of the smooth curve that the set
-of points is presumed to be sampled from.  To do this, we fit a circle
-to the points as follows.  The circle is defined by its center,
-\(\bm{r}_{\C} = (x_{\C}, y_{\C})\), and radius, \(R_{\C}\).  For a
-given circle, we define a mean radius of the set of points from the
-circle center:
+Consider a set of \(N\) points on the plane of the sky,\footnote{%
+  In the main body of the paper, the prime symbol (\('\)) is used to
+  distinguish projected from ``true'' quantities.  In this Appendix,
+  for simplicity, we omit the primes since \emph{all} quantities are
+  projected.} %
+with Cartesian coordinates \(\bm{r}_k = (x_k, y_k)\) for
+\(k = 1 \dots N\).  We wish to estimate the radius of curvature of the
+smooth curve that the set of points is presumed to be sampled from.
+To do this, we fit a circle to the points as follows.  The circle is
+defined by its center, \(\bm{r}_{\C} = (x_{\C}, y_{\C})\), and radius,
+\(R_{\C}\).  For a given circle, we define a mean radius of the set of
+points from the circle center:
 \begin{equation}
   \label{eq:rcurv-mean-radius}
-  \bar{R}(x_{\C}, y_{\C}) = \frac{1}{N}  \sum_{k = 1}^{N} \Abs{\bm{r}_k - \bm{r}_{\C}}  \ .
-\end{equation}
-We then optimize\footnote{%
-  For example, using a Levenberg-Marquardt algorithm, such as
-  \texttt{astropy.modeling.fitting.LevMarLSQFitter} from the AstroPy
-  library \citep{Astropy-Collaboration:2013a}.} %
+  \bar{R}_\C(x_{\C}, y_{\C}) = \frac{1}{N}  \sum_{k = 1}^{N} \Abs{\bm{r}_k - \bm{r}_{\C}}  \ .
+\end{equation}
+We then optimize
+% \footnote{%
+%   For example, using a Levenberg-Marquardt algorithm, such as
+%   \texttt{astropy.modeling.fitting.LevMarLSQFitter} from the AstroPy
+%   library \citep{Astropy-Collaboration:2013a}.} %
 to find best-fit values \((x_{\C}^*, y_{\C}^*)\), which minimize the
@@
 \end{equation}
-A refinement of the method is then to repeat the circle fit after
-restricting the set of points to those lying within a certain angle
-\(\Delta\theta\) of the bow axis by requiring
+A refinement of the method is then to iteratively repeat the circle
+fit after restricting the set of points to those lying within a
+certain angle \(\Delta\theta\) of the bow axis, where we find that best results
+are obtained with \(\Delta\theta \approx \ang{60}\) to \ang{75}.  That is, 
 \begin{equation}
   \label{eq:rcurv-delta-theta}
-  \uvec{\xi} \cdot 
-  {\left( \bm{r}_k - \bm{r}_{\C}^* \right) }
-  \ge   {\Abs{\bm{r}_k - \bm{r}_{\C}^*}}
-  \cos \Delta\theta \ ,
-\end{equation}
-where we find that best results are obtained with \(\Delta\theta \le \ang{30}\).
+  \Abs{\theta_k} < \Delta\theta \ , 
+\end{equation}
+where the signed angle \(\theta_k\) of each point from the
+axis,\footnote{%
+  Although the sign of \(\theta_k\) is not relevant to
+  equation~\eqref{eq:rcurv-delta-theta}, it is used below in
+  calculating the perpendicular radii.  } %
+measured at the source position \(r_0\), can be calculated as
+\begin{equation}
+  \label{eq:rcurv-theta-k}
+  \theta_k = \arctan \left[  
+    \frac{\left( \bm{r}_k - \bm{r}_0 \right) \cdot \uvec{\xi}^\perp}
+    {\left( \bm{r}_k - \bm{r}_0 \right) \cdot \uvec{\xi}}
+  \right] \ .
+\end{equation}
+In the preceding equation, the ``perpendicular'' operator (\(\perp\))
+rotates its vector argument counter-clockwise by \ang{90}, so that
+\((x, y)^\perp = (-y, x)\).
+
+Two or three iterations are sufficient for convergence in most cases,
+although in some cases it is possible that the process will converge
+to a stable flip-flop oscillation between two different solutions.
+This is due to the dependence of the \(\theta_k\), via \(\uvec{\xi}\), on
+the \(\bm{r}_{\C}^*\) of the previous iteration, which can lead to
+points entering and leaving the fitted set.  We have not found this to
+be a serious problem in practice, since the two solutions tend to be
+very close to one another.  It could be mitigated by averaging
+\(\bm{r}_{\C}^*\) over two previous iterations.  The alternative of
+measuring the angle with respect to the center of curvature,
+\(\bm{r}_{\C}^*\), instead of the source, \(\bm{r}_0\), is found to be
+much less stable.
 
@@
 measurements of \(\bm{r}_k\), then it is appropriate to incorporate
-weights of \(\epsilon_k^{-2}\) in the objective function.  In cases where the
-bow shape is traced by eye, based on real or synthetic observations, a
-more practical approach is to maintain uniform weighting but to place
-a greater density of points \(\bm{r}_k\) in regions where the shape is
-well-determined and to place them more sparsely in regions where the
-shape is less certain.
-
-Note that this method is not necessary if the orientation of the bow
-axis is known a~priori, in which case the Taylor series method
-described in \S~\ref{sec:plan-alat-bow} is more efficient and
-accurate.
+weights of \(\epsilon_k^{-2}\) in the objective function.  However, it is
+rare for the \(\epsilon_k\) to be objectively quantifiable, since the
+uncertainties are often systematic and/or subjective.  In cases
+where the bow shape is traced by eye, based on real or synthetic
+observations, a more practical approach is to maintain uniform
+weighting but to place a greater density of points \(\bm{r}_k\) in
+regions where the shape is well-determined and to place them more
+sparsely in regions where the shape is less certain.
+
+Since there is no guarantee of symmetry about the axis \(\uvec{\xi}\),
+the perpendicular radius will in general be different in the two wings
+of the bow, with values \(R_{90+}\) and \(R_{90-}\).  These can be
+estimated by defining
+\begin{equation}
+  \label{eq:rcurv-R-k}
+  R_k = \Abs{\bm{r}_k - \bm{r}_0}
+\end{equation}
+and linearly interpolating between the points \((\theta_k, R_k)\) at
+\(\theta = \pm \ang{90}\).
+
+Our Python language implementation of this algorithm is freely
+available at \url{https://github.com/div-B-equals-0/circle-fit}.  An
+example application to real data is given in \S~\ref{sec:obs} and
+Figure~\ref{fig:000-400-fit}.  Note that this method is not necessary
+if the orientation of the bow axis is known a~priori, in which case
+the Taylor series method described in \S~\ref{sec:plan-alat-bow} is
+more efficient and accurate.
 

### 2018-03-07 papers/Papers1234/sec-intro.tex
Add mention of new section to end of introduction

@@
 %
+In \S~\ref{sec:obs} we apply our methods to example observations of
+proplyd bow shocks in the Orion Nebula, paying close attention to the
+systematic uncertainties that arise when our algorithms are applied to
+real data.
+%
 In \S~\ref{sec:conc} we summarise our results and outline how
-following papers will apply these ideas to observations and to a more
-extensive set of models and numerical simulations.
+following papers will apply these ideas to a more extensive set of
+observations, models and numerical simulations.
 

### 2018-03-07 papers/paper1-submit/latexdiff/ms-bows02-expand.tex
Final version with latexdiff to show changes

@@
 
-\makeatletter
 %% Bundled custom packages
-\newlength{\table@note@skip}
-\setlength{\table@note@skip}{0.5ex}
-\def\@eapj@cap@font{\bfseries}
-\gdef\tblnote@list{}
-\gdef\tblref@list{}
-\newcommand\tablecomments[1]{\@tablecom{#1}}% 
-\newcommand\tablerefs[1]{\@tableref{#1}}% 
-\def\@tablecom#1{% 
- \vspace*{\table@note@skip}
-\par 
-{\parbox{\linewidth}{\hskip1em\rmfamily {\@eapj@cap@font Note}. --- #1}\par}% 
-}% 
-\def\@tableref#1{% 
- \vspace*{\table@note@skip}
-\par 
-{\parbox{\linewidth}{\hskip1em\rmfamily {\@eapj@cap@font References}. --- #1}\par}% 
-}% 
-\def\spew@tblnotes{% 
- \@ifx@empty\tblref@list{}{% 
-  \@tablenotes{\tblref@list}%
-  \vspace*{\table@note@skip}%
-  \global\let\tblref@list\@empty 
- }% 
- \@ifx@empty\tblnote@list{}{% 
-  \@tablenotes{\tblnote@list}% 
-  \vspace*{\table@note@skip}%
-  \global\let\tblnote@list\@empty
- }
- \the\DT@p@ftn%
-}% 
-\def\@tablenotes#1{% 
- \par 
-% \footnoterule% 
- {\@table@type@size#1}% 
-}%
-
-\def\tabletypesize#1{\def\table@hook{#1}\gdef\@table@type@size{#1}}
-\tabletypesize{\footnotesize}
-
-\global\let\tablenotemark\relax
-\global\def\tablenotemark#1{{\normalfont\textsuperscript{#1}}}
-\global\let\tablenotetext\relax
-% \global\def\tablenotetext#1#2{\footnotetext[#1]{\@table@type@size#2}} 
-\global\def\tablenotetext#1#2{\noindent\textsuperscript{#1}{\@table@type@size#2}}
-
-\newcommand\nodata{ ~$\cdots$~ }%
-
-\newcommand\phn{\phantom{0}}% 
-\newcommand\phd{\phantom{.}}% 
-\newcommand\phs{\phantom{$-$}}% 
-\newcommand\phm[1]{\phantom{#1}}% 
-\makeatother
+\usepackage{aastex-compat}
 
@@
 projects.  We appreciate the thoughtful comments of the anonymous
-referee, which were led us to clarify the presentation of our results
-and prompted the addition of \S~\ref{sec:obs}.
+referee, which led us to clarify the presentation of our results and
+prompted the addition of \S~\ref{sec:obs} and
+Appendices~\ref{sec:radius-curvature}
+and~\ref{sec:plane-sky-projection}.
 

### 2018-03-07 papers/Papers1234/sec-projection.tex
Add references to Wilkin thesis and to Ng

@@
 
-Note that equation~(\ref{eq:tanphi}) will not have a solution for
+Equation~(\ref{eq:tanphi}) will not have a solution for
 arbitrary values of $\theta$ and $i$, but only when
@@
 and will no longer look like a bow shock to the observer.
+
+After completing this work, it was brought to our attention that the
+principal results of this section had already been derived in
+Appendix~B of the PhD thesis \citet{Wilkin:1997a}.  For instance,
+Wilkin's equation~(8) is equivalent (apart from differences in
+notation) to our equation~\eqref{eq:tanphi}.
 

### 2018-03-07 papers/Papers1234/sec-thin-shell.tex
Add references to Wilkin thesis and to Ng

@@
 apparent bow shapes of various thin shell models (wilkinoid, cantoids,
-ancantoids) for different inclination angles \(\abs{i}\).  For
-comparison, Figure~\ref{fig:xyprime}a shows the confocal paraboloid,
-whose apparent shape is independent of inclination (see
+ancantoids)\footnote{%
+  See also previous studies of the projected shape of the wilkinoid
+  \citep{Wilkin:1997a, Cox:2012a, Ng:2017a} and the cantoids
+  \citep{Robberto:2005a}.} %
+for different inclination angles \(\abs{i}\).  For comparison,
+Figure~\ref{fig:xyprime}a shows the confocal paraboloid, whose
+apparent shape is independent of inclination (see
 Appendix~\ref{app:parabola}).  The wilkinoid (Fig.~\ref{fig:xyprime}b)

### 2018-03-07 papers/paper1-submit/latexdiff/ms-bows02-expand.tex
Add references to Wilkin thesis and to Ng

@@
 \(R_{90}\) and \(R_0\) as a diagnostic of bow shape (for example
-\citealp{Robberto:2005, Cox:2012a, Meyer:2016a}), but as far as we
-know, we are the first to include \(R_{\C}\).  \citet{Robberto:2005}
+\citealp{Robberto:2005a, Cox:2012a, Meyer:2016a}), but as far as we
+know, we are the first to include \(R_{\C}\).  \citet{Robberto:2005a}
 \S~4.2 use the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd
@@
 
+\bibitem[\protect\citeauthoryear{{Ng}, {Bandiera}, {Hunstead}  \&
+  {Johnston}}{{Ng} et~al.}{2017}]{Ng:2017a}
+{Ng} C.-Y.,  {Bandiera} R.,  {Hunstead} R.~W.,   {Johnston} S.,  2017, \apj,
+  842, 100
+
 \bibitem[\protect\citeauthoryear{{O'Dell} \& {Wen}}{{O'Dell} \&
@@
 \bibitem[\protect\citeauthoryear{{Robberto} et~al.,}{{Robberto}
-  et~al.}{2005}]{Robberto:2005}
-{Robberto} M.,  et~al., 2005, \mn@doi [\aj] {10.1086/428000}, \href
-  {http://adsabs.harvard.edu/abs/2005AJ....129.1534R} {129, 1534}
+  et~al.}{2005}]{Robberto:2005a}
+{Robberto} M.,  et~al., 2005, \aj, 129, 1534
 
@@
 {Wilkin} F.~P.,  1996, \apjl, 459, L31
+
+\bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{1997}]{Wilkin:1997a}
+{Wilkin} F.~P.,  1997, PhD thesis, University of California, Berkeley
 

### 2018-03-09 papers/Papers1234/sec-dust-bow-intro.tex
New figure showing bow shocks, bow waves, dust waves

@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \framebox{
-    \parbox[m][4cm]{0.8\linewidth}
-    {\centerline{\textbf{\dotfill TODO\dotfill}}}}
+  \includegraphics[width=\linewidth]{figs/bows-and-waves}
   \caption{Bow shocks, bow waves, and dust waves}
   \label{fig:3-types-bow}
-\end{figure}
+\end{figure*}
 
@@
   \label{eq:rad-poten}
-  \int_{R_0}^\infty a_{\text{rad}} \, dr = \tfrac12 v^2 \ , 
+  \int_{R_0}^\infty a_{\text{rad}} \, dr = \tfrac12 v_\infty^2 \ , 
 \end{equation}
@@
   \label{eq:effective-luminosity}
-  L_{\text{eff}} = L \bigl(1 - \Gamma\Edd^{-1}\bigr) \ ,
+  L_{\text{eff}} = L \bigl(1 - \Gamma\Edd^{\,-1}\bigr) \ ,
 \end{equation}
@@
     B-type supergiant instead of main sequence stars.  This is similar
-    to Fig.~\ref{fig:zones-v-n-plane} in all respects, except the
-    trapping of the ionization front, which occurs for much lower
-    outer stream densities.}
+    to the early O MS star of Fig.~\ref{fig:zones-v-n-plane}\textit{c}
+    in many respects, except for the trapping of the ionization front,
+    which occurs for much lower outer stream densities.}
   \label{fig:B-supergiant}
@@
 front of \(n > 40 v_{10}^2\).  The advective flux, \(\mathcal{A}\), is
-relatively stronger for this star tan for the main-sequence stars, but
+relatively stronger for this star than for the main-sequence stars, but
 even for \(v_{10} < 2\), where the effect is strongest, the change is
-only of order the width of the red line in
+only of order the width of the dark red line in
 Figure~\ref{fig:B-supergiant}.

### 2018-04-25 papers/Papers1234/sec-dust-bow-intro.tex
Add two new graphs of Cloudy dust models

@@
 
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-dustprops}
+  \caption{Dust properties as a function of radius from star for three
+    selected Cloudy models. (a)~\SI{40}{M_\odot} main-sequence star in
+    medium of density \SI{e4}{cm^{-2}}. (b)~\SI{10}{M_\odot} main-sequence
+    star in medium of density \SI{1}{cm^{-2}}. (c)~Blue supergiant
+    star in medium of density \SI{1}{cm^{-2}}}.
+  \label{fig:multi-dustprops}
+\end{figure*}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/drift-gn}
+  \caption{Drift velocity versus FUV radiation parameter. Each line
+    represents a model with ambient density and stellar type as
+    indicated in the key.}
+  \label{fig:drift-gn}
+\end{figure*}
+
 \begin{figure}

### 2018-05-23 papers/Papers1234/sec-dust-bow-intro.tex
Add new figure on drag force

@@
 \begin{figure*}
+  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
+  \caption{Drag force as a function of gas--grain slip velocity,
+    \(w\), for different values of the grain potential,
+    \(\phi = U / k T\).  Contributions from proton and electron Coulomb
+    (electrostatic) drag, as well as Epstein (solid-body) drag are
+    indicated.  Inset shows \(\phi\) as a function of the radiation
+    parameter, \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a
+    log--linear scale.}
+  \label{fig:gas-grain-drag-photoionized}
+\end{figure*}
+
+\begin{figure*}
   \includegraphics[width=\linewidth]{figs/multi-dustprops}
@@
 \begin{figure*}
-  \includegraphics[width=\linewidth]{figs/drift-gn}
-  \caption{Drift velocity versus FUV radiation parameter. Each line
+  \includegraphics[width=\linewidth]{figs/drift-pratio-4panel}
+  \caption{Drift velocity versus radiation parameter \(\Xi_P\). Each line
     represents a model with ambient density and stellar type as
@@
 \end{figure}
+
+If the radiation field is sufficiently strong, then the collisional coupling between grains and gas will break down.
 

### 2018-05-23 papers/Papers1234/sec-dust-bow-intro.tex
Start writing up gas-grain decoupling

@@
 
-If the radiation field is sufficiently strong, then the collisional coupling between grains and gas will break down.
+If the radiation field is sufficiently strong, then the collisional
+coupling between grains and gas will break down.  In this section, we
+calculate the regions of star+stream parameter space where this might
+occur, leading to a separation of the bow into an outer dust wave and
+an inner, dust-free bow shock.
+
+The drag force on a charged dust grain moving at a relative speed
+\(w\) through a plasma has contributions from both direct collisions
+and from electrostatic Coulomb interactions with ions and electrons.
+We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
+summing over protons, electrons, and helium ions.\footnote{Helium is
+  assumed to be 50\% neutral and 50\% singly ionized, leading to only
+  a small contribution to the drag force.  For much hotter stars, such
+  as the central stars of planetary nebulae, helium may be doubly
+  ionized, which leads to a more significant drag contribution,
+  especially around \(w \approx \SI{5}{km.s^{-1}}\).} %
+Results are shown in Figure~\ref{fig:gas-grain-drag-photoionized} for
+different values of \(\phi = e U / kT\), where \(U = e Z\grain / a \) is
+the electrostatic potential of a grain of charge \(Z\grain\) and
+radius \(a\).
 

### 2018-05-24 papers/Papers1234/app-cloudy-dust-charging.tex
Move the Cloudy dust models to an appendix

--- 2018-04-25 papers/Papers1234/sec-dust-bow-intro.tex
@@
-\defcitealias{Tarango-Yong:2018a}{Paper~I}
-\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
-
-\section{Introduction}
-\label{sec:introduction}
-\newcommand\hii{\ion{H}{ii}}
-
-Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
-often interpreted as \textit{bow shocks}, due to a supersonic
-hydrodynamic interaction between the star's wind and an external
-stream. This stream may be due to the star's own motion or to an
-independent flow, such as an \hii{} region in the champagne phase
-\citep{Tenorio-Tagle:1979a}, or another star's wind
-\citep{Canto:1996}. However, an alternative interpretation in some
-cases may be a radiation-pressure driven bow wave, as first proposed
-by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
-emitted by the star are absorbed by dust grains in the incoming
-stream, with the resultant momentum transfer being sufficient to
-decelerate and deflect the grains within a certain distance from the
-star, forming a dust-free, bow-shaped cavity with an enhanced dust
-density at its edge.  Two regimes are possible, depending on the
-strength of coupling between the gas (or plasma) and the dust.  In the
-strong-coupling regime, gas--grain drag decelerates the gas along with
-the dust, forming a shocked gas shell in a similar fashion to the
-wind-driven bow shock case.  In the weak-coupling regime, the gas
-stream is relatively unaffected and the dust temporarily decouples to
-form a dust-only shell.  This second case has recently been studied in
-detail in the context of the interaction of late O-type stars (which
-have only weak stellar winds) with dusty photoevaporation flows inside
-\hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
-  Ochsendorf:2015a}.  We follow the nomenclature proposed by
-\citet{Ochsendorf:2014b}, in which \textit{dust wave} refers to the
-weak coupling case and \textit{bow wave} to the strong coupling case.
-More complex, hybrid scenarios are also possible, such as that studied
-by \citet{van-Marle:2011a}, where a hydrodynamic bow shock forms, but
-the larger dust grains that accompany the stellar wind pass right
-through the shocked gas shell, and form their own dust wave at a
-larger radius.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/bows-and-waves}
-  \caption{Bow shocks, bow waves, and dust waves}
-  \label{fig:3-types-bow}
-\end{figure*}
-
-In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
-new two-dimensional classification scheme for bow shapes: the
-projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
-measures the flatness of the bow's apex, while alatude measures the
-openness of the bow's wings.  Both are dimensionless ratios of lengths
-that can be estimated from observational images.  We have analyzed the
-inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
-geometric shapes (spheroids, paraboloids, hyperboloids) and for
-thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
-ancantoids).  In this paper, we will do the same for simple models of
-radiation-driven dust waves (dragoids) and bow waves (trapoids).
-
-The paper is organized as follows.
-%
-In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
-dusty radiation bow wave (dragoids), including the effects of
-gas-grain drag.
-%
-In \S~\ref{sec:perturbed-bows} we investigate the effects on the
-planitude--alatude plane of small-amplitude perturbations to the bow
-shape.
-%
-
-\section{Different types of bow}
-\label{sec:different-types-bow}
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
-  \caption{Bow regimes in parameter space (\(v, n\)) of the external
-    stream for main-sequence OB stars of different masses:
-    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}.  In all
-    cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
-    coupling is assumed. Solid black lines of varying width show the
-    bow size (star-apex separation, \(R_0\)), while gray shading shows
-    the radiation bow wave regime, with lower border \(\tau = \eta\) and
-    upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
-    depth through the bow.  For bows above the red solid line, the
-    ionization front is trapped inside the bow.  Blue lines delineate
-    different cooling regimes.  Above the thin blue line
-    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
-    forming a thin shocked shell.  Below the thick blue line
-    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
-    non-radiative.}
-  \label{fig:zones-v-n-plane}
-\end{figure*}
-
-In this section, we investigate the different types of bow interaction
-that will occur in different regions of parameter space. We will
-mainly treat the canonical case\footnote{%
-  Variant cases with differing arrangements of dust and radiation
-  sources are treated in \S~\ref{sec:case-inside-out}.} %
-of a bow around a star of bolometric luminosity, \(L\), with a
-radiatively driven wind, which is immersed in an external stream of
-gas and dust with density, \(\rho\), and velocity, \(v\).  The size and
-shape of the bow is determined by a generalized balance of pressure
-(or, equivalently, momentum) between internal and external sources.
-We assume that the stream is supersonic and super-alfvenic, so that
-the external pressure is dominated by the ram pressure: \(\rho v^2\).
-
-\subsection{Strong gas-grain coupling}
-\label{sec:strong-gas-grain}
-
-We first consider the case where the dust grains and gas are perfectly
-coupled by collisions.\footnote{%
-  Cases where this assumption does not hold are investigated below in
-  \S~\ref{sec:imperf-coupl-betw}.} %
-Although dust grains typically constitute only a small fraction
-\(Z\grain \sim 0.01\) of the mass of the external stream, they
-nevertheless dominate the broad-band opacity at FUV, optical and IR
-wavelengths if they are present.\footnote{%
-  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
-  dominates if the hydrogen neutral fraction is larger than
-  \(\approx 0.001\), see discussion of ionization front trapping
-  below.} %
-The strong coupling assumption means that all the radiative forces
-applied to the dust grains are directly felt by the gas also.
-
-The internal pressure is the sum of wind ram pressure and the
-effective radiation pressure that acts on the bow shell.  The
-radiative momentum loss rate of the star is \(L/c\) and the wind
-momentum loss rate can be expressed as
-\begin{equation}
-  \label{eq:wind-efficiency}
-  \dot{M} V = \eta L / c \ , 
-\end{equation}
-where \(\eta\) is the momentum efficiency of the wind, which is typically
-\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
-all of the stellar radiative momentum, emitted with rate \(L/c\), is
-trapped by the bow shell.  In the single scattering limit,\footnote{%
-  Although it may seem inconsistent to assume single scattering in the
-  case of high optical depths, this is defensible for the following
-  reasons. (1)~The grain albedo is not that high (typically
-  \(\sim 0.5\) at ultraviolet through optical wavelengths). (2)~The
-  scattered radiation field is more isotropic than the stellar field,
-  leading to cancellation in the radiative
-  flux. (3)~Absorbed radiation is re-emitted at infrared
-  wavelengths, where the dust opacity is very much lower.} %
-and temporarily neglecting the wind, then pressure balance at the bow
-apex, a distance \(R_0\) along the symmetry axis from the star is
-given by
-\begin{equation}
-  \label{eq:rad-press-balance-thick}
-  \frac{L}{4 \pi c R_0^2} = \rho v^2 \ ,
-\end{equation}
-which yields a fiducial bow shock radius in this optically thick limit
-as
-\begin{equation}
-  \label{eq:Rstar}
-  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
-\end{equation}
-
-We now consider the opposite, optically thin limit.  If the total
-opacity (gas plus dust) per total mass (gas plus dust) is \(\kappa\) (with
-units of \si{cm^2.g^{-1}}), then the radiative acceleration is
-\begin{equation}
-  \label{eq:rad-accel}
-  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ .
-\end{equation}
-Therefore, an incoming stream with initial velocity, \(v_\infty\), can be
-brought to rest by radiation alone\footnote{%
-  For simplicity, we here ignore the effects of gravity, which are
-  important for low ratios of \(\kappa L / M\), see
-  \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
-  shocks, which are important as the velocity approaches the sound
-  speed, \(\sound\) (in \S~XX below, we show that the resultant
-  corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
-at a distance \(R_0\) where
-\begin{equation}
-  \label{eq:rad-poten}
-  \int_{R_0}^\infty a_{\text{rad}} \, dr = \tfrac12 v_\infty^2 \ , 
-\end{equation}
-yielding
-\begin{equation}
-  \label{eq:rad:R0}
-  R_0 = \frac{\kappa L}{2\pi c v_\infty^2} \ .
-\end{equation}
-On the other hand, we can also argue as in the optically thick case
-above by approximating the bow shell as a surface, and balancing
-stellar radiation pressure against the ram pressure of the incoming
-stream.  The important difference when the shell is not optically
-thick is that only a fraction \(1 - e^{-\tau}\) of the radiative momentum
-is absorbed by the bow, so that
-equation~\eqref{eq:rad-press-balance-thick} is replaced with
-\begin{equation}
-  \label{eq:rad-press-balance-tau}
-  \frac{L (1 - e^{-\tau})}{4 \pi c R_0^2} = \rho v^2 \ .
-\end{equation}
-In the optically thin limit, \(1 - e^{-\tau} \approx \tau\), so these two
-descriptions can be seen to agree so long as
-\begin{equation}
-  \label{eq:tau-thin}
-  \tau = 2 \kappa \rho R_0 \ ,
-\end{equation}
-which we will assume to hold generally.
-
-Then, defining a fiducial optical depth,
-\begin{equation}
-  \label{eq:tau-star}
-  \tau_* = \rho \kappa R_* \ ,
-\end{equation}
-and adding in the stellar wind ram pressure\footnote{%
-  We implicitly assume that the interaction of the stellar wind with
-  the external stream can always be treated in the continuum limit.
-  This will be true if either the collisional mean free path or the
-  ion Larmor radius is much smaller than \(R_0\), which is almost
-  always the case.} %
-from equation~\eqref{eq:wind-efficiency}, we find that the general bow
-radius can be written in terms of the fiducial radius as
-\(R_0 = x R_*\), where \(x\) is the solution of
-\begin{equation}
-  \label{eq:rad-full-x}
-  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta = 0 \ .
-\end{equation}
-Since this is a transcendental equation, \(x\) must be found
-numerically, but we can write explicit expressions for three limiting
-cases:
-\begin{equation}
-  \label{eq:x-cases}
-  x \approx
-  \begin{cases}
-    \text{if \(\tau_* \gg 1\):} & (1 + \eta)^{1/2}  \\
-    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta \bigr)^{1/2} \approx
-    \begin{cases}
-      \text{if \(\tau_*^2 \gg \eta\):} & 2 \tau_*  \\
-      \text{if \(\tau_*^2 \ll \eta\):} & \eta^{1/2} 
-    \end{cases}
-  \end{cases}
-\end{equation}
-The first case, \(x \approx (1 + \eta)^{1/2}\), corresponds to a
-\textit{radiation bow shock}; the second case,
-\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave}; and the
-third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow shock}.
-The two bow shock cases are similar in that the external stream is
-oblivious to the presence of the star until it suddenly hits the bow
-shock shell, differing only in whether it is radiation or wind that is
-providing the internal pressure.  In the intermediate bow wave case,
-on the other hand, the external stream is gradually decelerated by
-absorption of photons as it approaches the bow.\footnote{A shock does
-  still form in this case, but shocked material constitutes only a
-  fraction of the total column density of the shell, see
-  \S~\ref{sec:shape-bow-wave}.}
-
-\begin{table*}
-  \centering
-  \caption{Stellar parameters for example stars}
-  \label{tab:stars}
-  \begin{tabular}{l S S S S S S S S S l}
-    \toprule
-    & {\(M / \si{M_\odot}\)} & {\(L_4\)}
-    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta \)}
-    & {Sp.~Type} 
-    & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
-    & {\(S_{49}\)} & Figures 
-    \\
-    \midrule
-    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
-                   & \ref{fig:zones-v-n-plane}a,
-                     \ref{fig:decouple-v-n-plane},
-                     \ref{fig:decouple-v40-versus-n} \\
-    Main-sequence OB stars
-    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
-                   & \ref{fig:zones-v-n-plane}b\\
-    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
-                   & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
-    Blue supergiant star
-    & 33 & 30.2 & 20.2 & 0.93 & 0.3079 & {B0.7\,Ia} & 23.5 & 0.123 & 0.016
-                   & \ref{fig:B-supergiant} \\[\smallskipamount]
-    Red supergiant star
-    & 20 & 15.6 & 100 & 0.015 & 0.0476 & {M1\,Ia} & 3.6 & 0.805 & 0
-                   & \ref{fig:M-supergiant} \\ 
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-We now consider the application to bow shocks around main sequence OB
-stars, expressing stellar and ambient parameters in terms of typical
-values as follows:
-\begin{align*}
-  \label{eq:stellar-parameters}
-  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
-  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
-  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
-  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
-  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
-  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
-\end{align*}
-where \(\bar{m}\) is the mean mass per hydrogen nucleon
-(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
-abundances).  Note that \(\kappa = \SI{600}{cm^2.g^{-1}}\) corresponds to a
-cross section of \(\approx \SI{e-21}{cm^2}\) per hydrogen nucleon, which is
-typical for interstellar medium dust \citep{Bertoldi:1996a} at far
-ultraviolet wavelengths, where OB stars emit most of their radiation.
-In terms of these parameters, we can express the stellar wind momentum
-efficiency as
-\begin{equation}
-  \label{eq:wind-eta-typical}
-  \eta = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
-\end{equation}
-and the fiducial radius and optical depth as
-\begin{align}
-  \label{eq:Rstar-typical}
-  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
-  \label{eq:taustar-typical}
-  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
-\end{align}
-In Figure~\ref{fig:zones-v-n-plane}, we show results for the bow size
-(apex distance, \(R_0\)) as a function of the density, \(n\), and
-relative velocity, \(v_\infty\), of the external stream, with each panel
-corresponding to a particular star, with parameters as shown in
-Table~\ref{tab:stars}.  To facilitate comparison with previous work,
-we choose stellar parameters similar to those used in the
-hydrodynamical simulations of \citet{Meyer:2014b, Meyer:2016a,
-  Meyer:2017a}, based on stellar evolution tracks for stars of
-\SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and theoretical wind
-prescriptions \citep{de-Jager:1988a, Vink:2000a}.  Although the
-stellar parameters do evolve with time, they change relatively little
-during the main-sequence lifetime of several million years.\footnote{%
-  \label{fn:meyer-velocities-too-low}
-  Note that we have recalculated the stellar wind terminal velocities,
-  since the values given in the \citeauthor{Meyer:2014b} papers are
-  troublingly low.  We have used the prescription
-  \(V = 2.6 V_{\text{esc}}\), where
-  \(V_{\text{esc}} = \left( 2 G M (1 - \Gamma_e)/ R \right)^{1/2}\) is the
-  photospheric escape velocity, which is appropriate for strong
-  line-driven winds with \(T_{\text{eff}} > \SI{21 000}{K}\)
-  \citep{Lamers:1995a}.  We find velocities of
-  \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
-  observations and theory \citep{Vink:1999a} for O~stars, but at least
-  two times higher than those cited by \citet{Meyer:2014b}. For
-  main-sequence B~stars, wind column densities are too low to reliably
-  measure the terminal velocity from near ultraviolet P~Cygni profiles
-  \citep{Prinja:1989a}, and so the values are theory-dependent
-  \citep{Krticka:2014a} and hence more uncertain.  A further
-  complication is the existence of a subset of OB stars with
-  anomalously weak winds \citep{Puls:2008a}, which in some cases is
-  related to the presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
-  \citep{Oskinova:2011b}.} %
-The three examples are an early B~star (\SI{10}{M_\odot}), a late O~star
-(\SI{20}{M_\odot}), and an early O~star (\SI{40}{M_\odot}), which cover the
-range of luminosities and wind strengths expected from bow-producing
-hot main sequence stars.  The luminosity is a steep function of
-stellar mass (\(L \sim M^{2.5}\)) and the wind mass-loss rate is a steep
-function of luminosity (\(\dot{M} \sim L^{2.2}\)), which means that the
-wind momentum efficiency is also a steep function of mass
-(\(\eta \sim M^3\)), approaching unity for early O~stars, but falling to
-less than 1\% for B~stars.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-RSG}
-  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for a cool M-type
-    supergiant instead of hot main sequence stars.  A smaller dust
-    opacity is used, \(\kappa = \SI{60}{cm^2.g^{-1}}\), because of the
-    reduced extinction efficiency at the optical/infrared wavelengths
-    emitted by this star.}
-  \label{fig:M-supergiant}
-\end{figure}
-
-It can be seen from Figure~\ref{fig:zones-v-n-plane} that the onset of
-the radiation bow wave regime is very similar for the three
-main-sequence stars, occurring at
-\(n > \text{\numrange{20}{40}} \, v_{10}^2\).  An important
-difference, however, is that for the \SI{40}{M_\odot} star, which has a
-powerful wind, the radiation bow wave regime only occurs for a very
-narrow range of densities, whereas for the \SI{10}{M_\odot} star, with a
-much weaker wind, the regime is much broader, extending to
-\(n < \num{e4} \, v_{10}^2\).  Another difference is the size scale of
-the bows in this regime, which is
-\(R_0 = \text{\SIrange{0.001}{0.003}{pc}}\) for the \SI{10}{M_\odot} star
-if \(v_\infty = \SI{40}{km.s^{-1}}\), but \(R_0 \approx \SI{0.1}{pc}\) for the
-\SI{40}{M_\odot} star, assuming the same inflow velocity.
-
-Figure~\ref{fig:M-supergiant} shows results for a cool M-type
-super-giant star with stellar parameters inspired by Betelgeuse
-(\chemalpha~Orionis), as listed in Table~\ref{tab:stars}.  Unlike the
-UV-dominated spectrum of the hot stars, this star emits predominantly
-in the near-infrared, where the dust extinction efficiency is lower,
-so we adopt a lower opacity of \SI{60}{cm^2.g^{-1}}.  This has the
-effect of shifting the radiation bow wave regime to higher densities:
-\(n = \text{\numrange{1000}{30 000}}\, v_{10}^2\) in this case.
-
-\subsubsection{Effects of stellar gravity}
-\label{sec:effects-gravity}
-
-In principle, gravitational attraction from the star, of mass \(M\),
-will partially counteract the radiative acceleration.  This can be
-accounted for by replacing \(L\) with an effective luminosity
-\newcommand\Edd{\ensuremath{_{\text{E}}}}
-\begin{equation}
-  \label{eq:effective-luminosity}
-  L_{\text{eff}} = L \bigl(1 - \Gamma\Edd^{\,-1}\bigr) \ ,
-\end{equation}
-in which \(\Gamma\Edd\) is the Eddington factor:
-\begin{equation}
-  \label{eq:eddington-factor}
-  \Gamma\Edd = \frac{\kappa L}{4\pi c G M} = 458.5 \, \frac{\kappa_{600} L_4}{ M } \ ,
-\end{equation}
-where, in the last expression, \(M\) is measured in solar masses.  For
-the stars in Table~\ref{tab:stars}, we find
-\(\Gamma\Edd \approx \text{\numrange{30}{400}}\), so gravity can be safely
-ignored.  The only exception is when the optical depth of the bow is
-very large: \(\tau > \ln\Gamma\Edd \sim 5\), in which case gravity may be
-important in the outer parts of the shell (see
-\citealt{Rodriguez-Ramirez:2016b}).
-
-\subsubsection{Ionization state of the bow shell}
-\label{sec:trapp-ioniz-front}
-
-\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
-\newcommand\shell{\ensuremath{_{\text{sh}}}}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-BSG}
-  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for an evolved
-    B-type supergiant instead of main sequence stars.  This is similar
-    to the early O MS star of Fig.~\ref{fig:zones-v-n-plane}\textit{c}
-    in many respects, except for the trapping of the ionization front,
-    which occurs for much lower outer stream densities.}
-  \label{fig:B-supergiant}
-\end{figure}
-
-In this section we calculate whether the star is capable of
-photoionizing the entire bow shock shell, or whether the ionization
-front will be trapped within it.  The number of hydrogen
-recombinations\footnote{%
-  The diffuse field is treated in the on-the-spot approximation,
-  assuming all emitted Lyman continuum photons are immediately
-  re-absorbed locally, so the case~B recombination co-efficient,
-  \(\alphaB = \num{2.6e-13}\, T_4^{-0.7}\, \si{cm^3.s^{-1}}\), is
-  used, where \(T_4 = T/\SI{e4}{K}\).} %
-per unit time per unit area in a fully ionized shell is
-\begin{equation}
-  \label{eq:shell-recombination-rate}
-  \mathcal{R} = \alphaB n\shell^2 h\shell \ ,
-\end{equation}
-while the advective flux of hydrogen nuclei through the shock is 
-\begin{equation}
-  \label{eq:shell-advective-flux}
-  \mathcal{A} = n v \ ,
-\end{equation}
-and the flux of hydrogen-ionizing photons
-(\(h \nu > \SI{13.6}{eV}\)) incident on the inner edge of the shell is
-\begin{equation}
-  \label{eq:shell-ionizing-flux}
-  \mathcal{F} = \frac{S} {4 \pi R_0^2} \ , 
-\end{equation}
-where \(S\) is the ionizing photon luminosity of the star.  Any shell
-with \(\mathcal{R} + \mathcal{A} > \mathcal{F}\) cannot be entirely
-photoionized by the star, and so must have trapped the ionization
-front.
-
-The ratio of advective particle flux to ionizing flux is, from equations~\eqref{eq:Rstar}, \eqref{eq:shell-advective-flux}, \eqref{eq:shell-ionizing-flux},
-\begin{equation}
-  \label{eq:advective-over-ionizing-flux}
-  \frac{\mathcal{A}}{\mathcal{F}} = \num{5.86e-5} \frac{x^2 L_4}{v_{10} S_{49}} \ , 
-\end{equation}
-which is nearly always small.  For clarity of exposition, we therefore
-ignore \(\mathcal{A}\) in the following discussion, although it is
-included in quantitative calculations.  The column density of the
-shocked shell can be found, for example, from equations~(10) and~(12)
-of \citet{Wilkin:1996a} in the limit \(v_\infty/V \to 0\) (Wilkin's parameter
-\(\alpha\)) and \(\theta \to 0\).  This yields
-\begin{equation}
-  \label{eq:shocked-shell-column}
-  n\shell h\shell = \tfrac34 n R_0 \ .
-\end{equation}
-Assuming strong cooling behind the shock,\footnote{%
-  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
-} %
-the shell density is
-\begin{equation}
-  \label{eq:isothermal-shell-density}
-  n\shell = \mathcal{M}_0^2 n \,
-\end{equation}
-where
-\(\mathcal{M}_0 = v_\infty / \sound\) is the isothermal Mach number of the
-external stream.\footnote{%
-  \label{fn:temperature-dependence}
-  The sound speed depends on the temperature and hydrogen and helium
-  ionization fractions, \(y\) and \(y_{\text{He}}\) as
-  \(\sound^2 = (1 + y + z_{\text{He}} y_{\text{He}}) (k T /
-  \bar{m})\), where \(z_{\text{He}}\) is the helium nucleon abundance
-  by number relative to hydrogen and
-  \(k = \SI{1.3806503e-16}{erg.K^{-1}}\) is Boltzmann's constant.  We
-  assume \(y = 1\), \(y_{\text{He}} = 0.5\), \(z_{\text{He}} = 0.09\),
-  so that \(\sound = \num{11.4}\, T_4^{1/2}\, \si{km.s^{-1}}\). } %
-Putting these together with equations~\eqref{eq:Rstar} and
-~\eqref{eq:tau-star}, one finds that \(\mathcal{R} > \mathcal{F}\)
-implies
-\begin{equation}
-  \label{eq:ifront-trap-x-cubed-taustar}
-  x^3 \tau_* > \frac{4 S c \sound \bar{m}^2 \kappa}{3 \alpha L} \ .
-\end{equation}
-From equation~\eqref{eq:rad-full-x}, it can be seen that \(x\) depends
-on the external stream parameters, \(n\), \(v_\infty\) only via
-\(\tau_*\), and so equation~\eqref{eq:ifront-trap-x-cubed-taustar} is a
-condition for \(\tau_*\), which, by using equation~\eqref{eq:taustar-typical}, becomes a condition on \(n / v_{10}^2\).  In the radiation bow shock case,
-\(x = (1 + \eta)^{1/2}\), and the condition can be written:
-\begin{equation}
-  \label{eq:ifront-trap-density-RBS}
-  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta)^3} \ , 
-\end{equation}
-where
-\begin{equation*}
-  S_{49} = S / \bigl( \SI{e49}{s^{-1}} \bigr) \ .
-\end{equation*}
-Numerical values of \(S_{49}\) for our three example stars are given
-in Table~\ref{tab:stars}, taken from Figure~4 of
-\citet{Sternberg:2003a}.  In the radiation bow wave case,
-\(x = 2\tau_*\), and the condition can be written:
-\begin{equation}
-  \label{eq:ifront-trap-taustar-RBW}
-  \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ . 
-\end{equation}
-In the wind bow shock case, the result is the same as
-equation~\eqref{eq:ifront-trap-density-RBS}, but changing the factor
-\((1 + \eta)^3\) to \(\eta^3\).  For the example hot stars in
-Table~\ref{tab:stars}, and assuming \(\kappa_{600} = 1\),
-\(T_4 = 0.8\), the resulting density threshold is
-\(n > (\text{\numrange{1000}{5000}})\, v_{10}^2\), depending only
-weakly on the stellar parameters, which is shown by the red lines in
-Figure~\ref{fig:zones-v-n-plane}.  For the \SI{10}{M_\odot} star, this is
-in the radiation bow wave regime, whereas for the higher mass stars it
-is in the radiation bow shock regime.  When the external stream is
-denser than this, then the outer parts of the shocked shell may be
-neutral instead of ionized, giving rise to a cometary compact \hii{}
-region \citep{Mac-Low:1991a, Arthur:2006a}.  This is only necessarily
-true, however, when the star is isolated.  If the star is in a cluster
-environment, then the contribution of other nearby massive stars to
-the ionizing radiation field must be considered.
-
-Quite different results are obtained for a B-type supergiant star (see
-Tab.~\ref{tab:stars} and Fig.~\ref{fig:B-supergiant}), which has a
-similar bolometric luminosity and wind strength to the \SI{40}{M_\odot}
-main-sequence star, but a hundred times lower ionizing luminosity.
-This results in a far lower threshold for trapping the ionization
-front of \(n > 40 v_{10}^2\).  The advective flux, \(\mathcal{A}\), is
-relatively stronger for this star than for the main-sequence stars, but
-even for \(v_{10} < 2\), where the effect is strongest, the change is
-only of order the width of the dark red line in
-Figure~\ref{fig:B-supergiant}.
-
-In principle, when the ionization front trapping occurs in the bow
-wave regime, then the curves for \(R_0\) will be modified in the
-region above the red line because all of the ionizing radiation is
-trapped in the shell due to gas opacity, which is not included in
-equation~\eqref{eq:tau-thin}.  However, this only happens for our
-\SI{10}{M_\odot} star, which has a relatively soft spectrum.
-Table~\ref{tab:stars} gives the peak wavelength of the stellar
-spectrum for this star as \(\lambda_{\text{eff}} = \SI{0.115}{\um}\), which
-is significantly larger than the hydrogen ionization threshold at
-\SI{0.0912}{\um}, meaning that only a small fraction of the total
-stellar luminosity is in the EUV band and affected by the gas opacity.
-The effect on \(R_0\) is therefore small.  For the higher mass stars,
-\(\lambda_{\text{eff}} < \SI{0.0912}{\um}\), so the majority of the
-luminosity is in the EUV band, but in these cases the ionization front
-trapping occurs well inside the radiation bow shock zone, where the
-dust optical depth is already sufficient to trap all of the radiative
-momentum.
-
-\subsubsection{Radiative cooling lengths}
-\label{sec:radi-cool-lengths}
-\newcommand\M{\ensuremath{\mathcal{M}}}
-In this section, we calculate whether the radiative cooling is
-sufficiently rapid behind the bow shock to allow the formation of a
-thin, dense shell.  Since cooling is least efficient at low densities,
-we will assume that the wind bow shock regime applies unless otherwise
-specified. We label quantities just outside the shock by the subscript
-``0'', quantities just inside the shock (after thermalization, but
-before any radiative cooling) by the subscript ``1'', and quantities
-after the gas has cooled back to the photoionization equilibrium
-temperature by the subscript ``2''.  Assuming a ratio of specific
-heats, \(\gamma = 5/3\), the relation between the pre-shock and immediate
-post-shock quantities is
-\begin{align}
-  % \M_1 &= \left(\frac{\M_0^2 + 3} {5\M_0^2 - 1}\right)^{1/2} \\
-  \label{eq:shock-n-jump}
-  \frac{n_1}{n_0} &= \frac{4 \M_0^2} {\M_0^2 + 3} \\
-  \label{eq:shock-T-jump}
-  \frac{T_1}{T_0} &= \tfrac1{16} \bigl( 5\M_0^2 - 1 \bigr) \bigl( 1 + 3/\M_0^2 \bigr) \\
-  \label{eq:shock-v-jump}
-  \frac{v_1}{v_0} &= \left(\frac{n_1}{n_0}\right)^{-1} \ ,
-\end{align}
-where \(\M_0 = v_0 / \sound\).  The cooling length of the post-shock
-gas can be written as
-\newcommand\cool{\ensuremath{_{\text{cool}}}}
-\begin{equation}
-  \label{eq:dcool}
-  d\cool = \frac{3 P_1 v_1} { 2 \bigl(  \mathcal{L}_1 - \mathcal{G}_1 \bigr) }\ ,  
-\end{equation}
-where \(P_1\) is the thermal pressure and \(\mathcal{L}_1\),
-\(\mathcal{G}_1\) are the volumetric radiative cooling and heating
-rates.  For fully photoionized gas, we have
-\(P_1 \approx 2 n_1 k T_1\), \(\mathcal{L}_1 = n_1^2 \Lambda(T_1)\), and
-\(\mathcal{G}_1 = n_1^2 \Gamma(T_1)\), where \(\Lambda(T)\) is the cooling
-coefficient, which is dominated by metal emission lines that are
-excited by electron collisions, and \(\Gamma(T)\) is the heating
-coefficient, which is dominated by hydrogen photo-electrons
-\citep{Osterbrock:2006a}. The cooling coefficient has a maximum around
-\SI{e5}{K}, and for typical ISM abundances can be approximated as
-follows:
-\begin{align}
-  \label{eq:cooling-coefficient}
-  \Lambda_{\text{warm}} &= \num{3.3e-24} \, T_4^{2.3} \, \si{erg.cm^{-3}.s^{-1}}\\
-  \Lambda_{\text{hot}} &= \num{e-20} \, T_4^{-1}\, \si{erg.cm^{-3}.s^{-1}} \\
-  \Lambda &= \left( \Lambda_{\text{warm}}^{-k} +  \Lambda_{\text{hot}}^{-k} \right)^{-1/k}
-      \quad \text{with} \quad k = 3 \ ,
-\end{align}
-which is valid in the range \(0.7 < T_4 < 1000\).  We approximate the heating coefficient as
-\begin{equation}
-  \label{eq:heating-coefficient}
-  \Gamma = \num{1.77e-24} \, T_4^{-1/2} \, \si{erg.cm^{-3}.s^{-1}} \ ,
-\end{equation}
-where the coefficient is chosen so as to give \(\Gamma = \Lambda\) at
-an equilibrium temperature of \(T_4 = 0.8\).
-
-In Figure~\ref{fig:zones-v-n-plane} we show curves calculated from
-equations~\eqref{eq:shock-n-jump} to~\eqref{eq:heating-coefficient},
-corresponding to \(d\cool = R_0\) (thick blue line) and
-\(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
-thickness in the efficient cooling case.  In this context, \(n_0 = n\)
-and \(n_2 = n\shell\), so that \(h_0\) follows from
-equations~\eqref{eq:shocked-shell-column}
-and~\eqref{eq:isothermal-shell-density} as
-\begin{equation}
-  \label{eq:strong-cooling-h0}
-  h_0 = \tfrac34 \M_0^{-2} R_0 \ .
-\end{equation}
-The bends in the curves at \(v \approx \SI{50}{km.s^{-1}}\) are due to the
-maximum in the cooling coefficient \(\Lambda(T)\) around
-\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
-blue line, radiative cooling is so efficient that the bow shock can be
-considered isothermal, and so the shell is dense and thin (at least,
-in the apex region).  It can be seen that the ionization front
-trapping always occurs at densities larger than this, which justifies
-the use of equation~\eqref{eq:isothermal-shell-density} in the
-previous section.  For bows with outer stream densities below the
-thick blue line, cooling is unimportant and the bow shock can be
-considered non-radiative.  In this case the shell is thicker than in
-the radiative case,
-\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
-  An approximate value can be found from
-  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
-  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
-  Consideration of the slight increase in density between the shock
-  and the contact discontinuity reduces this value by 5--10\%.} %
-For bows with outer stream densities between the two blue lines,
-cooling does occur, albeit inefficiently, so that the shell thickness
-is set by \(d\cool\) rather than \(h_0\).
-
-\subsection{Imperfect coupling between gas and dust}
-\label{sec:imperf-coupl-betw}
+\section{Cloudy models of dust charging around OB stars}
+\label{sec:cloudy-models-dust}
 
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
-  \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
-    gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
-  \label{fig:decouple-v-n-plane}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/decouple-v40-versus-n}
-  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
-    showing bow radius and different regimes for a fixed inflow
-    velocity of \SI{40}{km.s^{-1}}.}
-  \label{fig:decouple-v40-versus-n}
-\end{figure}
-
-\subsection{The case of inside-out bows}
-\label{sec:case-inside-out}
-
-So far, we have considered the case where the inner source dominates
-the radiation, while dust is present only in the outer stream, which
-applies to hot stars interacting with the ISM.  However, in the case
-of cool stars, the inner wind will also be dusty.  Examples are the
-red supergiant (RSG) phase of high-mass evolution, or the asymptotic
-giant branch (AGB) stage of low/intermediate-mass evolution.  In both
-these cases, it is still the inner source that provides the radiation
-field.  However, not all winds are radiatively driven and in those
-cases it is conceivable that it is the outer source that dominates the
-radiation field.  An example is the case of photoevaporating
-protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
-regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
-thermally driven photoevaporation flow \citep{HA:1998, Henney:1999a},
-while the outer stream is the stellar wind from an O~star
-\citep{Garcia-Arredondo:2001a}.
-
 %%% Local Variables:

### 2018-05-24 papers/Papers1234/sec-dust-bow-intro.tex
Move the Cloudy dust models to an appendix

@@
   \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
-  \caption{Drag force as a function of gas--grain slip velocity,
-    \(w\), for different values of the grain potential,
-    \(\phi = U / k T\).  Contributions from proton and electron Coulomb
-    (electrostatic) drag, as well as Epstein (solid-body) drag are
-    indicated.  Inset shows \(\phi\) as a function of the radiation
-    parameter, \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a
-    log--linear scale.}
+  \caption{Dimensionless drag force, \(f\drag / f_*\), as a function
+    of gas--grain slip velocity, \(w\), for different values of the
+    grain potential in thermal units, \(\phi\).  Contributions from
+    proton and electron Coulomb (electrostatic) drag, as well as
+    Epstein (solid-body) drag are indicated.  Examples of subsonic and
+    highly supersonic stable drift velocities are shown (thin dark
+    blue arrows), where the drag force is in equilibrium with the
+    radiation force (thick dark blue dashed lines), while blue shading
+    indicates the unstable, mildly supersonic velocity regime, where
+    no stable drift equilibrium exists.  Inset graph shows \(\phi\) as a
+    function of the radiation parameter,
+    \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a log--linear scale
+    for a collection of Cloudy models (see
+    Appendix~\ref{sec:cloudy-models-dust}).}
   \label{fig:gas-grain-drag-photoionized}
-\end{figure*}
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/multi-dustprops}
-  \caption{Dust properties as a function of radius from star for three
-    selected Cloudy models. (a)~\SI{40}{M_\odot} main-sequence star in
-    medium of density \SI{e4}{cm^{-2}}. (b)~\SI{10}{M_\odot} main-sequence
-    star in medium of density \SI{1}{cm^{-2}}. (c)~Blue supergiant
-    star in medium of density \SI{1}{cm^{-2}}}.
-  \label{fig:multi-dustprops}
-\end{figure*}
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/drift-pratio-4panel}
-  \caption{Drift velocity versus radiation parameter \(\Xi_P\). Each line
-    represents a model with ambient density and stellar type as
-    indicated in the key.}
-  \label{fig:drift-gn}
 \end{figure*}
@@
 Results are shown in Figure~\ref{fig:gas-grain-drag-photoionized} for
-different values of \(\phi = e U / kT\), where \(U = e Z\grain / a \) is
-the electrostatic potential of a grain of charge \(Z\grain\) and
-radius \(a\).
+different values of the dimensionless grain potential:
+\(\phi = e^2 Z\grain / a kT\), which is the electrostatic potential
+energy of a unit charge at the surface of a grain of charge
+\(Z\grain\) and radius \(a\), in units of the characteristic thermal
+energy of a gas particle. 
+The drag force \(f\drag\) is put in
+dimensionless units by dividing by a characteristic force:
+\begin{equation}
+  \label{eq:fstar}
+  f_* = 2 n k T \cdot \pi a^2 \ , 
+\end{equation}
+which is approximately the gas pressure multiplied by the grain
+geometric cross section.
 

### 2018-05-24 papers/Papers1234/sec-dust-bow-intro.tex
Paragraph on the Epstein and Coulomb drag behavior

@@
 \end{equation}
-which is approximately the gas pressure multiplied by the grain
-geometric cross section.
+which is approximately\footnote{Exact in the case of a fully ionized,
+  pure hydrogen plasma.  For typical ISM abundances, the contribution
+  to the gas pressure of helium and its corresponding electrons gives
+  a correction of order 5\%.} %
+the ionized gas pressure multiplied by the grain geometric cross
+section.
+
+For grains with low electric charge, \(\phi^2 \ll 1\), the drag force is
+dominated by direct collisions of protons with the grain (Epstein
+drag).  This is illustrated by the \(\phi = 0.25\) case (blue line) in
+Figure~\ref{fig:gas-grain-drag-photoionized}. In the subsonic regime,
+\(f\drag\) increases linearly with the relative slip speed, \(w\),
+reaching \(f\drag \approx f_*\) at
+\(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to quadratic
+increase, \(f\drag \approx w^2 f_* / \sound^2\), in the supersonic regime.
+As \(\abs{\phi}\) increases, long-range electrostatic interactions with
+protons within the Debye radius (Coulomb drag) become increasingly
+important at subsonic relative velocities, as shown in
+Figure~\ref{fig:gas-grain-drag-photoionized} by the orange
+(\(\phi = 1\)), green (\(\phi = 4\)), and red (\(\phi = 16\)) lines.  However,
+the Coulomb drag has a peak when \(w\) is equal to the thermal
+speed of the colliders, which is \(\approx \SI{10}{km.s^{-1}}\) for protons,
+giving a maximum strength of
+\begin{equation}
+  \label{eq:fdrag-maximum}
+  f_{\mathrm{max}} = 0.5\, (\ln\Lambda)\, \phi^2 f_* \approx 10\, \phi^2 f_* \ , 
+\end{equation}
+where \(\Lambda\) is the plasma parameter (number of particles within a
+Debye volume), such that
+\(\ln\Lambda = 23.267 + 1.5 \ln T_4 - 0.5 \ln n\).  At highly super-thermal
+speeds, the Coulomb drag falls asymptotically as
+\(f\drag \propto 1 / w^{2}\).  The thermal speed of electrons is higher by a
+factor of \((m_p / m_e)^{1/2}\), so that the electron Coulomb drag
+gives a second peak of similar strength, but at
+\(w \approx \SI{430}{km.s^{-1}}\).
+
+% Or \Lambda = (4 pi / 3) n r_D^3?
+% Where Debye length is r_D^2 = k T / 4 pi n e^2
+% => \Lambda = n r_D (4 pi / 3) k T / 4 pi n e^2
+% = k T r_D / 3 e^2
+% This is 9 times less than the other expression
+% Anyway, from kappa notes I have
+% \ln\Lambda = 9.452 + 1.5 ln(T) - 0.5 ln(n)
+
+% If I am going to use log10, then the coefficients get divided by
+% ln(10) = 2.30258509299, and if we use T4, then we add 1.5 ln(1e4) =
+% 13.815.  So we get 23.267 + 0.651 log10(T4) - 0.217 log10(n).  Nope,
+% best with natural log
 

### 2018-05-25 papers/Papers1234/app-dust-wave.tex
Add in drag terms to magnetic dust waves
Get as far as describing the phi(Xi) relation

@@
-\section{Shape and structure of dust waves}
-\label{sec:shape-dust-wave}
+\section{Dust waves in the drag-free limit}
+\label{sec:gas-free-bow}
 
-As an alternative to hydrodynamic or magnetohydrodynamic bow shocks,
-it is possible that some observed emission arcs may be bow waves due
-to the action of radiation pressure on dust grains.
+% As an alternative to hydrodynamic or magnetohydrodynamic bow shocks,
+% it is possible that some observed emission arcs may be bow waves due
+% to the action of radiation pressure on dust grains.
 
@@
     a divergent stream of dust grains that originates from a source on
-    the \(x\) axis at a distance \(D = 10 R_0\) from the origin.  In
+    the \(x\) axis at a distance \(D = 10 R\starstar\) from the origin.  In
     this case, the inner edge of the bow wave is hyperbolic and the
@@
 radiation pressure efficiency\footnote{%
+  \label{fn:Qp}
   For absorption efficiency \(Q_{\text{abs}}\), scattering efficiency
@@
 
-\subsection{Gas-free dust wave}
-\label{sec:gas-free-bow}
+% \subsection{Gas-free dust wave}
 
@@
 radial velocity \(-v_\infty\), which is decelerated to zero at the distance
-of closest approach, \(R_0\), given by energy conservation:
+of closest approach, \(R\starstar\), given by energy conservation:
 \begin{equation}
   \label{eq:dust-r0}
-  R_0 = \frac{\xsec \Qp L} {2 \pi c m\grain v_\infty^2} \ ,
+  R\starstar = \frac{\xsec \Qp L} {2 \pi c m\grain v_\infty^2} \ ,
 \end{equation}
@@
 to be hyperbolic, characterized by an eccentricity,
-\(\varepsilon = \bigl( 1 + 4 b^2 / R_0^2\bigr)^{1/2}\), and polar angle of
+\(\varepsilon = \bigl( 1 + 4 b^2 / R\starstar^2\bigr)^{1/2}\), and polar angle of
 closest approach, \(\thm = \cos^{-1} \varepsilon^{-1}\).  The trajectory is
@@
   \label{eq:dust-r-theta}
-  \frac{R\grain(\theta; b)} {R_0} = 
+  \frac{R\grain(\theta; b)} {R\starstar} = 
   \frac{ \tfrac12 \bigl( \varepsilon^2 - 1 \bigr)} {\varepsilon \cos(\theta - \thm) - 1} \ , 
@@
 with a total deflection angle of \(2 \thm\), which is equal to
-\ang{90} when \(b = 0.5 R_0\).
+\ang{90} when \(b = 0.5 R\starstar\).
 
-\subsubsection{Parallel dust stream}
+\subsection{Parallel dust stream}
 \label{sec:dust-parallel}
@@
 trajectories with varying \(b\), but the same \(v_\infty\), then deflection
-by the radiative force will form a bow wave around the radiation
-source, as shown in Figure~\ref{fig:dust-trajectories}.  However, the
-inner edge of the bow wave, \(R_{\text{in}}(\theta)\) is not given by the
-closest approach along individual trajectories, \(R\grain(\thm; b)\),
-but instead must found by minimizing \(R\grain(\theta; b)\) over all
-\(b\) for each value of \(\theta\), which yields
+by the radiative force will form a bow-shaped dust wave around the
+radiation source, as shown in Figure~\ref{fig:dust-trajectories}.
+However, the inner edge of the dust wave, \(R_{\text{in}}(\theta)\) is not
+given by the closest approach along individual trajectories,
+\(R\grain(\thm; b)\), but instead must found by minimizing
+\(R\grain(\theta; b)\) over all \(b\) for each value of \(\theta\), which yields
 \begin{equation}
   \label{eq:dust-r-in}
-  \frac{R_{\text{in}}(\theta)} {R_0} = \frac{2}{1 + \cos\theta} \ .
+  \frac{R_{\text{in}}(\theta)} {R\starstar} = \frac{2}{1 + \cos\theta} \ .
 \end{equation}
@@
 
-\subsubsection{Divergent dust stream}
+\subsection{Divergent dust stream}
 \label{sec:dust-divergent}
@@
 Fig.~\ref{Q-fig:crw-schema} of \PaperI{}). We parametrize the degree
-of divergence as \(\mu = R_0 / D\) and, as before,
+of divergence as \(\mu = R\starstar / D\) and, as before,
 \(R\grain(\theta + \theta_1(b, \mu); b)\) is minimized over all trajectories to
@@
   \label{eq:dust-divergent-r-in}
-  \frac{R_{\text{in}}(\theta; \mu)} {R_0} = \frac{1 + \varepsilon_\mu}{1 + \varepsilon_\mu\cos\theta} \ ,
+  \frac{R_{\text{in}}(\theta; \mu)} {R\starstar} = \frac{1 + \varepsilon_\mu}{1 + \varepsilon_\mu\cos\theta} \ ,
 \end{equation}
@@
   \caption{Dust-gas coupling for an on-axis (purely radial)
-    trajectory.  (a)~Grain radial position, \(R/R_0\), gas--grain
+    trajectory.  (a)~Grain radial position, \(R/R\starstar\), gas--grain
     velocity difference, \(w/v_\infty\), and local asymptotic drift
@@
 
-\subsection{Bow wave with gas drag}
+\section{Toy model of dust wave with gas drag}
 \label{sec:bow-wave-drag}
@@
   \label{eq:dust-alpha}
-  \alpha\drag \equiv \frac{v_\infty} {w\drift(R_0)} = \left(
-    Q\drag \frac{R_0 / a\grain} {\rho\grain / \rho\gas}
+  \alpha\drag \equiv \frac{v_\infty} {w\drift(R\starstar)} = \left(
+    Q\drag \frac{R\starstar / a\grain} {\rho\grain / \rho\gas}
   \right)^{1/2} \ ,
@@
 \textit{re-couple} to the inflowing gas stream around a radius
-\(\approx R_0 / \alpha\drag \) and be swept back in again for another approach to
+\(\approx R\starstar / \alpha\drag \) and be swept back in again for another approach to
 the source.  A further effect of increasing \(\alpha\drag\) is that the
@@
 (panel b) is a spiral, which converges on the stagnation point
-\((R, v) = (R_0 / \alpha\drag, 0)\). The cases \(\alpha\drag = 0.5\) and
+\((R, v) = (R\starstar / \alpha\drag, 0)\). The cases \(\alpha\drag = 0.5\) and
 \(\alpha\drag = 2\) are shown, and it can be seen that with larger
@@
 parameter.  In the \(\alpha\drag = 1.0\) case, the oscillating trajectories
-are more confined, forming a thick shell around \(R_0\).  In the
+are more confined, forming a thick shell around \(R\starstar\).  In the
 \(\alpha\drag = 2.0\) case, the shell is much thinner and concentrated at
 the inner rim.  As \(\alpha\drag\) increases, the oscillations are damped
-further so that the stagnation radius \(R_0 / \alpha\drag\) becomes a good
+further so that the stagnation radius \(R\starstar / \alpha\drag\) becomes a good
 approximation to the apex radius of the density wave.  All the cases
@@
 
-\subsection{Bow wave with magnetic field}
+\section{Dust wave with magnetic field}
 \label{sec:bow-wave-with}
@@
 
-\subsection{Applicability of the bow wave models}
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/dust-lorentz-stream-3d-turb-b90-L2000-Ma0100-Z+000}
+  \includegraphics[width=\linewidth]{figs/dust-lorentz-stream-3d-turbz-b90-L2000-Ma0100-Y+000}
+  \caption{Streamlines in three dimensions of resolved gyro-radius }
+  \label{fig:stream-3d}
+\end{figure}
+
+\subsection{Resolved Larmor radius}
+\label{sec:resolv-larm-radi}
+
+\section{Applicability of the dust wave models}
 \label{sec:dust-applicability}
 
-The apex turn-around radius, \(R_0\), of the bow wave depends on the
+The apex turn-around radius, \(R\starstar\), of the bow wave depends on the
 grain properties via the combination \(\xsec \Qp / m\grain\).  For
@@
 efficiency is \(\Qp \sim 1\), whereas for \(\lambda > a\grain\) it is
-\(\Qp \sim a\grain/\lambda\).  Therefore, we would expect \(R_0\) to be almost
+\(\Qp \sim a\grain/\lambda\).  Therefore, we would expect \(R\starstar\) to be almost
 independent of grain size for small grains, but to vary as
-\(R_0 \propto a\grain^{-1}\) for large grains, where small/large is relative
+\(R\starstar \propto a\grain^{-1}\) for large grains, where small/large is relative
 to the peak wavelength of the radiation source.  In principle, a
@@
 
-\subsection{Apparent shapes of projected dragoids}
+\section{Apparent shapes of projected dragoids}
 \label{sec:dust-wave-apparent}

### 2018-05-25 papers/Papers1234/sec-dust-bow-intro.tex
Get as far as describing the phi(Xi) relation

@@
 \(Z\grain\) and radius \(a\), in units of the characteristic thermal
-energy of a gas particle. 
-The drag force \(f\drag\) is put in
-dimensionless units by dividing by a characteristic force:
+energy of a gas particle.  The drag force \(f\drag\) is put in dimensionless units by dividing by
+a characteristic force:
 \begin{equation}
@@
 \end{equation}
-which is approximately\footnote{Exact in the case of a fully ionized,
-  pure hydrogen plasma.  For typical ISM abundances, the contribution
-  to the gas pressure of helium and its corresponding electrons gives
-  a correction of order 5\%.} %
+which is approximately\footnote{%
+  To simplify the exposition, the gas pressure in this section is
+  calculated assuming a fully ionized, pure hydrogen plasma, yielding
+  \(P\gas = 2 n k T\). For typical ISM abundances, the contribution of
+  helium and its corresponding electrons gives a correction to this of
+  order 5\%.  The required modifications when the stream is neutral
+  are discussed later.  } %
 the ionized gas pressure multiplied by the grain geometric cross
@@
 For grains with low electric charge, \(\phi^2 \ll 1\), the drag force is
-dominated by direct collisions of protons with the grain (Epstein
-drag).  This is illustrated by the \(\phi = 0.25\) case (blue line) in
-Figure~\ref{fig:gas-grain-drag-photoionized}. In the subsonic regime,
-\(f\drag\) increases linearly with the relative slip speed, \(w\),
-reaching \(f\drag \approx f_*\) at
-\(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to quadratic
-increase, \(f\drag \approx w^2 f_* / \sound^2\), in the supersonic regime.
+dominated by direct collisions of protons with the grain.  The gas
+collisional mean free path is much larger than the grain size, so the
+drag is in the Epstein regime \citep{Weidenschilling:1977b}.  This is
+illustrated by the \(\phi = 0.25\) case (blue line) in
+Figure~\ref{fig:gas-grain-drag-photoionized}. As the relative
+gas--grain slip speed, \(w\), increases, \(f\drag\) first increases
+linearly with \(w\) reaching \(f\drag \approx f_*\) at
+\(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to a quadratic
+increase in the supersonic regime:
+\begin{equation}
+  \label{eq:fdrag-epstein}
+  f\drag \approx
+  \begin{cases}
+    \text{if \(\phi^2 \ll 1\) and \(w_{10} < 1\):} & w_{10}\, f_* \\
+    \text{if \(\phi^2 \ll 1\) and \(w_{10} > 1\):} & w_{10}^2\, f_* \\
+  \end{cases}
+  \ ,
+\end{equation}
+where \(w_{10} = w / \SI{10}{km.s^{-1}}\).
+
 As \(\abs{\phi}\) increases, long-range electrostatic interactions with
@@
 speeds, the Coulomb drag falls asymptotically as
-\(f\drag \propto 1 / w^{2}\).  The thermal speed of electrons is higher by a
-factor of \((m_p / m_e)^{1/2}\), so that the electron Coulomb drag
-gives a second peak of similar strength, but at
+\(f\drag \propto 1 / w^{2}\).  The thermal speed of electrons is higher than
+that of the protons by a factor of \((m_p / m_e)^{1/2}\), so that the
+electron Coulomb drag gives a second peak of similar strength, but at
 \(w \approx \SI{430}{km.s^{-1}}\).
@@
 % best with natural log
+
+In Appendix~\ref{sec:gas-free-bow} we calculate the behaviour of an
+incoming stream of dust grains, subject only to the repulsive
+radiative force from a star.  We are now in a position to see how
+gas--grain drag will modify this picture.  From
+equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar}, we can write
+the radiation force acting on a grain as
+\begin{equation}
+  \label{eq:frad-Xi}
+  f\rad = \Qp\, \Xi\, f_* \ ,
+\end{equation}
+where \(\Qp\) is the grain's radiation pressure efficiency (see
+footnote~\ref{fn:Qp} in Appendix~\ref{sec:gas-free-bow}) and \(\Xi\) is
+the local radiation parameter, defined as the ratio of direct stellar
+radiation pressure to gas pressure:
+\begin{equation}
+  \label{eq:Xi-Prad-over-Pgas}
+  \Xi \equiv \frac{P\rad}{P\gas} \approx \frac{L}{4 \pi R^2 c\, (2 n k T)} \ ,
+\end{equation}
+where the last expression corresponds to the optically thin limit and
+pure ionized hydrogen.  The grain potential \(\phi\) is also primarily
+determined by \(\Xi\), as shown in Appendix~\ref{sec:cloudy-models-dust}
+and the inset graph of Figure~\ref{fig:gas-grain-drag-photoionized},
+but with a slow dependence, which can be approximated\footnote{%
+  There is a slight secondary dependence on the grain composition and
+  stellar spectrum.  The relationship given in
+  eq.~\eqref{eq:phi-vs-Xi} is appropriate for graphite grains and for
+  stellar effective temperatures in the range \SIrange{20}{30}{kK}.
+  For hotter stars than this, \(\phi\) should be multiplied by a further
+  factor of \(1.5\), while for silicate grains it should be divided by
+  \(1.5\).  } %
+as
+\begin{equation}
+  \label{eq:phi-vs-Xi}
+  \phi \approx 1.5 \bigl( 2.3 +  \ln \Xi \bigr) \ .
+\end{equation}
 

### 2018-05-27 papers/Papers1234/sec-dust-bow-intro.tex
Add new figures for the gas-grain drag

@@
 
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/test-Fdrag-components}
+  \caption{Contributions of different collider species to the
+    dimensionless drag force, \(f\drag / f_*\), as a function of
+    gas--grain slip velocity, \(w\).  Solid lines show the Coulomb
+    (electrostatic) drag, while dashed lines show the Epstein
+    (solid-body) drag.  Results are shown for dimensionless grain
+    potential \(\phi = 10\).  All Coulomb forces scale with
+    \(\phi^2\), while the Epstein forces are independent of \(\phi\).  The
+    species labelled ``CNO++'' represents the combined effect of all
+    metals (total abundance \num{8.5e-4}, effective atomic weight
+    \num{15.3}), which are assumed to be doubly ionized.}
+  \label{fig:drag-components}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/test-Fdrag-param-space}
+  \caption{Regimes of gas--grain drag as a function of slip velocity
+    and grain potential.  The different regimes are indicated by bold
+    roman numerals, as explained in
+    Table~\ref{tab:fdrag-regimes}. Blue shading indicates regions
+    dominated by Epstein (solid-body) drag, whereas red and green
+    shading indicate regions dominated by Coulomb drag due to protons
+    and electrons, respectively.  In each case, the saturated color
+    represents a contribution \(> 70\%\) of the relevant component to
+    the total drag force, while progressively lighter shading
+    represents the \(> 60\%\) and \(> 50\%\) levels.  The thick white
+    dotted line indicates the transition between the subthermal and
+    superthermal regimes for protons, while the thin white dotted line
+    indicates the corresponding transition for electrons.  Contours
+    show the total drag force in units of \(f_*\) (see
+    eq.~\eqref{eq:fstar}) in decade intervals from \(0.1\) to
+    \(10^4\), as labelled.  Results are shown for
+    \(T = \SI{8000}{K}\) and \(n = \SI{100}{cm^{-3}}\), but the
+    differences are very slight throughout the ranges
+    \(T = \text{\SIrange{5000}{15000}{K}}\) and
+    \(n = \text{\SIrange{e-3}{e6}{cm^{-3}}}\).}
+  \label{fig:drag-v-phi-plane}
+\end{figure}
+
 \begin{figure*}
@@
 
+\subsubsection{Drag force on grains}
+\label{sec:drag-force-grains}
+
+\begin{table}
+  \centering
+  \caption{Regimes of drag force as function of grain potential and slip speed}
+  \label{tab:fdrag-regimes}
+  \renewcommand\arraystretch{1.3}
+  \resizebox{\linewidth}{!}{%
+    \begin{tabular}{@{}r l l l@{}}
+    \toprule
+      & Regime & Approximate criteria & \(f\drag / f_*\) \\ \midrule
+      I & Epstein subsonic & \(\phi^2 \ll 1\)
+                             and \(w_{10} < 1\) & \(1.5\, w_{10}\) \\
+      II & Epstein supersonic & \(w_{10} > 1\)
+                                and \(w_{10} > 5\,\abs{\phi}\)& \( w_{10}^2\) \\
+      III & Coulomb p\(^+\) subthermal & \(\phi^2 > 1\)
+                                         and \(w_{10} < 1\) & \((1 + 20\, \phi^2)\,
+                                                              w_{10}\) \\
+    % & Coulomb p\(^+\) peak & \(\phi^2 > 1\)
+    %                          and \(w_{10} \approx 1\) & \(1 + 10\, \phi^2\) \\
+      IV & Coulomb p\(^+\) superthermal & \(\phi^2 > 1\)
+                                          and \(1 < w_{10} < 5\) & \(w_{10}^2
+                                                                   + 10\, \phi^2/w_{10}^2 \) \\
+      V & Coulomb e\(^-\) subthermal & \(\phi^2 > 20\)
+                                 and \(5 < w_{10} < 42\) & \(0.48\, \phi^2 \,
+                                                           w_{10}\) \\
+    \bottomrule
+  \end{tabular}
+  }
+\end{table}
+
 The drag force on a charged dust grain moving at a relative speed
@@
   \(P\gas = 2 n k T\). For typical ISM abundances, the contribution of
-  helium and its corresponding electrons gives a correction to this of
-  order 5\%.  The required modifications when the stream is neutral
-  are discussed later.  } %
+  helium and its corresponding electrons yield a correction to this of
+  order 5\%.  The required modifications when a cool star interacts
+  with a predominantly neutral gas stream are discussed later.  } %
 the ionized gas pressure multiplied by the grain geometric cross
@@
 \(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to a quadratic
-increase in the supersonic regime:
-\begin{equation}
-  \label{eq:fdrag-epstein}
-  f\drag \approx
-  \begin{cases}
-    \text{if \(\phi^2 \ll 1\) and \(w_{10} < 1\):} & w_{10}\, f_* \\
-    \text{if \(\phi^2 \ll 1\) and \(w_{10} > 1\):} & w_{10}^2\, f_* \\
-  \end{cases}
-  \ ,
-\end{equation}
-where \(w_{10} = w / \SI{10}{km.s^{-1}}\).
+increase in the supersonic regime.
 
@@
 that of the protons by a factor of \((m_p / m_e)^{1/2}\), so that the
-electron Coulomb drag gives a second peak of similar strength, but at
-\(w \approx \SI{430}{km.s^{-1}}\).
+electron Coulomb drag gives a second peak fof similar strength, but at
+\(w \approx \SI{430}{km.s^{-1}}\).  The behavior of \(f\drag\) in all these
+different regimes is summarised in Table~\ref{tab:fdrag-regimes}, in
+terms of \(\phi\) and \(w_{10} = w / \SI{10}{km.s^{-1}}\).
+
+% \begin{equation}
+%   \label{eq:fdrag-regimes}
+%   f\drag \approx
+%   \begin{cases}
+%     \text{Epstein subsonic (\(\phi^2 \ll 1\) and \(w_{10} < 1\)):}
+%     & w_{10}\, f_* \\
+%     \text{Epstein supersonic (\(\phi^2 \ll 1\) and \(w_{10} > 1\)):}
+%     & w_{10}^2\, f_* \\
+%     \text{Coulomb p\(^+\) subthermal (\(\phi^2 > 1\) and \(w_{10} < 1\)):}
+%     & (1 + 20 \phi^2)\, w_{10}\, f_* \\
+%     \text{Coulomb p\(^+\) peak (\(\phi^2 > 1\) and \(w_{10} \approx 1\)):}
+%     & (1 + 10 \phi^2)\, f_* \\
+%     \text{Coulomb p\(^+\) superthermal (\(\phi^2 > 1\) and \(1 < w_{10} < 5\)):}
+%     & (w_{10}^2 + 10 \phi^2/w_{10}^2) \, f_* \\
+%     \text{Coulomb e\(^-\) subthermal (\(\phi^2 > 20\) and \(5 < w_{10} < 42\)):}
+%     & 0.48 \phi^2 \, w_{10}\, f_* \\
+%   \end{cases}
+% \end{equation}
 
@@
 % best with natural log
+
+\subsubsection{Gas--grain separation: drift and rip}
+\label{sec:gas-grain-separ}
 
@@
 \end{equation}
-where the last expression corresponds to the optically thin limit and
-pure ionized hydrogen.  The grain potential \(\phi\) is also primarily
-determined by \(\Xi\), as shown in Appendix~\ref{sec:cloudy-models-dust}
-and the inset graph of Figure~\ref{fig:gas-grain-drag-photoionized},
-but with a slow dependence, which can be approximated\footnote{%
+where the last expression corresponds to the optically thin limit.
+The grain potential \(\phi\) is also primarily determined by \(\Xi\), as
+shown in Appendix~\ref{sec:cloudy-models-dust} and the inset graph of
+Figure~\ref{fig:gas-grain-drag-photoionized}, but with a slow
+dependence, which can be approximated\footnote{%
   There is a slight secondary dependence on the grain composition and
@@
 \end{equation}
+
+In the outer regions of the photoionized volume around an OB star,
+close to the ionization front, the radiation parameter is low, with
+typical value \(\Xi \sim 0.1\).  In this regime, the negative charge
+current at the grain surface due to electron collisions is roughly in
+balance with the positive current due to the ultraviolet photoelectric
+effect \citep{Weingartner:2001b}, leading to a low grain potential,
+\(\abs{\phi} < 1\), which may be positive or negative.  The low
+\(\Xi\) means that the radiative force is also weak:
+\(f\rad \sim 0.1 f_*\) from equation~\eqref{eq:frad-Xi} if
+\(\Qp \sim 1\) at UV wavelengths, which is true for all but the smallest
+grains.  Thus, from equation~\eqref{eq:fdrag-epstein}, the radiative
+force can be balanced by Epstein drag if \(w_{10} \sim 0.1\), leading to
+a small drift velocity, \(w\drift \sim \SI{1}{km.s^{-1}}\), of the grains
+with respect to the gas.
+
+As a dust grain
+approaches a star, the radiation parameter \(\Xi\) will increase as
+\(R^{-2}\)
 

### 2018-05-28 papers/Papers1234/sec-dust-bow-intro.tex
Write about rip point

@@
 different regimes is summarised in Table~\ref{tab:fdrag-regimes}, in
-terms of \(\phi\) and \(w_{10} = w / \SI{10}{km.s^{-1}}\).
+terms of \(\phi\) and \(w_{10} = w / \SI{10}{km.s^{-1}}\).  This is
+further illustrated in Figure~\ref{fig:drag-v-phi-plane}, where the
+drag regimes are located on the \((w, \abs{\phi})\) plane.
 
@@
 incoming stream of dust grains, subject only to the repulsive
-radiative force from a star.  We are now in a position to see how
-gas--grain drag will modify this picture.  From
-equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar}, we can write
-the radiation force acting on a grain as
+radiation force from a star.  For an initial inward radial trajectory,
+the dust grain motion is decelerated and turned around, reaching a
+minimum radius \(R\starstar\), given by equation~\eqref{eq:dust-r0}.
+This drag-free radiative turnaround radius, \(R\starstar\), is smaller
+for higher initial inward velocities, but is independent of the
+density of the incoming stream.  We are now in a position to see how
+gas--grain drag will modify this picture.
+
+From equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar}, we can
+write the radiation force acting on a grain as
 \begin{equation}
@@
 Figure~\ref{fig:gas-grain-drag-photoionized}, but with a slow
-dependence, which can be approximated\footnote{%
-  There is a slight secondary dependence on the grain composition and
-  stellar spectrum.  The relationship given in
-  eq.~\eqref{eq:phi-vs-Xi} is appropriate for graphite grains and for
-  stellar effective temperatures in the range \SIrange{20}{30}{kK}.
-  For hotter stars than this, \(\phi\) should be multiplied by a further
-  factor of \(1.5\), while for silicate grains it should be divided by
-  \(1.5\).  } %
-as
+dependence, which can be approximated as
 \begin{equation}
@@
 \end{equation}
+There are also slight secondary dependencies on the grain composition and
+stellar spectrum.  The relationship given in eq.~\eqref{eq:phi-vs-Xi}
+is appropriate for graphite grains and for stellar effective
+temperatures in the range \SIrange{20}{30}{kK}.  For hotter stars than
+this, \(\phi\) should be multiplied by a further factor of \(1.5\), while
+for silicate grains it should be divided by \(1.5\).
 
@@
 \(\Qp \sim 1\) at UV wavelengths, which is true for all but the smallest
-grains.  Thus, from equation~\eqref{eq:fdrag-epstein}, the radiative
-force can be balanced by Epstein drag if \(w_{10} \sim 0.1\), leading to
-a small drift velocity, \(w\drift \sim \SI{1}{km.s^{-1}}\), of the grains
-with respect to the gas.
+grains.  Thus, from the equations for \(f\drag\) given in
+Table~\ref{tab:fdrag-regimes}, the radiative force can be balanced by
+Epstein drag if \(w_{10} \sim 0.1\), leading to a small equilibrium drift
+velocity, \(w\drift < \SI{1}{km.s^{-1}}\), of the grains with respect
+to the gas.  This drift is much smaller than the inward stream
+velocities that we are considering
+(\(v_\infty > \SI{10}{km.s^{-1}}\)), so the dust follows the gas stream at
+a slightly reduced velocity (\(< 10\%\)), and (by mass conservation) a
+slightly increased density.  Each grain exerts an exactly opposite
+force to \(f\drag\) upon the gas, but since the dust-gas mass ratio,
+\(Z\grain\), is small, this produces a negligible acceleration of the
+gas.
 
-As a dust grain
-approaches a star, the radiation parameter \(\Xi\) will increase as
-\(R^{-2}\)
+As the dusty stream approaches the star, the radiation parameter
+\(\Xi\) will increase, with a dependence of \(R^{-2}\) once the stream
+is well away from the ionization front.  This increases \(f\rad\)
+(eq.~\eqref{eq:frad-Xi}), but also increases the grain potential,
+\(\phi\) (eq.~\eqref{eq:phi-vs-Xi}) due to the increasing dominance of
+grain charging by photoelectric ejection.  Initially, this results in
+a lowering of the equilibrium drift velocity to \(w_{10} \sim 0.01\) as
+the Coulomb drag kicks in (see Appendix~\ref{sec:cloudy-models-dust}).
+However, at smaller radii the slow logarithmic increase in
+\(\phi(\Xi)\) means that the drift velocity must start increasing again to
+accommodate the linear increase of \(f\rad(\Xi)\).  Eventually,
+\(f\rad\) exceeds \(f_{\mathrm{max}}\), the maximum drag force that
+proton Coulomb interactions can provide
+(eq.~\eqref{eq:fdrag-maximum}).  This occurs at a critical value of
+the radiation parameter, which we denote the \textit{rip point}:
+\(\Xi_\dag \sim 1000\).  The variations in \(\Xi_\dag\) with star and grain
+parameters, which are of order \SI{+- 0.5}{dex}, are listed in
+Table~\ref{tab:Xi-rip}.
+
+\begin{table}
+  \caption{Critical values of radiation parameter at the rip point: \(\Xi_\dag\)}
+  \centering
+  \begin{tabular}{l @{\quad\quad\quad} S S} \toprule
+    & \multicolumn{2}{c}{Grain composition} \\
+    Spectrum & {Graphite} & {Silicate}
+    \\ \midrule
+    B star & 1000 +- 400 & 350 +- 150 \\
+    O star & 3000 +- 500 & 2500 +- 500 \\
+    \bottomrule
+    \addlinespace
+    \multicolumn{3}{@{}p{0.6\columnwidth}@{}}{
+    Uncertainties represent variations with grain size and gas density
+    (see Appendix~\ref{sec:cloudy-models-dust}).}
+  \end{tabular}
+  \label{tab:Xi-rip}
+\end{table}
 

### 2018-05-28 papers/Papers1234/sec-dust-bow-intro.tex
More about the rip point

@@
     species labelled ``CNO++'' represents the combined effect of all
-    metals (total abundance \num{8.5e-4}, effective atomic weight
-    \num{15.3}), which are assumed to be doubly ionized.}
+    metals (see footnote~\ref{fn:metal-drag}).}
   \label{fig:drag-components}
@@
 We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
-summing over protons, electrons, and helium ions.\footnote{Helium is
-  assumed to be 50\% neutral and 50\% singly ionized, leading to only
+considering the contributions from protons, electrons, helium
+ions,\footnote{Helium is assumed to be singly ionized, leading to only
   a small contribution to the drag force.  For much hotter stars, such
   as the central stars of planetary nebulae, helium may be doubly
-  ionized, which leads to a more significant drag contribution,
-  especially around \(w \approx \SI{5}{km.s^{-1}}\).} %
-Results are shown in Figure~\ref{fig:gas-grain-drag-photoionized} for
-different values of the dimensionless grain potential:
-\(\phi = e^2 Z\grain / a kT\), which is the electrostatic potential
+  ionized, which leads to a fourfold increase in its Coulomb drag
+  contribution, which is significant for \(w < \SI{5}{km.s^{-1}}\).} %
+and metal ions.\footnote{%
+  \label{fn:metal-drag}
+  All metals are lumped together as a single species, assuming
+  standard \hii{} region gas-phase abundances.  They are dominated by
+  C and O, with minor contributions from N and Ne.  The total
+  abundance is \num{8.5e-4} and the effective atomic weight is
+  \num{15.3}.  All are assumed to be doubly ionized.  Their largest
+  relative contribution to the drag force is for
+  \(w < \SI{2}{km.s^{-1}}\), but is less than 1\% even there.} %
+Results are shown in Figure~\ref{fig:drag-components}, where dashed lines correspond to direct solid body collisions and solid lines to electrostatic interactions.
+The latter depend on the grain potential, which is described in dimensionless terms by \(\phi\), which is the electrostatic potential
 energy of a unit charge at the surface of a grain of charge
 \(Z\grain\) and radius \(a\), in units of the characteristic thermal
-energy of a gas particle.  The drag force \(f\drag\) is put in dimensionless units by dividing by
-a characteristic force:
+energy of a gas particle:
+\begin{equation}
+  \label{eq:phi-potential}
+  \phi = \frac{e^2 Z\grain}{a kT} \ .
+\end{equation}
+The electrostatic contributions to \(f\drag\) are proportional to
+\(\phi^2\) (results are shown for \(\abs{\phi} = 10\)), whereas the
+solid-body contributions are independent of \(\phi\).  The drag force is
+put in dimensionless units by dividing by a characteristic force:
 \begin{equation}
@@
 For grains with low electric charge, \(\phi^2 \ll 1\), the drag force is
-dominated by direct collisions of protons with the grain.  The gas
-collisional mean free path is much larger than the grain size, so the
-drag is in the Epstein regime \citep{Weidenschilling:1977b}.  This is
-illustrated by the \(\phi = 0.25\) case (blue line) in
-Figure~\ref{fig:gas-grain-drag-photoionized}. As the relative
-gas--grain slip speed, \(w\), increases, \(f\drag\) first increases
-linearly with \(w\) reaching \(f\drag \approx f_*\) at
+dominated by direct collisions of protons with the grain (dashed red
+line in Fig.~\ref{fig:drag-components}).  The gas collisional mean
+free path is much larger than the grain size, so the drag is in the
+Epstein regime \citep{Weidenschilling:1977b}.
+% This is illustrated by
+% the \(\phi = 0.25\) case (blue line) in
+% Figure~\ref{fig:gas-grain-drag-photoionized}.
+As the relative gas--grain slip speed, \(w\), increases, \(f\drag\)
+first increases linearly with \(w\) reaching \(f\drag \approx f_*\) at
 \(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to a quadratic
@@
 protons within the Debye radius (Coulomb drag) become increasingly
-important at subsonic relative velocities, as shown in
-Figure~\ref{fig:gas-grain-drag-photoionized} by the orange
-(\(\phi = 1\)), green (\(\phi = 4\)), and red (\(\phi = 16\)) lines.  However,
-the Coulomb drag has a peak when \(w\) is equal to the thermal
-speed of the colliders, which is \(\approx \SI{10}{km.s^{-1}}\) for protons,
-giving a maximum strength of
+important at subsonic relative velocities, as shown by the solid lines
+in Figure~\ref{fig:drag-components}).
+% in
+% Figure~\ref{fig:gas-grain-drag-photoionized} by the orange
+% (\(\phi = 1\)), green (\(\phi = 4\)), and red (\(\phi = 16\)) lines.
+However, the Coulomb drag has a peak when \(w\) is equal to the
+thermal speed of the colliders, which is
+\(\approx \SI{10}{km.s^{-1}}\) for protons, giving a maximum strength of
 \begin{equation}
@@
 that of the protons by a factor of \((m_p / m_e)^{1/2}\), so that the
-electron Coulomb drag gives a second peak fof similar strength, but at
-\(w \approx \SI{430}{km.s^{-1}}\).  The behavior of \(f\drag\) in all these
-different regimes is summarised in Table~\ref{tab:fdrag-regimes}, in
-terms of \(\phi\) and \(w_{10} = w / \SI{10}{km.s^{-1}}\).  This is
-further illustrated in Figure~\ref{fig:drag-v-phi-plane}, where the
-drag regimes are located on the \((w, \abs{\phi})\) plane.
+electron Coulomb drag (solid light blue line) gives a second peak of
+similar strength, but at \(w \approx \SI{430}{km.s^{-1}}\).  The behavior of
+\(f\drag\) in all these different regimes is summarised in
+Table~\ref{tab:fdrag-regimes}, in terms of \(\phi\) and
+\(w_{10} = w / \SI{10}{km.s^{-1}}\).  This is further illustrated in
+Figure~\ref{fig:drag-v-phi-plane}, where each of the drag regimes is
+located on the \((w, \abs{\phi})\) plane.
 
@@
   \label{eq:phi-vs-Xi}
-  \phi \approx 1.5 \bigl( 2.3 +  \ln \Xi \bigr) \ .
+  \phi(\Xi) \approx 1.5 \bigl( 2.3 +  \ln \Xi \bigr) \ .
 \end{equation}
@@
 
+\begin{table}
+  \caption{Critical values of radiation parameter at the rip point: \(\Xi_\dag\)}
+  \centering
+  \begin{tabular*}{0.75\columnwidth}{l @{\quad\quad\quad\quad} S S} \toprule
+    & \multicolumn{2}{c}{Grain composition} \\
+    Spectrum & {Graphite} & {Silicate}
+    \\ \midrule
+    B star & 1000 +- 400 & 350 +- 150 \\
+    O star & 3000 +- 500 & 2500 +- 500 \\
+    \bottomrule
+    \addlinespace
+    \multicolumn{3}{@{}p{0.75\columnwidth}@{}}{
+    Calculated from the Cloudy models shown in Figure~\ref{fig:drift-gn}. 
+    Uncertainties represent variations with grain size and gas density. 
+    See Appendix~\ref{sec:cloudy-models-dust} for further details.}
+  \end{tabular*}
+  \label{tab:Xi-rip}
+\end{table}
+
 As the dusty stream approaches the star, the radiation parameter
 \(\Xi\) will increase, with a dependence of \(R^{-2}\) once the stream
-is well away from the ionization front.  This increases \(f\rad\)
+is well inside the ionization front.  This increases \(f\rad\)
 (eq.~\eqref{eq:frad-Xi}), but also increases the grain potential,
@@
 parameters, which are of order \SI{+- 0.5}{dex}, are listed in
-Table~\ref{tab:Xi-rip}.
-
-\begin{table}
-  \caption{Critical values of radiation parameter at the rip point: \(\Xi_\dag\)}
-  \centering
-  \begin{tabular}{l @{\quad\quad\quad} S S} \toprule
-    & \multicolumn{2}{c}{Grain composition} \\
-    Spectrum & {Graphite} & {Silicate}
-    \\ \midrule
-    B star & 1000 +- 400 & 350 +- 150 \\
-    O star & 3000 +- 500 & 2500 +- 500 \\
-    \bottomrule
-    \addlinespace
-    \multicolumn{3}{@{}p{0.6\columnwidth}@{}}{
-    Uncertainties represent variations with grain size and gas density
-    (see Appendix~\ref{sec:cloudy-models-dust}).}
-  \end{tabular}
-  \label{tab:Xi-rip}
-\end{table}
-
-\subsection{The case of inside-out bows}
+Table~\ref{tab:Xi-rip} and illustrated graphically in
+Figure~\ref{fig:drift-gn}.  The radius of the rip point, \(R_\dag\), can
+be expressed in terms of \(R_*\), the fiducial optically thick bow
+shock radius introduced in \S~\ref{sec:strong-gas-grain}:
+\begin{equation}
+  \label{eq:Rdag-over-Rstar}
+  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
+\end{equation}
+where we have made use of equations~\eqref{eq:Rstar} and~\eqref{eq:Xi-Prad-over-Pgas}.
+
+\subsubsection{Grain trajectories for the on-axis case}
+\label{sec:grain-traj-axis}
+
+What happens to the dust grain following this catastrophic breakdown
+of gas--grain coupling depends on the relation between the rip point
+radius, \(R_\dag\), and the drag-free radiative turnaround radius,
+\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
+will still carry it in as far as \(R\starstar\) and the initial
+trajectory will be almost identical to that described in
+Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
+being turned around by the radiation field and pushed out past
+\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
+dragged back for a second approach.\footnote{If the initial impact
+  parameter of the trajectory is not strictly \(b = 0\), then the
+  resultant lateral component of \(f\rad\) will mean that \(b\) will
+  be much increased for the second approach.} %
+If, on the other hand, \(R_\dag < R\starstar\), then the tail wind
+provided by the gas drags the grain closer to the star than it
+``wants'' to be.
+
+\subsubsection{Dust waves in stream parameter space}
+\label{sec:dust-waves-stream}
+
+\section{The case of inside-out bows}
 \label{sec:case-inside-out}

### 2018-05-28 papers/Papers1234/sec-dust-bow-intro.tex
Figure with dust wave existence conditions

@@
     show the total drag force in units of \(f_*\) (see
-    eq.~\eqref{eq:fstar}) in decade intervals from \(0.1\) to
+    eq.~[\ref{eq:fstar}]) in decade intervals from \(0.1\) to
     \(10^4\), as labelled.  Results are shown for
@@
 is well inside the ionization front.  This increases \(f\rad\)
-(eq.~\eqref{eq:frad-Xi}), but also increases the grain potential,
-\(\phi\) (eq.~\eqref{eq:phi-vs-Xi}) due to the increasing dominance of
+(eq.~[\ref{eq:frad-Xi}]), but also increases the grain potential,
+\(\phi\) (eq.~[\ref{eq:phi-vs-Xi}]) due to the increasing dominance of
 grain charging by photoelectric ejection.  Initially, this results in
@@
 proton Coulomb interactions can provide
-(eq.~\eqref{eq:fdrag-maximum}).  This occurs at a critical value of
+(eq.~[\ref{eq:fdrag-maximum}]).  This occurs at a critical value of
 the radiation parameter, which we denote the \textit{rip point}:
@@
 Table~\ref{tab:Xi-rip} and illustrated graphically in
-Figure~\ref{fig:drift-gn}.  The radius of the rip point, \(R_\dag\), can
-be expressed in terms of \(R_*\), the fiducial optically thick bow
-shock radius introduced in \S~\ref{sec:strong-gas-grain}:
+Figure~\ref{fig:drift-gn}.
+
+\subsubsection{Existence conditions for a separate dust wave}
+\label{sec:exist-cond-separ}
+
+In order for a separate dust wave to exist, it is necessary for the
+grains to decouple from the incoming gas stream before the stream hits
+the hydrodynamic bow shock caused by the stellar wind.  The radius of
+the rip point, \(R_\dag\), can be expressed in terms of \(R_*\), the
+fiducial optically thick bow shock radius introduced in
+\S~\ref{sec:strong-gas-grain}:
 \begin{equation}
@@
 \end{equation}
-where we have made use of equations~\eqref{eq:Rstar} and~\eqref{eq:Xi-Prad-over-Pgas}.
+where we have made use of equations~\eqref{eq:Rstar}
+and~\eqref{eq:Xi-Prad-over-Pgas}.  The wind bow shock radius is
+\(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]), where \(\eta\) is the
+wind momentum efficiency (eq.~[\ref{eq:wind-eta-typical}]).
+Therefore, the condition \(R_\dag > R_0\) becomes
+\begin{equation}
+  \label{eq:dust-wave-velocity-condition}
+  v_{10} > \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
+\end{equation}
+For O stars, the wind efficiency is generally high (\(\eta > 0.1\)) and
+\(\Xi_\dag > 1000\) (Tab.~\ref{tab:Xi-rip}), so that
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/existence-dust-wave}
+  \caption{Regions of stream parameter space where separated dust waves may exist}
+  \label{fig:existence-dust-wave}
+\end{figure*}
 
@@
 
-\subsubsection{Dust waves in stream parameter space}
-\label{sec:dust-waves-stream}
-
 \section{The case of inside-out bows}

### 2018-05-28 papers/Papers1234/sec-dust-bow-intro.tex
Low density existence condition for dust waves

@@
 For O stars, the wind efficiency is generally high (\(\eta > 0.1\)) and
-\(\Xi_\dag > 1000\) (Tab.~\ref{tab:Xi-rip}), so that
+\(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
+exist when the stream velocity is very high
+(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
+can be much weaker (\(\eta < 0.01\)) and \((\Xi_\dag\) is also smaller, so
+that dust waves are permitted by this criterion for much lower stream
+velocities: (\(v_\infty > \SI{30}{km.s^{-1}}\)).
 
@@
 
-\subsubsection{Grain trajectories for the on-axis case}
-\label{sec:grain-traj-axis}
+However, there are other conditions that need to be satisfied in order
+for the dust wave to exist.  For instance, the drag-free turnaround
+radius must also be outside the bow shock: \(R\starstar > R_0\),
+otherwise the radiation is incapable of repelling the grain
+opportunely, even once it has decoupled from the gas.  From
+equations~\eqref{eq:Rstar}, \eqref{eq:tau-star},
+and~\eqref{eq:dust-r0} we find
+\begin{equation}
+  \label{eq:Rstarstar-over-Rstar}
+  \frac{R\starstar}{R_*} = \frac{2 \sigma\grain \Qp \tau_*}{\kappa m\grain} \ , 
+\end{equation}
+so, if we define a single-grain opacity as
+\(\kappa\grain = \sigma\grain \Qp / m\grain\), then this condition becomes
+\begin{equation}
+  \label{eq:dust-wave-low-density-condition}
+  \tau_* >  0.5\, \frac{\kappa}{\kappa\grain}\, \eta^{1/2} 
+  % \frac{\kappa \eta^{1/2}}{2 \kappa\grain}
+  \ . 
+\end{equation}
+The average value of the factor \(\kappa / \kappa\grain\) over the entire
+grain population must be equal to the dust--gas mass ratio,
+\(Z\grain \approx 0.01\), but the factor will vary between grains, according
+to their size and composition.\footnote{%
+  Remember that \(\kappa\) is the opacity per unit mass of gas, while
+  \(\kappa\grain\) is the opacity per unit mass of a particular grain. In
+  both cases, averaged over the stellar spectrum.} %
+In particular, it will be relatively larger for the largest grains
+(\(\approx \SI{0.2}{\um}\)), which dominate the total dust mass, and smaller
+for the smaller grains (\(\approx \SI{0.02}{\um}\)), which dominate the UV
+opacity.
+
+Further restrictions on the existence of dust waves arise when the
+effects of magnetic fields are considered, as will be discussed in
+\S~\ref{sec:magn-effects-grain} below.
+
+\subsubsection{Grain trajectories along the symmetry axis}
+\label{sec:grain-traj-along}
 
@@
 If, on the other hand, \(R_\dag < R\starstar\), then the tail wind
-provided by the gas drags the grain closer to the star than it
-``wants'' to be.
+provided by the gas drags the grain closer to the star than its
+inertia would naturally take it.
+
+\subsubsection{Magnetic effects on grain trajectories }
+\label{sec:magn-effects-grain}
 

### 2018-05-29 papers/Papers1234/sec-dust-bow-intro.tex
Third existence condition for dust waves

@@
 applied to the dust grains are directly felt by the gas also.
+
+\subsubsection{Bows supported by radiation and wind}
+\label{sec:three-bow-regimes}
 
@@
 energy of a unit charge at the surface of a grain of charge
-\(Z\grain\) and radius \(a\), in units of the characteristic thermal
+\(z\grain\) and radius \(a\), in units of the characteristic thermal
 energy of a gas particle:
@@
   \label{eq:phi-potential}
-  \phi = \frac{e^2 Z\grain}{a kT} \ .
+  \phi = \frac{e^2 z\grain}{a kT} \ .
 \end{equation}
@@
 (\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
-can be much weaker (\(\eta < 0.01\)) and \((\Xi_\dag\) is also smaller, so
+can be much weaker (\(\eta < 0.01\)) and \(\Xi_\dag\) is also smaller, so
 that dust waves are permitted by this criterion for much lower stream
@@
 \end{equation}
-The average value of the factor \(\kappa / \kappa\grain\) over the entire
-grain population must be equal to the dust--gas mass ratio,
+The average value of the factor \(\kappa / \kappa\grain\) over the entire grain
+population must be equal to the dust--gas mass ratio,
 \(Z\grain \approx 0.01\), but the factor will vary between grains, according
@@
 In particular, it will be relatively larger for the largest grains
-(\(\approx \SI{0.2}{\um}\)), which dominate the total dust mass, and smaller
-for the smaller grains (\(\approx \SI{0.02}{\um}\)), which dominate the UV
-opacity.
+(\(a \approx \SI{0.2}{\um}\)), which dominate the total dust mass, and
+smaller for the smaller grains (\(a \approx \SI{0.02}{\um}\)), which
+dominate the UV opacity.  Given the dependence of \(\tau_*\) on the
+stream parameters (eq.~[\ref{eq:taustar-typical}]), for a given
+stellar luminosity this condition corresponds to a minimum value for
+\(n / v_\infty^2\).
+
+A third condition comes from requiring \(R_\dag > R_0\) in the radiation
+bow wave regime (see \S~\ref{sec:three-bow-regimes}), where
+\(R_0 \approx 2 \tau_* R_*\).  This yields
+\begin{equation}
+  \label{eq:dust-wave-high-density-condition}
+  \tau_* < 0.5\, v_{10}\, \Xi_\dag^{-1/2} \ , 
+\end{equation}
+which, for a given stellar luminosity, corresponds to a maximum value
+for \(n / v_\infty^4\).  Thus, for a given stream velocity that satisfies
+equation~\eqref{eq:dust-wave-velocity-condition},
+equations~(\ref{eq:dust-wave-low-density-condition},
+\ref{eq:dust-wave-high-density-condition}) determine respectively the
+minimum and maximum stream density for which a dust wave can exist.
 

### 2018-05-29 papers/Papers1234/sec-dust-bow-intro.tex
Fig caption for dust wave existence and Rdag = Rstarstar

@@
 
-\subsubsection{Existence conditions for a separate dust wave}
+\subsubsection{Existence conditions for dust waves}
 \label{sec:exist-cond-separ}
@@
   \label{eq:dust-wave-velocity-condition}
-  v_{10} > \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
+  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
 \end{equation}
@@
   \includegraphics[width=\linewidth]{figs/existence-dust-wave}
-  \caption{Regions of stream parameter space where separated dust waves may exist}
+  \caption{Regions of stream parameter space \((v, n)\) where dust
+    waves may form around main-sequence OB stars of
+    \SIlist{10;20;40}{M_\odot} (see Tab.~\ref{tab:stars}).  Figure is
+    similar to Fig.~\ref{fig:zones-v-n-plane}, except that the
+    velocity axis is logarithmic and extends out to
+    \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show parameters
+    where dust waves may be allowed in the cases of large
+    (\(a = \SI{0.2}{\um}\)) and small (\(a = \SI{0.02}{\um}\))
+    graphite and silicate grains, as labeled in the left panel.  For
+    \((v, n)\) outside of these shapes, dust waves cannot occur for
+    the reasons indicated by yellow text boxes in the right panel. }
   \label{fig:existence-dust-wave}
@@
   \label{eq:dust-wave-low-density-condition}
-  \tau_* >  0.5\, \frac{\kappa}{\kappa\grain}\, \eta^{1/2} 
+  \tau_* >  \tau_{*,\text{min}} = 0.5\, \frac{\kappa}{\kappa\grain}\, \eta^{1/2} 
   % \frac{\kappa \eta^{1/2}}{2 \kappa\grain}
@@
   \label{eq:dust-wave-high-density-condition}
-  \tau_* < 0.5\, v_{10}\, \Xi_\dag^{-1/2} \ , 
+  \tau_* < \tau_{*,\text{max}} = 0.5\, v_{10}\, \Xi_\dag^{-1/2} \ , 
 \end{equation}
@@
   be much increased for the second approach.} %
-If, on the other hand, \(R_\dag < R\starstar\), then the tail wind
-provided by the gas drags the grain closer to the star than its
-inertia would naturally take it.
+From equations~(\ref{eq:Rdag-over-Rstar},
+\ref{eq:Rstarstar-over-Rstar},
+\ref{eq:dust-wave-high-density-condition}), the condition
+\(R_\dag > R\starstar\) corresponds to
+\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
+lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
+on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
+by the gas drags the grain closer to the star than its inertia would
+naturally take it.
 

### 2018-05-29 papers/Papers1234/sec-dust-bow-intro.tex
Write about stagnant drift velocity and tweak some figures

@@
 
-The ratio of advective particle flux to ionizing flux is, from equations~\eqref{eq:Rstar}, \eqref{eq:shell-advective-flux}, \eqref{eq:shell-ionizing-flux},
+The ratio of advective particle flux to ionizing flux is, from
+equations~\eqref{eq:Rstar}, \eqref{eq:shell-advective-flux},
+\eqref{eq:shell-ionizing-flux},
 \begin{equation}
@@
 \(\tau_*\), and so equation~\eqref{eq:ifront-trap-x-cubed-taustar} is a
-condition for \(\tau_*\), which, by using equation~\eqref{eq:taustar-typical}, becomes a condition on \(n / v_{10}^2\).  In the radiation bow shock case,
+condition for \(\tau_*\), which, by using
+equation~\eqref{eq:taustar-typical}, becomes a condition on
+\(n / v_{10}^2\).  In the radiation bow shock case,
 \(x = (1 + \eta)^{1/2}\), and the condition can be written:
@@
     \((v, n)\) outside of these shapes, dust waves cannot occur for
-    the reasons indicated by yellow text boxes in the right panel. }
+    the reasons indicated by labeled orange arrows in the center
+    panel.  Labeled dashed lines in the right panel show the
+    correspondence between the region boundaries and each dust wave
+    existence condition given in
+    equations~(\ref{eq:dust-wave-velocity-condition},
+    \ref{eq:dust-wave-low-density-condition},
+    \ref{eq:dust-wave-high-density-condition}). Heavy dashed lines in
+    the left panel show where the rip point and the drag-free
+    turnaround radius coincide.  For dust waves below these lines,
+    drag forces are unimportant for the grains.  }
   \label{fig:existence-dust-wave}
@@
 on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
-by the gas drags the grain closer to the star than its inertia would
-naturally take it.
+by the gas carries the grain closer to the star than its inertia would
+naturally take it.  When the grain finally decouples at \(R_\dag\) it
+experiences a much higher unbalanced \(f\rad\), which can initially
+accelerate it to outward velocities \(\gg \abs{v_\infty}\) if
+\(R_\dag \ll R\starstar\).
+
+The post-decoupling behavior of the grain depends on the sign of
+\(d f\drag / d w\) when \(w = \abs{v_\infty}\).  If this derivative is
+positive, as is the case in drag regimes~II and V (see
+Tab.~\ref{tab:fdrag-regimes} and Fig.~\ref{fig:drag-v-phi-plane}),
+then the grain can reach a stable equilibrium drift at rest with
+respect to the star\footnote{%
+  Again, this is only strictly true when the impact parameter is zero.
+  However, as we show below, it is a reasonable approximation over a
+  range of impact parameters in the case where the angle between the
+  magnetic field direction and the stream velocity is not too
+  large.} %
+at a point \(R_\ddag\), which we call the \textit{stagnant drift
+  radius}. If the stream velocity is not excessively high
+(\(v_\infty < \SI{150}{km.s^{-1}}\) when \(\phi = 4\), or
+\(< \SI{300}{km.s^{-1}}\) when \(\phi = 16\)), then the equilibrium
+\(f\rad\) is less than the value at the rip point, requiring a lower
+value of the radiation parameter: \(\Xi_\ddag < \Xi_\dag\).  The resultant
+stagnant drift radius is therefore outside the rip point:
+\(R_\ddag > R_\dag\).
+
+whether or not
+the incoming stream velocity lies in drag regime IV
+(Table~\ref{tab:fdrag-regimes}) with , which
+produces the unstable drift region identified in
+Figure~\ref{fig:gas-grain-drag-photoionized}.
 

### 2018-05-31 papers/Papers1234/sec-dust-bow-intro.tex
Figure showing phase space trajectories

@@
 experiences a much higher unbalanced \(f\rad\), which can initially
-accelerate it to outward velocities \(\gg \abs{v_\infty}\) if
-\(R_\dag \ll R\starstar\).
+accelerate it to outward velocities significantly higher than the
+inflow velocity if \(R_\dag \ll R\starstar\).
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/dust-wave-phase-trajectories-annotate}
+  \caption{Phase space trajectories along the symmetry axis}
+  \label{fig:phase-space-trajectories}
+\end{figure*}
 

### 2018-06-01 papers/Papers1234/sec-dust-bow-intro.tex
Write about the limit cycle

@@
   \includegraphics[width=\linewidth]{figs/dust-wave-phase-trajectories-annotate}
-  \caption{Phase space trajectories along the symmetry axis}
+  \caption{Trajectories of small graphite grains
+    (\(a = \SI{0.02}{\um}\)) at impact parameter \(b = 0\) for two
+    example cases (see yellow ``+'' symbols in left panel of
+    Fig.~\ref{fig:existence-dust-wave}), which differ only in the
+    stream velocity: \(v = \SI{40}{km.s^{-1}}\) (left panels) and
+    \SI{80}{km.s^{-1}} (right panels).  In both cases, the stream
+    density is \(n = \SI{1}{cm^{-3}}\) and the central star is a
+    \SI{10}{M_\odot} main-sequence B star (see Tab.~\ref{tab:stars}).
+    Upper panels show the evolution of grain radius, \(R\) (blue
+    curve, normalized by the rip point radius, \(R_\dag\)), and grain
+    velocity, \(v\) (orange curve, normalized by the gas stream
+    velocity).  The origin of the time axis is set to the moment of
+    closest approach of the grain to the star: \(R = \Rmin\).  Lower
+    panels show the trajectories in phase space: position versus
+    gas--grain relative slip velocity (\(w = \abs{v - v_\infty}\)).  Filled
+    contours show the net force on the grain: \(f\rad - f\drag\), with
+    positive values in blue and negative values in red.  The heavy
+    dotted line shows where there is no net force: \(f\rad = f\drag\).
+    The grain trajectory (thick, solid black line with arrows)
+    initially follows this line, but departs from it after the rip
+    point. In the left panel, the grain enters a limit cycle between
+    decoupling (rip) and re-coupling (snap back).  In the right panel,
+    the grain spirals in on the stagnant drift point.  See text for
+    further details.}
     \label{fig:phase-space-trajectories}
@@
 
+On the other hand, if \(d f\drag / d w < 0\) when
+\(w = \abs{v_\infty}\), then the equilibrium is unstable and no stagnant
+drift is possible.  This occurs for drag regime~IV, which applies when
+\(\phi > 1\) and
+\(\SI{10}{km.s^{-1}} < v_\infty < \SI{50}{km.s^{-1}}\).  There is also a
+second unstable regime (partially visible in the upper-right corner of
+Fig.~\ref{fig:drag-v-phi-plane}), which is related to the thermal peak
+in the electron Coulomb drag when \(\phi > 30\) and
+\(\SI{400}{km.s^{-1}} < v_\infty < \SI{2000}{km.s^{-1}}\), but this is not
+relevant to bow shocks around OB~stars.\footnote{%
+  It may apply in other contexts, such as outflows from AGN, since
+  detailed modeling of grain charging around quasars
+  \citep{Weingartner:2006a} implies that grain potentials as high as
+  \(\phi \sim 100\) can be achieved.} %
+
+Examples of the each of these two behaviors are illustrated in
+Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
+case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
+regime, resulting in periodic ``limit-cycle'' behavior (the parameters
+of this model correspond to the yellow ``plus'' symbol labeled ``40''
+in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
+grain's approach it initially follows an equilibrium drift phase
+trajectory (lower left panel) along the \(f\rad - f\drag = 0\)
+contour, with a very slight deceleration.  Then, when it reaches the
+rip point, \(R = R_\dag\), it suddenly experiences an unbalanced outward
+radiation force (blue region of phase space in
+Fig.~\ref{fig:phase-space-trajectories}). The grain's inward momentum
+carries it to the point \(R\min\), which is only slightly inside
+\(R_\dag\), before it is expelled at roughly twice the inflow speed.
+However, after moving outward, it finds itself in a drag-dominated
+region of phase space (red in the figure), and so recouples to the
+inflowing gas stream.  The recoupling is gradual at first, as the
+grain's outward motion is slowed and it begins to move inward again,
+but is completed suddenly once \(w\) falls below \SI{10}{km.s^{-1}} in
+what we term \textit{snap back}. The net result is the grain is back
+on the same phase track that it came in on, and so repeats the cycle
+indefinitely.
+
+The grain trajectory can be seen to follow a limit cycle, in which
+
 whether or not

### 2018-06-03 papers/Papers1234/sec-dust-bow-intro.tex
Write about the stagnant drift solution

@@
 
-Examples of the each of these two behaviors are illustrated in
+An examples of each of these two behaviors is illustrated in
 Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
@@
 in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
-grain's approach it initially follows an equilibrium drift phase
-trajectory (lower left panel) along the \(f\rad - f\drag = 0\)
-contour, with a very slight deceleration.  Then, when it reaches the
-rip point, \(R = R_\dag\), it suddenly experiences an unbalanced outward
-radiation force (blue region of phase space in
-Fig.~\ref{fig:phase-space-trajectories}). The grain's inward momentum
-carries it to the point \(R\min\), which is only slightly inside
-\(R_\dag\), before it is expelled at roughly twice the inflow speed.
-However, after moving outward, it finds itself in a drag-dominated
-region of phase space (red in the figure), and so recouples to the
-inflowing gas stream.  The recoupling is gradual at first, as the
-grain's outward motion is slowed and it begins to move inward again,
-but is completed suddenly once \(w\) falls below \SI{10}{km.s^{-1}} in
-what we term \textit{snap back}. The net result is the grain is back
-on the same phase track that it came in on, and so repeats the cycle
-indefinitely.
-
-The grain trajectory can be seen to follow a limit cycle, in which
-
-whether or not
-the incoming stream velocity lies in drag regime IV
-(Table~\ref{tab:fdrag-regimes}) with , which
-produces the unstable drift region identified in
-Figure~\ref{fig:gas-grain-drag-photoionized}.
+grain's first approach, it starts to follow a phase trajectory (lower
+left panel) along the \(f\rad - f\drag = 0\) contour, corresponding to
+equilibrium drift, in which the grain begins to move a few
+\si{km.s^{-1}} slower than the gas stream.  Then, when it reaches the
+rip point (\(R = R_\dag\), \(w \approx \SI{10}{km.s^{-1}}\)) it suddenly
+experiences a large unbalanced outward radiation force (blue region of
+phase space in Fig.~\ref{fig:phase-space-trajectories}). The grain's
+inward momentum carries it to the point \(\Rmin \approx 0.85 R_\dag\), before
+it is expelled at roughly twice the inflow speed.  However, after
+moving outward, it finds itself in a drag-dominated region of phase
+space (red in the figure), and so recouples to the inflowing gas
+stream.  The recoupling initiates gradually, as the grain's outward
+motion is slowed and it begins to move inward again, but is completed
+suddenly once \(w\) again falls below \SI{10}{km.s^{-1}}, in what we
+term \textit{snap back}. The net result is that the grain has returned
+to exactly the same phase track that it started in on, and so repeats
+the cycle indefinitely.
+
+The right panels of Figure~\ref{fig:phase-space-trajectories} show the
+case where the stream velocity is doubled to
+\(v_\infty = \SI{80}{km.s^{-1}}\), but all other parameters remain the
+same.  At this velocity, the equilibrium drift is stable and so the
+grain can achieve a stagnant drift solution, where it is stationary
+with respect to the star.  The trajectory during the first approach is
+similar to the previous case, except that the overshoot of the rip
+point is greater, so that \(\Rmin \approx 0.65 R_\dag\) in this case.  This is
+a consequence of the fact that the rip point is closer to the
+drag-free turnaround radius (\(R_\dag / R\star\star\) is not so small as in the
+lower velocity case), so that the grain inertia is relatively more
+important.  A second consequence is that the speed of the initial
+expulsion is not so large, being only a little higher than the inflow
+velocity (but opposite to it).  The qualitative difference between the
+two cases emerges after the first recoupling: instead of the snap back
+and endless limit cycle, the grain oscillates about the stagnant drift
+radius with ever decreasing amplitude, so that it has come almost to
+rest after a few oscillation periods.
 

### 2018-06-05 papers/Papers1234/sec-dust-bow-intro.tex
Add the bow radius versus density vertical cut

@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
-  \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
-    gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
-  \label{fig:decouple-v-n-plane}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/decouple-v40-versus-n}
-  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
-    showing bow radius and different regimes for a fixed inflow
-    velocity of \SI{40}{km.s^{-1}}.}
-  \label{fig:decouple-v40-versus-n}
-\end{figure}
+% \begin{figure}
+%   \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
+%   \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
+%     gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
+%   \label{fig:decouple-v-n-plane}
+% \end{figure}
 
@@
 a consequence of the fact that the rip point is closer to the
-drag-free turnaround radius (\(R_\dag / R\star\star\) is not so small as in the
-lower velocity case), so that the grain inertia is relatively more
-important.  A second consequence is that the speed of the initial
-expulsion is not so large, being only a little higher than the inflow
-velocity (but opposite to it).  The qualitative difference between the
-two cases emerges after the first recoupling: instead of the snap back
-and endless limit cycle, the grain oscillates about the stagnant drift
-radius with ever decreasing amplitude, so that it has come almost to
-rest after a few oscillation periods.
+drag-free turnaround radius (\(R_\dag / R\starstar\) is larger than in
+the lower velocity case), so that the grain inertia is relatively more
+important.  A second consequence of this is that the speed of the
+initial expulsion is not so large, being only a little higher than the
+inflow velocity.  The qualitative difference between the two cases
+emerges after the first recoupling: instead of the snap back and
+endless limit cycle, the grain oscillates about the stagnant drift
+radius with ever decreasing amplitude, so that after a few oscillation
+periods it has come to almost a complete rest.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/onaxis-stats-plot-MS10-v080-gra002}
+  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
+    showing bow radius and different regimes for a fixed inflow
+    velocity of \SI{80}{km.s^{-1}}.}
+  \label{fig:decouple-vertical-cut}
+\end{figure}
+
+\subsubsection{Back reaction on the gas flow}
+\label{sec:back-reaction-gas}
 

### 2018-06-05 papers/Papers1234/sec-dust-bow-intro.tex
Make a start on the back reaction section

@@
   \(w < \SI{2}{km.s^{-1}}\), but is less than 1\% even there.} %
-Results are shown in Figure~\ref{fig:drag-components}, where dashed lines correspond to direct solid body collisions and solid lines to electrostatic interactions.
-The latter depend on the grain potential, which is described in dimensionless terms by \(\phi\), which is the electrostatic potential
-energy of a unit charge at the surface of a grain of charge
-\(z\grain\) and radius \(a\), in units of the characteristic thermal
-energy of a gas particle:
+Results are shown in Figure~\ref{fig:drag-components}, where dashed
+lines correspond to direct solid body collisions and solid lines to
+electrostatic interactions.  The latter depend on the grain potential,
+which is described in dimensionless terms by \(\phi\), which is the
+electrostatic potential energy of a unit charge at the surface of a
+grain of charge \(z\grain\) and radius \(a\), in units of the
+characteristic thermal energy of a gas particle:
 \begin{equation}
@@
 Figure~\ref{fig:drift-gn}.
-
-\subsubsection{Existence conditions for dust waves}
-\label{sec:exist-cond-separ}
-
-In order for a separate dust wave to exist, it is necessary for the
-grains to decouple from the incoming gas stream before the stream hits
-the hydrodynamic bow shock caused by the stellar wind.  The radius of
-the rip point, \(R_\dag\), can be expressed in terms of \(R_*\), the
-fiducial optically thick bow shock radius introduced in
-\S~\ref{sec:strong-gas-grain}:
-\begin{equation}
-  \label{eq:Rdag-over-Rstar}
-  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
-\end{equation}
-where we have made use of equations~\eqref{eq:Rstar}
-and~\eqref{eq:Xi-Prad-over-Pgas}.  The wind bow shock radius is
-\(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]), where \(\eta\) is the
-wind momentum efficiency (eq.~[\ref{eq:wind-eta-typical}]).
-Therefore, the condition \(R_\dag > R_0\) becomes
-\begin{equation}
-  \label{eq:dust-wave-velocity-condition}
-  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
-\end{equation}
-For O stars, the wind efficiency is generally high (\(\eta > 0.1\)) and
-\(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
-exist when the stream velocity is very high
-(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
-can be much weaker (\(\eta < 0.01\)) and \(\Xi_\dag\) is also smaller, so
-that dust waves are permitted by this criterion for much lower stream
-velocities: (\(v_\infty > \SI{30}{km.s^{-1}}\)).
 
@@
 
+\subsubsection{Existence conditions for dust waves}
+\label{sec:exist-cond-separ}
+
+In order for a separate dust wave to exist, it is necessary for the
+grains to decouple from the incoming gas stream before the stream hits
+the hydrodynamic bow shock caused by the stellar wind.  The radius of
+the rip point, \(R_\dag\), can be expressed in terms of \(R_*\), the
+fiducial optically thick bow shock radius introduced in
+\S~\ref{sec:strong-gas-grain}:
+\begin{equation}
+  \label{eq:Rdag-over-Rstar}
+  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
+\end{equation}
+where we have made use of equations~\eqref{eq:Rstar}
+and~\eqref{eq:Xi-Prad-over-Pgas}.  The wind bow shock radius is
+\(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]), where \(\eta\) is the
+wind momentum efficiency (eq.~[\ref{eq:wind-eta-typical}]).
+Therefore, the condition \(R_\dag > R_0\) becomes
+\begin{equation}
+  \label{eq:dust-wave-velocity-condition}
+  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
+\end{equation}
+For O stars, the wind efficiency is generally high (\(\eta > 0.1\)) and
+\(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
+exist when the stream velocity is very high
+(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
+can be much weaker (\(\eta < 0.01\)) and \(\Xi_\dag\) is also smaller, so
+that dust waves are permitted by this criterion for much lower stream
+velocities: (\(v_\infty > \SI{30}{km.s^{-1}}\)).
+
 However, there are other conditions that need to be satisfied in order
@@
 
-Further restrictions on the existence of dust waves arise when the
-effects of magnetic fields are considered, as will be discussed in
+The combined effects of the three conditions are illustrated in
+Figure~\ref{fig:existence-dust-wave} for each of the three example
+main sequence stars from Table~\ref{tab:stars}.  Further restrictions
+on the existence of dust waves arise when the effects of magnetic
+fields are considered, as will be discussed in
 \S~\ref{sec:magn-effects-grain} below.
-
-\subsubsection{Grain trajectories along the symmetry axis}
-\label{sec:grain-traj-along}
-
-What happens to the dust grain following this catastrophic breakdown
-of gas--grain coupling depends on the relation between the rip point
-radius, \(R_\dag\), and the drag-free radiative turnaround radius,
-\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
-will still carry it in as far as \(R\starstar\) and the initial
-trajectory will be almost identical to that described in
-Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
-being turned around by the radiation field and pushed out past
-\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
-dragged back for a second approach.\footnote{If the initial impact
-  parameter of the trajectory is not strictly \(b = 0\), then the
-  resultant lateral component of \(f\rad\) will mean that \(b\) will
-  be much increased for the second approach.} %
-From equations~(\ref{eq:Rdag-over-Rstar},
-\ref{eq:Rstarstar-over-Rstar},
-\ref{eq:dust-wave-high-density-condition}), the condition
-\(R_\dag > R\starstar\) corresponds to
-\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
-lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
-on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
-by the gas carries the grain closer to the star than its inertia would
-naturally take it.  When the grain finally decouples at \(R_\dag\) it
-experiences a much higher unbalanced \(f\rad\), which can initially
-accelerate it to outward velocities significantly higher than the
-inflow velocity if \(R_\dag \ll R\starstar\).
 
@@
 
+\subsubsection{Grain trajectories along the symmetry axis}
+\label{sec:grain-traj-along}
+
+What happens to the dust grain following this catastrophic breakdown
+of gas--grain coupling depends on the relation between the rip point
+radius, \(R_\dag\), and the drag-free radiative turnaround radius,
+\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
+will still carry it in as far as \(R\starstar\) and the initial
+trajectory will be almost identical to that described in
+Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
+being turned around by the radiation field and pushed out past
+\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
+dragged back for a second approach.\footnote{If the initial impact
+  parameter of the trajectory is not strictly \(b = 0\), then the
+  resultant lateral component of \(f\rad\) will mean that \(b\) will
+  be much increased for the second approach.} %
+From equations~(\ref{eq:Rdag-over-Rstar},
+\ref{eq:Rstarstar-over-Rstar},
+\ref{eq:dust-wave-high-density-condition}), the condition
+\(R_\dag > R\starstar\) corresponds to
+\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
+lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
+on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
+by the gas carries the grain closer to the star than its inertia would
+naturally take it.  When the grain finally decouples at \(R_\dag\) it
+experiences a much higher unbalanced \(f\rad\), which can initially
+accelerate it to outward velocities significantly higher than the
+inflow velocity if \(R_\dag \ll R\starstar\).
+
 The post-decoupling behavior of the grain depends on the sign of
@@
 
+So far we have ignored the effect of the drag force on the gas stream
+itself, but it is clear that this must become important as \(\tau_*\)
+approaches \(\tau_{*,\text{max}})\), since that is the point where the
+dust wave transitions to a bow wave, in which the dust and gas are
+perfectly coupled.  A full treatment of this problem would require
+solving the hydrodynamic equations simultaneously with the equations
+of motion of the dust grains, which is beyond the scope of this paper.
+Instead, we outline a heuristic approach that qualitatively captures
+the physics involved.
+
+The maximum drag force experienced by a grain is at the rip point.
+Since the grain follows a zero-net-force phase track up until that
+point, this can be written with the help of
+equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0}) as
+\begin{equation}
+  \label{eq:fdrag-max}
+  f\drag (R_\dag) = f\rad(R_\dag) =   \frac{m\grain v_\infty^2 R\starstar}{ 2 R_\dag^2} 
+\end{equation}
+The timescale of the flow can be characterized by the crossing time
+\(R_\dag / v_\infty\), but the residence time of the grain at the bow apex
+will be several times larger than this (see previous section).  On the
+other hand, the average drag force during this residence will be
+several times smaller than the \(f\drag (R_\dag)\).
+Therefore, we introduce a dimensionless factor, \(\alpha\), which we expect to be of order unity, and write the total impulse imparted to the grain by drag as
+\begin{equation}
+  \label{eq:grain-impulse}
+  J\drag = \alpha f\drag (R_\dag) \frac{R_\dag}{v_\infty}
+  = \tfrac12 \alpha m\grain v_\infty \frac{R\starstar}{R_\dag} \ .
+\end{equation}
+
 \subsubsection{Magnetic effects on grain trajectories }

### 2018-06-05 papers/Papers1234/sec-dust-bow-intro.tex
Nearly finished the decoupling section

@@
 itself, but it is clear that this must become important as \(\tau_*\)
-approaches \(\tau_{*,\text{max}})\), since that is the point where the
+approaches \(\tau_{*,\text{max}}\), since that is the point where the
 dust wave transitions to a bow wave, in which the dust and gas are
@@
 other hand, the average drag force during this residence will be
-several times smaller than the \(f\drag (R_\dag)\).
-Therefore, we introduce a dimensionless factor, \(\alpha\), which we expect to be of order unity, and write the total impulse imparted to the grain by drag as
+several times smaller than \(f\drag (R_\dag)\) if
+\(R_\ddag > R_\dag\), which is typically the case.  We therefore parameterize
+our ignorance via a dimensionless factor, \(\alpha\), which we expect to be
+of order unity, and write the total impulse imparted to the grain by
+drag as
 \begin{equation}
   \label{eq:grain-impulse}
-  J\drag = \alpha f\drag (R_\dag) \frac{R_\dag}{v_\infty}
-  = \tfrac12 \alpha m\grain v_\infty \frac{R\starstar}{R_\dag} \ .
-\end{equation}
+  J\drag \equiv \int \!f\drag \, dt \approx \alpha f\drag (R_\dag) \frac{R_\dag}{v_\infty}
+  = \tfrac12 \alpha \, m\grain v_\infty \, \frac{R\starstar}{R_\dag} \ .
+\end{equation}
+
+By Newton's Third Law, an equal and opposite impulse is imparted to
+the gas, which will act to decelerate the gas stream as it decouples
+from the grains.  Realistically, \(J\drag\) should be summed over the
+grain size distribution, but for simplicity we assume that all grains
+are identical, so that the mass of gas that accompanies each grain is
+given by
+\begin{equation}
+  \label{eq:gas-mass}
+  m_{\text{gas}} = \frac{m\grain}{Z\grain} =  m\grain \, \frac{\kappa\grain}{\kappa} \ . 
+\end{equation}
+If the gas remains supersonic after decoupling, then thermal pressure
+can be ignored and the gas will suffer a change in momentum equal to
+\(J\drag\), so that its velocity is reduced by
+\(\Delta v = J\drag / m_{\text{gas}}\), which by
+equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
+\ref{eq:dust-wave-high-density-condition}, \ref{eq:grain-impulse},
+\ref{eq:gas-mass}) is
+\begin{equation}
+  \label{eq:gas-dv}
+  \Delta v = \tfrac12 \alpha \frac{\tau_*}{\tau_{*, \text{max}}} \ .
+\end{equation}
+This deceleration reduces the gas stream's ram pressure before it
+interacts with the central star's stellar wind.  The radius of the
+dust-free bow shock formed by this interaction is therefore increased
+by a factor \((1 - \Delta v / v_\infty)^{-1}\) with respect to the case
+calculated in \S~\ref{sec:three-bow-regimes}, yielding
+\begin{equation}
+  \label{eq:gas-free-bow-shock}
+  R_{\text{dfbs}} \approx \frac{\eta^{1/2} R_*}{1 - \tfrac12 \alpha \tau_* / \tau_{*, \text{max}}} \ .
+\end{equation}
+
+An example is illustrated in Figure~\ref{fig:decouple-vertical-cut},
+where the dust-free bow shock radius is shown by the green dashed line
+as a function of stream density, \(n\).  This is calculated for fixed
+stream velocity and grain and star properties, so that
+\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).  In order for
+\(R_{\text{dfbs}}\) to match the dust-wave and bow-wave radii at the
+point where they cross at \(\tau_* = \tau_{*, \text{max}}\), we find
+\(\alpha = 1.5\) is required.  It can be seen that the gas deceleration is
+negligible over most of the density range for which a separate dust
+wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does \(R_{\text{dfbs}}\) begin
+to curve up from the general \(n^{-1/2}\) trend, becoming essentially
+flat until the full-coupling point at \(n \approx \SI{3e4}{cm^{-3}}\)
 

### 2018-06-05 papers/Papers1234/sec-dust-bow-intro.tex
Write long caption for figure 10

@@
   \includegraphics[width=\linewidth]{figs/onaxis-stats-plot-MS10-v080-gra002}
-  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
-    showing bow radius and different regimes for a fixed inflow
-    velocity of \SI{80}{km.s^{-1}}.}
+  \caption{Bow radius as a function of stream density for a stream of
+    initial velocity \SI{80}{km.s^{-1}}, which interacts with a
+    \SI{10}{M_\odot} main-sequence B~star.  This corresponds to a vertical
+    slice through the left panel of
+    Fig.~\ref{fig:existence-dust-wave}.  At low densities, the
+    hydrodynamic bow shock (blue line) is larger than the drag-free
+    turnaround radius for small carbon grains, meaning that a grain's
+    inertia carries it into the bow shock along with the gas, even
+    though the gas--grain coupling is not particularly strong.  At
+    densities above about \SI{0.05}{cm^{-3}}, however, this is no
+    longer true and a separate dust wave forms outside of the
+    hydrodynamic bow shock, which is now dust-free (green dashed
+    line).  The grains in the dust wave will occupy a range of radii
+    (pale orange shading) between \(\Rmin\) (solid orange line) and
+    \(R_\ddag\), the stagnant drift radius.  At densities above about
+    \SI{1000}{cm^{-3}}, the gas stream starts to feel the effect of
+    passing through the dust wave, and above \SI{3e4}{cm^{-3}}, the
+    dust wave and bow shock merge to form a radiative bow wave (red
+    line), which becomes an optically thick radiative bow shock
+    (purple line) above \SI{e6}{cm^{-3}}.}
   \label{fig:decouple-vertical-cut}
@@
 negligible over most of the density range for which a separate dust
-wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does \(R_{\text{dfbs}}\) begin
-to curve up from the general \(n^{-1/2}\) trend, becoming essentially
-flat until the full-coupling point at \(n \approx \SI{3e4}{cm^{-3}}\)
+wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does
+\(R_{\text{dfbs}}\) begin to curve up from the general \(n^{-1/2}\)
+trend, becoming essentially flat at a value
+\(R_{\text{dfbs}} \approx (\kappa/\kappa\grain) R\starstar\) until full-coupling is
+established at \(n > \SI{3e4}{cm^{-3}}\).  Note, however, that the
+treatment described here is very approximate: it does not take into
+account the shock that will form once \(J\drag\) reaches an
+appreciable fraction of \(m_{\text{gas}} v_\infty\) and, additionally, it
+includes a factor, \(\alpha\), whose appropriate value is unclear.  More
+detailed modeling is required to fully understand the bow behavior in
+this transition regime.
 

### 2018-06-18 papers/Papers1234/sec-dust-bow-intro.tex
Start writing up the magnetic field part for dust wave paper

@@
     the left panel show where the rip point and the drag-free
-    turnaround radius coincide.  For dust waves below these lines,
-    drag forces are unimportant for the grains.  }
+    turnaround radius coincide.  Dust waves above these lines are drag
+    dominated, while dust waves below the lines are inertia dominated.
+  }
   \label{fig:existence-dust-wave}
@@
   be much increased for the second approach.} %
-From equations~(\ref{eq:Rdag-over-Rstar},
-\ref{eq:Rstarstar-over-Rstar},
+We will refer to this as an \textit{inertia-dominated dust wave}.  From
+equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
 \ref{eq:dust-wave-high-density-condition}), the condition
@@
 accelerate it to outward velocities significantly higher than the
-inflow velocity if \(R_\dag \ll R\starstar\).
+inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
+as a \textit{drag-dominated dust wave}.
 
@@
 
-An examples of each of these two behaviors is illustrated in
+An example of each of these two behaviors is illustrated in
 Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
@@
 point where they cross at \(\tau_* = \tau_{*, \text{max}}\), we find
-\(\alpha = 1.5\) is required.  It can be seen that the gas deceleration is
+\(\alpha \approx 1.5\) is required.  It can be seen that the gas deceleration is
 negligible over most of the density range for which a separate dust
@@
 appreciable fraction of \(m_{\text{gas}} v_\infty\) and, additionally, it
-includes a factor, \(\alpha\), whose appropriate value is unclear.  More
-detailed modeling is required to fully understand the bow behavior in
-this transition regime.
+includes a factor, \(\alpha\), whose value has not been rigorously
+justified.  More detailed modeling is required to fully understand the
+bow behavior in this transition regime.
 
@@
 \label{sec:magn-effects-grain}
+
+An important effect that we have not considered up to now is the
+Lorentz force on charged grains due to the plasma's magnetic field:
+\begin{equation}
+  \label{eq:f-lorentz}
+  \bm{f}\!\B = \frac{z\grain e}{c} \, \bm{w} \times \bm{B} \ . 
+\end{equation}
+The direction of the force is perpendicular both to the magnetic
+field, \(\bm{B}\), and to the relative velocity, \(\bm{w}\), of the
+grain with respect to the plasma.  If \(\bm{w}\) and \(\bm{B}\) (as
+seen by the grain) are changing slowly, compared with the
+gyrofrequency, \(\omega\B = z\grain e B / m\grain c\), then the grain
+motion perpendicular to \(\bm{B}\) is constrained to be a circle of
+radius equal to the Larmor radius:
+\begin{equation}
+  \label{eq:Larmor}
+  r\B = \frac{m\grain c w_\perp} {\abs{z\grain} e B} \ ,
+\end{equation}
+where \(B = \abs{\bm{B}}\) and \(w_\perp\) is the perpendicular component
+of \(\bm{w}\).  The component of \(\bm{w}\) parallel to \(\bm{B}\) is
+unaffected by \(\bm{f}\!\B\), so the resultant trajectory is helical.
+
+The relative importance of the magnetic field can be characterized by
+the ratio of the Larmor radius to the minimum radius, \(\Rmin\),
+reached by the grain in the dust wave (see
+\S~\ref{sec:grain-traj-along}), where \(\Rmin \approx R_\dag\) for
+drag-dominated dust waves, or \(\Rmin \approx R\starstar\) for
+inertia-dominated dust waves.  We write the field strength in terms of
+the Alfvén speed,
+\begin{equation}
+  \label{eq:alfven}
+  v\alfven = \frac{B}{(4\pi\rho\gas)^{1/2}} \ ,
+\end{equation}
+and the grain charge \(z\grain e\) in terms of the potential \(\phi\) (eq.~[\ref{eq:phi-potential}]) to obtain
+\begin{equation}
+  \label{eq:larmor-over-Rdag}
+  \frac{r\B}{R_\dag} = 0.0140 \,
+  a_{\si{\um}}^2 \,
+  \frac{w_\perp}{v\alfven} \,
+  \left( \frac{\Xi_\dag}{L_4 T_4} \right)^{1/2}
+  \frac{\rho\grain}{\phi_\dag}
+\end{equation}
+and
+\begin{equation}
+  \label{eq:larmor-over-Rstarstar}
+  \frac{r\B}{R\starstar} = 0.0544 \,
+  a_{\si{\um}}^3 \,
+  \frac{w_\perp}{v\alfven} \,
+  \frac{v_{10}^2 }{n^{1/2}} \,
+  \frac{1}{L_4 T_4} \,
+  \frac{\rho\grain^2}{\Qp \phi\starstar} \ ,
+\end{equation}
+where \(a_{\si{\um}} = a / \SI{1}{\um}\), \(\rho\grain\) is the grain
+material density in \si{g.cm^{-3}}, and we have made use of
+equations~(\ref{eq:Rstar-typical}, \ref{eq:Rdag-over-Rstar},
+\ref{eq:dust-r0}).
+
+If \(r\B / \Rmin \ll 1\), then the grains are so strongly coupled to the
+field that they can be treated in the guiding-center approximation, in
+which the trajectory is decomposed into a tight circular gyromotion
+around the field lines, plus a sliding of the guiding center
+along the field lines, which is governed by the radiation and drag
+forces (we ignore the slow \(\bm{f} \times \bm{B}\) drift across the field
+lines).  In the opposite limit, \(r\B / \Rmin \gg 1\), magnetic coupling
+is so weak that the results of the previous sections are scarcely
+modified.
 

### 2018-06-21 papers/Papers1234/sec-dust-bow-intro.tex
Write a bit more about the B fields

@@
     turnaround radius coincide.  Dust waves above these lines are drag
-    dominated, while dust waves below the lines are inertia dominated.
+    confined, while dust waves below the lines are inertia confined.
   }
@@
   be much increased for the second approach.} %
-We will refer to this as an \textit{inertia-dominated dust wave}.  From
+We will refer to this as an \textit{inertia-confined dust wave}.  From
 equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
@@
 inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
-as a \textit{drag-dominated dust wave}.
+as a \textit{drag-confined dust wave}.
 
@@
 \S~\ref{sec:grain-traj-along}), where \(\Rmin \approx R_\dag\) for
-drag-dominated dust waves, or \(\Rmin \approx R\starstar\) for
-inertia-dominated dust waves.  We write the field strength in terms of
+drag-confined dust waves, or \(\Rmin \approx R\starstar\) for
+inertia-confined dust waves.  We write the field strength in terms of
 the Alfvén speed,
@@
   \label{eq:alfven}
-  v\alfven = \frac{B}{(4\pi\rho\gas)^{1/2}} \ ,
+  v\alfven = \frac{B}{(4\pi\rho\gas)^{1/2}}
+  = 1.9\, \frac{B}{\si{\micro G}} n^{-1/2} \, \si{km.s^{-1}} \ ,
 \end{equation}
@@
 which the trajectory is decomposed into a tight circular gyromotion
-around the field lines, plus a sliding of the guiding center
-along the field lines, which is governed by the radiation and drag
-forces (we ignore the slow \(\bm{f} \times \bm{B}\) drift across the field
-lines).  In the opposite limit, \(r\B / \Rmin \gg 1\), magnetic coupling
-is so weak that the results of the previous sections are scarcely
-modified.
+around the field lines, plus a sliding of the guiding center along the
+field lines, which is governed by the radiation and drag forces (we
+ignore the slow \(\bm{f} \times \bm{B}\) drift across the field lines).  In
+the opposite limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak
+that the results of the previous sections are scarcely modified.
+Assuming \(w_\perp \sim v_\infty\) and adopting a threshold of
+\(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
+\ref{eq:larmor-over-Rstarstar}) can be transformed into conditions on
+the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
+will apply:
+\newcommand\freeze{\ensuremath{_{\text{tight}}}}
+\begin{equation}
+  \label{eq:velocity-strong-B-coupling}
+  v_{\infty} < v\freeze \approx
+  \begin{cases}
+    \text{drag-confined:}
+    & 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2}\\
+    \text{inertia-confined:}
+    & 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \\
+  \end{cases} \ ,
+\end{equation}
+where we have substituted typical values of the minor parameters
+\(\Xi_\dag\), \(\phi_{\dag}\), \(\phi_{**}\), \(\rho\grain\),
+\(T_4\).\footnote{%
+  The most significant systematic variation in \(v\freeze\) from these
+  suppressed parameters is due to grain composition, yielding slightly
+  higher values for graphite than for silicate (\SI{+-0.15}{dex}).} %
+It is apparent that \(v\freeze\) is very sensitive to the grain size.
+For instance, taking a typical \hii{} region value of
+\(v\alfven = \SI{2}{km.s^{-1}}\) \citep{Arthur:2011a} and
+\(L_4 = 0.63\) (Tab.~\ref{tab:stars}, B1.5~V star), then for the
+drag-confined case \(v\freeze \approx \SI{30}{km.s^{-1}}\) for \SI{0.2}{\um}
+grains but \(v\freeze \approx \SI{3000}{km.s^{-1}}\) for \SI{0.02}{\um}
+grains. Thus, for typical stream velocities of
+\SIrange{20}{100}{km.s^{-1}}, the small grains are always tightly
+coupled to the magnetic field, but the large grains are only loosely
+coupled for the faster streams.
+
+We now investigate how the results of the previous sections are
+modified by magnetic fields in the tight coupling limit.  For
+simplicity, we assume a uniform field in the incoming stream, with
+field lines oriented at an angle \(\theta\B\) to the velocity vector that
+defines the bow axis.  We also assume a super-alfvénic stream,
+\(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
+is unaffected, and take \(t_* \ll \tau_{*, \text{max}}\), so that the
+back-reaction of the grain drag on the plasma is negligible (see
+previous section) and \(B\) remains uniform in magnitude and direction
+in the dust wave region, outside of the bow shock.
 

### 2018-06-22 papers/Papers1234/app-dust-wave.tex
New figure of the perpendicular field case for the appendix
Write up analytic solution for thetaB=0 in appendix

@@
 recedes from the source along the same radius, reaching a velocity of
-\(+v_\infty\) at large distance.  For \(b > 0\), the trajectory,
-\(R\grain(\theta; b)\), is found\footnote{%
+\(+v_\infty\) at large distance.  Note that \(R\starstar\) as given by
+equation~\eqref{eq:dust-r0} is the equivalent of
+equation~\eqref{eq:rad:R0}, except for a single grain considered in
+isolation, rather than a well-coupled dusty plasma.
+
+For \(b > 0\), the trajectory, \(R\grain(\theta; b)\), is
+found\footnote{%
   The problem is formally identical to that of Rutherford scattering,
@@
 to be hyperbolic, characterized by an eccentricity,
-\(\varepsilon = \bigl( 1 + 4 b^2 / R\starstar^2\bigr)^{1/2}\), and polar angle of
-closest approach, \(\thm = \cos^{-1} \varepsilon^{-1}\).  The trajectory is
+\(\varepsilon = \bigl( 1 + 4 b^2 / R\starstar^2\bigr)^{1/2}\), and polar angle
+of closest approach, \(\thm = \cos^{-1} \varepsilon^{-1}\).  The trajectory is
 symmetrical about \(\thm\) and can be written as
@@
 both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\).
+
+\subsection{Tight magnetic coupling}
+\label{sec:tight-magn-coupl}
+
+As discussed in \S~\ref{sec:magn-effects-grain}, for small grains
+(\(a < \SI{0.1}{\um}\)) the Larmor magnetic gyration radius, \(r\B\)
+is typically small compared with other length scales of interest, and
+so the grains are effectively tied to the magnetic field lines.  In
+this approximation, we can calculate the grain dynamics in the
+drag-free limit using \(f\rad\) as the sole force as above, but this
+time allowing acceleration only along the field lines.  Assuming a
+uniform magnetic field, the only extra parameter needed is
+\(\theta\B\), the angle between the field direction and the direction of
+the dust stream (assumed to be plane parallel).  The radiation force
+will also produce an out-of-plane drift, given by
+\begin{equation}
+  \label{eq:perpendicular-drift}
+  \bm{v}_{\text{drift}} = \frac{c}{e z\grain} \, \frac{\bm{f}\!\rad \times \bm{B}}{B^2}
+  \ ,
+\end{equation}
+but from equations~(\ref{eq:Larmor}, \ref{eq:dust-rad-force},
+\ref{eq:dust-r0}) it follows that
+\begin{equation}
+  \label{eq:vdrift-over-vinfinity}
+  \frac{v_{\text{drift}}(R\starstar)}{v_\infty} = \frac{r\B}{2 R\starstar} \ ,
+\end{equation}
+so it is valid to ignore this drift in the limit of small \(r\B\).
+
+For \(\theta\B = 0\), the \(b = 0\) trajectory is identical to the
+non-magnetic case since the grain velocity and radiation force are
+both parallel to the field, which yields zero Lorentz force and zero
+\(\bm{f} \times \bm{B}\) drift. Therefore, the axial turnaround radius,
+\(R\starstar\), is still given by equation~\eqref{eq:dust-r0},
+whatever the value of \(r\B\).  For \(b > 0 \), \(f\rad\) has
+a component perpendicular to \(\bm{B}\), which will induce a helical
+gyromotion around the field lines, but the guiding center must move
+parallel to the axis if \(r\B \ll R\starstar\).  Thus, the guiding
+center motion can be found from conservation of potential plus kinetic
+energy in one dimension:
+\begin{equation}
+  \label{eq:parallel-energy-balance}
+  \frac{v^2}{v_\infty^2} + V\rad = 1 \ , 
+\end{equation}
+where \(V\rad\) is a suitably normalized radiation potential
+integrated along the field lines (\(x\) axis, where
+\(x = R \cos\theta = b \cot\theta\)):
+\begin{equation}
+  \label{eq:parallel-radiation-potential}
+  V\rad = R\starstar \int_x^\infty \frac{\cos\theta}{R^2}\, dx
+  = \frac{R\starstar\sin\theta}{b}
+  = \frac{R\starstar}{R} \ .
+\end{equation}
+From equation~\eqref{eq:parallel-energy-balance}, the trajectory must
+turn around when \(V\rad = 1\), and
+equation~\eqref{eq:parallel-radiation-potential} shows that this
+occurs at the same spherical radius, \(R = R\starstar\), for all
+impact parameters, \(b\), so that the inner boundary of the dust wave
+is hemispherical in shape:
+\begin{equation}
+  \label{eq:thB-0-shape}
+  \frac{R_{\text{in}}(\theta)} {R\starstar} = 1 \ ,
+\end{equation}
+with \(\Pi = \Lambda = 1\).  Note, however, that this only applies to
+streamlines with \(b \le R\starstar\).  For those with
+\(b > R\starstar\), the maximum \(V\rad\), which occurs at \(x = 0\),
+is smaller than unity, so that grains on these streamlines slow down
+as they go past the star, but then speed up again without turning
+round.
 
@@
 
+\textit{Do the analytic solution for parallel case.  Discuss perp case too - see figure.}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
+  \caption{Inertia-confined dust wave with perpendicular field}
+  \label{fig:inertia-thB90}
+\end{figure}
+
 First consider the limit of very small gyro-radius, which is the case

### 2018-06-22 papers/Papers1234/sec-dust-bow-intro.tex
Move the oscillating bows section to the observational paper
Write up analytic solution for thetaB=0 in appendix

@@
-\defcitealias{Tarango-Yong:2018a}{Paper~I}
-\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
-
 \section{Introduction}
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/bows-and-waves}
+  \includegraphics[width=0.8\linewidth]{figs/bows-and-waves}
   \caption{Bow shocks, bow waves, and dust waves}
@@
   corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
-at a distance \(R_0\) where
+at a distance \(R\starstar\) where
 \begin{equation}
   \label{eq:rad-poten}
-  \int_{R_0}^\infty a_{\text{rad}} \, dr = \tfrac12 v_\infty^2 \ , 
+  \int_{R\starstar}^\infty a_{\text{rad}} \, dr = \tfrac12 v_\infty^2 \ , 
 \end{equation}
@@
   \label{eq:rad:R0}
-  R_0 = \frac{\kappa L}{2\pi c v_\infty^2} \ .
+  R\starstar = \frac{\kappa L}{2\pi c v_\infty^2} \ .
 \end{equation}
@@
 In the optically thin limit, \(1 - e^{-\tau} \approx \tau\), so these two
-descriptions can be seen to agree so long as
+descriptions can be seen to agree (\(R_0 \to R\starstar\)) so long as
 \begin{equation}
@@
 radius can be written in terms of the fiducial radius as
-\(R_0 = x R_*\), where \(x\) is the solution of
+\begin{equation}
+  \label{eq:R0-definition}
+  R_0 = x R_* \ ,
+\end{equation}
+where \(x\) is the solution of
 \begin{equation}

### 2018-06-25 papers/Papers1234/app-dust-wave.tex
Add figure for the parallel inertia-confined dust wave

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/parallel-bfield-dust-wave-inertia}
+  \caption{Dust wave formed by action of radiation forces on grains
+    that are tightly coupled to a uniform parallel magnetic field.}
+  \label{fig:inertia-thB0}
+\end{figure}
+
 As discussed in \S~\ref{sec:magn-effects-grain}, for small grains
@@
 round.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
+  \caption{Dust wave formed by action of radiation forces on grains
+    that are tightly coupled to a uniform perpendicular magnetic
+    field.}
+  \label{fig:inertia-thB90}
+\end{figure}
+
+For \(\theta\B = \ang{90}\), the guiding center is forced to move at a
+constant speed in the \(x\) direction, so that \(x = -v_\infty t\), while
+the motion in the \(y\) direction obeys the ODE:
+\begin{equation}
+  \label{eq:ode-perp-bfield}
+  \frac{d^2 Y}{d X^2} = \frac{Y}{2 \left( X^2 + Y^2\right)^{3/2}} \ ,
+\end{equation}
+where \(X = x / R\starstar\) and \(Y = y / R\starstar\).  We have been
+unable to find an analytic solution to this equation, but a numerical
+solution is shown in Figure~\ref{fig:inertia-thB90}.
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
-  \caption{Inertia-confined dust wave with perpendicular field}
-  \label{fig:inertia-thB90}
-\end{figure}
-
 First consider the limit of very small gyro-radius, which is the case

### 2018-06-26 papers/Papers1234/app-dust-wave.tex
Finish text in appendix about inertia-confined dust waves

@@
 \end{equation}
-with a total deflection angle of \(2 \thm\), which is equal to
+with a total deflection angle of \(\ang{180} - 2 \thm\), which is equal to
 \ang{90} when \(b = 0.5 R\starstar\).
@@
   \caption{Dust wave formed by action of radiation forces on grains
-    that are tightly coupled to a uniform parallel magnetic field.}
+    that are tightly coupled to a uniform parallel magnetic field.
+    Two example trajectories, one with \(b > R\starstar\) (upper) and
+    one with \(b < R\starstar\) (lower) are shown schematically in
+    orange.  The orientation of the magnetic field lines is shown in
+    blue.  The grayscale image shows the resultant dust density
+    distribution.}
   \label{fig:inertia-thB0}
@@
 
+We now calculate in detail the grain trajectories in this limit for
+two cases, with the magnetic field oriented parallel and perpendicular
+to the stream\footnote{In both cases, the stream trajectories are
+  assumed parallel to one another, as in \S~\ref{sec:dust-parallel}.}
+direction, respectively. These are sufficient to give a flavor of the
+effects of a magnetic field on the dust wave structure.  Further
+models at intermediate angles, and which also include the effects of
+gas drag, are shown in \S~\ref{sec:magn-effects-grain}.
+
+\subsubsection{Parallel magnetic field}
+\label{sec:parall-magn-field}
+
 For \(\theta\B = 0\), the \(b = 0\) trajectory is identical to the
@@
 \end{equation}
-where \(V\rad\) is a suitably normalized radiation potential
-integrated along the field lines (\(x\) axis, where
+where \(V\rad\) is a suitably normalized potential of the projected
+radiation force along the field lines (\(x\) axis, where
 \(x = R \cos\theta = b \cot\theta\)):
@@
 
+The grain density of the inflowing stream follows from mass continuity as:
+\begin{equation}
+  \label{eq:thB-0-density}
+  n\grain(R) = \frac{n \bar{m} Z\grain}{m\grain} \left( 1 - R^{-1} \right)^{-1/2} \ ,
+\end{equation}
+where for simplicity we assume a single grain species of mass
+\(m\grain\) and dust-gas ratio \(Z\grain\). The outflowing stream has
+exactly the same velocity profile as the inflowing one, apart from a
+change of sign for those streamlines that turn round.  Therefore, in
+the region where the two streams co-exist (\(y \le R\starstar\),
+\(x > 0\), and \(R > R\starstar\)), the total density is double that
+given by equation~\eqref{eq:thB-0-density}.  This is illustrated in
+Figure~\ref{fig:inertia-thB0}.
+
+\subsubsection{Perpendicular magnetic field}
+\label{sec:perp-magn-field}
+
 \begin{figure}
@@
 unable to find an analytic solution to this equation, but a numerical
-solution is shown in Figure~\ref{fig:inertia-thB90}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/dust-coupling-1d}
-  \caption{Dust-gas coupling for an on-axis (purely radial)
-    trajectory.  (a)~Grain radial position, \(R/R\starstar\), gas--grain
-    velocity difference, \(w/v_\infty\), and local asymptotic drift
-    velocity, \(w\drift/v_\infty\), versus time for
-    \(\alpha\drag = 0.5\).  The behavior is typical of the dynamics of a
-    damped harmonic oscillator. (b)~Phase space (position, velocity)
-    trajectories for \(\alpha\drag = 0\), 0.5, and 2. All trajectories
-    begin in the lower right corner and evolve in a clockwise
-    direction. For \(\alpha\drag > 0\), the grain spirals in on the point
-    \((x, u) = (\alpha\drag^{-1}, 0)\).}
-  \label{fig:dust-coupling-1d}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/dust-couple-stream-annotate}
-  \caption{Dust grain trajectories under influence of gas drag in
-    addition to a repulsive central radiative force.  The dust
-    streamlines are shown as black lines with arrows and the dust
-    density as a linear gray scale, with maximum (black) of twice the
-    ambient dust density.  Results are shown for four values of the
-    drag parameter (see text): \(\alpha_\text{drag} = 0.25\), \(0.5\),
-    \(1.0\), and \(2.0\). The shape of the bow wave for the drag-free
-    case (Fig.~\ref{fig:dust-trajectories}) is shown by the thick
-    dotted line.  Faint patterns visible in the density away from the
-    bow wave are numerical aliasing artefacts caused by sparse
-    sampling of the streamlines in the low density regions.}
-  \label{fig:dust-wave-coupling}
-\end{figure*}
-
-\section{Toy model of dust wave with gas drag}
-\label{sec:bow-wave-drag}
-More realistically, a grain will also be subject to a drag force,
-\(f\drag\), due to its relative motion with respect to gas or plasma
-particles. If the gas density, velocity, and sound speed are
-\(\rho\gas\), \(v\gas\), and \(\soundspeed\), then a grain with velocity
-\(v\grain\) will experience a drag force that is directed opposite to
-the relative velocity, \(\bm{w} = \bm{v}\grain - \bm{v}\gas\).  In the
-supersonic limit, \(w \equiv \abs{\bm{w}} \gg \soundspeed\), the magnitude of
-the force is
-\begin{equation}
-  \label{eq:dust-fdrag}
-  \abs{f\drag} \approx Q\drag \xsec \rho\gas w^2 \ ,
-\end{equation}
-where \(Q\drag\) is an efficiency factor (which may be smaller or
-greater than unity) that accounts for details such as sticking
-probability and the boost in cross section due to the Coulomb force
-when a charged grain interacts with an ionized plasma
-\citep{Draine:1979a}.  We neglect the back reaction of the dust on the
-gas motion and assume a uniform background gas flow that is perfectly
-coupled to the incoming dust stream at large radii.  So, for the
-parallel stream case, we have \(\bm{v}\gas = -v_\infty \uvec{x}\) everywhere.
-
-Considering the incoming flow on the symmetry axis, at each radius
-there is an asymptotic gas--grain drift speed, \(w\drift\), for which
-the radiative and drag forces exactly cancel, \(f\drag = -\frad\),
-yielding
-\begin{equation}
-  \label{eq:dust-wdrift}
-  w\drift = \left( \frac{\Qp L} {4\pi c Q\drag \rho\gas R^2} \right)^{1/2} \ .
-\end{equation}
-Any deviation of \(w\) from \(w\drift\) produces unbalanced forces
-that tend to restore \(w \to w\drift\), although the grain inertia means
-that this will not happen instantaneously, so that if \(w\drift\)
-varies rapidly along a streamline, then changes in \(w\) will lag
-behind.  We define a dimensionless coupling coefficient,
-\(\alpha\drag\), to be the speed of the incoming stream in units of the
-drift velocity at the radiative turn-around radius:
-\begin{equation}
-  \label{eq:dust-alpha}
-  \alpha\drag \equiv \frac{v_\infty} {w\drift(R\starstar)} = \left(
-    Q\drag \frac{R\starstar / a\grain} {\rho\grain / \rho\gas}
-  \right)^{1/2} \ ,
-\end{equation}
-where we have used equation~\eqref{eq:dust-r0} and suppressed a
-grain-shape dependent geometric factor of order unity.  If
-\(\alpha\drag \ll 1\), then \(w\drift \gg v_\infty\) out to several times the
-turn-around radius, so the radiation field has no difficulty in
-effectively decoupling the grain from the gas and producing the
-velocity difference that is required to turn the grain around and
-expel it towards the direction whence it came (\(w = 2 v_\infty\)).
-However, for non-zero \(\alpha\drag\) the \(R^{-1}\) dependence of
-\(w\drift\) (eq.~\eqref{eq:dust-wdrift}) means that the grain will
-\textit{re-couple} to the inflowing gas stream around a radius
-\(\approx R\starstar / \alpha\drag \) and be swept back in again for another approach to
-the source.  A further effect of increasing \(\alpha\drag\) is that the
-grain penetrates closer to the star on its initial approach, thanks to
-the tail wind provided by the gas flow.  Both these behaviors are
-illustrated in Figure~\ref{fig:dust-coupling-1d}, where the inertial
-lag of \(w\) behind \(w\drift\) means that the phase space trajectory
-(panel b) is a spiral, which converges on the stagnation point
-\((R, v) = (R\starstar / \alpha\drag, 0)\). The cases \(\alpha\drag = 0.5\) and
-\(\alpha\drag = 2\) are shown, and it can be seen that with larger
-\(\alpha\drag\) the oscillations about the stagnation radius are
-significantly damped.
-
-However, this description only applies to grains with impact
-parameter, \(b\), that is exactly zero.  Even a very small finite
-\(b\) means that \(\frad\) has a component perpendicular to the axis,
-which pushes the grain to the side and means that, after re-coupling,
-its second approach is at a much larger impact parameter than its
-first, so it is dragged around the wings of the bow wave before it can
-bounce in and out more than twice.  This is illustrated in
-Figure~\ref{fig:dust-wave-coupling}, which shows grain trajectories
-and the resulting dust density structure, calculated from numerical
-integration of equations~\eqref{eq:dust-rad-force}
-and~\eqref{eq:dust-fdrag} in 2-D cylindrical coordinates.  Results are
-shown for a range of coupling parameters, \(\alpha\drag\).  The
-\(\alpha\drag = 0.25\) case appears qualitatively similar to the no-drag
-case shown in Figure~\ref{fig:dust-trajectories}a, except that the
-inner edge of the bow wave has been shifted to a smaller radius.
-Recoupling of the outgoing streamlines to the gas flow does occur
-eventually, but on length scales larger than shown in the figure. The
-\(\alpha\drag = 0.5\) case shows the oscillating trajectories discussed
-above for those grains that come in with a small initial impact
-parameter.  In the \(\alpha\drag = 1.0\) case, the oscillating trajectories
-are more confined, forming a thick shell around \(R\starstar\).  In the
-\(\alpha\drag = 2.0\) case, the shell is much thinner and concentrated at
-the inner rim.  As \(\alpha\drag\) increases, the oscillations are damped
-further so that the stagnation radius \(R\starstar / \alpha\drag\) becomes a good
-approximation to the apex radius of the density wave.  All the cases
-illustrated are for a parallel incident stream, but a divergent stream
-gives qualitatively similar behavior, as shown in
-Appendix~\ref{sec:equat-moti-grains}.  We propose the term
-\textit{dragoid} for the 3-dimensional shapes of the bow waves, found
-by rotating results such as Figure~\ref{fig:dust-wave-coupling} about
-the symmetry axis.
-
-\section{Dust wave with magnetic field}
-\label{sec:bow-wave-with}
-
-\newcommand\Larmor{\ensuremath{_{\text{L}}}}
-
-\textit{Do the analytic solution for parallel case.  Discuss perp case too - see figure.}
-
-First consider the limit of very small gyro-radius, which is the case
-when the Lorentz force is much larger than other forces acting on the
-grain. The grains will then follow tightly wound helical paths around
-the magnetic field lines, which can be decomposed into a circular
-motion of radius \(r\Larmor\) plus the motion if the \textit{guiding
-  center} along the field line.  The motion of the guiding center is
-explicitly followed by accounting for the components parallel to the
-field lines of the radiative and drag forces, whereas forces
-perpendicular to the field lines, which would only effect the circular
-motion are ignored in the first instance (but see \S~XXX below).
-
-\begin{figure}
-
-  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b15-z0000}
-  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b45-z0000}
-  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b75-z0000}
-  \caption{Grain trajectories for magnetised dust waves in the limit
-    of no gas drag and small gyro-radius. }
-  \label{fig:magnetic-dust-waves}
-\end{figure}
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-15}
-  \caption{xxx}
-  \label{fig:projected-magnetic-dust-waves-15}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-45}
-  \caption{xxx}
-  \label{fig:projected-magnetic-dust-waves-45}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-75}
-  \caption{xxx}
-  \label{fig:projected-magnetic-dust-waves-75}
-\end{figure*}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/dust-lorentz-stream-3d-turb-b90-L2000-Ma0100-Z+000}
-  \includegraphics[width=\linewidth]{figs/dust-lorentz-stream-3d-turbz-b90-L2000-Ma0100-Y+000}
-  \caption{Streamlines in three dimensions of resolved gyro-radius }
-  \label{fig:stream-3d}
-\end{figure}
-
-\subsection{Resolved Larmor radius}
-\label{sec:resolv-larm-radi}
-
-\section{Applicability of the dust wave models}
-\label{sec:dust-applicability}
-
-The apex turn-around radius, \(R\starstar\), of the bow wave depends on the
-grain properties via the combination \(\xsec \Qp / m\grain\).  For
-grains of size \(a\grain\) and internal density \(\rho\grain\), we have
-\(\xsec / m\grain \approx (a\grain \rho\grain)^{-1}\).  For radiation with
-wavelength smaller than the grain size, \(\lambda < a\grain\), the
-efficiency is \(\Qp \sim 1\), whereas for \(\lambda > a\grain\) it is
-\(\Qp \sim a\grain/\lambda\).  Therefore, we would expect \(R\starstar\) to be almost
-independent of grain size for small grains, but to vary as
-\(R\starstar \propto a\grain^{-1}\) for large grains, where small/large is relative
-to the peak wavelength of the radiation source.  In principle, a
-polydisperse population of grains could produce a blurring of the
-observed bow wave, but only if large grains contribute significantly
-to the dust emission.
-
-\TODO{Variation of \(\alpha\drag\) with grain size, charged grains.}
-
-\TODO{Lorentz force, Larmor radius}
-
-\TODO{Back-reaction on gas, \(\alpha\drag \to \infty\), recovery of drag-free
-  result for \(R_0\) but with increased effective grain mass.}
-
-\section{Apparent shapes of projected dragoids}
-\label{sec:dust-wave-apparent}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/test_xyprime_dragoid}
-  \caption{Apparent bow shapes in the plane of the sky for
-    parallel-stream dragoids as a function of inclination angle.  Drag
-    coefficient, \(\alpha\drag\) increases from top-left to bottom-right.
-    Inclination \(\abs{i}\) is shown in \ang{15} increments, indicated
-    by line color and thickness (see key).}
-  \label{fig:dragoid-xy-prime}
-\end{figure}
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/test_xyprime_div_dragoid}
-  \caption{As Fig.~\ref{fig:dragoid-xy-prime} but for divergent stream
-    dragoids.  Drag coefficient increases from top to bottom, while
-    degree of divergence increases from left to right. }
-  \label{fig:dragoid-div-xy-prime}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/dragoid-R90-vs-Rc}
-  \caption{Apparent projected shapes of dragoids in the
-    \(\Pi'\)--\(\Lambda'\) plane. Colored symbols indicate the
-    \(\abs{i} = 0\) position for selected models (see key).  Thin
-    lines show the inclination-dependent tracks of each model, with
-    tick marks along each track for 20 equal-spaced values of
-    \(\abs{\sin i}\). Gray shaded regions are as in
-    Fig.~\ref{Q-fig:quadric-projection-continued}a of \PaperI{}.  The
-    wilkinoid track is shown in white. }
-  \label{fig:dragoid-Rc-R90}
-\end{figure}
-
-\section{Shape and structure of bow waves}
-\label{sec:shape-bow-wave}
+solution is shown in Figure~\ref{fig:inertia-thB90}.  When the impact
+parameter is larger than \(b \sim R\starstar\), the trajectories are very
+similar to in the non-magnetic case
+(Fig.~\ref{fig:dust-trajectories}a).  As shown in
+Figure~\ref{fig:inertia-thB90}b, the interaction of the grain with the
+radiation field in this large-\(b\) regime can be approximated as an
+impulsive acceleration of magnitude \(\sim b^{-2}\) and duration
+\(\sim b\), producing a final \(y\) velocity of \(\sim b^{-1}\).  Since the
+\(x\) velocity is constant, the total deflection angle is also of
+order \(\sim b^{-1}\).  The overlap of the outgoing trajectories produces
+a dense concentration of grains at the inner edge, which is roughly
+parabolic in shape.  However, for \(b < R\starstar\) the remorseless
+advance of the magnetic field does not allow the grains to slow down
+and turn round, as they do in the non-magnetic and parallel-field
+cases.  As a result, no dense shell forms in the apex region, but
+instead there is a diffuse minimum in the density of grains around the
+star due to the high grain velocities reached there.  This means that
+the apparent morphology of a pure dust wave becomes very sensitive to
+the radial dependence of the grain emissivity.  If this is
+sufficiently steep, then the apex would coincide with the position of
+the star, although in practice the presence of a wind-supported bow
+shock, however small, will complicate the picture.
 

### 2018-06-26 papers/Papers1234/removed-dustwave-material.tex
Finish text in appendix about inertia-confined dust waves

--- 2017-11-21 papers/Paper1/app-dust-wave.tex
@@
-\section{Shape of a dusty radiative bow wave}
-\label{sec:shape-dust-wave}
-
-As an alternative to hydrodynamic or magnetohydrodynamic bow shocks,
-it is possible that some observed emission arcs may be bow waves due
-to the action of radiation pressure on dust grains.
-
-\begin{figure}
-  (a)\\
-  \includegraphics[width=\linewidth]{figs/dust-trajectories}
-  (b)\\
-  \includegraphics[width=\linewidth]{figs/dust-divergent}
-  \caption[Dust grain trajectories]{Dust grain trajectories under
-    influence of a repulsive central \(r^{-2}\) radiative force.
-    (a)~A parallel stream of dust grains approach from the right at a
-    uniform velocity and with a variety of impact parameters (initial
-    \(y\)-coordinate). The central source is marked by a red star at
-    the origin, and its radiative force deflects the trajectories into
-    a hyperbolic shape, each of which reaches a minimum radius marked
-    by a small black square.  The incoming hyperbolic trajectories are
-    traced in gray and the outgoing trajectories are traced in red.
-    The locus of closest approach of the outgoing trajectories is
-    parabolic in shape (traced by the thick, light gray line) and this
-    constitutes the inner edge of the bow wave.  (b)~The same but for
-    a divergent stream of dust grains that originates from a source on
-    the \(x\) axis at a distance \(D = 10 R_0\) from the origin.  In
-    this case, the inner edge of the bow wave is hyperbolic and the
-    parallel stream result is also shown for comparison.}
-  \label{fig:dust-trajectories}
-\end{figure}
-
-\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
-\newcommand{\grain}{\ensuremath{_{\text{d}}}}
-\newcommand{\xsec}{\ensuremath{\sigma\grain}}
-\newcommand\frad{\ensuremath{f_{\text{rad}}}}
-\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
-A dust grain of geometrical cross-section \(\xsec\) situated a
-distance \(R\) from a point source of radiation with luminosity \(L\)
-will experience a repulsive, radially directed radiative force
-\citep[e.g.,][]{Spitzer:1978a}
-\begin{equation}
-  \label{eq:dust-rad-force}
-  \frad = \frac{\xsec \Qp L} {4 \pi R^2 c} e^{-\tau}
-\end{equation}
-where \Qp{} is the frequency-averaged\footnote{%
-  Frequency averages of any quantity \(x\) should be understood as
-  weighted by the attenuated source spectrum:
-  \(\langle x \rangle_\nu = (L \, e^{-\tau})^{-1} \int_0^\infty x(\nu)\, L_\nu \, e^{-\tau_\nu} \, d\nu
-  \).  } %
-radiation pressure efficiency\footnote{%
-  For absorption efficiency \(Q_{\text{abs}}\), scattering efficiency
-  \(Q_{\text{scat}}\), and asymmetry parameter (mean scattering
-  cosine) \(g\), we have
-  \(\Qp = Q_{\text{abs}} + (1 - g) Q_{\text{scat}}\)
-  \citep[e.g., \S~4.5 of][]{Bohren:1983a}.} %
-of the grain, \(c\) is the speed of light, and \(\tau\) is the
-frequency-averaged optical depth between the source and the grain.
-For simplicity, we will consider only the optically thin case,
-\(\tau \to 0\).
-
-\subsection{Gas-free bow wave}
-\label{sec:gas-free-bow}
-
-If \(\frad\) is the only force experienced by the grain, then it will
-move on a \textit{ballistic} trajectory, determined by its initial
-speed at large distance, \(v_\infty\), and its impact parameter, \(b\).
-For \(b = 0\), the grain radially approaches the source with initial
-radial velocity \(-v_\infty\), which is decelerated to zero at the distance
-of closest approach, \(R_0\), given by energy conservation:
-\begin{equation}
-  \label{eq:dust-r0}
-  R_0 = \frac{\xsec \Qp L} {2 \pi c m\grain v_\infty^2} \ ,
-\end{equation}
-where \(m\grain\) is the grain mass.  The grain then turns round and
-recedes from the source along the same radius, reaching a velocity of
-\(+v_\infty\) at large distance.  For \(b > 0\), the trajectory,
-\(R\grain(\theta; b)\), is found\footnote{%
-  The problem is formally identical to that of Rutherford scattering,
-  or (modulo a change of sign) planetary orbits.  The method of
-  solution (via introduction of a centrifugal potential term and
-  reduction to a 1-dimensional problem) can be found in any classical
-  mechanics text \citep[e.g.,][\S~14]{Landau:1976a}.} %
-to be hyperbolic, characterized by an eccentricity,
-\(\varepsilon = \bigl( 1 + 4 b^2 / R_0^2\bigr)^{1/2}\), and polar angle of
-closest approach, \(\thm = \cos^{-1} \varepsilon^{-1}\).  The trajectory is
-symmetrical about \(\thm\) and can be written as
-\begin{equation}
-  \label{eq:dust-r-theta}
-  \frac{R\grain(\theta; b)} {R_0} = 
-  \frac{ \tfrac12 \bigl( \varepsilon^2 - 1 \bigr)} {\varepsilon \cos(\theta - \thm) - 1} \ , 
-\end{equation}
-with a total deflection angle of \(2 \thm\), which is equal to
-\(90^\circ\) when \(b = 0.5 R_0\).
-
-\subsubsection{Parallel dust stream}
-\label{sec:dust-parallel}
-
-If the incoming dust grains initially travel along parallel
-trajectories with varying \(b\), but the same \(v_\infty\), then deflection
-by the radiative force will form a bow wave around the radiation
-source, as shown in Figure~\ref{fig:dust-trajectories}.  However, the
-inner edge of the bow wave, \(R_{\text{in}}(\theta)\) is not given by the
-closest approach along individual trajectories, \(R\grain(\thm; b)\),
-but instead must found by minimizing \(R\grain(\theta; b)\) over all
-\(b\) for each value of \(\theta\), which yields
-\begin{equation}
-  \label{eq:dust-r-in}
-  \frac{R_{\text{in}}(\theta)} {R_0} = \frac{2}{1 + \cos\theta} \ .
-\end{equation}
-This is the polar form of the equation for the confocal parabola,
-which we have already discussed in detail in \PaperI{}'s
-\S~\ref{Q-sec:conic} and Appendix~\ref{Q-app:parabola}.  Its planitude
-and alatude are \(\Gamma = \Lambda = 2\) and these are unchanged under projection
-at any inclination.
-
-\subsubsection{Divergent dust stream}
-\label{sec:dust-divergent}
-
-If the dust grains are assumed to originate from a second point
-source, located at a distance \(D\) from the radiation source, then
-the incoming stream will be divergent instead of plane parallel.  The
-individual streamlines are not affected by this change and are still
-described by equation~\eqref{eq:dust-r-theta}, except that the
-trajectory axes for \(b > 0\) are no longer aligned with the global
-symmetry axis, so we must make the substitution
-\(\theta \to \theta + \theta_1(b)\), where \(\sin \theta_1 = b / D\) (see
-Fig.~\ref{Q-fig:crw-schema} of \PaperI{}). We parametrize the degree
-of divergence as \(\mu = R_0 / D\) and, as before,
-\(R\grain(\theta + \theta_1(b, \mu); b)\) is minimized over all trajectories to
-find the shape of the bow wave's inner edge.  This time, the result is
-a confocal hyperbola:
-\begin{equation}
-  \label{eq:dust-divergent-r-in}
-  \frac{R_{\text{in}}(\theta; \mu)} {R_0} = \frac{1 + \varepsilon_\mu}{1 + \varepsilon_\mu\cos\theta} \ ,
-\end{equation}
-where the eccentricity is (to first order in \(\mu\))
-\( \varepsilon_\mu = (1 - 2\mu)^{-1}\).  An example is shown in
-Figure~\ref{fig:dust-trajectories} for \(\mu = 0.1\).  Unsurprisingly,
-the resulting bow shape is more open than in the parallel stream case,
-increasingly so with increasing \(\mu\).  The planitude and alatude are
-both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\).
-
-\newcommand\drag{\ensuremath{_{\text{drag}}}}
-\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
-\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
-\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
-
 \begin{figure}
@@
 
-\subsection{Applicability of the bow wave models}
+\section{Dust wave with magnetic field}
+\label{sec:bow-wave-with}
+
+\newcommand\Larmor{\ensuremath{_{\text{L}}}}
+
+\textit{Do the analytic solution for parallel case.  Discuss perp case too - see figure.}
+
+First consider the limit of very small gyro-radius, which is the case
+when the Lorentz force is much larger than other forces acting on the
+grain. The grains will then follow tightly wound helical paths around
+the magnetic field lines, which can be decomposed into a circular
+motion of radius \(r\Larmor\) plus the motion if the \textit{guiding
+  center} along the field line.  The motion of the guiding center is
+explicitly followed by accounting for the components parallel to the
+field lines of the radiative and drag forces, whereas forces
+perpendicular to the field lines, which would only effect the circular
+motion are ignored in the first instance (but see \S~XXX below).
+
+\begin{figure}
+
+  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b15-z0000}
+  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b45-z0000}
+  \includegraphics[width=0.8\linewidth]{figs/dust-bfield-stream-b75-z0000}
+  \caption{Grain trajectories for magnetised dust waves in the limit
+    of no gas drag and small gyro-radius. }
+  \label{fig:magnetic-dust-waves}
+\end{figure}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-15}
+  \caption{xxx}
+  \label{fig:projected-magnetic-dust-waves-15}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-45}
+  \caption{xxx}
+  \label{fig:projected-magnetic-dust-waves-45}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-view-dust-bfield-75}
+  \caption{xxx}
+  \label{fig:projected-magnetic-dust-waves-75}
+\end{figure*}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/dust-lorentz-stream-3d-turb-b90-L2000-Ma0100-Z+000}
+  \includegraphics[width=\linewidth]{figs/dust-lorentz-stream-3d-turbz-b90-L2000-Ma0100-Y+000}
+  \caption{Streamlines in three dimensions of resolved gyro-radius }
+  \label{fig:stream-3d}
+\end{figure}
+
+\subsection{Resolved Larmor radius}
+\label{sec:resolv-larm-radi}
+
+\section{Applicability of the dust wave models}
 \label{sec:dust-applicability}
 
-The apex turn-around radius, \(R_0\), of the bow wave depends on the
+The apex turn-around radius, \(R\starstar\), of the bow wave depends on the
 grain properties via the combination \(\xsec \Qp / m\grain\).  For

### 2018-06-26 papers/Papers1234/app-dust-wave.tex
Finish the figure caption for perpendicular B field

@@
     that are tightly coupled to a uniform perpendicular magnetic
-    field.}
+    field.  (a)~Sample trajectories are shown by thin black lines and
+    the resultant dust density distribution in grayscale.  Two
+    parabolic fits to the inner edge of the dust wave in the wing
+    region (\(y > R\starstar\)) are shown. The orange line shows a
+    simultaneous fit to both wings, while the green line shows a fit
+    to a single wing, in which the parabola apex is not constrained to
+    lie on the axis.  The second fit has much smaller residuals,
+    indicating that the overall dust wave shape is ``pointier'' than a
+    parabola, but this is hard to quantify because the disappearance
+    of the dense shell in the apex region makes it impossible to
+    define \(R_0\) for the bow.  (b)~Trajectory parameters over a wide
+    range of impact parameters, shown on a log--log scale. Distances
+    are in units of \(R\starstar\), times in units of
+    \(R\starstar / v_\infty\), velocities in units of \(v_\infty\), and
+    accelerations in units of \(v_\infty^2 / R\starstar\). The grain's
+    acceleration along the \(y\) axis has a maximum value,
+    \(a_{\text{max}}\), which occurs at a position
+    \(x(a_{\text{max}}), y(a_{\text{max}})\), just before the grain is
+    swept past the star, with a duration (FWHM) of \(\Delta t\).  The
+    grain's asymptotic \(y\) velocity is \(v_{\text{final}}\) and the
+    fact that this closely tracks \(a_{\text{max}} \times \Delta t\) indicates
+    that the majority of the acceleration occurs in a sharp impulse.
+    The curves tend to straight lines at the right side of the graph,
+    which gives the asymptotic scaling relations discussed in the
+    text.}
   \label{fig:inertia-thB90}
@@
   \label{eq:ode-perp-bfield}
-  \frac{d^2 Y}{d X^2} = \frac{Y}{2 \left( X^2 + Y^2\right)^{3/2}} \ ,
+  \frac{d^2 y}{d x^2} = \tfrac12 R\starstar  \,
+  y \, \bigl( x^2 + y^2\bigr)^{-3/2} \ .
 \end{equation}
-where \(X = x / R\starstar\) and \(Y = y / R\starstar\).  We have been
-unable to find an analytic solution to this equation, but a numerical
-solution is shown in Figure~\ref{fig:inertia-thB90}.  When the impact
-parameter is larger than \(b \sim R\starstar\), the trajectories are very
-similar to in the non-magnetic case
+We have been unable to find an analytic solution to this equation, but
+a numerical solution is shown in Figure~\ref{fig:inertia-thB90}.  When
+the impact parameter is larger than \(b \sim R\starstar\), the
+trajectories are very similar to in the non-magnetic case
 (Fig.~\ref{fig:dust-trajectories}a).  As shown in

### 2018-06-26 papers/Papers1234/sec-dust-bow-discuss.tex
Finish long footnote on stellar wind models
And add a bit to a new section about observations of IR arcs in Carina
Add figure for drag-confined magnetic dust waves

--- 2017-11-20 papers/Paper1/sec-dust-bow-discuss.tex
@@
 \section{Summary and discussion}
+\label{sec:summary-discussion}
 
@@
 
+Justification for standing waves: Fig.~3 of \citet{Meyer:2016a} shows
+a time sequence of thin-shell instability, which looks a bit like a
+standing wave. But much larger amplitude than we are considering.
+
+Deviations from axisymmetry as an alternative to oscillations.
+
+\subsection{The case of inside-out bows}
+\label{sec:case-inside-out}
+
+So far, we have considered the case where the inner source dominates
+the radiation, while dust is present only in the outer stream, which
+applies to hot stars interacting with the ISM.  However, in the case
+of cool stars, the inner wind will also be dusty.  Examples are the
+red supergiant (RSG) phase of high-mass evolution, or the asymptotic
+giant branch (AGB) stage of low/intermediate-mass evolution.  In both
+these cases, it is still the inner source that provides the radiation
+field.  However, not all winds are radiatively driven and in those
+cases it is conceivable that it is the outer source that dominates the
+radiation field.  An example is the case of photoevaporating
+protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
+regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
+thermally driven photoevaporation flow \citep{HA:1998, Henney:1999a},
+while the outer stream is the stellar wind from an O~star
+\citep{Garcia-Arredondo:2001a}.
+
 %%% Local Variables:

### 2018-06-26 papers/Papers1234/sec-dust-bow-intro.tex
Add figure for drag-confined magnetic dust waves

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/frozen-stream-map-multi}
+  \caption{Drag-confined dust waves with tight magnetic coupling.
+    Upper panels show a quasi-parallel field, \(\theta\B = \ang{10}\),
+    while lower panels show a quasi-perpendicular field,
+    \(\theta\B = \ang{75}\).  Left panels show an incident stream velocity of
+    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels show
+    \(v_\infty = \SI{80}{km.s^{-1}}\).  In all cases, the stream density is
+    \(n = \SI{10}{cm^{-3}}\) and the calculations are performed for
+    small graphite grains, \(a = \SI{0.02}{\um}\), and the
+    \SI{10}{M_\odot} main-sequence B~star.  Continuous black lines show
+    grain trajectories, with triplets of colored symbols indicating
+    the progress of individual cohorts, which entered from the right
+    edge at a particular time.  Continuous blue lines show the
+    magnetic field, which flows from right to left along with the
+    incident stream.  The radius of the rip point, \(R_\dag\), and the
+    stagnant drift point, \(R_\ddag\), are shown respectively by red and
+    blue dashed lines.  The approximate shape of the wind-supported
+    bow shock is shown by the dotted gray line.  The calculations are
+    no longer valid after trajectories cross this surface.}
+  \label{fig:frozen-stream}
+\end{figure*}
+
 An important effect that we have not considered up to now is the
@@
 previous section) and \(B\) remains uniform in magnitude and direction
-in the dust wave region, outside of the bow shock.
-
-\section{The case of inside-out bows}
-\label{sec:case-inside-out}
-
-So far, we have considered the case where the inner source dominates
-the radiation, while dust is present only in the outer stream, which
-applies to hot stars interacting with the ISM.  However, in the case
-of cool stars, the inner wind will also be dusty.  Examples are the
-red supergiant (RSG) phase of high-mass evolution, or the asymptotic
-giant branch (AGB) stage of low/intermediate-mass evolution.  In both
-these cases, it is still the inner source that provides the radiation
-field.  However, not all winds are radiatively driven and in those
-cases it is conceivable that it is the outer source that dominates the
-radiation field.  An example is the case of photoevaporating
-protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
-regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
-thermally driven photoevaporation flow \citep{HA:1998, Henney:1999a},
-while the outer stream is the stellar wind from an O~star
-\citep{Garcia-Arredondo:2001a}.
+in the dust wave region, outside of the bow shock.  In
+Appendix~\ref{sec:tight-magn-coupl}, we derive results in the limit of
+zero gas--grain drag, which is appropriate for inertia-confined dust
+waves.
 

### 2018-06-26 papers/Papers1234/sec-dust-bow-intro.tex
Add figure with example magnetic trajectories

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/frozen-trajectories-multi}
+  \caption{Sample grain trajectories for drag-confined dust waves with
+    tight magnetic coupling.}
+  \label{fig:frozen-trajectories}
+\end{figure}
+
 An important effect that we have not considered up to now is the
@@
 zero gas--grain drag, which is appropriate for inertia-confined dust
-waves.
+waves, while in Figures~\ref{fig:frozen-stream}
+and~\ref{fig:frozen-trajectories} we show example results for
+drag-confined dust waves.
 

### 2018-06-29 papers/Papers1234/_region_.tex
Reorganize and expand existence condition part

@@
-\message{ !name(quadrics-bowshock.tex)}%\RequirePackage{amsmath}
-\documentclass[useAMS, usenatbib, a4paper]{mnras}
+\message{ !name(dusty-bow-wave.tex)}\documentclass[useAMS, usenatbib, a4paper]{mnras}
 \pdfsuppresswarningpagegroup=1
 
-% The following is needed to fix the margins if using Letter-size paper
-% REMOVE if your LaTeX uses A4 paper by default
-%\addtolength\topmargin{-1.8cm}
-
-% Standard LaTeX packages
-% \usepackage[varg]{txfonts}
 \usepackage{graphicx}
@@
 \usepackage{siunitx}
+\sisetup{separate-uncertainty = true}
 \usepackage{color}
@@
 \usepackage[varvw,smallerops]{newtxmath}
+
+\usepackage{chemgreek}
+\activatechemgreekmapping{newtx}
 
@@
 \robustify\itshape
+
+%% The following hack solves a problem with
+%% ERROR: \pdfendlink ended up in different nesting level than \pdfstartlink.
+%% See https://tex.stackexchange.com/a/249743
+\makeatletter
+\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
+  \errmessage{\noexpand\@combinedblfloats could not be patched}%
+}%
+\makeatother
 
@@
 
-% Definitions needed in abstract
-\newcommand\hii{\ion{H}{ii}}
-
-\title[Bow shock shapes]{True versus apparent shapes of bow shocks and bow waves}
+\title
+{Bow shocks, bow waves, and dust waves}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Tarango Yong \& Henney]{
-  Jorge A. Tarango Yong \& William J. Henney\\
+\author[Henney, Arthur, \& Tarango Yong]{
+  William J. Henney, S. Jane Arthur, \& Jorge A. Tarango-Yong\\
   \AddressCRyA
@@
 \pubyear{2017}
-
 \DeclareMathOperator{\sgn}{sgn}
@@
 \providecommand{\abs}[1]{\lvert#1\rvert}
+\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
+\newcommand\TODO[1]{%
+  \begin{center}
+    \framebox{\parbox{0.8\linewidth}{
+        \texttt{\footnotesize\color{red} #1}}}
+  \end{center}}
+
+\newcommand\uvec[1]{\bm{\hat{#1}}}
+\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+
+\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
+\newcommand{\grain}{\ensuremath{_{\text{d}}}}
+\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
+\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
+\newcommand{\xsec}{\ensuremath{\sigma\grain}}
+\newcommand\frad{\ensuremath{f_{\text{rad}}}}
+\newcommand\fmax{\ensuremath{f_{\text{max}}}}
+\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
+\newcommand\drag{\ensuremath{_{\text{drag}}}}
+\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
+\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
+\newcommand\rad{\ensuremath{_{\text{rad}}}}
+\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
+% Why do I need both of these?
+\newcommand\sound{\ensuremath{c_{\text{s}}}}
+\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
+\newcommand\starstar{\ensuremath{_{**}}}
+
+\defcitealias{Tarango-Yong:2018a}{Paper~I}
+\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
 
@@
 
-\message{ !name(app-shape-parameters.tex) !offset(-107) }
+\message{ !name(sec-dust-bow-intro.tex) !offset(-112) }
 
-\section{Analytic derivation of thin-shell bow shapes}
-\label{sec:thin-shell-shapes}
+\section{Introduction}
+\label{sec:introduction}
+\newcommand\hii{\ion{H}{ii}}
 
-In this appendix, we provide analytic calculations of the planitude
-(exact) and alatude (approximate) for the wilkinoid, cantoids, and
-ancantoids.  We first consider the most general case of the
-ancantoids, and then show how results for cantoids and the wilkinoid
-follow as special cases.
+Curved emission arcs around stars \citep[e.g.,][]{Gull:1979a} are
+often interpreted as \textit{bow shocks}, due to a supersonic
+hydrodynamic interaction between the star's wind and an external
+stream. This stream may be due to the star's own motion or to an
+independent flow, such as an \hii{} region in the champagne phase
+\citep{Tenorio-Tagle:1979a}, or another star's wind
+\citep{Canto:1996}. However, an alternative interpretation in some
+cases may be a radiation-pressure driven bow wave, as first proposed
+by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
+emitted by the star are absorbed by dust grains in the incoming
+stream, with the resultant momentum transfer being sufficient to
+decelerate and deflect the grains within a certain distance from the
+star, forming a dust-free, bow-shaped cavity with an enhanced dust
+density at its edge.  Two regimes are possible, depending on the
+strength of coupling between the gas (or plasma) and the dust.  In the
+strong-coupling regime, gas--grain drag decelerates the gas along with
+the dust, forming a shocked gas shell in a similar fashion to the
+wind-driven bow shock case.  In the weak-coupling regime, the gas
+stream is relatively unaffected and the dust temporarily decouples to
+form a dust-only shell.  This second case has recently been studied in
+detail in the context of the interaction of late O-type stars (which
+have only weak stellar winds) with dusty photoevaporation flows inside
+\hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
+  Ochsendorf:2015a}.  We follow the nomenclature proposed by
+\citet{Ochsendorf:2014b}, in which \textit{dust wave} refers to the
+weak coupling case and \textit{bow wave} to the strong coupling case.
+More complex, hybrid scenarios are also possible, such as that studied
+by \citet{van-Marle:2011a}, where a hydrodynamic bow shock forms, but
+the larger dust grains that accompany the stellar wind pass right
+through the shocked gas shell, and form their own dust wave at a
+larger radius.
 
-\subsection{Planitude of ancantoids}
-\label{sec:ancantoid-planitude}
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{figs/bows-and-waves}
+  \caption{Bow shocks, bow waves, and dust waves}
+  \label{fig:3-types-bow}
+\end{figure*}
 
-From equations~\eqref{eq:radius-curvature} and~\eqref{eq:planitude},
-the planitude depends on the apex second derivative,
-\(R_{\theta\theta,0}\), as
+In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
+new two-dimensional classification scheme for bow shapes: the
+projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
+measures the flatness of the bow's apex, while alatude measures the
+openness of the bow's wings.  Both are dimensionless ratios of lengths
+that can be estimated from observational images.  We have analyzed the
+inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
+geometric shapes (spheroids, paraboloids, hyperboloids) and for
+thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
+ancantoids).  In this paper, we will do the same for simple models of
+radiation-driven dust waves (dragoids) and bow waves (trapoids).
+
+The paper is organized as follows.
+%
+In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
+dusty radiation bow wave (dragoids), including the effects of
+gas-grain drag.
+%
+In \S~\ref{sec:perturbed-bows} we investigate the effects on the
+planitude--alatude plane of small-amplitude perturbations to the bow
+shape.
+%
+
+\section{Different types of bow}
+\label{sec:different-types-bow}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
+  \caption{Bow regimes in parameter space (\(v, n\)) of the external
+    stream for main-sequence OB stars of different masses:
+    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}.  In all
+    cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
+    coupling is assumed. Solid black lines of varying width show the
+    bow size (star-apex separation, \(R_0\)), while gray shading shows
+    the radiation bow wave regime, with lower border \(\tau = \eta\) and
+    upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
+    depth through the bow.  For bows above the red solid line, the
+    ionization front is trapped inside the bow.  Blue lines delineate
+    different cooling regimes.  Above the thin blue line
+    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
+    forming a thin shocked shell.  Below the thick blue line
+    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
+    non-radiative.}
+  \label{fig:zones-v-n-plane}
+\end{figure*}
+
+In this section, we investigate the different types of bow interaction
+that will occur in different regions of parameter space. We will
+mainly treat the canonical case\footnote{%
+  Variant cases with differing arrangements of dust and radiation
+  sources are treated in \S~\ref{sec:case-inside-out}.} %
+of a bow around a star of bolometric luminosity, \(L\), with a
+radiatively driven wind, which is immersed in an external stream of
+gas and dust with density, \(\rho\), and velocity, \(v\).  The size and
+shape of the bow is determined by a generalized balance of pressure
+(or, equivalently, momentum) between internal and external sources.
+We assume that the stream is supersonic and super-alfvenic, so that
+the external pressure is dominated by the ram pressure: \(\rho v^2\).
+
+\subsection{Strong gas-grain coupling}
+\label{sec:strong-gas-grain}
+
+We first consider the case where the dust grains and gas are perfectly
+coupled by collisions.\footnote{%
+  Cases where this assumption does not hold are investigated below in
+  \S~\ref{sec:imperf-coupl-betw}.} %
+Although dust grains typically constitute only a small fraction
+\(Z\grain \sim 0.01\) of the mass of the external stream, they
+nevertheless dominate the broad-band opacity at FUV, optical and IR
+wavelengths if they are present.\footnote{%
+  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
+  dominates if the hydrogen neutral fraction is larger than
+  \(\approx 0.001\), see discussion of ionization front trapping
+  below.} %
+The strong coupling assumption means that all the radiative forces
+applied to the dust grains are directly felt by the gas also.
+
+\subsubsection{Bows supported by radiation and wind}
+\label{sec:three-bow-regimes}
+
+The internal pressure is the sum of wind ram pressure and the
+effective radiation pressure that acts on the bow shell.  The
+radiative momentum loss rate of the star is \(L/c\) and the wind
+momentum loss rate can be expressed as
 \begin{equation}
-  \label{eq:planitude-from-2nd-derivative}
-  \Pi = \left(  1 - R_{\theta\theta,0} / R_0\right)^{-1} \ .
+  \label{eq:wind-efficiency}
+  \dot{M} V = \eta L / c \ , 
 \end{equation}
-From equation~\eqref{eq:taylor-R-theta}, the second derivative can be
-found from the coefficient of \(\theta^2\) in the Taylor expansion
-of \(R(\theta)\).  Since we do not have \(R(\theta)\) in explicit analytic form,
-we proceed via a Taylor expansion of the implicit
-equations~\eqref{eq:crw-angles}
-and~\eqref{eq:ancantoid-theta-theta1-implicit}, retaining terms up to
-\(\theta^4\) to obtain from
-equation~\eqref{eq:ancantoid-theta-theta1-implicit}:
+where \(\eta\) is the momentum efficiency of the wind, which is typically
+\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
+all of the stellar radiative momentum, emitted with rate \(L/c\), is
+trapped by the bow shell.  In the single scattering limit,\footnote{%
+  Although it may seem inconsistent to assume single scattering in the
+  case of high optical depths, this is defensible for the following
+  reasons. (1)~The grain albedo is not that high (typically
+  \(\sim 0.5\) at ultraviolet through optical wavelengths). (2)~The
+  scattered radiation field is more isotropic than the stellar field,
+  leading to cancellation in the radiative
+  flux. (3)~Absorbed radiation is re-emitted at infrared
+  wavelengths, where the dust opacity is very much lower.} %
+and temporarily neglecting the wind, then pressure balance at the bow
+apex, a distance \(R_0\) along the symmetry axis from the star is
+given by
 \begin{equation}
-  \label{eq:taylor-expansion-implicit}
-  \theta_1^2 = \beta \theta^2 \left( 1 + C_{k\beta} \theta^2\right) + \mathcal{O}(\theta^6)\ , 
+  \label{eq:rad-press-balance-thick}
+  \frac{L}{4 \pi c R_0^2} = \rho v^2 \ ,
 \end{equation}
-with the coefficient \(C_{k\beta}\) given by
+which yields a fiducial bow shock radius in this optically thick limit
+as
 \begin{equation}
-  \label{eq:C-k-beta}
-  C_{k\beta} = \frac{1}{15} - \frac{3k}{20} - \frac{\beta}{15}  \ .
-\end{equation}
-Note that it is necessary to include the \(\theta^4\) term in the expansion
-of \(\theta_1^2\) so that \(\theta_1/\theta\) is accurate to order
-\(\theta^2\).  Then, from equation~\eqref{eq:crw-angles} we find
-\begin{align}
-  \label{eq:taylor-R-over-D}
-  \frac{R}{D} & = \frac{\sin \theta_1} {\sin (\theta + \theta_1)} \nonumber \\
-              & = \frac{\beta^{1/2}}{1+\beta^{1/2}}
-                \left\lbrace 1 + \theta^2
-                \left[ \frac{C_{k\beta}} {2 \left(1+\beta^{1/2}\right)}
-                + \frac{1}{6} \left(1+2\beta^{1/2} \right)
-                \right]
-                \right\rbrace + \mathcal{O}(\theta^4) \ ,
-\end{align}
-where in the second line we have carried out a Taylor expansion of the
-two \(\sin\) terms and substituted
-\eqref{eq:taylor-expansion-implicit}.  Comparing coefficients of unity
-and \(\theta^2\) between equations~\eqref{eq:taylor-R-theta} and
-\eqref{eq:taylor-R-over-D} we find
-\begin{align}
-  \label{eq:again-R0-over-D}
-  \frac{R_0} {D} &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
-  \label{eq:final-second-derivative}
-  \frac{R_{\theta\theta,0}} {R_0} &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{3}\left(1+2\beta^{1/2}\right) \ ,
-\end{align}
-so that the final result for the planitude, from~\eqref{eq:planitude-from-2nd-derivative}, is
-\begin{equation}
-  \label{eq:final-planitude}
-  \text{ancantoid} \quad
-  \Pi = \left[ {1 - \frac{C_{k\beta}}{1+\beta^{1/2}} - \frac{1}{3}\left(1+2\beta^{1/2}\right)}
-  \right]^{-1} \ .
+  \label{eq:Rstar}
+  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
 \end{equation}
 
-\subsection{Alatude of ancantoids}
-\label{sec:ancantoid-alatude}
+We now consider the opposite, optically thin limit.  If the total
+opacity (gas plus dust) per total mass (gas plus dust) is \(\kappa\) (with
+units of \si{cm^2.g^{-1}}), then the radiative acceleration is
+\begin{equation}
+  \label{eq:rad-accel}
+  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ .
+\end{equation}
+Therefore, an incoming stream with initial velocity, \(v_\infty\), can be
+brought to rest by radiation alone\footnote{%
+  For simplicity, we here ignore the effects of gravity, which are
+  important for low ratios of \(\kappa L / M\), see
+  \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
+  shocks, which are important as the velocity approaches the sound
+  speed, \(\sound\) (in \S~XX below, we show that the resultant
+  corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
+at a distance \(R\starstar\) where
+\begin{equation}
+  \label{eq:rad-poten}
+  \int_{R\starstar}^\infty a_{\text{rad}} \, dr = \tfrac12 v_\infty^2 \ , 
+\end{equation}
+yielding
+\begin{equation}
+  \label{eq:rad:R0}
+  R\starstar = \frac{\kappa L}{2\pi c v_\infty^2} \ .
+\end{equation}
+On the other hand, we can also argue as in the optically thick case
+above by approximating the bow shell as a surface, and balancing
+stellar radiation pressure against the ram pressure of the incoming
+stream.  The important difference when the shell is not optically
+thick is that only a fraction \(1 - e^{-\tau}\) of the radiative momentum
+is absorbed by the bow, so that
+equation~\eqref{eq:rad-press-balance-thick} is replaced with
+\begin{equation}
+  \label{eq:rad-press-balance-tau}
+  \frac{L (1 - e^{-\tau})}{4 \pi c R_0^2} = \rho v^2 \ .
+\end{equation}
+In the optically thin limit, \(1 - e^{-\tau} \approx \tau\), so these two
+descriptions can be seen to agree (\(R_0 \to R\starstar\)) so long as
+\begin{equation}
+  \label{eq:tau-thin}
+  \tau = 2 \kappa \rho R_0 \ ,
+\end{equation}
+which we will assume to hold generally.
 
-To find the alatude, \(\Lambda = R_{90} / R_0\), we use equation~\eqref{eq:crw-angles} at \(\theta = 90^\circ\) to write
+Then, defining a fiducial optical depth,
 \begin{equation}
-  \label{eq:Lambda-from-theta-1-90}
-  \Lambda = \frac{D} {R_0} \tan \theta_{1,90} \ , 
+  \label{eq:tau-star}
+  \tau_* = \rho \kappa R_* \ ,
 \end{equation}
-where \(\theta_{1,90} = \theta_1(\theta = 90^\circ)\), which, following
-equation~\eqref{eq:ancantoid-theta-theta1-implicit}, must satisfy
+and adding in the stellar wind ram pressure\footnote{%
+  We implicitly assume that the interaction of the stellar wind with
+  the external stream can always be treated in the continuum limit.
+  This will be true if either the collisional mean free path or the
+  ion Larmor radius is much smaller than \(R_0\), which is almost
+  always the case.} %
+from equation~\eqref{eq:wind-efficiency}, we find that the general bow
+radius can be written in terms of the fiducial radius as
 \begin{equation}
-  \label{eq:theta-1-90-implicit}
-  \theta_{1,90} \cot \theta_{1,90}  = 1 - \frac{2 \beta}{k + 2} \ . 
+  \label{eq:R0-definition}
+  R_0 = x R_* \ ,
 \end{equation}
-Combining \eqref{eq:Lambda-from-theta-1-90} and
-\eqref{eq:theta-1-90-implicit} with \eqref{eq:again-R0-over-D} yields
+where \(x\) is the solution of
 \begin{equation}
-  \label{eq:Lambda-beta-xi-theta-1-90}
-  \Lambda = \frac{ \left(1 + \beta^{1/2}\right) \,\theta_{1,90}} {\beta^{1/2} \left(1 - \xi_k \beta\right)} \ ,
+  \label{eq:rad-full-x}
+  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta = 0 \ .
+\end{equation}
+Since this is a transcendental equation, \(x\) must be found
+numerically, but we can write explicit expressions for three limiting
+cases:
+\begin{equation}
+  \label{eq:x-cases}
+  x \approx
+  \begin{cases}
+    \text{if \(\tau_* \gg 1\):} & (1 + \eta)^{1/2}  \\
+    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta \bigr)^{1/2} \approx
+    \begin{cases}
+      \text{if \(\tau_*^2 \gg \eta\):} & 2 \tau_*  \\
+      \text{if \(\tau_*^2 \ll \eta\):} & \eta^{1/2} 
+    \end{cases}
+  \end{cases}
+\end{equation}
+The first case, \(x \approx (1 + \eta)^{1/2}\), corresponds to a
+\textit{radiation bow shock}; the second case,
+\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave}; and the
+third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow shock}.
+The two bow shock cases are similar in that the external stream is
+oblivious to the presence of the star until it suddenly hits the bow
+shock shell, differing only in whether it is radiation or wind that is
+providing the internal pressure.  In the intermediate bow wave case,
+on the other hand, the external stream is gradually decelerated by
+absorption of photons as it approaches the bow.\footnote{A shock does
+  still form in this case, but shocked material constitutes only a
+  fraction of the total column density of the shell, see
+  \S~\ref{sec:shape-bow-wave}.}
+
+\begin{table*}
+  \centering
+  \caption{Stellar parameters for example stars}
+  \label{tab:stars}
+  \begin{tabular}{l S S S S S S S S S l}
+    \toprule
+    & {\(M / \si{M_\odot}\)} & {\(L_4\)}
+    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta \)}
+    & {Sp.~Type} 
+    & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
+    & {\(S_{49}\)} & Figures 
+    \\
+    \midrule
+    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
+                   & \ref{fig:zones-v-n-plane}a,
+                     \ref{fig:decouple-v-n-plane},
+                     \ref{fig:decouple-v40-versus-n} \\
+    Main-sequence OB stars
+    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
+                   & \ref{fig:zones-v-n-plane}b\\
+    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
+                   & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
+    Blue supergiant star
+    & 33 & 30.2 & 20.2 & 0.93 & 0.3079 & {B0.7\,Ia} & 23.5 & 0.123 & 0.016
+                   & \ref{fig:B-supergiant} \\[\smallskipamount]
+    Red supergiant star
+    & 20 & 15.6 & 100 & 0.015 & 0.0476 & {M1\,Ia} & 3.6 & 0.805 & 0
+                   & \ref{fig:M-supergiant} \\ 
+    \bottomrule
+  \end{tabular}
+\end{table*}
+
+We now consider the application to bow shocks around main sequence OB
+stars, expressing stellar and ambient parameters in terms of typical
+values as follows:
+\begin{align*}
+  \label{eq:stellar-parameters}
+  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
+  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
+  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
+  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
+  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
+  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
+\end{align*}
+where \(\bar{m}\) is the mean mass per hydrogen nucleon
+(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
+abundances).  Note that \(\kappa = \SI{600}{cm^2.g^{-1}}\) corresponds to a
+cross section of \(\approx \SI{e-21}{cm^2}\) per hydrogen nucleon, which is
+typical for interstellar medium dust \citep{Bertoldi:1996a} at far
+ultraviolet wavelengths, where OB stars emit most of their radiation.
+In terms of these parameters, we can express the stellar wind momentum
+efficiency as
+\begin{equation}
+  \label{eq:wind-eta-typical}
+  \eta = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
+\end{equation}
+and the fiducial radius and optical depth as
+\begin{align}
+  \label{eq:Rstar-typical}
+  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
+  \label{eq:taustar-typical}
+  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
+\end{align}
+In Figure~\ref{fig:zones-v-n-plane}, we show results for the bow size
+(apex distance, \(R_0\)) as a function of the density, \(n\), and
+relative velocity, \(v_\infty\), of the external stream, with each panel
+corresponding to a particular star, with parameters as shown in
+Table~\ref{tab:stars}.  To facilitate comparison with previous work,
+we choose stellar parameters similar to those used in the
+hydrodynamical simulations of \citet{Meyer:2014b, Meyer:2016a,
+  Meyer:2017a}, based on stellar evolution tracks for stars of
+\SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and theoretical wind
+prescriptions \citep{de-Jager:1988a, Vink:2000a}.  Although the
+stellar parameters do evolve with time, they change relatively little
+during the main-sequence lifetime of several million years.\footnote{%
+  \label{fn:meyer-velocities-too-low}
+  Note that we have recalculated the stellar wind terminal velocities,
+  since the values given in the \citeauthor{Meyer:2014b} papers are
+  troublingly low.  We have used the prescription
+  \(V = 2.6 V_{\text{esc}}\), where
+  \(V_{\text{esc}} = \left( 2 G M (1 - \Gamma_e)/ R \right)^{1/2}\) is the
+  photospheric escape velocity, which is appropriate for strong
+  line-driven winds with \(T_{\text{eff}} > \SI{21 000}{K}\)
+  \citep{Lamers:1995a}.  We find velocities of
+  \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
+  observations and theory \citep{Vink:1999a} for O~stars, but at least
+  two times higher than those cited by \citet{Meyer:2014b}. For
+  main-sequence B~stars, wind column densities are too low to reliably
+  measure the terminal velocity from near ultraviolet P~Cygni profiles
+  \citep{Prinja:1989a}, and so the values are theory-dependent
+  \citep{Krticka:2014a} and hence more uncertain.  A further
+  complication is the existence of a subset of OB stars with
+  anomalously weak winds \citep{Puls:2008a}, which in some cases is
+  related to the presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
+  \citep{Oskinova:2011b}.} %
+The three examples are an early B~star (\SI{10}{M_\odot}), a late O~star
+(\SI{20}{M_\odot}), and an early O~star (\SI{40}{M_\odot}), which cover the
+range of luminosities and wind strengths expected from bow-producing
+hot main sequence stars.  The luminosity is a steep function of
+stellar mass (\(L \sim M^{2.5}\)) and the wind mass-loss rate is a steep
+function of luminosity (\(\dot{M} \sim L^{2.2}\)), which means that the
+wind momentum efficiency is also a steep function of mass
+(\(\eta \sim M^3\)), approaching unity for early O~stars, but falling to
+less than 1\% for B~stars.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-RSG}
+  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for a cool M-type
+    supergiant instead of hot main sequence stars.  A smaller dust
+    opacity is used, \(\kappa = \SI{60}{cm^2.g^{-1}}\), because of the
+    reduced extinction efficiency at the optical/infrared wavelengths
+    emitted by this star.}
+  \label{fig:M-supergiant}
+\end{figure}
+
+It can be seen from Figure~\ref{fig:zones-v-n-plane} that the onset of
+the radiation bow wave regime is very similar for the three
+main-sequence stars, occurring at
+\(n > \text{\numrange{20}{40}} \, v_{10}^2\).  An important
+difference, however, is that for the \SI{40}{M_\odot} star, which has a
+powerful wind, the radiation bow wave regime only occurs for a very
+narrow range of densities, whereas for the \SI{10}{M_\odot} star, with a
+much weaker wind, the regime is much broader, extending to
+\(n < \num{e4} \, v_{10}^2\).  Another difference is the size scale of
+the bows in this regime, which is
+\(R_0 = \text{\SIrange{0.001}{0.003}{pc}}\) for the \SI{10}{M_\odot} star
+if \(v_\infty = \SI{40}{km.s^{-1}}\), but \(R_0 \approx \SI{0.1}{pc}\) for the
+\SI{40}{M_\odot} star, assuming the same inflow velocity.
+
+Figure~\ref{fig:M-supergiant} shows results for a cool M-type
+super-giant star with stellar parameters inspired by Betelgeuse
+(\chemalpha~Orionis), as listed in Table~\ref{tab:stars}.  Unlike the
+UV-dominated spectrum of the hot stars, this star emits predominantly
+in the near-infrared, where the dust extinction efficiency is lower,
+so we adopt a lower opacity of \SI{60}{cm^2.g^{-1}}.  This has the
+effect of shifting the radiation bow wave regime to higher densities:
+\(n = \text{\numrange{1000}{30 000}}\, v_{10}^2\) in this case.
+
+\subsubsection{Effects of stellar gravity}
+\label{sec:effects-gravity}
+
+In principle, gravitational attraction from the star, of mass \(M\),
+will partially counteract the radiative acceleration.  This can be
+accounted for by replacing \(L\) with an effective luminosity
+\newcommand\Edd{\ensuremath{_{\text{E}}}}
+\begin{equation}
+  \label{eq:effective-luminosity}
+  L_{\text{eff}} = L \bigl(1 - \Gamma\Edd^{\,-1}\bigr) \ ,
+\end{equation}
+in which \(\Gamma\Edd\) is the Eddington factor:
+\begin{equation}
+  \label{eq:eddington-factor}
+  \Gamma\Edd = \frac{\kappa L}{4\pi c G M} = 458.5 \, \frac{\kappa_{600} L_4}{ M } \ ,
+\end{equation}
+where, in the last expression, \(M\) is measured in solar masses.  For
+the stars in Table~\ref{tab:stars}, we find
+\(\Gamma\Edd \approx \text{\numrange{30}{400}}\), so gravity can be safely
+ignored.  The only exception is when the optical depth of the bow is
+very large: \(\tau > \ln\Gamma\Edd \sim 5\), in which case gravity may be
+important in the outer parts of the shell (see
+\citealt{Rodriguez-Ramirez:2016b}).
+
+\subsubsection{Ionization state of the bow shell}
+\label{sec:trapp-ioniz-front}
+
+\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
+\newcommand\shell{\ensuremath{_{\text{sh}}}}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-BSG}
+  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for an evolved
+    B-type supergiant instead of main sequence stars.  This is similar
+    to the early O MS star of Fig.~\ref{fig:zones-v-n-plane}\textit{c}
+    in many respects, except for the trapping of the ionization front,
+    which occurs for much lower outer stream densities.}
+  \label{fig:B-supergiant}
+\end{figure}
+
+In this section we calculate whether the star is capable of
+photoionizing the entire bow shock shell, or whether the ionization
+front will be trapped within it.  The number of hydrogen
+recombinations\footnote{%
+  The diffuse field is treated in the on-the-spot approximation,
+  assuming all emitted Lyman continuum photons are immediately
+  re-absorbed locally, so the case~B recombination co-efficient,
+  \(\alphaB = \num{2.6e-13}\, T_4^{-0.7}\, \si{cm^3.s^{-1}}\), is
+  used, where \(T_4 = T/\SI{e4}{K}\).} %
+per unit time per unit area in a fully ionized shell is
+\begin{equation}
+  \label{eq:shell-recombination-rate}
+  \mathcal{R} = \alphaB n\shell^2 h\shell \ ,
+\end{equation}
+while the advective flux of hydrogen nuclei through the shock is 
+\begin{equation}
+  \label{eq:shell-advective-flux}
+  \mathcal{A} = n v \ ,
+\end{equation}
+and the flux of hydrogen-ionizing photons
+(\(h \nu > \SI{13.6}{eV}\)) incident on the inner edge of the shell is
+\begin{equation}
+  \label{eq:shell-ionizing-flux}
+  \mathcal{F} = \frac{S} {4 \pi R_0^2} \ , 
+\end{equation}
+where \(S\) is the ionizing photon luminosity of the star.  Any shell
+with \(\mathcal{R} + \mathcal{A} > \mathcal{F}\) cannot be entirely
+photoionized by the star, and so must have trapped the ionization
+front.
+
+The ratio of advective particle flux to ionizing flux is, from
+equations~\eqref{eq:Rstar}, \eqref{eq:shell-advective-flux},
+\eqref{eq:shell-ionizing-flux},
+\begin{equation}
+  \label{eq:advective-over-ionizing-flux}
+  \frac{\mathcal{A}}{\mathcal{F}} = \num{5.86e-5} \frac{x^2 L_4}{v_{10} S_{49}} \ , 
+\end{equation}
+which is nearly always small.  For clarity of exposition, we therefore
+ignore \(\mathcal{A}\) in the following discussion, although it is
+included in quantitative calculations.  The column density of the
+shocked shell can be found, for example, from equations~(10) and~(12)
+of \citet{Wilkin:1996a} in the limit \(v_\infty/V \to 0\) (Wilkin's parameter
+\(\alpha\)) and \(\theta \to 0\).  This yields
+\begin{equation}
+  \label{eq:shocked-shell-column}
+  n\shell h\shell = \tfrac34 n R_0 \ .
+\end{equation}
+Assuming strong cooling behind the shock,\footnote{%
+  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
+} %
+the shell density is
+\begin{equation}
+  \label{eq:isothermal-shell-density}
+  n\shell = \mathcal{M}_0^2 n \,
 \end{equation}
 where
+\(\mathcal{M}_0 = v_\infty / \sound\) is the isothermal Mach number of the
+external stream.\footnote{%
+  \label{fn:temperature-dependence}
+  The sound speed depends on the temperature and hydrogen and helium
+  ionization fractions, \(y\) and \(y_{\text{He}}\) as
+  \(\sound^2 = (1 + y + z_{\text{He}} y_{\text{He}}) (k T /
+  \bar{m})\), where \(z_{\text{He}}\) is the helium nucleon abundance
+  by number relative to hydrogen and
+  \(k = \SI{1.3806503e-16}{erg.K^{-1}}\) is Boltzmann's constant.  We
+  assume \(y = 1\), \(y_{\text{He}} = 0.5\), \(z_{\text{He}} = 0.09\),
+  so that \(\sound = \num{11.4}\, T_4^{1/2}\, \si{km.s^{-1}}\). } %
+Putting these together with equations~\eqref{eq:Rstar} and
+~\eqref{eq:tau-star}, one finds that \(\mathcal{R} > \mathcal{F}\)
+implies
 \begin{equation}
-  \label{eq:xi-k}
-  \xi_k = \frac{2} {k +2} \ .
+  \label{eq:ifront-trap-x-cubed-taustar}
+  x^3 \tau_* > \frac{4 S c \sound \bar{m}^2 \kappa}{3 \alpha L} \ .
 \end{equation}
-We now take the Taylor expansion of equation~\eqref{eq:theta-1-90-implicit} to find
+From equation~\eqref{eq:rad-full-x}, it can be seen that \(x\) depends
+on the external stream parameters, \(n\), \(v_\infty\) only via
+\(\tau_*\), and so equation~\eqref{eq:ifront-trap-x-cubed-taustar} is a
+condition for \(\tau_*\), which, by using
+equation~\eqref{eq:taustar-typical}, becomes a condition on
+\(n / v_{10}^2\).  In the radiation bow shock case,
+\(x = (1 + \eta)^{1/2}\), and the condition can be written:
 \begin{equation}
-  \label{eq:theta-1-90-Taylor}
-  \theta_{1,90}^2 + \tfrac{1}{15}  \theta_{1,90}^4 + \mathcal{O}(\theta_{1,90}^6)
-  = 3 \xi_k \beta \ , 
-\end{equation}
-which, if \(\theta_{1,90}\) is small, has the approximate solution
-\begin{equation}
-  \label{eq:theta-1-90-approx}
-  \theta_{1,90} \approx \left( \frac{3 \xi_k \beta} {1 + \tfrac15 \xi_k \beta} \right) \ .
-\end{equation}
-Substituting back into equation~\eqref{eq:Lambda-from-theta-1-90}
-yields an approximate value for the alatude of
-\begin{equation}
-  \label{eq:Lambda-approx}
-  \text{ancantoid} \quad
-  \Lambda \approx \frac {(3 \xi_k)^{1/2} \left( 1 + \beta^{1/2} \right)}
-  { \left( 1 + \tfrac15 \xi_k \beta \right)^{1/2} \left( 1 - \xi_k \beta \right)} \ .
-\end{equation}
-This approximation is surprisingly accurate, with a relative error of
-order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).  The
-leading term in the relative error scales as \((\beta / (k + 2))^2\), so the
-approximation is even better for smaller \(\beta\) and larger \(k\).
-
-\subsection{Planitude and alatude of cantoids and wilkinoid}
-\label{sec:cantoid-wilkinoid-shapes}
-
-Since \(\Pi\) and \(\Lambda\) depend on only that portion of the inner wind
-emitted in the forward hemisphere, \(\theta \le 90^\circ\), the results for the
-cantoids can be found by taking \(k = 0\), in which case
-equations~(\ref{eq:C-k-beta}, \ref{eq:final-planitude}, \ref{eq:xi-k},
-\ref{eq:Lambda-approx}) yield
-\begin{gather}
-  \label{eq:cantoid-Pi-Lambda}
-  \text{cantoid} \quad
-  \begin{cases}
-    \quad \Pi &= \dfrac {5} {3 \left( 1 - \beta^{1/2} \right)}\\[12pt]
-    \quad \Lambda &= \dfrac { \sqrt 3} {\left( 1 + \tfrac15 \beta \right)^{1/2} \left( 1 - \beta^{1/2} \right)} \ .
-  \end{cases}
-\end{gather}
-The wilkinoid shape is equal to the \(\beta \to 0\) limit of the cantoid, so
-its planitude and alatude are given by:
-\begin{gather}
-  \label{eq:wilkinoid-Pi-Lambda}
-  \text{wilkinoid} \quad
-  \begin{cases}
-    \quad \Pi &= \dfrac {5} {3}\\[10pt]
-    \quad \Lambda &= \sqrt 3 \ .
-  \end{cases}
-\end{gather}
-
-\subsection{Asymptotic opening angle}
-\label{sec:asympt-open-angle}
-
-The asymptotic opening angle
-of the far wings, \(\theta_\infty\), can be found from
-equation~\eqref{eq:ancantoid-theta-theta1-implicit} for the
-ancantoids, together with the condition that
-\(\theta_\infty + \theta_{1\infty} = \pi\).  These yield the implicit equation
-\begin{equation}
-  \label{eq:anacantoid-theta-inf}
-  \theta_\infty - \left( \frac {k + 2 (1 - \beta)} {k + 2} \right) \tan \theta_\infty
-  = \pi + 2 \beta I_k(\pi/2) \ ,
+  \label{eq:ifront-trap-density-RBS}
+  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta)^3} \ , 
 \end{equation}
 where
+\begin{equation*}
+  S_{49} = S / \bigl( \SI{e49}{s^{-1}} \bigr) \ .
+\end{equation*}
+Numerical values of \(S_{49}\) for our three example stars are given
+in Table~\ref{tab:stars}, taken from Figure~4 of
+\citet{Sternberg:2003a}.  In the radiation bow wave case,
+\(x = 2\tau_*\), and the condition can be written:
 \begin{equation}
-  I_k(\pi/2) = \frac{\sqrt \pi}{4} \,
-      \frac{  \GammaFunc\left( \frac{k+1}{2} \right)} {\GammaFunc\left(\frac{k+4}{2}\right)}
+  \label{eq:ifront-trap-taustar-RBW}
+  \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ . 
 \end{equation}
-and \(\GammaFunc\) is the usual Gamma function.  This can be compared with the equivalent result obtained by \CRW{} for the cantoids:
+In the wind bow shock case, the result is the same as
+equation~\eqref{eq:ifront-trap-density-RBS}, but changing the factor
+\((1 + \eta)^3\) to \(\eta^3\).  For the example hot stars in
+Table~\ref{tab:stars}, and assuming \(\kappa_{600} = 1\),
+\(T_4 = 0.8\), the resulting density threshold is
+\(n > (\text{\numrange{1000}{5000}})\, v_{10}^2\), depending only
+weakly on the stellar parameters, which is shown by the red lines in
+Figure~\ref{fig:zones-v-n-plane}.  For the \SI{10}{M_\odot} star, this is
+in the radiation bow wave regime, whereas for the higher mass stars it
+is in the radiation bow shock regime.  When the external stream is
+denser than this, then the outer parts of the shocked shell may be
+neutral instead of ionized, giving rise to a cometary compact \hii{}
+region \citep{Mac-Low:1991a, Arthur:2006a}.  This is only necessarily
+true, however, when the star is isolated.  If the star is in a cluster
+environment, then the contribution of other nearby massive stars to
+the ionizing radiation field must be considered.
+
+Quite different results are obtained for a B-type supergiant star (see
+Tab.~\ref{tab:stars} and Fig.~\ref{fig:B-supergiant}), which has a
+similar bolometric luminosity and wind strength to the \SI{40}{M_\odot}
+main-sequence star, but a hundred times lower ionizing luminosity.
+This results in a far lower threshold for trapping the ionization
+front of \(n > 40 v_{10}^2\).  The advective flux, \(\mathcal{A}\), is
+relatively stronger for this star than for the main-sequence stars, but
+even for \(v_{10} < 2\), where the effect is strongest, the change is
+only of order the width of the dark red line in
+Figure~\ref{fig:B-supergiant}.
+
+In principle, when the ionization front trapping occurs in the bow
+wave regime, then the curves for \(R_0\) will be modified in the
+region above the red line because all of the ionizing radiation is
+trapped in the shell due to gas opacity, which is not included in
+equation~\eqref{eq:tau-thin}.  However, this only happens for our
+\SI{10}{M_\odot} star, which has a relatively soft spectrum.
+Table~\ref{tab:stars} gives the peak wavelength of the stellar
+spectrum for this star as \(\lambda_{\text{eff}} = \SI{0.115}{\um}\), which
+is significantly larger than the hydrogen ionization threshold at
+\SI{0.0912}{\um}, meaning that only a small fraction of the total
+stellar luminosity is in the EUV band and affected by the gas opacity.
+The effect on \(R_0\) is therefore small.  For the higher mass stars,
+\(\lambda_{\text{eff}} < \SI{0.0912}{\um}\), so the majority of the
+luminosity is in the EUV band, but in these cases the ionization front
+trapping occurs well inside the radiation bow shock zone, where the
+dust optical depth is already sufficient to trap all of the radiative
+momentum.
+
+\subsubsection{Radiative cooling lengths}
+\label{sec:radi-cool-lengths}
+\newcommand\M{\ensuremath{\mathcal{M}}}
+In this section, we calculate whether the radiative cooling is
+sufficiently rapid behind the bow shock to allow the formation of a
+thin, dense shell.  Since cooling is least efficient at low densities,
+we will assume that the wind bow shock regime applies unless otherwise
+specified. We label quantities just outside the shock by the subscript
+``0'', quantities just inside the shock (after thermalization, but
+before any radiative cooling) by the subscript ``1'', and quantities
+after the gas has cooled back to the photoionization equilibrium
+temperature by the subscript ``2''.  Assuming a ratio of specific
+heats, \(\gamma = 5/3\), the relation between the pre-shock and immediate
+post-shock quantities is
+\begin{align}
+  % \M_1 &= \left(\frac{\M_0^2 + 3} {5\M_0^2 - 1}\right)^{1/2} \\
+  \label{eq:shock-n-jump}
+  \frac{n_1}{n_0} &= \frac{4 \M_0^2} {\M_0^2 + 3} \\
+  \label{eq:shock-T-jump}
+  \frac{T_1}{T_0} &= \tfrac1{16} \bigl( 5\M_0^2 - 1 \bigr) \bigl( 1 + 3/\M_0^2 \bigr) \\
+  \label{eq:shock-v-jump}
+  \frac{v_1}{v_0} &= \left(\frac{n_1}{n_0}\right)^{-1} \ ,
+\end{align}
+where \(\M_0 = v_0 / \sound\).  The cooling length of the post-shock
+gas can be written as
+\newcommand\cool{\ensuremath{_{\text{cool}}}}
 \begin{equation}
-  \label{eq:cantoid-theta-inf}
-  \theta_\infty - \tan \theta_\infty = \frac{\pi}{1 - \beta} \ .
+  \label{eq:dcool}
+  d\cool = \frac{3 P_1 v_1} { 2 \bigl(  \mathcal{L}_1 - \mathcal{G}_1 \bigr) }\ ,  
 \end{equation}
-Note that, unlike the case for \(\Pi\) and \(\Lambda\),
-equation~\eqref{eq:anacantoid-theta-inf} does \emph{not} reduce to
-equation~\eqref{eq:cantoid-theta-inf} in the limit \(k \to 0\).  This is
-because, for \(\theta > 90^\circ\), the \(k = 0\) ancantoid differs from the
-cantoid since there is no wind in the backward hemisphere (see
-Figure~\ref{fig:anisotropic-arrows}).  Therefore there is less inner
-support for the far wings of the bow, and so \(\theta_\infty\) is smaller than
-in the cantoid case.  The wilkinoid result again follows from
-\(\beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that
-the far wings are asymptotically parallel to the symmetry axis, as is
-the case for the paraboloid (App.~\ref{app:parabola}).  In the case of
-the wilkinoid, however, the behavior is cubic in the wings,
-\(z \sim r^3\), as opposed to quadratic as in the paraboloid.
+where \(P_1\) is the thermal pressure and \(\mathcal{L}_1\),
+\(\mathcal{G}_1\) are the volumetric radiative cooling and heating
+rates.  For fully photoionized gas, we have
+\(P_1 \approx 2 n_1 k T_1\), \(\mathcal{L}_1 = n_1^2 \Lambda(T_1)\), and
+\(\mathcal{G}_1 = n_1^2 \Gamma(T_1)\), where \(\Lambda(T)\) is the cooling
+coefficient, which is dominated by metal emission lines that are
+excited by electron collisions, and \(\Gamma(T)\) is the heating
+coefficient, which is dominated by hydrogen photo-electrons
+\citep{Osterbrock:2006a}. The cooling coefficient has a maximum around
+\SI{e5}{K}, and for typical ISM abundances can be approximated as
+follows:
+\begin{align}
+  \label{eq:cooling-coefficient}
+  \Lambda_{\text{warm}} &= \num{3.3e-24} \, T_4^{2.3} \, \si{erg.cm^{-3}.s^{-1}}\\
+  \Lambda_{\text{hot}} &= \num{e-20} \, T_4^{-1}\, \si{erg.cm^{-3}.s^{-1}} \\
+  \Lambda &= \left( \Lambda_{\text{warm}}^{-k} +  \Lambda_{\text{hot}}^{-k} \right)^{-1/k}
+      \quad \text{with} \quad k = 3 \ ,
+\end{align}
+which is valid in the range \(0.7 < T_4 < 1000\).  We approximate the heating coefficient as
+\begin{equation}
+  \label{eq:heating-coefficient}
+  \Gamma = \num{1.77e-24} \, T_4^{-1/2} \, \si{erg.cm^{-3}.s^{-1}} \ ,
+\end{equation}
+where the coefficient is chosen so as to give \(\Gamma = \Lambda\) at
+an equilibrium temperature of \(T_4 = 0.8\).
+
+In Figure~\ref{fig:zones-v-n-plane} we show curves calculated from
+equations~\eqref{eq:shock-n-jump} to~\eqref{eq:heating-coefficient},
+corresponding to \(d\cool = R_0\) (thick blue line) and
+\(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
+thickness in the efficient cooling case.  In this context, \(n_0 = n\)
+and \(n_2 = n\shell\), so that \(h_0\) follows from
+equations~\eqref{eq:shocked-shell-column}
+and~\eqref{eq:isothermal-shell-density} as
+\begin{equation}
+  \label{eq:strong-cooling-h0}
+  h_0 = \tfrac34 \M_0^{-2} R_0 \ .
+\end{equation}
+The bends in the curves at \(v \approx \SI{50}{km.s^{-1}}\) are due to the
+maximum in the cooling coefficient \(\Lambda(T)\) around
+\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
+blue line, radiative cooling is so efficient that the bow shock can be
+considered isothermal, and so the shell is dense and thin (at least,
+in the apex region).  It can be seen that the ionization front
+trapping always occurs at densities larger than this, which justifies
+the use of equation~\eqref{eq:isothermal-shell-density} in the
+previous section.  For bows with outer stream densities below the
+thick blue line, cooling is unimportant and the bow shock can be
+considered non-radiative.  In this case the shell is thicker than in
+the radiative case,
+\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
+  An approximate value can be found from
+  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
+  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
+  Consideration of the slight increase in density between the shock
+  and the contact discontinuity reduces this value by 5--10\%.} %
+For bows with outer stream densities between the two blue lines,
+cooling does occur, albeit inefficiently, so that the shell thickness
+is set by \(d\cool\) rather than \(h_0\).
+
+\subsection{Imperfect coupling between gas and dust}
+\label{sec:imperf-coupl-betw}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/test-Fdrag-components}
+  \caption{Contributions of different collider species to the
+    dimensionless drag force, \(f\drag / f_*\), as a function of
+    gas--grain slip velocity, \(w\).  Solid lines show the Coulomb
+    (electrostatic) drag, while dashed lines show the Epstein
+    (solid-body) drag.  Results are shown for dimensionless grain
+    potential \(\phi = 10\).  All Coulomb forces scale with
+    \(\phi^2\), while the Epstein forces are independent of \(\phi\).  The
+    species labelled ``CNO++'' represents the combined effect of all
+    metals (see footnote~\ref{fn:metal-drag}).}
+  \label{fig:drag-components}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/test-Fdrag-param-space}
+  \caption{Regimes of gas--grain drag as a function of slip velocity
+    and grain potential.  The different regimes are indicated by bold
+    roman numerals, as explained in
+    Table~\ref{tab:fdrag-regimes}. Blue shading indicates regions
+    dominated by Epstein (solid-body) drag, whereas red and green
+    shading indicate regions dominated by Coulomb drag due to protons
+    and electrons, respectively.  In each case, the saturated color
+    represents a contribution \(> 70\%\) of the relevant component to
+    the total drag force, while progressively lighter shading
+    represents the \(> 60\%\) and \(> 50\%\) levels.  The thick white
+    dotted line indicates the transition between the subthermal and
+    superthermal regimes for protons, while the thin white dotted line
+    indicates the corresponding transition for electrons.  Contours
+    show the total drag force in units of \(f_*\) (see
+    eq.~[\ref{eq:fstar}]) in decade intervals from \(0.1\) to
+    \(10^4\), as labelled.  Results are shown for
+    \(T = \SI{8000}{K}\) and \(n = \SI{100}{cm^{-3}}\), but the
+    differences are very slight throughout the ranges
+    \(T = \text{\SIrange{5000}{15000}{K}}\) and
+    \(n = \text{\SIrange{e-3}{e6}{cm^{-3}}}\).}
+  \label{fig:drag-v-phi-plane}
+\end{figure}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
+  \caption{Dimensionless drag force, \(f\drag / f_*\), as a function
+    of gas--grain slip velocity, \(w\), for different values of the
+    grain potential in thermal units, \(\phi\).  Contributions from
+    proton and electron Coulomb (electrostatic) drag, as well as
+    Epstein (solid-body) drag are indicated.  Examples of subsonic and
+    highly supersonic stable drift velocities are shown (thin dark
+    blue arrows), where the drag force is in equilibrium with the
+    radiation force (thick dark blue dashed lines), while blue shading
+    indicates the unstable, mildly supersonic velocity regime, where
+    no stable drift equilibrium exists.  Inset graph shows \(\phi\) as a
+    function of the radiation parameter,
+    \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a log--linear scale
+    for a collection of Cloudy models (see
+    Appendix~\ref{sec:cloudy-models-dust}).}
+  \label{fig:gas-grain-drag-photoionized}
+\end{figure*}
+
+% \begin{figure}
+%   \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
+%   \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
+%     gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
+%   \label{fig:decouple-v-n-plane}
+% \end{figure}
+
+If the radiation field is sufficiently strong, then the collisional
+coupling between grains and gas will break down.  In this section, we
+calculate the regions of star+stream parameter space where this might
+occur, leading to a separation of the bow into an outer dust wave and
+an inner, dust-free bow shock.
+
+\subsubsection{Drag force on grains}
+\label{sec:drag-force-grains}
+
+\begin{table}
+  \centering
+  \caption{Regimes of drag force as function of grain potential and slip speed}
+  \label{tab:fdrag-regimes}
+  \renewcommand\arraystretch{1.3}
+  \resizebox{\linewidth}{!}{%
+    \begin{tabular}{@{}r l l l@{}}
+    \toprule
+      & Regime & Approximate criteria & \(f\drag / f_*\) \\ \midrule
+      I & Epstein subsonic & \(\phi^2 \ll 1\)
+                             and \(w_{10} < 1\) & \(1.5\, w_{10}\) \\
+      II & Epstein supersonic & \(w_{10} > 1\)
+                                and \(w_{10} > 5\,\abs{\phi}\)& \( w_{10}^2\) \\
+      III & Coulomb p\(^+\) subthermal & \(\phi^2 > 1\)
+                                         and \(w_{10} < 1\) & \((1 + 20\, \phi^2)\,
+                                                              w_{10}\) \\
+    % & Coulomb p\(^+\) peak & \(\phi^2 > 1\)
+    %                          and \(w_{10} \approx 1\) & \(1 + 10\, \phi^2\) \\
+      IV & Coulomb p\(^+\) superthermal & \(\phi^2 > 1\)
+                                          and \(1 < w_{10} < 5\) & \(w_{10}^2
+                                                                   + 10\, \phi^2/w_{10}^2 \) \\
+      V & Coulomb e\(^-\) subthermal & \(\phi^2 > 20\)
+                                 and \(5 < w_{10} < 42\) & \(0.48\, \phi^2 \,
+                                                           w_{10}\) \\
+    \bottomrule
+  \end{tabular}
+  }
+\end{table}
+
+The drag force on a charged dust grain moving at a relative speed
+\(w\) through a plasma has contributions from both direct collisions
+and from electrostatic Coulomb interactions with ions and electrons.
+We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
+considering the contributions from protons, electrons, helium
+ions,\footnote{Helium is assumed to be singly ionized, leading to only
+  a small contribution to the drag force.  For much hotter stars, such
+  as the central stars of planetary nebulae, helium may be doubly
+  ionized, which leads to a fourfold increase in its Coulomb drag
+  contribution, which is significant for \(w < \SI{5}{km.s^{-1}}\).} %
+and metal ions.\footnote{%
+  \label{fn:metal-drag}
+  All metals are lumped together as a single species, assuming
+  standard \hii{} region gas-phase abundances.  They are dominated by
+  C and O, with minor contributions from N and Ne.  The total
+  abundance is \num{8.5e-4} and the effective atomic weight is
+  \num{15.3}.  All are assumed to be doubly ionized.  Their largest
+  relative contribution to the drag force is for
+  \(w < \SI{2}{km.s^{-1}}\), but is less than 1\% even there.} %
+Results are shown in Figure~\ref{fig:drag-components}, where dashed
+lines correspond to direct solid body collisions and solid lines to
+electrostatic interactions.  The latter depend on the grain potential,
+which is described in dimensionless terms by \(\phi\), which is the
+electrostatic potential energy of a unit charge at the surface of a
+grain of charge \(z\grain\) and radius \(a\), in units of the
+characteristic thermal energy of a gas particle:
+\begin{equation}
+  \label{eq:phi-potential}
+  \phi = \frac{e^2 z\grain}{a kT} \ .
+\end{equation}
+The electrostatic contributions to \(f\drag\) are proportional to
+\(\phi^2\) (results are shown for \(\abs{\phi} = 10\)), whereas the
+solid-body contributions are independent of \(\phi\).  The drag force is
+put in dimensionless units by dividing by a characteristic force:
+\begin{equation}
+  \label{eq:fstar}
+  f_* = 2 n k T \cdot \pi a^2 \ , 
+\end{equation}
+which is approximately\footnote{%
+  To simplify the exposition, the gas pressure in this section is
+  calculated assuming a fully ionized, pure hydrogen plasma, yielding
+  \(P\gas = 2 n k T\). For typical ISM abundances, the contribution of
+  helium and its corresponding electrons yield a correction to this of
+  order 5\%.  The required modifications when a cool star interacts
+  with a predominantly neutral gas stream are discussed later.  } %
+the ionized gas pressure multiplied by the grain geometric cross
+section.
+
+For grains with low electric charge, \(\phi^2 \ll 1\), the drag force is
+dominated by direct collisions of protons with the grain (dashed red
+line in Fig.~\ref{fig:drag-components}).  The gas collisional mean
+free path is much larger than the grain size, so the drag is in the
+Epstein regime \citep{Weidenschilling:1977b}.
+% This is illustrated by
+% the \(\phi = 0.25\) case (blue line) in
+% Figure~\ref{fig:gas-grain-drag-photoionized}.
+As the relative gas--grain slip speed, \(w\), increases, \(f\drag\)
+first increases linearly with \(w\) reaching \(f\drag \approx f_*\) at
+\(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to a quadratic
+increase in the supersonic regime.
+
+As \(\abs{\phi}\) increases, long-range electrostatic interactions with
+protons within the Debye radius (Coulomb drag) become increasingly
+important at subsonic relative velocities, as shown by the solid lines
+in Figure~\ref{fig:drag-components}).
+% in
+% Figure~\ref{fig:gas-grain-drag-photoionized} by the orange
+% (\(\phi = 1\)), green (\(\phi = 4\)), and red (\(\phi = 16\)) lines.
+However, the Coulomb drag has a peak when \(w\) is equal to the
+thermal speed of the colliders, which is
+\(\approx \SI{10}{km.s^{-1}}\) for protons, giving a maximum strength of
+\begin{equation}
+  \label{eq:fdrag-maximum}
+  f_{\mathrm{max}} = 0.5\, (\ln\Lambda)\, \phi^2 f_* \approx 10\, \phi^2 f_* \ , 
+\end{equation}
+where \(\Lambda\) is the plasma parameter (number of particles within a
+Debye volume), such that
+\(\ln\Lambda = 23.267 + 1.5 \ln T_4 - 0.5 \ln n\).  At highly super-thermal
+speeds, the Coulomb drag falls asymptotically as
+\(f\drag \propto 1 / w^{2}\).  The thermal speed of electrons is higher than
+that of the protons by a factor of \((m_p / m_e)^{1/2}\), so that the
+electron Coulomb drag (solid light blue line) gives a second peak of
+similar strength, but at \(w \approx \SI{430}{km.s^{-1}}\).  The behavior of
+\(f\drag\) in all these different regimes is summarised in
+Table~\ref{tab:fdrag-regimes}, in terms of \(\phi\) and
+\(w_{10} = w / \SI{10}{km.s^{-1}}\).  This is further illustrated in
+Figure~\ref{fig:drag-v-phi-plane}, where each of the drag regimes is
+located on the \((w, \abs{\phi})\) plane.
+
+% \begin{equation}
+%   \label{eq:fdrag-regimes}
+%   f\drag \approx
+%   \begin{cases}
+%     \text{Epstein subsonic (\(\phi^2 \ll 1\) and \(w_{10} < 1\)):}
+%     & w_{10}\, f_* \\
+%     \text{Epstein supersonic (\(\phi^2 \ll 1\) and \(w_{10} > 1\)):}
+%     & w_{10}^2\, f_* \\
+%     \text{Coulomb p\(^+\) subthermal (\(\phi^2 > 1\) and \(w_{10} < 1\)):}
+%     & (1 + 20 \phi^2)\, w_{10}\, f_* \\
+%     \text{Coulomb p\(^+\) peak (\(\phi^2 > 1\) and \(w_{10} \approx 1\)):}
+%     & (1 + 10 \phi^2)\, f_* \\
+%     \text{Coulomb p\(^+\) superthermal (\(\phi^2 > 1\) and \(1 < w_{10} < 5\)):}
+%     & (w_{10}^2 + 10 \phi^2/w_{10}^2) \, f_* \\
+%     \text{Coulomb e\(^-\) subthermal (\(\phi^2 > 20\) and \(5 < w_{10} < 42\)):}
+%     & 0.48 \phi^2 \, w_{10}\, f_* \\
+%   \end{cases}
+% \end{equation}
+
+% Or \Lambda = (4 pi / 3) n r_D^3?
+% Where Debye length is r_D^2 = k T / 4 pi n e^2
+% => \Lambda = n r_D (4 pi / 3) k T / 4 pi n e^2
+% = k T r_D / 3 e^2
+% This is 9 times less than the other expression
+% Anyway, from kappa notes I have
+% \ln\Lambda = 9.452 + 1.5 ln(T) - 0.5 ln(n)
+
+% If I am going to use log10, then the coefficients get divided by
+% ln(10) = 2.30258509299, and if we use T4, then we add 1.5 ln(1e4) =
+% 13.815.  So we get 23.267 + 0.651 log10(T4) - 0.217 log10(n).  Nope,
+% best with natural log
+
+\subsubsection{Gas--grain separation: drift and rip}
+\label{sec:gas-grain-separ}
+
+In Appendix~\ref{sec:gas-free-bow} we calculate the behaviour of an
+incoming stream of dust grains, subject only to the repulsive
+radiation force from a star.  For an initial inward radial trajectory,
+the dust grain motion is decelerated and turned around, reaching a
+minimum radius \(R\starstar\), given by equation~\eqref{eq:dust-r0}.
+This drag-free radiative turnaround radius, \(R\starstar\), is smaller
+for higher initial inward velocities, but is independent of the
+density of the incoming stream.  We are now in a position to see how
+gas--grain drag will modify this picture.
+
+From equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar}, we can
+write the radiation force acting on a grain as
+\begin{equation}
+  \label{eq:frad-Xi}
+  f\rad = \Qp\, \Xi\, f_* \ ,
+\end{equation}
+where \(\Qp\) is the grain's radiation pressure efficiency (see
+footnote~\ref{fn:Qp} in Appendix~\ref{sec:gas-free-bow}) and \(\Xi\) is
+the local radiation parameter, defined as the ratio of direct stellar
+radiation pressure to gas pressure:
+\begin{equation}
+  \label{eq:Xi-Prad-over-Pgas}
+  \Xi \equiv \frac{P\rad}{P\gas} \approx \frac{L}{4 \pi R^2 c\, (2 n k T)} \ ,
+\end{equation}
+where the last expression corresponds to the optically thin limit.
+The grain potential \(\phi\) is also primarily determined by \(\Xi\), as
+shown in Appendix~\ref{sec:cloudy-models-dust} and the inset graph of
+Figure~\ref{fig:gas-grain-drag-photoionized}, but with a slow
+dependence, which can be approximated as
+\begin{equation}
+  \label{eq:phi-vs-Xi}
+  \phi(\Xi) \approx 1.5 \bigl( 2.3 +  \ln \Xi \bigr) \ .
+\end{equation}
+There are also slight secondary dependencies on the grain composition and
+stellar spectrum.  The relationship given in eq.~\eqref{eq:phi-vs-Xi}
+is appropriate for graphite grains and for stellar effective
+temperatures in the range \SIrange{20}{30}{kK}.  For hotter stars than
+this, \(\phi\) should be multiplied by a further factor of \(1.5\), while
+for silicate grains it should be divided by \(1.5\).
+
+In the outer regions of the photoionized volume around an OB star,
+close to the ionization front, the radiation parameter is low, with
+typical value \(\Xi \sim 0.1\).  In this regime, the negative charge
+current at the grain surface due to electron collisions is roughly in
+balance with the positive current due to the ultraviolet photoelectric
+effect \citep{Weingartner:2001b}, leading to a low grain potential,
+\(\abs{\phi} < 1\), which may be positive or negative.  The low
+\(\Xi\) means that the radiative force is also weak:
+\(f\rad \sim 0.1 f_*\) from equation~\eqref{eq:frad-Xi} if
+\(\Qp \sim 1\) at UV wavelengths, which is true for all but the smallest
+grains.  Thus, from the equations for \(f\drag\) given in
+Table~\ref{tab:fdrag-regimes}, the radiative force can be balanced by
+Epstein drag if \(w_{10} \sim 0.1\), leading to a small equilibrium drift
+velocity, \(w\drift < \SI{1}{km.s^{-1}}\), of the grains with respect
+to the gas.  This drift is much smaller than the inward stream
+velocities that we are considering
+(\(v_\infty > \SI{10}{km.s^{-1}}\)), so the dust follows the gas stream at
+a slightly reduced velocity (\(< 10\%\)), and (by mass conservation) a
+slightly increased density.  Each grain exerts an exactly opposite
+force to \(f\drag\) upon the gas, but since the dust-gas mass ratio,
+\(Z\grain\), is small, this produces a negligible acceleration of the
+gas.
+
+\begin{table}
+  \caption{Critical values of radiation parameter at the rip point: \(\Xi_\dag\)}
+  \centering
+  \begin{tabular*}{0.75\columnwidth}{l @{\quad\quad\quad\quad} S S} \toprule
+    & \multicolumn{2}{c}{Grain composition} \\
+    Spectrum & {Graphite} & {Silicate}
+    \\ \midrule
+    B star & 1000 +- 400 & 350 +- 150 \\
+    O star & 3000 +- 500 & 2500 +- 500 \\
+    \bottomrule
+    \addlinespace
+    \multicolumn{3}{@{}p{0.75\columnwidth}@{}}{
+    Calculated from the Cloudy models shown in Figure~\ref{fig:drift-gn}. 
+    Uncertainties represent variations with grain size and gas density. 
+    See Appendix~\ref{sec:cloudy-models-dust} for further details.}
+  \end{tabular*}
+  \label{tab:Xi-rip}
+\end{table}
+
+As the dusty stream approaches the star, the radiation parameter
+\(\Xi\) will increase, with a dependence of \(R^{-2}\) once the stream
+is well inside the ionization front.  This increases \(f\rad\)
+(eq.~[\ref{eq:frad-Xi}]), but also increases the grain potential,
+\(\phi\) (eq.~[\ref{eq:phi-vs-Xi}]) due to the increasing dominance of
+grain charging by photoelectric ejection.  Initially, this results in
+a lowering of the equilibrium drift velocity to \(w_{10} \sim 0.01\) as
+the Coulomb drag kicks in (see Appendix~\ref{sec:cloudy-models-dust}).
+However, at smaller radii the slow logarithmic increase in
+\(\phi(\Xi)\) means that the drift velocity must start increasing again to
+accommodate the linear increase of \(f\rad(\Xi)\).  Eventually,
+\(f\rad\) exceeds \(f_{\mathrm{max}}\), the maximum drag force that
+proton Coulomb interactions can provide
+(eq.~[\ref{eq:fdrag-maximum}]).  This occurs at a critical value of
+the radiation parameter, which we denote the \textit{rip point}:
+\(\Xi_\dag \sim 1000\).  The variations in \(\Xi_\dag\) with star and grain
+parameters, which are of order \SI{+- 0.5}{dex}, are listed in
+Table~\ref{tab:Xi-rip} and illustrated graphically in
+Figure~\ref{fig:drift-gn}.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/existence-dust-wave}
+  \caption{Regions of stream parameter space \((v, n)\) where dust
+    waves may form around main-sequence OB stars of
+    \SIlist{10;20;40}{M_\odot} (see Tab.~\ref{tab:stars}).  Figure is
+    similar to Fig.~\ref{fig:zones-v-n-plane}, except that the
+    velocity axis is logarithmic and extends out to
+    \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show parameters
+    where dust waves may be allowed in the cases of large
+    (\(a = \SI{0.2}{\um}\)) and small (\(a = \SI{0.02}{\um}\))
+    graphite and silicate grains, as labeled in the left panel.  For
+    \((v, n)\) outside of these shapes, dust waves cannot occur for
+    the reasons indicated by labeled orange arrows in the center
+    panel.  Labeled dashed lines in the right panel show the
+    correspondence between the region boundaries and each dust wave
+    existence condition given in
+    equations~(\ref{eq:dust-wave-velocity-condition},
+    \ref{eq:dust-wave-low-density-condition},
+    \ref{eq:dust-wave-high-density-condition}). Heavy dashed lines in
+    the left panel show where the rip point and the drag-free
+    turnaround radius coincide.  Dust waves above these lines are drag
+    confined, while dust waves below the lines are inertia confined.
+  }
+  \label{fig:existence-dust-wave}
+\end{figure*}
+
+\subsubsection{Existence conditions for dust waves}
+\label{sec:exist-cond-separ}
+
+In order for a separate dust wave to exist, it is necessary for the
+grains to decouple from the incoming gas stream before the stream hits
+the hydrodynamic bow shock caused by the stellar wind.  The radius of
+the rip point, \(R_\dag\), can be expressed in terms of \(R_*\), the
+fiducial optically thick bow shock radius introduced in
+\S~\ref{sec:strong-gas-grain}:
+\begin{equation}
+  \label{eq:Rdag-over-Rstar}
+  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
+\end{equation}
+where we have made use of equations~\eqref{eq:Rstar}
+and~\eqref{eq:Xi-Prad-over-Pgas}.  The wind bow shock radius is
+\(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]), where \(\eta\) is the
+wind momentum efficiency (eq.~[\ref{eq:wind-eta-typical}]).
+Therefore, the condition \(R_\dag > R_0\) becomes
+\begin{equation}
+  \label{eq:dust-wave-velocity-condition}
+  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
+\end{equation}
+For O stars, the wind efficiency is generally high (\(\eta > 0.1\)) and
+\(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
+exist when the stream velocity is very high
+(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
+can be much weaker (\(\eta < 0.01\)) and \(\Xi_\dag\) is also smaller, so
+that dust waves are permitted by this criterion for much lower stream
+velocities: (\(v_\infty > \SI{30}{km.s^{-1}}\)).
+
+However, there are other conditions that need to be satisfied in order
+for the dust wave to exist.  For instance, the drag-free turnaround
+radius must also be outside the bow shock: \(R\starstar > R_0\),
+otherwise the radiation is incapable of repelling the grain
+opportunely, even once it has decoupled from the gas.  From
+equations~\eqref{eq:Rstar}, \eqref{eq:tau-star},
+and~\eqref{eq:dust-r0} we find
+\begin{equation}
+  \label{eq:Rstarstar-over-Rstar}
+  \frac{R\starstar}{R_*} = \frac{2 \sigma\grain \Qp \tau_*}{\kappa m\grain} \ , 
+\end{equation}
+so, if we define a single-grain opacity as
+\(\kappa\grain = \sigma\grain \Qp / m\grain\), then this condition becomes
+\begin{equation}
+  \label{eq:dust-wave-low-density-condition}
+  \tau_* >  \tau_{*,\text{min}} = 0.5\, \frac{\kappa}{\kappa\grain}\, \eta^{1/2} 
+  % \frac{\kappa \eta^{1/2}}{2 \kappa\grain}
+  \ . 
+\end{equation}
+The average value of the factor \(\kappa / \kappa\grain\) over the entire grain
+population must be equal to the dust--gas mass ratio,
+\(Z\grain \approx 0.01\), but the factor will vary between grains, according
+to their size and composition.\footnote{%
+  Remember that \(\kappa\) is the opacity per unit mass of gas, while
+  \(\kappa\grain\) is the opacity per unit mass of a particular grain. In
+  both cases, averaged over the stellar spectrum.} %
+In particular, it will be relatively larger for the largest grains
+(\(a \approx \SI{0.2}{\um}\)), which dominate the total dust mass, and
+smaller for the smaller grains (\(a \approx \SI{0.02}{\um}\)), which
+dominate the UV opacity.  Given the dependence of \(\tau_*\) on the
+stream parameters (eq.~[\ref{eq:taustar-typical}]), for a given
+stellar luminosity this condition corresponds to a minimum value for
+\(n / v_\infty^2\).
+
+A third condition comes from requiring \(R_\dag > R_0\) in the radiation
+bow wave regime (see \S~\ref{sec:three-bow-regimes}), where
+\(R_0 \approx 2 \tau_* R_*\).  This yields
+\begin{equation}
+  \label{eq:dust-wave-high-density-condition}
+  \tau_* < \tau_{*,\text{max}} = 0.5\, v_{10}\, \Xi_\dag^{-1/2} \ , 
+\end{equation}
+which, for a given stellar luminosity, corresponds to a maximum value
+for \(n / v_\infty^4\).  Thus, for a given stream velocity that satisfies
+equation~\eqref{eq:dust-wave-velocity-condition},
+equations~(\ref{eq:dust-wave-low-density-condition},
+\ref{eq:dust-wave-high-density-condition}) determine respectively the
+minimum and maximum stream density for which a dust wave can exist.
+
+The combined effects of the three conditions are illustrated in
+Figure~\ref{fig:existence-dust-wave} for each of the three example
+main sequence stars from Table~\ref{tab:stars}.  Further restrictions
+on the existence of dust waves arise when the effects of magnetic
+fields are considered, as will be discussed in
+\S~\ref{sec:magn-effects-grain} below.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/dust-wave-phase-trajectories-annotate}
+  \caption{Trajectories of small graphite grains
+    (\(a = \SI{0.02}{\um}\)) at impact parameter \(b = 0\) for two
+    example cases (see yellow ``+'' symbols in left panel of
+    Fig.~\ref{fig:existence-dust-wave}), which differ only in the
+    stream velocity: \(v = \SI{40}{km.s^{-1}}\) (left panels) and
+    \SI{80}{km.s^{-1}} (right panels).  In both cases, the stream
+    density is \(n = \SI{1}{cm^{-3}}\) and the central star is a
+    \SI{10}{M_\odot} main-sequence B star (see Tab.~\ref{tab:stars}).
+    Upper panels show the evolution of grain radius, \(R\) (blue
+    curve, normalized by the rip point radius, \(R_\dag\)), and grain
+    velocity, \(v\) (orange curve, normalized by the gas stream
+    velocity).  The origin of the time axis is set to the moment of
+    closest approach of the grain to the star: \(R = \Rmin\).  Lower
+    panels show the trajectories in phase space: position versus
+    gas--grain relative slip velocity (\(w = \abs{v - v_\infty}\)).  Filled
+    contours show the net force on the grain: \(f\rad - f\drag\), with
+    positive values in blue and negative values in red.  The heavy
+    dotted line shows where there is no net force: \(f\rad = f\drag\).
+    The grain trajectory (thick, solid black line with arrows)
+    initially follows this line, but departs from it after the rip
+    point. In the left panel, the grain enters a limit cycle between
+    decoupling (rip) and re-coupling (snap back).  In the right panel,
+    the grain spirals in on the stagnant drift point.  See text for
+    further details.}
+    \label{fig:phase-space-trajectories}
+\end{figure*}
+
+\subsubsection{Grain trajectories along the symmetry axis}
+\label{sec:grain-traj-along}
+
+What happens to the dust grain following this catastrophic breakdown
+of gas--grain coupling depends on the relation between the rip point
+radius, \(R_\dag\), and the drag-free radiative turnaround radius,
+\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
+will still carry it in as far as \(R\starstar\) and the initial
+trajectory will be almost identical to that described in
+Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
+being turned around by the radiation field and pushed out past
+\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
+dragged back for a second approach.\footnote{If the initial impact
+  parameter of the trajectory is not strictly \(b = 0\), then the
+  resultant lateral component of \(f\rad\) will mean that \(b\) will
+  be much increased for the second approach.} %
+We will refer to this as an \textit{inertia-confined dust wave}.  From
+equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
+\ref{eq:dust-wave-high-density-condition}), the condition
+\(R_\dag > R\starstar\) corresponds to
+\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
+lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
+on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
+by the gas carries the grain closer to the star than its inertia would
+naturally take it.  When the grain finally decouples at \(R_\dag\) it
+experiences a much higher unbalanced \(f\rad\), which can initially
+accelerate it to outward velocities significantly higher than the
+inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
+as a \textit{drag-confined dust wave}.
+
+The post-decoupling behavior of the grain depends on the sign of
+\(d f\drag / d w\) when \(w = \abs{v_\infty}\).  If this derivative is
+positive, as is the case in drag regimes~II and V (see
+Tab.~\ref{tab:fdrag-regimes} and Fig.~\ref{fig:drag-v-phi-plane}),
+then the grain can reach a stable equilibrium drift at rest with
+respect to the star\footnote{%
+  Again, this is only strictly true when the impact parameter is zero.
+  However, as we show below, it is a reasonable approximation over a
+  range of impact parameters in the case where the angle between the
+  magnetic field direction and the stream velocity is not too
+  large.} %
+at a point \(R_\ddag\), which we call the \textit{stagnant drift
+  radius}. If the stream velocity is not excessively high
+(\(v_\infty < \SI{150}{km.s^{-1}}\) when \(\phi = 4\), or
+\(< \SI{300}{km.s^{-1}}\) when \(\phi = 16\)), then the equilibrium
+\(f\rad\) is less than the value at the rip point, requiring a lower
+value of the radiation parameter: \(\Xi_\ddag < \Xi_\dag\).  The resultant
+stagnant drift radius is therefore outside the rip point:
+\(R_\ddag > R_\dag\).
+
+On the other hand, if \(d f\drag / d w < 0\) when
+\(w = \abs{v_\infty}\), then the equilibrium is unstable and no stagnant
+drift is possible.  This occurs for drag regime~IV, which applies when
+\(\phi > 1\) and
+\(\SI{10}{km.s^{-1}} < v_\infty < \SI{50}{km.s^{-1}}\).  There is also a
+second unstable regime (partially visible in the upper-right corner of
+Fig.~\ref{fig:drag-v-phi-plane}), which is related to the thermal peak
+in the electron Coulomb drag when \(\phi > 30\) and
+\(\SI{400}{km.s^{-1}} < v_\infty < \SI{2000}{km.s^{-1}}\), but this is not
+relevant to bow shocks around OB~stars.\footnote{%
+  It may apply in other contexts, such as outflows from AGN, since
+  detailed modeling of grain charging around quasars
+  \citep{Weingartner:2006a} implies that grain potentials as high as
+  \(\phi \sim 100\) can be achieved.} %
+
+An example of each of these two behaviors is illustrated in
+Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
+case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
+regime, resulting in periodic ``limit-cycle'' behavior (the parameters
+of this model correspond to the yellow ``plus'' symbol labeled ``40''
+in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
+grain's first approach, it starts to follow a phase trajectory (lower
+left panel) along the \(f\rad - f\drag = 0\) contour, corresponding to
+equilibrium drift, in which the grain begins to move a few
+\si{km.s^{-1}} slower than the gas stream.  Then, when it reaches the
+rip point (\(R = R_\dag\), \(w \approx \SI{10}{km.s^{-1}}\)) it suddenly
+experiences a large unbalanced outward radiation force (blue region of
+phase space in Fig.~\ref{fig:phase-space-trajectories}). The grain's
+inward momentum carries it to the point \(\Rmin \approx 0.85 R_\dag\), before
+it is expelled at roughly twice the inflow speed.  However, after
+moving outward, it finds itself in a drag-dominated region of phase
+space (red in the figure), and so recouples to the inflowing gas
+stream.  The recoupling initiates gradually, as the grain's outward
+motion is slowed and it begins to move inward again, but is completed
+suddenly once \(w\) again falls below \SI{10}{km.s^{-1}}, in what we
+term \textit{snap back}. The net result is that the grain has returned
+to exactly the same phase track that it started in on, and so repeats
+the cycle indefinitely.
+
+The right panels of Figure~\ref{fig:phase-space-trajectories} show the
+case where the stream velocity is doubled to
+\(v_\infty = \SI{80}{km.s^{-1}}\), but all other parameters remain the
+same.  At this velocity, the equilibrium drift is stable and so the
+grain can achieve a stagnant drift solution, where it is stationary
+with respect to the star.  The trajectory during the first approach is
+similar to the previous case, except that the overshoot of the rip
+point is greater, so that \(\Rmin \approx 0.65 R_\dag\) in this case.  This is
+a consequence of the fact that the rip point is closer to the
+drag-free turnaround radius (\(R_\dag / R\starstar\) is larger than in
+the lower velocity case), so that the grain inertia is relatively more
+important.  A second consequence of this is that the speed of the
+initial expulsion is not so large, being only a little higher than the
+inflow velocity.  The qualitative difference between the two cases
+emerges after the first recoupling: instead of the snap back and
+endless limit cycle, the grain oscillates about the stagnant drift
+radius with ever decreasing amplitude, so that after a few oscillation
+periods it has come to almost a complete rest.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/onaxis-stats-plot-MS10-v080-gra002}
+  \caption{Bow radius as a function of stream density for a stream of
+    initial velocity \SI{80}{km.s^{-1}}, which interacts with a
+    \SI{10}{M_\odot} main-sequence B~star.  This corresponds to a vertical
+    slice through the left panel of
+    Fig.~\ref{fig:existence-dust-wave}.  At low densities, the
+    hydrodynamic bow shock (blue line) is larger than the drag-free
+    turnaround radius for small carbon grains, meaning that a grain's
+    inertia carries it into the bow shock along with the gas, even
+    though the gas--grain coupling is not particularly strong.  At
+    densities above about \SI{0.05}{cm^{-3}}, however, this is no
+    longer true and a separate dust wave forms outside of the
+    hydrodynamic bow shock, which is now dust-free (green dashed
+    line).  The grains in the dust wave will occupy a range of radii
+    (pale orange shading) between \(\Rmin\) (solid orange line) and
+    \(R_\ddag\), the stagnant drift radius.  At densities above about
+    \SI{1000}{cm^{-3}}, the gas stream starts to feel the effect of
+    passing through the dust wave, and above \SI{3e4}{cm^{-3}}, the
+    dust wave and bow shock merge to form a radiative bow wave (red
+    line), which becomes an optically thick radiative bow shock
+    (purple line) above \SI{e6}{cm^{-3}}.}
+  \label{fig:decouple-vertical-cut}
+\end{figure}
+
+\subsubsection{Back reaction on the gas flow}
+\label{sec:back-reaction-gas}
+
+So far we have ignored the effect of the drag force on the gas stream
+itself, but it is clear that this must become important as \(\tau_*\)
+approaches \(\tau_{*,\text{max}}\), since that is the point where the
+dust wave transitions to a bow wave, in which the dust and gas are
+perfectly coupled.  A full treatment of this problem would require
+solving the hydrodynamic equations simultaneously with the equations
+of motion of the dust grains, which is beyond the scope of this paper.
+Instead, we outline a heuristic approach that qualitatively captures
+the physics involved.
+
+The maximum drag force experienced by a grain is at the rip point.
+Since the grain follows a zero-net-force phase track up until that
+point, this can be written with the help of
+equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0}) as
+\begin{equation}
+  \label{eq:fdrag-max}
+  f\drag (R_\dag) = f\rad(R_\dag) =   \frac{m\grain v_\infty^2 R\starstar}{ 2 R_\dag^2} 
+\end{equation}
+The timescale of the flow can be characterized by the crossing time
+\(R_\dag / v_\infty\), but the residence time of the grain at the bow apex
+will be several times larger than this (see previous section).  On the
+other hand, the average drag force during this residence will be
+several times smaller than \(f\drag (R_\dag)\) if
+\(R_\ddag > R_\dag\), which is typically the case.  We therefore parameterize
+our ignorance via a dimensionless factor, \(\alpha\), which we expect to be
+of order unity, and write the total impulse imparted to the grain by
+drag as
+\begin{equation}
+  \label{eq:grain-impulse}
+  J\drag \equiv \int \!f\drag \, dt \approx \alpha f\drag (R_\dag) \frac{R_\dag}{v_\infty}
+  = \tfrac12 \alpha \, m\grain v_\infty \, \frac{R\starstar}{R_\dag} \ .
+\end{equation}
+
+By Newton's Third Law, an equal and opposite impulse is imparted to
+the gas, which will act to decelerate the gas stream as it decouples
+from the grains.  Realistically, \(J\drag\) should be summed over the
+grain size distribution, but for simplicity we assume that all grains
+are identical, so that the mass of gas that accompanies each grain is
+given by
+\begin{equation}
+  \label{eq:gas-mass}
+  m_{\text{gas}} = \frac{m\grain}{Z\grain} =  m\grain \, \frac{\kappa\grain}{\kappa} \ . 
+\end{equation}
+If the gas remains supersonic after decoupling, then thermal pressure
+can be ignored and the gas will suffer a change in momentum equal to
+\(J\drag\), so that its velocity is reduced by
+\(\Delta v = J\drag / m_{\text{gas}}\), which by
+equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
+\ref{eq:dust-wave-high-density-condition}, \ref{eq:grain-impulse},
+\ref{eq:gas-mass}) is
+\begin{equation}
+  \label{eq:gas-dv}
+  \Delta v = \tfrac12 \alpha \frac{\tau_*}{\tau_{*, \text{max}}} \ .
+\end{equation}
+This deceleration reduces the gas stream's ram pressure before it
+interacts with the central star's stellar wind.  The radius of the
+dust-free bow shock formed by this interaction is therefore increased
+by a factor \((1 - \Delta v / v_\infty)^{-1}\) with respect to the case
+calculated in \S~\ref{sec:three-bow-regimes}, yielding
+\begin{equation}
+  \label{eq:gas-free-bow-shock}
+  R_{\text{dfbs}} \approx \frac{\eta^{1/2} R_*}{1 - \tfrac12 \alpha \tau_* / \tau_{*, \text{max}}} \ .
+\end{equation}
+
+An example is illustrated in Figure~\ref{fig:decouple-vertical-cut},
+where the dust-free bow shock radius is shown by the green dashed line
+as a function of stream density, \(n\).  This is calculated for fixed
+stream velocity and grain and star properties, so that
+\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).  In order for
+\(R_{\text{dfbs}}\) to match the dust-wave and bow-wave radii at the
+point where they cross at \(\tau_* = \tau_{*, \text{max}}\), we find
+\(\alpha \approx 1.5\) is required.  It can be seen that the gas deceleration is
+negligible over most of the density range for which a separate dust
+wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does
+\(R_{\text{dfbs}}\) begin to curve up from the general \(n^{-1/2}\)
+trend, becoming essentially flat at a value
+\(R_{\text{dfbs}} \approx (\kappa/\kappa\grain) R\starstar\) until full-coupling is
+established at \(n > \SI{3e4}{cm^{-3}}\).  Note, however, that the
+treatment described here is very approximate: it does not take into
+account the shock that will form once \(J\drag\) reaches an
+appreciable fraction of \(m_{\text{gas}} v_\infty\) and, additionally, it
+includes a factor, \(\alpha\), whose value has not been rigorously
+justified.  More detailed modeling is required to fully understand the
+bow behavior in this transition regime.
+
+\subsubsection{Magnetic effects on grain trajectories }
+\label{sec:magn-effects-grain}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/frozen-stream-map-multi}
+  \caption{Drag-confined dust waves with tight magnetic coupling.
+    Upper panels show a quasi-parallel field, \(\theta\B = \ang{10}\),
+    while lower panels show a quasi-perpendicular field,
+    \(\theta\B = \ang{75}\).  Left panels show an incident stream velocity of
+    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels show
+    \(v_\infty = \SI{80}{km.s^{-1}}\).  In all cases, the stream density is
+    \(n = \SI{10}{cm^{-3}}\) and the calculations are performed for
+    small graphite grains, \(a = \SI{0.02}{\um}\), and the
+    \SI{10}{M_\odot} main-sequence B~star.  Continuous black lines show
+    grain trajectories, with triplets of colored symbols indicating
+    the progress of individual cohorts, which entered from the right
+    edge at a particular time.  Continuous blue lines show the
+    magnetic field, which flows from right to left along with the
+    incident stream.  The radius of the rip point, \(R_\dag\), and the
+    stagnant drift point, \(R_\ddag\), are shown respectively by red and
+    blue dashed lines.  The approximate shape of the wind-supported
+    bow shock is shown by the dotted gray line.  The calculations are
+    no longer valid after trajectories cross this surface.}
+  \label{fig:frozen-stream}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/frozen-trajectories-multi}
+  \caption{Sample grain trajectories for drag-confined dust waves with
+    tight magnetic coupling.}
+  \label{fig:frozen-trajectories}
+\end{figure}
+
+An important effect that we have not considered up to now is the
+Lorentz force on charged grains due to the plasma's magnetic field:
+\begin{equation}
+  \label{eq:f-lorentz}
+  \bm{f}\!\B = \frac{z\grain e}{c} \, \bm{w} \times \bm{B} \ . 
+\end{equation}
+The direction of the force is perpendicular both to the magnetic
+field, \(\bm{B}\), and to the relative velocity, \(\bm{w}\), of the
+grain with respect to the plasma.  If \(\bm{w}\) and \(\bm{B}\) (as
+seen by the grain) are changing slowly, compared with the
+gyrofrequency, \(\omega\B = z\grain e B / m\grain c\), then the grain
+motion perpendicular to \(\bm{B}\) is constrained to be a circle of
+radius equal to the Larmor radius:
+\begin{equation}
+  \label{eq:Larmor}
+  r\B = \frac{m\grain c w_\perp} {\abs{z\grain} e B} \ ,
+\end{equation}
+where \(B = \abs{\bm{B}}\) and \(w_\perp\) is the perpendicular component
+of \(\bm{w}\).  The component of \(\bm{w}\) parallel to \(\bm{B}\) is
+unaffected by \(\bm{f}\!\B\), so the resultant trajectory is helical.
+
+The relative importance of the magnetic field can be characterized by
+the ratio of the Larmor radius to the minimum radius, \(\Rmin\),
+reached by the grain in the dust wave (see
+\S~\ref{sec:grain-traj-along}), where \(\Rmin \approx R_\dag\) for
+drag-confined dust waves, or \(\Rmin \approx R\starstar\) for
+inertia-confined dust waves.  We write the field strength in terms of
+the Alfvén speed,
+\begin{equation}
+  \label{eq:alfven}
+  v\alfven = \frac{B}{(4\pi\rho\gas)^{1/2}}
+  = 1.9\, \frac{B}{\si{\micro G}} n^{-1/2} \, \si{km.s^{-1}} \ ,
+\end{equation}
+and the grain charge \(z\grain e\) in terms of the potential \(\phi\) (eq.~[\ref{eq:phi-potential}]) to obtain
+\begin{equation}
+  \label{eq:larmor-over-Rdag}
+  \frac{r\B}{R_\dag} = 0.0140 \,
+  a_{\si{\um}}^2 \,
+  \frac{w_\perp}{v\alfven} \,
+  \left( \frac{\Xi_\dag}{L_4 T_4} \right)^{1/2}
+  \frac{\rho\grain}{\phi_\dag}
+\end{equation}
+and
+\begin{equation}
+  \label{eq:larmor-over-Rstarstar}
+  \frac{r\B}{R\starstar} = 0.0544 \,
+  a_{\si{\um}}^3 \,
+  \frac{w_\perp}{v\alfven} \,
+  \frac{v_{10}^2 }{n^{1/2}} \,
+  \frac{1}{L_4 T_4} \,
+  \frac{\rho\grain^2}{\Qp \phi\starstar} \ ,
+\end{equation}
+where \(a_{\si{\um}} = a / \SI{1}{\um}\), \(\rho\grain\) is the grain
+material density in \si{g.cm^{-3}}, and we have made use of
+equations~(\ref{eq:Rstar-typical}, \ref{eq:Rdag-over-Rstar},
+\ref{eq:dust-r0}).
+
+If \(r\B / \Rmin \ll 1\), then the grains are so strongly coupled to the
+field that they can be treated in the guiding-center approximation, in
+which the trajectory is decomposed into a tight circular gyromotion
+around the field lines, plus a sliding of the guiding center along the
+field lines, which is governed by the radiation and drag forces (the
+slow \(\bm{f} \times \bm{B}\) drift across the field lines is negligible in
+this case, see App.~\ref{sec:tight-magn-coupl}).  In the opposite
+limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
+results of the previous sections are scarcely modified.  Assuming
+\(w_\perp \sim v_\infty\) and adopting a threshold of
+\(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
+\ref{eq:larmor-over-Rstarstar}) can be transformed into conditions on
+the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
+will apply: \newcommand\freeze{\ensuremath{_{\text{tight}}}}
+\begin{equation}
+  \label{eq:velocity-strong-B-coupling}
+  v_{\infty} < v\freeze \approx
+  \begin{cases}
+    \text{drag-confined:}
+    & 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2}\\
+    \text{inertia-confined:}
+    & 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \\
+  \end{cases} \ ,
+\end{equation}
+where we have substituted typical values of the minor parameters
+\(\Xi_\dag\), \(\phi_{\dag}\), \(\phi_{**}\), \(\rho\grain\),
+\(T_4\).\footnote{%
+  The most significant systematic variation in \(v\freeze\) from these
+  suppressed parameters is due to grain composition, yielding slightly
+  higher values for graphite than for silicate (\SI{+-0.15}{dex}).} %
+It is apparent that \(v\freeze\) is very sensitive to the grain size.
+For instance, taking a typical \hii{} region value of
+\(v\alfven = \SI{2}{km.s^{-1}}\) \citep{Arthur:2011a} and
+\(L_4 = 0.63\) (Tab.~\ref{tab:stars}, B1.5~V star), then for the
+drag-confined case \(v\freeze \approx \SI{30}{km.s^{-1}}\) for \SI{0.2}{\um}
+grains but \(v\freeze \approx \SI{3000}{km.s^{-1}}\) for \SI{0.02}{\um}
+grains. Thus, for typical stream velocities of
+\SIrange{20}{100}{km.s^{-1}}, the small grains are always tightly
+coupled to the magnetic field, but the large grains are only loosely
+coupled for the faster streams.
+
+We can now investigate how the results of the previous sections are
+modified by magnetic fields in the tight coupling limit.  For
+simplicity, we assume a uniform field in the incoming stream, with
+field lines oriented at an angle \(\theta\B\) to the velocity vector that
+defines the bow axis.  We also assume a super-alfvénic stream,
+\(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
+is unaffected by the magnetic field, and additionally assume
+\(\tau_* \ll \tau_{*, \text{max}}\), so that the back-reaction of the grain
+drag on the plasma is negligible (see previous section) and \(B\)
+remains uniform in magnitude and direction in the dust wave region,
+outside of the bow shock.
+
+In Appendix~\ref{sec:tight-magn-coupl}, we derive results in the limit
+of zero gas--grain drag, which is appropriate for inertia-confined dust
+waves. We find very different structures, depending on the orientation
+of the field.  For a parallel field (Fig.~\ref{fig:inertia-thB0}), the
+apex of the dust wave occurs at the same point, \(R\starstar\), as in
+the non-magnetic case, but the shape of the dust wave wings is more
+closed, being hemispherical rather than parabolic in shape.  For a
+perpendicular field (Fig.~\ref{fig:inertia-thB90}), on the other hand,
+grains in the apex region are dragged very close to the star and no
+dust wave forms there.  A dust wave can form in the wings, with impact
+parameter \(> R\starstar\), which is roughly parabolic in shape, but
+more swept-back than in the non-magnetic case.  Whether such a dust
+wave will exist in practice depends critically on the size and shape
+of the MHD wind-supported bow shock.
+
+In Figures~\ref{fig:frozen-stream} and~\ref{fig:frozen-trajectories}
+we show example results for drag-confined dust waves. Apart from the
+inclusion of the magnetic field, the model parameters are the same as
+used in Figure~\ref{fig:phase-space-trajectories}, with the exception
+that the stream density is increased to \SI{10}{cm^{-3}}.\footnote{The
+  reason for using a higher density is to decrease the amplitude of
+  the radial oscillations of the trajectories, which allows the dust
+  wave structure to be more clearly perceived in the figures. } This
+time, we use quasi-parallel (\(\theta\B = \ang{10}\)) and
+quasi-perpendicular (\(\theta\B = \ang{75}\)) field orientations.  The
+quasi-parallel field is closest to the non-magnetic case, and the
+models shown in the two upper panels of Figure~\ref{fig:frozen-stream} closely parallel the cases shown in Figure~\ref{fig:phase-space-trajectories}, with a limit cycle behavior when \(v_\infty = \SI{40}{km.s^{-1}}\) and stagnant drift when \(v_\infty = \SI{80}{km.s^{-1}}\).
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock"
+%%% TeX-master: "dusty-bow-wave"
 %%% End:
 
-\message{ !name(quadrics-bowshock.tex) !offset(-137) }
+\message{ !name(dusty-bow-wave.tex) !offset(-1513) }
 

### 2018-06-29 papers/Papers1234/sec-dust-bow-intro.tex
Reorganize and expand existence condition part

--- 2018-06-26 papers/Papers1234/sec-dust-bow-intro.tex
@@
 
+What happens to the dust grain following this catastrophic breakdown
+of gas--grain coupling depends on the relation between the rip point
+radius, \(R_\dag\), and the drag-free radiative turnaround radius,
+\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
+will still carry it in as far as \(R\starstar\) and the initial
+trajectory will be almost identical to that described in
+Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
+being turned around by the radiation field and pushed out past
+\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
+dragged back for a second approach.\footnote{If the initial impact
+  parameter of the trajectory is not strictly \(b = 0\), then the
+  resultant lateral component of \(f\rad\) will mean that \(b\) will
+  be much increased for the second approach.} %
+We will refer to this as an \textit{inertia-confined dust wave}.  From
+equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
+\ref{eq:dust-wave-high-density-condition}), the condition
+\(R_\dag > R\starstar\) corresponds to
+\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
+lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
+on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
+by the gas carries the grain closer to the star than its inertia would
+naturally take it.  When the grain finally decouples at \(R_\dag\) it
+experiences a much higher unbalanced \(f\rad\), which can initially
+accelerate it to outward velocities significantly higher than the
+inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
+as a \textit{drag-confined dust wave}.
+
 \begin{figure*}
@@
 
-In order for a separate dust wave to exist, it is necessary for the
-grains to decouple from the incoming gas stream before the stream hits
-the hydrodynamic bow shock caused by the stellar wind.  The radius of
-the rip point, \(R_\dag\), can be expressed in terms of \(R_*\), the
-fiducial optically thick bow shock radius introduced in
+In order for a separate outer dust wave to exist, it is necessary for
+the grains to decouple from the incoming gas stream before the stream
+hits the hydrodynamic bow shock caused by the stellar wind.  The
+radius of the rip point, \(R_\dag\), can be expressed in terms of
+\(R_*\), the fiducial optically thick bow shock radius introduced in
 \S~\ref{sec:strong-gas-grain}:
@@
 fields are considered, as will be discussed in
-\S~\ref{sec:magn-effects-grain} below.
+\S~\ref{sec:magn-effects-grain} below.  Note that the three conditions
+are restrictions solely on the formation of an \textit{outer} dust
+wave, that is, outside of the wind-supported hydrodynamic bow shock.
+In the case of the equation~\eqref{eq:dust-wave-low-density-condition}
+condition, there is a further possibility: if the gas--grain coupling
+(and magnetic coupling) is so weak that it is still unimportant at the
+higher densities found in the bow shock shell, then an
+inertia-confined \textit{inner} dust wave may form inside the bow
+shock, even when \(t_* < \tau_{*,\text{min}}\).  Although the same might
+be thought to apply to the condition of
+equation~\eqref{eq:dust-wave-velocity-condition}, this is not the
+case, since the density compression in the bow shock will reduce the
+radiation parameter, \(\Xi\), which moves the rip point, \(R_\dag\), to an
+even smaller radius.  Therefore, if radiation has not managed to
+decouple a grain before it passes through the shock, it is unlikely to
+be able to do it afterwards.
 
@@
 
-What happens to the dust grain following this catastrophic breakdown
-of gas--grain coupling depends on the relation between the rip point
-radius, \(R_\dag\), and the drag-free radiative turnaround radius,
-\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
-will still carry it in as far as \(R\starstar\) and the initial
-trajectory will be almost identical to that described in
-Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
-being turned around by the radiation field and pushed out past
-\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
-dragged back for a second approach.\footnote{If the initial impact
-  parameter of the trajectory is not strictly \(b = 0\), then the
-  resultant lateral component of \(f\rad\) will mean that \(b\) will
-  be much increased for the second approach.} %
-We will refer to this as an \textit{inertia-confined dust wave}.  From
-equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
-\ref{eq:dust-wave-high-density-condition}), the condition
-\(R_\dag > R\starstar\) corresponds to
-\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
-lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
-on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
-by the gas carries the grain closer to the star than its inertia would
-naturally take it.  When the grain finally decouples at \(R_\dag\) it
-experiences a much higher unbalanced \(f\rad\), which can initially
-accelerate it to outward velocities significantly higher than the
-inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
-as a \textit{drag-confined dust wave}.
-
 The post-decoupling behavior of the grain depends on the sign of
@@
   \label{eq:gas-dv}
-  \Delta v = \tfrac12 \alpha \frac{\tau_*}{\tau_{*, \text{max}}} \ .
+  \Delta v = \tfrac12 \alpha \frac{\tau_*}{\tau_{*, \text{max}}} v_\infty\ .
 \end{equation}
@@
 around the field lines, plus a sliding of the guiding center along the
-field lines, which is governed by the radiation and drag forces (we
-ignore the slow \(\bm{f} \times \bm{B}\) drift across the field lines).  In
-the opposite limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak
-that the results of the previous sections are scarcely modified.
-Assuming \(w_\perp \sim v_\infty\) and adopting a threshold of
+field lines, which is governed by the radiation and drag forces (the
+slow \(\bm{f} \times \bm{B}\) drift across the field lines is negligible in
+this case, see App.~\ref{sec:tight-magn-coupl}).  In the opposite
+limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
+results of the previous sections are scarcely modified.  Assuming
+\(w_\perp \sim v_\infty\) and adopting a threshold of
 \(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
@@
 the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
-will apply:
-\newcommand\freeze{\ensuremath{_{\text{tight}}}}
+will apply: \newcommand\freeze{\ensuremath{_{\text{tight}}}}
 \begin{equation}
@@
 
-We now investigate how the results of the previous sections are
+We can now investigate how the results of the previous sections are
 modified by magnetic fields in the tight coupling limit.  For
@@
 \(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
-is unaffected, and take \(t_* \ll \tau_{*, \text{max}}\), so that the
-back-reaction of the grain drag on the plasma is negligible (see
-previous section) and \(B\) remains uniform in magnitude and direction
-in the dust wave region, outside of the bow shock.  In
-Appendix~\ref{sec:tight-magn-coupl}, we derive results in the limit of
-zero gas--grain drag, which is appropriate for inertia-confined dust
-waves.
+is unaffected by the magnetic field, and additionally assume
+\(\tau_* \ll \tau_{*, \text{max}}\), so that the back-reaction of the grain
+drag on the plasma is negligible (see previous section) and \(B\)
+remains uniform in magnitude and direction in the dust wave region,
+outside of the bow shock.
+
+In Appendix~\ref{sec:tight-magn-coupl}, we derive results in the limit
+of zero gas--grain drag, which is appropriate for inertia-confined dust
+waves. We find very different structures, depending on the orientation
+of the field.  For a parallel field (Fig.~\ref{fig:inertia-thB0}), the
+apex of the dust wave occurs at the same point, \(R\starstar\), as in
+the non-magnetic case, but the shape of the dust wave wings is more
+closed, being hemispherical rather than parabolic in shape.  For a
+perpendicular field (Fig.~\ref{fig:inertia-thB90}), on the other hand,
+grains in the apex region are dragged very close to the star and no
+dust wave forms there.  A dust wave can form in the wings, with impact
+parameter \(> R\starstar\), which is roughly parabolic in shape, but
+more swept-back than in the non-magnetic case.  Whether such a dust
+wave will exist in practice depends critically on the size and shape
+of the MHD wind-supported bow shock.
+
+In Figures~\ref{fig:frozen-stream} and~\ref{fig:frozen-trajectories}
+we show example results for drag-confined dust waves. Apart from the
+inclusion of the magnetic field, the model parameters are the same as
+used in Figure~\ref{fig:phase-space-trajectories}, with the exception
+that the stream density is increased to \SI{10}{cm^{-3}}.\footnote{The
+  reason for using a higher density is to decrease the amplitude of
+  the radial oscillations of the trajectories, which allows the dust
+  wave structure to be more clearly perceived in the figures. } This
+time, we use quasi-parallel (\(\theta\B = \ang{10}\)) and
+quasi-perpendicular (\(\theta\B = \ang{75}\)) field orientations.  The
+quasi-parallel field is most similar to the non-magnetic case, and the
+models shown in the two upper panels of Figure~\ref{fig:frozen-stream}
+closely mirror the cases shown in
+Figure~\ref{fig:phase-space-trajectories}, with a limit cycle behavior
+when \(v_\infty = \SI{40}{km.s^{-1}}\) and stagnant drift when
+\(v_\infty = \SI{80}{km.s^{-1}}\).  The principle difference from the 1-D
+axial trajectories discussed in \S~\ref{sec:grain-traj-along} is that
+the small \ang{10} misalignment of \(\bm{B}\) from the incident stream
+direction causes a slow sideways migration, which puts a finite limit
+on the time a grain can reside in front of the star.  This can be
+appreciated more clearly in Figure~\ref{fig:frozen-trajectories},
+which shows the grain position and velocity along a sample streamline
+with initial impact parameter \(b = -0.4 R_\dag\) for the two
+quasi-parallel models.  In panel~a, we see the same rip-and-snap-back
+cycle of de-coupling and re-coupling that was discussed previously,
+but only two periods of the cycle are completed before the grain's
+lateral migration takes it as far as \(y \approx +R_\dag\), at which point
+nothing can stop the gas stream from dragging it past the star and
+away.
 

### 2018-06-30 papers/Papers1234/sec-dust-bow-intro.tex
Finish description of quasi-parallel cases

@@
 Table~\ref{tab:Xi-rip} and illustrated graphically in
-Figure~\ref{fig:drift-gn}.
+Figure~\ref{fig:drift-gn}.  The radius of the rip point, \(R_\dag\), can
+be expressed in terms of \(R_*\), the fiducial optically thick bow
+shock radius introduced in \S~\ref{sec:strong-gas-grain}:
+\begin{equation}
+  \label{eq:Rdag-over-Rstar}
+  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
+\end{equation}
+where we have made use of equations~\eqref{eq:Rstar}
+and~\eqref{eq:Xi-Prad-over-Pgas}.
 
@@
 the grains to decouple from the incoming gas stream before the stream
-hits the hydrodynamic bow shock caused by the stellar wind.  The
-radius of the rip point, \(R_\dag\), can be expressed in terms of
-\(R_*\), the fiducial optically thick bow shock radius introduced in
-\S~\ref{sec:strong-gas-grain}:
-\begin{equation}
-  \label{eq:Rdag-over-Rstar}
-  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
-\end{equation}
-where we have made use of equations~\eqref{eq:Rstar}
-and~\eqref{eq:Xi-Prad-over-Pgas}.  The wind bow shock radius is
-\(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]), where \(\eta\) is the
-wind momentum efficiency (eq.~[\ref{eq:wind-eta-typical}]).
-Therefore, the condition \(R_\dag > R_0\) becomes
+hits the hydrodynamic bow shock caused by the stellar wind.  The wind
+bow shock radius is \(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]),
+where \(\eta\) is the wind momentum efficiency
+(eq.~[\ref{eq:wind-eta-typical}]).  Therefore, the condition
+\(R_\dag > R_0\) becomes from equation~\eqref{eq:Rdag-over-Rstar}:
 \begin{equation}
@@
 inertia-confined \textit{inner} dust wave may form inside the bow
-shock, even when \(t_* < \tau_{*,\text{min}}\).  Although the same might
+shock, even when \(\tau_* < \tau_{*,\text{min}}\).  Although the same might
 be thought to apply to the condition of
@@
 when \(v_\infty = \SI{40}{km.s^{-1}}\) and stagnant drift when
-\(v_\infty = \SI{80}{km.s^{-1}}\).  The principle difference from the 1-D
-axial trajectories discussed in \S~\ref{sec:grain-traj-along} is that
-the small \ang{10} misalignment of \(\bm{B}\) from the incident stream
-direction causes a slow sideways migration, which puts a finite limit
-on the time a grain can reside in front of the star.  This can be
-appreciated more clearly in Figure~\ref{fig:frozen-trajectories},
-which shows the grain position and velocity along a sample streamline
-with initial impact parameter \(b = -0.4 R_\dag\) for the two
-quasi-parallel models.  In panel~a, we see the same rip-and-snap-back
-cycle of de-coupling and re-coupling that was discussed previously,
-but only two periods of the cycle are completed before the grain's
-lateral migration takes it as far as \(y \approx +R_\dag\), at which point
-nothing can stop the gas stream from dragging it past the star and
-away.
+\(v_\infty = \SI{80}{km.s^{-1}}\).
+
+The principle difference from the 1-D axial trajectories discussed in
+\S~\ref{sec:grain-traj-along} is that the small \ang{10} misalignment
+of \(\bm{B}\) from the incident stream direction causes a slow
+sideways migration, which puts a finite limit on the time a grain can
+reside in front of the star.  This can be appreciated more clearly in
+Figure~\ref{fig:frozen-trajectories}, which shows the grain position
+and velocity along a sample streamline with initial impact parameter
+\(b = -0.4 R_\dag\) for the two quasi-parallel models.  In panel~a,
+corresponding to \(v_\infty = \SI{40}{km.s^{-1}}\), we see the same
+rip-and-snap-back cycle of de-coupling and re-coupling that was
+discussed previously, but only two periods of the cycle are completed
+before the grain's lateral migration takes it as far as
+\(y \approx +R_\dag\), at which point nothing can stop the gas stream from
+dragging it past the star and away.  All told, the grain remains in
+the apex region for about \(1/\sin\theta\B\) times longer than the crossing
+time, \(R_\dag / v_\infty\).
+
+In panel~b, corresponding to \(v_\infty = \SI{80}{km.s^{-1}}\), the grain
+settles for a while around the stagnant drift radius, \(R_\ddag\), after
+the initial rip and turn around.  Again, it slowly migrates sideways,
+and eventually recouples to the incident stream, but this time after
+reaching \(y \approx +R_\ddag\).  The grain residence time in the apex region,
+measured in crossing times, is slightly longer than in panel~a, but is
+of the same order.  In both these cases, a second, exterior dense
+shell is formed in addition to the hemispherical one produced by the
+initial turn around inside \(R_\dag\). In the limit-cycle case, it forms
+at the snap-back point, while in the stagnant-drift case, it forms at
+\(R_\ddag\) and is significantly denser than the interior shell (upper
+right panel of Fig.~\ref{fig:frozen-stream}).
 

### 2018-07-04 papers/Papers1234/sec-dust-bow-intro.tex
Make start on description of when dust wave crosses mhd bow shock

@@
 
+The assumptions behind these models break down when the grain
+trajectory intersects the outer shock of the dust-free wind-supported
+bow shock.  The increased gas density in the bow shock shell will
+reduce \(\Xi\), which is likely to cause recoupling in the case of
+drag-confined dust waves (see also discussion in the final paragraph
+of \S~\ref{sec:exist-cond-separ}).  However, detailed modeling of this
+requires magnetohydrodynamical simulations, which are beyond the scope
+of this paper.  In Figure~\ref{fig:frozen-stream} we show the shape of
+a Wilkinoid (gray dotted lines)
+
 %%% Local Variables:

### 2018-07-10 papers/Papers1234/sec-dust-bow-intro.tex
Finish magnetic dust waves section!

--- 2018-06-30 papers/Papers1234/sec-dust-bow-intro.tex
@@
 
+The assumptions behind these models break down when the grain
+trajectory intersects the outer shock of the dust-free wind-supported
+bow shock.  The increased gas density in the bow shock shell will
+reduce \(\Xi\), which is likely to cause gas--grain recoupling in the
+case of drag-confined dust waves (see also discussion in the final
+paragraph of \S~\ref{sec:exist-cond-separ}).  However, detailed
+modeling of this requires magnetohydrodynamical simulations, which are
+beyond the scope of this paper.  In Figure~\ref{fig:frozen-stream} we
+show in gray dotted lines the Wilkinoid surface \citep{Wilkin:1996a},
+which is an approximation to the shape of the inner bow shock, see
+\PaperI.  It can be seen that the majority of dust streamlines do not
+cross this surface until well into the wings of the bow, so that a
+separate exterior dust wave can exist for this quasi-parallel
+magnetic field orientation.
+
+This is no longer the case for the quasi-perpendicular field
+orientation, as illustrated in the lower panels of
+Figure~\ref{fig:frozen-stream}, where the behavior is similar to the
+perpendicular inertia-confined case studied in
+Appendix~\ref{sec:perp-magn-field}.  Although the grains decouple from
+the gas inside the rip point, for small impact parameters the magnetic
+geometry does not allow the radiation field to expel them until they
+are much nearer to the star.  Since the inner wind-supported bow shock
+radius is only a few times smaller than \(R_\dag\), it is possible that
+they will pass through the shock surface and re-couple before
+expulsion can occur.  For the \SI{40}{km.s^{-1}} model (lower left
+panel), all of the streamlines with impact parameters
+\(\abs{b} < R_\dag\) intersect the Wilkinoid surface before they are
+deflected, and so no separate dust wave would form in this case.  For
+the \SI{80}{km.s^{-1}} model (lower left panel), some of the
+streamlines (mainly those with \(b > 0\)) do manage to avoid crossing
+the bow shock surface, so it is possible that a dust wave may still
+form, although it would only be on one side of the axis.
+
 %%% Local Variables:

### 2018-08-23 papers/Papers1234/sec-dust-case-studies.tex
Add some details of LP Ori to the Case Studies section
But I have now broken out this work into a new repo

https://github.com/div-B-equals-0/dust-wave-case-studies
Start writing up the magnetic field part for dust wave paper
Write a bit more about the B fields
Return to the observations section

@@
-\section{Case studies}
+\section{Observational evidence for radiation-supported bows}
 \label{sec:case-studies}
 
-Carina mid-infrared bow shocks \citep{Sexton:2015b} are in a high
-density environment, \SI{1000}{cm^{-3}}, so they may be bow waves.
-There seems to be spectral types for most of them: B0 (but supergiant)
-to O7.  Sizes are 3 to 12 arcsec, which at Carina (\SI{2.3}{kpc}) is
+In observational studies of bow-shaped arcs around OB stars, it is
+frequently assumed that all such objects are wind-supported bow shocks
+(e.g., \citealp{Kobulnicky:2016a}). Our results from
+\S~\ref{sec:strong-gas-grain} show that this is indeed a fair
+assumption in the absence of gas-grain decoupling, so long as the
+ambient density is less than about \SI{100}{cm^{-3}} (see
+Fig.~\ref{fig:zones-v-n-plane}). In other words, most OB stars
+interacting with the diffuse interstellar medium are probably in the
+wind bow shock regime.  Therefore, to find examples of
+radiation-supported bow waves and bow shocks it is necessary to look
+at arcs inside \hii{} regions and star-forming clouds, where the
+ambient densities are much higher.
+
+One potentially promising sample is the Carina mid-infrared bow shocks
+\citep{Sexton:2015b}.   are in a high density environment,
+\SI{1000}{cm^{-3}}, so they may be bow waves.  There seems to be
+spectral types for most of them: B0 (but supergiant) to O7.  Sizes are
+3 to 12 arcsec, which at Carina (\SI{2.3}{kpc}) is
 \SIrange{0.033}{0.134}{pc}.
@@
 
+Two small bows in M42:
+
+\(\theta^1\)\,Ori~D (Ney--Allen nebula) \citep{Robberto:2005a}
+
+LP~Ori: B1.5V star, like our \SI{10}{M_\odot} example. Radius about
+\(3''\), so 0.005 pc.  With \(v = 80\) that would clearly be a dust
+wave and would require \SIrange{100}{1000}{cm^{-3}}. Gaia distance \SI{408 +- 11}{pc}
+
+Ones that Ochsendorf claims are dust waves (Narrator: they aren't).
+
 %%% Local Variables:

### 2018-11-07 papers/Papers1234/sec-dust-case-studies.tex
Start on graph for Sickle Nebula in Carina
Add some figures to the observations section

@@
-\section{Observational evidence for radiation-supported bows}
+\section{Observational case studies}
 \label{sec:case-studies}
@@
 ambient densities are much higher.
+
+\subsection{Evidence for radiation-supported bows}
 
@@
 
-\(\theta^1\)\,Ori~D (Ney--Allen nebula) \citep{Robberto:2005a}
+\newcommand{\thD}{\(\theta^1\)\,Ori~D}
+\th1D{} (Ney--Allen nebula) \citep{Robberto:2005a}
 
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/orion-LP-and-th1D-color}
+  \caption{Bows driven by the OB stars \thD{} and LP~Ori in the Orion
+    Nebula.  (a)~Large-scale infrared view of the Orion Molecular
+    Cloud.  Red, green, and blue intensity show respectively Herschel
+    PACS observations at \SIlist{160; 70}{\um}, and Spitzer IRAC
+    observations at \SI{8}{\um}.  Red traces thermal emission from
+    cool dust (\(T < \SI{30}{K}\)) in the dense molecular filament.
+    Green traces thermal emission from warmer dust
+    (\(T \approx \SI{40}{K}\)) in the neutral PDR, which is heated by
+    far-ultraviolet radiation from the OB stars in the cluster. Blue
+    traces emission from PAH \SIlist{7.6;7.85}{\um} bands in the same
+    neutral PDR plus thermal emission from hotter dust
+    (\(T > \SI{100}{K}\)), which is found inside the ionized \hii{}
+    region.  (b)~Zoom on the central parsec of the Orion Nebula (M42),
+    showing short-wavelength mid-infrared emission from Spitzer IRAC
+    observations (\SIlist{8.0;5.8;4.5}{\um}).  Red shows the same as
+    blue in panel~a.  Green show predominantly the \SI{6.2}{\um} PAH
+    band.  Blue shows mainly stellar photospheric emission, plus a
+    minor contribution due to the Br~\(\alpha\) emission line from ionized
+    gas. Some major components of the nebula are labelled: the
+    Trapezium cluster, which contains the majority of the massive
+    stars; the Kleinmann-Low reflection nebula, illuminated by massive
+    stars embedded in the molecular filament; the Orion Bar, a
+    prominent edge-on ionization front and PDR.  (c)~Zoom on the
+    central \SI{0.1}{pc} of the Trapezium cluster, showing longer
+    wavelength mid-infrared emission from UKIRT MAX
+    (\SIlist{19.7;10.1}{\um}).  In this central zone, these
+    wavelengths (shown in red and green) are dominated by warm
+    (\SIrange{100}{300}{K}) silicate grains, while the IRAC
+    \SI{5.8}{\um} emission (blue) shows stellar photospheres and the
+    very warmest dust.}
+  \label{fig:orion-bows}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/ney-allen-sed}
+  \caption{Infrared spectral energy distribution of the Ney--Allen
+    nebula that surrounds \thD. }
+  \label{fig:ney-allen-sed}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/lp-ori-sed}
+  \caption{Optical/infrared spectral energy distribution of the LP Ori
+    and associated nebula. }
+  \label{fig:lp-ori-sed}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/lp-ori-wfpc2-continuum-subtract}
+  \caption{Narrow-band images of LP Ori nebula }
+  \label{fig:lp-ori-sed}
+\end{figure}
+
 %%% Local Variables:

### 2019-01-14 papers/Papers1234/sec-dust-case-studies.tex
Fancy SED graph for LP Ori
Separate out the Orion observational material into new paper!

@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/ney-allen-sed}
-  \caption{Infrared spectral energy distribution of the Ney--Allen
+  \includegraphics[width=\linewidth]{figs/ney-allen-sed-edited}
+  \caption{Ultraviolet-to-infrared spectral energy distribution of the Ney--Allen
     nebula that surrounds \thD. }
   \label{fig:ney-allen-sed}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/lp-ori-sed}
-  \caption{Optical/infrared spectral energy distribution of the LP Ori
+  \includegraphics[width=\linewidth]{figs/lp-ori-sed-edited}
+  \caption{Ultraviolet-to-infrared spectral energy distribution of LP~Ori
     and associated nebula. }
   \label{fig:lp-ori-sed}
-\end{figure}
+\end{figure*}
 
@@
 
+% Model shell-R001-n27-LP_Ori20Bz5 from cloudy-dust-charging
+The Cloudy model for LP Ori
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "dusty-bow-wave"
+%%% TeX-master: "two-orions-bow"
 %%% End:

### 2019-01-14 papers/Papers1234/dusty-bow-wave.tex
Make a start on writing up the different dust regimes
Finish equations for different regimes in well-coupled case
Write more of inside-out section
Also, finish replacing the stellar data properly and re-doing the
figures for the new faster wind speeds.  And add Jane as an author,
since she has been helping with the stellar parameters.
Finish long footnote on stellar wind models
And add a bit to a new section about observations of IR arcs in Carina
Further simplification of the i-front trapping
Move the complicated version to an appendix, which will probably be
dropped from the final version
Ad

--- 2017-11-23 papers/Paper1/dusty-bow-wave.tex
@@
 
+\usepackage{chemgreek}
+\activatechemgreekmapping{newtx}
+
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
@@
 
-\title[Dust waves, bow waves, bow shocks]
-{Shapes of dust waves, bow waves, and bow shocks}
+\title
+{Bow shocks, bow waves, and dust waves}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Henney \& Tarango Yong]{
-  William J. Henney \& Jorge A. Tarango Yong\\
+\author[Henney, Arthur, \& Tarango Yong]{
+  William J. Henney, S. Jane Arthur, \& Jorge A. Tarango-Yong\\
   \AddressCRyA
@@
 
+\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
+\newcommand{\grain}{\ensuremath{_{\text{d}}}}
+\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
+\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
+\newcommand{\xsec}{\ensuremath{\sigma\grain}}
+\newcommand\frad{\ensuremath{f_{\text{rad}}}}
+\newcommand\fmax{\ensuremath{f_{\text{max}}}}
+\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
+\newcommand\drag{\ensuremath{_{\text{drag}}}}
+\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
+\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
+\newcommand\rad{\ensuremath{_{\text{rad}}}}
+\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
+% Why do I need both of these?
+\newcommand\sound{\ensuremath{c_{\text{s}}}}
+\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
+\newcommand\starstar{\ensuremath{_{**}}}
+
+\defcitealias{Tarango-Yong:2018a}{Paper~I}
+\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
+
 \begin{document}
@@
   for explaining the curved arcs of infrared emission seen around some
-  stars.  We employ simple cylindrically symmetric models for the dust
-  grain dynamics under the influence of radiation and weak gas--grain
-  coupling, which produce bow shapes that we call dragoids.  We also
-  show how thin-shell hydrodynamic models can be modified to treat the
-  case of strong gas-grain coupling, producing bow shapes that we call
-  trapoids.  Using our recently developed two-dimensional
-  classification scheme for projected bow shapes, we then analyze the
-  inclination-dependent tracks of the dragoids and trapoids in the
-  planitude--alatude plane, finding interesting differences from the
-  wilkinoid, cantoid, and ancantoid shapes of hydrodynamic bow shock
-  models. We further show how these are modified in the presence of
-  small-amplitude standing-wave oscillations of the basic shape, as
-  may be produced by hydrodynamic instabilities or a time-varying
-  source.  We analyze the prospects of using shape analysis of
-  observational datasets to discriminate between different bow models,
-  finding that sample sizes of order 100 are required.
+  stars.  We develop simple models for the combined effects of
+  radiation and stellar winds on an ambient flow in the case where gas
+  and grains are perfectly coupled. We find that wind-supported bow
+  shocks predominate when the ambient density is low
+  (\(\ltae \SIrange{100}{1000}{cm^{-3}}\)) for a broad class of
+  stellar parameters.  At higher densities, radiation-supported bows
+  can form, tending to be optically thin bow waves in the case of B
+  stars, or optically thick bow shocks in the case of early O stars.
+  We further investigate the dynamics of dust grains when the
+  radiation field is sufficiently strong to overcome the collisional
+  coupling between grains and gas, showing that this occurs at a
+  \textit{rip-point}, where the ratio of radiation pressure to gas
+  pressure exceeds a critical value (\(P\rad/\Pgas > 1000\)).
+
 \end{abstract}
@@
 \input{sec-dust-bow-intro}
-\input{app-dust-wave}
-\input{sec-standing-wave}
 \input{sec-dust-bow-discuss}
@@
 \appendix
+\input{app-cloudy-dust-charging}
+\input{app-dust-wave}
 \input{app-dust-equations}
+%\input{app-dust-ifront-trap}
 

### 2019-01-15 papers/Papers1234/dusty-bow-wave.tex
Finish abstract (still need to cut 20 words)

@@
   Dust waves and bow waves result from the action of a star's
-  radiation pressure on a stream of dust grains that is flowing past
-  it.  They are an alternative mechanism to hydrodynamic bow shocks
-  for explaining the curved arcs of infrared emission seen around some
-  stars.  We develop simple models for the combined effects of
-  radiation and stellar winds on an ambient flow in the case where gas
-  and grains are perfectly coupled. We find that wind-supported bow
-  shocks predominate when the ambient density is low
-  (\(\ltae \SIrange{100}{1000}{cm^{-3}}\)) for a broad class of
-  stellar parameters.  At higher densities, radiation-supported bows
-  can form, tending to be optically thin bow waves in the case of B
-  stars, or optically thick bow shocks in the case of early O stars.
-  We further investigate the dynamics of dust grains when the
-  radiation field is sufficiently strong to overcome the collisional
-  coupling between grains and gas, showing that this occurs at a
-  \textit{rip-point}, where the ratio of radiation pressure to gas
-  pressure exceeds a critical value (\(P\rad/\Pgas > 1000\)).
-
+  radiation pressure on a stream of dusty plasma that flows past it.
+  They are an alternative mechanism to hydrodynamic bow shocks for
+  explaining the curved arcs of infrared emission seen around some
+  stars.  When gas and grains are perfectly coupled, for a broad class
+  of stellar parameters, wind-supported bow shocks predominate when
+  the ambient density is below \SIrange{100}{1000}{cm^{-3}}.  At
+  higher densities radiation-supported bows can form, tending to be
+  optically thin bow waves around B~stars, or optically thick bow
+  shocks around early O~stars.  The radiation field is sufficiently
+  strong to overcome the collisional coupling between grains and gas
+  at a \textit{rip-point}, where the ratio of radiation pressure to
+  gas pressure exceeds a critical value of roughly 1000.  When the rip
+  point occurs outside the hydrodynamic bow shock, a separate dust
+  wave may form, decoupled from the gas shell, which can either be
+  drag-confined or inertia-confined, depending on the stream density
+  and relative velocity.  In the drag-confined case, there is a
+  minimum stream velocity of roughly \SI{60}{km.s^{-1}} that allows a
+  steady-state stagnant drift solution for the dust wave apex.  For
+  lower relative velocities, the dust dynamics close to the axis
+  exhibit a limit cycle behavior (rip and snap back) between two
+  different radii.  Strong coupling of charged grains to the plasma's
+  magnetic field can modify these effects, but for a quasi-parallel
+  field orientation the results are qualitatively similar. For a
+  quasi-perpendicular field, on the other hand, the formation of a
+  decoupled dust wave is strongly suppressed.
 \end{abstract}

### 2019-01-15 papers/Papers1234/sec-dust-bow-intro.tex
Revise intro and promote subsections to sections

@@
 star, forming a dust-free, bow-shaped cavity with an enhanced dust
-density at its edge.  Two regimes are possible, depending on the
-strength of coupling between the gas (or plasma) and the dust.  In the
-strong-coupling regime, gas--grain drag decelerates the gas along with
-the dust, forming a shocked gas shell in a similar fashion to the
-wind-driven bow shock case.  In the weak-coupling regime, the gas
-stream is relatively unaffected and the dust temporarily decouples to
-form a dust-only shell.  This second case has recently been studied in
-detail in the context of the interaction of late O-type stars (which
-have only weak stellar winds) with dusty photoevaporation flows inside
-\hii{} regions \citep{Ochsendorf:2014a, Ochsendorf:2014b,
-  Ochsendorf:2015a}.  We follow the nomenclature proposed by
-\citet{Ochsendorf:2014b}, in which \textit{dust wave} refers to the
-weak coupling case and \textit{bow wave} to the strong coupling case.
-More complex, hybrid scenarios are also possible, such as that studied
-by \citet{van-Marle:2011a}, where a hydrodynamic bow shock forms, but
-the larger dust grains that accompany the stellar wind pass right
-through the shocked gas shell, and form their own dust wave at a
-larger radius.
+density at its edge.
+
+Two regimes are possible, depending on the strength of coupling
+between the gas (or plasma) and the dust.  In the strong-coupling
+regime, gas--grain drag decelerates the gas along with the dust.  If
+the stream is optically thin to the star's ultraviolet radiation, then
+the deceleration occurs gradually over a range of radii, forming a
+relatively thick shell.  On the other hand, if the stream is optically
+thick, then a shocked gas shell forms in a similar fashion to the
+wind-driven bow shock case, except internally supported by trapped
+radiation instead of shocked stellar wind.  In the weak-coupling
+regime, the gas stream is relatively unaffected and the dust
+temporarily decouples to form a dust-only shell.  This second case has
+recently been studied in detail in the context of the interaction of
+late O-type stars (some of which have very weak stellar winds) with
+dusty photoevaporation flows inside \hii{} regions
+\citep{Ochsendorf:2014a, Ochsendorf:2014b, Ochsendorf:2015a}.  We
+follow the nomenclature proposed by \citet{Ochsendorf:2014b}, in which
+\textit{dust wave} refers to the weak coupling case and \textit{bow
+  wave} to the strong coupling case.  More complex, hybrid scenarios
+are also possible, such as that studied by \citet{van-Marle:2011a},
+where a hydrodynamic bow shock forms, but the larger dust grains that
+accompany the stellar wind pass right through the shocked gas shell,
+and form their own dust wave at a larger radius.
 
@@
 
-In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
-new two-dimensional classification scheme for bow shapes: the
-projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
-measures the flatness of the bow's apex, while alatude measures the
-openness of the bow's wings.  Both are dimensionless ratios of lengths
-that can be estimated from observational images.  We have analyzed the
-inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
-geometric shapes (spheroids, paraboloids, hyperboloids) and for
-thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
-ancantoids).  In this paper, we will do the same for simple models of
-radiation-driven dust waves (dragoids) and bow waves (trapoids).
-
+% In \citet[][hereafter \PaperI{}]{Tarango-Yong:2018a}, we proposed a
+% new two-dimensional classification scheme for bow shapes: the
+% projected planitude--alatude, or \(\Pi'\)--\(\Lambda'\), diagram.  Planitude
+% measures the flatness of the bow's apex, while alatude measures the
+% openness of the bow's wings.  Both are dimensionless ratios of lengths
+% that can be estimated from observational images.  We have analyzed the
+% inclination-dependent tracks on the \(\Pi'\)--\(\Lambda'\) plane for simple
+% geometric shapes (spheroids, paraboloids, hyperboloids) and for
+% thin-shell hydrodynamic bow shock models (wilkinoid, cantoids,
+% ancantoids).  In this paper, we will do the same for simple models of
+% radiation-driven dust waves (dragoids) and bow waves (trapoids).
+
+In this paper, we develop simple physical models to show in detail
+when and how these different interaction regimes apply when varying
+the parameters of the star, the dust grains, and the ambient stream.
+We concentrate primarily on the case of luminous early type stars,
+where dust is present only in the ambient stream, and not in the
+stellar wind.
+%
 The paper is organized as follows.
 %
-In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
-dusty radiation bow wave (dragoids), including the effects of
-gas-grain drag.
+In \S~\ref{sec:strong-gas-grain} we consider the case where the grains
+are perfectly coupled to the gas via collisions, investigating the
+relative importance of wind and radiation in providing internal
+support for the bow shell as a function of the density and velocity of
+the ambient stream, as well as calculating the shell's ionization
+state and radiative cooling efficiency.
 %
-In \S~\ref{sec:perturbed-bows} we investigate the effects on the
-planitude--alatude plane of small-amplitude perturbations to the bow
-shape.
+In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
+charging and dynamics, subject to radiation and drag forces, in order
+to determine the rip point where gas--grain coupling catastrophically
+breaks down.  This is used to determine existence conditions for the
+presence of a decoupled dust wave.
 %
-
-\section{Different types of bow}
-\label{sec:different-types-bow}
+In \S~\ref{sec:magn-effects-grain} we consider the additional coupling
+between the grains and the plasma's magnetic field, and how this
+effects the existence and structure of dust waves.
+%
+In \S~\ref{sec:summary-discussion} we briefly discuss the application
+of our models to observed bows.
+%
+In \S~\ref{sec:conclusions} we summarise the conclusions of our study. 
+%
+A series of appendices provide additional technical information on
+dust physics (Appendix~\ref{sec:cloudy-models-dust}), analytical
+models of the shape of dust waves in the drag-free limit
+(Appendix~\ref{sec:gas-free-bow}), and the numerical calculation of
+grain trajectories (Appendix~\ref{sec:equat-moti-grains}).
+
+% In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
+% dusty radiation bow wave (dragoids), including the effects of
+% gas-grain drag.
+% %
+% In \S~\ref{sec:perturbed-bows} we investigate the effects on the
+% planitude--alatude plane of small-amplitude perturbations to the bow
+% shape.
+% %
 
@@
 
-In this section, we investigate the different types of bow interaction
-that will occur in different regions of parameter space. We will
-mainly treat the canonical case\footnote{%
-  Variant cases with differing arrangements of dust and radiation
-  sources are treated in \S~\ref{sec:case-inside-out}.} %
-of a bow around a star of bolometric luminosity, \(L\), with a
-radiatively driven wind, which is immersed in an external stream of
-gas and dust with density, \(\rho\), and velocity, \(v\).  The size and
-shape of the bow is determined by a generalized balance of pressure
-(or, equivalently, momentum) between internal and external sources.
-We assume that the stream is supersonic and super-alfvenic, so that
-the external pressure is dominated by the ram pressure: \(\rho v^2\).
-
-\subsection{Strong gas-grain coupling}
+\section{Strong gas-grain coupling}
 \label{sec:strong-gas-grain}
 
-We first consider the case where the dust grains and gas are perfectly
-coupled by collisions.\footnote{%
-  Cases where this assumption does not hold are investigated below in
-  \S~\ref{sec:imperf-coupl-betw}.} %
+We consider the canonical case of a bow around a star of bolometric
+luminosity, \(L\), with a radiatively driven wind, which is immersed
+in an external stream of gas and dust with density, \(\rho\), and
+velocity, \(v\).  The size and shape of the bow is determined by a
+generalized balance of pressure (or, equivalently, momentum) between
+internal and external sources.  We assume that the stream is
+supersonic and super-alfvenic, so that the external pressure is
+dominated by the ram pressure: \(\rho v^2\).  We first consider the case
+where the dust grains and gas are perfectly coupled by collisions.
+
 Although dust grains typically constitute only a small fraction
@@
 
-\subsubsection{Bows supported by radiation and wind}
+\subsection{Bows supported by radiation and wind}
 \label{sec:three-bow-regimes}
@@
 
-\subsubsection{Effects of stellar gravity}
+\subsection{Effects of stellar gravity}
 \label{sec:effects-gravity}
@@
 
-\subsubsection{Ionization state of the bow shell}
+\subsection{Ionization state of the bow shell}
 \label{sec:trapp-ioniz-front}
@@
 
-\subsubsection{Radiative cooling lengths}
+\subsection{Radiative cooling lengths}
 \label{sec:radi-cool-lengths}
 \newcommand\M{\ensuremath{\mathcal{M}}}
+%
 In this section, we calculate whether the radiative cooling is
 sufficiently rapid behind the bow shock to allow the formation of a
-thin, dense shell.  Since cooling is least efficient at low densities,
-we will assume that the wind bow shock regime applies unless otherwise
-specified. We label quantities just outside the shock by the subscript
-``0'', quantities just inside the shock (after thermalization, but
-before any radiative cooling) by the subscript ``1'', and quantities
-after the gas has cooled back to the photoionization equilibrium
-temperature by the subscript ``2''.  Assuming a ratio of specific
-heats, \(\gamma = 5/3\), the relation between the pre-shock and immediate
-post-shock quantities is
+thin, dense shell.  Since this is mainly a concern at low densities,
+where cooling is least efficient, we will assume that the wind bow
+shock regime applies unless otherwise specified. We label quantities
+just outside the shock by the subscript ``0'', quantities just inside
+the shock (after thermalization, but before any radiative cooling) by
+the subscript ``1'', and quantities after the gas has cooled back to
+the photoionization equilibrium temperature by the subscript ``2''.
+Assuming a ratio of specific heats, \(\gamma = 5/3\), the relation between
+the pre-shock and immediate post-shock quantities is
 \begin{align}
@@
 
-\subsection{Imperfect coupling between gas and dust}
+\section{Imperfect coupling between gas and dust}
 \label{sec:imperf-coupl-betw}
@@
 
-\subsubsection{Drag force on grains}
+\subsection{Drag force on grains}
 \label{sec:drag-force-grains}
@@
 
-\subsubsection{Gas--grain separation: drift and rip}
+\subsection{Gas--grain separation: drift and rip}
 \label{sec:gas-grain-separ}
@@
 
-\subsubsection{Existence conditions for dust waves}
+\subsection{Existence conditions for dust waves}
 \label{sec:exist-cond-separ}
@@
 
-\subsubsection{Grain trajectories along the symmetry axis}
+\subsection{Grain trajectories along the symmetry axis}
 \label{sec:grain-traj-along}
@@
 
-\subsubsection{Back reaction on the gas flow}
+\subsection{Back reaction on the gas flow}
 \label{sec:back-reaction-gas}
@@
 
-\subsubsection{Magnetic effects on grain trajectories }
+\section{Magnetic effects on grain trajectories }
 \label{sec:magn-effects-grain}

### 2019-01-19 papers/Papers1234/app-cloudy-dust-charging.tex
Write about stagnant drift velocity and tweak some figures
Finish appendix on CLoudy models

@@
-\section{Cloudy models of dust charging around OB stars}
+\section{Grain charging and gas--grain coupling around OB stars}
 \label{sec:cloudy-models-dust}
+
+We calculate models of the physical properties of dust grains using
+the plasma physics code Cloudy \citep{Ferland:2013a, Ferland:2017a},
+which self consistently solves the multi-frequency radiative transfer
+together with thermal, ionization, and excitation balance of all
+plasma constituents.  Cloudy incorporates grain charging as described
+in \citet{Baldwin:1991a} and \citet{van-Hoof:2004a} with photoelectric
+emission theory from \citet{Weingartner:2001b, Weingartner:2006a}.  We
+use the default ``ISM'' dust mixture included in Cloudy, which
+comprises ten size bins each for spherical silicate and graphite
+grains in the range \num{0.005} to \SI{0.25}{\um}, and which is
+designed to reproduce the average Galactic extinction curve
+\citep{Weingartner:2001a, Abel:2008a}.
+
+To ascertain the expected variation in grain properties in the
+circumstellar environs of luminous stars, we calculate a series of
+spherically symmetric, steady-state, constant density Cloudy models,
+illuminated by the stars listed in Table~\ref{tab:stars}, with stellar
+spectra taken from the OSTAR2002 and BSTAR2006 grids, calculated with
+the TLUSTY model atmosphere code \citep{Lanz:2003a, Lanz:2007a}.
+Models are calculated for hydrogen densities of
+\numlist{1;10;100;e3;e4} \si{cm^{-3}} and assuming standard \hii{} region
+gas phase abundances.  The calculation is stopped when the ionization
+front is reached and the inner radius is chosen to be roughly 1\% of this.
 
@@
     selected Cloudy models. (a)~\SI{40}{M_\odot} main-sequence star in
-    medium of density \SI{e4}{cm^{-2}}. (b)~\SI{10}{M_\odot} main-sequence
-    star in medium of density \SI{1}{cm^{-2}}. (c)~Blue supergiant
-    star in medium of density \SI{1}{cm^{-2}}}.
+    medium of density \SI{e4}{cm^{-3}}. (b)~\SI{10}{M_\odot} main-sequence
+    star in medium of density \SI{1}{cm^{-3}}. (c)~Blue supergiant
+    star in medium of density \SI{1}{cm^{-3}}}.
   \label{fig:multi-dustprops}
 \end{figure*}
+Figure~\ref{fig:multi-dustprops} shows resultant radial profiles of
+dust properties for representative models: grain temperature, grain
+abundance, grain potential, and grain drift velocity.  Line types
+correspond to the different size bins of graphite and silicate grains,
+as indicated in the key from smallest to largest. The left hand panels
+show results for a high-density (\(n = \SI{e4}{cm^{-3}}\)), compact
+(\(R \approx \SI{0.1}{pc}\)) region around an early O star, where the grain
+temperature is very high, especially for the smaller silicate grains,
+and sublimation significantly reduces the grain abundance in the inner
+regions.  The remaining columns show low density
+(\(n = \SI{1}{cm^{-3}}\)), extended (\(R \sim \SI{10}{pc}\)) regions
+around main-sequence and supergiant B-type stars, in which the grain
+temperatures are much lower, ranging from \SIrange{20}{50}{K} in the
+outer parts up to \SIrange{100}{200}{K} in the inner parts.
 
@@
   \includegraphics[width=\linewidth]{figs/drift-pratio-4panel}
-  \caption{Drift velocity versus radiation parameter \(\Xi_P\). Each line
-    represents a model with ambient density and stellar type as
-    indicated in the key.}
+  \caption{Drift velocity \(w\drift\) versus radiation parameter
+    \(\Xi\). Each line represents a model with ambient density and
+    stellar type as indicated in the key.  Results are shown for
+    graphite and silicate grains of two different sizes.  The rip
+    point, which corresponds to gas--grain decoupling, is the
+    discontinuity in the curves at
+    \(w\drift \approx \SI{10}{km.s^{-1}}\), indicated by the upper
+    horizontal dashed line.  The vertical dashed lines show the narrow
+    range of radiation parameter, \(\Xi = 1000 \pm \SI{0.5}{dex}\), that
+    encompasses the rip point for all models. }
   \label{fig:drift-gn}
 \end{figure*}
+
+Unlike the strong differences in thermal properties, the radial
+dependence of grain electrostatic potential (third row in
+Fig.~\ref{fig:multi-dustprops}) is qualitatively similar for all the
+models.  The grains are predominantly positively charged, with high
+potentials (\(> 10\) times the thermal energy of gas particles) close
+to the star due to the strong EUV and FUV photo-ejection.  The
+potential falls to much lower values in the outer ionized region, as
+the EUV flux falls off, and then climbs again at the ionization front
+due to the fall in electron density, while the FUV photo-ejection
+persists well into the neutral region.  There are small differences
+between the models due to the increasing relative importance of the
+EUV radiation for hotter stars, which leads to a deeper dip in the
+potential just inside the ionization front for the \SI{40}{M_\odot} case,
+even reaching negative values for some grain species.
+
+Equilibrium drift velocity for each grain species is calculated in the
+Cloudy models using the same theory \citep{Draine:1979a} as outlined
+in \S~\ref{sec:drag-force-grains}.  The way that this is implemented
+by default in Cloudy means that if the only solution at the inner
+radius is a superthermal one, then the superthermal solution branch
+(upper right corner of Fig.~\ref{fig:gas-grain-drag-photoionized}) is
+followed as far as possible through the outer spatial zones.  We have
+modified the code so as to instead always prefer the slower subthermal
+branch when multiple solutions are available.  This makes the most
+sense in our context, where the grains are moving towards the star and
+so the radiative force is gradually increasing from an initial low
+value.  Example results are shown in the bottom row of
+Figure~\ref{fig:multi-dustprops} and again they are qualitatively
+similar for all the models.  Close to the star, the radiation force is
+higher than the upper limit on the Coulomb drag force
+(eq.~[\ref{eq:fdrag-maximum}]), so that the equilibrium drift velocity
+is exceedingly high.\footnote{Note that such high drift velocities are
+  much higher than any realistic true relative velocity between grains
+  and gas, since they are based on the assumption that the radiation
+  force remains constant while the grain is accelerated, which can
+  never be the case.  Instead, they are simply an indication that the
+  gas and grains have completely decoupled.}.  As the radial distance
+from the star increases, the radiation field is increasingly diluted
+but the grain potential falls only slowly, so eventually one reaches a
+point where an equilibrium between Coulomb drag and radiation force
+can be established, which corresponds to a discontinuity in the drift
+velocity.  This is the \textit{rip point} discussed in
+\S~\ref{sec:gas-grain-separ}.  The drift velocity carries on falling
+towards the outside of the \hii{} region, but then increases again
+just inside the ionization front due to the drop in grain potential
+there.
+
+Both the charge balance and the force balance are essentially due to
+competition between the photons and the charged particles that
+interact with the grain.  It is therefore reasonable to surmise that
+the gas--grain decoupling that occurs at the rip point might be
+determined principally by the ratio of photons to gas particles.  We
+test this hypothesis in Figure~\ref{fig:drift-gn}, where we
+characterize the photon-gas ratio by a dimensionless radiation
+parameter, \(\Xi\), equal to the radiation pressure divided by the gas
+pressure.  Results are shown for four different grain types and for
+all combinations of stellar parameters and ambient densities for which
+we have run models.  It can be seen that the rip point does indeed
+always occur at a similar value of \(\Xi \sim 1000\) for all models, albeit
+with some variation according to the spectral type of the star and the
+grain composition, as given in Table~\ref{tab:Xi-rip}.  The gas
+density and grain size have very little influence on this critical
+value \(\Xi_\dag\), with the only exception being the very smallest grains
+(\(a < \SI{0.006}{\um}\), not illustrated), which show
+\(\Xi_\dag \approx \num{e4}\), but such grains are only minor contributors to the
+UV opacity (\(< 10\%\) in EUV and \(< 1\%\) in FUV).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/phi-versus-xi-annotate}
+  \caption{Grain potential in thermal units (linear scale) versus
+    radiation parameter (logarithmic scale). All densities and stellar
+    types are shown, with line colors as in Fig.~\ref{fig:drift-gn}.
+    Solid lines show silicate grains and dashed lines show graphite
+    grains.  Line width increases with grain size (to reduce clutter,
+    only every second size bin is shown).  The solid and dashed lines
+    show the logarithmic fits discussed in the text.}
+  \label{fig:phi-vs-Xi}
+\end{figure}
+Finally, Figure~\ref{fig:phi-vs-Xi} shows the slow dependence of grain
+potential on radiation parameter for all the models on a linear versus
+logarithmic scale.  The logarithmic fit of
+equation~\eqref{eq:phi-vs-Xi}, most appropriate for carbon grains
+around cooler stars, is shown by the solid line.  The dashed lines
+show the modifications for silicate grains and for hotter stars (see
+\S~\ref{sec:gas-grain-separ}).
 

### 2019-01-19 papers/Papers1234/sec-dust-bow-intro.tex
Finish appendix on CLoudy models

@@
   scattered radiation field is more isotropic than the stellar field,
-  leading to cancellation in the radiative
-  flux. (3)~Absorbed radiation is re-emitted at infrared
-  wavelengths, where the dust opacity is very much lower.} %
-and temporarily neglecting the wind, then pressure balance at the bow
-apex, a distance \(R_0\) along the symmetry axis from the star is
-given by
+  leading to cancellation in the radiative flux. (3)~Absorbed
+  radiation is re-emitted at infrared wavelengths, where the dust
+  opacity is very much lower.} %
+and temporarily neglecting the wind for clarity of exposition, then
+pressure balance at the bow apex, a distance \(R_0\) along the
+symmetry axis from the star is given by
 \begin{equation}
@@
 \end{equation}
-which yields a fiducial bow shock radius in this optically thick limit
-as
+which yields a fiducial bow shock radius in this optically thick,
+radiation-only limit as
 \begin{equation}
@@
 Therefore, an incoming stream with initial velocity, \(v_\infty\), can be
-brought to rest by radiation alone\footnote{%
-  For simplicity, we here ignore the effects of gravity, which are
-  important for low ratios of \(\kappa L / M\), see
-  \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
-  shocks, which are important as the velocity approaches the sound
-  speed, \(\sound\) (in \S~XX below, we show that the resultant
-  corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
+brought to rest by radiation alone
+% \footnote{%
+%   For simplicity, we here ignore the effects of gravity, which are
+%   important for low ratios of \(\kappa L / M\), see
+%   \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
+%   shocks, which are important as the velocity approaches the sound
+%   speed, \(\sound\) (in \S~XX below, we show that the resultant
+%   corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
 at a distance \(R\starstar\) where
@@
 \end{equation}
-and adding in the stellar wind ram pressure\footnote{%
-  We implicitly assume that the interaction of the stellar wind with
-  the external stream can always be treated in the continuum limit.
-  This will be true if either the collisional mean free path or the
-  ion Larmor radius is much smaller than \(R_0\), which is almost
-  always the case.} %
+and now reinstating the stellar wind ram pressure term
+% \footnote{%
+%   We implicitly assume that the interaction of the stellar wind with
+%   the external stream can always be treated in the continuum limit.
+%   This will be true if either the collisional mean free path or the
+%   ion Larmor radius is much smaller than \(R_0\), which is almost
+%   always the case.} %
 from equation~\eqref{eq:wind-efficiency}, we find that the general bow
@@
 The first case, \(x \approx (1 + \eta)^{1/2}\), corresponds to a
-\textit{radiation bow shock}; the second case,
-\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave}; and the
-third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow shock}.
-The two bow shock cases are similar in that the external stream is
-oblivious to the presence of the star until it suddenly hits the bow
-shock shell, differing only in whether it is radiation or wind that is
-providing the internal pressure.  In the intermediate bow wave case,
-on the other hand, the external stream is gradually decelerated by
-absorption of photons as it approaches the bow.\footnote{A shock does
-  still form in this case, but shocked material constitutes only a
-  fraction of the total column density of the shell, see
-  \S~\ref{sec:shape-bow-wave}.}
+\textit{radiation bow shock} (RBS); the second case,
+\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave} (RBW);
+and the third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow
+  shock} (WBS).  The two bow shock cases are similar in that the
+external stream is oblivious to the presence of the star until it
+suddenly hits the bow shock shell, differing only in whether it is
+radiation or wind that is providing the internal pressure.  In the
+intermediate bow wave case, on the other hand, the external stream is
+gradually decelerated by absorption of photons as it approaches the
+bow.\footnote{A shock can still form in this case, but shocked
+  material constitutes only a small fraction of the total column
+  density of the shell.}
+
+\subsection{Dependence on stellar type}
+\label{sec:depend-stell-type}
 
@@
 We now consider the application to bow shocks around main sequence OB
-stars, expressing stellar and ambient parameters in terms of typical
-values as follows:
+stars, as well as cool and hot supergiants, expressing stellar and
+ambient parameters in terms of typical values as follows:
 \begin{align*}
@@
 \end{equation}
-which is nearly always small.  For clarity of exposition, we therefore
-ignore \(\mathcal{A}\) in the following discussion, although it is
-included in quantitative calculations.  The column density of the
-shocked shell can be found, for example, from equations~(10) and~(12)
-of \citet{Wilkin:1996a} in the limit \(v_\infty/V \to 0\) (Wilkin's parameter
-\(\alpha\)) and \(\theta \to 0\).  This yields
+where
+\begin{equation*}
+  S_{49} = S / \bigl( \SI{e49}{s^{-1}} \bigr) \ .
+\end{equation*}
+Numerical values of \(S_{49}\) for our three example stars are given
+in Table~\ref{tab:stars}, taken from Figure~4 of
+\citet{Sternberg:2003a}.  Since \(\mathcal{A} \ll \mathcal{F}\) in
+nearly all cases, for clarity of exposition we ignore \(\mathcal{A}\)
+in the following discussion, although it is included in quantitative
+calculations.  The column density of the shocked shell can be found,
+for example, from equations~(10) and~(12) of \citet{Wilkin:1996a} in
+the limit \(v_\infty/V \to 0\) (Wilkin's parameter \(\alpha\)) and
+\(\theta \to 0\).  This yields
 \begin{equation}
@@
   \label{eq:ifront-trap-density-RBS}
-  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta)^3} \ , 
-\end{equation}
-where
-\begin{equation*}
-  S_{49} = S / \bigl( \SI{e49}{s^{-1}} \bigr) \ .
-\end{equation*}
-Numerical values of \(S_{49}\) for our three example stars are given
-in Table~\ref{tab:stars}, taken from Figure~4 of
-\citet{Sternberg:2003a}.  In the radiation bow wave case,
-\(x = 2\tau_*\), and the condition can be written:
+  \text{RBS:}\quad
+  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta)^3} \ .
+\end{equation}
+In the radiation bow wave case, \(x = 2\tau_*\), and the condition can be
+written:
 \begin{equation}
   \label{eq:ifront-trap-taustar-RBW}
+  \text{RBW:}\quad
   \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ . 
@@
   Consideration of the slight increase in density between the shock
-  and the contact discontinuity reduces this value by 5--10\%.} %
+  and the contact/tangential discontinuity reduces this value by 5--10\%.} %
 For bows with outer stream densities between the two blue lines,
@@
   be much increased for the second approach.} %
-We will refer to this as an \textit{inertia-confined dust wave}.  From
-equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
+We will refer to this as an \textit{inertia-confined dust wave}
+(IDW).  From equations~(\ref{eq:Rdag-over-Rstar},
+\ref{eq:Rstarstar-over-Rstar},
 \ref{eq:dust-wave-high-density-condition}), the condition
@@
 inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
-as a \textit{drag-confined dust wave}.
+as a \textit{drag-confined dust wave} (DDW).
 
@@
 
-\section{Magnetic effects on grain trajectories }
+\section{Magnetic coupling of grains}
 \label{sec:magn-effects-grain}
@@
   \caption{Sample grain trajectories for drag-confined dust waves with
-    tight magnetic coupling.}
+    tight magnetic coupling and a quasi-parallel field
+    orientation. These are the same models as in the upper row of
+    Fig.~\ref{fig:frozen-stream}. (a)~Incident stream velocity of
+    \(v_\infty = \SI{40}{km.s^{-1}}\), showing quasi-limit-cycle behavior
+    (\numrange{0}{4000} years).  (b)~Incident stream velocity of
+    \(v_\infty = \SI{80}{km.s^{-1}}\), showing quasi-stagnation behavior
+    (\numrange{500}{2000} years).  In both cases, the streamline with
+    initial impact parameter \(y = -0.4 R_\dag\) is shown.}
   \label{fig:frozen-trajectories}
@@
 \S~\ref{sec:grain-traj-along}), where \(\Rmin \approx R_\dag\) for
-drag-confined dust waves, or \(\Rmin \approx R\starstar\) for
-inertia-confined dust waves.  We write the field strength in terms of
-the Alfvén speed,
+drag-confined dust waves (DDW), or \(\Rmin \approx R\starstar\) for
+inertia-confined dust waves (IDW).  We write the field strength in
+terms of the Alfvén speed,
 \begin{equation}
@@
   \label{eq:larmor-over-Rdag}
+  \text{DDW:}\quad \frac{r\B}{\Rmin} =  
   \frac{r\B}{R_\dag} = 0.0140 \,
@@
   \label{eq:larmor-over-Rstarstar}
+  \text{IDW:}\quad \frac{r\B}{\Rmin} =  
   \frac{r\B}{R\starstar} = 0.0544 \,
@@
 limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
-results of the previous sections are scarcely modified.  Assuming
-\(w_\perp \sim v_\infty\) and adopting a threshold of
+non-magnetic results of \S~\ref{sec:imperf-coupl-betw} are scarcely
+modified.  Assuming \(w_\perp \sim v_\infty\) and adopting a threshold of
 \(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
@@
 coupled for the faster streams.
+
+\subsection{Grain trajectories with tight magnetic coupling}
+\label{sec:grain-traj-with}
 

### 2019-01-21 papers/Papers1234/app-dust-equations.tex
Draine & Salpeter equations in Appendix C

--- 2017-11-18 papers/Paper1/app-dust-equations.tex
@@
 \label{sec:equat-moti-grains}
+
+Following \citet{Draine:1979a}, the drag force on a grain that is
+moving at relative velocity \(w\) through a partially ionized gas can
+be written as a sum over each collider species, \(k\), with mass
+\(m_k\), abundance relative to hydrogen \(\alpha_k\) and charge
+\(z_k\). If the velocity is normalized to the thermal velocity of each
+species:
+\begin{equation}
+  \label{eq:s-velocity}
+  s_k = \left( m_k w^2 / 2 k T  \right)^{1/2} \ ,
+\end{equation}
+then the force is given by
+\begin{equation}
+  \label{eq:ds79}
+  f\drag = f_* \sum_k \alpha_k \left[ G_0(s_k) + z_k^2 \phi^2 \ln(\Lambda/z_k) G_2(s_k) \right],
+\end{equation}
+where \(f_*\) is a characteristic thermal force on the grain
+(see eq.~[\ref{eq:fstar}]). The
+dimensionless functions of normalized speed \(G_0(s)\) and \(G_2(s)\)
+are given by
+\begin{align}
+  \label{eq:G0}
+  G_0(s) & = \left( s^2 + 1 - \frac{1}{4 s^2} \right) \erf(s)
+  +  \left( s + \frac{1}{2 s} \right) \frac{e^{-s^2}}{\sqrt{\pi}}\\
+  \label{eq:G2}
+  G_2(s) & = \frac{\erf(s)}{s^2} - \frac{2 e^{-s^2}}{s \sqrt{\pi}} \ .
+\end{align}
+The \(G_0\) term is due to inelastic solid-body collisions in the
+Epstein limit, and is derived in \S~4 of \citet{Baines:1965a}.  The
+\(G_2\) term is due to electrostatic Coulomb interactions, with
+\(\phi\) being the grain potential in thermal units
+(eq.~[\ref{eq:phi-potential}]) and \(\Lambda\) the plasma parameter.  It was
+first derived in the different context of dynamic friction in stellar
+systems by \citet{Chandrasekhar:1941a}.
+
+We provide a python implementation of these equations in the file
+\texttt{ds79.py}, available from
+\url{https://github.com/div-B-equals-0/dust-trajectories}.
+Figure~\ref{fig:drag-components}--\ref{fig:gas-grain-drag-photoionized}
+show example applications to gas--grain drag in a photoionized region.
 
@@
     \frac{d U}{d t} &= \frac12 \left[  
-      X \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 \left(U - U_1\right)
+      X \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 D_1 \left(U - U_1\right)
     \right] \\
     \frac{d V}{d t} &= \frac12 \left[  
-      Y \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 \left(V - V_1\right)
+      Y \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 D_1 \left(V - V_1\right)
     \right] \ ,
@@
 is the distance from the second source, located at
-\((X, Y) = (\mu^{-1}, 0)\).
+\((X, Y) = (\mu^{-1}, 0)\).  The dimensionless gas density, \(D_1\),
+normalized by the value at \((X, Y) = (1, 0)\), is
+\begin{equation}
+  \label{eq:dust-gas-density}
+  D_1 = 
+  \begin{cases}
+    \text{parallel stream} & 1\\
+    \text{divergent stream} & \dfrac{\bigl(\mu^{-1} - 1\bigr)^2} {R_1^{2}} \ .
+  \end{cases}
+\end{equation}
 

### 2019-01-22 papers/Papers1234/app-dust-equations.tex
Finish the technical appendices

--- 2017-11-17 papers/Paper1/app-dust-equations.tex
@@
-\section{Equations of motion for grains with radiation and gas drag}
+\section{Equation of motion for grains with radiation, gas drag, and
+  magnetic field}
 \label{sec:equat-moti-grains}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/dust-couple-div-stream}
-  \caption{Divergent dragoids}
-  \label{fig:divergent-dragoids}
-\end{figure}
+Following \citet{Draine:1979a}, the drag force on a grain that is
+moving at relative velocity \(\bm{w} = \bm{v}\grain - \bm{v}\gas\)
+through a partially ionized gas can be written as a sum over each
+collider species, \(k\), with mass \(m_k\), abundance relative to
+hydrogen \(\alpha_k\) and charge \(z_k\). If the relative speed,
+\(w = \abs{\bm{w}}\), is normalized to the thermal speed of each
+species:
+\begin{equation}
+  \label{eq:s-velocity}
+  s_k = \left( m_k w^2 / 2 k T  \right)^{1/2} \ ,
+\end{equation}
+then the magnitude of the force is 
+\begin{equation}
+  \label{eq:ds79}
+  f\drag = f_* \sum_k \alpha_k \left[ G_0(s_k) + z_k^2 \phi^2 \ln(\Lambda/z_k) G_2(s_k) \right],
+\end{equation}
+where \(f_*\) is a characteristic thermal force on the grain (see
+eq.~[\ref{eq:fstar}]). The dimensionless functions of normalized speed
+\(G_0(s)\) and \(G_2(s)\) are given by
+\begin{align}
+  \label{eq:G0}
+  G_0(s) & = \left( s^2 + 1 - \frac{1}{4 s^2} \right) \erf(s)
+  +  \left( s + \frac{1}{2 s} \right) \frac{e^{-s^2}}{\sqrt{\pi}}\\
+  \label{eq:G2}
+  G_2(s) & = \frac{\erf(s)}{s^2} - \frac{2 e^{-s^2}}{s \sqrt{\pi}} \ .
+\end{align}
+The \(G_0\) term is due to inelastic solid-body collisions in the
+Epstein limit, and is derived in \S~4 of \citet{Baines:1965a}.  The
+\(G_2\) term is due to electrostatic Coulomb interactions, with
+\(\phi\) being the grain potential in thermal units
+(eq.~[\ref{eq:phi-potential}]) and \(\Lambda\) the plasma parameter.  It was
+first derived in the different context of dynamical friction in
+stellar systems by \citet{Chandrasekhar:1941a}.
+Figures~\ref{fig:drag-components}--\ref{fig:gas-grain-drag-photoionized}
+show example applications to gas--grain drag in a photoionized region.
 
-To find the dust grain trajectories \(R\grain(\theta)\) in the presence of
-radiation and drag forces (\S~\ref{sec:bow-wave-drag}), we numerically
-integrate the equations of motion. We define dimensionless cylindrical
-polar coordinates,
+The grain trajectories presented in \S~\ref{sec:grain-traj-along} and
+\ref{sec:grain-traj-with} are calculated by numerically solving the
+grain equation of motion:
 \begin{equation}
-  \label{eq:dust-XY}
-  (X, Y) = \left(\frac{R\grain(\theta) \cos\theta } {R_0}, \ 
-    \frac{R\grain(\theta) \sin\theta } {R_0}\right)
-  \ ,
+  \label{eq:grain-equation-motion}
+  m\grain \frac{d^2 \bm{r}}{d t^2} = \bm{f} \ .
 \end{equation}
-and dust grain velocities,
+The total force \(\bm{f}\) is the sum of radiation, drag, and Lorentz
+terms:
 \begin{equation}
-  \label{eq:dust-UV}
-  (U, V) = \left( \frac{\bm{v}\grain \cdot \uvec{x}} {v_\infty}, \ 
-  \frac{\bm{v}\grain \cdot \uvec{y}} {v_\infty}\right) \ ,
+  \label{eq:total-force}
+  \bm{f} = \frac{\sigma\grain \Qp L}{4\pi R^2 c} \hat{\bm{r}}
+  - f\drag \hat{\bm{w}}
+  + \frac{z\grain e}{c} \bm{w} \times \bm{B} \ ,
 \end{equation}
-where \(\uvec{x}\) and \(\uvec{y}\) are unit vectors along the \(X\)
-and \(Y\) axes (parallel and perpendicular, respectively, to the
-symmetry axis).  The grain equation of motion then follows from
-equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0},
-\ref{eq:dust-fdrag}--\ref{eq:dust-alpha}) as the following set of
-coupled differential equations:
-\begin{gather}
-  \label{eq:dust-motion}
-  \begin{aligned}
-    \frac{d X}{d t} &= U \quad\quad
-    \frac{d Y}{d t} = V \\
-    \frac{d U}{d t} &= \frac12 \left[  
-      X \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 \left(U - U_1\right)
-    \right] \\
-    \frac{d V}{d t} &= \frac12 \left[  
-      Y \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 \left(V - V_1\right)
-    \right] \ ,
-  \end{aligned}
-\end{gather}
-where \((U_1, V_1)\) are the components of the gas velocity (assumed
-fixed), given by
+with \(f\drag\) given by equation~\eqref{eq:ds79} and where
+\(\hat{\bm{r}}\) is the unit vector in the radial direction and
+\(\hat{\bm{w}} = \bm{w} / w\) is the unit vector along the direction
+of gas--grain relative motion.  In the strong magnetic coupling limit
+(see \S~\ref{sec:grain-traj-with} and \ref{sec:tight-magn-coupl}), the
+Lorentz term is not included explicitly, but instead the equation of
+motion is solved for the guiding center by replacing \(\bm{f}\) by its
+projection along the magnetic field: 
 \begin{equation}
-  \label{eq:dust-gas-velocities}
-  (U_1, V_1) = 
-  \begin{cases}
-    \text{parallel stream} & (-1, 0)\\
-    \text{divergent stream} &
-    \left( \dfrac{X - \mu^{-1}}{R_1},\ \dfrac{Y}{R_1}\right) \ ,
-  \end{cases}
+  \label{eq:projected-force}
+  \widetilde{\bm{f}} = (\bm{f} \cdot \hat{\bm{b}})  \, \hat{\bm{b}} \ ,
 \end{equation}
-where
+where \(\hat{\bm{b}} = \bm{B} / B\).
+
+If distances are measured in units of the radiative turnaround radius,
+\(R\starstar\) (eq.~[\ref{eq:dust-r0}]), and times in units of
+\(R\starstar / v_\infty\), then the grain acceleration
+\(\bm{a}\grain = \bm{f} / m\grain\) in the non-magnetic case can be
+written in non-dimensional form as
 \begin{equation}
-  \label{eq:dust-R1}
-  R_1 = \left( \bigl(X - \mu^{-1}\bigr)^2 + Y^2 \right)^{1/2}
+  \label{eq:grain-accelration}
+  \frac{\bm{a}\grain}{a\starstar}
+  = \frac{R\starstar^2}{2 R^{2}} \hat{\bm{r}}
+  - C\drag \frac{f\drag}{f_*} \hat{\bm{w}} \, 
 \end{equation}
-is the distance from the second source, located at
-\((X, Y) = (\mu^{-1}, 0)\).
+where \(a\starstar = v_\infty^2 / R\starstar\) is a characteristic
+acceleration scale and the dimensionless drag constant is
+\begin{equation}
+  \label{eq:drag-constant}
+  C\drag = \frac{4}{\Qp} \left(\frac{\sound \tau_* \kappa\grain}{v_\infty \kappa}\right)^2 \ .
+\end{equation}
 
-Equations~\eqref{eq:dust-motion} are integrated
+A collection of python programs that implement the equations of this
+appendix is available at
+\url{https://github.com/div-B-equals-0/dust-trajectories}, including
+programs to generate all the grain trajectory figures of this paper
+plus additional figures and movies.  The integration of
+equation~\eqref{eq:grain-equation-motion} is carried out using the
+python library function \texttt{scipy.integrate.odeint}, which wraps
+the Fortran ODEPACK library \citep{Hindmarsh:1983a, Jones:2001a}.
+
+% \begin{figure}
+%   \includegraphics[width=\linewidth]{figs/dust-couple-div-stream}
+%   \caption{Divergent dragoids}
+%   \label{fig:divergent-dragoids}
+% \end{figure}
+
+% To find the dust grain trajectories \(R\grain(\theta)\) in the presence of
+% radiation and drag forces (\S~\ref{sec:bow-wave-drag}), we numerically
+% integrate the equations of motion. We define dimensionless cylindrical
+% polar coordinates,
+% \begin{equation}
+%   \label{eq:dust-XY}
+%   (X, Y) = \left(\frac{R\grain(\theta) \cos\theta } {R_0}, \ 
+%     \frac{R\grain(\theta) \sin\theta } {R_0}\right)
+%   \ ,
+% \end{equation}
+% and dust grain velocities,
+% \begin{equation}
+%   \label{eq:dust-UV}
+%   (U, V) = \left( \frac{\bm{v}\grain \cdot \uvec{x}} {v_\infty}, \ 
+%   \frac{\bm{v}\grain \cdot \uvec{y}} {v_\infty}\right) \ ,
+% \end{equation}
+% where \(\uvec{x}\) and \(\uvec{y}\) are unit vectors along the \(X\)
+% and \(Y\) axes (parallel and perpendicular, respectively, to the
+% symmetry axis).  The grain equation of motion then follows from
+% equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0},
+% \ref{eq:dust-fdrag}--\ref{eq:dust-alpha}) as the following set of
+% coupled differential equations:
+% \begin{gather}
+%   \label{eq:dust-motion}
+%   \begin{aligned}
+%     \frac{d X}{d t} &= U \quad\quad
+%     \frac{d Y}{d t} = V \\
+%     \frac{d U}{d t} &= \frac12 \left[  
+%       X \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 D_1 \left(U - U_1\right)
+%     \right] \\
+%     \frac{d V}{d t} &= \frac12 \left[  
+%       Y \left(X^2 + Y^2\right)^{-3/2} - \alpha\drag^2 D_1 \left(V - V_1\right)
+%     \right] \ ,
+%   \end{aligned}
+% \end{gather}
+% where \((U_1, V_1)\) are the components of the gas velocity (assumed
+% fixed), given by
+% \begin{equation}
+%   \label{eq:dust-gas-velocities}
+%   (U_1, V_1) = 
+%   \begin{cases}
+%     \text{parallel stream} & (-1, 0)\\
+%     \text{divergent stream} &
+%     \left( \dfrac{X - \mu^{-1}}{R_1},\ \dfrac{Y}{R_1}\right) \ ,
+%   \end{cases}
+% \end{equation}
+% where
+% \begin{equation}
+%   \label{eq:dust-R1}
+%   R_1 = \left( \bigl(X - \mu^{-1}\bigr)^2 + Y^2 \right)^{1/2}
+% \end{equation}
+% is the distance from the second source, located at
+% \((X, Y) = (\mu^{-1}, 0)\).  The dimensionless gas density, \(D_1\),
+% normalized by the value at \((X, Y) = (1, 0)\), is
+% \begin{equation}
+%   \label{eq:dust-gas-density}
+%   D_1 = 
+%   \begin{cases}
+%     \text{parallel stream} & 1\\
+%     \text{divergent stream} & \dfrac{\bigl(\mu^{-1} - 1\bigr)^2} {R_1^{2}} \ .
+%   \end{cases}
+% \end{equation}
+
+% Equations~\eqref{eq:dust-motion} are integrated using the python
+% wrapper \texttt{scipy.integrate.odeint} to the Fortran ODEPACK library
+% \citep{Hindmarsh:1983a, Jones:2001a}, with results shown in
+% Figure~\ref{fig:dust-wave-coupling} for parallel-stream cases and
+% Figure~\ref{fig:divergent-dragoids} for divergent-stream cases.
 

### 2019-01-30 papers/Papers1234/sec-dust-bow-discuss.tex
Revise intro and promote subsections to sections
Finish the technical appendices
Move sigma ori to a new paper

@@
-\section{Summary and discussion}
+\section{Discussion}
 \label{sec:summary-discussion}
+
+Are there any objects that might not be bow shocks?
+
+Progression in density:
+\begin{gather*}
+  \text{Increasing density} \longrightarrow \\
+  \text{WBS} \to \text{WBS} + \text{IDW} \to \text{WBS} + \text{DDW} \to \text{(RBW)} \to \text{RBS}
+\end{gather*}
+
+Chief diagnostic for radiation supported bows (RBW or RBS cases) is
+infrared luminosity of bow.  Favored by high densities.
+
+Dust waves favored by high velocities and intermediate densities.
+
+\subsection{$\sigma$ Ori as a dust wave candidate}
+\label{sec:sigma-ori-as}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/sigma-ori-comparison}
+  \caption{Optical and infrared images of $\sigma$~Ori}
+  \label{fig:sig-ori}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/sigma-ori-eastwest-cuts}
+  \caption{Brightness profiles through $\sigma$~Ori inner arc.}
+  \label{fig:sig-ori-cuts}
+\end{figure}
 
@@
 
+\section{Summary and conclusions}
+\label{sec:conclusions}
+
 %%% Local Variables:

### 2019-01-30 papers/Papers1234/sec-dust-bow-intro.tex
Move sigma ori to a new paper

@@
   \label{eq:cooling-coefficient}
-  \Lambda_{\text{warm}} &= \num{3.3e-24} \, T_4^{2.3} \, \si{erg.cm^{-3}.s^{-1}}\\
-  \Lambda_{\text{hot}} &= \num{e-20} \, T_4^{-1}\, \si{erg.cm^{-3}.s^{-1}} \\
+  \Lambda_{\text{warm}} &= \num{3.3e-24} \, T_4^{2.3} \, \si{erg.cm^{3}.s^{-1}}\\
+  \Lambda_{\text{hot}} &= \num{e-20} \, T_4^{-1}\, \si{erg.cm^{3}.s^{-1}} \\
   \Lambda &= \left( \Lambda_{\text{warm}}^{-k} +  \Lambda_{\text{hot}}^{-k} \right)^{-1/k}
@@
   \label{eq:heating-coefficient}
-  \Gamma = \num{1.77e-24} \, T_4^{-1/2} \, \si{erg.cm^{-3}.s^{-1}} \ ,
+  \Gamma = \num{1.77e-24} \, T_4^{-1/2} \, \si{erg.cm^{3}.s^{-1}} \ ,
 \end{equation}
@@
 
-In Appendix~\ref{sec:tight-magn-coupl}, we derive results in the limit
-of zero gas--grain drag, which is appropriate for inertia-confined dust
-waves. We find very different structures, depending on the orientation
-of the field.  For a parallel field (Fig.~\ref{fig:inertia-thB0}), the
-apex of the dust wave occurs at the same point, \(R\starstar\), as in
-the non-magnetic case, but the shape of the dust wave wings is more
-closed, being hemispherical rather than parabolic in shape.  For a
-perpendicular field (Fig.~\ref{fig:inertia-thB90}), on the other hand,
-grains in the apex region are dragged very close to the star and no
-dust wave forms there.  A dust wave can form in the wings, with impact
-parameter \(> R\starstar\), which is roughly parabolic in shape, but
-more swept-back than in the non-magnetic case.  Whether such a dust
-wave will exist in practice depends critically on the size and shape
-of the MHD wind-supported bow shock.
+In Appendix~\ref{sec:tight-magn-coupl}, we derive analytic and
+semi-analytic results in the limit of zero gas--grain drag, which is
+appropriate for inertia-confined dust waves. We find very different
+structures, depending on the orientation of the field.  For a parallel
+field (Fig.~\ref{fig:inertia-thB0}), the apex of the dust wave occurs
+at the same point, \(R\starstar\), as in the non-magnetic case, but
+the shape of the dust wave wings is more closed, being hemispherical
+rather than parabolic in shape.  For a perpendicular field
+(Fig.~\ref{fig:inertia-thB90}), on the other hand, grains in the apex
+region are dragged very close to the star and no dust wave forms
+there.  A dust wave can form in the wings, with impact parameter
+\(> R\starstar\), which is roughly parabolic in shape, but more
+swept-back than in the non-magnetic case.  Whether such a dust wave
+will exist in practice depends critically on the size and shape of the
+MHD wind-supported bow shock.
 
 In Figures~\ref{fig:frozen-stream} and~\ref{fig:frozen-trajectories}
-we show example results for drag-confined dust waves. Apart from the
+we show example results for drag-confined dust waves, which are
+calculated by numerically integrating the grain's equation of motion,
+as described in Appendix~\ref{sec:equat-moti-grains}. Apart from the
 inclusion of the magnetic field, the model parameters are the same as

### 2019-01-30 papers/Papers1234/sigma-ori-arcs.tex
Move sigma ori to a new paper

--- 2019-01-14 papers/Papers1234/dusty-bow-wave.tex
@@
 \title
-{Bow shocks, bow waves, and dust waves}
+% {No radiation supported dust wave around \(\sigma\) Orionis}
+% OR
+{Is the dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Henney, Arthur, \& Tarango Yong]{
-  William J. Henney, S. Jane Arthur, \& Jorge A. Tarango-Yong\\
+\author[Henney \& Arthur]{
+  William J. Henney \& S. Jane Arthur\\
   \AddressCRyA
@@
 \newcommand\starstar{\ensuremath{_{**}}}
+\newcommand\hii{\ion{H}{ii}}
 
@@
 \begin{abstract}
-  Dust waves and bow waves result from the action of a star's
-  radiation pressure on a stream of dust grains that is flowing past
-  it.  They are an alternative mechanism to hydrodynamic bow shocks
-  for explaining the curved arcs of infrared emission seen around some
-  stars.  We develop simple models for the combined effects of
-  radiation and stellar winds on an ambient flow in the case where gas
-  and grains are perfectly coupled. We find that wind-supported bow
-  shocks predominate when the ambient density is low
-  (\(\ltae \SIrange{100}{1000}{cm^{-3}}\)) for a broad class of
-  stellar parameters.  At higher densities, radiation-supported bows
-  can form, tending to be optically thin bow waves in the case of B
-  stars, or optically thick bow shocks in the case of early O stars.
-  We further investigate the dynamics of dust grains when the
-  radiation field is sufficiently strong to overcome the collisional
-  coupling between grains and gas, showing that this occurs at a
-  \textit{rip-point}, where the ratio of radiation pressure to gas
-  pressure exceeds a critical value (\(P\rad/\Pgas > 1000\)).
-
+  We critically evaluate the role of radiation and hydrodynamics in
+  providing internal support for the bow-shaped infrared arc around
+  the massive triple star system \(\sigma\)~Ori Aa/Ab/B in the IC434 \hii{}
+  region.  We present evidence for hydrogen recombination line
+  emission from the arc, which demonstrates that it cannot be a dust
+  wave in which the grains have separated from the gas, as has been
+  previously claimed.  On the other hand, we show that the fraction of
+  the stellar luminosity trapped by the arc is insufficient for it to
+  be supported by radiation if the grains and gas are well coupled.
+  Therefore, the arc must be supported by the ram pressure of an
+  internal wind.  However, the stellar wind from the OB stars in the
+  \(\sigma\)~Ori Aa/Ab/B system are too weak by more than an order of
+  magnitude.  We propose instead that it is the photoevaporated disk
+  wind from the enclosed proplyd IRS~1B that provides the ram pressure
+  support for the bow.
 \end{abstract}
@@
 
-\input{sec-dust-bow-intro}
-\input{sec-dust-bow-discuss}
+\input{sec-dust-case-studies}
 \bibliographystyle{mnras}
 \bibliography{bowshocks-biblio}
-\appendix
-\input{app-cloudy-dust-charging}
-\input{app-dust-wave}
-\input{app-dust-equations}
-%\input{app-dust-ifront-trap}
 

### 2019-02-02 papers/Papers1234/sigma-ori-arcs.tex
Write more on sigma Ori and start AE Aur paper

@@
 % OR
-{Is the dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}
+{\boldmath A dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}
 
@@
   region.  We present evidence for hydrogen recombination line
-  emission from the arc, which demonstrates that it cannot be a dust
-  wave in which the grains have separated from the gas, as has been
-  previously claimed.  On the other hand, we show that the fraction of
-  the stellar luminosity trapped by the arc is insufficient for it to
-  be supported by radiation if the grains and gas are well coupled.
-  Therefore, the arc must be supported by the ram pressure of an
-  internal wind.  However, the stellar wind from the OB stars in the
-  \(\sigma\)~Ori Aa/Ab/B system are too weak by more than an order of
-  magnitude.  We propose instead that it is the photoevaporated disk
-  wind from the enclosed proplyd IRS~1B that provides the ram pressure
-  support for the bow.
+  emission from the arc, which demonstrates that it cannot be a
+  decoupled dust wave, as has previously been claimed.  On the other
+  hand, we show that the fraction of the stellar luminosity trapped by
+  the arc is insufficient for it to be supported by radiation if the
+  grains and gas are well coupled.  Therefore, the arc must be
+  supported by the ram pressure of an internal wind.  However, the
+  stellar winds from the OB stars in the \(\sigma\)~Ori Aa/Ab/B system seem
+  too weak to provide this support on their own.  We propose instead
+  that it is the photoevaporated disk wind from the enclosed proplyd
+  IRS~1B that dominates the ram pressure support for the bow.
 \end{abstract}
@@
 
-\input{sec-dust-case-studies}
+\section{Why the inner arc cannot be a decoupled dust wave}
+\label{sec:why-not-dust}
+
+\section{Why the inner arc cannot be radiation-supported}
+\label{sec:why-not-radiation}
+
+SEDs of the two arcs
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/sigma-ori-comparison}
+  \caption{Optical and infrared images of $\sigma$~Ori}
+  \label{fig:sig-ori}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/sigma-ori-eastwest-cuts}
+  \caption{Brightness profiles through $\sigma$~Ori inner arc.}
+  \label{fig:sig-ori-cuts}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/sigma-ori-inner-outer}
+  \caption{Combined mid-infrared and far-infrared views of the inner and outer arcs around $\sigma$~Ori}
+  \label{fig:sig-ori-outer}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \caption{Spectral energy distributions of arcs around $\sigma$~Ori}
+  \label{fig:sig-ori-SED}
+\end{figure}
+
+\section{Weak stellar winds from the massive triple Aa/Ab/B}
+\label{sec:stellar-winds-AB}
+
+\section{Photoevaporation flow from the proplyd IRS~1B}
+\label{sec:phot-flow-from}
+
+\section{The nature of the outer dust arc}
+
+\section{Conclusions}
+\label{sec:conclusions}
+
 \bibliographystyle{mnras}

### 2019-02-05 papers/Papers1234/_region_.tex
Massive figure caption for observational diagnostics

--- 2017-12-06 papers/Papers1234/_region_.tex
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2017}
-
+\pubyear{2019}
 \DeclareMathOperator{\sgn}{sgn}
@@
 \DeclareMathOperator{\GammaFunc}{\Gamma}
+\DeclareMathOperator\erf{erf}
 \newcommand\w{\ensuremath{\mathrm{w}}}
@@
 
-\message{ !name(app-shape-parameters.tex) !offset(-107) }
-
-\section{Analytic derivation of thin-shell bow shapes}
-\label{sec:thin-shell-shapes}
-
-In this appendix, we provide analytic calculations of the planitude
-(exact) and alatude (approximate) for the wilkinoid, cantoids, and
-ancantoids.  We first consider the most general case of the
-ancantoids, and then show how results for cantoids and the wilkinoid
-follow as special cases.
-
-\subsection{Planitude of ancantoids}
-\label{sec:ancantoid-planitude}
-
-From equations~\eqref{eq:radius-curvature} and~\eqref{eq:planitude},
-the planitude depends on the apex second derivative,
-\(R_{\theta\theta,0}\), as
-\begin{equation}
-  \label{eq:planitude-from-2nd-derivative}
-  \Pi = \left(  1 - R_{\theta\theta,0} / R_0\right)^{-1} \ .
-\end{equation}
-From equation~\eqref{eq:taylor-R-theta}, the second derivative can be
-found from the coefficient of \(\theta^2\) in the Taylor expansion
-of \(R(\theta)\).  Since we do not have \(R(\theta)\) in explicit analytic form,
-we proceed via a Taylor expansion of the implicit
-equations~\eqref{eq:crw-angles}
-and~\eqref{eq:ancantoid-theta-theta1-implicit}, retaining terms up to
-\(\theta^4\) to obtain from
-equation~\eqref{eq:ancantoid-theta-theta1-implicit}:
-\begin{equation}
-  \label{eq:taylor-expansion-implicit}
-  \theta_1^2 = \beta \theta^2 \left( 1 + C_{k\beta} \theta^2\right) + \mathcal{O}(\theta^6)\ , 
-\end{equation}
-with the coefficient \(C_{k\beta}\) given by
-\begin{equation}
-  \label{eq:C-k-beta}
-  C_{k\beta} = \frac{1}{15} - \frac{3k}{20} - \frac{\beta}{15}  \ .
-\end{equation}
-Note that it is necessary to include the \(\theta^4\) term in the expansion
-of \(\theta_1^2\) so that \(\theta_1/\theta\) is accurate to order
-\(\theta^2\).  Then, from equation~\eqref{eq:crw-angles} we find
-\begin{align}
-  \label{eq:taylor-R-over-D}
-  \frac{R}{D} & = \frac{\sin \theta_1} {\sin (\theta + \theta_1)} \nonumber \\
-              & = \frac{\beta^{1/2}}{1+\beta^{1/2}}
-                \left\lbrace 1 + \theta^2
-                \left[ \frac{C_{k\beta}} {2 \left(1+\beta^{1/2}\right)}
-                + \frac{1}{6} \left(1+2\beta^{1/2} \right)
-                \right]
-                \right\rbrace + \mathcal{O}(\theta^4) \ ,
-\end{align}
-where in the second line we have carried out a Taylor expansion of the
-two \(\sin\) terms and substituted
-\eqref{eq:taylor-expansion-implicit}.  Comparing coefficients of unity
-and \(\theta^2\) between equations~\eqref{eq:taylor-R-theta} and
-\eqref{eq:taylor-R-over-D} we find
-\begin{align}
-  \label{eq:again-R0-over-D}
-  \frac{R_0} {D} &= \frac{\beta^{1/2}}{1+\beta^{1/2}} \\
-  \label{eq:final-second-derivative}
-  \frac{R_{\theta\theta,0}} {R_0} &= \frac{C_{k\beta}}{1+\beta^{1/2}}+\frac{1}{3}\left(1+2\beta^{1/2}\right) \ ,
-\end{align}
-so that the final result for the planitude, from~\eqref{eq:planitude-from-2nd-derivative}, is
-\begin{equation}
-  \label{eq:final-planitude}
-  \text{ancantoid} \quad
-  \Pi = \left[ {1 - \frac{C_{k\beta}}{1+\beta^{1/2}} - \frac{1}{3}\left(1+2\beta^{1/2}\right)}
-  \right]^{-1} \ .
-\end{equation}
-
-\subsection{Alatude of ancantoids}
-\label{sec:ancantoid-alatude}
-
-To find the alatude, \(\Lambda = R_{90} / R_0\), we use equation~\eqref{eq:crw-angles} at \(\theta = 90^\circ\) to write
-\begin{equation}
-  \label{eq:Lambda-from-theta-1-90}
-  \Lambda = \frac{D} {R_0} \tan \theta_{1,90} \ , 
-\end{equation}
-where \(\theta_{1,90} = \theta_1(\theta = 90^\circ)\), which, following
-equation~\eqref{eq:ancantoid-theta-theta1-implicit}, must satisfy
-\begin{equation}
-  \label{eq:theta-1-90-implicit}
-  \theta_{1,90} \cot \theta_{1,90}  = 1 - \frac{2 \beta}{k + 2} \ . 
-\end{equation}
-Combining \eqref{eq:Lambda-from-theta-1-90} and
-\eqref{eq:theta-1-90-implicit} with \eqref{eq:again-R0-over-D} yields
-\begin{equation}
-  \label{eq:Lambda-beta-xi-theta-1-90}
-  \Lambda = \frac{ \left(1 + \beta^{1/2}\right) \,\theta_{1,90}} {\beta^{1/2} \left(1 - \xi_k \beta\right)} \ ,
-\end{equation}
-where
-\begin{equation}
-  \label{eq:xi-k}
-  \xi_k = \frac{2} {k +2} \ .
-\end{equation}
-We now take the Taylor expansion of equation~\eqref{eq:theta-1-90-implicit} to find
-\begin{equation}
-  \label{eq:theta-1-90-Taylor}
-  \theta_{1,90}^2 + \tfrac{1}{15}  \theta_{1,90}^4 + \mathcal{O}(\theta_{1,90}^6)
-  = 3 \xi_k \beta \ , 
-\end{equation}
-which, if \(\theta_{1,90}\) is small, has the approximate solution
-\begin{equation}
-  \label{eq:theta-1-90-approx}
-  \theta_{1,90} \approx \left( \frac{3 \xi_k \beta} {1 + \tfrac15 \xi_k \beta} \right) \ .
-\end{equation}
-Substituting back into equation~\eqref{eq:Lambda-from-theta-1-90}
-yields an approximate value for the alatude of
-\begin{equation}
-  \label{eq:Lambda-approx}
-  \text{ancantoid} \quad
-  \Lambda \approx \frac {(3 \xi_k)^{1/2} \left( 1 + \beta^{1/2} \right)}
-  { \left( 1 + \tfrac15 \xi_k \beta \right)^{1/2} \left( 1 - \xi_k \beta \right)} \ .
-\end{equation}
-This approximation is surprisingly accurate, with a relative error of
-order \(1\%\) even for \(\beta\) as large as \(0.5\) with \(k = 0\).  The
-leading term in the relative error scales as \((\beta / (k + 2))^2\), so the
-approximation is even better for smaller \(\beta\) and larger \(k\).
-
-\subsection{Planitude and alatude of cantoids and wilkinoid}
-\label{sec:cantoid-wilkinoid-shapes}
-
-Since \(\Pi\) and \(\Lambda\) depend on only that portion of the inner wind
-emitted in the forward hemisphere, \(\theta \le 90^\circ\), the results for the
-cantoids can be found by taking \(k = 0\), in which case
-equations~(\ref{eq:C-k-beta}, \ref{eq:final-planitude}, \ref{eq:xi-k},
-\ref{eq:Lambda-approx}) yield
-\begin{gather}
-  \label{eq:cantoid-Pi-Lambda}
-  \text{cantoid} \quad
-  \begin{cases}
-    \quad \Pi &= \dfrac {5} {3 \left( 1 - \beta^{1/2} \right)}\\[12pt]
-    \quad \Lambda &= \dfrac { \sqrt 3} {\left( 1 + \tfrac15 \beta \right)^{1/2} \left( 1 - \beta^{1/2} \right)} \ .
-  \end{cases}
-\end{gather}
-The wilkinoid shape is equal to the \(\beta \to 0\) limit of the cantoid, so
-its planitude and alatude are given by:
-\begin{gather}
-  \label{eq:wilkinoid-Pi-Lambda}
-  \text{wilkinoid} \quad
-  \begin{cases}
-    \quad \Pi &= \dfrac {5} {3}\\[10pt]
-    \quad \Lambda &= \sqrt 3 \ .
-  \end{cases}
-\end{gather}
-
-\subsection{Asymptotic opening angle}
-\label{sec:asympt-open-angle}
-
-The asymptotic opening angle
-of the far wings, \(\theta_\infty\), can be found from
-equation~\eqref{eq:ancantoid-theta-theta1-implicit} for the
-ancantoids, together with the condition that
-\(\theta_\infty + \theta_{1\infty} = \pi\).  These yield the implicit equation
-\begin{equation}
-  \label{eq:anacantoid-theta-inf}
-  \theta_\infty - \left( \frac {k + 2 (1 - \beta)} {k + 2} \right) \tan \theta_\infty
-  = \pi + 2 \beta I_k(\pi/2) \ ,
-\end{equation}
-where
-\begin{equation}
-  I_k(\pi/2) = \frac{\sqrt \pi}{4} \,
-      \frac{  \GammaFunc\left( \frac{k+1}{2} \right)} {\GammaFunc\left(\frac{k+4}{2}\right)}
-\end{equation}
-and \(\GammaFunc\) is the usual Gamma function.  This can be compared with the equivalent result obtained by \CRW{} for the cantoids:
-\begin{equation}
-  \label{eq:cantoid-theta-inf}
-  \theta_\infty - \tan \theta_\infty = \frac{\pi}{1 - \beta} \ .
-\end{equation}
-Note that, unlike the case for \(\Pi\) and \(\Lambda\),
-equation~\eqref{eq:anacantoid-theta-inf} does \emph{not} reduce to
-equation~\eqref{eq:cantoid-theta-inf} in the limit \(k \to 0\).  This is
-because, for \(\theta > 90^\circ\), the \(k = 0\) ancantoid differs from the
-cantoid since there is no wind in the backward hemisphere (see
-Figure~\ref{fig:anisotropic-arrows}).  Therefore there is less inner
-support for the far wings of the bow, and so \(\theta_\infty\) is smaller than
-in the cantoid case.  The wilkinoid result again follows from
-\(\beta \to 0\), implying that \(\theta_\infty = \pi\), or, in other words, that
-the far wings are asymptotically parallel to the symmetry axis, as is
-the case for the paraboloid (App.~\ref{app:parabola}).  In the case of
-the wilkinoid, however, the behavior is cubic in the wings,
-\(z \sim r^3\), as opposed to quadratic as in the paraboloid.
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "quadrics-bowshock"
-%%% End:
-
-\message{ !name(quadrics-bowshock.tex) !offset(-137) }
+\message{ !name(sec-dust-bow-discuss.tex) !offset(-77) }
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
+  \caption[K18 pair plot]{Pair plots of correlations between observed
+\message{ !name(dusty-bow-wave.tex) !offset(41) }
 

### 2019-02-05 papers/Papers1234/app-dust-wave.tex
Finish the technical appendices
Massive figure caption for observational diagnostics

@@
 \end{equation}
-with \(\Pi = \Lambda = 1\).  Note, however, that this only applies to
-streamlines with \(b \le R\starstar\).  For those with
-\(b > R\starstar\), the maximum \(V\rad\), which occurs at \(x = 0\),
-is smaller than unity, so that grains on these streamlines slow down
-as they go past the star, but then speed up again without turning
-round.
+yielding planitude and alatude of \(\Pi = \Lambda = 1\).  Note, however, that
+this only applies to streamlines with \(b \le R\starstar\).  For those
+with \(b > R\starstar\), the maximum \(V\rad\), which occurs at
+\(x = 0\), is smaller than unity, so that grains on these streamlines
+do not turn around, although they do slow down temporarily as they go
+past the star.
 
@@
   \label{eq:thB-0-density}
-  n\grain(R) = \frac{n \bar{m} Z\grain}{m\grain} \left( 1 - R^{-1} \right)^{-1/2} \ ,
+  n\grain(R) = \frac{n \bar{m} Z\grain}{m\grain}
+  \left( 1 - \frac{R\starstar}{R} \right)^{-1/2} \ ,
 \end{equation}

### 2019-02-05 papers/Papers1234/app-k17-k18.tex
Massive figure caption for observational diagnostics

\section{Bow shock data from Kobulnicky et al. (2016, 2017, 2018)}
In a series of papers \citet{Kobulnicky:2016a, Kobulnicky:2017a,
  Kobulnicky:2018a} provide an extensive mid-infrared-selected sample
of over 700 candidate stellar bow shock nebulae.  For 20 of these
sources, reliable distances and spectral classifications are provided
(Table~5 of \citealp{Kobulnicky:2017a} and 
\citealp{Kobulnicky:2018a}), and these are used in
\S~\ref{sec:summary-discussion}, where we discuss the
\(\tau\)--\(\eta\) diagnostic diagram.  In this appendix, we outline our
treatment and analysis of the data in these catalogs, which differs in
some important respects from that of the original authors.

The most important quantity to be derived from the observations is the
absorption optical depth, \(\tau\), of the bow shell to the stellar radiation.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/K18-flux-comparison}
  \includegraphics[width=\linewidth]{figs/K17-tau-comparison}
  \caption{Comparison}
  \label{fig:k17-k18-comparison}
\end{figure}

% So everything looks OK, except:

% * Source 67 is over 10 times too bright in the Kobulnicky table

% So, I will use my fluxes instead.

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
  \caption[K18 pair plot]{Pair plots of correlations between observed
    and derived parameters of bows from the \citep{Kobulnicky:2018a}
    sample.}
  \label{fig:K18-pairplot-edited}
\end{figure*}

% In this graph we compare the original luminosity ratio taken directly from the Kobulnicky (2017) table (x axis) with the ratio calculated using my new total IR fluxes, combined with the new luminosities in the Kobulnicky (2018) table (y axis).   Most of the points show reasonable agreement between the two methods, with a few exceptions:

% * 67: this had the $F_\text{IR}$ overestimated in K17.  Using a more reasonable value gives a lower $\tau$
% * 341: The spectral class has changed from B2 (K17) to O9 (K18), increasing the assumed $L_*$, which lowers $\tau$
% * 411: The luminosity class has changed from Ib (K17) to V (K18), so $L_*$ has been greatly reduced, which increases the estimated $\tau$

% And there doesn't seem to be any significant correlation with stellar luminosity.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dusty-bow-wave"
%%% End:

### 2019-02-05 papers/Papers1234/sec-dust-bow-discuss.tex
Write more on sigma Ori and start AE Aur paper
Massive figure caption for observational diagnostics

@@
 
-\subsection{$\sigma$ Ori as a dust wave candidate}
-\label{sec:sigma-ori-as}
+\newcommand\IR{\ensuremath{_{\text{IR}}}}
 
-\begin{figure}
+In order to provide an empirical anchor to our theoretical
+calculations, we now consider how the parameters of our models might
+be determined from observations.  A fundamental parameter is the
+optical depth, \(\tau\), of the bow shell to UV radiation, which
+determines what fraction of the stellar photon momentum is available
+to support the shell (see \S~\ref{sec:three-bow-regimes}).  But the
+same photons also heat the dust grains in the bow, which re-radiate
+that energy predominantly at mid-infrared wavelengths (roughly
+\SIrange{10}{100}{\um}) with luminosity \(L\IR\).  Assuming that
+Ly\(\alpha\) and mechanical heating of the dust shell is negligible and
+that the emitting shell subtends a solid angle \(\Omega\), as seen from the
+star, then the optical depth can be estimated as
+\begin{equation}
+  \label{eq:tau-empirical}
+  \tau = -\ln \left( 1 - \frac{4\pi}{\Omega} \frac{L\IR}{L_*} \right)
+  \approx \frac{2 L\IR}{L_*} \ ,
+\end{equation}
+where the last approximate equality holds if \(\tau \ll 1\) and the shell
+emission covers one hemisphere.\footnote{%
+  The \(\tau\) of \S~\ref{sec:three-bow-regimes} is not exactly the same
+  as the \(\tau\) of equation~\eqref{eq:tau-empirical}, but is larger by
+  a factor of \(1 + \varpi (1 - g)/(1 - \varpi)\), where \(\varpi\) is
+  the grain albedo and \(g\) the scattering asymmetry (see
+  App.~\ref{sec:gas-free-bow}).} %
+
+\begin{table}
   \centering
-  \includegraphics[width=\linewidth]{figs/sigma-ori-comparison}
-  \caption{Optical and infrared images of $\sigma$~Ori}
-  \label{fig:sig-ori}
-\end{figure}
+  \caption[Observational]{Key observational parameters for star/bow systems}
+  \label{tab:observations}
+  \begin{tabular}{l S S S}
+    \toprule
+    Star & {\(L_* / \si{L_\odot}\)} & {\(L_{\text{IR}} / \si{L_\odot}\)} & {\(R_0 / \si{pc}\)} \\
+    \midrule
+    \thD & 2.95e4 & 620 & 0.003 \\
+    LP~Ori & 1600 & 240 & 0.01 \\
+    \(\sigma\)~Ori & 6e4 & 15 & 0.12 \\[\smallskipamount]
+    K18 Sources & \numrange{1.4e4}{8.7e5} & \numrange{8}{2800} & \numrange{0.02}{1.35} \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/sigma-ori-eastwest-cuts}
-  \caption{Brightness profiles through $\sigma$~Ori inner arc.}
-  \label{fig:sig-ori-cuts}
-\end{figure}
+  \includegraphics[width=\linewidth]{figs/All-sources-eta-tau}
+  \caption[Observational diagnostic diagram]{Observational diagnostic
+    diagram for bow shocks.  The shell optical depth \(\tau\) (\(x\)
+    axis) and momentum efficiency \(\eta\shell\) (\(y\) axis) can be
+    estimated from observations of the bolometric stellar luminosity,
+    infrared shell luminosity, and shell radius, as described in the
+    text.  Results are shown for the 20 sources (circle symbols) from
+    \citet{Kobulnicky:2018a} plus three further sources (square
+    symbols), where we have obtained the measurements ourselves (see
+    Tab.~\ref{tab:observations}).  The color of each symbol indicates
+    the stellar luminosity (dark to light) as indicated by the scale
+    bar. The shell pressure is determined assuming a gas temperature
+    \(T = \SI{e4}{K}\), an absorption opacity
+    \(\kappa = \SI{600}{cm^2.g^{-1}}\), and a thickness-to-radius ratio
+    \(H/R = 0.25\).  The sensitivity of the results to a
+    factor-of-three change in each parameter is shown in the upper
+    inset box.  Exceptions are the two Orion Nebula sources, \thD{}
+    and LP~Ori, where the small dim squares show the results of
+    assuming the standard shell parameters, while the large squares
+    show the results of modifications according to the peculiar
+    circumstances of each object, as described in the text.  The lower
+    inset box shows the sensitivity of the results to a factor-of-two
+    uncertainty in each observed quantity: distance to source \(D\);
+    stellar luminosity \(L_*\), shell infrared flux \(F\IR\); shell
+    angular size \(\theta\).  Lines and shading indicate different
+    theoretical bow regimes (see \S\S~\ref{sec:strong-gas-grain} and
+    \ref{sec:imperf-coupl-betw}).  The dashed blue diagonal line
+    corresponds to radiation-supported bows, while the upper left
+    region corresponds to wind-supported bows.  The upper right corner
+    (purple) corresponds to optically thick bow shocks, while the
+    lower left corner (yellow) is the region where grain--gas
+    separation \textit{may} occur, leading to a potential dust wave.
+    However, the existence of a dust wave in this region is not
+    automatic, since it only includes one of the four necessary
+    conditions (\S~\ref{sec:exist-cond-separ} and
+    \S~\ref{sec:grain-traj-with}). The lower-right region is strictly
+    forbidden unless the assumption that dust heating is dominated by
+    stellar radiation is violated. }
+  \label{fig:All-sources-eta-tau}
+\end{figure*}
 

### 2019-02-05 papers/Papers1234/sec-dust-bow-intro.tex
Massive figure caption for observational diagnostics

@@
     & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
-                   & \ref{fig:zones-v-n-plane}a,
-                     \ref{fig:decouple-v-n-plane},
-                     \ref{fig:decouple-v40-versus-n} \\
+                   & \ref{fig:zones-v-n-plane}a, \ref{fig:existence-dust-wave}a,
+                     \ref{fig:phase-space-trajectories}--~\ref{fig:frozen-trajectories} \\
     Main-sequence OB stars
     & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
-                   & \ref{fig:zones-v-n-plane}b\\
+                   & \ref{fig:zones-v-n-plane}b, \ref{fig:existence-dust-wave}b \\
     & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
-                   & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
+                   & \ref{fig:zones-v-n-plane}c, \ref{fig:existence-dust-wave}c \\[\smallskipamount]
     Blue supergiant star

### 2019-02-07 papers/Papers1234/app-cloudy-dust-charging.tex
Write more discussion and add new cloudy dust extinction fig

@@
 the plasma physics code Cloudy \citep{Ferland:2013a, Ferland:2017a},
-which self consistently solves the multi-frequency radiative transfer
+which self-consistently solves the multi-frequency radiative transfer
 together with thermal, ionization, and excitation balance of all
@@
 designed to reproduce the average Galactic extinction curve
-\citep{Weingartner:2001a, Abel:2008a}.
+\citep{Weingartner:2001a, Abel:2008a}.  The optical properties of each
+grain species are calculated using Mie theory \citep{Bohren:1983a},
+assuming solid spheres.  The resultant wavelength-dependent extinction
+properties of the mixture are summarised in
+Figure~\ref{fig:cloudy-ism-dust-opacity}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/cloudy-ism-dust-opacity}
+  \caption{Extinction properties of Cloudy's standard ``ISM'' dust
+    mixture. %
+    (a)~Wavelength dependence of mean values over the entire mixture
+    of three dimensionless quantities related to scattering: albedo,
+    \(\varpi\) (solid line); scattering asymmetry,
+    \(g = \langle \cos\theta \rangle\) (dashed line); ratio of radiation pressure
+    efficiency to absorption efficiency, \(Q_P / Q_{\text{abs}}\)
+    (dotted line).
+    %
+    (b)~Wavelength dependence of mass opacity (cross section per unit
+    mass of gas) for the whole mixture (heavy black line) and broken
+    down by size bin and grain composition (colored lines, see key). }
+  \label{fig:cloudy-ism-dust-opacity}
+\end{figure}
 
@@
 circumstellar environs of luminous stars, we calculate a series of
-spherically symmetric, steady-state, constant density Cloudy models,
+spherically symmetric, steady-state, constant density Cloudy simulations,
 illuminated by the stars listed in Table~\ref{tab:stars}, with stellar
@@
 the TLUSTY model atmosphere code \citep{Lanz:2003a, Lanz:2007a}.
-Models are calculated for hydrogen densities of
+Simulations are run for hydrogen densities of
 \numlist{1;10;100;e3;e4} \si{cm^{-3}} and assuming standard \hii{} region
@@
   \caption{Dust properties as a function of radius from star for three
-    selected Cloudy models. (a)~\SI{40}{M_\odot} main-sequence star in
+    selected Cloudy simulations. (a)~\SI{40}{M_\odot} main-sequence star in
     medium of density \SI{e4}{cm^{-3}}. (b)~\SI{10}{M_\odot} main-sequence
@@
 Figure~\ref{fig:multi-dustprops} shows resultant radial profiles of
-dust properties for representative models: grain temperature, grain
+dust properties for representative simulations: grain temperature, grain
 abundance, grain potential, and grain drift velocity.  Line types
@@
 show results for a high-density (\(n = \SI{e4}{cm^{-3}}\)), compact
-(\(R \approx \SI{0.1}{pc}\)) region around an early O star, where the grain
+(\(R \approx \SI{0.1}{pc}\)) region around an early O~star, where the grain
 temperature is very high, especially for the smaller silicate grains,
 and sublimation significantly reduces the grain abundance in the inner
-regions.  The remaining columns show low density
+regions.  The remaining columns show low-density
 (\(n = \SI{1}{cm^{-3}}\)), extended (\(R \sim \SI{10}{pc}\)) regions
@@
   \caption{Drift velocity \(w\drift\) versus radiation parameter
-    \(\Xi\). Each line represents a model with ambient density and
+    \(\Xi\). Each line represents a simulation with ambient density and
     stellar type as indicated in the key.  Results are shown for
@@
     range of radiation parameter, \(\Xi = 1000 \pm \SI{0.5}{dex}\), that
-    encompasses the rip point for all models. }
+    encompasses the rip point for all simulations. }
   \label{fig:drift-gn}
@@
 Fig.~\ref{fig:multi-dustprops}) is qualitatively similar for all the
-models.  The grains are predominantly positively charged, with high
+simulations.  The grains are predominantly positively charged, with high
 potentials (\(> 10\) times the thermal energy of gas particles) close
@@
 persists well into the neutral region.  There are small differences
-between the models due to the increasing relative importance of the
+between the simulations due to the increasing relative importance of the
 EUV radiation for hotter stars, which leads to a deeper dip in the
@@
 Equilibrium drift velocity for each grain species is calculated in the
-Cloudy models using the same theory \citep{Draine:1979a} as outlined
+Cloudy simulations using the same theory \citep{Draine:1979a} as outlined
 in \S~\ref{sec:drag-force-grains}.  The way that this is implemented
@@
 modified the code so as to instead always prefer the slower subthermal
-branch when multiple solutions are available.  This makes the most
+branch whenever multiple solutions are available.  This makes the most
 sense in our context, where the grains are moving towards the star and
@@
 Figure~\ref{fig:multi-dustprops} and again they are qualitatively
-similar for all the models.  Close to the star, the radiation force is
+similar for all the simulations.  Close to the star, the radiation force is
 higher than the upper limit on the Coulomb drag force
@@
 all combinations of stellar parameters and ambient densities for which
-we have run models.  It can be seen that the rip point does indeed
-always occur at a similar value of \(\Xi \sim 1000\) for all models, albeit
+we have run simulations.  It can be seen that the rip point does indeed
+always occur at a similar value of \(\Xi \sim 1000\) for all simulations, albeit
 with some variation according to the spectral type of the star and the
@@
 \(\Xi_\dag \approx \num{e4}\), but such grains are only minor contributors to the
-UV opacity (\(< 10\%\) in EUV and \(< 1\%\) in FUV).
+UV opacity (\(< 10\%\) in EUV and \(< 1\%\) in FUV, see
+Fig.~\ref{fig:cloudy-ism-dust-opacity}).
 
@@
 Finally, Figure~\ref{fig:phi-vs-Xi} shows the slow dependence of grain
-potential on radiation parameter for all the models on a linear versus
+potential on radiation parameter for all the simulations on a linear versus
 logarithmic scale.  The logarithmic fit of

### 2019-02-07 papers/Papers1234/app-k17-k18.tex
Write more discussion and add new cloudy dust extinction fig

@@
 \section{Bow shock data from Kobulnicky et al. (2016, 2017, 2018)}
+\label{app:bow-shock-data}
+
 In a series of papers \citet{Kobulnicky:2016a, Kobulnicky:2017a,

### 2019-02-07 papers/Papers1234/sec-dust-bow-discuss.tex
Write more discussion and add new cloudy dust extinction fig

@@
 calculations, we now consider how the parameters of our models might
-be determined from observations.  A fundamental parameter is the
-optical depth, \(\tau\), of the bow shell to UV radiation, which
-determines what fraction of the stellar photon momentum is available
-to support the shell (see \S~\ref{sec:three-bow-regimes}).  But the
-same photons also heat the dust grains in the bow, which re-radiate
-that energy predominantly at mid-infrared wavelengths (roughly
-\SIrange{10}{100}{\um}) with luminosity \(L\IR\).  Assuming that
-Ly\(\alpha\) and mechanical heating of the dust shell is negligible and
-that the emitting shell subtends a solid angle \(\Omega\), as seen from the
-star, then the optical depth can be estimated as
+be determined from observations.  The parameter space diagrams, such
+as Figures~\ref{fig:zones-v-n-plane} and
+\ref{fig:existence-dust-wave}, are not particularly useful in this
+regard, since in many cases the ambient density and relative stellar
+velocity are not directly measured.  Instead, we aim to construct
+diagnostics based on the most common observations, which are of the
+infrared dust emission.
+
+A fundamental parameter is the optical depth, \(\tau\), of the bow shell
+to UV radiation, which determines what fraction of the stellar photon
+momentum is available to support the shell (see
+\S~\ref{sec:three-bow-regimes}).  But the same photons also heat the
+dust grains in the bow, which re-radiate that energy predominantly at
+mid-infrared wavelengths (roughly \SIrange{10}{100}{\um}) with
+luminosity \(L\IR\).  Assuming that Ly\(\alpha\) and mechanical heating of
+the dust shell is negligible and that the emitting shell subtends a
+solid angle \(\Omega\), as seen from the star, then the optical depth can
+be estimated as
 \begin{equation}
@@
   App.~\ref{sec:gas-free-bow}).} %
+
+A second important parameter is the thermal plus magnetic pressure in
+the shocked shell, which is doubly useful since in a steady state it
+is equal to \emph{both} the internal supporting pressure (wind ram
+pressure plus absorbed stellar radiation) \emph{and} the external
+confining pressure (ram pressure of ambient stream).  The shell pressure is
+not given directly by the observations, but can be determined as
+follows:
+\begin{enumerate}[1.]
+\item The shell mass column (\si{g.cm^{-2}}) can be estimated from the
+  optical depth by assuming an effective UV opacity: \(\Sigma\shell = \tau / \kappa\)
+\item The shell density (\si{g.cm^{-3}}) can be found from the mass
+  column if the shell thickness is known:
+  \(\rho\shell = \Sigma / h\shell\).  In the absence of other information, a
+  fixed fraction of the shell radius can be used.  In particular, we
+  normalize by a typical value of one~quarter\footnote{%
+    This corresponds to a Mach number \(\M_0 = \surd 3\) if the stream
+    shock is radiative, or \(\M_0 \gg 1\) if non-radiative (see
+    \S~\ref{sec:radi-cool-lengths}).  Further discussion is given in
+    Appendix~\ref{app:bow-shock-data}} %
+  the star--apex distance:
+  \(h_{1/4} = h\shell / (0.25 R_0)\).
+\item Finally, the pressure (\si{dyne.cm^{-2}}) follows by assuming
+  values for the sound speed and Alfvén speed:
+  \(P\shell = \rho\shell (\sound^2 + \frac12 v\alfven^2) \).
+\end{enumerate}
+It is natural to normalize this pressure to the stellar radiation
+pressure at the shell, so we define a shell momentum efficiency
+\newcommand\pc{\ensuremath{_{\text{pc}}}}
+\begin{equation}
+  \label{eq:eta-shell}
+  \eta\shell \equiv \frac{P\shell}{P\rad}
+  = \frac{4\pi R_0^2\, (\sound^2 + \frac12 v\alfven^2)\, \tau}{L_*\, \kappa\, h\shell}
+  \approx 245 \frac{R\pc \, T_4 \, \tau}{L_4 \, \kappa_{600} \, h_{1/4}} \ , 
+\end{equation}
+where in the last step we have assumed ionized gas with negligible
+magnetic support (\(v\alfven \ll \sound\)) and written the stellar
+luminosity and shell parameters in terms of typical values, as in
+\S~\ref{sec:depend-stell-type}.  Note that the shell momentum
+efficiency is simply the reciprocal of the radiation parameter of
+equation~\eqref{eq:Xi-Prad-over-Pgas}:
+\(\eta\shell = \Xi\shell^{-1}\), which provides yet a third use for
+\(\eta\shell\), since \(\Xi\) is paramount in determining whether the
+grains and gas remain well-coupled (see
+\S~\ref{sec:exist-cond-separ}).
 
@@
     \S~\ref{sec:grain-traj-with}). The lower-right region is strictly
-    forbidden unless the assumption that dust heating is dominated by
-    stellar radiation is violated. }
+    forbidden, except in case of violation of the assumption that dust
+    heating be dominated by stellar radiation. }
   \label{fig:All-sources-eta-tau}
 \end{figure*}
+
+Mass loss rates - starting from \citet{Kobulnicky:2010a}
+
+Different scenarios for producing velocities: dynamic ejection from
+young clusters \citep{Hoogerwerf:2001a, Oh:2016c} produce high
+velocities, dissolution of binary systems following core-collapse SN
+\citep{Renzo:2018a} tend to produce lower velocities for the unbound
+MS companion (walkaways, slower than 30 km/s).  Also, champagne flows
+have low velocities.
 

### 2019-02-07 papers/Papers1234/sec-dust-bow-intro.tex
Write more discussion and add new cloudy dust extinction fig

@@
     bow size (star-apex separation, \(R_0\)), while gray shading shows
-    the radiation bow wave regime, with lower border \(\tau = \eta\) and
+    the radiation bow wave regime, with lower border \(\tau = \eta\wind\) and
     upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
@@
   \label{eq:wind-efficiency}
-  \dot{M} V = \eta L / c \ , 
-\end{equation}
-where \(\eta\) is the momentum efficiency of the wind, which is typically
+  \dot{M} V = \eta\wind L / c \ , 
+\end{equation}
+where \(\eta\wind\) is the momentum efficiency of the wind, which is typically
 \(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
@@
   \label{eq:rad-full-x}
-  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta = 0 \ .
+  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta\wind = 0 \ .
 \end{equation}
@@
   \begin{cases}
-    \text{if \(\tau_* \gg 1\):} & (1 + \eta)^{1/2}  \\
-    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta \bigr)^{1/2} \approx
+    \text{if \(\tau_* \gg 1\):} & (1 + \eta\wind)^{1/2}  \\
+    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta\wind \bigr)^{1/2} \approx
     \begin{cases}
-      \text{if \(\tau_*^2 \gg \eta\):} & 2 \tau_*  \\
-      \text{if \(\tau_*^2 \ll \eta\):} & \eta^{1/2} 
+      \text{if \(\tau_*^2 \gg \eta\wind\):} & 2 \tau_*  \\
+      \text{if \(\tau_*^2 \ll \eta\wind\):} & \eta\wind^{1/2} 
     \end{cases}
@@
 \end{equation}
-The first case, \(x \approx (1 + \eta)^{1/2}\), corresponds to a
+The first case, \(x \approx (1 + \eta\wind)^{1/2}\), corresponds to a
 \textit{radiation bow shock} (RBS); the second case,
 \(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave} (RBW);
-and the third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow
+and the third case, \(x \approx \eta\wind^{1/2}\), corresponds to a \textit{wind bow
   shock} (WBS).  The two bow shock cases are similar in that the
@@
     & {\(M / \si{M_\odot}\)} & {\(L_4\)}
-    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta \)}
+    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta\wind \)}
     & {Sp.~Type} 
@@
   \label{eq:wind-eta-typical}
-  \eta = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
+  \eta\wind = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
 \end{equation}
@@
 wind momentum efficiency is also a steep function of mass
-(\(\eta \sim M^3\)), approaching unity for early O~stars, but falling to
+(\(\eta\wind \sim M^3\)), approaching unity for early O~stars, but falling to
 less than 1\% for B~stars.
@@
 \(n / v_{10}^2\).  In the radiation bow shock case,
-\(x = (1 + \eta)^{1/2}\), and the condition can be written:
+\(x = (1 + \eta\wind)^{1/2}\), and the condition can be written:
 \begin{equation}
@@
   \text{RBS:}\quad
-  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta)^3} \ .
+  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta\wind)^3} \ .
 \end{equation}
@@
 equation~\eqref{eq:ifront-trap-density-RBS}, but changing the factor
-\((1 + \eta)^3\) to \(\eta^3\).  For the example hot stars in
+\((1 + \eta\wind)^3\) to \(\eta\wind^3\).  For the example hot stars in
 Table~\ref{tab:stars}, and assuming \(\kappa_{600} = 1\),
@@
 hits the hydrodynamic bow shock caused by the stellar wind.  The wind
-bow shock radius is \(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]),
-where \(\eta\) is the wind momentum efficiency
+bow shock radius is \(R_0 = \eta\wind^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]),
+where \(\eta\wind\) is the wind momentum efficiency
 (eq.~[\ref{eq:wind-eta-typical}]).  Therefore, the condition
@@
   \label{eq:dust-wave-velocity-condition}
-  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
-\end{equation}
-For O stars, the wind efficiency is generally high (\(\eta > 0.1\)) and
+  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta\wind \bigr)^{1/2} \ . 
+\end{equation}
+For O stars, the wind efficiency is generally high (\(\eta\wind > 0.1\)) and
 \(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
@@
 (\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
-can be much weaker (\(\eta < 0.01\)) and \(\Xi_\dag\) is also smaller, so
+can be much weaker (\(\eta\wind < 0.01\)) and \(\Xi_\dag\) is also smaller, so
 that dust waves are permitted by this criterion for much lower stream
@@
   \label{eq:dust-wave-low-density-condition}
-  \tau_* >  \tau_{*,\text{min}} = 0.5\, \frac{\kappa}{\kappa\grain}\, \eta^{1/2} 
-  % \frac{\kappa \eta^{1/2}}{2 \kappa\grain}
+  \tau_* >  \tau_{*,\text{min}} = 0.5\, \frac{\kappa}{\kappa\grain}\, \eta\wind^{1/2} 
+  % \frac{\kappa \eta\wind^{1/2}}{2 \kappa\grain}
   \ . 
@@
   \label{eq:gas-free-bow-shock}
-  R_{\text{dfbs}} \approx \frac{\eta^{1/2} R_*}{1 - \tfrac12 \alpha \tau_* / \tau_{*, \text{max}}} \ .
+  R_{\text{dfbs}} \approx \frac{\eta\wind^{1/2} R_*}{1 - \tfrac12 \alpha \tau_* / \tau_{*, \text{max}}} \ .
 \end{equation}

### 2019-02-12 papers/Papers1234/app-cloudy-dust-charging.tex
Add a bunch of new figures to appendix A and D
Still need to write about them

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/grain-j70-vs-U-edited}
+  \caption{Grain emissivity at \SI{70}{\um} for all Cloudy models
+    (lines colored as in Fig.~\ref{fig:drift-gn}), compared with grain
+    models from \citet{Draine:2007a} (dark gray symbols), which assume
+    illumination by a scaled interstellar radiation field, which has a
+    SED with a very different shape from that of an OB star.  }
+  \label{fig:grain-j70}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/sed-comparison}
+  \caption{Comparison between the spectral energy distribution (SED)
+    of a typical OB star (blue line) and the interstellar radiation
+    field in the solar neighborhood (orange line).  The OB star is the
+    \SI{20}{M_\odot} model from Table~\ref{tab:stars} and is plotted for a
+    distance from the star of \SI{1}{pc}.  The interstellar SED is
+    from \citet{Mathis:1983a} and is multiplied by \num{100} so that
+    the total FUV-to-NIR flux is similar for the two SEDs.}
+  \label{fig:sed-comparison}
+\end{figure}
+
 %%% Local Variables:

### 2019-02-14 papers/Papers1234/app-cloudy-dust-charging.tex
Add grain T vs U graph

@@
 Finally, Figure~\ref{fig:phi-vs-Xi} shows the slow dependence of grain
-potential on radiation parameter for all the simulations on a linear versus
-logarithmic scale.  The logarithmic fit of
+potential on radiation parameter for all the simulations on a linear
+versus logarithmic scale.  The logarithmic fit of
 equation~\eqref{eq:phi-vs-Xi}, most appropriate for carbon grains
@@
 show the modifications for silicate grains and for hotter stars (see
-\S~\ref{sec:gas-grain-separ}).
+\S~\ref{sec:gas-grain-separ}).  Further details of the Cloudy dust
+models are discussed in Appendix~\ref{sec:grain-temp-emiss}.
+
+\section{Grain temperature and mid-infrared emissivity}
+\label{sec:grain-temp-emiss}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/grain-T-vs-U}
+  \caption{Grain temperature versus radiation field mean intensity,
+    \(U\), in units of the interstellar radiation field in the solar
+    neighborhood.  Line types and colors are as in
+    Fig.~\ref{fig:phi-vs-Xi} and correspond to a variety of stellar
+    spectral shapes, gas densities, and grain species.}
+  \label{fig:grain-T-vs-U}
+\end{figure}
 
@@
     illumination by a scaled interstellar radiation field, which has a
-    SED with a very different shape from that of an OB star.  }
+    SED with a very different shape from that of an OB star, see
+    Fig.~\ref{fig:sed-comparison}.  }
   \label{fig:grain-j70}
@@
     distance from the star of \SI{1}{pc}.  The interstellar SED is
-    from \citet{Mathis:1983a} and is multiplied by \num{100} so that
-    the total FUV-to-NIR flux is similar for the two SEDs.}
+    from \citet{Mathis:1983a} and is multiplied by \num{80} so that
+    the total FUV-to-NIR flux is equal for the two SEDs.}
   \label{fig:sed-comparison}

### 2019-02-18 papers/Papers1234/app-cloudy-dust-charging.tex
Nearly finish new appendices

@@
 Equilibrium drift velocity for each grain species is calculated in the
-Cloudy simulations using the same theory \citep{Draine:1979a} as outlined
-in \S~\ref{sec:drag-force-grains}.  The way that this is implemented
-by default in Cloudy means that if the only solution at the inner
-radius is a superthermal one, then the superthermal solution branch
-(upper right corner of Fig.~\ref{fig:gas-grain-drag-photoionized}) is
-followed as far as possible through the outer spatial zones.  We have
-modified the code so as to instead always prefer the slower subthermal
-branch whenever multiple solutions are available.  This makes the most
-sense in our context, where the grains are moving towards the star and
-so the radiative force is gradually increasing from an initial low
-value.  Example results are shown in the bottom row of
+Cloudy simulations using the same theory \citep{Draine:1979a} as
+outlined in \S~\ref{sec:drag-force-grains}.  The way that this is
+implemented by default in Cloudy means that if the only solution at
+the inner radius is a superthermal one, then the superthermal solution
+branch (upper right corner of
+Fig.~\ref{fig:gas-grain-drag-photoionized}) is followed as far as
+possible through the outer spatial zones.  We have modified the code
+so as to instead always prefer the slower subthermal branch whenever
+multiple solutions are available.  This makes the most sense in our
+context, where the grains are moving towards the star and so the
+radiative force is gradually increasing from an initial low value.
+Example results are shown in the bottom row of
 Figure~\ref{fig:multi-dustprops} and again they are qualitatively
-similar for all the simulations.  Close to the star, the radiation force is
-higher than the upper limit on the Coulomb drag force
+similar for all the simulations.  Close to the star, the radiation
+force is higher than the upper limit on the Coulomb drag force
 (eq.~[\ref{eq:fdrag-maximum}]), so that the equilibrium drift velocity
@@
   and gas, since they are based on the assumption that the radiation
-  force remains constant while the grain is accelerated, which can
-  never be the case.  Instead, they are simply an indication that the
-  gas and grains have completely decoupled.}.  As the radial distance
-from the star increases, the radiation field is increasingly diluted
-but the grain potential falls only slowly, so eventually one reaches a
-point where an equilibrium between Coulomb drag and radiation force
-can be established, which corresponds to a discontinuity in the drift
-velocity.  This is the \textit{rip point} discussed in
-\S~\ref{sec:gas-grain-separ}.  The drift velocity carries on falling
-towards the outside of the \hii{} region, but then increases again
-just inside the ionization front due to the drop in grain potential
-there.
+  force remains constant while the grain is accelerated, which is not
+  the case near the rip point.  Instead, they are simply an indication
+  that the gas and grains have completely decoupled.}.  As the radial
+distance from the star increases, the radiation field is increasingly
+diluted but the grain potential falls only slowly, so eventually one
+reaches a point where an equilibrium between Coulomb drag and
+radiation force can be established, which corresponds to a
+discontinuity in the drift velocity.  This is the \textit{rip point}
+discussed in \S~\ref{sec:gas-grain-separ}.  The drift velocity carries
+on falling towards the outside of the \hii{} region, but then
+increases again just inside the ionization front due to the drop in
+grain potential there.
 
@@
 
+Figure~\ref{fig:grain-T-vs-U} shows equilibrium grain temperatures for
+the Cloudy models discussed in Appendix~\ref{sec:cloudy-models-dust}
+as a function of the nominal energy density of the radiation field,
+\(U = u / u\mmp \), where \(u = L / 4 \pi R^2 c\) and \(u\mmp\) is the
+energy density of the interstellar radiation field for
+\(\lambda < \SI{8}{\um}\) in the solar neighborhood
+\citep{Mathis:1983a}:
+\begin{equation}
+  \label{eq:u-mmp83}
+  u\mmp\,c = \SI{0.0217}{erg.s^{-1}.cm^{-2}} \ .
+\end{equation}
+The tight relationship seen in figure~\ref{fig:grain-T-vs-U} between
+\(T\) and \(U\) is evidence for the dominance of stellar radiative
+heating (see \S~\ref{sec:unimp-other-heat} below), while the variation
+about the mean relation is mainly due to differences in grain size and
+composition, with smaller grains and graphite grains being relatively
+hotter.  The downward hooks seen on the left end of each simulation's
+individual curve are due to the fact that our calculation of \(U\)
+does not account for internal absorption, which starts to become
+important near the ionization front.
+
 \begin{figure}
@@
 \end{figure}
+
+The grain emissivity at \SI{70}{\um} (Herschel PACS blue band) for the
+Cloudy simulations (colored lines) is shown in
+Figure~\ref{fig:grain-j70}, where it is compared with the same
+quantity from the grain models (dark gray symbols) of
+\citet{Draine:2007a}.  A clear difference is seen between the two sets
+of models, but this is due almost entirely to a difference in the
+assumed spectrum of the illuminating radiation, as illustrated in
+Figure~\ref{fig:sed-comparison}.  \citet{Draine:2007a} use a SED that
+is typical of the interstellar radiation field in the Galaxy, which is
+dominated by an old stellar population, which peaks in the near
+infrared, with only a small FUV contribution from younger stars (about
+8\% of the total energy density).  This is very different from the OB
+star SEDs, which are dominated by the FUV and EUV bands.  Since the
+grain absorption opacity is much higher at UV wavelengths than in the
+visible/IR (see Fig.~\ref{fig:cloudy-ism-dust-opacity}), the effective
+grain heating efficiency of the OB star SED is correspondingly higher.
+The light gray symbols show the effect on the \citet{Draine:2007a}
+models of multiplying the radiation field by a factor of \num{8} in
+order to offset this difference in efficiency, which can be seen to
+bring them into close agreement with the Cloudy models.  A further
+difference is that the \citet{Draine:2007a} model includes small PAH
+particles, which we do not include in our Cloudy models, since they
+are believed to be largely absent in photoionized regions
+\citep{Giard:1994a, Lebouteiller:2011a}.  However, this only effects
+the emissivity at shorter mid-infrared wavelengths \(< \SI{20}{\um}\).
 
@@
 
+In terms of the characteristic parameters introduced in
+\S~\ref{sec:depend-stell-type} the dimensionless radiation field becomes
+\begin{equation}
+  \label{eq:U-from-L4-and-Rpc}
+  U = 14.7\, L_4\, R_{\text{pc}}^{-2} \ ,
+\end{equation}
+or, alternatively, it can be expressed in terms of the ambient stream as
+\begin{equation}
+  \label{eq:U-from-ambient}
+  U = 3.01 \, n \, v_{10}^2 / x^2 \ , 
+\end{equation}
+where \(x = R_0/R_*\) is given by equation~\eqref{eq:x-cases}.  It can
+also be related to the radiation parameter \(\Xi\), defined in
+equation~\eqref{eq:Xi-Prad-over-Pgas}, as
+\begin{equation}
+  \label{eq:U-vs-Xi}
+  U = 3.82 \, n T_4 \, \Xi \ .
+\end{equation}
+A common alternative approach to scaling the radiation field (see
+\citealp{Tielens:1985a} and citations thereof) is to normalize in the
+FUV band (\SIrange{0.0912}{0.24}{\um}), where the local interstellar
+value is known as the Habing flux \citep{Habing:1968a}:
+\begin{equation}
+  \label{eq:Habing-flux}
+  F\Hab = \SI{0.0016}{erg.s^{-1}.cm^{-2}} \ .
+\end{equation}
+The resultant dimensionless flux is often denoted by \(G_0\), and the
+relationship between \(G_0\) and \(U\) depends on the fraction
+\(f_{\text{fuv}}\) of the stellar luminosity that is emitted in the
+FUV band:
+\begin{equation}
+  \label{eq:G-vs-U}
+  G_0 = f_{\text{fuv}} \frac{u\mmp\, c}{F\Hab} \,U = (\text{\numrange{6}{10}}) \,U \ ,
+\end{equation}
+where we give the range corresponding to early O (\(f_{\text{fuv}} \approx 0.4\)) to early B (\(f_{\text{fuv}} \approx 0.7\)) stars.
+
+%% Single-photon heating of small grains
+
+\subsection{Unimportance of other heating mechanisms}
+\label{sec:unimp-other-heat}
+The grain temperature in bows around OB stars is determined
+principally by the steady-state equilibrium between the absorption of
+stellar UV radiation (heating) and the thermal emission of infrared
+radiation (cooling).  Other processes such as single-photon stochastic
+heating, Lyman~\(\alpha\) line radiation, and post-shock collisional
+heating can dominate in other contexts, but these are generally
+unimportant for circumstellar bows, as we now demonstrate.
+
+\subsubsection{Stochastic single-photon heating}
+
+When the radiation field is sufficiently dilute, then a grain that
+absorbs a photon has sufficient time to radiate all that energy away
+before it absorbs another photon \citep{Duley:1973a}.  In this case,
+the emitted infrared spectrum for \(\lambda < \SI{50}{\um}\) becomes
+relatively insensitive of the energy density of the incident radiation
+\citep{Draine:2001a}.  However, this is most important for the very
+smallest grains.  From equation~(47) of \citet{Draine:2001a}, one
+finds that grains with sizes larger than
+\(a = \SI{0.005}{\um} = \SI{5}{nm}\) (the smallest size included in
+our Cloudy models) should be close to thermal equilibrium for
+\(U > 30\), which is small compared with typical bow shock values
+(\(U = \text{\numrange{e3}{e6}}\)).  As mentioned above, PAHs are not
+expected to be present in the interior of \hii{} regions.
+\citealp{Desert:1990a} found them to be strongly depleted for
+\(U > 100\) around O stars.  However, other types of ultra-small
+grains, down to sub-nm sizes \citep{Xie:2018a} may be present in bows,
+and stochastic heating \emph{would} be important for grains with
+\(a = \SI{1}{nm}\) if \(U < \num{e5}\).  Note, however that grains
+smaller than \SI{0.6}{nm} would be destroyed by sublimation after
+absorbing a single He-ionizing photon.
+
+\subsubsection{Lyman \(\alpha\) heating}
+
+On the scale of an entire \hii{} region, the dust heating is typically
+dominated by Lyman \(\alpha\) hydrogen recombination line photons, which
+are trapped by resonant scattering (e.g., \citealp{Spitzer:1978a}
+\S~9.1b).  However, this is no longer true on the much smaller scale
+of typical bow shocks.  An upper limit on the Lyman \(\alpha\) energy
+density can be found by assuming all line photons are ultimately
+destroyed by dust absorption rather than escaping in the line wings
+(e.g., \citealp{Henney:1998b}), which yields
+\begin{equation}
+  \label{eq:U-Lya}
+  U\Lya \approx 0.1 n / \kappa_{600} \ .
+\end{equation}
+This can be combined with equation~\eqref{eq:U-from-ambient} to give
+the ratio of Lyman \(\alpha\) to direct stellar radiation as
+\begin{equation}
+  \label{eq:Lya-over-stellar}
+  \frac{U\Lya}{U} \approx 0.03 \frac{x^2}{v_{10}^2 \kappa_{600}} \ .
+\end{equation}
+Taking the most favorable parameters imaginable of a slow stream
+(\(v_{10} = 2\)), very strong wind (\(x \approx 1\)), and reduced dust
+opacity (\(\kappa_{600} = 0.1\)) gives a Lyman \(\alpha\) flux of only 10\% of the
+stellar flux.  In any other circumstances, the fraction would be even
+lower.
+
+\subsubsection{Shock heating}
+\newcommand\kin{\ensuremath{_{\text{kin}}}}
+The outer shock thermalizes the kinetic energy of the ambient stream,
+which may in principle contribute to the infrared emission of the bow.
+In order for this process to be competitive, the following three
+conditions must all hold:
+\begin{enumerate}[1.]
+\item The post-shock gas must radiate efficiently with a cooling
+  length less than the bow size, see \S~\ref{sec:radi-cool-lengths}.
+  This is satisfied for all but the lowest densities (see
+  Fig.~\ref{fig:zones-v-n-plane}).
+\item A significant fraction of the shock energy must be radiated by
+  dust.  This requires that the post-shock temperature be greater than
+  \SI{e6}{K}, which requires a stream velocity
+  \(v > \SI{200}{km.s^{-1}}\) \citep{Draine:1981a}.  This also
+  coincides with the range of shock velocities where the smaller
+  grains will start to be destroyed by sputtering in the post-shock
+  gas.
+\item The kinetic energy flux through the shock must be significant,
+  compared with the fraction of the stellar radiation flux that is
+  absorbed and reprocessed by the bow shell.
+\end{enumerate}
+It turns out that the third condition is the most stringent, so we
+will consider it in detail.  The kinetic energy flux through the outer shock for an ambient stream of density \(\rho\) and velocity \(v\) is
+\begin{equation}
+  \label{eq:Fkin}
+  F\ke = \tfrac12 \rho v^3 = \tfrac12 P\shell v \ , 
+\end{equation}
+while the stellar radiative energy flux absorbed by the shell is
+\begin{equation}
+  \label{eq:Ftrap}
+  F\trap \approx \tau L / 4 \pi R_0^2 \ ,
+\end{equation}
+assuming an absorption optical depth \(\tau \ll 1\). The shell
+pressure in the WBS case can be equated to the ram pressure of the
+internal stellar wind (see \S~\ref{sec:three-bow-regimes}), so that
+the ratio of the two energy fluxes is
+\begin{equation}
+  \label{eq:F-ratio-shock}
+  \frac{F\ke}{F\trap} = \frac12 \frac{\eta\wind}{\tau} \frac{v}{c} \ .
+\end{equation}
+An upper limit to the stellar wind momentum efficiency \(\eta\wind\)
+is the shell momentum efficiency \(\eta\shell\) that is derived
+observationally in \S~\ref{sec:summary-discussion}, where it is found
+that \(\eta\shell / \tau < 30\) for all sources considered.  Therefore,
+for a stream velocity \(v = \SI{200}{km.s^{-1}}\), we have
+\(F\ke/F\trap < 0.01\) and the shock-excited dust emission is still
+negligible.  Only in stars with \(v > \SI{1000}{km.s^{-1}}\) would the
+shock emission start to be significant, and such hyper-velocity stars
+\citep{Brown:2015a} do not show bow shocks.
+
+% Inner shock \dots no dust \dots proton Larmor radius very small, so
+% no penetration across contact discontinuity
+
 %%% Local Variables:

### 2019-02-18 papers/Papers1234/app-dust-equations.tex
Nearly finish new appendices

@@
 \begin{equation}
-  \label{eq:grain-accelration}
+  \label{eq:grain-acceleration}
   \frac{\bm{a}\grain}{a\starstar}
@@
 plus additional figures and movies.  The integration of
-equation~\eqref{eq:grain-equation-motion} is carried out using the
+equation~\eqref{eq:grain-acceleration} is carried out using the
 python library function \texttt{scipy.integrate.odeint}, which wraps

### 2019-02-18 papers/Papers1234/app-k17-k18.tex
Add a bunch of new figures to appendix A and D
Still need to write about them
Nearly finish new appendices

@@
-\section{Bow shock data from Kobulnicky et al. (2016, 2017, 2018)}
+\section{Reanalysis of bow shock sources from Kobulnicky et al. (2016,
+  2017, 2018)}
 \label{app:bow-shock-data}
 
-In a series of papers \citet{Kobulnicky:2016a, Kobulnicky:2017a,
-  Kobulnicky:2018a} provide an extensive mid-infrared-selected sample
-of over 700 candidate stellar bow shock nebulae.  For 20 of these
+In a series of papers \citeauthor{Kobulnicky:2018a} provide an
+extensive mid-infrared-selected sample of over 700 candidate stellar
+bow shock nebulae (\citealp{Kobulnicky:2016a, Kobulnicky:2017a,
+  Kobulnicky:2018a}, hereafter K16, K17, and K18).  For 20 of these
 sources, reliable distances and spectral classifications are provided
-(Table~5 of \citealp{Kobulnicky:2017a} and 
-\citealp{Kobulnicky:2018a}), and these are used in
+(Table~5 of K17 and Tables~1 and~2 of K18), and these are used in
 \S~\ref{sec:summary-discussion}, where we discuss the
@@
 
-The most important quantity to be derived from the observations is the
-absorption optical depth, \(\tau\), of the bow shell to the stellar radiation.
+The UV optical depth of the bow shell is obtained
+(eq.~[\ref{eq:tau-empirical}]) from the ratio of infrared shell
+luminosity to stellar luminosity.  The inverse of this ratio is given
+in Table~5 of K17, but we choose to re-derive the values since the
+spectral classification of some of the sources was revised between K17
+and K18.  Although K17 found the total shell fluxes from fitting dust
+emission models to the observed SEDs, we adopt the simpler approach of
+taking a weighted sum of the flux densities \(F_\nu\) (in \si{Jy}) in
+three mid-infrared bands:
+\begin{multline}
+  \label{eq:total-ir-flux}
+  F_{\text{IR}}  \approx \bigl[  2.4\,(F_8 \text{ or } F_{12})
+    + 1.6\,(F_{22} \text{ or } F_{24})  \\
+  + 0.51\,F_{70}\bigr]
+  \,\times \SI{e-10}{erg.s^{-1}.cm^{-2}} \ ,
+\end{multline}
+where \(F_8\) is Spitzer IRAC \SI{8.0}{\um}, \(F_{24}\) is Spitzer
+MIPS \SI{23.7}{\um}, \(F_{12}\) and \(F_{22}\) are WISE bands 3 and 4,
+and \(F_{70}\) is Herschel PACS \SI{70}{\um}.  The weights are chosen
+so that the integral \(\int_0^\infty F_\nu \,d\nu\) is approximated by the sum
+\(\Sigma_k F_k\, \Delta\nu_k\), under the assumption that fluxes in shorter (e.g.,
+IRAC \SI{5.8}{\um}) and longer (e.g., PACS \SI{150}{\um}) wavebands
+are negligible.  Shell fluxes are converted to luminosities using the
+assumed distance to each source, and stellar luminosities are taken
+directly from K18 Table~2, based on spectroscopic classification and
+the calibrations of gravity and effective temperature from
+\citet{Martins:2005a}.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/K18-flux-comparison}
   \includegraphics[width=\linewidth]{figs/K17-tau-comparison}
-  \caption{Comparison}
+  \caption{Comparison between shell-to-star luminosity ratios
+    calculated in the text (\(y\) axis) with those given in K17 (\(x\)
+    axis).  The blue dashed line signifies equality and the gray band
+    shows ratios between 1/2 and 2.}
   \label{fig:k17-k18-comparison}
 \end{figure}
+
+In Figure~\ref{fig:k17-k18-comparison} we compare the \(\tau\) obtained
+using the shell luminosity as described above with that obtained using
+the luminosity ratios directly from K17 Table~5.  It can be seen that
+for the majority of sources the two measurements are consistent within
+a factor of two (gray band).  The three furthest-flung outliers can be
+understood as follows:
+\begin{description}
+\item[\textit{Source 67}] This has a very poor-quality spectral fit in
+  K17 (see lower left panel of their Fig.~12) and so the
+  \(F_{\text{IR}}\) is overestimated by a factor of 10.
+\item[\textit{Sources 341 and 342}] The spectral classes changed from
+  B2V in K17 to O9V and B1V, respectively, in K18, increasing the
+  derived \(L_*\), which lowers \(\tau\).
+\item[\textit{Source 411}] The luminosity class changed from Ib (K17)
+  to V (K18), so \(L_*\) has been greatly reduced, which increases
+  \(\tau\).
+\end{description}
 
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
-  \caption[K18 pair plot]{Pair plots of correlations between observed
-    and derived parameters of bows from the \citep{Kobulnicky:2018a}
-    sample.}
-  \label{fig:K18-pairplot-edited}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
+%   \caption[K18 pair plot]{Pair plots of correlations between observed
+%     and derived parameters of bows from the \citep{Kobulnicky:2018a}
+%     sample.}
+%   \label{fig:K18-pairplot-edited}
+% \end{figure*}
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
+  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
+    identified in K18.  Red crosses show the emissivities given in
+    K18's Table~2 as a function of the radiation field \(U\), while
+    the solid gray line shows the emissivities that they claim to be
+    using from \citet{Draine:2007a}.  The dashed line shows the
+    emissivities that we believe they should have been using, which
+    correct for the fact that the illuminating SED in
+    \citet{Draine:2007a} is dominated by longer wavelengths (see
+    App.~\ref{sec:grain-temp-emiss}).}
+  \label{fig:k18-emissivity}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-mdot-Ux8-comparison}
+  \caption{Effects on mass-loss determination of correcting the K18
+    emissivities.  The mass-loss rates from Table~2 of K18 are shown
+    on the \(x\) axis, while the corrected values are shown on the
+    \(y\) axis.  The corrected mass-loss rates are predominantly lower
+    by a factor of roughly 2.}
+  \label{fig:k18-mdot-corrected-emissivity}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-mdot-corrected-comparison-R0}
+  \caption{Comparison of two mass-loss methods.}
+  \label{fig:mass-loss-comparison}
+\end{figure}
+
 %%% Local Variables:

### 2019-02-18 papers/Papers1234/sec-dust-bow-discuss.tex
Nearly finish new appendices

@@
   \centering
-  \includegraphics[width=\linewidth]{figs/All-sources-eta-tau}
+  \includegraphics[width=0.8\linewidth]{figs/All-sources-eta-tau}
   \caption[Observational diagnostic diagram]{Observational diagnostic
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/Mdot-from-eta-vs-luminosity}
+  \includegraphics[width=\linewidth]{figs/Mdot-K18-corrected-vs-luminosity}
+  \caption{Mass loss rates}
+  \label{fig:mass-loss-vs-luminosity}
+\end{figure}
+
 Different scenarios for producing velocities: dynamic ejection from
@@
 regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
-thermally driven photoevaporation flow \citep{HA:1998, Henney:1999a},
+thermally driven photoevaporation flow \citep{Henney:1998b, Henney:1999a},
 while the outer stream is the stellar wind from an O~star

### 2019-02-18 papers/Papers1234/app-cloudy-dust-charging.tex
Write up impossibility of stellar wind exciting dust emission

@@
 (\(v_{10} = 2\)), very strong wind (\(x \approx 1\)), and reduced dust
-opacity (\(\kappa_{600} = 0.1\)) gives a Lyman \(\alpha\) flux of only 10\% of the
-stellar flux.  In any other circumstances, the fraction would be even
-lower.
+opacity (\(\kappa_{600} = 0.1\)) gives a Lyman \(\alpha\) contribution of only
+10\% of the stellar radiative energy density.  In any other
+circumstances, the fraction would be even lower.
 
@@
 shock emission start to be significant, and such hyper-velocity stars
-\citep{Brown:2015a} do not show bow shocks.
+\citep{Brown:2015a} do not show detectable bow shocks.
+
+So far, we have only considered the outer shock, but the inner shock
+that decelerates the stellar wind will have a velocity of
+\SIrange{1000}{3000}{km.s^{-1}} and therefore might have a
+significant kinetic energy flux by eq.~\eqref{eq:F-ratio-shock}.
+However, the stellar wind from hot stars will be free of
+dust,\footnote{%
+  With the exception of Wolf-Rayet colliding wind binary systems
+  \citep{Tuthill:1999a, Callingham:2019a}.} %
+so that it would be necessary for the stellar wind protons to cross
+the contact/tangential discontinuity and deposit their energy in the
+dusty plasma of the shocked ambient stream.  This is not possible
+because the Larmor radius (see \S~\ref{sec:magn-effects-grain}) of a
+\SI{3000}{km.s^{-1}} proton in a \SI{1}{\micro G} field is only
+\SI{3e10}{cm}, which is millions of times smaller than typical bow
+sizes.  The magnetic field in the outer shell is unlikely to be
+smaller than \(\approx n^{1/2} \si{\micro G}\), given that Alfvén
+speeds of \SI{2}{km.s^{-1}} are typical of photoionized regions
+(cf.~eq.~[\ref{eq:alfven}]) and if the density were much lower than
+\SI{1}{cm^{-3}}, then the scale of the bow would be commensurately
+larger anyway.  Three-dimensional MHD simulations of bow shocks
+\citep{Katushkina:2017a, Gvaramadze:2018a} show that the magnetic
+field lines are always oriented parallel to the shell, so that high
+energy particles from the stellar wind would be efficiently reflected
+in a very thin layer and cannot contribute to grain heating.  For the
+same reason, heat conduction by electrons across the contact
+discontinuity is also greatly suppressed \citep{Meyer:2017a}.
 

### 2019-02-19 papers/Papers1234/app-k17-k18.tex
Write up impossibility of stellar wind exciting dust emission
Discussion of eta tau diagram and observational uncertainties

@@
   \caption{Comparison between shell-to-star luminosity ratios
-    calculated in the text (\(y\) axis) with those given in K17 (\(x\)
-    axis).  The blue dashed line signifies equality and the gray band
-    shows ratios between 1/2 and 2.}
+    calculated as described in the text (\(y\) axis) with those given
+    in K17 (\(x\) axis).  The blue dashed line signifies equality and
+    the gray band shows ratios between 1/2 and 2.}
   \label{fig:k17-k18-comparison}
@@
 for the majority of sources the two measurements are consistent within
-a factor of two (gray band).  The three furthest-flung outliers can be
+a factor of two (gray band).  The four furthest-flung outliers can be
 understood as follows:
@@
 \item[\textit{Source 67}] This has a very poor-quality spectral fit in
-  K17 (see lower left panel of their Fig.~12) and so the
-  \(F_{\text{IR}}\) is overestimated by a factor of 10.
+  K17 (see lower left panel of their Fig.~12) and so 
+  \(F_{\text{IR}}\) is overestimated by them by a factor of 10.
 \item[\textit{Sources 341 and 342}] The spectral classes changed from
@@
 \end{description}
-
-% So everything looks OK, except:
-
-% * Source 67 is over 10 times too bright in the Kobulnicky table
-
-% So, I will use my fluxes instead.
 
@@
 
-% In this graph we compare the original luminosity ratio taken directly from the Kobulnicky (2017) table (x axis) with the ratio calculated using my new total IR fluxes, combined with the new luminosities in the Kobulnicky (2018) table (y axis).
-Most of the points show reasonable agreement between the two methods, with a few exceptions:
-
-% * 67: this had the $F_\text{IR}$ overestimated in K17.  Using a more reasonable value gives a lower $\tau$
-% * 341: The spectral class has changed from B2 (K17) to O9 (K18), increasing the assumed $L_*$, which lowers $\tau$
-% * 411: The luminosity class has changed from Ib (K17) to V (K18), so $L_*$ has been greatly reduced, which increases the estimated $\tau$
-
-% And there doesn't seem to be any significant correlation with stellar luminosity.
-
 \begin{figure}
@@
     emissivities that we believe they should have been using, which
-    correct for the fact that the illuminating SED in
-    \citet{Draine:2007a} is dominated by longer wavelengths (see
-    App.~\ref{sec:grain-temp-emiss}).}
+    correct for the marked difference in spectral energy distribution
+    between OB stars and the Galactic interstellar radiation field
+    (see App.~\ref{sec:grain-temp-emiss}).}
   \label{fig:k18-emissivity}
 \end{figure}
+
+\newcommand\LOS{\ensuremath{_{\text{los}}}}
+K18 derive mass loss rates for their sources using a method that is
+different from the one that we employ in
+\S~\ref{sec:summary-discussion}.  Both methods are based on
+determining the stellar wind ram pressure that supports the bow shell,
+but K18 do so via the following steps:
+\begin{enumerate}[K1.]
+\item \label{K1} The line-of-sight mass column through the shell is
+  calculated by combining the peak surface brightness at \SI{70}{\um},
+  \(S_{70}\), with a theoretical emissivity per nucleon,
+  \(j_{70}(U)\), from \citet{Draine:2007a}:
+  \(\Sigma\LOS = S_{70} / \bar{m} j_{70}(U)\).  This depends on
+  knowledge of the stellar radiation field at the shell:
+  \(U \propto L_* / R_0^2\).
+\item \label{K2} The shell density is found from the line-of-sight
+  mass column using an observationally determined ``chord diameter'',
+  \(\ell\), which is assumed to be equal to the depth along the line
+  of sight: \(\rho\shell = \Sigma\LOS / \ell\).
+\item \label{K3} The internal ram pressure is equated to the external
+  ram pressure, which is found by assuming a stream velocity of
+  \SI{30}{km.s^{-1}} and a compression factor of 4 across the outer
+  shock:
+  \(P_{\text{stream}} = 0.25 \rho\shell \times
+  (\SI{30}{km.s^{-1}})^2\).
+\end{enumerate}
+There are clear parallels but also differences between steps
+K\ref{K1}--K\ref{K3} and our own steps P\ref{P1}--P\ref{P3}.  Our
+step~P\ref{P1} depends on the total observed infrared flux of the bow
+combined with an assumption about the grain opacity at ultraviolet
+wavelengths, while step~K\ref{K1} depends on the peak brightness at a
+single wavelength combined with an assumption about the grain
+emissivity at infrared wavelengths.  Our step~P\ref{P2} requires an
+assumption about the relative thickness of the shell, while
+step~K\ref{K2} is more directly tied to observations.\footnote{%
+  Note that there is a relation between the chord length, \(\ell\),
+  and the shell thickness, \(h\shell\), but this depends on the
+  planitude, \(\Pi\) of the bow shape \citep{Tarango-Yong:2018a}:
+  \( h\shell/R_0 = \Pi \bigl(1 - \{1 - [\ell/(2 \Pi R_0)]^2\}^{1/2}\bigr)\).  } %
+On the other hand, step~K\ref{K3} makes a roughly equivalent
+assumption about the shock compression factor,\footnote{%
+  In reality, the compression factor may be larger or smaller than 4,
+  depending on the efficiency of the post-shock cooling (see
+  \S~\ref{sec:radi-cool-lengths}).  For instance, for
+  \(v = \SI{30}{km.s^{-1}}\) as assumed by K18 and \(T = \SI{e4}{K}\),
+  one has a Mach number of \(\M_0 = 2.63\) and a compression factor of
+  2.8 for a non-radiative shock (by eq.~[\ref{eq:shock-n-jump}]) or a
+  factor of \(\M_0^2 =6.9\) for a strongly radiative one.  } %
+and a further assumption about the stream velocity. These assumptions
+are not necessary for our step~P\ref{P3}, but we do need to assume a
+value for the shell gas temperature.
+
+In principle, both methods are valid and their different assumptions
+and dependencies on observed quantities and auxiliary parameters
+provide an important cross check on one another.  However, as
+explained in detail in Appendix~\ref{sec:grain-temp-emiss}, the
+\(j_\nu(U)\) relation depends on the shape of the illuminating SED,
+which means that the \citet{Draine:2007a} models require modification
+when applied to grains around OB stars.  In addition, when attempting
+to replicate the K18 values of \(j_{70}\) we find that they only
+follow the \citet{Draine:2007a} values for \(U > \num{e4}\), tending
+to a constant value for weaker radiation fields.  The situation is
+summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
+directly from Table~2 of K18 are shown by red crosses, the values they
+claim to be using are shown by the gray solid line (this curve is
+consistent with that shown in K18 Fig.~2), and the values they
+\textit{should} have been using are shown by the gray dashed line.
+
+% If we replaced K3 with M3, then mass loss rates would be reduced by 1.86 across the board
 
@@
     on the \(x\) axis, while the corrected values are shown on the
-    \(y\) axis.  The corrected mass-loss rates are predominantly lower
-    by a factor of roughly 2.}
+    \(y\) axis.  Symbols are color coded by the strength of the
+    radiation field, \(U\). The corrected mass-loss rates are
+    predominantly lower by a factor of roughly 2.}
   \label{fig:k18-mdot-corrected-emissivity}
 \end{figure}
+
+After correcting the \SI{70}{\um} emissivities in this way, we
+re-derive the mass loss rates, following the same steps as in K18,
+which are then used in Figure~\ref{fig:mass-loss-vs-luminosity}b of
+\S~\ref{sec:summary-discussion}.  The difference between these
+corrected mass-loss rates and those published in K18 is shown in
+Figure~\ref{fig:k18-mdot-corrected-emissivity}.  It can be seen that
+sources with \(U \approx \num{e3}\) (darker shading) are relatively
+unaffected but that sources with stronger radiation fields (lighter
+shading) have their mass-loss increasingly reduced, as could be
+surmised from Figure~\ref{fig:k18-emissivity}.  The average reduction
+is by a factor of about two.
 
@@
   \includegraphics[width=\linewidth]{figs/K18-mdot-corrected-comparison-R0}
-  \caption{Comparison of two mass-loss methods.}
+  \caption{Comparison of the two mass-loss methods: K18 corrected
+    method (\(x\) axis) versus our method (\(y\) axis).  Error bars on
+    the \(y\) axis correspond to a factor-three uncertainty in
+    \(\eta\shell\).  Sources for which these error bars overlap with
+    the RBW zone are only upper limits for the wind mass-loss rate,
+    and are indicated by faint symbols.}
   \label{fig:mass-loss-comparison}
 \end{figure}
+
+Finally, in Figure~\ref{fig:mass-loss-comparison} we compare our own
+mass-loss determinations with the corrected K18 values.  The plot
+symbols are shaded according to the physical size of the bow, \(R_0\).
+It is apparent that the two methods are broadly in agreement on
+average, but there is considerable dispersion for individual objects,
+with only a weak correlation between the results of the two techniques
+(Pearson correlation coefficient \(r = 0.67\)).  Interestingly, the
+smaller bows (darker shading) show much better agreement than the
+larger bows (lighter shading).  The five bows with
+\(R_0 > \SI{0.4}{pc}\) (339, 344, 369, 381, 382) show a difference of
+nearly an order of magnitude, in the sense that our method
+consistently predicts lower mass-loss rates than K18.  For a further
+five of the sources (380, 407, 409, 410, 411), our method gives only
+an upper limit to the wind mass-loss rate if one assumes a
+factor-three uncertainty in \(\eta\shell\), and these bows are among
+the smallest in the sample, all with \(R_0 < \SI{0.1}{pc}\).
 

### 2019-02-19 papers/Papers1234/sec-dust-bow-discuss.tex
Discussion of eta tau diagram and observational uncertainties

@@
 \end{equation}
-where the last approximate equality holds if \(\tau \ll 1\) and the shell
-emission covers one hemisphere.\footnote{%
-  The \(\tau\) of \S~\ref{sec:three-bow-regimes} is not exactly the same
-  as the \(\tau\) of equation~\eqref{eq:tau-empirical}, but is larger by
-  a factor of \(1 + \varpi (1 - g)/(1 - \varpi)\), where \(\varpi\) is
-  the grain albedo and \(g\) the scattering asymmetry (see
-  App.~\ref{sec:gas-free-bow}).} %
+where the last approximate equality holds if \(\tau \ll 1\) and the
+shell emission covers one hemisphere.\footnote{%
+  The \(\tau\) of \S~\ref{sec:three-bow-regimes} is not exactly the
+  same as the \(\tau\) of equation~\eqref{eq:tau-empirical}, but is
+  larger by a factor of
+  \(Q_P / Q_{\text{abs}} = 1 + \varpi (1 - g)/(1 - \varpi)\), where
+  \(\varpi\) is the grain albedo and \(g\) the scattering asymmetry
+  (see App.~\ref{sec:gas-free-bow}).} %
 
@@
 pressure plus absorbed stellar radiation) \emph{and} the external
-confining pressure (ram pressure of ambient stream).  The shell pressure is
-not given directly by the observations, but can be determined as
-follows:
-\begin{enumerate}[1.]
-\item The shell mass column (\si{g.cm^{-2}}) can be estimated from the
-  optical depth by assuming an effective UV opacity: \(\Sigma\shell = \tau / \kappa\)
-\item The shell density (\si{g.cm^{-3}}) can be found from the mass
-  column if the shell thickness is known:
-  \(\rho\shell = \Sigma / h\shell\).  In the absence of other information, a
-  fixed fraction of the shell radius can be used.  In particular, we
-  normalize by a typical value of one~quarter\footnote{%
+confining pressure (ram pressure of ambient stream).  The shell
+pressure is not given directly by the observations, but can be
+determined by the following three steps:
+\begin{enumerate}[P1.]
+\item \label{P1} The shell mass column (\si{g.cm^{-2}}) can be
+  estimated from the optical depth by assuming an effective UV
+  opacity: \(\Sigma\shell = \tau / \kappa\)
+\item \label{P2} The shell density (\si{g.cm^{-3}}) can be found from
+  the mass column if the shell thickness is known:
+  \(\rho\shell = \Sigma / h\shell\).  In the absence of other
+  information, a fixed fraction of the shell radius can be used.  In
+  particular, we normalize by a typical value of
+  one~quarter\footnote{%
     This corresponds to a Mach number \(\M_0 = \surd 3\) if the stream
@@
     Appendix~\ref{app:bow-shock-data}} %
-  the star--apex distance:
-  \(h_{1/4} = h\shell / (0.25 R_0)\).
-\item Finally, the pressure (\si{dyne.cm^{-2}}) follows by assuming
-  values for the sound speed and Alfvén speed:
+  the star--apex distance: \(h_{1/4} = h\shell / (0.25 R_0)\).
+\item \label{P3} Finally, the pressure (\si{dyne.cm^{-2}}) follows by
+  assuming values for the sound speed and Alfvén speed:
   \(P\shell = \rho\shell (\sound^2 + \frac12 v\alfven^2) \).
@@
 
+In Figure~\ref{fig:All-sources-eta-tau} we show the resultant
+diagnostic diagram: \(\eta\shell\) versus \(\tau\).  The horizontal
+axis shows the fraction of the stellar radiative \emph{energy} that is
+reprocessed by the bow shell, while the vertical axis shows the
+fraction of stellar radiative \emph{momentum} that is imparted to the
+shell, either directly by absorption, or indirectly by the stellar
+wind (which is itself radiatively driven).  Radiatively supported bows
+(DW, RBW, or RBS, or cases) should lie on the diagonal line
+\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where
+we have used the ratio of grain radiation pressure efficiency to
+absorption efficiency found in the FUV band for the dust mixture shown
+in Figure~\ref{fig:cloudy-ism-dust-opacity}.  Wind-supported bows
+should lie above this line and no bows should lie below the
+\(\eta = \tau\) line, since \(Q_P\) cannot be smaller than
+\(Q_{\text{abs}}\).
+
+We have calculated \(\eta\shell\) and \(\tau\) using the
+above-described methods for the 20 mid-infrared sources studied by
+\citet{Kobulnicky:2018a} and plotted them on our diagnostic diagram.
+Details of our treatment of this observational material are provided
+in Appendix~\ref{app:bow-shock-data}.  In order to expand the range of
+physical conditions, we have included three additional sources (data
+in Table~\ref{tab:observations}): bows around \thD{}
+\citep{Smith:2005a} and LP~Ori \citep{ODell:2001c} in the Orion
+Nebula, which show larger optical depths, plus the inner bow around
+\(\sigma\)~Ori, which illuminates the Horsehead Nebula and has
+previously been claimed to be a dust wave \citep{Ochsendorf:2014b,
+  Ochsendorf:2015a}.  Details of the observations of these additional
+sources will be published elsewhere.
+
+Rather than clutter the diagram with error bars, we instead show the
+sensitivity to observational errors in the lower-right gray box, where
+each arrow corresponds to a factor of two increase (0.3~dex) in an
+observational quantity: distance, \(D\); stellar luminosity, \(L_*\);
+total infrared flux, \(F_{\text{IR}}\); and bow angular apex distance,
+\(\theta\).  Most sources are members of known high-mass clusters with
+distance uncertainties less than 20\% (0.08~dex).\footnote{The only
+  exception is Source~329 in Cygnus, for which the distance
+  uncertainty is roughly a factor of 2 \citep{Kobulnicky:2018a}.}  The
+stellar luminosity is determined from spectral classification, which
+makes it independent of distance.  Taking a \SI{2000}{K} dispersion in
+the effective temperature scale \citep{Martins:2005a} gives an
+uncertainty of 25\% in the luminosity, and adding in possible errors
+in gravity and the effect of binaries, we estimate a total uncertainty
+in \(L_*\) of 50\% (0.45~mag or 0.18~dex).  We estimate the
+uncertainty in shell bolometric flux, \(F_{\text{IR}}\), by comparing
+two different methods: model fitting \citep{Kobulnicky:2017a} and a
+weighted sum of the 8, 24, and \SI{70}{\um} bands
+(App.~\ref{app:bow-shock-data}), giving a standard deviation of 17\%
+(0.07~dex).\footnote{%
+  The absolute flux calibration uncertainty for both Herschel CAPS
+  \citep{Balog:2014a} and Spitzer MIPS \citep{Engelbracht:2007a} is
+  less than 5\%.} %
+For the angular apex distance, \(\theta\), the largest uncertainty for
+well-resolved sources is due to the unknown inclination.
+\citet{Tarango-Yong:2018a} show that the dispersion in true to
+projected distances can introduce an uncertainty of \(30\%\)
+(0.11~dex) in unfavorable cases (e.g., their Fig.~26).  For 5 of the
+20 sources from \citet{Kobulnicky:2018a}, \(\theta\) is of order the
+Spitzer PSF width at \SI{24}{\um}, so the errors may be larger.
+Assuming all these observational errors to be independent yields a
+total \(\pm 1~\sigma\) observational uncertainty shown by the blue
+dashed ellipse in the figure.
+
 Mass loss rates - starting from \citet{Kobulnicky:2010a}
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/Mdot-from-eta-vs-luminosity}
-  \includegraphics[width=\linewidth]{figs/Mdot-K18-corrected-vs-luminosity}
+  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
   \caption{Mass loss rates}
   \label{fig:mass-loss-vs-luminosity}
-\end{figure}
+\end{figure*}
 

### 2019-02-21 papers/Papers1234/sec-dust-bow-discuss.tex
Start caption for mass-loss figure

@@
 weighted sum of the 8, 24, and \SI{70}{\um} bands
-(App.~\ref{app:bow-shock-data}), giving a standard deviation of 17\%
-(0.07~dex).\footnote{%
-  The absolute flux calibration uncertainty for both Herschel CAPS
+(App.~\ref{app:bow-shock-data}, eq.~[\ref{eq:total-ir-flux}]), giving
+a standard deviation of 17\% (0.07~dex).\footnote{%
+  The absolute flux calibration uncertainty for both Herschel PACS
   \citep{Balog:2014a} and Spitzer MIPS \citep{Engelbracht:2007a} is
@@
   \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
-  \caption{Mass loss rates}
+  \caption{Wind mass-loss rates as a function of stellar luminosity,
+    derived from (a)~our momentum efficiency method and (b)~the grain
+    emissivity method of \citet{Kobulnicky:2018a}, with corrections as
+    described in Appendix~\ref{app:bow-shock-data}.  Circle symbols
+    show the sources from K18, colored according to the stellar
+    effective temperature (see key at far right). }
   \label{fig:mass-loss-vs-luminosity}

### 2019-02-23 papers/Papers1234/app-dust-wave.tex
Nearly finish new appendices
Write about error covariances

@@
 This is the polar form of the equation for the confocal parabola,
-which we have already discussed in detail in \PaperI{}'s
-\S~\ref{Q-sec:conic} and Appendix~\ref{Q-app:parabola}.  Its planitude
-and alatude are \(\Gamma = \Lambda = 2\) and these are unchanged under projection
-at any inclination.
+which we have already discussed in detail in \S~\ref{Q-sec:conic} and
+Appendix~\ref{Q-app:parabola} of \citet{Tarango-Yong:2018a}.  Its
+planitude and alatude are \(\Gamma = \Lambda = 2\) and these are
+unchanged under projection at any inclination.
 
@@
 models at intermediate angles, and which also include the effects of
-gas drag, are shown in \S~\ref{sec:magn-effects-grain}.
+gas drag, are presented in \S~\ref{sec:magn-effects-grain}.
 

### 2019-02-23 papers/Papers1234/app-k17-k18.tex
Write about error covariances

@@
   \centering
-  \includegraphics[width=\linewidth]{figs/K18-mdot-corrected-comparison-R0}
+  \includegraphics[width=\linewidth]{figs/K18-mdot-corrected-comparison-R0-edited}
   \caption{Comparison of the two mass-loss methods: K18 corrected
@@
 
+\subsection{Uncertainty estimates for observational quantities}
+\label{sec:uncert-estim-observ}
+
+In this section, we estimate the \(1\sigma\) uncertainties in
+observational measurements, which contribute to the uncertainties in
+the derived quantities: \(\tau\), \(\eta\), and \(\dot M\) (see
+\S~\ref{sec:summary-discussion}).
+
+\subsubsection{Distance}
+\label{sec:distance}
+
+Most sources are members of known high-mass clusters with distance
+uncertainties less than 20\% (0.08~dex). The only exception is
+Source~329 in Cygnus, for which the distance uncertainty is roughly a
+factor of 2 \citep{Kobulnicky:2018a}.
+
+\subsubsection{Stellar luminosity}
+\label{sec:stellar-luminosity}
+
+The stellar luminosity is determined from spectral classification,
+which makes it independent of distance.  Taking a \SI{2000}{K}
+dispersion in the effective temperature scale \citep{Martins:2005a}
+gives an uncertainty of 25\% in the luminosity, and adding in possible
+errors in gravity and the effect of binaries, we estimate a total
+uncertainty in \(L_*\) of 50\% (0.45~mag or 0.18~dex).
+
+\subsubsection{Shell flux and surface brightness}
+\label{sec:shell-flux-surface}
+
+We estimate the uncertainty in shell bolometric flux,
+\(F_{\text{IR}}\), by comparing two different methods: model fitting
+\citep{Kobulnicky:2017a} and a weighted sum of the 8, 24, and
+\SI{70}{\um} bands (eq.~[\ref{eq:total-ir-flux}]), giving a standard
+deviation of 17\% (0.07~dex).  To this, we add the estimate of 25\%
+for the effects of background subtraction uncertainties on individual
+photometric measurements \citep{Kobulnicky:2017a}. The absolute flux
+calibration uncertainty for both Herschel PACS \citep{Balog:2014a} and
+Spitzer MIPS \citep{Engelbracht:2007a} is less than 5\%, which is
+small in comparison. Combining the 3 contributions in quadrature gives
+a total uncertainty of 0.12~dex.  We adopt the same uncertainty for
+the \SI{70}{\um} surface brightness.
+
+\subsubsection{Angular sizes}
+\label{sec:angular-sizes}
+
+For the angular apex distance, \(\theta\), the largest uncertainty for
+well-resolved sources is due to the unknown inclination.
+\citet{Tarango-Yong:2018a} show that the dispersion in true to
+projected distances can introduce an uncertainty of \(30\%\)
+(0.11~dex) in unfavorable cases (e.g., their Fig.~26).  For 5 of the
+20 sources from \citet{Kobulnicky:2018a}, \(\theta\) is of order the
+Spitzer PSF width at \SI{24}{\um}, so the errors may be larger.
+
+\subsubsection{Stellar wind velocity}
+\label{sec:stell-wind-veloc}
+
+Although this is not strictly an observed quantity for the K18 sample,
+we will treat it as such since it is estimated per star, based on the
+spectral type.
+
+\subsubsection{Uncertainties and covariance for derived quantities}
+\label{sec:comb-uncert-covar}
+
+\begin{table}
+  \centering
+  \caption[Derived]{Propagation of observational uncertainties to derived quantities}
+  \label{tab:derived-parameters}
+  \setlength\tabcolsep{3pt}
+  \begin{tabular}{l S S S S S S}
+    \toprule
+    \(x_i\) & {\(\sigma_{x_i}\)}
+    & {\(\Delta_{x_i} (\tau)\)} & {\(\Delta_{x_i} (\eta\shell)\)}
+    & {\(\Delta_{x_i} (\dot M)\)} & {\(\Delta_{x_i} (\dot M_{\text{K18}})\)}
+    & {\(\Delta_{x_i} (L_*)\)}
+    \\
+    \midrule
+    \(D\)     & 0.08 & 2  & 3 & 3 & 2 & 0\\
+    \(L_*\)   & 0.18 & -1 & -2 & -1 & -0.5 & 1\\
+    \(F\IR\)  & 0.12 & 1 & 1 & 1 & 0 & 0\\
+    \(I_{70}\) & 0.12 & 0 & 0 & 0 & 1 & 0\\
+    \(\theta\) & 0.11 & 0 & 1 & 1 & 2 & 0\\
+    \(\ell/R\) & 0.08 & 0 & 0 & 0 & -1 & 0\\
+    \(V\wind\) & 0.18 & 0 & 0 & -1 & -1 & 0\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Even though errors in the fundamental observed quantities, \(x_i\),
+are assumed independent, errors in the derived quantities,
+\(f_k(x_1, x_2, \dots)\), will not necessarily be so.  For the
+purposes of this paper:
+\begin{align}
+  \label{eq:observed-and-derived}
+  x_i \in &  \left\{D;\ L_*;\ F\IR;\ I_{70};\ \theta;\ \ell/R;\ V\wind \right\} \\
+  f_k \in & \left\{\tau;\ \eta\shell;\ \dot M;\ \dot M_{\text{K18}};\ L_* \right\}
+            \ .
+\end{align}
+Note that \(L_*\) appears in both lists because we use it as a graph
+axis in Figure~\ref{fig:mass-loss-vs-luminosity}.  For the case where
+each \(f_k\) is a simple product of powers of the \(x_i\), the
+propagation of errors reduces to linear algebra of log
+quantities. This is exactly true for \(\tau\) and \(\eta\shell\), but
+only approximately so for \(\dot M\) and
+\(\dot M_{\text{K18}}\).\footnote{%
+  For \(\dot M\) it is true for \(\eta\shell \gg 1.25 \tau\) and for
+  \(\dot M_{\text{K18}}\) it is true in the limit that the grain
+  emissivity can be expressed as a power law in \(U\).} %
+We define \(\Delta_{x_i} (f_k)\) as the logarithmic derivative
+\(d \ln f_k / d \ln x_i \) and \(\sigma_{x_i}\) as the rms dispersion
+in \(x_i\), measured in dex.  These are given in
+Table~\ref{tab:derived-parameters}.  Then, the elements of the
+variance--covariance matrix for the derived parameters are
+\begin{equation}
+  \label{eq:covariance}
+  C_{k,k'} = \sum_{i} \Delta_{x_i} (f_k) \, \sigma_{x_i}^2 \, \Delta_{x_i} (f_{k'}) \ , 
+\end{equation}
+which are given in Table~\ref{tab:covariance}, assuming the
+\(\sigma_{x_i}\) derived in
+\S~\ref{sec:distance}--\ref{sec:stell-wind-veloc} as suitable for the
+K18 sources.  It can be seen that many of the off-diagonal elements
+are of similar magnitude to the diagonal elements, which is an
+indication of significant correlations between the errors in the
+different parameters.
+
+\begin{table}
+  \centering
+  \caption[Covariance]{Variance--covariance matrix \(C_{k,k'}\) for derived quantities}
+  \label{tab:covariance}
+  \setlength\tabcolsep{3pt}
+  \begin{tabular}{l S S S S S }
+    \toprule
+    & {\(\tau\)} & {\(\eta\shell\)}
+    & {\(\dot M\)} & {\(\dot M_{\text{K18}}\)} & {\(L_*\)}
+    \\
+    \midrule
+    \(\tau\)               &  0.0724 &  0.1176 &  0.0852 &  0.0418 & -0.0324 \\
+    \(\eta\shell\)         &  0.1176 &  0.2137 &  0.1489 &   0.095 & -0.0648 \\
+    \(\dot M\)             &  0.0852 &  0.1489 &  0.1489 &  0.1112 & -0.0324 \\
+    \(\dot M_{\text{K18}}\)&  0.0418 &   0.095 &  0.1112 &  0.1353 & -0.0162 \\
+    \(L_*\)                & -0.0324 & -0.0648 & -0.0324 & -0.0162 &  0.0324 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+For any particular pair of derived quantities, \(f_m\) and \(f_{n}\),
+one can find the \textit{error ellipse} that characterises the
+projection of observational errors onto the \(f_m\)--\(f_{n}\) plane.
+The ellipse can be described by standard deviations along major and
+minor axes, \(\sigma_a\), \(\sigma_b\), together with the angle
+\(\theta_a\) between the \(f_m\) axis and the ellipse major axis.
+These are given via the eigenvalues and eigenvectors of the relevant
+\(2 \times 2\) submatrix of the covariance matrix:
+\begin{align}
+  \label{eq:error-ellipse}
+  \sigma_a^2 = & \frac12 \left\{   C_{m,m} + C_{n,n}
+                 + \left[ \left( C_{m,m} + C_{n,n} \right)^2
+                 - 4 C_{m,n}^2 \right]^{1/2}\right\} \\
+  \sigma_b^2 = & \frac12 \left\{   C_{m,m} + C_{n,n}
+                 - \left[ \left( C_{m,m} + C_{n,n} \right)^2
+                 - 4 C_{m,n}^2 \right]^{1/2}\right\} \\
+  \theta_a = & \frac12 \arctan \left( \frac{2 C_{m,n}}{C_{m,m} - C_{n,n}} \right) \ .
+\end{align}
+For instance, Table~\ref{tab:error-ellipse} shows the resultant error
+ellipse parameters for the relations plotted in
+Figures~\ref{fig:All-sources-eta-tau} and
+\ref{fig:mass-loss-vs-luminosity}ab, which are shown in blue on the
+respective graphs.
+
+\begin{table}
+  \centering
+  \caption[Error ellipse]{Error ellipse parameters for particular pairs of derived quantities}
+  \label{tab:error-ellipse}
+  \begin{tabular}{l l S S S l}
+    \toprule
+    \(f_m\) & \(f_n\) &  {\(\sigma_a\)} & {\(\sigma_b\)}
+    & {\(\theta_a\), \si{\degree}} & Figure   \\
+    \midrule
+    \(\tau\) & \(\eta\) & 0.529 & 0.077 & 60.5 & \ref{fig:All-sources-eta-tau} \\
+    \(L_*\) & \(\dot M\) & 0.397 & 0.155 & -75.5 & \ref{fig:mass-loss-vs-luminosity}a \\
+    \(L_*\) & \(\dot M_{\text{K18}}\) & 0.371 & 0.173 & -81.3 & \ref{fig:mass-loss-vs-luminosity}b \\
+    \(\dot M_{\text{K18}}\) & \(\dot M\) & 0.503 & 0.175 & 46.7 & \ref{fig:mass-loss-comparison} \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{figure}
+  \centering
+  \footnotesize
+  \begin{verbatim}
+import numpy as np
+sigx = np.diag([0.08, 0.18, 0.12, 0.12, 0.11, 0.08, 0.18])
+Dfx = np.array([
+    [2, -1, 1, 0, 0, 0, 0],
+    [3, -2, 1, 0, 1, 0, 0],
+    [3, -1, 1, 0, 1, 0, -1],
+    [2, -0.5, 0, 1, 2, -1, -1],
+    [0, 1, 0, 0, 0, 0, 0]
+])
+C = Dfx @ sigx**2 @ Dfx.T
+  \end{verbatim}
+  \caption{Snippet of Python code that calculates the
+    covariance matrix of Table~\ref{tab:covariance}.  The last line
+    implements equation~\eqref{eq:covariance} by a triple matrix
+    product of the derivatives matrix \texttt{Dfx}, the square of a
+    diagonal matrix of observational standard deviations \texttt{sigx},
+    and the transpose of \texttt{Dfx}.}
+  \label{fig:python-covar}
+\end{figure}
+
 %%% Local Variables:

### 2019-02-23 papers/Papers1234/sec-dust-bow-discuss.tex
Write about error covariances

--- 2019-02-19 papers/Papers1234/sec-dust-bow-discuss.tex
@@
 Dust waves favored by high velocities and intermediate densities.
-
-\newcommand\IR{\ensuremath{_{\text{IR}}}}
 
@@
 above-described methods for the 20 mid-infrared sources studied by
-\citet{Kobulnicky:2018a} and plotted them on our diagnostic diagram.
-Details of our treatment of this observational material are provided
-in Appendix~\ref{app:bow-shock-data}.  In order to expand the range of
-physical conditions, we have included three additional sources (data
-in Table~\ref{tab:observations}): bows around \thD{}
+\citet{Kobulnicky:2018a} (K18) and plotted them on our diagnostic
+diagram.  Details of our treatment of this observational material are
+provided in Appendix~\ref{app:bow-shock-data}.  In order to expand the
+range of physical conditions, we have included three additional
+sources (data in Table~\ref{tab:observations}): bows around \thD{}
 \citep{Smith:2005a} and LP~Ori \citep{ODell:2001c} in the Orion
@@
 Rather than clutter the diagram with error bars, we instead show the
-sensitivity to observational errors in the lower-right gray box, where
-each arrow corresponds to a factor of two increase (0.3~dex) in an
+sensitivity to observational errors in the lower-right box, where each
+arrow corresponds to a factor of two increase (0.3~dex) in an
 observational quantity: distance, \(D\); stellar luminosity, \(L_*\);
 total infrared flux, \(F_{\text{IR}}\); and bow angular apex distance,
-\(\theta\).  Most sources are members of known high-mass clusters with
-distance uncertainties less than 20\% (0.08~dex).\footnote{The only
-  exception is Source~329 in Cygnus, for which the distance
-  uncertainty is roughly a factor of 2 \citep{Kobulnicky:2018a}.}  The
-stellar luminosity is determined from spectral classification, which
-makes it independent of distance.  Taking a \SI{2000}{K} dispersion in
-the effective temperature scale \citep{Martins:2005a} gives an
-uncertainty of 25\% in the luminosity, and adding in possible errors
-in gravity and the effect of binaries, we estimate a total uncertainty
-in \(L_*\) of 50\% (0.45~mag or 0.18~dex).  We estimate the
-uncertainty in shell bolometric flux, \(F_{\text{IR}}\), by comparing
-two different methods: model fitting \citep{Kobulnicky:2017a} and a
-weighted sum of the 8, 24, and \SI{70}{\um} bands
-(App.~\ref{app:bow-shock-data}), giving a standard deviation of 17\%
-(0.07~dex).\footnote{%
-  The absolute flux calibration uncertainty for both Herschel CAPS
-  \citep{Balog:2014a} and Spitzer MIPS \citep{Engelbracht:2007a} is
-  less than 5\%.} %
-For the angular apex distance, \(\theta\), the largest uncertainty for
-well-resolved sources is due to the unknown inclination.
-\citet{Tarango-Yong:2018a} show that the dispersion in true to
-projected distances can introduce an uncertainty of \(30\%\)
-(0.11~dex) in unfavorable cases (e.g., their Fig.~26).  For 5 of the
-20 sources from \citet{Kobulnicky:2018a}, \(\theta\) is of order the
-Spitzer PSF width at \SI{24}{\um}, so the errors may be larger.
-Assuming all these observational errors to be independent yields a
-total \(\pm 1~\sigma\) observational uncertainty shown by the blue
-dashed ellipse in the figure.
+\(\theta\).  In \S~\ref{app:bow-shock-data} we estimate the
+uncertainty in each observational quantity, which we then combine to
+find the \(\pm 1~\sigma\) error ellipse shown in blue in the figure.
+It can be seen that observational uncertainties in \(\tau\) and
+\(\eta\) are highly correlated: the dispersion is \SI{0.7}{dex} in the
+product \(\eta\tau\) but only \SI{0.16}{dex} in the ratio
+\(\eta/\tau\), with stellar luminosity errors dominating in both
+cases.  Observational uncertainties are therefore relatively
+unimportant in determining whether a given source is wind-driven or
+radiation-driven.
 
@@
   \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
-  \caption{Mass loss rates}
+  \caption{Wind mass-loss rates as a function of stellar luminosity,
+    derived from (a)~our trapped energy/momentum method and (b)~the
+    grain emissivity method of \citet{Kobulnicky:2018a}, with
+    corrections as described in our Appendix~\ref{app:bow-shock-data}.
+    Circle symbols show the sources from K18, colored according to the
+    stellar effective temperature (see key at far right). In panel a,
+    squares show two of our additional sources
+    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
+    given for sources that lie close to the radiation-supported line
+    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
+    symbols and downward-pointing arrows.  Sources that lie less than
+    a factor of three above the line have enhanced downward
+    uncertainties and are also shown by slightly fainter symbols.  For
+    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
+    luminosities of the triple OB system Aa, Ab, and B
+    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
+    the luminosity of only the most massive component Aa.  Lines show
+    the predictions of stellar wind models: red lines are the commonly
+    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
+    (dashed), and supergiants (dotted), while black lines show
+    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
+    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
+    mass-loss measurements from NUV lines for weak-wind O~dwarfs
+    \citep{Marcolino:2009a}, while the green plus symbol shows the
+    measurement from infrared H recombination lines for \(\sigma\)~Ori
+    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
+    to observational uncertainties (lower right) and assumed shell
+    parameters (upper left).}
   \label{fig:mass-loss-vs-luminosity}

### 2019-02-23 papers/Papers1234/app-k17-k18.tex
Tidy up last part of app E

@@
     \(x_i\) & {\(\sigma_{x_i}\)}
-    & {\(\Delta_{x_i} (\tau)\)} & {\(\Delta_{x_i} (\eta\shell)\)}
-    & {\(\Delta_{x_i} (\dot M)\)} & {\(\Delta_{x_i} (\dot M_{\text{K18}})\)}
-    & {\(\Delta_{x_i} (L_*)\)}
+    & {\(J_{x_i} (\tau)\)} & {\(J_{x_i} (\eta\shell)\)}
+    & {\(J_{x_i} (\dot M)\)} & {\(J_{x_i} (\dot M_{\text{K18}})\)}
+    & {\(J_{x_i} (L_*)\)}
     \\
@@
   emissivity can be expressed as a power law in \(U\).} %
-We define \(\Delta_{x_i} (f_k)\) as the logarithmic derivative
-\(d \ln f_k / d \ln x_i \) and \(\sigma_{x_i}\) as the rms dispersion
-in \(x_i\), measured in dex.  These are given in
-Table~\ref{tab:derived-parameters}.  Then, the elements of the
-variance--covariance matrix for the derived parameters are
+We define \(J_{x_i} (f_k)\) as the elements of the Jacobian matrix of
+logarithmic derivatives \(d \ln f_k / d \ln x_i \), which are given
+for our quantities in Table~\ref{tab:derived-parameters}.  Then, the
+elements of the variance--covariance matrix for the derived parameters
+are
 \begin{equation}
   \label{eq:covariance}
-  C_{k,k'} = \sum_{i} \Delta_{x_i} (f_k) \, \sigma_{x_i}^2 \, \Delta_{x_i} (f_{k'}) \ , 
+  C_{k,k'} = \sum_{i} J_{x_i} (f_k) \, \sigma_{x_i}^2 \, J_{x_i} (f_{k'}) \ , 
 \end{equation}
-which are given in Table~\ref{tab:covariance}, assuming the
-\(\sigma_{x_i}\) derived in
-\S~\ref{sec:distance}--\ref{sec:stell-wind-veloc} as suitable for the
-K18 sources.  It can be seen that many of the off-diagonal elements
-are of similar magnitude to the diagonal elements, which is an
-indication of significant correlations between the errors in the
-different parameters.
+where the \(\sigma_{x_i}\) are the rms dispersions in \(x_i\),
+measured in dex.  In Figure~\ref{fig:python-covar} we give example
+python code for calculating this matrix, using the \(\sigma_{x_i}\)
+derived in \S~\ref{sec:distance}--\ref{sec:stell-wind-veloc} for the
+K18 sources (second column of Tab.~\ref{tab:derived-parameters}), with
+results given in Table~\ref{tab:covariance}.  It can be seen that many
+of the off-diagonal elements are of similar magnitude to the diagonal
+elements, which is an indication of significant correlations between
+the errors in the different parameters.
 
@@
 projection of observational errors onto the \(f_m\)--\(f_{n}\) plane.
-The ellipse can be described by standard deviations along major and
+The ellipse is characterized by standard deviations along major and
 minor axes, \(\sigma_a\), \(\sigma_b\), together with the angle
@@
 For instance, Table~\ref{tab:error-ellipse} shows the resultant error
-ellipse parameters for the relations plotted in
-Figures~\ref{fig:All-sources-eta-tau} and
-\ref{fig:mass-loss-vs-luminosity}ab, which are shown in blue on the
-respective graphs.
+ellipse parameters (shown in blue on the respective graphs) for the
+relations plotted in Figures~\ref{fig:All-sources-eta-tau},
+\ref{fig:mass-loss-vs-luminosity}ab, and
+\ref{fig:mass-loss-comparison}.
 
@@
 import numpy as np
-sigx = np.diag([0.08, 0.18, 0.12, 0.12, 0.11, 0.08, 0.18])
-Dfx = np.array([
+sig = np.diag([0.08, 0.18, 0.12, 0.12, 0.11, 0.08, 0.18])
+J = np.array([
     [2, -1, 1, 0, 0, 0, 0],
@@
 ])
-C = Dfx @ sigx**2 @ Dfx.T
+C = J @ sig**2 @ J.T
   \end{verbatim}
@@
     implements equation~\eqref{eq:covariance} by a triple matrix
-    product of the derivatives matrix \texttt{Dfx}, the square of a
-    diagonal matrix of observational standard deviations \texttt{sigx},
-    and the transpose of \texttt{Dfx}.}
+    product of the Jacobian matrix \texttt{J}, the square of a
+    diagonal matrix of observational standard deviations \texttt{sig},
+    and the transpose of \texttt{J}.}
   \label{fig:python-covar}

### 2019-02-26 papers/Papers1234/app-k17-k18.tex
Finish discussion of V750 Mon

@@
 the derived quantities: \(\tau\), \(\eta\), and \(\dot M\) (see
-\S~\ref{sec:summary-discussion}).
+\S~\ref{sec:comb-uncert-covar} and \S~\ref{sec:summary-discussion}).
 
@@
 we will treat it as such since it is estimated per star, based on the
-spectral type.
+spectral type.  K18 estimate 50\% uncertainty, and we adopt the same
+here (0.18~dex).
 
-\subsubsection{Uncertainties and covariance for derived quantities}
+\subsection{Covariance of derived quantities from propagation of observational uncertainties}
 \label{sec:comb-uncert-covar}
@@
 Even though errors in the fundamental observed quantities, \(x_i\),
-are assumed independent, errors in the derived quantities,
-\(f_k(x_1, x_2, \dots)\), will not necessarily be so.  For the
-purposes of this paper:
+are assumed independent,\footnote{%
+  It is of course true that \(F\IR\) and \(I_{70}\) are not completely
+  independent from one another, but this does not matter since we
+  consider only derived quantities that are a function of one or the
+  other, not both.} %
+errors in the derived quantities, \(f_k(x_1, x_2, \dots)\), will not
+necessarily be so.  For the purposes of this paper:
 \begin{align}
@@
   \end{verbatim}
+  \vspace*{-\baselineskip}
   \caption{Snippet of Python code that calculates the
@@
 
+\subsection{Notes on particular sources}
+\label{sec:notes-part-sourc}
+
+\subsubsection{Source~380, HD~53367, V750~Mon}
+\label{sec:hd-53367-v750}
+
+This is a Herbig Be star with spectral type B0V--B0III and mass 12 to
+\SI{15}{M_\odot}, which shows long-scale irregular photometric
+variability \citep{Tjin-A-Djie:2001a, Pogodin:2006a} together with
+cyclic radial velocity variations, which are interpreted as an
+eccentric binary with a \SI{5}{M_\odot} pre-main-sequence companion.
+It is located outside the solar circle and, although it was originally
+classified as part of the CMa OB association at about \SI{1}{kpc}
+\citep{Tjin-A-Djie:2001a}, more recent estimates put it much closer.
+K18 assume a distance of \SI{260}{pc}, based on Hipparcos measurements
+\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
+\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
+puts it closer still at \SI{140 \pm 30}{pc}.\footnote{%
+  Median and 90\% confidence interval, estimated from Bayesian
+  inference using an exponential density distribution with scale
+  length of \SI{1350}{pc} as a prior (see
+  \url{https://github.com/agabrown/astrometry-inference-tutorials/}). }
+
+\citet{Quireza:2006b} report a kinematic distance to the associated
+\hii{} region IC~2177 (G\num{223.70}\num{-1.90}) of \SI{1.6}{kpc},
+based an LSR radio recombination line velocity of \SI{+16}{km.s^{-1}}
+\citep{Quireza:2006a} and the outer Galaxy rotation curve of
+\citet{Brand:1993a}.  However, given the dispersion in peculiar
+velocities of star-forming clouds (\SIrange{7}{9}{km.s^{-1}},
+\citealp{Stark:1984a}) and likely streaming motions of the ionized gas
+(\(\approx \SI{10}{km.s^{-1}}\), \citealp{Matzner:2002a, Lee:2012a}),
+this is still consistent with a much smaller distance, which would
+also help in bringing the radio continuum-derived nebular electron
+density into agreement with the value (\(\approx \SI{100}{cm^{-3}}\))
+derived from the optical [\ion{S}{ii}] line ratio
+\citep{Hawley:1978a}.
+
+\citet{Fairlamb:2015a} derive a distance of \SI{340 \pm 60}{pc} from
+combining a spectroscopically determined effective temperature,
+gravity, and reddening with photometry and pre-main sequence
+evolutionary tracks.  They also determine a luminosity of \SI{13000
+  \pm 1000}{L_\odot}, which is only half that assumed by K18, and
+would have to be even lower to bring the photometry into concordance
+with the Gaia distance.  Alternatively, the luminosity could remain
+the same if the total-to-selective extinction ratio were higher than
+the \(R_V = 3.1\) assumed by \citet{Fairlamb:2015a}.  Taking
+\(R_V = 5.5\) instead, as in Orion, would give \(A_V = 3.34\) and a
+predicted \(V\) magnitude of 6.7 if we assume \(L_4 = 1.3\),
+\(D = \SI{170}{pc}\) (furthest distance in Gaia 90\% confidence
+interval) and \(T_{\text{eff}} = \SI{29.5}{kK}\)
+\citep{Fairlamb:2015a} for a bolometric correction of \(-2.86\)
+\citep{Nieva:2013a}.  The observed brightness varies between
+\(V = 6.9\) and 7.2, which is still at least 20\% fainter than
+predicted, but this is the best that can be achieved without rejecting
+the Gaia parallax distance entirely.
+
+A final sanity check can be performed by considering the free-free
+radio continuum flux of V750~Mon's surrounding \hii{} region, which,
+after converting to a luminosity, should be proportional to the total
+recombination rate in the nebula and therefore, assuming
+photoionization equilibrium and negligible dust absorption in the
+ionized gas, also proportional to the ionizing photon luminosity of
+the star.  \citet{Quireza:2006b} report a flux density of \SI{6}{Jy}
+at \SI{8.6}{Ghz} for G\num{223.70}\num{-1.90}, as compared with a flux
+density of \SI{260}{Jy} for the Orion Nebula using the same
+instrumental setup.  Assuming an ionizing photon luminosity of
+\(S_{49} = 1\) and distance \SI{410}{pc} for the ionizing Trapezium
+stars in Orion, therefore implies
+\(S_{49} = 0.0027 (D/\SI{140}{pc})^2\) for V750~Mon.  Using an
+ionizing flux of \SI{3.2e22}{cm^{-2}.s^{-1}} from the curves in Fig.~4
+of \citet{Sternberg:2003a}, this translates to a bolometric luminosity
+of \(L_4 = 0.96 (D/\SI{140}{pc})^2\), which is consistent with the
+\citet{Fairlamb:2015a} value if we take a distance towards the high
+end of the Gaia range.
+
+\subsubsection{Source 407, HD~93249}
+\label{sec:source-407}
+
 %%% Local Variables:

### 2019-02-26 papers/Papers1234/sec-dust-bow-discuss.tex
Finish discussion of V750 Mon

@@
 
-Are there any objects that might not be bow shocks?
+% Are there any objects that might not be bow shocks?
 
-Progression in density:
-\begin{gather*}
-  \text{Increasing density} \longrightarrow \\
-  \text{WBS} \to \text{WBS} + \text{IDW} \to \text{WBS} + \text{DDW} \to \text{(RBW)} \to \text{RBS}
-\end{gather*}
+% Progression in density:
+% \begin{gather*}
+%   \text{Increasing density} \longrightarrow \\
+%   \text{WBS} \to \text{WBS} + \text{IDW} \to \text{WBS} + \text{DDW} \to \text{(RBW)} \to \text{RBS}
+% \end{gather*}
 
-Chief diagnostic for radiation supported bows (RBW or RBS cases) is
-infrared luminosity of bow.  Favored by high densities.
+% Chief diagnostic for radiation supported bows (RBW or RBS cases) is
+% infrared luminosity of bow.  Favored by high densities.
 
-Dust waves favored by high velocities and intermediate densities.
+% Dust waves favored by high velocities and intermediate densities.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\linewidth]{figs/All-sources-eta-tau}
+  \caption[Observational diagnostic diagram]{Observational diagnostic
+    diagram for bow shocks.  The shell optical depth \(\tau\) (\(x\)
+    axis) and momentum efficiency \(\eta\shell\) (\(y\) axis) can be
+    estimated from observations of the bolometric stellar luminosity,
+    infrared shell luminosity, and shell radius, as described in the
+    text.  Results are shown for the 20 sources (circle symbols) from
+    \citet{Kobulnicky:2018a} plus three further sources (square
+    symbols), where we have obtained the measurements ourselves (see
+    Tab.~\ref{tab:observations}).  The color of each symbol indicates
+    the stellar luminosity (dark to light) as indicated by the scale
+    bar. The shell pressure is determined assuming a gas temperature
+    \(T = \SI{e4}{K}\), an absorption opacity
+    \(\kappa = \SI{600}{cm^2.g^{-1}}\), and a thickness-to-radius ratio
+    \(H/R = 0.25\).  The sensitivity of the results to a
+    factor-of-three change in each parameter is shown in the upper
+    inset box.  Exceptions are the two Orion Nebula sources, \thD{}
+    and LP~Ori, where the small dim squares show the results of
+    assuming the standard shell parameters, while the large squares
+    show the results of modifications according to the peculiar
+    circumstances of each object, as described in the text.  The lower
+    inset box shows the sensitivity of the results to a factor-of-two
+    uncertainty in each observed quantity: distance to source \(D\);
+    stellar luminosity \(L_*\), shell infrared flux \(F\IR\); shell
+    angular size \(\theta\).  Lines and shading indicate different
+    theoretical bow regimes (see \S\S~\ref{sec:strong-gas-grain} and
+    \ref{sec:imperf-coupl-betw}).  The dashed blue diagonal line
+    corresponds to radiation-supported bows, while the upper left
+    region corresponds to wind-supported bows.  The upper right corner
+    (purple) corresponds to optically thick bow shocks, while the
+    lower left corner (yellow) is the region where grain--gas
+    separation \textit{may} occur, leading to a potential dust wave.
+    However, the existence of a dust wave in this region is not
+    automatic, since it only includes one of the four necessary
+    conditions (\S~\ref{sec:exist-cond-separ} and
+    \S~\ref{sec:grain-traj-with}). The lower-right region is strictly
+    forbidden, except in case of violation of the assumption that dust
+    heating be dominated by stellar radiation. }
+  \label{fig:All-sources-eta-tau}
+\end{figure*}
 
@@
 diagnostics based on the most common observations, which are of the
-infrared dust emission.
+infrared dust emission.  Key questions that we wish to address include
+\begin{enumerate}[1.]
+\item Can we distinguish observationally between radiation support
+  (bow waves and dust waves) and wind support (bow shocks)?
+\item Are there any clear examples of sources with radiation-supported bows?
+\item In the case of wind support, can we reliably determine mass loss
+  rates from mid-infrared observations?
+\end{enumerate}
 
-A fundamental parameter is the optical depth, \(\tau\), of the bow shell
-to UV radiation, which determines what fraction of the stellar photon
-momentum is available to support the shell (see
+\subsection{Energy trapping versus momentum trapping}
+\label{sec:energy-trapp-vers}
+
+A fundamental parameter is the optical depth, \(\tau\), of the bow
+shell to UV radiation, which determines what fraction of the stellar
+photon momentum is available to support the shell (see
 \S~\ref{sec:three-bow-regimes}).  But the same photons also heat the
@@
 mid-infrared wavelengths (roughly \SIrange{10}{100}{\um}) with
-luminosity \(L\IR\).  Assuming that Ly\(\alpha\) and mechanical heating of
-the dust shell is negligible and that the emitting shell subtends a
-solid angle \(\Omega\), as seen from the star, then the optical depth can
-be estimated as
+luminosity \(L\IR\).  Assuming that Ly\(\alpha\) and mechanical
+heating of the dust shell is negligible (see
+\S~\ref{sec:unimp-other-heat}) and that the emitting shell subtends a
+solid angle \(\Omega\), as seen from the star, then the optical depth
+can be estimated as
 \begin{equation}
@@
 
+\subsection[The eta-tau diagnostic diagram]
+{\boldmath The \(\eta\shell\)--\(\tau\) diagnostic diagram}
+\label{sec:eta-tau-diagnostic}
+
 \begin{table}
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\linewidth]{figs/All-sources-eta-tau}
-  \caption[Observational diagnostic diagram]{Observational diagnostic
-    diagram for bow shocks.  The shell optical depth \(\tau\) (\(x\)
-    axis) and momentum efficiency \(\eta\shell\) (\(y\) axis) can be
-    estimated from observations of the bolometric stellar luminosity,
-    infrared shell luminosity, and shell radius, as described in the
-    text.  Results are shown for the 20 sources (circle symbols) from
-    \citet{Kobulnicky:2018a} plus three further sources (square
-    symbols), where we have obtained the measurements ourselves (see
-    Tab.~\ref{tab:observations}).  The color of each symbol indicates
-    the stellar luminosity (dark to light) as indicated by the scale
-    bar. The shell pressure is determined assuming a gas temperature
-    \(T = \SI{e4}{K}\), an absorption opacity
-    \(\kappa = \SI{600}{cm^2.g^{-1}}\), and a thickness-to-radius ratio
-    \(H/R = 0.25\).  The sensitivity of the results to a
-    factor-of-three change in each parameter is shown in the upper
-    inset box.  Exceptions are the two Orion Nebula sources, \thD{}
-    and LP~Ori, where the small dim squares show the results of
-    assuming the standard shell parameters, while the large squares
-    show the results of modifications according to the peculiar
-    circumstances of each object, as described in the text.  The lower
-    inset box shows the sensitivity of the results to a factor-of-two
-    uncertainty in each observed quantity: distance to source \(D\);
-    stellar luminosity \(L_*\), shell infrared flux \(F\IR\); shell
-    angular size \(\theta\).  Lines and shading indicate different
-    theoretical bow regimes (see \S\S~\ref{sec:strong-gas-grain} and
-    \ref{sec:imperf-coupl-betw}).  The dashed blue diagonal line
-    corresponds to radiation-supported bows, while the upper left
-    region corresponds to wind-supported bows.  The upper right corner
-    (purple) corresponds to optically thick bow shocks, while the
-    lower left corner (yellow) is the region where grain--gas
-    separation \textit{may} occur, leading to a potential dust wave.
-    However, the existence of a dust wave in this region is not
-    automatic, since it only includes one of the four necessary
-    conditions (\S~\ref{sec:exist-cond-separ} and
-    \S~\ref{sec:grain-traj-with}). The lower-right region is strictly
-    forbidden, except in case of violation of the assumption that dust
-    heating be dominated by stellar radiation. }
-  \label{fig:All-sources-eta-tau}
-\end{figure*}
-
 In Figure~\ref{fig:All-sources-eta-tau} we show the resultant
@@
 should lie above this line and no bows should lie below the
-\(\eta = \tau\) line, since \(Q_P\) cannot be smaller than
+\(\eta\shell = \tau\) line, since \(Q_P\) cannot be smaller than
 \(Q_{\text{abs}}\).
@@
 
-Rather than clutter the diagram with error bars, we instead show the
-sensitivity to observational errors in the lower-right box, where each
-arrow corresponds to a factor of two increase (0.3~dex) in an
-observational quantity: distance, \(D\); stellar luminosity, \(L_*\);
-total infrared flux, \(F_{\text{IR}}\); and bow angular apex distance,
-\(\theta\).  In \S~\ref{app:bow-shock-data} we estimate the
-uncertainty in each observational quantity, which we then combine to
-find the \(\pm 1~\sigma\) error ellipse shown in blue in the figure.
-It can be seen that observational uncertainties in \(\tau\) and
-\(\eta\) are highly correlated: the dispersion is \SI{0.7}{dex} in the
-product \(\eta\tau\) but only \SI{0.16}{dex} in the ratio
-\(\eta/\tau\), with stellar luminosity errors dominating in both
+\subsubsection{Random uncertainties due to observational errors}
+\label{sec:rand-syst-uncert}
+
+The fundamental observational quantities that go into determining
+\(\tau\) and \(\eta\shell\) for each source are distance, \(D\);
+stellar luminosity, \(L_*\); total infrared flux, \(F_{\text{IR}}\);
+and bow angular apex distance, \(\theta\).  From these, the shell
+radius and infrared luminosity are found as \(R_0 = \theta D\) and
+\(L_{\text{IR}} = 4\pi D^2 F_{\text{IR}}\).  Rather than clutter the
+diagram with error bars, we instead show the sensitivity to
+observational errors in the lower-right box, where each arrow
+corresponds to a factor of two increase (0.3~dex) in each quantity:
+\(D\), \(L_*\), \(F_{\text{IR}}\), and \(\theta\).  In
+\S~\ref{sec:uncert-estim-observ} we estimate the uncertainty in each
+observational quantity for the K18 sources.  We then combine these in
+\S~\ref{sec:comb-uncert-covar} to find the \(\pm 1~\sigma\) error
+ellipse, shown in blue in the figure.  It can be seen that
+observational uncertainties in \(\tau\) and \(\eta\shell\) are highly
+correlated: the dispersion is \SI{0.7}{dex} in the product
+\(\eta\shell \tau\) but only \SI{0.16}{dex} in the ratio
+\(\eta\shell/\tau\), with stellar luminosity errors dominating in both
 cases.  Observational uncertainties are therefore relatively
 unimportant in determining whether a given source is wind-driven or
-radiation-driven.
+radiation-driven, which depends only on \(\eta\shell/\tau\).  On the
+other hand, they do significantly effect the question of whether a
+source has a sufficiently high radiation parameter \(\Xi\) to possibly
+be a dust wave.
+
+\subsubsection{Systematic uncertainties due to assumed shell parameters}
+\label{sec:syst-uncert-due}
+
+A further source of uncertainty arises from the parameters of the
+shocked shell that are assumed in steps P\ref{P1}--P\ref{P3}, namely
+the relative shell thickness, \(h\shell/R_0\), the ultraviolet grain
+opacity per mass of gas, \(\kappa\), and the shell temperature, \(T\).
+These parameters effect only \(\eta\shell\), not \(\tau\), with a
+sensitivity shown by arrows in the upper left box of
+Figure~\ref{fig:All-sources-eta-tau}.
+
+\subparagraph{Shell thickness}
+We do not expect a great deal of variation in the shell thickness,
+except for in the case of fast runaway stars
+(\(v > \SI{100}{km.s^{-1}}\)), for which the shell may be dramatically
+thinner if the post-shock cooling is sufficiently rapid
+(\(h / R_0 \sim M_0^{-2}\)).  For ambient densities less than about
+\SI{10}{cm^{-3}}, the minimum thickness is about ten times smaller
+than we are assuming.  This occurs at
+\(v \approx \SI{60}{km.s^{-1}}\), corresponding to the peak in the
+cooling curve at \SI{e5}{K} (see \S~\ref{sec:radi-cool-lengths}),
+since the thickness is set by the cooling length at higher speeds.  In
+principle, the shell thickness can be measured observationally if the
+source is sufficiently well resolved \citep{Kobulnicky:2017a},
+although this is complicated by projection effects.
+
+\subparagraph{Dust opacity}
+The dust opacity will depend on the total dust-gas ratio and on the
+composition and size distribution of the grains.  Our adopted value of
+\SI{600}{cm^2.g^{-1}}, or \SI{1.3e-21}{cm^2.H^{-1}}, is appropriate
+for average Galactic interstellar grains in the EUV and FUV (e.g.,
+\citealp{Weingartner:2001a}), but there is ample evidence for
+substantial spatial variations in grain extinction properties
+\citep{Fitzpatrick:2007a}, both on Galactic scales
+\citep{Schlafly:2016a} and within a single star forming region
+\citep{Beitia-Antero:2017a}.  The properties of grains within
+photoionized regions are very poorly constrained observationally
+because the optical depth is generally much lower than in overlying
+neutral material.  In the Orion Nebula, there is some evidence
+\citep{Salgado:2016a} that the FUV dust opacity in the ionized gas may
+be as low as \SI{90}{cm^2.g^{-1}}, although the uncertainties in this
+estimate are large and different results are obtained in other
+regions, such as W3(A) \citep{Salgado:2012a}.
+
+\subparagraph{Shell gas temperature} For bows around O~stars, the
+shell temperature should be close to the photoionization equilibrium
+value of \(\approx \SI{e4}{K}\), since the post-shock cooling length
+is short in ambient densities above \SI{0.1}{cm^{-3}}
+(\S~\ref{sec:radi-cool-lengths}) and the shell does not trap the
+ionization front for ambient densities below \SI{e4}{cm^{-3}}
+(\S~\ref{sec:trapp-ioniz-front}).  For B~stars, on the other hand,
+these two density limits move closer together (cf.~the smaller gap
+between the blue and red lines in Figs.~\ref{fig:zones-v-n-plane}a and
+\ref{fig:B-supergiant}, as compared with \ref{fig:zones-v-n-plane}b
+and~c), making it more likely that a bow will lie in a different
+temperature regime.  The only source for which we have evidence that
+this occurs is LP~Ori, as discussed in the next section.
+
+\subsubsection{Special treatment of particular sources}
+\label{sec:spec-treatm-part}
+
+For two of the additional bows listed in Table~\ref{tab:observations},
+we are forced to deviate from the default values for the shell
+parameters.  For LP~Ori, the bow shell appears to be formed from
+neutral gas \citep{ODell:2001c} and its relatively high \(\tau\) value
+is more than sufficient to trap the weak ionizing photon output of a
+B3 star.  We therefore move its point in
+Figure~\ref{fig:All-sources-eta-tau} downward to reflect a temperature
+of \SI{1000}{K} (or, equivalently, a magnetically supported shell with
+\(v\alfven \approx \SI{3}{km.s^{-1}}\)).  For the case of the Orion
+Trapezium star \thD{}, we find that using the default parameters
+results in a placement well inside the forbidden zone of
+Figure~\ref{fig:All-sources-eta-tau} (indicated by fainter symbol).
+For this object there is no reason to suspect anything but the usual
+photoionized temperature of \SI{e4}{K}, but its placement could be
+resolved either by decreasing the shell thickness, or decreasing the
+UV dust opacity, or both. Given the moderate limb brightening seen in
+the highest resolution images of the Ney--Allen nebula
+\citep{Robberto:2005a, Smith:2005a}, the shell thickness is unlikely
+to be less than half our default value.  But, if this were combined
+with a factor 5 decrease in \(\kappa\), as suggested by
+\citet{Salgado:2016a}, then this would be sufficient to move the
+source up to the RBW line, or slightly above.
+
+\subsection{Candidate radiation-supported bows}
+\label{sec:cand-radi-supp}
+
+Four sources are sufficiently close to the diagonal line
+\(\eta\shell = 1.25 \tau\) in Figure~\ref{fig:All-sources-eta-tau}
+that they should be treated as potential candidates for
+radiation-supported bows. These are K18 sources~380 (HD~53367,
+V750~Mon) and 407 (HD~93249 in Carina) plus \thD{} and LP~Ori.  Of the
+four, source 380 is the only one that is also a candidate for
+grain-gas decoupling.  Details of some of these sources are presented
+in \S~\ref{sec:notes-part-sourc}, where for source~380 we show that
+reducing both luminosity and distance by a factor of roughly 2 with
+respect to the values used by K18 would provide a better fit to the
+totality of observational data.  However, the ratio
+\(\eta\shell /\tau\) is proportional to \(D / L_*\) so it would not be
+affected by such an adjustment and the bow remains
+radiation-supported.  On the other hand \(\eta\shell\) (proportional
+to \(D / L_*^2\)) would increase by 2, making the classification as
+dust wave candidate more marginal.
+
+\subsection{Stellar wind mass-loss rates}
+\label{sec:stellar-wind-mass}
 
@@
 \end{figure*}
+
+Source~342 is anomalous in both methods.
+
+Evidence for small grains around Arches cluster near Galactic center \citep{Hankins:2017a}
 

### 2019-02-26 papers/Papers1234/app-cloudy-dust-charging.tex
Divide dust wave paper in three parts

--- 2019-02-14 papers/Papers1234/app-cloudy-dust-charging.tex
@@
 
-\section{Grain temperature and mid-infrared emissivity}
-\label{sec:grain-temp-emiss}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/grain-T-vs-U}
-  \caption{Grain temperature versus radiation field mean intensity,
-    \(U\), in units of the interstellar radiation field in the solar
-    neighborhood.  Line types and colors are as in
-    Fig.~\ref{fig:phi-vs-Xi} and correspond to a variety of stellar
-    spectral shapes, gas densities, and grain species.}
-  \label{fig:grain-T-vs-U}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/grain-j70-vs-U-edited}
-  \caption{Grain emissivity at \SI{70}{\um} for all Cloudy models
-    (lines colored as in Fig.~\ref{fig:drift-gn}), compared with grain
-    models from \citet{Draine:2007a} (dark gray symbols), which assume
-    illumination by a scaled interstellar radiation field, which has a
-    SED with a very different shape from that of an OB star, see
-    Fig.~\ref{fig:sed-comparison}.  }
-  \label{fig:grain-j70}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/sed-comparison}
-  \caption{Comparison between the spectral energy distribution (SED)
-    of a typical OB star (blue line) and the interstellar radiation
-    field in the solar neighborhood (orange line).  The OB star is the
-    \SI{20}{M_\odot} model from Table~\ref{tab:stars} and is plotted for a
-    distance from the star of \SI{1}{pc}.  The interstellar SED is
-    from \citet{Mathis:1983a} and is multiplied by \num{80} so that
-    the total FUV-to-NIR flux is equal for the two SEDs.}
-  \label{fig:sed-comparison}
-\end{figure}
+% Inner shock \dots no dust \dots proton Larmor radius very small, so
+% no penetration across contact discontinuity
 

### 2019-02-26 papers/Papers1234/app-cloudy-dust-heating.tex
Divide dust wave paper in three parts

\section{Grain temperature and mid-infrared emissivity}
\label{sec:grain-temp-emiss}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/grain-T-vs-U}
  \caption{Grain temperature versus radiation field mean intensity,
    \(U\), in units of the interstellar radiation field in the solar
    neighborhood.  Line types and colors are as in
    Fig.~\ref{fig:phi-vs-Xi} and correspond to a variety of stellar
    spectral shapes, gas densities, and grain species.}
  \label{fig:grain-T-vs-U}
\end{figure}

Figure~\ref{fig:grain-T-vs-U} shows equilibrium grain temperatures for
the Cloudy models discussed in Appendix~\ref{sec:cloudy-models-dust}
as a function of the nominal energy density of the radiation field,
\(U = u / u\mmp \), where \(u = L / 4 \pi R^2 c\) and \(u\mmp\) is the
energy density of the interstellar radiation field for
\(\lambda < \SI{8}{\um}\) in the solar neighborhood
\citep{Mathis:1983a}:
\begin{equation}
  \label{eq:u-mmp83}
  u\mmp\,c = \SI{0.0217}{erg.s^{-1}.cm^{-2}} \ .
\end{equation}
The tight relationship seen in figure~\ref{fig:grain-T-vs-U} between
\(T\) and \(U\) is evidence for the dominance of stellar radiative
heating (see \S~\ref{sec:unimp-other-heat} below), while the variation
about the mean relation is mainly due to differences in grain size and
composition, with smaller grains and graphite grains being relatively
hotter.  The downward hooks seen on the left end of each simulation's
individual curve are due to the fact that our calculation of \(U\)
does not account for internal absorption, which starts to become
important near the ionization front.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/grain-j70-vs-U-edited}
  \caption{Grain emissivity at \SI{70}{\um} for all Cloudy models
    (lines colored as in Fig.~\ref{fig:drift-gn}), compared with grain
    models from \citet{Draine:2007a} (dark gray symbols), which assume
    illumination by a scaled interstellar radiation field, which has a
    SED with a very different shape from that of an OB star, see
    Fig.~\ref{fig:sed-comparison}.  }
  \label{fig:grain-j70}
\end{figure}

The grain emissivity at \SI{70}{\um} (Herschel PACS blue band) for the
Cloudy simulations (colored lines) is shown in
Figure~\ref{fig:grain-j70}, where it is compared with the same
quantity from the grain models (dark gray symbols) of
\citet{Draine:2007a}.  A clear difference is seen between the two sets
of models, but this is due almost entirely to a difference in the
assumed spectrum of the illuminating radiation, as illustrated in
Figure~\ref{fig:sed-comparison}.  \citet{Draine:2007a} use a SED that
is typical of the interstellar radiation field in the Galaxy, which is
dominated by an old stellar population, which peaks in the near
infrared, with only a small FUV contribution from younger stars (about
8\% of the total energy density).  This is very different from the OB
star SEDs, which are dominated by the FUV and EUV bands.  Since the
grain absorption opacity is much higher at UV wavelengths than in the
visible/IR (see Fig.~\ref{fig:cloudy-ism-dust-opacity}), the effective
grain heating efficiency of the OB star SED is correspondingly higher.
The light gray symbols show the effect on the \citet{Draine:2007a}
models of multiplying the radiation field by a factor of \num{8} in
order to offset this difference in efficiency, which can be seen to
bring them into close agreement with the Cloudy models.  A further
difference is that the \citet{Draine:2007a} model includes small PAH
particles, which we do not include in our Cloudy models, since they
are believed to be largely absent in photoionized regions
\citep{Giard:1994a, Lebouteiller:2011a}.  However, this only effects
the emissivity at shorter mid-infrared wavelengths \(< \SI{20}{\um}\).

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sed-comparison}
  \caption{Comparison between the spectral energy distribution (SED)
    of a typical OB star (blue line) and the interstellar radiation
    field in the solar neighborhood (orange line).  The OB star is the
    \SI{20}{M_\odot} model from Table~\ref{tab:stars} and is plotted for a
    distance from the star of \SI{1}{pc}.  The interstellar SED is
    from \citet{Mathis:1983a} and is multiplied by \num{80} so that
    the total FUV-to-NIR flux is equal for the two SEDs.}
  \label{fig:sed-comparison}
\end{figure}

In terms of the characteristic parameters introduced in
\S~\ref{sec:depend-stell-type} the dimensionless radiation field becomes
\begin{equation}
  \label{eq:U-from-L4-and-Rpc}
  U = 14.7\, L_4\, R_{\text{pc}}^{-2} \ ,
\end{equation}
or, alternatively, it can be expressed in terms of the ambient stream as
\begin{equation}
  \label{eq:U-from-ambient}
  U = 3.01 \, n \, v_{10}^2 / x^2 \ , 
\end{equation}
where \(x = R_0/R_*\) is given by equation~\eqref{eq:x-cases}.  It can
also be related to the radiation parameter \(\Xi\), defined in
equation~\eqref{eq:Xi-Prad-over-Pgas}, as
\begin{equation}
  \label{eq:U-vs-Xi}
  U = 3.82 \, n T_4 \, \Xi \ .
\end{equation}
A common alternative approach to scaling the radiation field (see
\citealp{Tielens:1985a} and citations thereof) is to normalize in the
FUV band (\SIrange{0.0912}{0.24}{\um}), where the local interstellar
value is known as the Habing flux \citep{Habing:1968a}:
\begin{equation}
  \label{eq:Habing-flux}
  F\Hab = \SI{0.0016}{erg.s^{-1}.cm^{-2}} \ .
\end{equation}
The resultant dimensionless flux is often denoted by \(G_0\), and the
relationship between \(G_0\) and \(U\) depends on the fraction
\(f_{\text{fuv}}\) of the stellar luminosity that is emitted in the
FUV band:
\begin{equation}
  \label{eq:G-vs-U}
  G_0 = f_{\text{fuv}} \frac{u\mmp\, c}{F\Hab} \,U = (\text{\numrange{6}{10}}) \,U \ ,
\end{equation}
where we give the range corresponding to early O (\(f_{\text{fuv}} \approx 0.4\)) to early B (\(f_{\text{fuv}} \approx 0.7\)) stars.

%% Single-photon heating of small grains

\subsection{Unimportance of other heating mechanisms}
\label{sec:unimp-other-heat}
The grain temperature in bows around OB stars is determined
principally by the steady-state equilibrium between the absorption of
stellar UV radiation (heating) and the thermal emission of infrared
radiation (cooling).  Other processes such as single-photon stochastic
heating, Lyman~\(\alpha\) line radiation, and post-shock collisional
heating can dominate in other contexts, but these are generally
unimportant for circumstellar bows, as we now demonstrate.

\subsubsection{Stochastic single-photon heating}

When the radiation field is sufficiently dilute, then a grain that
absorbs a photon has sufficient time to radiate all that energy away
before it absorbs another photon \citep{Duley:1973a}.  In this case,
the emitted infrared spectrum for \(\lambda < \SI{50}{\um}\) becomes
relatively insensitive of the energy density of the incident radiation
\citep{Draine:2001a}.  However, this is most important for the very
smallest grains.  From equation~(47) of \citet{Draine:2001a}, one
finds that grains with sizes larger than
\(a = \SI{0.005}{\um} = \SI{5}{nm}\) (the smallest size included in
our Cloudy models) should be close to thermal equilibrium for
\(U > 30\), which is small compared with typical bow shock values
(\(U = \text{\numrange{e3}{e6}}\)).  As mentioned above, PAHs are not
expected to be present in the interior of \hii{} regions.
\citealp{Desert:1990a} found them to be strongly depleted for
\(U > 100\) around O stars.  However, other types of ultra-small
grains, down to sub-nm sizes \citep{Xie:2018a} may be present in bows,
and stochastic heating \emph{would} be important for grains with
\(a = \SI{1}{nm}\) if \(U < \num{e5}\).  Note, however that grains
smaller than \SI{0.6}{nm} would be destroyed by sublimation after
absorbing a single He-ionizing photon.

\subsubsection{Lyman \(\alpha\) heating}

On the scale of an entire \hii{} region, the dust heating is typically
dominated by Lyman \(\alpha\) hydrogen recombination line photons, which
are trapped by resonant scattering (e.g., \citealp{Spitzer:1978a}
\S~9.1b).  However, this is no longer true on the much smaller scale
of typical bow shocks.  An upper limit on the Lyman \(\alpha\) energy
density can be found by assuming all line photons are ultimately
destroyed by dust absorption rather than escaping in the line wings
(e.g., \citealp{Henney:1998b}), which yields
\begin{equation}
  \label{eq:U-Lya}
  U\Lya \approx 0.1 n / \kappa_{600} \ .
\end{equation}
This can be combined with equation~\eqref{eq:U-from-ambient} to give
the ratio of Lyman \(\alpha\) to direct stellar radiation as
\begin{equation}
  \label{eq:Lya-over-stellar}
  \frac{U\Lya}{U} \approx 0.03 \frac{x^2}{v_{10}^2 \kappa_{600}} \ .
\end{equation}
Taking the most favorable parameters imaginable of a slow stream
(\(v_{10} = 2\)), very strong wind (\(x \approx 1\)), and reduced dust
opacity (\(\kappa_{600} = 0.1\)) gives a Lyman \(\alpha\) contribution of only
10\% of the stellar radiative energy density.  In any other
circumstances, the fraction would be even lower.

\subsubsection{Shock heating}
\newcommand\kin{\ensuremath{_{\text{kin}}}}
The outer shock thermalizes the kinetic energy of the ambient stream,
which may in principle contribute to the infrared emission of the bow.
In order for this process to be competitive, the following three
conditions must all hold:
\begin{enumerate}[1.]
\item The post-shock gas must radiate efficiently with a cooling
  length less than the bow size, see \S~\ref{sec:radi-cool-lengths}.
  This is satisfied for all but the lowest densities (see
  Fig.~\ref{fig:zones-v-n-plane}).
\item A significant fraction of the shock energy must be radiated by
  dust.  This requires that the post-shock temperature be greater than
  \SI{e6}{K}, which requires a stream velocity
  \(v > \SI{200}{km.s^{-1}}\) \citep{Draine:1981a}.  This also
  coincides with the range of shock velocities where the smaller
  grains will start to be destroyed by sputtering in the post-shock
  gas.
\item The kinetic energy flux through the shock must be significant,
  compared with the fraction of the stellar radiation flux that is
  absorbed and reprocessed by the bow shell.
\end{enumerate}
It turns out that the third condition is the most stringent, so we
will consider it in detail.  The kinetic energy flux through the outer shock for an ambient stream of density \(\rho\) and velocity \(v\) is
\begin{equation}
  \label{eq:Fkin}
  F\ke = \tfrac12 \rho v^3 = \tfrac12 P\shell v \ , 
\end{equation}
while the stellar radiative energy flux absorbed by the shell is
\begin{equation}
  \label{eq:Ftrap}
  F\trap \approx \tau L / 4 \pi R_0^2 \ ,
\end{equation}
assuming an absorption optical depth \(\tau \ll 1\). The shell
pressure in the WBS case can be equated to the ram pressure of the
internal stellar wind (see \S~\ref{sec:three-bow-regimes}), so that
the ratio of the two energy fluxes is
\begin{equation}
  \label{eq:F-ratio-shock}
  \frac{F\ke}{F\trap} = \frac12 \frac{\eta\wind}{\tau} \frac{v}{c} \ .
\end{equation}
An upper limit to the stellar wind momentum efficiency \(\eta\wind\)
is the shell momentum efficiency \(\eta\shell\) that is derived
observationally in \S~\ref{sec:summary-discussion}, where it is found
that \(\eta\shell / \tau < 30\) for all sources considered.  Therefore,
for a stream velocity \(v = \SI{200}{km.s^{-1}}\), we have
\(F\ke/F\trap < 0.01\) and the shock-excited dust emission is still
negligible.  Only in stars with \(v > \SI{1000}{km.s^{-1}}\) would the
shock emission start to be significant, and such hyper-velocity stars
\citep{Brown:2015a} do not show detectable bow shocks.

So far, we have only considered the outer shock, but the inner shock
that decelerates the stellar wind will have a velocity of
\SIrange{1000}{3000}{km.s^{-1}} and therefore might have a
significant kinetic energy flux by eq.~\eqref{eq:F-ratio-shock}.
However, the stellar wind from hot stars will be free of
dust,\footnote{%
  With the exception of Wolf-Rayet colliding wind binary systems
  \citep{Tuthill:1999a, Callingham:2019a}.} %
so that it would be necessary for the stellar wind protons to cross
the contact/tangential discontinuity and deposit their energy in the
dusty plasma of the shocked ambient stream.  This is not possible
because the Larmor radius (see \S~\ref{sec:magn-effects-grain}) of a
\SI{3000}{km.s^{-1}} proton in a \SI{1}{\micro G} field is only
\SI{3e10}{cm}, which is millions of times smaller than typical bow
sizes.  The magnetic field in the outer shell is unlikely to be
smaller than \(\approx n^{1/2} \si{\micro G}\), given that Alfvén
speeds of \SI{2}{km.s^{-1}} are typical of photoionized regions
(cf.~eq.~[\ref{eq:alfven}]) and if the density were much lower than
\SI{1}{cm^{-3}}, then the scale of the bow would be commensurately
larger anyway.  Three-dimensional MHD simulations of bow shocks
\citep{Katushkina:2017a, Gvaramadze:2018a} show that the magnetic
field lines are always oriented parallel to the shell, so that high
energy particles from the stellar wind would be efficiently reflected
in a very thin layer and cannot contribute to grain heating.  For the
same reason, heat conduction by electrons across the contact
discontinuity is also greatly suppressed \citep{Meyer:2017a}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "bs-bw-dw-03"
%%% End:

### 2019-02-26 papers/Papers1234/bs-bw-dw-01.tex
Divide dust wave paper in three parts

--- 2019-01-15 papers/Papers1234/dusty-bow-wave.tex
@@
 \usepackage{hyperref}
-\externaldocument[Q-]{quadrics-bowshock}
 
@@
 \activatechemgreekmapping{newtx}
+\usepackage{listings}
 
@@
 \title
-{Bow shocks, bow waves, and dust waves}
+{Bow shocks, bow waves, and dust waves. I. Strong coupling limit}
 
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2017}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\Sin}{\mathcal{S}}
-\DeclareMathOperator{\Cos}{\mathcal{C}}
-\DeclareMathOperator{\Cot}{\mathcal{T}}
-\DeclareMathOperator{\GammaFunc}{\Gamma}
-\newcommand\w{\ensuremath{\mathrm{w}}}
-\newcommand\C{\ensuremath{\mathrm{c}}}
-\providecommand{\abs}[1]{\lvert#1\rvert}
-\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
-\newcommand\TODO[1]{%
-  \begin{center}
-    \framebox{\parbox{0.8\linewidth}{
-        \texttt{\footnotesize\color{red} #1}}}
-  \end{center}}
+\pubyear{2019}
 
-\newcommand\uvec[1]{\bm{\hat{#1}}}
-\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+\input{bs-bw-dw-defs.tex}
 
-\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
-\newcommand{\grain}{\ensuremath{_{\text{d}}}}
-\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
-\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
-\newcommand{\xsec}{\ensuremath{\sigma\grain}}
-\newcommand\frad{\ensuremath{f_{\text{rad}}}}
-\newcommand\fmax{\ensuremath{f_{\text{max}}}}
-\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
-\newcommand\drag{\ensuremath{_{\text{drag}}}}
-\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
-\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
-\newcommand\rad{\ensuremath{_{\text{rad}}}}
-\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
-% Why do I need both of these?
-\newcommand\sound{\ensuremath{c_{\text{s}}}}
-\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
-\newcommand\starstar{\ensuremath{_{**}}}
+% \externaldocument[Q-]{quadrics-bowshock}
+% \externaldocument[II-]{bs-bw-dw-02}
+% \externaldocument[III-]{bs-bw-dw-03}
 
@@
   optically thin bow waves around B~stars, or optically thick bow
-  shocks around early O~stars.  The radiation field is sufficiently
-  strong to overcome the collisional coupling between grains and gas
-  at a \textit{rip-point}, where the ratio of radiation pressure to
-  gas pressure exceeds a critical value of roughly 1000.  When the rip
-  point occurs outside the hydrodynamic bow shock, a separate dust
-  wave may form, decoupled from the gas shell, which can either be
-  drag-confined or inertia-confined, depending on the stream density
-  and relative velocity.  In the drag-confined case, there is a
-  minimum stream velocity of roughly \SI{60}{km.s^{-1}} that allows a
-  steady-state stagnant drift solution for the dust wave apex.  For
-  lower relative velocities, the dust dynamics close to the axis
-  exhibit a limit cycle behavior (rip and snap back) between two
-  different radii.  Strong coupling of charged grains to the plasma's
-  magnetic field can modify these effects, but for a quasi-parallel
-  field orientation the results are qualitatively similar. For a
-  quasi-perpendicular field, on the other hand, the formation of a
-  decoupled dust wave is strongly suppressed.
+  shocks around early O~stars.  
 \end{abstract}
@@
 \input{sec-dust-bow-intro}
-\input{sec-dust-bow-discuss}
+\input{sec-strong-coupling}
 \bibliographystyle{mnras}
 \bibliography{bowshocks-biblio}
-\appendix
-\input{app-cloudy-dust-charging}
-\input{app-dust-wave}
-\input{app-dust-equations}
-%\input{app-dust-ifront-trap}
 

### 2019-02-26 papers/Papers1234/bs-bw-dw-02.tex
Divide dust wave paper in three parts

--- 2019-01-15 papers/Papers1234/dusty-bow-wave.tex
@@
 \title
-{Bow shocks, bow waves, and dust waves}
+{Bow shocks, bow waves, and dust waves. II. Beyond the rip point}
 
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2017}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\Sin}{\mathcal{S}}
-\DeclareMathOperator{\Cos}{\mathcal{C}}
-\DeclareMathOperator{\Cot}{\mathcal{T}}
-\DeclareMathOperator{\GammaFunc}{\Gamma}
-\newcommand\w{\ensuremath{\mathrm{w}}}
-\newcommand\C{\ensuremath{\mathrm{c}}}
-\providecommand{\abs}[1]{\lvert#1\rvert}
-\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
-\newcommand\TODO[1]{%
-  \begin{center}
-    \framebox{\parbox{0.8\linewidth}{
-        \texttt{\footnotesize\color{red} #1}}}
-  \end{center}}
+\pubyear{2019}
 
-\newcommand\uvec[1]{\bm{\hat{#1}}}
-\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+\input{bs-bw-dw-defs.tex}
 
-\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
-\newcommand{\grain}{\ensuremath{_{\text{d}}}}
-\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
-\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
-\newcommand{\xsec}{\ensuremath{\sigma\grain}}
-\newcommand\frad{\ensuremath{f_{\text{rad}}}}
-\newcommand\fmax{\ensuremath{f_{\text{max}}}}
-\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
-\newcommand\drag{\ensuremath{_{\text{drag}}}}
-\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
-\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
-\newcommand\rad{\ensuremath{_{\text{rad}}}}
-\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
-% Why do I need both of these?
-\newcommand\sound{\ensuremath{c_{\text{s}}}}
-\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
-\newcommand\starstar{\ensuremath{_{**}}}
+\externaldocument[Q-]{quadrics-bowshock}
+%\externaldocument[I-]{bs-bw-dw-01}
+%\externaldocument[III-]{bs-bw-dw-03}
 
@@
 \begin{abstract}
-  Dust waves and bow waves result from the action of a star's
-  radiation pressure on a stream of dusty plasma that flows past it.
-  They are an alternative mechanism to hydrodynamic bow shocks for
-  explaining the curved arcs of infrared emission seen around some
-  stars.  When gas and grains are perfectly coupled, for a broad class
-  of stellar parameters, wind-supported bow shocks predominate when
-  the ambient density is below \SIrange{100}{1000}{cm^{-3}}.  At
-  higher densities radiation-supported bows can form, tending to be
-  optically thin bow waves around B~stars, or optically thick bow
-  shocks around early O~stars.  The radiation field is sufficiently
-  strong to overcome the collisional coupling between grains and gas
-  at a \textit{rip-point}, where the ratio of radiation pressure to
-  gas pressure exceeds a critical value of roughly 1000.  When the rip
-  point occurs outside the hydrodynamic bow shock, a separate dust
-  wave may form, decoupled from the gas shell, which can either be
-  drag-confined or inertia-confined, depending on the stream density
-  and relative velocity.  In the drag-confined case, there is a
-  minimum stream velocity of roughly \SI{60}{km.s^{-1}} that allows a
-  steady-state stagnant drift solution for the dust wave apex.  For
+  Dust waves are a result of gas--grain decoupling in a stream of
+  dusty plasma that flows past a luminous star.  The radiation field
+  is sufficiently strong to overcome the collisional coupling between
+  grains and gas at a \textit{rip-point}, where the ratio of radiation
+  pressure to gas pressure exceeds a critical value of roughly 1000.
+  When the rip point occurs outside the hydrodynamic bow shock, a
+  separate dust wave may form, decoupled from the gas shell, which can
+  either be drag-confined or inertia-confined, depending on the stream
+  density and relative velocity.  In the drag-confined case, there is
+  a minimum stream velocity of roughly \SI{60}{km.s^{-1}} that allows
+  a steady-state stagnant drift solution for the dust wave apex.  For
   lower relative velocities, the dust dynamics close to the axis
@@
   magnetic field can modify these effects, but for a quasi-parallel
-  field orientation the results are qualitatively similar. For a
-  quasi-perpendicular field, on the other hand, the formation of a
-  decoupled dust wave is strongly suppressed.
+  field orientation the results are qualitatively similar to the
+  non-magnetic case. For a quasi-perpendicular field, on the other
+  hand, the formation of a decoupled dust wave is strongly suppressed.
 \end{abstract}
@@
 
-\input{sec-dust-bow-intro}
-\input{sec-dust-bow-discuss}
+\input{sec-weak-coupling}
 \bibliographystyle{mnras}
@@
 \input{app-dust-equations}
-%\input{app-dust-ifront-trap}
 

### 2019-02-26 papers/Papers1234/sec-dust-bow-intro.tex
Divide dust wave paper in three parts

--- 2019-01-30 papers/Papers1234/sec-dust-bow-intro.tex
@@
 \label{sec:introduction}
-\newcommand\hii{\ion{H}{ii}}
 
@@
 cases may be a radiation-pressure driven bow wave, as first proposed
-by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario, photons
-emitted by the star are absorbed by dust grains in the incoming
-stream, with the resultant momentum transfer being sufficient to
-decelerate and deflect the grains within a certain distance from the
-star, forming a dust-free, bow-shaped cavity with an enhanced dust
-density at its edge.
+by \citet[\S\textsc{vi}]{van-Buren:1988a}.  In this scenario (see
+Fig.~\ref{fig:3-types-bow}), photons emitted by the star are absorbed
+by dust grains in the incoming stream, with the resultant momentum
+transfer being sufficient to decelerate and deflect the grains within
+a certain distance from the star, forming a dust-free, bow-shaped
+cavity with an enhanced dust density at its edge.
 
@@
   \includegraphics[width=0.8\linewidth]{figs/bows-and-waves}
-  \caption{Bow shocks, bow waves, and dust waves}
+  \caption{Regimes in the supersonic interaction of a luminous star
+    with its environment.  When radiation effects are unimportant, we
+    have the standard (magneto-)hydrodynamical wind-supported bow
+    shock (upper left), where the ram pressure of the stellar wind
+    balances the ram pressure of the oncoming stream.  As the optical
+    depth of the shocked shell increases, the stellar radiation
+    momentum adds to the wind ram pressure to help support the bow.
+    If the shell is completely opaque to stellar radiation, we have a
+    radiation-supported bow shock (lower right), where it is the
+    stellar radiation pressure that balances the ram pressure of the
+    external stream.  For intermediate optical depths, we have two
+    cases depending on the strength of coupling between grains and
+    gas.  If the coupling is strong, then we have a
+    radiation-supported bow wave (upper right), where the plasma
+    stream as a whole is gradually radiatively decelerated as it
+    approaches the star.  If the coupling is weak, then the radiation
+    momentum is felt only by the dust, which decouples from the gas to
+    form a dust wave, with the gas stream continuing inward to form a
+    wind-supported bow shock closer to the star.  Note that the
+    gas--grain coupling is both direct (via collisions) and indirect
+    (via the magnetic field) (see Paper~II).}
   \label{fig:3-types-bow}
@@
 
-In this paper, we develop simple physical models to show in detail
-when and how these different interaction regimes apply when varying
-the parameters of the star, the dust grains, and the ambient stream.
-We concentrate primarily on the case of luminous early type stars,
-where dust is present only in the ambient stream, and not in the
-stellar wind.
+This is the first in a series of papers where we develop simple
+physical models to show in detail when and how these different
+interaction regimes apply when varying the parameters of the star, the
+dust grains, and the ambient stream.  We concentrate primarily on the
+case of luminous early type stars, where dust is present only in the
+ambient stream, and not in the stellar wind.  In this first paper, we
+consider the case where the grains are perfectly coupled to the gas
+via collisions.  The following two papers consider the decoupling of
+grains and gas in a sufficiently strong radiation field
+\citep[Paper~II]{Henney:2019b}, and how observations can distinguish
+between different classes of bow \citep[Paper~III]{Henney:2019c}.
 %
@@
 %
-In \S~\ref{sec:strong-gas-grain} we consider the case where the grains
-are perfectly coupled to the gas via collisions, investigating the
-relative importance of wind and radiation in providing internal
-support for the bow shell as a function of the density and velocity of
-the ambient stream, as well as calculating the shell's ionization
-state and radiative cooling efficiency.
-%
-In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
-charging and dynamics, subject to radiation and drag forces, in order
-to determine the rip point where gas--grain coupling catastrophically
-breaks down.  This is used to determine existence conditions for the
-presence of a decoupled dust wave.
-%
-In \S~\ref{sec:magn-effects-grain} we consider the additional coupling
-between the grains and the plasma's magnetic field, and how this
-effects the existence and structure of dust waves.
+In \S~\ref{sec:strong-gas-grain} we propose a simple model for stellar
+bows and investigate the relative importance of wind and radiation in
+providing internal support for the bow shell as a function of the
+density and velocity of the ambient stream, and for different types of
+star.  In \S~\ref{sec:phys-state-shock} we calculate the physical
+state of the bow shell, considering under what circumstances it can
+trap within itself the star's ionization front and how efficient
+radiative cooling will be.
 %
@@
 %
-A series of appendices provide additional technical information on
-dust physics (Appendix~\ref{sec:cloudy-models-dust}), analytical
-models of the shape of dust waves in the drag-free limit
-(Appendix~\ref{sec:gas-free-bow}), and the numerical calculation of
-grain trajectories (Appendix~\ref{sec:equat-moti-grains}).
 
@@
 
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
-  \caption{Bow regimes in parameter space (\(v, n\)) of the external
-    stream for main-sequence OB stars of different masses:
-    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}.  In all
-    cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
-    coupling is assumed. Solid black lines of varying width show the
-    bow size (star-apex separation, \(R_0\)), while gray shading shows
-    the radiation bow wave regime, with lower border \(\tau = \eta\) and
-    upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
-    depth through the bow.  For bows above the red solid line, the
-    ionization front is trapped inside the bow.  Blue lines delineate
-    different cooling regimes.  Above the thin blue line
-    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
-    forming a thin shocked shell.  Below the thick blue line
-    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
-    non-radiative.}
-  \label{fig:zones-v-n-plane}
-\end{figure*}
-
-\section{Strong gas-grain coupling}
-\label{sec:strong-gas-grain}
-
-We consider the canonical case of a bow around a star of bolometric
-luminosity, \(L\), with a radiatively driven wind, which is immersed
-in an external stream of gas and dust with density, \(\rho\), and
-velocity, \(v\).  The size and shape of the bow is determined by a
-generalized balance of pressure (or, equivalently, momentum) between
-internal and external sources.  We assume that the stream is
-supersonic and super-alfvenic, so that the external pressure is
-dominated by the ram pressure: \(\rho v^2\).  We first consider the case
-where the dust grains and gas are perfectly coupled by collisions.
-
-Although dust grains typically constitute only a small fraction
-\(Z\grain \sim 0.01\) of the mass of the external stream, they
-nevertheless dominate the broad-band opacity at FUV, optical and IR
-wavelengths if they are present.\footnote{%
-  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
-  dominates if the hydrogen neutral fraction is larger than
-  \(\approx 0.001\), see discussion of ionization front trapping
-  below.} %
-The strong coupling assumption means that all the radiative forces
-applied to the dust grains are directly felt by the gas also.
-
-\subsection{Bows supported by radiation and wind}
-\label{sec:three-bow-regimes}
-
-The internal pressure is the sum of wind ram pressure and the
-effective radiation pressure that acts on the bow shell.  The
-radiative momentum loss rate of the star is \(L/c\) and the wind
-momentum loss rate can be expressed as
-\begin{equation}
-  \label{eq:wind-efficiency}
-  \dot{M} V = \eta L / c \ , 
-\end{equation}
-where \(\eta\) is the momentum efficiency of the wind, which is typically
-\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
-all of the stellar radiative momentum, emitted with rate \(L/c\), is
-trapped by the bow shell.  In the single scattering limit,\footnote{%
-  Although it may seem inconsistent to assume single scattering in the
-  case of high optical depths, this is defensible for the following
-  reasons. (1)~The grain albedo is not that high (typically
-  \(\sim 0.5\) at ultraviolet through optical wavelengths). (2)~The
-  scattered radiation field is more isotropic than the stellar field,
-  leading to cancellation in the radiative flux. (3)~Absorbed
-  radiation is re-emitted at infrared wavelengths, where the dust
-  opacity is very much lower.} %
-and temporarily neglecting the wind for clarity of exposition, then
-pressure balance at the bow apex, a distance \(R_0\) along the
-symmetry axis from the star is given by
-\begin{equation}
-  \label{eq:rad-press-balance-thick}
-  \frac{L}{4 \pi c R_0^2} = \rho v^2 \ ,
-\end{equation}
-which yields a fiducial bow shock radius in this optically thick,
-radiation-only limit as
-\begin{equation}
-  \label{eq:Rstar}
-  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
-\end{equation}
-
-We now consider the opposite, optically thin limit.  If the total
-opacity (gas plus dust) per total mass (gas plus dust) is \(\kappa\) (with
-units of \si{cm^2.g^{-1}}), then the radiative acceleration is
-\begin{equation}
-  \label{eq:rad-accel}
-  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ .
-\end{equation}
-Therefore, an incoming stream with initial velocity, \(v_\infty\), can be
-brought to rest by radiation alone
-% \footnote{%
-%   For simplicity, we here ignore the effects of gravity, which are
-%   important for low ratios of \(\kappa L / M\), see
-%   \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
-%   shocks, which are important as the velocity approaches the sound
-%   speed, \(\sound\) (in \S~XX below, we show that the resultant
-%   corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
-at a distance \(R\starstar\) where
-\begin{equation}
-  \label{eq:rad-poten}
-  \int_{R\starstar}^\infty a_{\text{rad}} \, dr = \tfrac12 v_\infty^2 \ , 
-\end{equation}
-yielding
-\begin{equation}
-  \label{eq:rad:R0}
-  R\starstar = \frac{\kappa L}{2\pi c v_\infty^2} \ .
-\end{equation}
-On the other hand, we can also argue as in the optically thick case
-above by approximating the bow shell as a surface, and balancing
-stellar radiation pressure against the ram pressure of the incoming
-stream.  The important difference when the shell is not optically
-thick is that only a fraction \(1 - e^{-\tau}\) of the radiative momentum
-is absorbed by the bow, so that
-equation~\eqref{eq:rad-press-balance-thick} is replaced with
-\begin{equation}
-  \label{eq:rad-press-balance-tau}
-  \frac{L (1 - e^{-\tau})}{4 \pi c R_0^2} = \rho v^2 \ .
-\end{equation}
-In the optically thin limit, \(1 - e^{-\tau} \approx \tau\), so these two
-descriptions can be seen to agree (\(R_0 \to R\starstar\)) so long as
-\begin{equation}
-  \label{eq:tau-thin}
-  \tau = 2 \kappa \rho R_0 \ ,
-\end{equation}
-which we will assume to hold generally.
-
-Then, defining a fiducial optical depth,
-\begin{equation}
-  \label{eq:tau-star}
-  \tau_* = \rho \kappa R_* \ ,
-\end{equation}
-and now reinstating the stellar wind ram pressure term
-% \footnote{%
-%   We implicitly assume that the interaction of the stellar wind with
-%   the external stream can always be treated in the continuum limit.
-%   This will be true if either the collisional mean free path or the
-%   ion Larmor radius is much smaller than \(R_0\), which is almost
-%   always the case.} %
-from equation~\eqref{eq:wind-efficiency}, we find that the general bow
-radius can be written in terms of the fiducial radius as
-\begin{equation}
-  \label{eq:R0-definition}
-  R_0 = x R_* \ ,
-\end{equation}
-where \(x\) is the solution of
-\begin{equation}
-  \label{eq:rad-full-x}
-  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta = 0 \ .
-\end{equation}
-Since this is a transcendental equation, \(x\) must be found
-numerically, but we can write explicit expressions for three limiting
-cases:
-\begin{equation}
-  \label{eq:x-cases}
-  x \approx
-  \begin{cases}
-    \text{if \(\tau_* \gg 1\):} & (1 + \eta)^{1/2}  \\
-    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta \bigr)^{1/2} \approx
-    \begin{cases}
-      \text{if \(\tau_*^2 \gg \eta\):} & 2 \tau_*  \\
-      \text{if \(\tau_*^2 \ll \eta\):} & \eta^{1/2} 
-    \end{cases}
-  \end{cases}
-\end{equation}
-The first case, \(x \approx (1 + \eta)^{1/2}\), corresponds to a
-\textit{radiation bow shock} (RBS); the second case,
-\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave} (RBW);
-and the third case, \(x \approx \eta^{1/2}\), corresponds to a \textit{wind bow
-  shock} (WBS).  The two bow shock cases are similar in that the
-external stream is oblivious to the presence of the star until it
-suddenly hits the bow shock shell, differing only in whether it is
-radiation or wind that is providing the internal pressure.  In the
-intermediate bow wave case, on the other hand, the external stream is
-gradually decelerated by absorption of photons as it approaches the
-bow.\footnote{A shock can still form in this case, but shocked
-  material constitutes only a small fraction of the total column
-  density of the shell.}
-
-\subsection{Dependence on stellar type}
-\label{sec:depend-stell-type}
-
-\begin{table*}
-  \centering
-  \caption{Stellar parameters for example stars}
-  \label{tab:stars}
-  \begin{tabular}{l S S S S S S S S S l}
-    \toprule
-    & {\(M / \si{M_\odot}\)} & {\(L_4\)}
-    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta \)}
-    & {Sp.~Type} 
-    & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
-    & {\(S_{49}\)} & Figures 
-    \\
-    \midrule
-    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
-                   & \ref{fig:zones-v-n-plane}a,
-                     \ref{fig:decouple-v-n-plane},
-                     \ref{fig:decouple-v40-versus-n} \\
-    Main-sequence OB stars
-    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
-                   & \ref{fig:zones-v-n-plane}b\\
-    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
-                   & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
-    Blue supergiant star
-    & 33 & 30.2 & 20.2 & 0.93 & 0.3079 & {B0.7\,Ia} & 23.5 & 0.123 & 0.016
-                   & \ref{fig:B-supergiant} \\[\smallskipamount]
-    Red supergiant star
-    & 20 & 15.6 & 100 & 0.015 & 0.0476 & {M1\,Ia} & 3.6 & 0.805 & 0
-                   & \ref{fig:M-supergiant} \\ 
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-We now consider the application to bow shocks around main sequence OB
-stars, as well as cool and hot supergiants, expressing stellar and
-ambient parameters in terms of typical values as follows:
-\begin{align*}
-  \label{eq:stellar-parameters}
-  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
-  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
-  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
-  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
-  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
-  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
-\end{align*}
-where \(\bar{m}\) is the mean mass per hydrogen nucleon
-(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
-abundances).  Note that \(\kappa = \SI{600}{cm^2.g^{-1}}\) corresponds to a
-cross section of \(\approx \SI{e-21}{cm^2}\) per hydrogen nucleon, which is
-typical for interstellar medium dust \citep{Bertoldi:1996a} at far
-ultraviolet wavelengths, where OB stars emit most of their radiation.
-In terms of these parameters, we can express the stellar wind momentum
-efficiency as
-\begin{equation}
-  \label{eq:wind-eta-typical}
-  \eta = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
-\end{equation}
-and the fiducial radius and optical depth as
-\begin{align}
-  \label{eq:Rstar-typical}
-  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
-  \label{eq:taustar-typical}
-  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
-\end{align}
-In Figure~\ref{fig:zones-v-n-plane}, we show results for the bow size
-(apex distance, \(R_0\)) as a function of the density, \(n\), and
-relative velocity, \(v_\infty\), of the external stream, with each panel
-corresponding to a particular star, with parameters as shown in
-Table~\ref{tab:stars}.  To facilitate comparison with previous work,
-we choose stellar parameters similar to those used in the
-hydrodynamical simulations of \citet{Meyer:2014b, Meyer:2016a,
-  Meyer:2017a}, based on stellar evolution tracks for stars of
-\SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and theoretical wind
-prescriptions \citep{de-Jager:1988a, Vink:2000a}.  Although the
-stellar parameters do evolve with time, they change relatively little
-during the main-sequence lifetime of several million years.\footnote{%
-  \label{fn:meyer-velocities-too-low}
-  Note that we have recalculated the stellar wind terminal velocities,
-  since the values given in the \citeauthor{Meyer:2014b} papers are
-  troublingly low.  We have used the prescription
-  \(V = 2.6 V_{\text{esc}}\), where
-  \(V_{\text{esc}} = \left( 2 G M (1 - \Gamma_e)/ R \right)^{1/2}\) is the
-  photospheric escape velocity, which is appropriate for strong
-  line-driven winds with \(T_{\text{eff}} > \SI{21 000}{K}\)
-  \citep{Lamers:1995a}.  We find velocities of
-  \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
-  observations and theory \citep{Vink:1999a} for O~stars, but at least
-  two times higher than those cited by \citet{Meyer:2014b}. For
-  main-sequence B~stars, wind column densities are too low to reliably
-  measure the terminal velocity from near ultraviolet P~Cygni profiles
-  \citep{Prinja:1989a}, and so the values are theory-dependent
-  \citep{Krticka:2014a} and hence more uncertain.  A further
-  complication is the existence of a subset of OB stars with
-  anomalously weak winds \citep{Puls:2008a}, which in some cases is
-  related to the presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
-  \citep{Oskinova:2011b}.} %
-The three examples are an early B~star (\SI{10}{M_\odot}), a late O~star
-(\SI{20}{M_\odot}), and an early O~star (\SI{40}{M_\odot}), which cover the
-range of luminosities and wind strengths expected from bow-producing
-hot main sequence stars.  The luminosity is a steep function of
-stellar mass (\(L \sim M^{2.5}\)) and the wind mass-loss rate is a steep
-function of luminosity (\(\dot{M} \sim L^{2.2}\)), which means that the
-wind momentum efficiency is also a steep function of mass
-(\(\eta \sim M^3\)), approaching unity for early O~stars, but falling to
-less than 1\% for B~stars.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-RSG}
-  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for a cool M-type
-    supergiant instead of hot main sequence stars.  A smaller dust
-    opacity is used, \(\kappa = \SI{60}{cm^2.g^{-1}}\), because of the
-    reduced extinction efficiency at the optical/infrared wavelengths
-    emitted by this star.}
-  \label{fig:M-supergiant}
-\end{figure}
-
-It can be seen from Figure~\ref{fig:zones-v-n-plane} that the onset of
-the radiation bow wave regime is very similar for the three
-main-sequence stars, occurring at
-\(n > \text{\numrange{20}{40}} \, v_{10}^2\).  An important
-difference, however, is that for the \SI{40}{M_\odot} star, which has a
-powerful wind, the radiation bow wave regime only occurs for a very
-narrow range of densities, whereas for the \SI{10}{M_\odot} star, with a
-much weaker wind, the regime is much broader, extending to
-\(n < \num{e4} \, v_{10}^2\).  Another difference is the size scale of
-the bows in this regime, which is
-\(R_0 = \text{\SIrange{0.001}{0.003}{pc}}\) for the \SI{10}{M_\odot} star
-if \(v_\infty = \SI{40}{km.s^{-1}}\), but \(R_0 \approx \SI{0.1}{pc}\) for the
-\SI{40}{M_\odot} star, assuming the same inflow velocity.
-
-Figure~\ref{fig:M-supergiant} shows results for a cool M-type
-super-giant star with stellar parameters inspired by Betelgeuse
-(\chemalpha~Orionis), as listed in Table~\ref{tab:stars}.  Unlike the
-UV-dominated spectrum of the hot stars, this star emits predominantly
-in the near-infrared, where the dust extinction efficiency is lower,
-so we adopt a lower opacity of \SI{60}{cm^2.g^{-1}}.  This has the
-effect of shifting the radiation bow wave regime to higher densities:
-\(n = \text{\numrange{1000}{30 000}}\, v_{10}^2\) in this case.
-
-\subsection{Effects of stellar gravity}
-\label{sec:effects-gravity}
-
-In principle, gravitational attraction from the star, of mass \(M\),
-will partially counteract the radiative acceleration.  This can be
-accounted for by replacing \(L\) with an effective luminosity
-\newcommand\Edd{\ensuremath{_{\text{E}}}}
-\begin{equation}
-  \label{eq:effective-luminosity}
-  L_{\text{eff}} = L \bigl(1 - \Gamma\Edd^{\,-1}\bigr) \ ,
-\end{equation}
-in which \(\Gamma\Edd\) is the Eddington factor:
-\begin{equation}
-  \label{eq:eddington-factor}
-  \Gamma\Edd = \frac{\kappa L}{4\pi c G M} = 458.5 \, \frac{\kappa_{600} L_4}{ M } \ ,
-\end{equation}
-where, in the last expression, \(M\) is measured in solar masses.  For
-the stars in Table~\ref{tab:stars}, we find
-\(\Gamma\Edd \approx \text{\numrange{30}{400}}\), so gravity can be safely
-ignored.  The only exception is when the optical depth of the bow is
-very large: \(\tau > \ln\Gamma\Edd \sim 5\), in which case gravity may be
-important in the outer parts of the shell (see
-\citealt{Rodriguez-Ramirez:2016b}).
-
-\subsection{Ionization state of the bow shell}
-\label{sec:trapp-ioniz-front}
-
-\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
-\newcommand\shell{\ensuremath{_{\text{sh}}}}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-BSG}
-  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for an evolved
-    B-type supergiant instead of main sequence stars.  This is similar
-    to the early O MS star of Fig.~\ref{fig:zones-v-n-plane}\textit{c}
-    in many respects, except for the trapping of the ionization front,
-    which occurs for much lower outer stream densities.}
-  \label{fig:B-supergiant}
-\end{figure}
-
-In this section we calculate whether the star is capable of
-photoionizing the entire bow shock shell, or whether the ionization
-front will be trapped within it.  The number of hydrogen
-recombinations\footnote{%
-  The diffuse field is treated in the on-the-spot approximation,
-  assuming all emitted Lyman continuum photons are immediately
-  re-absorbed locally, so the case~B recombination co-efficient,
-  \(\alphaB = \num{2.6e-13}\, T_4^{-0.7}\, \si{cm^3.s^{-1}}\), is
-  used, where \(T_4 = T/\SI{e4}{K}\).} %
-per unit time per unit area in a fully ionized shell is
-\begin{equation}
-  \label{eq:shell-recombination-rate}
-  \mathcal{R} = \alphaB n\shell^2 h\shell \ ,
-\end{equation}
-while the advective flux of hydrogen nuclei through the shock is 
-\begin{equation}
-  \label{eq:shell-advective-flux}
-  \mathcal{A} = n v \ ,
-\end{equation}
-and the flux of hydrogen-ionizing photons
-(\(h \nu > \SI{13.6}{eV}\)) incident on the inner edge of the shell is
-\begin{equation}
-  \label{eq:shell-ionizing-flux}
-  \mathcal{F} = \frac{S} {4 \pi R_0^2} \ , 
-\end{equation}
-where \(S\) is the ionizing photon luminosity of the star.  Any shell
-with \(\mathcal{R} + \mathcal{A} > \mathcal{F}\) cannot be entirely
-photoionized by the star, and so must have trapped the ionization
-front.
-
-The ratio of advective particle flux to ionizing flux is, from
-equations~\eqref{eq:Rstar}, \eqref{eq:shell-advective-flux},
-\eqref{eq:shell-ionizing-flux},
-\begin{equation}
-  \label{eq:advective-over-ionizing-flux}
-  \frac{\mathcal{A}}{\mathcal{F}} = \num{5.86e-5} \frac{x^2 L_4}{v_{10} S_{49}} \ , 
-\end{equation}
-where
-\begin{equation*}
-  S_{49} = S / \bigl( \SI{e49}{s^{-1}} \bigr) \ .
-\end{equation*}
-Numerical values of \(S_{49}\) for our three example stars are given
-in Table~\ref{tab:stars}, taken from Figure~4 of
-\citet{Sternberg:2003a}.  Since \(\mathcal{A} \ll \mathcal{F}\) in
-nearly all cases, for clarity of exposition we ignore \(\mathcal{A}\)
-in the following discussion, although it is included in quantitative
-calculations.  The column density of the shocked shell can be found,
-for example, from equations~(10) and~(12) of \citet{Wilkin:1996a} in
-the limit \(v_\infty/V \to 0\) (Wilkin's parameter \(\alpha\)) and
-\(\theta \to 0\).  This yields
-\begin{equation}
-  \label{eq:shocked-shell-column}
-  n\shell h\shell = \tfrac34 n R_0 \ .
-\end{equation}
-Assuming strong cooling behind the shock,\footnote{%
-  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
-} %
-the shell density is
-\begin{equation}
-  \label{eq:isothermal-shell-density}
-  n\shell = \mathcal{M}_0^2 n \,
-\end{equation}
-where
-\(\mathcal{M}_0 = v_\infty / \sound\) is the isothermal Mach number of the
-external stream.\footnote{%
-  \label{fn:temperature-dependence}
-  The sound speed depends on the temperature and hydrogen and helium
-  ionization fractions, \(y\) and \(y_{\text{He}}\) as
-  \(\sound^2 = (1 + y + z_{\text{He}} y_{\text{He}}) (k T /
-  \bar{m})\), where \(z_{\text{He}}\) is the helium nucleon abundance
-  by number relative to hydrogen and
-  \(k = \SI{1.3806503e-16}{erg.K^{-1}}\) is Boltzmann's constant.  We
-  assume \(y = 1\), \(y_{\text{He}} = 0.5\), \(z_{\text{He}} = 0.09\),
-  so that \(\sound = \num{11.4}\, T_4^{1/2}\, \si{km.s^{-1}}\). } %
-Putting these together with equations~\eqref{eq:Rstar} and
-~\eqref{eq:tau-star}, one finds that \(\mathcal{R} > \mathcal{F}\)
-implies
-\begin{equation}
-  \label{eq:ifront-trap-x-cubed-taustar}
-  x^3 \tau_* > \frac{4 S c \sound \bar{m}^2 \kappa}{3 \alpha L} \ .
-\end{equation}
-From equation~\eqref{eq:rad-full-x}, it can be seen that \(x\) depends
-on the external stream parameters, \(n\), \(v_\infty\) only via
-\(\tau_*\), and so equation~\eqref{eq:ifront-trap-x-cubed-taustar} is a
-condition for \(\tau_*\), which, by using
-equation~\eqref{eq:taustar-typical}, becomes a condition on
-\(n / v_{10}^2\).  In the radiation bow shock case,
-\(x = (1 + \eta)^{1/2}\), and the condition can be written:
-\begin{equation}
-  \label{eq:ifront-trap-density-RBS}
-  \text{RBS:}\quad
-  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta)^3} \ .
-\end{equation}
-In the radiation bow wave case, \(x = 2\tau_*\), and the condition can be
-written:
-\begin{equation}
-  \label{eq:ifront-trap-taustar-RBW}
-  \text{RBW:}\quad
-  \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ . 
-\end{equation}
-In the wind bow shock case, the result is the same as
-equation~\eqref{eq:ifront-trap-density-RBS}, but changing the factor
-\((1 + \eta)^3\) to \(\eta^3\).  For the example hot stars in
-Table~\ref{tab:stars}, and assuming \(\kappa_{600} = 1\),
-\(T_4 = 0.8\), the resulting density threshold is
-\(n > (\text{\numrange{1000}{5000}})\, v_{10}^2\), depending only
-weakly on the stellar parameters, which is shown by the red lines in
-Figure~\ref{fig:zones-v-n-plane}.  For the \SI{10}{M_\odot} star, this is
-in the radiation bow wave regime, whereas for the higher mass stars it
-is in the radiation bow shock regime.  When the external stream is
-denser than this, then the outer parts of the shocked shell may be
-neutral instead of ionized, giving rise to a cometary compact \hii{}
-region \citep{Mac-Low:1991a, Arthur:2006a}.  This is only necessarily
-true, however, when the star is isolated.  If the star is in a cluster
-environment, then the contribution of other nearby massive stars to
-the ionizing radiation field must be considered.
-
-Quite different results are obtained for a B-type supergiant star (see
-Tab.~\ref{tab:stars} and Fig.~\ref{fig:B-supergiant}), which has a
-similar bolometric luminosity and wind strength to the \SI{40}{M_\odot}
-main-sequence star, but a hundred times lower ionizing luminosity.
-This results in a far lower threshold for trapping the ionization
-front of \(n > 40 v_{10}^2\).  The advective flux, \(\mathcal{A}\), is
-relatively stronger for this star than for the main-sequence stars, but
-even for \(v_{10} < 2\), where the effect is strongest, the change is
-only of order the width of the dark red line in
-Figure~\ref{fig:B-supergiant}.
-
-In principle, when the ionization front trapping occurs in the bow
-wave regime, then the curves for \(R_0\) will be modified in the
-region above the red line because all of the ionizing radiation is
-trapped in the shell due to gas opacity, which is not included in
-equation~\eqref{eq:tau-thin}.  However, this only happens for our
-\SI{10}{M_\odot} star, which has a relatively soft spectrum.
-Table~\ref{tab:stars} gives the peak wavelength of the stellar
-spectrum for this star as \(\lambda_{\text{eff}} = \SI{0.115}{\um}\), which
-is significantly larger than the hydrogen ionization threshold at
-\SI{0.0912}{\um}, meaning that only a small fraction of the total
-stellar luminosity is in the EUV band and affected by the gas opacity.
-The effect on \(R_0\) is therefore small.  For the higher mass stars,
-\(\lambda_{\text{eff}} < \SI{0.0912}{\um}\), so the majority of the
-luminosity is in the EUV band, but in these cases the ionization front
-trapping occurs well inside the radiation bow shock zone, where the
-dust optical depth is already sufficient to trap all of the radiative
-momentum.
-
-\subsection{Radiative cooling lengths}
-\label{sec:radi-cool-lengths}
-\newcommand\M{\ensuremath{\mathcal{M}}}
-%
-In this section, we calculate whether the radiative cooling is
-sufficiently rapid behind the bow shock to allow the formation of a
-thin, dense shell.  Since this is mainly a concern at low densities,
-where cooling is least efficient, we will assume that the wind bow
-shock regime applies unless otherwise specified. We label quantities
-just outside the shock by the subscript ``0'', quantities just inside
-the shock (after thermalization, but before any radiative cooling) by
-the subscript ``1'', and quantities after the gas has cooled back to
-the photoionization equilibrium temperature by the subscript ``2''.
-Assuming a ratio of specific heats, \(\gamma = 5/3\), the relation between
-the pre-shock and immediate post-shock quantities is
-\begin{align}
-  % \M_1 &= \left(\frac{\M_0^2 + 3} {5\M_0^2 - 1}\right)^{1/2} \\
-  \label{eq:shock-n-jump}
-  \frac{n_1}{n_0} &= \frac{4 \M_0^2} {\M_0^2 + 3} \\
-  \label{eq:shock-T-jump}
-  \frac{T_1}{T_0} &= \tfrac1{16} \bigl( 5\M_0^2 - 1 \bigr) \bigl( 1 + 3/\M_0^2 \bigr) \\
-  \label{eq:shock-v-jump}
-  \frac{v_1}{v_0} &= \left(\frac{n_1}{n_0}\right)^{-1} \ ,
-\end{align}
-where \(\M_0 = v_0 / \sound\).  The cooling length of the post-shock
-gas can be written as
-\newcommand\cool{\ensuremath{_{\text{cool}}}}
-\begin{equation}
-  \label{eq:dcool}
-  d\cool = \frac{3 P_1 v_1} { 2 \bigl(  \mathcal{L}_1 - \mathcal{G}_1 \bigr) }\ ,  
-\end{equation}
-where \(P_1\) is the thermal pressure and \(\mathcal{L}_1\),
-\(\mathcal{G}_1\) are the volumetric radiative cooling and heating
-rates.  For fully photoionized gas, we have
-\(P_1 \approx 2 n_1 k T_1\), \(\mathcal{L}_1 = n_1^2 \Lambda(T_1)\), and
-\(\mathcal{G}_1 = n_1^2 \Gamma(T_1)\), where \(\Lambda(T)\) is the cooling
-coefficient, which is dominated by metal emission lines that are
-excited by electron collisions, and \(\Gamma(T)\) is the heating
-coefficient, which is dominated by hydrogen photo-electrons
-\citep{Osterbrock:2006a}. The cooling coefficient has a maximum around
-\SI{e5}{K}, and for typical ISM abundances can be approximated as
-follows:
-\begin{align}
-  \label{eq:cooling-coefficient}
-  \Lambda_{\text{warm}} &= \num{3.3e-24} \, T_4^{2.3} \, \si{erg.cm^{3}.s^{-1}}\\
-  \Lambda_{\text{hot}} &= \num{e-20} \, T_4^{-1}\, \si{erg.cm^{3}.s^{-1}} \\
-  \Lambda &= \left( \Lambda_{\text{warm}}^{-k} +  \Lambda_{\text{hot}}^{-k} \right)^{-1/k}
-      \quad \text{with} \quad k = 3 \ ,
-\end{align}
-which is valid in the range \(0.7 < T_4 < 1000\).  We approximate the heating coefficient as
-\begin{equation}
-  \label{eq:heating-coefficient}
-  \Gamma = \num{1.77e-24} \, T_4^{-1/2} \, \si{erg.cm^{3}.s^{-1}} \ ,
-\end{equation}
-where the coefficient is chosen so as to give \(\Gamma = \Lambda\) at
-an equilibrium temperature of \(T_4 = 0.8\).
-
-In Figure~\ref{fig:zones-v-n-plane} we show curves calculated from
-equations~\eqref{eq:shock-n-jump} to~\eqref{eq:heating-coefficient},
-corresponding to \(d\cool = R_0\) (thick blue line) and
-\(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
-thickness in the efficient cooling case.  In this context, \(n_0 = n\)
-and \(n_2 = n\shell\), so that \(h_0\) follows from
-equations~\eqref{eq:shocked-shell-column}
-and~\eqref{eq:isothermal-shell-density} as
-\begin{equation}
-  \label{eq:strong-cooling-h0}
-  h_0 = \tfrac34 \M_0^{-2} R_0 \ .
-\end{equation}
-The bends in the curves at \(v \approx \SI{50}{km.s^{-1}}\) are due to the
-maximum in the cooling coefficient \(\Lambda(T)\) around
-\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
-blue line, radiative cooling is so efficient that the bow shock can be
-considered isothermal, and so the shell is dense and thin (at least,
-in the apex region).  It can be seen that the ionization front
-trapping always occurs at densities larger than this, which justifies
-the use of equation~\eqref{eq:isothermal-shell-density} in the
-previous section.  For bows with outer stream densities below the
-thick blue line, cooling is unimportant and the bow shock can be
-considered non-radiative.  In this case the shell is thicker than in
-the radiative case,
-\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
-  An approximate value can be found from
-  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
-  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
-  Consideration of the slight increase in density between the shock
-  and the contact/tangential discontinuity reduces this value by 5--10\%.} %
-For bows with outer stream densities between the two blue lines,
-cooling does occur, albeit inefficiently, so that the shell thickness
-is set by \(d\cool\) rather than \(h_0\).
-
-\section{Imperfect coupling between gas and dust}
-\label{sec:imperf-coupl-betw}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/test-Fdrag-components}
-  \caption{Contributions of different collider species to the
-    dimensionless drag force, \(f\drag / f_*\), as a function of
-    gas--grain slip velocity, \(w\).  Solid lines show the Coulomb
-    (electrostatic) drag, while dashed lines show the Epstein
-    (solid-body) drag.  Results are shown for dimensionless grain
-    potential \(\phi = 10\).  All Coulomb forces scale with
-    \(\phi^2\), while the Epstein forces are independent of \(\phi\).  The
-    species labelled ``CNO++'' represents the combined effect of all
-    metals (see footnote~\ref{fn:metal-drag}).}
-  \label{fig:drag-components}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/test-Fdrag-param-space}
-  \caption{Regimes of gas--grain drag as a function of slip velocity
-    and grain potential.  The different regimes are indicated by bold
-    roman numerals, as explained in
-    Table~\ref{tab:fdrag-regimes}. Blue shading indicates regions
-    dominated by Epstein (solid-body) drag, whereas red and green
-    shading indicate regions dominated by Coulomb drag due to protons
-    and electrons, respectively.  In each case, the saturated color
-    represents a contribution \(> 70\%\) of the relevant component to
-    the total drag force, while progressively lighter shading
-    represents the \(> 60\%\) and \(> 50\%\) levels.  The thick white
-    dotted line indicates the transition between the subthermal and
-    superthermal regimes for protons, while the thin white dotted line
-    indicates the corresponding transition for electrons.  Contours
-    show the total drag force in units of \(f_*\) (see
-    eq.~[\ref{eq:fstar}]) in decade intervals from \(0.1\) to
-    \(10^4\), as labelled.  Results are shown for
-    \(T = \SI{8000}{K}\) and \(n = \SI{100}{cm^{-3}}\), but the
-    differences are very slight throughout the ranges
-    \(T = \text{\SIrange{5000}{15000}{K}}\) and
-    \(n = \text{\SIrange{e-3}{e6}{cm^{-3}}}\).}
-  \label{fig:drag-v-phi-plane}
-\end{figure}
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
-  \caption{Dimensionless drag force, \(f\drag / f_*\), as a function
-    of gas--grain slip velocity, \(w\), for different values of the
-    grain potential in thermal units, \(\phi\).  Contributions from
-    proton and electron Coulomb (electrostatic) drag, as well as
-    Epstein (solid-body) drag are indicated.  Examples of subsonic and
-    highly supersonic stable drift velocities are shown (thin dark
-    blue arrows), where the drag force is in equilibrium with the
-    radiation force (thick dark blue dashed lines), while blue shading
-    indicates the unstable, mildly supersonic velocity regime, where
-    no stable drift equilibrium exists.  Inset graph shows \(\phi\) as a
-    function of the radiation parameter,
-    \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a log--linear scale
-    for a collection of Cloudy models (see
-    Appendix~\ref{sec:cloudy-models-dust}).}
-  \label{fig:gas-grain-drag-photoionized}
-\end{figure*}
-
-% \begin{figure}
-%   \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
-%   \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
-%     gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
-%   \label{fig:decouple-v-n-plane}
-% \end{figure}
-
-If the radiation field is sufficiently strong, then the collisional
-coupling between grains and gas will break down.  In this section, we
-calculate the regions of star+stream parameter space where this might
-occur, leading to a separation of the bow into an outer dust wave and
-an inner, dust-free bow shock.
-
-\subsection{Drag force on grains}
-\label{sec:drag-force-grains}
-
-\begin{table}
-  \centering
-  \caption{Regimes of drag force as function of grain potential and slip speed}
-  \label{tab:fdrag-regimes}
-  \renewcommand\arraystretch{1.3}
-  \resizebox{\linewidth}{!}{%
-    \begin{tabular}{@{}r l l l@{}}
-    \toprule
-      & Regime & Approximate criteria & \(f\drag / f_*\) \\ \midrule
-      I & Epstein subsonic & \(\phi^2 \ll 1\)
-                             and \(w_{10} < 1\) & \(1.5\, w_{10}\) \\
-      II & Epstein supersonic & \(w_{10} > 1\)
-                                and \(w_{10} > 5\,\abs{\phi}\)& \( w_{10}^2\) \\
-      III & Coulomb p\(^+\) subthermal & \(\phi^2 > 1\)
-                                         and \(w_{10} < 1\) & \((1 + 20\, \phi^2)\,
-                                                              w_{10}\) \\
-    % & Coulomb p\(^+\) peak & \(\phi^2 > 1\)
-    %                          and \(w_{10} \approx 1\) & \(1 + 10\, \phi^2\) \\
-      IV & Coulomb p\(^+\) superthermal & \(\phi^2 > 1\)
-                                          and \(1 < w_{10} < 5\) & \(w_{10}^2
-                                                                   + 10\, \phi^2/w_{10}^2 \) \\
-      V & Coulomb e\(^-\) subthermal & \(\phi^2 > 20\)
-                                 and \(5 < w_{10} < 42\) & \(0.48\, \phi^2 \,
-                                                           w_{10}\) \\
-    \bottomrule
-  \end{tabular}
-  }
-\end{table}
-
-The drag force on a charged dust grain moving at a relative speed
-\(w\) through a plasma has contributions from both direct collisions
-and from electrostatic Coulomb interactions with ions and electrons.
-We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
-considering the contributions from protons, electrons, helium
-ions,\footnote{Helium is assumed to be singly ionized, leading to only
-  a small contribution to the drag force.  For much hotter stars, such
-  as the central stars of planetary nebulae, helium may be doubly
-  ionized, which leads to a fourfold increase in its Coulomb drag
-  contribution, which is significant for \(w < \SI{5}{km.s^{-1}}\).} %
-and metal ions.\footnote{%
-  \label{fn:metal-drag}
-  All metals are lumped together as a single species, assuming
-  standard \hii{} region gas-phase abundances.  They are dominated by
-  C and O, with minor contributions from N and Ne.  The total
-  abundance is \num{8.5e-4} and the effective atomic weight is
-  \num{15.3}.  All are assumed to be doubly ionized.  Their largest
-  relative contribution to the drag force is for
-  \(w < \SI{2}{km.s^{-1}}\), but is less than 1\% even there.} %
-Results are shown in Figure~\ref{fig:drag-components}, where dashed
-lines correspond to direct solid body collisions and solid lines to
-electrostatic interactions.  The latter depend on the grain potential,
-which is described in dimensionless terms by \(\phi\), which is the
-electrostatic potential energy of a unit charge at the surface of a
-grain of charge \(z\grain\) and radius \(a\), in units of the
-characteristic thermal energy of a gas particle:
-\begin{equation}
-  \label{eq:phi-potential}
-  \phi = \frac{e^2 z\grain}{a kT} \ .
-\end{equation}
-The electrostatic contributions to \(f\drag\) are proportional to
-\(\phi^2\) (results are shown for \(\abs{\phi} = 10\)), whereas the
-solid-body contributions are independent of \(\phi\).  The drag force is
-put in dimensionless units by dividing by a characteristic force:
-\begin{equation}
-  \label{eq:fstar}
-  f_* = 2 n k T \cdot \pi a^2 \ , 
-\end{equation}
-which is approximately\footnote{%
-  To simplify the exposition, the gas pressure in this section is
-  calculated assuming a fully ionized, pure hydrogen plasma, yielding
-  \(P\gas = 2 n k T\). For typical ISM abundances, the contribution of
-  helium and its corresponding electrons yield a correction to this of
-  order 5\%.  The required modifications when a cool star interacts
-  with a predominantly neutral gas stream are discussed later.  } %
-the ionized gas pressure multiplied by the grain geometric cross
-section.
-
-For grains with low electric charge, \(\phi^2 \ll 1\), the drag force is
-dominated by direct collisions of protons with the grain (dashed red
-line in Fig.~\ref{fig:drag-components}).  The gas collisional mean
-free path is much larger than the grain size, so the drag is in the
-Epstein regime \citep{Weidenschilling:1977b}.
-% This is illustrated by
-% the \(\phi = 0.25\) case (blue line) in
-% Figure~\ref{fig:gas-grain-drag-photoionized}.
-As the relative gas--grain slip speed, \(w\), increases, \(f\drag\)
-first increases linearly with \(w\) reaching \(f\drag \approx f_*\) at
-\(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to a quadratic
-increase in the supersonic regime.
-
-As \(\abs{\phi}\) increases, long-range electrostatic interactions with
-protons within the Debye radius (Coulomb drag) become increasingly
-important at subsonic relative velocities, as shown by the solid lines
-in Figure~\ref{fig:drag-components}).
-% in
-% Figure~\ref{fig:gas-grain-drag-photoionized} by the orange
-% (\(\phi = 1\)), green (\(\phi = 4\)), and red (\(\phi = 16\)) lines.
-However, the Coulomb drag has a peak when \(w\) is equal to the
-thermal speed of the colliders, which is
-\(\approx \SI{10}{km.s^{-1}}\) for protons, giving a maximum strength of
-\begin{equation}
-  \label{eq:fdrag-maximum}
-  f_{\mathrm{max}} = 0.5\, (\ln\Lambda)\, \phi^2 f_* \approx 10\, \phi^2 f_* \ , 
-\end{equation}
-where \(\Lambda\) is the plasma parameter (number of particles within a
-Debye volume), such that
-\(\ln\Lambda = 23.267 + 1.5 \ln T_4 - 0.5 \ln n\).  At highly super-thermal
-speeds, the Coulomb drag falls asymptotically as
-\(f\drag \propto 1 / w^{2}\).  The thermal speed of electrons is higher than
-that of the protons by a factor of \((m_p / m_e)^{1/2}\), so that the
-electron Coulomb drag (solid light blue line) gives a second peak of
-similar strength, but at \(w \approx \SI{430}{km.s^{-1}}\).  The behavior of
-\(f\drag\) in all these different regimes is summarised in
-Table~\ref{tab:fdrag-regimes}, in terms of \(\phi\) and
-\(w_{10} = w / \SI{10}{km.s^{-1}}\).  This is further illustrated in
-Figure~\ref{fig:drag-v-phi-plane}, where each of the drag regimes is
-located on the \((w, \abs{\phi})\) plane.
-
-% \begin{equation}
-%   \label{eq:fdrag-regimes}
-%   f\drag \approx
-%   \begin{cases}
-%     \text{Epstein subsonic (\(\phi^2 \ll 1\) and \(w_{10} < 1\)):}
-%     & w_{10}\, f_* \\
-%     \text{Epstein supersonic (\(\phi^2 \ll 1\) and \(w_{10} > 1\)):}
-%     & w_{10}^2\, f_* \\
-%     \text{Coulomb p\(^+\) subthermal (\(\phi^2 > 1\) and \(w_{10} < 1\)):}
-%     & (1 + 20 \phi^2)\, w_{10}\, f_* \\
-%     \text{Coulomb p\(^+\) peak (\(\phi^2 > 1\) and \(w_{10} \approx 1\)):}
-%     & (1 + 10 \phi^2)\, f_* \\
-%     \text{Coulomb p\(^+\) superthermal (\(\phi^2 > 1\) and \(1 < w_{10} < 5\)):}
-%     & (w_{10}^2 + 10 \phi^2/w_{10}^2) \, f_* \\
-%     \text{Coulomb e\(^-\) subthermal (\(\phi^2 > 20\) and \(5 < w_{10} < 42\)):}
-%     & 0.48 \phi^2 \, w_{10}\, f_* \\
-%   \end{cases}
-% \end{equation}
-
-% Or \Lambda = (4 pi / 3) n r_D^3?
-% Where Debye length is r_D^2 = k T / 4 pi n e^2
-% => \Lambda = n r_D (4 pi / 3) k T / 4 pi n e^2
-% = k T r_D / 3 e^2
-% This is 9 times less than the other expression
-% Anyway, from kappa notes I have
-% \ln\Lambda = 9.452 + 1.5 ln(T) - 0.5 ln(n)
-
-% If I am going to use log10, then the coefficients get divided by
-% ln(10) = 2.30258509299, and if we use T4, then we add 1.5 ln(1e4) =
-% 13.815.  So we get 23.267 + 0.651 log10(T4) - 0.217 log10(n).  Nope,
-% best with natural log
-
-\subsection{Gas--grain separation: drift and rip}
-\label{sec:gas-grain-separ}
-
-In Appendix~\ref{sec:gas-free-bow} we calculate the behaviour of an
-incoming stream of dust grains, subject only to the repulsive
-radiation force from a star.  For an initial inward radial trajectory,
-the dust grain motion is decelerated and turned around, reaching a
-minimum radius \(R\starstar\), given by equation~\eqref{eq:dust-r0}.
-This drag-free radiative turnaround radius, \(R\starstar\), is smaller
-for higher initial inward velocities, but is independent of the
-density of the incoming stream.  We are now in a position to see how
-gas--grain drag will modify this picture.
-
-From equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar}, we can
-write the radiation force acting on a grain as
-\begin{equation}
-  \label{eq:frad-Xi}
-  f\rad = \Qp\, \Xi\, f_* \ ,
-\end{equation}
-where \(\Qp\) is the grain's radiation pressure efficiency (see
-footnote~\ref{fn:Qp} in Appendix~\ref{sec:gas-free-bow}) and \(\Xi\) is
-the local radiation parameter, defined as the ratio of direct stellar
-radiation pressure to gas pressure:
-\begin{equation}
-  \label{eq:Xi-Prad-over-Pgas}
-  \Xi \equiv \frac{P\rad}{P\gas} \approx \frac{L}{4 \pi R^2 c\, (2 n k T)} \ ,
-\end{equation}
-where the last expression corresponds to the optically thin limit.
-The grain potential \(\phi\) is also primarily determined by \(\Xi\), as
-shown in Appendix~\ref{sec:cloudy-models-dust} and the inset graph of
-Figure~\ref{fig:gas-grain-drag-photoionized}, but with a slow
-dependence, which can be approximated as
-\begin{equation}
-  \label{eq:phi-vs-Xi}
-  \phi(\Xi) \approx 1.5 \bigl( 2.3 +  \ln \Xi \bigr) \ .
-\end{equation}
-There are also slight secondary dependencies on the grain composition and
-stellar spectrum.  The relationship given in eq.~\eqref{eq:phi-vs-Xi}
-is appropriate for graphite grains and for stellar effective
-temperatures in the range \SIrange{20}{30}{kK}.  For hotter stars than
-this, \(\phi\) should be multiplied by a further factor of \(1.5\), while
-for silicate grains it should be divided by \(1.5\).
-
-In the outer regions of the photoionized volume around an OB star,
-close to the ionization front, the radiation parameter is low, with
-typical value \(\Xi \sim 0.1\).  In this regime, the negative charge
-current at the grain surface due to electron collisions is roughly in
-balance with the positive current due to the ultraviolet photoelectric
-effect \citep{Weingartner:2001b}, leading to a low grain potential,
-\(\abs{\phi} < 1\), which may be positive or negative.  The low
-\(\Xi\) means that the radiative force is also weak:
-\(f\rad \sim 0.1 f_*\) from equation~\eqref{eq:frad-Xi} if
-\(\Qp \sim 1\) at UV wavelengths, which is true for all but the smallest
-grains.  Thus, from the equations for \(f\drag\) given in
-Table~\ref{tab:fdrag-regimes}, the radiative force can be balanced by
-Epstein drag if \(w_{10} \sim 0.1\), leading to a small equilibrium drift
-velocity, \(w\drift < \SI{1}{km.s^{-1}}\), of the grains with respect
-to the gas.  This drift is much smaller than the inward stream
-velocities that we are considering
-(\(v_\infty > \SI{10}{km.s^{-1}}\)), so the dust follows the gas stream at
-a slightly reduced velocity (\(< 10\%\)), and (by mass conservation) a
-slightly increased density.  Each grain exerts an exactly opposite
-force to \(f\drag\) upon the gas, but since the dust-gas mass ratio,
-\(Z\grain\), is small, this produces a negligible acceleration of the
-gas.
-
-\begin{table}
-  \caption{Critical values of radiation parameter at the rip point: \(\Xi_\dag\)}
-  \centering
-  \begin{tabular*}{0.75\columnwidth}{l @{\quad\quad\quad\quad} S S} \toprule
-    & \multicolumn{2}{c}{Grain composition} \\
-    Spectrum & {Graphite} & {Silicate}
-    \\ \midrule
-    B star & 1000 +- 400 & 350 +- 150 \\
-    O star & 3000 +- 500 & 2500 +- 500 \\
-    \bottomrule
-    \addlinespace
-    \multicolumn{3}{@{}p{0.75\columnwidth}@{}}{
-    Calculated from the Cloudy models shown in Figure~\ref{fig:drift-gn}. 
-    Uncertainties represent variations with grain size and gas density. 
-    See Appendix~\ref{sec:cloudy-models-dust} for further details.}
-  \end{tabular*}
-  \label{tab:Xi-rip}
-\end{table}
-
-As the dusty stream approaches the star, the radiation parameter
-\(\Xi\) will increase, with a dependence of \(R^{-2}\) once the stream
-is well inside the ionization front.  This increases \(f\rad\)
-(eq.~[\ref{eq:frad-Xi}]), but also increases the grain potential,
-\(\phi\) (eq.~[\ref{eq:phi-vs-Xi}]) due to the increasing dominance of
-grain charging by photoelectric ejection.  Initially, this results in
-a lowering of the equilibrium drift velocity to \(w_{10} \sim 0.01\) as
-the Coulomb drag kicks in (see Appendix~\ref{sec:cloudy-models-dust}).
-However, at smaller radii the slow logarithmic increase in
-\(\phi(\Xi)\) means that the drift velocity must start increasing again to
-accommodate the linear increase of \(f\rad(\Xi)\).  Eventually,
-\(f\rad\) exceeds \(f_{\mathrm{max}}\), the maximum drag force that
-proton Coulomb interactions can provide
-(eq.~[\ref{eq:fdrag-maximum}]).  This occurs at a critical value of
-the radiation parameter, which we denote the \textit{rip point}:
-\(\Xi_\dag \sim 1000\).  The variations in \(\Xi_\dag\) with star and grain
-parameters, which are of order \SI{+- 0.5}{dex}, are listed in
-Table~\ref{tab:Xi-rip} and illustrated graphically in
-Figure~\ref{fig:drift-gn}.  The radius of the rip point, \(R_\dag\), can
-be expressed in terms of \(R_*\), the fiducial optically thick bow
-shock radius introduced in \S~\ref{sec:strong-gas-grain}:
-\begin{equation}
-  \label{eq:Rdag-over-Rstar}
-  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
-\end{equation}
-where we have made use of equations~\eqref{eq:Rstar}
-and~\eqref{eq:Xi-Prad-over-Pgas}.
-
-What happens to the dust grain following this catastrophic breakdown
-of gas--grain coupling depends on the relation between the rip point
-radius, \(R_\dag\), and the drag-free radiative turnaround radius,
-\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
-will still carry it in as far as \(R\starstar\) and the initial
-trajectory will be almost identical to that described in
-Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
-being turned around by the radiation field and pushed out past
-\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
-dragged back for a second approach.\footnote{If the initial impact
-  parameter of the trajectory is not strictly \(b = 0\), then the
-  resultant lateral component of \(f\rad\) will mean that \(b\) will
-  be much increased for the second approach.} %
-We will refer to this as an \textit{inertia-confined dust wave}
-(IDW).  From equations~(\ref{eq:Rdag-over-Rstar},
-\ref{eq:Rstarstar-over-Rstar},
-\ref{eq:dust-wave-high-density-condition}), the condition
-\(R_\dag > R\starstar\) corresponds to
-\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
-lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
-on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
-by the gas carries the grain closer to the star than its inertia would
-naturally take it.  When the grain finally decouples at \(R_\dag\) it
-experiences a much higher unbalanced \(f\rad\), which can initially
-accelerate it to outward velocities significantly higher than the
-inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
-as a \textit{drag-confined dust wave} (DDW).
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/existence-dust-wave}
-  \caption{Regions of stream parameter space \((v, n)\) where dust
-    waves may form around main-sequence OB stars of
-    \SIlist{10;20;40}{M_\odot} (see Tab.~\ref{tab:stars}).  Figure is
-    similar to Fig.~\ref{fig:zones-v-n-plane}, except that the
-    velocity axis is logarithmic and extends out to
-    \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show parameters
-    where dust waves may be allowed in the cases of large
-    (\(a = \SI{0.2}{\um}\)) and small (\(a = \SI{0.02}{\um}\))
-    graphite and silicate grains, as labeled in the left panel.  For
-    \((v, n)\) outside of these shapes, dust waves cannot occur for
-    the reasons indicated by labeled orange arrows in the center
-    panel.  Labeled dashed lines in the right panel show the
-    correspondence between the region boundaries and each dust wave
-    existence condition given in
-    equations~(\ref{eq:dust-wave-velocity-condition},
-    \ref{eq:dust-wave-low-density-condition},
-    \ref{eq:dust-wave-high-density-condition}). Heavy dashed lines in
-    the left panel show where the rip point and the drag-free
-    turnaround radius coincide.  Dust waves above these lines are drag
-    confined, while dust waves below the lines are inertia confined.
-  }
-  \label{fig:existence-dust-wave}
-\end{figure*}
-
-\subsection{Existence conditions for dust waves}
-\label{sec:exist-cond-separ}
-
-In order for a separate outer dust wave to exist, it is necessary for
-the grains to decouple from the incoming gas stream before the stream
-hits the hydrodynamic bow shock caused by the stellar wind.  The wind
-bow shock radius is \(R_0 = \eta^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]),
-where \(\eta\) is the wind momentum efficiency
-(eq.~[\ref{eq:wind-eta-typical}]).  Therefore, the condition
-\(R_\dag > R_0\) becomes from equation~\eqref{eq:Rdag-over-Rstar}:
-\begin{equation}
-  \label{eq:dust-wave-velocity-condition}
-  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta \bigr)^{1/2} \ . 
-\end{equation}
-For O stars, the wind efficiency is generally high (\(\eta > 0.1\)) and
-\(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
-exist when the stream velocity is very high
-(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
-can be much weaker (\(\eta < 0.01\)) and \(\Xi_\dag\) is also smaller, so
-that dust waves are permitted by this criterion for much lower stream
-velocities: (\(v_\infty > \SI{30}{km.s^{-1}}\)).
-
-However, there are other conditions that need to be satisfied in order
-for the dust wave to exist.  For instance, the drag-free turnaround
-radius must also be outside the bow shock: \(R\starstar > R_0\),
-otherwise the radiation is incapable of repelling the grain
-opportunely, even once it has decoupled from the gas.  From
-equations~\eqref{eq:Rstar}, \eqref{eq:tau-star},
-and~\eqref{eq:dust-r0} we find
-\begin{equation}
-  \label{eq:Rstarstar-over-Rstar}
-  \frac{R\starstar}{R_*} = \frac{2 \sigma\grain \Qp \tau_*}{\kappa m\grain} \ , 
-\end{equation}
-so, if we define a single-grain opacity as
-\(\kappa\grain = \sigma\grain \Qp / m\grain\), then this condition becomes
-\begin{equation}
-  \label{eq:dust-wave-low-density-condition}
-  \tau_* >  \tau_{*,\text{min}} = 0.5\, \frac{\kappa}{\kappa\grain}\, \eta^{1/2} 
-  % \frac{\kappa \eta^{1/2}}{2 \kappa\grain}
-  \ . 
-\end{equation}
-The average value of the factor \(\kappa / \kappa\grain\) over the entire grain
-population must be equal to the dust--gas mass ratio,
-\(Z\grain \approx 0.01\), but the factor will vary between grains, according
-to their size and composition.\footnote{%
-  Remember that \(\kappa\) is the opacity per unit mass of gas, while
-  \(\kappa\grain\) is the opacity per unit mass of a particular grain. In
-  both cases, averaged over the stellar spectrum.} %
-In particular, it will be relatively larger for the largest grains
-(\(a \approx \SI{0.2}{\um}\)), which dominate the total dust mass, and
-smaller for the smaller grains (\(a \approx \SI{0.02}{\um}\)), which
-dominate the UV opacity.  Given the dependence of \(\tau_*\) on the
-stream parameters (eq.~[\ref{eq:taustar-typical}]), for a given
-stellar luminosity this condition corresponds to a minimum value for
-\(n / v_\infty^2\).
-
-A third condition comes from requiring \(R_\dag > R_0\) in the radiation
-bow wave regime (see \S~\ref{sec:three-bow-regimes}), where
-\(R_0 \approx 2 \tau_* R_*\).  This yields
-\begin{equation}
-  \label{eq:dust-wave-high-density-condition}
-  \tau_* < \tau_{*,\text{max}} = 0.5\, v_{10}\, \Xi_\dag^{-1/2} \ , 
-\end{equation}
-which, for a given stellar luminosity, corresponds to a maximum value
-for \(n / v_\infty^4\).  Thus, for a given stream velocity that satisfies
-equation~\eqref{eq:dust-wave-velocity-condition},
-equations~(\ref{eq:dust-wave-low-density-condition},
-\ref{eq:dust-wave-high-density-condition}) determine respectively the
-minimum and maximum stream density for which a dust wave can exist.
-
-The combined effects of the three conditions are illustrated in
-Figure~\ref{fig:existence-dust-wave} for each of the three example
-main sequence stars from Table~\ref{tab:stars}.  Further restrictions
-on the existence of dust waves arise when the effects of magnetic
-fields are considered, as will be discussed in
-\S~\ref{sec:magn-effects-grain} below.  Note that the three conditions
-are restrictions solely on the formation of an \textit{outer} dust
-wave, that is, outside of the wind-supported hydrodynamic bow shock.
-In the case of the equation~\eqref{eq:dust-wave-low-density-condition}
-condition, there is a further possibility: if the gas--grain coupling
-(and magnetic coupling) is so weak that it is still unimportant at the
-higher densities found in the bow shock shell, then an
-inertia-confined \textit{inner} dust wave may form inside the bow
-shock, even when \(\tau_* < \tau_{*,\text{min}}\).  Although the same might
-be thought to apply to the condition of
-equation~\eqref{eq:dust-wave-velocity-condition}, this is not the
-case, since the density compression in the bow shock will reduce the
-radiation parameter, \(\Xi\), which moves the rip point, \(R_\dag\), to an
-even smaller radius.  Therefore, if radiation has not managed to
-decouple a grain before it passes through the shock, it is unlikely to
-be able to do it afterwards.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/dust-wave-phase-trajectories-annotate}
-  \caption{Trajectories of small graphite grains
-    (\(a = \SI{0.02}{\um}\)) at impact parameter \(b = 0\) for two
-    example cases (see yellow ``+'' symbols in left panel of
-    Fig.~\ref{fig:existence-dust-wave}), which differ only in the
-    stream velocity: \(v = \SI{40}{km.s^{-1}}\) (left panels) and
-    \SI{80}{km.s^{-1}} (right panels).  In both cases, the stream
-    density is \(n = \SI{1}{cm^{-3}}\) and the central star is a
-    \SI{10}{M_\odot} main-sequence B star (see Tab.~\ref{tab:stars}).
-    Upper panels show the evolution of grain radius, \(R\) (blue
-    curve, normalized by the rip point radius, \(R_\dag\)), and grain
-    velocity, \(v\) (orange curve, normalized by the gas stream
-    velocity).  The origin of the time axis is set to the moment of
-    closest approach of the grain to the star: \(R = \Rmin\).  Lower
-    panels show the trajectories in phase space: position versus
-    gas--grain relative slip velocity (\(w = \abs{v - v_\infty}\)).  Filled
-    contours show the net force on the grain: \(f\rad - f\drag\), with
-    positive values in blue and negative values in red.  The heavy
-    dotted line shows where there is no net force: \(f\rad = f\drag\).
-    The grain trajectory (thick, solid black line with arrows)
-    initially follows this line, but departs from it after the rip
-    point. In the left panel, the grain enters a limit cycle between
-    decoupling (rip) and re-coupling (snap back).  In the right panel,
-    the grain spirals in on the stagnant drift point.  See text for
-    further details.}
-    \label{fig:phase-space-trajectories}
-\end{figure*}
-
-\subsection{Grain trajectories along the symmetry axis}
-\label{sec:grain-traj-along}
-
-The post-decoupling behavior of the grain depends on the sign of
-\(d f\drag / d w\) when \(w = \abs{v_\infty}\).  If this derivative is
-positive, as is the case in drag regimes~II and V (see
-Tab.~\ref{tab:fdrag-regimes} and Fig.~\ref{fig:drag-v-phi-plane}),
-then the grain can reach a stable equilibrium drift at rest with
-respect to the star\footnote{%
-  Again, this is only strictly true when the impact parameter is zero.
-  However, as we show below, it is a reasonable approximation over a
-  range of impact parameters in the case where the angle between the
-  magnetic field direction and the stream velocity is not too
-  large.} %
-at a point \(R_\ddag\), which we call the \textit{stagnant drift
-  radius}. If the stream velocity is not excessively high
-(\(v_\infty < \SI{150}{km.s^{-1}}\) when \(\phi = 4\), or
-\(< \SI{300}{km.s^{-1}}\) when \(\phi = 16\)), then the equilibrium
-\(f\rad\) is less than the value at the rip point, requiring a lower
-value of the radiation parameter: \(\Xi_\ddag < \Xi_\dag\).  The resultant
-stagnant drift radius is therefore outside the rip point:
-\(R_\ddag > R_\dag\).
-
-On the other hand, if \(d f\drag / d w < 0\) when
-\(w = \abs{v_\infty}\), then the equilibrium is unstable and no stagnant
-drift is possible.  This occurs for drag regime~IV, which applies when
-\(\phi > 1\) and
-\(\SI{10}{km.s^{-1}} < v_\infty < \SI{50}{km.s^{-1}}\).  There is also a
-second unstable regime (partially visible in the upper-right corner of
-Fig.~\ref{fig:drag-v-phi-plane}), which is related to the thermal peak
-in the electron Coulomb drag when \(\phi > 30\) and
-\(\SI{400}{km.s^{-1}} < v_\infty < \SI{2000}{km.s^{-1}}\), but this is not
-relevant to bow shocks around OB~stars.\footnote{%
-  It may apply in other contexts, such as outflows from AGN, since
-  detailed modeling of grain charging around quasars
-  \citep{Weingartner:2006a} implies that grain potentials as high as
-  \(\phi \sim 100\) can be achieved.} %
-
-An example of each of these two behaviors is illustrated in
-Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
-case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
-regime, resulting in periodic ``limit-cycle'' behavior (the parameters
-of this model correspond to the yellow ``plus'' symbol labeled ``40''
-in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
-grain's first approach, it starts to follow a phase trajectory (lower
-left panel) along the \(f\rad - f\drag = 0\) contour, corresponding to
-equilibrium drift, in which the grain begins to move a few
-\si{km.s^{-1}} slower than the gas stream.  Then, when it reaches the
-rip point (\(R = R_\dag\), \(w \approx \SI{10}{km.s^{-1}}\)) it suddenly
-experiences a large unbalanced outward radiation force (blue region of
-phase space in Fig.~\ref{fig:phase-space-trajectories}). The grain's
-inward momentum carries it to the point \(\Rmin \approx 0.85 R_\dag\), before
-it is expelled at roughly twice the inflow speed.  However, after
-moving outward, it finds itself in a drag-dominated region of phase
-space (red in the figure), and so recouples to the inflowing gas
-stream.  The recoupling initiates gradually, as the grain's outward
-motion is slowed and it begins to move inward again, but is completed
-suddenly once \(w\) again falls below \SI{10}{km.s^{-1}}, in what we
-term \textit{snap back}. The net result is that the grain has returned
-to exactly the same phase track that it started in on, and so repeats
-the cycle indefinitely.
-
-The right panels of Figure~\ref{fig:phase-space-trajectories} show the
-case where the stream velocity is doubled to
-\(v_\infty = \SI{80}{km.s^{-1}}\), but all other parameters remain the
-same.  At this velocity, the equilibrium drift is stable and so the
-grain can achieve a stagnant drift solution, where it is stationary
-with respect to the star.  The trajectory during the first approach is
-similar to the previous case, except that the overshoot of the rip
-point is greater, so that \(\Rmin \approx 0.65 R_\dag\) in this case.  This is
-a consequence of the fact that the rip point is closer to the
-drag-free turnaround radius (\(R_\dag / R\starstar\) is larger than in
-the lower velocity case), so that the grain inertia is relatively more
-important.  A second consequence of this is that the speed of the
-initial expulsion is not so large, being only a little higher than the
-inflow velocity.  The qualitative difference between the two cases
-emerges after the first recoupling: instead of the snap back and
-endless limit cycle, the grain oscillates about the stagnant drift
-radius with ever decreasing amplitude, so that after a few oscillation
-periods it has come to almost a complete rest.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/onaxis-stats-plot-MS10-v080-gra002}
-  \caption{Bow radius as a function of stream density for a stream of
-    initial velocity \SI{80}{km.s^{-1}}, which interacts with a
-    \SI{10}{M_\odot} main-sequence B~star.  This corresponds to a vertical
-    slice through the left panel of
-    Fig.~\ref{fig:existence-dust-wave}.  At low densities, the
-    hydrodynamic bow shock (blue line) is larger than the drag-free
-    turnaround radius for small carbon grains, meaning that a grain's
-    inertia carries it into the bow shock along with the gas, even
-    though the gas--grain coupling is not particularly strong.  At
-    densities above about \SI{0.05}{cm^{-3}}, however, this is no
-    longer true and a separate dust wave forms outside of the
-    hydrodynamic bow shock, which is now dust-free (green dashed
-    line).  The grains in the dust wave will occupy a range of radii
-    (pale orange shading) between \(\Rmin\) (solid orange line) and
-    \(R_\ddag\), the stagnant drift radius.  At densities above about
-    \SI{1000}{cm^{-3}}, the gas stream starts to feel the effect of
-    passing through the dust wave, and above \SI{3e4}{cm^{-3}}, the
-    dust wave and bow shock merge to form a radiative bow wave (red
-    line), which becomes an optically thick radiative bow shock
-    (purple line) above \SI{e6}{cm^{-3}}.}
-  \label{fig:decouple-vertical-cut}
-\end{figure}
-
-\subsection{Back reaction on the gas flow}
-\label{sec:back-reaction-gas}
-
-So far we have ignored the effect of the drag force on the gas stream
-itself, but it is clear that this must become important as \(\tau_*\)
-approaches \(\tau_{*,\text{max}}\), since that is the point where the
-dust wave transitions to a bow wave, in which the dust and gas are
-perfectly coupled.  A full treatment of this problem would require
-solving the hydrodynamic equations simultaneously with the equations
-of motion of the dust grains, which is beyond the scope of this paper.
-Instead, we outline a heuristic approach that qualitatively captures
-the physics involved.
-
-The maximum drag force experienced by a grain is at the rip point.
-Since the grain follows a zero-net-force phase track up until that
-point, this can be written with the help of
-equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0}) as
-\begin{equation}
-  \label{eq:fdrag-max}
-  f\drag (R_\dag) = f\rad(R_\dag) =   \frac{m\grain v_\infty^2 R\starstar}{ 2 R_\dag^2} 
-\end{equation}
-The timescale of the flow can be characterized by the crossing time
-\(R_\dag / v_\infty\), but the residence time of the grain at the bow apex
-will be several times larger than this (see previous section).  On the
-other hand, the average drag force during this residence will be
-several times smaller than \(f\drag (R_\dag)\) if
-\(R_\ddag > R_\dag\), which is typically the case.  We therefore parameterize
-our ignorance via a dimensionless factor, \(\alpha\), which we expect to be
-of order unity, and write the total impulse imparted to the grain by
-drag as
-\begin{equation}
-  \label{eq:grain-impulse}
-  J\drag \equiv \int \!f\drag \, dt \approx \alpha f\drag (R_\dag) \frac{R_\dag}{v_\infty}
-  = \tfrac12 \alpha \, m\grain v_\infty \, \frac{R\starstar}{R_\dag} \ .
-\end{equation}
-
-By Newton's Third Law, an equal and opposite impulse is imparted to
-the gas, which will act to decelerate the gas stream as it decouples
-from the grains.  Realistically, \(J\drag\) should be summed over the
-grain size distribution, but for simplicity we assume that all grains
-are identical, so that the mass of gas that accompanies each grain is
-given by
-\begin{equation}
-  \label{eq:gas-mass}
-  m_{\text{gas}} = \frac{m\grain}{Z\grain} =  m\grain \, \frac{\kappa\grain}{\kappa} \ . 
-\end{equation}
-If the gas remains supersonic after decoupling, then thermal pressure
-can be ignored and the gas will suffer a change in momentum equal to
-\(J\drag\), so that its velocity is reduced by
-\(\Delta v = J\drag / m_{\text{gas}}\), which by
-equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
-\ref{eq:dust-wave-high-density-condition}, \ref{eq:grain-impulse},
-\ref{eq:gas-mass}) is
-\begin{equation}
-  \label{eq:gas-dv}
-  \Delta v = \tfrac12 \alpha \frac{\tau_*}{\tau_{*, \text{max}}} v_\infty\ .
-\end{equation}
-This deceleration reduces the gas stream's ram pressure before it
-interacts with the central star's stellar wind.  The radius of the
-dust-free bow shock formed by this interaction is therefore increased
-by a factor \((1 - \Delta v / v_\infty)^{-1}\) with respect to the case
-calculated in \S~\ref{sec:three-bow-regimes}, yielding
-\begin{equation}
-  \label{eq:gas-free-bow-shock}
-  R_{\text{dfbs}} \approx \frac{\eta^{1/2} R_*}{1 - \tfrac12 \alpha \tau_* / \tau_{*, \text{max}}} \ .
-\end{equation}
-
-An example is illustrated in Figure~\ref{fig:decouple-vertical-cut},
-where the dust-free bow shock radius is shown by the green dashed line
-as a function of stream density, \(n\).  This is calculated for fixed
-stream velocity and grain and star properties, so that
-\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).  In order for
-\(R_{\text{dfbs}}\) to match the dust-wave and bow-wave radii at the
-point where they cross at \(\tau_* = \tau_{*, \text{max}}\), we find
-\(\alpha \approx 1.5\) is required.  It can be seen that the gas deceleration is
-negligible over most of the density range for which a separate dust
-wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does
-\(R_{\text{dfbs}}\) begin to curve up from the general \(n^{-1/2}\)
-trend, becoming essentially flat at a value
-\(R_{\text{dfbs}} \approx (\kappa/\kappa\grain) R\starstar\) until full-coupling is
-established at \(n > \SI{3e4}{cm^{-3}}\).  Note, however, that the
-treatment described here is very approximate: it does not take into
-account the shock that will form once \(J\drag\) reaches an
-appreciable fraction of \(m_{\text{gas}} v_\infty\) and, additionally, it
-includes a factor, \(\alpha\), whose value has not been rigorously
-justified.  More detailed modeling is required to fully understand the
-bow behavior in this transition regime.
-
-\section{Magnetic coupling of grains}
-\label{sec:magn-effects-grain}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/frozen-stream-map-multi}
-  \caption{Drag-confined dust waves with tight magnetic coupling.
-    Upper panels show a quasi-parallel field, \(\theta\B = \ang{10}\),
-    while lower panels show a quasi-perpendicular field,
-    \(\theta\B = \ang{75}\).  Left panels show an incident stream velocity of
-    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels show
-    \(v_\infty = \SI{80}{km.s^{-1}}\).  In all cases, the stream density is
-    \(n = \SI{10}{cm^{-3}}\) and the calculations are performed for
-    small graphite grains, \(a = \SI{0.02}{\um}\), and the
-    \SI{10}{M_\odot} main-sequence B~star.  Continuous black lines show
-    grain trajectories, with triplets of colored symbols indicating
-    the progress of individual cohorts, which entered from the right
-    edge at a particular time.  Continuous blue lines show the
-    magnetic field, which flows from right to left along with the
-    incident stream.  The radius of the rip point, \(R_\dag\), and the
-    stagnant drift point, \(R_\ddag\), are shown respectively by red and
-    blue dashed lines.  The approximate shape of the wind-supported
-    bow shock is shown by the dotted gray line.  The calculations are
-    no longer valid after trajectories cross this surface.}
-  \label{fig:frozen-stream}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/frozen-trajectories-multi}
-  \caption{Sample grain trajectories for drag-confined dust waves with
-    tight magnetic coupling and a quasi-parallel field
-    orientation. These are the same models as in the upper row of
-    Fig.~\ref{fig:frozen-stream}. (a)~Incident stream velocity of
-    \(v_\infty = \SI{40}{km.s^{-1}}\), showing quasi-limit-cycle behavior
-    (\numrange{0}{4000} years).  (b)~Incident stream velocity of
-    \(v_\infty = \SI{80}{km.s^{-1}}\), showing quasi-stagnation behavior
-    (\numrange{500}{2000} years).  In both cases, the streamline with
-    initial impact parameter \(y = -0.4 R_\dag\) is shown.}
-  \label{fig:frozen-trajectories}
-\end{figure}
-
-An important effect that we have not considered up to now is the
-Lorentz force on charged grains due to the plasma's magnetic field:
-\begin{equation}
-  \label{eq:f-lorentz}
-  \bm{f}\!\B = \frac{z\grain e}{c} \, \bm{w} \times \bm{B} \ . 
-\end{equation}
-The direction of the force is perpendicular both to the magnetic
-field, \(\bm{B}\), and to the relative velocity, \(\bm{w}\), of the
-grain with respect to the plasma.  If \(\bm{w}\) and \(\bm{B}\) (as
-seen by the grain) are changing slowly, compared with the
-gyrofrequency, \(\omega\B = z\grain e B / m\grain c\), then the grain
-motion perpendicular to \(\bm{B}\) is constrained to be a circle of
-radius equal to the Larmor radius:
-\begin{equation}
-  \label{eq:Larmor}
-  r\B = \frac{m\grain c w_\perp} {\abs{z\grain} e B} \ ,
-\end{equation}
-where \(B = \abs{\bm{B}}\) and \(w_\perp\) is the perpendicular component
-of \(\bm{w}\).  The component of \(\bm{w}\) parallel to \(\bm{B}\) is
-unaffected by \(\bm{f}\!\B\), so the resultant trajectory is helical.
-
-The relative importance of the magnetic field can be characterized by
-the ratio of the Larmor radius to the minimum radius, \(\Rmin\),
-reached by the grain in the dust wave (see
-\S~\ref{sec:grain-traj-along}), where \(\Rmin \approx R_\dag\) for
-drag-confined dust waves (DDW), or \(\Rmin \approx R\starstar\) for
-inertia-confined dust waves (IDW).  We write the field strength in
-terms of the Alfvén speed,
-\begin{equation}
-  \label{eq:alfven}
-  v\alfven = \frac{B}{(4\pi\rho\gas)^{1/2}}
-  = 1.9\, \frac{B}{\si{\micro G}} n^{-1/2} \, \si{km.s^{-1}} \ ,
-\end{equation}
-and the grain charge \(z\grain e\) in terms of the potential \(\phi\) (eq.~[\ref{eq:phi-potential}]) to obtain
-\begin{equation}
-  \label{eq:larmor-over-Rdag}
-  \text{DDW:}\quad \frac{r\B}{\Rmin} =  
-  \frac{r\B}{R_\dag} = 0.0140 \,
-  a_{\si{\um}}^2 \,
-  \frac{w_\perp}{v\alfven} \,
-  \left( \frac{\Xi_\dag}{L_4 T_4} \right)^{1/2}
-  \frac{\rho\grain}{\phi_\dag}
-\end{equation}
-and
-\begin{equation}
-  \label{eq:larmor-over-Rstarstar}
-  \text{IDW:}\quad \frac{r\B}{\Rmin} =  
-  \frac{r\B}{R\starstar} = 0.0544 \,
-  a_{\si{\um}}^3 \,
-  \frac{w_\perp}{v\alfven} \,
-  \frac{v_{10}^2 }{n^{1/2}} \,
-  \frac{1}{L_4 T_4} \,
-  \frac{\rho\grain^2}{\Qp \phi\starstar} \ ,
-\end{equation}
-where \(a_{\si{\um}} = a / \SI{1}{\um}\), \(\rho\grain\) is the grain
-material density in \si{g.cm^{-3}}, and we have made use of
-equations~(\ref{eq:Rstar-typical}, \ref{eq:Rdag-over-Rstar},
-\ref{eq:dust-r0}).
-
-If \(r\B / \Rmin \ll 1\), then the grains are so strongly coupled to the
-field that they can be treated in the guiding-center approximation, in
-which the trajectory is decomposed into a tight circular gyromotion
-around the field lines, plus a sliding of the guiding center along the
-field lines, which is governed by the radiation and drag forces (the
-slow \(\bm{f} \times \bm{B}\) drift across the field lines is negligible in
-this case, see App.~\ref{sec:tight-magn-coupl}).  In the opposite
-limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
-non-magnetic results of \S~\ref{sec:imperf-coupl-betw} are scarcely
-modified.  Assuming \(w_\perp \sim v_\infty\) and adopting a threshold of
-\(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
-\ref{eq:larmor-over-Rstarstar}) can be transformed into conditions on
-the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
-will apply: \newcommand\freeze{\ensuremath{_{\text{tight}}}}
-\begin{equation}
-  \label{eq:velocity-strong-B-coupling}
-  v_{\infty} < v\freeze \approx
-  \begin{cases}
-    \text{drag-confined:}
-    & 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2}\\
-    \text{inertia-confined:}
-    & 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \\
-  \end{cases} \ ,
-\end{equation}
-where we have substituted typical values of the minor parameters
-\(\Xi_\dag\), \(\phi_{\dag}\), \(\phi_{**}\), \(\rho\grain\),
-\(T_4\).\footnote{%
-  The most significant systematic variation in \(v\freeze\) from these
-  suppressed parameters is due to grain composition, yielding slightly
-  higher values for graphite than for silicate (\SI{+-0.15}{dex}).} %
-It is apparent that \(v\freeze\) is very sensitive to the grain size.
-For instance, taking a typical \hii{} region value of
-\(v\alfven = \SI{2}{km.s^{-1}}\) \citep{Arthur:2011a} and
-\(L_4 = 0.63\) (Tab.~\ref{tab:stars}, B1.5~V star), then for the
-drag-confined case \(v\freeze \approx \SI{30}{km.s^{-1}}\) for \SI{0.2}{\um}
-grains but \(v\freeze \approx \SI{3000}{km.s^{-1}}\) for \SI{0.02}{\um}
-grains. Thus, for typical stream velocities of
-\SIrange{20}{100}{km.s^{-1}}, the small grains are always tightly
-coupled to the magnetic field, but the large grains are only loosely
-coupled for the faster streams.
-
-\subsection{Grain trajectories with tight magnetic coupling}
-\label{sec:grain-traj-with}
-
-We can now investigate how the results of the previous sections are
-modified by magnetic fields in the tight coupling limit.  For
-simplicity, we assume a uniform field in the incoming stream, with
-field lines oriented at an angle \(\theta\B\) to the velocity vector that
-defines the bow axis.  We also assume a super-alfvénic stream,
-\(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
-is unaffected by the magnetic field, and additionally assume
-\(\tau_* \ll \tau_{*, \text{max}}\), so that the back-reaction of the grain
-drag on the plasma is negligible (see previous section) and \(B\)
-remains uniform in magnitude and direction in the dust wave region,
-outside of the bow shock.
-
-In Appendix~\ref{sec:tight-magn-coupl}, we derive analytic and
-semi-analytic results in the limit of zero gas--grain drag, which is
-appropriate for inertia-confined dust waves. We find very different
-structures, depending on the orientation of the field.  For a parallel
-field (Fig.~\ref{fig:inertia-thB0}), the apex of the dust wave occurs
-at the same point, \(R\starstar\), as in the non-magnetic case, but
-the shape of the dust wave wings is more closed, being hemispherical
-rather than parabolic in shape.  For a perpendicular field
-(Fig.~\ref{fig:inertia-thB90}), on the other hand, grains in the apex
-region are dragged very close to the star and no dust wave forms
-there.  A dust wave can form in the wings, with impact parameter
-\(> R\starstar\), which is roughly parabolic in shape, but more
-swept-back than in the non-magnetic case.  Whether such a dust wave
-will exist in practice depends critically on the size and shape of the
-MHD wind-supported bow shock.
-
-In Figures~\ref{fig:frozen-stream} and~\ref{fig:frozen-trajectories}
-we show example results for drag-confined dust waves, which are
-calculated by numerically integrating the grain's equation of motion,
-as described in Appendix~\ref{sec:equat-moti-grains}. Apart from the
-inclusion of the magnetic field, the model parameters are the same as
-used in Figure~\ref{fig:phase-space-trajectories}, with the exception
-that the stream density is increased to \SI{10}{cm^{-3}}.\footnote{The
-  reason for using a higher density is to decrease the amplitude of
-  the radial oscillations of the trajectories, which allows the dust
-  wave structure to be more clearly perceived in the figures. } This
-time, we use quasi-parallel (\(\theta\B = \ang{10}\)) and
-quasi-perpendicular (\(\theta\B = \ang{75}\)) field orientations.  The
-quasi-parallel field is most similar to the non-magnetic case, and the
-models shown in the two upper panels of Figure~\ref{fig:frozen-stream}
-closely mirror the cases shown in
-Figure~\ref{fig:phase-space-trajectories}, with a limit cycle behavior
-when \(v_\infty = \SI{40}{km.s^{-1}}\) and stagnant drift when
-\(v_\infty = \SI{80}{km.s^{-1}}\).
-
-The principle difference from the 1-D axial trajectories discussed in
-\S~\ref{sec:grain-traj-along} is that the small \ang{10} misalignment
-of \(\bm{B}\) from the incident stream direction causes a slow
-sideways migration, which puts a finite limit on the time a grain can
-reside in front of the star.  This can be appreciated more clearly in
-Figure~\ref{fig:frozen-trajectories}, which shows the grain position
-and velocity along a sample streamline with initial impact parameter
-\(b = -0.4 R_\dag\) for the two quasi-parallel models.  In panel~a,
-corresponding to \(v_\infty = \SI{40}{km.s^{-1}}\), we see the same
-rip-and-snap-back cycle of de-coupling and re-coupling that was
-discussed previously, but only two periods of the cycle are completed
-before the grain's lateral migration takes it as far as
-\(y \approx +R_\dag\), at which point nothing can stop the gas stream from
-dragging it past the star and away.  All told, the grain remains in
-the apex region for about \(1/\sin\theta\B\) times longer than the crossing
-time, \(R_\dag / v_\infty\).
-
-In panel~b, corresponding to \(v_\infty = \SI{80}{km.s^{-1}}\), the grain
-settles for a while around the stagnant drift radius, \(R_\ddag\), after
-the initial rip and turn around.  Again, it slowly migrates sideways,
-and eventually recouples to the incident stream, but this time after
-reaching \(y \approx +R_\ddag\).  The grain residence time in the apex region,
-measured in crossing times, is slightly longer than in panel~a, but is
-of the same order.  In both these cases, a second, exterior dense
-shell is formed in addition to the hemispherical one produced by the
-initial turn around inside \(R_\dag\). In the limit-cycle case, it forms
-at the snap-back point, while in the stagnant-drift case, it forms at
-\(R_\ddag\) and is significantly denser than the interior shell (upper
-right panel of Fig.~\ref{fig:frozen-stream}).
-
-The assumptions behind these models break down when the grain
-trajectory intersects the outer shock of the dust-free wind-supported
-bow shock.  The increased gas density in the bow shock shell will
-reduce \(\Xi\), which is likely to cause gas--grain recoupling in the
-case of drag-confined dust waves (see also discussion in the final
-paragraph of \S~\ref{sec:exist-cond-separ}).  However, detailed
-modeling of this requires magnetohydrodynamical simulations, which are
-beyond the scope of this paper.  In Figure~\ref{fig:frozen-stream} we
-show in gray dotted lines the Wilkinoid surface \citep{Wilkin:1996a},
-which is an approximation to the shape of the inner bow shock, see
-\PaperI.  It can be seen that the majority of dust streamlines do not
-cross this surface until well into the wings of the bow, so that a
-separate exterior dust wave can exist for this quasi-parallel
-magnetic field orientation.
-
-This is no longer the case for the quasi-perpendicular field
-orientation, as illustrated in the lower panels of
-Figure~\ref{fig:frozen-stream}, where the behavior is similar to the
-perpendicular inertia-confined case studied in
-Appendix~\ref{sec:perp-magn-field}.  Although the grains decouple from
-the gas inside the rip point, for small impact parameters the magnetic
-geometry does not allow the radiation field to expel them until they
-are much nearer to the star.  Since the inner wind-supported bow shock
-radius is only a few times smaller than \(R_\dag\), it is possible that
-they will pass through the shock surface and re-couple before
-expulsion can occur.  For the \SI{40}{km.s^{-1}} model (lower left
-panel), all of the streamlines with impact parameters
-\(\abs{b} < R_\dag\) intersect the Wilkinoid surface before they are
-deflected, and so no separate dust wave would form in this case.  For
-the \SI{80}{km.s^{-1}} model (lower left panel), some of the
-streamlines (mainly those with \(b > 0\)) do manage to avoid crossing
-the bow shock surface, so it is possible that a dust wave may still
-form, although it would only be on one side of the axis.
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "dusty-bow-wave"
+%%% TeX-master: "bs-bw-dw-01"
 %%% End:

### 2019-02-26 papers/Papers1234/sec-strong-coupling.tex
Divide dust wave paper in three parts

\section{A simple model for stellar bows}
\label{sec:strong-gas-grain}

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
  \caption{Bow regimes in parameter space (\(v, n\)) of the external
    stream for main-sequence OB stars of different masses:
    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}.  In all
    cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
    coupling is assumed. Solid black lines of varying width show the
    bow size (star-apex separation, \(R_0\)), while gray shading shows
    the radiation bow wave regime, with lower border \(\tau = \eta\wind\) and
    upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
    depth through the bow.  For bows above the red solid line, the
    ionization front is trapped inside the bow.  Blue lines delineate
    different cooling regimes.  Above the thin blue line
    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
    forming a thin shocked shell.  Below the thick blue line
    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
    non-radiative.}
  \label{fig:zones-v-n-plane}
\end{figure*}

We consider the canonical case of a bow around a star of bolometric
luminosity, \(L\), with a radiatively driven wind, which is immersed
in an external stream of gas and dust with density, \(\rho\), and
velocity, \(v\).  The size and shape of the bow is determined by a
generalized balance of pressure (or, equivalently, momentum) between
internal and external sources.  We assume that the stream is
supersonic and super-alfvenic, so that the external pressure is
dominated by the ram pressure, \(\rho v^2\), and that dust grains and gas
are perfectly coupled by collisions (the breakdown of this assumption
is the topic of Paper~II).

Although dust grains typically constitute only a small fraction
\(Z\grain \sim 0.01\) of the mass of the external stream, they
nevertheless dominate the broad-band opacity at FUV, optical and IR
wavelengths if they are present.\footnote{%
  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
  dominates if the hydrogen neutral fraction is larger than
  \(\approx 0.001\), see discussion of ionization front trapping
  below.} %
The strong coupling assumption means that all the radiative forces
applied to the dust grains are directly felt by the gas also.

\subsection{Bows supported by radiation and wind}
\label{sec:three-bow-regimes}

The internal pressure is the sum of wind ram pressure and the
effective radiation pressure that acts on the bow shell.  The
radiative momentum loss rate of the star is \(L/c\) and the wind
momentum loss rate can be expressed as
\begin{equation}
  \label{eq:wind-efficiency}
  \dot{M} V = \eta\wind L / c \ , 
\end{equation}
where \(\eta\wind\) is the momentum efficiency of the wind, which is typically
\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
all of the stellar radiative momentum, emitted with rate \(L/c\), is
trapped by the bow shell.  In the single scattering limit,\footnote{%
  Although it may seem inconsistent to assume single scattering in the
  case of high optical depths, this is defensible for the following
  reasons. (1)~The grain albedo is not that high (typically
  \(\sim 0.5\) at ultraviolet through optical wavelengths). (2)~The
  scattered radiation field is more isotropic than the stellar field,
  leading to cancellation in the radiative flux. (3)~Absorbed
  radiation is re-emitted at infrared wavelengths, where the dust
  opacity is very much lower.} %
and temporarily neglecting the wind for clarity of exposition, then
pressure balance at the bow apex, a distance \(R_0\) along the
symmetry axis from the star is given by
\begin{equation}
  \label{eq:rad-press-balance-thick}
  \frac{L}{4 \pi c R_0^2} = \rho v^2 \ ,
\end{equation}
which yields a fiducial bow shock radius in this optically thick,
radiation-only limit as
\begin{equation}
  \label{eq:Rstar}
  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
\end{equation}

We now consider the opposite, optically thin limit.  If the total
opacity (gas plus dust) per total mass (gas plus dust) is \(\kappa\) (with
units of \si{cm^2.g^{-1}}), then the radiative acceleration is
\begin{equation}
  \label{eq:rad-accel}
  a_{\text{rad}} = \frac{\kappa L}{4 \pi c R^2} \ .
\end{equation}
Therefore, an incoming stream with initial velocity, \(v_\infty\), can be
brought to rest by radiation alone
% \footnote{%
%   For simplicity, we here ignore the effects of gravity, which are
%   important for low ratios of \(\kappa L / M\), see
%   \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
%   shocks, which are important as the velocity approaches the sound
%   speed, \(\sound\) (in \S~XX below, we show that the resultant
%   corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
at a distance \(R\starstar\) where
\begin{equation}
  \label{eq:rad-poten}
  \int_{R\starstar}^\infty a_{\text{rad}} \, dr = \tfrac12 v_\infty^2 \ , 
\end{equation}
yielding
\begin{equation}
  \label{eq:rad:R0}
  R\starstar = \frac{\kappa L}{2\pi c v_\infty^2} \ .
\end{equation}
On the other hand, we can also argue as in the optically thick case
above by approximating the bow shell as a surface, and balancing
stellar radiation pressure against the ram pressure of the incoming
stream.  The important difference when the shell is not optically
thick is that only a fraction \(1 - e^{-\tau}\) of the radiative momentum
is absorbed by the bow, so that
equation~\eqref{eq:rad-press-balance-thick} is replaced with
\begin{equation}
  \label{eq:rad-press-balance-tau}
  \frac{L (1 - e^{-\tau})}{4 \pi c R_0^2} = \rho v^2 \ .
\end{equation}
In the optically thin limit, \(1 - e^{-\tau} \approx \tau\), so these two
descriptions can be seen to agree (\(R_0 \to R\starstar\)) so long as
\begin{equation}
  \label{eq:tau-thin}
  \tau = 2 \kappa \rho R_0 \ ,
\end{equation}
which we will assume to hold generally.

Then, defining a fiducial optical depth,
\begin{equation}
  \label{eq:tau-star}
  \tau_* = \rho \kappa R_* \ ,
\end{equation}
and now reinstating the stellar wind ram pressure term
% \footnote{%
%   We implicitly assume that the interaction of the stellar wind with
%   the external stream can always be treated in the continuum limit.
%   This will be true if either the collisional mean free path or the
%   ion Larmor radius is much smaller than \(R_0\), which is almost
%   always the case.} %
from equation~\eqref{eq:wind-efficiency}, we find that the general bow
radius can be written in terms of the fiducial radius as
\begin{equation}
  \label{eq:R0-definition}
  R_0 = x R_* \ ,
\end{equation}
where \(x\) is the solution of
\begin{equation}
  \label{eq:rad-full-x}
  x^2 - \bigl(1 - e^{-2 \tau_* x} \bigr) - \eta\wind = 0 \ .
\end{equation}
Since this is a transcendental equation, \(x\) must be found
numerically, but we can write explicit expressions for three limiting
cases:
\begin{equation}
  \label{eq:x-cases}
  x \approx
  \begin{cases}
    \text{if \(\tau_* \gg 1\):} & (1 + \eta\wind)^{1/2}  \\
    \text{if \(\tau_*^2 \ll 1\):} & \tau_* + \bigl( \tau_*^2 + \eta\wind \bigr)^{1/2} \approx
    \begin{cases}
      \text{if \(\tau_*^2 \gg \eta\wind\):} & 2 \tau_*  \\
      \text{if \(\tau_*^2 \ll \eta\wind\):} & \eta\wind^{1/2} 
    \end{cases}
  \end{cases}
\end{equation}
The first case, \(x \approx (1 + \eta\wind)^{1/2}\), corresponds to a
\textit{radiation bow shock} (RBS); the second case,
\(x \approx 2 \tau_* \), corresponds to a \textit{radiation bow wave} (RBW);
and the third case, \(x \approx \eta\wind^{1/2}\), corresponds to a
\textit{wind bow shock} (WBS).  The two bow shock cases are similar in
that the external stream is oblivious to the presence of the star
until it suddenly hits the bow shock shell, differing only in whether
it is radiation or wind that is providing the internal pressure.  In
the intermediate bow wave case, on the other hand, the external stream
is gradually decelerated by absorption of photons as it approaches the
bow.\footnote{A shock can still form in this case, but shocked
  material constitutes only a small fraction of the total column
  density of the shell.}

\subsection{Dependence on stellar type}
\label{sec:depend-stell-type}

\begin{table*}
  \centering
  \caption{Stellar parameters for example stars}
  \label{tab:stars}
  \begin{tabular}{l S S S S S S S S S l}
    \toprule
    & {\(M / \si{M_\odot}\)} & {\(L_4\)}
    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta\wind \)}
    & {Sp.~Type} 
    & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
    & {\(S_{49}\)} & Figures 
    \\
    \midrule
    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
                   & \ref{fig:zones-v-n-plane}a, \ref{fig:existence-dust-wave}a,
                     \ref{fig:phase-space-trajectories}--~\ref{fig:frozen-trajectories} \\
    Main-sequence OB stars
    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
                   & \ref{fig:zones-v-n-plane}b, \ref{fig:existence-dust-wave}b \\
    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
                   & \ref{fig:zones-v-n-plane}c, \ref{fig:existence-dust-wave}c \\[\smallskipamount]
    Blue supergiant star
    & 33 & 30.2 & 20.2 & 0.93 & 0.3079 & {B0.7\,Ia} & 23.5 & 0.123 & 0.016
                   & \ref{fig:B-supergiant} \\[\smallskipamount]
    Red supergiant star
    & 20 & 15.6 & 100 & 0.015 & 0.0476 & {M1\,Ia} & 3.6 & 0.805 & 0
                   & \ref{fig:M-supergiant} \\ 
    \bottomrule
  \end{tabular}
\end{table*}

We now consider the application to bow shocks around main sequence OB
stars, as well as cool and hot supergiants, expressing stellar and
ambient parameters in terms of typical values as follows:
\begin{align*}
  \label{eq:stellar-parameters}
  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
\end{align*}
where \(\bar{m}\) is the mean mass per hydrogen nucleon
(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
abundances).  Note that \(\kappa = \SI{600}{cm^2.g^{-1}}\) corresponds to a
cross section of \(\approx \SI{e-21}{cm^2}\) per hydrogen nucleon, which is
typical for interstellar medium dust \citep{Bertoldi:1996a} at far
ultraviolet wavelengths, where OB stars emit most of their radiation.
In terms of these parameters, we can express the stellar wind momentum
efficiency as
\begin{equation}
  \label{eq:wind-eta-typical}
  \eta\wind = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
\end{equation}
and the fiducial radius and optical depth as
\begin{align}
  \label{eq:Rstar-typical}
  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
  \label{eq:taustar-typical}
  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
\end{align}
In Figure~\ref{fig:zones-v-n-plane}, we show results for the bow size
(apex distance, \(R_0\)) as a function of the density, \(n\), and
relative velocity, \(v_\infty\), of the external stream, with each panel
corresponding to a particular star, with parameters as shown in
Table~\ref{tab:stars}.  To facilitate comparison with previous work,
we choose stellar parameters similar to those used in the
hydrodynamical simulations of \citet{Meyer:2014b, Meyer:2016a,
  Meyer:2017a}, based on stellar evolution tracks for stars of
\SIlist{10;20;40}{M_\odot} \citep{Brott:2011a} and theoretical wind
prescriptions \citep{de-Jager:1988a, Vink:2000a}.  Although the
stellar parameters do evolve with time, they change relatively little
during the main-sequence lifetime of several million years.\footnote{%
  \label{fn:meyer-velocities-too-low}
  Note that we have recalculated the stellar wind terminal velocities,
  since the values given in the \citeauthor{Meyer:2014b} papers are
  troublingly low.  We have used the prescription
  \(V = 2.6 V_{\text{esc}}\), where
  \(V_{\text{esc}} = \left( 2 G M (1 - \Gamma_e)/ R \right)^{1/2}\) is the
  photospheric escape velocity, which is appropriate for strong
  line-driven winds with \(T_{\text{eff}} > \SI{21 000}{K}\)
  \citep{Lamers:1995a}.  We find velocities of
  \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
  observations and theory \citep{Vink:1999a} for O~stars, but at least
  two times higher than those cited by \citet{Meyer:2014b}. For
  main-sequence B~stars, wind column densities are too low to reliably
  measure the terminal velocity from near ultraviolet P~Cygni profiles
  \citep{Prinja:1989a}, and so the values are theory-dependent
  \citep{Krticka:2014a} and hence more uncertain.  A further
  complication is the existence of a subset of OB stars with
  anomalously weak winds \citep{Puls:2008a}, which in some cases is
  related to the presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
  \citep{Oskinova:2011b}.} %
The three examples are an early B~star (\SI{10}{M_\odot}), a late O~star
(\SI{20}{M_\odot}), and an early O~star (\SI{40}{M_\odot}), which cover the
range of luminosities and wind strengths expected from bow-producing
hot main sequence stars.  The luminosity is a steep function of
stellar mass (\(L \sim M^{2.5}\)) and the wind mass-loss rate is a steep
function of luminosity (\(\dot{M} \sim L^{2.2}\)), which means that the
wind momentum efficiency is also a steep function of mass
(\(\eta\wind \sim M^3\)), approaching unity for early O~stars, but falling to
less than 1\% for B~stars.

\begin{figure}
  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-RSG}
  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for a cool M-type
    supergiant instead of hot main sequence stars.  A smaller dust
    opacity is used, \(\kappa = \SI{60}{cm^2.g^{-1}}\), because of the
    reduced extinction efficiency at the optical/infrared wavelengths
    emitted by this star.}
  \label{fig:M-supergiant}
\end{figure}

It can be seen from Figure~\ref{fig:zones-v-n-plane} that the onset of
the radiation bow wave regime is very similar for the three
main-sequence stars, occurring at
\(n > \text{\numrange{20}{40}} \, v_{10}^2\).  An important
difference, however, is that for the \SI{40}{M_\odot} star, which has a
powerful wind, the radiation bow wave regime only occurs for a very
narrow range of densities, whereas for the \SI{10}{M_\odot} star, with a
much weaker wind, the regime is much broader, extending to
\(n < \num{e4} \, v_{10}^2\).  Another difference is the size scale of
the bows in this regime, which is
\(R_0 = \text{\SIrange{0.001}{0.003}{pc}}\) for the \SI{10}{M_\odot} star
if \(v_\infty = \SI{40}{km.s^{-1}}\), but \(R_0 \approx \SI{0.1}{pc}\) for the
\SI{40}{M_\odot} star, assuming the same inflow velocity.

Figure~\ref{fig:M-supergiant} shows results for a cool M-type
super-giant star with stellar parameters inspired by Betelgeuse
(\chemalpha~Orionis), as listed in Table~\ref{tab:stars}.  Unlike the
UV-dominated spectrum of the hot stars, this star emits predominantly
in the near-infrared, where the dust extinction efficiency is lower,
so we adopt a lower opacity of \SI{60}{cm^2.g^{-1}}.  This has the
effect of shifting the radiation bow wave regime to higher densities:
\(n = \text{\numrange{1000}{30 000}}\, v_{10}^2\) in this case.

\subsection{Effects of stellar gravity}
\label{sec:effects-gravity}

In principle, gravitational attraction from the star, of mass \(M\),
will partially counteract the radiative acceleration.  This can be
accounted for by replacing \(L\) with an effective luminosity
\newcommand\Edd{\ensuremath{_{\text{E}}}}
\begin{equation}
  \label{eq:effective-luminosity}
  L_{\text{eff}} = L \bigl(1 - \Gamma\Edd^{\,-1}\bigr) \ ,
\end{equation}
in which \(\Gamma\Edd\) is the Eddington factor:
\begin{equation}
  \label{eq:eddington-factor}
  \Gamma\Edd = \frac{\kappa L}{4\pi c G M} = 458.5 \, \frac{\kappa_{600} L_4}{ M } \ ,
\end{equation}
where, in the last expression, \(M\) is measured in solar masses.  For
the stars in Table~\ref{tab:stars}, we find
\(\Gamma\Edd \approx \text{\numrange{30}{400}}\), so gravity can be safely
ignored.  The only exception is when the optical depth of the bow is
very large: \(\tau > \ln\Gamma\Edd \sim 5\), in which case gravity may be
important in the outer parts of the shell (see
\citealt{Rodriguez-Ramirez:2016b}).

\section{Physical state of the bow shell}
\label{sec:phys-state-shock}

The bow shell consists of two parts: an inner zone of shocked stellar
wind, and an outer zone of decelerated ambient stream. For OB stars,
dust grains are present only in the ambient stream, whereas for cool
stars they will also be present in the stellar wind.  In the remainder
of this paper, we will concentrate on the OB star case, where it is
the outer zone that is most important observationally.  Bows are
typically detected via their infrared radiation (absorption and
re-emission by dust of stellar radiation), or by emission lines such
as the hydrogen H\(\alpha\) line.

% In the WBS and RBW case, this is also shocked

\subsection{Ionization state}
\label{sec:trapp-ioniz-front}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-BSG}
  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for an evolved
    B-type supergiant instead of main sequence stars.  This is similar
    to the early O MS star of Fig.~\ref{fig:zones-v-n-plane}\textit{c}
    in many respects, except for the trapping of the ionization front,
    which occurs for much lower outer stream densities.}
  \label{fig:B-supergiant}
\end{figure}

In this section we calculate whether the star is capable of
photoionizing the entire bow shock shell, or whether the ionization
front will be trapped within it.  The number of hydrogen
recombinations\footnote{%
  The diffuse field is treated in the on-the-spot approximation,
  assuming all emitted Lyman continuum photons are immediately
  re-absorbed locally, so the case~B recombination co-efficient,
  \(\alphaB = \num{2.6e-13}\, T_4^{-0.7}\, \si{cm^3.s^{-1}}\), is
  used, where \(T_4 = T/\SI{e4}{K}\).} %
per unit time per unit area in a fully ionized shell is
\begin{equation}
  \label{eq:shell-recombination-rate}
  \mathcal{R} = \alphaB n\shell^2 h\shell \ ,
\end{equation}
while the advective flux of hydrogen nuclei through the shock is 
\begin{equation}
  \label{eq:shell-advective-flux}
  \mathcal{A} = n v \ ,
\end{equation}
and the flux of hydrogen-ionizing photons
(\(h \nu > \SI{13.6}{eV}\)) incident on the inner edge of the shell is
\begin{equation}
  \label{eq:shell-ionizing-flux}
  \mathcal{F} = \frac{S} {4 \pi R_0^2} \ , 
\end{equation}
where \(S\) is the ionizing photon luminosity of the star.  Any shell
with \(\mathcal{R} + \mathcal{A} > \mathcal{F}\) cannot be entirely
photoionized by the star, and so must have trapped the ionization
front.

The ratio of advective particle flux to ionizing flux is, from
equations~\eqref{eq:Rstar}, \eqref{eq:shell-advective-flux},
\eqref{eq:shell-ionizing-flux},
\begin{equation}
  \label{eq:advective-over-ionizing-flux}
  \frac{\mathcal{A}}{\mathcal{F}} = \num{5.86e-5} \frac{x^2 L_4}{v_{10} S_{49}} \ , 
\end{equation}
where
\begin{equation*}
  S_{49} = S / \bigl( \SI{e49}{s^{-1}} \bigr) \ .
\end{equation*}
Numerical values of \(S_{49}\) for our three example stars are given
in Table~\ref{tab:stars}, taken from Figure~4 of
\citet{Sternberg:2003a}.  Since \(\mathcal{A} \ll \mathcal{F}\) in
nearly all cases, for clarity of exposition we ignore \(\mathcal{A}\)
in the following discussion, although it is included in quantitative
calculations.  The column density of the shocked shell can be found,
for example, from equations~(10) and~(12) of \citet{Wilkin:1996a} in
the limit \(v_\infty/V \to 0\) (Wilkin's parameter \(\alpha\)) and
\(\theta \to 0\).  This yields
\begin{equation}
  \label{eq:shocked-shell-column}
  n\shell h\shell = \tfrac34 n R_0 \ .
\end{equation}
Assuming strong cooling behind the shock,\footnote{%
  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
} %
the shell density is
\begin{equation}
  \label{eq:isothermal-shell-density}
  n\shell = \mathcal{M}_0^2 n \,
\end{equation}
where
\(\mathcal{M}_0 = v_\infty / \sound\) is the isothermal Mach number of the
external stream.\footnote{%
  \label{fn:temperature-dependence}
  The sound speed depends on the temperature and hydrogen and helium
  ionization fractions, \(y\) and \(y_{\text{He}}\) as
  \(\sound^2 = (1 + y + z_{\text{He}} y_{\text{He}}) (k T /
  \bar{m})\), where \(z_{\text{He}}\) is the helium nucleon abundance
  by number relative to hydrogen and
  \(k = \SI{1.3806503e-16}{erg.K^{-1}}\) is Boltzmann's constant.  We
  assume \(y = 1\), \(y_{\text{He}} = 0.5\), \(z_{\text{He}} = 0.09\),
  so that \(\sound = \num{11.4}\, T_4^{1/2}\, \si{km.s^{-1}}\). } %
Putting these together with equations~\eqref{eq:Rstar} and
~\eqref{eq:tau-star}, one finds that \(\mathcal{R} > \mathcal{F}\)
implies
\begin{equation}
  \label{eq:ifront-trap-x-cubed-taustar}
  x^3 \tau_* > \frac{4 S c \sound \bar{m}^2 \kappa}{3 \alpha L} \ .
\end{equation}
From equation~\eqref{eq:rad-full-x}, it can be seen that \(x\) depends
on the external stream parameters, \(n\), \(v_\infty\) only via
\(\tau_*\), and so equation~\eqref{eq:ifront-trap-x-cubed-taustar} is a
condition for \(\tau_*\), which, by using
equation~\eqref{eq:taustar-typical}, becomes a condition on
\(n / v_{10}^2\).  In the radiation bow shock case,
\(x = (1 + \eta\wind)^{1/2}\), and the condition can be written:
\begin{equation}
  \label{eq:ifront-trap-density-RBS}
  \text{RBS:}\quad
  \frac{n}{v_{10}^2} > \num{2.65e8} \, \frac{S_{49}^2 T_4^{3.4}}{L_4^3 (1 + \eta\wind)^3} \ .
\end{equation}
In the radiation bow wave case, \(x = 2\tau_*\), and the condition can be
written:
\begin{equation}
  \label{eq:ifront-trap-taustar-RBW}
  \text{RBW:}\quad
  \frac{n}{v_{10}^2} > \num{5.36e4} \, \frac{S_{49}^{1/2} T_4^{0.85} }{\kappa_{600}^{3/2} L_4^{3/2}} \ . 
\end{equation}
In the wind bow shock case, the result is the same as
equation~\eqref{eq:ifront-trap-density-RBS}, but changing the factor
\((1 + \eta\wind)^3\) to \(\eta\wind^3\).  For the example hot stars in
Table~\ref{tab:stars}, and assuming \(\kappa_{600} = 1\),
\(T_4 = 0.8\), the resulting density threshold is
\(n > (\text{\numrange{1000}{5000}})\, v_{10}^2\), depending only
weakly on the stellar parameters, which is shown by the red lines in
Figure~\ref{fig:zones-v-n-plane}.  For the \SI{10}{M_\odot} star, this is
in the radiation bow wave regime, whereas for the higher mass stars it
is in the radiation bow shock regime.  When the external stream is
denser than this, then the outer parts of the shocked shell may be
neutral instead of ionized, giving rise to a cometary compact \hii{}
region \citep{Mac-Low:1991a, Arthur:2006a}.  This is only necessarily
true, however, when the star is isolated.  If the star is in a cluster
environment, then the contribution of other nearby massive stars to
the ionizing radiation field must be considered.

Quite different results are obtained for a B-type supergiant star (see
Tab.~\ref{tab:stars} and Fig.~\ref{fig:B-supergiant}), which has a
similar bolometric luminosity and wind strength to the \SI{40}{M_\odot}
main-sequence star, but a hundred times lower ionizing luminosity.
This results in a far lower threshold for trapping the ionization
front of \(n > 40 v_{10}^2\).  The advective flux, \(\mathcal{A}\), is
relatively stronger for this star than for the main-sequence stars, but
even for \(v_{10} < 2\), where the effect is strongest, the change is
only of order the width of the dark red line in
Figure~\ref{fig:B-supergiant}.

In principle, when the ionization front trapping occurs in the bow
wave regime, then the curves for \(R_0\) will be modified in the
region above the red line because all of the ionizing radiation is
trapped in the shell due to gas opacity, which is not included in
equation~\eqref{eq:tau-thin}.  However, this only happens for our
\SI{10}{M_\odot} star, which has a relatively soft spectrum.
Table~\ref{tab:stars} gives the peak wavelength of the stellar
spectrum for this star as \(\lambda_{\text{eff}} = \SI{0.115}{\um}\), which
is significantly larger than the hydrogen ionization threshold at
\SI{0.0912}{\um}, meaning that only a small fraction of the total
stellar luminosity is in the EUV band and affected by the gas opacity.
The effect on \(R_0\) is therefore small.  For the higher mass stars,
\(\lambda_{\text{eff}} < \SI{0.0912}{\um}\), so the majority of the
luminosity is in the EUV band, but in these cases the ionization front
trapping occurs well inside the radiation bow shock zone, where the
dust optical depth is already sufficient to trap all of the radiative
momentum.

\subsection{Efficiency of radiative cooling}
\label{sec:radi-cool-lengths}
%
In this section, we calculate whether the radiative cooling is
sufficiently rapid behind the bow shock to allow the formation of a
thin, dense shell.  In general, cooling is least efficient at low
densities, so we will assume that the wind bow shock regime applies
unless otherwise specified. We label quantities just outside the shock
by the subscript ``0'', quantities just inside the shock (after
thermalization, but before any radiative cooling) by the subscript
``1'', and quantities after the gas has cooled back to the
photoionization equilibrium temperature by the subscript ``2''.
Assuming a ratio of specific heats, \(\gamma = 5/3\), the relation between
the pre-shock and immediate post-shock quantities is
\begin{align}
  % \M_1 &= \left(\frac{\M_0^2 + 3} {5\M_0^2 - 1}\right)^{1/2} \\
  \label{eq:shock-n-jump}
  \frac{n_1}{n_0} &= \frac{4 \M_0^2} {\M_0^2 + 3} \\
  \label{eq:shock-T-jump}
  \frac{T_1}{T_0} &= \tfrac1{16} \bigl( 5\M_0^2 - 1 \bigr) \bigl( 1 + 3/\M_0^2 \bigr) \\
  \label{eq:shock-v-jump}
  \frac{v_1}{v_0} &= \left(\frac{n_1}{n_0}\right)^{-1} \ ,
\end{align}
where \(\M_0 = v_0 / \sound\).  The cooling length of the post-shock
gas can be written as
\newcommand\cool{\ensuremath{_{\text{cool}}}}
\begin{equation}
  \label{eq:dcool}
  d\cool = \frac{3 P_1 v_1} { 2 \bigl(  \mathcal{L}_1 - \mathcal{G}_1 \bigr) }\ ,  
\end{equation}
where \(P_1\) is the thermal pressure and \(\mathcal{L}_1\),
\(\mathcal{G}_1\) are the volumetric radiative cooling and heating
rates.  For fully photoionized gas, we have
\(P_1 \approx 2 n_1 k T_1\), \(\mathcal{L}_1 = n_1^2 \Lambda(T_1)\), and
\(\mathcal{G}_1 = n_1^2 \Gamma(T_1)\), where \(\Lambda(T)\) is the cooling
coefficient, which is dominated by metal emission lines that are
excited by electron collisions, and \(\Gamma(T)\) is the heating
coefficient, which is dominated by hydrogen photo-electrons
\citep{Osterbrock:2006a}. The cooling coefficient has a maximum around
\SI{e5}{K}, and for typical ISM abundances can be approximated as
follows:
\begin{align}
  \label{eq:cooling-coefficient}
  \Lambda_{\text{warm}} &= \num{3.3e-24} \, T_4^{2.3} \, \si{erg.cm^{3}.s^{-1}}\\
  \Lambda_{\text{hot}} &= \num{e-20} \, T_4^{-1}\, \si{erg.cm^{3}.s^{-1}} \\
  \Lambda &= \left( \Lambda_{\text{warm}}^{-k} +  \Lambda_{\text{hot}}^{-k} \right)^{-1/k}
      \quad \text{with} \quad k = 3 \ ,
\end{align}
which is valid in the range \(0.7 < T_4 < 1000\).  We approximate the heating coefficient as
\begin{equation}
  \label{eq:heating-coefficient}
  \Gamma = \num{1.77e-24} \, T_4^{-1/2} \, \si{erg.cm^{3}.s^{-1}} \ ,
\end{equation}
where the coefficient is chosen so as to give \(\Gamma = \Lambda\) at
an equilibrium temperature of \(T_4 = 0.8\).

In Figure~\ref{fig:zones-v-n-plane} we show curves calculated from
equations~\eqref{eq:shock-n-jump} to~\eqref{eq:heating-coefficient},
corresponding to \(d\cool = R_0\) (thick blue line) and
\(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
thickness in the efficient cooling case.  In this context, \(n_0 = n\)
and \(n_2 = n\shell\), so that \(h_0\) follows from
equations~\eqref{eq:shocked-shell-column}
and~\eqref{eq:isothermal-shell-density} as
\begin{equation}
  \label{eq:strong-cooling-h0}
  h_0 = \tfrac34 \M_0^{-2} R_0 \ .
\end{equation}
The bends in the curves at \(v \approx \SI{50}{km.s^{-1}}\) are due to the
maximum in the cooling coefficient \(\Lambda(T)\) around
\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
blue line, radiative cooling is so efficient that the bow shock can be
considered isothermal, and so the shell is dense and thin (at least,
in the apex region).  It can be seen that the ionization front
trapping always occurs at densities larger than this, which justifies
the use of equation~\eqref{eq:isothermal-shell-density} in the
previous section.  For bows with outer stream densities below the
thick blue line, cooling is unimportant and the bow shock can be
considered non-radiative.  In this case the shell is thicker than in
the radiative case,
\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
  An approximate value can be found from
  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
  Consideration of the slight increase in density between the shock
  and the contact/tangential discontinuity reduces this value by 5--10\%.} %
For bows with outer stream densities between the two blue lines,
cooling does occur, albeit inefficiently, so that the shell thickness
is set by \(d\cool\) rather than \(h_0\).

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "bs-bw-dw-01"
%%% End:

### 2019-02-26 papers/Papers1234/sec-weak-coupling.tex
Divide dust wave paper in three parts

\section{Introduction}
\label{sec:rip-introduction}

In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
charging and dynamics, subject to radiation and drag forces, in order
to determine the rip point where gas--grain coupling catastrophically
breaks down.  This is used to determine existence conditions for the
presence of a decoupled dust wave.
%
In \S~\ref{sec:magn-effects-grain} we consider the additional coupling
between the grains and the plasma's magnetic field, and how this
effects the existence and structure of dust waves.
%
A series of appendices provide additional technical information on
dust physics (Appendix~\ref{sec:cloudy-models-dust}), analytical
models of the shape of dust waves in the drag-free limit
(Appendix~\ref{sec:gas-free-bow}), and the numerical calculation of
grain trajectories (Appendix~\ref{sec:equat-moti-grains}).

\section{Imperfect coupling between gas and dust}
\label{sec:imperf-coupl-betw}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/test-Fdrag-components}
  \caption{Contributions of different collider species to the
    dimensionless drag force, \(f\drag / f_*\), as a function of
    gas--grain slip velocity, \(w\).  Solid lines show the Coulomb
    (electrostatic) drag, while dashed lines show the Epstein
    (solid-body) drag.  Results are shown for dimensionless grain
    potential \(\phi = 10\).  All Coulomb forces scale with
    \(\phi^2\), while the Epstein forces are independent of \(\phi\).  The
    species labelled ``CNO++'' represents the combined effect of all
    metals (see footnote~\ref{fn:metal-drag}).}
  \label{fig:drag-components}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/test-Fdrag-param-space}
  \caption{Regimes of gas--grain drag as a function of slip velocity
    and grain potential.  The different regimes are indicated by bold
    roman numerals, as explained in
    Table~\ref{tab:fdrag-regimes}. Blue shading indicates regions
    dominated by Epstein (solid-body) drag, whereas red and green
    shading indicate regions dominated by Coulomb drag due to protons
    and electrons, respectively.  In each case, the saturated color
    represents a contribution \(> 70\%\) of the relevant component to
    the total drag force, while progressively lighter shading
    represents the \(> 60\%\) and \(> 50\%\) levels.  The thick white
    dotted line indicates the transition between the subthermal and
    superthermal regimes for protons, while the thin white dotted line
    indicates the corresponding transition for electrons.  Contours
    show the total drag force in units of \(f_*\) (see
    eq.~[\ref{eq:fstar}]) in decade intervals from \(0.1\) to
    \(10^4\), as labelled.  Results are shown for
    \(T = \SI{8000}{K}\) and \(n = \SI{100}{cm^{-3}}\), but the
    differences are very slight throughout the ranges
    \(T = \text{\SIrange{5000}{15000}{K}}\) and
    \(n = \text{\SIrange{e-3}{e6}{cm^{-3}}}\).}
  \label{fig:drag-v-phi-plane}
\end{figure}

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
  \caption{Dimensionless drag force, \(f\drag / f_*\), as a function
    of gas--grain slip velocity, \(w\), for different values of the
    grain potential in thermal units, \(\phi\).  Contributions from
    proton and electron Coulomb (electrostatic) drag, as well as
    Epstein (solid-body) drag are indicated.  Examples of subsonic and
    highly supersonic stable drift velocities are shown (thin dark
    blue arrows), where the drag force is in equilibrium with the
    radiation force (thick dark blue dashed lines), while blue shading
    indicates the unstable, mildly supersonic velocity regime, where
    no stable drift equilibrium exists.  Inset graph shows \(\phi\) as a
    function of the radiation parameter,
    \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a log--linear scale
    for a collection of Cloudy models (see
    Appendix~\ref{sec:cloudy-models-dust}).}
  \label{fig:gas-grain-drag-photoionized}
\end{figure*}

% \begin{figure}
%   \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
%   \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
%     gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
%   \label{fig:decouple-v-n-plane}
% \end{figure}

If the radiation field is sufficiently strong, then the collisional
coupling between grains and gas will break down.  In this section, we
calculate the regions of star+stream parameter space where this might
occur, leading to a separation of the bow into an outer dust wave and
an inner, dust-free bow shock.

\subsection{Drag force on grains}
\label{sec:drag-force-grains}

\begin{table}
  \centering
  \caption{Regimes of drag force as function of grain potential and slip speed}
  \label{tab:fdrag-regimes}
  \renewcommand\arraystretch{1.3}
  \resizebox{\linewidth}{!}{%
    \begin{tabular}{@{}r l l l@{}}
    \toprule
      & Regime & Approximate criteria & \(f\drag / f_*\) \\ \midrule
      I & Epstein subsonic & \(\phi^2 \ll 1\)
                             and \(w_{10} < 1\) & \(1.5\, w_{10}\) \\
      II & Epstein supersonic & \(w_{10} > 1\)
                                and \(w_{10} > 5\,\abs{\phi}\)& \( w_{10}^2\) \\
      III & Coulomb p\(^+\) subthermal & \(\phi^2 > 1\)
                                         and \(w_{10} < 1\) & \((1 + 20\, \phi^2)\,
                                                              w_{10}\) \\
    % & Coulomb p\(^+\) peak & \(\phi^2 > 1\)
    %                          and \(w_{10} \approx 1\) & \(1 + 10\, \phi^2\) \\
      IV & Coulomb p\(^+\) superthermal & \(\phi^2 > 1\)
                                          and \(1 < w_{10} < 5\) & \(w_{10}^2
                                                                   + 10\, \phi^2/w_{10}^2 \) \\
      V & Coulomb e\(^-\) subthermal & \(\phi^2 > 20\)
                                 and \(5 < w_{10} < 42\) & \(0.48\, \phi^2 \,
                                                           w_{10}\) \\
    \bottomrule
  \end{tabular}
  }
\end{table}

The drag force on a charged dust grain moving at a relative speed
\(w\) through a plasma has contributions from both direct collisions
and from electrostatic Coulomb interactions with ions and electrons.
We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
considering the contributions from protons, electrons, helium
ions,\footnote{Helium is assumed to be singly ionized, leading to only
  a small contribution to the drag force.  For much hotter stars, such
  as the central stars of planetary nebulae, helium may be doubly
  ionized, which leads to a fourfold increase in its Coulomb drag
  contribution, which is significant for \(w < \SI{5}{km.s^{-1}}\).} %
and metal ions.\footnote{%
  \label{fn:metal-drag}
  All metals are lumped together as a single species, assuming
  standard \hii{} region gas-phase abundances.  They are dominated by
  C and O, with minor contributions from N and Ne.  The total
  abundance is \num{8.5e-4} and the effective atomic weight is
  \num{15.3}.  All are assumed to be doubly ionized.  Their largest
  relative contribution to the drag force is for
  \(w < \SI{2}{km.s^{-1}}\), but is less than 1\% even there.} %
Results are shown in Figure~\ref{fig:drag-components}, where dashed
lines correspond to direct solid body collisions and solid lines to
electrostatic interactions.  The latter depend on the grain potential,
which is described in dimensionless terms by \(\phi\), which is the
electrostatic potential energy of a unit charge at the surface of a
grain of charge \(z\grain\) and radius \(a\), in units of the
characteristic thermal energy of a gas particle:
\begin{equation}
  \label{eq:phi-potential}
  \phi = \frac{e^2 z\grain}{a kT} \ .
\end{equation}
The electrostatic contributions to \(f\drag\) are proportional to
\(\phi^2\) (results are shown for \(\abs{\phi} = 10\)), whereas the
solid-body contributions are independent of \(\phi\).  The drag force is
put in dimensionless units by dividing by a characteristic force:
\begin{equation}
  \label{eq:fstar}
  f_* = 2 n k T \cdot \pi a^2 \ , 
\end{equation}
which is approximately\footnote{%
  To simplify the exposition, the gas pressure in this section is
  calculated assuming a fully ionized, pure hydrogen plasma, yielding
  \(P\gas = 2 n k T\). For typical ISM abundances, the contribution of
  helium and its corresponding electrons yield a correction to this of
  order 5\%.  The required modifications when a cool star interacts
  with a predominantly neutral gas stream are discussed later.  } %
the ionized gas pressure multiplied by the grain geometric cross
section.

For grains with low electric charge, \(\phi^2 \ll 1\), the drag force is
dominated by direct collisions of protons with the grain (dashed red
line in Fig.~\ref{fig:drag-components}).  The gas collisional mean
free path is much larger than the grain size, so the drag is in the
Epstein regime \citep{Weidenschilling:1977b}.
% This is illustrated by
% the \(\phi = 0.25\) case (blue line) in
% Figure~\ref{fig:gas-grain-drag-photoionized}.
As the relative gas--grain slip speed, \(w\), increases, \(f\drag\)
first increases linearly with \(w\) reaching \(f\drag \approx f_*\) at
\(w = \sound \approx \SI{10}{km.s^{-1}}\), then transitions to a quadratic
increase in the supersonic regime.

As \(\abs{\phi}\) increases, long-range electrostatic interactions with
protons within the Debye radius (Coulomb drag) become increasingly
important at subsonic relative velocities, as shown by the solid lines
in Figure~\ref{fig:drag-components}).
% in
% Figure~\ref{fig:gas-grain-drag-photoionized} by the orange
% (\(\phi = 1\)), green (\(\phi = 4\)), and red (\(\phi = 16\)) lines.
However, the Coulomb drag has a peak when \(w\) is equal to the
thermal speed of the colliders, which is
\(\approx \SI{10}{km.s^{-1}}\) for protons, giving a maximum strength of
\begin{equation}
  \label{eq:fdrag-maximum}
  f_{\mathrm{max}} = 0.5\, (\ln\Lambda)\, \phi^2 f_* \approx 10\, \phi^2 f_* \ , 
\end{equation}
where \(\Lambda\) is the plasma parameter (number of particles within a
Debye volume), such that
\(\ln\Lambda = 23.267 + 1.5 \ln T_4 - 0.5 \ln n\).  At highly super-thermal
speeds, the Coulomb drag falls asymptotically as
\(f\drag \propto 1 / w^{2}\).  The thermal speed of electrons is higher than
that of the protons by a factor of \((m_p / m_e)^{1/2}\), so that the
electron Coulomb drag (solid light blue line) gives a second peak of
similar strength, but at \(w \approx \SI{430}{km.s^{-1}}\).  The behavior of
\(f\drag\) in all these different regimes is summarised in
Table~\ref{tab:fdrag-regimes}, in terms of \(\phi\) and
\(w_{10} = w / \SI{10}{km.s^{-1}}\).  This is further illustrated in
Figure~\ref{fig:drag-v-phi-plane}, where each of the drag regimes is
located on the \((w, \abs{\phi})\) plane.

% \begin{equation}
%   \label{eq:fdrag-regimes}
%   f\drag \approx
%   \begin{cases}
%     \text{Epstein subsonic (\(\phi^2 \ll 1\) and \(w_{10} < 1\)):}
%     & w_{10}\, f_* \\
%     \text{Epstein supersonic (\(\phi^2 \ll 1\) and \(w_{10} > 1\)):}
%     & w_{10}^2\, f_* \\
%     \text{Coulomb p\(^+\) subthermal (\(\phi^2 > 1\) and \(w_{10} < 1\)):}
%     & (1 + 20 \phi^2)\, w_{10}\, f_* \\
%     \text{Coulomb p\(^+\) peak (\(\phi^2 > 1\) and \(w_{10} \approx 1\)):}
%     & (1 + 10 \phi^2)\, f_* \\
%     \text{Coulomb p\(^+\) superthermal (\(\phi^2 > 1\) and \(1 < w_{10} < 5\)):}
%     & (w_{10}^2 + 10 \phi^2/w_{10}^2) \, f_* \\
%     \text{Coulomb e\(^-\) subthermal (\(\phi^2 > 20\) and \(5 < w_{10} < 42\)):}
%     & 0.48 \phi^2 \, w_{10}\, f_* \\
%   \end{cases}
% \end{equation}

% Or \Lambda = (4 pi / 3) n r_D^3?
% Where Debye length is r_D^2 = k T / 4 pi n e^2
% => \Lambda = n r_D (4 pi / 3) k T / 4 pi n e^2
% = k T r_D / 3 e^2
% This is 9 times less than the other expression
% Anyway, from kappa notes I have
% \ln\Lambda = 9.452 + 1.5 ln(T) - 0.5 ln(n)

% If I am going to use log10, then the coefficients get divided by
% ln(10) = 2.30258509299, and if we use T4, then we add 1.5 ln(1e4) =
% 13.815.  So we get 23.267 + 0.651 log10(T4) - 0.217 log10(n).  Nope,
% best with natural log

\subsection{Gas--grain separation: drift and rip}
\label{sec:gas-grain-separ}

In Appendix~\ref{sec:gas-free-bow} we calculate the behaviour of an
incoming stream of dust grains, subject only to the repulsive
radiation force from a star.  For an initial inward radial trajectory,
the dust grain motion is decelerated and turned around, reaching a
minimum radius \(R\starstar\), given by equation~\eqref{eq:dust-r0}.
This drag-free radiative turnaround radius, \(R\starstar\), is smaller
for higher initial inward velocities, but is independent of the
density of the incoming stream.  We are now in a position to see how
gas--grain drag will modify this picture.

From equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar}, we can
write the radiation force acting on a grain as
\begin{equation}
  \label{eq:frad-Xi}
  f\rad = \Qp\, \Xi\, f_* \ ,
\end{equation}
where \(\Qp\) is the grain's radiation pressure efficiency (see
footnote~\ref{fn:Qp} in Appendix~\ref{sec:gas-free-bow}) and \(\Xi\) is
the local radiation parameter, defined as the ratio of direct stellar
radiation pressure to gas pressure:
\begin{equation}
  \label{eq:Xi-Prad-over-Pgas}
  \Xi \equiv \frac{P\rad}{P\gas} \approx \frac{L}{4 \pi R^2 c\, (2 n k T)} \ ,
\end{equation}
where the last expression corresponds to the optically thin limit.
The grain potential \(\phi\) is also primarily determined by \(\Xi\), as
shown in Appendix~\ref{sec:cloudy-models-dust} and the inset graph of
Figure~\ref{fig:gas-grain-drag-photoionized}, but with a slow
dependence, which can be approximated as
\begin{equation}
  \label{eq:phi-vs-Xi}
  \phi(\Xi) \approx 1.5 \bigl( 2.3 +  \ln \Xi \bigr) \ .
\end{equation}
There are also slight secondary dependencies on the grain composition and
stellar spectrum.  The relationship given in eq.~\eqref{eq:phi-vs-Xi}
is appropriate for graphite grains and for stellar effective
temperatures in the range \SIrange{20}{30}{kK}.  For hotter stars than
this, \(\phi\) should be multiplied by a further factor of \(1.5\), while
for silicate grains it should be divided by \(1.5\).

In the outer regions of the photoionized volume around an OB star,
close to the ionization front, the radiation parameter is low, with
typical value \(\Xi \sim 0.1\).  In this regime, the negative charge
current at the grain surface due to electron collisions is roughly in
balance with the positive current due to the ultraviolet photoelectric
effect \citep{Weingartner:2001b}, leading to a low grain potential,
\(\abs{\phi} < 1\), which may be positive or negative.  The low
\(\Xi\) means that the radiative force is also weak:
\(f\rad \sim 0.1 f_*\) from equation~\eqref{eq:frad-Xi} if
\(\Qp \sim 1\) at UV wavelengths, which is true for all but the smallest
grains.  Thus, from the equations for \(f\drag\) given in
Table~\ref{tab:fdrag-regimes}, the radiative force can be balanced by
Epstein drag if \(w_{10} \sim 0.1\), leading to a small equilibrium drift
velocity, \(w\drift < \SI{1}{km.s^{-1}}\), of the grains with respect
to the gas.  This drift is much smaller than the inward stream
velocities that we are considering
(\(v_\infty > \SI{10}{km.s^{-1}}\)), so the dust follows the gas stream at
a slightly reduced velocity (\(< 10\%\)), and (by mass conservation) a
slightly increased density.  Each grain exerts an exactly opposite
force to \(f\drag\) upon the gas, but since the dust-gas mass ratio,
\(Z\grain\), is small, this produces a negligible acceleration of the
gas.

\begin{table}
  \caption{Critical values of radiation parameter at the rip point: \(\Xi_\dag\)}
  \centering
  \begin{tabular*}{0.75\columnwidth}{l @{\quad\quad\quad\quad} S S} \toprule
    & \multicolumn{2}{c}{Grain composition} \\
    Spectrum & {Graphite} & {Silicate}
    \\ \midrule
    B star & 1000 +- 400 & 350 +- 150 \\
    O star & 3000 +- 500 & 2500 +- 500 \\
    \bottomrule
    \addlinespace
    \multicolumn{3}{@{}p{0.75\columnwidth}@{}}{
    Calculated from the Cloudy models shown in Figure~\ref{fig:drift-gn}. 
    Uncertainties represent variations with grain size and gas density. 
    See Appendix~\ref{sec:cloudy-models-dust} for further details.}
  \end{tabular*}
  \label{tab:Xi-rip}
\end{table}

As the dusty stream approaches the star, the radiation parameter
\(\Xi\) will increase, with a dependence of \(R^{-2}\) once the stream
is well inside the ionization front.  This increases \(f\rad\)
(eq.~[\ref{eq:frad-Xi}]), but also increases the grain potential,
\(\phi\) (eq.~[\ref{eq:phi-vs-Xi}]) due to the increasing dominance of
grain charging by photoelectric ejection.  Initially, this results in
a lowering of the equilibrium drift velocity to \(w_{10} \sim 0.01\) as
the Coulomb drag kicks in (see Appendix~\ref{sec:cloudy-models-dust}).
However, at smaller radii the slow logarithmic increase in
\(\phi(\Xi)\) means that the drift velocity must start increasing again to
accommodate the linear increase of \(f\rad(\Xi)\).  Eventually,
\(f\rad\) exceeds \(f_{\mathrm{max}}\), the maximum drag force that
proton Coulomb interactions can provide
(eq.~[\ref{eq:fdrag-maximum}]).  This occurs at a critical value of
the radiation parameter, which we denote the \textit{rip point}:
\(\Xi_\dag \sim 1000\).  The variations in \(\Xi_\dag\) with star and grain
parameters, which are of order \SI{+- 0.5}{dex}, are listed in
Table~\ref{tab:Xi-rip} and illustrated graphically in
Figure~\ref{fig:drift-gn}.  The radius of the rip point, \(R_\dag\), can
be expressed in terms of \(R_*\), the fiducial optically thick bow
shock radius introduced in \S~\ref{sec:strong-gas-grain}:
\begin{equation}
  \label{eq:Rdag-over-Rstar}
  R_\dag = \frac{v_\infty}{\sound}\, \Xi_\dag^{-1/2} R_* \approx v_{10}\, \Xi_\dag^{-1/2} R_* \ ,
\end{equation}
where we have made use of equations~\eqref{eq:Rstar}
and~\eqref{eq:Xi-Prad-over-Pgas}.

What happens to the dust grain following this catastrophic breakdown
of gas--grain coupling depends on the relation between the rip point
radius, \(R_\dag\), and the drag-free radiative turnaround radius,
\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
will still carry it in as far as \(R\starstar\) and the initial
trajectory will be almost identical to that described in
Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
being turned around by the radiation field and pushed out past
\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
dragged back for a second approach.\footnote{If the initial impact
  parameter of the trajectory is not strictly \(b = 0\), then the
  resultant lateral component of \(f\rad\) will mean that \(b\) will
  be much increased for the second approach.} %
We will refer to this as an \textit{inertia-confined dust wave}
(IDW).  From equations~(\ref{eq:Rdag-over-Rstar},
\ref{eq:Rstarstar-over-Rstar},
\ref{eq:dust-wave-high-density-condition}), the condition
\(R_\dag > R\starstar\) corresponds to
\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
by the gas carries the grain closer to the star than its inertia would
naturally take it.  When the grain finally decouples at \(R_\dag\) it
experiences a much higher unbalanced \(f\rad\), which can initially
accelerate it to outward velocities significantly higher than the
inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
as a \textit{drag-confined dust wave} (DDW).

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/existence-dust-wave}
  \caption{Regions of stream parameter space \((v, n)\) where dust
    waves may form around main-sequence OB stars of
    \SIlist{10;20;40}{M_\odot} (see Tab.~\ref{tab:stars}).  Figure is
    similar to Fig.~\ref{fig:zones-v-n-plane}, except that the
    velocity axis is logarithmic and extends out to
    \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show parameters
    where dust waves may be allowed in the cases of large
    (\(a = \SI{0.2}{\um}\)) and small (\(a = \SI{0.02}{\um}\))
    graphite and silicate grains, as labeled in the left panel.  For
    \((v, n)\) outside of these shapes, dust waves cannot occur for
    the reasons indicated by labeled orange arrows in the center
    panel.  Labeled dashed lines in the right panel show the
    correspondence between the region boundaries and each dust wave
    existence condition given in
    equations~(\ref{eq:dust-wave-velocity-condition},
    \ref{eq:dust-wave-low-density-condition},
    \ref{eq:dust-wave-high-density-condition}). Heavy dashed lines in
    the left panel show where the rip point and the drag-free
    turnaround radius coincide.  Dust waves above these lines are drag
    confined, while dust waves below the lines are inertia confined.
  }
  \label{fig:existence-dust-wave}
\end{figure*}

\subsection{Existence conditions for dust waves}
\label{sec:exist-cond-separ}

In order for a separate outer dust wave to exist, it is necessary for
the grains to decouple from the incoming gas stream before the stream
hits the hydrodynamic bow shock caused by the stellar wind.  The wind
bow shock radius is \(R_0 = \eta\wind^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]),
where \(\eta\wind\) is the wind momentum efficiency
(eq.~[\ref{eq:wind-eta-typical}]).  Therefore, the condition
\(R_\dag > R_0\) becomes from equation~\eqref{eq:Rdag-over-Rstar}:
\begin{equation}
  \label{eq:dust-wave-velocity-condition}
  v_{10} > v_{10,\text{min}} = \bigl( \Xi_\dag \, \eta\wind \bigr)^{1/2} \ . 
\end{equation}
For O stars, the wind efficiency is generally high (\(\eta\wind > 0.1\)) and
\(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
exist when the stream velocity is very high
(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
can be much weaker (\(\eta\wind < 0.01\)) and \(\Xi_\dag\) is also smaller, so
that dust waves are permitted by this criterion for much lower stream
velocities: (\(v_\infty > \SI{30}{km.s^{-1}}\)).

However, there are other conditions that need to be satisfied in order
for the dust wave to exist.  For instance, the drag-free turnaround
radius must also be outside the bow shock: \(R\starstar > R_0\),
otherwise the radiation is incapable of repelling the grain
opportunely, even once it has decoupled from the gas.  From
equations~\eqref{eq:Rstar}, \eqref{eq:tau-star},
and~\eqref{eq:dust-r0} we find
\begin{equation}
  \label{eq:Rstarstar-over-Rstar}
  \frac{R\starstar}{R_*} = \frac{2 \sigma\grain \Qp \tau_*}{\kappa m\grain} \ , 
\end{equation}
so, if we define a single-grain opacity as
\(\kappa\grain = \sigma\grain \Qp / m\grain\), then this condition becomes
\begin{equation}
  \label{eq:dust-wave-low-density-condition}
  \tau_* >  \tau_{*,\text{min}} = 0.5\, \frac{\kappa}{\kappa\grain}\, \eta\wind^{1/2} 
  % \frac{\kappa \eta\wind^{1/2}}{2 \kappa\grain}
  \ . 
\end{equation}
The average value of the factor \(\kappa / \kappa\grain\) over the entire grain
population must be equal to the dust--gas mass ratio,
\(Z\grain \approx 0.01\), but the factor will vary between grains, according
to their size and composition.\footnote{%
  Remember that \(\kappa\) is the opacity per unit mass of gas, while
  \(\kappa\grain\) is the opacity per unit mass of a particular grain. In
  both cases, averaged over the stellar spectrum.} %
In particular, it will be relatively larger for the largest grains
(\(a \approx \SI{0.2}{\um}\)), which dominate the total dust mass, and
smaller for the smaller grains (\(a \approx \SI{0.02}{\um}\)), which
dominate the UV opacity.  Given the dependence of \(\tau_*\) on the
stream parameters (eq.~[\ref{eq:taustar-typical}]), for a given
stellar luminosity this condition corresponds to a minimum value for
\(n / v_\infty^2\).

A third condition comes from requiring \(R_\dag > R_0\) in the radiation
bow wave regime (see \S~\ref{sec:three-bow-regimes}), where
\(R_0 \approx 2 \tau_* R_*\).  This yields
\begin{equation}
  \label{eq:dust-wave-high-density-condition}
  \tau_* < \tau_{*,\text{max}} = 0.5\, v_{10}\, \Xi_\dag^{-1/2} \ , 
\end{equation}
which, for a given stellar luminosity, corresponds to a maximum value
for \(n / v_\infty^4\).  Thus, for a given stream velocity that satisfies
equation~\eqref{eq:dust-wave-velocity-condition},
equations~(\ref{eq:dust-wave-low-density-condition},
\ref{eq:dust-wave-high-density-condition}) determine respectively the
minimum and maximum stream density for which a dust wave can exist.

The combined effects of the three conditions are illustrated in
Figure~\ref{fig:existence-dust-wave} for each of the three example
main sequence stars from Table~\ref{tab:stars}.  Further restrictions
on the existence of dust waves arise when the effects of magnetic
fields are considered, as will be discussed in
\S~\ref{sec:magn-effects-grain} below.  Note that the three conditions
are restrictions solely on the formation of an \textit{outer} dust
wave, that is, outside of the wind-supported hydrodynamic bow shock.
In the case of the equation~\eqref{eq:dust-wave-low-density-condition}
condition, there is a further possibility: if the gas--grain coupling
(and magnetic coupling) is so weak that it is still unimportant at the
higher densities found in the bow shock shell, then an
inertia-confined \textit{inner} dust wave may form inside the bow
shock, even when \(\tau_* < \tau_{*,\text{min}}\).  Although the same might
be thought to apply to the condition of
equation~\eqref{eq:dust-wave-velocity-condition}, this is not the
case, since the density compression in the bow shock will reduce the
radiation parameter, \(\Xi\), which moves the rip point, \(R_\dag\), to an
even smaller radius.  Therefore, if radiation has not managed to
decouple a grain before it passes through the shock, it is unlikely to
be able to do it afterwards.

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/dust-wave-phase-trajectories-annotate}
  \caption{Trajectories of small graphite grains
    (\(a = \SI{0.02}{\um}\)) at impact parameter \(b = 0\) for two
    example cases (see yellow ``+'' symbols in left panel of
    Fig.~\ref{fig:existence-dust-wave}), which differ only in the
    stream velocity: \(v = \SI{40}{km.s^{-1}}\) (left panels) and
    \SI{80}{km.s^{-1}} (right panels).  In both cases, the stream
    density is \(n = \SI{1}{cm^{-3}}\) and the central star is a
    \SI{10}{M_\odot} main-sequence B star (see Tab.~\ref{tab:stars}).
    Upper panels show the evolution of grain radius, \(R\) (blue
    curve, normalized by the rip point radius, \(R_\dag\)), and grain
    velocity, \(v\) (orange curve, normalized by the gas stream
    velocity).  The origin of the time axis is set to the moment of
    closest approach of the grain to the star: \(R = \Rmin\).  Lower
    panels show the trajectories in phase space: position versus
    gas--grain relative slip velocity (\(w = \abs{v - v_\infty}\)).  Filled
    contours show the net force on the grain: \(f\rad - f\drag\), with
    positive values in blue and negative values in red.  The heavy
    dotted line shows where there is no net force: \(f\rad = f\drag\).
    The grain trajectory (thick, solid black line with arrows)
    initially follows this line, but departs from it after the rip
    point. In the left panel, the grain enters a limit cycle between
    decoupling (rip) and re-coupling (snap back).  In the right panel,
    the grain spirals in on the stagnant drift point.  See text for
    further details.}
    \label{fig:phase-space-trajectories}
\end{figure*}

\subsection{Grain trajectories along the symmetry axis}
\label{sec:grain-traj-along}

The post-decoupling behavior of the grain depends on the sign of
\(d f\drag / d w\) when \(w = \abs{v_\infty}\).  If this derivative is
positive, as is the case in drag regimes~II and V (see
Tab.~\ref{tab:fdrag-regimes} and Fig.~\ref{fig:drag-v-phi-plane}),
then the grain can reach a stable equilibrium drift at rest with
respect to the star\footnote{%
  Again, this is only strictly true when the impact parameter is zero.
  However, as we show below, it is a reasonable approximation over a
  range of impact parameters in the case where the angle between the
  magnetic field direction and the stream velocity is not too
  large.} %
at a point \(R_\ddag\), which we call the \textit{stagnant drift
  radius}. If the stream velocity is not excessively high
(\(v_\infty < \SI{150}{km.s^{-1}}\) when \(\phi = 4\), or
\(< \SI{300}{km.s^{-1}}\) when \(\phi = 16\)), then the equilibrium
\(f\rad\) is less than the value at the rip point, requiring a lower
value of the radiation parameter: \(\Xi_\ddag < \Xi_\dag\).  The resultant
stagnant drift radius is therefore outside the rip point:
\(R_\ddag > R_\dag\).

On the other hand, if \(d f\drag / d w < 0\) when
\(w = \abs{v_\infty}\), then the equilibrium is unstable and no stagnant
drift is possible.  This occurs for drag regime~IV, which applies when
\(\phi > 1\) and
\(\SI{10}{km.s^{-1}} < v_\infty < \SI{50}{km.s^{-1}}\).  There is also a
second unstable regime (partially visible in the upper-right corner of
Fig.~\ref{fig:drag-v-phi-plane}), which is related to the thermal peak
in the electron Coulomb drag when \(\phi > 30\) and
\(\SI{400}{km.s^{-1}} < v_\infty < \SI{2000}{km.s^{-1}}\), but this is not
relevant to bow shocks around OB~stars.\footnote{%
  It may apply in other contexts, such as outflows from AGN, since
  detailed modeling of grain charging around quasars
  \citep{Weingartner:2006a} implies that grain potentials as high as
  \(\phi \sim 100\) can be achieved.} %

An example of each of these two behaviors is illustrated in
Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
regime, resulting in periodic ``limit-cycle'' behavior (the parameters
of this model correspond to the yellow ``plus'' symbol labeled ``40''
in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
grain's first approach, it starts to follow a phase trajectory (lower
left panel) along the \(f\rad - f\drag = 0\) contour, corresponding to
equilibrium drift, in which the grain begins to move a few
\si{km.s^{-1}} slower than the gas stream.  Then, when it reaches the
rip point (\(R = R_\dag\), \(w \approx \SI{10}{km.s^{-1}}\)) it suddenly
experiences a large unbalanced outward radiation force (blue region of
phase space in Fig.~\ref{fig:phase-space-trajectories}). The grain's
inward momentum carries it to the point \(\Rmin \approx 0.85 R_\dag\), before
it is expelled at roughly twice the inflow speed.  However, after
moving outward, it finds itself in a drag-dominated region of phase
space (red in the figure), and so recouples to the inflowing gas
stream.  The recoupling initiates gradually, as the grain's outward
motion is slowed and it begins to move inward again, but is completed
suddenly once \(w\) again falls below \SI{10}{km.s^{-1}}, in what we
term \textit{snap back}. The net result is that the grain has returned
to exactly the same phase track that it started in on, and so repeats
the cycle indefinitely.

The right panels of Figure~\ref{fig:phase-space-trajectories} show the
case where the stream velocity is doubled to
\(v_\infty = \SI{80}{km.s^{-1}}\), but all other parameters remain the
same.  At this velocity, the equilibrium drift is stable and so the
grain can achieve a stagnant drift solution, where it is stationary
with respect to the star.  The trajectory during the first approach is
similar to the previous case, except that the overshoot of the rip
point is greater, so that \(\Rmin \approx 0.65 R_\dag\) in this case.  This is
a consequence of the fact that the rip point is closer to the
drag-free turnaround radius (\(R_\dag / R\starstar\) is larger than in
the lower velocity case), so that the grain inertia is relatively more
important.  A second consequence of this is that the speed of the
initial expulsion is not so large, being only a little higher than the
inflow velocity.  The qualitative difference between the two cases
emerges after the first recoupling: instead of the snap back and
endless limit cycle, the grain oscillates about the stagnant drift
radius with ever decreasing amplitude, so that after a few oscillation
periods it has come to almost a complete rest.

\begin{figure}
  \includegraphics[width=\linewidth]{figs/onaxis-stats-plot-MS10-v080-gra002}
  \caption{Bow radius as a function of stream density for a stream of
    initial velocity \SI{80}{km.s^{-1}}, which interacts with a
    \SI{10}{M_\odot} main-sequence B~star.  This corresponds to a vertical
    slice through the left panel of
    Fig.~\ref{fig:existence-dust-wave}.  At low densities, the
    hydrodynamic bow shock (blue line) is larger than the drag-free
    turnaround radius for small carbon grains, meaning that a grain's
    inertia carries it into the bow shock along with the gas, even
    though the gas--grain coupling is not particularly strong.  At
    densities above about \SI{0.05}{cm^{-3}}, however, this is no
    longer true and a separate dust wave forms outside of the
    hydrodynamic bow shock, which is now dust-free (green dashed
    line).  The grains in the dust wave will occupy a range of radii
    (pale orange shading) between \(\Rmin\) (solid orange line) and
    \(R_\ddag\), the stagnant drift radius.  At densities above about
    \SI{1000}{cm^{-3}}, the gas stream starts to feel the effect of
    passing through the dust wave, and above \SI{3e4}{cm^{-3}}, the
    dust wave and bow shock merge to form a radiative bow wave (red
    line), which becomes an optically thick radiative bow shock
    (purple line) above \SI{e6}{cm^{-3}}.}
  \label{fig:decouple-vertical-cut}
\end{figure}

\subsection{Back reaction on the gas flow}
\label{sec:back-reaction-gas}

So far we have ignored the effect of the drag force on the gas stream
itself, but it is clear that this must become important as \(\tau_*\)
approaches \(\tau_{*,\text{max}}\), since that is the point where the
dust wave transitions to a bow wave, in which the dust and gas are
perfectly coupled.  A full treatment of this problem would require
solving the hydrodynamic equations simultaneously with the equations
of motion of the dust grains, which is beyond the scope of this paper.
Instead, we outline a heuristic approach that qualitatively captures
the physics involved.

The maximum drag force experienced by a grain is at the rip point.
Since the grain follows a zero-net-force phase track up until that
point, this can be written with the help of
equations~(\ref{eq:dust-rad-force}, \ref{eq:dust-r0}) as
\begin{equation}
  \label{eq:fdrag-max}
  f\drag (R_\dag) = f\rad(R_\dag) =   \frac{m\grain v_\infty^2 R\starstar}{ 2 R_\dag^2} 
\end{equation}
The timescale of the flow can be characterized by the crossing time
\(R_\dag / v_\infty\), but the residence time of the grain at the bow apex
will be several times larger than this (see previous section).  On the
other hand, the average drag force during this residence will be
several times smaller than \(f\drag (R_\dag)\) if
\(R_\ddag > R_\dag\), which is typically the case.  We therefore parameterize
our ignorance via a dimensionless factor, \(\alpha\), which we expect to be
of order unity, and write the total impulse imparted to the grain by
drag as
\begin{equation}
  \label{eq:grain-impulse}
  J\drag \equiv \int \!f\drag \, dt \approx \alpha f\drag (R_\dag) \frac{R_\dag}{v_\infty}
  = \tfrac12 \alpha \, m\grain v_\infty \, \frac{R\starstar}{R_\dag} \ .
\end{equation}

By Newton's Third Law, an equal and opposite impulse is imparted to
the gas, which will act to decelerate the gas stream as it decouples
from the grains.  Realistically, \(J\drag\) should be summed over the
grain size distribution, but for simplicity we assume that all grains
are identical, so that the mass of gas that accompanies each grain is
given by
\begin{equation}
  \label{eq:gas-mass}
  m_{\text{gas}} = \frac{m\grain}{Z\grain} =  m\grain \, \frac{\kappa\grain}{\kappa} \ . 
\end{equation}
If the gas remains supersonic after decoupling, then thermal pressure
can be ignored and the gas will suffer a change in momentum equal to
\(J\drag\), so that its velocity is reduced by
\(\Delta v = J\drag / m_{\text{gas}}\), which by
equations~(\ref{eq:Rdag-over-Rstar}, \ref{eq:Rstarstar-over-Rstar},
\ref{eq:dust-wave-high-density-condition}, \ref{eq:grain-impulse},
\ref{eq:gas-mass}) is
\begin{equation}
  \label{eq:gas-dv}
  \Delta v = \tfrac12 \alpha \frac{\tau_*}{\tau_{*, \text{max}}} v_\infty\ .
\end{equation}
This deceleration reduces the gas stream's ram pressure before it
interacts with the central star's stellar wind.  The radius of the
dust-free bow shock formed by this interaction is therefore increased
by a factor \((1 - \Delta v / v_\infty)^{-1}\) with respect to the case
calculated in \S~\ref{sec:three-bow-regimes}, yielding
\begin{equation}
  \label{eq:gas-free-bow-shock}
  R_{\text{dfbs}} \approx \frac{\eta\wind^{1/2} R_*}{1 - \tfrac12 \alpha \tau_* / \tau_{*, \text{max}}} \ .
\end{equation}

An example is illustrated in Figure~\ref{fig:decouple-vertical-cut},
where the dust-free bow shock radius is shown by the green dashed line
as a function of stream density, \(n\).  This is calculated for fixed
stream velocity and grain and star properties, so that
\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).  In order for
\(R_{\text{dfbs}}\) to match the dust-wave and bow-wave radii at the
point where they cross at \(\tau_* = \tau_{*, \text{max}}\), we find
\(\alpha \approx 1.5\) is required.  It can be seen that the gas deceleration is
negligible over most of the density range for which a separate dust
wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does
\(R_{\text{dfbs}}\) begin to curve up from the general \(n^{-1/2}\)
trend, becoming essentially flat at a value
\(R_{\text{dfbs}} \approx (\kappa/\kappa\grain) R\starstar\) until full-coupling is
established at \(n > \SI{3e4}{cm^{-3}}\).  Note, however, that the
treatment described here is very approximate: it does not take into
account the shock that will form once \(J\drag\) reaches an
appreciable fraction of \(m_{\text{gas}} v_\infty\) and, additionally, it
includes a factor, \(\alpha\), whose value has not been rigorously
justified.  More detailed modeling is required to fully understand the
bow behavior in this transition regime.

\section{Magnetic coupling of grains}
\label{sec:magn-effects-grain}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/frozen-stream-map-multi}
  \caption{Drag-confined dust waves with tight magnetic coupling.
    Upper panels show a quasi-parallel field, \(\theta\B = \ang{10}\),
    while lower panels show a quasi-perpendicular field,
    \(\theta\B = \ang{75}\).  Left panels show an incident stream velocity of
    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels show
    \(v_\infty = \SI{80}{km.s^{-1}}\).  In all cases, the stream density is
    \(n = \SI{10}{cm^{-3}}\) and the calculations are performed for
    small graphite grains, \(a = \SI{0.02}{\um}\), and the
    \SI{10}{M_\odot} main-sequence B~star.  Continuous black lines show
    grain trajectories, with triplets of colored symbols indicating
    the progress of individual cohorts, which entered from the right
    edge at a particular time.  Continuous blue lines show the
    magnetic field, which flows from right to left along with the
    incident stream.  The radius of the rip point, \(R_\dag\), and the
    stagnant drift point, \(R_\ddag\), are shown respectively by red and
    blue dashed lines.  The approximate shape of the wind-supported
    bow shock is shown by the dotted gray line.  The calculations are
    no longer valid after trajectories cross this surface.}
  \label{fig:frozen-stream}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/frozen-trajectories-multi}
  \caption{Sample grain trajectories for drag-confined dust waves with
    tight magnetic coupling and a quasi-parallel field
    orientation. These are the same models as in the upper row of
    Fig.~\ref{fig:frozen-stream}. (a)~Incident stream velocity of
    \(v_\infty = \SI{40}{km.s^{-1}}\), showing quasi-limit-cycle behavior
    (\numrange{0}{4000} years).  (b)~Incident stream velocity of
    \(v_\infty = \SI{80}{km.s^{-1}}\), showing quasi-stagnation behavior
    (\numrange{500}{2000} years).  In both cases, the streamline with
    initial impact parameter \(y = -0.4 R_\dag\) is shown.}
  \label{fig:frozen-trajectories}
\end{figure}

An important effect that we have not considered up to now is the
Lorentz force on charged grains due to the plasma's magnetic field:
\begin{equation}
  \label{eq:f-lorentz}
  \bm{f}\!\B = \frac{z\grain e}{c} \, \bm{w} \times \bm{B} \ . 
\end{equation}
The direction of the force is perpendicular both to the magnetic
field, \(\bm{B}\), and to the relative velocity, \(\bm{w}\), of the
grain with respect to the plasma.  If \(\bm{w}\) and \(\bm{B}\) (as
seen by the grain) are changing slowly, compared with the
gyrofrequency, \(\omega\B = z\grain e B / m\grain c\), then the grain
motion perpendicular to \(\bm{B}\) is constrained to be a circle of
radius equal to the Larmor radius:
\begin{equation}
  \label{eq:Larmor}
  r\B = \frac{m\grain c w_\perp} {\abs{z\grain} e B} \ ,
\end{equation}
where \(B = \abs{\bm{B}}\) and \(w_\perp\) is the perpendicular component
of \(\bm{w}\).  The component of \(\bm{w}\) parallel to \(\bm{B}\) is
unaffected by \(\bm{f}\!\B\), so the resultant trajectory is helical.

The relative importance of the magnetic field can be characterized by
the ratio of the Larmor radius to the minimum radius, \(\Rmin\),
reached by the grain in the dust wave (see
\S~\ref{sec:grain-traj-along}), where \(\Rmin \approx R_\dag\) for
drag-confined dust waves (DDW), or \(\Rmin \approx R\starstar\) for
inertia-confined dust waves (IDW).  We write the field strength in
terms of the Alfvén speed,
\begin{equation}
  \label{eq:alfven}
  v\alfven = \frac{B}{(4\pi\rho\gas)^{1/2}}
  = 1.9\, \frac{B}{\si{\micro G}} n^{-1/2} \, \si{km.s^{-1}} \ ,
\end{equation}
and the grain charge \(z\grain e\) in terms of the potential \(\phi\) (eq.~[\ref{eq:phi-potential}]) to obtain
\begin{equation}
  \label{eq:larmor-over-Rdag}
  \text{DDW:}\quad \frac{r\B}{\Rmin} =  
  \frac{r\B}{R_\dag} = 0.0140 \,
  a_{\si{\um}}^2 \,
  \frac{w_\perp}{v\alfven} \,
  \left( \frac{\Xi_\dag}{L_4 T_4} \right)^{1/2}
  \frac{\rho\grain}{\phi_\dag}
\end{equation}
and
\begin{equation}
  \label{eq:larmor-over-Rstarstar}
  \text{IDW:}\quad \frac{r\B}{\Rmin} =  
  \frac{r\B}{R\starstar} = 0.0544 \,
  a_{\si{\um}}^3 \,
  \frac{w_\perp}{v\alfven} \,
  \frac{v_{10}^2 }{n^{1/2}} \,
  \frac{1}{L_4 T_4} \,
  \frac{\rho\grain^2}{\Qp \phi\starstar} \ ,
\end{equation}
where \(a_{\si{\um}} = a / \SI{1}{\um}\), \(\rho\grain\) is the grain
material density in \si{g.cm^{-3}}, and we have made use of
equations~(\ref{eq:Rstar-typical}, \ref{eq:Rdag-over-Rstar},
\ref{eq:dust-r0}).

If \(r\B / \Rmin \ll 1\), then the grains are so strongly coupled to the
field that they can be treated in the guiding-center approximation, in
which the trajectory is decomposed into a tight circular gyromotion
around the field lines, plus a sliding of the guiding center along the
field lines, which is governed by the radiation and drag forces (the
slow \(\bm{f} \times \bm{B}\) drift across the field lines is negligible in
this case, see App.~\ref{sec:tight-magn-coupl}).  In the opposite
limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
non-magnetic results of \S~\ref{sec:imperf-coupl-betw} are scarcely
modified.  Assuming \(w_\perp \sim v_\infty\) and adopting a threshold of
\(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
\ref{eq:larmor-over-Rstarstar}) can be transformed into conditions on
the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
will apply: \newcommand\freeze{\ensuremath{_{\text{tight}}}}
\begin{equation}
  \label{eq:velocity-strong-B-coupling}
  v_{\infty} < v\freeze \approx
  \begin{cases}
    \text{drag-confined:}
    & 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2}\\
    \text{inertia-confined:}
    & 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \\
  \end{cases} \ ,
\end{equation}
where we have substituted typical values of the minor parameters
\(\Xi_\dag\), \(\phi_{\dag}\), \(\phi_{**}\), \(\rho\grain\),
\(T_4\).\footnote{%
  The most significant systematic variation in \(v\freeze\) from these
  suppressed parameters is due to grain composition, yielding slightly
  higher values for graphite than for silicate (\SI{+-0.15}{dex}).} %
It is apparent that \(v\freeze\) is very sensitive to the grain size.
For instance, taking a typical \hii{} region value of
\(v\alfven = \SI{2}{km.s^{-1}}\) \citep{Arthur:2011a} and
\(L_4 = 0.63\) (Tab.~\ref{tab:stars}, B1.5~V star), then for the
drag-confined case \(v\freeze \approx \SI{30}{km.s^{-1}}\) for \SI{0.2}{\um}
grains but \(v\freeze \approx \SI{3000}{km.s^{-1}}\) for \SI{0.02}{\um}
grains. Thus, for typical stream velocities of
\SIrange{20}{100}{km.s^{-1}}, the small grains are always tightly
coupled to the magnetic field, but the large grains are only loosely
coupled for the faster streams.

\subsection{Grain trajectories with tight magnetic coupling}
\label{sec:grain-traj-with}

We can now investigate how the results of the previous sections are
modified by magnetic fields in the tight coupling limit.  For
simplicity, we assume a uniform field in the incoming stream, with
field lines oriented at an angle \(\theta\B\) to the velocity vector that
defines the bow axis.  We also assume a super-alfvénic stream,
\(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
is unaffected by the magnetic field, and additionally assume
\(\tau_* \ll \tau_{*, \text{max}}\), so that the back-reaction of the grain
drag on the plasma is negligible (see previous section) and \(B\)
remains uniform in magnitude and direction in the dust wave region,
outside of the bow shock.

In Appendix~\ref{sec:tight-magn-coupl}, we derive analytic and
semi-analytic results in the limit of zero gas--grain drag, which is
appropriate for inertia-confined dust waves. We find very different
structures, depending on the orientation of the field.  For a parallel
field (Fig.~\ref{fig:inertia-thB0}), the apex of the dust wave occurs
at the same point, \(R\starstar\), as in the non-magnetic case, but
the shape of the dust wave wings is more closed, being hemispherical
rather than parabolic in shape.  For a perpendicular field
(Fig.~\ref{fig:inertia-thB90}), on the other hand, grains in the apex
region are dragged very close to the star and no dust wave forms
there.  A dust wave can form in the wings, with impact parameter
\(> R\starstar\), which is roughly parabolic in shape, but more
swept-back than in the non-magnetic case.  Whether such a dust wave
will exist in practice depends critically on the size and shape of the
MHD wind-supported bow shock.

In Figures~\ref{fig:frozen-stream} and~\ref{fig:frozen-trajectories}
we show example results for drag-confined dust waves, which are
calculated by numerically integrating the grain's equation of motion,
as described in Appendix~\ref{sec:equat-moti-grains}. Apart from the
inclusion of the magnetic field, the model parameters are the same as
used in Figure~\ref{fig:phase-space-trajectories}, with the exception
that the stream density is increased to \SI{10}{cm^{-3}}.\footnote{The
  reason for using a higher density is to decrease the amplitude of
  the radial oscillations of the trajectories, which allows the dust
  wave structure to be more clearly perceived in the figures. } This
time, we use quasi-parallel (\(\theta\B = \ang{10}\)) and
quasi-perpendicular (\(\theta\B = \ang{75}\)) field orientations.  The
quasi-parallel field is most similar to the non-magnetic case, and the
models shown in the two upper panels of Figure~\ref{fig:frozen-stream}
closely mirror the cases shown in
Figure~\ref{fig:phase-space-trajectories}, with a limit cycle behavior
when \(v_\infty = \SI{40}{km.s^{-1}}\) and stagnant drift when
\(v_\infty = \SI{80}{km.s^{-1}}\).

The principle difference from the 1-D axial trajectories discussed in
\S~\ref{sec:grain-traj-along} is that the small \ang{10} misalignment
of \(\bm{B}\) from the incident stream direction causes a slow
sideways migration, which puts a finite limit on the time a grain can
reside in front of the star.  This can be appreciated more clearly in
Figure~\ref{fig:frozen-trajectories}, which shows the grain position
and velocity along a sample streamline with initial impact parameter
\(b = -0.4 R_\dag\) for the two quasi-parallel models.  In panel~a,
corresponding to \(v_\infty = \SI{40}{km.s^{-1}}\), we see the same
rip-and-snap-back cycle of de-coupling and re-coupling that was
discussed previously, but only two periods of the cycle are completed
before the grain's lateral migration takes it as far as
\(y \approx +R_\dag\), at which point nothing can stop the gas stream from
dragging it past the star and away.  All told, the grain remains in
the apex region for about \(1/\sin\theta\B\) times longer than the crossing
time, \(R_\dag / v_\infty\).

In panel~b, corresponding to \(v_\infty = \SI{80}{km.s^{-1}}\), the grain
settles for a while around the stagnant drift radius, \(R_\ddag\), after
the initial rip and turn around.  Again, it slowly migrates sideways,
and eventually recouples to the incident stream, but this time after
reaching \(y \approx +R_\ddag\).  The grain residence time in the apex region,
measured in crossing times, is slightly longer than in panel~a, but is
of the same order.  In both these cases, a second, exterior dense
shell is formed in addition to the hemispherical one produced by the
initial turn around inside \(R_\dag\). In the limit-cycle case, it forms
at the snap-back point, while in the stagnant-drift case, it forms at
\(R_\ddag\) and is significantly denser than the interior shell (upper
right panel of Fig.~\ref{fig:frozen-stream}).

The assumptions behind these models break down when the grain
trajectory intersects the outer shock of the dust-free wind-supported
bow shock.  The increased gas density in the bow shock shell will
reduce \(\Xi\), which is likely to cause gas--grain recoupling in the
case of drag-confined dust waves (see also discussion in the final
paragraph of \S~\ref{sec:exist-cond-separ}).  However, detailed
modeling of this requires magnetohydrodynamical simulations, which are
beyond the scope of this paper.  In Figure~\ref{fig:frozen-stream} we
show in gray dotted lines the Wilkinoid surface \citep{Wilkin:1996a},
which is an approximation to the shape of the inner bow shock, see
\PaperI.  It can be seen that the majority of dust streamlines do not
cross this surface until well into the wings of the bow, so that a
separate exterior dust wave can exist for this quasi-parallel
magnetic field orientation.

This is no longer the case for the quasi-perpendicular field
orientation, as illustrated in the lower panels of
Figure~\ref{fig:frozen-stream}, where the behavior is similar to the
perpendicular inertia-confined case studied in
Appendix~\ref{sec:perp-magn-field}.  Although the grains decouple from
the gas inside the rip point, for small impact parameters the magnetic
geometry does not allow the radiation field to expel them until they
are much nearer to the star.  Since the inner wind-supported bow shock
radius is only a few times smaller than \(R_\dag\), it is possible that
they will pass through the shock surface and re-couple before
expulsion can occur.  For the \SI{40}{km.s^{-1}} model (lower left
panel), all of the streamlines with impact parameters
\(\abs{b} < R_\dag\) intersect the Wilkinoid surface before they are
deflected, and so no separate dust wave would form in this case.  For
the \SI{80}{km.s^{-1}} model (lower left panel), some of the
streamlines (mainly those with \(b > 0\)) do manage to avoid crossing
the bow shock surface, so it is possible that a dust wave may still
form, although it would only be on one side of the axis.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "bs-bw-dw-02"
%%% End:

### 2019-03-04 papers/Papers1234/sec-strong-coupling.tex
Start writing about the shell structure figure

@@
 \(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
-thickness in the efficient cooling case.  In this context, \(n_0 = n\)
-and \(n_2 = n\shell\), so that \(h_0\) follows from
+thickness in the limit of instantaneous cooling.  In this context,
+\(n_0 = n\) and \(n_2 = n\shell\), so that \(h_0\) follows from
 equations~\eqref{eq:shocked-shell-column}
@@
 
+\subsection{Axial structure of bow shells}
+\label{sec:axial-structure-bow}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/shell-profiles}
+  \caption{Profiles of physical variables along the axis of bow shells
+    for (a)~wind-supported bow shock; (b)~radiation-supported bow
+    wave, and (c)~radiation-supported bow shock.  In all cases, a
+    stream velocity of \SI{30}{km.s^{-1}} and an equilibrium ionized
+    sound speed of \SI{10}{km.s^{-1}} are assumed.}
+  \label{fig:axial-structure}
+\end{figure}
+
+In the shell of a wind-supported bow shock, the gas density is highest
+at the contact discontinuity, but this is no longer true for
+radiation-supported bows, as illustrated in
+Figure~\ref{fig:axial-structure}.  For the optically thin RBW case,
+equations~\eqref{eq:rad-accel} to~\eqref{eq:rad:R0} can be combined to
+give the radial dependence of the stream velocity as it approaches the
+star:
+\begin{equation}
+  \label{eq:v-RBW-ballistic}
+  v(R) = \left( 1 - \frac{R_{**}}{R} \right)^{1/2} v_\infty \ .
+\end{equation}
+This ballistic approximation (shown by the dashed red line in
+Fig.~\ref{fig:axial-structure}b) predicts that the velocity smoothly
+decreases to zero at \(R = R_{**}\).  However, although this is valid
+in the limit of high Mach number, it ignores the effects of gas
+pressure and so becomes invalid once the stream velocity falls close
+to the sound speed.
+
+\section{Discussion}
+\label{sec:discussion}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-Weak}
+  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for a weak-wind
+    O~star, similar to the sample observed by \citet{Martins:2005b}.
+    For this star, radiation-supported bow waves (gray shading) occur
+    over a much larger region of parameter space than for a
+    normal-wind star of the same spectral type
+    (see Fig.~\ref{fig:zones-v-n-plane}b).}
+  \label{fig:O-weak-wind}
+\end{figure}
+
+Hot stars, comparison with expected velocities and densities.
+
+Expected velocities.  There are cases of high velocities, e.g., AE~Aur, but they are probably rare. \citep{Renzo:2018a}
+In cases, where proper motions are measured, they are often low.
+
+Metallicity dependence of wind strength. RBW more likely at lower metallicities.
+
+Weak wind stars - repeat the 20 Msun case, but for a much lower \(\eta\wind\)
+
+Cool stars, comparison with observed densities (Betelgeuse, for
+instance). Other ones in \citep{Cox:2012a}.
+
+Prospects for observation in LMC: 1 parsec = 4 arcsec, so need JWST to get most of them.
+
 %%% Local Variables:

### 2019-03-05 papers/Papers1234/sec-strong-coupling.tex
Finish section on shell structure

@@
 radiation-supported bows, as illustrated in
-Figure~\ref{fig:axial-structure}.  For the optically thin RBW case,
+Figure~\ref{fig:axial-structure}, where we schematically show the
+shell structure for the three cases: WBS, RBW, and RBS.  In all cases,
+we assume a far-field mach number of \(\M_\infty = 3\) for the incident
+stream of density \(n_\infty\).  For the WBS case
+(Fig.~\ref{fig:axial-structure}a), the stream is unchanged until it
+reaches the shock, so \(\M_0 = \M_\infty\) and \(n_0 = n_\infty\).  The density
+increases to \(n_1 = 3 n_0\) in the shock
+(eq.~[\ref{eq:shock-n-jump}]), and then to \(n_2 = 9 n_0\)
+(eq.~[\ref{eq:isothermal-shell-density}]) after it has cooled back
+down to the equilibrium photoionized temperature.  In the figure, we
+show the case where \(d\cool < h_0\), so that most of the shell is at
+roughly constant density.  Note that although the mass flux along the
+axis, \(n v\), is approximately conserved in most of the flow, this is
+no longer true close to the contact discontinuity, since the
+streamlines bend away from the axis due to lateral pressure gradients.
+This is what allows \(v\) to tend to zero, while \(n\) remains
+constant.  The thermal pressure in the shocked stellar wind is equal
+to the shell pressure, but its density is much smaller due to a
+temperature that is higher by a factor of \(\approx 3100 V_3^2\),
+(eq.~[\ref{eq:shock-T-jump}], assuming inefficient cooling).
+
+For the optically thin RBW case (Fig.~\ref{fig:axial-structure}b),
 equations~\eqref{eq:rad-accel} to~\eqref{eq:rad:R0} can be combined to
@@
 pressure and so becomes invalid once the stream velocity falls close
-to the sound speed.
+to the sound speed.  The situation bears similarities to the flow in a
+supersonic diffuser, such as the inlet of a ramjet or other supersonic
+aircraft engine \citep{Seddon:1999a}, which slows supersonic airflow
+down to subsonic speeds before combustion.  Exactly the opposite flow
+configuration is present in a rocket nozzle \citep{Courant:1948a},
+where the flow can smoothly pass from subsonic to supersonic
+velocities at the throat of the nozzle.  An analogy between an
+isothermal stellar wind and a rocket nozzle is developed in detail in
+\S~3.5 of \citet{Lamers:1999b}.  However, in the reverse case of a
+supersonic diffuser, a smooth transition from supersonic to subsonic
+flow is not possible \citep{Morawetz:1956a}.  Instead, a normal shock
+wave develops, which decelerates the supersonically entering flow,
+allowing it to exit subsonically \citep{Embid:1984a, Hafez:1999a}.
+The supersonic inlet/bow wave analogy is not so exact as the rocket
+nozzle/stellar wind analogy due to the multi-dimensional nature of the
+bow shell, which means that lateral flows of gas away from the apex
+become important when the velocity is subsonic.\footnote{%
+  In the aeronautical case, the inlet is usually designed so that
+  multiple oblique shocks partially decelerate the flow before it
+  passes through the normal shock.  This is the analogy of the initial
+  gradual radiative deceleration in the bow wave.  } %
+Nonetheless, we expect that a normal shock must be present in the
+flow, although there does not seem to be any simple argument for
+predicting the exact Mach number where it will occur.  In
+Figure.~\ref{fig:axial-structure}b, we assume that the shock occurs at
+a Mach number \(\M_0 = 1.5\), but multidimensional numerical
+simulations are necessary to test this supposition.
+
+The shell in the RBW case therefore consists of two parts: an outer
+radiatively braked sub-shell, and an inner shocked sub-shell.  In the
+outer sub-shell, the density gradually increases inwards as the stream
+is decelerated by the absorbed photons, reaching
+\begin{equation}
+  \label{eq:outer-shell-density}
+  n_0 = \frac{\M_\infty}{\M_0} n_\infty
+\end{equation}
+just outside the shock (\(n_0 = 2 n_\infty\) for the case illustrated).  In
+the inner sub-shell, on the other hand, the pressure must increase
+outwards, since it is subsonic and therefore in approximate
+hydrostatic equilibrium with an outward-pointing effective gravity
+from the radiation force.  The shell thickness will be set by the
+hydrostatic scale height, \(h_a = \sound^2 / a\rad\), which by
+eqs.~(\ref{eq:rad-accel}, \ref{eq:rad:R0}) is given by
+\begin{equation}
+  \label{eq:scale-height}
+  h_a = \frac{2 R_{**}}{\M_\infty^2} \ .
+\end{equation}
+If the cooling is efficient (\(d\cool < h_a\)), then most of the
+sub-shell is isothermal and the density will fall off exponentially
+towards the star.  The contact discontinuity with the stellar wind
+will form at the point where the shell pressure has fallen by a factor
+of order \(\tau / \eta\wind\), but this has no influence on the bulk of the
+shell, which is pressurized by radiation, not wind.  If, as we
+suspect, \(\M_0\) depends only weakly, if at all, on \(\M_\infty\), then
+eqs.~(\ref{eq:outer-shell-density}, \ref{eq:scale-height}) imply that
+the inner shocked sub-shell represents a fraction
+\(\approx \M_\infty^{-1}\) of the total shell optical depth, which means that the
+outer supersonic sub-shell dominates for highly supersonic stream
+velocities.
+
+For the optically thick RBS case (Fig.~\ref{fig:axial-structure}c),
+the shell density profile is no longer simply exponential since the
+pressure scale height now increases as one moves away from the star,
+due to the extinction-induced decline in radiation flux. Assuming
+single scattering and plane geometry, the resultant hydrostatic
+density profile is doubly exponential:
+\begin{equation}
+  \label{eq:rbs-density-profile}
+  n(R) = n_2 e^{-e^{-x}} \text{\quad where\quad } x = n_2 \bar{m} \kappa (R - R_*) \ . 
+\end{equation}
+The shell density increases from \(e^{-1} n_2\) at \(R_*\) to saturate
+at \(n_2\) for \(R > R_* + h_a\), where \(h_a \approx 8 h_0 / \tau\).  We show
+results for a total shell optical depth \(\tau = 3\), for which
+\(h_a\) and \(h_0\) are almost equal.  For larger optical depths,
+\(h_0 > h_a\) so that the constant density portion of the shell will
+dominate the total column.  A small fraction \(e^{-\tau}\) of the photons
+will penetrate the shell and be available to decelerate the supersonic
+stream, as in the RBW case, yielding
+\(v_0 = (1 - \tau e^{-\tau}) v_\infty\).  In the illustrated case of
+\(\tau = 3\), the resultant speed reduction before the shock is only 8\%.
 

### 2019-03-07 papers/Papers1234/bs-bw-dw-01.tex
Start writing about the shell structure figure
Write lots of discussion for Paper I

@@
 \author[Henney \& Arthur]{
-  William J. Henney \& S. Jane Arthur\\
+  William J. Henney \& S. J. Arthur\\
   \AddressCRyA
@@
   of stellar parameters, wind-supported bow shocks predominate when
-  the ambient density is below \SIrange{100}{1000}{cm^{-3}}.  At
-  higher densities radiation-supported bows can form, tending to be
-  optically thin bow waves around B~stars, or optically thick bow
-  shocks around early O~stars.  
+  the ambient density is below \SI{100}{cm^{-3}}.  At higher densities
+  radiation-supported bows can form, tending to be optically thin bow
+  waves around B~stars, or optically thick bow shocks around early
+  O~stars.  For OB stars with particularly weak stellar winds,
+  radiation-supported bows become more prevalent.
 \end{abstract}

### 2019-03-07 papers/Papers1234/sec-strong-coupling.tex
Write lots of discussion for Paper I

@@
     bow size (star-apex separation, \(R_0\)), while gray shading shows
-    the radiation bow wave regime, with lower border \(\tau = \eta\wind\) and
-    upper border \(\tau = 1\), where \(\tau = 2 \kappa \rho R_0\) is the optical
-    depth through the bow.  For bows above the red solid line, the
-    ionization front is trapped inside the bow.  Blue lines delineate
-    different cooling regimes.  Above the thin blue line
-    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
-    forming a thin shocked shell.  Below the thick blue line
-    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
-    non-radiative.}
+    the radiation bow wave regime, with lower border
+    \(\tau = \eta\wind\) and upper border \(\tau = 1\), where
+    \(\tau = 2 \kappa \rho R_0\) is the optical depth through the bow.  For bows
+    above the red solid line, the ionization front is trapped inside
+    the bow (\S~\ref{sec:trapp-ioniz-front}).  Blue lines delineate
+    different cooling regimes (\S~\ref{sec:radi-cool-lengths}).  Above
+    the thin blue line (\(d_{\text{cool}} = h_0\)), the bow shock
+    radiates efficiently, forming a thin shocked shell.  Below the
+    thick blue line (\(d_{\text{cool}} = R_0\)), the bow shock is
+    essentially non-radiative.}
   \label{fig:zones-v-n-plane}
@@
     & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
-                   & \ref{fig:zones-v-n-plane}a, \ref{fig:existence-dust-wave}a,
-                     \ref{fig:phase-space-trajectories}--~\ref{fig:frozen-trajectories} \\
+                   & \ref{fig:zones-v-n-plane}a \\
     Main-sequence OB stars
     & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
-                   & \ref{fig:zones-v-n-plane}b, \ref{fig:existence-dust-wave}b \\
+                   & \ref{fig:zones-v-n-plane}b, \ref{fig:O-weak-wind} \\
     & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
-                   & \ref{fig:zones-v-n-plane}c, \ref{fig:existence-dust-wave}c \\[\smallskipamount]
+                   & \ref{fig:zones-v-n-plane}c\\[\smallskipamount]
     Blue supergiant star
@@
   \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
-  observations and theory \citep{Vink:1999a} for O~stars, but at least
-  two times higher than those cited by \citet{Meyer:2014b}. For
-  main-sequence B~stars, wind column densities are too low to reliably
-  measure the terminal velocity from near ultraviolet P~Cygni profiles
-  \citep{Prinja:1989a}, and so the values are theory-dependent
-  \citep{Krticka:2014a} and hence more uncertain.  A further
-  complication is the existence of a subset of OB stars with
-  anomalously weak winds \citep{Puls:2008a}, which in some cases is
-  related to the presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
-  \citep{Oskinova:2011b}.} %
+  observations and theory \citep{Vink:1999a}, but at least two times
+  higher than those cited by \citet{Meyer:2014b}. } %
 The three examples are an early B~star (\SI{10}{M_\odot}), a late O~star
@@
 wind momentum efficiency is also a steep function of mass
-(\(\eta\wind \sim M^3\)), approaching unity for early O~stars, but falling to
-less than 1\% for B~stars.
+(\(\eta\wind \sim M^3\)), approaching unity for early O~stars, but falling
+to less than 1\% for B~stars.
 
@@
 \(\Gamma\Edd \approx \text{\numrange{30}{400}}\), so gravity can be safely
-ignored.  The only exception is when the optical depth of the bow is
-very large: \(\tau > \ln\Gamma\Edd \sim 5\), in which case gravity may be
-important in the outer parts of the shell (see
-\citealt{Rodriguez-Ramirez:2016b}).
+ignored.  When the optical depth of the bow is very large,
+\(\tau > \ln\Gamma\Edd \sim 5\), gravity will exceed the radiation force in the
+outer parts of the shell (see \citealt{Rodriguez-Ramirez:2016b}), but
+it is generally too weak to effect the shell structure even in such a
+case, see \S~\ref{sec:axial-structure-bow} below.
 
@@
 
-The bow shell consists of two parts: an inner zone of shocked stellar
-wind, and an outer zone of decelerated ambient stream. For OB stars,
-dust grains are present only in the ambient stream, whereas for cool
-stars they will also be present in the stellar wind.  In the remainder
-of this paper, we will concentrate on the OB star case, where it is
-the outer zone that is most important observationally.  Bows are
-typically detected via their infrared radiation (absorption and
-re-emission by dust of stellar radiation), or by emission lines such
-as the hydrogen H\(\alpha\) line.
+There are two shocked zones in the bow: an inner zone of shocked
+stellar wind, and an outer zone of decelerated ambient stream. For OB
+stars, dust grains are present only in the ambient stream, whereas for
+cool stars they will also be present in the stellar wind.  In the
+remainder of this paper, we will concentrate on the OB star case,
+where it is the outer zone that is most important observationally.
+Bows are typically detected via their infrared radiation (absorption
+and re-emission by dust of stellar radiation), or by emission lines
+such as the hydrogen H\(\alpha\) line.
 
@@
 The shell density increases from \(e^{-1} n_2\) at \(R_*\) to saturate
-at \(n_2\) for \(R > R_* + h_a\), where \(h_a \approx 8 h_0 / \tau\).  We show
-results for a total shell optical depth \(\tau = 3\), for which
-\(h_a\) and \(h_0\) are almost equal.  For larger optical depths,
-\(h_0 > h_a\) so that the constant density portion of the shell will
-dominate the total column.  A small fraction \(e^{-\tau}\) of the photons
-will penetrate the shell and be available to decelerate the supersonic
-stream, as in the RBW case, yielding
-\(v_0 = (1 - \tau e^{-\tau}) v_\infty\).  In the illustrated case of
+at \(n_2\) for \(R > R_* + h_a\), where \(h_a\) is now the pressure
+scale height at the inner edge of the shell.  From
+equations~(\ref{eq:Rstar}, \ref{eq:rad:R0}, \ref{eq:tau-thin},
+\ref{eq:strong-cooling-h0}, \ref{eq:scale-height}), and taking \(R_0 \approx R_*\), we find
+\begin{equation}
+  \label{eq:ha-versus-h0}
+  h_a \approx \frac{4 h_0}{3 \tau} \ .
+\end{equation}
+We show results for a total shell optical depth \(\tau = 3\), for which
+\(h_a\) is a significant fraction of \(h_0\).  For much larger optical
+depths, \(h_0 \gg h_a\) so that the constant density portion of the
+shell will dominate the total column.  A small fraction \(e^{-\tau}\) of
+the photons will penetrate the shell and be available to decelerate
+the supersonic stream, as in the RBW case, yielding
+\(v_0 = (1 - \tau e^{-\tau})\, v_\infty\).  In the illustrated case of
 \(\tau = 3\), the resultant speed reduction before the shock is only 8\%.
+As mentioned in \S~\ref{sec:effects-gravity}, radiative acceleration
+becomes less important than gravity in the outer regions of an opaque
+shell.  However, in order for this to have a significant effect on the
+shell, the gravitational scale height would have to be be less than
+the shell thickness: \(\Gamma\Edd h_a < h_0\).  From
+equation~\eqref{eq:ha-versus-h0} this translates to
+\(\tau > \frac43 \Gamma\Edd\), where Eddington factors are
+\(\Gamma\Edd \sim 100\) for luminous stars.  Such large optical depths would
+require extremely high ambient densities of
+\(n > \num{2e7} L_4 \,v_{10}^2 \left( \SI{10}{M_\odot}/M \right)^2 \,
+\si{cm^{-3}} \), where we have used equations~(\ref{eq:tau-star},
+\ref{eq:eddington-factor}) and that \(\tau \approx 2\tau_*\) in the RBS limit.
 
@@
 \label{sec:discussion}
+
+\subsection{Environments of bow-forming stars}
+\label{sec:popul-bow-prod}
+
+The stellar bows modeled in this paper can be seen as either due to
+the motion of a star through the interstellar medium, or due to the
+motion of the interstellar medium that flows past the star.  The
+first case corresponds to runaway stars \citep{Blaauw:1961a}, which
+have been ejected from a binary system or stellar cluster
+\citep{Hoogerwerf:2001a}, while the second case can be due to
+photoevaporation and champagne flows in \hii{} regions
+\citep{Tenorio-Tagle:1979a, Shu:2002a, Henney:2005a}, or to general
+turbulent flows in the Galaxy
+\citep[e.g.,][]{Ballesteros-Paredes:1999a}.  In this section, we
+consider the stream densities and velocities expected in each of these
+scenarios, and compare them with our predictions for the type of bows
+that should result.
+
+Although some runaway stars have velocities exceeding
+\SI{100}{km.s^{-1}}, most are moving considerably slower, with a
+median peculiar velocity of about \SI{30}{km.s^{-1}}
+\citep{Tetzlaff:2011a}.  The higher velocity runaways are likely
+produced by dynamical interactions in the center of young clusters
+\citep{Gualandris:2004a}, whereas the supernova-induced dissolution of
+binary systems is predicted to primarily produce ``walkaways'' with
+even slower velocities of order \SI{10}{km.s^{-1}}
+\citep{Renzo:2018a}.  Environmental flows are also expected to be of
+order \SI{10}{km.s^{-1}}, which is a characteristic velocity
+dispersion for warm neutral gas in the inner Galaxy
+\citep{Marasco:2017a} and also a typical expansion velocity for
+\ion{H}{i} shells \citep{Ehlerova:2005a}.  Internal velocity
+dispersions within \hii{} regions are subsonic
+(\SIrange{5}{10}{km.s^{-1}}) for small regions, such as the Orion
+Nebula, containing one or a few ionizing stars
+\citep{Arthur:2016a}. This increases slowly for more luminous regions
+as \(\sigma \propto L^{1/4}\) \citep{Bordalo:2011a}, so giant star forming
+complexes such as Carina (100 times more luminous than Orion) show
+velocity dispersions of order \SI{20}{km.s^{-1}}
+\citep{Damiani:2016a}.  Higher velocities of
+\SIrange{30}{40}{km.s^{-1}} are reached in divergent photoevaporation
+flows \citep{Dyson:1968a}, but this is achieved at expense of a lower
+density.  Given all the above, we expect there to be many more bows
+with relative stream velocity \(v_\infty \sim \SI{20}{km.s^{-1}}\) than bows
+with \(v_\infty \sim \SI{100}{km.s^{-1}}\).
+
+Turning now to the ambient density, if bow shock stars were randomly
+sampling the volume of the Galactic disk, then we would expect the
+average density to be \(< \SI{1}{cm^{-3}}\).  The dominant gas phase
+\citep{Ferriere:2001a} near the Galactic mid-plane is the Warm Neutral
+Medium with a volume filling fraction of 45\% \citep[Fig.~11
+of][]{Kalberla:2009a} and an average density of \SI{0.9}{cm^{-3}} at
+the Solar circle \citep[\S~4 of][]{Kalberla:2008a}.  Significant
+fractions of the volume (\(\approx 20\%\) each) are also occupied by the
+Warm Ionized Medium and Hot Ionized Medium, which have even lower
+densities (\(\approx \SI{0.3}{cm^{-3}}\) and \SI{e-3}{cm^{-3}},
+respectively) and which increasingly dominate the volume for heights
+\(z > \SI{500}{pc}\) above the plane.  The denser Cold Neutral Medium
+(\(n \approx \text{\SIrange{10}{100}{cm^{-3}}}\)) and Molecular Clouds
+(\(n > \SI{1000}{cm^{-3}}\)) occupy much smaller volumes
+(\(\approx 10\%\) and \(< 1\%\), respectively).  However, observations of
+stellar bows are clearly biased towards these higher densities.
+
+In part, this bias is due to bows being easier to detect in denser
+environments.  Depending on the emission mechanism, the shell
+luminosity will be proportional to the column density
+(\(\propto n R_0\)) or volume emission measure
+(\(\propto n^2 R_0^3\)), which are both increasing functions of
+\(n\).\footnote{%
+  From \S~\ref{sec:three-bow-regimes}, the bow size falls relatively
+  slowly as \(R_0 \propto n^{-1/2}\) in the WBS and RBS cases, and is
+  independent of \(n\) in the RBW case.}  Another contribution to the
+high-density bias is simply that none but the highest velocity
+high-mass stars can move far during their lifetime from the molecular
+clouds where they were born.  Even a runaway star with
+\(v = \SI{30}{km.s^{-1}}\), will travel \(< \SI{120}{pc}\) during an
+O-star lifetime of \(< \SI{4}{Myr}\), which is of the same order as
+the sizes of Giant Molecular Clouds.  Many observed stellar bows are
+found in high mass star clusters associated with large \hii{} regions
+\citep{Povich:2008a, Sexton:2015b}.  The ionized gas density in
+Carina, for example, has an average value of
+\(\approx \SI{100}{cm^{-3}}\) \citep{Oberst:2011a, Damiani:2016a}, although
+with peaks \(> \SI{3000}{cm^{-3}}\) in photoevaporation flows from
+embedded molecular globules \citep{Smith:2004a}.  In more compact
+\hii{} regions, such as the Orion Nebula, ionized densities up to
+\SI{e4}{cm^{-3}} are found on scales of about \(\SI{0.1}{pc}\)
+\citep{Weilbacher:2015a, ODell:2017b}.
+
+In \S~\ref{sec:depend-stell-type} we found that the bow is
+wind-supported when \(\tau_*^2 < \eta\wind\), where \(\tau_*\) is a fiducial
+optical depth (eq.~[\ref{eq:taustar-typical}]) and \(\eta\wind\) is the
+radiative momentum efficiency of the stellar wind
+(eq.~[\ref{eq:wind-eta-typical}]).  This translates into a maximum
+stream density for wind-supported bows of
+\newcommand\crit{\ensuremath{_{\text{max}}}}
+\newcommand\vink{\ensuremath{_{\text{\tiny Vink}}}}
+\begin{equation}
+  \label{eq:ncrit}
+  n\crit \approx \left(\SI{30}{cm^{-3}}\right)
+  \left(  \frac{v} {\SI{10}{km.s^{-1}}}\right)^2
+  \left( \frac{\eta\wind}{\eta\vink} \right)
+  \left( \frac{\SI{600}{cm^2.g^{-1}}}{\kappa} \right)
+  \ ,
+\end{equation}
+which is largely insensitive to spectral type between early-B and
+early-O stars.  In this equation, we have expressed the wind
+efficiency in terms of the Table~\ref{tab:stars} values,
+\(\eta\vink\), which are calculated from the \citet{Vink:1999a} recipe,
+and the UV dust opacity in terms of the standard ISM value adopted in
+\S~\ref{sec:depend-stell-type}.
+
+Therefore, runaway stars moving through the diffuse ISM with
+\(n \sim \SI{1}{cm^{-3}}\) and \(v \sim \SI{30}{km.s^{-1}}\) are safely in
+the WBS regime, having \(n \approx \num{0.004}\, n\crit\) for the default
+wind and dust parameters.  On the other hand, slow-moving stars in
+\hii{} regions of moderate density (\(n \sim \SI{100}{cm^{-3}}\)) can
+easily have \(n > n\crit\), meaning that their bows will be radiation
+supported.
+
+For cases where the stellar wind or dust properties differ from our
+assumed values, then these conclusions may change.  For instance,
+there are a growing number of stars, for which very low mass-loss
+rates have been diagnosed from UV, optical or infrared line profiles
+\citep{Martins:2005b, Marcolino:2009a, Najarro:2011a, Martins:2012a,
+  Smith:2017b}.  Most of these stars are late-type O~dwarfs, for which
+the \citet{Vink:2000a} prescription predicts a mass-loss rate of
+\num{3e-8} to \SI{e-7}{M_\odot.yr^{-1}}, whereas the observed values are
+in the range \num{e-10} to \SI{3e-9}{M_\odot.yr^{-1}} -- a shortfall of 10
+to 1000!  This ``weak wind problem'' is a far larger discrepancy than
+can be explained by clumping effects.  A potential (partial)
+resolution is to suppose that internal shocks near the base of the
+wind, together with thermal conduction, heat a large fraction of the
+gas to coronal temperatures, where it is no longer detectable by means
+of standard wind diagnostic lines \citep{Lucy:2012a}.  However, in
+cases where x-ray diagnostics have been used to trace the mass loss
+this hot component (\(\mu\)~Col, \citealp{Huenemoerder:2012a};
+\(\zeta\)~Oph, \citealp{Cohen:2014a}), rates that are still an order of
+magnitude below the Vink values are found.  We therefore show in
+
+\subsection{Impact of the weak-wind phenomenon}
+\label{sec:impact-weak-wind}
 
@@
 
+% For main-sequence B~stars, wind column densities are too low to
+% reliably measure the terminal velocity from near ultraviolet P~Cygni
+% profiles \citep{Prinja:1989a}, and so the values are theory-dependent
+% \citep{Krticka:2014a} and hence more uncertain.  A further
+% complication is the existence of a subset of OB stars with anomalously
+% weak winds \citep{Puls:2008a}, which in some cases is related to the
+% presence of strong (\(\sim \SI{1}{kG}\)) magnetic fields
+% \citep{Oskinova:2011b}.
+
 Cool stars, comparison with observed densities (Betelgeuse, for
@@
 
+\subsection{Diagnosing bow type from shell emission profile}
+\label{sec:diagnosing-bow-type}
+
+Given that the predicted shell density profile varies between
+wind-supported and radiation-supported bows
+(\S~\ref{sec:axial-structure-bow} and Fig.~\ref{fig:axial-structure}),
+it is worth considering whether it may be possible to use observed
+emission profiles to distinguish between the two.
+
 %%% Local Variables:

### 2019-03-07 papers/Papers1234/_region_.tex
Finish first complete draft of Paper I

@@
-\message{ !name(dusty-bow-wave.tex)}\documentclass[useAMS, usenatbib, a4paper]{mnras}
+\message{ !name(bs-bw-dw-03.tex)}\documentclass[useAMS, usenatbib, a4paper]{mnras}
 \pdfsuppresswarningpagegroup=1
@@
 \title
-{Bow shocks, bow waves, and dust waves}
+{Bow shocks, bow waves, and dust waves. III. Diagnostics}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Henney, Arthur, \& Tarango Yong]{
-  William J. Henney, S. Jane Arthur, \& Jorge A. Tarango-Yong\\
+\author[Henney \& Arthur]{
+  William J. Henney \& S. J. Arthur\\
   \AddressCRyA
@@
 \pubyear{2019}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\Sin}{\mathcal{S}}
-\DeclareMathOperator{\Cos}{\mathcal{C}}
-\DeclareMathOperator{\Cot}{\mathcal{T}}
-\DeclareMathOperator{\GammaFunc}{\Gamma}
-\DeclareMathOperator\erf{erf}
-\newcommand\w{\ensuremath{\mathrm{w}}}
-\newcommand\C{\ensuremath{\mathrm{c}}}
-\providecommand{\abs}[1]{\lvert#1\rvert}
-\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
-\newcommand\TODO[1]{%
-  \begin{center}
-    \framebox{\parbox{0.8\linewidth}{
-        \texttt{\footnotesize\color{red} #1}}}
-  \end{center}}
 
-\newcommand\uvec[1]{\bm{\hat{#1}}}
-\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
-
-\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
-\newcommand{\grain}{\ensuremath{_{\text{d}}}}
-\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
-\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
-\newcommand{\xsec}{\ensuremath{\sigma\grain}}
-\newcommand\frad{\ensuremath{f_{\text{rad}}}}
-\newcommand\fmax{\ensuremath{f_{\text{max}}}}
-\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
-\newcommand\drag{\ensuremath{_{\text{drag}}}}
-\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
-\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
-\newcommand\rad{\ensuremath{_{\text{rad}}}}
-\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
-% Why do I need both of these?
-\newcommand\sound{\ensuremath{c_{\text{s}}}}
-\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
-\newcommand\starstar{\ensuremath{_{**}}}
+\input{bs-bw-dw-defs.tex}
 
@@
 
+% External document commands after macro definitions
+\externaldocument[Q-]{quadrics-bowshock}
+%\externaldocument[I-]{bs-bw-dw-01}
+%\externaldocument[II-]{bs-bw-dw-02}
+
 \begin{document}
 
-\message{ !name(sec-dust-bow-discuss.tex) !offset(-77) }
-\begin{figure}
+\message{ !name(sec-observational-diagnostics.tex) !offset(-85) }
+\section{Observational diagnostics}
+\label{sec:summary-discussion}
+
+% Are there any objects that might not be bow shocks?
+
+% Progression in density:
+% \begin{gather*}
+%   \text{Increasing density} \longrightarrow \\
+%   \text{WBS} \to \text{WBS} + \text{IDW} \to \text{WBS} + \text{DDW} \to \text{(RBW)} \to \text{RBS}
+% \end{gather*}
+
+% Chief diagnostic for radiation supported bows (RBW or RBS cases) is
+% infrared luminosity of bow.  Favored by high densities.
+
+% Dust waves favored by high velocities and intermediate densities.
+
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
-  \caption[K18 pair plot]{Pair plots of correlations between observed
-\message{ !name(dusty-bow-wave.tex) !offset(41) }
+  \includegraphics[width=0.8\linewidth]{figs/All-sources-eta-tau}
+  \caption[Observational diagnostic diagram]{Observational diagnostic
+    diagram for bow shocks.  The shell optical depth \(\tau\) (\(x\)
+    axis) and momentum efficiency \(\eta\shell\) (\(y\) axis) can be
+    estimated from observations of the bolometric stellar luminosity,
+    infrared shell luminosity, and shell radius, as described in the
+    text.  Results are shown for the 20 sources (circle symbols) from
+    \citet{Kobulnicky:2018a} plus three further sources (square
+    symbols), where we have obtained the measurements ourselves (see
+    Tab.~\ref{tab:observations}).  The color of each symbol indicates
+    the stellar luminosity (dark to light) as indicated by the scale
+    bar. The shell pressure is determined assuming a gas temperature
+    \(T = \SI{e4}{K}\), an absorption opacity
+    \(\kappa = \SI{600}{cm^2.g^{-1}}\), and a thickness-to-radius ratio
+    \(H/R = 0.25\).  The sensitivity of the results to a
+    factor-of-three change in each parameter is shown in the upper
+    inset box.  Exceptions are the two Orion Nebula sources, \thD{}
+    and LP~Ori, where the small dim squares show the results of
+    assuming the standard shell parameters, while the large squares
+    show the results of modifications according to the peculiar
+    circumstances of each object, as described in the text.  The lower
+    inset box shows the sensitivity of the results to a factor-of-two
+    uncertainty in each observed quantity: distance to source \(D\);
+    stellar luminosity \(L_*\), shell infrared flux \(F\IR\); shell
+    angular size \(\theta\).  Lines and shading indicate different
+    theoretical bow regimes (see \S\S~\ref{sec:strong-gas-grain} and
+    \ref{sec:imperf-coupl-betw}).  The dashed blue diagonal line
+    corresponds to radiation-supported bows, while the upper left
+    region corresponds to wind-supported bows.  The upper right corner
+    (purple) corresponds to optically thick bow shocks, while the
+    lower left corner (yellow) is the region where grain--gas
+    separation \textit{may} occur, leading to a potential dust wave.
+    However, the existence of a dust wave in this region is not
+    automatic, since it only includes one of the four necessary
+    conditions (\S~\ref{sec:exist-cond-separ} and
+    \S~\ref{sec:grain-traj-with}). The lower-right region is strictly
+    forbidden, except in case of violation of the assumption that dust
+    heating be dominated by stellar radiation. }
+  \label{fig:All-sources-eta-tau}
+\end{figure*}
+
+In order to provide an empirical anchor to our theoretical
+calculations, we now consider how the parameters of our models might
+be determined from observations.  The parameter space diagrams, such
+as Figures~\ref{fig:zones-v-n-plane} and
+\ref{fig:existence-dust-wave}, are not particularly useful in this
+regard, since in many cases the ambient density and relative stellar
+velocity are not directly measured.  Instead, we aim to construct
+diagnostics based on the most common observations, which are of the
+infrared dust emission.  Key questions that we wish to address include
+\begin{enumerate}[1.]
+\item Can we distinguish observationally between radiation support
+  (bow waves and dust waves) and wind support (bow shocks)?
+\item Are there any clear examples of sources with radiation-supported bows?
+\item In the case of wind support, can we reliably determine mass loss
+  rates from mid-infrared observations?
+\end{enumerate}
+
+\subsection{Energy trapping versus momentum trapping}
+\label{sec:energy-trapp-vers}
+
+A fundamental parameter is the optical depth, \(\tau\), of the bow
+shell to UV radiation, which determines what fraction of the stellar
+photon momentum is available to support the shell (see
+\S~\ref{sec:three-bow-regimes}).  But the same photons also heat the
+dust grains in the bow, which re-radiate that energy predominantly at
+mid-infrared wavelengths (roughly \SIrange{10}{100}{\um}) with
+luminosity \(L\IR\).  Assuming that Ly\(\alpha\) and mechanical
+heating of the dust shell is negligible (see
+\S~\ref{sec:unimp-other-heat}) and that the emitting shell subtends a
+solid angle \(\Omega\), as seen from the star, then the optical depth
+can be estimated as
+\begin{equation}
+  \label{eq:tau-empirical}
+  \tau = -\ln \left( 1 - \frac{4\pi}{\Omega} \frac{L\IR}{L_*} \right)
+  \approx \frac{2 L\IR}{L_*} \ ,
+\end{equation}
+where the last approximate equality holds if \(\tau \ll 1\) and the
+shell emission covers one hemisphere.\footnote{%
+  The \(\tau\) of \S~\ref{sec:three-bow-regimes} is not exactly the
+  same as the \(\tau\) of equation~\eqref{eq:tau-empirical}, but is
+  larger by a factor of
+  \(Q_P / Q_{\text{abs}} = 1 + \varpi (1 - g)/(1 - \varpi)\), where
+  \(\varpi\) is the grain albedo and \(g\) the scattering asymmetry
+  (see App.~\ref{sec:gas-free-bow}).} %
+
+A second important parameter is the thermal plus magnetic pressure in
+the shocked shell, which is doubly useful since in a steady state it
+is equal to \emph{both} the internal supporting pressure (wind ram
+pressure plus absorbed stellar radiation) \emph{and} the external
+confining pressure (ram pressure of ambient stream).  The shell
+pressure is not given directly by the observations, but can be
+determined by the following three steps:
+\begin{enumerate}[P1.]
+\item \label{P1} The shell mass column (\si{g.cm^{-2}}) can be
+  estimated from the optical depth by assuming an effective UV
+  opacity: \(\Sigma\shell = \tau / \kappa\)
+\item \label{P2} The shell density (\si{g.cm^{-3}}) can be found from
+  the mass column if the shell thickness is known:
+  \(\rho\shell = \Sigma / h\shell\).  In the absence of other
+  information, a fixed fraction of the shell radius can be used.  In
+  particular, we normalize by a typical value of
+  one~quarter\footnote{%
+    This corresponds to a Mach number \(\M_0 = \surd 3\) if the stream
+    shock is radiative, or \(\M_0 \gg 1\) if non-radiative (see
+    \S~\ref{sec:radi-cool-lengths}).  Further discussion is given in
+    Appendix~\ref{app:bow-shock-data}} %
+  the star--apex distance: \(h_{1/4} = h\shell / (0.25 R_0)\).
+\item \label{P3} Finally, the pressure (\si{dyne.cm^{-2}}) follows by
+  assuming values for the sound speed and Alfvén speed:
+  \(P\shell = \rho\shell (\sound^2 + \frac12 v\alfven^2) \).
+\end{enumerate}
+It is natural to normalize this pressure to the stellar radiation
+pressure at the shell, so we define a shell momentum efficiency
+\newcommand\pc{\ensuremath{_{\text{pc}}}}
+\begin{equation}
+  \label{eq:eta-shell}
+  \eta\shell \equiv \frac{P\shell}{P\rad}
+  = \frac{4\pi R_0^2\, (\sound^2 + \frac12 v\alfven^2)\, \tau}{L_*\, \kappa\, h\shell}
+  \approx 245 \frac{R\pc \, T_4 \, \tau}{L_4 \, \kappa_{600} \, h_{1/4}} \ , 
+\end{equation}
+where in the last step we have assumed ionized gas with negligible
+magnetic support (\(v\alfven \ll \sound\)) and written the stellar
+luminosity and shell parameters in terms of typical values, as in
+\S~\ref{sec:depend-stell-type}.  Note that the shell momentum
+efficiency is simply the reciprocal of the radiation parameter of
+equation~\eqref{eq:Xi-Prad-over-Pgas}:
+\(\eta\shell = \Xi\shell^{-1}\), which provides yet a third use for
+\(\eta\shell\), since \(\Xi\) is paramount in determining whether the
+grains and gas remain well-coupled (see
+\S~\ref{sec:exist-cond-separ}).
+
+\subsection[The eta-tau diagnostic diagram]
+{\boldmath The \(\eta\shell\)--\(\tau\) diagnostic diagram}
+\label{sec:eta-tau-diagnostic}
+
+\begin{table}
+  \centering
+  \caption[Observational]{Key observational parameters for star/bow systems}
+  \label{tab:observations}
+  \begin{tabular}{l S S S}
+    \toprule
+    Star & {\(L_* / \si{L_\odot}\)} & {\(L_{\text{IR}} / \si{L_\odot}\)} & {\(R_0 / \si{pc}\)} \\
+    \midrule
+    \thD & 2.95e4 & 620 & 0.003 \\
+    LP~Ori & 1600 & 240 & 0.01 \\
+    \(\sigma\)~Ori & 6e4 & 15 & 0.12 \\[\smallskipamount]
+    K18 Sources & \numrange{1.4e4}{8.7e5} & \numrange{8}{2800} & \numrange{0.02}{1.35} \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+In Figure~\ref{fig:All-sources-eta-tau} we show the resultant
+diagnostic diagram: \(\eta\shell\) versus \(\tau\).  The horizontal
+axis shows the fraction of the stellar radiative \emph{energy} that is
+reprocessed by the bow shell, while the vertical axis shows the
+fraction of stellar radiative \emph{momentum} that is imparted to the
+shell, either directly by absorption, or indirectly by the stellar
+wind (which is itself radiatively driven).  Radiatively supported bows
+(DW, RBW, or RBS, or cases) should lie on the diagonal line
+\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where
+we have used the ratio of grain radiation pressure efficiency to
+absorption efficiency found in the FUV band for the dust mixture shown
+in Figure~\ref{fig:cloudy-ism-dust-opacity}.  Wind-supported bows
+should lie above this line and no bows should lie below the
+\(\eta\shell = \tau\) line, since \(Q_P\) cannot be smaller than
+\(Q_{\text{abs}}\).
+
+We have calculated \(\eta\shell\) and \(\tau\) using the
+above-described methods for the 20 mid-infrared sources studied by
+\citet{Kobulnicky:2018a} (K18) and plotted them on our diagnostic
+diagram.  Details of our treatment of this observational material are
+provided in Appendix~\ref{app:bow-shock-data}.  In order to expand the
+range of physical conditions, we have included three additional
+sources (data in Table~\ref{tab:observations}): bows around \thD{}
+\citep{Smith:2005a} and LP~Ori \citep{ODell:2001c} in the Orion
+Nebula, which show larger optical depths, plus the inner bow around
+\(\sigma\)~Ori, which illuminates the Horsehead Nebula and has
+previously been claimed to be a dust wave \citep{Ochsendorf:2014b,
+  Ochsendorf:2015a}.  Details of the observations of these additional
+sources will be published elsewhere.
+
+\subsubsection{Random uncertainties due to observational errors}
+\label{sec:rand-syst-uncert}
+
+The fundamental observational quantities that go into determining
+\(\tau\) and \(\eta\shell\) for each source are distance, \(D\);
+stellar luminosity, \(L_*\); total infrared flux, \(F_{\text{IR}}\);
+and bow angular apex distance, \(\theta\).  From these, the shell
+radius and infrared luminosity are found as \(R_0 = \theta D\) and
+\(L_{\text{IR}} = 4\pi D^2 F_{\text{IR}}\).  Rather than clutter the
+diagram with error bars, we instead show the sensitivity to
+observational errors in the lower-right box, where each arrow
+corresponds to a factor of two increase (0.3~dex) in each quantity:
+\(D\), \(L_*\), \(F_{\text{IR}}\), and \(\theta\).  In
+\S~\ref{sec:uncert-estim-observ} we estimate the uncertainty in each
+observational quantity for the K18 sources.  We then combine these in
+\S~\ref{sec:comb-uncert-covar} to find the \(\pm 1~\sigma\) error
+ellipse, shown in blue in the figure.  It can be seen that
+observational uncertainties in \(\tau\) and \(\eta\shell\) are highly
+correlated: the dispersion is \SI{0.7}{dex} in the product
+\(\eta\shell \tau\) but only \SI{0.16}{dex} in the ratio
+\(\eta\shell/\tau\), with stellar luminosity errors dominating in both
+cases.  Observational uncertainties are therefore relatively
+unimportant in determining whether a given source is wind-driven or
+radiation-driven, which depends only on \(\eta\shell/\tau\).  On the
+other hand, they do significantly effect the question of whether a
+source has a sufficiently high radiation parameter \(\Xi\) to possibly
+be a dust wave.
+
+\subsubsection{Systematic uncertainties due to assumed shell parameters}
+\label{sec:syst-uncert-due}
+
+A further source of uncertainty arises from the parameters of the
+shocked shell that are assumed in steps P\ref{P1}--P\ref{P3}, namely
+the relative shell thickness, \(h\shell/R_0\), the ultraviolet grain
+opacity per mass of gas, \(\kappa\), and the shell temperature, \(T\).
+These parameters effect only \(\eta\shell\), not \(\tau\), with a
+sensitivity shown by arrows in the upper left box of
+Figure~\ref{fig:All-sources-eta-tau}.
+
+\subparagraph{Shell thickness}
+We do not expect a great deal of variation in the shell thickness,
+except for in the case of fast runaway stars
+(\(v > \SI{100}{km.s^{-1}}\)), for which the shell may be dramatically
+thinner if the post-shock cooling is sufficiently rapid
+(\(h / R_0 \sim M_0^{-2}\)).  For ambient densities less than about
+\SI{10}{cm^{-3}}, the minimum thickness is about ten times smaller
+than we are assuming.  This occurs at
+\(v \approx \SI{60}{km.s^{-1}}\), corresponding to the peak in the
+cooling curve at \SI{e5}{K} (see \S~\ref{sec:radi-cool-lengths}),
+since the thickness is set by the cooling length at higher speeds.  In
+principle, the shell thickness can be measured observationally if the
+source is sufficiently well resolved \citep{Kobulnicky:2017a},
+although this is complicated by projection effects.
+
+\subparagraph{Dust opacity}
+The dust opacity will depend on the total dust-gas ratio and on the
+composition and size distribution of the grains.  Our adopted value of
+\SI{600}{cm^2.g^{-1}}, or \SI{1.3e-21}{cm^2.H^{-1}}, is appropriate
+for average Galactic interstellar grains in the EUV and FUV (e.g.,
+\citealp{Weingartner:2001a}), but there is ample evidence for
+substantial spatial variations in grain extinction properties
+\citep{Fitzpatrick:2007a}, both on Galactic scales
+\citep{Schlafly:2016a} and within a single star forming region
+\citep{Beitia-Antero:2017a}.  The properties of grains within
+photoionized regions are very poorly constrained observationally
+because the optical depth is generally much lower than in overlying
+neutral material.  In the Orion Nebula, there is some evidence
+\citep{Salgado:2016a} that the FUV dust opacity in the ionized gas may
+be as low as \SI{90}{cm^2.g^{-1}}, although the uncertainties in this
+estimate are large and different results are obtained in other
+regions, such as W3(A) \citep{Salgado:2012a}.
+
+\subparagraph{Shell gas temperature} For bows around O~stars, the
+shell temperature should be close to the photoionization equilibrium
+value of \(\approx \SI{e4}{K}\), since the post-shock cooling length
+is short in ambient densities above \SI{0.1}{cm^{-3}}
+(\S~\ref{sec:radi-cool-lengths}) and the shell does not trap the
+ionization front for ambient densities below \SI{e4}{cm^{-3}}
+(\S~\ref{sec:trapp-ioniz-front}).  For B~stars, on the other hand,
+these two density limits move closer together (cf.~the smaller gap
+between the blue and red lines in Figs.~\ref{fig:zones-v-n-plane}a and
+\ref{fig:B-supergiant}, as compared with \ref{fig:zones-v-n-plane}b
+and~c), making it more likely that a bow will lie in a different
+temperature regime.  The only source for which we have evidence that
+this occurs is LP~Ori, as discussed in the next section.
+
+\subsubsection{Special treatment of particular sources}
+\label{sec:spec-treatm-part}
+
+For two of the additional bows listed in Table~\ref{tab:observations},
+we are forced to deviate from the default values for the shell
+parameters.  For LP~Ori, the bow shell appears to be formed from
+neutral gas \citep{ODell:2001c} and its relatively high \(\tau\) value
+is more than sufficient to trap the weak ionizing photon output of a
+B3 star.  We therefore move its point in
+Figure~\ref{fig:All-sources-eta-tau} downward to reflect a temperature
+of \SI{1000}{K} (or, equivalently, a magnetically supported shell with
+\(v\alfven \approx \SI{3}{km.s^{-1}}\)).  For the case of the Orion
+Trapezium star \thD{}, we find that using the default parameters
+results in a placement well inside the forbidden zone of
+Figure~\ref{fig:All-sources-eta-tau} (indicated by fainter symbol).
+For this object there is no reason to suspect anything but the usual
+photoionized temperature of \SI{e4}{K}, but its placement could be
+resolved either by decreasing the shell thickness, or decreasing the
+UV dust opacity, or both. Given the moderate limb brightening seen in
+the highest resolution images of the Ney--Allen nebula
+\citep{Robberto:2005a, Smith:2005a}, the shell thickness is unlikely
+to be less than half our default value.  But, if this were combined
+with a factor 5 decrease in \(\kappa\), as suggested by
+\citet{Salgado:2016a}, then this would be sufficient to move the
+source up to the RBW line, or slightly above.
+
+\subsection{Candidate radiation-supported bows}
+\label{sec:cand-radi-supp}
+
+Four sources are sufficiently close to the diagonal line
+\(\eta\shell = 1.25 \tau\) in Figure~\ref{fig:All-sources-eta-tau}
+that they should be treated as potential candidates for
+radiation-supported bows. These are K18 sources~380 (HD~53367,
+V750~Mon) and 407 (HD~93249 in Carina) plus \thD{} and LP~Ori.  Of the
+four, source 380 is the only one that is also a candidate for
+grain-gas decoupling.  Details of some of these sources are presented
+in \S~\ref{sec:notes-part-sourc}, where for source~380 we show that
+reducing both luminosity and distance by a factor of roughly 2 with
+respect to the values used by K18 would provide a better fit to the
+totality of observational data.  However, the ratio
+\(\eta\shell /\tau\) is proportional to \(D / L_*\) so it would not be
+affected by such an adjustment and the bow remains
+radiation-supported.  On the other hand \(\eta\shell\) (proportional
+to \(D / L_*^2\)) would increase by 2, making the classification as
+dust wave candidate more marginal.
+
+\subsection{Stellar wind mass-loss rates}
+\label{sec:stellar-wind-mass}
+
+Third method used by \citet{Gvaramadze:2012a}, relies on measurements
+of \hii{} region and bow. Only works for isolated stars.
+
+Mass loss rates - starting from \citet{Kobulnicky:2010a}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
+  \caption{Wind mass-loss rates as a function of stellar luminosity,
+    derived from (a)~our trapped energy/momentum method and (b)~the
+    grain emissivity method of \citet{Kobulnicky:2018a}, with
+    corrections as described in our Appendix~\ref{app:bow-shock-data}.
+    Circle symbols show the sources from K18, colored according to the
+    stellar effective temperature (see key at far right). In panel a,
+    squares show two of our additional sources
+    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
+    given for sources that lie close to the radiation-supported line
+    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
+    symbols and downward-pointing arrows.  Sources that lie less than
+    a factor of three above the line have enhanced downward
+    uncertainties and are also shown by slightly fainter symbols.  For
+    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
+    luminosities of the triple OB system Aa, Ab, and B
+    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
+    the luminosity of only the most massive component Aa.  Lines show
+    the predictions of stellar wind models: red lines are the commonly
+    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
+    (dashed), and supergiants (dotted), while black lines show
+    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
+    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
+    mass-loss measurements from NUV lines for weak-wind O~dwarfs
+    \citep{Marcolino:2009a}, while the green plus symbol shows the
+    measurement from infrared H recombination lines for \(\sigma\)~Ori
+    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
+    to observational uncertainties (lower right) and assumed shell
+    parameters (upper left).}
+  \label{fig:mass-loss-vs-luminosity}
+\end{figure*}
+
+Source~342 is anomalous in both methods.
+
+Evidence for small grains around Arches cluster near Galactic center \citep{Hankins:2017a}
+
+Different scenarios for producing velocities: dynamic ejection from
+young clusters \citep{Hoogerwerf:2001a, Oh:2016c} produce high
+velocities, dissolution of binary systems following core-collapse SN
+\citep{Renzo:2018a} tend to produce lower velocities for the unbound
+MS companion (walkaways, slower than 30 km/s).  Also, champagne flows
+have low velocities.
+
+How different regions of the \(\Pi\)--\(\Lambda\) plane are populated.
+Bottom-right quadrant hard to get to (except for standing wave
+oscillations), but may be due to finite shell thickness, which (for
+low Mach number) will be more apparent in the wings, which might
+decrease \(\Lambda\) more than \(\Pi\).  Fact that thin-shell solutions should
+trace the contact discontinuity, but in some cases it may be only the
+inner or the outer shell that is visible.
+
+Justification for standing waves: Fig.~3 of \citet{Meyer:2016a} shows
+a time sequence of thin-shell instability, which looks a bit like a
+standing wave. But much larger amplitude than we are considering.
+
+Deviations from axisymmetry as an alternative to oscillations.
+
+\subsection{Diagnosing bow type from shell emission profile}
+\label{sec:diagnosing-bow-type}
+
+Given that the predicted shell density profile varies between
+wind-supported and radiation-supported bows (Paper~I) it is worth
+considering whether it may be possible to use observed emission
+profiles to distinguish between the two.
+
+\subsection{The case of inside-out bows}
+\label{sec:case-inside-out}
+
+So far, we have considered the case where the inner source dominates
+the radiation, while dust is present only in the outer stream, which
+applies to hot stars interacting with the ISM.  However, in the case
+of cool stars, the inner wind will also be dusty.  Examples are the
+red supergiant (RSG) phase of high-mass evolution, or the asymptotic
+giant branch (AGB) stage of low/intermediate-mass evolution.  In both
+these cases, it is still the inner source that provides the radiation
+field.  However, not all winds are radiatively driven and in those
+cases it is conceivable that it is the outer source that dominates the
+radiation field.  An example is the case of photoevaporating
+protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
+regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
+thermally driven photoevaporation flow \citep{Henney:1998b, Henney:1999a},
+while the outer stream is the stellar wind from an O~star
+\citep{Garcia-Arredondo:2001a}.
+
+\section{Summary and conclusions}
+\label{sec:conclusions}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "bs-bw-dw-03"
+%%% End:
+
+\message{ !name(bs-bw-dw-03.tex) !offset(-415) }
 

### 2019-03-07 papers/Papers1234/bs-bw-dw-02.tex
Start writing about the shell structure figure
Finish first complete draft of Paper I

@@
 \input{sec-weak-coupling}
+
+\section*{Acknowledgements}
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grants Programa de Apoyo a Proyectos de Investigación
+e Inovación Tecnológica IN112816 and IN107019.  This work has made
+extensive use of Python language libraries from the SciPy
+\citep{Jones:2001a} and AstroPy \citep{Astropy-Collaboration:2013a,
+  Astropy-Collaboration:2018a} projects.
+
 \bibliographystyle{mnras}

### 2019-03-07 papers/Papers1234/sec-dust-bow-intro.tex
Finish first complete draft of Paper I

@@
 %
-In \S~\ref{sec:summary-discussion} we briefly discuss the application
+In \S~\ref{sec:discussion} we briefly discuss the application
 of our models to observed bows.
 %
-In \S~\ref{sec:conclusions} we summarise the conclusions of our study. 
+In \S~\ref{sec:summary} we summarise the conclusions of our study. 
 %

### 2019-03-07 papers/Papers1234/sec-observational-diagnostics.tex
Divide dust wave paper in three parts
Finish first complete draft of Paper I

--- 2019-02-26 papers/Papers1234/sec-dust-bow-discuss.tex
@@
-\section{Discussion}
+\section{Observational diagnostics}
 \label{sec:summary-discussion}
@@
 
+Third method used by \citet{Gvaramadze:2012a}, relies on measurements
+of \hii{} region and bow. Only works for isolated stars.
+
 Mass loss rates - starting from \citet{Kobulnicky:2010a}
@@
 
+\subsection{Diagnosing bow type from shell emission profile}
+\label{sec:diagnosing-bow-type}
+
+Given that the predicted shell density profile varies between
+wind-supported and radiation-supported bows (Paper~I) it is worth
+considering whether it may be possible to use observed emission
+profiles to distinguish between the two.
+
 \subsection{The case of inside-out bows}
@@
 %%% mode: latex
-%%% TeX-master: "dusty-bow-wave"
+%%% TeX-master: "bs-bw-dw-03"
 %%% End:

### 2019-03-07 papers/Papers1234/sec-strong-coupling.tex
Finish first complete draft of Paper I

@@
   \SIrange{2500}{3300}{km.s^{-1}}, which are consistent with
-  observations and theory \citep{Vink:1999a}, but at least two times
+  observations and theory \citep{Vink:2000a}, but at least two times
   higher than those cited by \citet{Meyer:2014b}. } %
@@
 
-\subsection{Environments of bow-forming stars}
-\label{sec:popul-bow-prod}
-
 The stellar bows modeled in this paper can be seen as either due to
@@
 efficiency in terms of the Table~\ref{tab:stars} values,
-\(\eta\vink\), which are calculated from the \citet{Vink:1999a} recipe,
+\(\eta\vink\), which are calculated from the \citet{Vink:2000a} recipe,
 and the UV dust opacity in terms of the standard ISM value adopted in
@@
 supported.
-
-For cases where the stellar wind or dust properties differ from our
-assumed values, then these conclusions may change.  For instance,
-there are a growing number of stars, for which very low mass-loss
-rates have been diagnosed from UV, optical or infrared line profiles
-\citep{Martins:2005b, Marcolino:2009a, Najarro:2011a, Martins:2012a,
-  Smith:2017b}.  Most of these stars are late-type O~dwarfs, for which
-the \citet{Vink:2000a} prescription predicts a mass-loss rate of
-\num{3e-8} to \SI{e-7}{M_\odot.yr^{-1}}, whereas the observed values are
-in the range \num{e-10} to \SI{3e-9}{M_\odot.yr^{-1}} -- a shortfall of 10
-to 1000!  This ``weak wind problem'' is a far larger discrepancy than
-can be explained by clumping effects.  A potential (partial)
-resolution is to suppose that internal shocks near the base of the
-wind, together with thermal conduction, heat a large fraction of the
-gas to coronal temperatures, where it is no longer detectable by means
-of standard wind diagnostic lines \citep{Lucy:2012a}.  However, in
-cases where x-ray diagnostics have been used to trace the mass loss
-this hot component (\(\mu\)~Col, \citealp{Huenemoerder:2012a};
-\(\zeta\)~Oph, \citealp{Cohen:2014a}), rates that are still an order of
-magnitude below the Vink values are found.  We therefore show in
-
-\subsection{Impact of the weak-wind phenomenon}
-\label{sec:impact-weak-wind}
 
@@
 
-Hot stars, comparison with expected velocities and densities.
+For cases where the stellar wind or dust properties differ from our
+assumed values, then these conclusions may change.  For instance,
+there are a growing number of stars, for which very low mass-loss
+rates have been diagnosed from UV, optical or infrared line profiles
+\citep{Martins:2005b, Marcolino:2009a, Najarro:2011a, Martins:2012a,
+  Shenar:2017a, Smith:2017b}.  Most of these stars are late-type
+O~dwarfs, for which the \citet{Vink:2000a} prescription predicts a
+mass-loss rate of \num{3e-8} to \SI{e-7}{M_\odot.yr^{-1}}, whereas the
+observed values are in the range \num{e-10} to \SI{3e-9}{M_\odot.yr^{-1}}
+-- a shortfall of 10 to 1000!  This ``weak wind problem'' is a far
+larger discrepancy than can be explained by clumping effects.  A
+potential (partial) resolution is to suppose that internal shocks near
+the base of the wind, together with thermal conduction, heat a large
+fraction of the gas to coronal temperatures, where it is no longer
+detectable by means of standard wind diagnostic lines
+\citep{Lucy:2012a}.  However, in cases where x-ray diagnostics have
+been used to trace the mass loss of this hot component (\(\mu\)~Col,
+\citealp{Huenemoerder:2012a}; \(\zeta\)~Oph, \citealp{Cohen:2014a}), rates
+that are still an order of magnitude below the Vink values are found
+(see also \citealp{Shenar:2017a}).  In Figure~\ref{fig:O-weak-wind},
+we show results for a weak-wind O9 dwarf, which is identical to the
+\SI{20}{M_\odot} star from Table~\ref{tab:stars}, except with
+\(\eta\wind = 0.01 \eta\vink\) (approximating the measurements from the
+sample of \citealp{Martins:2005b}).  For such stars, the boundary
+between the wind-supported and radiation-supported regimes shifts to
+lower ambient densities, reaching \(n\crit \sim \SI{1}{cm^{-3}}\) for
+\(v = \SI{20}{km.s^{-1}}\).  This means that radiation-supported bows
+become feasible even in the diffuse ISM for this important class of
+stars (if winds are really as weak as the UV diagnostics suggest).  It
+is therefore important to critically re-evaluate attempts to
+\emph{measure} mass loss rates using observations of bows
+\citep{Gvaramadze:2012a, Kobulnicky:2018a} since such calculations
+invariably assume that the WBS regime is universally applicable.  This
+issue is addressed in detail in Paper~III.
 
-Expected velocities.  There are cases of high velocities, e.g., AE~Aur, but they are probably rare. \citep{Renzo:2018a}
-In cases, where proper motions are measured, they are often low.
+Variations in the UV dust opacity would also effect our results.
+These may be due to variations in the dust/gas ratio or to changes in
+the size distribution of the grains.  The UV opacity is dominated by
+very small grains (VSG) with radius \(a \sim \SI{10}{nm}\), which
+represent a small fraction (\(\simeq 5\%\)) of the total dust mass in
+standard grain mixtures \citep{Desert:1990a}.  This same VSG
+population dominates the mid-infrared continuum emission around
+\SI{24}{\um}, which is where stellar bows are most easily detected
+\citep{Meyer:2016a, Kobulnicky:2016a}. There is some evidence that
+such grains may be depleted in the ionized gas of the Orion Nebula
+\citep{Salgado:2016a}, leading to a decrease in \(\kappa\) by a factor of
+about six.  By equation~\eqref{eq:ncrit}, this would increase
+\(n\crit\) by the same factor, making radiation-supported bows less
+likely.  On the other hand, the process of Radiative Torque Disruption
+is predicted to be important \citep{Hoang:2018a} for the high
+radiation fields found in stellar bows, and this would tend to
+\emph{increase} the VSG abundance (and hence \(\kappa\)) via the
+centrifugal destruction of larger grains.  In LMC \hii{} regions,
+\citet{Stephens:2014b} find observational evidence that the VSG
+abundance increases as the radiation field gets stronger.
 
-Metallicity dependence of wind strength. RBW more likely at lower metallicities.
-
-Weak wind stars - repeat the 20 Msun case, but for a much lower \(\eta\wind\)
+Variations in metallicity will also be reflected in
+\(\kappa\), assuming that the total dust-gas ratio is roughly proportional
+to the metal abundance, \(Z\).  However, the wind strength
+\(\eta\wind\) will also increases with metallicity
+(\(\dot{M} V\wind \propto Z^{0.82}\), \citealp{Vink:2001a}), which will
+largely cancel out the effect in our bow models.
 
@@
 
-Cool stars, comparison with observed densities (Betelgeuse, for
-instance). Other ones in \citep{Cox:2012a}.
+% Cool stars, comparison with observed densities (Betelgeuse, for
+% instance). Other ones in \citep{Cox:2012a}.
 
-Prospects for observation in LMC: 1 parsec = 4 arcsec, so need JWST to get most of them.
+% Prospects for observation in LMC: 1 parsec = 4 arcsec, so need JWST to get most of them.
 
-\subsection{Diagnosing bow type from shell emission profile}
-\label{sec:diagnosing-bow-type}
+\section{Summary}
+\label{sec:summary}
 
-Given that the predicted shell density profile varies between
-wind-supported and radiation-supported bows
-(\S~\ref{sec:axial-structure-bow} and Fig.~\ref{fig:axial-structure}),
-it is worth considering whether it may be possible to use observed
-emission profiles to distinguish between the two.
+We present a systematic study of the formation of emission arcs, or
+bows, around luminous stars that move supersonically relative to their
+surrounding medium, taking into account both the stellar wind and
+radiation pressure of the star.  In this initial study, we consider
+the case where gas and grains are perfectly coupled via collisions,
+and apply our models to OB stars.  Our principal results are as
+follows:
+\begin{enumerate}[1.]
+\item Three different regimes of interaction are possible, in order of
+  increasing optical depth of the bow shell: Wind-supported Bow Shock
+  (WBS), Radiation-supported Bow Wave (RBW), and Radiation-supported
+  Bow Shock (RBS).
+\item For a broad range of stellar types, the WBS regime occurs when
+  the ambient density is below a critical density:
+  \(n\crit \approx \SI{100}{cm^{-3}}\) for a typical relative velocity of
+  \SI{20}{km.s^{-1}}.
+\item The critical density increases for faster moving stars, but
+  decreases for stars with weak stellar winds.
+\item At densities higher than \(n\crit\), B~stars tend to be in the
+  RBW regime, and O~stars in the RBS regime.
+\item For main sequence OB stars, the bow shell remains fully
+  photoionized for ambient densities up to about 100 times
+  \(n\crit\). For isolated B~supergiants, on the other hand, the
+  ionization front may be trapped by the shell even in the WBS regime.
+\item The bow shell in the RBW regime tends to be broad, with the
+  density gradually ramping up at the inner and outer edges, whereas
+  in the WBS and RBS regimes the shell is thinner with more sharply
+  defined edges.
+\item Studies that have estimated wind mass-loss rates from
+  observations of bows need to be re-evaluated in the light of
+  possible radiation support. 
+\end{enumerate}
 

### 2019-03-08 papers/Papers1234/app-dust-wave.tex
Paper II - fix lots of xrefs, reorganize and tidy up

@@
 
-A dust grain of geometrical cross-section \(\xsec\) situated a
-distance \(R\) from a point source of radiation with luminosity \(L\)
-will experience a repulsive, radially directed radiative force
-\citep[e.g.,][]{Spitzer:1978a}
+In the optically thin limit, a spherical dust grain of radius \(a\)
+situated a distance \(R\) from a point source of radiation with
+luminosity spectrum \(L_\nu\) will experience a repulsive, radially
+directed radiative force \citep[e.g.,][]{Spitzer:1978a}
 \begin{equation}
   \label{eq:dust-rad-force}
-  \frad = \frac{\xsec \Qp L} {4 \pi R^2 c} e^{-\tau}
+  \frad = \frac{\pi a^2 } {4 \pi R^2 c}  \int_0^\infty \Qp \, L_\nu \, d\nu 
 \end{equation}
-where \Qp{} is the frequency-averaged\footnote{%
-  Frequency averages of any quantity \(x\) should be understood as
-  weighted by the attenuated source spectrum:
-  \(\langle x \rangle_\nu = (L \, e^{-\tau})^{-1} \int_0^\infty x(\nu)\, L_\nu \, e^{-\tau_\nu} \, d\nu
-  \).  } %
-radiation pressure efficiency\footnote{%
+where \Qp{} is the frequency-dependent radiation pressure efficiency\footnote{%
   \label{fn:Qp}
@@
   cosine) \(g\), we have
-  \(\Qp = Q_{\text{abs}} + (1 - g) Q_{\text{scat}}\)
-  \citep[e.g., \S~4.5 of][]{Bohren:1983a}.} %
-of the grain, \(c\) is the speed of light, and \(\tau\) is the
-frequency-averaged optical depth between the source and the grain.
-For simplicity, we will consider only the optically thin case,
-\(\tau \to 0\).
+  \(\Qp = Q_{\text{abs}} + (1 - g) Q_{\text{scat}}\) \citep[e.g.,
+  \S~4.5 of][]{Bohren:1983a}.} %
+of the grain, and \(c\) is the speed of light.
 
@@
   \label{eq:dust-r0}
-  R\starstar = \frac{\xsec \Qp L} {2 \pi c m\grain v_\infty^2} \ ,
+  R\starstar = \frac{\kappa\grain L} {2 \pi c v_\infty^2} \ ,
 \end{equation}
-where \(m\grain\) is the grain mass.  The grain then turns round and
-recedes from the source along the same radius, reaching a velocity of
-\(+v_\infty\) at large distance.  Note that \(R\starstar\) as given by
-equation~\eqref{eq:dust-r0} is the equivalent of
-equation~\eqref{eq:rad:R0}, except for a single grain considered in
-isolation, rather than a well-coupled dusty plasma.
+where we have defined a frequency-averaged single-grain opacity
+(\si{cm^2.g^{-1}}) as
+\begin{equation}
+  \label{eq:kappa-grain}
+  \kappa\grain = \frac{\pi a^2}{m\grain L} \int_0^\infty \Qp \, L_\nu \, d\nu \ ,
+\end{equation}
+in which \(m\grain\) is the grain mass and \(L\) is the bolometric
+source luminosity.  The grain then turns round and recedes from the
+source along the same radius, reaching a velocity of \(+v_\infty\) at large
+distance.  Note that \(R\starstar\) as given by
+equation~\eqref{eq:dust-r0} is formally identical to Paper~I's
+equation~(6), but with the important difference that it is for a
+single grain considered in isolation, rather than a well-coupled dusty
+plasma.  If
 
-For \(b > 0\), the trajectory, \(R\grain(\theta; b)\), is
-found\footnote{%
-  The problem is formally identical to that of Rutherford scattering,
-  or (modulo a change of sign) planetary orbits.  The method of
-  solution (via introduction of a centrifugal potential term and
+For \(b > 0\), the problem is formally identical to that of Rutherford
+scattering, or (modulo a change of sign) planetary orbits.  The method
+of solution (via introduction of a centrifugal potential term and
 reduction to a 1-dimensional problem) can be found in any classical
-  mechanics text \citep[e.g.,][\S~14]{Landau:1976a}.} %
-to be hyperbolic, characterized by an eccentricity,
+mechanics text \citep[e.g.,][\S~14]{Landau:1976a}.  The trajectory,
+\(R\grain(\theta; b)\), is found to be hyperbolic, characterized by an
+eccentricity,
 \(\varepsilon = \bigl( 1 + 4 b^2 / R\starstar^2\bigr)^{1/2}\), and polar angle
@@
 \(\theta \to \theta + \theta_1(b)\), where \(\sin \theta_1 = b / D\) (see
-Fig.~\ref{Q-fig:crw-schema} of \PaperI{}). We parametrize the degree
-of divergence as \(\mu = R\starstar / D\) and, as before,
-\(R\grain(\theta + \theta_1(b, \mu); b)\) is minimized over all trajectories to
-find the shape of the bow wave's inner edge.  This time, the result is
-a confocal hyperbola:
+Fig.~\ref{Q-fig:crw-schema} of \citealp{Tarango-Yong:2018a}). We
+parameterize the degree of divergence as \(\mu = R\starstar / D\) and, as
+before, \(R\grain(\theta + \theta_1(b, \mu); b)\) is minimized over all
+trajectories to find the shape of the bow wave's inner edge.  This
+time, the result is a confocal hyperbola:
 \begin{equation}
@@
 
-\subsection{Tight magnetic coupling}
+\subsection{Magnetized dust waves}
 \label{sec:tight-magn-coupl}
@@
 
-As discussed in \S~\ref{sec:magn-effects-grain}, for small grains
-(\(a < \SI{0.1}{\um}\)) the Larmor magnetic gyration radius, \(r\B\)
+We will show later in \S~\ref{sec:magn-effects-grain} that for
+sufficiently small grains the Larmor magnetic gyration radius, \(r\B\)
 is typically small compared with other length scales of interest, and
@@
 %%% mode: latex
-%%% TeX-master: "dusty-bow-wave"
+%%% TeX-master: "bs-bw-dw-02"
 %%% End:

### 2019-03-08 papers/Papers1234/bs-bw-dw-02.tex
Paper II - fix lots of xrefs, reorganize and tidy up

@@
 
+\section{Introduction}
+\label{sec:rip-introduction}
+
+In \S~\ref{sec:gas-free-bow} we calculate analytical
+models of the shape of dust waves in the drag-free limit.
+%
+In \S\ref{sec:cloudy-models-dust} we discuss the relevant dust physics
+and the Cloudy models that we employ.
+%
+In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
+charging and dynamics, subject to radiation and drag forces, in order
+to determine the rip point where gas--grain coupling catastrophically
+breaks down.  This is used to determine existence conditions for the
+presence of a decoupled dust wave.
+%
+In \S~\ref{sec:magn-effects-grain} we consider the additional coupling
+between the grains and the plasma's magnetic field, and how this
+effects the existence and structure of dust waves.
+%
+In Appendix~\ref{sec:equat-moti-grains} we provide additional
+technical information on the numerical calculation of grain
+trajectories.
+
+\input{app-dust-wave}
+
+\input{app-cloudy-dust-charging}
+
 \input{sec-weak-coupling}
@@
 \appendix
-\input{app-cloudy-dust-charging}
-\input{app-dust-wave}
 \input{app-dust-equations}

### 2019-03-08 papers/Papers1234/sec-weak-coupling.tex
Paper II - fix lots of xrefs, reorganize and tidy up

@@
-\section{Introduction}
-\label{sec:rip-introduction}
-
-In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
-charging and dynamics, subject to radiation and drag forces, in order
-to determine the rip point where gas--grain coupling catastrophically
-breaks down.  This is used to determine existence conditions for the
-presence of a decoupled dust wave.
-%
-In \S~\ref{sec:magn-effects-grain} we consider the additional coupling
-between the grains and the plasma's magnetic field, and how this
-effects the existence and structure of dust waves.
-%
-A series of appendices provide additional technical information on
-dust physics (Appendix~\ref{sec:cloudy-models-dust}), analytical
-models of the shape of dust waves in the drag-free limit
-(Appendix~\ref{sec:gas-free-bow}), and the numerical calculation of
-grain trajectories (Appendix~\ref{sec:equat-moti-grains}).
-
 \section{Imperfect coupling between gas and dust}
@@
 be expressed in terms of \(R_*\), the fiducial optically thick bow
-shock radius introduced in \S~\ref{sec:strong-gas-grain}:
+shock radius introduced in Paper~I's \S~2.1:
+%% XREF \ref{sec:three-bow-regimes}
 \begin{equation}
@@
 \end{equation}
-where we have made use of equations~\eqref{eq:Rstar}
-and~\eqref{eq:Xi-Prad-over-Pgas}.
+where we have made use of equation~\eqref{eq:Xi-Prad-over-Pgas} and
+Paper~I's equation~(3).
+%% XREF \eqref{eq:Rstar}
 
@@
     waves may form around main-sequence OB stars of
-    \SIlist{10;20;40}{M_\odot} (see Tab.~\ref{tab:stars}).  Figure is
-    similar to Fig.~\ref{fig:zones-v-n-plane}, except that the
-    velocity axis is logarithmic and extends out to
+    \SIlist{10;20;40}{M_\odot} (see Paper~I's Tab.~1).  This figure is
+    similar to Paper~I's Fig.~2,
+    %% XREF\ref{fig:zones-v-n-plane},
+    except that the velocity axis is logarithmic and extends out to
     \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show parameters
@@
 hits the hydrodynamic bow shock caused by the stellar wind.  The wind
-bow shock radius is \(R_0 = \eta\wind^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]),
+bow shock radius is \(R_0 = \eta\wind^{1/2} R_*\) (Paper~I's eq.~[12]),
+%% XREF \ref{eq:x-cases}
 where \(\eta\wind\) is the wind momentum efficiency
-(eq.~[\ref{eq:wind-eta-typical}]).  Therefore, the condition
+(Paper~I's eq.~[13]).
+%% XREF \ref{eq:wind-eta-typical}
+Therefore, the condition
 \(R_\dag > R_0\) becomes from equation~\eqref{eq:Rdag-over-Rstar}:
@@
 \end{equation}
-For O stars, the wind efficiency is generally high (\(\eta\wind > 0.1\)) and
+For early O main-sequence stars and OB supergiants, the wind
+efficiency is generally high (\(\eta\wind > 0.1\)) and
 \(\Xi_\dag > 2000\) (Tab.~\ref{tab:Xi-rip}), so that dust waves can only
 exist when the stream velocity is very high
-(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For B~stars, in contrast, the wind
-can be much weaker (\(\eta\wind < 0.01\)) and \(\Xi_\dag\) is also smaller, so
-that dust waves are permitted by this criterion for much lower stream
-velocities: (\(v_\infty > \SI{30}{km.s^{-1}}\)).
+(\(v_\infty > \SI{150}{km.s^{-1}}\)).  For main-sequence B~stars, in
+contrast, the wind can be much weaker (\(\eta\wind < 0.01\)) and
+\(\Xi_\dag\) is also smaller, so that dust waves are permitted by this
+criterion for much lower stream velocities:
+(\(v_\infty > \SI{30}{km.s^{-1}}\)).  The same will be true of the
+``weak-wind'' class of late O main-sequence stars, which also show
+\(\eta\wind < 0.01\) (see Paper~I, \S~4).
 
@@
 opportunely, even once it has decoupled from the gas.  From
-equations~\eqref{eq:Rstar}, \eqref{eq:tau-star},
-and~\eqref{eq:dust-r0} we find
+equation~\eqref{eq:dust-r0}, together with Paper~I's equations~(3, 9),
+%% XREF \eqref{eq:Rstar}
+%% XREF \eqref{eq:tau-star},
+we find
 \begin{equation}
   \label{eq:Rstarstar-over-Rstar}
-  \frac{R\starstar}{R_*} = \frac{2 \sigma\grain \Qp \tau_*}{\kappa m\grain} \ , 
+  \frac{R\starstar}{R_*} = \frac{2 \kappa\grain \tau_*}{\kappa} \ , 
 \end{equation}
-so, if we define a single-grain opacity as
-\(\kappa\grain = \sigma\grain \Qp / m\grain\), then this condition becomes
+so the condition becomes
 \begin{equation}
@@
 dominate the UV opacity.  Given the dependence of \(\tau_*\) on the
-stream parameters (eq.~[\ref{eq:taustar-typical}]), for a given
+stream parameters (Paper~I's eq.~[15]),
+%% XREF \ref{eq:taustar-typical}
+for a given
 stellar luminosity this condition corresponds to a minimum value for
@@
 A third condition comes from requiring \(R_\dag > R_0\) in the radiation
-bow wave regime (see \S~\ref{sec:three-bow-regimes}), where
+bow wave regime (see Paper~I's \S~2.1),
+%% XREF \ref{sec:three-bow-regimes}
+where
 \(R_0 \approx 2 \tau_* R_*\).  This yields
@@
 Figure~\ref{fig:existence-dust-wave} for each of the three example
-main sequence stars from Table~\ref{tab:stars}.  Further restrictions
+main sequence stars from Paper~I's Table~1.
+%% XREF \ref{tab:stars}
+Further restrictions
 on the existence of dust waves arise when the effects of magnetic
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/frozen-stream-map-multi}
-  \caption{Drag-confined dust waves with tight magnetic coupling.
-    Upper panels show a quasi-parallel field, \(\theta\B = \ang{10}\),
-    while lower panels show a quasi-perpendicular field,
-    \(\theta\B = \ang{75}\).  Left panels show an incident stream velocity of
-    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels show
-    \(v_\infty = \SI{80}{km.s^{-1}}\).  In all cases, the stream density is
-    \(n = \SI{10}{cm^{-3}}\) and the calculations are performed for
-    small graphite grains, \(a = \SI{0.02}{\um}\), and the
-    \SI{10}{M_\odot} main-sequence B~star.  Continuous black lines show
-    grain trajectories, with triplets of colored symbols indicating
-    the progress of individual cohorts, which entered from the right
-    edge at a particular time.  Continuous blue lines show the
-    magnetic field, which flows from right to left along with the
-    incident stream.  The radius of the rip point, \(R_\dag\), and the
-    stagnant drift point, \(R_\ddag\), are shown respectively by red and
-    blue dashed lines.  The approximate shape of the wind-supported
-    bow shock is shown by the dotted gray line.  The calculations are
-    no longer valid after trajectories cross this surface.}
-  \label{fig:frozen-stream}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/frozen-trajectories-multi}
-  \caption{Sample grain trajectories for drag-confined dust waves with
-    tight magnetic coupling and a quasi-parallel field
-    orientation. These are the same models as in the upper row of
-    Fig.~\ref{fig:frozen-stream}. (a)~Incident stream velocity of
-    \(v_\infty = \SI{40}{km.s^{-1}}\), showing quasi-limit-cycle behavior
-    (\numrange{0}{4000} years).  (b)~Incident stream velocity of
-    \(v_\infty = \SI{80}{km.s^{-1}}\), showing quasi-stagnation behavior
-    (\numrange{500}{2000} years).  In both cases, the streamline with
-    initial impact parameter \(y = -0.4 R_\dag\) is shown.}
-  \label{fig:frozen-trajectories}
-\end{figure}
-
-An important effect that we have not considered up to now is the
-Lorentz force on charged grains due to the plasma's magnetic field:
+It remains to calculate in detail the effects on grain dynamics of the
+plasma's magnetic field, in order to justify the approach taken in
+\S~\ref{sec:tight-magn-coupl} and extend those results to include the
+effects of gas--grain collisions as in \S~\ref{sec:imperf-coupl-betw}.
+The Lorentz force on charged grains due to a magnetic field is
 \begin{equation}
@@
 material density in \si{g.cm^{-3}}, and we have made use of
-equations~(\ref{eq:Rstar-typical}, \ref{eq:Rdag-over-Rstar},
-\ref{eq:dust-r0}).
+equations~(\ref{eq:dust-r0}, \ref{eq:Rdag-over-Rstar}), together with Paper~I's equation~(14).
+%% XREF \ref{eq:Rstar-typical}
 
@@
 \label{sec:grain-traj-with}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/frozen-stream-map-multi}
+  \caption{Drag-confined dust waves with tight magnetic coupling.
+    Upper panels show a quasi-parallel field, \(\theta\B = \ang{10}\),
+    while lower panels show a quasi-perpendicular field,
+    \(\theta\B = \ang{75}\).  Left panels show an incident stream velocity of
+    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels show
+    \(v_\infty = \SI{80}{km.s^{-1}}\).  In all cases, the stream density is
+    \(n = \SI{10}{cm^{-3}}\) and the calculations are performed for
+    small graphite grains, \(a = \SI{0.02}{\um}\), and the
+    \SI{10}{M_\odot} main-sequence B~star.  Continuous black lines show
+    grain trajectories, with triplets of colored symbols indicating
+    the progress of individual cohorts, which entered from the right
+    edge at a particular time.  Continuous blue lines show the
+    magnetic field, which flows from right to left along with the
+    incident stream.  The radius of the rip point, \(R_\dag\), and the
+    stagnant drift point, \(R_\ddag\), are shown respectively by red and
+    blue dashed lines.  The approximate shape of the wind-supported
+    bow shock is shown by the dotted gray line.  The calculations are
+    no longer valid after trajectories cross this surface.}
+  \label{fig:frozen-stream}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/frozen-trajectories-multi}
+  \caption{Sample grain trajectories for drag-confined dust waves with
+    tight magnetic coupling and a quasi-parallel field
+    orientation. These are the same models as in the upper row of
+    Fig.~\ref{fig:frozen-stream}. (a)~Incident stream velocity of
+    \(v_\infty = \SI{40}{km.s^{-1}}\), showing quasi-limit-cycle behavior
+    (\numrange{0}{4000} years).  (b)~Incident stream velocity of
+    \(v_\infty = \SI{80}{km.s^{-1}}\), showing quasi-stagnation behavior
+    (\numrange{500}{2000} years).  In both cases, the streamline with
+    initial impact parameter \(y = -0.4 R_\dag\) is shown.}
+  \label{fig:frozen-trajectories}
+\end{figure}
 

### 2019-03-08 papers/Papers1234/app-cloudy-dust-charging.tex
Major surgery on Paper II

@@
-\section{Grain charging and gas--grain coupling around OB stars}
-\label{sec:cloudy-models-dust}
-
-We calculate models of the physical properties of dust grains using
-the plasma physics code Cloudy \citep{Ferland:2013a, Ferland:2017a},
-which self-consistently solves the multi-frequency radiative transfer
-together with thermal, ionization, and excitation balance of all
-plasma constituents.  Cloudy incorporates grain charging as described
-in \citet{Baldwin:1991a} and \citet{van-Hoof:2004a} with photoelectric
-emission theory from \citet{Weingartner:2001b, Weingartner:2006a}.  We
-use the default ``ISM'' dust mixture included in Cloudy, which
-comprises ten size bins each for spherical silicate and graphite
-grains in the range \num{0.005} to \SI{0.25}{\um}, and which is
-designed to reproduce the average Galactic extinction curve
-\citep{Weingartner:2001a, Abel:2008a}.  The optical properties of each
-grain species are calculated using Mie theory \citep{Bohren:1983a},
-assuming solid spheres.  The resultant wavelength-dependent extinction
-properties of the mixture are summarised in
-Figure~\ref{fig:cloudy-ism-dust-opacity}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/cloudy-ism-dust-opacity}
-  \caption{Extinction properties of Cloudy's standard ``ISM'' dust
-    mixture. %
-    (a)~Wavelength dependence of mean values over the entire mixture
-    of three dimensionless quantities related to scattering: albedo,
-    \(\varpi\) (solid line); scattering asymmetry,
-    \(g = \langle \cos\theta \rangle\) (dashed line); ratio of radiation pressure
-    efficiency to absorption efficiency, \(Q_P / Q_{\text{abs}}\)
-    (dotted line).
-    %
-    (b)~Wavelength dependence of mass opacity (cross section per unit
-    mass of gas) for the whole mixture (heavy black line) and broken
-    down by size bin and grain composition (colored lines, see key). }
-  \label{fig:cloudy-ism-dust-opacity}
-\end{figure}
-
-To ascertain the expected variation in grain properties in the
-circumstellar environs of luminous stars, we calculate a series of
-spherically symmetric, steady-state, constant density Cloudy simulations,
-illuminated by the stars listed in Table~\ref{tab:stars}, with stellar
-spectra taken from the OSTAR2002 and BSTAR2006 grids, calculated with
-the TLUSTY model atmosphere code \citep{Lanz:2003a, Lanz:2007a}.
-Simulations are run for hydrogen densities of
-\numlist{1;10;100;e3;e4} \si{cm^{-3}} and assuming standard \hii{} region
-gas phase abundances.  The calculation is stopped when the ionization
-front is reached and the inner radius is chosen to be roughly 1\% of this.
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/multi-dustprops}
-  \caption{Dust properties as a function of radius from star for three
-    selected Cloudy simulations. (a)~\SI{40}{M_\odot} main-sequence star in
-    medium of density \SI{e4}{cm^{-3}}. (b)~\SI{10}{M_\odot} main-sequence
-    star in medium of density \SI{1}{cm^{-3}}. (c)~Blue supergiant
-    star in medium of density \SI{1}{cm^{-3}}}.
-  \label{fig:multi-dustprops}
-\end{figure*}
-Figure~\ref{fig:multi-dustprops} shows resultant radial profiles of
-dust properties for representative simulations: grain temperature, grain
-abundance, grain potential, and grain drift velocity.  Line types
-correspond to the different size bins of graphite and silicate grains,
-as indicated in the key from smallest to largest. The left hand panels
-show results for a high-density (\(n = \SI{e4}{cm^{-3}}\)), compact
-(\(R \approx \SI{0.1}{pc}\)) region around an early O~star, where the grain
-temperature is very high, especially for the smaller silicate grains,
-and sublimation significantly reduces the grain abundance in the inner
-regions.  The remaining columns show low-density
-(\(n = \SI{1}{cm^{-3}}\)), extended (\(R \sim \SI{10}{pc}\)) regions
-around main-sequence and supergiant B-type stars, in which the grain
-temperatures are much lower, ranging from \SIrange{20}{50}{K} in the
-outer parts up to \SIrange{100}{200}{K} in the inner parts.
-
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/drift-pratio-4panel}
-  \caption{Drift velocity \(w\drift\) versus radiation parameter
-    \(\Xi\). Each line represents a simulation with ambient density and
-    stellar type as indicated in the key.  Results are shown for
-    graphite and silicate grains of two different sizes.  The rip
-    point, which corresponds to gas--grain decoupling, is the
-    discontinuity in the curves at
-    \(w\drift \approx \SI{10}{km.s^{-1}}\), indicated by the upper
-    horizontal dashed line.  The vertical dashed lines show the narrow
-    range of radiation parameter, \(\Xi = 1000 \pm \SI{0.5}{dex}\), that
-    encompasses the rip point for all simulations. }
-  \label{fig:drift-gn}
-\end{figure*}
-
-Unlike the strong differences in thermal properties, the radial
-dependence of grain electrostatic potential (third row in
-Fig.~\ref{fig:multi-dustprops}) is qualitatively similar for all the
-simulations.  The grains are predominantly positively charged, with high
-potentials (\(> 10\) times the thermal energy of gas particles) close
-to the star due to the strong EUV and FUV photo-ejection.  The
-potential falls to much lower values in the outer ionized region, as
-the EUV flux falls off, and then climbs again at the ionization front
-due to the fall in electron density, while the FUV photo-ejection
-persists well into the neutral region.  There are small differences
-between the simulations due to the increasing relative importance of the
-EUV radiation for hotter stars, which leads to a deeper dip in the
-potential just inside the ionization front for the \SI{40}{M_\odot} case,
-even reaching negative values for some grain species.
-
-Equilibrium drift velocity for each grain species is calculated in the
-Cloudy simulations using the same theory \citep{Draine:1979a} as
-outlined in \S~\ref{sec:drag-force-grains}.  The way that this is
-implemented by default in Cloudy means that if the only solution at
-the inner radius is a superthermal one, then the superthermal solution
-branch (upper right corner of
-Fig.~\ref{fig:gas-grain-drag-photoionized}) is followed as far as
-possible through the outer spatial zones.  We have modified the code
-so as to instead always prefer the slower subthermal branch whenever
-multiple solutions are available.  This makes the most sense in our
-context, where the grains are moving towards the star and so the
-radiative force is gradually increasing from an initial low value.
-Example results are shown in the bottom row of
-Figure~\ref{fig:multi-dustprops} and again they are qualitatively
-similar for all the simulations.  Close to the star, the radiation
-force is higher than the upper limit on the Coulomb drag force
-(eq.~[\ref{eq:fdrag-maximum}]), so that the equilibrium drift velocity
-is exceedingly high.\footnote{Note that such high drift velocities are
-  much higher than any realistic true relative velocity between grains
-  and gas, since they are based on the assumption that the radiation
-  force remains constant while the grain is accelerated, which is not
-  the case near the rip point.  Instead, they are simply an indication
-  that the gas and grains have completely decoupled.}.  As the radial
-distance from the star increases, the radiation field is increasingly
-diluted but the grain potential falls only slowly, so eventually one
-reaches a point where an equilibrium between Coulomb drag and
-radiation force can be established, which corresponds to a
-discontinuity in the drift velocity.  This is the \textit{rip point}
-discussed in \S~\ref{sec:gas-grain-separ}.  The drift velocity carries
-on falling towards the outside of the \hii{} region, but then
-increases again just inside the ionization front due to the drop in
-grain potential there.
-
-Both the charge balance and the force balance are essentially due to
-competition between the photons and the charged particles that
-interact with the grain.  It is therefore reasonable to surmise that
-the gas--grain decoupling that occurs at the rip point might be
-determined principally by the ratio of photons to gas particles.  We
-test this hypothesis in Figure~\ref{fig:drift-gn}, where we
-characterize the photon-gas ratio by a dimensionless radiation
-parameter, \(\Xi\), equal to the radiation pressure divided by the gas
-pressure.  Results are shown for four different grain types and for
-all combinations of stellar parameters and ambient densities for which
-we have run simulations.  It can be seen that the rip point does indeed
-always occur at a similar value of \(\Xi \sim 1000\) for all simulations, albeit
-with some variation according to the spectral type of the star and the
-grain composition, as given in Table~\ref{tab:Xi-rip}.  The gas
-density and grain size have very little influence on this critical
-value \(\Xi_\dag\), with the only exception being the very smallest grains
-(\(a < \SI{0.006}{\um}\), not illustrated), which show
-\(\Xi_\dag \approx \num{e4}\), but such grains are only minor contributors to the
-UV opacity (\(< 10\%\) in EUV and \(< 1\%\) in FUV, see
-Fig.~\ref{fig:cloudy-ism-dust-opacity}).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/phi-versus-xi-annotate}
-  \caption{Grain potential in thermal units (linear scale) versus
-    radiation parameter (logarithmic scale). All densities and stellar
-    types are shown, with line colors as in Fig.~\ref{fig:drift-gn}.
-    Solid lines show silicate grains and dashed lines show graphite
-    grains.  Line width increases with grain size (to reduce clutter,
-    only every second size bin is shown).  The solid and dashed lines
-    show the logarithmic fits discussed in the text.}
-  \label{fig:phi-vs-Xi}
-\end{figure}
-Finally, Figure~\ref{fig:phi-vs-Xi} shows the slow dependence of grain
-potential on radiation parameter for all the simulations on a linear
-versus logarithmic scale.  The logarithmic fit of
-equation~\eqref{eq:phi-vs-Xi}, most appropriate for carbon grains
-around cooler stars, is shown by the solid line.  The dashed lines
-show the modifications for silicate grains and for hotter stars (see
-\S~\ref{sec:gas-grain-separ}).  Further details of the Cloudy dust
-models are discussed in Appendix~\ref{sec:grain-temp-emiss}.
-
 % Inner shock \dots no dust \dots proton Larmor radius very small, so

### 2019-03-08 papers/Papers1234/app-dust-equations.tex
Major surgery on Paper II

@@
 stellar systems by \citet{Chandrasekhar:1941a}.
+
 Figures~\ref{fig:drag-components}--\ref{fig:gas-grain-drag-photoionized}
-show example applications to gas--grain drag in a photoionized region.
+show example applications of these equations to gas--grain drag in a
+photoionized region.  The included collider species are protons,
+electrons, helium ions, and metal ions.  Helium is assumed to be
+singly ionized, leading to only a small contribution to the drag
+force.  For much hotter stars, such as the central stars of planetary
+nebulae, helium may be doubly ionized, which leads to a fourfold
+increase in its Coulomb drag contribution, which is significant for
+\(w < \SI{5}{km.s^{-1}}\).  All metals are lumped together as a single
+species, assuming standard \hii{} region gas-phase abundances.  They
+are dominated by C and O, with minor contributions from N and Ne.  The
+total abundance is \num{8.5e-4} and the effective atomic weight is
+\num{15.3}.  All are assumed to be doubly ionized.  Their largest
+relative contribution to the drag force is for
+\(w < \SI{2}{km.s^{-1}}\), but is less than 1\% even there.
 
@@
   \label{eq:total-force}
-  \bm{f} = \frac{\sigma\grain \Qp L}{4\pi R^2 c} \hat{\bm{r}}
+  \bm{f} = \frac{\sigma\grain \Qpbar L}{4\pi R^2 c} \hat{\bm{r}}
   - f\drag \hat{\bm{w}}
@@
   \label{eq:drag-constant}
-  C\drag = \frac{4}{\Qp} \left(\frac{\sound \tau_* \kappa\grain}{v_\infty \kappa}\right)^2 \ .
+  C\drag = \frac{4}{\Qpbar} \left(\frac{\sound \tau_* \kappa\grain}{v_\infty \kappa}\right)^2 \ .
 \end{equation}

### 2019-03-08 papers/Papers1234/app-dust-wave.tex
Major surgery on Paper II

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
+  \caption{Dust wave formed by action of radiation forces on grains
+    that are tightly coupled to a uniform perpendicular magnetic
+    field.  (a)~Sample trajectories are shown by thin black lines and
+    the resultant dust density distribution in grayscale.  Two
+    parabolic fits to the inner edge of the dust wave in the wing
+    region (\(y > R\starstar\)) are shown. The orange line shows a
+    simultaneous fit to both wings, while the green line shows a fit
+    to a single wing, in which the parabola apex is not constrained to
+    lie on the axis.  The second fit has much smaller residuals,
+    indicating that the overall dust wave shape is ``pointier'' than a
+    parabola, but this is hard to quantify because the disappearance
+    of the dense shell in the apex region makes it impossible to
+    define \(R_0\) for the bow.  (b)~Trajectory parameters over a wide
+    range of impact parameters, shown on a log--log scale. Distances
+    are in units of \(R\starstar\), times in units of
+    \(R\starstar / v_\infty\), velocities in units of \(v_\infty\), and
+    accelerations in units of \(v_\infty^2 / R\starstar\). The grain's
+    acceleration along the \(y\) axis has a maximum value,
+    \(a_{\text{max}}\), which occurs at a position
+    \(x(a_{\text{max}}), y(a_{\text{max}})\), just before the grain is
+    swept past the star, with a duration (FWHM) of \(\Delta t\).  The
+    grain's asymptotic \(y\) velocity is \(v_{\text{final}}\) and the
+    fact that this closely tracks \(a_{\text{max}} \times \Delta t\) indicates
+    that the majority of the acceleration occurs in a sharp impulse.
+    The curves tend to straight lines at the right side of the graph,
+    which gives the asymptotic scaling relations discussed in the
+    text.}
+  \label{fig:inertia-thB90}
+\end{figure}
+
 We will show later in \S~\ref{sec:magn-effects-grain} that for
-sufficiently small grains the Larmor magnetic gyration radius, \(r\B\)
+sufficiently small grains the Larmor magnetic gyration radius, \(r\B\),
 is typically small compared with other length scales of interest, and
@@
 \(\theta\B\), the angle between the field direction and the direction of
-the dust stream (assumed to be plane parallel).  The radiation force
-will also produce an out-of-plane drift, given by
-\begin{equation}
-  \label{eq:perpendicular-drift}
-  \bm{v}_{\text{drift}} = \frac{c}{e z\grain} \, \frac{\bm{f}\!\rad \times \bm{B}}{B^2}
-  \ ,
-\end{equation}
-but from equations~(\ref{eq:Larmor}, \ref{eq:dust-rad-force},
-\ref{eq:dust-r0}) it follows that
-\begin{equation}
-  \label{eq:vdrift-over-vinfinity}
-  \frac{v_{\text{drift}}(R\starstar)}{v_\infty} = \frac{r\B}{2 R\starstar} \ ,
-\end{equation}
-so it is valid to ignore this drift in the limit of small \(r\B\).
+the dust stream (assumed to be plane parallel).
 
@@
 two cases, with the magnetic field oriented parallel and perpendicular
-to the stream\footnote{In both cases, the stream trajectories are
-  assumed parallel to one another, as in \S~\ref{sec:dust-parallel}.}
-direction, respectively. These are sufficient to give a flavor of the
-effects of a magnetic field on the dust wave structure.  Further
+to the stream direction, respectively. In both cases, the stream
+trajectories are assumed parallel to one another, as in
+\S~\ref{sec:dust-parallel}. These are sufficient to give a flavor of
+the effects of a magnetic field on the dust wave structure.  Further
 models at intermediate angles, and which also include the effects of
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
-  \caption{Dust wave formed by action of radiation forces on grains
-    that are tightly coupled to a uniform perpendicular magnetic
-    field.  (a)~Sample trajectories are shown by thin black lines and
-    the resultant dust density distribution in grayscale.  Two
-    parabolic fits to the inner edge of the dust wave in the wing
-    region (\(y > R\starstar\)) are shown. The orange line shows a
-    simultaneous fit to both wings, while the green line shows a fit
-    to a single wing, in which the parabola apex is not constrained to
-    lie on the axis.  The second fit has much smaller residuals,
-    indicating that the overall dust wave shape is ``pointier'' than a
-    parabola, but this is hard to quantify because the disappearance
-    of the dense shell in the apex region makes it impossible to
-    define \(R_0\) for the bow.  (b)~Trajectory parameters over a wide
-    range of impact parameters, shown on a log--log scale. Distances
-    are in units of \(R\starstar\), times in units of
-    \(R\starstar / v_\infty\), velocities in units of \(v_\infty\), and
-    accelerations in units of \(v_\infty^2 / R\starstar\). The grain's
-    acceleration along the \(y\) axis has a maximum value,
-    \(a_{\text{max}}\), which occurs at a position
-    \(x(a_{\text{max}}), y(a_{\text{max}})\), just before the grain is
-    swept past the star, with a duration (FWHM) of \(\Delta t\).  The
-    grain's asymptotic \(y\) velocity is \(v_{\text{final}}\) and the
-    fact that this closely tracks \(a_{\text{max}} \times \Delta t\) indicates
-    that the majority of the acceleration occurs in a sharp impulse.
-    The curves tend to straight lines at the right side of the graph,
-    which gives the asymptotic scaling relations discussed in the
-    text.}
-  \label{fig:inertia-thB90}
-\end{figure}
-
 For \(\theta\B = \ang{90}\), the guiding center is forced to move at a

### 2019-03-08 papers/Papers1234/bs-bw-dw-02.tex
Major surgery on Paper II

--- 2019-03-07 papers/Papers1234/bs-bw-dw-02.tex
@@
 
+\section{Introduction}
+\label{sec:rip-introduction}
+
+In \S~\ref{sec:gas-free-bow} we calculate analytical
+models of the shape of dust waves in the drag-free limit.
+% %
+% In \S\ref{sec:cloudy-models-dust} we discuss the relevant dust physics
+% and the Cloudy models that we employ.
+%
+In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
+charging and dynamics, subject to radiation and drag forces, in order
+to determine the \textit{rip point}, which is where gas--grain coupling
+catastrophically breaks down.  This is used to determine existence
+conditions for the presence of a decoupled dust wave.
+%
+In \S~\ref{sec:magn-effects-grain} we consider the coupling between
+the grains and the plasma's magnetic field, and how this effects the
+existence and structure of dust waves.
+%
+In Appendix~\ref{sec:equat-moti-grains} we provide additional
+technical information on the numerical calculation of grain
+trajectories.
+
+\input{app-dust-wave}
+
 \input{sec-weak-coupling}

### 2019-03-08 papers/Papers1234/sec-weak-coupling.tex
Major surgery on Paper II

@@
     species labelled ``CNO++'' represents the combined effect of all
-    metals (see footnote~\ref{fn:metal-drag}).}
+    metals (see App.~\ref{sec:equat-moti-grains}).}
   \label{fig:drag-components}
@@
 
-\begin{figure*}
-  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
-  \caption{Dimensionless drag force, \(f\drag / f_*\), as a function
-    of gas--grain slip velocity, \(w\), for different values of the
-    grain potential in thermal units, \(\phi\).  Contributions from
-    proton and electron Coulomb (electrostatic) drag, as well as
-    Epstein (solid-body) drag are indicated.  Examples of subsonic and
-    highly supersonic stable drift velocities are shown (thin dark
-    blue arrows), where the drag force is in equilibrium with the
-    radiation force (thick dark blue dashed lines), while blue shading
-    indicates the unstable, mildly supersonic velocity regime, where
-    no stable drift equilibrium exists.  Inset graph shows \(\phi\) as a
-    function of the radiation parameter,
-    \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a log--linear scale
-    for a collection of Cloudy models (see
-    Appendix~\ref{sec:cloudy-models-dust}).}
-  \label{fig:gas-grain-drag-photoionized}
-\end{figure*}
-
 % \begin{figure}
@@
 coupling between grains and gas will break down.  In this section, we
-calculate the regions of star+stream parameter space where this might
+calculate the regions of star/stream parameter space where this might
 occur, leading to a separation of the bow into an outer dust wave and
@@
 
-The drag force on a charged dust grain moving at a relative speed
-\(w\) through a plasma has contributions from both direct collisions
-and from electrostatic Coulomb interactions with ions and electrons.
-We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
-considering the contributions from protons, electrons, helium
-ions,\footnote{Helium is assumed to be singly ionized, leading to only
-  a small contribution to the drag force.  For much hotter stars, such
-  as the central stars of planetary nebulae, helium may be doubly
-  ionized, which leads to a fourfold increase in its Coulomb drag
-  contribution, which is significant for \(w < \SI{5}{km.s^{-1}}\).} %
-and metal ions.\footnote{%
-  \label{fn:metal-drag}
-  All metals are lumped together as a single species, assuming
-  standard \hii{} region gas-phase abundances.  They are dominated by
-  C and O, with minor contributions from N and Ne.  The total
-  abundance is \num{8.5e-4} and the effective atomic weight is
-  \num{15.3}.  All are assumed to be doubly ionized.  Their largest
-  relative contribution to the drag force is for
-  \(w < \SI{2}{km.s^{-1}}\), but is less than 1\% even there.} %
-Results are shown in Figure~\ref{fig:drag-components}, where dashed
-lines correspond to direct solid body collisions and solid lines to
-electrostatic interactions.  The latter depend on the grain potential,
-which is described in dimensionless terms by \(\phi\), which is the
-electrostatic potential energy of a unit charge at the surface of a
-grain of charge \(z\grain\) and radius \(a\), in units of the
-characteristic thermal energy of a gas particle:
+The drag force \(f\drag\) on a charged dust grain moving at a relative
+speed \(w\) through a plasma has contributions from both direct
+collisions and from electrostatic Coulomb interactions with ions and
+electrons \citep{Draine:1979a}.  Full details of the equations and
+collider species used are given in
+Appendix~\ref{sec:equat-moti-grains}. Results are shown in
+Figure~\ref{fig:drag-components}, where dashed lines correspond to
+direct solid body collisions and solid lines to electrostatic
+interactions.  The latter depend on the grain potential, which is
+described in dimensionless terms by \(\phi\), the electrostatic potential
+energy of a unit charge at the surface of a grain of charge
+\(z\grain\) and radius \(a\), in units of the characteristic thermal
+energy of a gas particle:
 \begin{equation}
@@
 \end{equation}
-which is approximately\footnote{%
-  To simplify the exposition, the gas pressure in this section is
-  calculated assuming a fully ionized, pure hydrogen plasma, yielding
-  \(P\gas = 2 n k T\). For typical ISM abundances, the contribution of
-  helium and its corresponding electrons yield a correction to this of
-  order 5\%.  The required modifications when a cool star interacts
-  with a predominantly neutral gas stream are discussed later.  } %
-the ionized gas pressure multiplied by the grain geometric cross
-section.
+which is approximately the ionized gas pressure multiplied by the
+grain geometric cross section.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/cloudy-ism-dust-opacity}
+  \caption{Extinction properties of Cloudy's standard ``ISM'' dust
+    mixture. %
+    (a)~Wavelength dependence of mean values over the entire mixture
+    of three dimensionless quantities related to scattering: albedo,
+    \(\varpi\) (solid line); scattering asymmetry,
+    \(g = \langle \cos\theta \rangle\) (dashed line); ratio of radiation pressure
+    efficiency to absorption efficiency, \(Q_P / Q_{\text{abs}}\)
+    (dotted line).
+    %
+    (b)~Wavelength dependence of mass opacity (cross section per unit
+    mass of gas) for the whole mixture (heavy black line) and broken
+    down by size bin and grain composition (colored lines, see key). }
+  \label{fig:cloudy-ism-dust-opacity}
+\end{figure}
+
+\begin{table*}
+  \centering
+  \caption{Stellar parameters for example stars}
+  \label{tab:stars}
+  \begin{tabular}{l S S S S S S S S S}
+    \toprule
+    & {\(M / \si{M_\odot}\)} & {\(L_4\)}
+    & {\(\dot{M}_{-7}\)} & {\(V_3\)} & {\( \eta\wind \)}
+    & {Sp.~Type} 
+    & {\(T_{\text{eff}} / \si{kK}\)} & {\(\lambda_{\text{eff}}\) / \si{\um}}
+    & {\(S_{49}\)} 
+    \\
+    \midrule
+    & 10 & 0.63 & 0.0034 & 2.47 & 0.0066 & {B1.5\,V} & 25.2 & 0.115 & 0.00013
+                   \\
+    Main-sequence OB stars
+    & 20 & 5.45 & 0.492 & 2.66 & 0.1199 & {O9\,V} & 33.9 & 0.086 & 0.16
+                    \\
+    & 40 & 22.2 & 5.1 & 3.31 & 0.4468 & {O5\,V} & 42.5 & 0.068 & 1.41
+                   \\[\smallskipamount]
+    Blue supergiant star
+    & 33 & 30.2 & 20.2 & 0.93 & 0.3079 & {B0.7\,Ia} & 23.5 & 0.123 & 0.016
+                   \\
+    \bottomrule
+  \end{tabular}
+\end{table*}
+
+\subsection{Grain charging and gas--grain coupling}
+\label{sec:cloudy-models-dust}
+
+We calculate models of the physical properties of dust grains using
+the plasma physics code Cloudy \citep{Ferland:2013a, Ferland:2017a},
+which self-consistently solves the multi-frequency radiative transfer
+together with thermal, ionization, and excitation balance of all
+plasma constituents.  Cloudy incorporates grain charging as described
+in \citet{Baldwin:1991a} and \citet{van-Hoof:2004a} with photoelectric
+emission theory from \citet{Weingartner:2001b, Weingartner:2006a}.  We
+use the default ``ISM'' dust mixture included in Cloudy, which
+comprises ten size bins each for spherical silicate and graphite
+grains in the range \num{0.005} to \SI{0.25}{\um}, and which is
+designed to reproduce the average Galactic extinction curve
+\citep{Weingartner:2001a, Abel:2008a}.  The optical properties of each
+grain species are calculated using Mie theory \citep{Bohren:1983a},
+assuming solid spheres.  The resultant wavelength-dependent extinction
+properties of the mixture are summarised in
+Figure~\ref{fig:cloudy-ism-dust-opacity}.
+
+To ascertain the expected variation in grain properties in the
+circumstellar environs of luminous stars, we calculate a series of
+spherically symmetric, steady-state, constant density Cloudy
+simulations, illuminated by the stars listed in Table~\ref{tab:stars},
+which are the same ones as used in Paper~I.\@ Stellar spectra are
+taken from the OSTAR2002 and BSTAR2006 grids, calculated with the
+TLUSTY model atmosphere code \citep{Lanz:2003a, Lanz:2007a}.
+Simulations are run for hydrogen densities of \numlist{1;10;100;e3;e4}
+\si{cm^{-3}} and assuming standard \hii{} region gas phase abundances.
+The calculation is stopped when the ionization front is reached and
+the inner radius is chosen to be roughly 1\% of this.
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/multi-dustprops}
+  \caption{Dust properties as a function of radius from star for three
+    selected Cloudy simulations. (a)~\SI{40}{M_\odot} main-sequence star in
+    medium of density \SI{e4}{cm^{-3}}. (b)~\SI{10}{M_\odot} main-sequence
+    star in medium of density \SI{1}{cm^{-3}}. (c)~Blue supergiant
+    star in medium of density \SI{1}{cm^{-3}}}.
+  \label{fig:multi-dustprops}
+\end{figure*}
+
+Figure~\ref{fig:multi-dustprops} shows resultant radial profiles of
+dust properties for representative simulations: grain temperature, grain
+abundance, grain potential, and grain drift velocity.  Line types
+correspond to the different size bins of graphite and silicate grains,
+as indicated in the key from smallest to largest. The left hand panels
+show results for a high-density (\(n = \SI{e4}{cm^{-3}}\)), compact
+(\(R \approx \SI{0.1}{pc}\)) region around an early O~star, where the grain
+temperature is very high, especially for the smaller silicate grains,
+and sublimation significantly reduces the grain abundance in the inner
+regions.  The remaining columns show low-density
+(\(n = \SI{1}{cm^{-3}}\)), extended (\(R \sim \SI{10}{pc}\)) regions
+around main-sequence and supergiant B-type stars, in which the grain
+temperatures are much lower, ranging from \SIrange{20}{50}{K} in the
+outer parts up to \SIrange{100}{200}{K} in the inner parts.
+
+Unlike the strong differences in thermal properties, the radial
+dependence of grain electrostatic potential (third row in
+Fig.~\ref{fig:multi-dustprops}) is qualitatively similar for all the
+simulations.  The grains are predominantly positively charged, with high
+potentials (\(> 10\) times the thermal energy of gas particles) close
+to the star due to the strong EUV and FUV photo-ejection.  The
+potential falls to much lower values in the outer ionized region, as
+the EUV flux falls off, and then climbs again at the ionization front
+due to the fall in electron density, while the FUV photo-ejection
+persists well into the neutral region.  There are small differences
+between the simulations due to the increasing relative importance of the
+EUV radiation for hotter stars, which leads to a deeper dip in the
+potential just inside the ionization front for the \SI{40}{M_\odot} case,
+even reaching negative values for some grain species.
+
+Equilibrium drift velocity for each grain species is calculated in the
+Cloudy simulations using the same \citet{Draine:1979a} theory as
+described in \S~\ref{sec:drag-force-grains} and
+Appendix~\ref{sec:equat-moti-grains}.  The way that this is
+implemented by default in Cloudy means that if the only solution at
+the inner radius is a superthermal one, then the superthermal solution
+branch (upper right corner of
+Fig.~\ref{fig:gas-grain-drag-photoionized}) is followed as far as
+possible through the outer spatial zones.  We have modified the code
+so as to instead always prefer the slower subthermal branch whenever
+multiple solutions are available.  This makes more sense than the
+default behavior for our context, where the grains are moving towards
+the star and so the radiative force is gradually increasing from an
+initial low value.
+
+Example results are shown in the bottom row of
+Figure~\ref{fig:multi-dustprops} and again they are qualitatively
+similar for all the simulations.  Close to the star, the radiation
+force is higher than the upper limit on the Coulomb drag force
+(eq.~\eqref{eq:fdrag-maximum}), so that the equilibrium drift velocity
+is exceedingly high.  We discuss this situation in greater detail
+below in \S~\ref{sec:drag-force-grains}.  Note that such high drift
+velocities are much higher than any realistic true relative velocity
+between grains and gas, since they are based on the assumption that
+the radiation force remains constant while the grain is accelerated,
+which is not the case under these conditions.  Instead, they are
+simply an indication that the gas and grains have completely
+decoupled.
+
+As the radial distance from the star increases, the radiation field is
+increasingly diluted but the grain potential falls only slowly, so
+eventually one reaches a point where an equilibrium between Coulomb
+drag and radiation force can be established, which corresponds to a
+discontinuity in the drift velocity.  The drift velocity carries
+on falling towards the outside of the \hii{} region, but then
+increases again just inside the ionization front due to the drop in
+grain potential there.
+
 \subsection{Gas--grain separation: drift and rip}
@@
 
-In Appendix~\ref{sec:gas-free-bow} we calculate the behaviour of an
+In \S~\ref{sec:gas-free-bow} we calculate the behaviour of an
 incoming stream of dust grains, subject only to the repulsive
@@
 
-From equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar}, we can
-write the radiation force acting on a grain as
-\begin{equation}
-  \label{eq:frad-Xi}
-  f\rad = \Qp\, \Xi\, f_* \ ,
-\end{equation}
-where \(\Qp\) is the grain's radiation pressure efficiency (see
-footnote~\ref{fn:Qp} in Appendix~\ref{sec:gas-free-bow}) and \(\Xi\) is
-the local radiation parameter, defined as the ratio of direct stellar
-radiation pressure to gas pressure:
+We introduce the local radiation parameter, \(\Xi\), defined as the
+ratio of direct stellar radiation pressure to gas pressure:
 \begin{equation}
@@
 \end{equation}
-where the last expression corresponds to the optically thin limit.
-The grain potential \(\phi\) is also primarily determined by \(\Xi\), as
-shown in Appendix~\ref{sec:cloudy-models-dust} and the inset graph of
-Figure~\ref{fig:gas-grain-drag-photoionized}, but with a slow
-dependence, which can be approximated as
+where the last expression corresponds to the optically thin limit.  Then, if we define the grain's frequency-averaged radiation pressure
+efficiency as
+\begin{equation}
+  \label{eq:Qpbar}
+  \Qpbar = \frac{1}{L} \int_0^\infty \!\Qp \, L_\nu \, d\nu \ ,
+\end{equation}
+then equations~\eqref{eq:dust-rad-force} and~\eqref{eq:fstar} give the
+radiation force acting on a grain as
+\begin{equation}
+  \label{eq:frad-Xi}
+  f\rad = \Qpbar\, \Xi\, f_* \ .
+\end{equation}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/phi-versus-xi-annotate}
+  \caption{Grain potential in thermal units (linear scale) versus
+    radiation parameter (logarithmic scale). All densities and stellar
+    types are shown, with line colors as in Fig.~\ref{fig:drift-gn}.
+    Solid lines show silicate grains and dashed lines show graphite
+    grains.  Line width increases with grain size (to reduce clutter,
+    only every second size bin is shown).  Straight black lines show
+    the logarithmic fits discussed in the text:
+    eq.~\eqref{eq:phi-vs-Xi}, most appropriate for carbon grains
+    around cooler stars, is shown by the dashed line, while the solid
+    lines show the modifications for silicate grains and for hotter
+    stars.}
+  \label{fig:phi-vs-Xi}
+\end{figure}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
+  \caption{Dimensionless drag force, \(f\drag / f_*\), as a function
+    of gas--grain slip velocity, \(w\), for different values of the
+    grain potential in thermal units, \(\phi\).  Contributions from
+    proton and electron Coulomb (electrostatic) drag, as well as
+    Epstein (solid-body) drag are indicated.  Examples of subsonic and
+    highly supersonic stable drift velocities are shown (thin dark
+    blue arrows), where the drag force is in equilibrium with the
+    radiation force (thick dark blue dashed lines), while blue shading
+    indicates the unstable, mildly supersonic velocity regime, where
+    no stable drift equilibrium exists. }
+  \label{fig:gas-grain-drag-photoionized}
+\end{figure*}
+
+The grain potential \(\phi\), which is crucial for determining
+\(f\drag\) (Tab.~\ref{tab:fdrag-regimes}), is due to competition
+between the photons and the charged particles that interact with the
+grain.  It is therefore reasonable to suppose that \(\phi\) should also
+be primarily determined by \(\Xi\).  This is confirmed in
+Figure~\ref{fig:phi-vs-Xi} using the Cloudy simulations of
+\S~\ref{sec:cloudy-models-dust}, for which we find a slow dependence
+that can be approximated as
 \begin{equation}
@@
 a lowering of the equilibrium drift velocity to \(w_{10} \sim 0.01\) as
-the Coulomb drag kicks in (see Appendix~\ref{sec:cloudy-models-dust}).
-However, at smaller radii the slow logarithmic increase in
-\(\phi(\Xi)\) means that the drift velocity must start increasing again to
-accommodate the linear increase of \(f\rad(\Xi)\).  Eventually,
-\(f\rad\) exceeds \(f_{\mathrm{max}}\), the maximum drag force that
-proton Coulomb interactions can provide
+the Coulomb drag kicks in (see lower panels of
+Fig.~\ref{fig:multi-dustprops}).  However, at smaller radii the slow
+logarithmic increase in \(\phi(\Xi)\) means that the drift velocity must
+start increasing again to accommodate the linear increase of
+\(f\rad(\Xi)\).  Eventually, \(f\rad\) exceeds \(f_{\mathrm{max}}\), the
+maximum drag force that proton Coulomb interactions can provide
 (eq.~[\ref{eq:fdrag-maximum}]).  This occurs at a critical value of
 the radiation parameter, which we denote the \textit{rip point}:
-\(\Xi_\dag \sim 1000\).  The variations in \(\Xi_\dag\) with star and grain
-parameters, which are of order \SI{+- 0.5}{dex}, are listed in
-Table~\ref{tab:Xi-rip} and illustrated graphically in
-Figure~\ref{fig:drift-gn}.  The radius of the rip point, \(R_\dag\), can
-be expressed in terms of \(R_*\), the fiducial optically thick bow
-shock radius introduced in Paper~I's \S~2.1:
+\(\Xi_\dag \sim 1000\).
+
+\begin{figure*}
+  \includegraphics[width=\linewidth]{figs/drift-pratio-4panel}
+  \caption{Drift velocity \(w\drift\) versus radiation parameter
+    \(\Xi\). Each line represents a simulation with ambient density and
+    stellar type as indicated in the key.  Results are shown for
+    graphite and silicate grains of two different sizes.  The rip
+    point, which corresponds to gas--grain decoupling, is the
+    discontinuity in the curves at
+    \(w\drift \approx \SI{10}{km.s^{-1}}\), indicated by the upper
+    horizontal dashed line.  The vertical dashed lines show the narrow
+    range of radiation parameter, \(\Xi = 1000 \pm \SI{0.5}{dex}\), that
+    encompasses the rip point for all simulations. }
+  \label{fig:drift-gn}
+\end{figure*}
+
+To test these ideas, we plot in Figure~\ref{fig:drift-gn} the grain
+drift velocity from the Cloudy simulations as a function of \(\Xi\),
+showing results for four different grain types and for all
+combinations of stellar parameters and ambient densities for which we
+have run simulations.  It can be seen that the radiation parameter at
+the rip point \(\Xi_\dagger\) is indeed confined to a narrow range.  The
+fundamental explanation for this is that both the charge balance and
+the force balance are essentially due to competition between the
+photons and the charged particles that interact with the grain.  The
+small variations in \(\Xi_\dag\) with stellar type and grain composition,
+which are of order \SI{+- 0.5}{dex}, are listed in
+Table~\ref{tab:Xi-rip}.  The gas density and grain size have very
+little influence on this critical value \(\Xi_\dag\), with the only
+exception being the very smallest grains (\(a < \SI{0.006}{\um}\), not
+illustrated), which show \(\Xi_\dag \approx \num{e4}\), but such grains are only
+minor contributors to the UV opacity for our adopted dust mixture
+(\(< 10\%\) in EUV and \(< 1\%\) in FUV, see
+Fig.~\ref{fig:cloudy-ism-dust-opacity}).
+
+The radius of the rip point, \(R_\dag\), can be expressed in terms of
+\(R_*\), the fiducial optically thick bow shock radius introduced in
+Paper~I's \S~2.1:
 %% XREF \ref{sec:three-bow-regimes}
@@
 %% XREF \eqref{eq:Rstar}
-
-What happens to the dust grain following this catastrophic breakdown
-of gas--grain coupling depends on the relation between the rip point
-radius, \(R_\dag\), and the drag-free radiative turnaround radius,
-\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
-will still carry it in as far as \(R\starstar\) and the initial
-trajectory will be almost identical to that described in
-Appendix~\ref{sec:gas-free-bow} for the drag-free case. However, after
-being turned around by the radiation field and pushed out past
-\(R_\dag\) again, the grain will \emph{recouple} to the gas and be
-dragged back for a second approach.\footnote{If the initial impact
-  parameter of the trajectory is not strictly \(b = 0\), then the
-  resultant lateral component of \(f\rad\) will mean that \(b\) will
-  be much increased for the second approach.} %
-We will refer to this as an \textit{inertia-confined dust wave}
-(IDW).  From equations~(\ref{eq:Rdag-over-Rstar},
-\ref{eq:Rstarstar-over-Rstar},
-\ref{eq:dust-wave-high-density-condition}), the condition
-\(R_\dag > R\starstar\) corresponds to
-\(\tau_* < (\kappa/\kappa\grain) \tau_{*,\text{max}}\), which is indicated by dashed
-lines in the left panel of Figure~\ref{fig:existence-dust-wave}.  If,
-on the other hand, \(R_\dag < R\starstar\), then the tail wind provided
-by the gas carries the grain closer to the star than its inertia would
-naturally take it.  When the grain finally decouples at \(R_\dag\) it
-experiences a much higher unbalanced \(f\rad\), which can initially
-accelerate it to outward velocities significantly higher than the
-inflow velocity if \(R_\dag \ll R\starstar\).  We will refer to this case
-as a \textit{drag-confined dust wave} (DDW).
 
@@
 Figure~\ref{fig:existence-dust-wave} for each of the three example
-main sequence stars from Paper~I's Table~1.
-%% XREF \ref{tab:stars}
-Further restrictions
+main sequence stars from Table~\ref{tab:stars}.  Further restrictions
 on the existence of dust waves arise when the effects of magnetic
@@
 
-\subsection{Grain trajectories along the symmetry axis}
+\subsection{Post-rip grain dynamics}
+\label{sec:two-regimes-post}
+
+We now investigate the trajectory of the dust grain following the
+catastrophic breakdown of gas--grain coupling at the rip point.  Two
+regimes are possible, depending on the relation between the rip point
+radius, \(R_\dag\), and the drag-free radiative turnaround radius,
+\(R\starstar\).  If \(R_\dag > R\starstar\), then the grain's inertia
+will still carry it in as far as \(R\starstar\) and the initial
+trajectory will be almost identical to that described in
+\S~\ref{sec:gas-free-bow} for the drag-free case. But once the grain
+has been turned around by the radiation field and pushed out past
+\(R_\dag\) again, it will \emph{recouple} to the gas.  
+We will refer to this as an \textit{inertia-confined dust wave} (IDW).
+From equations~(\ref{eq:Rdag-over-Rstar},
+\ref{eq:Rstarstar-over-Rstar},
+\ref{eq:dust-wave-high-density-condition}), the condition
+\(R_\dag > R\starstar\) corresponds to
+\begin{equation}
+  \label{eq:IDW}
+  \tau_* < \frac{\kappa}{\kappa\grain} \tau_{*,\text{max}} \ , 
+\end{equation}
+which is indicated by dashed lines in the left panel of
+Figure~\ref{fig:existence-dust-wave}.  If, on the other hand,
+\(R_\dag < R\starstar\), then the tail wind provided by the gas carries
+the grain closer to the star than its inertia would naturally take it.
+When the grain finally decouples at \(R_\dag\) it experiences a much
+higher unbalanced \(f\rad\), which can initially accelerate it to
+outward velocities significantly higher than the inflow velocity if
+\(R_\dag \ll R\starstar\).  We will refer to this case as a
+\textit{drag-confined dust wave} (DDW).  As in the IDW case, the
+expelled grain will eventually recouple to the gas once it moves away
+from the star.
+
 \label{sec:grain-traj-along}
 
-The post-decoupling behavior of the grain depends on the sign of
+What happens to the grain after recoupling depends on the sign of
 \(d f\drag / d w\) when \(w = \abs{v_\infty}\).  If this derivative is
@@
 then the grain can reach a stable equilibrium drift at rest with
-respect to the star\footnote{%
-  Again, this is only strictly true when the impact parameter is zero.
-  However, as we show below, it is a reasonable approximation over a
+respect to the star at a point \(R_\ddag\), which we call the
+\textit{stagnant drift radius}. If the stream velocity is not
+excessively high (\(v_\infty < \SI{150}{km.s^{-1}}\) when
+\(\phi = 4\), or \(< \SI{300}{km.s^{-1}}\) when \(\phi = 16\)), then the
+equilibrium \(f\rad\) is less than the value at the rip point,
+requiring a lower value of the radiation parameter:
+\(\Xi_\ddag < \Xi_\dag\).  The resultant stagnant drift radius is therefore
+outside the rip point: \(R_\ddag > R_\dag\).  Of course, a static equilibrium
+is only possible when the impact parameter is exactly zero.
+Otherwise, there will be an unbalanced lateral component of the
+radiation force, which will cause a sideways drift.  However, as we
+show below, strong coupling to the magnetic field means that the
+strictly on-axis calculation is a reasonable approximation over a
 range of impact parameters in the case where the angle between the
-  magnetic field direction and the stream velocity is not too
-  large.} %
-at a point \(R_\ddag\), which we call the \textit{stagnant drift
-  radius}. If the stream velocity is not excessively high
-(\(v_\infty < \SI{150}{km.s^{-1}}\) when \(\phi = 4\), or
-\(< \SI{300}{km.s^{-1}}\) when \(\phi = 16\)), then the equilibrium
-\(f\rad\) is less than the value at the rip point, requiring a lower
-value of the radiation parameter: \(\Xi_\ddag < \Xi_\dag\).  The resultant
-stagnant drift radius is therefore outside the rip point:
-\(R_\ddag > R_\dag\).
+magnetic field direction and the stream velocity is not too large.
 
@@
 \(\phi > 1\) and
-\(\SI{10}{km.s^{-1}} < v_\infty < \SI{50}{km.s^{-1}}\).  There is also a
-second unstable regime (partially visible in the upper-right corner of
+\(\SI{10}{km.s^{-1}} < v_\infty < \SI{50}{km.s^{-1}}\), as illustrated in
+Figure~\ref{fig:gas-grain-drag-photoionized}.  There is also a second
+unstable regime (partially visible in the upper-right corner of
 Fig.~\ref{fig:drag-v-phi-plane}), which is related to the thermal peak
 in the electron Coulomb drag when \(\phi > 30\) and
-\(\SI{400}{km.s^{-1}} < v_\infty < \SI{2000}{km.s^{-1}}\), but this is not
-relevant to bow shocks around OB~stars.\footnote{%
-  It may apply in other contexts, such as outflows from AGN, since
-  detailed modeling of grain charging around quasars
-  \citep{Weingartner:2006a} implies that grain potentials as high as
-  \(\phi \sim 100\) can be achieved.} %
+\(\SI{400}{km.s^{-1}} < v_\infty < \SI{2000}{km.s^{-1}}\).  This is not
+relevant to bow shocks around OB~stars since \(\phi\) does not reach such
+high values, but it may apply in other contexts, such as outflows from
+AGN, where grain potentials as high as \(\phi \sim 100\) can be achieved
+\citep{Weingartner:2006a}.
 
@@
 by a factor \((1 - \Delta v / v_\infty)^{-1}\) with respect to the case
-calculated in \S~\ref{sec:three-bow-regimes}, yielding
+calculated in Paper~I's \S~2.1,
+% XREF \ref{sec:three-bow-regimes}
+yielding
 \begin{equation}
@@
 stream velocity and grain and star properties, so that
-\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).  In order for
+\(\tau_* \propto n^{1/2}\) (Paper~I's eq.~[15]).
+% XREF \ref{eq:taustar-typical}
+In order for
 \(R_{\text{dfbs}}\) to match the dust-wave and bow-wave radii at the
@@
 treatment described here is very approximate: it does not take into
-account the shock that will form once \(J\drag\) reaches an
+account the shock that must form once \(J\drag\) reaches an
 appreciable fraction of \(m_{\text{gas}} v_\infty\) and, additionally, it
@@
 \S~\ref{sec:tight-magn-coupl} and extend those results to include the
-effects of gas--grain collisions as in \S~\ref{sec:imperf-coupl-betw}.
-The Lorentz force on charged grains due to a magnetic field is
+effects of drag forces from the gas.  The Lorentz force on charged
+grains due to a magnetic field is
 \begin{equation}
@@
 around the field lines, plus a sliding of the guiding center along the
-field lines, which is governed by the radiation and drag forces (the
-slow \(\bm{f} \times \bm{B}\) drift across the field lines is negligible in
-this case, see App.~\ref{sec:tight-magn-coupl}).  In the opposite
-limit, \(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
+field lines, which is governed by the radiation and drag forces.  The
+radiation force will also produce an out-of-plane drift, given by
+\begin{equation}
+  \label{eq:perpendicular-drift}
+  \bm{v}_{\text{drift}} = \frac{c}{e z\grain} \, \frac{\bm{f}\!\rad \times \bm{B}}{B^2}
+  \ ,
+\end{equation}
+but from equations~(\ref{eq:Larmor}, \ref{eq:dust-rad-force},
+\ref{eq:dust-r0}) it follows that
+\begin{equation}
+  \label{eq:vdrift-over-vinfinity}
+  \frac{v_{\text{drift}}(R\starstar)}{v_\infty} = \frac{r\B}{2 R\starstar} \ ,
+\end{equation}
+so it is valid to ignore this drift in the limit of small \(r\B\).
+This is the limit that was applied in \S~\ref{sec:tight-magn-coupl}
+for the case of zero drag.  In the opposite limit,
+\(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
 non-magnetic results of \S~\ref{sec:imperf-coupl-betw} are scarcely
@@
 
-We can now investigate how the results of the previous sections are
-modified by magnetic fields in the tight coupling limit.  For
-simplicity, we assume a uniform field in the incoming stream, with
-field lines oriented at an angle \(\theta\B\) to the velocity vector that
-defines the bow axis.  We also assume a super-alfvénic stream,
-\(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
-is unaffected by the magnetic field, and additionally assume
-\(\tau_* \ll \tau_{*, \text{max}}\), so that the back-reaction of the grain
-drag on the plasma is negligible (see previous section) and \(B\)
-remains uniform in magnitude and direction in the dust wave region,
-outside of the bow shock.
-
-In Appendix~\ref{sec:tight-magn-coupl}, we derive analytic and
+We can now investigate how the results of the
+section~\ref{sec:imperf-coupl-betw} are modified by magnetic fields in
+the tight coupling limit.  For simplicity, we assume a uniform field
+in the incoming stream, with field lines oriented at an angle
+\(\theta\B\) to the velocity vector that defines the bow axis.  We also
+assume a super-alfvénic stream, \(v_\infty > v\alfven\), so that the
+radius, \(R_0\), of the wind bow shock is unaffected by the magnetic
+field, and additionally assume \(\tau_* \ll \tau_{*, \text{max}}\), so that
+the back-reaction of the grain drag on the plasma is negligible
+(\S~\ref{sec:back-reaction-gas}) and \(B\) remains uniform in
+magnitude and direction in the dust wave region, outside of the bow
+shock.
+
+In \S~\ref{sec:tight-magn-coupl}, we derived analytic and
 semi-analytic results in the limit of zero gas--grain drag, which is
-appropriate for inertia-confined dust waves. We find very different
-structures, depending on the orientation of the field.  For a parallel
-field (Fig.~\ref{fig:inertia-thB0}), the apex of the dust wave occurs
-at the same point, \(R\starstar\), as in the non-magnetic case, but
-the shape of the dust wave wings is more closed, being hemispherical
-rather than parabolic in shape.  For a perpendicular field
-(Fig.~\ref{fig:inertia-thB90}), on the other hand, grains in the apex
-region are dragged very close to the star and no dust wave forms
+appropriate for inertia-confined dust waves.  The resultant dust wave
+structure is highly dependent on the field orientation.  For a
+parallel field (Fig.~\ref{fig:inertia-thB0}), the apex of the dust
+wave occurs at the same point, \(R\starstar\), as in the non-magnetic
+case, but the shape of the dust wave wings is more closed, being
+hemispherical rather than parabolic in shape.  For a perpendicular
+field (Fig.~\ref{fig:inertia-thB90}), on the other hand, grains in the
+apex region are dragged very close to the star and no dust wave forms
 there.  A dust wave can form in the wings, with impact parameter
@@
 will exist in practice depends critically on the size and shape of the
-MHD wind-supported bow shock.
+interior MHD wind-supported bow shock.
 
@@
 measured in crossing times, is slightly longer than in panel~a, but is
-of the same order.  In both these cases, a second, exterior dense
+of the same order.  In both these cases, a second, exterior dust
 shell is formed in addition to the hemispherical one produced by the
@@
 which is an approximation to the shape of the inner bow shock, see
-\PaperI.  It can be seen that the majority of dust streamlines do not
-cross this surface until well into the wings of the bow, so that a
-separate exterior dust wave can exist for this quasi-parallel
-magnetic field orientation.
+\citet{Tarango-Yong:2018a}.  It can be seen that the majority of dust
+streamlines do not cross this surface until well into the wings of the
+bow, so that a separate exterior dust wave can exist for this
+quasi-parallel magnetic field orientation.
 
@@
 perpendicular inertia-confined case studied in
-Appendix~\ref{sec:perp-magn-field}.  Although the grains decouple from
-the gas inside the rip point, for small impact parameters the magnetic
+\S~\ref{sec:perp-magn-field}.  Although the grains decouple from the
+gas inside the rip point, for small impact parameters the magnetic
 geometry does not allow the radiation field to expel them until they
@@
 the bow shock surface, so it is possible that a dust wave may still
-form, although it would only be on one side of the axis.
+form, although it would be on only one side of the axis.
 

### 2019-03-08 papers/Papers1234/sec-strong-coupling.tex
Jane's Paper I corrections, up to end of sec 2.3

@@
     cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
-    coupling is assumed. Solid black lines of varying width show the
+    coupling is assumed. Solid black lines of varying thickness show the
     bow size (star-apex separation, \(R_0\)), while gray shading shows
@@
 nevertheless dominate the broad-band opacity at FUV, optical and IR
-wavelengths if they are present.\footnote{%
-  At EUV wavelengths (\(\lambda < \SI{912}{\angstrom}\)), gas opacity
-  dominates if the hydrogen neutral fraction is larger than
-  \(\approx 0.001\), see discussion of ionization front trapping
-  below.} %
-The strong coupling assumption means that all the radiative forces
-applied to the dust grains are directly felt by the gas also.
+wavelengths if they are present. They also dominate at EUV wavelengths
+(\(\lambda < \SI{912}{\angstrom}\)), if the hydrogen neutral fraction is
+less than \(\approx 0.001\).  The strong coupling assumption means that all
+the radiative forces applied to the dust grains are directly felt by
+the gas also.
 
@@
 \end{equation}
-where \(\eta\wind\) is the momentum efficiency of the wind, which is typically
-\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
+where \(\eta\wind\) is the momentum efficiency of the wind, which is
+\(< 1\) in all cases except WR stars \citep{Lamers:1999b}. If the
+optical depth at UV/optical wavelengths is sufficiently large, then
 all of the stellar radiative momentum, emitted with rate \(L/c\), is
-trapped by the bow shell.  In the single scattering limit,\footnote{%
-  Although it may seem inconsistent to assume single scattering in the
-  case of high optical depths, this is defensible for the following
-  reasons. (1)~The grain albedo is not that high (typically
-  \(\sim 0.5\) at ultraviolet through optical wavelengths). (2)~The
-  scattered radiation field is more isotropic than the stellar field,
-  leading to cancellation in the radiative flux. (3)~Absorbed
-  radiation is re-emitted at infrared wavelengths, where the dust
-  opacity is very much lower.} %
-and temporarily neglecting the wind for clarity of exposition, then
-pressure balance at the bow apex, a distance \(R_0\) along the
-symmetry axis from the star is given by
+trapped by the bow shell.  At the infrared wavelengths where the
+absorbed radiation is re-emitted, the grain opacity is much lower, so
+the bow is optically thin to this radiation.  Combined with the fact
+that the UV single-scattering albedo is only \(\approx 0.5\), this means
+that the single-scattering limit is approximately valid, and we adopt
+it here.
+
+We define a fiducial bow shock radius \(R_*\) in the optically thick,
+radiation-only limit by balancing stellar radiation pressure against
+stream ram pressure at the bow apex along the
+symmetry axis from the star:
 \begin{equation}
   \label{eq:rad-press-balance-thick}
-  \frac{L}{4 \pi c R_0^2} = \rho v^2 \ ,
+  \frac{L}{4 \pi c R_*^2} = \rho v^2 \ ,
 \end{equation}
-which yields a fiducial bow shock radius in this optically thick,
-radiation-only limit as
+which yields 
 \begin{equation}
@@
 Therefore, an incoming stream with initial velocity, \(v_\infty\), can be
-brought to rest by radiation alone
-% \footnote{%
-%   For simplicity, we here ignore the effects of gravity, which are
-%   important for low ratios of \(\kappa L / M\), see
-%   \S~\ref{sec:effects-gravity}.  We also ignore pressure gradients and
-%   shocks, which are important as the velocity approaches the sound
-%   speed, \(\sound\) (in \S~XX below, we show that the resultant
-%   corrections to \(R_0\) are of order \(\sound / v_\infty\)).} %
-at a distance \(R\starstar\) where
+brought to rest by radiation alone at a distance \(R\starstar\) where
 \begin{equation}
@@
 
-Then, defining a fiducial optical depth,
+We define a fiducial optical depth,
 \begin{equation}
   \label{eq:tau-star}
-  \tau_* = \rho \kappa R_* \ ,
+  \tau_* = \rho \kappa R_* \ .
 \end{equation}
-and now reinstating the stellar wind ram pressure term
-% \footnote{%
-%   We implicitly assume that the interaction of the stellar wind with
-%   the external stream can always be treated in the continuum limit.
-%   This will be true if either the collisional mean free path or the
-%   ion Larmor radius is much smaller than \(R_0\), which is almost
-%   always the case.} %
-from equation~\eqref{eq:wind-efficiency}, we find that the general bow
-radius can be written in terms of the fiducial radius as
+With these fiducial values established, we return to the combined
+radiation plus wind scenario.  Adding the stellar wind ram pressure
+term from equation~\eqref{eq:wind-efficiency} allows us to write the
+general bow radius in terms of the fiducial radius as
 \begin{equation}
@@
 is gradually decelerated by absorption of photons as it approaches the
-bow.\footnote{A shock can still form in this case, but shocked
-  material constitutes only a small fraction of the total column
-  density of the shell.}
+bow.  We remark that a shock can still form in this case, but shocked
+material constitutes only a fraction of the total column density of
+the shell, as we will show in \S~\ref{sec:axial-structure-bow}.
 
@@
 UV-dominated spectrum of the hot stars, this star emits predominantly
-in the near-infrared, where the dust extinction efficiency is lower,
+in the near-infrared, where the dust extinction efficiency is lower \citep{Weingartner:2001a},
 so we adopt a lower opacity of \SI{60}{cm^2.g^{-1}}.  This has the
@@
 outer parts of the shell (see \citealt{Rodriguez-Ramirez:2016b}), but
-it is generally too weak to effect the shell structure even in such a
+it is generally too weak to affect the shell structure even in such a
 case, see \S~\ref{sec:axial-structure-bow} below.

### 2019-03-09 papers/Papers1234/bs-bw-dw-02.tex
Submit BS-BW-DW-01 paper

@@
 
-In \S~\ref{sec:gas-free-bow} we calculate analytical
-models of the shape of dust waves in the drag-free limit.
+In \citet{Henney:2019a} (hereafter, Paper~I) we studied the formation
+of bows around OB stars that are moving supersonically relative to
+their surrounding medium.  For the case of strong collisional coupling
+between gas and dust grains, we showed that three different regimes of
+interaction are possible: a taxonomy of bow types
+
+The plan of the paper is as follows.
+%
+In \S~\ref{sec:recap-paper-i} we give some results from Paper~I that
+we will need in later sections.
+%
+In \S~\ref{sec:gas-free-bow} we calculate analytical models of the
+shape of dust waves in the drag-free limit.
 % %
@@
 trajectories.
+
+\section{Important results from Paper~I}
+\label{sec:recap-paper-i}
+
+%% XREF \eqref{eq:Rstar}
+\begin{equation}
+  \label{eq:Rstar}
+  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
+\end{equation}
+
+%% XREF \eqref{eq:tau-star},
+\begin{equation}
+  \label{eq:tau-star}
+  \tau_* = \rho \kappa R_* \ .
+\end{equation}
+
+\begin{equation}
+  \label{eq:wind-efficiency}
+  \eta\wind  = \frac{L}{c\, \dot{M} V\wind} \ , 
+\end{equation}
+
+%% XREF \ref{eq:x-cases}
+\begin{equation}
+  \label{eq:x-cases}
+  R_0 \approx
+  \begin{cases}
+    \text{RBS (\(\tau_* > 1\)):} & (1 + \eta\wind)^{1/2} \, R_*  \\
+    \text{RBW (\(\eta\wind < \tau_* < 1\)):} & 2 \, \tau_* \, R_* \\
+    \text{WBS (\(\tau_* < \eta\wind^{1/2}\)):} & \eta\wind^{1/2} \, R_*  
+  \end{cases}
+\end{equation}
+
+\begin{align*}
+  \label{eq:stellar-parameters}
+  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
+  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
+  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
+  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
+  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
+  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
+\end{align*}
+where \(\bar{m}\) is the mean mass per hydrogen nucleon
+(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
+abundances).
+
+%% XREF \ref{eq:wind-eta-typical}
+\begin{equation}
+  \label{eq:wind-eta-typical}
+  \eta\wind = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
+\end{equation}
+
+%% XREF \ref{eq:taustar-typical}
+%% XREF \ref{eq:Rstar-typical}
+\begin{align}
+  \label{eq:Rstar-typical}
+  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
+  \label{eq:taustar-typical}
+  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
+\end{align}
 

### 2019-03-09 papers/Papers1234/sec-strong-coupling.tex
Submit BS-BW-DW-01 paper

@@
 photoionizing the entire bow shock shell, or whether the ionization
-front will be trapped within it.  The number of hydrogen
-recombinations\footnote{%
-  The diffuse field is treated in the on-the-spot approximation,
-  assuming all emitted Lyman continuum photons are immediately
-  re-absorbed locally, so the case~B recombination co-efficient,
-  \(\alphaB = \num{2.6e-13}\, T_4^{-0.7}\, \si{cm^3.s^{-1}}\), is
-  used, where \(T_4 = T/\SI{e4}{K}\).} %
-per unit time per unit area in a fully ionized shell is
+front will be trapped within it.  Using the on-the-spot approximation
+for the diffuse fields \citep{Osterbrock:2006a}, the number of
+hydrogen recombinations per unit time per unit area in a fully ionized
+shell of density \(n\shell\) and thickness \(h\shell\) is
 \begin{equation}
@@
 \end{equation}
-while the advective flux of hydrogen nuclei through the shock is 
+where \(\alphaB = \num{2.6e-13}\, T_4^{-0.7}\, \si{cm^3.s^{-1}}\) is
+the case~B recombination coefficient and \(T_4 = T/\SI{e4}{K}\).
+The advective flux of hydrogen nuclei through the shock is
 \begin{equation}
   \label{eq:shell-advective-flux}
-  \mathcal{A} = n v \ ,
+  \mathcal{A} = n v_\infty \ ,
 \end{equation}
@@
 \end{equation}
-Assuming strong cooling behind the shock,\footnote{%
-  This is shown to be justified in \S~\ref{sec:radi-cool-lengths}.
-} %
-the shell density is
+Assuming strong cooling behind the shock
+(\S~\ref{sec:radi-cool-lengths}), the shell density is
 \begin{equation}
@@
 weakly on the stellar parameters, which is shown by the red lines in
-Figure~\ref{fig:zones-v-n-plane}.  For the \SI{10}{M_\odot} star, this is
+Figure~\ref{fig:zones-v-n-plane}.  For the \SI{10}{M_\odot} star this is
 in the radiation bow wave regime, whereas for the higher mass stars it
@@
 even for \(v_{10} < 2\), where the effect is strongest, the change is
-only of order the width of the dark red line in
+only of order the thickness of the dark red line in
 Figure~\ref{fig:B-supergiant}.
@@
 Assuming a ratio of specific heats, \(\gamma = 5/3\), the relation between
-the pre-shock and immediate post-shock quantities is
+the pre-shock and immediate post-shock quantities
+\citep{ZelDovich:1967} is
 \begin{align}
@@
 the radiative case,
-\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
-  An approximate value can be found from
-  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
-  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
-  Consideration of the slight increase in density between the shock
-  and the contact/tangential discontinuity reduces this value by 5--10\%.} %
-For bows with outer stream densities between the two blue lines,
-cooling does occur, albeit inefficiently, so that the shell thickness
-is set by \(d\cool\) rather than \(h_0\).
+\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).  This value can be found
+from equation~\eqref{eq:shocked-shell-column} by substituting
+\(n = n_0\) and \(n\shell \approx 1.1 n_1\), then using
+equation~\eqref{eq:shock-n-jump}. The factor \num{1.1} comes from
+consideration of the slight increase in density between the shock and
+the contact/tangential discontinuity.  For bows with outer stream
+densities between the two blue lines, cooling does occur, albeit
+inefficiently, so that the shell thickness \(h\shell\) is set by
+\(d\cool\) rather than \(h_0\).
 
@@
 predicting the exact Mach number where it will occur.  In
-Figure.~\ref{fig:axial-structure}b, we assume that the shock occurs at
+Figure.~\ref{fig:axial-structure}b we assume that the shock occurs at
 a Mach number \(\M_0 = 1.5\), but multidimensional numerical
@@
 equation~\eqref{eq:ha-versus-h0} this translates to
-\(\tau > \frac43 \Gamma\Edd\), where Eddington factors are
-\(\Gamma\Edd \sim 100\) for luminous stars.  Such large optical depths would
+\(\tau > \frac43 \Gamma\Edd\), where dust-opacity Eddington factors are
+\(\Gamma\Edd \sim 100\) for OB stars.  Such large optical depths would
 require extremely high ambient densities of
@@
 (\(\propto n R_0\)) or volume emission measure
-(\(\propto n^2 R_0^3\)), which are both increasing functions of
-\(n\).\footnote{%
-  From \S~\ref{sec:three-bow-regimes}, the bow size falls relatively
+(\(\propto n^2 R_0^3\)), which are both increasing functions of \(n\) since,
+from \S~\ref{sec:three-bow-regimes}, the bow size falls relatively
 slowly as \(R_0 \propto n^{-1/2}\) in the WBS and RBS cases, and is
-  independent of \(n\) in the RBW case.}  Another contribution to the
+independent of \(n\) in the RBW case.  Another contribution to the
 high-density bias is simply that none but the highest velocity
@@
 assumed values, then these conclusions may change.  For instance,
-there are a growing number of stars, for which very low mass-loss
-rates have been diagnosed from UV, optical or infrared line profiles
+there are a growing number of stars for which very low mass-loss rates
+have been diagnosed from UV, optical or infrared line profiles
 \citep{Martins:2005b, Marcolino:2009a, Najarro:2011a, Martins:2012a,
@@
 mass-loss rate of \num{3e-8} to \SI{e-7}{M_\odot.yr^{-1}}, whereas the
-observed values are in the range \num{e-10} to \SI{3e-9}{M_\odot.yr^{-1}}
--- a shortfall of 10 to 1000!  This ``weak wind problem'' is a far
-larger discrepancy than can be explained by clumping effects.  A
-potential (partial) resolution is to suppose that internal shocks near
-the base of the wind, together with thermal conduction, heat a large
-fraction of the gas to coronal temperatures, where it is no longer
-detectable by means of standard wind diagnostic lines
-\citep{Lucy:2012a}.  However, in cases where x-ray diagnostics have
-been used to trace the mass loss of this hot component (\(\mu\)~Col,
-\citealp{Huenemoerder:2012a}; \(\zeta\)~Oph, \citealp{Cohen:2014a}), rates
-that are still an order of magnitude below the Vink values are found
-(see also \citealp{Shenar:2017a}).  In Figure~\ref{fig:O-weak-wind},
-we show results for a weak-wind O9 dwarf, which is identical to the
-\SI{20}{M_\odot} star from Table~\ref{tab:stars}, except with
-\(\eta\wind = 0.01 \eta\vink\) (approximating the measurements from the
-sample of \citealp{Martins:2005b}).  For such stars, the boundary
-between the wind-supported and radiation-supported regimes shifts to
-lower ambient densities, reaching \(n\crit \sim \SI{1}{cm^{-3}}\) for
+observationally derived values are in the range \num{e-10} to
+\SI{3e-9}{M_\odot.yr^{-1}} -- a shortfall of 10 to 1000!  This ``weak wind
+problem'' is a far larger discrepancy than can be explained by
+clumping effects.  A potential (partial) resolution is to suppose that
+internal shocks near the base of the wind, together with thermal
+conduction, heat a large fraction of the gas to coronal temperatures,
+where it is no longer detectable by means of standard wind diagnostic
+lines \citep{Lucy:2012a}.  However, in cases where x-ray diagnostics
+have been used to trace the mass loss of this hot component
+(\(\mu\)~Col, \citealp{Huenemoerder:2012a}; \(\zeta\)~Oph,
+\citealp{Cohen:2014a}), rates that are still an order of magnitude
+below the Vink values are found (see also \citealp{Shenar:2017a}).  In
+Figure~\ref{fig:O-weak-wind}, we show results for a weak-wind O9
+dwarf, which is identical to the \SI{20}{M_\odot} star from
+Table~\ref{tab:stars}, except with \(\eta\wind = 0.01 \eta\vink\)
+(approximating the measurements from the sample of
+\citealp{Martins:2005b}).  For such stars, the boundary between the
+wind-supported and radiation-supported regimes shifts to lower ambient
+densities, reaching \(n\crit \sim \SI{1}{cm^{-3}}\) for
 \(v = \SI{20}{km.s^{-1}}\).  This means that radiation-supported bows
@@
 These may be due to variations in the dust/gas ratio or to changes in
-the size distribution of the grains.  The UV opacity is dominated by
-very small grains (VSG) with radius \(a \sim \SI{10}{nm}\), which
-represent a small fraction (\(\simeq 5\%\)) of the total dust mass in
-standard grain mixtures \citep{Desert:1990a}.  This same VSG
-population dominates the mid-infrared continuum emission around
-\SI{24}{\um}, which is where stellar bows are most easily detected
-\citep{Meyer:2016a, Kobulnicky:2016a}. There is some evidence that
-such grains may be depleted in the ionized gas of the Orion Nebula
-\citep{Salgado:2016a}, leading to a decrease in \(\kappa\) by a factor of
-about six.  By equation~\eqref{eq:ncrit}, this would increase
-\(n\crit\) by the same factor, making radiation-supported bows less
-likely.  On the other hand, the process of Radiative Torque Disruption
-is predicted to be important \citep{Hoang:2018a} for the high
-radiation fields found in stellar bows, and this would tend to
-\emph{increase} the VSG abundance (and hence \(\kappa\)) via the
-centrifugal destruction of larger grains.  In LMC \hii{} regions,
-\citet{Stephens:2014b} find observational evidence that the VSG
-abundance increases as the radiation field gets stronger.
+the composition or size distribution of the grains.  The UV opacity is
+dominated by very small grains (VSG) with radius
+\(a \sim \SI{10}{nm}\), which represent a small fraction
+(\(\simeq 5\%\)) of the total dust mass in standard grain mixtures
+\citep{Desert:1990a}.  This same VSG population dominates the
+mid-infrared continuum emission around \SI{24}{\um}, which is where
+stellar bows are most easily detected \citep{Meyer:2016a,
+  Kobulnicky:2016a}. There is some evidence that such grains may be
+depleted in the ionized gas of the Orion Nebula \citep{Salgado:2016a},
+leading to a decrease in \(\kappa\) by a factor of about six.  By
+equation~\eqref{eq:ncrit}, this would increase \(n\crit\) by the same
+factor, making radiation-supported bows less likely.  On the other
+hand, the process of Radiative Torque Disruption is predicted to be
+important \citep{Hoang:2018a} for the high radiation fields found in
+stellar bows, and this would tend to \emph{increase} the VSG abundance
+(and hence \(\kappa\)) via the centrifugal destruction of larger grains.
+In LMC \hii{} regions, \citet{Stephens:2014b} find observational
+evidence that the VSG abundance increases as the radiation field gets
+stronger.
 
-Variations in metallicity will also be reflected in
-\(\kappa\), assuming that the total dust-gas ratio is roughly proportional
-to the metal abundance, \(Z\).  However, the wind strength
-\(\eta\wind\) will also increases with metallicity
-(\(\dot{M} V\wind \propto Z^{0.82}\), \citealp{Vink:2001a}), which will
-largely cancel out the effect in our bow models.
+Variations in metallicity will also be reflected in \(\kappa\), assuming
+that the total dust-gas ratio is roughly proportional to the metal
+abundance, \(Z\).  However, the wind strength \(\eta\wind\) also
+increases with metallicity (\(\dot{M} V\wind \propto Z^{0.82}\),
+\citealp{Vink:2001a}), which will largely cancel out the effect in our
+bow models.
 
@@
 
-We present a systematic study of the formation of emission arcs, or
-bows, around luminous stars that move supersonically relative to their
-surrounding medium, taking into account both the stellar wind and
-radiation pressure of the star.  In this initial study, we consider
-the case where gas and grains are perfectly coupled via collisions,
-and apply our models to OB stars.  Our principal results are as
-follows:
+We have presented a systematic study of the formation of emission
+arcs, or bows, around luminous stars that move supersonically relative
+to their surrounding medium, taking into account both the stellar wind
+and radiation pressure of the star.  In this initial study, we
+considered the case where gas and grains are perfectly coupled via
+collisions, and applied our models to OB stars.  Our principal results
+are as follows:
 \begin{enumerate}[1.]

### 2019-03-11 papers/Papers1234/bs-bw-dw-02.tex
Finish intro to paper II

@@
 \label{sec:rip-introduction}
+Stellar bow shocks are predicted to occur whenever a star moves
+supersonically relative to its surrounding medium, which may either be
+due to the star's own motion \citetext{runaways, e.g.,
+  \citealp{Blaauw:1961a}}, or due to an independent environmental flow
+\citetext{weather vanes, e.g., \citealp{Povich:2008a}}.  Bow shocks
+are associated with a large variety of different types of stars, for
+example: AGB stars and red super-giants \citep{Cox:2012a}; OB stars
+\citep{Kobulnicky:2017a}; T~Tauri stars \citep{Gull:1979a,
+  Henney:2013a}; photoevaporating protoplanetary disks
+\citep{Garcia-Arredondo:2001a, Smith:2005a}; neutron stars
+\citep{Cordes:1993a, Brownsberger:2014a}; planetary nebula halos
+\citep{Ali:2012a}; and Galactic Center sources \citep{Geballe:2004a,
+  Sanchez-Bermudez:2014a}.  The dominant emission mechanism can vary
+considerably between the different classes of sources, but
+recombination line radiation such as H\(\alpha\), infrared continuum
+radiation from warm dust, and free-free radio continuum are common
+\citep{Canto:2005a, Acreman:2016a, Meyer:2016a}.  In nearly all cases,
+stellar bow shocks are easily spatially resolved and mapped, allowing
+their shapes to be compared with theoretical predictions
+\citep{Wilkin:1996a, Tarango-Yong:2018a}.  A different class of
+stellar bow shocks are found in interacting binary systems
+\citep{Stevens:1992a}, but these typically emit by non-thermal
+mechanisms and are only resolvable using radio interferometry
+techniques \citep{Contreras:1999a, Dzib:2013a}.
 
 In \citet{Henney:2019a} (hereafter, Paper~I) we studied the formation
-of bows around OB stars that are moving supersonically relative to
-their surrounding medium.  For the case of strong collisional coupling
-between gas and dust grains, we showed that three different regimes of
-interaction are possible: a taxonomy of bow types
+of bows around OB stars by the combined action of their winds and
+radiation.  For the case of strong collisional coupling between gas
+and dust grains, we showed that three different regimes of interaction
+are possible, according to the relative values of stellar wind
+radiative momentum efficiency \(\eta\wind\) and the UV optical depth of
+the bow shell \(\tau\):
+\begin{enumerate}[{\(\star\)}]
+\item Wind-supported bow shocks (WBS) where \(\tau < \eta\wind\).  These are
+  purely hydrodynamic (or MHD) interactions, in which the stellar
+  radiation is dynamically unimportant.  This regime dominates for
+  fast-moving stars and for low-density environments.
+\item Radiation-supported bow waves (RBW) where
+  \(\eta\wind < \tau < 1\).  In these optically thin bows, the stellar
+  radiative momentum gradually decelerates the oncoming stream in a
+  broad shell.  This regime is important for B~stars and weak-wind
+  O~stars in moderate density environments (\(> \SI{100}{cm^{-3}}\)).
+\item Radiation-supported bow shocks (RBS) where \(\tau > 1\).  These are
+  optically thick shells, internally supported by the trapped stellar
+  radiation pressure.  This regime applies to slow-moving O~stars in
+  dense environments.
+\end{enumerate}
+In this paper, we investigate under what circumstances the strong
+gas--grain coupling might break down, leading to a fourth regime: a
+separate dust wave outside of the hydrodynamic bow shock (see Fig.~1
+of Paper~I).
+
+In neutral and molecular regions, the drag forces are relatively weak
+and so divergent dynamics of gas and grains are frequently found in
+the context of molecular clouds \citetext{\citealp{Hopkins:2016a,
+    Lee:2017a, Mattsson:2019a}, but see \citealp{Tricco:2017a}} and
+protoplanetary disks \citep{Weidenschilling:1977b, Birnstiel:2010a,
+  Dipierro:2018a}.  In ionized regions, the electrostatic forces
+between charged dust grains and charged gas particles (principally
+protons) leads to greatly increased drag forces, which tend to
+maintain a tight coupling between dust and gas \citep{Draine:2011a}.
+However, in a photoionized \hii{} region around a high-mass star, the
+dust feels a much larger radiation force than does the gas. This leads
+to a slow relative drift between the two components in the outer
+regions of the nebula \citep{Gail:1979a, Akimkin:2015a, Akimkin:2017a,
+  Ishiki:2018a} and a total decoupling very close to the central star
+\citep[Fig.~8 of][]{Draine:2011a}
+
+With respect to stellar bow shocks, gas--grain decoupling has been
+previously studied in the context of post-shock flow, where it is the
+sudden deceleration of the gas that is the primary impetus for the
+dust to separate.  The case of a cool red supergiant was simulated by
+\citet{van-Marle:2011a}, where large grains present in the stellar
+wind are not stopped in the inner termination shock, but are carried
+through the contact discontinuity by their inertia, penetrating into
+the interstellar medium.  \citet{Katushkina:2017a} simulated the
+opposite case, where grains in the ambient medium become decoupled
+from the gas after passing the outer bow shock, and subsequently
+gyrate about the magnetic field, forming filamentary structures (see
+also \citealp{Katushkina:2018a}).  In this paper, we study a different
+decoupling mechanism, where it is the stellar radiation force acting
+on the grains that causes the separation from the gas.  This mechanism
+was first proposed by \citet{Ochsendorf:2014b} to explain the infrared
+emission arc around the high-mass multiple system \(\sigma\)~Ori.
 
@@
 existence and structure of dust waves.
+%
+In \S~\ref{sec:discussion} we discuss our results in the context of observed bows.
+%
+In \S~\ref{sec:summary} we summarise our findings.
 %
@@
   \begin{cases}
-    \text{RBS (\(\tau_* > 1\)):} & (1 + \eta\wind)^{1/2} \, R_*  \\
-    \text{RBW (\(\eta\wind < \tau_* < 1\)):} & 2 \, \tau_* \, R_* \\
-    \text{WBS (\(\tau_* < \eta\wind^{1/2}\)):} & \eta\wind^{1/2} \, R_*  
+    \text{RBS (\(\tau_*^2 > 1\)):} & (1 + \eta\wind)^{1/2} \, R_*  \\
+    \text{RBW (\(\eta\wind < \tau_*^2 < 1\)):} & 2 \, \tau_* \, R_* \\
+    \text{WBS (\(\tau_*^2 < \eta\)):} & \eta\wind^{1/2} \, R_*  
   \end{cases}
@@
 
+\input{sec-dust-wave-discussion}
+
 \section*{Acknowledgements}

### 2019-03-11 papers/Papers1234/sec-dust-wave-discussion.tex
Finish intro to paper II

\section{Discussion}
\label{sec:discussion}

In molecular clouds:  \citet{Hopkins:2016a, Lee:2017a} say they
decouple. \citet{Tricco:2017a} says they don't.  But then
\citet{Mattsson:2019a} say they do.

In \citep{Akimkin:2015a} they used the drift approximation (ignored
grain inertia effects) and also ignore back reaction on gas. In
\citet{Akimkin:2017a} they do include back reaction.

Instabilities: Resonant Drag Instability \citep{Squire:2018a, Hopkins:2018a}

Survival of dust grains.  Sputtering \citep{Draine:2011a}.  Radiative Torque Disruption \citep{Hoang:2018a}.

\section{Summary}
\label{sec:summary}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "bs-bw-dw-02"
%%% End:

### 2019-03-11 papers/Papers1234/sec-weak-coupling.tex
Submit BS-BW-DW-01 paper
Finish intro to paper II

@@
-\section{Imperfect coupling between gas and dust}
+\section{Gas--grain coupling and decoupling}
 \label{sec:imperf-coupl-betw}
@@
 \end{equation}
-where the last expression corresponds to the optically thin limit.  Then, if we define the grain's frequency-averaged radiation pressure
-efficiency as
+where the last expression corresponds to the optically thin limit.  If
+we define the grain's frequency-averaged radiation pressure efficiency
+as
 \begin{equation}
@@
 \(f\rad \sim 0.1 f_*\) from equation~\eqref{eq:frad-Xi} if
-\(\Qp \sim 1\) at UV wavelengths, which is true for all but the smallest
+\(\Qpbar \approx 1\) at UV wavelengths, which is true for all but the smallest
 grains.  Thus, from the equations for \(f\drag\) given in
@@
 \(\Xi\) will increase, with a dependence of \(R^{-2}\) once the stream
-is well inside the ionization front.  This increases \(f\rad\)
-(eq.~[\ref{eq:frad-Xi}]), but also increases the grain potential,
+is well inside the ionization front, assuming roughly constant
+pressure in the \hii{} region.  This increases \(f\rad\)
+(eq.~[\ref{eq:frad-Xi}]), but also increases the grain potential
 \(\phi\) (eq.~[\ref{eq:phi-vs-Xi}]) due to the increasing dominance of

### 2019-03-14 papers/Papers1234/app-dust-wave.tex
Submit BS-BW-DW-01 paper
Write lots of discussion for Paper II

@@
     a divergent stream of dust grains that originates from a source on
-    the \(x\) axis at a distance \(D = 10 R\starstar\) from the origin.  In
-    this case, the inner edge of the bow wave is hyperbolic and the
-    parallel stream result is also shown for comparison.}
+    the \(x\) axis at a distance \(D = 10 R\starstar\) from the
+    origin.  In this case, the inner edge of the bow wave is
+    hyperbolic and the parallel stream result is also shown (inner
+    thick light gray line) for comparison.}
   \label{fig:dust-trajectories}
@@
 distance.  Note that \(R\starstar\) as given by
-equation~\eqref{eq:dust-r0} is formally identical to Paper~I's
+equation~\eqref{eq:dust-r0} is almost the same as Paper~I's
 equation~(6), but with the important difference that it is for a
 single grain considered in isolation, rather than a well-coupled dusty
-plasma.  If
+plasma.  Since we are here ignoring collisional effects, there is no
+pressure, and therefore nothing to stop the spatial coexistence of an
+inbound and outbound dust stream.  For the well-coupled case, this is
+not possible and a shocked shell must form (see Paper~I's Fig.~5b).
 
@@
 This is the polar form of the equation for the confocal parabola,
-which we have already discussed in detail in \S~\ref{Q-sec:conic} and
-Appendix~\ref{Q-app:parabola} of \citet{Tarango-Yong:2018a}.  Its
-planitude and alatude are \(\Gamma = \Lambda = 2\) and these are
-unchanged under projection at any inclination.
+which is discussed in detail in \S~\ref{Q-sec:conic} and
+Appendix~\ref{Q-app:parabola} of \citet{Tarango-Yong:2018a}.  In that
+paper, the dimensionless quantities \textit{planitude} \(\Pi\) and
+\textit{alatude} \(\Lambda\) are introduced as a way of efficiently
+characterizing bow shapes.  The confocal parabola has planitude and
+alatude of \(\Pi = \Lambda = 2\) and these are unchanged under projection at
+any inclination.
 
@@
 We will show later in \S~\ref{sec:magn-effects-grain} that for
-sufficiently small grains the Larmor magnetic gyration radius, \(r\B\),
-is typically small compared with other length scales of interest, and
+sufficiently small grains the Larmor magnetic gyration radius,
+\(r\B\), is small compared with other length scales of interest, and
 so the grains are effectively tied to the magnetic field lines.  In
@@
 the star, although in practice the presence of a wind-supported bow
-shock, however small, will complicate the picture.
+shock, however small, will complicate the picture.  Since there is no
+unambiguous definition of the star--apex distance in this case, it is
+not possible to define the shape parameters \(\Pi\) and \(\Lambda\) either.
 

### 2019-03-14 papers/Papers1234/bs-bw-dw-02.tex
Write lots of discussion for Paper II

@@
 decoupling mechanism, where it is the stellar radiation force acting
-on the grains that causes the separation from the gas.  This mechanism
-was first proposed by \citet{Ochsendorf:2014b} to explain the infrared
-emission arc around the high-mass multiple system \(\sigma\)~Ori.
+on the grains that causes a separation from the gas \emph{before the
+  stream reaches the bow shock}.  This mechanism was first proposed by
+\citet{Ochsendorf:2014b} to explain the infrared emission arc around
+the high-mass multiple system \(\sigma\)~Ori.
 
@@
 %
-In \S~\ref{sec:discussion} we discuss our results in the context of observed bows.
+In \S~\ref{sec:discussion} we discuss our results in the context of
+previous studies.
 %
@@
 
-\section{Important results from Paper~I}
+\section{Recapitulation of Paper~I}
 \label{sec:recap-paper-i}
 
-%% XREF \eqref{eq:Rstar}
-\begin{equation}
-  \label{eq:Rstar}
-  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
-\end{equation}
-
-%% XREF \eqref{eq:tau-star},
-\begin{equation}
-  \label{eq:tau-star}
-  \tau_* = \rho \kappa R_* \ .
-\end{equation}
-
-\begin{equation}
-  \label{eq:wind-efficiency}
-  \eta\wind  = \frac{L}{c\, \dot{M} V\wind} \ , 
-\end{equation}
-
+In Paper~I, we found approximate expressions for the bow radius in each of the three regimes discussed in the introduction: 
 %% XREF \ref{eq:x-cases}
@@
 \end{equation}
+In these expressions, we use a fiducial radius
+%% XREF \eqref{eq:Rstar}
+\begin{equation}
+  \label{eq:Rstar}
+  R_* = \left(\frac{L}{4\pi c \rho v_\infty^2}\right)^{1/2} \ ,
+\end{equation}
+a fiducial optical depth
+%% XREF \eqref{eq:tau-star},
+\begin{equation}
+  \label{eq:tau-star}
+  \tau_* = \rho \kappa R_* \ ,
+\end{equation}
+and a factor that describes the efficiency of the stellar wind as the fraction of the stellar radiation momentum that is converted to wind momentum
+\begin{equation}
+  \label{eq:wind-efficiency}
+  \eta\wind  = \frac{c\, \dot{M} V\wind}{L} \ .
+\end{equation}
+Paper~I's equation~(11) allows a more exact value for \(R_0\) to be
+found numerically in intermediate cases.  Note that \(R_0\) is the
+star--apex distance measured along the symmetry axis of the bow
+\citetext{see \citealp{Tarango-Yong:2018a} for explanation of
+  nomenclature and discussion of bow shapes}, and is calculated in the
+limit that the momentum transfer occurs at a surface.  In cases where
+the shell's finite width is significant, \(R_0\), should correspond
+approximately to the astropause (contact discontinuity) in the WBS
+regime, or a UV optical depth of unity (as measured from the star) in
+the RBS regime.  The total perpendicular optical depth of the shell to
+stellar radiation can be found as
+\begin{equation}
+  \label{eq:actual-tau}
+  \tau = \frac{R_0}{R_*} \, \tau_* \ .
+\end{equation}
 
+In the foregoing, we employ the stellar bolometric luminosity, \(L\),
+wind mass-loss rate, \(\dot{M}\), and terminal velocity, \(V\wind\),
+together with the ambient stream's mass density, \(\rho\), relative
+velocity \(v_\infty\), and effective dust opacity, \(\kappa\).  It is convenient
+to define dimensionless versions of these parameters by normalizing to
+typical values:
 \begin{align*}
-  \label{eq:stellar-parameters}
+  % \label{eq:stellar-parameters}
   \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
@@
 (\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
-abundances).
-
+abundances).  In terms of these dimensionless parameters,
+equations~(\ref{eq:Rstar}--\ref{eq:wind-efficiency}) take the
+convenient forms:
 %% XREF \ref{eq:wind-eta-typical}
-\begin{equation}
-  \label{eq:wind-eta-typical}
-  \eta\wind = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
-\end{equation}
-
 %% XREF \ref{eq:taustar-typical}
@@
   \label{eq:taustar-typical}
-  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
+  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \\
+  \label{eq:wind-eta-typical}
+  \eta\wind &= \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1} \ .
 \end{align}
@@
 \citep{Jones:2001a} and AstroPy \citep{Astropy-Collaboration:2013a,
-  Astropy-Collaboration:2018a} projects.
+  Astropy-Collaboration:2018a} projects.  We thank Olga Katushkina for useful discussions.
 

### 2019-03-14 papers/Papers1234/sec-dust-wave-discussion.tex
Write lots of discussion for Paper II

@@
 
-In molecular clouds:  \citet{Hopkins:2016a, Lee:2017a} say they
-decouple. \citet{Tricco:2017a} says they don't.  But then
-\citet{Mattsson:2019a} say they do.
+In this section we place our results in the context of previous work
+on gas--grain coupling in the environs of high-mass stars.  We
+concentrate on conceptual and theoretical aspects, postponing
+empirical questions about particular sources for later papers.
 
-In \citep{Akimkin:2015a} they used the drift approximation (ignored
-grain inertia effects) and also ignore back reaction on gas. In
-\citet{Akimkin:2017a} they do include back reaction.
+The distinction that we draw in \S~\ref{sec:exist-cond-separ} between
+inertia-confined dust waves and drag-confined dust waves is novel.
+However, the concept of the \textit{rip point} can be found in
+previous works, although not under that name and it has generally been
+assumed to be of little interest.  For instance, Figure~8 of
+\citet{Draine:2011a} clearly shows the discontinuity in drift velocity
+that occurs at small radii within an \hii{} region (differences from
+our own Figs.~\ref{fig:multi-dustprops} and~\ref{fig:drift-gn} are due
+to \citeauthor{Draine:2011a}'s assumption of constant grain
+potential).  However, the region of supersonic drift involves a very
+small fraction of the total dust in the \hii{} region, so it was not
+relevant to the concerns of that paper. Similarly, in \S~3.1 of
+\citet{Hopkins:2018c} the possibility is raised of a ``decoupling
+instability'' in the case that coupling strength decreases with
+increasing slip velocity, but they go on to dismiss this as physically
+irrelevant.  On the contrary, we show in this paper that it \emph{is}
+relevant so long as the grain potential is high, so that a distinct
+local maximum occurs in the drag-versus-velocity profile (see
+Fig.~\ref{fig:gas-grain-drag-photoionized}).  In \S~9 of
+\citet{Hopkins:2018a}, various issues relating to grain charging and
+drag are discussed.  The quantity
+\(e_{\text{rad}} / e_{\text{therm}}\) from \S~9.1.4 of that paper is
+the same as our radiation parameter, \(\Xi\).  In \S~9.2.3 they give an
+expression for the critical radius that divides subsonic from
+supersonic drift, which is exactly equivalent to our
+equation~\eqref{eq:Rdag-over-Rstar} for the rip point radius.  The
+parameters assumed by \citeauthor{Hopkins:2018a} yield
+\(\Xi_\dag = 3200\), which is within the range of values that we find for
+O~stars in Table~\ref{tab:Xi-rip}.
 
-Instabilities: Resonant Drag Instability \citep{Squire:2018a, Hopkins:2018a}
+\citet{Akimkin:2017a} studied the effect of radiation pressure on the
+time-dependent evolution of an \hii{} region, taking full account of
+dynamical coupling between grains and gas, thus extending a previous
+study \citep{Akimkin:2015a} that had ignored the back-reaction on the
+gas (see our \S~\ref{sec:back-reaction-gas}).  They found that the
+dust completely decouples from the gas in the zone around the star
+(\(< \SI{0.2}{pc}\) on timescales \(\sim \SI{0.5}{Myr}\)), which produces
+an inner dust hole but partially eliminates the inner gas density hole
+that is found in models that assume perfect coupling
+\citep{Mathews:1967a, Draine:2011a, Kim:2016b}. The decoupling is more
+pronounced for stars of lower effective temperature, which is probably
+related to the fact that we find the critical radiation parameter
+\(\Xi_\dag\) to be lower for B~stars than for O~stars
+(Table~\ref{tab:Xi-rip}).  A similar dust hole for the central region
+is found by \citet{Ishiki:2018a}.
 
-Survival of dust grains.  Sputtering \citep{Draine:2011a}.  Radiative Torque Disruption \citep{Hoang:2018a}.
+The gas--grain decoupling that we have discussed so far occurs at high
+radiation parameter, \(\Xi \sim 1000\), but there is another regime of
+potential decoupling that occurs at low \(\Xi\).  It has long been
+recognized \citep{Gail:1979a} that Coulomb gas--grain coupling should
+weaken in the outer zones of an \hii{} region due to the fact that the
+grain potential passes through (or close to) zero as a result of
+electron collisions becoming competitive with photoelectric ejection
+as the radiation field weakens.  This is the regime around
+\(\Xi = \text{\numrange{0.1}{1.0}}\) in Figure~\ref{fig:drift-gn},
+giving drift velocities of order \SI{1}{km.s^{-1}} for larger grains
+(\SI{0.2}{\um}), which may be sufficient to produce significant
+spatial variations in grain abundance on Myr timescales
+\citep{Ishiki:2018a}. It remains to be seen whether this is still true
+once effects that have been neglected in existing models are accounted
+for, such as the \hii{} region's magnetic field \citep{Krumholz:2007a,
+  Arthur:2011a, Gendelev:2012a} and internal turbulence
+\citep{Arthur:2016a}.  Yet another regime of potential decoupling
+occurs in the neutral shell outside the \hii{} region
+\citep{Gustafsson:2018a}, but since the drift velocity in both these
+cases is much less than interesting values of the stream velocity,
+\(v_\infty\), neither low-\(\Xi\) regime is relevant to dust waves.
+
+The most detailed simulations to date of the combined dynamics of
+dust, gas, and magnetic field in an OB bow was carried out by
+\citet{Katushkina:2017a}, who followed the trajectories of dust
+particles after passing through an MHD bow shock, under the influence
+of the stellar radiation force and Lorentz force.  The gas is
+decelerated in the shock, but the dust initially carries on with its
+pre-shock motion, which produces a relative velocity with respect to
+the plasma. The component of this velocity perpendicular to the
+magnetic field induces gyration about the field lines
+(cf~\S~\ref{sec:magn-effects-grain}), which forms filaments of
+enhanced dust density that are oriented perpendicular to the bow axis
+and with characteristic separation equal to the bulk plasma velocity
+times the gyration period.  In \citet{Katushkina:2018a}, similar such
+simulations are applied to observations of the runaway B1 supergiant
+\(\kappa\)~Cas, moving at \(\approx \SI{30}{km.s^{-1}}\), in order to explain the
+filaments of infrared dust emission seen at \SI{24}{\um}.  It is found
+that the simulations can only fit the observations with very large
+dust grains (\(\approx \SI{1}{\um}\)) and a very strong perpendicular
+magnetic field \(v\alfven \approx \SI{20}{km.s^{-1}}\).  The stellar
+parameters of \(\kappa\)~Cas are roughly those given in the last row of
+Table~\ref{tab:stars} and the observed radius of the dust arc (assumed
+to correspond to the astropause) is \SI{0.75}{pc} for a distance of
+\SI{1}{kpc}.  The \citeauthor{Katushkina:2018a} simulations do not
+explicitly include the Coulomb drag force on the dust grains, although
+our own results (\S~\ref{sec:cloudy-models-dust}) suggest that this
+must be important around \(\kappa\)~Cas.  \citet{Katushkina:2018a} argue
+that small grains are swept out by stellar radiation before reaching
+the bow shock, and this would indeed be true if drag forces were
+negligible.  However, we find \(\Xi \approx 20\) for the
+\(\kappa\)~Cas shell, implying strong gas--grain coupling and that even
+small grains cannot be repelled by the radiation force.  The root
+cause of our difference with these authors is that they are assuming a
+grain potential \(\phi \sim 1\), as seen in the ISM in the Solar
+neighborhood, as opposed to \(\phi \sim 10\), which is more appropriate to
+the environs of an OB star.  We also note that even when the Lorentz
+force vastly exceeds all other forces, it does not necessarily follow
+that the other forces are unimportant.  For example, in the
+magnetized dust wave models that we present in
+\S~\ref{sec:tight-magn-coupl} and \S~\ref{sec:grain-traj-with}, the
+Lorentz force is infinitely stronger than other forces.  Nevertheless,
+the radiation and drag forces are crucial in determining the structure
+of the dust waves, which is possible because the component of the
+Lorentz force projected along the field lines is zero.
+
+The survival of dust grains of different sizes in close proximity to
+OB stars is something that must be considered.  Potential destruction
+mechanisms include thermal evaporation, photosputtering, particle
+sputtering, and radiative torque destruction.
+
+Sputtering
+\citep{Draine:2011a}.  Radiative Torque Disruption
+\citep{Hoang:2018a}.
+
+Instabilities: Resonant Drag Instability \citep{Squire:2018a, Hopkins:2018a} - application to stagnant drift case.
 

### 2019-03-14 papers/Papers1234/sec-weak-coupling.tex
Write lots of discussion for Paper II

@@
     Uncertainties represent variations with grain size and gas density. 
-    See Appendix~\ref{sec:cloudy-models-dust} for further details.}
+    }
   \end{tabular*}
@@
 The radius of the rip point, \(R_\dag\), can be expressed in terms of
-\(R_*\), the fiducial optically thick bow shock radius introduced in
-Paper~I's \S~2.1:
+\(R_*\), the fiducial optically thick bow shock radius
+(eq.~[\ref{eq:Rstar}]):
 %% XREF \ref{sec:three-bow-regimes}
@@
 where we have made use of equation~\eqref{eq:Xi-Prad-over-Pgas} and
-Paper~I's equation~(3).
+the final approximate equality assumes a typical \hii{} region
+temperature of \SI{e4}{K}.
 %% XREF \eqref{eq:Rstar}
@@
     waves may form around main-sequence OB stars of
-    \SIlist{10;20;40}{M_\odot} (see Paper~I's Tab.~1).  This figure is
-    similar to Paper~I's Fig.~2,
-    %% XREF\ref{fig:zones-v-n-plane},
-    except that the velocity axis is logarithmic and extends out to
-    \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show parameters
-    where dust waves may be allowed in the cases of large
+    \SIlist{10;20;40}{M_\odot} with standard wind parameters (see
+    Tab.~\ref{tab:stars}).  This figure is similar to Paper~I's
+    Fig.~2, except that the velocity axis is logarithmic and extends
+    out to \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show
+    parameters where dust waves may be allowed in the cases of large
     (\(a = \SI{0.2}{\um}\)) and small (\(a = \SI{0.02}{\um}\))
     graphite and silicate grains, as labeled in the left panel.  For
-    \((v, n)\) outside of these shapes, dust waves cannot occur for
+    \((v_\infty, n)\) outside of these shapes, dust waves cannot occur for
     the reasons indicated by labeled orange arrows in the center
@@
     the left panel show where the rip point and the drag-free
-    turnaround radius coincide.  Dust waves above these lines are drag
-    confined, while dust waves below the lines are inertia confined.
-  }
+    turnaround radius coincide.  Dust waves above and to the left of
+    these lines are drag confined, while dust waves below and to the
+    right of the lines are inertia confined.  }
   \label{fig:existence-dust-wave}
@@
 hits the hydrodynamic bow shock caused by the stellar wind.  The wind
-bow shock radius is \(R_0 = \eta\wind^{1/2} R_*\) (Paper~I's eq.~[12]),
+bow shock radius is \(R_0 = \eta\wind^{1/2} R_*\) (eq.~[\ref{eq:x-cases}]),
 %% XREF \ref{eq:x-cases}
 where \(\eta\wind\) is the wind momentum efficiency
-(Paper~I's eq.~[13]).
+(eq.~[\ref{eq:wind-eta-typical}]).
 %% XREF \ref{eq:wind-eta-typical}
@@
 opportunely, even once it has decoupled from the gas.  From
-equation~\eqref{eq:dust-r0}, together with Paper~I's equations~(3, 9),
+equation~\eqref{eq:dust-r0}, together with Paper~I's
+equations~(\ref{eq:Rstar}, \ref{eq:tau-star}),
 %% XREF \eqref{eq:Rstar}
@@
 dominate the UV opacity.  Given the dependence of \(\tau_*\) on the
-stream parameters (Paper~I's eq.~[15]),
+stream parameters (eq.~[\ref{eq:taustar-typical}]),
 %% XREF \ref{eq:taustar-typical}
@@
 inertia-confined \textit{inner} dust wave may form inside the bow
-shock, even when \(\tau_* < \tau_{*,\text{min}}\).  Although the same might
-be thought to apply to the condition of
-equation~\eqref{eq:dust-wave-velocity-condition}, this is not the
-case, since the density compression in the bow shock will reduce the
-radiation parameter, \(\Xi\), which moves the rip point, \(R_\dag\), to an
-even smaller radius.  Therefore, if radiation has not managed to
-decouple a grain before it passes through the shock, it is unlikely to
-be able to do it afterwards.
+shock, even when \(\tau_* < \tau_{*,\text{min}}\).  This is similar to the
+case studied by \citet{Katushkina:2017a, Katushkina:2018a}, which
+requires simultaneous modeling of the grain dynamics with the
+magnetohydrodynamics of the bow shock.  Note that unlike with
+equation~\eqref{eq:dust-wave-low-density-condition}, violation of
+equation~\eqref{eq:dust-wave-velocity-condition} cannot lead to an
+inner dust wave, since the density compression in the bow shock will
+reduce the radiation parameter, \(\Xi\), which moves the rip point,
+\(R_\dag\), to an even smaller radius.  Therefore, if radiation has not
+managed to decouple a grain before it passes through the shock, it is
+unlikely to be able to do so afterwards.
 
@@
 dust-free bow shock formed by this interaction is therefore increased
-by a factor \((1 - \Delta v / v_\infty)^{-1}\) with respect to the case
-calculated in Paper~I's \S~2.1,
-% XREF \ref{sec:three-bow-regimes}
-yielding
+by a factor \((1 - \Delta v / v_\infty)^{-1}\) with respect to the value given
+by equation~\eqref{eq:x-cases}, yielding
 \begin{equation}
@@
 stream velocity and grain and star properties, so that
-\(\tau_* \propto n^{1/2}\) (Paper~I's eq.~[15]).
+\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).
 % XREF \ref{eq:taustar-typical}
@@
 material density in \si{g.cm^{-3}}, and we have made use of
-equations~(\ref{eq:dust-r0}, \ref{eq:Rdag-over-Rstar}), together with Paper~I's equation~(14).
+equations~(\ref{eq:Rstar-typical}, \ref{eq:dust-r0}, \ref{eq:Rdag-over-Rstar}).
 %% XREF \ref{eq:Rstar-typical}
@@
 trajectory intersects the outer shock of the dust-free wind-supported
-bow shock.  The increased gas density in the bow shock shell will
+bow shock.  The increased gas pressure in the bow shock shell will
 reduce \(\Xi\), which is likely to cause gas--grain recoupling in the

### 2019-03-16 papers/Papers1234/app-dust-wave.tex
First complete draft of BS-BW-DW paper II

@@
 \( \varepsilon_\mu = (1 - 2\mu)^{-1}\).  An example is shown in
-Figure~\ref{fig:dust-trajectories} for \(\mu = 0.1\).  Unsurprisingly,
+Figure~\ref{fig:dust-trajectories}b for \(\mu = 0.1\).  Unsurprisingly,
 the resulting bow shape is more open than in the parallel stream case,
 increasingly so with increasing \(\mu\).  The planitude and alatude are
-both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\).
+both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\)
+(\((\Pi = \Lambda = 2.25\) in Fig.~\ref{fig:dust-trajectories}b).
 

### 2019-03-16 papers/Papers1234/sec-dust-wave-discussion.tex
First complete draft of BS-BW-DW paper II

@@
 
-In this section we place our results in the context of previous work
-on gas--grain coupling in the environs of high-mass stars.  We
-concentrate on conceptual and theoretical aspects, postponing
-empirical questions about particular sources for later papers.
+In this section we briefly discuss our predictions for the
+appearance of dust waves and place our results in the context of
+previous work on gas--grain coupling in the environs of high-mass
+stars.  We concentrate on conceptual and theoretical aspects,
+postponing empirical questions about particular sources for later
+papers.
+
+\subsection{Predicted appearance of dust waves}
+\label{sec:pred-shape-struct}
+By definition, dust waves do not correspond to any structure in the
+gas and so are only detectable via the mid-infrared thermal emission
+of the grains.  The emissivity is proportional to the grain density
+but also depends on the grain temperature, which is a decreasing
+function of radius, \(R\), from the star \citetext{see, for example,
+  synthetic observations in \citealp{Mackey:2016a, Acreman:2016a,
+    Meyer:2017a}}.  In radiative equilibrium, the bolometric
+emissivity is proportional to the stellar flux \(\propto R^{-2}\), but the
+radial dependence of the monochromatic emissivity will be much steeper
+than this on the short-wavelength side of the average grain thermal
+spectrum.  With this in mind, we can crudely estimate the appearance
+of the example dust waves calculated in \S\S~\ref{sec:gas-free-bow}
+and \ref{sec:grain-traj-with}.
+
+In the inertia-confined case, the radius \(R\starstar\) is
+proportional to the single-grain opacity \(\kappa\grain\) and will
+therefore vary with grain size and composition.  For a spherical grain
+of radius \(\amu\,\si{\um}\) and solid density
+\(\rho\grain \, \si{g.cm^{-3}}\), equation~\eqref{eq:kappa-grain} yields
+\begin{equation}
+  \label{eq:kappa-d-dependence}
+  \kappa\grain = 7500 \frac{\Qpbar}{\rho\grain \amu} \ . 
+\end{equation}
+The radiation pressure efficiency is \(\Qpbar \sim 1\) for
+\(\amu > 0.02\), but falls as \(\Qpbar \propto a\) for smaller grains
+\citep[e.g., Fig.~7 of][]{Draine:2011a}.  Therefore, all the smallest
+grains will form the dust wave at the same point, but grains larger
+than \SI{0.02}{\um} will be spread out with
+\(R\starstar \propto a^{-1}\).  It might be thought that this would produce
+a very broad diffuse appearance to the dust wave, but this is
+mitigated by the fact that it is the smaller grains that dominate the
+UV opacity and mid-IR emissivity.  Also, the larger grains may be
+destroyed by radiative torques (see \S~\ref{sec:grain-survival-dust}).
+For the drag-confined case, the situation is clearer since the dust
+wave will form just inside the rip point, \(R_\dag\), which is relatively
+insensitive to the grain size.
+
+The effect of a roughly parallel magnetic field is mainly seen in the
+shape of the dust wave, which becomes hemispherical
+(Fig.~\ref{fig:inertia-thB0}) instead of parabolic as was found in the
+non-magnetic case (Fig.~\ref{fig:dust-trajectories}).  Interestingly,
+this effect is the opposite of what is seen in simulations of MHD bow
+shocks \citep{Meyer:2016a}, where a parallel B-field leads to
+flatter-nosed bow shapes with a high planitude \citetext{see Fig.~25
+  of \citealp{Tarango-Yong:2018a}}.  Figure~\ref{fig:frozen-stream}ab
+shows that the field orientation has a similar effect on the dust wave
+shape for drag-confined magnetic dust waves, but with the added
+complication that a second dense shell forms on one side of the axis
+at the stagnant drift radius, \(R_\ddag\), in cases where
+\(v_\infty > \SI{60}{km.s^{-1}}\).  However, since \(R_\ddag\) is several times
+larger than \(R_\dag\), the emission from this outer shell is likely to
+be weak, given the steep radial dependence of the mid-IR emissivity
+discussed above.
+
+When the magnetic field is close to perpendicular to the axis, then a
+dense dust shell does not form in the apex region for either the
+inertia-confined (Fig.~\ref{fig:inertia-thB90}) or drag-confined
+(Fig.~\ref{fig:frozen-stream}cd) cases.  Nonetheless, it is possible
+that a dust wave might form in the wings in such cases.
+
+\subsection{Gas--grain dynamics in \hii{} regions}
+\label{sec:gas-grain-dynamics-hii}
 
@@
   Arthur:2011a, Gendelev:2012a} and internal turbulence
-\citep{Arthur:2016a}.  Yet another regime of potential decoupling
-occurs in the neutral shell outside the \hii{} region
+\citep{Arthur:2016a}.  On the other hand, grain abundance variations
+may be enhanced by the resonant drag instability \citep{Squire:2018a,
+  Hopkins:2018a}.  Yet another regime of potential decoupling occurs
+in the neutral shell outside the \hii{} region
 \citep{Gustafsson:2018a}, but since the drift velocity in both these
@@
 \(v_\infty\), neither low-\(\Xi\) regime is relevant to dust waves.
+
+\subsection{Gas--grain dynamics in stellar bows}
+\label{sec:gas-grain-dynamics-bs}
+
+The term \textit{dust wave} was first coined to described the
+radiative decoupling of grains from the plasma flowing past a massive
+star by \citet{Ochsendorf:2014b}, who attempted to explain the
+infrared emission arc around \(\sigma\)~Ori.  The concept was subsequently
+applied to additional dust arcs in RCW~82 and RCW~120
+\citep{Ochsendorf:2014a} and a refined model was applied to further
+observations of \(\sigma\)~Ori \citep{Ochsendorf:2015a}.  These works
+provided the inspiration for the present paper, where we have
+attempted to take a more a priori and systematic approach to the
+problem, including factors such as the Lorentz force that were
+neglected by \citeauthor{Ochsendorf:2014b}.
 
@@
 
+\subsection{Grain survival}
+\label{sec:grain-survival-dust}
+
 The survival of dust grains of different sizes in close proximity to
 OB stars is something that must be considered.  Potential destruction
-mechanisms include thermal evaporation, photosputtering, particle
-sputtering, and radiative torque destruction.
+mechanisms include thermal evaporation, particle sputtering, and
+radiative torque destruction.  Thermal evaporation requires that the
+grain radiative equilibrium temperature exceed the sublimation
+temperature (\SIrange{1500}{2000}{K}, depending on composition), which
+occurs for radiative fluxes about \SI{e9} times higher than the
+interstellar radiation field.  For a drag-confined dust wave, we have
+a fixed radiation parameter \(\Xi_\dag \sim 1000\), so this becomes a
+threshold on the gas density, requiring \(n > \SI{3e5}{cm^{-3}}\).
+Combining this with the maximum allowed density for a dust wave
+(eq.~[\ref{eq:dust-wave-high-density-condition}]), we also obtain a
+condition on the stream velocity:
+\(v_\infty > 170 \kappa_{600}^{0.5} L_4^{0.15} \, \si{km.s^{-1}}\).  Therefore,
+thermal evaporation is generally unimportant in dust waves, except for
+fast-moving stars in very high density environments.
 
-Sputtering
-\citep{Draine:2011a}.  Radiative Torque Disruption
-\citep{Hoang:2018a}.
+Ion sputtering is only effective for collider kinetic energies in
+excess of \SI{100}{eV} \citep{Draine:1995a, Field:1997a}, which is
+significantly larger than thermal energies in photoionized gas.  It
+therefore requires supersonic gas--grain slip velocities
+\(w > \SI{75}{km.s^{-1}}\), but this does not necessarily imply that
+the stream velocity need be quite so high.  For inertia-confined dust
+waves, \(w\) has a maximum value of \(2 v_\infty\) and for drag-confined
+dust waves it can be even higher (for instance, reaching
+\(w \approx 4 v_\infty\) in Fig.~\ref{fig:frozen-trajectories}a), so that
+\(v_\infty > \SI{30}{km.s^{-1}}\) is probably sufficient.  However, in
+order to be destroyed by sputtering it is also necessary that a dust
+grain of radius \(\amu\)\,\si{\um} should traverse a gas column
+density of \(\approx \num{2e21}\, \amu \,\si{cm^{-2}}\)
+\citep{Draine:2011a}.  For magnetic field orientations close to
+parallel (which is the case that most favors dust wave formation), the
+grains linger in the dust wave for several dynamical times (see
+\S~\ref{sec:grain-traj-with}), so we estimate a total column of
+\(\approx 10 n R_\dag\).  Using equations~(\ref{eq:Rstar-typical},
+\ref{eq:Rdag-over-Rstar}) then implies that grains smaller than
+\(\amu \sim 0.001 (L_4 n)^{1/2}\) can be destroyed by sputtering in the
+dust wave.
 
-Instabilities: Resonant Drag Instability \citep{Squire:2018a, Hopkins:2018a} - application to stagnant drift case.
+Radiative torque disruption \citep{Hoang:2018a} is the centrifugal
+rupture of an irregular grain of non-zero helicity that has been
+suprathermally spun up by the anisotropic absorption of radiation
+\citep{Dolginov:1976a, Draine:1996b, Lazarian:2007a}.  The process has
+a very steep size dependence, being most effective in destroying
+larger grains.  Using \citeauthor{Hoang:2018a}'s equation~(27) and
+assuming a grain tensile strength of
+\(S_{\text{max}} = \SI{2e10}{dyne.cm^{-2}}\) \citetext{\S~2.4 of
+  \citealp{Borkowski:1995a}}, we find that grains larger than
+\(\amu \sim 0.04\, n^{-0.123}\) are efficiently destroyed by this
+mechanism at a distance \(R_\dag\) from the star. The spin-up timescales
+are less than \(100\, n^{-1}\,\si{yr}\), which is short compared with
+the dust wave dynamic timescale.
+
+In summary, refractory grains in the size range
+\SIrange{0.001}{0.04}{\um} are predicted to survive in dust waves.
+Larger grains than this are unlikely to be able to resist
+disintegration by radiative torques and smaller grains may be
+destroyed by sputtering.
+
+% \subsection{Dust wave stability}
+% \label{sec:dust-wave-stability}
+
+% Instabilities: Resonant Drag Instability - application to stagnant drift case.
 
@@
 \label{sec:summary}
+
+We have extended our previous study of bows around OB stars (Paper~I)
+in order to consider the weak coupling case, in which a
+radiation-supported dust wave decouples from the gas to form an
+infrared emission arc outside of any hydrodynamic bow shock.  Our
+principle findings are as follows:
+\begin{enumerate}[1.]
+\item Dust waves can only exist when the star's relative velocity with
+  respect to its environment exceeds a critical value
+  \(v_\infty > v_{\text{min}}\)
+  (eq.~[\ref{eq:dust-wave-velocity-condition}]).  For O~stars with
+  strong winds,
+  \(v_{\text{min}} = \text{\SIrange{150}{300}{km.s^{-1}}}\), although
+  for weak-wind stars and B~stars it can be as low as
+  \SI{30}{km.s^{-1}}.
+\item Additionally, the ambient density is constrained to lie within a
+  certain range, \(n_{\text{min}} \to n_{\text{max}}\). For the lowest
+  allowed relative velocities, \(v_\infty \approx v_{\text{min}}\), these are
+  \(n_{\text{min}} = \SI{0.01}{cm^{-3}}\),
+  \(n_{\text{max}} = \SI{100}{cm^{-3}}\) for B stars and
+  \(n_{\text{min}} = \SI{1}{cm^{-3}}\),
+  \(n_{\text{max}} = \SI{e5}{cm^{-3}}\) for strong-wind O~stars (see
+  Fig.~\ref{fig:existence-dust-wave}).  Both these limits increase for
+  higher velocities, as \(n_{\text{min}} \propto v_\infty^2\) and
+  \(n_{\text{max}} \propto v_\infty^4\).
+\item Dust waves may either be \textit{inertia-confined} or
+  \textit{drag-confined}, where the inertia-confined regime (in which
+  gas drag is always negligible) corresponds to a relatively narrow
+  range of densities above \(n_{\text{min}}\).
+\item In drag-confined dust waves, the gas--grain decoupling occurs
+  suddenly at a \textit{rip point}, where the Coulomb drag
+  catastrophically breaks down. The rip point occurs at a particular
+  value of the radiation-to-gas pressure ratio:
+  \(\Xi_\dag \sim 1000\), with little dependence on other parameters.
+\item The post-rip grain trajectories are unstable for
+  \(v_\infty = \text{\SIrange{10}{50}{km.s^{-1}}}\), exhibiting limit-cycle
+  decoupling/recoupling behavior of repeated rip followed by
+  snap-back.  For higher velocities a quasi-stationary stagnant drift
+  shell can form on the axis.
+\item Grain coupling to magnetic fields can modify these results, but
+  this depends critically on the angle \(\theta\B\) between the field and
+  the star's relative velocity vector.  For the quasi-parallel case
+  (\(\theta\B < \ang{30}\)), the axial structure of the dust wave is
+  little-changed, but the shape of the dust wave wings become more
+  closed (hemispherical) than in the non-magnetic case.  For the
+  quasi-perpendicular case (\(\theta\B > \ang{60}\)), a dust wave cannot form
+  on the axis, although it is possible it may do so in the wings.
+\end{enumerate}
 

### 2019-03-16 papers/Papers1234/sec-weak-coupling.tex
First complete draft of BS-BW-DW paper II

@@
 
-If the radiation field is sufficiently strong, then the collisional
-coupling between grains and gas will break down.  In this section, we
-calculate the regions of star/stream parameter space where this might
-occur, leading to a separation of the bow into an outer dust wave and
-an inner, dust-free bow shock.
+We now consider how the results of the previous section are changed
+when one accounts for drag forces from the gas.  After considering the
+general form of these forces in \S~\ref{sec:drag-force-grains}, we
+study the behavior of the grain electrostatic potential in
+\S~\ref{sec:cloudy-models-dust} and the nature of the decoupling that
+occurs for sufficiently strong radiation fields in
+\S~\ref{sec:gas-grain-separ}.  In \S~\ref{sec:exist-cond-separ} we use
+this information to deduce conditions for the existence of dust waves,
+and calculate grain trajectories in \S~\ref{sec:two-regimes-post} and
+estimate the back-reaction on the plasma in
+\S~\ref{sec:back-reaction-gas}.
+
+% If the radiation field is
+% sufficiently strong, then this collisional coupling between grains and
+% gas will break down at some point.  In this section, we calculate the
+% regions of star/stream parameter space where this might occur, leading
+% to a separation of the bow into an outer dust wave and an inner,
+% dust-free bow shock.
 

### 2019-03-16 papers/Papers1234/bs-bw-dw-03.tex
Divide dust wave paper in three parts
Start writing about the shell structure figure
Begin reorganization of Paper III

--- 2017-11-23 papers/Paper1/dusty-bow-wave.tex
@@
 
+\usepackage{chemgreek}
+\activatechemgreekmapping{newtx}
+\usepackage{listings}
+
 \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
@@
 
-\title[Dust waves, bow waves, bow shocks]
-{Shapes of dust waves, bow waves, and bow shocks}
+\title
+{Bow shocks, bow waves, and dust waves. III. Diagnostics}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Henney \& Tarango Yong]{
-  William J. Henney \& Jorge A. Tarango Yong\\
+\author[Henney \& Arthur]{
+  William J. Henney \& S. J. Arthur\\
   \AddressCRyA
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2017}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\Sin}{\mathcal{S}}
-\DeclareMathOperator{\Cos}{\mathcal{C}}
-\DeclareMathOperator{\Cot}{\mathcal{T}}
-\DeclareMathOperator{\GammaFunc}{\Gamma}
-\newcommand\w{\ensuremath{\mathrm{w}}}
-\newcommand\C{\ensuremath{\mathrm{c}}}
-\providecommand{\abs}[1]{\lvert#1\rvert}
-\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
-\newcommand\TODO[1]{%
-  \begin{center}
-    \framebox{\parbox{0.8\linewidth}{
-        \texttt{\footnotesize\color{red} #1}}}
-  \end{center}}
+\pubyear{2019}
 
-\newcommand\uvec[1]{\bm{\hat{#1}}}
-\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+\input{bs-bw-dw-defs.tex}
 
@@
 \begin{abstract}
-  Dust waves and bow waves result from the action of a star's
-  radiation pressure on a stream of dust grains that is flowing past
-  it.  They are an alternative mechanism to hydrodynamic bow shocks
-  for explaining the curved arcs of infrared emission seen around some
-  stars.  We employ simple cylindrically symmetric models for the dust
-  grain dynamics under the influence of radiation and weak gas--grain
-  coupling, which produce bow shapes that we call dragoids.  We also
-  show how thin-shell hydrodynamic models can be modified to treat the
-  case of strong gas-grain coupling, producing bow shapes that we call
-  trapoids.  Using our recently developed two-dimensional
-  classification scheme for projected bow shapes, we then analyze the
-  inclination-dependent tracks of the dragoids and trapoids in the
-  planitude--alatude plane, finding interesting differences from the
-  wilkinoid, cantoid, and ancantoid shapes of hydrodynamic bow shock
-  models. We further show how these are modified in the presence of
-  small-amplitude standing-wave oscillations of the basic shape, as
-  may be produced by hydrodynamic instabilities or a time-varying
-  source.  We analyze the prospects of using shape analysis of
-  observational datasets to discriminate between different bow models,
-  finding that sample sizes of order 100 are required.
+  Stellar bow shocks, bow waves, and dust waves all result from the
+  action of a star's wind and radiation pressure on a stream of dusty
+  plasma that flows past it.  The dust in these bows emits prominently
+  at mid-infrared wavelengths in the range \SIrange{8}{60}{\um}. We
+  propose a novel diagnostic method, the \(\tau\)--\(\eta\) diagram, for
+  analyzing these bows, which is based on comparing the fractions of
+  stellar radiative energy and stellar radiative momentum that is
+  trapped by the bow shell.  This diagram allows the discrimination of
+  radiation-supported bows from wind-supported bows.  For the latter,
+  it allows the stellar wind mass loss rate to be determined.  We
+  critically compare our method with a previous method that has been
+  proposed for determining wind mass loss rates from bow shock
+  observations. We find that the dust emissivity model used previously
+  needs to be corrected to account for differences in the spectral
+  energy distribution between OB stars and the interstellar radiation
+  field, which results in a downward revision by a factor of two in
+  the mass loss rates.  After correction, the methods complement one
+  another to some degree, with differing sensitivities to systematic
+  model uncertainties.  We point out that observations of bows are of
+  limited utility in constraining mass loss rates of weak-wind stars,
+  since these tend to have radiation-supported bows, which yield only
+  upper limits to the mass loss rate.
 \end{abstract}
@@
 
-\input{sec-dust-bow-intro}
-\input{app-dust-wave}
-\input{sec-standing-wave}
-\input{sec-dust-bow-discuss}
+\section{Introduction}
+\label{sec:introduction}
+
+In order to provide an empirical anchor to our theoretical
+calculations, we now consider how the parameters of our models might
+be determined from observations.  The parameter space diagrams, such
+as Figures~\ref{fig:zones-v-n-plane} and
+\ref{fig:existence-dust-wave}, are not particularly useful in this
+regard, since in many cases the ambient density and relative stellar
+velocity are not directly measured.  Instead, we aim to construct
+diagnostics based on the most common observations, which are of the
+infrared dust emission.  Key questions that we wish to address include
+\begin{enumerate}[1.]
+\item Can we distinguish observationally between radiation support
+  (bow waves and dust waves) and wind support (bow shocks)?
+\item Are there any clear examples of sources with radiation-supported bows?
+\item In the case of wind support, can we reliably determine mass loss
+  rates from mid-infrared observations?
+\end{enumerate}
+
+\input{app-cloudy-dust-heating}
+\input{sec-observational-diagnostics}
 \bibliographystyle{mnras}
@@
 \appendix
-\input{app-dust-equations}
+\input{app-k17-k18}
 

### 2019-03-16 papers/Papers1234/sec-observational-diagnostics.tex
Begin reorganization of Paper III

@@
 \end{figure*}
-
-In order to provide an empirical anchor to our theoretical
-calculations, we now consider how the parameters of our models might
-be determined from observations.  The parameter space diagrams, such
-as Figures~\ref{fig:zones-v-n-plane} and
-\ref{fig:existence-dust-wave}, are not particularly useful in this
-regard, since in many cases the ambient density and relative stellar
-velocity are not directly measured.  Instead, we aim to construct
-diagnostics based on the most common observations, which are of the
-infrared dust emission.  Key questions that we wish to address include
-\begin{enumerate}[1.]
-\item Can we distinguish observationally between radiation support
-  (bow waves and dust waves) and wind support (bow shocks)?
-\item Are there any clear examples of sources with radiation-supported bows?
-\item In the case of wind support, can we reliably determine mass loss
-  rates from mid-infrared observations?
-\end{enumerate}
 

### 2019-03-17 papers/Papers1234/app-k17-k18.tex
Major surgery on Paper III to get stuff out of appendices

--- 2019-02-23 papers/Papers1234/app-k17-k18.tex
@@
-\section{Reanalysis of bow shock sources from Kobulnicky et al. (2016,
-  2017, 2018)}
-\label{app:bow-shock-data}
-
-In a series of papers \citeauthor{Kobulnicky:2018a} provide an
-extensive mid-infrared-selected sample of over 700 candidate stellar
-bow shock nebulae (\citealp{Kobulnicky:2016a, Kobulnicky:2017a,
-  Kobulnicky:2018a}, hereafter K16, K17, and K18).  For 20 of these
-sources, reliable distances and spectral classifications are provided
-(Table~5 of K17 and Tables~1 and~2 of K18), and these are used in
-\S~\ref{sec:summary-discussion}, where we discuss the
-\(\tau\)--\(\eta\) diagnostic diagram.  In this appendix, we outline our
-treatment and analysis of the data in these catalogs, which differs in
-some important respects from that of the original authors.
-
-The UV optical depth of the bow shell is obtained
-(eq.~[\ref{eq:tau-empirical}]) from the ratio of infrared shell
-luminosity to stellar luminosity.  The inverse of this ratio is given
-in Table~5 of K17, but we choose to re-derive the values since the
-spectral classification of some of the sources was revised between K17
-and K18.  Although K17 found the total shell fluxes from fitting dust
-emission models to the observed SEDs, we adopt the simpler approach of
-taking a weighted sum of the flux densities \(F_\nu\) (in \si{Jy}) in
-three mid-infrared bands:
-\begin{multline}
-  \label{eq:total-ir-flux}
-  F_{\text{IR}}  \approx \bigl[  2.4\,(F_8 \text{ or } F_{12})
-    + 1.6\,(F_{22} \text{ or } F_{24})  \\
-  + 0.51\,F_{70}\bigr]
-  \,\times \SI{e-10}{erg.s^{-1}.cm^{-2}} \ ,
-\end{multline}
-where \(F_8\) is Spitzer IRAC \SI{8.0}{\um}, \(F_{24}\) is Spitzer
-MIPS \SI{23.7}{\um}, \(F_{12}\) and \(F_{22}\) are WISE bands 3 and 4,
-and \(F_{70}\) is Herschel PACS \SI{70}{\um}.  The weights are chosen
-so that the integral \(\int_0^\infty F_\nu \,d\nu\) is approximated by the sum
-\(\Sigma_k F_k\, \Delta\nu_k\), under the assumption that fluxes in shorter (e.g.,
-IRAC \SI{5.8}{\um}) and longer (e.g., PACS \SI{150}{\um}) wavebands
-are negligible.  Shell fluxes are converted to luminosities using the
-assumed distance to each source, and stellar luminosities are taken
-directly from K18 Table~2, based on spectroscopic classification and
-the calibrations of gravity and effective temperature from
-\citet{Martins:2005a}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/K17-tau-comparison}
-  \caption{Comparison between shell-to-star luminosity ratios
-    calculated as described in the text (\(y\) axis) with those given
-    in K17 (\(x\) axis).  The blue dashed line signifies equality and
-    the gray band shows ratios between 1/2 and 2.}
-  \label{fig:k17-k18-comparison}
-\end{figure}
-
-In Figure~\ref{fig:k17-k18-comparison} we compare the \(\tau\) obtained
-using the shell luminosity as described above with that obtained using
-the luminosity ratios directly from K17 Table~5.  It can be seen that
-for the majority of sources the two measurements are consistent within
-a factor of two (gray band).  The four furthest-flung outliers can be
-understood as follows:
-\begin{description}
-\item[\textit{Source 67}] This has a very poor-quality spectral fit in
-  K17 (see lower left panel of their Fig.~12) and so 
-  \(F_{\text{IR}}\) is overestimated by them by a factor of 10.
-\item[\textit{Sources 341 and 342}] The spectral classes changed from
-  B2V in K17 to O9V and B1V, respectively, in K18, increasing the
-  derived \(L_*\), which lowers \(\tau\).
-\item[\textit{Source 411}] The luminosity class changed from Ib (K17)
-  to V (K18), so \(L_*\) has been greatly reduced, which increases
-  \(\tau\).
-\end{description}
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
-%   \caption[K18 pair plot]{Pair plots of correlations between observed
-%     and derived parameters of bows from the \citep{Kobulnicky:2018a}
-%     sample.}
-%   \label{fig:K18-pairplot-edited}
-% \end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
-  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
-    identified in K18.  Red crosses show the emissivities given in
-    K18's Table~2 as a function of the radiation field \(U\), while
-    the solid gray line shows the emissivities that they claim to be
-    using from \citet{Draine:2007a}.  The dashed line shows the
-    emissivities that we believe they should have been using, which
-    correct for the marked difference in spectral energy distribution
-    between OB stars and the Galactic interstellar radiation field
-    (see App.~\ref{sec:grain-temp-emiss}).}
-  \label{fig:k18-emissivity}
-\end{figure}
-
-\newcommand\LOS{\ensuremath{_{\text{los}}}}
-K18 derive mass loss rates for their sources using a method that is
-different from the one that we employ in
-\S~\ref{sec:summary-discussion}.  Both methods are based on
-determining the stellar wind ram pressure that supports the bow shell,
-but K18 do so via the following steps:
-\begin{enumerate}[K1.]
-\item \label{K1} The line-of-sight mass column through the shell is
-  calculated by combining the peak surface brightness at \SI{70}{\um},
-  \(S_{70}\), with a theoretical emissivity per nucleon,
-  \(j_{70}(U)\), from \citet{Draine:2007a}:
-  \(\Sigma\LOS = S_{70} / \bar{m} j_{70}(U)\).  This depends on
-  knowledge of the stellar radiation field at the shell:
-  \(U \propto L_* / R_0^2\).
-\item \label{K2} The shell density is found from the line-of-sight
-  mass column using an observationally determined ``chord diameter'',
-  \(\ell\), which is assumed to be equal to the depth along the line
-  of sight: \(\rho\shell = \Sigma\LOS / \ell\).
-\item \label{K3} The internal ram pressure is equated to the external
-  ram pressure, which is found by assuming a stream velocity of
-  \SI{30}{km.s^{-1}} and a compression factor of 4 across the outer
-  shock:
-  \(P_{\text{stream}} = 0.25 \rho\shell \times
-  (\SI{30}{km.s^{-1}})^2\).
-\end{enumerate}
-There are clear parallels but also differences between steps
-K\ref{K1}--K\ref{K3} and our own steps P\ref{P1}--P\ref{P3}.  Our
-step~P\ref{P1} depends on the total observed infrared flux of the bow
-combined with an assumption about the grain opacity at ultraviolet
-wavelengths, while step~K\ref{K1} depends on the peak brightness at a
-single wavelength combined with an assumption about the grain
-emissivity at infrared wavelengths.  Our step~P\ref{P2} requires an
-assumption about the relative thickness of the shell, while
-step~K\ref{K2} is more directly tied to observations.\footnote{%
-  Note that there is a relation between the chord length, \(\ell\),
-  and the shell thickness, \(h\shell\), but this depends on the
-  planitude, \(\Pi\) of the bow shape \citep{Tarango-Yong:2018a}:
-  \( h\shell/R_0 = \Pi \bigl(1 - \{1 - [\ell/(2 \Pi R_0)]^2\}^{1/2}\bigr)\).  } %
-On the other hand, step~K\ref{K3} makes a roughly equivalent
-assumption about the shock compression factor,\footnote{%
-  In reality, the compression factor may be larger or smaller than 4,
-  depending on the efficiency of the post-shock cooling (see
-  \S~\ref{sec:radi-cool-lengths}).  For instance, for
-  \(v = \SI{30}{km.s^{-1}}\) as assumed by K18 and \(T = \SI{e4}{K}\),
-  one has a Mach number of \(\M_0 = 2.63\) and a compression factor of
-  2.8 for a non-radiative shock (by eq.~[\ref{eq:shock-n-jump}]) or a
-  factor of \(\M_0^2 =6.9\) for a strongly radiative one.  } %
-and a further assumption about the stream velocity. These assumptions
-are not necessary for our step~P\ref{P3}, but we do need to assume a
-value for the shell gas temperature.
-
-In principle, both methods are valid and their different assumptions
-and dependencies on observed quantities and auxiliary parameters
-provide an important cross check on one another.  However, as
-explained in detail in Appendix~\ref{sec:grain-temp-emiss}, the
-\(j_\nu(U)\) relation depends on the shape of the illuminating SED,
-which means that the \citet{Draine:2007a} models require modification
-when applied to grains around OB stars.  In addition, when attempting
-to replicate the K18 values of \(j_{70}\) we find that they only
-follow the \citet{Draine:2007a} values for \(U > \num{e4}\), tending
-to a constant value for weaker radiation fields.  The situation is
-summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
-directly from Table~2 of K18 are shown by red crosses, the values they
-claim to be using are shown by the gray solid line (this curve is
-consistent with that shown in K18 Fig.~2), and the values they
-\textit{should} have been using are shown by the gray dashed line.
-
-% If we replaced K3 with M3, then mass loss rates would be reduced by 1.86 across the board
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/K18-mdot-Ux8-comparison}
-  \caption{Effects on mass-loss determination of correcting the K18
-    emissivities.  The mass-loss rates from Table~2 of K18 are shown
-    on the \(x\) axis, while the corrected values are shown on the
-    \(y\) axis.  Symbols are color coded by the strength of the
-    radiation field, \(U\). The corrected mass-loss rates are
-    predominantly lower by a factor of roughly 2.}
-  \label{fig:k18-mdot-corrected-emissivity}
-\end{figure}
-
-After correcting the \SI{70}{\um} emissivities in this way, we
-re-derive the mass loss rates, following the same steps as in K18,
-which are then used in Figure~\ref{fig:mass-loss-vs-luminosity}b of
-\S~\ref{sec:summary-discussion}.  The difference between these
-corrected mass-loss rates and those published in K18 is shown in
-Figure~\ref{fig:k18-mdot-corrected-emissivity}.  It can be seen that
-sources with \(U \approx \num{e3}\) (darker shading) are relatively
-unaffected but that sources with stronger radiation fields (lighter
-shading) have their mass-loss increasingly reduced, as could be
-surmised from Figure~\ref{fig:k18-emissivity}.  The average reduction
-is by a factor of about two.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/K18-mdot-corrected-comparison-R0-edited}
-  \caption{Comparison of the two mass-loss methods: K18 corrected
-    method (\(x\) axis) versus our method (\(y\) axis).  Error bars on
-    the \(y\) axis correspond to a factor-three uncertainty in
-    \(\eta\shell\).  Sources for which these error bars overlap with
-    the RBW zone are only upper limits for the wind mass-loss rate,
-    and are indicated by faint symbols.}
-  \label{fig:mass-loss-comparison}
-\end{figure}
-
-Finally, in Figure~\ref{fig:mass-loss-comparison} we compare our own
-mass-loss determinations with the corrected K18 values.  The plot
-symbols are shaded according to the physical size of the bow, \(R_0\).
-It is apparent that the two methods are broadly in agreement on
-average, but there is considerable dispersion for individual objects,
-with only a weak correlation between the results of the two techniques
-(Pearson correlation coefficient \(r = 0.67\)).  Interestingly, the
-smaller bows (darker shading) show much better agreement than the
-larger bows (lighter shading).  The five bows with
-\(R_0 > \SI{0.4}{pc}\) (339, 344, 369, 381, 382) show a difference of
-nearly an order of magnitude, in the sense that our method
-consistently predicts lower mass-loss rates than K18.  For a further
-five of the sources (380, 407, 409, 410, 411), our method gives only
-an upper limit to the wind mass-loss rate if one assumes a
-factor-three uncertainty in \(\eta\shell\), and these bows are among
-the smallest in the sample, all with \(R_0 < \SI{0.1}{pc}\).
-
-\subsection{Uncertainty estimates for observational quantities}
-\label{sec:uncert-estim-observ}
-
-In this section, we estimate the \(1\sigma\) uncertainties in
-observational measurements, which contribute to the uncertainties in
-the derived quantities: \(\tau\), \(\eta\), and \(\dot M\) (see
-\S~\ref{sec:summary-discussion}).
-
-\subsubsection{Distance}
-\label{sec:distance}
-
-Most sources are members of known high-mass clusters with distance
-uncertainties less than 20\% (0.08~dex). The only exception is
-Source~329 in Cygnus, for which the distance uncertainty is roughly a
-factor of 2 \citep{Kobulnicky:2018a}.
-
-\subsubsection{Stellar luminosity}
-\label{sec:stellar-luminosity}
-
-The stellar luminosity is determined from spectral classification,
-which makes it independent of distance.  Taking a \SI{2000}{K}
-dispersion in the effective temperature scale \citep{Martins:2005a}
-gives an uncertainty of 25\% in the luminosity, and adding in possible
-errors in gravity and the effect of binaries, we estimate a total
-uncertainty in \(L_*\) of 50\% (0.45~mag or 0.18~dex).
-
-\subsubsection{Shell flux and surface brightness}
-\label{sec:shell-flux-surface}
-
-We estimate the uncertainty in shell bolometric flux,
-\(F_{\text{IR}}\), by comparing two different methods: model fitting
-\citep{Kobulnicky:2017a} and a weighted sum of the 8, 24, and
-\SI{70}{\um} bands (eq.~[\ref{eq:total-ir-flux}]), giving a standard
-deviation of 17\% (0.07~dex).  To this, we add the estimate of 25\%
-for the effects of background subtraction uncertainties on individual
-photometric measurements \citep{Kobulnicky:2017a}. The absolute flux
-calibration uncertainty for both Herschel PACS \citep{Balog:2014a} and
-Spitzer MIPS \citep{Engelbracht:2007a} is less than 5\%, which is
-small in comparison. Combining the 3 contributions in quadrature gives
-a total uncertainty of 0.12~dex.  We adopt the same uncertainty for
-the \SI{70}{\um} surface brightness.
-
-\subsubsection{Angular sizes}
-\label{sec:angular-sizes}
-
-For the angular apex distance, \(\theta\), the largest uncertainty for
-well-resolved sources is due to the unknown inclination.
-\citet{Tarango-Yong:2018a} show that the dispersion in true to
-projected distances can introduce an uncertainty of \(30\%\)
-(0.11~dex) in unfavorable cases (e.g., their Fig.~26).  For 5 of the
-20 sources from \citet{Kobulnicky:2018a}, \(\theta\) is of order the
-Spitzer PSF width at \SI{24}{\um}, so the errors may be larger.
-
-\subsubsection{Stellar wind velocity}
-\label{sec:stell-wind-veloc}
-
-Although this is not strictly an observed quantity for the K18 sample,
-we will treat it as such since it is estimated per star, based on the
-spectral type.
-
-\subsubsection{Uncertainties and covariance for derived quantities}
+\section{Covariance of derived quantities from propagation of observational uncertainties}
 \label{sec:comb-uncert-covar}

### 2019-03-17 papers/Papers1234/bs-bw-dw-03.tex
Major surgery on Paper III to get stuff out of appendices

@@
 
+In \citet{Henney:2019a, Henney:2019b} (Paper~I and Paper~II) we
+presented a taxonomy of stellar bows, which we divided into
+wind-supported bow shocks (WBS) and various classes of
+radiation-supported bows.  When the dust and gas remains well-coupled
+(Paper~I), these are optically thin radiation-supported bow waves
+(RBW) and optically thick radiation-supported bow shocks (RBS).  When
+the dust decouples from the gas (Paper~II), one has inertia-confined
+dust waves (IDW) and drag-confined dust waves (DDW).
+
+In Paper~I we derived expressions for the bow radius \(R_0\)in each of
+the three well-coupled regimes as a function of the parameters of the
+star and the ambient medium.  In Paper~II, we found the criteria for
+the dust to decouple from the gas to form a separate dust wave outside
+of the hydrodynamic bow shock.  The most important of these is that
+the ratio of radiation pressure to gas pressure should exceed a
+critical value, \(\Xi_\dag \sim 1000\).
+
 In order to provide an empirical anchor to our theoretical
 calculations, we now consider how the parameters of our models might
-be determined from observations.  The parameter space diagrams, such
-as Figures~\ref{fig:zones-v-n-plane} and
-\ref{fig:existence-dust-wave}, are not particularly useful in this
-regard, since in many cases the ambient density and relative stellar
-velocity are not directly measured.  Instead, we aim to construct
-diagnostics based on the most common observations, which are of the
-infrared dust emission.  Key questions that we wish to address include
+be determined from observations.  The parameter-space diagrams, such
+as Figure~2 of Paper~I, are not always useful in this regard, since in
+many cases the ambient density and relative stellar velocity are not
+directly measured.  Instead, we aim to construct diagnostics based on
+the most common observations, which are of the infrared dust emission.
+Key questions that we wish to address include
 \begin{enumerate}[1.]
@@
 
-\input{app-cloudy-dust-heating}
+The outline of the paper is as follows. In
+\S~\ref{sec:energy-trapp-vers} we describe how the optical depth and
+the gas pressure in the bow shell can be estimated from a small number
+of observed quantities.  In \S~\ref{sec:eta-tau-diagnostic} we place
+observed bow sources on a diagnostic diagram of these two quantities
+and discuss the influence of observational errors and systematic model
+uncertainties. In \S~\ref{sec:cand-radi-supp} we use the diagram to
+identify some candidates for radiation-supported bows. In
+\S~\ref{sec:grain-temp-emiss} we calculate the grain emissivity as a
+function of the stellar radiation field around OB stars.  In
+\S~\ref{sec:stellar-wind-mass} we compare two different methods of
+estimating the stellar wind mass loss rates from observations of the
+bows.  In \S~\ref{sec:conclusions} we summarise out findings.
+
 \input{sec-observational-diagnostics}

### 2019-03-17 papers/Papers1234/sec-observational-diagnostics.tex
Major surgery on Paper III to get stuff out of appendices

@@
-\section{Observational diagnostics}
-\label{sec:summary-discussion}
-
 % Are there any objects that might not be bow shocks?
@@
 % Dust waves favored by high velocities and intermediate densities.
+
+\section{Optical depth and pressure of the bow shell}
+\label{sec:energy-trapp-vers}
 
@@
 \end{figure*}
-
-\subsection{Energy trapping versus momentum trapping}
-\label{sec:energy-trapp-vers}
 
@@
 
-\subsection[The eta-tau diagnostic diagram]
+\section[The eta-tau diagnostic diagram]
 {\boldmath The \(\eta\shell\)--\(\tau\) diagnostic diagram}
@@
 
-\subsubsection{Random uncertainties due to observational errors}
+\subsection{Treatment of sources from \citeauthor{Kobulnicky:2018a}}
+\label{sec:kobulnicky}
+
+In a series of papers \citeauthor{Kobulnicky:2018a} provide an
+extensive mid-infrared-selected sample of over 700 candidate stellar
+bow shock nebulae (\citealp{Kobulnicky:2016a, Kobulnicky:2017a,
+  Kobulnicky:2018a}, hereafter K16, K17, and K18).  For 20 of these
+sources, reliable distances and spectral classifications are provided
+(Table~5 of K17 and Tables~1 and~2 of K18), and these are used in
+\S~\ref{sec:summary-discussion}, where we discuss the
+\(\tau\)--\(\eta\) diagnostic diagram.  In this appendix, we outline our
+treatment and analysis of the data in these catalogs, which differs in
+some important respects from that of the original authors.
+
+The UV optical depth of the bow shell is obtained
+(eq.~[\ref{eq:tau-empirical}]) from the ratio of infrared shell
+luminosity to stellar luminosity.  The inverse of this ratio is given
+in Table~5 of K17, but we choose to re-derive the values since the
+spectral classification of some of the sources was revised between K17
+and K18.  Although K17 found the total shell fluxes from fitting dust
+emission models to the observed SEDs, we adopt the simpler approach of
+taking a weighted sum of the flux densities \(F_\nu\) (in \si{Jy}) in
+three mid-infrared bands:
+\begin{multline}
+  \label{eq:total-ir-flux}
+  F_{\text{IR}}  \approx \bigl[  2.4\,(F_8 \text{ or } F_{12})
+    + 1.6\,(F_{22} \text{ or } F_{24})  \\
+  + 0.51\,F_{70}\bigr]
+  \,\times \SI{e-10}{erg.s^{-1}.cm^{-2}} \ ,
+\end{multline}
+where \(F_8\) is Spitzer IRAC \SI{8.0}{\um}, \(F_{24}\) is Spitzer
+MIPS \SI{23.7}{\um}, \(F_{12}\) and \(F_{22}\) are WISE bands 3 and 4,
+and \(F_{70}\) is Herschel PACS \SI{70}{\um}.  The weights are chosen
+so that the integral \(\int_0^\infty F_\nu \,d\nu\) is approximated by the sum
+\(\Sigma_k F_k\, \Delta\nu_k\), under the assumption that fluxes in shorter (e.g.,
+IRAC \SI{5.8}{\um}) and longer (e.g., PACS \SI{150}{\um}) wavebands
+are negligible.  Shell fluxes are converted to luminosities using the
+assumed distance to each source, and stellar luminosities are taken
+directly from K18 Table~2, based on spectroscopic classification and
+the calibrations of gravity and effective temperature from
+\citet{Martins:2005a}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K17-tau-comparison}
+  \caption{Comparison between shell-to-star luminosity ratios
+    calculated as described in the text (\(y\) axis) with those given
+    in K17 (\(x\) axis).  The blue dashed line signifies equality and
+    the gray band shows ratios between 1/2 and 2.}
+  \label{fig:k17-k18-comparison}
+\end{figure}
+
+In Figure~\ref{fig:k17-k18-comparison} we compare the \(\tau\) obtained
+using the shell luminosity as described above with that obtained using
+the luminosity ratios directly from K17 Table~5.  It can be seen that
+for the majority of sources the two measurements are consistent within
+a factor of two (gray band).  The four furthest-flung outliers can be
+understood as follows:
+\begin{description}
+\item[\textit{Source 67}] This has a very poor-quality spectral fit in
+  K17 (see lower left panel of their Fig.~12) and so 
+  \(F_{\text{IR}}\) is overestimated by them by a factor of 10.
+\item[\textit{Sources 341 and 342}] The spectral classes changed from
+  B2V in K17 to O9V and B1V, respectively, in K18, increasing the
+  derived \(L_*\), which lowers \(\tau\).
+\item[\textit{Source 411}] The luminosity class changed from Ib (K17)
+  to V (K18), so \(L_*\) has been greatly reduced, which increases
+  \(\tau\).
+\end{description}
+
+\subsection{Random uncertainties due to observational errors}
 \label{sec:rand-syst-uncert}
@@
 The fundamental observational quantities that go into determining
-\(\tau\) and \(\eta\shell\) for each source are distance, \(D\);
-stellar luminosity, \(L_*\); total infrared flux, \(F_{\text{IR}}\);
-and bow angular apex distance, \(\theta\).  From these, the shell
-radius and infrared luminosity are found as \(R_0 = \theta D\) and
+\(\tau\) and \(\eta\shell\) for each source are distance, \(D\); stellar
+luminosity, \(L_*\); total infrared flux, \(F_{\text{IR}}\); and bow
+angular apex distance, \(\theta\).  From these, the shell radius and
+infrared luminosity are found as \(R_0 = \theta D\) and
 \(L_{\text{IR}} = 4\pi D^2 F_{\text{IR}}\).  Rather than clutter the
@@
 corresponds to a factor of two increase (0.3~dex) in each quantity:
-\(D\), \(L_*\), \(F_{\text{IR}}\), and \(\theta\).  In
-\S~\ref{sec:uncert-estim-observ} we estimate the uncertainty in each
-observational quantity for the K18 sources.  We then combine these in
-\S~\ref{sec:comb-uncert-covar} to find the \(\pm 1~\sigma\) error
+\(D\), \(L_*\), \(F_{\text{IR}}\), and \(\theta\).  Below we estimate the
+uncertainty in each observational quantity for the K18 sources, which
+we then combine using the techniques described in
+Appendix~\ref{sec:comb-uncert-covar} to find the \(\pm 1~\sigma\) error
 ellipse, shown in blue in the figure.  It can be seen that
@@
 unimportant in determining whether a given source is wind-driven or
-radiation-driven, which depends only on \(\eta\shell/\tau\).  On the
-other hand, they do significantly effect the question of whether a
-source has a sufficiently high radiation parameter \(\Xi\) to possibly
-be a dust wave.
+radiation-driven, which depends only on \(\eta\shell/\tau\).  On the other
+hand, they do significantly effect the question of whether a source
+has a sufficiently high radiation parameter \(\Xi\) to possibly be a
+dust wave.
 
-\subsubsection{Systematic uncertainties due to assumed shell parameters}
+We include here uncertainty estimates for individual observational
+quantities that are used in deriving not only \(\tau\) and
+\(\eta\shell\), but also mass-loss rates, as discussed later in
+\S~\ref{sec:stellar-wind-mass}.
+
+\subsubsection{Distance}
+\label{sec:distance}
+
+Most sources are members of known high-mass clusters with distance
+uncertainties less than 20\% (0.08~dex). The only exception is
+Source~329 in Cygnus, for which the distance uncertainty is roughly a
+factor of~2 \citep{Kobulnicky:2018a}.
+
+\subsubsection{Stellar luminosity}
+\label{sec:stellar-luminosity}
+
+The stellar luminosity is determined from spectral classification,
+which makes it independent of distance.  Taking a \SI{2000}{K}
+dispersion in the effective temperature scale \citep{Martins:2005a}
+gives an uncertainty of 25\% in the luminosity, and adding in possible
+errors in gravity and the effect of binaries, we estimate a total
+uncertainty in \(L_*\) of 50\% (0.45~mag or 0.18~dex).
+
+\subsubsection{Shell flux and surface brightness}
+\label{sec:shell-flux-surface}
+
+We estimate the uncertainty in shell bolometric flux,
+\(F_{\text{IR}}\), by comparing two different methods: model fitting
+\citep{Kobulnicky:2017a} and a weighted sum of the 8, 24, and
+\SI{70}{\um} bands (eq.~[\ref{eq:total-ir-flux}]), giving a standard
+deviation of 17\% (0.07~dex).  To this, we add the estimate of 25\%
+for the effects of background subtraction uncertainties on individual
+photometric measurements \citep{Kobulnicky:2017a}. The absolute flux
+calibration uncertainty for both Herschel PACS \citep{Balog:2014a} and
+Spitzer MIPS \citep{Engelbracht:2007a} is less than 5\%, which is
+small in comparison. Combining the 3 contributions in quadrature gives
+a total uncertainty of 0.12~dex.  We adopt the same uncertainty for
+the \SI{70}{\um} surface brightness.
+
+\subsubsection{Angular sizes}
+\label{sec:angular-sizes}
+
+For the angular apex distance, \(\theta\), the largest uncertainty for
+well-resolved sources is due to the unknown inclination.
+\citet{Tarango-Yong:2018a} show that the dispersion in true to
+projected distances can introduce an uncertainty of \(30\%\)
+(0.11~dex) in unfavorable cases (e.g., their Fig.~26).  For 5 of the
+20 sources from \citet{Kobulnicky:2018a}, \(\theta\) is of order the
+Spitzer PSF width at \SI{24}{\um}, so the errors may be larger.
+
+\subsubsection{Stellar wind velocity}
+\label{sec:stell-wind-veloc}
+
+Although this is not strictly an observed quantity for the K18 sample,
+we will treat it as such since it is estimated per star, based on the
+spectral type.  K18 estimate 50\% uncertainty, and we adopt the same
+here (0.18~dex).
+
+\subsection{Systematic uncertainties due to assumed shell parameters}
 \label{sec:syst-uncert-due}
@@
 
-\subparagraph{Shell thickness}
+\subsubsection{Shell thickness}
+\label{sec:shell-thickness}
 We do not expect a great deal of variation in the shell thickness,
@@
 
-\subparagraph{Dust opacity}
+\subsubsection{Dust opacity}
+\label{sec:dust-opacity}
 The dust opacity will depend on the total dust-gas ratio and on the
@@
 
-\subparagraph{Shell gas temperature} For bows around O~stars, the
-shell temperature should be close to the photoionization equilibrium
-value of \(\approx \SI{e4}{K}\), since the post-shock cooling length
-is short in ambient densities above \SI{0.1}{cm^{-3}}
-(\S~\ref{sec:radi-cool-lengths}) and the shell does not trap the
-ionization front for ambient densities below \SI{e4}{cm^{-3}}
-(\S~\ref{sec:trapp-ioniz-front}).  For B~stars, on the other hand,
-these two density limits move closer together (cf.~the smaller gap
-between the blue and red lines in Figs.~\ref{fig:zones-v-n-plane}a and
-\ref{fig:B-supergiant}, as compared with \ref{fig:zones-v-n-plane}b
-and~c), making it more likely that a bow will lie in a different
-temperature regime.  The only source for which we have evidence that
-this occurs is LP~Ori, as discussed in the next section.
+\subsubsection{Shell gas temperature}
+\label{sec:shell-gas-temp}
+For bows around O~stars, the shell temperature should be close to the
+photoionization equilibrium value of \(\approx \SI{e4}{K}\), since the
+post-shock cooling length is short in ambient densities above
+\SI{0.1}{cm^{-3}} (\S~\ref{sec:radi-cool-lengths}) and the shell does
+not trap the ionization front for ambient densities below
+\SI{e4}{cm^{-3}} (\S~\ref{sec:trapp-ioniz-front}).  For B~stars, on
+the other hand, these two density limits move closer together (cf.~the
+smaller gap between the blue and red lines in
+Figs.~\ref{fig:zones-v-n-plane}a and \ref{fig:B-supergiant}, as
+compared with \ref{fig:zones-v-n-plane}b and~c), making it more likely
+that a bow will lie in a different temperature regime.  The only
+source for which we have evidence that this occurs is LP~Ori, as
+discussed in the next section.
 
-\subsubsection{Special treatment of particular sources}
+\subsection{Special treatment of particular sources}
 \label{sec:spec-treatm-part}
@@
 
-\subsection{Candidate radiation-supported bows}
+\section{Candidate radiation-supported bows}
 \label{sec:cand-radi-supp}
@@
 
-\subsection{Stellar wind mass-loss rates}
+% \subsection{Notes on particular sources}
+% \label{sec:notes-part-sourc}
+
+\subsection{Source~380, HD~53367, V750~Mon}
+\label{sec:hd-53367-v750}
+
+This is a Herbig Be star with spectral type B0V--B0III and mass 12 to
+\SI{15}{M_\odot}, which shows long-scale irregular photometric
+variability \citep{Tjin-A-Djie:2001a, Pogodin:2006a} together with
+cyclic radial velocity variations, which are interpreted as an
+eccentric binary with a \SI{5}{M_\odot} pre-main-sequence companion.
+It is located outside the solar circle and, although it was originally
+classified as part of the CMa OB association at about \SI{1}{kpc}
+\citep{Tjin-A-Djie:2001a}, more recent estimates put it much closer.
+K18 assume a distance of \SI{260}{pc}, based on Hipparcos measurements
+\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
+\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
+puts it closer still at \SI{140 \pm 30}{pc}.\footnote{%
+  Median and 90\% confidence interval, estimated from Bayesian
+  inference using an exponential density distribution with scale
+  length of \SI{1350}{pc} as a prior (see
+  \url{https://github.com/agabrown/astrometry-inference-tutorials/}). }
+
+\citet{Quireza:2006b} report a kinematic distance to the associated
+\hii{} region IC~2177 (G\num{223.70}\num{-1.90}) of \SI{1.6}{kpc},
+based an LSR radio recombination line velocity of \SI{+16}{km.s^{-1}}
+\citep{Quireza:2006a} and the outer Galaxy rotation curve of
+\citet{Brand:1993a}.  However, given the dispersion in peculiar
+velocities of star-forming clouds (\SIrange{7}{9}{km.s^{-1}},
+\citealp{Stark:1984a}) and likely streaming motions of the ionized gas
+(\(\approx \SI{10}{km.s^{-1}}\), \citealp{Matzner:2002a, Lee:2012a}),
+this is still consistent with a much smaller distance, which would
+also help in bringing the radio continuum-derived nebular electron
+density into agreement with the value (\(\approx \SI{100}{cm^{-3}}\))
+derived from the optical [\ion{S}{ii}] line ratio
+\citep{Hawley:1978a}.
+
+\citet{Fairlamb:2015a} derive a distance of \SI{340 \pm 60}{pc} from
+combining a spectroscopically determined effective temperature,
+gravity, and reddening with photometry and pre-main sequence
+evolutionary tracks.  They also determine a luminosity of \SI{13000
+  \pm 1000}{L_\odot}, which is only half that assumed by K18, and
+would have to be even lower to bring the photometry into concordance
+with the Gaia distance.  Alternatively, the luminosity could remain
+the same if the total-to-selective extinction ratio were higher than
+the \(R_V = 3.1\) assumed by \citet{Fairlamb:2015a}.  Taking
+\(R_V = 5.5\) instead, as in Orion, would give \(A_V = 3.34\) and a
+predicted \(V\) magnitude of 6.7 if we assume \(L_4 = 1.3\),
+\(D = \SI{170}{pc}\) (furthest distance in Gaia 90\% confidence
+interval) and \(T_{\text{eff}} = \SI{29.5}{kK}\)
+\citep{Fairlamb:2015a} for a bolometric correction of \(-2.86\)
+\citep{Nieva:2013a}.  The observed brightness varies between
+\(V = 6.9\) and 7.2, which is still at least 20\% fainter than
+predicted, but this is the best that can be achieved without rejecting
+the Gaia parallax distance entirely.
+
+A final sanity check can be performed by considering the free-free
+radio continuum flux of V750~Mon's surrounding \hii{} region, which,
+after converting to a luminosity, should be proportional to the total
+recombination rate in the nebula and therefore, assuming
+photoionization equilibrium and negligible dust absorption in the
+ionized gas, also proportional to the ionizing photon luminosity of
+the star.  \citet{Quireza:2006b} report a flux density of \SI{6}{Jy}
+at \SI{8.6}{Ghz} for G\num{223.70}\num{-1.90}, as compared with a flux
+density of \SI{260}{Jy} for the Orion Nebula using the same
+instrumental setup.  Assuming an ionizing photon luminosity of
+\(S_{49} = 1\) and distance \SI{410}{pc} for the ionizing Trapezium
+stars in Orion, therefore implies
+\(S_{49} = 0.0027 (D/\SI{140}{pc})^2\) for V750~Mon.  Using an
+ionizing flux of \SI{3.2e22}{cm^{-2}.s^{-1}} from the curves in Fig.~4
+of \citet{Sternberg:2003a}, this translates to a bolometric luminosity
+of \(L_4 = 0.96 (D/\SI{140}{pc})^2\), which is consistent with the
+\citet{Fairlamb:2015a} value if we take a distance towards the high
+end of the Gaia range.
+
+\subsection{Source 407, HD~93249}
+\label{sec:source-407}
+
+\input{app-cloudy-dust-heating}
+
+\section{Stellar wind mass-loss rates}
 \label{sec:stellar-wind-mass}
@@
 Mass loss rates - starting from \citet{Kobulnicky:2010a}
+
+\subsection{Mass loss determination from the \(\tau\)--\(\eta\shell\) diagram}
+\label{sec:mass-loss-determ}
+
+\subsection{Mass loss determination method of \protect\citet{Kobulnicky:2018a}}
+\label{app:bow-shock-data}
+
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
+%   \caption[K18 pair plot]{Pair plots of correlations between observed
+%     and derived parameters of bows from the \citep{Kobulnicky:2018a}
+%     sample.}
+%   \label{fig:K18-pairplot-edited}
+% \end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
+  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
+    identified in K18.  Red crosses show the emissivities given in
+    K18's Table~2 as a function of the radiation field \(U\), while
+    the solid gray line shows the emissivities that they claim to be
+    using from \citet{Draine:2007a}.  The dashed line shows the
+    emissivities that we believe they should have been using, which
+    correct for the marked difference in spectral energy distribution
+    between OB stars and the Galactic interstellar radiation field
+    (see App.~\ref{sec:grain-temp-emiss}).}
+  \label{fig:k18-emissivity}
+\end{figure}
+
+\newcommand\LOS{\ensuremath{_{\text{los}}}}
+K18 derive mass loss rates for their sources using a method that is
+different from the one that we employ in
+\S~\ref{sec:summary-discussion}.  Both methods are based on
+determining the stellar wind ram pressure that supports the bow shell,
+but K18 do so via the following steps:
+\begin{enumerate}[K1.]
+\item \label{K1} The line-of-sight mass column through the shell is
+  calculated by combining the peak surface brightness at \SI{70}{\um},
+  \(S_{70}\), with a theoretical emissivity per nucleon,
+  \(j_{70}(U)\), from \citet{Draine:2007a}:
+  \(\Sigma\LOS = S_{70} / \bar{m} j_{70}(U)\).  This depends on
+  knowledge of the stellar radiation field at the shell:
+  \(U \propto L_* / R_0^2\).
+\item \label{K2} The shell density is found from the line-of-sight
+  mass column using an observationally determined ``chord diameter'',
+  \(\ell\), which is assumed to be equal to the depth along the line
+  of sight: \(\rho\shell = \Sigma\LOS / \ell\).
+\item \label{K3} The internal ram pressure is equated to the external
+  ram pressure, which is found by assuming a stream velocity of
+  \SI{30}{km.s^{-1}} and a compression factor of 4 across the outer
+  shock:
+  \(P_{\text{stream}} = 0.25 \rho\shell \times
+  (\SI{30}{km.s^{-1}})^2\).
+\end{enumerate}
+There are clear parallels but also differences between steps
+K\ref{K1}--K\ref{K3} and our own steps P\ref{P1}--P\ref{P3}.  Our
+step~P\ref{P1} depends on the total observed infrared flux of the bow
+combined with an assumption about the grain opacity at ultraviolet
+wavelengths, while step~K\ref{K1} depends on the peak brightness at a
+single wavelength combined with an assumption about the grain
+emissivity at infrared wavelengths.  Our step~P\ref{P2} requires an
+assumption about the relative thickness of the shell, while
+step~K\ref{K2} is more directly tied to observations.\footnote{%
+  Note that there is a relation between the chord length, \(\ell\),
+  and the shell thickness, \(h\shell\), but this depends on the
+  planitude, \(\Pi\) of the bow shape \citep{Tarango-Yong:2018a}:
+  \( h\shell/R_0 = \Pi \bigl(1 - \{1 - [\ell/(2 \Pi R_0)]^2\}^{1/2}\bigr)\).  } %
+On the other hand, step~K\ref{K3} makes a roughly equivalent
+assumption about the shock compression factor,\footnote{%
+  In reality, the compression factor may be larger or smaller than 4,
+  depending on the efficiency of the post-shock cooling (see
+  \S~\ref{sec:radi-cool-lengths}).  For instance, for
+  \(v = \SI{30}{km.s^{-1}}\) as assumed by K18 and \(T = \SI{e4}{K}\),
+  one has a Mach number of \(\M_0 = 2.63\) and a compression factor of
+  2.8 for a non-radiative shock (by eq.~[\ref{eq:shock-n-jump}]) or a
+  factor of \(\M_0^2 =6.9\) for a strongly radiative one.  } %
+and a further assumption about the stream velocity. These assumptions
+are not necessary for our step~P\ref{P3}, but we do need to assume a
+value for the shell gas temperature.
+
+In principle, both methods are valid and their different assumptions
+and dependencies on observed quantities and auxiliary parameters
+provide an important cross check on one another.  However, as
+explained in detail in Appendix~\ref{sec:grain-temp-emiss}, the
+\(j_\nu(U)\) relation depends on the shape of the illuminating SED,
+which means that the \citet{Draine:2007a} models require modification
+when applied to grains around OB stars.  In addition, when attempting
+to replicate the K18 values of \(j_{70}\) we find that they only
+follow the \citet{Draine:2007a} values for \(U > \num{e4}\), tending
+to a constant value for weaker radiation fields.  The situation is
+summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
+directly from Table~2 of K18 are shown by red crosses, the values they
+claim to be using are shown by the gray solid line (this curve is
+consistent with that shown in K18 Fig.~2), and the values they
+\textit{should} have been using are shown by the gray dashed line.
+
+% If we replaced K3 with M3, then mass loss rates would be reduced by 1.86 across the board
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-mdot-Ux8-comparison}
+  \caption{Effects on mass-loss determination of correcting the K18
+    emissivities.  The mass-loss rates from Table~2 of K18 are shown
+    on the \(x\) axis, while the corrected values are shown on the
+    \(y\) axis.  Symbols are color coded by the strength of the
+    radiation field, \(U\). The corrected mass-loss rates are
+    predominantly lower by a factor of roughly 2.}
+  \label{fig:k18-mdot-corrected-emissivity}
+\end{figure}
+
+After correcting the \SI{70}{\um} emissivities in this way, we
+re-derive the mass loss rates, following the same steps as in K18,
+which are then used in Figure~\ref{fig:mass-loss-vs-luminosity}b of
+\S~\ref{sec:summary-discussion}.  The difference between these
+corrected mass-loss rates and those published in K18 is shown in
+Figure~\ref{fig:k18-mdot-corrected-emissivity}.  It can be seen that
+sources with \(U \approx \num{e3}\) (darker shading) are relatively
+unaffected but that sources with stronger radiation fields (lighter
+shading) have their mass-loss increasingly reduced, as could be
+surmised from Figure~\ref{fig:k18-emissivity}.  The average reduction
+is by a factor of about two.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-mdot-corrected-comparison-R0-edited}
+  \caption{Comparison of the two mass-loss methods: K18 corrected
+    method (\(x\) axis) versus our method (\(y\) axis).  Error bars on
+    the \(y\) axis correspond to a factor-three uncertainty in
+    \(\eta\shell\).  Sources for which these error bars overlap with
+    the RBW zone are only upper limits for the wind mass-loss rate,
+    and are indicated by faint symbols.}
+  \label{fig:mass-loss-comparison}
+\end{figure}
+
+Finally, in Figure~\ref{fig:mass-loss-comparison} we compare our own
+mass-loss determinations with the corrected K18 values.  The plot
+symbols are shaded according to the physical size of the bow, \(R_0\).
+It is apparent that the two methods are broadly in agreement on
+average, but there is considerable dispersion for individual objects,
+with only a weak correlation between the results of the two techniques
+(Pearson correlation coefficient \(r = 0.67\)).  Interestingly, the
+smaller bows (darker shading) show much better agreement than the
+larger bows (lighter shading).  The five bows with
+\(R_0 > \SI{0.4}{pc}\) (339, 344, 369, 381, 382) show a difference of
+nearly an order of magnitude, in the sense that our method
+consistently predicts lower mass-loss rates than K18.  For a further
+five of the sources (380, 407, 409, 410, 411), our method gives only
+an upper limit to the wind mass-loss rate if one assumes a
+factor-three uncertainty in \(\eta\shell\), and these bows are among
+the smallest in the sample, all with \(R_0 < \SI{0.1}{pc}\).
 

### 2019-03-18 papers/Papers1234/app-cloudy-dust-heating.tex
Major surgery on Paper III to get stuff out of appendices
Consistency fixes for Paper III complete to end of sec 5

@@
-\section{Grain temperature and mid-infrared emissivity}
+\section{Mid-infrared grain emissivity}
 \label{sec:grain-temp-emiss}
+
+In preparation for our discussion of different wind mass loss
+diagnostic methods below, in this section we calculate the grain
+emissivity predicted by models of dust heated by a nearby OB star.  We
+use the same simulations that we employed in \S~4.2 of Paper~II,
+% XREF: Paper II \ref{sec:cloudy-models-dust}
+which employ the plasma physics code Cloudy \citep{Ferland:2013a,
+  Ferland:2017a}.  In summary, simulations of spherically symmetric,
+steady-state, constant density \hii{} regions were carried out for
+four different stellar types from B1.5 to O5 (Table~2 of Paper~II), a
+range of gas densities from \SIrange{1}{e4}{cm^{-3}}, and using
+Cloudy's default ``ISM'' graphite/silicate dust mixture with 10 size
+bins from \SIrange{0.005}{0.25}{\um}.
 
@@
     \(U\), in units of the interstellar radiation field in the solar
-    neighborhood.  Line types and colors are as in
-    Fig.~\ref{fig:phi-vs-Xi} and correspond to a variety of stellar
-    spectral shapes, gas densities, and grain species.}
+    neighborhood.  Line types and colors correspond to a variety of
+    stellar spectral shapes, gas densities, and grain species.  Dashed
+    lines show carbon grains, solid lines show silicate grains, with
+    line thickness increasing and opacity decreasing with increasing
+    grain size.  Stellar spectral types are O5\,V (blue), O9\,V
+    (orange), B1.5\,V (purple), and B0.7\,Ia (green), with lighter
+    shades denoting higher gas densities. }
   \label{fig:grain-T-vs-U}
@@
 Figure~\ref{fig:grain-T-vs-U} shows equilibrium grain temperatures for
-the Cloudy models discussed in Appendix~\ref{sec:cloudy-models-dust}
-as a function of the nominal energy density of the radiation field,
-\(U = u / u\mmp \), where \(u = L / 4 \pi R^2 c\) and \(u\mmp\) is the
-energy density of the interstellar radiation field for
-\(\lambda < \SI{8}{\um}\) in the solar neighborhood
+these Cloudy models as a function of the nominal energy density of the
+radiation field, \(U = u / u\mmp \), where \(u = L / 4 \pi R^2 c\) and
+\(u\mmp\) is the energy density of the interstellar radiation field
+for \(\lambda < \SI{8}{\um}\) in the solar neighborhood
 \citep{Mathis:1983a}:
@@
 \end{equation}
-The tight relationship seen in figure~\ref{fig:grain-T-vs-U} between
+The tight relationship seen in Figure~\ref{fig:grain-T-vs-U} between
 \(T\) and \(U\) is evidence for the dominance of stellar radiative
-heating (see \S~\ref{sec:unimp-other-heat} below), while the variation
-about the mean relation is mainly due to differences in grain size and
-composition, with smaller grains and graphite grains being relatively
-hotter.  The downward hooks seen on the left end of each simulation's
-individual curve are due to the fact that our calculation of \(U\)
-does not account for internal absorption, which starts to become
-important near the ionization front.
+heating, which we justify on theoretical grounds in
+\S~\ref{sec:unimp-other-heat} below.  The variation about the mean
+relation is mainly due to differences in grain size and composition,
+with smaller grains and graphite grains being relatively hotter.  The
+downward hooks seen on the left end of each simulation's individual
+curve are due to the fact that our calculation of \(U\) does not
+account for internal absorption, which starts to become important near
+the ionization front.
 
@@
   \includegraphics[width=\linewidth]{figs/grain-j70-vs-U-edited}
-  \caption{Grain emissivity at \SI{70}{\um} for all Cloudy models
-    (lines colored as in Fig.~\ref{fig:drift-gn}), compared with grain
-    models from \citet{Draine:2007a} (dark gray symbols), which assume
-    illumination by a scaled interstellar radiation field, which has a
-    SED with a very different shape from that of an OB star, see
-    Fig.~\ref{fig:sed-comparison}.  }
+  \caption{Grain emissivity at \SI{70}{\um} for all Cloudy models,
+    with lines colored as in Fig.~\ref{fig:grain-T-vs-U}, but without
+    the variation in line type and thickness since emissivity is
+    integrated over all grain types and sizes.  For comparison, the
+    emissivity from the grain models of \citet{Draine:2007a} are shown
+    as dark gray symbols, which assume illumination by a scaled
+    interstellar radiation field with a SED with a very different
+    shape from that of an OB star, see Fig.~\ref{fig:sed-comparison}.
+    The light gray symbols show the effect of using an 8 times higher
+    \(U\) with the \citeauthor{Draine:2007a} models, which
+    approximately compensates for this difference in SED.  }
   \label{fig:grain-j70}
@@
 star SEDs, which are dominated by the FUV and EUV bands.  Since the
-grain absorption opacity is much higher at UV wavelengths than in the
-visible/IR (see Fig.~\ref{fig:cloudy-ism-dust-opacity}), the effective
-grain heating efficiency of the OB star SED is correspondingly higher.
-The light gray symbols show the effect on the \citet{Draine:2007a}
-models of multiplying the radiation field by a factor of \num{8} in
-order to offset this difference in efficiency, which can be seen to
-bring them into close agreement with the Cloudy models.  A further
-difference is that the \citet{Draine:2007a} model includes small PAH
-particles, which we do not include in our Cloudy models, since they
-are believed to be largely absent in photoionized regions
-\citep{Giard:1994a, Lebouteiller:2011a}.  However, this only effects
-the emissivity at shorter mid-infrared wavelengths \(< \SI{20}{\um}\).
+grain absorption opacity is substantially higher at UV wavelengths
+than in the visible/IR (see Fig.~6 of Paper~II),
+% XREF: Paper II \ref{fig:cloudy-ism-dust-opacity}
+the effective grain heating efficiency of the OB star SED is
+correspondingly higher.  The light gray symbols show the effect on the
+\citet{Draine:2007a} models of multiplying the radiation field by a
+factor of \num{8} in order to offset this difference in efficiency,
+which can be seen to bring them into close agreement with the Cloudy
+models.  A further difference is that the \citet{Draine:2007a} model
+includes small PAH particles, which we do not include in our Cloudy
+models, since they are believed to be largely absent in photoionized
+regions \citep{Giard:1994a, Lebouteiller:2011a}.  However, this only
+effects the emissivity at shorter mid-infrared wavelengths
+\(< \SI{20}{\um}\).
 
@@
 In terms of the characteristic parameters introduced in
-\S~\ref{sec:depend-stell-type} the dimensionless radiation field becomes
+\S~\ref{sec:energy-trapp-vers} the dimensionless radiation field
+becomes
 \begin{equation}
@@
   \label{eq:U-from-ambient}
-  U = 3.01 \, n \, v_{10}^2 / x^2 \ , 
+  U = 3.01 \, n_\infty \, v_{10}^2 / x^2 \ , 
 \end{equation}
-where \(x = R_0/R_*\) is given by equation~\eqref{eq:x-cases}.  It can
-also be related to the radiation parameter \(\Xi\), defined in
-equation~\eqref{eq:Xi-Prad-over-Pgas}, as
+where \(x = R_0/R_*\) is given by Paper~I's equation~(12).
+% XREF: Paper I \eqref{eq:x-cases}
+It can also be related to the radiation parameter \(\Xi\), defined in
+Paper~II's equation~(23), as
+% XREF: Paper II \eqref{eq:Xi-Prad-over-Pgas}
 \begin{equation}
@@
 \item The post-shock gas must radiate efficiently with a cooling
-  length less than the bow size, see \S~\ref{sec:radi-cool-lengths}.
-  This is satisfied for all but the lowest densities (see
-  Fig.~\ref{fig:zones-v-n-plane}).
+  length less than the bow size, see \S~3.2 of Paper~I.\@
+  % XREF Paper I \ref{sec:radi-cool-lengths}
+  This is satisfied for all but the lowest densities (Paper~I's
+  Fig.~2).
+  % XREF Paper I \ref{fig:zones-v-n-plane}
 \item A significant fraction of the shock energy must be radiated by
@@
   \SI{e6}{K}, which requires a stream velocity
-  \(v > \SI{200}{km.s^{-1}}\) \citep{Draine:1981a}.  This also
+  \(v_\infty > \SI{200}{km.s^{-1}}\) \citep{Draine:1981a}.  This also
   coincides with the range of shock velocities where the smaller
@@
 It turns out that the third condition is the most stringent, so we
-will consider it in detail.  The kinetic energy flux through the outer shock for an ambient stream of density \(\rho\) and velocity \(v\) is
+will consider it in detail.  The kinetic energy flux through the outer shock for an ambient stream of density \(\rho_\infty\) and velocity \(v_\infty\) is
 \begin{equation}
   \label{eq:Fkin}
-  F\ke = \tfrac12 \rho v^3 = \tfrac12 P\shell v \ , 
+  F\ke = \tfrac12 \rho_\infty v_\infty^3 = \tfrac12 P\shell v_\infty \ , 
 \end{equation}
@@
 pressure in the WBS case can be equated to the ram pressure of the
-internal stellar wind (see \S~\ref{sec:three-bow-regimes}), so that
-the ratio of the two energy fluxes is
+internal stellar wind (see
+% XREF Paper I \ref{sec:three-bow-regimes}
+\S~2.1 of Paper~I), so that the ratio of the two energy fluxes is
 \begin{equation}
   \label{eq:F-ratio-shock}
-  \frac{F\ke}{F\trap} = \frac12 \frac{\eta\wind}{\tau} \frac{v}{c} \ .
+  \frac{F\ke}{F\trap} = \frac12 \frac{\eta\wind}{\tau} \frac{v_\infty}{c} \ .
 \end{equation}
-An upper limit to the stellar wind momentum efficiency \(\eta\wind\)
-is the shell momentum efficiency \(\eta\shell\) that is derived
-observationally in \S~\ref{sec:summary-discussion}, where it is found
-that \(\eta\shell / \tau < 30\) for all sources considered.  Therefore,
-for a stream velocity \(v = \SI{200}{km.s^{-1}}\), we have
+An upper limit to the stellar wind momentum efficiency \(\eta\wind\) is
+the shell momentum efficiency \(\eta\shell\) that is derived
+observationally in \S~\ref{sec:energy-trapp-vers}, where it is found
+that \(\eta\shell / \tau < 30\) for all sources considered.  Therefore, for
+a stream velocity \(v_\infty = \SI{200}{km.s^{-1}}\), we have
 \(F\ke/F\trap < 0.01\) and the shock-excited dust emission is still
-negligible.  Only in stars with \(v > \SI{1000}{km.s^{-1}}\) would the
-shock emission start to be significant, and such hyper-velocity stars
-\citep{Brown:2015a} do not show detectable bow shocks.
+negligible.  Only in stars with \(v_\infty > \SI{1000}{km.s^{-1}}\) would
+the shock emission start to be significant, and such hyper-velocity
+stars \citep{Brown:2015a} do not show detectable bow shocks.
 
@@
 that decelerates the stellar wind will have a velocity of
-\SIrange{1000}{3000}{km.s^{-1}} and therefore might have a
-significant kinetic energy flux by eq.~\eqref{eq:F-ratio-shock}.
-However, the stellar wind from hot stars will be free of
-dust,\footnote{%
+\SIrange{1000}{3000}{km.s^{-1}} and therefore might have a significant
+kinetic energy flux by eq.~\eqref{eq:F-ratio-shock}.  However, the
+stellar wind from hot stars will be free of dust,\footnote{%
   With the exception of Wolf-Rayet colliding wind binary systems
@@
 the contact/tangential discontinuity and deposit their energy in the
-dusty plasma of the shocked ambient stream.  This is not possible
-because the Larmor radius (see \S~\ref{sec:magn-effects-grain}) of a
-\SI{3000}{km.s^{-1}} proton in a \SI{1}{\micro G} field is only
+dusty plasma of the shocked ambient stream in order for this source of
+energy to contribute to the grain emission.  This is not possible
+because the Larmor radius (see \S~5 of Paper~II)
+% XREF Paper II \ref{sec:magn-effects-grain}
+of a \SI{3000}{km.s^{-1}} proton in a \SI{1}{\micro G} field is only
 \SI{3e10}{cm}, which is millions of times smaller than typical bow
 sizes.  The magnetic field in the outer shell is unlikely to be
-smaller than \(\approx n^{1/2} \si{\micro G}\), given that Alfvén
-speeds of \SI{2}{km.s^{-1}} are typical of photoionized regions
-(cf.~eq.~[\ref{eq:alfven}]) and if the density were much lower than
+smaller than \(\approx n^{1/2} \si{\micro G}\), given that Alfvén speeds of
+\SI{2}{km.s^{-1}} are typical of photoionized regions (cf.~Paper~II's
+eq.~[40])
+% XREF Paper II \\ref{eq:alfven}
+and if the density were much lower than
 \SI{1}{cm^{-3}}, then the scale of the bow would be commensurately

### 2019-03-18 papers/Papers1234/bs-bw-dw-03.tex
Consistency fixes for Paper III complete to end of sec 5

@@
 
-In \citet{Henney:2019a, Henney:2019b} (Paper~I and Paper~II) we
+In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
 presented a taxonomy of stellar bows, which we divided into
@@
 
-In Paper~I we derived expressions for the bow radius \(R_0\)in each of
+In Paper~I we derived expressions for the bow radius \(R_0\) in each of
 the three well-coupled regimes as a function of the parameters of the

### 2019-03-18 papers/Papers1234/sec-observational-diagnostics.tex
Consistency fixes for Paper III complete to end of sec 5

@@
     angular size \(\theta\).  Lines and shading indicate different
-    theoretical bow regimes (see \S\S~\ref{sec:strong-gas-grain} and
-    \ref{sec:imperf-coupl-betw}).  The dashed blue diagonal line
-    corresponds to radiation-supported bows, while the upper left
-    region corresponds to wind-supported bows.  The upper right corner
-    (purple) corresponds to optically thick bow shocks, while the
-    lower left corner (yellow) is the region where grain--gas
-    separation \textit{may} occur, leading to a potential dust wave.
-    However, the existence of a dust wave in this region is not
-    automatic, since it only includes one of the four necessary
-    conditions (\S~\ref{sec:exist-cond-separ} and
-    \S~\ref{sec:grain-traj-with}). The lower-right region is strictly
-    forbidden, except in case of violation of the assumption that dust
-    heating be dominated by stellar radiation. }
+    theoretical bow regimes (see Paper~I and Paper~II).  The dashed
+    blue diagonal line corresponds to radiation-supported bows, while
+    the upper left region corresponds to wind-supported bows.  The
+    upper right corner (purple) corresponds to optically thick bow
+    shocks, while the lower left corner (yellow) is the region where
+    grain--gas separation \textit{may} occur, leading to a potential
+    dust wave.  However, the existence of a dust wave in this region
+    is not automatic, since it only includes one of the four necessary
+    conditions (\S\S~4.4 and 5.1 of Paper~II). The lower-right region
+    is strictly forbidden, except in case of violation of the
+    assumption that dust heating be dominated by stellar radiation. }
   \label{fig:All-sources-eta-tau}
@@
 photon momentum is available to support the shell (see
-\S~\ref{sec:three-bow-regimes}).  But the same photons also heat the
+\S~2.1 of Paper~I).  But the same photons also heat the
 dust grains in the bow, which re-radiate that energy predominantly at
@@
 \end{equation}
-where the last approximate equality holds if \(\tau \ll 1\) and the
-shell emission covers one hemisphere.\footnote{%
-  The \(\tau\) of \S~\ref{sec:three-bow-regimes} is not exactly the
-  same as the \(\tau\) of equation~\eqref{eq:tau-empirical}, but is
-  larger by a factor of
+where the last approximate equality holds if \(\tau \ll 1\) and the shell
+emission covers one hemisphere.  Note that the \(\tau\) of Paper~I is not
+exactly the same as the \(\tau\) of equation~\eqref{eq:tau-empirical},
+but is larger by a factor of
 \(Q_P / Q_{\text{abs}} = 1 + \varpi (1 - g)/(1 - \varpi)\), where
-  \(\varpi\) is the grain albedo and \(g\) the scattering asymmetry
-  (see App.~\ref{sec:gas-free-bow}).} %
+\(\varpi\) is the grain albedo and \(g\) the scattering asymmetry.
+This is plotted in Figure~6a of Paper~II for Cloudy's default ISM
+grain mixture (see \S~\ref{sec:grain-temp-emiss} below), where it can
+be seen that \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at
+EUV/FUV wavelengths (\(\lambda = \text{\SIrange{0.05}{0.2}{\um}}\)), so the
+correction is small.
 
@@
   the mass column if the shell thickness is known:
-  \(\rho\shell = \Sigma / h\shell\).  In the absence of other
-  information, a fixed fraction of the shell radius can be used.  In
-  particular, we normalize by a typical value of
-  one~quarter\footnote{%
-    This corresponds to a Mach number \(\M_0 = \surd 3\) if the stream
-    shock is radiative, or \(\M_0 \gg 1\) if non-radiative (see
-    \S~\ref{sec:radi-cool-lengths}).  Further discussion is given in
-    Appendix~\ref{app:bow-shock-data}} %
-  the star--apex distance: \(h_{1/4} = h\shell / (0.25 R_0)\).
+  \(\rho\shell = \Sigma / h\shell\).  In the absence of other information, a
+  fixed fraction of the shell radius can be used.  In particular, we
+  normalize by a typical value of one~quarter the star--apex distance:
+  \(h_{1/4} = h\shell / (0.25 R_0)\).  This corresponds to a Mach
+  number \(\M_0 = \surd 3\) if the stream shock is radiative, or
+  \(\M_0 \gg 1\) if non-radiative (see \S~3.2 of Paper~I). Further
+  discussion is given in \S~\ref{app:bow-shock-data} below. 
 \item \label{P3} Finally, the pressure (\si{dyne.cm^{-2}}) follows by
@@
 magnetic support (\(v\alfven \ll \sound\)) and written the stellar
-luminosity and shell parameters in terms of typical values, as in
-\S~\ref{sec:depend-stell-type}.  Note that the shell momentum
-efficiency is simply the reciprocal of the radiation parameter of
-equation~\eqref{eq:Xi-Prad-over-Pgas}:
+luminosity and shell parameters in terms of typical values, which we
+summarize below.  Note that the shell momentum efficiency is simply
+the reciprocal of the radiation parameter from Paper~II's equation~(23):
 \(\eta\shell = \Xi\shell^{-1}\), which provides yet a third use for
 \(\eta\shell\), since \(\Xi\) is paramount in determining whether the
-grains and gas remain well-coupled (see
-\S~\ref{sec:exist-cond-separ}).
+grains and gas remain well-coupled (see \S~4.4 of Paper~II).
+
+In this section and the remainder of the paper, we employ
+dimensionless versions of the stellar bolometric luminosity, \(L_*\),
+wind mass-loss rate, \(\dot{M}\), and terminal velocity, \(V\wind\),
+together with the ambient stream's mass density, \(\rho\), relative
+velocity \(v_\infty\), and effective dust opacity, \(\kappa\).  These are
+defined as follows:
+\begin{align*}
+  % \label{eq:stellar-parameters}
+  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
+  V_3 &= V\wind / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
+  L_4 &= L_* / \bigl(\SI{e4}{L_\odot}\bigr) \\
+  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
+  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
+  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
+\end{align*}
+where \(\bar{m}\) is the mean mass per hydrogen nucleon
+(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
+abundances).
 
@@
 In Figure~\ref{fig:All-sources-eta-tau} we show the resultant
-diagnostic diagram: \(\eta\shell\) versus \(\tau\).  The horizontal
-axis shows the fraction of the stellar radiative \emph{energy} that is
+diagnostic diagram: \(\eta\shell\) versus \(\tau\).  The horizontal axis
+shows the fraction of the stellar radiative \emph{energy} that is
 reprocessed by the bow shell, while the vertical axis shows the
@@
 (DW, RBW, or RBS, or cases) should lie on the diagonal line
-\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where
-we have used the ratio of grain radiation pressure efficiency to
-absorption efficiency found in the FUV band for the dust mixture shown
-in Figure~\ref{fig:cloudy-ism-dust-opacity}.  Wind-supported bows
-should lie above this line and no bows should lie below the
-\(\eta\shell = \tau\) line, since \(Q_P\) cannot be smaller than
-\(Q_{\text{abs}}\).
+\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where we have used
+the ratio of grain radiation pressure efficiency to absorption
+efficiency found in the FUV band for the dust mixture shown in
+Paper~II's Figure~6.  Wind-supported bows should lie above this line
+and no bows should lie below the \(\eta\shell = \tau\) line, since
+\(Q_P\) cannot be smaller than \(Q_{\text{abs}}\).
 
-We have calculated \(\eta\shell\) and \(\tau\) using the
-above-described methods for the 20 mid-infrared sources studied by
+We have calculated \(\eta\shell\) and \(\tau\) using the above-described
+methods for the 20 mid-infrared sources studied by
 \citet{Kobulnicky:2018a} (K18) and plotted them on our diagnostic
 diagram.  Details of our treatment of this observational material are
-provided in Appendix~\ref{app:bow-shock-data}.  In order to expand the
-range of physical conditions, we have included three additional
-sources (data in Table~\ref{tab:observations}): bows around \thD{}
+provided in the following subsection.  In order to expand the range of
+physical conditions, we have included three additional sources (data
+in Table~\ref{tab:observations}): bows around \thD{}
 \citep{Smith:2005a} and LP~Ori \citep{ODell:2001c} in the Orion
 Nebula, which show larger optical depths, plus the inner bow around
-\(\sigma\)~Ori, which illuminates the Horsehead Nebula and has
-previously been claimed to be a dust wave \citep{Ochsendorf:2014b,
+\(\sigma\)~Ori, which illuminates the Horsehead Nebula and has previously
+been claimed to be a dust wave \citep{Ochsendorf:2014b,
   Ochsendorf:2015a}.  Details of the observations of these additional
@@
 sources, reliable distances and spectral classifications are provided
-(Table~5 of K17 and Tables~1 and~2 of K18), and these are used in
-\S~\ref{sec:summary-discussion}, where we discuss the
-\(\tau\)--\(\eta\) diagnostic diagram.  In this appendix, we outline our
-treatment and analysis of the data in these catalogs, which differs in
-some important respects from that of the original authors.
+in Table~5 of K17 and Tables~1 and~2 of K18. In this section, we
+outline how we obtain \(\tau\) and \(\eta\shell\) from the data in these
+catalogs, while further aspects of the \citeauthor{Kobulnicky:2018a}
+material are discussed in \S~\ref{app:bow-shock-data}.
 
@@
 corresponds to a factor of two increase (0.3~dex) in each quantity:
-\(D\), \(L_*\), \(F_{\text{IR}}\), and \(\theta\).  Below we estimate the
-uncertainty in each observational quantity for the K18 sources, which
-we then combine using the techniques described in
-Appendix~\ref{sec:comb-uncert-covar} to find the \(\pm 1~\sigma\) error
-ellipse, shown in blue in the figure.  It can be seen that
-observational uncertainties in \(\tau\) and \(\eta\shell\) are highly
-correlated: the dispersion is \SI{0.7}{dex} in the product
-\(\eta\shell \tau\) but only \SI{0.16}{dex} in the ratio
-\(\eta\shell/\tau\), with stellar luminosity errors dominating in both
-cases.  Observational uncertainties are therefore relatively
-unimportant in determining whether a given source is wind-driven or
-radiation-driven, which depends only on \(\eta\shell/\tau\).  On the other
-hand, they do significantly effect the question of whether a source
-has a sufficiently high radiation parameter \(\Xi\) to possibly be a
-dust wave.
-
-We include here uncertainty estimates for individual observational
-quantities that are used in deriving not only \(\tau\) and
-\(\eta\shell\), but also mass-loss rates, as discussed later in
-\S~\ref{sec:stellar-wind-mass}.
+\(D\), \(L_*\), \(F_{\text{IR}}\), and \(\theta\).  We now calculate
+uncertainty estimates for individual observational quantities that are
+used in deriving not only \(\tau\) and \(\eta\shell\), but also mass-loss
+rates, as discussed later in \S~\ref{sec:stellar-wind-mass}.
 
@@
 
+\subsubsection{Combined effect of uncertainties on the
+  \(\tau\)--\(\eta\shell\) diagram}
+\label{sec:comb-effect-uncert}
+
+Assuming that the uncertainty in each observational quantity is
+independent, we can now combine them using the techniques described in
+Appendix~\ref{sec:comb-uncert-covar} to find the \(\pm 1~\sigma\) error
+ellipse, shown in blue in the figure.  It can be seen that
+observational uncertainties in \(\tau\) and \(\eta\shell\) are highly
+correlated: the dispersion is \SI{0.7}{dex} in the product
+\(\eta\shell \tau\) but only \SI{0.16}{dex} in the ratio
+\(\eta\shell/\tau\), with stellar luminosity errors dominating in both
+cases.  Observational uncertainties are therefore relatively
+unimportant in determining whether a given source is wind-driven or
+radiation-driven, which depends only on \(\eta\shell/\tau\).  On the other
+hand, they do significantly effect the question of whether a source
+has a sufficiently high radiation parameter \(\Xi\) to possibly be a
+dust wave.
+
 \subsection{Systematic uncertainties due to assumed shell parameters}
@@
 A further source of uncertainty arises from the parameters of the
-shocked shell that are assumed in steps P\ref{P1}--P\ref{P3}, namely
+shocked shell that are assumed in steps P\ref{P1}--P\ref{P3}. Namely,
 the relative shell thickness, \(h\shell/R_0\), the ultraviolet grain
@@
 than we are assuming.  This occurs at
-\(v \approx \SI{60}{km.s^{-1}}\), corresponding to the peak in the
-cooling curve at \SI{e5}{K} (see \S~\ref{sec:radi-cool-lengths}),
+\(v \approx \SI{60}{km.s^{-1}}\), corresponding to the peak in the cooling
+curve at \SI{e5}{K} (see \S~3.2 of Paper~I),
+% XREF: Paper I \S~\ref{sec:radi-cool-lengths}
 since the thickness is set by the cooling length at higher speeds.  In
@@
 estimate are large and different results are obtained in other
-regions, such as W3(A) \citep{Salgado:2012a}.
+regions, such as W3(A) \citep{Salgado:2012a}.  It is even possible
+that the FUV dust opacity may be larger than the ISM value if the
+abundance of very small grains is enhanced through radiative torque
+disruption of larger grains \citep{Hoang:2018a}.
 
@@
 post-shock cooling length is short in ambient densities above
-\SI{0.1}{cm^{-3}} (\S~\ref{sec:radi-cool-lengths}) and the shell does
-not trap the ionization front for ambient densities below
-\SI{e4}{cm^{-3}} (\S~\ref{sec:trapp-ioniz-front}).  For B~stars, on
-the other hand, these two density limits move closer together (cf.~the
-smaller gap between the blue and red lines in
-Figs.~\ref{fig:zones-v-n-plane}a and \ref{fig:B-supergiant}, as
-compared with \ref{fig:zones-v-n-plane}b and~c), making it more likely
-that a bow will lie in a different temperature regime.  The only
-source for which we have evidence that this occurs is LP~Ori, as
+\SI{0.1}{cm^{-3}} (\S~3.2 of Paper~I)
+% XREF: Paper I \ref{sec:radi-cool-lengths}
+and the shell does not trap the ionization front for ambient densities
+below \SI{e4}{cm^{-3}} (\S~3.1 of Paper~I).
+% XREF: Paper I \\ref{sec:trapp-ioniz-front}
+For B~stars, on the other hand, these two density limits move closer
+together (cf.~the smaller gap between the blue and red lines in
+% XREF: Paper I \ref{fig:zones-v-n-plane}a
+% XREF: Paper I \ref{fig:B-supergiant}
+% XREF: Paper I \ref{fig:zones-v-n-plane}bc
+Paper~I's Figs.~2a and 4, as compared with 2b and~c), making it more
+likely that a bow will lie in a different temperature regime.  The
+only source for which we have evidence that this occurs is LP~Ori, as
 discussed in the next section.
@@
 Four sources are sufficiently close to the diagonal line
-\(\eta\shell = 1.25 \tau\) in Figure~\ref{fig:All-sources-eta-tau}
-that they should be treated as potential candidates for
-radiation-supported bows. These are K18 sources~380 (HD~53367,
-V750~Mon) and 407 (HD~93249 in Carina) plus \thD{} and LP~Ori.  Of the
-four, source 380 is the only one that is also a candidate for
-grain-gas decoupling.  Details of some of these sources are presented
-in \S~\ref{sec:notes-part-sourc}, where for source~380 we show that
-reducing both luminosity and distance by a factor of roughly 2 with
-respect to the values used by K18 would provide a better fit to the
-totality of observational data.  However, the ratio
-\(\eta\shell /\tau\) is proportional to \(D / L_*\) so it would not be
-affected by such an adjustment and the bow remains
-radiation-supported.  On the other hand \(\eta\shell\) (proportional
-to \(D / L_*^2\)) would increase by 2, making the classification as
-dust wave candidate more marginal.
+\(\eta\shell = 1.25 \tau\) in Figure~\ref{fig:All-sources-eta-tau} that they
+should be treated as potential candidates for radiation-supported
+bows. These are K18 sources~380 (HD~53367, V750~Mon) and 407 (HD~93249
+in Carina) plus \thD{} and LP~Ori.  Of the four, source 380 is the
+only one that is also a candidate for grain-gas decoupling.  Further
+details of the two K18 sources are presented in following subsections,
+where for source~380 we show that reducing both luminosity and
+distance by a factor of roughly 2 with respect to the values used by
+K18 would provide a better fit to the totality of observational data.
+However, the ratio \(\eta\shell /\tau\) is proportional to \(D / L_*\) so it
+would not be affected by such an adjustment and the bow remains
+radiation-supported.  On the other hand \(\eta\shell\) (proportional to
+\(D / L_*^2\)) would increase by 2, making the classification as dust
+wave candidate more marginal.
 
@@
 \label{sec:source-407}
+
+TODO
 

### 2019-03-18 papers/Papers1234/sec-observational-diagnostics.tex
Start on mass loss section of Paper III

@@
 
-Third method used by \citet{Gvaramadze:2012a}, relies on measurements
-of \hii{} region and bow. Only works for isolated stars.
+Various methods have been proposed to derive stellar wind mass-loss
+rates from observations of stellar bow shocks \citetext{for example,
+  \citealp{Kobulnicky:2010a, Gvaramadze:2012a, Kobulnicky:2018a}}.  In
+this section, we will show how the \(\tau\)--\(\eta\shell\) diagram can be
+used to derive the mass-loss rate for bows in the wind-supported
+regime.  We then compare our method with the method used by
+\citet{Kobulnicky:2018a}, which is a refinement of that originally
+proposed in \citet{Kobulnicky:2010a}.  The method used by
+\citet{Gvaramadze:2012a} uses combined measurements of the bow shock
+and the surrounding \hii{} region.  It has the advantage of depending
+on fewer free parameters than the other methods, but can only be used
+in the case of isolated stars, whereas the majority of the sources
+considered here are in cluster environments.
 
-Mass loss rates - starting from \citet{Kobulnicky:2010a}
-
-\subsection{Mass loss determination from the \(\tau\)--\(\eta\shell\) diagram}
+\subsection{Mass loss determination from the \boldmath \(\tau\)--\(\eta\shell\) diagram}
 \label{sec:mass-loss-determ}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
+  \caption{Wind mass-loss rates as a function of stellar luminosity,
+    derived from (a)~our trapped energy/momentum method and (b)~the
+    grain emissivity method of \citet{Kobulnicky:2018a}, with
+    corrections as described in our Appendix~\ref{app:bow-shock-data}.
+    Circle symbols show the sources from K18, colored according to the
+    stellar effective temperature (see key at far right). In panel a,
+    squares show two of our additional sources
+    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
+    given for sources that lie close to the radiation-supported line
+    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
+    symbols and downward-pointing arrows.  Sources that lie less than
+    a factor of three above the line have enhanced downward
+    uncertainties and are also shown by slightly fainter symbols.  For
+    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
+    luminosities of the triple OB system Aa, Ab, and B
+    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
+    the luminosity of only the most massive component Aa.  Lines show
+    the predictions of stellar wind models: red lines are the commonly
+    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
+    (dashed), and supergiants (dotted), while black lines show
+    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
+    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
+    mass-loss measurements from NUV lines for weak-wind O~dwarfs
+    \citep{Marcolino:2009a}, while the green plus symbol shows the
+    measurement from infrared H recombination lines for \(\sigma\)~Ori
+    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
+    to observational uncertainties (lower right) and assumed shell
+    parameters (upper left).}
+  \label{fig:mass-loss-vs-luminosity}
+\end{figure*}
 
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
-  \caption{Wind mass-loss rates as a function of stellar luminosity,
-    derived from (a)~our trapped energy/momentum method and (b)~the
-    grain emissivity method of \citet{Kobulnicky:2018a}, with
-    corrections as described in our Appendix~\ref{app:bow-shock-data}.
-    Circle symbols show the sources from K18, colored according to the
-    stellar effective temperature (see key at far right). In panel a,
-    squares show two of our additional sources
-    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
-    given for sources that lie close to the radiation-supported line
-    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
-    symbols and downward-pointing arrows.  Sources that lie less than
-    a factor of three above the line have enhanced downward
-    uncertainties and are also shown by slightly fainter symbols.  For
-    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
-    luminosities of the triple OB system Aa, Ab, and B
-    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
-    the luminosity of only the most massive component Aa.  Lines show
-    the predictions of stellar wind models: red lines are the commonly
-    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
-    (dashed), and supergiants (dotted), while black lines show
-    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
-    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
-    mass-loss measurements from NUV lines for weak-wind O~dwarfs
-    \citep{Marcolino:2009a}, while the green plus symbol shows the
-    measurement from infrared H recombination lines for \(\sigma\)~Ori
-    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
-    to observational uncertainties (lower right) and assumed shell
-    parameters (upper left).}
-  \label{fig:mass-loss-vs-luminosity}
-\end{figure*}
-
 Source~342 is anomalous in both methods.

### 2019-03-18 papers/Papers1234/sec-observational-diagnostics.tex
More about mass loss rates for paper III

@@
     grain emissivity method of \citet{Kobulnicky:2018a}, with
-    corrections as described in our Appendix~\ref{app:bow-shock-data}.
+    corrections as described in our \S~\ref{app:bow-shock-data}.
     Circle symbols show the sources from K18, colored according to the
@@
 \end{figure*}
+
+Taking into account the support from stellar wind ram pressure and the
+absorbed stellar radiation pressure, the pressure of the bow shell can
+be written
+\begin{equation}
+  \label{eq:eta-shell-components}
+  \eta\shell = \eta\wind +  \left(  1 - e^{-\Qp \tau / Q_{\text{abs}}}\right) \ ,
+\end{equation}
+which is valid in all 3 regimes: WBS, RBW, and RBS.\@ The wind
+momentum efficiency is defined in terms of the stellar wind parameters
+(eq.~[13] of Paper~I):
+\begin{equation}
+  \label{eq:wind-eta-typical}
+  \eta\wind = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1} \ .
+\end{equation}
+Therefore, assuming \(\Qp/Q_{\text{abs}} = 1.25\) as in
+\S~\ref{sec:energy-trapp-vers}, the mass-loss rate can be estimated as
+\begin{equation}
+  \label{eq:mdot-tau-eta}
+  \dot{M}_{-7} = 2.02 \, L_4 \, V_3^{-1} \,
+  \left[ \eta\shell - \left(  1 - e^{-1.25 \tau} \right) \right]  \ .
+\end{equation}
+In the wind-supported WBS regime
+(\(\tau \ll \eta\wind \approx \eta\shell\)), the second term in the brackets is
+negligible, and we can use equations~(\ref{eq:tau-empirical},
+\ref{eq:eta-shell}) to write
+\begin{equation}
+  \label{eq:mdot-eta-wbs}
+  \dot{M}_{-7} \approx 990 \frac{R\pc \, T_4 \, L_{\text{IR},4}}
+  {L_4 \, V_3 \, \kappa_{600} \, h_{1/4}} \ .
+\end{equation}
+On the other hand, if \(\eta\shell\) does not greatly exceed \(\tau\), then
+the full equation~\eqref{eq:mdot-tau-eta} should be used, although the
+uncertainties in \(\eta\shell\) and \(\tau\) mean that the mass loss will be
+poorly constrained in such a case.
+
+Resulting mass-loss rates are shown as a function of stellar
+luminosity in Figure~\ref{fig:mass-loss-vs-luminosity}a for the K18 and
+Orion sources.
 

### 2019-03-18 papers/Papers1234/_region_.tex
Jane corrections to paper II complete to end of sec 3

--- 2019-02-05 papers/Papers1234/_region_.tex
@@
-\message{ !name(dusty-bow-wave.tex)}\documentclass[useAMS, usenatbib, a4paper]{mnras}
+\message{ !name(bs-bw-dw-02.tex)}\documentclass[useAMS, usenatbib, a4paper]{mnras}
 \pdfsuppresswarningpagegroup=1
@@
 \pubyear{2019}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\Sin}{\mathcal{S}}
-\DeclareMathOperator{\Cos}{\mathcal{C}}
-\DeclareMathOperator{\Cot}{\mathcal{T}}
-\DeclareMathOperator{\GammaFunc}{\Gamma}
-\DeclareMathOperator\erf{erf}
-\newcommand\w{\ensuremath{\mathrm{w}}}
-\newcommand\C{\ensuremath{\mathrm{c}}}
-\providecommand{\abs}[1]{\lvert#1\rvert}
-\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
-\newcommand\TODO[1]{%
-  \begin{center}
-    \framebox{\parbox{0.8\linewidth}{
-        \texttt{\footnotesize\color{red} #1}}}
-  \end{center}}
 
-\newcommand\uvec[1]{\bm{\hat{#1}}}
-\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+\input{bs-bw-dw-defs.tex}
 
-\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
-\newcommand{\grain}{\ensuremath{_{\text{d}}}}
-\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
-\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
-\newcommand{\xsec}{\ensuremath{\sigma\grain}}
-\newcommand\frad{\ensuremath{f_{\text{rad}}}}
-\newcommand\fmax{\ensuremath{f_{\text{max}}}}
-\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
-\newcommand\drag{\ensuremath{_{\text{drag}}}}
-\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
-\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
-\newcommand\rad{\ensuremath{_{\text{rad}}}}
-\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
-% Why do I need both of these?
-\newcommand\sound{\ensuremath{c_{\text{s}}}}
-\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
-\newcommand\starstar{\ensuremath{_{**}}}
+\externaldocument[Q-]{quadrics-bowshock}
+%\externaldocument[I-]{bs-bw-dw-01}
+%\externaldocument[III-]{bs-bw-dw-03}
 
@@
 
-\message{ !name(sec-dust-bow-discuss.tex) !offset(-77) }
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/K18-pairplot-edited}
-  \caption[K18 pair plot]{Pair plots of correlations between observed
-\message{ !name(dusty-bow-wave.tex) !offset(41) }
+\message{ !name(bs-bw-dw-02.tex) !offset(154) }
+    \text{RBS (\(\tau_*^2 > 1\)):} & (1 + \eta\wind)^{1/2} \, R_*  \\
+    \text{RBW (\(\eta\wind < \tau_*^2 < 1\)):} & 2 \, \tau_* \, R_* \\
+    \text{WBS (\(\tau_*^2 < \eta\)):} & \eta\wind^{1/2} \, R_*  
+  \end{cases}
+\end{equation}
+
+\message{ !name(bs-bw-dw-02.tex) !offset(250) }
 

### 2019-03-18 papers/Papers1234/app-dust-wave.tex
Jane corrections to paper II complete to end of sec 3

@@
 If the incoming dust grains initially travel along parallel
-trajectories with varying \(b\), but the same \(v_\infty\), then deflection
+trajectories with varying \(b\) but the same \(v_\infty\), then deflection
 by the radiative force will form a bow-shaped dust wave around the
@@
 both equal: \(\Pi = \Lambda = 1 + \varepsilon_\mu\)
-(\((\Pi = \Lambda = 2.25\) in Fig.~\ref{fig:dust-trajectories}b).
+(\(\Pi = \Lambda = 2.25\) in Fig.~\ref{fig:dust-trajectories}b).
 
@@
     range of impact parameters, shown on a log--log scale. Distances
-    are in units of \(R\starstar\), times in units of
-    \(R\starstar / v_\infty\), velocities in units of \(v_\infty\), and
-    accelerations in units of \(v_\infty^2 / R\starstar\). The grain's
+    are in units of \(R\starstar\), times are in units of
+    \(R\starstar / v_\infty\), velocities are in units of \(v_\infty\), and
+    accelerations are in units of \(v_\infty^2 / R\starstar\). The grain's
     acceleration along the \(y\) axis has a maximum value,
@@
 
-We will show later in \S~\ref{sec:magn-effects-grain} that for
+We will show in \S~\ref{sec:magn-effects-grain} that for
 sufficiently small grains the Larmor magnetic gyration radius,
@@
 trajectories are assumed parallel to one another, as in
-\S~\ref{sec:dust-parallel}. These are sufficient to give a flavor of
-the effects of a magnetic field on the dust wave structure.  Further
-models at intermediate angles, and which also include the effects of
-gas drag, are presented in \S~\ref{sec:magn-effects-grain}.
+\S~\ref{sec:dust-parallel}. These two cases are sufficient to give a
+flavor of the effects of a magnetic field on the dust wave structure.
+Further models at intermediate angles, and which also include the
+effects of gas drag, are presented in \S~\ref{sec:magn-effects-grain}.
 
@@
 We have been unable to find an analytic solution to this equation, but
-a numerical solution is shown in Figure~\ref{fig:inertia-thB90}.  When
-the impact parameter is larger than \(b \sim R\starstar\), the
+a numerical solution is shown in Figure~\ref{fig:inertia-thB90}a.
+When the impact parameter is larger than \(b \sim R\starstar\), the
 trajectories are very similar to in the non-magnetic case

### 2019-03-18 papers/Papers1234/sec-observational-diagnostics.tex
Jane corrections to paper II complete to end of sec 3

@@
 the full equation~\eqref{eq:mdot-tau-eta} should be used, although the
-uncertainties in \(\eta\shell\) and \(\tau\) mean that the mass loss will be
-poorly constrained in such a case.
+uncertainties in \(\eta\shell\) and \(\tau\), combined with the partial
+cancellation of two similar-sized terms, mean that the mass loss will
+be poorly constrained in such cases.
 

### 2019-03-18 papers/Papers1234/sec-weak-coupling.tex
Jane corrections Paper II up to end of sec 4.4

--- 2019-03-14 papers/Papers1234/sec-weak-coupling.tex
@@
 
-If the radiation field is sufficiently strong, then the collisional
-coupling between grains and gas will break down.  In this section, we
-calculate the regions of star/stream parameter space where this might
-occur, leading to a separation of the bow into an outer dust wave and
-an inner, dust-free bow shock.
+We now consider how the results of the previous section are changed
+when drag forces from the gas are taken into account.  After
+considering the general form of these forces in
+\S~\ref{sec:drag-force-grains}, we study the behavior of the grain
+electrostatic potential in \S~\ref{sec:cloudy-models-dust} and the
+nature of the decoupling that occurs for sufficiently strong radiation
+fields in \S~\ref{sec:gas-grain-separ}.  In
+\S~\ref{sec:exist-cond-separ} we use this information to deduce
+conditions for the existence of dust waves, and calculate grain
+trajectories in \S~\ref{sec:two-regimes-post} and estimate the
+back-reaction on the plasma in \S~\ref{sec:back-reaction-gas}.
+
+% If the radiation field is
+% sufficiently strong, then this collisional coupling between grains and
+% gas will break down at some point.  In this section, we calculate the
+% regions of star/stream parameter space where this might occur, leading
+% to a separation of the bow into an outer dust wave and an inner,
+% dust-free bow shock.
 
@@
 thermal speed of the colliders, which is
-\(\approx \SI{10}{km.s^{-1}}\) for protons, giving a maximum strength of
+\(\approx \SI{10}{km.s^{-1}}\) for protons, giving a maximum strength from
+equation~\eqref{eq:ds79} of
 \begin{equation}
@@
 in \citet{Baldwin:1991a} and \citet{van-Hoof:2004a} with photoelectric
-emission theory from \citet{Weingartner:2001b, Weingartner:2006a}.  We
-use the default ``ISM'' dust mixture included in Cloudy, which
-comprises ten size bins each for spherical silicate and graphite
-grains in the range \num{0.005} to \SI{0.25}{\um}, and which is
-designed to reproduce the average Galactic extinction curve
-\citep{Weingartner:2001a, Abel:2008a}.  The optical properties of each
-grain species are calculated using Mie theory \citep{Bohren:1983a},
-assuming solid spheres.  The resultant wavelength-dependent extinction
-properties of the mixture are summarised in
-Figure~\ref{fig:cloudy-ism-dust-opacity}.
+emission theory from \citet{Weingartner:2001b} and
+\citet{Weingartner:2006a}.  We use the default ``ISM'' dust mixture
+included in Cloudy, which comprises ten size bins each for spherical
+silicate and graphite grains in the range \num{0.005} to
+\SI{0.25}{\um}, and which is designed to reproduce the average
+Galactic extinction curve \citep{Weingartner:2001a, Abel:2008a}.  The
+optical properties of each grain species are calculated using Mie
+theory \citep{Bohren:1983a}, assuming solid spheres.  The resultant
+wavelength-dependent extinction properties of the mixture are
+summarised in Figure~\ref{fig:cloudy-ism-dust-opacity}.
 
@@
 and sublimation significantly reduces the grain abundance in the inner
-regions.  The remaining columns show low-density
+regions \citep{Arthur:2004a}.  The remaining columns show low-density
 (\(n = \SI{1}{cm^{-3}}\)), extended (\(R \sim \SI{10}{pc}\)) regions
@@
 the inner radius is a superthermal one, then the superthermal solution
-branch (upper right corner of
-Fig.~\ref{fig:gas-grain-drag-photoionized}) is followed as far as
-possible through the outer spatial zones.  We have modified the code
-so as to instead always prefer the slower subthermal branch whenever
-multiple solutions are available.  This makes more sense than the
-default behavior for our context, where the grains are moving towards
-the star and so the radiative force is gradually increasing from an
-initial low value.
+branch is followed as far as possible through the outer spatial zones.
+We have modified the code so as to instead always prefer the slower
+subthermal branch whenever multiple solutions are available.  This
+makes more sense than the default behavior for our context, where the
+grains are moving towards the star and so the radiative force is
+gradually increasing from an initial low value.
 
@@
 increasingly diluted but the grain potential falls only slowly, so
-eventually one reaches a point where an equilibrium between Coulomb
+eventually a point is reached where an equilibrium between Coulomb
 drag and radiation force can be established, which corresponds to a
@@
     radiation parameter (logarithmic scale). All densities and stellar
-    types are shown, with line colors as in Fig.~\ref{fig:drift-gn}.
-    Solid lines show silicate grains and dashed lines show graphite
-    grains.  Line width increases with grain size (to reduce clutter,
-    only every second size bin is shown).  Straight black lines show
-    the logarithmic fits discussed in the text:
-    eq.~\eqref{eq:phi-vs-Xi}, most appropriate for carbon grains
+    types are shown, with line colors as indicated (blue/orange for
+    O~stars, purple/green for B~stars) and lighter shades indicating
+    higher gas densities.  Solid lines show silicate grains and dashed
+    lines show graphite grains.  Line width increases with grain size
+    (to reduce clutter, only every second size bin is shown).
+    Straight black lines show the logarithmic fits discussed in the
+    text: eq.~\eqref{eq:phi-vs-Xi}, most appropriate for carbon grains
     around cooler stars, is shown by the dashed line, while the solid
@@
 the radiation parameter, which we denote the \textit{rip point}:
-\(\Xi_\dag \sim 1000\).
+\(\Xi_\dag \sim 1000\). The process is illustrated in
+Figure~\ref{fig:gas-grain-drag-photoionized}, which shows the regions
+of stability and instability as a function of gas--grain slip velocity
+as the grain potential and radiation force are increased.
 
@@
 to their size and composition.\footnote{%
-  Remember that \(\kappa\) is the opacity per unit mass of gas, while
+  Recall that \(\kappa\) is the opacity per unit mass of gas, while
   \(\kappa\grain\) is the opacity per unit mass of a particular grain. In

### 2019-03-18 papers/Papers1234/sec-dust-wave-discussion.tex
Finish Jane corrections to Paper II

@@
 therefore vary with grain size and composition.  For a spherical grain
-of radius \(\amu\,\si{\um}\) and solid density
+of size \(\amu\,\si{\um}\) and solid density
 \(\rho\grain \, \si{g.cm^{-3}}\), equation~\eqref{eq:kappa-grain} yields
@@
 grain radiative equilibrium temperature exceed the sublimation
-temperature (\SIrange{1500}{2000}{K}, depending on composition), which
+temperature (\SIrange{1400}{1750}{K}, depending on composition), which
 occurs for radiative fluxes about \SI{e9} times higher than the
@@
 a very steep size dependence, being most effective in destroying
-larger grains.  Using \citeauthor{Hoang:2018a}'s equation~(27) and
+larger grains.  Using equation~(27) of \citet{Hoang:2018a} and
 assuming a grain tensile strength of

### 2019-03-18 papers/Papers1234/sec-weak-coupling.tex
Finish Jane corrections to Paper II

@@
 force is higher than the upper limit on the Coulomb drag force
-(eq.~\eqref{eq:fdrag-maximum}), so that the equilibrium drift velocity
+(eq.~[\ref{eq:fdrag-maximum}]), so that the equilibrium drift velocity
 is exceedingly high.  We discuss this situation in greater detail
@@
     these lines are drag confined, while dust waves below and to the
-    right of the lines are inertia confined.  }
+    right of the lines are inertia confined.  Yellow plus symbols show
+    the parameters for the two example trajectories shown in
+    Fig.~\ref{fig:phase-space-trajectories}.}
   \label{fig:existence-dust-wave}
@@
     \SI{10}{M_\odot} main-sequence B star (see Tab.~\ref{tab:stars}).
-    Upper panels show the evolution of grain radius, \(R\) (blue
+    Upper panels show the evolution of the grain position, \(R\) (blue
     curve, normalized by the rip point radius, \(R_\dag\)), and grain
@@
 stream.  The recoupling initiates gradually, as the grain's outward
-motion is slowed and it begins to move inward again, but is completed
-suddenly once \(w\) again falls below \SI{10}{km.s^{-1}}, in what we
-term \textit{snap back}. The net result is that the grain has returned
-to exactly the same phase track that it started in on, and so repeats
-the cycle indefinitely.
+motion is slowed and turns around, but is completed suddenly once
+\(w\) again falls below \SI{10}{km.s^{-1}}, in what we term
+\textit{snap back}. The net result is that the grain has returned to
+exactly the same phase track that it started in on, and so repeats the
+cycle indefinitely.
 
@@
 the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
-will apply: \newcommand\freeze{\ensuremath{_{\text{tight}}}}
+will apply: \(v_{\infty} < v\freeze\), where
 \begin{equation}
   \label{eq:velocity-strong-B-coupling}
-  v_{\infty} < v\freeze \approx
-  \begin{cases}
-    \text{drag-confined:}
-    & 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2}\\
-    \text{inertia-confined:}
-    & 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \\
-  \end{cases} \ ,
-\end{equation}
-where we have substituted typical values of the minor parameters
+  \begin{aligned}
+    \text{drag-confined:}\quad v\freeze
+    &\approx 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2} \ , \\
+    \text{inertia-confined:}\quad v\freeze
+    &\approx 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \ ,
+  \end{aligned}
+\end{equation}
+in which we have substituted typical values of the minor parameters
 \(\Xi_\dag\), \(\phi_{\dag}\), \(\phi_{**}\), \(\rho\grain\),
@@
 measured in crossing times, is slightly longer than in panel~a, but is
-of the same order.  In both these cases, a second, exterior dust
+of the same order.  In both these cases a second, exterior dust
 shell is formed in addition to the hemispherical one produced by the

### 2019-03-22 papers/Papers1234/bs-bw-dw-03.tex
Lots more writing of discussion for Paper III

@@
 \input{sec-observational-diagnostics}
+
+\section{Summary}
+\label{sec:conclusions}
+
+\section*{Acknowledgements}
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grants Programa de Apoyo a Proyectos de Investigación
+e Inovación Tecnológica IN112816 and IN107019.  This work has made
+extensive use of Python language libraries from the SciPy
+\citep{Jones:2001a}, AstroPy \citep{Astropy-Collaboration:2013a,
+  Astropy-Collaboration:2018a} and Pandas \citep{McKinney:2010a}
+projects.  We thank Chip Kobulnicky for useful discussions.
+
 \bibliographystyle{mnras}
@@
 \input{app-k17-k18}
+
+\section{Notes on particular sources}
+\label{sec:notes-part-sourc}
+
+\subsection{Source~380, HD~53367, V750~Mon}
+\label{sec:hd-53367-v750}
+
+This is a Herbig Be star with spectral type B0V--B0III and mass 12 to
+\SI{15}{M_\odot}, which shows long-scale irregular photometric
+variability \citep{Tjin-A-Djie:2001a, Pogodin:2006a} together with
+cyclic radial velocity variations, which are interpreted as an
+eccentric binary with a \SI{5}{M_\odot} pre-main-sequence companion.
+It is located outside the solar circle and, although it was originally
+classified as part of the CMa OB association at about \SI{1}{kpc}
+\citep{Tjin-A-Djie:2001a}, more recent estimates put it much closer.
+K18 assume a distance of \SI{260}{pc}, based on Hipparcos measurements
+\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
+\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
+puts it closer still at \SI{140 \pm 30}{pc}.\footnote{%
+  Median and 90\% confidence interval, estimated from Bayesian
+  inference using an exponential density distribution with scale
+  length of \SI{1350}{pc} as a prior (see
+  \url{https://github.com/agabrown/astrometry-inference-tutorials/}). }
+
+\citet{Quireza:2006b} report a kinematic distance to the associated
+\hii{} region IC~2177 (G\num{223.70}\num{-1.90}) of \SI{1.6}{kpc},
+based an LSR radio recombination line velocity of \SI{+16}{km.s^{-1}}
+\citep{Quireza:2006a} and the outer Galaxy rotation curve of
+\citet{Brand:1993a}.  However, given the dispersion in peculiar
+velocities of star-forming clouds (\SIrange{7}{9}{km.s^{-1}},
+\citealp{Stark:1984a}) and likely streaming motions of the ionized gas
+(\(\approx \SI{10}{km.s^{-1}}\), \citealp{Matzner:2002a, Lee:2012a}),
+this is still consistent with a much smaller distance, which would
+also help in bringing the radio continuum-derived nebular electron
+density into agreement with the value (\(\approx \SI{100}{cm^{-3}}\))
+derived from the optical [\ion{S}{ii}] line ratio
+\citep{Hawley:1978a}.
+
+\citet{Fairlamb:2015a} derive a distance of \SI{340 \pm 60}{pc} from
+combining a spectroscopically determined effective temperature,
+gravity, and reddening with photometry and pre-main sequence
+evolutionary tracks.  They also determine a luminosity of \SI{13000
+  \pm 1000}{L_\odot}, which is only half that assumed by K18, and
+would have to be even lower to bring the photometry into concordance
+with the Gaia distance.  Alternatively, the luminosity could remain
+the same if the total-to-selective extinction ratio were higher than
+the \(R_V = 3.1\) assumed by \citet{Fairlamb:2015a}.  Taking
+\(R_V = 5.5\) instead, as in Orion, would give \(A_V = 3.34\) and a
+predicted \(V\) magnitude of 6.7 if we assume \(L_4 = 1.3\),
+\(D = \SI{170}{pc}\) (furthest distance in Gaia 90\% confidence
+interval) and \(T_{\text{eff}} = \SI{29.5}{kK}\)
+\citep{Fairlamb:2015a} for a bolometric correction of \(-2.86\)
+\citep{Nieva:2013a}.  The observed brightness varies between
+\(V = 6.9\) and 7.2, which is still at least 20\% fainter than
+predicted, but this is the best that can be achieved without rejecting
+the Gaia parallax distance entirely.
+
+A final sanity check can be performed by considering the free-free
+radio continuum flux of V750~Mon's surrounding \hii{} region, which,
+after converting to a luminosity, should be proportional to the total
+recombination rate in the nebula and therefore, assuming
+photoionization equilibrium and negligible dust absorption in the
+ionized gas, also proportional to the ionizing photon luminosity of
+the star.  \citet{Quireza:2006b} report a flux density of \SI{6}{Jy}
+at \SI{8.6}{Ghz} for G\num{223.70}\num{-1.90}, as compared with a flux
+density of \SI{260}{Jy} for the Orion Nebula using the same
+instrumental setup.  Assuming an ionizing photon luminosity of
+\(S_{49} = 1\) and distance \SI{410}{pc} for the ionizing Trapezium
+stars in Orion, therefore implies
+\(S_{49} = 0.0027 (D/\SI{140}{pc})^2\) for V750~Mon.  Using an
+ionizing flux of \SI{3.2e22}{cm^{-2}.s^{-1}} from the curves in Fig.~4
+of \citet{Sternberg:2003a}, this translates to a bolometric luminosity
+of \(L_4 = 0.96 (D/\SI{140}{pc})^2\), which is consistent with the
+\citet{Fairlamb:2015a} value if we take a distance towards the high
+end of the Gaia range.
+
+\subsection{Source 407, HD~93249}
+\label{sec:source-407}
+
+TODO
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/cygnus-bows-midir-combo}
+  \caption{Two bows in Cygnus}
+  \label{fig:cygnus-bows}
+\end{figure}
+
+\subsection{Source 342}
+\label{sec:source-342}
+
+Source~342 is anomalous in both methods. Has high mass loss for low luminosity.
+
+\subsection{Source 344}
+\label{sec:source-344}
+
+This has big disagreement between K18 and me.  My mass-loss rate seems too low, given its high luminosity. Why?
 

### 2019-03-22 papers/Papers1234/sec-obs-conclusions.tex
Submitted first paper! To MNRAS and arxiv
Lots more writing of discussion for Paper III

--- 2017-11-30 papers/Paper1/sec-obs-conclusions.tex
@@
 
+\citet{Meyer:2014a} say that in cool stars the dust emission comes
+from the shocked inner wind, rather than from near the contact
+discontinuity for hot stars.  This could explain the difference in
+shape between the Herschel and Spitzer samples.
+
+How different regions of the \(\Pi\)--\(\Lambda\) plane are populated.
+Bottom-right quadrant hard to get to (except for standing wave
+oscillations), but may be due to finite shell thickness, which (for
+low Mach number) will be more apparent in the wings, which might
+decrease \(\Lambda\) more than \(\Pi\).  Fact that thin-shell solutions should
+trace the contact discontinuity, but in some cases it may be only the
+inner or the outer shell that is visible.
+
+Justification for standing waves: Fig.~3 of \citet{Meyer:2016a} shows
+a time sequence of thin-shell instability, which looks a bit like a
+standing wave. But much larger amplitude than we are considering.
+
+Deviations from axisymmetry as an alternative to oscillations.
+
+\subsection{The case of inside-out bows}
+\label{sec:case-inside-out}
+
+So far, we have considered the case where the inner source dominates
+the radiation, while dust is present only in the outer stream, which
+applies to hot stars interacting with the ISM.  However, in the case
+of cool stars, the inner wind will also be dusty.  Examples are the
+red supergiant (RSG) phase of high-mass evolution, or the asymptotic
+giant branch (AGB) stage of low/intermediate-mass evolution.  In both
+these cases, it is still the inner source that provides the radiation
+field.  However, not all winds are radiatively driven and in those
+cases it is conceivable that it is the outer source that dominates the
+radiation field.  An example is the case of photoevaporating
+protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
+regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
+thermally driven photoevaporation flow \citep{Henney:1998b, Henney:1999a},
+while the outer stream is the stellar wind from an O~star
+\citep{Garcia-Arredondo:2001a}.
+
 %%% Local Variables:

### 2019-03-22 papers/Papers1234/sec-observational-diagnostics.tex
Lots more writing of discussion for Paper III

@@
 \label{sec:shell-thickness}
-We do not expect a great deal of variation in the shell thickness,
-except for in the case of fast runaway stars
-(\(v > \SI{100}{km.s^{-1}}\)), for which the shell may be dramatically
-thinner if the post-shock cooling is sufficiently rapid
-(\(h / R_0 \sim M_0^{-2}\)).  For ambient densities less than about
-\SI{10}{cm^{-3}}, the minimum thickness is about ten times smaller
-than we are assuming.  This occurs at
-\(v \approx \SI{60}{km.s^{-1}}\), corresponding to the peak in the cooling
-curve at \SI{e5}{K} (see \S~3.2 of Paper~I),
+For maximally efficient post-shock radiative cooling, the shell
+thickness depends on the Mach number of the shock as
+\(h / R_0 \sim M_0^{-2}\).  However, for ambient densities less than
+about \SI{10}{cm^{-3}}, the minimum thickness is only about ten times
+smaller than the \(h / R_0 = 0.25\) that we are assuming.  In
+photoionized gas, this occurs at \(v \approx \SI{60}{km.s^{-1}}\),
+corresponding to the peak in the cooling curve at \SI{e5}{K} (see
+\S~3.2 of Paper~I),
 % XREF: Paper I \S~\ref{sec:radi-cool-lengths}
 since the thickness is set by the cooling length at higher speeds.  In
+the case that the Alfv\'en speed is a significant fraction of the
+sound speed, this will also tend to increase the thickness.  In
 principle, the shell thickness can be measured observationally if the
 source is sufficiently well resolved \citep{Kobulnicky:2017a},
-although this is complicated by projection effects.
+although this is complicated by projection effects.  We return to the
+issue of the shell thickness in the discussion below.
 
@@
 
-\section{Candidate radiation-supported bows}
+\subsection{Candidate radiation-supported bows}
 \label{sec:cand-radi-supp}
@@
 Four sources are sufficiently close to the diagonal line
-\(\eta\shell = 1.25 \tau\) in Figure~\ref{fig:All-sources-eta-tau} that they
-should be treated as potential candidates for radiation-supported
-bows. These are K18 sources~380 (HD~53367, V750~Mon) and 407 (HD~93249
-in Carina) plus \thD{} and LP~Ori.  Of the four, source 380 is the
-only one that is also a candidate for grain-gas decoupling.  Further
-details of the two K18 sources are presented in following subsections,
-where for source~380 we show that reducing both luminosity and
-distance by a factor of roughly 2 with respect to the values used by
-K18 would provide a better fit to the totality of observational data.
-However, the ratio \(\eta\shell /\tau\) is proportional to \(D / L_*\) so it
-would not be affected by such an adjustment and the bow remains
-radiation-supported.  On the other hand \(\eta\shell\) (proportional to
-\(D / L_*^2\)) would increase by 2, making the classification as dust
-wave candidate more marginal.
+\(\eta\shell = 1.25 \tau\) in Figure~\ref{fig:All-sources-eta-tau}
+that they should be treated as strong candidates for
+radiation-supported bows. These are K18 sources~380 (HD~53367,
+V750~Mon) and 407 (HD~93249 in Carina) plus \thD{} and LP~Ori.  Of the
+four, source 380 is the only one that is also a candidate for
+grain-gas decoupling.  Further details of the two K18 sources are
+presented in Appendix~\ref{sec:notes-part-sourc}, where for source~380
+we show that reducing both luminosity and distance by a factor of
+roughly 2 with respect to the values used by K18 would provide a
+better fit to the totality of observational data.  However, the ratio
+\(\eta\shell /\tau\) is proportional to \(D / L_*\) so it would not be
+affected by such an adjustment and the bow remains
+radiation-supported.  On the other hand \(\eta\shell\) (proportional
+to \(D / L_*^2\)) would increase by 2, making the classification as
+dust wave candidate more marginal.
 
-% \subsection{Notes on particular sources}
-% \label{sec:notes-part-sourc}
-
-\subsection{Source~380, HD~53367, V750~Mon}
-\label{sec:hd-53367-v750}
-
-This is a Herbig Be star with spectral type B0V--B0III and mass 12 to
-\SI{15}{M_\odot}, which shows long-scale irregular photometric
-variability \citep{Tjin-A-Djie:2001a, Pogodin:2006a} together with
-cyclic radial velocity variations, which are interpreted as an
-eccentric binary with a \SI{5}{M_\odot} pre-main-sequence companion.
-It is located outside the solar circle and, although it was originally
-classified as part of the CMa OB association at about \SI{1}{kpc}
-\citep{Tjin-A-Djie:2001a}, more recent estimates put it much closer.
-K18 assume a distance of \SI{260}{pc}, based on Hipparcos measurements
-\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
-\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
-puts it closer still at \SI{140 \pm 30}{pc}.\footnote{%
-  Median and 90\% confidence interval, estimated from Bayesian
-  inference using an exponential density distribution with scale
-  length of \SI{1350}{pc} as a prior (see
-  \url{https://github.com/agabrown/astrometry-inference-tutorials/}). }
-
-\citet{Quireza:2006b} report a kinematic distance to the associated
-\hii{} region IC~2177 (G\num{223.70}\num{-1.90}) of \SI{1.6}{kpc},
-based an LSR radio recombination line velocity of \SI{+16}{km.s^{-1}}
-\citep{Quireza:2006a} and the outer Galaxy rotation curve of
-\citet{Brand:1993a}.  However, given the dispersion in peculiar
-velocities of star-forming clouds (\SIrange{7}{9}{km.s^{-1}},
-\citealp{Stark:1984a}) and likely streaming motions of the ionized gas
-(\(\approx \SI{10}{km.s^{-1}}\), \citealp{Matzner:2002a, Lee:2012a}),
-this is still consistent with a much smaller distance, which would
-also help in bringing the radio continuum-derived nebular electron
-density into agreement with the value (\(\approx \SI{100}{cm^{-3}}\))
-derived from the optical [\ion{S}{ii}] line ratio
-\citep{Hawley:1978a}.
-
-\citet{Fairlamb:2015a} derive a distance of \SI{340 \pm 60}{pc} from
-combining a spectroscopically determined effective temperature,
-gravity, and reddening with photometry and pre-main sequence
-evolutionary tracks.  They also determine a luminosity of \SI{13000
-  \pm 1000}{L_\odot}, which is only half that assumed by K18, and
-would have to be even lower to bring the photometry into concordance
-with the Gaia distance.  Alternatively, the luminosity could remain
-the same if the total-to-selective extinction ratio were higher than
-the \(R_V = 3.1\) assumed by \citet{Fairlamb:2015a}.  Taking
-\(R_V = 5.5\) instead, as in Orion, would give \(A_V = 3.34\) and a
-predicted \(V\) magnitude of 6.7 if we assume \(L_4 = 1.3\),
-\(D = \SI{170}{pc}\) (furthest distance in Gaia 90\% confidence
-interval) and \(T_{\text{eff}} = \SI{29.5}{kK}\)
-\citep{Fairlamb:2015a} for a bolometric correction of \(-2.86\)
-\citep{Nieva:2013a}.  The observed brightness varies between
-\(V = 6.9\) and 7.2, which is still at least 20\% fainter than
-predicted, but this is the best that can be achieved without rejecting
-the Gaia parallax distance entirely.
-
-A final sanity check can be performed by considering the free-free
-radio continuum flux of V750~Mon's surrounding \hii{} region, which,
-after converting to a luminosity, should be proportional to the total
-recombination rate in the nebula and therefore, assuming
-photoionization equilibrium and negligible dust absorption in the
-ionized gas, also proportional to the ionizing photon luminosity of
-the star.  \citet{Quireza:2006b} report a flux density of \SI{6}{Jy}
-at \SI{8.6}{Ghz} for G\num{223.70}\num{-1.90}, as compared with a flux
-density of \SI{260}{Jy} for the Orion Nebula using the same
-instrumental setup.  Assuming an ionizing photon luminosity of
-\(S_{49} = 1\) and distance \SI{410}{pc} for the ionizing Trapezium
-stars in Orion, therefore implies
-\(S_{49} = 0.0027 (D/\SI{140}{pc})^2\) for V750~Mon.  Using an
-ionizing flux of \SI{3.2e22}{cm^{-2}.s^{-1}} from the curves in Fig.~4
-of \citet{Sternberg:2003a}, this translates to a bolometric luminosity
-of \(L_4 = 0.96 (D/\SI{140}{pc})^2\), which is consistent with the
-\citet{Fairlamb:2015a} value if we take a distance towards the high
-end of the Gaia range.
-
-\subsection{Source 407, HD~93249}
-\label{sec:source-407}
-
-TODO
+Three additional K18 sources (409, 410, 411) are within a factor of 3
+of the radiation-supported line, so they too must be considered as
+potential candidates, given our estimated systematic uncertainty in
+the shell parameters (\S~\ref{sec:syst-uncert-due}).
 
@@
 Resulting mass-loss rates are shown as a function of stellar
-luminosity in Figure~\ref{fig:mass-loss-vs-luminosity}a for the K18 and
-Orion sources.
+luminosity in Figure~\ref{fig:mass-loss-vs-luminosity}a for the K18
+and Orion sources.  As in Figure~\ref{fig:All-sources-eta-tau} we show
+separately the uncertainties in the measurements due to observational
+errors (lower right box) and systematic model uncertainties (upper
+left box).  Typical observational uncertainties are combined into an
+error ellipse using the techniques of
+Appendix~\ref{sec:comb-uncert-covar}, which is shown in light blue.
+Sources that are close to the RBW line in the \(\tau\)--\(\eta\shell\)
+diagram yield only upper limits to the mass-loss rate and these are
+shown as faint symbols in the figure.
+
+Our results are compared with the commonly used mass-loss recipes of
+\citet{Vink:2000a} (red lines) and more recent whole-atmosphere
+simulations of wind formation in B~stars \citep{Krticka:2014a} and
+O~stars \citep{Krticka:2017a}.  Additionally, we show observational
+mass loss determinations for weak wind O~dwarfs
+\citep{Marcolino:2009a} as orange plus symbols.  It can be seen that
+the majority of the K18 sources fall below the \citeauthor{Vink:2000a}
+line and are more consistent with the \citet{Krticka:2017a} models.
+
+\textit{Write about sigma Ori}
 
@@
 \newcommand\LOS{\ensuremath{_{\text{los}}}}
+
 K18 derive mass loss rates for their sources using a method that is
-different from the one that we employ in
-\S~\ref{sec:summary-discussion}.  Both methods are based on
-determining the stellar wind ram pressure that supports the bow shell,
-but K18 do so via the following steps:
+different from the one that we employ above.  Both methods are based
+on determining the stellar wind ram pressure that supports the bow
+shell, but K18 do so via the following steps:
 \begin{enumerate}[K1.]
@@
 assumption about the relative thickness of the shell, while
-step~K\ref{K2} is more directly tied to observations.\footnote{%
-  Note that there is a relation between the chord length, \(\ell\),
-  and the shell thickness, \(h\shell\), but this depends on the
-  planitude, \(\Pi\) of the bow shape \citep{Tarango-Yong:2018a}:
-  \( h\shell/R_0 = \Pi \bigl(1 - \{1 - [\ell/(2 \Pi R_0)]^2\}^{1/2}\bigr)\).  } %
+step~K\ref{K2} is more directly tied to observations.
 On the other hand, step~K\ref{K3} makes a roughly equivalent
@@
   depending on the efficiency of the post-shock cooling (see
-  \S~\ref{sec:radi-cool-lengths}).  For instance, for
-  \(v = \SI{30}{km.s^{-1}}\) as assumed by K18 and \(T = \SI{e4}{K}\),
-  one has a Mach number of \(\M_0 = 2.63\) and a compression factor of
-  2.8 for a non-radiative shock (by eq.~[\ref{eq:shock-n-jump}]) or a
-  factor of \(\M_0^2 =6.9\) for a strongly radiative one.  } %
+  % XREF Paper I \ref{sec:radi-cool-lengths}
+  \S~3.2 of Paper~I).  For instance, for \(v = \SI{30}{km.s^{-1}}\) as
+  assumed by K18 and \(T = \SI{e4}{K}\), one has a Mach number of
+  \(\M_0 = 2.63\) and a compression factor of 2.8 for a non-radiative
+  shock (by
+  % XREF Paper I \ref{eq:shock-n-jump}
+  eq.~[27] of Paper~I) or a factor of
+  \(\M_0^2 =6.9\) for a strongly radiative one.} %
 and a further assumption about the stream velocity. These assumptions
@@
 provide an important cross check on one another.  However, as
-explained in detail in Appendix~\ref{sec:grain-temp-emiss}, the
+explained in detail in \S~\ref{sec:grain-temp-emiss}, the
 \(j_\nu(U)\) relation depends on the shape of the illuminating SED,
@@
 re-derive the mass loss rates, following the same steps as in K18,
-which are then used in Figure~\ref{fig:mass-loss-vs-luminosity}b of
-\S~\ref{sec:summary-discussion}.  The difference between these
-corrected mass-loss rates and those published in K18 is shown in
+which are then used in Figure~\ref{fig:mass-loss-vs-luminosity}b
+above.  The difference between these corrected mass-loss rates and
+those published in K18 is shown in
 Figure~\ref{fig:k18-mdot-corrected-emissivity}.  It can be seen that
@@
 is by a factor of about two.
+
+% Different scenarios for producing velocities: dynamic ejection from
+% young clusters \citep{Hoogerwerf:2001a, Oh:2016c} produce high
+% velocities, dissolution of binary systems following core-collapse SN
+% \citep{Renzo:2018a} tend to produce lower velocities for the unbound
+% MS companion (walkaways, slower than 30 km/s).  Also, champagne flows
+% have low velocities.
+
+% \subsection{Diagnosing bow type from shell emission profile}
+% \label{sec:diagnosing-bow-type}
+
+% Given that the predicted shell density profile varies between
+% wind-supported and radiation-supported bows (Paper~I) it is worth
+% considering whether it may be possible to use observed emission
+% profiles to distinguish between the two.
+
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Why the two mass-loss methods differ}
+\label{sec:underst-diff-betw}
 
@@
 
-Finally, in Figure~\ref{fig:mass-loss-comparison} we compare our own
-mass-loss determinations with the corrected K18 values.  The plot
-symbols are shaded according to the physical size of the bow, \(R_0\).
-It is apparent that the two methods are broadly in agreement on
-average, but there is considerable dispersion for individual objects,
-with only a weak correlation between the results of the two techniques
-(Pearson correlation coefficient \(r = 0.67\)).  Interestingly, the
-smaller bows (darker shading) show much better agreement than the
-larger bows (lighter shading).  The five bows with
-\(R_0 > \SI{0.4}{pc}\) (339, 344, 369, 381, 382) show a difference of
-nearly an order of magnitude, in the sense that our method
-consistently predicts lower mass-loss rates than K18.  For a further
-five of the sources (380, 407, 409, 410, 411), our method gives only
-an upper limit to the wind mass-loss rate if one assumes a
-factor-three uncertainty in \(\eta\shell\), and these bows are among
-the smallest in the sample, all with \(R_0 < \SI{0.1}{pc}\).
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/mdot_correlations_edited}
+  \caption{Correlations of derived mass loss rates with star and bow
+    parameters. First row is for mass-loss rate derived using the
+    method of this paper (\S~\ref{sec:mass-loss-determ}).  Second row
+    is for mass-loss rate derived using the corrected K18 method
+    (\S~\ref{app:bow-shock-data}).  Third row is the ratio of these
+    two methods.  Points show 18 of the 20 K18 sources, omitting the
+    two strongest candidates for radiation support.  The correlation
+    coefficient, \(r\), and linear regression slope, \(m\), are shown
+    for selected pairs of interest (fainter text indicates weaker
+    correlations).  These were calculated using the Python library
+    function \texttt{scipy.stats.linregress}.}
+  \label{fig:correlations}
+\end{figure*}
 
-Source~342 is anomalous in both methods.
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/H_versus_ell_annotated}
+  \caption{Relative chord length versus shell thickness.  The line and
+    gray shading shows the theoretical relation (eq.~\eqref{eq:h-R0})
+    for planitude of \(\Pi = 1.8 \pm 0.9\).  The short vertical lines
+    at the top of the graph show the chord lengths for each of the 20
+    K18 sources.  The sources with the four smallest and four largest
+    values of \(\ell/R_0\) are individually labelled. The mean value
+    of \(\ell / R_0 = 1.8\) is indicated by a dashed line, which
+    corresponds to \(H/R_0 = 0.25\), which is the common value that we
+    use in deriving \(\eta\) and therefore \(\dot{M}\) by our method.
+    Inset diagram at lower right shows the geometry that leads to
+    eq.~\eqref{eq:h-R0}.  }
+  \label{fig:H-versus-ell}
+\end{figure}
+
+From comparing the two panels in
+Figure~\ref{fig:mass-loss-vs-luminosity} it is clear that there is a
+broad average agreement between the \(\dot{M}\) values from the two
+methods.  Nevertheless, there is considerable disparity for individual
+sources.  Obviously this is to be expected for sources where the
+\(\tau\)--\(\eta\shell\) method implies radiation support, since the
+K18 method assumes stellar wind support in all cases, and so has no
+way of identifying these.  However, discrepancies remain even for
+sources that are well above the diagonal line in
+Figure~\ref{fig:All-sources-eta-tau}.  This is shown more clearly in
+Figure~\ref{fig:mass-loss-comparison}, where we compare the two
+mass-loss determinations. Plot symbols are colored according to the
+physical size of the bow, \(R_0\), and radiation-support candidates
+are shown fainter.  It is apparent that there is only weak correlation
+between the two techniques (Pearson correlation coefficient
+\(r = 0.67\)).  Interestingly, the smaller bows (red/orange shading)
+show much better agreement than the larger bows (yellow shading).  The
+five bows with \(R_0 > \SI{0.4}{pc}\) (339, 344, 369, 381, 382) show a
+difference of nearly an order of magnitude, in the sense that our
+method consistently predicts lower mass-loss rates than K18.  The
+error ellipse for the combined observational errors (see
+Tab.~\ref{tab:error-ellipse} in App.~\ref{sec:comb-uncert-covar}) is
+highly elongated along the leading diagonal in
+Figure~\ref{fig:mass-loss-comparison} due to the fact that most of the
+observational uncertainties effect both mass-loss methods in a similar
+way.  It is therefore unlikely that observational errors are a
+significant contribution to the \textit{difference} in the two
+\(\dot M\) methods, which must instead be due to the systematic model
+uncertainties.  These are represented in the figure by the vertical
+error bars, which show the effect of a factor of three uncertainty in
+\(\eta\shell\) due to variations in shell thickness, dust opacity, and
+shell gas temperature.  It can be seen that systematic errors of this
+magnitude could indeed account for the observed differences, but the
+questions remain: which parameter is causing the problem? and can we
+correct for it?
+
+Although we have seen (Fig.~\ref{fig:mass-loss-comparison}) that the
+mass-loss discrepancy increases with \(R_0\), it is hard to understand
+why the physical size per~se might cause this.  We have therefore
+looked at the correlations between all of the observed and derived
+quantities, showing some of the more interesting results in
+Figure~\ref{fig:correlations}.  Each row of plots shows the dependence
+(\(y\) axis) of the two different derived mass-loss rates, and their
+ratio, on different parameters (\(x\) axis) of the star (leftmost four
+columns) and bow shell (remaining six columns).  The most significant
+correlations are marked in red with the value of the Pearson
+correlation coefficient, \(r\) (calculated after taking the log of all
+quantities).  The values shown with dark text have \(r^2 > 0.5\),
+which means that at least 50\% of the variance in the \(y\) quantity
+is ``explained'' by the variance in the \(x\) quantity (although this
+cannot necessarily be taken to imply causation in either
+direction). For some correlations, we also mark the linear regression
+slope, \(m\).  Since we are working in logarithmic space, this is
+equal to the power index in the relation \(y \propto x^m\).  Some
+selected weaker correlations are also shown (fainter text).
+
+For our \(\eta\)--\(\tau\shell\) mass-loss method (top row) the only
+significant correlation is a positive one with the shell infrared
+luminosity \(L\IR\) (rightmost column), with slope
+\(m = 0.6 \pm 0.1\).  For the K18 mass-loss method (middle row), the
+situation is very different, showing significant correlation with a
+trio of quantities: a positive correlation with bow radius, \(R_0\),
+and negative correlations with relative chord length, \(\ell/R_0\),
+and radiation field at the shell, \(U\).  The same three correlations
+(with inverted sense) are seen for the ratio of the two methods
+(bottom row).  This is due to the fact that the
+\(\eta\)--\(\tau\shell\) method shows much shallower slopes in its
+(weak) correlations with these quantities.  As an example, we show the
+values for \(\ell/R_0\) on the figure (seventh column):
+\(m = -2.3 \pm 0.4\) for the K18 method but \(m = -0.7 \pm 0.4\) for
+our method, which leaves a significant slope in the ratio of
+\(m = 1.6 \pm 0.4\).  For the shell luminosity, on the other hand, the
+ratio does not show any significant correlation at all.  This is
+because both methods have essentially the same slope in their
+correlation with \(L\IR\): \(m = 0.6 \pm 0.1\) for our method, and a
+weak correlation with \(m = 0.5 \pm 0.3\) for the K18 method.
+
+% From https://www.socscistatistics.com/pvalues/pearsondistribution.aspx
+% With 18 points: r^2 > 0.22 for p < 0.05 (|r| > 0.469)
+% With 18 points: r^2 > 0.35 for p < 0.01 (|r| > 0.590)
+% With 18 points: r^2 > 0.50 for p < 0.001 (|r| > 0.71)
+
+Out of the three quantities, \(R_0\), \(\ell/R_0\), and \(U\) (which
+are highly correlated between themselves) we will concentrate on the
+relative chord length \(\ell/R_0\) as the most likely culprit for the
+discrepancy between the two mass-loss estimates.  This is because it
+contains observational information that is used in the K18 method
+(step K\ref{K2} of \S~\ref{app:bow-shock-data}), but is \textit{not
+  used} in the \(\tau\)--\(\eta\shell\) method.  The closest
+equivalent of \(\ell\) in our method is the shell thickness,
+\(h\shell\), which enters in step~P\ref{P2} of
+\S~\ref{sec:energy-trapp-vers}, but crucially we use a fixed fraction
+of the bow radius, \(h\shell / R_0 = 0.25\), rather than basing it on
+any observations.  In principle, we could derive \(h\shell\) from
+\(\ell\) if we knew the radius of curvature of the shell,
+\(R_{\text{c}}\), or equivalently the planitude:
+\(\Pi = R_{\text{c}} / R_0\)\citep{Tarango-Yong:2018a}.  This is
+illustrated in the inset to Figure~\ref{fig:H-versus-ell}, from which
+we find
+\begin{equation}
+  \label{eq:h-R0}
+  \frac{h\shell}{R_0} = \frac{1}{8\Pi} \left(\frac{\ell}{R_0}\right)^2 \ .
+\end{equation}
+This is plotted in Figure~\ref{fig:H-versus-ell} for planitudes of
+\(\Pi = 1.8 \pm 0.9\), which are typical of OB star bows (this will be
+shown in detail in the upcoming Paper~IV).  Also shown in the figure
+are the individual relative chord lengths for the K18 sources (rug
+plot at top).  Although the mean value of \(\ell/R_0 \approx 1.8\)
+corresponds closely to the \(h\shell/R_0 = 0.25\) that we have used,
+
+\subsection{Shared properties of candidates for radiation support}
+\label{sec:comm-prop-cand}
+
+For five of the K18 sources (380, 407, 409, 410, 411), our method of
+\S~\ref{sec:mass-loss-determ} gives only an upper limit to the wind
+mass-loss rate if one assumes a factor-three uncertainty in
+\(\eta\shell\), raising the possibility that they may be
+radiation-supported instead of wind-supported (see Paper~I).  It is
+notable that these sources are among the smallest in the K18 sample,
+all with \(R_0 < \SI{0.1}{pc}\).  The two Orion Nebula bows, LP~Ori
+and \thD{} also fall into this category, and they are smaller still,
+with \(R_0 < \SI{0.01}{pc}\).  Six of these 7 stars also occupy a
+narrow range of spectral type\footnote{%
+  However, this is not particularly statistically significant.  For
+  instance, out of the twenty K18 sources, 7 have spectral type O8 or
+  earlier.  Therefore, taking as the null hypothesis that the 5
+  sources were randomly selected from the 20, then the chance that
+  they should all be O9 or later is
+  \(p = (1 - \frac{7}{20})^5 = 0.116\), which fails to meet the
+  conventional \(2\sigma\) significance level of \(p = 0.05\).} %
+between O9 and B0, corresponding to
+\(T_{\text{eff}} = \text{\SIrange{28}{31}{kK}}\) (LP~Ori is a much
+cooler B2 star with \(T_{\text{eff}} = \SI{20}{kK}\),
+\citealp{Petit:2008a, Alecian:2013a}).
+
+The small bow sizes are fully consistent with the expectations from
+theory developed in Paper~I.  Radiation-supported bows are predicted
+to occur either in high-density environments
+(\(n > \SI{100}{cm^{-3}}\)) or for stars with particularly weak winds.
+In either case, the bow is expected to be smaller than \SI{0.1}{pc}
+for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~6 of
+Paper~I.\@
+
+Another common property of these sources is that they all have high
+ratios of chord length to stand-off radius, \(\ell/R_0\).  For
+instance, from Figure~\ref{fig:H-versus-ell}, the four sources with
+the highest \(\ell/R_0\) values are all among the five
+radiation-supported candidates.\footnote{%
+  In this case, the statistical significance is far higher, since
+  \(p = (\frac{5}{20})^4 = 0.0039\) for the null hypothesis.}  From
+equation~\eqref{eq:h-R0} this means they also should have thicker than
+average shells.  This is consistent with our finding from Paper~I's
+\S~3.3 that the shell tends to be broad in the radiation-supported bow
+wave regime.  Furthermore, if the larger than average \(H/R_0\) were
+to be taken account in the calculation of \(\eta\shell\)
+(eq.~\eqref{eq:eta-shell}), then it would strengthen the case for
+radiation support in these objects.
+
+\subsection{The anomalous B~star KGK2010~2 in Cygnus: strong wind or
+  trapped ionization front?}
+\label{sec:anomalous-b-star}
+
+Using emissivity at different wavelength, such as \SI{24}{\um}.  No
+good reason to fear stochastic heating.  They mention not getting 70/24 ratio right.  Probably be better with our correction.
+
+Correlations between observed parameters and with mass loss rates.
+Pair plot from my jupyter notebook.
+
+How both the UV opacity and the IR emissivity depend on the same VSG grains.
+
+Effects of grain evolution.  RATD destroying larger grains.  How would
+this effect the abundance of smaller grains? Calculate maximum grain
+size for the \(U\) distribution of the K18 sample.  Do we see any
+effects that seem to vary with \(U\)?
 
 Evidence for small grains around Arches cluster near Galactic center \citep{Hankins:2017a}
-
-Different scenarios for producing velocities: dynamic ejection from
-young clusters \citep{Hoogerwerf:2001a, Oh:2016c} produce high
-velocities, dissolution of binary systems following core-collapse SN
-\citep{Renzo:2018a} tend to produce lower velocities for the unbound
-MS companion (walkaways, slower than 30 km/s).  Also, champagne flows
-have low velocities.
-
-How different regions of the \(\Pi\)--\(\Lambda\) plane are populated.
-Bottom-right quadrant hard to get to (except for standing wave
-oscillations), but may be due to finite shell thickness, which (for
-low Mach number) will be more apparent in the wings, which might
-decrease \(\Lambda\) more than \(\Pi\).  Fact that thin-shell solutions should
-trace the contact discontinuity, but in some cases it may be only the
-inner or the outer shell that is visible.
-
-Justification for standing waves: Fig.~3 of \citet{Meyer:2016a} shows
-a time sequence of thin-shell instability, which looks a bit like a
-standing wave. But much larger amplitude than we are considering.
-
-Deviations from axisymmetry as an alternative to oscillations.
-
-\subsection{Diagnosing bow type from shell emission profile}
-\label{sec:diagnosing-bow-type}
-
-Given that the predicted shell density profile varies between
-wind-supported and radiation-supported bows (Paper~I) it is worth
-considering whether it may be possible to use observed emission
-profiles to distinguish between the two.
-
-\subsection{The case of inside-out bows}
-\label{sec:case-inside-out}
-
-So far, we have considered the case where the inner source dominates
-the radiation, while dust is present only in the outer stream, which
-applies to hot stars interacting with the ISM.  However, in the case
-of cool stars, the inner wind will also be dusty.  Examples are the
-red supergiant (RSG) phase of high-mass evolution, or the asymptotic
-giant branch (AGB) stage of low/intermediate-mass evolution.  In both
-these cases, it is still the inner source that provides the radiation
-field.  However, not all winds are radiatively driven and in those
-cases it is conceivable that it is the outer source that dominates the
-radiation field.  An example is the case of photoevaporating
-protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
-regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
-thermally driven photoevaporation flow \citep{Henney:1998b, Henney:1999a},
-while the outer stream is the stellar wind from an O~star
-\citep{Garcia-Arredondo:2001a}.
-
-\section{Summary and conclusions}
-\label{sec:conclusions}
 

### 2019-03-25 papers/Papers1234/bs-bw-dw-03.tex
Finish sec 6.4 and half of sec 6.3 of Paper III

@@
 
+We have proposed a novel diagnostic method, the \(\tau\)-\(eta\shell\)
+diagram, for analyzing observations of stellar bow shocks around OB
+stars, which allows discrimination between radiation-supported and
+wind-supported bows.  Our principal results are as follows:
+\begin{enumerate}[1.]
+\item The UV optical depth of the bow shell can be estimated from the
+  observed infrared shell luminosity \(L\IR\) and stellar luminosity
+  \(L_*\) as \(\tau = 2 L\IR/L_*\).
+\item With the  
+\end{enumerate}
+
 \section*{Acknowledgements}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/cygnus-bows-midir-combo}
-  \caption{Two bows in Cygnus}
-  \label{fig:cygnus-bows}
-\end{figure}
-
 \subsection{Source 342}

### 2019-03-25 papers/Papers1234/sec-observational-diagnostics.tex
Finish sec 6.4 and half of sec 6.3 of Paper III

@@
 
-\subsection{Why the two mass-loss methods differ}
+\subsection{Why do the two mass-loss methods differ?}
 \label{sec:underst-diff-betw}
@@
 \(R_{\text{c}}\), or equivalently the planitude:
-\(\Pi = R_{\text{c}} / R_0\)\citep{Tarango-Yong:2018a}.  This is
-illustrated in the inset to Figure~\ref{fig:H-versus-ell}, from which
-we find
+\(\Pi = R_{\text{c}} / R_0\)\citep{Tarango-Yong:2018a}.  The idealized
+geometry is illustrated in the inset to Figure~\ref{fig:H-versus-ell},
+from which we find
 \begin{equation}
@@
 corresponds closely to the \(h\shell/R_0 = 0.25\) that we have used,
-
-\subsection{Shared properties of candidates for radiation support}
+the sources with \(\ell/R_0 < 1\) are predicted to have thinner shells
+with \(h\shell/R_0 < 0.1\).  The four sources with the lowest values
+of \(\ell/R_0\) are labeled on the figure (369, 339, 382, 344) and
+these are precisely those sources that show the largest discrepancy
+between the two mass loss methods
+(Fig.~\ref{fig:mass-loss-comparison}).  Using a smaller value of
+\(h\shell\) would increase \(\eta\shell\) (eq.~[\ref{eq:eta-shell}])
+and hence \(\dot{M}\) (eq.~[\ref{eq:mdot-tau-eta}]), thereby reducing
+the discrepancy between the two methods.
+
+We choose not make this correction to the \(\tau\)--\(\eta\shell\)
+method in this paper since we want to test the methods using published
+data alone and without excessive fine-tuning.  However, for future
+applications an empirical measurement of the shell thicknesses would
+clearly help improve the reliability of the method.
+
+\subsection{Common characteristics of radiation-supported candidates}
 \label{sec:comm-prop-cand}
@@
 narrow range of spectral type\footnote{%
-  However, this is not particularly statistically significant.  For
+  However, the statistically significance is not strong.  For
   instance, out of the twenty K18 sources, 7 have spectral type O8 or
@@
   \(p = (1 - \frac{7}{20})^5 = 0.116\), which fails to meet the
-  conventional \(2\sigma\) significance level of \(p = 0.05\).} %
+  conventional \(2\sigma\) significance level of \(p = 0.05\),
+  thereby lending only weak support for rejection of the null.} %
 between O9 and B0, corresponding to
@@
 The small bow sizes are fully consistent with the expectations from
-theory developed in Paper~I.  Radiation-supported bows are predicted
+the theory developed in Paper~I.  Radiation-supported bows are predicted
 to occur either in high-density environments
@@
   In this case, the statistical significance is far higher, since
-  \(p = (\frac{5}{20})^4 = 0.0039\) for the null hypothesis.}  From
-equation~\eqref{eq:h-R0} this means they also should have thicker than
-average shells.  This is consistent with our finding from Paper~I's
-\S~3.3 that the shell tends to be broad in the radiation-supported bow
-wave regime.  Furthermore, if the larger than average \(H/R_0\) were
-to be taken account in the calculation of \(\eta\shell\)
-(eq.~\eqref{eq:eta-shell}), then it would strengthen the case for
-radiation support in these objects.
+  \(p = (\frac{5}{20})^4 = 0.0039\) for the null hypothesis, giving
+  strong support for its rejection.}  From equation~\eqref{eq:h-R0}
+this means they also should have thicker than average shells.  This is
+consistent with our finding from Paper~I's \S~3.3 that the shell tends
+to be broad in the radiation-supported bow wave regime.  Furthermore,
+if the larger than average \(H/R_0\) were to be taken account in the
+calculation of \(\eta\shell\) (eq.~[\ref{eq:eta-shell}]), then it
+would strengthen the case for radiation support in these objects.
 
@@
 
-Using emissivity at different wavelength, such as \SI{24}{\um}.  No
-good reason to fear stochastic heating.  They mention not getting 70/24 ratio right.  Probably be better with our correction.
-
-Correlations between observed parameters and with mass loss rates.
-Pair plot from my jupyter notebook.
-
-How both the UV opacity and the IR emissivity depend on the same VSG grains.
-
-Effects of grain evolution.  RATD destroying larger grains.  How would
-this effect the abundance of smaller grains? Calculate maximum grain
-size for the \(U\) distribution of the K18 sample.  Do we see any
-effects that seem to vary with \(U\)?
-
-Evidence for small grains around Arches cluster near Galactic center \citep{Hankins:2017a}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/cygnus-bows-midir-combo}
+  \caption{Two neighboring but highly contrasting bows in Cygnus:
+    KGK2010~2 (source~342) and KGK2010~1 (source~341). Each panel
+    shows the same \(3.6' \times 7.4'\) field, centered on equatorial
+    coordinates
+    \((\alpha, \delta) = 20^{\text{h}}34^{\text{m}}34.50^{\text{s}},
+    \ang{+41;58;27.4}\), but in different combinations of three
+    filters, as marked. }
+  \label{fig:cygnus-bows}
+\end{figure}
+
+K18 source~342 is the only source that shows a significant discrepancy
+\textit{above} the theoretical mass-loss rate predictions.  This is
+bow shock candidate~2 in a survey of mid-infrared arcs in Cygnus~X
+\citep{Kobulnicky:2010a}, and is referred to as KGK2010~2 in
+subsequent works.  For its early~B spectral type,
+\(\dot{M} \approx \SI{3e-9}{M_\odot.yr^{-1}}\) is expected, whereas
+the derived values from both mass-loss methods (panels a and b of
+Fig.~\ref{fig:mass-loss-vs-luminosity}) are about 10 times larger.
+This fact was already noted in K18, who suggested that the grain
+emissivity models may not be appropriate for this object.  We propose
+instead that the shell may be predominantly neutral instead of
+ionized, which might help explain other peculiar aspects of the
+source.  Figure~\ref{fig:cygnus-bows} shows infrared images of the
+field containing both sources~342 and 341.  The field is located in
+the Cygnus~X North region, between the DR~20 and DR~21 star forming
+regions, about \SI{17}{pc} north of the center of the Cygnus OB2
+association \citep[e.g.,][]{Schneider:2016a}.  It can be seen that the
+two bow shocks have very contrasting morphologies and spectra.
+Source~341 has a semi-circular shape, a very diffuse outer boundary,
+and is only prominent between wavelengths of \SI{12}{\um} and
+\SI{24}{\um}.  These characteristics are typical of many optically
+thin bows seen in fully ionized gas, such as the Ney--Allen nebula
+around \thD{} \citetext{compare the bow shape in Fig.~3a of
+  \citealp{Smith:2005a}}, source~406 \citetext{HD~92607, which is
+  ERO~36 in Carina, \citealp{Sexton:2015b}}, and the central star of
+RCW~120 \citetext{not included in current samples, but see
+  \citealp{Mackey:2015a, Mackey:2016a}}.  Source~342, on the other
+hand, has a more parabolic shape, a sharply defined arc, and emits
+strongly at all wavelengths from \SI{3.6}{\um} to \SI{150}{\um}
+\citetext{see also Fig.~13 of \citealp{Kobulnicky:2010a}}.  The
+parabolic arc shape and the broad SED are both reminiscent of LP~Ori
+(more details on the Orion Nebula bows will be provide in Paper~VI),
+and another bow that bears some similarities is Carina's Sickle object
+\citetext{ERO~21 \citealp{Sexton:2015b}, see also
+  \citealp{Ngoumou:2013a}}.  Note also the second outer arc in this
+source, which emits primarily at \SI{5.8}{\um} and \SI{7.9}{\um} and
+appears similar to the double-bow structure seen in IRAS~03063+5735
+\citep{Kobulnicky:2012a}.
+
+\subsection{Evolution of grain size}
+\label{sec:evolution-grain-size}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/xsec-dust-ratd-ism_10}
+  \caption{Change in dust opacity due to Radiative Torque Disruption
+    of large grains.  Black line shows the total absorption opacity of
+    Cloudy's standard ISM dust mixture.  The red line shows the result
+    of simulating the RATD process by removing the grains larger than
+    \SI{0.04}{\um} and distributing their mass among smaller grain
+    sizes.}
+  \label{fig:ratd}
+\end{figure}
+
+The properties of dust grains in bow shocks might be significantly
+different from those in the general interstellar medium, particularly
+because of the strong radiation field to which they are exposed, which
+has effects at both the small and large ends of the grain size
+distribution.  At the small end, sub-nanometer sized particles, such
+as PAHs can be destroyed by hard EUV photons
+\citep{Lebouteiller:2007a, Lebouteiller:2011a}.  Larger grains, on the
+other hand, are most vulnerable to Radiative Torque Disruption
+\citep[RATD;][]{Hoang:2018a}, see discussion in \S~6.4 of Paper~II.\@
+This is important for our diagnostics because it would tend to reduce
+the average grain size, while maintaining the same total grain mass,
+which would have the effect of increasing the ultraviolet opacity,
+while leaving the mid-infrared opacity unchanged.\footnote{The
+  mid-infrared emissivity, on the other hand, would also increase
+  since smaller grains tend to have higher radiative equilibrium
+  temperatures.} %
+We do not know the exact size distribution of fragments that would
+result from the RATD process, but we can estimate its effect by
+assuming that all grains with \(a > \SI{0.05}{\um}\) are transformed
+into grains with \(a = \text{\SIrange{0.025}{0.05}{\um}}\).  We
+implement this crudely in the Cloudy grain model
+(\S~\ref{sec:grain-temp-emiss}) by setting to zero the abundance of
+graphite and silicate grains in size bins 7, 8, 9, 10, while at the
+same time distributing their mass equally between size bins 5, and 6,
+which increases the abundance in those bins by factors of 5.19 and
+4.45, respectively.  The results are shown in Figure~\ref{fig:ratd},
+which shows the wavelength-dependent absorption opacity \(\kappa\) for
+both the standard ISM grain mixture and this RATD-modified mixture.
+As expected, the UV opacity is increased in the RATD mixture, but only
+by about 50\%, whereas the near-infrared opacity is decreased and the
+visual extinction becomes much steeper, which would correspond to a
+small total-to-selective extinction ratio of \(R_V < 3\).
+
+This modest increase in opacity from RATD grain processing is well
+within the systematic uncertainties that we have been assuming and so
+does not invalidate the results of the previous sections.  If the
+larger grains were instead to break up into many small fragments, the
+effect would be much larger.  If we repeat the above exercise, but
+assuming the fragment size is \(< \SI{0.01}{\um}\), then we find an
+increase by a factor of five in the UV opacity, but we do not feel
+that this is realistic. Studies of the break-up of fast-spinning small
+asteroids \citep{Hirabayashi:2015a, Zhang:2018a} show that when the
+tensile strength dominates over self-gravity, then stresses are
+highest in the center of the body, leading to break up into a small
+number of similarly sized pieces, as observed in asteroid P/2013~R3
+\citep{Jewitt:2014a}.  In the case of dust grains, the tensile
+strength and angular velocity are both far higher than in the asteroid
+case, but we expect a similar behavior so that the fragment size
+should be predominantly within a factor of about two below the
+critical size given in equation~(28) of \citet{Hoang:2018a}, as we
+assumed in Figure~\ref{fig:ratd}.
+
+% Using emissivity at different wavelength, such as \SI{24}{\um}.  No
+% good reason to fear stochastic heating.  They mention not getting 70/24 ratio right.  Probably be better with our correction.
+
+% How both the UV opacity and the IR emissivity depend on the same VSG grains.
+
+% Evidence for small grains around Arches cluster near Galactic center \citep{Hankins:2017a}
 

### 2019-03-26 papers/Papers1234/bs-bw-dw-03.tex
Finish everything except summary on Paper III

--- 2019-03-22 papers/Papers1234/bs-bw-dw-03.tex
@@
 
+We have proposed a novel diagnostic method, the \(\tau\)-\(\eta\shell\)
+diagram, for analyzing observations of stellar bow shocks around OB
+stars, which allows discrimination between radiation-supported and
+wind-supported bows.  Our principal results are as follows:
+\begin{enumerate}[1.]
+\item The UV optical depth \(\tau\) of the bow shell can be estimated
+  from the observed infrared shell luminosity \(L\IR\) and stellar
+  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\).
+\item The shell momentum efficiency \(\eta\shell\), which is the
+  fraction of stellar radiative momentum that is transferred to the
+  shell either directly or indirectly (via stellar wind), can be
+  estimated from \(\tau\) and the observed shell radius \(R_0\), after
+  making some auxiliary assumptions about the physical conditions in
+  the shell.
+\item By comparing \(\tau\) and \(\eta\shell\), it is possible to
+  discriminate between three regimes (see Paper~I): wind-supported bow
+  shocks (\(\eta\shell \gg \tau\)), radiation-supported bow waves
+  (\(\eta\shell \sim \tau < 1\)), and radiation-supported bow shocks
+  (\(\eta\shell \sim \tau > 1\)).
+\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a fourth
+  dust-wave regime where gas--grain collisional coupling may break
+  down (see Paper~II).
+\item 
+\end{enumerate}
+
 \section*{Acknowledgements}
@@
 
-\section{Notes on particular sources}
+% \section{Notes on particular sources}
+
+\section{The Herbig Be star V750~Mon}
 \label{sec:notes-part-sourc}
-
-\subsection{Source~380, HD~53367, V750~Mon}
 \label{sec:hd-53367-v750}
 
-This is a Herbig Be star with spectral type B0V--B0III and mass 12 to
-\SI{15}{M_\odot}, which shows long-scale irregular photometric
-variability \citep{Tjin-A-Djie:2001a, Pogodin:2006a} together with
-cyclic radial velocity variations, which are interpreted as an
-eccentric binary with a \SI{5}{M_\odot} pre-main-sequence companion.
-It is located outside the solar circle and, although it was originally
-classified as part of the CMa OB association at about \SI{1}{kpc}
-\citep{Tjin-A-Djie:2001a}, more recent estimates put it much closer.
-K18 assume a distance of \SI{260}{pc}, based on Hipparcos measurements
+K18 source~380 (HD~53367, V750~Mon) is a Herbig Be star with spectral
+type B0V--B0III and mass 12 to \SI{15}{M_\odot}, which shows
+long-scale irregular photometric variability \citep{Tjin-A-Djie:2001a,
+  Pogodin:2006a} together with cyclic radial velocity variations,
+which are interpreted as an eccentric binary with a \SI{5}{M_\odot}
+pre-main-sequence companion.  It is located outside the solar circle
+and, although it was originally classified as part of the CMa OB
+association at about \SI{1}{kpc} \citep{Tjin-A-Djie:2001a}, more
+recent estimates put it much closer.  K18 assume a distance of
+\SI{260}{pc}, based on Hipparcos measurements
 \citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
 \citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
-puts it closer still at \SI{140 \pm 30}{pc}.\footnote{%
-  Median and 90\% confidence interval, estimated from Bayesian
-  inference using an exponential density distribution with scale
-  length of \SI{1350}{pc} as a prior (see
-  \url{https://github.com/agabrown/astrometry-inference-tutorials/}). }
+puts it closer still at \SI{140 \pm 30}{pc}.  This is the median and
+90\% confidence interval, estimated from Bayesian
+inference\footnote{\url{https://github.com/agabrown/astrometry-inference-tutorials/}.}
+using an exponential density distribution with scale length of
+\SI{1350}{pc} as a prior.
 
@@
 
-\subsection{Source 407, HD~93249}
-\label{sec:source-407}
+% \subsection{Source 407, HD~93249}
+% \label{sec:source-407}
 
-TODO
+% TODO
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/cygnus-bows-midir-combo}
-  \caption{Two bows in Cygnus}
-  \label{fig:cygnus-bows}
-\end{figure}
+% \subsection{Source 342}
+% \label{sec:source-342}
 
-\subsection{Source 342}
-\label{sec:source-342}
+% Source~342 is anomalous in both methods. Has high mass loss for low luminosity.
 
-Source~342 is anomalous in both methods. Has high mass loss for low luminosity.
+% \subsection{Source 344}
+% \label{sec:source-344}
 
-\subsection{Source 344}
-\label{sec:source-344}
-
-This has big disagreement between K18 and me.  My mass-loss rate seems too low, given its high luminosity. Why?
+% This has big disagreement between K18 and me.  My mass-loss rate seems too low, given its high luminosity. Why?
 

### 2019-03-26 papers/Papers1234/sec-observational-diagnostics.tex
Finish everything except summary on Paper III

@@
 
-\section{Stellar wind mass-loss rates}
-\label{sec:stellar-wind-mass}
-
-Various methods have been proposed to derive stellar wind mass-loss
-rates from observations of stellar bow shocks \citetext{for example,
-  \citealp{Kobulnicky:2010a, Gvaramadze:2012a, Kobulnicky:2018a}}.  In
-this section, we will show how the \(\tau\)--\(\eta\shell\) diagram can be
-used to derive the mass-loss rate for bows in the wind-supported
-regime.  We then compare our method with the method used by
-\citet{Kobulnicky:2018a}, which is a refinement of that originally
-proposed in \citet{Kobulnicky:2010a}.  The method used by
-\citet{Gvaramadze:2012a} uses combined measurements of the bow shock
-and the surrounding \hii{} region.  It has the advantage of depending
-on fewer free parameters than the other methods, but can only be used
-in the case of isolated stars, whereas the majority of the sources
-considered here are in cluster environments.
-
-\subsection{Mass loss determination from the \boldmath \(\tau\)--\(\eta\shell\) diagram}
-\label{sec:mass-loss-determ}
 \begin{figure*}
@@
 \end{figure*}
+
+\section{Stellar wind mass-loss rates}
+\label{sec:stellar-wind-mass}
+
+Various methods have been proposed to derive stellar wind mass-loss
+rates from observations of stellar bow shocks \citetext{for example,
+  \citealp{Kobulnicky:2010a, Gvaramadze:2012a, Kobulnicky:2018a}}.  In
+this section, we will show how the \(\tau\)--\(\eta\shell\) diagram can be
+used to derive the mass-loss rate for bows in the wind-supported
+regime.  We then compare our method with the method used by
+\citet{Kobulnicky:2018a}, which is a refinement of that originally
+proposed in \citet{Kobulnicky:2010a}.  The method used by
+\citet{Gvaramadze:2012a} uses combined measurements of the bow shock
+and the surrounding \hii{} region.  It has the advantage of depending
+on fewer free parameters than the other methods, but can only be used
+in the case of isolated stars, whereas the majority of the sources
+considered here are in cluster environments.
+
+\subsection{Mass loss determination from the \boldmath \(\tau\)--\(\eta\shell\) diagram}
+\label{sec:mass-loss-determ}
 
@@
 
-\textit{Write about sigma Ori}
-
 \subsection{Mass loss determination method of \protect\citet{Kobulnicky:2018a}}
@@
 \end{figure}
-
-\newcommand\LOS{\ensuremath{_{\text{los}}}}
 
@@
 
-\subsection{Why do the two mass-loss methods differ?}
+In this section we discuss various issues related to our results,
+beginning in \S~\ref{sec:evolution-grain-size} with a consideration of
+how the optical properties of the grain population in bow shocks might
+be affected by the extreme radiation environment.  This is followed by
+examination of various sub-groups of sources that are unusual in some
+way: those where the two mass-loss methods give discrepant results
+(\S~\ref{sec:underst-diff-betw}), those that may be
+radiation-supported (\S~\ref{sec:comm-prop-cand}), and one source that
+shows a very large apparent mass-loss rate for its luminosity
+(\S~\ref{sec:anomalous-b-star}).
+
+\subsection{Evolution of grain size}
+\label{sec:evolution-grain-size}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/xsec-dust-ratd-ism_10}
+  \caption{Change in dust opacity due to Radiative Torque Disruption
+    of large grains.  Black line shows the total absorption opacity of
+    Cloudy's standard ISM dust mixture.  The red line shows the result
+    of simulating the RATD process by removing the grains larger than
+    \SI{0.04}{\um} and distributing their mass among smaller grain
+    sizes.}
+  \label{fig:ratd}
+\end{figure}
+
+The properties of dust grains in bow shocks might be significantly
+different from those in the general interstellar medium, particularly
+because of the strong radiation field to which they are exposed, which
+has effects at both the small and large ends of the grain size
+distribution.  At the small end, sub-nanometer sized particles, such
+as PAHs can be destroyed by hard EUV photons
+\citep{Lebouteiller:2007a, Lebouteiller:2011a}.  Larger grains, on the
+other hand, are most vulnerable to Radiative Torque Disruption
+\citep[RATD;][]{Hoang:2018a}, see discussion in \S~6.4 of Paper~II.\@
+This is important for our diagnostics because it would tend to reduce
+the average grain size, while maintaining the same total grain mass,
+which would have the effect of increasing the ultraviolet opacity,
+while leaving the mid-infrared opacity unchanged.\footnote{The
+  mid-infrared emissivity, on the other hand, would also increase
+  since smaller grains tend to have higher radiative equilibrium
+  temperatures.} %
+We do not know the exact size distribution of fragments that would
+result from the RATD process, but we can estimate its effect by
+assuming that all grains with \(a > \SI{0.05}{\um}\) are transformed
+into grains with \(a = \text{\SIrange{0.025}{0.05}{\um}}\).  We
+implement this crudely in the Cloudy grain model
+(\S~\ref{sec:grain-temp-emiss}) by setting to zero the abundance of
+graphite and silicate grains in size bins 7, 8, 9, 10, while at the
+same time distributing their mass equally between size bins 5, and 6,
+which increases the abundance in those bins by factors of 5.19 and
+4.45, respectively.  The results are shown in Figure~\ref{fig:ratd},
+which shows the wavelength-dependent absorption opacity \(\kappa\) for
+both the standard ISM grain mixture and this RATD-modified mixture.
+As expected, the UV opacity is increased in the RATD mixture, but only
+by about 50\%, whereas the near-infrared opacity is decreased and the
+visual extinction becomes much steeper, which would correspond to a
+small total-to-selective extinction ratio of \(R_V < 3\).
+
+This modest increase in opacity from RATD grain processing is well
+within the systematic uncertainties that we have been assuming and so
+does not invalidate the results of the previous sections.  If the
+larger grains were instead to break up into many small fragments, the
+effect would be much larger.  If we repeat the above exercise, but
+assuming the fragment size is \(< \SI{0.01}{\um}\), then we find an
+increase by a factor of five in the UV opacity, but we do not feel
+that this is realistic. Studies of the break-up of fast-spinning small
+asteroids \citep{Hirabayashi:2015a, Zhang:2018a} show that when the
+tensile strength dominates over self-gravity, then stresses are
+highest in the center of the body, leading to break up into a small
+number of similarly sized pieces, as observed in asteroid P/2013~R3
+\citep{Jewitt:2014a}.  In the case of dust grains, the tensile
+strength and angular velocity are both far higher than in the asteroid
+case, but we expect a similar behavior so that the fragment size
+should be predominantly within a factor of about two below the
+critical size given in equation~(28) of \citet{Hoang:2018a}, as we
+assumed in Figure~\ref{fig:ratd}.
+
+\subsection{Why do results of the two mass-loss methods differ?}
 \label{sec:underst-diff-betw}
@@
 is ``explained'' by the variance in the \(x\) quantity (although this
-cannot necessarily be taken to imply causation in either
-direction). For some correlations, we also mark the linear regression
-slope, \(m\).  Since we are working in logarithmic space, this is
-equal to the power index in the relation \(y \propto x^m\).  Some
-selected weaker correlations are also shown (fainter text).
+cannot necessarily be taken to imply causation in either direction
+since it might be due to the fact that both \(x\) and \(y\) are
+partially determined by a third quantity, \(z\)). For some
+correlations, we also mark the linear regression slope, \(m\).  Since
+we are working in logarithmic space, this is equal to the power index
+in the relation \(y \propto x^m\).  Some selected weaker correlations
+are also shown (fainter text).
 
@@
 \(R_{\text{c}}\), or equivalently the planitude:
-\(\Pi = R_{\text{c}} / R_0\)\citep{Tarango-Yong:2018a}.  The idealized
+\(\Pi = R_{\text{c}} / R_0\) \citep{Tarango-Yong:2018a}.  The idealized
 geometry is illustrated in the inset to Figure~\ref{fig:H-versus-ell},
@@
 emissivity models may not be appropriate for this object.  We propose
-instead that the shell may be predominantly neutral instead of
-ionized, which might help explain other peculiar aspects of the
-source.  Figure~\ref{fig:cygnus-bows} shows infrared images of the
-field containing both sources~342 and 341.  The field is located in
-the Cygnus~X North region, between the DR~20 and DR~21 star forming
-regions, about \SI{17}{pc} north of the center of the Cygnus OB2
-association \citep[e.g.,][]{Schneider:2016a}.  It can be seen that the
-two bow shocks have very contrasting morphologies and spectra.
+instead to investigate the idea that the shell may be predominantly
+neutral instead of ionized, which might help explain other peculiar
+aspects of the source.  Figure~\ref{fig:cygnus-bows} shows infrared
+images of the field containing both sources~342 and 341.  The field is
+located in the Cygnus~X North region, between the DR~20 and DR~21 star
+forming regions, about \SI{17}{pc} north of the center of the Cygnus
+OB2 association \citep[e.g.,][]{Schneider:2016a}.  It can be seen that
+the two bow shocks have very contrasting morphologies and spectra.
 Source~341 has a semi-circular shape, a very diffuse outer boundary,
@@
   \citealp{Mackey:2015a, Mackey:2016a}}.  Source~342, on the other
-hand, has a more parabolic shape, a sharply defined arc, and emits
-strongly at all wavelengths from \SI{3.6}{\um} to \SI{150}{\um}
-\citetext{see also Fig.~13 of \citealp{Kobulnicky:2010a}}.  The
-parabolic arc shape and the broad SED are both reminiscent of LP~Ori
-(more details on the Orion Nebula bows will be provide in Paper~VI),
-and another bow that bears some similarities is Carina's Sickle object
-\citetext{ERO~21 \citealp{Sexton:2015b}, see also
-  \citealp{Ngoumou:2013a}}.  Note also the second outer arc in this
-source, which emits primarily at \SI{5.8}{\um} and \SI{7.9}{\um} and
-appears similar to the double-bow structure seen in IRAS~03063+5735
-\citep{Kobulnicky:2012a}.
-
-\subsection{Evolution of grain size}
-\label{sec:evolution-grain-size}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/xsec-dust-ratd-ism_10}
-  \caption{Change in dust opacity due to Radiative Torque Disruption
-    of large grains.  Black line shows the total absorption opacity of
-    Cloudy's standard ISM dust mixture.  The red line shows the result
-    of simulating the RATD process by removing the grains larger than
-    \SI{0.04}{\um} and distributing their mass among smaller grain
-    sizes.}
-  \label{fig:ratd}
-\end{figure}
-
-The properties of dust grains in bow shocks might be significantly
-different from those in the general interstellar medium, particularly
-because of the strong radiation field to which they are exposed, which
-has effects at both the small and large ends of the grain size
-distribution.  At the small end, sub-nanometer sized particles, such
-as PAHs can be destroyed by hard EUV photons
-\citep{Lebouteiller:2007a, Lebouteiller:2011a}.  Larger grains, on the
-other hand, are most vulnerable to Radiative Torque Disruption
-\citep[RATD;][]{Hoang:2018a}, see discussion in \S~6.4 of Paper~II.\@
-This is important for our diagnostics because it would tend to reduce
-the average grain size, while maintaining the same total grain mass,
-which would have the effect of increasing the ultraviolet opacity,
-while leaving the mid-infrared opacity unchanged.\footnote{The
-  mid-infrared emissivity, on the other hand, would also increase
-  since smaller grains tend to have higher radiative equilibrium
-  temperatures.} %
-We do not know the exact size distribution of fragments that would
-result from the RATD process, but we can estimate its effect by
-assuming that all grains with \(a > \SI{0.05}{\um}\) are transformed
-into grains with \(a = \text{\SIrange{0.025}{0.05}{\um}}\).  We
-implement this crudely in the Cloudy grain model
-(\S~\ref{sec:grain-temp-emiss}) by setting to zero the abundance of
-graphite and silicate grains in size bins 7, 8, 9, 10, while at the
-same time distributing their mass equally between size bins 5, and 6,
-which increases the abundance in those bins by factors of 5.19 and
-4.45, respectively.  The results are shown in Figure~\ref{fig:ratd},
-which shows the wavelength-dependent absorption opacity \(\kappa\) for
-both the standard ISM grain mixture and this RATD-modified mixture.
-As expected, the UV opacity is increased in the RATD mixture, but only
-by about 50\%, whereas the near-infrared opacity is decreased and the
-visual extinction becomes much steeper, which would correspond to a
-small total-to-selective extinction ratio of \(R_V < 3\).
-
-This modest increase in opacity from RATD grain processing is well
-within the systematic uncertainties that we have been assuming and so
-does not invalidate the results of the previous sections.  If the
-larger grains were instead to break up into many small fragments, the
-effect would be much larger.  If we repeat the above exercise, but
-assuming the fragment size is \(< \SI{0.01}{\um}\), then we find an
-increase by a factor of five in the UV opacity, but we do not feel
-that this is realistic. Studies of the break-up of fast-spinning small
-asteroids \citep{Hirabayashi:2015a, Zhang:2018a} show that when the
-tensile strength dominates over self-gravity, then stresses are
-highest in the center of the body, leading to break up into a small
-number of similarly sized pieces, as observed in asteroid P/2013~R3
-\citep{Jewitt:2014a}.  In the case of dust grains, the tensile
-strength and angular velocity are both far higher than in the asteroid
-case, but we expect a similar behavior so that the fragment size
-should be predominantly within a factor of about two below the
-critical size given in equation~(28) of \citet{Hoang:2018a}, as we
-assumed in Figure~\ref{fig:ratd}.
+hand, has a more parabolic shape, a sharply defined outer boundary to
+its arc, and emits strongly at all wavelengths from \SI{3.6}{\um} to
+\SI{150}{\um} \citetext{see also Fig.~13 of
+  \citealp{Kobulnicky:2010a}}.  The parabolic arc shape and the broad
+SED are both reminiscent of LP~Ori (more details on the Orion Nebula
+bows will be provide in Paper~VI), and another bow that bears some
+similarities is Carina's Sickle object \citetext{ERO~21
+  \citealp{Sexton:2015b}, see also \citealp{Ngoumou:2013a} and \S~4 of
+  \citealp{Hartigan:2015a}}.  Note also the second outer rim in this
+source, which emits primarily at \SI{5.8}{\um}, \SI{7.9}{\um}, and
+\SI{12}{\um}. This appears similar to the double-bow structure seen in
+IRAS~03063+5735 \citep{Kobulnicky:2012a}.  Finally, it has the coldest
+dust of any of the K18 sources, as determined from the mid-to-far
+infrared color temperatures (\(T_{22/70} = \SI{70}{K}\),
+\(T_{70/150} = \SI{69}{K}\) from Tab.~5 of
+\citealp{Kobulnicky:2017a}).
+
+If source~342 has trapped the ionization front in its shell, then
+\(\eta\shell\) has been overestimated and the source should be moved
+vertically down on Figure~\ref{fig:All-sources-eta-tau} in a similar
+way to LP~Ori.  The exact correction factor is unknown, since it
+depends on the temperature and magnetic field in the neutral shell,
+but it could easily be of order 10, which would take the shell into
+the radiation-supported regime.  The derived mass-loss rate would
+hence be reduced from the anomalously high value of
+Figure~\ref{fig:mass-loss-comparison} to essentially zero.  However,
+this requires that the shell be capable of absorbing all the ionizing
+photons from the central star, which implies a lower limit to the
+shell optical depth: \(\tau > \tau\iftrap\), see Paper~I's
+\S~3.1.\footnote{%
+  Note that \(\tau\iftrap < 1\) is allowed, since \(\tau\) is the
+  ultraviolet \emph{dust} optical depth of the shell, whereas it is
+  the EUV \textit{gas} opacity that is most important for trapping the
+  ionization front.  } %
+In the radiation-supported bow wave (RBW) regime this is
+\begin{equation}
+  \label{eq:tau-trap-rbw}
+  \text{RBW:}\quad \tau\iftrap \approx 7.1 \, \left( \frac{S_{49} \, \kappa_{600}}{L_4} \right)^{1/2} \ ,
+\end{equation}
+while in the wind-supported bow shock (WBS) regime it is
+\begin{equation}
+  \label{eq:tau-trap-wbs}
+  \text{WBS:}\quad \tau\iftrap \approx 102 \, \frac{S_{49} \, \kappa_{600}}{\eta\wind\, L_4}  \ .
+\end{equation}
+In these equations, which are derived from equations~(8, 10, 12, 24)
+of Paper~I, \(S_{49}\) is the ionizing photon luminosity of the star
+in units of \SI{e49}{s^{-1}}, while \(L_4\) and \(\kappa_{600}\) are
+defined in \S~\ref{sec:energy-trapp-vers} and \(\eta\wind\) in
+\S~\ref{sec:mass-loss-determ}.  Within the uncertainties, the
+observationally inferred spectral type of B0--B2V of source~342 is the
+same as the \SI{10}{M_\odot} main-sequence star used in Papers~I
+and~II, which has a ratio of ionizing to bolometric luminosity
+\(S_{49}/L_4 = \num{2.1e-4}\).  Substituting into
+equation~\eqref{eq:tau-trap-rbw} yields \(\tau\iftrap \approx 0.1 \)
+for the RBW case, whereas the observed optical depth is more than an
+order of magnitude lower: \(\tau \approx 0.005\).  Similar
+difficulties arise if one assumes a wind-supported bow shock, in which
+case \(\tau < \eta\wind\) by definition.  Combined with
+equation~\eqref{eq:tau-trap-wbs}, this then implies a lower limit for
+the wind momentum efficiency: \(\eta\wind > 0.14\).  Given that we
+must always have \(\eta\shell \ge \eta\wind\)
+(eq.~[\ref{eq:eta-shell-components}]), this is inconsistent with the
+observed \(\eta\shell = 0.07 T_4 / \kappa_{600} h_{1/4}\), especially
+since the whole point of the exercise is to reduce \(\eta\shell\) via
+a reduction in \(T_4\).
+
+Therefore, we have shown that a neutral shell is not consistent with
+the observational data for source~342, and so this is unlikely to be
+the explanation for the seemingly high mass loss rate.  Instead, it is
+possible that the explanation is simply that the stellar luminosity
+has been underestimated, since the luminosity class is not well
+constrained by spectroscopy (K18).  If the star were B1~III instead of
+B1~V, then the luminosity would be 4 times higher.  This could be due
+to a combination of having underestimated the distance and having
+underestimated the foreground extinction.  The assumed distance of
+\(D= \SI{1.3}{kpc}\) comes from a study of eclipsing binaries in the
+Cygnus~OB2 association \citep{Kiminki:2015a}, but GAIA~DR2 parallaxes
+for the association clearly show two sub-groups at
+\(D = \SI{1.76}{kpc}\) and \SI{1.35}{kpc}, with the farther group
+being the dominant one \citep{Berlanas:2019a}.  The GAIA parallax for
+source~342 yields a median and 90\% confidence interval of
+\(1.65^{+0.18}_{-0.16} \, \si{kpc}\) (same methodology as
+App.~\ref{sec:hd-53367-v750}),
+% \SIrange{1.49}{1.83}{kpc}
+which clearly indicates it is in the farther group.  Taking the median
+distance of \SI{1.65}{kpc} would raise \(L_*\) by a factor 1.61 and
+increasing the visual extinction \(A_V\) by 1 magnitude would give an
+additional factor of 2.51 for a total increase by \(\approx 4\), as we
+are looking for.  To find the effects on the derived quantities, we
+can sum the Jacobian elements in the first two rows of
+Table~\ref{tab:derived-parameters}, multiplied by the changes in
+observed log quantities: \(\Delta D \approx \SI{+0.1}{dex}\) and
+\(\Delta L_* \approx \SI{+0.6}{dex}\). For example:
+\begin{equation}
+  \label{eq:delta-derived}
+  \Delta\tau = J_D(\tau)\, \Delta D + J_{L_*}(\tau)\, \Delta L_*
+\end{equation}
+and similarly for the other quantities.  This yields
+\(\Delta \tau \approx \SI{-0.4}{dex}\),
+\(\Delta \eta\shell \approx \SI{-0.9}{dex}\),
+\(\Delta \dot{M} \approx \SI{-0.3}{dex}\), and
+\(\Delta \dot{M}_{\text{K18}} \approx \SI{-0.1}{dex}\).  In
+Figure~\ref{fig:mass-loss-vs-luminosity}a this would move source~342
+substantially to the right and slightly down, thus transforming it
+from an extreme outlier to an unremarkable source in the center of the
+pack.  It would be disappointing if such a prosaic explanation were
+the correct one, given all the other peculiarities of this source
+listed in the first paragraph of this section.  However, based on
+current evidence, the more interesting and exotic explanations are
+less plausible.
 

### 2019-03-26 papers/Papers1234/bs-bw-dw-03.tex
Write summary for Paper III

@@
   from the observed infrared shell luminosity \(L\IR\) and stellar
-  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\).
+  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\)
+  (\S~\ref{sec:energy-trapp-vers}).
 \item The shell momentum efficiency \(\eta\shell\), which is the
@@
   making some auxiliary assumptions about the physical conditions in
-  the shell.
+  the shell (\S~\ref{sec:energy-trapp-vers}).
 \item By comparing \(\tau\) and \(\eta\shell\), it is possible to
-  discriminate between three regimes (see Paper~I): wind-supported bow
-  shocks (\(\eta\shell \gg \tau\)), radiation-supported bow waves
+  discriminate between three regimes (\S~\ref{sec:eta-tau-diagnostic}
+  and see Paper~I): wind-supported bow shocks
+  (\(\eta\shell \gg \tau\)), radiation-supported bow waves
   (\(\eta\shell \sim \tau < 1\)), and radiation-supported bow shocks
   (\(\eta\shell \sim \tau > 1\)).
-\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a fourth
-  dust-wave regime where gas--grain collisional coupling may break
-  down (see Paper~II).
-\item 
+\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a
+  fourth regime of dust waves, where gas--grain collisional coupling
+  breaks down (see Paper~II).
+\item By analyzing a published sample of 20 mid-infrared bow shock
+  candidates \citep[K18]{Kobulnicky:2018a}, plus additional compact
+  bows in Orion, we find 4 strong candidates for radiation-supported
+  bow waves plus 3 marginal cases (\S\S~\ref{sec:cand-radi-supp} and
+  \ref{sec:comm-prop-cand}).  No strong candidates for dust waves are
+  found.
+\item For wind-supported bow shocks, the stellar wind mass-loss rate
+  can be found from \(\tau\) and \(\eta\shell\)
+  (\S~\ref{sec:mass-loss-determ}). We compare this method with the
+  previously proposed method of K18 (\S~\ref{app:bow-shock-data}) and
+  suggest a correction to the dust emissivities used in the latter,
+  which reduces the mass-loss rates by a factor of about 2.
+\item After this correction, the two mass-loss methods agree well for
+  small bows (\(R_0 \le \SI{0.3}{pc}\)), but the
+  \(\tau\)--\(\eta\shell\) method under-predicts the mass-loss rate by
+  up to a factor of 10 for larger bows, which also tend to have
+  relatively thin shells (\S~\ref{sec:underst-diff-betw}).  This
+  discrepancy could be eliminated by extending the
+  \(\tau\)--\(\eta\shell\) method to include the observed shell
+  thickness.
+\item Disruption of the largest dust grains by rotational torques in
+  the strong circumstellar radiation field is predicted to have a
+  relatively modest effect on the optical properties of the dust
+  mixture (\S~\ref{sec:evolution-grain-size}), increasing the UV
+  opacity by about 50\%.
 \end{enumerate}

### 2019-03-26 papers/Papers1234/bs-bw-dw-03.tex
Fix abstract for Paper III

@@
   at mid-infrared wavelengths in the range \SIrange{8}{60}{\um}. We
-  propose a novel diagnostic method, the \(\tau\)--\(\eta\) diagram, for
-  analyzing these bows, which is based on comparing the fractions of
-  stellar radiative energy and stellar radiative momentum that is
+  propose a novel diagnostic method, the \(\tau\)--\(\eta\) diagram,
+  for analyzing these bows, which is based on comparing the fractions
+  of stellar radiative energy and stellar radiative momentum that is
   trapped by the bow shell.  This diagram allows the discrimination of
-  radiation-supported bows from wind-supported bows.  For the latter,
-  it allows the stellar wind mass loss rate to be determined.  We
-  critically compare our method with a previous method that has been
-  proposed for determining wind mass loss rates from bow shock
-  observations. We find that the dust emissivity model used previously
-  needs to be corrected to account for differences in the spectral
-  energy distribution between OB stars and the interstellar radiation
-  field, which results in a downward revision by a factor of two in
-  the mass loss rates.  After correction, the methods complement one
-  another to some degree, with differing sensitivities to systematic
-  model uncertainties.  We point out that observations of bows are of
-  limited utility in constraining mass loss rates of weak-wind stars,
-  since these tend to have radiation-supported bows, which yield only
-  upper limits to the mass loss rate.
+  wind-supported bow shocks, radiation-supported bow waves, and dust
+  waves in which grains decouple from the gas.  For the wind-supported
+  bow shocks, it allows the stellar wind mass loss rate to be
+  determined.  We critically compare our method with a previous method
+  that has been proposed for determining wind mass-loss rates from bow
+  shock observations. This comparison points to ways in which both
+  methods can be improved and suggests a downward revision by a factor
+  of two with respect to previously reported mass-loss rates.  From a
+  sample of 23 mid-infrared bow-shaped sources, we identify 4 strong
+  candidates for radiation-supported bow waves, which need to be
+  confirmed by more detailed studies, but no strong candidates for
+  dust waves.
 \end{abstract}
@@
   Astropy-Collaboration:2018a} and Pandas \citep{McKinney:2010a}
-projects.  We thank Chip Kobulnicky for useful discussions.
+projects.  We thank Chip Kobulnicky for sharing results in advance of
+publication.
 

### 2019-03-30 papers/Papers1234/app-cloudy-dust-heating.tex
Fix abstract for Paper III
Finish source 342 revision - start on general intro

@@
     field in the solar neighborhood (orange line).  The OB star is the
-    \SI{20}{M_\odot} model from Table~\ref{tab:stars} and is plotted for a
-    distance from the star of \SI{1}{pc}.  The interstellar SED is
+    \SI{20}{M_\odot} model from Table~1 of Paper~I and is plotted for
+    a distance from the star of \SI{1}{pc}.  The interstellar SED is
     from \citet{Mathis:1983a} and is multiplied by \num{80} so that
@@
 \subsubsection{Stochastic single-photon heating}
-
+\label{sec:stoch-single-phot}
 When the radiation field is sufficiently dilute, then a grain that

### 2019-03-30 papers/Papers1234/bs-bw-dw-03.tex
Finish source 342 revision - start on general intro

@@
   waves in which grains decouple from the gas.  For the wind-supported
-  bow shocks, it allows the stellar wind mass loss rate to be
+  bow shocks, it allows the stellar wind mass-loss rate to be
   determined.  We critically compare our method with a previous method
@@
   of two with respect to previously reported mass-loss rates.  From a
-  sample of 23 mid-infrared bow-shaped sources, we identify 4 strong
-  candidates for radiation-supported bow waves, which need to be
-  confirmed by more detailed studies, but no strong candidates for
+  sample of 23 mid-infrared bow-shaped sources, we identify at least 4
+  strong candidates for radiation-supported bow waves, which need to
+  be confirmed by more detailed studies, but no strong candidates for
   dust waves.
@@
 
+Early searches for bow shocks around OB stars \citep{van-Buren:1995a}
+concentrated on runaway stars \citep{Hoogerwerf:2011a} that have been ejected at high
+velocities (\(> \SI{30}{km.s^{-1}}\)) due to multi-body encounters in
+star clusters or the core-collapse supernova of a binary companion.
+
+Walkaways \citep{Renzo:2018a}
+
+Absence of bow shocks \citep{Huthoff:2002a} HMXRBs \citep{Prisegen:2019a}
+
+High-mass x-ray binaries
+
+WISE surveys \citep{Peri:2012a, Peri:2015a} and Spitzer surveys \citep{Kobulnicky:2016a, Kobulnicky:2017a, Kobulnicky:2018a}.
+Particular high-mass star forming regions such as Carina \citep{Sexton:2015a}, Cygnus~X \citep{Kobulnicky:2010a}
+
+Galactic Center region H1 \citep{Dong:2017a} (UCHII)
+
+were originally searched for \citep{Noriega-Crespo:1997b} in the context of
+
+In the Orion Nebula, at least three different classes of stellar bow
+shocks have been identified. As well as small number of OB bow shocks \citep{Smith:2005a, ODell:2001c},
+
+HMXRB in external galaxies, possible bowshock in LMC~X-1 \citep{Hyde:2017a}.
+
+Non-thermal radio emission from BD+43~3654 \citep{Benaglia:2010a}, has been searched for but
+
+Analytic and semi-analytic thin-shell models of bow shocks
+\citep{van-Buren:1992a, Wilkin:1996a, Canto:1996a}, including
+non-spherical winds and nonaxisymmetric bows \citep{Wilkin:2000a,
+  Henney:2002a, Canto:2005a, Tarango-Yong:2018a}.  Numerical
+hydrodynamic simulations \citep{Matsuda:1989a, Raga:1997a}
+
+Slow subsonic velocities of a star through its \hii{} region may be
+sufficient \citep{Mackey:2015a, Mackey:2016a} to distort the inner
+stellar wind shock and produce a bow shock appearance, even though
+there is no shock in the dusty ambient stream.
+
+Cooler red supergiant and asymptotic giant branch stars
+\citep{Ueta:2008a, Sahai:2010a, Cox:2012a}.
+
 In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
@@
 (RBW) and optically thick radiation-supported bow shocks (RBS).  When
-the dust decouples from the gas (Paper~II), one has inertia-confined
-dust waves (IDW) and drag-confined dust waves (DDW).
+the dust decouples from the gas (Paper~II), inertia-confined dust
+waves (IDW) and drag-confined dust waves (DDW) can result.
 
@@
 estimating the stellar wind mass loss rates from observations of the
-bows.  In \S~\ref{sec:conclusions} we summarise out findings.
+bows. In \S~\ref{sec:discussion} we discuss various groups of bows
+that require special treatment due to their diverse physical
+conditions. In \S~\ref{sec:conclusions} we summarise out findings.
 

### 2019-03-30 papers/Papers1234/sec-observational-diagnostics.tex
Finish source 342 revision - start on general intro

@@
 in Table~5 of K17 and Tables~1 and~2 of K18. In this section, we
-outline how we obtain \(\tau\) and \(\eta\shell\) from the data in these
-catalogs, while further aspects of the \citeauthor{Kobulnicky:2018a}
-material are discussed in \S~\ref{app:bow-shock-data}.
+outline how we obtain \(\tau\) and \(\eta\shell\) from the data in
+these catalogs, while further aspects of the
+\citeauthor{Kobulnicky:2018a} material are discussed in
+\S~\ref{app:bow-shock-data}.  As this paper was being written, we
+became aware of a new mass-loss study that greatly expands on the
+earlier results of K18 (H.~Kobulnicky, priv.~comm.).  The new study
+includes 70 bow shock sources and incorporates Gaia distances and
+proper motions, together with new optical/IR spectroscopy of the
+central stars.  Apart from making use of an updated spectral
+classification of one source (\S~\ref{sec:anomalous-b-star}), we have
+elected to concentrate on only the published K18 sample in this paper,
+but will address the expanded sample in future publications.
 
@@
     between OB stars and the Galactic interstellar radiation field
-    (see App.~\ref{sec:grain-temp-emiss}).}
+    (see \S~\ref{sec:grain-temp-emiss}).}
   \label{fig:k18-emissivity}
@@
 provide an important cross check on one another.  However, as
-explained in detail in \S~\ref{sec:grain-temp-emiss}, the
-\(j_\nu(U)\) relation depends on the shape of the illuminating SED,
-which means that the \citet{Draine:2007a} models require modification
-when applied to grains around OB stars.  In addition, when attempting
-to replicate the K18 values of \(j_{70}\) we find that they only
-follow the \citet{Draine:2007a} values for \(U > \num{e4}\), tending
-to a constant value for weaker radiation fields.  The situation is
+explained in detail in \S~\ref{sec:grain-temp-emiss}, the \(j_\nu(U)\)
+relation depends on the shape of the illuminating SED, which means
+that the \citet{Draine:2007a} models require modification when applied
+to grains around OB stars.  In addition, when attempting to replicate
+the K18 values of \(j_{70}\) we find that they only follow the
+\citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
+constant value for weaker radiation fields.  The situation is
 summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
@@
 consistent with that shown in K18 Fig.~2), and the values they
-\textit{should} have been using are shown by the gray dashed line.
+\textit{should} have been using are shown by the gray dashed
+line. Note that this correction may also resolve the color temperature
+discrepancy noted by \citet{Kobulnicky:2017a}.
 
@@
 applications an empirical measurement of the shell thicknesses would
-clearly help improve the reliability of the method.
+clearly help improve the reliability of the \(\tau\)--\(\eta\shell\)
+method.
+
+It is hard to say which of the two mass-loss methods is ``better'',
+except that the \(\tau\)--\(\eta\shell\) method has the advantage of
+being able to identify radiation-supported bows, for which the mass
+loss cannot be determined.  We recommend that both be employed if
+possible as a cross-check on one another.  The
+\(\tau\)--\(\eta\shell\) method has the disadvantage of requiring
+shell photometry at a range of wavelengths: \SIrange{8}{70}{\um} in
+order to be sure of covering the bulk of the grain emission, whereas
+the K18 method needs only the \SI{70}{\um} surface brightness.  On the
+other hand, we suspect that this makes the \(\tau\)--\(\eta\shell\)
+method less sensitive to possible variations in grain composition and
+size distribution.  This is because it depends on the average grain
+opacity over a broad range of ultraviolet wavelengths, rather than the
+emissivity in a single infrared band.  Additionally, many bows are
+weak emitters at \SI{70}{\um}, whereas the background emission from
+the PDRs surrounding \hii{} regions is very bright and variable.  The
+contrast of the bow against the background is usually much higher at
+\SI{24}{\um}, but K18 avoid this waveband on the grounds that it may
+be dominated by emission from stochastic heating of very small grains.
+We maintain that this avoidance is over-conservative (see
+\S~\ref{sec:stoch-single-phot}), since (i)~the high circumstellar
+radiation fields (\(U > 1000\)) mean that stochastic heating is only
+relevant for ultra-small nanometer-sized grains \citep{Draine:2001a},
+and (ii)~the most important class of such grains in the general ISM is
+PAHs, and these are destroyed by the ionizing radiation from O~stars
+\citep{Desert:1990a}.  Although PAHs may survive in bows around
+B~stars, which lack the energetic photons (\(h\nu > \SI{40}{eV}\))
+that most efficiently destroy them \citep{Lebouteiller:2007a}, their
+contribution to the \SI{24}{\um} emissivity is likely to be small
+compared with the slightly larger grains (\(> \SI{5}{nm}\)), which are
+in thermal equilibrium with the radiation field.  It may therefore be
+worth modifying the K18 method to use the \SI{24}{\um} surface
+brightness instead of \SI{70}{\um}.  In the case of the
+\(\tau\)--\(\eta\shell\) method, this is all irrelevant since
+equation~\eqref{eq:tau-empirical} is valid in a time-averaged sense,
+irrespective of whether stochastic heating is important or not.
 
@@
 
-Therefore, we have shown that a neutral shell is not consistent with
-the observational data for source~342, and so this is unlikely to be
-the explanation for the seemingly high mass loss rate.  Instead, it is
-possible that the explanation is simply that the stellar luminosity
-has been underestimated, since the luminosity class is not well
-constrained by spectroscopy (K18).  If the star were B1~III instead of
-B1~V, then the luminosity would be 4 times higher.  This could be due
-to a combination of having underestimated the distance and having
-underestimated the foreground extinction.  The assumed distance of
-\(D= \SI{1.3}{kpc}\) comes from a study of eclipsing binaries in the
-Cygnus~OB2 association \citep{Kiminki:2015a}, but GAIA~DR2 parallaxes
-for the association clearly show two sub-groups at
-\(D = \SI{1.76}{kpc}\) and \SI{1.35}{kpc}, with the farther group
-being the dominant one \citep{Berlanas:2019a}.  The GAIA parallax for
-source~342 yields a median and 90\% confidence interval of
-\(1.65^{+0.18}_{-0.16} \, \si{kpc}\) (same methodology as
-App.~\ref{sec:hd-53367-v750}),
-% \SIrange{1.49}{1.83}{kpc}
-which clearly indicates it is in the farther group.  Taking the median
-distance of \SI{1.65}{kpc} would raise \(L_*\) by a factor 1.61 and
-increasing the visual extinction \(A_V\) by 1 magnitude would give an
-additional factor of 2.51 for a total increase by \(\approx 4\), as we
-are looking for.  To find the effects on the derived quantities, we
-can sum the Jacobian elements in the first two rows of
-Table~\ref{tab:derived-parameters}, multiplied by the changes in
-observed log quantities: \(\Delta D \approx \SI{+0.1}{dex}\) and
-\(\Delta L_* \approx \SI{+0.6}{dex}\). For example:
-\begin{equation}
-  \label{eq:delta-derived}
-  \Delta\tau = J_D(\tau)\, \Delta D + J_{L_*}(\tau)\, \Delta L_*
-\end{equation}
-and similarly for the other quantities.  This yields
-\(\Delta \tau \approx \SI{-0.4}{dex}\),
-\(\Delta \eta\shell \approx \SI{-0.9}{dex}\),
-\(\Delta \dot{M} \approx \SI{-0.3}{dex}\), and
-\(\Delta \dot{M}_{\text{K18}} \approx \SI{-0.1}{dex}\).  In
-Figure~\ref{fig:mass-loss-vs-luminosity}a this would move source~342
-substantially to the right and slightly down, thus transforming it
-from an extreme outlier to an unremarkable source in the center of the
-pack.  It would be disappointing if such a prosaic explanation were
-the correct one, given all the other peculiarities of this source
-listed in the first paragraph of this section.  However, based on
-current evidence, the more interesting and exotic explanations are
-less plausible.
-
-% Using emissivity at different wavelength, such as \SI{24}{\um}.  No
-% good reason to fear stochastic heating.  They mention not getting 70/24 ratio right.  Probably be better with our correction.
-
-% How both the UV opacity and the IR emissivity depend on the same VSG grains.
+Therefore, we have shown that source~342 cannot have a neutral shell
+if we take the published observational data at face value.  However,
+more recent spectroscopic observations revise the spectral
+classification to B4~V (H.~Kobulnicky, priv.~comm.) and this would
+change the picture completely.  A B4 dwarf, with effective temperature
+of \SI{16700}{K} \citep[Tab.~4 of][]{Pecaut:2013a} would have a very
+small ionizing luminosity. Interpolating on Table~4 of
+\citet{Lanz:2007a}, we find \(S_{49} / L_4 \approx \num{4e-6}\), which
+yields \(\tau\iftrap = 0.017\) from equation~\eqref{eq:tau-trap-rbw}.
+At the same time, the revised spectroscopy implies a smaller \(L_*\)
+by roughly a factor of 10, which increases the shell's derived
+\(\tau\) by the same factor (eq.~[\ref{eq:tau-empirical}]), yielding
+\(\tau \approx 0.05\).  Since we now have \(\tau > \tau\iftrap\) it is
+possible that ionization front may be trapped, giving a predominately
+neutral shell.  This also relies, however, on the radiation field from
+the nearby Cygnus OB2 cluster being insufficient to ionize the shell.
+Given that the cluster's stellar population \citep{Wright:2015a}
+includes 3 WR stars and a handful of early-O supergiants, the ionizing
+luminosity must be of order \SI{e51}{s^{-1}}.  In the absence of
+absorption, and assuming that the true separation to be no more than a
+few times larger than the projected separation, the cluster stars
+would contribute over 100 times greater ionizing flux at the position
+of source 34 than that due to the B4 star itself.  It is therefore
+necessary for the source to lie outside of the cluster's \hii{} region
+in order for the shell to be neutral.  It is quite plausible that this
+might be the case, since radio continuum observations \citetext{Fig.~4
+  of \citealp{Wendker:1991a} and Fig.~7 of \citealp{Tung:2017a}}
+indicate that the neighborhood of source~342 is a local minimum in
+free-free emission between discrete \hii{} regions of the Cygnus~X
+complex, while Herschel maps \citep{Schneider:2016a} show the
+presence of both warm and cold dust along the line of sight and clumps
+of Class~0 and~I YSOs are seen nearby \citep{Beerer:2010a}, indicative
+of shielded neutral/molecular gas.
+
+%%%
+%%% PREVIOUS VERSION, WHEN WE THOUGHT 342 WAS A B1V STAR
+%%%
+% % Therefore, we have shown that a neutral shell is not consistent with
+% % the observational data for source~342, and so this is unlikely to be
+% % the explanation for the seemingly high mass loss rate.  Instead, it is
+% % possible that the explanation is simply that the stellar luminosity
+% % has been underestimated, since the luminosity class is not well
+% % constrained by spectroscopy (K18).  If the star were B1~III instead of
+% % B1~V, then the luminosity would be 4 times higher.  This could be due
+% % to a combination of having underestimated the distance and having
+% % underestimated the foreground extinction.  The assumed distance of
+% % \(D= \SI{1.3}{kpc}\) comes from a study of eclipsing binaries in the
+% % Cygnus~OB2 association \citep{Kiminki:2015a}, but GAIA~DR2 parallaxes
+% % for the association clearly show two sub-groups at
+% % \(D = \SI{1.76}{kpc}\) and \SI{1.35}{kpc}, with the farther group
+% % being the dominant one \citep{Berlanas:2019a}.  The GAIA parallax for
+% % source~342 yields a median and 90\% confidence interval of
+% % \(1.65^{+0.18}_{-0.16} \, \si{kpc}\) (same methodology as
+% % App.~\ref{sec:hd-53367-v750}),
+% % % \SIrange{1.49}{1.83}{kpc}
+% % which clearly indicates it is in the farther group.  Taking the median
+% % distance of \SI{1.65}{kpc} would raise \(L_*\) by a factor 1.61 and
+% % increasing the visual extinction \(A_V\) by 1 magnitude would give an
+% % additional factor of 2.51 for a total increase by \(\approx 4\), as we
+% % are looking for.  To find the effects on the derived quantities, we
+% % can sum the Jacobian elements in the first two rows of
+% % Table~\ref{tab:derived-parameters}, multiplied by the changes in
+% % observed log quantities: \(\Delta D \approx \SI{+0.1}{dex}\) and
+% % \(\Delta L_* \approx \SI{+0.6}{dex}\). For example:
+% % \begin{equation}
+% %   \label{eq:delta-derived}
+% %   \Delta\tau = J_D(\tau)\, \Delta D + J_{L_*}(\tau)\, \Delta L_*
+% % \end{equation}
+% % and similarly for the other quantities.  This yields
+% % \(\Delta \tau \approx \SI{-0.4}{dex}\),
+% % \(\Delta \eta\shell \approx \SI{-0.9}{dex}\),
+% % \(\Delta \dot{M} \approx \SI{-0.3}{dex}\), and
+% % \(\Delta \dot{M}_{\text{K18}} \approx \SI{-0.1}{dex}\).  In
+% % Figure~\ref{fig:mass-loss-vs-luminosity}a this would move source~342
+% % substantially to the right and slightly down, thus transforming it
+% % from an extreme outlier to an unremarkable source in the center of the
+% % pack.  It would be disappointing if such a prosaic explanation were
+% % the correct one, given all the other peculiarities of this source
+% % listed in the first paragraph of this section.  However, based on
+% % current evidence, the more interesting and exotic explanations are
+% % less plausible.
 

### 2019-03-30 papers/Papers1234/bs-bw-dw-03.tex
Finish intro for Paper III

--- 2019-03-26 papers/Papers1234/bs-bw-dw-03.tex
@@
 \author[Henney \& Arthur]{
-  William J. Henney \& S. J. Arthur\\
+  William J. Henney\thanks{w.henney@irya.unam.mx}
+  \& S. J. Arthur\\
   \AddressCRyA
@@
 
+Bow-shaped circumstellar nebulae are observed around a wide variety of
+stars \citep{Gull:1979a, Cox:2012a, Cordes:1993a} but are most
+numerous around luminous OB stars \citep{Kobulnicky:2016a}.  They are
+most commonly interpreted as bow shocks, due to a supersonic relative
+motion of the surrounding medium, which interacts with the stellar
+wind \citep{Wilkin:1996a}.  Early surveys for bow shocks around OB
+stars \citep{van-Buren:1995a} concentrated on runaway stars
+\citep{Blaauw:1961a, Hoogerwerf:2001a} that have been ejected at high
+velocities (\(> \SI{30}{km.s^{-1}}\)) due to multi-body encounters in
+star clusters or due to the core-collapse supernova explosion of a
+binary companion.  However, only a small fraction of runaways show
+detectable bow shocks \citep{Huthoff:2002a, Peri:2012a, Peri:2015a,
+  Prisegen:2019a}. Targeted searches at mid-infrared wavelengths of
+particular high-mass star forming regions such as M17 and RCW~49
+\citep{Povich:2008a}, Cygnus~X \citep{Kobulnicky:2010a}, and Carina
+\citep{Sexton:2015b} have revealed many bows around slower moving
+stars.  In many cases, it may be streaming motions in the interstellar
+medium that provide most of the relative velocity: weather vanes
+rather than runaways \citep{Povich:2008a}.  More recently, large-scale
+surveys of the Galactic Plane \citep{Kobulnicky:2016a,
+  Kobulnicky:2017a} and of nearby stars in the Bright Star Catalog
+\citep{Bodensteiner:2018a} have revealed hundreds more such bow shocks.
+
+Analytic and semi-analytic thin-shell models of bow shocks have been
+developed \citep{van-Buren:1992a, Wilkin:1996a, Canto:1996},
+including the effects of non-spherical winds and nonaxisymmetric bows
+\citep{Wilkin:2000a, Henney:2002a, Canto:2005a, Tarango-Yong:2018a}.
+Increasingly realistic numerical hydrodynamic simulations have been
+performed \citep{Matsuda:1989a, Raga:1997a, Comeron:1998a,
+  Meyer:2014b, Mackey:2015a}, including magnetic fields
+\citep{Meyer:2017a, Katushkina:2017a, Katushkina:2018a} and detailed
+predictions of the dust emission \citep{Meyer:2016a, Acreman:2016a,
+  Mackey:2016a}.
+
+% Despite the almost
+% universal use of the term ``bow shock'' to describe these objects, it
+% may be that slow subsonic velocities of a star through its \hii{}
+% region are sufficient \citep{Mackey:2015a, Mackey:2016a} to distort
+% the inner stellar wind shock and produce a bow appearance to the
+% mid-infrared emission, even though there is no shock in the dusty
+% ambient stream.
+
 In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we

### 2019-03-30 papers/Papers1234/sec-obs-intro.tex
Finish intro for Paper III

\section{Introduction}
\label{sec:introduction}

In the Orion Nebula, at least three different classes of stellar bow
shocks have been identified. As well as small number of OB bow shocks \citep{Smith:2005a, ODell:2001c},

HMXRB in external galaxies, possible bowshock in LMC~X-1 \citep{Hyde:2017a}.

Non-thermal radio emission from BD+43~3654 \citep{Benaglia:2010a}, has
been searched for but

Cooler red supergiant and asymptotic giant branch stars
\citep{Ueta:2008a, Sahai:2010a, Cox:2012a}.

Instability of bow \citep{Blondin:1988a}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "obs-bowshocks"
%%% End:

### 2019-03-31 papers/Papers1234/app-cloudy-dust-heating.tex
Finished second draft of Paper III

@@
 
-In preparation for our discussion of different wind mass loss
+In preparation for our discussion of different wind mass-loss
 diagnostic methods below, in this section we calculate the grain
@@
     lines show carbon grains, solid lines show silicate grains, with
-    line thickness increasing and opacity decreasing with increasing
-    grain size.  Stellar spectral types are O5\,V (blue), O9\,V
-    (orange), B1.5\,V (purple), and B0.7\,Ia (green), with lighter
-    shades denoting higher gas densities. }
+    line thickness and transparency increasing with grain size.
+    Stellar spectral types are O5\,V (blue), O9\,V (orange), B1.5\,V
+    (purple), and B0.7\,Ia (green), with lighter shades denoting
+    higher gas densities. }
   \label{fig:grain-T-vs-U}
@@
 smaller than \(\approx n^{1/2} \si{\micro G}\), given that Alfvén speeds of
-\SI{2}{km.s^{-1}} are typical of photoionized regions (cf.~Paper~II's
-eq.~[40])
+\SI{2}{km.s^{-1}} are typical of photoionized regions \citep{Arthur:2011a, Planck-Collaboration:2016c}
 % XREF Paper II \\ref{eq:alfven}

### 2019-03-31 papers/Papers1234/bs-bw-dw-03.tex
Finished second draft of Paper III

@@
 Asuntos del Personal Académico, Universidad Nacional Autónoma de
-México, through grants Programa de Apoyo a Proyectos de Investigación
-e Inovación Tecnológica IN112816 and IN107019.  This work has made
-extensive use of Python language libraries from the SciPy
-\citep{Jones:2001a}, AstroPy \citep{Astropy-Collaboration:2013a,
-  Astropy-Collaboration:2018a} and Pandas \citep{McKinney:2010a}
-projects.  We thank Chip Kobulnicky for sharing results in advance of
-publication.
+México, through grant Programa de Apoyo a Proyectos de Investigación e
+Inovación Tecnológica IN107019.  This work has made extensive use of
+Python language libraries from the SciPy \citep{Jones:2001a}, AstroPy
+\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a} and
+Pandas \citep{McKinney:2010a} projects.  We thank Chip Kobulnicky for
+sharing results in advance of publication.
 

### 2019-03-31 papers/Papers1234/sec-observational-diagnostics.tex
Finished second draft of Paper III

@@
 where the last approximate equality holds if \(\tau \ll 1\) and the shell
-emission covers one hemisphere.  Note that the \(\tau\) of Paper~I is not
-exactly the same as the \(\tau\) of equation~\eqref{eq:tau-empirical},
-but is larger by a factor of
+emission covers one hemisphere.\footnote{%
+  Note that the \(\tau\) of Paper~I is not exactly the same as the
+  \(\tau\) of equation~\eqref{eq:tau-empirical}, but is larger by a
+  factor of
   \(Q_P / Q_{\text{abs}} = 1 + \varpi (1 - g)/(1 - \varpi)\), where
   \(\varpi\) is the grain albedo and \(g\) the scattering asymmetry.
-This is plotted in Figure~6a of Paper~II for Cloudy's default ISM
-grain mixture (see \S~\ref{sec:grain-temp-emiss} below), where it can
-be seen that \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at
-EUV/FUV wavelengths (\(\lambda = \text{\SIrange{0.05}{0.2}{\um}}\)), so the
-correction is small.
+  For standard ISM grain mixtures,
+  \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
+  wavelengths.}
+% This is plotted in Figure~6a of Paper~II for Cloudy's default ISM
+% grain mixture (see \S~\ref{sec:grain-temp-emiss} below), where it
+% can be seen that
+% \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
+% wavelengths (\(\lambda = \text{\SIrange{0.05}{0.2}{\um}}\)), so the
+% correction is small.
 
@@
   the mass column if the shell thickness is known:
-  \(\rho\shell = \Sigma / h\shell\).  In the absence of other information, a
+  \(\rho\shell = \Sigma\shell / h\shell\).  In the absence of other information, a
   fixed fraction of the shell radius can be used.  In particular, we
@@
   \eta\shell \equiv \frac{P\shell}{P\rad}
-  = \frac{4\pi R_0^2\, (\sound^2 + \frac12 v\alfven^2)\, \tau}{L_*\, \kappa\, h\shell}
+  = \frac{4\pi R_0^2\, (\sound^2 + \frac12 v\alfven^2)\, c\, \tau}{L_*\, \kappa\, h\shell}
   \approx 245 \frac{R\pc \, T_4 \, \tau}{L_4 \, \kappa_{600} \, h_{1/4}} \ , 
 \end{equation}
-where in the last step we have assumed ionized gas with negligible
+where \(c\) is the speed of light. In the last step we have assumed
+ionized gas at temperature \(\num{e4}\,T_4\,\si{K}\) with negligible
 magnetic support (\(v\alfven \ll \sound\)) and written the stellar
@@
 summarize below.  Note that the shell momentum efficiency is simply
-the reciprocal of the radiation parameter from Paper~II's equation~(23):
-\(\eta\shell = \Xi\shell^{-1}\), which provides yet a third use for
-\(\eta\shell\), since \(\Xi\) is paramount in determining whether the
-grains and gas remain well-coupled (see \S~4.4 of Paper~II).
+the reciprocal of the radiation parameter from Paper~II's
+equation~(23): \(\eta\shell = \Xi\shell^{-1}\), which provides yet a third
+use for \(\eta\shell\), since \(\Xi\) is paramount in determining whether
+the grains and gas remain well-coupled (see \S~4.4 of Paper~II).
 
@@
     \toprule
-    Star & {\(L_* / \si{L_\odot}\)} & {\(L_{\text{IR}} / \si{L_\odot}\)} & {\(R_0 / \si{pc}\)} \\
+    Star & {\(L_* / \SI{e4}{L_\odot}\)}
+    & {\(L_{\text{IR}} / \si{L_\odot}\)} & {\(R_0 / \si{pc}\)} \\
     \midrule
-    \thD & 2.95e4 & 620 & 0.003 \\
-    LP~Ori & 1600 & 240 & 0.01 \\
-    \(\sigma\)~Ori & 6e4 & 15 & 0.12 \\[\smallskipamount]
-    K18 Sources & \numrange{1.4e4}{8.7e5} & \numrange{8}{2800} & \numrange{0.02}{1.35} \\
+    \thD & 2.95 & 620 & 0.003 \\
+    LP~Ori & 0.16 & 240 & 0.01 \\
+    \(\sigma\)~Ori & 6.0 & 15 & 0.12 \\[\smallskipamount]
+    K18 Sources & \numrange{1.4}{87} & \numrange{8}{2800} & \numrange{0.02}{1.35} \\
     \bottomrule
@@
 and \(F_{70}\) is Herschel PACS \SI{70}{\um}.  The weights are chosen
-so that the integral \(\int_0^\infty F_\nu \,d\nu\) is approximated by the sum
-\(\Sigma_k F_k\, \Delta\nu_k\), under the assumption that fluxes in shorter (e.g.,
-IRAC \SI{5.8}{\um}) and longer (e.g., PACS \SI{150}{\um}) wavebands
-are negligible.  Shell fluxes are converted to luminosities using the
-assumed distance to each source, and stellar luminosities are taken
-directly from K18 Table~2, based on spectroscopic classification and
-the calibrations of gravity and effective temperature from
-\citet{Martins:2005a}.
+so that the integral \(\int_0^\infty F_\nu \,d\nu\) is approximated by the
+quadrature sum \(\Sigma_k F_k\, \Delta\nu_k\), under the assumption that fluxes in
+shorter (e.g., IRAC \SI{5.8}{\um}) and longer (e.g., PACS
+\SI{150}{\um}) wavebands are negligible.  Shell fluxes are converted
+to luminosities using the assumed distance to each source, and stellar
+luminosities are taken directly from K18 Table~2, based on
+spectroscopic classification and the calibrations of gravity and
+effective temperature from \citet{Martins:2005a}.
 
@@
 uncertainty estimates for individual observational quantities that are
-used in deriving not only \(\tau\) and \(\eta\shell\), but also mass-loss
+used in deriving not only \(\tau\) and \(\eta\shell\) but also mass-loss
 rates, as discussed later in \S~\ref{sec:stellar-wind-mass}.
@@
 radiation-driven, which depends only on \(\eta\shell/\tau\).  On the other
-hand, they do significantly effect the question of whether a source
+hand, they do significantly affect the question of whether a source
 has a sufficiently high radiation parameter \(\Xi\) to possibly be a
@@
 post-shock cooling length is short in ambient densities above
-\SI{0.1}{cm^{-3}} (\S~3.2 of Paper~I)
+\SI{0.1}{cm^{-3}}
+% (\S~3.2 of Paper~I)
 % XREF: Paper I \ref{sec:radi-cool-lengths}
 and the shell does not trap the ionization front for ambient densities
-below \SI{e4}{cm^{-3}} (\S~3.1 of Paper~I).
+below \SI{e4}{cm^{-3}} (see Paper~I's \S\S~3.1 and 3.2 for details).
+% (\S~3.1 of Paper~I).
 % XREF: Paper I \\ref{sec:trapp-ioniz-front}
 For B~stars, on the other hand, these two density limits move closer
-together (cf.~the smaller gap between the blue and red lines in
+together,
+% (cf.~the smaller gap between the blue and red lines in
 % XREF: Paper I \ref{fig:zones-v-n-plane}a
@@
 % XREF: Paper I \ref{fig:zones-v-n-plane}bc
-Paper~I's Figs.~2a and 4, as compared with 2b and~c), making it more
-likely that a bow will lie in a different temperature regime.  The
-only source for which we have evidence that this occurs is LP~Ori, as
-discussed in the next section.
+% Paper~I's Figs.~2a and 4, as compared with 2b and~c),
+making it more likely that a bow will lie in a different temperature
+regime.  The only source for which we have evidence that this occurs
+is LP~Ori, as discussed in the next section.
 
@@
 parameters.  For LP~Ori, the bow shell appears to be formed from
-neutral gas \citep{ODell:2001c} and its relatively high \(\tau\) value
-is more than sufficient to trap the weak ionizing photon output of a
-B3 star.  We therefore move its point in
-Figure~\ref{fig:All-sources-eta-tau} downward to reflect a temperature
-of \SI{1000}{K} (or, equivalently, a magnetically supported shell with
+neutral gas \citep{ODell:2001c} and its relatively high \(\tau\) value is
+more than sufficient to trap the weak ionizing photon output of a B3
+star.  We therefore move its point in
+Figure~\ref{fig:All-sources-eta-tau} downward by a factor of ten,
+which could be a thermally supported neutral shell at \SI{2000}{K} or
+a magnetically supported shell with
 \(v\alfven \approx \SI{3}{km.s^{-1}}\)).  For the case of the Orion
@@
 
-K18 derive mass loss rates for their sources using a method that is
+K18 derive mass-loss rates for their sources using a method that is
 different from the one that we employ above.  Both methods are based
@@
 narrow range of spectral type\footnote{%
-  However, the statistically significance is not strong.  For
+  However, the statistical significance is not strong.  For
   instance, out of the twenty K18 sources, 7 have spectral type O8 or
@@
 subsequent works.  For its early~B spectral type,
-\(\dot{M} \approx \SI{3e-9}{M_\odot.yr^{-1}}\) is expected, whereas
-the derived values from both mass-loss methods (panels a and b of
+\(\dot{M} \approx \SI{3e-9}{M_\odot.yr^{-1}}\) is expected, whereas the derived
+values from both mass-loss methods (panels a and b of
 Fig.~\ref{fig:mass-loss-vs-luminosity}) are about 10 times larger.
@@
 SED are both reminiscent of LP~Ori (more details on the Orion Nebula
-bows will be provide in Paper~VI), and another bow that bears some
+bows will be provided in Paper~VI), and another bow that bears some
 similarities is Carina's Sickle object \citetext{ERO~21
@@
 IRAS~03063+5735 \citep{Kobulnicky:2012a}.  Finally, it has the coldest
-dust of any of the K18 sources, as determined from the mid-to-far
-infrared color temperatures (\(T_{22/70} = \SI{70}{K}\),
-\(T_{70/150} = \SI{69}{K}\) from Tab.~5 of
-\citealp{Kobulnicky:2017a}).
+dust of any of the K18 sources,\footnote{%
+  Even with such a low dust temperature, adding the \SI{150}{\um} flux
+  to the quadrature sum would only increase the total infrared flux by
+  20\% over that given by equation~\eqref{eq:total-ir-flux}.} %
+as determined from the mid-to-far infrared color temperatures
+(\(T_{22/70} = \SI{70}{K}\), \(T_{70/150} = \SI{69}{K}\) from Tab.~5
+of \citealp{Kobulnicky:2017a}).
 

### 2019-04-01 papers/Papers1234/bs-bw-dw-03.tex
Submit Paper III to MNRAS and astro-ph

@@
 rather than runaways \citep{Povich:2008a}.  More recently, large-scale
-surveys of the Galactic Plane \citep{Kobulnicky:2016a,
+surveys of the Galactic plane \citep{Kobulnicky:2016a,
   Kobulnicky:2017a} and of nearby stars in the Bright Star Catalog
@@
 Increasingly realistic numerical hydrodynamic simulations have been
-performed \citep{Matsuda:1989a, Raga:1997a, Comeron:1998a,
+performed \citep{Matsuda:1989a, Raga:1997a, Comeron:1998a, Arthur:2006a,
   Meyer:2014b, Mackey:2015a}, including magnetic fields
@@
   opacity by about 50\%.
+\item The bow source KGK2010~2 is a low-luminosity B~star with an
+  anomalously high apparent mass-loss rate.  This discrepancy could be
+  eliminated if the bow shell has trapped the ionization front and is
+  predominantly neutral, in which case it would become yet another
+  candidate for radiation support.
 \end{enumerate}

### 2019-04-01 papers/Papers1234/sec-observational-diagnostics.tex
Submit Paper III to MNRAS and astro-ph

@@
 luminosity must be of order \SI{e51}{s^{-1}}.  In the absence of
-absorption, and assuming that the true separation to be no more than a
+absorption, and assuming that the true separation be no more than a
 few times larger than the projected separation, the cluster stars
 would contribute over 100 times greater ionizing flux at the position
-of source 34 than that due to the B4 star itself.  It is therefore
+of source~342 than that due to the B4 star itself.  It is therefore
 necessary for the source to lie outside of the cluster's \hii{} region

### 2019-04-01 papers/Papers1234/sec-quadrics-observations.tex
Start work on Paper IV - change Pi-Lambda graphs to log scale

--- 2017-10-06 papers/Paper1/sec-quadrics-observations.tex
@@
     or above.  All 5-star sources plus those 4-star sources with
-    \(R_c/R_0 < 1\) are labelled with their \cite{Kobulnicky:2016a}
+    \(\Pi < 1\) are labelled with their \cite{Kobulnicky:2016a}
     catalog number.  Horizontal error bars do not directly reflect the
-    uncertainty in \(R_c/R_0\) but are instead simply the standard
+    uncertainty in \(\Pi\) but are instead simply the standard
     deviation from the circle fit of bowshock points \(R_k\) within
     \(\pm 45\degr\) of the axis.  Values on the vertical axis
-    represent the average of \(R_{90+}\) and \(R_{90-}\), with thin
-    vertical error bars showing the difference between \(R_{90+}\) and
-    \(R_{90-}\), and thick vertical error bars showing the rms
+    represent the average of \(\Lambda_{+}\) and \(\Lambda_{-}\), with thin
+    vertical error bars showing the difference between \(\Lambda_{+}\) and
+    \(\Lambda_{-}\), and thick vertical error bars showing the rms
     dispersion of \(R_k\) about these values for bow shock points
@@
     \(0.18 \times 0.12\). Thumbnail images of representative 4- and 5-star
-    sources at different points on the \(R_c\)--\(R_{90}\) plane are
+    sources at different points on the \(\Pi\)--\(\Lambda\) plane are
     also shown. The angular scale of each image is indicated by a
@@
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock.tex"
+%%% TeX-master: "obs-bowshocks.tex"
 %%% End:

### 2019-04-02 papers/Papers1234/sec-observational-diagnostics.tex
Remove the figure about K18 interpolation error from Paper III
Requested by Chip Kobulnicky

@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
-  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
-    identified in K18.  Red crosses show the emissivities given in
-    K18's Table~2 as a function of the radiation field \(U\), while
-    the solid gray line shows the emissivities that they claim to be
-    using from \citet{Draine:2007a}.  The dashed line shows the
-    emissivities that we believe they should have been using, which
-    correct for the marked difference in spectral energy distribution
-    between OB stars and the Galactic interstellar radiation field
-    (see \S~\ref{sec:grain-temp-emiss}).}
-  \label{fig:k18-emissivity}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
+%   \caption{Discrepancies in \SI{70}{\um} emissivities that we have
+%     identified in K18.  Red crosses show the emissivities given in
+%     K18's Table~2 as a function of the radiation field \(U\), while
+%     the solid gray line shows the emissivities that they claim to be
+%     using from \citet{Draine:2007a}.  The dashed line shows the
+%     emissivities that we believe they should have been using, which
+%     correct for the marked difference in spectral energy distribution
+%     between OB stars and the Galactic interstellar radiation field
+%     (see \S~\ref{sec:grain-temp-emiss}).}
+%   \label{fig:k18-emissivity}
+% \end{figure}
 
@@
 that the \citet{Draine:2007a} models require modification when applied
-to grains around OB stars.  In addition, when attempting to replicate
-the K18 values of \(j_{70}\) we find that they only follow the
-\citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
-constant value for weaker radiation fields.  The situation is
-summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
-directly from Table~2 of K18 are shown by red crosses, the values they
-claim to be using are shown by the gray solid line (this curve is
-consistent with that shown in K18 Fig.~2), and the values they
-\textit{should} have been using are shown by the gray dashed
-line. Note that this correction may also resolve the color temperature
-discrepancy noted by \citet{Kobulnicky:2017a}.
-
-% If we replaced K3 with M3, then mass loss rates would be reduced by 1.86 across the board
+to grains around OB stars.  A further discrepancy arises due to an
+interpolation error in K18, which resulted in values of \(j_{70}\)
+being overestimated by about a factor of 2 for sources with weak
+radiation fields (H.~Kobulnicky, priv.~comm.).
+
+% In addition, when attempting to replicate
+% the K18 values of \(j_{70}\) we find that they only follow the
+% \citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
+% constant value for weaker radiation fields.
+
+% The situation is
+% summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
+% directly from Table~2 of K18 are shown by red crosses, the values they
+% claim to be using are shown by the gray solid line (this curve is
+% consistent with that shown in K18 Fig.~2), and the values they
+% \textit{should} have been using are shown by the gray dashed
+% line. Note that this correction may also resolve the color temperature
+% discrepancy noted by \citet{Kobulnicky:2017a}.
 
@@
 unaffected but that sources with stronger radiation fields (lighter
-shading) have their mass-loss increasingly reduced, as could be
-surmised from Figure~\ref{fig:k18-emissivity}.  The average reduction
-is by a factor of about two.
+shading) have their mass-loss increasingly reduced.
+% , as could be
+% surmised from Figure~\ref{fig:k18-emissivity}.
+The average reduction is by a factor of about two.
 

### 2019-04-02 papers/Papers1234/sec-quadrics-observations.tex
More improvements for Paper IV

@@
   \centering
-  \setlength\tabcolsep{0pt}
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[height=1.167\linewidth]
+  \includegraphics[width=\linewidth]
   {figs/mipsgal-boxplot-Rc-R90-versus-R0}
-        & \includegraphics[height=1.167\linewidth]
-          {figs/mipsgal-boxplot-Rc-R90-versus-H0}
-  \end{tabular}
-  \caption{(a) Box plots of the distributions of bow shock shape
-    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), together with a
-    measure of the tail asymmetry, \(|R_{90+} - R_{90-}| / R_{90}\),
+  \caption{Box plots of the distributions of bow shock shape
+    parameters, \(\Pi\) and \(\Lambda\), together with a
+    measure of the tail asymmetry, \(|\Lambda_{+} - \Lambda_{-}| / \Lambda\),
     after partitioning on the bow shock size, \(R_0\).  All 3-, 4-,
@@
     \(p\)-value given at the bottom of each panel.   It is apparent
-    that the dispersion in \(R_{90} / R_0\) (upper panel) increases
+    that the dispersion in \(\Lambda\) (upper panel) increases
     systematically with \(R_0\), although the central value is roughly
     constant.  No clear systematic changes are apparent in
-    \(R_c / R_{90}\) (middle panel).  (b)~As (a), but partitioning on
-    the extinction-corrected \(H\)-band magnitude, \(H_0\).  Note that
-    sub-samples are plotted in order of \textit{decreasing} magnitude
-    to allow comparison between (a) and (b), given the negative
-    correlation between \(H_0\) and \(R_0\) (see
-    Fig.~\ref{fig:mipsgal-pairplot}).}
+    \(\Pi\) (middle panel).}
   \label{fig:mipsgal-boxplot}
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
+  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
   \caption[]{Comparison of bow shock shapes between Herschel RSG/AGB
@@
   \label{fig:herschel-compare-mipsgal}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
+  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
   \caption[]{Comparison of Orion with OB stars.  Other details of the
@@
   \label{fig:ll-compare-mipsgal}
-\end{figure*}
+\end{figure}
 

### 2019-04-02 Dust-wave/compare_xyprime_wave.py

@@ -49,7 +49,7 @@ phase_labels = ["phase = 0.0, 1.0", "phase = 0.25, 0.75", "phase = 0.5"]
 colors = 'b', 'k', 'r'
 linewidths = [2, 1, 2]
 # Different (amplitude, wavenumber) are different panels
-amplitudes = [0.1, 0.05, 0.02]
+amplitudes = [0.2, 0.1, 0.04]
 wavenumbers = [1.0, 2.0, 5.0]
 
 # All are for zero inclination

### 2019-04-02 Dust-wave/wave-R90-vs-Rc.py

@@ -2,7 +2,7 @@ import sys
 import json
 import numpy as np
 from matplotlib import pyplot as plt
-import matplotlib.ticker
+import matplotlib.ticker as mticker
 import seaborn as sns
 
 try:
@@ -12,6 +12,9 @@ except:
     sys.exit(f"Usage: {sys.argv[0]} WAVE_ID SHAPE_ID [SHAPE_ID ...]")
 
 plotfile = sys.argv[0].replace('.py', f'-{WAVE_ID}.pdf')
+
+range_ = [0.35, 9.5]
+ticks = [0.4, 0.5, 0.7, 1.0, 1.5, 2.0, 3.0, 4.0, 5.0, 7.0]
 
 sns.set_style('ticks')
 fig, ax = plt.subplots(figsize=(5, 5))
@@ -29,7 +32,7 @@ ax.axvline(1.0, lw=0.5, alpha=0.5, color='k', zorder=-1)
 ax.plot([0.0, 10.0], [0.0, 10.0], lw=0.5, alpha=0.5, color='k', zorder=-1)
 
 # Put a cross at the Wilkinoid coordinates: [5/3, sqrt(3)]
-ax.plot([5./3.], [np.sqrt(3.0)], '+', c='w', ms=10, alpha=1.0)
+ax.plot([5./3.], [np.sqrt(3.0)], '+', c='w', ms=10, alpha=1.0, zorder=100)
 
 nshapes = len(BASE_SHAPE_IDS)
 colors = sns.color_palette(n_colors=nshapes)
@@ -39,22 +42,23 @@ for base_shape_id, color in zip(BASE_SHAPE_IDS, colors):
     data = np.load(prefix + '.npz')
     Rc, R90 = data['Rc'], data['R90']
     for x, y in zip(Rc, R90):
-        ax.plot(x, y, '-', lw=2, c=color, label="_nolabel_", alpha=0.3)
-    ax.plot(Rc[0], R90[0], '-', lw=3, c=color,
+        ax.plot(x, y, '.', ms=5, mec="none", c=color, label="_nolabel_", alpha=0.1)
+    ax.plot([], [], '.', ms=9, mec="none", c=color,
             label=metadata['shape_label'], alpha=0.8)
 
 ax.legend(title=metadata['wave_label'])
 
 ax.set(
-    yscale='linear',
-    xscale='linear',
-    xlim=[0.0, 5.1],
-    ylim=[0.0, 5.1],
[…]

### 2019-04-07 papers/Papers1234/sec-strong-coupling.tex
Correct typo in eq (24) of Paper I
Update Paper I to split shell profiles figure in 3 parts

@@
   \label{eq:ifront-trap-x-cubed-taustar}
-  x^3 \tau_* > \frac{4 S c \sound \bar{m}^2 \kappa}{3 \alpha L} \ .
+  x^3 \tau_* > \frac{4 S c \sound^2 \bar{m}^2 \kappa}{3 \alpha L} \ .
 \end{equation}
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/shell-profiles}
-  \caption{Profiles of physical variables along the axis of bow shells
-    for (a)~wind-supported bow shock; (b)~radiation-supported bow
-    wave, and (c)~radiation-supported bow shock.  In all cases, a
+  \includegraphics[width=\linewidth]{figs/shell-profile-wbs}
+  \caption{Profiles of physical variables along the axis of the bow
+    shell for a wind-supported bow shock.  The case is shown of a
     stream velocity of \SI{30}{km.s^{-1}} and an equilibrium ionized
-    sound speed of \SI{10}{km.s^{-1}} are assumed.}
-  \label{fig:axial-structure}
+    sound speed of \SI{10}{km.s^{-1}}.}
+  \label{fig:axial-structure-wbs}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/shell-profile-rbw}
+  \caption{As Fig.~\ref{fig:axial-structure-wbs} but for a
+    radiation-supported bow wave.}
+  \label{fig:axial-structure-rbw}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/shell-profile-rbs}
+  \caption{As Fig.~\ref{fig:axial-structure-wbs} but for a
+    radiation-supported bow shock.}
+  \label{fig:axial-structure-rbs}
 \end{figure}
@@
 radiation-supported bows, as illustrated in
-Figure~\ref{fig:axial-structure}, where we schematically show the
-shell structure for the three cases: WBS, RBW, and RBS.  In all cases,
-we assume a far-field mach number of \(\M_\infty = 3\) for the incident
-stream of density \(n_\infty\).  For the WBS case
-(Fig.~\ref{fig:axial-structure}a), the stream is unchanged until it
+Figures~\ref{fig:axial-structure-wbs} to
+\ref{fig:axial-structure-rbs}, where we schematically show the shell
+structure for the three cases: WBS, RBW, and RBS.  In all cases, we
+assume a far-field mach number of \(\M_\infty = 3\) for the incident stream
+of density \(n_\infty\).  For the WBS case
+(Fig.~\ref{fig:axial-structure-wbs}), the stream is unchanged until it
 reaches the shock, so \(\M_0 = \M_\infty\) and \(n_0 = n_\infty\).  The density
@@
 
-For the optically thin RBW case (Fig.~\ref{fig:axial-structure}b),
+For the optically thin RBW case (Fig.~\ref{fig:axial-structure-rbw}),
 equations~\eqref{eq:rad-accel} to~\eqref{eq:rad:R0} can be combined to
@@
 This ballistic approximation (shown by the dashed red line in
-Fig.~\ref{fig:axial-structure}b) predicts that the velocity smoothly
+Fig.~\ref{fig:axial-structure-rbw}) predicts that the velocity smoothly
 decreases to zero at \(R = R_{**}\).  However, although this is valid
@@
 predicting the exact Mach number where it will occur.  In
-Figure.~\ref{fig:axial-structure}b we assume that the shock occurs at
+Figure.~\ref{fig:axial-structure-rbw} we assume that the shock occurs at
 a Mach number \(\M_0 = 1.5\), but multidimensional numerical
@@
 
-For the optically thick RBS case (Fig.~\ref{fig:axial-structure}c),
+For the optically thick RBS case (Fig.~\ref{fig:axial-structure-rbs}),
 the shell density profile is no longer simply exponential since the

### 2019-04-07 papers/Papers1234/bsbwdw04-extras.tex
Redo standing wave figures for Paper IV
Increase the amplitude of oscillation

--- 2019-04-02 papers/Papers1234/sec-quadrics-observations.tex
@@
-\section{Comparison with observations}
-\label{sec:comp-with-observ}
-
-Placing various classes of objects on the \(R_{90}\)--\(R_c\) plane:
-\begin{itemize}
-\item LL arcs
-\item runaway O stars
-\item AGB stars
-\end{itemize}
-
-\subsection{Mid-infrared arcs around early-type stars}
-\label{sec:mid-infrared-arcs}
-
-\begin{figure*}
-  \setlength\tabcolsep{0pt}
-  \begin{tabular}{ll}
-    (a)
-    & (b) \\
-    \includegraphics
-    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0510-3-star}
-    & \includegraphics
-      [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0506-4-star} \\
-    (c)
-    & (d) \\
-    \includegraphics
-    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0517-5-star}
-    & \multicolumn{1}{c}
-      {\includegraphics[width=0.35\linewidth, trim=20 20 20 20]
-      {figs/mipsgal-r0-r0-plus-dPA-edited}}
-  \end{tabular}
-  \caption[]{Examples of typical fits to the bow shock shapes of
-    MIPSGAL sources with different star ratings: (a) K510, 3-star
-    rating; (b) K506, 4-star rating; (c) K517, 5-star rating.  Right
-    panels of parts (a)--(c) show a 4\('\) square \SI{24}{\um} image,
-    centered on each source.  Contours are ten linearly spaced levels
-    between the median brightness of the entire image and the maximum
-    brightness of the bow shock arc. Grids of galactic coordinates
-    (light blue lines, parallel to the box sides) and equatorial
-    coordinates (tilted magenta lines) are shown.  The stellar source
-    and the bow shock axis, as determined by \citet{Kobulnicky:2016a}
-    are indicated by an orange star and an orange line, respectively,
-    where the line extends from \(-2 R_0\) to \(+2 R_0\).  The
-    automatically traced arc shapes using the ``mean'' and ``peak''
-    methods (see text) are shown by blue and red dots, respectively.
-    The magenta circle shows the fit to the arc points within
-    \(\pm 45^\circ\) of the nominal bowshock axis, with the magenta dot
-    showing the center of curvature and the magenta line showing the
-    fitted bow shock axis, which is the line passing through the
-    source and the center of curvature.  Left panels of parts (a)--(c)
-    show the radius measured from the source (upper panel) and
-    brightness (lower panel) of the arc points, plotted as a function
-    of angle \(\theta\) from the nominal bow shock axis, and with the same
-    color coding as used on the image. Angular ranges of
-    \(\theta = \pm 45\degr\) and \(\pm 90\degr\) are shown by gray shaded
-    boxes In the upper panel, the \(R_0\) value tabulated by
-    \citet{Kobulnicky:2016a} is shown by a horizontal blue line. (d)
-    Comparison of the bow shock sizes (scatter plot) and position
-    angles (inset histograms) determined from our fits with those
-    tabulated by \citet{Kobulnicky:2016a} for the MIPSGAL sources.
-    The horizontal dotted line on the main plot shows the MIPS
-    \SI{24}{\um} point spread function FWHM of \(5.5\arcsec\).  The
-    standard deviation (s.d.) of the position angle differences is
-    shown on each inset histogram.}
-  \label{fig:mipsgal-examples}
-\end{figure*}
-
-The most extensive observational sample of stellar bow shock nebulae
-to date is a catalog of 709 arcs \citep{Kobulnicky:2016a} detected in
-mid-infrared surveys of the Galactic Plane by the \textit{Spitzer
-  Space Telescope} (\textit{SST}, \citealp{Werner:2004a}) and
-\textit{Wide-field Infrared Survey Explorer} (\textit{WISE},
-\citealp{Wright:2010a}).  These sources are believed to be powered by
-the winds of early-type stars, which are either moving supersonically
-through the interstellar medium (runaway stars,
-\citealp{Gvaramadze:2008a}), or are interacting with a local bulk
-flow, such as the champagne flow from a nearby \hii{} region (weather
-vanes, \citealp{Povich:2008a}).
-
-\subsubsection{Automatic tracing and fitting of bow shocks}
-\label{sec:autom-trac-fitt}
-
-In order to study the shapes of these bow shocks, we downloaded data
-from the NASA/IPAC Infrared Science Archive archive\footnote{
-  \url{http://irsa.ipac.caltech.edu/docs/program_interface/api_images.html}}
-and extracted 4\arcmin{} square images in the \SI{24}{\um} bandpass of
-the Multiband Imaging Photometer for \textit{Spitzer} (MIPS) centered
-on each of the 471 \citet{Kobulnicky:2016a} sources that are covered
-by the MIPSGAL \citep{Carey:2009a} survey, which includes most of the
-sources with Galactic longitude within \(\pm 60\degr\) of the Galactic
-center.
-
-We developed a methodology for automatically tracing the arcs as follows:
-\begin{enumerate}[1.]
-\item Calculate arrays of celestial coordinates, \(C\), for each pixel
-  of the image.
-\item Using the central source coordinates, \(C_0\) and nominal
-  bowshock radius, \(R_0\) from \citet{Kobulnicky:2016a}, construct a
-  pixel mask that includes only those pixels with separations from the
-  source that satisfy \(\frac12 R_0 \le |C - C_0| \le 3 R_0\).  This mask
-  will be used for all subsequent operations, which serves to help
-  avoid confusion from the star itself and other bright sources in the
-  field of view.
-\item Define a ``step-back'' point, \(C_1\), which is located at a
-  separation \(2 R_0\) from the source, but in the opposite direction
-  from the apex of the bow shock. That is, along a position angle
-  180\degr{} from the nominal position angle, \(\text{PA}_0\), of the
-  bow shock axis.  This point is at one end of the orange line shown
-  superimposed on the bow shock images in
-  Figure~\ref{fig:mipsgal-examples}.
-\item Looping over a grid of 50 position angles, \(\text{PA}_k\),
-  within \(\pm 60\degr\) of \(\text{PA}_0\), estimate the location of
-  the arc along rays cast from the step-back point, using two
-  different methods:
-  \begin{enumerate}[(a)]
-  \item The pixel with the peak brightness, with coordinates
-    \(C_{k,\text{peak}}\) (red dots in
-    Fig.~\ref{fig:mipsgal-examples}).
-  \item The mean brightness-weighted separation from \(C_1\), with
-    coordinates \(C_{k,\text{mean}}\) (light blue dots in
-    Fig.~\ref{fig:mipsgal-examples}).
-  \end{enumerate}
-  For each \(\text{PA}_k\) in the grid, the calculation is performed
-  over only those pixels that satisfy
-  \(|\text{PA}(C, C_1) - \text{PA}_k| < \frac12 \delta\theta\), where
-  \(\delta\theta = 120/50 = 2.4\degr\), which defines a thin radial wedge from
-  \(C_1\).  The results are shown as red and blue dots superimposed
-  on the images in Figure~\ref{fig:mipsgal-examples}. Each of the two
-  methods, ``peak'' and ``mean'', works better in some objects and
-  worse in others (according to the subjective judgment of
-  ``correctly'' tracing the bow shock shape).  We therefore take the
-  average by amalgamating all the \(C_{k,\text{peak}}\) and
-  \(C_{k,\text{mean}}\) points into a single set, \(C_{k}\), for
-  the following steps.
-\item For each of the points \(C_{k}\), determine the radial
-  separation from the central source, \(R_k = |C_k - C_0|\) and the
-  angle from the bow shock axis about the central source
-  \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\).  These are plotted in
-  the upper left panels of Figure~\ref{fig:mipsgal-examples}.  Note
-  that, even though the rays are cast from the step-back point \(C_1\)
-  within \(\pm 60\degr\) of \(\text{PA}_0\), the angles \(\theta_k\) are
-  measured from the source, \(C_0\), which is closer to the bow shock
-  than \(C_1\) and therefore \(|\theta_k|\) can be much larger than
-  \(60\degr\).
-\item Make our own estimate of the axial size, \(R_0\), of the bow
-  shock by calculating the mean of \(R_k\) over all points \(C_k\)
-  with \(|\theta_k| \le 10\degr\).  Note that this is distinct from the
-  nominal value of \(R_0\) given in the \citet{Kobulnicky:2016a}
-  catalog, which was ``measured by eye''.  We denote by
-  \(\epsilon(R_0)\) the standard deviation of the \(R_k\) that go into
-  calculating \(R_0\).\label{step:R0}
-\item Estimate the radius of curvature, \(R_c\), by fitting a circle
-  to all those points within \(\pm 45\degr\) of the nominal axis
-  (\(|\theta_k| < 45\degr\)), but after excluding any point with
-  \(R_k < \frac12 R_m\) or \(R_k > 2 R_m\), where \(R_m\) is the median
-  \(R_k\) for \(|\theta_k| < 45\degr\).
-\item Determine two separate estimates, \(R_{90+}\) and \(R_{90-}\),
-  of the perpendicular radius, \(R_{90}\), by taking the mean of
-  \(R_k\) over all points \(C_k\) with
-  \(|\theta_k - 90\degr| \le 10\degr\) for \(R_{90+}\), and with
-  \(|\theta_k + 90\degr| \le 10\degr\) for \(R_{90-}\).  The average of the
-  two standard deviations of the \(R_k\) that contribute to
-  \(R_{90+}\) and \(R_{90-}\) is denoted by \(\epsilon(R_{90})\).\label{step:R90}
-\end{enumerate}
-
-\subsubsection{Subjective evaluation of the fit quality}
-\label{sec:subj-eval-fit}
-
-After these automatic steps, we subjectively evaluate the results by giving a star rating to each source:
-
-\paragraph*{0 stars} The fitting algorithm failed for some reason.
-
-\paragraph*{1 star} The fit was formally successful, but the results
-for \(R_c\) or \(R_{90}\) are far removed from what a human would
-predict by looking at the image.  For example, in the smallest
-bowshocks, which are only marginally resolved by Spitzer's 6\arcsec{}
-beam, the dispersion in \(R_k\) can be a significant fraction of
-\(R_0\), in which case our algorithm tends to erroneously favor
-\(R_c < R_0\).
-
-\paragraph*{2 stars} The fit results are not totally outlandish, but
-nonetheless some problem is apparent that casts doubt on their
-reliability.  For example, a double-shell structure to the bow shock
-that leads to large differences between the ``peak'' and ``mean''
-methods, or point sources near to the bow shock that interfere with
-the tracing procedure.
-
-\paragraph*{3 stars} A good fit, but where the dispersion in \(R_k\)
-and/or the asymmetry in the bow shock reduces the precision in the
-determination of \(R_c\) and \(R_{90}\), giving subjectively estimated
-uncertainties around the 20\% level.  An example of a 3-star fit is
-shown in Figure~\ref{fig:mipsgal-examples}a.
-
-\paragraph*{4 stars} A high quality fit, with subjectively estimated
-uncertainties in \(R_c\) and \(R_{90}\) around the 10\% level. An
-example of a 4-star fit is shown in
-Figure~\ref{fig:mipsgal-examples}b.
-
-\paragraph*{5 stars} The highest-quality fit, usually corresponding to
-large, sharply defined bow shocks, whose shape is determined with high
-precision. An example of a 5-star fit is shown in
-Figure~\ref{fig:mipsgal-examples}c.
-
-\bigskip
-%
-Figure~\ref{fig:mipsgal-examples}d compares the bow shock size,
-\(R_0\), determined by our fits (vertical axis) with the corresponding
-value given in the \citet{Kobulnicky:2016a} catalog (horizontal axis).
-For most sources with 3-star or higher rating, the two estimates agree
-to within \(\pm 20\%\), but there are a small number of sources with a
-discrepancy of more than a factor of two.  In all cases that we
-checked, we believe that our estimates of \(R_0\) are more accurate
-than those in the catalog.  It is apparent that the star ratings are
-correlated with the bow shock size, with larger bow shocks tending to
-receive higher ratings, although there is considerable overlap.  In
-particular, most of the 1- and 2-star sources are close to the
-resolution limit of the MIPSGAL \SI{24}{\um} images (\(6\arcsec\),
-indicated by the dotted horizontal line in te figure).
-
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth, trim=0 0 30 0]
-    {figs/mipsgal-Rc-R90-zoom-annotated}
-        & \includegraphics[width=0.45\textwidth, trim=0 0 30 0]
-          {figs/mipsgal-Rc-R90-thumbnails} 
-  \end{tabular}
-  \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
-    of dimensionless radius of curvature versus perpendicular radius.
-    The regions corresponding to different classes of cuadrics are
-    shown by shading (see \S~\ref{sec:conic}): oblate spheroids (light
-    gray background); prolate spheroids (darker gray background);
-    paraboloids (curved black line); hyperboloids (white background).
-    (a) Individual sources with bow shock fit quality rating of 3-star
-    or above.  All 5-star sources plus those 4-star sources with
-    \(\Pi < 1\) are labelled with their \cite{Kobulnicky:2016a}
-    catalog number.  Horizontal error bars do not directly reflect the
-    uncertainty in \(\Pi\) but are instead simply the standard
-    deviation from the circle fit of bowshock points \(R_k\) within
-    \(\pm 45\degr\) of the axis.  Values on the vertical axis
-    represent the average of \(\Lambda_{+}\) and \(\Lambda_{-}\), with thin
-    vertical error bars showing the difference between \(\Lambda_{+}\) and
-    \(\Lambda_{-}\), and thick vertical error bars showing the rms
-    dispersion of \(R_k\) about these values for bow shock points
-    within \(\pm 10\degr\) of the \(+90\degr\) and \(-90\degr\)
-    directions.  (b) Kernel density estimator (KDE) of the
-    distribution for 3-star sources (blue, filled contours) and 4-
-    plus 5-star sources (orange/brown, unfilled contours).  The KDE
-    uses an anisotropic gaussian kernel with bandwidths of
-    \(0.18 \times 0.12\). Thumbnail images of representative 4- and 5-star
-    sources at different points on the \(\Pi\)--\(\Lambda\) plane are
-    also shown. The angular scale of each image is indicated by a
-    yellow circle of diameter \(7.5''\), centered on the stellar
-    source.}
-  \label{fig:mipsgal-shapes}
-\end{figure*}
-
-In the following analysis, only those sources with a 3-star or higher
-rating are used.  These comprise approximately half (227 out of 471)
-of all the MIPSGAL arc sources.  In some cases of poor and failed
-fits, there is nothing apparently ``wrong'' with the source itself,
-and it is likely that minor tweaks to the methodology would improve
-matters, but we have elected not to do so, in order to maintain a
-uniform methodology across all sources.
-
-The inset of Figure~\ref{fig:mipsgal-examples}d shows histograms of
-the difference between the position angle, \(\text{PA}_0\) determined
-by our fits and that listed in \citet{Kobulnicky:2016a}.  Although
-observational uncertainties undoubtedly contribute in part, the
-differences are mainly due to real asymmetries in the bow shocks,
-especially for the 4- and 5-star sources.  The
-\citeauthor{Kobulnicky:2016a} catalog \(\text{PA}_0\) values are
-mostly sensitive to the orientation of the bow shock wings, whereas
-our fitted \(\text{PA}_0\) values are determined by the point in the
-bow shock head that is closest to the stellar source.  For this
-reason, we use the catalog \(\text{PA}_0\) values for defining the
-axis when measuring \(R_{90+}\) and \(R_{90-}\). On the other hand,
-the fitted values of \(\text{PA}_0\) are better correlated with the
-position of the bow shock's brightness peak, as is apparent in the
-lower left panels of Figure~\ref{fig:mipsgal-examples}a and c.
-
-\subsubsection{OB bow shock shapes on the diagnostic plane}
-\label{sec:ob-shapes}
-
-The derived bowshock shapes of all the 3-, 4-, and 5-star sources are
-shown in Figure~\ref{fig:mipsgal-shapes} on the plane of \(R_c/R_0\)
-versus \(R_{90} / R_0\).  Panel a shows the individual points
-superimposed on the theoretical results for quadrics of revolution
-(see figure caption and \S~\ref{sec:conic}), while panel b shows
-contours of the kernel density estimator (KDE, see
-\citealp{Leiva-Murillo:2012a, Scott:2015a}) of the two-dimensional
-distribution of points on the \(R_c\)--\(R_{90}\) plane.  The
-horizontal axis corresponds to the shape of the head of the bow shock
-near its apex, ranging from sharper, pointier shapes with
-\(R_c/R_0 < 1\) to flatter, snubber shapes with \(R_c/R_0 \gg 1\), where
-it must be understood that all judgments of sharpness/flatness are
-with respect to the axial separation, \(R_0\), between the source and
-the bow shock apex.  The vertical axis corresponds to the shape of the
-bow shock wings, ranging from closed ``C'' shapes for smaller values
-of \(R_{90} / R_0\) to open ``V'' shapes for larger values of
-\(R_{90} / R_0\).  The boundary between closed and open corresponds to
-the paraboloids, and is shown by the solid curved line that divides
-the shaded from the unshaded regions of the graph.
-
-The KDE contours in Figure~\ref{fig:mipsgal-shapes}b show that the
-distribution of 3-star sources is very similar to that of 4- and
-5-star sources, although the higher-rated sources are shifted slightly
-to the upper right.  Possible reasons for this are discussed in
-\S~\ref{sec:corr-shape} below.
-% This is probably due to higher-rated sources
-% being on average bigger, as will be discussed further below.
-The bulk of the sources are concentrated around the paraboloid line,
-with \(1 < R_c/R_0 < 2.5\), and \(1.2 < R_{90}/R_0 < 2\).  But
-significant minorities are found in three other regions: (1)~a clump
-with \(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\)
-at \(R_c/R_0 \approx 2\); and (3)~a broad horizontal tail towards higher
-\(R_c\) at \(R_{90}/R_0 \la 2\).
-
-\subsubsection{Correlation between bow shock size and other parameters}
-\label{sec:corr-size}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/mipsgal-pairplot}
-  \caption[]{Matrix of pair plots that illustrate distributions of and
-    correlations between the non-shape parameters of all MIPSGAL bow
-    shock sources from \citet{Kobulnicky:2016a}.  Plots on the leading
-    diagonal show histograms of the following parameters: bow shock
-    angular size, \(\log_{10} R_0\); Galactic latitude,
-    \(\log_{10}|b|\); Galactic longitude, \(\cos \ell\);
-    extinction-corrected \(H\)-band magnitude of the stellar source,
-    \(H_0\); \(K\)-band extinction, \(A_K\).  Scatter plots in the
-    upper triangle show the joint distribution of each pair of
-    parameters.  These are repeated in the lower triangle but showing
-    the KDEs of the joint distributions, which are annotated with the
-    Pearson linear correlation coefficient, \(r\), for each pair. The
-    straight lines shown superimposed on the plots of stellar magnitude
-    versus bowshock size correspond to toy model results for the same star
-    at a sequence of distances (dashed lines) and a sequence of
-    stellar luminosities at a fixed distance (dotted lines).  See text
-    for details. }
-  \label{fig:mipsgal-pairplot}
-\end{figure*}
-
-In Figure~\ref{fig:mipsgal-pairplot} we show the distributions over
-all MIPSGAL bow shock sources of the bow shock size, Galactic
-coordinates, extinction-corrected stellar source magnitude, and dust
-extinction.  For the bow shock size, \(R_0\), we use the results from
-our model fitting rather than the values given in the
-\citet{Kobulnicky:2016a} catalog, but the distribution is very
-similar, as can be seen by comparing the top-left plot of
-Figure~\ref{fig:mipsgal-pairplot} with \citeauthor{Kobulnicky:2016a}'s
-Figure~8.
-
-The catalog gives the \(K\)-band extinction, \(A_K\), derived using
-the method of \citet{Majewski:2011a}, but that assumes an intrinsic
-color of \((H - [\SI{4.5}{\um}])_0 = +0.08\) magnitudes, which is too
-red if the sources are assumed to be OB stars.  We therefore re-derive
-\(A_K\) from the catalog magnitudes combined with the
-\citet{Indebetouw:2005a} reddening law, but assuming
-\((H - [\SI{4.5}{\um}])_0 = -0.1\) magnitudes, which is more typical
-of early type stars.  This does not make very much difference (compare
-the top-right plot of our Fig.~\ref{fig:mipsgal-pairplot} with
-\citeauthor{Kobulnicky:2016a}'s Fig.~9), but it does eliminate some of
-the apparent negative extinctions that are found in the catalog.  The
-same reddening law gives \(A_H = 1.55 A_K\), and this is used to
-derive extinction-corrected \(H\)-band apparent magnitudes, \(H_0\).
-
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
-  \end{tabular}
-  \caption[]{Example comparisons between the distribution of bowshock
-    shapes when the sources are divided into two or more sub-samples
-    according to the value of a categorical parameter.  Contours show
-    the KDE of the distribution of each sub-sample for all 3-, 4-, and
-    5-star sources, while filled circle symbols show 5-star sources
-    only. Inset histograms show the marginal distributions on the two
-    shape axes. (a)~Source environment, divided into three
-    sub-samples: ``Isolated'' (purple symbols and purple filled
-    contours), ``Facing \hii{} region or \SI{8}{\um} bright-rimmed
-    cloud'' (orange symbols and orange-brown hollow continuous
-    contours), and ``Within \hii{} region'' (green symbols and green
-    hollow dashed contours). (b)~Uncertainty in stellar source
-    identification, divided into two sub-samples: ``Multiple
-    candidates for stellar source'' (green symbols and green filled
-    contours) and ``Single candidate for stellar source'' (orange
-    symbols and orange-brown hollow continuous contours).}
-  \label{fig:mipsgal-uncorrelated}
-\end{figure*}
-
-The most significant linear correlation between any pair of parameters
-in Figure~\ref{fig:mipsgal-pairplot} is that between bow shock size
-and stellar source brightness: \(H_0\) versus \(\log_{10} R_0\), with
-correlation coefficient \(r = -0.43\).  The distribution of \(H_0\)
-depends on the absolute magnitude, \(M_H\), and the distance, \(d\),
-to the source.  It is likely that variation in \(d\) is the more
-important of the two because \(M_H\) changes relatively little for
-main-sequence OB stars, ranging from \(M_H \approx -4\) (early-O) to
-\(M_H \approx -1.5\) (mid-B).  This is because part of the increase in
-bolometric luminosity, \(L\), as one ascends the main sequence is
-offset by an increase in the effective temperature,
-\(T_{\text{eff}}\), which shifts the peak of the stellar spectrum
-farther away from the \(H\)~band, resulting in
-\(L_H \propto L / T_{\text{eff}}^3 \sim L^{0.53}\), where the last step uses
-the upper main-sequence mass--luminosity and mass--radius scalings from
-\citet{Eker:2015a}. It is true that evolved OB supergiants can be much
-brighter, reaching \(M_H \approx -7\), but such stars are expected to be
-rare.  Assuming a B2V star (\(M_H = -2\)), then the observed range
-\(H_0 = 5\)--\(12\) corresponds to distances
-\(d = 100\)--\SI{6300}{pc}, and the histogram peak at
-\(H_0 \approx 9.5\) corresponds to \(d \approx \SI{2000}{pc}\), which is all
-perfectly reasonable.
-
-Turning now to the distribution of bow shock angular size, \(R_0\),
-this will also be affected by distance to at least some degree, since
-for a constant physical size the angular size will vary as
-\(R_0 \propto d^{-1}\).  For instance, if we assume that the physical size
-of all bow shocks is \SI{0.1}{pc} and the absolute magnitude of all
-stars is \(M_H = -2\), as above, then we find the relation
-\(H_0 = 14.57 - 5 \log_{10} R_0\) if \(R_0\) is measured in
-arcseconds. This is shown as a dashed line on the relevant panels of
-Figure~\ref{fig:mipsgal-pairplot} for values of \(R_0\) that
-correspond to \(d = \SI{300}{pc}\) to \SI{8000}{pc}.  It can be seen
-that this relation is in excellent agreement with the linear trend in
-the data. On the other hand, the correlation coefficient of
-\(r = -0.43\) means in broad terms that only a fraction
-\(r^2 \approx 20\%\) of the total variance in \(H_0\) is ``explained'' by
-changes in \(R_0\), and vice~versa, implying that one or both of
-\(H_0\) and \(R_0\) is only a very imperfect proxy for \(d\).  We have
-already seen that the spread in \(H_0\) probably \emph{is} mostly due
-to a spread in distance, rather than a spread in \(H\)-band stellar
-luminosity.  If this is true, it follows that it is \(R_0\) that
-depends only weakly on \(d\) and is more influenced by other factors.
-
-One such factor is the stellar/environmental momentum-loss ratio,
-\(\beta\), between the two supersonic flows that form the bow shock.  All
-other things being equal, we have \(R_0 \propto \beta^{1/2}\) for
-\(\beta \ll 1\), as is typically the case.  If the environment flow is
-constant and the OB star wind has mass-loss rate \(\dot{M}\) and
-terminal velocity \(V_\infty\), then
-\(\beta \propto \dot{M}{V_\infty}\).  Empirical and theoretical studies of hot star
-winds (e.g., \citealp{Puls:1996a}) imply
-\(\dot{M}{V_\infty} \sim L^{1.88} R^{-1/2} \sim L^{1.80} \sim L_H^{3.40}\), where
-the final two steps apply only to main-sequence stars and again use
-the relations of \citet{Eker:2015a}.  If we assume as above that a B2V
-star with \(M_H = -2\) has a bow shock physical size of \SI{0.1}{pc},
-and consider a sequence of stars with varying \(H\)-band luminosities
-but all at a fixed distance of \(d = \SI{2000}{pc}\), then we find the
-relation \(H_0 = 8.02 - 1.49 \log_{10} R_0\).  This is shown as a
-dotted line in the relevant panels of
-Figure~\ref{fig:mipsgal-pairplot} for the absolute magnitude range
-\(M_H = -3.6\) (O6V) to \(M_H = -1.5\) (B5V).  It can be seen that
-this relation does not match the linear trend in the data, and
-predicts a much larger spread in \(R_0\) over a narrow range in
-\(H_0\) than is observed.  This could mean one of two things: first,
-it may be that the range of stellar luminosities is significantly
-narrower than we have supposed, implying that B stars vastly outnumber
-O stars among the sources.  Alternatively, there may be a positive
-correlation between the stellar luminosity and the momentum of the
-environmental flow, with the result that \(\beta\) varies less steeply
-with \(L_H\) than we have assumed.  That could arise if more luminous
-stars were preferentially found in denser environments, or, in the
-case of runaways, if more luminous stars tended to be faster moving.
-
-A third factor that may influence \(R_0\) is the inclination, \(i\),
-of the bow shock axis with respect to the plane of the sky.
-Figure~\ref{fig:quadric-projection}b shows that for \(R_c > 1\), then
-the projected \(R_0'\) becomes larger than the true \(R_0\) as \(|i|\)
-increases.  This is further illustrated in
-Figure~\ref{fig:projected-R90-Rc-snapshots} for simple quadric shapes
-(spheroids, paraboloids, hyperboloids) and in
-Figure~\ref{fig:thin-shell-R90-Rc-snapshots} for the wilkinoid,
-cantoids, and ancantoids.  It can be seen that the effect is
-relatively modest for bow shocks with projected shapes falling in the
-range \(1 < R_c/R_0 < 3\) and \(R_{90}/R_0 < 3\), as the vast majority
-of our observed sources do.  The increase in \(R_0\) is no more than a
-factor of 2 to 3 for moderate inclinations of \(30\) to \(60\degr\),
-although it can reach a factor of 5 to 10 for some shapes at more
-extreme inclinations.
-
-%% Maybe talk about the other correlations later if we have time
-
-\subsubsection{Correlation between bow shock shape and other parameters}
-\label{sec:corr-shape}
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
-  \end{tabular}
-  \caption[]{As Fig.~\ref{fig:mipsgal-uncorrelated} but for median
-    splits of continuous parameters. (a)~Bow shock angular size,
-    \(R_0\), divided into two equal-sized sub-samples: large (blue
-    symbols and blue filled contours) and small (red symbols and red
-    hollow contours).  (b)~Extinction-corrected \(H\)-band magnitude
-    of the stellar source, divided into two equal-sized sub-samples:
-    bright (red symbols and orange filled contours) and faint (green
-    symbols and green hollow contours).}
-  \label{fig:mipsgal-correlated}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]
-  {figs/mipsgal-boxplot-Rc-R90-versus-R0}
-  \caption{Box plots of the distributions of bow shock shape
-    parameters, \(\Pi\) and \(\Lambda\), together with a
-    measure of the tail asymmetry, \(|\Lambda_{+} - \Lambda_{-}| / \Lambda\),
-    after partitioning on the bow shock size, \(R_0\).  All 3-, 4-,
-    and 5-star sources are sorted according to \(R_0\) and divided
-    into 5 non-overlapping sub-samples of roughly equal size, each
-    labelled by their median value of \(R_0\) in arcseconds, as
-    illustrated in the lower panel.  The colored boxes show the
-    interquartile range, with the median indicated by a horizontal
-    line, the 1st-to-9th interdecile range by error bars, and outliers
-    by diamonds.  A 5-sample Anderson--Darling test and Brown--Forsythe
-    test is performed for each dependent variable, with resultant
-    \(p\)-value given at the bottom of each panel.   It is apparent
-    that the dispersion in \(\Lambda\) (upper panel) increases
-    systematically with \(R_0\), although the central value is roughly
-    constant.  No clear systematic changes are apparent in
-    \(\Pi\) (middle panel).}
-  \label{fig:mipsgal-boxplot}
-\end{figure}
-
 \begin{figure}
@@
 
-We now investigate if the bow shock shapes of the MIPSGAL sources are
-correlated with any other parameters via the following methodology:
-\begin{enumerate}[1.]
-\item For each of the parameters in the \citet{Kobulnicky:2016a}
-  catalog, we divide the sources into two or more sub-samples,
-  according to the value of the parameter.  For quantitative
-  parameters, such as those discussed in the previous section, we use
-  two sub-samples of equal size, with membership determined by whether
-  the parameter is larger or smaller than the median value.  But we
-  also use categorical parameters, such as the type of bow shock
-  environment, or the presence/absence of \SI{8}{\um} emission, in
-  which case the sub-samples are of unequal size.
-\item We plot the KDEs of the two sub-samples separately on the
-  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
-  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
-  differences.
-\item We check if there is any statistically significant difference
-  between the bow shock shapes of the sub-samples by applying three
-  different non-parametric tests to \(R_c/R_0\) and \(R_{90}/R_0\)
-  separately.  The principal test used is the two-sample
-  Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a,
-    Makarov:2017a}, which is a general test of the \textit{null
-    hypothesis} that the two sub-samples are drawn from the same
-  distribution.  It returns a \(p\)-value, which is the estimated
-  probability that the observed difference between the two sub-samples
-  would be as large as it is purely by chance if they were all were
-  drawn from the same distribution.  We consider two different
-  thresholds for significance: \(p < 0.05\) (approximately
-  2-\(\sigma\) for a normal distribution) and \(p < 0.003\) (approximately
-  3-\(\sigma\)).  We show in Appendix~\ref{sec:distr-p-values} that the
-  more stringent \(p < 0.003\) condition is required in order to
-  confidently reject the null hypothesis and declare a ``significant''
-  difference between the two sub-samples, but we also consider the
-  less strict threshold of \(p < 0.05\) as an indicator of
-  ``possible'' difference.  We supplement the general-purpose
-  Anderson--Darling test with two tests that probe specific features of
-  the sample distributions: the Mann--Whitney--Wilcoxon \(U\) test
-  \citep{Mann:1947a}, which is sensitive to differences in the central
-  value (e.g., median) and the Brown--Forsythe test
-  \citep{Brown:1974a}, which is sensitive to differences in the
-  variance, or width, of the distribution (see
-  Appendix~\ref{sec:distr-p-values} for details).
-\end{enumerate}
-
-As shown in detail in Table~\ref{tab:big-p}, there is remarkably
-little variation in the bow shock shape distributions as a function of
-most of the other parameters.  Two examples in which there is
-\textit{no} significant shape difference between the sub-samples are
-shown in Figure~\ref{fig:mipsgal-uncorrelated}.  This lack of
-difference is interesting because in both examples there are a priori
-grounds to suspect that differences might exist.  The first example (Fig.~\ref{fig:mipsgal-uncorrelated}a) is
-the bow shock environment, which was categorized in
-\citet{Kobulnicky:2016a} as ``Isolated'' (I), ``Facing a large \hii{}
-region'' (FH), ``Facing a \SI{8}{\um} bright-rimmed cloud'' (FB), and
-``Within a giant \hii{} region'' (H), and where we have merged the FH
-and FB categories, labelled ``Facing'' in the figure.\footnote{Similar
-  results are also found for the FB and FH categories separately.}
-The shapes might be expected to vary with environment because the FB
-and FH categories should be associated with ``weather vane''
-interactions \citep{Povich:2008a} between the stellar wind and a
-divergent photoevaporation flow.  This is expected to give a more open
-bow shock than in the ``runaway'' case of interaction of a moving star
-with a static environment.  In the thin-shell approximation, the
-predicted shapes are a cantoid for weather vanes and a wilkinoid
-for runaways, see \S~\ref{sec:crw-scenario}.  The fact that no such
-difference is detected could be explained in one of two ways: (i)~the
-momentum ratio \(\beta\) for the weather vanes could be small, since the
-cantoid becomes indistinguishable from the wilkinoid as
-\(\beta \to 0\), or (ii)~many of the bow shocks classified as ``Isolated''
-might also be weather vanes rather than runaways.
-
-The second example (Fig.~\ref{fig:mipsgal-uncorrelated}b) divides the
-sources according to whether or not \citet{Kobulnicky:2016a} judged
-there to be multiple candidates for the identity of the central star
-that drives the bow shock.  If the central star were to be
-misidentified in a significant number of sources, then the measured
-value of \(R_0\) for those sources would be erroneous, which would
-increase the scatter in both \(R_c/R_0\) and \(R_{90}/R_0\).  The
-fact that no significant difference is seen in the shape distributions
-between sources with/without multiple candidates implies that such
-mistakes in identification of the central star must be rare.
-
-We also tested all the other source parameters listed in
-\citeauthor{Kobulnicky:2016a}'s catalog, finding no significant shape
-differences for sources with/without \SI{8}{\um} emission, with
-low/high extinction, closer/farther from the Galactic plane, or
-closer/farther from the Galactic center. Details are given in
-Table~\ref{tab:big-p}.  In all these cases, differences in mean or
-median \(R_{90}/R_0\) less than \(0.06\) and in \(R_c/R_0\) less than
-\(0.16\) are found, corresponding to rank biserial correlation
-coefficients (a non-parametric dimensionless measure of the difference
-between two samples, see Appendix~\ref{sec:distr-p-values}) of
-\(r_b < 0.15\), which are not significant even at the 2-\(\sigma\) level.
-
-The only parameters that \emph{do} show a possible correlation with
-the bowshock shape are the bow shock angular size, \(R_0\), and the
-extinction-corrected magnitude of the central star, \(H_0\), which are
-illustrated in Figure~\ref{fig:mipsgal-correlated}.  In both cases,
-the general purpose Anderson--Darling test indicates differences in the
-sub-sample distributions of \(R_{90} / R_0\) at the 2-\(\sigma\) level.  It
-is apparent from the histograms shown in the right-hand inset graphs
-of Figure~\ref{fig:mipsgal-correlated}a that in the case of the
-small/large \(R_0\) sub-samples it is the width rather than the
-central tendency of the distributions that is different, which is
-confirmed by the more specific Brown--Forsythe test, which indicates a
-difference between the sub-sample dispersions at the 3-\(\sigma\) level.
-In the case of the faint/bright \(H_0\) sub-samples
-(Fig.~\ref{fig:mipsgal-heteroscedastic}b), it is less clear what
-feature of the distributions differ.
-
-In order to investigate these effects in more detail and look for
-systematic trends, we divide the independent parameter (\(R_0\) or
-\(H_0\)) into 5 rather than 2 equal-sized sub-samples, with results
-shown as box plots in Figure~\ref{fig:mipsgal-boxplot}.  A systematic
-increase with \(R_0\) in the dispersion of \(R_{90}/R_0\) (upper panel
-of Fig.~\ref{fig:mipsgal-boxplot}a) is apparent from both the
-interquartile range (colored boxes) and interdecile range (error
-bars).  As a check on whether observational uncertainties might be
-contributing to this trend, the third and fourth rows of box plots
-show the statistics for, respectively, the fractional asymmetry of the
-bowshock wings and the standard deviation, \(\epsilon(R_{90})\), of the
-individual points on the bow shock that go into determining \(R_{90}\)
-(see step~\ref{step:R90} of the tracing/fitting methodology described
-in \S~\ref{sec:autom-trac-fitt}).  It can be seen that neither of
-these quantities tends to increase with \(R_0\), and in fact there is
-a significant \emph{decrease} in \(\epsilon(R_{90})\) with \(R_0\).  This
-implies that the increase with angular size of the diversity of bow
-shock wing shapes is real, and not due to observational uncertainties.  
-On the other hand, the fact that no clear trends are evident as a
-function of source magnitude \(H_0\) (Fig.~\ref{fig:mipsgal-boxplot}b)
-leads us to suspect that the \(p < 0.05\) result obtained for the
-2-sample Anderson--Darling test was a \emph{false positive}, which is
-also supported by the analysis in Appendix~\ref{sec:distr-p-values}
-and Figure~\ref{fig:histo-p-values}.
-
-So, the only correlation that survives scrutiny is the increase in
-dispersion of \(R_{90}/R_0\) with increasing \(R_0\), which is finally
-presented in the greatest detail in
-Figure~\ref{fig:mipsgal-heteroscedastic}, where we eschew any binning
-and perform linear regressions of the individual sources as a function
-of \(\log_{10} R_0\).  As expected from the previous 2-sample and
-5-sample analyses, the regression of \(R_{90}/R_0\) is almost flat,
-with a low correlation coefficient, whereas a regression of the
-absolute residuals to this fit against \(\log_{10} R_0\) shows a
-significant positive slope.  This increase in dispersion of shape with
-angular size is only evident for \(R_0 < 30''\), becoming flat at the
-largest sizes (see middle panel of
-Fig.~\ref{fig:mipsgal-heteroscedastic}).
-
-As mentioned in \S~\ref{sec:ob-shapes} there is also a shape
-difference between the 3-star sources and the 4/5-star sources (see
-Fig.~\ref{fig:mipsgal-shapes}b).  The \(p\)-values of statistical
-tests (see Table~\ref{tab:big-p}) indicate that this is much more
-significant than any correlation with the other parameters discussed
-in this section (\(p < 10^{-4}\) for \(R_{90}/R_0\) and
-\(p < 10^{-5}\) for \(R_c/R_0\)).  This means that it cannot be simply
-due to the tendency of the higher-rated sources to have larger angular
-sizes.  However, the subjective nature of the star ratings makes this
-result hard to interpret.
-
-\subsection{Far-infrared arcs around late-type stars}
-\label{sec:far-infrared-arcs}
-
-\begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
-    (a) & (b) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/alphaori-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}\\
-    (c) & (d) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/rhya-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}\\
-    (e) & (f) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/uuaur-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}\\
-    (g) & (h) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/rcas-imageplot}
-  \end{tabular}
-  \caption{RSG and AGB shells observed with Herschel.  Selected
-    Class~I sources (``fermata-like'') from the MESS survey
-    \citet{Cox:2012a}, where the arc structure is particularly clear
-    and symmetrical.  Left panels show PACS \SI{70}{\um} surface
-    brightness (blue) and \SI{160}{\um} (orange).  Right panels show
-    tracing of the bow shock arc (red symbols) and circle fit (magenta
-    lines and symbols) superimposed on a low-contrast image of the
-    \SI{70}{\um} surface brightness. (a)~\(\alpha\)~Ori. (b)~\(\mu\)~Cep.
-    (c)~R~Hya. (d)~R~Leo. (e)~UU~Aur. (f)~V1934~Sgr. (g)~X~Pav.
-    (h)~R~Cas.}
-  \label{fig:herschel-arc-fits}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
-    (a) & (b) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot} \\
-    (c) & (d) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot} \\
-    (e) & (f) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot} \\
-    (g) & (h) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
-  \end{tabular}
-  \caption{As Fig~\ref{fig:herschel-arc-fits}, but for a further 8
-    Class~I sources from \citet{Cox:2012a} where the arc structure is
-    more diffuse, weak, and/or asymmetric. (a)~CW~Leo. For this source
-    only, the right-hand panel shows a grayscale image of the
-    \SI{160}{\um} rather than \SI{70}{\um}
-    emission. (b)~EP~Aqr. (c)~\(\chi\)~Cyg. (d)~RT~Vir. (e)~W~Aql. (f)~W~Pic. (g)~R~Scl.
-    (h)~\(\theta\)~Aps.}
-  \label{fig:herschel-arc-fits-poor}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
-  \caption[]{Comparison of bow shock shapes between Herschel RSG/AGB
-    arcs (large red symbols and hollow red contours) and MIPSGAL OB
-    star arcs (small purple symbols and filled purple contours).
-    Other details of the plots are as in
-    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
-    except that the diagnostic plots are zoomed in slightly to show
-    more detail, and a smaller KDE smoothing bandwidth of
-    \(0.12 \times 0.08\) is used.}
-  \label{fig:herschel-compare-mipsgal}
-\end{figure}
-
-We obtain a second sample of bow shocks from a far-infrared survey
-\citep{Cox:2012a} of circumstellar shells around asymptotic giant
-branch (AGB) stars and cool supergiants, obtained as part of the
-\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
-\citep{Groenewegen:2011a}.  The survey sources were divided into four
-classes by \citeauthor{Cox:2012a}, according to the overall shape of
-the extended emission at \SI{70}{\um}: ``fermata~\textfermata'', or
-arcs (Class~I); ``eyes~\faEye'' (Class~II); ``rings~{\Large
-  \(\odot\)}'' (Class~III), and ``irregular~\staveXXV'' (Class~IV).  Of
-these, only the Class~I sources clearly correspond to bow shocks,
-which represent 22 out of 50 total sources detected with extended
-emission.  For our sample, we select the 16 Class~I sources where the
-shape parameters can be reliably measured, and which are shown in
-Figures~\ref{fig:herschel-arc-fits}
-and~\ref{fig:herschel-arc-fits-poor}. The remaining six Class~I
-sources (Fig.~1 of \citealp{Cox:2012a}) are too asymmetrical or
-irregular to reliably determine \(R_{c}\) and \(R_{90}\), and are
-therefore excluded from our sample.
-
-In most sources, the bow shock shell is most clearly visible in the
-\SI{70}{\um} band, with the exception being CW~Leo where the
-\SI{180}{\um} band is used instead.  In several sources, the shell is
-split into multiple filaments, with the clearest example being
-\(\alpha\)~Ori (Betelgeuse), shown in
-Figure~\ref{fig:herschel-arc-fits}(a).  For such sources, we take the
-outer envelope of the filaments as the bow shock arc.  Given this
-complication, and the fact that the angular resolution relative to the
-bow shock size is much better than in the MIPSGAL sources, we judge
-that the arc tracing is best performed by eye and this is carried out
-using the SAOImage~DS9 FITS viewer \citep{Joye:2003a}, with results
-shown as small red open circles in Figures~\ref{fig:herschel-arc-fits}
-and~\ref{fig:herschel-arc-fits-poor}.  Subsequently, the bow shock
-parameters \(R_0\), \(R_{90}\), and \(R_c\) are determined by circle
-fits, as in steps 5--8 of \S~\ref{sec:autom-trac-fitt}, with results
-shown in magenta on the figures.
-
-Figure~\ref{fig:herschel-compare-mipsgal} compares the distributions
-of bow shock shapes between the Herschel (RSG/AGB) and MIGSGAL (OB
-star) samples.  The Anderson--Darling test gives a highly significant
-difference between the \(R_{90}/R_0\) ratio distributions of the two
-samples, but only a marginally significant difference between the
-\(R_c/R_0\) ratio distributions (detailed results are shown in
-Table~\ref{tab:big-p}).  The Herschel sources show considerably
-smaller \(R_{90}\) ratio (median \(R_{90}/R_0 \approx 1.4\), implying bow
-shock wings that are more closed than in the MIPSGAL sources (median
-\(R_{90}/R_0 \approx 1.7\)).  For the radius of curvature ratio, there is
-only a slight difference in average values: median
-\(R_c/R_0 \approx 1.5\) for Herschel versus \(\approx 1.6\) for MIPSGAL, which is
-not statistically significant (rank biserial \(p = 0.29\)).  On the
-other hand, the dispersion in \(R_c/R_0\) is four times smaller for
-the Herschel sample, which is marginally significant (Brown--Forsythe
-\(p = 0.015\)).  In particular, the MIPSGAL sample shows a significant
-minority of very flat-nosed shapes (\(R_c/R_0 > 2\)), but these are
-absent in the Herschel sample.  The same can be seen directly by
-comparing the RSG/AGB bow shock shapes in
-Figures~\ref{fig:herschel-arc-fits}
-and~\ref{fig:herschel-arc-fits-poor} with the representative OB bow
-shocks of Figure~\ref{fig:mipsgal-shapes}b.  The MIPSGAL sources K489
-and K123 have shapes that are similar to specific Herschel sources
-(UU~Aur and R~Hya, respectively), while sources such as K447 (extreme
-flat head) or K517 (extreme open wings) have no analog among the
-Herschel sources.
-
-\subsection{Stationary emission line arcs in M42}
-\label{sec:stat-emiss-line}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/annotated-ll-arcs}
-  \caption[]{Stationary bow shock arcs in the Orion Nebula.}
-  \label{fig:ll-arcs}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
-  \caption[]{Comparison of Orion with OB stars.  Other details of the
-    plots are as in Figs.~\ref{fig:mipsgal-shapes}
-    and~\ref{fig:mipsgal-uncorrelated}, except that the diagnostic
-    plots are zoomed out to encompass larger ratio values, and a
-    larger KDE smoothing bandwidth of \(0.3 \times 0.2\) is used.}
-  \label{fig:ll-compare-mipsgal}
-\end{figure}
-
-Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "obs-bowshocks.tex"
+%%% TeX-master: "obs-bowshocks"
 %%% End:

### 2019-04-07 papers/Papers1234/sec-quadrics-observations.tex
Redo standing wave figures for Paper IV
Increase the amplitude of oscillation

@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/mipsgal-R90-ratio-versus-R0-heteroscedastic}
-  \caption{Regression analysis of bow shock wings shape versus size.
-    The top panel shows a linear fit to \(R_{90}/R_0\) versus
-    \(\log_{10} R_0\), which is essentially flat and is consistent
-    with no correlation between the two quantities.  On the other
-    hand, in the central panel, which shows the absolute values of the
-    residuals from this fit, it is apparent that the dispersion about
-    the average value of the bow shock shape parameter \(R_{90}/R_0\)
-    increases with bow shock size.  A linear fit to all the data is
-    shown by the blue dotted line, while a locally weighted regression
-    (LOWESS; \citealp{Cleveland:1979a, Cleveland:1988a}) is shown by
-    the heavy green dashed line.  The negative curvature of the LOWESS
-    curve suggests that the slope of the linear fit is a compromise
-    between a steeper slope for smaller bow shocks and a flat (or
-    negative) slope for the largest bow shocks.  We therefore repeat
-    the linear fit, but after excluding sources with \(R_0 > 25''\),
-    with results shown by the red dotted line.  The bottom panel shows
-    the bow shock wings asymmetry parameter,
-    \(|R_{90+} - R_{90-}| / R_{90}\), together with a linear fit.
-    Symbol size indicates the star rating of each source, from 3-star
-    (smallest) to 5-star (largest).}
-  \label{fig:mipsgal-heteroscedastic}
-\end{figure}
-
 We now investigate if the bow shock shapes of the MIPSGAL sources are

### 2019-04-07 papers/Papers1234/bs-bw-dw-01.tex
Finish first complete draft of Paper I
Submit BS-BW-DW-01 paper
Finish intro for Paper III
Submit revised version of Paper I to MNRAS
Expanded captions for Figs 5, 6, 7.  Change "bow" to "bow shell" in
many places.

@@
   the ambient density is below \SI{100}{cm^{-3}}.  At higher densities
-  radiation-supported bows can form, tending to be optically thin bow
-  waves around B~stars, or optically thick bow shocks around early
-  O~stars.  For OB stars with particularly weak stellar winds,
-  radiation-supported bows become more prevalent.
+  radiation-supported bow shells can form, tending to be optically
+  thin bow waves around B~stars, or optically thick bow shocks around
+  early O~stars.  For OB stars with particularly weak stellar winds,
+  radiation-supported bow shells become more prevalent.
 \end{abstract}
@@
 \input{sec-strong-coupling}
+
+\section*{Acknowledgements}
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grants Programa de Apoyo a Proyectos de Investigación
+e Inovación Tecnológica IN112816 and IN107019.  We thank the referee
+for a helpful report.
+
 \bibliographystyle{mnras}

### 2019-04-07 papers/Papers1234/sec-dust-bow-intro.tex
Jane's Paper I corrections, up to end of sec 2.3
Submit revised version of Paper I to MNRAS
Expanded captions for Figs 5, 6, 7.  Change "bow" to "bow shell" in
many places.

@@
     depth of the shocked shell increases, the stellar radiation
-    momentum adds to the wind ram pressure to help support the bow.
-    If the shell is completely opaque to stellar radiation, we have a
-    radiation-supported bow shock (lower right), where it is the
-    stellar radiation pressure that balances the ram pressure of the
-    external stream.  For intermediate optical depths, we have two
+    momentum adds to the wind ram pressure to help support the bow
+    shell.  If the shell is completely opaque to stellar radiation, we
+    have a radiation-supported bow shock (lower right), where it is
+    the stellar radiation pressure that balances the ram pressure of
+    the external stream.  For intermediate optical depths, we have two
     cases depending on the strength of coupling between grains and
@@
 \citep[Paper~II]{Henney:2019b}, and how observations can distinguish
-between different classes of bow \citep[Paper~III]{Henney:2019c}.
+between different classes of bow shell
+\citep[Paper~III]{Henney:2019c}.
 %
@@
 In \S~\ref{sec:strong-gas-grain} we propose a simple model for stellar
-bows and investigate the relative importance of wind and radiation in
+bow shells and investigate the relative importance of wind and radiation in
 providing internal support for the bow shell as a function of the
@@
 In \S~\ref{sec:discussion} we briefly discuss the application
-of our models to observed bows.
+of our models to observed bow shells.
 %
-In \S~\ref{sec:summary} we summarise the conclusions of our study. 
+In \S~\ref{sec:summary} we summarise our findings. 
 %

### 2019-04-07 papers/Papers1234/sec-strong-coupling.tex
Submit revised version of Paper I to MNRAS
Expanded captions for Figs 5, 6, 7.  Change "bow" to "bow shell" in
many places.

@@
-\section{A simple model for stellar bows}
+\section{A simple model for stellar bow shells}
 \label{sec:strong-gas-grain}
@@
   \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
-  \caption{Bow regimes in parameter space (\(v, n\)) of the external
-    stream for main-sequence OB stars of different masses:
+  \caption{Bow shell regimes in parameter space (\(v, n\)) of the
+    external stream for main-sequence OB stars of different masses:
     (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}.  In all
     cases, \(\kappa = \SI{600}{cm^2.g^{-1}}\) and efficient gas-grain
-    coupling is assumed. Solid black lines of varying thickness show the
-    bow size (star-apex separation, \(R_0\)), while gray shading shows
-    the radiation bow wave regime, with lower border
+    coupling is assumed. Solid black lines of varying thickness show
+    the bow shell size (star-apex separation, \(R_0\)), while gray
+    shading shows the radiation bow wave regime, with lower border
     \(\tau = \eta\wind\) and upper border \(\tau = 1\), where
-    \(\tau = 2 \kappa \rho R_0\) is the optical depth through the bow.  For bows
-    above the red solid line, the ionization front is trapped inside
-    the bow (\S~\ref{sec:trapp-ioniz-front}).  Blue lines delineate
-    different cooling regimes (\S~\ref{sec:radi-cool-lengths}).  Above
-    the thin blue line (\(d_{\text{cool}} = h_0\)), the bow shock
-    radiates efficiently, forming a thin shocked shell.  Below the
-    thick blue line (\(d_{\text{cool}} = R_0\)), the bow shock is
-    essentially non-radiative.}
+    \(\tau = 2 \kappa \rho R_0\) is the optical depth through the bow.  For bow
+    shells above the red solid line, the ionization front is trapped
+    inside the bow shell (\S~\ref{sec:trapp-ioniz-front}).  Blue lines
+    delineate different cooling regimes
+    (\S~\ref{sec:radi-cool-lengths}).  Above the thin blue line
+    (\(d_{\text{cool}} = h_0\)), the bow shock radiates efficiently,
+    forming a thin shocked shell.  Below the thick blue line
+    (\(d_{\text{cool}} = R_0\)), the bow shock is essentially
+    non-radiative.}
   \label{fig:zones-v-n-plane}
@@
 
-We consider the canonical case of a bow around a star of bolometric
-luminosity, \(L\), with a radiatively driven wind, which is immersed
-in an external stream of gas and dust with density, \(\rho\), and
-velocity, \(v\).  The size and shape of the bow is determined by a
-generalized balance of pressure (or, equivalently, momentum) between
-internal and external sources.  We assume that the stream is
-supersonic and super-alfvenic, so that the external pressure is
-dominated by the ram pressure, \(\rho v^2\), and that dust grains and gas
-are perfectly coupled by collisions (the breakdown of this assumption
-is the topic of Paper~II).
+We consider the canonical case of a bow shell around a star of
+bolometric luminosity, \(L\), with a radiatively driven wind, which is
+immersed in an external stream of gas and dust with density, \(\rho\),
+and velocity, \(v\).  The size and shape of the bow shell is
+determined by a generalized balance of pressure (or, equivalently,
+momentum) between internal and external sources.  We assume that the
+stream is supersonic and super-alfvenic, so that the external pressure
+is dominated by the ram pressure, \(\rho v^2\), and that dust grains and
+gas are perfectly coupled by collisions (the breakdown of this
+assumption is the topic of Paper~II).
 
@@
 
-\subsection{Bows supported by radiation and wind}
+\subsection{Bow shells supported by radiation and wind}
 \label{sec:three-bow-regimes}
@@
 absorbed radiation is re-emitted, the grain opacity is much lower, so
-the bow is optically thin to this radiation.  Combined with the fact
+the bow shell is optically thin to this radiation.  Combined with the fact
 that the UV single-scattering albedo is only \(\approx 0.5\), this means
@@
 term from equation~\eqref{eq:wind-efficiency} allows us to write the
-general bow radius in terms of the fiducial radius as
+general bow shell radius in terms of the fiducial radius as
 \begin{equation}
@@
 \(n < \num{e4} \, v_{10}^2\).  Another difference is the size scale of
-the bows in this regime, which is
+the bow shells in this regime, which is
 \(R_0 = \text{\SIrange{0.001}{0.003}{pc}}\) for the \SI{10}{M_\odot} star
@@
 \(\Gamma\Edd \approx \text{\numrange{30}{400}}\), so gravity can be safely
-ignored.  When the optical depth of the bow is very large,
+ignored.  When the optical depth of the bow shell is very large,
 \(\tau > \ln\Gamma\Edd \sim 5\), gravity will exceed the radiation force in the
@@
 where it is the outer zone that is most important observationally.
-Bows are typically detected via their infrared radiation (absorption
+Bow shells are typically detected via their infrared radiation (absorption
 and re-emission by dust of stellar radiation), or by emission lines
@@
 maximum in the cooling coefficient \(\Lambda(T)\) around
-\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
+\(\SI{e5}{K}\).  For bow shells with outer stream densities above the thin
 blue line, radiative cooling is so efficient that the bow shock can be
@@
 the use of equation~\eqref{eq:isothermal-shell-density} in the
-previous section.  For bows with outer stream densities below the
+previous section.  For bow shells with outer stream densities below the
 thick blue line, cooling is unimportant and the bow shock can be
@@
 consideration of the slight increase in density between the shock and
-the contact/tangential discontinuity.  For bows with outer stream
+the contact/tangential discontinuity.  For bow shells with outer stream
 densities between the two blue lines, cooling does occur, albeit
@@
   \caption{Profiles of physical variables along the axis of the bow
-    shell for a wind-supported bow shock.  The case is shown of a
-    stream velocity of \SI{30}{km.s^{-1}} and an equilibrium ionized
-    sound speed of \SI{10}{km.s^{-1}}.}
+    shell for a wind-supported bow shock.  The top panel shows the gas
+    density (purple) and the gas thermal pressure (green dashed line)
+    as a function of radius from the star. The bottom panel shows the
+    absolute value of the gas velocity (red line) and sound speed
+    (orange line).  The stellar wind comes from the left with positive
+    velocity, while the ambient stream comes from the right. All
+    velocities are in the frame of reference of the star, which is
+    located off the left-hand edge of the figure.  The case shown is
+    for a stream velocity of \SI{30}{km.s^{-1}} and an equilibrium
+    ionized sound speed of \SI{10}{km.s^{-1}}, with a post-shock
+    cooling length \(d\cool\) that is smaller than the shell thickness
+    \(h_0\). The different flow regions are described in the text.}
   \label{fig:axial-structure-wbs}
@@
   \caption{As Fig.~\ref{fig:axial-structure-wbs} but for a
-    radiation-supported bow wave.}
+    radiation-supported bow wave.  The heavy dashed red line in the
+    lower panel shows the ballistic approximation to the velocity
+    profile, which would be followed in the case of a highly
+    supersonic incident stream.  The ambient stream is gradually
+    decelerated by absorption of stellar radiation, leading to a lower
+    velocity and higher density just before the shock, \(v_0\) and
+    \(n_0\), as compared to the values at large distances,
+    \(v_\infty\) and \(n_\infty\), which are shown by dashed horizontal lines.}
   \label{fig:axial-structure-rbw}
@@
   \caption{As Fig.~\ref{fig:axial-structure-wbs} but for a
-    radiation-supported bow shock.}
+    radiation-supported bow shock.  A smaller cooling length is assumed
+    than in the previous figures since the RBS regime occurs at higher
+    ambient densities.}
   \label{fig:axial-structure-rbs}
@@
 at the contact discontinuity, but this is no longer true for
-radiation-supported bows, as illustrated in
+radiation-supported bow shells, as illustrated in
 Figures~\ref{fig:axial-structure-wbs} to
@@
 equations~(\ref{eq:Rstar}, \ref{eq:rad:R0}, \ref{eq:tau-thin},
-\ref{eq:strong-cooling-h0}, \ref{eq:scale-height}), and taking \(R_0 \approx R_*\), we find
+\ref{eq:strong-cooling-h0}, \ref{eq:scale-height}), and taking
+\(R_0 \approx R_*\), we find
 \begin{equation}
@@
 
-The stellar bows modeled in this paper can be seen as either due to
+The stellar bow shells modeled in this paper can be seen as either due to
 the motion of a star through the interstellar medium, or due to the
@@
 consider the stream densities and velocities expected in each of these
-scenarios, and compare them with our predictions for the type of bows
+scenarios, and compare them with our predictions for the type of bow shells
 that should result.
@@
 flows \citep{Dyson:1968a}, but this is achieved at expense of a lower
-density.  Given all the above, we expect there to be many more bows
-with relative stream velocity \(v_\infty \sim \SI{20}{km.s^{-1}}\) than bows
+density.  Given all the above, we expect there to be many more bow shells
+with relative stream velocity \(v_\infty \sim \SI{20}{km.s^{-1}}\) than bow shells
 with \(v_\infty \sim \SI{100}{km.s^{-1}}\).
@@
 (\(\approx 10\%\) and \(< 1\%\), respectively).  However, observations of
-stellar bows are clearly biased towards these higher densities.
-
-In part, this bias is due to bows being easier to detect in denser
+stellar bow shells are clearly biased towards these higher densities.
+
+In part, this bias is due to bow shells being easier to detect in denser
 environments.  Depending on the emission mechanism, the shell
@@
 (\(\propto n^2 R_0^3\)), which are both increasing functions of \(n\) since,
-from \S~\ref{sec:three-bow-regimes}, the bow size falls relatively
+from \S~\ref{sec:three-bow-regimes}, the bow shell size falls relatively
 slowly as \(R_0 \propto n^{-1/2}\) in the WBS and RBS cases, and is
@@
 O-star lifetime of \(< \SI{4}{Myr}\), which is of the same order as
-the sizes of Giant Molecular Clouds.  Many observed stellar bows are
+the sizes of Giant Molecular Clouds.  Many observed stellar bow shells are
 found in high mass star clusters associated with large \hii{} regions
@@
 
-In \S~\ref{sec:depend-stell-type} we found that the bow is
+In \S~\ref{sec:depend-stell-type} we found that the bow shell is
 wind-supported when \(\tau_*^2 < \eta\wind\), where \(\tau_*\) is a fiducial
@@
 (eq.~[\ref{eq:wind-eta-typical}]).  This translates into a maximum
-stream density for wind-supported bows of
+stream density for wind-supported bow shells of
 \newcommand\crit{\ensuremath{_{\text{max}}}}
@@
 \hii{} regions of moderate density (\(n \sim \SI{100}{cm^{-3}}\)) can
-easily have \(n > n\crit\), meaning that their bows will be radiation
+easily have \(n > n\crit\), meaning that their bow shells will be radiation
 supported.
@@
 densities, reaching \(n\crit \sim \SI{1}{cm^{-3}}\) for
-\(v = \SI{20}{km.s^{-1}}\).  This means that radiation-supported bows
+\(v = \SI{20}{km.s^{-1}}\).  This means that radiation-supported bow shells
 become feasible even in the diffuse ISM for this important class of
@@
 is therefore important to critically re-evaluate attempts to
-\emph{measure} mass loss rates using observations of bows
+\emph{measure} mass loss rates using observations of bow shells
 \citep{Gvaramadze:2012a, Kobulnicky:2018a} since such calculations
@@
 mid-infrared continuum emission around \SI{24}{\um}, which is where
-stellar bows are most easily detected \citep{Meyer:2016a,
+stellar bow shells are most easily detected \citep{Meyer:2016a,
   Kobulnicky:2016a}. There is some evidence that such grains may be
@@
 equation~\eqref{eq:ncrit}, this would increase \(n\crit\) by the same
-factor, making radiation-supported bows less likely.  On the other
+factor, making radiation-supported bow shells less likely.  On the other
 hand, the process of Radiative Torque Disruption is predicted to be
 important \citep{Hoang:2018a} for the high radiation fields found in
-stellar bows, and this would tend to \emph{increase} the VSG abundance
+stellar bow shells, and this would tend to \emph{increase} the VSG abundance
 (and hence \(\kappa\)) via the centrifugal destruction of larger grains.
@@
 \citealp{Vink:2001a}), which will largely cancel out the effect in our
-bow models.
+bow shell models.
 
@@
 We have presented a systematic study of the formation of emission
-arcs, or bows, around luminous stars that move supersonically relative
-to their surrounding medium, taking into account both the stellar wind
-and radiation pressure of the star.  In this initial study, we
-considered the case where gas and grains are perfectly coupled via
-collisions, and applied our models to OB stars.  Our principal results
-are as follows:
+arcs, or bow shells, around luminous stars that move supersonically
+relative to their surrounding medium, taking into account both the
+stellar wind and radiation pressure of the star.  In this initial
+study, we considered the case where gas and grains are perfectly
+coupled via collisions, and applied our models to OB stars.  Our
+principal results are as follows:
 \begin{enumerate}[1.]
@@
 \item Studies that have estimated wind mass-loss rates from
-  observations of bows need to be re-evaluated in the light of
+  observations of bow shells need to be re-evaluated in the light of
   possible radiation support. 

### 2019-04-08 papers/Papers1234/sec-obs-intro.tex
Write some introduction to Paper IV

@@
 \label{sec:introduction}
+
+Stellar bow shocks are produced by the relative motion between a star
+and its surrounding medium, and are commonly detected as curved arcs
+of emission at optical \citep{Gull:1979a, Brown:2005a}, infrared
+\citep{van-Buren:1988a, Kobulnicky:2016a}, or radio
+\citep{van-Buren:1990a, Benaglia:2010a} wavelengths.  The canonical
+theory for these objects is that they are formed by a two-shock
+interaction between the stellar wind and the interstellar medium
+\citep{Pikelner:1968a, Dyson:1972a}, which is distorted due to the
+supersonic motion of the star \citep{Baranov:1970a, Wilkin:1996a}.  In
+some instances, however, the absorbed stellar radiation pressure may
+be more important than the stellar wind in providing the inner support
+for the bow shell \citep[Paper~I]{Henney:2019a} and this may even be
+sufficient to break the collisional coupling between gas and dust
+grains \citep[Paper~II]{Henney:2019b}.  In other cases, the appearance
+of an infrared emission arc may be due to the illumination of the
+inner wall of an asymmetrical cavity \citep{Mackey:2016a}, rather than
+the formation of a dense shell, in which case the relative velocity of
+the star may be subsonic with respect to its surroundings
+\citep{Mackey:2015a}.
+
+The largest number of bow shocks have been detected around OB stars,
+via their mid-infrared dust emission \citep{van-Buren:1995a,
+  Smith:2005a, Povich:2008a, Kobulnicky:2010a, Peri:2012a, Peri:2015a,
+  Sexton:2015b, Kobulnicky:2016a, Bodensteiner:2018a}, and these have
+sizes ranging from \SIrange{0.01}{1}{pc}.
 
@@
 
+Interaction of wind with photoevaporation flow \citep{Dyson:1975a}
+
 HMXRB in external galaxies, possible bowshock in LMC~X-1 \citep{Hyde:2017a}.
+
+Wolf-Rayet bow shock nebulae \citep{Dyson:1989a}
 
@@
 \citep{Ueta:2008a, Sahai:2010a, Cox:2012a}. 
+Bowshocks from red supergiants \citep{Meyer:2014a}
 
-Instability of bow \citep{Blondin:1988a}
+Instability of bow \citep{Blondin:1998a}
 

### 2019-04-08 papers/Papers1234/sec-observational-diagnostics.tex
Write some introduction to Paper IV

@@
 wind (which is itself radiatively driven).  Radiatively supported bows
-(DW, RBW, or RBS, or cases) should lie on the diagonal line
+(DW, RBW, or RBS cases) should lie on the diagonal line
 \(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where we have used
@@
 In either case, the bow is expected to be smaller than \SI{0.1}{pc}
-for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~6 of
+for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~8 of
 Paper~I.\@

### 2019-04-12 papers/Papers1234/bs-bw-dw-03.tex
Revised versions of all 4 bow shock papers to astro-ph
Fix reference lists and other minor changes

@@
   thickness.
+% \item Disruption of the largest dust grains by rotational torques in
+%   the strong circumstellar radiation field is predicted to have a
+%   relatively modest effect on the optical properties of the dust
+%   mixture (\S~\ref{sec:evolution-grain-size}), increasing the UV
+%   opacity by about 50\%.
 \item Disruption of the largest dust grains by rotational torques in
-  the strong circumstellar radiation field is predicted to have a
-  relatively modest effect on the optical properties of the dust
-  mixture (\S~\ref{sec:evolution-grain-size}), increasing the UV
-  opacity by about 50\%.
+  the strong circumstellar radiation field is predicted to increase
+  the UV opacity by about 50\% (\S~\ref{sec:evolution-grain-size}),
+  although the effect could be larger if the resulting fragments are
+  very small.
 \item The bow source KGK2010~2 is a low-luminosity B~star with an
@@
 Pandas \citep{McKinney:2010a} projects.  We thank Chip Kobulnicky for
-sharing results in advance of publication.
+sharing results in advance of publication and Thiem Hoang for useful
+discussions.
 

### 2019-04-17 papers/Papers1234/app-dust-wave.tex
Submit to MNRAS revised version of Paper II

@@
 inbound and outbound dust stream.  For the well-coupled case, this is
-not possible and a shocked shell must form (see Paper~I's Fig.~5b).
+not possible and a shocked shell must form (see Paper~I's Fig.~6).
 
@@
 given by the closest approach along individual trajectories,
-\(R\grain(\thm; b)\), but instead must found by minimizing
+\(R\grain(\thm; b)\), but instead must be found by minimizing
 \(R\grain(\theta; b)\) over all \(b\) for each value of \(\theta\), which yields
@@
 This is the polar form of the equation for the confocal parabola,
-which is discussed in detail in \S~\ref{Q-sec:conic} and
-Appendix~\ref{Q-app:parabola} of \citet{Tarango-Yong:2018a}.  In that
+which is discussed in detail in \S~4 and
+Appendix~C of \citet{Tarango-Yong:2018a}.  In that
 paper, the dimensionless quantities \textit{planitude} \(\Pi\) and
@@
 \(\theta \to \theta + \theta_1(b)\), where \(\sin \theta_1 = b / D\) (see
-Fig.~\ref{Q-fig:crw-schema} of \citealp{Tarango-Yong:2018a}). We
+Fig.~3 of \citealp{Tarango-Yong:2018a}). We
 parameterize the degree of divergence as \(\mu = R\starstar / D\) and, as
@@
     Two example trajectories, one with \(b > R\starstar\) (upper) and
-    one with \(b < R\starstar\) (lower) are shown schematically in
-    orange.  The orientation of the magnetic field lines is shown in
-    blue.  The grayscale image shows the resultant dust density
-    distribution.}
+    one with \(b < R\starstar\) (lower) are shown schematically by
+    black lines with arrows.  The orientation of the magnetic field
+    lines is shown in blue.  The grayscale image shows the resultant
+    dust density distribution.}
   \label{fig:inertia-thB0}
@@
 When the impact parameter is larger than \(b \sim R\starstar\), the
-trajectories are very similar to in the non-magnetic case
+trajectories are very similar to those of the non-magnetic case
 (Fig.~\ref{fig:dust-trajectories}a).  As shown in

### 2019-04-17 papers/Papers1234/bs-bw-dw-02.tex
Jane corrections to paper II complete to end of sec 3
Finish intro for Paper III
Submit to MNRAS revised version of Paper II

@@
 \usepackage{rotating}
-\usepackage{xr-hyper}
 \usepackage{hyperref}
@@
 \input{bs-bw-dw-defs.tex}
-
-\externaldocument[Q-]{quadrics-bowshock}
-%\externaldocument[I-]{bs-bw-dw-01}
-%\externaldocument[III-]{bs-bw-dw-03}
 
@@
 their shapes to be compared with theoretical predictions
-\citep{Wilkin:1996a, Tarango-Yong:2018a}.  A different class of
-stellar bow shocks are found in interacting binary systems
-\citep{Stevens:1992a}, but these typically emit by non-thermal
-mechanisms and are only resolvable using radio interferometry
-techniques \citep{Contreras:1999a, Dzib:2013a}.
+\citep{Wilkin:1996a, Tarango-Yong:2018a}.  A different variety of
+stellar bow shock is found in interacting binary systems
+\citep{Stevens:1992a}, which frequently involve a Wolf-Rayet star and
+typically emit by non-thermal mechanisms.  The closest and widest of
+such binary systems, WR~147, is marginally resolved in x~ray
+observations \citep{Pittard:2002a, Zhekov:2010a} but most
+are only mappable using radio interferometry techniques
+\citep{Contreras:1999a, Dzib:2013a}.
 
@@
   Ishiki:2018a} and a total decoupling very close to the central star
-\citep[Fig.~8 of][]{Draine:2011a}
+\citep[Fig.~8 of][]{Draine:2011a}.
 
@@
 \begin{equation}
-  \label{eq:x-cases}
-  R_0 \approx
-  \begin{cases}
-    \text{RBS (\(\tau_*^2 > 1\)):} & (1 + \eta\wind)^{1/2} \, R_*  \\
-    \text{RBW (\(\eta\wind < \tau_*^2 < 1\)):} & 2 \, \tau_* \, R_* \\
-    \text{WBS (\(\tau_*^2 < \eta\)):} & \eta\wind^{1/2} \, R_*  
-  \end{cases}
+\begin{aligned}
+  \text{RBS} \quad& (\tau_*^2 > 1): & R_0 &\approx  (1 + \eta\wind)^{1/2} \, R_*  \\
+  \text{RBW} \quad& (\eta\wind < \tau_*^2 < 1): & R_0 &\approx 2 \, \tau_* \, R_* \\
+  \text{WBS} \quad& (\tau_*^2 < \eta): & R_0 &\approx \eta\wind^{1/2} \, R_*  
+\end{aligned}\label{eq:x-cases}
 \end{equation}
@@
 \citep{Jones:2001a} and AstroPy \citep{Astropy-Collaboration:2013a,
-  Astropy-Collaboration:2018a} projects.  We thank Olga Katushkina for useful discussions.
+  Astropy-Collaboration:2018a} projects.  We thank Olga Katushkina for
+useful discussions and the anonymous referee for a careful and
+helpful report.
 

### 2019-04-17 papers/Papers1234/sec-dust-wave-discussion.tex
Submit to MNRAS revised version of Paper II

@@
 
-\subsection{Gas--grain dynamics in stellar bows}
+\subsection{Gas--grain dynamics in stellar bow shells}
 \label{sec:gas-grain-dynamics-bs}
 
-The term \textit{dust wave} was first coined to described the
+The term \textit{dust wave} was first coined to describe the
 radiative decoupling of grains from the plasma flowing past a massive
@@
 The most detailed simulations to date of the combined dynamics of
-dust, gas, and magnetic field in an OB bow was carried out by
+dust, gas, and magnetic field in an OB bow shell was carried out by
 \citet{Katushkina:2017a}, who followed the trajectories of dust
@@
 filaments of infrared dust emission seen at \SI{24}{\um}.  It is found
-that the simulations can only fit the observations with very large
+that the simulations can fit the observations only with very large
 dust grains (\(\approx \SI{1}{\um}\)) and a very strong perpendicular
-magnetic field \(v\alfven \approx \SI{20}{km.s^{-1}}\).  The stellar
+magnetic field (\(B = \text{\numrange{18}{35}} \, \si{\micro G}\)
+corresponding to \(v\alfven \approx \SI{20}{km.s^{-1}}\)).  The stellar
 parameters of \(\kappa\)~Cas are roughly those given in the last row of
@@
 force vastly exceeds all other forces, it does not necessarily follow
-that the other forces are unimportant.  For example, in the
-magnetized dust wave models that we present in
-\S~\ref{sec:tight-magn-coupl} and \S~\ref{sec:grain-traj-with}, the
-Lorentz force is infinitely stronger than other forces.  Nevertheless,
-the radiation and drag forces are crucial in determining the structure
-of the dust waves, which is possible because the component of the
-Lorentz force projected along the field lines is zero.
+that the other forces are unimportant.  For example, in the magnetized
+dust wave models that we present in \S~\ref{sec:tight-magn-coupl} and
+\S~\ref{sec:grain-traj-with}, the Lorentz force is infinitely stronger
+than other forces.  Nevertheless, the radiation and drag forces are
+crucial in determining the structure of the dust waves, which is
+possible because the component of the Lorentz force projected along
+the field lines is zero.
 

### 2019-04-17 papers/Papers1234/sec-weak-coupling.tex
Submit to MNRAS revised version of Paper II

@@
   \caption{Drag-confined dust waves with tight magnetic coupling.
-    Upper panels show a quasi-parallel field, \(\theta\B = \ang{10}\),
-    while lower panels show a quasi-perpendicular field,
-    \(\theta\B = \ang{75}\).  Left panels show an incident stream velocity of
-    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels show
+    Upper panels (a and b) show a quasi-parallel field,
+    \(\theta\B = \ang{10}\), while lower panels (c and d) show a
+    quasi-perpendicular field, \(\theta\B = \ang{75}\).  Left panels (a and
+    c) show an incident stream velocity of
+    \(v_\infty = \SI{40}{km.s^{-1}}\), while right panels (b and d) show
     \(v_\infty = \SI{80}{km.s^{-1}}\).  In all cases, the stream density is

### 2019-04-18 papers/Papers1234/sec-obs-intro.tex
Final accepted version of Paper I as sent to MNRAS
Two more paras of introduction for Paper IV

@@
 via their mid-infrared dust emission \citep{van-Buren:1995a,
-  Smith:2005a, Povich:2008a, Kobulnicky:2010a, Peri:2012a, Peri:2015a,
-  Sexton:2015b, Kobulnicky:2016a, Bodensteiner:2018a}, and these have
-sizes ranging from \SIrange{0.01}{1}{pc}.
+  Noriega-Crespo:1997b, Povich:2008a, Kobulnicky:2010a, Peri:2012a,
+  Peri:2015a, Sexton:2015b, Kobulnicky:2016a, Bodensteiner:2018a}, and
+these have typical sizes ranging from \SIrange{0.01}{1}{pc}. In
+particularly dense environments, such as the inner Orion Nebula
+\citep{Smith:2005a} and the Galactic center region
+\citep{Geballe:2004a} they may be as small as \SI{0.003}{pc} and emit
+at near-infrared wavelengths \citep{Tanner:2005a,
+  Sanchez-Bermudez:2014a}.  Cometary ultracompact \hii{} regions
+detected at radio wavelengths \citep{Reid:1985a, Wood:1989a,
+  Klaassen:2018a} have also been interpreted as bow shocks
+\citep{van-Buren:1990a, Mac-Low:1991a}, although alternative models,
+such as a champagne flow caused by steep density gradients
+\citep{Cyganowski:2003a, Arthur:2006a, Immer:2014a, Steggles:2017a},
+are favored in many cases.  This illustrates a broader point: that it
+can be difficult to identify bow shocks from morphology alone, since
+other processes can give rise to emission arcs.  In particular, curved
+ionization fronts, as seen in evaporating globules \citep{Sahai:2012b}
+and proplyds \citep{ODell:1993a} can be mistaken for bow shocks.
+Kinematic observations can potentially resolve such ambiguities but
+are not always available.
 
-In the Orion Nebula, at least three different classes of stellar bow
-shocks have been identified. As well as small number of OB bow shocks \citep{Smith:2005a, ODell:2001c},
+Stellar bow shocks are also observed around other types of stars. Bow
+shocks around cool red supergiant and asymptotic giant branch stars
+are detected at mid-infrared and far-infrared wavelengths
+\citep{Ueta:2006a, Ueta:2008a, Sahai:2010a, Cox:2012a}.  Pulsar bow
+shock nebulae are detected principally by their H\(\alpha\) emission
+\citep{Kulkarni:1988a, Brownsberger:2014a}.  In the Orion Nebula (M42,
+NGC~1976), at least three different classes of stellar bow shock have
+been identified. As well as a small number of OB bow shocks
+\citep{Smith:2005a, ODell:2001c}, bow shocks are also seen around the
+closest proplyds to the dominant O~star \thC{} \citep{Hayward:1994a,
+  Bally:1998a, Robberto:2005a}.  The proplyds \citep{ODell:2008b} are
+photoevaporating protoplanetary disks around low-mass young stars
+\citep{Johnstone:1998a} and the bow shocks have been modeled as the
+interaction between the disk's ionized photoevaporation flow and the
+supersonic stellar wind from \thC{} \citep{Garcia-Arredondo:2001a}.
+The third class of Orion Nebula bow shock is the LL~Ori-type objects
+\citetext{\citealp{Gull:1979a}; \S~5 of \citealp{Bally:2000a}; \S~3.2
+  of \citealp{Bally:2001a}; \citealp{Henney:2013a}}, which tend to be
+found in the outer regions of the nebula.  These are probably due to
+interactions between the Orion Nebula's champagne flow
+\citep{Zuckerman:1973a} and outflows from T~Tauri stars, which may or
+may not be proplyds \citep{Bally:2000a, Gutierrez-Soto:2015a}.
 
-Interaction of wind with photoevaporation flow \citep{Dyson:1975a}
+The shapes of stellar bow shocks are frequently compared with what has
+become known as the \textit{wilkinoid} surface \citep{Cox:2012a},
+which is the result of the idealized interaction between a spherical
+wind and a plane-parallel stream in the hydrodynamic thin-shell
+approximation.  Numerical approximations to this shape were used by
+various authors \citep{Baranov:1971a, Mac-Low:1991a} before an elegant
+analytic solution was found by \citet{Wilkin:1996a} and extended to
+the case of interaction between two spherical winds
+\citep{Canto:1996}.  In \citet[hereafter, Paper~0]{Tarango-Yong:2018a}
+the study of bow shock shapes and their projection on the plane of the
+sky was formalized. The term \textit{cantoid} was introduced for the
+\citet{Canto:1996} family of shapes, together with \textit{ancantoid}
+for a generalization to the case where one of the winds is
+anisotropic, as is appropriate for the proplyds.  In addition, Paper~0
+proposed the use of two dimensionless parameters, \textit{planitude}
+and \textit{alatude}, to describe a general bow shock shape.  The
+planitude, \(\Pi = R_c / R_0\), measures the flatness of the bow shock
+apex (see Fig.~1 of Paper~0 for explanation of apex and other
+descriptive terms), where \(R_0\) is the star--apex distance and
+\(R_c\) is the radius of curvature measured at the apex.  The alatude,
+\(\Lambda = R_{90}/R_0\), measures the openness of the bow shock wings,
+where \(R_{90}\) is the lateral size of the bow, measured from the
+star in the direction perpendicular to the star--apex direction.
 
-HMXRB in external galaxies, possible bowshock in LMC~X-1 \citep{Hyde:2017a}.
+% Bowshocks from red supergiants \citep{Meyer:2014a}.  Simluations of AGB bows \citep{Villaver:2012a}, RSG \citep{Mohamed:2012a}
 
-Wolf-Rayet bow shock nebulae \citep{Dyson:1989a}
+% Wolf Rayet stars give bigger bow shocks (e.g., WR~128 \citealp{Moffat:1998})
 
-Non-thermal radio emission from BD+43~3654 \citep{Benaglia:2010a}, has
-been searched for but
+% Interaction of wind with photoevaporation flow \citep{Dyson:1975a}
 
-Cooler red supergiant and asymptotic giant branch stars
-\citep{Ueta:2008a, Sahai:2010a, Cox:2012a}. 
-Bowshocks from red supergiants \citep{Meyer:2014a}
+% HMXRB in external galaxies, possible bowshock in LMC~X-1 \citep{Hyde:2017a}.
+
+% Wolf-Rayet bow shock nebulae \citep{Dyson:1989a}
+
+% Non-thermal radio emission from BD+43~3654 \citep{Benaglia:2010a}, has
+% been searched for but
+
+% Supersonic pulsar wind nebulae \citep{Kargaltsev:2017a}
 

### 2019-04-18 papers/Papers1234/obs-bowshocks.tex
Add Luis A to the author list for paper 3
Move the oscillating bows section to the observational paper
Finish intro to paper II
Start work on Paper IV - change Pi-Lambda graphs to log scale
Two more paras of introduction for Paper IV
Lots of reorganizing of Paper IV

@@
 
-% The following is needed to fix the margins if using Letter-size paper
-% REMOVE if your LaTeX uses A4 paper by default
-%\addtolength\topmargin{-1.8cm}
-
 % Standard LaTeX packages
-% \usepackage[varg]{txfonts}
-\usepackage[varg]{newtxmath}
-\usepackage{newtxtext}
 \usepackage{graphicx}
@@
 
+\usepackage[T1]{fontenc} 
+\usepackage[utf8]{inputenc}
+
+% Fonts 
+\usepackage{newtxtext}
+% Note: newtxmath must come AFTER newtxtext
+\usepackage[varvw,smallerops]{newtxmath}
+
+\usepackage{chemgreek}
+\activatechemgreekmapping{newtx}
+
 % Define a fermata symbol for use inline with text
@@
 % Based on info in Secs 18.4.1 and 24.1 of musixdoc.pdf
+\let\ORIGna\na
 \usepackage{musixtex}
@@
 \makeatother
+\let\na\ORIGna
 
@@
 
+%% The following hack solves a problem with
+%% ERROR: \pdfendlink ended up in different nesting level than \pdfstartlink.
+%% See https://tex.stackexchange.com/a/249743
+\makeatletter
+\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
+  \errmessage{\noexpand\@combinedblfloats could not be patched}%
+}%
+\makeatother
+
 %% Bold italic
@@
 
-% Definitions needed in abstract
-\newcommand\hii{\ion{H}{ii}}
+\defcitealias{Tarango-Yong:2018a}{Paper~0}
+\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
 
-\title[Stellar bow shocks]{Weather vanes and runaways: Bow
-  shocks across the HR diagram}
+% \title[Stellar bow shocks]{Weather vanes and runaways: Bow
+%   shocks across the HR diagram}
+\title[Bow shocks, bow waves, and dust waves. IV.]{Bow shocks, bow
+  waves, and dust waves. IV. Bow shape statistics}
 
@@
   58090 Morelia, Michoac\'an, M\'exico}
-\author[Henney \& Tarango Yong]{
-  William J. Henney \& Jorge A. Tarango Yong \\
+\author[Henney et al.]{
+  William J. Henney,\thanks{w.henney@irya.unam.mx}
+  Jorge A. Tarango-Yong,
+  Luis \'Angel Guti\'errez-Soto,
+  \& S. J. Arthur
+  \\
   \AddressCRyA
 }
+
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2019}
+
+\input{bs-bw-dw-defs}
+
 \begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \maketitle
@@
   around hot main-sequence stars (\(N = 227\)); (2)~far-infrared arcs
-  around luminous cool stars (\(N = 7\)); and (3)~emission-line arcs
+  around luminous cool stars (\(N = 16\)); and (3)~emission-line arcs
   around proplyds and other young stars in the Orion Nebula
@@
   the other hand, have both significantly more open wings and
-  significantly flatter apices than the hot star bow shocks.  We
+  significantly flatter apexes than the hot star bow shocks.  We
   discuss the implications of these differences for understanding the
@@
 
+\begin{keywords}
+  circumstellar matter -- methods: statistical -- stars: winds, outflows
+\end{keywords}
+
 \input{sec-obs-intro}
-\clearpage
 \input{sec-quadrics-observations}
+\input{sec-standing-wave}
 \input{sec-obs-conclusions}
-\clearpage
+
+\section*{Acknowledgements}
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grants Programa de Apoyo a Proyectos de Investigación
+e Inovación Tecnológica IN111215 and IN107019.
+
 \bibliographystyle{mnras}
@@
 \input{app-p-values}
+
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 

### 2019-04-18 papers/Papers1234/sec-obs-intro.tex
Lots of reorganizing of Paper IV

@@
 
+In this paper, we investigate the shapes of stellar bow shocks by
+calculating the distributions of planitude and alatude for different
+classes of bow shock source.
+The remainder of the paper is organized as follows: in \S~\ref{sec:mid-infrared-arcs} we present an analysis of the shapes of several hundred bowshock candidates associated with OB stars from the
+
 % Bowshocks from red supergiants \citep{Meyer:2014a}.  Simluations of AGB bows \citep{Villaver:2012a}, RSG \citep{Mohamed:2012a}
@@
 
-Instability of bow \citep{Blondin:1998a}
-
 %%% Local Variables:

### 2019-04-18 papers/Papers1234/sec-quadrics-observations.tex
Lots of reorganizing of Paper IV

@@
-\section{Comparison with observations}
+\section{Mid-infrared arcs around early-type stars}
+\label{sec:mid-infrared-arcs}
 \label{sec:comp-with-observ}
-
-Placing various classes of objects on the \(R_{90}\)--\(R_c\) plane:
-\begin{itemize}
-\item LL arcs
-\item runaway O stars
-\item AGB stars
-\end{itemize}
-
-\subsection{Mid-infrared arcs around early-type stars}
-\label{sec:mid-infrared-arcs}
 
@@
 
-\subsubsection{Automatic tracing and fitting of bow shocks}
+\subsection{Automatic tracing and fitting of bow shocks}
 \label{sec:autom-trac-fitt}
@@
 
-\subsubsection{Subjective evaluation of the fit quality}
+\subsection{Subjective evaluation of the fit quality}
 \label{sec:subj-eval-fit}
@@
 
-\subsubsection{OB bow shock shapes on the diagnostic plane}
+\subsection{OB bow shock shapes on the diagnostic plane}
 \label{sec:ob-shapes}
@@
 
-\subsubsection{Correlation between bow shock size and other parameters}
+\subsection{Correlation between bow shock size and other parameters}
 \label{sec:corr-size}
@@
 
-\subsubsection{Correlation between bow shock shape and other parameters}
+\subsection{Correlation between bow shock shape and other parameters}
 \label{sec:corr-shape}
@@
   different non-parametric tests to \(R_c/R_0\) and \(R_{90}/R_0\)
-  separately.  The principal test used is the two-sample
-  Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a,
-    Makarov:2017a}, which is a general test of the \textit{null
-    hypothesis} that the two sub-samples are drawn from the same
-  distribution.  It returns a \(p\)-value, which is the estimated
-  probability that the observed difference between the two sub-samples
-  would be as large as it is purely by chance if they were all were
-  drawn from the same distribution.  We consider two different
-  thresholds for significance: \(p < 0.05\) (approximately
+  separately.  
+\end{enumerate}
+
+The principal test used is the two-sample Anderson--Darling test
+\citep{Anderson:1952a, Scholz:1987a, Makarov:2017a}, which is a
+general test of the \textit{null hypothesis} that the two sub-samples
+are drawn from the same distribution.  It returns a \(p\)-value, which
+is the estimated probability that the observed difference between the
+two sub-samples would be as large as it is purely by chance if they
+were all were drawn from the same distribution.  We consider two
+different thresholds for significance: \(p < 0.05\) (approximately
 2-\(\sigma\) for a normal distribution) and \(p < 0.003\) (approximately
-  3-\(\sigma\)).  We show in Appendix~\ref{sec:distr-p-values} that the
-  more stringent \(p < 0.003\) condition is required in order to
-  confidently reject the null hypothesis and declare a ``significant''
-  difference between the two sub-samples, but we also consider the
-  less strict threshold of \(p < 0.05\) as an indicator of
-  ``possible'' difference.  We supplement the general-purpose
-  Anderson--Darling test with two tests that probe specific features of
-  the sample distributions: the Mann--Whitney--Wilcoxon \(U\) test
-  \citep{Mann:1947a}, which is sensitive to differences in the central
-  value (e.g., median) and the Brown--Forsythe test
-  \citep{Brown:1974a}, which is sensitive to differences in the
-  variance, or width, of the distribution (see
+3-\(\sigma\)).  We show in Appendix~\ref{sec:distr-p-values} that the more
+stringent \(p < 0.003\) condition is required in order to confidently
+reject the null hypothesis and declare a ``significant'' difference
+between the two sub-samples, but we also consider the less strict
+threshold of \(p < 0.05\) as an indicator of ``possible'' difference.
+We supplement the general-purpose Anderson--Darling test with two tests
+that probe specific features of the sample distributions: the
+Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is
+sensitive to differences in the central value (e.g., median) and the
+Brown--Forsythe test \citep{Brown:1974a}, which is sensitive to
+differences in the variance, or width, of the distribution (see
 Appendix~\ref{sec:distr-p-values} for details).
-\end{enumerate}
 
@@
 
-\subsection{Far-infrared arcs around late-type stars}
+\section{Far-infrared arcs around late-type stars}
 \label{sec:far-infrared-arcs}
@@
 
-\subsection{Stationary emission line arcs in M42}
+\section{Stationary emission line arcs in M42}
 \label{sec:stat-emiss-line}

### 2019-04-19 papers/Papers1234/sec-obs-intro.tex
Finish intro for Paper IV

@@
 calculating the distributions of planitude and alatude for different
-classes of bow shock source.
-The remainder of the paper is organized as follows: in \S~\ref{sec:mid-infrared-arcs} we present an analysis of the shapes of several hundred bowshock candidates associated with OB stars from the
+classes of bow shock source.  The remainder of the paper is organized
+as follows. In \S~\ref{sec:mid-infrared-arcs} we present an analysis
+of the shapes of several hundred bowshock candidates associated with
+OB stars from the \SI{24}{\um} survey of \citet{Kobulnicky:2016a}.
+Our algorithm for automatically fitting and tracing the shapes is
+described in \S~\ref{sec:autom-trac-fitt}, together with our ``star
+rating'' system for evaluating the fit quality, while in
+\S~\ref{sec:ob-shapes} we locate the sources on the planitude--alatude
+plane.  In \S~\ref{sec:corr-size} we study the correlations amongst
+non-shape parameters of the bow shock sources, such as angular size
+and stellar magnitude, while in \S~\ref{sec:corr-shape} we explore the
+correlations these parameters and the planitude and alatude.  In
+\S~\ref{sec:far-infrared-arcs} we compare with results for bow shocks
+around cool luminous stars and in \S~\ref{sec:stat-emiss-line} we
+compare with results for staionary emission line arcs in the Orion
+Nebula.  In \S~\ref{sec:discussion} we discuss the implications of our
+findings for physical models of bow shock formation in the different
+classes of sources, and in \S~\ref{sec:conclusion} we summarise our
+results.  Further details of the statistical tests that we have
+applied are provided in Appendix~\ref{sec:distr-p-values}.
 

### 2019-04-19 papers/Papers1234/sec-standing-wave.tex
Get as far as describing the phi(Xi) relation
Lots of reorganizing of Paper IV
Finish intro for Paper IV

@@
+\section{Discussion}
+\label{sec:discussion}
+
 \begin{figure*}[t!]
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]
-  {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
-  \caption{Plane-of-sky projections of perturbed bow shapes.  In all
-    cases, the base bow shape is ancantoid with \(\xi = 0.8\),
-    \(\beta = 0.005\) and the perturbation is the same as in the central
-    panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
-    \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
-    inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
-    color and thickness, see key) and for different fractional phases
-    of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
-    (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
-    the spatial coordinates are normalized to the instantaneous
-    projected apex radius \(R_0'\) at each phase, so the apex does not
-    appear to move.}.
-  \label{fig:perturb-xy-prime}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\linewidth]
+%   {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
+%   \caption{Plane-of-sky projections of perturbed bow shapes.  In all
+%     cases, the base bow shape is ancantoid with \(\xi = 0.8\),
+%     \(\beta = 0.005\) and the perturbation is the same as in the central
+%     panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
+%     \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
+%     inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
+%     color and thickness, see key) and for different fractional phases
+%     of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
+%     (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
+%     the spatial coordinates are normalized to the instantaneous
+%     projected apex radius \(R_0'\) at each phase, so the apex does not
+%     appear to move.}.
+%   \label{fig:perturb-xy-prime}
+% \end{figure*}
 
-\section{Perturbed bows}
+\subsection{Perturbed bows}
 \label{sec:perturbed-bows}
+
+Instability of bow \citep{Blondin:1998a}
 
@@
   \includegraphics[width=\linewidth]
-  {figs/wave-R90-vs-Rc-A010-N10}
+  {figs/wave-R90-vs-Rc-A020-N10}
   \includegraphics[width=\linewidth]
-  {figs/wave-R90-vs-Rc-A005-N20}
+  {figs/wave-R90-vs-Rc-A010-N20}
   \caption{Diagnostic diagram for perturbed shapes}
@@
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock"
+%%% TeX-master: "obs-bowshocks"
 %%% End:

### 2019-04-20 papers/Papers1234/obs-bowshocks.tex
Finish going through sec 2.1 and 2.2 of Paper IV

@@
 \author[Henney et al.]{
-  William J. Henney,\thanks{w.henney@irya.unam.mx}
+  William J. Henney,\thanks{Email: w.henney@irya.unam.mx}
   Jorge A. Tarango-Yong,
-  Luis \'Angel Guti\'errez-Soto,
+  Luis \'Angel Guti\'errez-Soto,\thanks{%
+    Current address: Observatório do Valongo,
+    Universidade Federal do Rio de Janeiro,
+    Ladeira Pedro Antonio 43, 20080-090 Rio de Janeiro, Brazil}
   \& S. J. Arthur

### 2019-04-20 papers/Papers1234/sec-quadrics-observations.tex
Finish intro for Paper IV
Finish going through sec 2.1 and 2.2 of Paper IV

@@
 
-We developed a methodology for automatically tracing the arcs as follows:
+We have developed a method for automatically tracing the arcs and
+determining their planitude and alatude, which is an extension of the
+method described in Appendix~E of Paper~0.  The steps of the method
+are as follows:
 \begin{enumerate}[1.]
 \item Calculate arrays of celestial coordinates, \(C\), for each pixel
-  of the image.
+  of the image. In our implementation of the method we use functions
+  from the Python library \texttt{astropy.coordinates}
+  \citep{Astropy-Collaboration:2018a}.
 \item Using the central source coordinates, \(C_0\) and nominal
@@
   \(\delta\theta = 120/50 = 2.4\degr\), which defines a thin radial wedge from
-  \(C_1\).  The results are shown as red and blue dots superimposed
-  on the images in Figure~\ref{fig:mipsgal-examples}. Each of the two
+  \(C_1\).  The results are shown as red and blue dots superimposed on
+  the images in Figure~\ref{fig:mipsgal-examples}. Each of the two
   methods, ``peak'' and ``mean'', works better in some objects and
@@
   average by amalgamating all the \(C_{k,\text{peak}}\) and
-  \(C_{k,\text{mean}}\) points into a single set, \(C_{k}\), for
-  the following steps.
+  \(C_{k,\text{mean}}\) points into a single set, \(C_{k}\), for the
+  following steps.  We have found that the use of the step-back point
+  greatly improves the reliability of the method, as compared with the
+  simpler option of tracing rays from the stellar source.
 \item For each of the points \(C_{k}\), determine the radial
@@
   \(R_k < \frac12 R_m\) or \(R_k > 2 R_m\), where \(R_m\) is the median
-  \(R_k\) for \(|\theta_k| < 45\degr\).
+  \(R_k\) for \(|\theta_k| < 45\degr\).\label{step:Rc}
 \item Determine two separate estimates, \(R_{90+}\) and \(R_{90-}\),
@@
   \(R_{90+}\) and \(R_{90-}\) is denoted by \(\epsilon(R_{90})\).\label{step:R90}
+\item The planitude is determined as \(\Pi = R_c / R_0\) and the mean
+  alatude as \(\Lambda = \frac12 (R_{90+} + R_{90-}) / R_0\).  We also
+  calculate an alatude asymmetry as
+  \(\Delta\Lambda = \frac12 (R_{90+} - R_{90-}) / R_0\). Note that in this paper
+  we simplify the notation of Paper~0 by no longer using the prime
+  symbol (\('\)) to distinguish projected from intrinsic quantities.
+  All planitudes and alatudes should be understood as specifying the
+  projected bow shock shape on the plane of the sky unless noted
+  otherwise.\label{step:Pi-Lambda}
 \end{enumerate}
-
-\subsection{Subjective evaluation of the fit quality}
+% \subsubsection{Subjective evaluation of the fit quality}
 \label{sec:subj-eval-fit}
-
-After these automatic steps, we subjectively evaluate the results by giving a star rating to each source:
+After these automatic steps, we subjectively evaluate the resulting
+fit quality by giving a star rating to each source:
 
@@
 Figure~\ref{fig:mipsgal-examples}c.
+\bigskip
 
-\bigskip
 % 
@@
 The derived bowshock shapes of all the 3-, 4-, and 5-star sources are
-shown in Figure~\ref{fig:mipsgal-shapes} on the plane of \(R_c/R_0\)
-versus \(R_{90} / R_0\).  Panel a shows the individual points
-superimposed on the theoretical results for quadrics of revolution
-(see figure caption and \S~\ref{sec:conic}), while panel b shows
-contours of the kernel density estimator (KDE, see
-\citealp{Leiva-Murillo:2012a, Scott:2015a}) of the two-dimensional
-distribution of points on the \(R_c\)--\(R_{90}\) plane.  The
-horizontal axis corresponds to the shape of the head of the bow shock
-near its apex, ranging from sharper, pointier shapes with
-\(R_c/R_0 < 1\) to flatter, snubber shapes with \(R_c/R_0 \gg 1\), where
-it must be understood that all judgments of sharpness/flatness are
-with respect to the axial separation, \(R_0\), between the source and
-the bow shock apex.  The vertical axis corresponds to the shape of the
-bow shock wings, ranging from closed ``C'' shapes for smaller values
-of \(R_{90} / R_0\) to open ``V'' shapes for larger values of
-\(R_{90} / R_0\).  The boundary between closed and open corresponds to
-the paraboloids, and is shown by the solid curved line that divides
-the shaded from the unshaded regions of the graph.
+shown in Figure~\ref{fig:mipsgal-shapes} on the \(\Pi\)--\(\Lambda\) plane,
+which was discussed extensively in Paper~0.  Panel a shows each
+individual source with horizontal error bars that represent the
+dispersion of traced points from the circle fit (step~\ref{step:Rc} of
+the previous section) and vertical error bars that show the wing
+asymmetry \(\Delta\Lambda\) (step~\ref{step:Pi-Lambda}).  The horizontal error
+bars, which are a proxy for observational uncertainties, become very
+small for the 4- and 5-star sources, whereas the vertical error bars
+remain at roughly the \(10\%\) level since they reflect real
+asymmetries in the shapes of the bow shocks.
 
-The KDE contours in Figure~\ref{fig:mipsgal-shapes}b show that the
-distribution of 3-star sources is very similar to that of 4- and
-5-star sources, although the higher-rated sources are shifted slightly
-to the upper right.  Possible reasons for this are discussed in
-\S~\ref{sec:corr-shape} below.
+The horizontal axis corresponds to the shape of the head of the bow
+shock near its apex, ranging from sharper, pointier shapes with
+\(\Pi < 1\) to flatter, snubber shapes with \(\Pi \gg 1\), where it must be
+understood that all judgments of sharpness/flatness are with respect
+to the axial separation, \(R_0\), between the source and the bow shock
+apex.  The vertical axis corresponds to the shape of the bow shock
+wings, ranging from closed ``C'' shapes for smaller values of
+\(\Lambda\) to open ``V'' shapes for larger values of \(\Lambda\).  The background
+shading shows the regions of the \(\Pi\)--\(\Lambda\) plane occupied by simple
+quadric shapes (see \S~4 of Paper~0): oblate spheroids (light gray),
+prolate spheroids (dark gray), and hyperboloids (white). The boundary
+between closed and open corresponds to the paraboloids, and is shown
+by the solid curved line that divides the dark gray and white regions
+of the graph.
+
+In Figure~\ref{fig:mipsgal-shapes}b, we present a smoothed version of
+the same data.  The contours show the kernel density estimator (KDE,
+see \citealp{Leiva-Murillo:2012a, Scott:2015a}) of the two-dimensional
+distribution of points on the \(\Pi\)--\(\Lambda\) plane.  The KDE contours
+indicate that the distribution of 3-star sources is very similar to
+that of 4- and 5-star sources, although the higher-rated sources are
+shifted slightly to the upper right.  Possible reasons for this are
+discussed in \S~\ref{sec:corr-shape} below.
 % This is probably due to higher-rated sources
@@
 The bulk of the sources are concentrated around the paraboloid line,
-with \(1 < R_c/R_0 < 2.5\), and \(1.2 < R_{90}/R_0 < 2\).  But
-significant minorities are found in three other regions: (1)~a clump
-with \(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\)
-at \(R_c/R_0 \approx 2\); and (3)~a broad horizontal tail towards higher
-\(R_c\) at \(R_{90}/R_0 \la 2\).
+with \(1 < \Pi < 3\), and \(1.2 < \Lambda < 2\).  But significant minorities
+are found in three other regions: (1)~a clump with \(\Pi \la 1\); (2)~a
+vertical spur towards higher \(\Lambda\) at \(\Pi \approx 1.8\); and (3)~a broad
+horizontal tail towards higher \(\Pi\) at \(\Lambda \la 2\).  Thumbnail images
+of the \SI{24}{\um} emission of selected sources from different
+regions of the distribution are shown, in order to illustrate the
+range of bow shock morphologies encountered.
 
-\subsection{Correlation between bow shock size and other parameters}
+\subsection{Correlations between non-shape parameters of the OB sources}
 \label{sec:corr-size}

### 2019-04-20 papers/Papers1234/sec-quadrics-observations.tex
Finish revising sec 2.3 and 2.4 of Paper IV

@@
   \centering
+  \setlength\tabcolsep{0pt}
   \begin{tabular}{ll}
     (a) & (b) \\
-    \includegraphics[width=0.45\textwidth, trim=0 0 30 0]
+    \includegraphics[width=0.5\textwidth]
     {figs/mipsgal-Rc-R90-zoom-annotated}
-        & \includegraphics[width=0.45\textwidth, trim=0 0 30 0]
+        & \includegraphics[width=0.5\textwidth]
           {figs/mipsgal-Rc-R90-thumbnails} 
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figs/mipsgal-pairplot}
+  \includegraphics[width=0.85\textwidth]{figs/mipsgal-pairplot}
   \caption[]{Matrix of pair plots that illustrate distributions of and
@@
 \begin{figure*}
-  \centering
+  \setlength\tabcolsep{0pt}
   \begin{tabular}{ll}
     (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
+    \includegraphics[width=0.5\textwidth]{figs/mipsgal-Rc-R90-environment} &
+    \includegraphics[width=0.5\textwidth]{figs/mipsgal-Rc-R90-candidates} 
   \end{tabular}
@@
 \end{figure*}
+\begin{figure*}
+  \setlength\tabcolsep{0pt}
+  \begin{tabular}{ll}
+    (a) & (b) \\
+    \includegraphics[width=0.5\textwidth]{figs/mipsgal-Rc-R90-R0} &
+    \includegraphics[width=0.5\textwidth]{figs/mipsgal-Rc-R90-Mag} 
+  \end{tabular}
+  \caption[]{As Fig.~\ref{fig:mipsgal-uncorrelated} but for median
+    splits of continuous parameters. (a)~Bow shock angular size,
+    \(R_0\), divided into two equal-sized sub-samples: large (blue
+    symbols and blue filled contours) and small (red symbols and red
+    hollow contours).  (b)~Extinction-corrected \(H\)-band magnitude
+    of the stellar source, divided into two equal-sized sub-samples:
+    bright (red symbols and orange filled contours) and faint (green
+    symbols and green hollow contours).}
+  \label{fig:mipsgal-correlated}
+\end{figure*}
 
@@
 brighter, reaching \(M_H \approx -7\), but such stars are expected to be
-rare.  Assuming a B2V star (\(M_H = -2\)), then the observed range
-\(H_0 = 5\)--\(12\) corresponds to distances
+relatively rare.  Assuming a B2V star (\(M_H = -2\)), then the
+observed range \(H_0 = 5\)--\(12\) corresponds to distances
 \(d = 100\)--\SI{6300}{pc}, and the histogram peak at
@@
 of the bow shock axis with respect to the plane of the sky.
-Figure~\ref{fig:quadric-projection}b shows that for \(R_c > 1\), then
-the projected \(R_0'\) becomes larger than the true \(R_0\) as \(|i|\)
-increases.  This is further illustrated in
-Figure~\ref{fig:projected-R90-Rc-snapshots} for simple quadric shapes
-(spheroids, paraboloids, hyperboloids) and in
-Figure~\ref{fig:thin-shell-R90-Rc-snapshots} for the wilkinoid,
-cantoids, and ancantoids.  It can be seen that the effect is
-relatively modest for bow shocks with projected shapes falling in the
-range \(1 < R_c/R_0 < 3\) and \(R_{90}/R_0 < 3\), as the vast majority
-of our observed sources do.  The increase in \(R_0\) is no more than a
-factor of 2 to 3 for moderate inclinations of \(30\) to \(60\degr\),
-although it can reach a factor of 5 to 10 for some shapes at more
-extreme inclinations.
+Figure~11b of Paper~0 shows that for \(\Pi > 1\), then the projected
+\(R_0'\) becomes larger than the true \(R_0\) as \(|i|\) increases
+(see also Figs.~26 and 27 of Paper~0).  It can be seen that the effect
+is relatively modest, with an increase in \(R_0\) of no more than a
+factor of 2 to 3.
 
@@
 \label{sec:corr-shape}
-\begin{figure*}
-  \centering
-  \begin{tabular}{ll}
-    (a) & (b) \\
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
-    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
-  \end{tabular}
-  \caption[]{As Fig.~\ref{fig:mipsgal-uncorrelated} but for median
-    splits of continuous parameters. (a)~Bow shock angular size,
-    \(R_0\), divided into two equal-sized sub-samples: large (blue
-    symbols and blue filled contours) and small (red symbols and red
-    hollow contours).  (b)~Extinction-corrected \(H\)-band magnitude
-    of the stellar source, divided into two equal-sized sub-samples:
-    bright (red symbols and orange filled contours) and faint (green
-    symbols and green hollow contours).}
-  \label{fig:mipsgal-correlated}
-\end{figure*}
 
@@
   \caption{Box plots of the distributions of bow shock shape
-    parameters, \(\Pi\) and \(\Lambda\), together with a
-    measure of the tail asymmetry, \(|\Lambda_{+} - \Lambda_{-}| / \Lambda\),
-    after partitioning on the bow shock size, \(R_0\).  All 3-, 4-,
-    and 5-star sources are sorted according to \(R_0\) and divided
-    into 5 non-overlapping sub-samples of roughly equal size, each
-    labelled by their median value of \(R_0\) in arcseconds, as
-    illustrated in the lower panel.  The colored boxes show the
-    interquartile range, with the median indicated by a horizontal
-    line, the 1st-to-9th interdecile range by error bars, and outliers
-    by diamonds.  A 5-sample Anderson--Darling test and Brown--Forsythe
-    test is performed for each dependent variable, with resultant
-    \(p\)-value given at the bottom of each panel.   It is apparent
-    that the dispersion in \(\Lambda\) (upper panel) increases
+    parameters, \(\Pi\) and \(\Lambda\), together with a measure of the tail
+    asymmetry, \(2 |\Delta\Lambda| / \Lambda\), after partitioning on the bow shock
+    size, \(R_0\).  All 3-, 4-, and 5-star sources are sorted
+    according to \(R_0\) and divided into 5 non-overlapping
+    sub-samples of roughly equal size, each labelled by their median
+    value of \(R_0\) in arcseconds, as illustrated in the lower panel.
+    The colored boxes show the interquartile range of the data, with
+    the median indicated by a horizontal line and the notch showing
+    the 90\% confidence limits of the median, as determined from 1000
+    bootstrap resamplings.  The 5th-to-95th centile range of the data
+    is indicated by error bars.  A 5-sample Anderson--Darling test and
+    Brown--Forsythe test is performed for each dependent variable, with
+    resultant \(p\)-value given at the bottom of each panel.  It is
+    apparent that the dispersion in \(\Lambda\) (upper panel) increases
     systematically with \(R_0\), although the central value is roughly
-    constant.  No clear systematic changes are apparent in
-    \(\Pi\) (middle panel).}
+    constant.  No clear systematic changes are apparent in \(\Pi\)
+    (middle panel).}
   \label{fig:mipsgal-boxplot}
@@
 \item We plot the KDEs of the two sub-samples separately on the
-  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
+  \(\Pi\)--\(\Lambda\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
   \ref{fig:mipsgal-uncorrelated}) to check for any obvious
@@
   between the bow shock shapes of the sub-samples by applying three
-  different non-parametric tests to \(R_c/R_0\) and \(R_{90}/R_0\)
+  different non-parametric tests to \(\Pi\) and \(\Lambda\)
   separately.  
@@
 2-\(\sigma\) for a normal distribution) and \(p < 0.003\) (approximately
-3-\(\sigma\)).  We show in Appendix~\ref{sec:distr-p-values} that the more
-stringent \(p < 0.003\) condition is required in order to confidently
-reject the null hypothesis and declare a ``significant'' difference
-between the two sub-samples, but we also consider the less strict
-threshold of \(p < 0.05\) as an indicator of ``possible'' difference.
-We supplement the general-purpose Anderson--Darling test with two tests
-that probe specific features of the sample distributions: the
-Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is
-sensitive to differences in the central value (e.g., median) and the
-Brown--Forsythe test \citep{Brown:1974a}, which is sensitive to
-differences in the variance, or width, of the distribution (see
-Appendix~\ref{sec:distr-p-values} for details).
+3-\(\sigma\)).  We show in Appendix~\ref{sec:distr-p-values} that, given
+the large number of potential relationships that we are testing, the
+more stringent \(p < 0.003\) condition is required in order to
+confidently reject the null hypothesis and declare a ``significant''
+difference between the two sub-samples, but we also consider the less
+strict threshold of \(p < 0.05\) as an indicator of ``possible''
+difference.  We supplement the general-purpose Anderson--Darling test
+with two tests that probe specific features of the sample
+distributions: the Mann--Whitney--Wilcoxon \(U\) test
+\citep{Mann:1947a}, which is sensitive to differences in the central
+value (e.g., median) and the Brown--Forsythe test \citep{Brown:1974a},
+which is sensitive to differences in the variance, or width, of the
+distribution (see Appendix~\ref{sec:distr-p-values} for details).
 
@@
 difference is interesting because in both examples there are a priori
-grounds to suspect that differences might exist.  The first example (Fig.~\ref{fig:mipsgal-uncorrelated}a) is
-the bow shock environment, which was categorized in
-\citet{Kobulnicky:2016a} as ``Isolated'' (I), ``Facing a large \hii{}
-region'' (FH), ``Facing a \SI{8}{\um} bright-rimmed cloud'' (FB), and
-``Within a giant \hii{} region'' (H), and where we have merged the FH
-and FB categories, labelled ``Facing'' in the figure.\footnote{Similar
-  results are also found for the FB and FH categories separately.}
-The shapes might be expected to vary with environment because the FB
-and FH categories should be associated with ``weather vane''
-interactions \citep{Povich:2008a} between the stellar wind and a
-divergent photoevaporation flow.  This is expected to give a more open
-bow shock than in the ``runaway'' case of interaction of a moving star
-with a static environment.  In the thin-shell approximation, the
-predicted shapes are a cantoid for weather vanes and a wilkinoid
-for runaways, see \S~\ref{sec:crw-scenario}.  The fact that no such
-difference is detected could be explained in one of two ways: (i)~the
-momentum ratio \(\beta\) for the weather vanes could be small, since the
-cantoid becomes indistinguishable from the wilkinoid as
-\(\beta \to 0\), or (ii)~many of the bow shocks classified as ``Isolated''
-might also be weather vanes rather than runaways.
+grounds to suspect that differences might exist.  The first example
+(Fig.~\ref{fig:mipsgal-uncorrelated}a) is the bow shock environment,
+which was categorized in \citet{Kobulnicky:2016a} as ``Isolated'' (I),
+``Facing a large \hii{} region'' (FH), ``Facing a \SI{8}{\um}
+bright-rimmed cloud'' (FB), and ``Within a giant \hii{} region'' (H),
+and where we have merged the FH and FB categories, labelled ``Facing''
+in the figure.\footnote{Similar results are also found for the FB and
+  FH categories separately.}  The shapes might be expected to vary
+with environment because the FB and FH categories should be associated
+with ``weather vane'' interactions \citep{Povich:2008a} between the
+stellar wind and a divergent photoevaporation flow.  This is expected
+to give a more open bow shock than in the ``runaway'' case of
+interaction of a moving star with a static environment.  In the
+thin-shell approximation, the predicted shapes are a cantoid for
+weather vanes and a wilkinoid for runaways, see \S~6 of Paper~0.  The
+fact that no such difference is detected could be explained in one of
+two ways: (i)~the momentum ratio \(\beta\) for the weather vanes could be
+small, since the cantoid becomes indistinguishable from the wilkinoid
+as \(\beta \to 0\), or (ii)~many of the bow shocks classified as
+``Isolated'' might also be weather vanes rather than runaways.
 
@@
 value of \(R_0\) for those sources would be erroneous, which would
-increase the scatter in both \(R_c/R_0\) and \(R_{90}/R_0\).  The
-fact that no significant difference is seen in the shape distributions
-between sources with/without multiple candidates implies that such
-mistakes in identification of the central star must be rare.
+increase the scatter in both \(\Pi\) and \(\Lambda\).  The fact that no
+significant difference is seen in the shape distributions between
+sources with/without multiple candidates implies that such mistakes in
+identification of the central star must be rare.
 
@@
 Table~\ref{tab:big-p}.  In all these cases, differences in mean or
-median \(R_{90}/R_0\) less than \(0.06\) and in \(R_c/R_0\) less than
+median \(\Lambda\) less than \(0.06\) and in \(\Pi\) less than
 \(0.16\) are found, corresponding to rank biserial correlation
@@
 the general purpose Anderson--Darling test indicates differences in the
-sub-sample distributions of \(R_{90} / R_0\) at the 2-\(\sigma\) level.  It
+sub-sample distributions of \(\Lambda\) at the 2-\(\sigma\) level.  It
 is apparent from the histograms shown in the right-hand inset graphs
@@
 systematic trends, we divide the independent parameter (\(R_0\) or
-\(H_0\)) into 5 rather than 2 equal-sized sub-samples, with results
-shown as box plots in Figure~\ref{fig:mipsgal-boxplot}.  A systematic
-increase with \(R_0\) in the dispersion of \(R_{90}/R_0\) (upper panel
-of Fig.~\ref{fig:mipsgal-boxplot}a) is apparent from both the
+\(H_0\)) into 5 rather than 2 equal-sized sub-samples, with results in
+the case of \(R_0\) shown as box plots in
+Figure~\ref{fig:mipsgal-boxplot}.  A systematic increase with \(R_0\)
+in the dispersion of \(\Lambda\) (upper panel of
+Fig.~\ref{fig:mipsgal-boxplot}a) is apparent from both the
 interquartile range (colored boxes) and interdecile range (error
@@
 show the statistics for, respectively, the fractional asymmetry of the
-bowshock wings and the standard deviation, \(\epsilon(R_{90})\), of the
-individual points on the bow shock that go into determining \(R_{90}\)
-(see step~\ref{step:R90} of the tracing/fitting methodology described
-in \S~\ref{sec:autom-trac-fitt}).  It can be seen that neither of
-these quantities tends to increase with \(R_0\), and in fact there is
-a significant \emph{decrease} in \(\epsilon(R_{90})\) with \(R_0\).  This
-implies that the increase with angular size of the diversity of bow
-shock wing shapes is real, and not due to observational uncertainties.  
-On the other hand, the fact that no clear trends are evident as a
-function of source magnitude \(H_0\) (Fig.~\ref{fig:mipsgal-boxplot}b)
-leads us to suspect that the \(p < 0.05\) result obtained for the
-2-sample Anderson--Darling test was a \emph{false positive}, which is
-also supported by the analysis in Appendix~\ref{sec:distr-p-values}
-and Figure~\ref{fig:histo-p-values}.
+bowshock wings and the standard deviation, \(\epsilon(\Lambda)\), of the individual
+points on the bow shock that go into determining \(\Lambda\) (see
+step~\ref{step:R90} of the tracing/fitting methodology described in
+\S~\ref{sec:autom-trac-fitt}).  It can be seen that neither of these
+quantities tends to increase with \(R_0\), and in fact there is a
+significant \emph{decrease} in \(\epsilon(\Lambda)\) with \(R_0\).  This implies
+that the increase with angular size of the diversity of bow shock wing
+shapes is real, and not due to observational uncertainties.  On the
+other hand, we find that no clear trends are evident as a function of
+source magnitude \(H_0\) (not illustrated), which leads us to suspect
+that the \(p < 0.05\) result obtained for the 2-sample
+Anderson--Darling test was a \emph{false positive}, as is also
+supported by the analysis in Appendix~\ref{sec:distr-p-values} and
+Figure~\ref{fig:histo-p-values}.
 
-So, the only correlation that survives scrutiny is the increase in
-dispersion of \(R_{90}/R_0\) with increasing \(R_0\), which is finally
-presented in the greatest detail in
-Figure~\ref{fig:mipsgal-heteroscedastic}, where we eschew any binning
-and perform linear regressions of the individual sources as a function
-of \(\log_{10} R_0\).  As expected from the previous 2-sample and
-5-sample analyses, the regression of \(R_{90}/R_0\) is almost flat,
-with a low correlation coefficient, whereas a regression of the
-absolute residuals to this fit against \(\log_{10} R_0\) shows a
-significant positive slope.  This increase in dispersion of shape with
-angular size is only evident for \(R_0 < 30''\), becoming flat at the
-largest sizes (see middle panel of
-Fig.~\ref{fig:mipsgal-heteroscedastic}).
+% So, the only correlation that survives scrutiny is the increase in
+% dispersion of \(R_{90}/R_0\) with increasing \(R_0\), which is finally
+% presented in the greatest detail in
+% Figure~\ref{fig:mipsgal-heteroscedastic}, where we eschew any binning
+% and perform linear regressions of the individual sources as a function
+% of \(\log_{10} R_0\).  As expected from the previous 2-sample and
+% 5-sample analyses, the regression of \(R_{90}/R_0\) is almost flat,
+% with a low correlation coefficient, whereas a regression of the
+% absolute residuals to this fit against \(\log_{10} R_0\) shows a
+% significant positive slope.  This increase in dispersion of shape with
+% angular size is only evident for \(R_0 < 30''\), becoming flat at the
+% largest sizes (see middle panel of
+% Fig.~\ref{fig:mipsgal-heteroscedastic}).
 
@@
 significant than any correlation with the other parameters discussed
-in this section (\(p < 10^{-4}\) for \(R_{90}/R_0\) and
-\(p < 10^{-5}\) for \(R_c/R_0\)).  This means that it cannot be simply
-due to the tendency of the higher-rated sources to have larger angular
-sizes.  However, the subjective nature of the star ratings makes this
-result hard to interpret.
+in this section (\(p < 10^{-4}\) for \(\Lambda\) and \(p < 10^{-5}\) for
+\(\Pi\)).  This means that it cannot be simply due to the tendency of
+the higher-rated sources to have larger angular sizes.  However, the
+subjective nature of the star ratings makes this result hard to
+interpret.
 

### 2019-04-21 papers/Papers1234/sec-quadrics-observations.tex
Finish revisions to sec 3 of Paper IV

@@
   \centering
-  \includegraphics[width=0.85\textwidth]{figs/mipsgal-pairplot}
+  \includegraphics[width=0.86\textwidth]{figs/mipsgal-pairplot}
   \caption[]{Matrix of pair plots that illustrate distributions of and
@@
 In the case of the faint/bright \(H_0\) sub-samples
-(Fig.~\ref{fig:mipsgal-heteroscedastic}b), it is less clear what
+(Fig.~\ref{fig:mipsgal-correlated}b), it is less clear what
 feature of the distributions differ.
@@
 \begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
+  \setlength\tabcolsep{0pt}
+  \setkeys{Gin}{width=0.5\linewidth}
+  \begin{tabular}{ll}
     (a) & (b) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/alphaori-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}\\
+    \includegraphics[trim=10 0 65 20, clip]{figs/alphaori-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/mucep-imageplot}\\
     (c) & (d) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/rhya-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}\\
+    \includegraphics[trim=10 0 65 20, clip]{figs/rhya-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/rleo-imageplot}\\
     (e) & (f) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/uuaur-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}\\
+    \includegraphics[trim=10 0 65 20, clip]{figs/uuaur-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/v1943sgr-imageplot}\\
     (g) & (h) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/rcas-imageplot}
+    \includegraphics[trim=10 0 65 20, clip]{figs/xpav-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/rcas-imageplot}
   \end{tabular}
@@
 \begin{figure*}
-  \centering
-  \setkeys{Gin}{width=0.48\linewidth}
-  \begin{tabular}{@{}ll@{}}
+  \setlength\tabcolsep{0pt}
+  \setkeys{Gin}{width=0.5\linewidth}
+  \begin{tabular}{ll}
     (a) & (b) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot} \\
+    \includegraphics[trim=10 0 65 20, clip]{figs/cwleo-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/epaqr-imageplot} \\
     (c) & (d) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot} \\
+    \includegraphics[trim=10 0 65 20, clip]{figs/khicyg-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/rtvir-imageplot} \\
     (e) & (f) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot} \\
+    \includegraphics[trim=10 0 65 20, clip]{figs/waql-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/wpic-imageplot} \\
     (g) & (h) \\
-    \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
-    & \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
+    \includegraphics[trim=10 0 65 20, clip]{figs/rscl-imageplot}
+    & \includegraphics[trim=10 0 65 20, clip]{figs/tetaps-imageplot}
   \end{tabular}
@@
     Other details of the plots are as in
-    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
-    except that the diagnostic plots are zoomed in slightly to show
-    more detail, and a smaller KDE smoothing bandwidth of
-    \(0.12 \times 0.08\) is used.}
+    Figs.~\ref{fig:mipsgal-shapes}, \ref{fig:mipsgal-uncorrelated},
+    and \ref{fig:mipsgal-correlated}.}
   \label{fig:herschel-compare-mipsgal}
@@
 We obtain a second sample of bow shocks from a far-infrared survey
-\citep{Cox:2012a} of circumstellar shells around asymptotic giant
-branch (AGB) stars and cool supergiants, obtained as part of the
+\citep{Cox:2012a} of circumstellar shells around known asymptotic
+giant branch (AGB) stars and cool supergiants, obtained as part of the
 \textit{Herschel} MESS (Mass-loss of Evolved StarS) program
@@
 shown as small red open circles in Figures~\ref{fig:herschel-arc-fits}
-and~\ref{fig:herschel-arc-fits-poor}.  Subsequently, the bow shock
-parameters \(R_0\), \(R_{90}\), and \(R_c\) are determined by circle
-fits, as in steps 5--8 of \S~\ref{sec:autom-trac-fitt}, with results
-shown in magenta on the figures.
+and~\ref{fig:herschel-arc-fits-poor} (more details of this technique
+are given in \S\S~6 and 7 of Paper~0).  Subsequently, the bow shock
+parameters \(R_0\), \(\Pi\), and \(\Lambda\) are determined by circle fits, as
+in steps 5--9 of \S~\ref{sec:autom-trac-fitt}, with results shown in
+magenta on the figures.
 
@@
 star) samples.  The Anderson--Darling test gives a highly significant
-difference between the \(R_{90}/R_0\) ratio distributions of the two
-samples, but only a marginally significant difference between the
-\(R_c/R_0\) ratio distributions (detailed results are shown in
-Table~\ref{tab:big-p}).  The Herschel sources show considerably
-smaller \(R_{90}\) ratio (median \(R_{90}/R_0 \approx 1.4\), implying bow
-shock wings that are more closed than in the MIPSGAL sources (median
-\(R_{90}/R_0 \approx 1.7\)).  For the radius of curvature ratio, there is
-only a slight difference in average values: median
-\(R_c/R_0 \approx 1.5\) for Herschel versus \(\approx 1.6\) for MIPSGAL, which is
-not statistically significant (rank biserial \(p = 0.29\)).  On the
-other hand, the dispersion in \(R_c/R_0\) is four times smaller for
-the Herschel sample, which is marginally significant (Brown--Forsythe
-\(p = 0.015\)).  In particular, the MIPSGAL sample shows a significant
-minority of very flat-nosed shapes (\(R_c/R_0 > 2\)), but these are
-absent in the Herschel sample.  The same can be seen directly by
-comparing the RSG/AGB bow shock shapes in
-Figures~\ref{fig:herschel-arc-fits}
+difference between the \(\Lambda\) distributions of the two samples, but
+only a marginally significant difference between the \(\Pi\)
+distributions (detailed results are shown in Table~\ref{tab:big-p}).
+The Herschel sources show considerably smaller planitude (median
+\(\Lambda \approx 1.4\)), implying bow shock wings that are more closed than in
+the MIPSGAL sources (median \(\Lambda \approx 1.7\)).  For the planitude, there is
+only a slight difference in average values: median \(\Pi \approx 1.5\) for
+Herschel versus \(\approx 1.6\) for MIPSGAL, which is not statistically
+significant (rank biserial \(p = 0.29\)).  On the other hand, the
+dispersion in \(\Pi\) is four times smaller for the Herschel sample,
+which is marginally significant (Brown--Forsythe \(p = 0.015\)).  In
+particular, the MIPSGAL sample shows a substantial minority of very
+flat-nosed shapes (\(\Pi > 2\)), but these are absent in the Herschel
+sample.  The same can be seen directly by comparing the RSG/AGB bow
+shock shapes in Figures~\ref{fig:herschel-arc-fits}
 and~\ref{fig:herschel-arc-fits-poor} with the representative OB bow

### 2019-04-22 papers/Papers1234/sec-quadrics-observations.tex
Start writing about LL bows for Paper IV

@@
 
+We obtain a third sample of bow shocks from a catalog of stationary
+emission line arcs in the Orion Nebula \citep{Bally:2000a}, which are
+detected via their H\(\alpha\) emission in HST~ACS surveys of the nebula
+\citep{Bally:2006a, Robberto:2013a}.  Out of a total of 73 such
+objects \citep{Gutierrez-Soto:2015a} we have selected 18 where the
+observations are of sufficient quality to reliably measure the
+planitude and alatude.  Images in the ACS f658n filter of these
+sources are shown in Figure~\ref{fig:ll-arcs}.  Some of the sources
+were identified as LL~Orionis-type objects by \citet{Bally:2001a} and
+are identified as LL~1--6. The remaining sources are labeled by their
+coordinate-based designation according to the system of
+\citet{ODell:1994a}.
+
+In \S~7 of Paper~0, we discussed in detail 
+Two of the sources, 000--400 and 069--641, were discussed in detail in
+.
+
 Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.

### 2019-04-29 papers/Papers1234/sec-obs-intro.tex
Finish description of LL arc fitting process

@@
 
-The largest number of bow shocks have been detected around OB stars,
-via their mid-infrared dust emission \citep{van-Buren:1995a,
+The largest number of bow shocks have been detected around high-mass
+OB stars, via their mid-infrared dust emission \citep{van-Buren:1995a,
   Noriega-Crespo:1997b, Povich:2008a, Kobulnicky:2010a, Peri:2012a,

### 2019-04-29 papers/Papers1234/sec-quadrics-observations.tex
Finish description of LL arc fitting process

@@
   \includegraphics[width=\linewidth]{figs/annotated-ll-arcs}
-  \caption[]{Stationary bow shock arcs in the Orion Nebula.}
+  \caption[]{Stationary bow shock arcs in the Orion Nebula.  Images
+    are of H\(\alpha\) plus [\ion{N}{ii}] emission through the HST ACS f658n
+    filter. The angular scale of each image is different, with the
+    yellow horizontal lines indicating \(5''\), corresponding to a
+    physical scale of \(\approx\SI{0.01}{pc}\).  Orange arrows indicate the
+    direction to the principal ionizing star, \thC. }
   \label{fig:ll-arcs}
@@
   \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
-  \caption[]{Comparison of Orion with OB stars.  Other details of the
-    plots are as in Figs.~\ref{fig:mipsgal-shapes}
-    and~\ref{fig:mipsgal-uncorrelated}, except that the diagnostic
-    plots are zoomed out to encompass larger ratio values, and a
-    larger KDE smoothing bandwidth of \(0.3 \times 0.2\) is used.}
+  \caption[]{Shape comparison between Orion Nebula arcs and OB star
+    bow shocks.  Other details of the plots are as in
+    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
+    except that the diagnostic plots are zoomed out to encompass
+    larger ratio values, and a larger KDE smoothing bandwidth of
+    \(0.3 \times 0.2\) is used.}
   \label{fig:ll-compare-mipsgal}
@@
 coordinate-based designation according to the system of
-\citet{ODell:1994a}.
+\citet{ODell:1994a}.  The determination of the bow shock shape for
+each source was carried out as described in \S~7 of Paper~0, using the
+``ridge'' method for manually tracing the arc (see Fig.~28 of
+Paper~0).  The planitude and alatude are found by circle fitting using
+the algorithm described in Paper~0's Appendix~E, as implemented in the
+python program
+\texttt{circle-fit.py}.\footnote{\url{https://github.com/div-B-equals-0/circle-fit}}
+The only adjustable parameter of the algorithm is \(\Delta\theta\), the maximum
+angle from the bow shock axis of points that are included in the
+circle fit.  We tested all values of \(\Delta\theta\) in \ang{5} increments from
+\ang{45} to \ang{80} and found that \(\Delta\theta = \ang{55}\) to \ang{70}
+gives stable results for all sources.  The accuracy of the fitted
+planitudes can be estimated from the dispersion in values of \(\Pi\) for
+the same source with different \(\Delta\theta\), which we find to be
+\(\approx 10\%\).  The fitted alatudes have a much smaller dispersion
+\(\approx 1 \%\), but in this case the accuracy is limited by the asymmetry
+of the wings, as characterized by \(\Delta\Lambda/\Lambda\) with an RMS value of
+\(\approx 15\%\).
 
-In \S~7 of Paper~0, we discussed in detail 
-Two of the sources, 000--400 and 069--641, were discussed in detail in
-.
-
-Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.
+%Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.
 

### 2019-04-29 papers/Papers1234/sec-quadrics-observations.tex
Finish description of LL arcs shape statistics

@@
     or above.  All 5-star sources plus those 4-star sources with
-    \(\Pi < 1\) are labelled with their \cite{Kobulnicky:2016a}
-    catalog number.  Horizontal error bars do not directly reflect the
-    uncertainty in \(\Pi\) but are instead simply the standard
-    deviation from the circle fit of bowshock points \(R_k\) within
+    \(\Pi < 1\) are labelled with their \cite{Kobulnicky:2016a} catalog
+    number.  Horizontal error bars do not directly reflect the
+    uncertainty in \(\Pi\) but are instead simply the standard deviation
+    from the circle fit of bowshock points \(R_k\) within
     \(\pm 45\degr\) of the axis.  Values on the vertical axis
@@
     uses an anisotropic gaussian kernel with bandwidths of
-    \(0.18 \times 0.12\). Thumbnail images of representative 4- and 5-star
-    sources at different points on the \(\Pi\)--\(\Lambda\) plane are
-    also shown. The angular scale of each image is indicated by a
-    yellow circle of diameter \(7.5''\), centered on the stellar
-    source.}
+    \(0.06 \times 0.04\) in \(\log_{10}\) units. Thumbnail images of
+    representative 4- and 5-star sources at different points on the
+    \(\Pi\)--\(\Lambda\) plane are also shown. The angular scale of each image
+    is indicated by a yellow circle of diameter \(7.5''\), centered on
+    the stellar source.}
   \label{fig:mipsgal-shapes}
@@
     Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
-    except that the diagnostic plots are zoomed out to encompass
-    larger ratio values, and a larger KDE smoothing bandwidth of
-    \(0.3 \times 0.2\) is used.}
+    except that a larger KDE smoothing bandwidth of
+    \(0.06 \times 0.045\) is used for the Orion Nebula sample.}
   \label{fig:ll-compare-mipsgal}
@@
 
+The resultant shape distribution for the Orion Nebula arcs is shown in
+Figure~\ref{fig:ll-compare-mipsgal}, where it is compared with the OB
+star shapes from \S~\ref{sec:ob-shapes}.  It can be seen that both the
+planitude and alatude distributions are shifted towards higher values,
+with median values of \(\Pi = 2.70\) and \(\Lambda = 2.55\).  The difference
+from the MIPSGAL sources (\(\Pi = 1.57\) and \(\Lambda = 1.69\)) is highly
+statistically significant, as indicated by extremely low \(p\)-values
+for the Anderson--Darling tests.  It is also at least 4 times larger
+than the systematic fitting uncertainties discussed in the previous
+paragraph.  On closer inspection, it appears that the shape
+distribution is bimodal.  Four of the sources (005--514, 4468--605,
+116--3101, 308--3036) are similar to typical OB stars, with
+\(\Lambda \approx \Pi \approx 1.5\), whereas the remainder are concentrated in the range
+\(\Pi = 2\) to \(4\), with an extended tail towards higher planitude.
+The alatudes mainly follow the line for parabolas,
+\(\Lambda = (2\Pi)^{1/2}\) (see App.~C of Paper~0), and the deviations from
+this line can be readily understood in terms of peculiar morphologies
+of the source (Fig.~\ref{fig:ll-arcs}).  For instance, LL~4 and
+266--558 both show large alatudes for their respective planitudes and
+these are both sources where the bow shock wings seem to bend outwards
+instead of following the curve from the apex region.  In contrast,
+030--524 has a small alatude for its planitude and this is a very
+asymmetric source with an apparent corner to the shell on one side.
+
 %Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.

### 2019-05-01 papers/Papers1234/app-p-values.tex
Redo the stats table, and make it portrait orientation

--- 2017-09-29 papers/Paper1/app-p-values.tex
@@
-\clearpage
-
-% Landscape table needs to go on its own page, so we need to manually
-% adjust the section counter so that it will ``belong'' to the next
-% section
-\addtocounter{section}{1}
-\sisetup{detect-all=true, detect-inline-weight=math}
-\sisetup{round-mode=figures, round-precision=2}
-\begin{landscape}
-\begin{table}
-  \setlength\tabcolsep{3pt}
-  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
-Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
-  \label{tab:big-p}
-  \input{figs/mipsgal-summary-stats-table-body.tex}
-\end{table}
-\end{landscape}
-\begin{table}
-  \contcaption{Results of all statistical tests performed on observed
-    bow shock shape parameters.}
-  \begin{tabular}{p{0.9\linewidth}}
-    \toprule
-    \textit{Description of columns:}
-    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
-    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
-    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
-    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source, as in steps~\ref{step:R0} and \ref{step:R90} of \S~\ref{sec:autom-trac-fitt}.
-Note that in the case of \(R_c\), this is \(\epsilon(R_0)\), and so is not a direct measure of the observational uncertainty in \(R_c\).
-    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
-    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
-    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
-It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
-    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
-    (Col.~13)~Ratio of standard deviations between the two sub-samples.
-    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
-    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
-    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive 
-    (Col.~16)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
-    \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\addtocounter{section}{-1}
-
 \section{Distribution of p-values for all correlations tested}
 \label{sec:distr-p-values}
-\addtocounter{table}{1}
 
@@
 
-\begin{table}
-  \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
-  \label{tab:type-I}
-  \centering
-  \begin{tabular}{lrr} \toprule
-    Correlation & \(p\) & \(\alpha\) \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
-    \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
-    \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
-    \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
-    \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
-    \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
-    \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
-    \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
-    \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
-    \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
-    \(R_c\) vs Facing & 0.71 & 1 \\
-    \(R_c\) vs H II & 0.50 & 1 \\
-    \(R_{90}\) vs Facing & 0.60 & 1 \\
-    \(R_{90}\) vs H II & 0.52 & 1 \\
-    \(R_c\) vs Multiple & 1.00 & 1 \\
-    \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
-    \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
-    \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
-    \midrule
-    \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
-    \(R_c\) vs Herschel & 0.074 & 0.3437 \\
-    \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
-    \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
-    \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+% \begin{table}
+%   \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
+%   \label{tab:type-I}
+%   \centering
+%   \begin{tabular}{lrr} \toprule
+%     Correlation & \(p\) & \(\alpha\) \\
+%     \midrule
+%     \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
+%     \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
+%     \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
+%     \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
+%     \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
+%     \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
+%     \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
+%     \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
+%     \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
+%     \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
+%     \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
+%     \midrule
+%     \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
+%     \(R_c\) vs Facing & 0.71 & 1 \\
+%     \(R_c\) vs H II & 0.50 & 1 \\
+%     \(R_{90}\) vs Facing & 0.60 & 1 \\
+%     \(R_{90}\) vs H II & 0.52 & 1 \\
+%     \(R_c\) vs Multiple & 1.00 & 1 \\
+%     \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
+%     \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
+%     \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
+%     \midrule
+%     \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
+%     \(R_c\) vs Herschel & 0.074 & 0.3437 \\
+%     \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
+%     \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
+%     \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
+%     \bottomrule
+%   \end{tabular}
+% \end{table}
 
@@
 
+% \begin{table}
+%   \caption{Results of all statistical tests performed on observed
+%     bow shock shape parameters.}
+%   \begin{tabular}{p{0.95\linewidth}}
+%     \toprule
+%     \textit{Description of columns:}
+%     (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
+%     (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
+%     (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
+%     (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source, as in steps~\ref{step:R0} and \ref{step:R90} of \S~\ref{sec:autom-trac-fitt}.
+Note that in the case of \(R_c\), this is \(\epsilon(R_0)\), and so is not a direct measure of the observational uncertainty in \(R_c\).
+%     (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
+%     (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
+%     (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
+It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
+%     (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
+%     (Col.~13)~Ratio of standard deviations between the two sub-samples.
+%     (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
+%     (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
+%     (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive to differences in the central value of the distributions.
+%     (Col.~16)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
+%     \\
+%     \bottomrule
+%   \end{tabular}
+% \end{table}
+
+\sisetup{detect-all=true, detect-inline-weight=math}
+\sisetup{round-mode=figures, round-precision=2}
+\sisetup{table-align-exponent = false}
+\begin{table*}
+  \setlength\tabcolsep{2pt}
+  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
+Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
+  \label{tab:big-p}
+  \input{figs/mipsgal-summary-stats-table-body.tex}
+\end{table*}
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "quadrics-bowshock"
+%%% TeX-master: "obs-bowshocks"
 %%% End:

### 2019-05-01 papers/Papers1234/figs/mipsgal-summary-stats-table-body.tex
Submitted first paper! To MNRAS and arxiv
Redo the stats table, and make it portrait orientation

--- 2017-04-19 Stellar-Bowshocks-2017/mipsgal-summary-stats-table-body.tex
@@
 %%% Table automatically generated from mipsgal-summary-stats.tab
-%%% 2017-04-19 13:16:10.731012
+%%% 2019-04-30 22:48:49.149121
 %%%
@@
 	\newlength\Width\settowidth\Width{Comparison}
-	\begin{tabular}{@{} ll @{\quad } S[round-mode=places]S[round-mode=places] S[round-mode=places]S[round-mode=places] SS SS @{\quad\quad\quad} SSS[round-mode=places] @{\quad} S@{}S@{}S @{}}\toprule
-	  & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\
-	  {Comparison} & {Variable} & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)} & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)} & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)} & {\((\sigma/\!\sqrt n)_{\text{A}}\)} & {\((\sigma/\!\sqrt n)_{\text{B}}\)} & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)} & \multicolumn{1}{c}{Anderson--Darling} & \multicolumn{1}{c}{Rank biserial} &  \multicolumn{1}{c}{Brown--Forsythe}\\
-	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)} & {(3)} & {(4)} & {(5)} & {(6)} & {(7)} & {(8)} & {(9)} & {(10)}  & {(11)} & {(12)} & {(13)} & {(14)} & {(15)} & {(16)} \\  
-	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\
+	\begin{tabular}{
+	  @{} ll @{\quad }
+	  % Mean
+	  S[round-mode=places]S[round-mode=places]
+	  % Std Dev
+	  S[round-mode=places]S[round-mode=places]
+	  % Obs Disp
+	  SS
+	  % Effect sizes
+	  @{\quad} SSS[round-mode=places]
+	  % p values
+	  @{\quad}
+	  S[table-format = +1.2e1]
+	  S[table-format = +1.2e1]
+	  S[table-format = +1.2e1] @{}
+	  }\toprule
+	  & {Dependent}
+	  & \multicolumn{2}{c}{Mean}
+	  & \multicolumn{2}{c}{Std.\ Dev.}
+	  & \multicolumn{2}{c}{Obs.\ Disp.}
+	  & \multicolumn{3}{c @{} }{\dotfill Effect sizes\dotfill }
+	  & \multicolumn{3}{c @{}}{Non-parametric test \(p\)-values} \\ 
+	  {Comparison} & {Variable}
+	  & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)}
+	  & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)}
+	  & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)}
+	  & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)}
+	  & {K--S} & {Rank} &  {B--F}\\
+	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)}
+	  & {(3)} & {(4)}
+	  & {(5)} & {(6)}
+	  & {(7)} & {(8)}
+	  & {(9)} & {(10)} & {(11)}
+	  & {(12)} & {(13)} & {(14)}  \\  
+	  \midrule\multicolumn{10}{@{} l @{}}{\itshape Median split of continuous independent variables}\\
 \addlinespace
-Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
-\(H\) magnitude & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\
+Faint/bright & \(\Pi\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.123 & 0.303 & \itshape 1.654 & 0.254 & 0.111 & \itshape 0.0335\\
+\(H\) magnitude & \(\Lambda\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0156 & \itshape 0.0235 & 0.125\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.07 & 0.093 & 1.013 & 0.191 & 0.365 & 0.761\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & \itshape 0.428 & \bfseries 0.00139\\
-bow shock size, \(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\
+Low/high & \(\Pi\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.1 & 0.043 & 0.774 & 0.358 & 0.192 & 0.599\\
+bow shock size, \(R_0\) & \(\Lambda\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.061 & 0.11 & \bfseries 1.342 & 0.0815 & 0.428 & \bfseries 0.00139\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.091 & 0.176 & 1.054 & \itshape 0.042 & 0.238 & 0.193\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
-extinction, \(A_K\) & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\
+Low/high & \(\Pi\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.082 & 0.139 & 1.116 & 0.254 & 0.285 & 0.982\\
+extinction, \(A_K\) & \(\Lambda\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.04 & 0.132 & 1.213 & 0.524 & 0.602 & 0.123\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & -0.039 & 0.057 & 1.326 & 0.421 & 0.61 & 0.112\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
-\(\vert{}b\vert\) & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\
+Low/high & \(\Pi\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.069 & 0.181 & 1.358 & 0.0568 & 0.368 & 0.0842\\
+\(\vert{}b\vert\) & \(\Lambda\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.02 & 0.008 & 0.796 & 0.323 & 0.795 & 0.0534\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.009 & 0.021 & 1.005 & 0.95 & 0.907 & 0.694\\
 \addlinespace
-High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
-\(\cos \ell\) & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
-\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\
+High/low & \(\Pi\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & -0.0 & -0.064 & 0.785 & 0.998 & 0.999 & 0.549\\
+\(\cos \ell\) & \(\Lambda\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & -0.049 & -0.093 & 1.152 & 0.554 & 0.532 & 0.159\\
+\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(\Delta \Lambda\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.054 & 0.122 & 1.1 & 0.791 & 0.491 & 0.365\\
 \midrule
-\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\
+\multicolumn{10}{@{} l @{}}{\itshape Categorical independent variables}\\
 \addlinespace
-Environment: & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
-Isolated vs Facing & \(\Delta R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\
+Environment: & \(\Pi\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.042 & 0.11 & 1.053 & 0.67 & 0.676 & 0.377\\
+Isolated vs Facing & \(\Lambda\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & -0.07 & -0.142 & 1.194 & 0.877 & 0.49 & 0.392\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(\Delta \Lambda\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & -0.019 & 0.034 & 1.066 & 0.883 & 0.85 & 0.438\\
 \addlinespace
-Environment: & \(R_{90}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
-Isolated vs \hii & \(\Delta R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\
+Environment: & \(\Pi\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.024 & 0.174 & 1.118 & 0.587 & 0.875 & 0.255\\
+Isolated vs \hii & \(\Lambda\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & -0.13 & -0.193 & 1.092 & 0.67 & 0.391 & 0.782\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(\Delta \Lambda\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & -0.048 & -0.095 & 0.855 & 0.825 & 0.754 & 0.799\\
 \addlinespace
-Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
-source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
-\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\
+Single/multiple & \(\Pi\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.027 & 0.076 & 1.198 & 0.965 & 0.756 & 0.605\\
+source candidate & \(\Lambda\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.074 & 0.177 & 1.09 & 0.431 & 0.396 & 0.338\\
+\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(\Delta \Lambda\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.093 & 0.136 & 0.987 & 0.293 & 0.284 & 0.97\\
 \addlinespace
-With/without & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
-\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
-\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\
+With/without & \(\Pi\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & -0.012 & 0.101 & 1.547 & 0.948 & 0.904 & 0.2\\
+\SI{8}{\um} emission & \(\Lambda\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & -0.042 & -0.044 & 1.031 & 0.559 & 0.667 & 0.563\\
+\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(\Delta \Lambda\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.021 & -0.106 & 0.726 & 0.985 & 0.826 & 0.219\\
+\addlinespace
+3-star vs (4+5)-star & \(\Pi\) & 1.632 & 2.0 & 0.91 & 0.764 & 0.106 & 0.061 & \bfseries 0.386 & \bfseries 0.431 & 0.84 & \bfseries 5e-06 & \bfseries 7.66e-07 & 0.762\\
+ & \(\Lambda\) & 1.661 & 1.812 & 0.288 & 0.286 & 0.247 & 0.216 & \bfseries 0.328 & \bfseries 0.525 & 0.99 & \bfseries 8.45e-05 & \bfseries 2.63e-05 & 0.403\\
+\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(\Delta \Lambda\) & 0.189 & 0.19 & 0.162 & 0.161 &   &   & -0.007 & 0.009 & 0.994 & 0.676 & 0.927 & 0.561\\
 \midrule
-\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Intercomparison with other datasets \dotfill}\\
+\multicolumn{10}{@{} l @{}}{\itshape Intercomparison with other datasets}\\
 \addlinespace
-MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
- & \(\Delta R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\
+MIPS vs Orion & \(\Pi\) & 1.784 & 3.09 & 0.871 & 1.666 &   &   & \bfseries 0.57 & \bfseries 1.37 & \bfseries 1.911 & \bfseries 8.55e-05 & \bfseries 5.73e-05 & \bfseries 0.00133\\
+ & \(\Lambda\) & 1.723 & 2.532 & 0.297 & 0.749 &   &   & \bfseries 0.71 & \bfseries 2.308 & \bfseries 2.526 & \bfseries 6.62e-07 & \bfseries 5.49e-07 & \bfseries 1.49e-09\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(\Delta \Lambda\) & 0.19 & 0.658 & 0.162 & 0.513 &   &   & \bfseries 0.642 & \bfseries 2.243 & \bfseries 3.173 & \bfseries 4.98e-07 & \bfseries 5.95e-06 & \bfseries 1.07e-10\\
 \addlinespace
-MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
- & \(\Delta R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505
+MIPS vs RSG & \(\Pi\) & 1.784 & 1.479 & 0.871 & 0.227 &   &   & -0.159 & -0.362 & \itshape 0.26 & \itshape 0.0129 & 0.288 & \itshape 0.0151\\
+ & \(\Lambda\) & 1.723 & 1.41 & 0.297 & 0.101 &   &   & \bfseries -0.719 & \bfseries -1.089 & \itshape 0.339 & \bfseries 2.89e-06 & \bfseries 1.56e-06 & \itshape 0.004\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 16\) & \(\Delta \Lambda\) & 0.19 & 0.147 & 0.162 & 0.076 &   &   & -0.072 & -0.267 & 0.469 & 0.518 & 0.701 & 0.12
 \\
 \bottomrule
+\multicolumn{14}{@{}p{\linewidth}@{}}{
+  \textit{Description of columns:}
+  (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
+  (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
+  (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
+  (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source, as in steps~\ref{step:R0} and \ref{step:R90} of \S~\ref{sec:autom-trac-fitt}.
+Note that in the case of \(\Pi\), this is \(\epsilon(R_0)\), and so is not a direct measure of the observational uncertainty in \(\Pi\).
+  % (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
+  (Cols.~9--11)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
+  (Col.~9)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
+It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
+  (Col.~10)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
+  (Col.~11)~Ratio of standard deviations between the two sub-samples.
+  (Cols.~12--14)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
+  (Col.~12)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
+  (Col.~13)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive to differences in the central value of the distributions.
+  (Col.~14)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
+}
 \end{tabular}

### 2019-05-02 papers/Papers1234/app-p-values.tex
Switch to Kuiper test instead of K-S

@@
 
-Results from all the statistical tests discussed in \S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
+\begin{table*}
+  \sisetup{detect-all=true, detect-inline-weight=math}
+  \sisetup{round-mode=figures, round-precision=2}
+  \sisetup{table-align-exponent = false}
+  \setlength\tabcolsep{2pt}
+  \caption{Results of all statistical tests performed on observed bow
+    shock shape parameters. Significant correlations are shown in
+    \textbf{bold}, marginally significant correlations in
+    \textit{italic}}
+  \label{tab:big-p}
+  \input{figs/mipsgal-summary-stats-table-body.tex}
+\end{table*}
+
+Results from all the statistical tests discussed in
+\S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
 
@@
 
-\sisetup{detect-all=true, detect-inline-weight=math}
-\sisetup{round-mode=figures, round-precision=2}
-\sisetup{table-align-exponent = false}
-\begin{table*}
-  \setlength\tabcolsep{2pt}
-  \caption{Results of all statistical tests performed on observed bow shock shape parameters.
-Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
-  \label{tab:big-p}
-  \input{figs/mipsgal-summary-stats-table-body.tex}
-\end{table*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\linewidth]
+%   {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
+%   \caption{Plane-of-sky projections of perturbed bow shapes.  In all
+%     cases, the base bow shape is ancantoid with \(\xi = 0.8\),
+%     \(\beta = 0.005\) and the perturbation is the same as in the central
+%     panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
+%     \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
+%     inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
+%     color and thickness, see key) and for different fractional phases
+%     of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
+%     (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
+%     the spatial coordinates are normalized to the instantaneous
+%     projected apex radius \(R_0'\) at each phase, so the apex does not
+%     appear to move.}.
+%   \label{fig:perturb-xy-prime}
+% \end{figure*}
+
+\section{Perturbed bows}
+\label{sec:perturbed-bows}
+
+\begin{figure*}[t!]
+  \centering
+  \includegraphics[width=\linewidth]{figs/compare_xyprime_wave-wilkinoid}
+  \caption{Small-amplitude standing wave perturbations to wilkinoid
+    bow shapes.  The maximum deviations from the base shape are seen
+    at phases \(\phi = 0\) (blue line) and \(\phi = 0.5\) (red line), while
+    the perturbation is zero at \(\phi = 0.25\) and \(0.75\) (black
+    line).  Results are shown left to right for increasing wave
+    numbers \(N\) and decreasing amplitudes \(A\): (a)~\(A = 0.1\),
+    \(N = 1.0\), (b)~\(A = 0.05\), \(N = 2.0\), (a)~\(A = 0.02\),
+    \(N = 5.0\).}
+  \label{fig:perturb-shapes}
+\end{figure*}
+
+Instability of bow \citep{Blondin:1998a}
+
+The bow shock models that we have considered so far have been
+steady-state: although material is moving throughout the bow, the
+pattern of its structure does not vary with time.  In this section, we
+consider small, time-varying perturbations to such a steady-state
+structure.  These may be due to periodic variations in the
+momentum-loss rate of one of the winds, or due to dynamical
+instabilities in the shocked shell.
+
+We consider fractional perturbations \(\Delta(\theta, t)\) of a base shape
+\(R(\theta)\), such that
+\(R(\theta) \to [1 + \Delta(\theta, t)] R(\theta)\).  For simplicity,
+\(\Delta(\theta, t)\) is a standing wave of constant amplitude \(A\), which is
+periodic in \(\theta\), with wave number \(N\).  In cylindrical symmetry
+\(\Delta(\theta, t)\) must be even in \(\theta\), so can be expressed as
+\begin{equation}
+  \label{eq:standing-wave}
+  \Delta(\theta, t) = A \cos(N \theta) \cos(2\pi \varphi) . 
+\end{equation}
+For waves with period \(P\), the fractional phase \(\varphi\) will
+vary with time \(t\) as
+\begin{equation}
+  \label{eq:fractional-phase}
+  \varphi(t) = (\varphi_0 + t/P) \bmod 1.0\ ,
+\end{equation}
+where \(\varphi_0\) is an arbitrary reference phase.
+
+Example oscillations with wave numbers \(N = 1.0\), \(2.0\), and
+\(5.0\) superimposed on a wilkinoid base shape are shown in
+Figure~\ref{fig:perturb-shapes}.  There are \(N\) nodes of the
+oscillation between \(\theta = [0, \pi]\), always with an antinode at the apex
+(\(\theta = 0\)), as required by symmetry.  So, with \(N = 1.0\) there is a
+node (fixed point) in the near wing at \(\theta = \pi/2\), but an antinode in
+the far wing at \(\theta = \pi\), which is in antiphase with the oscillation
+of the apex, giving rise to a large-scale ``breathing'' mode of
+oscillation.  With \(N = 2.0\), there are nodes at \(\theta = \pi/4\) and
+\(3\pi/4\), while the antiphase antinode has moved to the near wing at
+\(\theta = \pi/2\).  There is still an antinode in the far wing at
+\(\theta = \pi\) but it is now in phase with the apex, giving rise to a
+``curling-up/straightening-out'' mode of oscillation.  With
+\(N = 5.0\), there are many more nodes and antinodes, giving a
+``ringing'' mode of oscillation.  Note that all our examples have
+\(A \propto 1/N\) in order to keep the local curvature relatively low.  If
+the product \(A N\) is not small compared to unity, then the local
+curvature can be so extreme as to reverse the concave shape of the
+base bow shape, producing locally convex regions.
+
+If the bow shape is viewed at different inclinations, then the effect
+of the oscillations on the projected shape will vary.  In particular,
+the apex-to-wing interval in body-frame angle changes from
+\(\theta = [0, \pi/2]\) at \(i = 0\) to
+\(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see
+equations~\eqref{Q-eq:thetapar} and \eqref{Q-eq:th90} of \PaperI{}.
+The difference \(\theta_{90} - \theta_0\) is always a declining function of
+\(|i|\), so the oscillations of the tangent line become increasingly
+stretched out as the inclination increases.  This effect can be seen
+in Figure~\ref{fig:perturb-xy-prime}, which shows an example of the
+variation in projected perturbed shape with inclination angle for 3
+different phases, this time for an ancantoid base shape and the
+\(N = 2.0\) perturbation shown in Figure~\ref{fig:perturb-shapes}b.
+The most marked changes with phase are seen for low inclinations,
+whereas the changes are smaller, although still noticeable, for
+\(|i| \ge 45^\circ\). If \(A N\) exceeds about 0.5, then the local curvature
+of the perturbations is so extreme that multiple tangent lines exist
+at intermediate inclinations, which produces the appearance of
+additional incomplete bright arcs inside the main arc of the bow.
 

### 2019-05-02 papers/Papers1234/sec-standing-wave.tex
Switch to Kuiper test instead of K-S

@@
 \label{sec:discussion}
-
-\begin{figure*}[t!]
-  \centering
-  \includegraphics[width=\linewidth]{figs/compare_xyprime_wave-wilkinoid}
-  \caption{Small-amplitude standing wave perturbations to wilkinoid
-    bow shapes.  The maximum deviations from the base shape are seen
-    at phases \(\phi = 0\) (blue line) and \(\phi = 0.5\) (red line), while
-    the perturbation is zero at \(\phi = 0.25\) and \(0.75\) (black
-    line).  Results are shown left to right for increasing wave
-    numbers \(N\) and decreasing amplitudes \(A\): (a)~\(A = 0.1\),
-    \(N = 1.0\), (b)~\(A = 0.05\), \(N = 2.0\), (a)~\(A = 0.02\),
-    \(N = 5.0\).}
-  \label{fig:perturb-shapes}
-\end{figure*}
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\linewidth]
-%   {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
-%   \caption{Plane-of-sky projections of perturbed bow shapes.  In all
-%     cases, the base bow shape is ancantoid with \(\xi = 0.8\),
-%     \(\beta = 0.005\) and the perturbation is the same as in the central
-%     panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
-%     \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
-%     inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
-%     color and thickness, see key) and for different fractional phases
-%     of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
-%     (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
-%     the spatial coordinates are normalized to the instantaneous
-%     projected apex radius \(R_0'\) at each phase, so the apex does not
-%     appear to move.}.
-%   \label{fig:perturb-xy-prime}
-% \end{figure*}
-
-\subsection{Perturbed bows}
-\label{sec:perturbed-bows}
-
-Instability of bow \citep{Blondin:1998a}
-
-The bow shock models that we have considered so far have been
-steady-state: although material is moving throughout the bow, the
-pattern of its structure does not vary with time.  In this section, we
-consider small, time-varying perturbations to such a steady-state
-structure.  These may be due to periodic variations in the
-momentum-loss rate of one of the winds, or due to dynamical
-instabilities in the shocked shell.
-
-We consider fractional perturbations \(\Delta(\theta, t)\) of a base shape
-\(R(\theta)\), such that
-\(R(\theta) \to [1 + \Delta(\theta, t)] R(\theta)\).  For simplicity,
-\(\Delta(\theta, t)\) is a standing wave of constant amplitude \(A\), which is
-periodic in \(\theta\), with wave number \(N\).  In cylindrical symmetry
-\(\Delta(\theta, t)\) must be even in \(\theta\), so can be expressed as
-\begin{equation}
-  \label{eq:standing-wave}
-  \Delta(\theta, t) = A \cos(N \theta) \cos(2\pi \varphi) . 
-\end{equation}
-For waves with period \(P\), the fractional phase \(\varphi\) will
-vary with time \(t\) as
-\begin{equation}
-  \label{eq:fractional-phase}
-  \varphi(t) = (\varphi_0 + t/P) \bmod 1.0\ ,
-\end{equation}
-where \(\varphi_0\) is an arbitrary reference phase.
-
-Example oscillations with wave numbers \(N = 1.0\), \(2.0\), and
-\(5.0\) superimposed on a wilkinoid base shape are shown in
-Figure~\ref{fig:perturb-shapes}.  There are \(N\) nodes of the
-oscillation between \(\theta = [0, \pi]\), always with an antinode at the apex
-(\(\theta = 0\)), as required by symmetry.  So, with \(N = 1.0\) there is a
-node (fixed point) in the near wing at \(\theta = \pi/2\), but an antinode in
-the far wing at \(\theta = \pi\), which is in antiphase with the oscillation
-of the apex, giving rise to a large-scale ``breathing'' mode of
-oscillation.  With \(N = 2.0\), there are nodes at \(\theta = \pi/4\) and
-\(3\pi/4\), while the antiphase antinode has moved to the near wing at
-\(\theta = \pi/2\).  There is still an antinode in the far wing at
-\(\theta = \pi\) but it is now in phase with the apex, giving rise to a
-``curling-up/straightening-out'' mode of oscillation.  With
-\(N = 5.0\), there are many more nodes and antinodes, giving a
-``ringing'' mode of oscillation.  Note that all our examples have
-\(A \propto 1/N\) in order to keep the local curvature relatively low.  If
-the product \(A N\) is not small compared to unity, then the local
-curvature can be so extreme as to reverse the concave shape of the
-base bow shape, producing locally convex regions.
-
-If the bow shape is viewed at different inclinations, then the effect
-of the oscillations on the projected shape will vary.  In particular,
-the apex-to-wing interval in body-frame angle changes from
-\(\theta = [0, \pi/2]\) at \(i = 0\) to
-\(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see
-equations~\eqref{Q-eq:thetapar} and \eqref{Q-eq:th90} of \PaperI{}.
-The difference \(\theta_{90} - \theta_0\) is always a declining function of
-\(|i|\), so the oscillations of the tangent line become increasingly
-stretched out as the inclination increases.  This effect can be seen
-in Figure~\ref{fig:perturb-xy-prime}, which shows an example of the
-variation in projected perturbed shape with inclination angle for 3
-different phases, this time for an ancantoid base shape and the
-\(N = 2.0\) perturbation shown in Figure~\ref{fig:perturb-shapes}b.
-The most marked changes with phase are seen for low inclinations,
-whereas the changes are smaller, although still noticeable, for
-\(|i| \ge 45^\circ\). If \(A N\) exceeds about 0.5, then the local curvature
-of the perturbations is so extreme that multiple tangent lines exist
-at intermediate inclinations, which produces the appearance of
-additional incomplete bright arcs inside the main arc of the bow.
 

### 2019-05-02 papers/Papers1234/sec-obs-intro.tex
Make a start on the discussion section of Paper IV

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/obs-shape-terminology}
+  \caption[Terminology]{Terminology employed in this paper to describe
+    bow shock shapes, following \citet{Tarango-Yong:2018a}.}
+  \label{fig:obs-shape-terminology}
+\end{figure}
+
 The shapes of stellar bow shocks are frequently compared with what has
@@
 proposed the use of two dimensionless parameters, \textit{planitude}
-and \textit{alatude}, to describe a general bow shock shape.  The
-planitude, \(\Pi = R_c / R_0\), measures the flatness of the bow shock
-apex (see Fig.~1 of Paper~0 for explanation of apex and other
-descriptive terms), where \(R_0\) is the star--apex distance and
-\(R_c\) is the radius of curvature measured at the apex.  The alatude,
+and \textit{alatude}, to describe a general bow shock shape, which we
+illustrate in Figure~\ref{fig:obs-shape-terminology}.  The planitude,
+\(\Pi = R_c / R_0\), measures the flatness of the bow shock apex, where
+\(R_0\) is the star--apex distance and \(R_c\) is the radius of
+curvature measured at the apex.  The alatude,
 \(\Lambda = R_{90}/R_0\), measures the openness of the bow shock wings,

### 2019-05-02 papers/Papers1234/sec-quadrics-observations.tex
Switch to Kuiper test instead of K-S
Make a start on the discussion section of Paper IV

@@
 to the axial separation, \(R_0\), between the source and the bow shock
-apex.  The vertical axis corresponds to the shape of the bow shock
-wings, ranging from closed ``C'' shapes for smaller values of
-\(\Lambda\) to open ``V'' shapes for larger values of \(\Lambda\).  The background
-shading shows the regions of the \(\Pi\)--\(\Lambda\) plane occupied by simple
-quadric shapes (see \S~4 of Paper~0): oblate spheroids (light gray),
-prolate spheroids (dark gray), and hyperboloids (white). The boundary
-between closed and open corresponds to the paraboloids, and is shown
-by the solid curved line that divides the dark gray and white regions
-of the graph.
+apex (see Fig.~\ref{fig:obs-shape-terminology}).  The vertical axis
+corresponds to the shape of the bow shock wings, ranging from closed
+``C'' shapes for smaller values of \(\Lambda\) to open ``V'' shapes for
+larger values of \(\Lambda\).  The background shading shows the regions of
+the \(\Pi\)--\(\Lambda\) plane occupied by simple quadric shapes (see \S~4 of
+Paper~0): oblate spheroids (light gray), prolate spheroids (dark
+gray), and hyperboloids (white). The boundary between closed and open
+corresponds to the paraboloids, and is shown by the solid curved line
+that divides the dark gray and white regions of the graph.
 
@@
 ``ridge'' method for manually tracing the arc (see Fig.~28 of
-Paper~0).  The planitude and alatude are found by circle fitting using
-the algorithm described in Paper~0's Appendix~E, as implemented in the
+Paper~0).  In some sources, such as LL~1, LL~6, 109--246, and 4468--605,
+a high-velocity jet flow is also seen to issue from the star
+\citep{Bally:2006a, Henney:2013a}.  We took care to when tracing the
+arcs of such sources to avoid regions where jet knot emission is
+projected on the bow shock shell.
+
+The planitude and alatude are found by circle fitting using the
+algorithm described in Paper~0's Appendix~E, as implemented in the
 python program

### 2019-05-02 papers/Papers1234/sec-standing-wave.tex
Make a start on the discussion section of Paper IV

@@
 \label{sec:discussion}
+
+In this section, we discuss the physical implications of our empirical
+findings regarding bow shock shapes.  Our most reliable result is the
+average shape of the OB bow shocks from the 227 MIPSGAL sources with
+quality rating of 3~stars or higher.  This yields mean values of
+\(\Pi = 1.78 \pm 0.06\) and \(\Lambda = 1.72 \pm 0.02\), or median values of
+\(\Pi = 1.57\) and \(\Lambda = 1.69\).  The uncertainty quoted on the mean
+values is the ``standard error of the mean'':
+\(\text{sem} = \sigma / \sqrt{n}\), where \(\sigma\) is the rms dispersion and
+\(n\) is the number of sources.  Note that in the case of the
+planitude \(\text{sem}(\Pi) = 0.06\) is considerably smaller than
+\(\text{mean}(\Pi) - \text{median}(\Pi) = 0.21\), so the latter would be a
+more conservative estimate of the uncertainty.\footnote{This is
+  because the distribution of \(\Pi\) is approximately log-normal, which
+  yields a significant tail towards high values when converted to
+  linear space.}  These values can be compared with the predictions of
+the thin-shell Wilkinoid model \citep{Wilkin:1996a}, which are
+\(\Pi = 1.67\), \(\Lambda = 1.73\) when the bow shock axis lies in the plane
+of the sky (following Paper~0, this is defined as the zero point of
+the inclination angle, \(i\)).  When the axis is inclined, both
+planitude and alatude are predicted to decrease but not by very much,
+tending to \(\Pi = 1.5\), \(\Lambda = 1.63\) as
+\(\abs{i} \to \ang{90}\) (see \S~5.3 of Paper~0).  The median observed
+value\footnote{In the presence of outliers, the median is a more
+  robust estimate of the central tendency than is the mean.} falls
+squarely inside this range for both the planitude and alatude, which
+is a remarkable triumph for the \citet{Wilkin:1996a} model.
+
+On the other hand, turning now to the \emph{variety} of bow shock
+shapes, we see that the wilkinoid can no longer explain our results.
+The rms dispersions of the planitude and alatude distributions for the
+MIPSGAL sources are \(\sigma(\Pi) = 0.87\) and
+\(\sigma(\Lambda) = 0.30\) (Tab.~\ref{tab:big-p}), which are respectively 5 times
+and 3 times larger than the total range of variation of \(\Pi\) and
+\(\Lambda\) predicted for the wilkinoid surface.  Although some of the
+dispersion is due to uncertainties in the observations and the fitting
+algorithm, this contribution is expected to be small, especially for
+the larger, well-resolved sources, for which systematic uncertainties
+in the methods for determining \(\Pi\) and \(\Lambda\) will
+dominate. Conservative upper limits to the relative size of these
+uncertainties were estimated in \S~7 of Paper~0 to be \(< 20\%\) for
+\(\Pi\) and \(< 10\%\) for \(\Lambda\), whereas the observed dispersions are
+roughly twice as large: \(\sigma(\Pi)/\Pi = 55\%\) and \(\sigma(\Lambda)/\Lambda = 18\%\).
 

### 2019-05-06 papers/Papers1234/sec-standing-wave.tex
Little bit more discussion for paper II

@@
 \(\Pi\) and \(< 10\%\) for \(\Lambda\), whereas the observed dispersions are
-roughly twice as large: \(\sigma(\Pi)/\Pi = 55\%\) and \(\sigma(\Lambda)/\Lambda = 18\%\).
+roughly twice as large: \(\sigma(\Pi)/\Pi = 55\%\) and
+\(\sigma(\Lambda)/\Lambda = 18\%\).  Furthermore, the variations in planitude and
+alatude are readily apparent by eye, as is demonstrated by the example
+bow shock images shown in Figure~\ref{fig:mipsgal-shapes}b.  Sources
+such as K123 have very typical shapes and fall near the center of the
+\(\Pi\)--\(\Lambda\) distribution, whereas high-\(\Pi\) sources such as K447 have
+a very flat apex region, while low-\(\Pi\) sources such as K566 have a
+pointier, almost triangular apex.  High-\(\Lambda\) sources, such as K517,
+have very open wings that bend away from the star, while
+low-\(\Lambda\) sources such as K489 have closed wings and a semi-circular
+appearance.
+
+In Paper~0 we found that certain bow shock shapes can show a much
+greater variation in their projected appearance as a function of
+inclination angle than is seen for the wilkinoid.  For example, the
+cantoids and ancantoids, which have asymptotically hyperbolic far
+wings, can shift towards higher apparent planitude and alatude as the
+inclination increases, generally with \(\Lambda \ge \Pi\) (Fig.~20 of Paper~0).
+This might plausibly explain the spur towards higher \(\Lambda\) seen in the
+empirical distribution ()
 

### 2019-05-07 papers/Papers1234/app-p-values.tex
Finish discussion of OB star shapes for Paper IV

@@
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\linewidth]
-%   {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
-%   \caption{Plane-of-sky projections of perturbed bow shapes.  In all
-%     cases, the base bow shape is ancantoid with \(\xi = 0.8\),
-%     \(\beta = 0.005\) and the perturbation is the same as in the central
-%     panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
-%     \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
-%     inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
-%     color and thickness, see key) and for different fractional phases
-%     of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
-%     (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
-%     the spatial coordinates are normalized to the instantaneous
-%     projected apex radius \(R_0'\) at each phase, so the apex does not
-%     appear to move.}.
-%   \label{fig:perturb-xy-prime}
-% \end{figure*}
-
 \section{Perturbed bows}
@@
 
-\begin{figure*}[t!]
+\begin{figure*}
   \centering
@@
     line).  Results are shown left to right for increasing wave
-    numbers \(N\) and decreasing amplitudes \(A\): (a)~\(A = 0.1\),
-    \(N = 1.0\), (b)~\(A = 0.05\), \(N = 2.0\), (a)~\(A = 0.02\),
-    \(N = 5.0\).}
+    numbers \(N\) and decreasing amplitudes \(A\): (a)~\(A = 0.2\),
+    \(N = 1.0\), (b)~\(A = 0.1\), \(N = 2.0\), (a)~\(A = 0.04\),
+    \(N = 5.0\).  The maximum curvature, proportional to \(A N\) is
+    the same in all three cases.}
   \label{fig:perturb-shapes}
 \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]
+  {figs/wave_xyprime-A010-N20-ancantoid-xi080-beta000500}
+  \caption{Plane-of-sky projections of perturbed bow shapes.  In all
+    cases, the base bow shape is ancantoid with \(\xi = 0.8\),
+    \(\beta = 0.005\) and the perturbation is the same as in the central
+    panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
+    \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
+    inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
+    color and thickness, see key) and for different fractional phases
+    of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
+    (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
+    the spatial coordinates are normalized to the instantaneous
+    projected apex radius \(R_0'\) at each phase, so the apex does not
+    appear to move.}.
+  \label{fig:perturb-xy-prime}
+\end{figure*}
 
-Instability of bow \citep{Blondin:1998a}
-
-The bow shock models that we have considered so far have been
-steady-state: although material is moving throughout the bow, the
-pattern of its structure does not vary with time.  In this section, we
-consider small, time-varying perturbations to such a steady-state
-structure.  These may be due to periodic variations in the
-momentum-loss rate of one of the winds, or due to dynamical
-instabilities in the shocked shell.
+In this appendix, we present a highly idealized model for small,
+time-varying perturbations to a steady-state bow shock shape, such as
+those discussed in \S~5 of Paper~0.  These perturbations may be due to
+periodic variations in the momentum-loss rate of one of the winds, or
+due to dynamical instabilities in the shocked shell.
 
@@
 \(\theta = [0, \pi/2]\) at \(i = 0\) to
-\(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see
-equations~\eqref{Q-eq:thetapar} and \eqref{Q-eq:th90} of \PaperI{}.
-The difference \(\theta_{90} - \theta_0\) is always a declining function of
-\(|i|\), so the oscillations of the tangent line become increasingly
-stretched out as the inclination increases.  This effect can be seen
-in Figure~\ref{fig:perturb-xy-prime}, which shows an example of the
-variation in projected perturbed shape with inclination angle for 3
-different phases, this time for an ancantoid base shape and the
-\(N = 2.0\) perturbation shown in Figure~\ref{fig:perturb-shapes}b.
-The most marked changes with phase are seen for low inclinations,
-whereas the changes are smaller, although still noticeable, for
-\(|i| \ge 45^\circ\). If \(A N\) exceeds about 0.5, then the local curvature
-of the perturbations is so extreme that multiple tangent lines exist
-at intermediate inclinations, which produces the appearance of
-additional incomplete bright arcs inside the main arc of the bow.
+\(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see equations~(18) and (21)
+of Paper~0.  The difference \(\theta_{90} - \theta_0\) is always a declining
+function of \(|i|\), so the oscillations of the tangent line become
+increasingly stretched out as the inclination increases.  This effect
+can be seen in Figure~\ref{fig:perturb-xy-prime}, which shows an
+example of the variation in projected perturbed shape with inclination
+angle for 3 different phases, this time for an ancantoid base shape
+and the \(N = 2.0\) perturbation shown in
+Figure~\ref{fig:perturb-shapes}b.  The most marked changes with phase
+are seen for low inclinations, whereas the changes are smaller,
+although still noticeable, for \(|i| \ge 45^\circ\). If \(A N\) exceeds
+about 0.5, then the local curvature of the perturbations is so extreme
+that multiple tangent lines exist at intermediate inclinations, which
+produces the appearance of additional incomplete bright arcs inside
+the main arc of the bow.
 

### 2019-05-07 papers/Papers1234/sec-standing-wave.tex
Finish discussion of OB star shapes for Paper IV

@@
   linear space.}  These values can be compared with the predictions of
-the thin-shell Wilkinoid model \citep{Wilkin:1996a}, which are
+the thin-shell wilkinoid model \citep{Wilkin:1996a}, which are
 \(\Pi = 1.67\), \(\Lambda = 1.73\) when the bow shock axis lies in the plane
@@
 inclination increases, generally with \(\Lambda \ge \Pi\) (Fig.~20 of Paper~0).
-This might plausibly explain the spur towards higher \(\Lambda\) seen in the
-empirical distribution ()
+This might plausibly explain the vertical spur towards higher
+\(\Lambda\) seen in the empirical distribution (\S~\ref{sec:ob-shapes}). A
+different behavior is shown by bow shocks with very flat apex regions,
+such as the MHD simulation from \citet{Meyer:2017a} that is analyzed
+in the \S~6 of Paper~0.  This shows a high planitude \(\Pi\) when the
+orientation is exactly edge-on, but \(\Pi\) decreases sharply along a
+roughly horizontal track as the inclination \(\abs{i}\) increases
+(Fig.~25 of Paper~0).  This is similar to the principal axis of
+variation of the observed shapes (e.g.,
+Fig.~\ref{fig:mipsgal-shapes}a).
+
+If such variations in orientation do make a significant contribution
+to the observed distribution of bow shock shapes in the
+\(\Pi\)-\(\Lambda\) plane, then various predictions follow, which might be
+observationally tested.  High-planitude sources with \(\Pi > 3\) would
+be expected to have low inclinations, \(\abs{i} < \ang{30}\), whereas
+high-alatude sources with \(\Lambda > 2\) would be expected to have high
+inclinations, \(\abs{i} > \ang{45}\).  Unfortunately, determination of
+the inclination for individual sources requires high resolution
+spectroscopy of emission lines in order to map the kinematics of the
+flow in the bow shock shell \citep[e.g.,][]{Henney:2013a}.  This is
+not currently available for the majority of the MIPSGAL sources, which
+are detected only by their dust continuum emission.  A further
+prediction for the high-alatude sources is that the environmental flow
+should be divergent rather than plane-parallel, in order to give a
+cantoid shape instead of a wilkinoid.  This would tend to favor
+``weather-vane'' cases, where the interstellar medium is flowing past
+the star, and disfavor ``runaway'' cases, where the star is moving
+through a static medium.  However, in \S~\ref{sec:corr-shape} we found
+no significant difference in the shape distributions as a function of
+the bow shock environment.  Figure~\ref{fig:mipsgal-uncorrelated}a
+shows that the alatudes of sources that are facing \hii{} regions or
+\SI{8}{\um} bright-rimmed clouds (and therefore might be expected to
+be immersed in a champagne flow) are no higher than sources that are
+isolated.
 
 \begin{figure}
-  \centering
+  (a)\\
   \includegraphics[width=\linewidth]
   {figs/wave-R90-vs-Rc-A020-N10}
+  (b)\\
   \includegraphics[width=\linewidth]
   {figs/wave-R90-vs-Rc-A010-N20}
-  \caption{Diagnostic diagram for perturbed shapes}
+  \caption{Diagnostic diagram for perturbed shapes from standing wave
+    oscillations.  Each model is characterized by a base shape
+    (colored symbols, as described in key) and an amplitude, \(A\),
+    and wavenumber, \(N\), of the oscillation: (a)~breathing mode with
+    \(N = 1\), \(A = 0.2\); (b)~curling mode with \(N = 2\),
+    \(A = 0.1\) (see Fig.~\ref{fig:perturb-shapes} for the
+    phase-dependent intrinsic shapes).  The plotted points show the
+    varying planitude and alatude of the projected bow shock shapes
+    with uniform sampling over an entire period of the oscillation and
+    for varying inclinations (sampled according to an isotropic
+    distribution of orientations).  Each individual point is plotted
+    with a low opacity so that the crowding of points in certain
+    regions of the plane can be appreciated.}
   \label{fig:perturb-Rc-R90}
 \end{figure}
+
+An alternative explanation for the variety of observed bow shock
+shapes is that they are due to time-dependent perturbations to an
+underlying base shape.  For instance, multiple studies have shown that
+stellar bow shock shells can be unstable \citep{Dgani:1996a,
+  Dgani:1996b, Blondin:1998a, Comeron:1998a, Meyer:2014a}, leading to
+large amplitude oscillations in the shell shape.  The oscillations are
+found to be most vigorous when the post shock cooling is highly
+efficient, allowing the formation of a thin shell (see Paper~I).  Even
+in cases where the shell is stable, oscillations may be driven by
+periodic variations in the stellar wind mass-loss rate or velocity, or
+by inhomogeneities in the ambient stream.  Rather than using a
+particular dynamical model of these oscillations, we instead crudely
+simulate their effect by assuming a constant amplitude standing wave
+perturbation to the base shape, as described in
+Appendix~\ref{sec:perturbed-bows}.  Example results are shown in
+Figure~\ref{fig:perturb-Rc-R90} for an ensemble of bows with different
+orientations and phases of oscillation, considering three different
+underlying base shapes.  It can be seen that modest amplitudes of 10
+to 20\% can give rise to a distribution in \(\Pi\) and \(\Lambda\) similar to
+that observed for the MIPSGAL sources when the oscillation wavelength
+is of same order as the bow shock size.
+
+An attractive feature of the oscillation hypothesis is that it
+naturally explains why we find little correlation between the bow
+shock shape and other source parameters (\S~\ref{sec:corr-shape}).
+The one significant correlation that we do find is that the alatude
+distribution is broader for bow shocks with larger angular sizes.
+This might be explained if the relative amplitude of oscillations were
+higher for sources with more powerful winds.  However, in that case it
+is hard to understand why no such variation is seen in the width of
+the planitude distribution.
+
+We now address the difference in shape distribution between the
+different classes of source.  Compared with the OB star bow shocks,
+the cool star sample from \citet{Cox:2012a} shows a significantly
+smaller alatude of \(\Lambda = 1.41 \pm 0.03\) (see
+Fig.~\ref{fig:herschel-compare-mipsgal}).\footnote{Although the
+  planitude also appears to be slightly smaller, this is not very
+  statistically significant due to the small number of cool star
+  sources and the large width of the OB star planitude distribution.}
+Such a closed shape for the wings is inconsistent with the wilkinoid
+value of \(\Lambda = \text{\numrange{1.63}{1.73}}\), which is surprising
+given that the emission shells in these sources are relatively narrow
+(Figs.~\ref{fig:herschel-arc-fits}
+and~\ref{fig:herschel-arc-fits-poor}), so one might have thought that
+the thin-shell approximation of \citet{Wilkin:1996a} would be
+\emph{more} appropriate than for the OB stars, but this is clearly not
+the case.  One possible explanation for this
 

### 2019-05-09 papers/Papers1234/sec-quadrics-observations.tex
Finish cool star discussion and make headway on Orion sources

@@
   \centering
-  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
-  \caption[]{Shape comparison between Orion Nebula arcs and OB star
-    bow shocks.  Other details of the plots are as in
+  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion-R0-D}
+  \caption[]{Shape comparison between Orion Nebula arcs (green) and OB
+    star bow shocks (purple).  Other details of the plots are as in
     Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
     except that a larger KDE smoothing bandwidth of
-    \(0.06 \times 0.045\) is used for the Orion Nebula sample.}
+    \(0.06 \times 0.045\) is used for the Orion Nebula sample.  The colors
+    of the individual points for the Orion Nebula sample show the
+    size-to-distance ratio, \(R_0/D\), on a logarithmic scale from
+    \(R_0/D = 0.002\) (dark green) to \(R_0/D = 0.018\) (light
+    green).}
   \label{fig:ll-compare-mipsgal}
@@
 
+Uniquely among the three bow shock datasets, for the Orion Nebula arcs
+we know the source of the external flow.  This is not the stellar wind
+from the high-mass stars at the center of the cluster, which has
+insufficient momentum at the position of the arcs \citep{Bally:2000a},
+nor is it due to stars' own motions, since the space velocities of all
+these sources are very low, conforming to the velocity dispersion
+\(\sigma_{\text{1D}} \approx \SI{2}{km.s^{-1}}\) of the Orion Nebular Cluster
+\citep{Dzib:2017a, Kim:2018b}.  Instead it is due to the transonic
+champagne flow of photoionized gas away from the core of the nebula
+\citep{Zuckerman:1973a, Henney:2005a}, which has its density peak in
+the Orion~S region \citep{Weilbacher:2015a}, located roughly \(30''\)
+SW of the dominant Trapezium star \thC.  The bow shock sources are
+located at much larger distances of \(D = 90''\) to \(700''\) from
+\thC, so that the ratio \(R_0/D\) can be used as a proxy for the local
+divergence of the champagne flow on the scale of the bow shock (notice
+that the symmetry axes of the bow shocks in Fig.~\ref{fig:ll-arcs} are
+always roughly parallel to the direction to \thC{}).  This is
+indicated by the color of the points in
+Figure~\ref{fig:ll-compare-mipsgal}, with lighter colors corresponding
+to a larger \(R_0/D\) and hence a more divergent external flow.  It
+can be seen that there is some correlation between the bow shock
+shapes and \(R_0/D\): the source with the largest \(\Pi\), 109--246, also
+has the largest \(R_0/D\), while the four sources with low \(\Pi\) and
+\(\Lambda\) all have low \(R_0/D\).  However, the correlation is far from
+perfect, with a Pearson correlation coefficient of only \(r = 0.47\)
+between \(\Pi\) and \(R_0/D\).
+
 %Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.

### 2019-05-09 papers/Papers1234/sec-standing-wave.tex
Finish cool star discussion and make headway on Orion sources

@@
 naturally explains why we find little correlation between the bow
-shock shape and other source parameters (\S~\ref{sec:corr-shape}).
+shock shape and other source parameters (\S~\ref{sec:corr-shape}),
+since the instantaneous shape at any instant is largely a matter of
+chance rather than being due to any intrinsic property of the source.
 The one significant correlation that we do find is that the alatude
@@
 This might be explained if the relative amplitude of oscillations were
-higher for sources with more powerful winds.  However, in that case it
-is hard to understand why no such variation is seen in the width of
-the planitude distribution.
+higher for sources with more powerful winds. \citet{Meyer:2016a} in
+their Fig.~2 plot the ``axis ratio'' (which is our \(\Lambda^{-1}\)) as a
+function of apex distance for a large set of hydrodynamic bow shock
+simulations.  They find the most unstable bow shocks (with the largest
+spread in \(\Lambda\)) to be those associated with the highest mass stars in
+a relatively dense medium, which have apex distances of
+\SIrange{0.3}{1}{pc}.  This corresponds to \(R_0 > 15''\) for
+distances less than \SI{4}{kpc}, which is larger than the median
+angular size for the MIPSGAL sources, making this a plausible explanation for our statistical result.
+% However, in that case it
+% is hard to understand why no such variation is seen in the width of
+% the planitude distribution.
 
@@
 different classes of source.  Compared with the OB star bow shocks,
-the cool star sample from \citet{Cox:2012a} shows a significantly
-smaller alatude of \(\Lambda = 1.41 \pm 0.03\) (see
+the cool star sample from \citet{Cox:2012a}\footnote{Three of these
+  sources are high-mass red supergiant (RSG) stars, while the
+  remaining 13 are intermediate-mass asymptotic giant branch (AGB)
+  stars.} shows a significantly smaller alatude of
+\(\Lambda = 1.41 \pm 0.03\) (see
 Fig.~\ref{fig:herschel-compare-mipsgal}).\footnote{Although the
@@
 \emph{more} appropriate than for the OB stars, but this is clearly not
-the case.  One possible explanation for this
+the case.  One possible explanation for this might be that the bow
+shocks have not had time to reach a steady-state configuration, as was
+suggested by \citet{Mohamed:2012a} for the case of \(\alpha\)~Ori.  The
+dynamical timescales, \(R_0 / V\wind\), for the cool star bow shocks
+are of order \SI{e4}{yr} and numerical simulations \citetext{e.g.,
+  Fig.~11 of \citealp{Mohamed:2012a} and Fig.~2 of
+  \citealp{van-Marle:2014a}} show that the bow shock wings take of
+order \SIrange{3e4}{e5}{yr} to fully unfold.  However, this is still
+short compared with typical RSG and AGB lifetimes, so while it might
+apply to a single source it does not work as an explanation for an
+entire class of sources, especially given that the alatude and
+planitude distributions for these sources are so narrow
+(Fig.~\ref{fig:herschel-compare-mipsgal}).  A more promising
+explanation is that the shape difference reflects a different origin
+for the infrared-emitting dust.  In hot stars, the stellar wind is
+dust-free, so the only dust shell comes from the interstellar medium
+and lies outside the astropause (contact discontinuity).  In cool
+stars, the stellar wind is dusty, which could give rise to significant
+infrared emission from near the stellar wind's termination shock.
+This is certainly the case for at least one of our cool star sources,
+the C-AGB star CW~Leo (IRC+10216), where ultraviolet GALEX
+observations \citep{Sahai:2010a} clearly show \emph{both} the outer
+shock and the wind termination shock, and comparison with the Herschel
+images demonstrate that the infrared dust emission is associated with
+the latter.
+
+% However, in order for the dust emission arc to be less open than the
+% wilkinoid case, one would require the shocked stellar wind shell to be
+% relatively thick, which means that either the Mach number must be low
+% or the post-shock cooling must be inefficient (see Paper~I).  In some
+% red supergiants, the stellar wind is heated and photoionized by the
+% ambient radiation field before reaching the bow shock
+% \citep{Morris:1983a, Mackey:2014a}, which would tend to produce a low
+% Mach number shock.
+
+In the case of the Orion Nebula bow shocks
+(\S~\ref{sec:stat-emiss-line}), we have the opposite situation, where
+the alatude and planitude are both significantly larger on average
+than for the OB star sources (Fig.~\ref{fig:ll-compare-mipsgal}).
+
+None of these sources have high velocities, but instead follow the
 

### 2019-05-09 papers/Papers1234/app-p-values.tex
Finish discussion for Paper IV - now just summary to go!

@@
     cases, the base bow shape is ancantoid with \(\xi = 0.8\),
-    \(\beta = 0.005\) and the perturbation is the same as in the central
-    panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
-    \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
+    \(\beta = 0.005\) and the perturbation is the curling mode shown in
+    the central panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
+    \(A = 0.1\) and wave number \(N = 2.0\). Results are shown for
     inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
@@
     of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
-    (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
-    the spatial coordinates are normalized to the instantaneous
-    projected apex radius \(R_0'\) at each phase, so the apex does not
-    appear to move.}.
+    (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes}, the
+    spatial coordinates are normalized to the instantaneous projected
+    apex radius \(R_0'\) at each phase, so the apex does not appear to
+    move.}.
   \label{fig:perturb-xy-prime}
@@
 \(\Delta(\theta, t)\) is a standing wave of constant amplitude \(A\), which is
-periodic in \(\theta\), with wave number \(N\).  In cylindrical symmetry
+periodic in \(\theta\), with wave number \(N\).  We assume that the
+oscillation occurs simultaneously and coherently at all azimuths, so
+that cylindrical symmetry is maintained.  This implies that
 \(\Delta(\theta, t)\) must be even in \(\theta\), so can be expressed as
@@
 Figure~\ref{fig:perturb-shapes}b.  The most marked changes with phase
-are seen for low inclinations, whereas the changes are smaller,
-although still noticeable, for \(|i| \ge 45^\circ\). If \(A N\) exceeds
-about 0.5, then the local curvature of the perturbations is so extreme
-that multiple tangent lines exist at intermediate inclinations, which
-produces the appearance of additional incomplete bright arcs inside
-the main arc of the bow.
+are seen for low inclinations (light colored lines), whereas the
+changes are smaller, although still noticeable, for
+\(|i| \ge 45^\circ\). If \(A N\) exceeds about 0.5, then the local curvature
+of the perturbations is so extreme that multiple tangent lines exist
+at intermediate inclinations, which produces the appearance of
+additional incomplete bright arcs inside the main arc of the bow.
 

### 2019-05-09 papers/Papers1234/sec-quadrics-observations.tex
Finish discussion for Paper IV - now just summary to go!

@@
     The regions corresponding to different classes of cuadrics are
-    shown by shading (see \S~\ref{sec:conic}): oblate spheroids (light
+    shown by shading (see \S~4 of Paper~0): oblate spheroids (light
     gray background); prolate spheroids (darker gray background);

### 2019-05-09 papers/Papers1234/sec-standing-wave.tex
Finish discussion for Paper IV - now just summary to go!

@@
 Appendix~\ref{sec:perturbed-bows}.  Example results are shown in
-Figure~\ref{fig:perturb-Rc-R90} for an ensemble of bows with different
-orientations and phases of oscillation, considering three different
-underlying base shapes.  It can be seen that modest amplitudes of 10
-to 20\% can give rise to a distribution in \(\Pi\) and \(\Lambda\) similar to
-that observed for the MIPSGAL sources when the oscillation wavelength
-is of same order as the bow shock size.
+Figure~\ref{fig:perturb-Rc-R90} for an ensemble of bow shocks with
+different orientations and phases of oscillation, considering three
+different underlying base shapes.  It can be seen that modest
+amplitudes of 10 to 20\% can give rise to a distribution in \(\Pi\) and
+\(\Lambda\) similar to that observed for the MIPSGAL sources when the
+oscillation wavelength is of the same order as the bow shock size.
 
@@
 the alatude and planitude are both significantly larger on average
-than for the OB star sources (Fig.~\ref{fig:ll-compare-mipsgal}).
+than for the OB star sources (Fig.~\ref{fig:ll-compare-mipsgal}).  On
+the face of it, this is surprising because there are two differences
+between the source classes that would tend to work in the other
+direction.  First, many of the Orion sources are proplyds, or
+externally illuminated photoevaporating disks \citep{ODell:2008b}, in
+which the inner wind is not isotropic but instead is mildly
+concentrated towards the symmetry axis \citep{Garcia-Arredondo:2001a},
+so that simple models predict an \textit{ancantoid} shape
+\citep[\S~5]{Tarango-Yong:2018a} that is less open than for an
+isotropic wind.  Second, as was the case with the cool star sources,
+both the shocked inner wind and the shocked outer stream are expected
+to contribute to the emission arcs.  Indeed, in several of the sources
+of Figure~\ref{fig:ll-arcs} (LL~3, 116--3101, 266-558, 308-3036, and
+LL~5), a two-component emission structure is apparent.  In the case of
+the cool star bow shocks, we invoked this as a possible explanation of
+their \emph{low} planitude and alatude (see previous paragraph), so
+some stronger countervailing factor is necessary in order to explain
+why the opposite is seen in the Orion Nebula bow shocks.
 
-None of these sources have high velocities, but instead follow the
+Four possible origins for this countervailing factor suggest
+themselves: (i)~the external flow may be more divergent in the Orion
+sources; (ii)~the Mach number of the external flow may be
+systematically lower; (iii)~the fact that the arcs are observed in
+recombination line emission instead of dust continuum may cause
+different observational biases; (iv)~the shapes may be influenced by
+collimated jet outflows from the young stars.  We now address each of
+these in turn.
+
+In case~(i) one would expect \(\Pi\) and \(\Lambda\) to be positively
+correlated with \(R_0/D\), where \(R_0\) is the bow shock size
+(star--apex separation) and \(D\) is the distance from the center of
+divergence of the external flow.  In \S~\ref{sec:stat-emiss-line} we
+found that these are indeed correlated, but only weakly.  A more
+serious objection to this idea is that according to hypersonic
+thin-shell models \citep{Canto:1996} the momentum ratio parameter
+\(\beta\) must be relatively large in order to give significantly open bow
+shock shapes.  From Figure~20 of Paper~0 we see that
+\(\beta > \num{e-3}\) is required in order to give
+\(\Pi, \Lambda > 2\).  However, for small \(\beta\) one has
+\(\beta \approx (R_0/D)^2\), which yields \(\beta = \num{4e-6}\) to \num{3e-4} for
+our sources, so that divergence ought to have little effect on the
+shapes.
+
+Case~(ii) arises from the fact that, if the hypersonic assumption is
+relaxed, then the opening angle between the outer bow shock and the
+contact discontinuity in the wings becomes increasingly large as the
+Mach number, \(\M\), drops towards unity.  This is a consequence of
+the \textit{shock polar} relation for oblique shocks \citep[\S\S~92
+and 113]{Landau:1987a} and applies to both the radiative and
+non-radiative case.  It will tend to produce more open shapes, at
+least in the case that the emission is dominated by the outer shell.
+At the same time, the relative thickness of the shell, \(h/R_0\), is
+predicted to increase as \(\M\) decreases \citetext{e.g., eq~[35] of
+  Paper~I}.  We have therefore measured \(h/R_0\) for the Orion
+sources, finding values ranging from \numrange{0.3}{0.8} with median
+of \num{0.5}.  We have not measured \(h/R_0\) for the full MIPSGAL
+sample, but Figure~11 of Paper~III gives the values for the sub-sample
+of OB bow shocks studied by \citep{Kobulnicky:2018a}.  The median
+value is 0.2, implying thinner shells than in the Orion Nebula bow
+shocks, which lends support to the idea that the Mach number may be
+lower in the latter.  However, among the Orion sources we find that
+\(h/R_0\) is completely uncorrelated with either \(\Pi\) or
+\(\Lambda\) (\(r = 0.02\) and \(-0.05\), respectively).
+
+Case~(iii) attempts to explain the difference in shapes as a result of
+an ``optical illusion'' whereby the OB star bow shocks are in reality
+more open than they appear. The hydrogen recombination line surface
+brightness from an isothermal shell is proportional to the emission
+measure (line of sight integral of the product of proton and electron
+densities), whereas the mid-infrared surface brightness is not simply
+proportional to the dust column density, since it results from the
+reprocessing of stellar radiation.  For typical bow shock grain
+temperatures \citetext{\(T = 50\) to \SI{150}{K},
+  \citealp{Kobulnicky:2017a}} the \SI{24}{\um} band used for the OB
+star sample lies on the short wavelength Wien side of the dust
+emission spectrum, which gives a very steep radial dependence of the
+emissivity.  \citet{Acreman:2016a} calculate synthetic emission maps
+from hydrodynamical simulations and show that, even for a relatively
+thin bow shock shell, the emission arc seen in H\(\alpha\) tends to be more
+open than the arc seen in the mid-infrared (see their Fig.~3).  The
+effect should be even larger for thicker shells, as demonstrated by
+\citet{Mackey:2016a}, who simulate the \emph{subsonic} motion of an O
+star through its \hii{} region and show that this can give rise to an
+\emph{apparent} bow shock at \SI{24}{\um} even when there is no
+corresponding dense shell at all.
+
+Finally, case~(iv) arises from the observation that several of the
+Orion sources possess high velocity (\(> \SI{100}{km.s^{-1}}\))
+collimated jets \citep{Bally:2006a}, which produce strings of emission
+knots that partially overlap the wings of the bow shock.  In the case
+of 109--246, LL~1, LL~4, LL~5, and LL~6, the projected jet axis is
+roughly perpendicular to the projected bow shock axis, and two of
+these (109--246 and LL~6) have the most extreme high values of \(\Pi\)
+and \(\Lambda\).  There are several other Orion Nebula bow shock sources
+with perpendicular jets (LL~2, 203--3039, 261--3018, 344--3020, and
+LL~7), which we omitted from our sample because of difficulty in
+measuring \(\Lambda\), but the majority also have large planitudes
+\(\Pi > 5\). Only one source, 4468--605, has a jet oriented parallel to
+the bow shock axis, and this has the smallest \(\Pi\) and third-smallest
+\(\Lambda\) of the sample.  The circumstantial evidence thus points towards
+the jets playing some role in shaping the bow shocks when they are
+oriented perpendicular to the axis, even though we took care when
+tracing the bow shock ridges to avoid any region with superimposed jet
+knots.  This would break the cylindrical symmetry of the bow shock,
+which should have a kinematic signature.  However, in the only two
+sources that have been studied kinematically \citep{Henney:2013a}, the
+bow shock shell does not show any sign of the red/blue asymmetry that
+is seen in the jet knots, which argues against any such an
+association.
 

### 2019-05-10 papers/Papers1234/sec-obs-conclusions.tex
Finish discussion for Paper IV - now just summary to go!
Finish the discussion and summary for Paper IV

--- 2017-10-13 papers/Paper1/sec-obs-conclusions.tex
@@
-\section{Conclusions}
+\section{Summary}
 \label{sec:conclusion}
+
+We have presented a statistical study of the shapes of three different
+classes of stellar bow shocks, as characterized by their flatness of
+apex (planitude, \(\Pi\)) and openness of wings (alatude,
+\(\Lambda\)), following the terminology of
+\citet[Paper~0]{Tarango-Yong:2018a}.  Our principal findings are as
+follows:
+\begin{enumerate}[1.]
+\item Bow shocks driven by hot OB stars, from the mid-infrared catalog
+  of \citet{Kobulnicky:2016a}, have an average shape
+  \((\Pi, \Lambda) \approx (1.6, 1.7)\) that is consistent with predictions of the
+  \citet{Wilkin:1996a} analytic model, but the dispersion in observed
+  shapes \((\sigma_\Pi, \sigma_\Lambda) \approx (0.9, 0.3)\) is many times larger than
+  predicted by that model.
+\item The bow shock shapes show little correlation with other
+  parameters of the source, such as stellar magnitude, Galactic
+  latitude or longitude, extinction, or type of environment (cluster
+  versus isolated).  The only exception is that the dispersion in
+  alatude is higher for bow shocks of larger angular size.
+\item A possible explanation for the previous results is that the
+  variation in shapes is caused by time dependent oscillations in the
+  bow shock surface, with relative amplitude of 10 to 20\% and
+  wavelength of order the bow shock size.  The oscillations may either
+  be due to dynamic instabilities in the bow shock shell or be driven
+  by temporal variations in the stellar wind.  If the oscillations
+  were more vigorous for stars with more powerful winds, it could
+  explain the correlation with angular size.
+\item Bow shocks driven by cool luminous stars (red supergiants and
+  asymptotic giant branch stars), from the catalog of
+  \citep{Cox:2012a}, have an average shape
+  \((\Pi, \Lambda) \approx (1.5, 1.4)\), which has a significantly smaller alatude
+  than the OB star sources, and which is not consistent with the
+  \citet{Wilkin:1996a} model.  We suggest that this may be due to
+  their dust emission being dominated by shocked stellar wind
+  material, instead of shocked ambient material as is the case with
+  the OB stars.
+\item Bow shocks driven by proplyds and other young stars in the outer
+  regions of the Orion Nebula, from the catalogs of
+  \citet{Bally:2006a} and \citet{Gutierrez-Soto:2015a}, have an
+  average shape of \((\Pi, \Lambda) \approx (2.7, 2.4)\), with a significant tail up
+  to \((\Pi, \Lambda) \approx (7, 4)\).  A minority of these sources
+  (\(\approx 20\%\)) have shapes similar to the OB star bow shocks, but the
+  remainder have much flatter apexes and more open wings.  We suggest
+  several possible mechanisms to explain this difference: divergent
+  ambient flow; low Mach number; observational biases; influence of
+  collimated jets, but the available evidence for and against each of
+  these is mixed.
+\end{enumerate}
+
+% Difference in SEDs between FIR and MIR samples?  \citet{Meyer:2016a}
+% say emission peaks at 3--50 micron for O star bow shocks.
+
+% Al other things being equal, larger bows will be at higher
+% inclinations (we should estimate how much variation in size we should
+% get due to inclination -- it will be more for flatter bows).  Higher
+% inclinations means less variation from the standing wave oscillations,
+% which goes against our result that larger bows have greater dispersion
+% in \(\Lambda'\).  Although the standing waves mainly give dispersion in
+% \(\Pi'\) anyhow.
+
+% \citet{Meyer:2014a} say that in cool stars the dust emission comes
+% from the shocked inner wind, rather than from near the contact
+% discontinuity for hot stars.  This could explain the difference in
+% shape between the Herschel and Spitzer samples.
+
+% How different regions of the \(\Pi\)--\(\Lambda\) plane are populated.
+% Bottom-right quadrant hard to get to (except for standing wave
+% oscillations), but may be due to finite shell thickness, which (for
+% low Mach number) will be more apparent in the wings, which might
+% decrease \(\Lambda\) more than \(\Pi\).  Fact that thin-shell solutions should
+% trace the contact discontinuity, but in some cases it may be only the
+% inner or the outer shell that is visible.
+
+% Justification for standing waves: Fig.~3 of \citet{Meyer:2016a} shows
+% a time sequence of thin-shell instability, which looks a bit like a
+% standing wave. But much larger amplitude than we are considering.
+
+% Deviations from axisymmetry as an alternative to oscillations.
+
+% \subsection{The case of inside-out bows}
+% \label{sec:case-inside-out}
+
+% So far, we have considered the case where the inner source dominates
+% the radiation, while dust is present only in the outer stream, which
+% applies to hot stars interacting with the ISM.  However, in the case
+% of cool stars, the inner wind will also be dusty.  Examples are the
+% red supergiant (RSG) phase of high-mass evolution, or the asymptotic
+% giant branch (AGB) stage of low/intermediate-mass evolution.  In both
+% these cases, it is still the inner source that provides the radiation
+% field.  However, not all winds are radiatively driven and in those
+% cases it is conceivable that it is the outer source that dominates the
+% radiation field.  An example is the case of photoevaporating
+% protoplanetary disks (proplyds) in the Orion Nebula and other \hii{}
+% regions \citep{ODell:1994a}.  In the proplyds, the inner wind is a
+% thermally driven photoevaporation flow \citep{Henney:1998b, Henney:1999a},
+% while the outer stream is the stellar wind from an O~star
+% \citep{Garcia-Arredondo:2001a}.
 

### 2019-05-10 papers/Papers1234/sec-standing-wave.tex
Finish the discussion and summary for Paper IV

@@
   {figs/wave-R90-vs-Rc-A010-N20}
+  \vspace*{-\baselineskip}
   \caption{Diagnostic diagram for perturbed shapes from standing wave
@@
 and lies outside the astropause (contact discontinuity).  In cool
-stars, the stellar wind is dusty, which could give rise to significant
-infrared emission from near the stellar wind's termination shock.
-This is certainly the case for at least one of our cool star sources,
-the C-AGB star CW~Leo (IRC+10216), where ultraviolet GALEX
-observations \citep{Sahai:2010a} clearly show \emph{both} the outer
-shock and the wind termination shock, and comparison with the Herschel
-images demonstrate that the infrared dust emission is associated with
-the latter.
+stars, the stellar wind is also dusty, which could give rise to
+significant infrared emission from near the stellar wind's termination
+shock, as has been found from hydrodynamic simulations
+\citep{Meyer:2014b}.  This is certainly the case for at least one of
+our cool star sources, the C-AGB star CW~Leo (IRC+10216), where
+ultraviolet GALEX observations \citep{Sahai:2010a} clearly show
+\emph{both} the outer shock and the wind termination shock, and
+comparison with the Herschel images demonstrate that the infrared dust
+emission is associated with the latter.
 
@@
 the cool star bow shocks, we invoked this as a possible explanation of
-their \emph{low} planitude and alatude (see previous paragraph), so
+their \emph{low} alatude (see previous paragraph), so
 some stronger countervailing factor is necessary in order to explain
@@
 reprocessing of stellar radiation.  For typical bow shock grain
-temperatures \citetext{\(T = 50\) to \SI{150}{K},
+temperatures \citetext{\(T = 50\) to \SI{100}{K},
   \citealp{Kobulnicky:2017a}} the \SI{24}{\um} band used for the OB
@@
 effect should be even larger for thicker shells, as demonstrated by
-\citet{Mackey:2016a}, who simulate the \emph{subsonic} motion of an O
-star through its \hii{} region and show that this can give rise to an
+\citet{Mackey:2016a}, who simulate the subsonic motion of an O star
+through its \hii{} region and show that this can give rise to an
 \emph{apparent} bow shock at \SI{24}{\um} even when there is no

### 2019-05-10 papers/Papers1234/app-p-values.tex
New version of abstract for Paper IV

@@
 
-Results from all the statistical tests discussed in
-\S~\ref{sec:corr-shape} are given in Table~\ref{tab:big-p}.
+Results from all the statistical tests of the shape distributions
+discussed in \S~\ref{sec:corr-shape} are given in
+Table~\ref{tab:big-p}.  The \(p\)-values are the probability of
+finding a difference between two populations at least as large as what
+is observed \emph{given} that there is no difference in the underlying
+distribution from which the two populations are drawn (that is, given
+that the null hypothesis is true).  Conventionally, the null
+hypothesis is rejected at a certain significance threshold \(\alpha\) when
+\(p < \alpha\).  Since we are blindly testing many different hypotheses at
+once, the commonly used \(\alpha = 0.05\) threshold is too lenient.  In
+Figure~\ref{fig:histo-p-values} we analyse the frequency distribution
+of \(p\) from all our tests \citep[see][]{Head:2015a}, finding a
+systematic excess over a uniform distribution only for \(p < 0.01\).
+We therefore take \(\alpha = 0.003\) as the optimum threshold in order to
+balance the risks of false positives and false negatives. A false
+positive is the erroneous rejection of the null hypothesis (the
+spurious detection of a correlation that is not really there), while a
+false negative is failing to detect a true correlation.
 
-% \begin{table}
-%   \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
-%   \label{tab:type-I}
-%   \centering
-%   \begin{tabular}{lrr} \toprule
-%     Correlation & \(p\) & \(\alpha\) \\
-%     \midrule
-%     \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
-%     \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
-%     \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
-%     \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
-%     \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
-%     \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
-%     \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
-%     \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
-%     \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
-%     \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
-%     \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
-%     \midrule
-%     \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
-%     \(R_c\) vs Facing & 0.71 & 1 \\
-%     \(R_c\) vs H II & 0.50 & 1 \\
-%     \(R_{90}\) vs Facing & 0.60 & 1 \\
-%     \(R_{90}\) vs H II & 0.52 & 1 \\
-%     \(R_c\) vs Multiple & 1.00 & 1 \\
-%     \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
-%     \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
-%     \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
-%     \midrule
-%     \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
-%     \(R_c\) vs Herschel & 0.074 & 0.3437 \\
-%     \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
-%     \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
-%     \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
-%     \bottomrule
-%   \end{tabular}
-% \end{table}
+% However, what we really want to
+% know is something else: the probability that the null hypothesis is
+% true, \emph{given} the observations.  That is, the probability,
+% \(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
+%   error rate}.  The common mistake of conflating these two definitions
+% is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
+% error of the transposed conditional'', as discussed in detail by
+% \citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
+% \(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
+% requires an estimate of the prior probability of the null hypothesis,
+% independent of the observations.  Alternatively, it is also possible
+% to find a lower bound on \(\alpha\) from a frequentist approach
+% \citep{Sellke:2001a}:
+% \begin{equation}
+%   \label{eq:type-I}
+%   \alpha(p) \ge \bigg[ 1 - \big(e\, p \ln p\big)^{-1} \bigg]^{-1}
+%   \quad \text{valid for } p < 1/e.
+% \end{equation}
+% This is the approach we adopt here, which also numerically coincides
+% with the Bayesian approach for the case where the prior probability of
+% the null hypothesis is 0.5.  The reason that this is only a lower
+% limit for \(\alpha\) is that if we have overwhelming a priori evidence that
+% the null hypothesis is true (for instance, from previous empirical
+% studies, or because it follows from a well-supported theory), then a
+% Bayesian calculation would give a much higher value of \(\alpha\) than
+% \eqref{eq:type-I} does.  In our case, however, we have no strong
+% reasons for favoring any of the null hypotheses, so it is reasonable
+% to assume \(\alpha\) is close to the lower limit given in \eqref{eq:type-I}.
 
-The \(p\)-values are the probability of finding a difference between
-two populations as large as (or larger than) what is observed,
-\emph{given} that there is no difference in the underlying
-distribution from which the two populations are drawn (that is, given
-that the null hypothesis is true).  However, what we really want to
-know is something else: the probability that the null hypothesis is
-true, \emph{given} the observations.  That is, the probability,
-\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
-  error rate}.  The common mistake of conflating these two definitions
-is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
-error of the transposed conditional'', as discussed in detail by
-\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
-\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
-requires an estimate of the prior probability of the null hypothesis,
-independent of the observations.  Alternatively, it is also possible
-to find a lower bound on \(\alpha\) from a frequentist approach
-\citep{Sellke:2001a}:
-\begin{equation}
-  \label{eq:type-I}
-  \alpha(p) \ge \bigg[ 1 - \big(e\, p \ln p\big)^{-1} \bigg]^{-1}
-  \quad \text{valid for } p < 1/e.
-\end{equation}
-This is the approach we adopt here, which also numerically coincides
-with the Bayesian approach for the case where the prior probability of
-the null hypothesis is 0.5.  The reason that this is only a lower
-limit for \(\alpha\) is that if we have overwhelming a priori evidence that
-the null hypothesis is true (for instance, from previous empirical
-studies, or because it follows from a well-supported theory), then a
-Bayesian calculation would give a much higher value of \(\alpha\) than
-\eqref{eq:type-I} does.  In our case, however, we have no strong
-reasons for favoring any of the null hypotheses, so it is reasonable
-to assume \(\alpha\) is close to the lower limit given in \eqref{eq:type-I}.
+% In order to choose a threshold \(p\)-value that counts as a
+% ``significant'' result, one then needs to balance the risks of false
+% positives against the risks of \textit{false negatives}.  The false
+% negative probability, \(\beta\), also known as \textit{Type II error
+%   rate}, is the probability of failing to reject an untrue null
+% hypothesis.  That is, in the context of this paper, it is the
+% probability of failing to detect a real difference between two
+% sub-samples, or a real correlation between two variables.  The
+% complementary probability, \(1 - \beta\), is known as the
+% \textit{statistical power} or sensitivity of the test.  The value of
+% \(\beta\) depends on three factors:
+% \begin{enumerate}[1.]
+% \item The \textit{effect size}, which is a measure of the magnitude of
+%   the difference in a dependent variable between two sub-samples, or
+%   the degree of correlation between two continuous variables.  For the
+%   two sub-sample case, it is common to use a standardised mean
+%   difference, such as Cohen's \(d\) statistic \citep{Cohen:1988a}:
+%   \(d = (\bar{X}_A - \bar{X}_B) / s\), where \(\bar{X}_A\),
+%   \(\bar{X}_B\) are the means of the dependent variable \(X\) for
+%   samples A and B, while \(s\) is the pooled standard deviation of
+%   \(X\).  For the case of two continuous variables, the Pearson linear
+%   correlation coefficient, \(r\), can be used.  In both cases, rules
+%   of thumb have been developed \citep{Ruscio:2008a} for classifying an
+%   effect as ``large'' (\(d > 0.8\), \(r > 0.4\)) or ``small''
+%   (\(d < 0.2\), \(r < 0.1\)).  Alternatively, non-parametric
+%   statistics can be used, such as the \(A\) measure of stochastic
+%   superiority \citep{Delaney:2002a}.
+% \end{enumerate}
 
-In order to choose a threshold \(p\)-value that counts as a
-``significant'' result, one then needs to balance the risks of false
-positives against the risks of \textit{false negatives}.  The false
-negative probability, \(\beta\), also known as \textit{Type II error
-  rate}, is the probability of failing to reject an untrue null
-hypothesis.  That is, in the context of this paper, it is the
-probability of failing to detect a real difference between two
-sub-samples, or a real correlation between two variables.  The
-complementary probability, \(1 - \beta\), is known as the
-\textit{statistical power} or sensitivity of the test.  The value of
-\(\beta\) depends on three factors:
-\begin{enumerate}[1.]
-\item The \textit{effect size}, which is a measure of the magnitude of
-  the difference in a dependent variable between two sub-samples, or
-  the degree of correlation between two continuous variables.  For the
-  two sub-sample case, it is common to use a standardised mean
-  difference, such as Cohen's \(d\) statistic \citep{Cohen:1988a}:
-  \(d = (\bar{X}_A - \bar{X}_B) / s\), where \(\bar{X}_A\),
-  \(\bar{X}_B\) are the means of the dependent variable \(X\) for
-  samples A and B, while \(s\) is the pooled standard deviation of
-  \(X\).  For the case of two continuous variables, the Pearson linear
-  correlation coefficient, \(r\), can be used.  In both cases, rules
-  of thumb have been developed \citep{Ruscio:2008a} for classifying an
-  effect as ``large'' (\(d > 0.8\), \(r > 0.4\)) or ``small''
-  (\(d < 0.2\), \(r < 0.1\)).  Alternatively, non-parametric
-  statistics can be used, such as the \(A\) measure of stochastic
-  superiority \citep{Delaney:2002a}.
-\end{enumerate}
+% Obviously, this depends on the \textit{effect size}, which is the
 
-Obviously, this depends on the \textit{effect size}, which is the
-
-All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).
+% All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).
 It is therefore important to guard against the ``multiple comparisons problem'', whereby seemingly significant correlations are found where none really exist, simply by virtue of the large number of tests that were carried out.
 
-Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.
+% Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.
 
-The p-curve \citep{Head:2015a}
+% The p-curve \citep{Head:2015a}
 
@@
 
-\section{Perturbed bows}
+\section{Perturbed bow shocks}
 \label{sec:perturbed-bows}

### 2019-05-10 papers/Papers1234/obs-bowshocks.tex
Redo the stats table, and make it portrait orientation
Switch to Kuiper test instead of K-S
New version of abstract for Paper IV

@@
 \title[Bow shocks, bow waves, and dust waves. IV.]{Bow shocks, bow
-  waves, and dust waves. IV. Bow shape statistics}
+  waves, and dust waves. IV. Shell shape statistics}
 
@@
 \begin{abstract}
-  Stellar bow shocks are the result of the supersonic interaction
-  between a stellar wind and its environment.  Some of these are
-  "runaways": high-velocity stars that have been ejected from a star
-  cluster.  Others are "weather vanes", where it is the local
-  interstellar medium itself that is moving, perhaps as the result of
-  a champagne flow of ionized gas from a nearby \hii{} region.
-  We recently proposed a new two-dimensional classification scheme for
-  the shape of such bow shocks, which we here apply to three very
-  different observational datasets: (1)~mid-infrared arcs
-  around hot main-sequence stars (\(N = 227\)); (2)~far-infrared arcs
-  around luminous cool stars (\(N = 16\)); and (3)~emission-line arcs
-  around proplyds and other young stars in the Orion Nebula
-  (\(N = 18\)).  We find significant differences between the three
-  datasets: cool star bow shocks have markedly more closed wings than
-  hot star bow shocks, while differences in the shape of the apex
-  region are only marginally significant.  The Orion Nebula arcs, on
-  the other hand, have both significantly more open wings and
-  significantly flatter apexes than the hot star bow shocks.  We
-  discuss the implications of these differences for understanding the
-  physics of the bow shock interaction in the three classes of
-  sources.
+  Stellar bow shocks result from stars that move with respect to their
+  environment. The interaction of the stellar wind and radiation with
+  gas and dust in the interstellar medium produces curved arcs of
+  emission at optical, infrared, and radio wavelengths.  We recently
+  proposed a new two-dimensional classification scheme for the shape
+  of such bow shocks, which we here apply to three very different
+  observational datasets: (1)~mid-infrared arcs around hot OB stars;
+  (2)~far-infrared arcs around luminous cool stars; and
+  (3)~H\(\alpha\) emission-line arcs around proplyds and other young stars
+  in the Orion Nebula.  For OB stars, the average shape is consistent
+  with simple thin-shell models for the interaction of a spherical
+  wind with a parallel stream, but the diversity of observed shapes is
+  many times larger than such models predict.  We propose that this
+  may be caused by time-dependent oscillations in the bow shocks, due
+  to either instabilities or wind variability.  Cool star bow shocks
+  have markedly more closed wings than hot star bow shocks, which may
+  be due to the dust emission arising in the shocked stellar wind
+  instead of the shocked interstellar medium.  The Orion Nebula arcs,
+  on the other hand, have both significantly more open wings and
+  significantly flatter apexes than the hot star bow shocks.  We test
+  several possible explanations for this difference: divergent ambient
+  stream, low Mach number, observational biases, and influence of
+  collimated jets.  Further observations are required to decide
+  between these.
 \end{abstract}
@@
 % Don't change these lines
+
 \bsp	% typesetting comment

### 2019-05-10 papers/Papers1234/sec-obs-intro.tex
Finish discussion of OB star shapes for Paper IV
Finish discussion for Paper IV - now just summary to go!
New version of abstract for Paper IV

@@
 sufficient to break the collisional coupling between gas and dust
-grains \citep[Paper~II]{Henney:2019b}.  In other cases, the appearance
-of an infrared emission arc may be due to the illumination of the
-inner wall of an asymmetrical cavity \citep{Mackey:2016a}, rather than
-the formation of a dense shell, in which case the relative velocity of
-the star may be subsonic with respect to its surroundings
+grains \citep[Paper~II]{Henney:2019b}.  We have proposed a diagnostic
+method to distinguish between these cases, based on the bow shock size
+and the luminosity ratio between the bow shock and the star
+\citep[Paper~III]{Henney:2019c}. In other cases, the appearance of an
+infrared emission arc may be due to the illumination of the inner wall
+of an asymmetrical cavity \citep{Mackey:2016a}, rather than the
+formation of a dense shell, in which case the relative velocity of the
+star may be subsonic with respect to its surroundings
 \citep{Mackey:2015a}.
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/obs-shape-terminology}
+  \includegraphics[width=0.6\linewidth]{figs/obs-shape-terminology}
   \caption[Terminology]{Terminology employed in this paper to describe
-    bow shock shapes, following \citet{Tarango-Yong:2018a}.}
+    bow shock shapes, following \citet[Paper~0]{Tarango-Yong:2018a}.}
   \label{fig:obs-shape-terminology}
@@
 results.  Further details of the statistical tests that we have
-applied are provided in Appendix~\ref{sec:distr-p-values}.
+applied are provided in Appendix~\ref{sec:distr-p-values} and a simple
+model for time-dependent oscillations of the bow shock surface is
+presented in Appendix~\ref{sec:perturbed-bows}.
 

### 2019-05-11 papers/Papers1234/obs-bowshocks.tex
First complete draft of Paper IV

@@
 %   shocks across the HR diagram}
-\title[Bow shocks, bow waves, and dust waves. IV.]{Bow shocks, bow
-  waves, and dust waves. IV. Shell shape statistics}
+\title[Bow shocks, bow waves, and dust waves. IV.] %
+{Bow shocks, bow waves, and dust waves. IV. Shell shape statistics}
 
@@
 \begin{abstract}
-  Stellar bow shocks result from stars that move with respect to their
-  environment. The interaction of the stellar wind and radiation with
-  gas and dust in the interstellar medium produces curved arcs of
+  Stellar bow shocks result from relative motions between stars and
+  their environment. The interaction of the stellar wind and radiation
+  with gas and dust in the interstellar medium produces curved arcs of
   emission at optical, infrared, and radio wavelengths.  We recently
@@
   of such bow shocks, which we here apply to three very different
-  observational datasets: (1)~mid-infrared arcs around hot OB stars;
-  (2)~far-infrared arcs around luminous cool stars; and
-  (3)~H\(\alpha\) emission-line arcs around proplyds and other young stars
-  in the Orion Nebula.  For OB stars, the average shape is consistent
-  with simple thin-shell models for the interaction of a spherical
-  wind with a parallel stream, but the diversity of observed shapes is
-  many times larger than such models predict.  We propose that this
-  may be caused by time-dependent oscillations in the bow shocks, due
-  to either instabilities or wind variability.  Cool star bow shocks
-  have markedly more closed wings than hot star bow shocks, which may
-  be due to the dust emission arising in the shocked stellar wind
-  instead of the shocked interstellar medium.  The Orion Nebula arcs,
-  on the other hand, have both significantly more open wings and
+  observational datasets: mid-infrared arcs around hot OB stars;
+  far-infrared arcs around luminous cool stars; and H\(\alpha\)
+  emission-line arcs around proplyds and other young stars in the
+  Orion Nebula.  For OB stars, the average shape is consistent with
+  simple thin-shell models for the interaction of a spherical wind
+  with a parallel stream, but the diversity of observed shapes is many
+  times larger than such models predict.  We propose that this may be
+  caused by time-dependent oscillations in the bow shocks, due to
+  either instabilities or wind variability.  Cool star bow shocks have
+  markedly more closed wings than hot star bow shocks, which may be
+  due to the dust emission arising in the shocked stellar wind instead
+  of the shocked interstellar medium.  The Orion Nebula arcs, on the
+  other hand, have both significantly more open wings and
   significantly flatter apexes than the hot star bow shocks.  We test
-  several possible explanations for this difference: divergent ambient
+  several possible explanations for this difference (divergent ambient
   stream, low Mach number, observational biases, and influence of
-  collimated jets.  Further observations are required to decide
-  between these.
+  collimated jets), but the evidence for each is inconclusive.
 \end{abstract}

### 2019-05-11 papers/Papers1234/sec-standing-wave.tex
First complete draft of Paper IV

@@
 bow shock shell does not show any sign of the red/blue asymmetry that
-is seen in the jet knots, which argues against any such an
-association.
+is seen in the jet knots, which argues against any such association.
 

### 2019-06-21 papers/Papers1234/bs-bw-dw-03.tex
Finish addressing point 2 of ref report for paper 3

@@
 \appendix
+
+\section{Dust opacity and optical depth}
+\label{app:dust-opacity}
+
+In the main body of the paper we use a frequency-averaged dust optical
+depth, \(\tau\), which we here relate to the frequency-dependent optical
+properties of the grains.  For simplicity, we assume a dust model that
+consists of a set \(k \in \{1 \dots N\}\) of discrete populations of
+solid spherical grains \citep[e.g.][]{Desert:1990a}, each with its own
+chemical composition and size distribution:
+\(y_{a,k} \equiv n_k^{-1} (d n_k / d a)\), where \(n_k\) is the volume
+density of the \(k\)-th population (\si{grain.cm^{-3}}) and \(a\) is
+the grain radius. The frequency-dependent dust opacity per unit mass
+of gas and dust is \(\kappa_\nu\), with units \si{cm^2.g^{-1}}, which can be
+expressed as
+\begin{equation}
+  \label{eq:dust-opacity-frequency}
+  \kappa_\nu = \rho^{-1} \sum_{k=1}^{N} \left[  n_k \int_0^\infty \!\!y_{a,k} \, Q_{a,k,\nu} \,\pi a^2 \, da\right]\ ,
+\end{equation}
+where \(\rho\) is the total material mass density and \(Q_{a,k,\nu}\) is
+the size-, composition-, and frequency-dependent dimensionless grain
+optical efficiency, which can be calculated from the grain refractive
+indices using Mie theory \citep{Bohren:1983a}.  There are different
+varieties of \(Q\), and therefore different varieties of opacity,
+according to whether one is interested in true absorption,
+\(Q_{\text{abs}}\), scattering, \(Q_{\text{scat}}\), or total
+extinction, \(Q_{\text{ext}} = Q_{\text{abs}} + Q_{\text{scat}}\).
+The relative importance of scattering is described by the grain
+albedo: \(\varpi = Q_{\text{scat}}/Q_{\text{ext}}\).  The radiation
+pressure acting on the grains is determined by a fourth variety of
+optical efficiency:
+\(Q_P = Q_{\text{abs}} + (1 - g) Q_{\text{scat}}\), where \(g\) is the
+mean scattering cosine.
+
+The monochromatic optical depth of a medium (in any of these 4
+varieties) along a path \(s\) is given by
+\begin{equation}
+  \label{eq:tau-monochromatic}
+  \tau_\nu = \int \rho \kappa_\nu \, ds \ .
+\end{equation}
+If the effects of multiple scattering are ignored, then the fraction
+of stellar radiation of frequency \(\nu\) that is absorbed by the shell
+is \(1 - e^{-\tau_\nu}\), in which the integral is performed with
+\(s\) along the radial direction, assuming the star to be effectively
+a point source at the position of the shell.  To find the fraction of
+radiative \emph{energy}, \(\kappa_\nu\) must be calculated using
+\(Q_{\text{abs}}\), whereas to find the fraction of radiative
+\emph{momentum}, it must be calculated using \(Q_P\).  This
+single-scattering regime \citep[e.g.][]{Wibking:2018a} is a good
+approximation so long as \(\varpi\) is not close to unity and the
+shell is optically thin at infrared wavelengths, which is always true
+for stellar bow shocks.
+
+The frequency-averaged optical depth \(\tau\) is defined such that the
+fraction of the frequency-integrated stellar radiative momentum
+absorbed by the shell is \(1 - e^{-\tau}\).  For a stellar spectrum of
+shape \(F_\nu\), this implies the formal relation
+\begin{equation}
+  \label{eq:tau-averaged}
+  \tau = - \ln \left[ \frac{\int_0^\infty F_\nu \, e^{-\tau_\nu} \, d\nu}{\int_0^\infty F_\nu  \, d\nu} \right] \ .
+\end{equation}
+Note that this equation is valid regardless of the physical units of
+\(F_\nu\) (e.g., flux or luminosity).  More approximately, \(\tau\) can
+simply be estimated by \(\tau_\nu\) at the peak frequency of the stellar
+radiation, which typically falls in the far-ultraviolet range,
+although this approximation breaks down if \(\tau_\nu > 1\) over a
+significant portion of the stellar spectrum.
+
+In the main body of the paper, we use \(\tau\) for the radiation pressure
+optical depth and \(\tau'\) for the absorption optical depth.  These are
+related by the ratio of the corresponding frequency-averaged optical
+efficiencies:
+\begin{equation}
+  \label{eq:tau_tauprime}
+  \tau = \frac{Q_P}{Q_{\text{abs}}} \tau' = \left(  1 + \varpi \frac{1 - g}{1 - \varpi}\right) \tau'\ .
+\end{equation}
+Specific results were given in Figure~6a of Paper~II for an example
+grain mixture, designed to reproduce average interstellar medium dust
+properties \citep{Weingartner:2001b, Abel:2008a, Ferland:2013a,
+  Ferland:2017a}.  For such a mixture the albedo is roughly constant
+at \(\varpi \approx 0.5\) throughout the ultraviolet and visible bands,
+falling to low values in the infrared.  The asymmetry parameter, or
+mean scattering cosine, falls across the ultraviolet band from
+\(g \approx 1\) at the highest frequencies to \(g\approx 0.5\) in the FUV.\@ This
+yields a conversion factor of
+\(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
+wavelengths.
+
 \input{app-k17-k18}

### 2019-06-21 papers/Papers1234/sec-observational-diagnostics.tex
Finish addressing point 2 of ref report for paper 3

@@
 
-A fundamental parameter is the optical depth, \(\tau\), of the bow
-shell to UV radiation, which determines what fraction of the stellar
-photon momentum is available to support the shell (see
-\S~2.1 of Paper~I).  But the same photons also heat the
-dust grains in the bow, which re-radiate that energy predominantly at
-mid-infrared wavelengths (roughly \SIrange{10}{100}{\um}) with
-luminosity \(L\IR\).  Assuming that Ly\(\alpha\) and mechanical
-heating of the dust shell is negligible (see
+A fundamental parameter is the average optical depth, \(\tau\), of the
+bow shell to the stellar radiation. In Appendix~\ref{app:dust-opacity}
+we discuss in detail the relation between \(\tau\) and the optical
+properties of the grains.  In the single-scattering approximation, a
+fraction \(1 - e^{-\tau}\) of the stellar photon momentum is available to
+support the shell (see \S~2.1 of Paper~I).  But the same photons also
+heat the dust grains in the bow, which re-radiate that energy
+predominantly at mid-infrared wavelengths (roughly
+\SIrange{10}{100}{\um}) with luminosity \(L\IR\).  Assuming that
+Ly\(\alpha\) and mechanical heating of the dust shell is negligible (see
 \S~\ref{sec:unimp-other-heat}) and that the emitting shell subtends a
-solid angle \(\Omega\), as seen from the star, then the optical depth
-can be estimated as
+solid angle \(\Omega\), as seen from the star, then an absorption optical depth can
+be estimated as
 \begin{equation}
   \label{eq:tau-empirical}
-  \tau = -\ln \left( 1 - \frac{4\pi}{\Omega} \frac{L\IR}{L_*} \right)
+  \tau' = -\ln \left( 1 - \frac{4\pi}{\Omega} \frac{L\IR}{L_*} \right)
   \approx \frac{2 L\IR}{L_*} \ ,
 \end{equation}
-where the last approximate equality holds if \(\tau \ll 1\) and the shell
-emission covers one hemisphere.\footnote{%
-  Note that the \(\tau\) of Paper~I is not exactly the same as the
-  \(\tau\) of equation~\eqref{eq:tau-empirical}, but is larger by a
-  factor of
-  \(Q_P / Q_{\text{abs}} = 1 + \varpi (1 - g)/(1 - \varpi)\), where
-  \(\varpi\) is the grain albedo and \(g\) the scattering asymmetry.
-  For standard ISM grain mixtures,
-  \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
-  wavelengths.}
-% This is plotted in Figure~6a of Paper~II for Cloudy's default ISM
-% grain mixture (see \S~\ref{sec:grain-temp-emiss} below), where it
-% can be seen that
-% \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
-% wavelengths (\(\lambda = \text{\SIrange{0.05}{0.2}{\um}}\)), so the
-% correction is small.
+where the last approximate equality holds if \(\tau' \ll 1\) and the shell
+emission covers one hemisphere.  The two optical depths, \(\tau\) and
+\(\tau'\), are not exactly the same, see
+equation~\eqref{eq:tau_tauprime}.  The first, \(\tau\), represents
+radiative momentum transfer, which is governed by the grain radiation
+pressure efficiency, \(Q_P\).  The second, \(\tau'\), represents
+radiative energy transfer, which is governed by the grain absorption
+efficiency, \(Q_{\text{abs}}\).  We adopt \(\tau = 1.25 \tau'\) based on
+Cloudy models of a standard ISM dust mixture, see Figure~6 of
+Paper~II and Appendix~\ref{app:dust-opacity}.
 

### 2019-06-21 papers/Papers1234/sigma-ori-arcs.tex
Finish intro to paper II
New amateur images of sigma Ori

@@
 % OR
-{\boldmath A dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}
+% {\boldmath A dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}
+% OR
+{\boldmath Bow shocks, bow waves, and dust waves. V. No dust wave for \(\sigma\) Ori}
 
@@
 \begin{abstract}
-  We critically evaluate the role of radiation and hydrodynamics in
+  We critically evaluate the role of radiation and ram pressure in
   providing internal support for the bow-shaped infrared arc around
@@
 
+We downloaded optical images of \(\sigma\)~Ori from the Astronomical Data
+Centre of the Cambridge Astronomy Survey
+Unit.\footnote{\url{http://casu.ast.cam.ac.uk/surveys-projects/adc}}
+These were obtained on 2008-11-19 with the Wide Field Camera of the
+Isaac Newton Telescope from an observational program of Rafael
+Barrena.  We use images in two filters: a narrow-band H\(\alpha\) filter
+(central wavelength, \(\lambda_0 = \SI{656.8}{nm}\), full-width half
+maximum, \(\Delta\lambda = \SI{9.5}{nm}\)) and a broad-band Sloan Gunn
+\(R\) filter (\(\lambda_0 = \SI{624.0}{nm}\), \(\Delta\lambda = \SI{134.7}{nm}\)).  We have removed the bias v
+
 \section{Why the inner arc cannot be radiation-supported}
@@
   \includegraphics[width=\linewidth]{figs/sigma-ori-comparison}
-  \caption{Optical and infrared images of $\sigma$~Ori}
+  \caption{Optical and infrared images of $\sigma$~Ori and its
+    surroundings.  (a)~Optical image in in the H\(\alpha\) line, shown in
+    negative grayscale.  (b)~Mid-infrared image in three Spitzer
+    bands: MIPS \SI{23.7}{\um} (red), IRAC \SI{7.87}{\um} (green), and
+    IRAC \SI{5.73}{\um} (blue).  The yellow dashed box shows the slit
+    for which profiles are extracted in Fig.~\ref{fig:sig-ori-cuts}.}
   \label{fig:sig-ori}
@@
   \includegraphics[width=\linewidth]{figs/sigma-ori-eastwest-cuts}
-  \caption{Brightness profiles through $\sigma$~Ori inner arc.}
+  \caption{Brightness profiles through $\sigma$~Ori inner arc.  (a)~H\(\alpha\) and  All
+    profiles are extracted in a \(40''\) wide slit, offset by \(80''\)
+    to the south of \(\sigma\)~Ori, as indicated in
+    Fig.~\ref{fig:sig-ori}b. }
   \label{fig:sig-ori-cuts}
@@
   \includegraphics[width=\linewidth]{figs/sigma-ori-inner-outer}
-  \caption{Combined mid-infrared and far-infrared views of the inner and outer arcs around $\sigma$~Ori}
+  \caption{Combined mid-infrared and far-infrared views of the inner
+    and outer arcs around $\sigma$~Ori}
   \label{fig:sig-ori-outer}
@@
 
+\section*{Acknowledgements}
+
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grant Programa de Apoyo a Proyectos de Investigación e
+Inovación Tecnológica IN107019.  We thank Bo Reipurth for advice on
+astronomical data archives.  This work is based in part on
+observations made in the Observatorios de Canarias del IAC with the
+Isaac Newton Telescope operated on the island of La Palma by the
+Instituto de Astrofísica de Canarias in the Observatorio del Roque de
+los Muchachos. 
+% Based in part on observations made with the Isaac Newton Telescope
+% under Director’s Discretionary Time of Spain’s Instituto de
+% Astrofísica de Canarias.
+This work is based in part on observations made with the Spitzer Space
+Telescope, which is operated by the Jet Propulsion Laboratory,
+California Institute of Technology under a contract with NASA.\@ This
+work makes use of imagery from David Mittelman Astrophotography.
+
 \bibliographystyle{mnras}

### 2019-06-22 papers/Papers1234/app-cloudy-dust-heating.tex
Finish fixes to paper 3 for referee

@@
   \label{eq:U-from-ambient}
-  U = 3.01 \, n_\infty \, v_{10}^2 / x^2 \ , 
+  U = 3.01 \, n \, v_{10}^2 / x^2 \ , 
 \end{equation}
@@
 \end{equation}
-where we give the range corresponding to early O (\(f_{\text{fuv}} \approx 0.4\)) to early B (\(f_{\text{fuv}} \approx 0.7\)) stars.
+where we give the range corresponding to early O
+(\(f_{\text{fuv}} \approx 0.4\)) to early B
+(\(f_{\text{fuv}} \approx 0.7\)) stars, calculated from TLUSTY stellar
+atmosphere models \citep{Lanz:2003a, Lanz:2007a}.
 

### 2019-06-22 papers/Papers1234/bs-bw-dw-03.tex
Finish fixes to paper 3 for referee

@@
 
-In Paper~I we derived expressions for the bow radius \(R_0\) in each of
-the three well-coupled regimes as a function of the parameters of the
-star and the ambient medium.  In Paper~II, we found the criteria for
-the dust to decouple from the gas to form a separate dust wave outside
-of the hydrodynamic bow shock.  The most important of these is that
-the ratio of radiation pressure to gas pressure should exceed a
-critical value, \(\Xi_\dag \sim 1000\).
+In Paper~I we derived expressions for the bow radius \(R_0\)
+(star--apex distance) in each of the three well-coupled regimes as a
+function of the parameters of the star and the ambient medium.  In
+Paper~II, we found the criteria for the dust to decouple from the gas
+to form a separate dust wave outside of the hydrodynamic bow shock.
+The most important of these is that the ratio of radiation pressure to
+gas pressure should exceed a critical value, \(\Xi_\dag \sim 1000\).
 
@@
 
-In the main body of the paper, we use \(\tau\) for the radiation pressure
-optical depth and \(\tau'\) for the absorption optical depth.  These are
+In the main body of the paper, we use \(\tau_P\) for the radiation pressure
+optical depth and \(\tau_{\text{abs}}\) for the absorption optical depth.  These are
 related by the ratio of the corresponding frequency-averaged optical
@@
   \label{eq:tau_tauprime}
-  \tau = \frac{Q_P}{Q_{\text{abs}}} \tau' = \left(  1 + \varpi \frac{1 - g}{1 - \varpi}\right) \tau'\ .
+  \tau_P = \frac{Q_P}{Q_{\text{abs}}} \tau_{\text{abs}} = \left(  1 + \varpi \frac{1 - g}{1 - \varpi}\right) \tau_{\text{abs}}\ .
 \end{equation}

### 2019-06-22 papers/Papers1234/sec-observational-diagnostics.tex
Finish fixes to paper 3 for referee

--- 2019-04-08 papers/Papers1234/sec-observational-diagnostics.tex
@@
 
-A fundamental parameter is the optical depth, \(\tau\), of the bow
-shell to UV radiation, which determines what fraction of the stellar
-photon momentum is available to support the shell (see
-\S~2.1 of Paper~I).  But the same photons also heat the
-dust grains in the bow, which re-radiate that energy predominantly at
-mid-infrared wavelengths (roughly \SIrange{10}{100}{\um}) with
-luminosity \(L\IR\).  Assuming that Ly\(\alpha\) and mechanical
-heating of the dust shell is negligible (see
-\S~\ref{sec:unimp-other-heat}) and that the emitting shell subtends a
-solid angle \(\Omega\), as seen from the star, then the optical depth
-can be estimated as
+A fundamental parameter is the average optical depth, \(\tau\), of the
+bow shell to the stellar radiation. In Appendix~\ref{app:dust-opacity}
+we discuss in detail the relation between \(\tau\) and the optical
+properties of the grains, as well as the slight differences between
+the optical depths for absorption, \(\tau_{\text{abs}}\), scattering,
+\(\tau_{\text{scat}}\), and radiation pressure, \(\tau_P\).  In the
+single-scattering approximation, a fraction \(1 - e^{-\tau_P}\) of the
+stellar photon momentum is available to support the shell (see \S~2.1
+of Paper~I).  But the same photons also heat the dust grains in the
+bow, which re-radiate that energy predominantly at mid-infrared
+wavelengths (roughly \SIrange{10}{100}{\um}) with luminosity \(L\IR\).
+Assuming that Ly\(\alpha\) and mechanical heating of the dust shell is
+negligible (see \S~\ref{sec:unimp-other-heat}) and that the emitting
+shell subtends a solid angle \(\Omega\), as seen from the star, then an
+absorption optical depth can be estimated as
 \begin{equation}
   \label{eq:tau-empirical}
-  \tau = -\ln \left( 1 - \frac{4\pi}{\Omega} \frac{L\IR}{L_*} \right)
+  \tau_{\text{abs}} = -\ln \left( 1 - \frac{4\pi}{\Omega} \frac{L\IR}{L_*} \right)
   \approx \frac{2 L\IR}{L_*} \ ,
 \end{equation}
-where the last approximate equality holds if \(\tau \ll 1\) and the shell
-emission covers one hemisphere.\footnote{%
-  Note that the \(\tau\) of Paper~I is not exactly the same as the
-  \(\tau\) of equation~\eqref{eq:tau-empirical}, but is larger by a
-  factor of
-  \(Q_P / Q_{\text{abs}} = 1 + \varpi (1 - g)/(1 - \varpi)\), where
-  \(\varpi\) is the grain albedo and \(g\) the scattering asymmetry.
-  For standard ISM grain mixtures,
-  \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
-  wavelengths.}
-% This is plotted in Figure~6a of Paper~II for Cloudy's default ISM
-% grain mixture (see \S~\ref{sec:grain-temp-emiss} below), where it
-% can be seen that
-% \(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
-% wavelengths (\(\lambda = \text{\SIrange{0.05}{0.2}{\um}}\)), so the
-% correction is small.
+where the last approximate equality holds if
+\(\tau_{\text{abs}} \ll 1\) and the shell emission covers one hemisphere.
+The two optical depths, \(\tau_P\) and \(\tau_{\text{abs}}\), are not
+exactly the same, see equation~\eqref{eq:tau_tauprime}.  The first
+represents radiative momentum transfer, which is governed by the grain
+radiation pressure efficiency, \(Q_P\), while the second represents
+radiative energy transfer, which is governed by the grain absorption
+efficiency, \(Q_{\text{abs}}\).  We adopt
+\(\tau_P = 1.25 \tau_{\text{abs}}\) based on Cloudy models of a standard ISM
+dust mixture, see Figure~6 of Paper~II and
+Appendix~\ref{app:dust-opacity}.  In the remainder of the paper, we
+drop the subscript and set \(\tau = \tau_{\text{abs}}\).
 
@@
 luminosity and shell parameters in terms of typical values, which we
-summarize below.  Note that the shell momentum efficiency is simply
-the reciprocal of the radiation parameter from Paper~II's
-equation~(23): \(\eta\shell = \Xi\shell^{-1}\), which provides yet a third
-use for \(\eta\shell\), since \(\Xi\) is paramount in determining whether
-the grains and gas remain well-coupled (see \S~4.4 of Paper~II).
+summarize below.  In equation~(23) of Paper~II, we defined a radiation
+parameter as the ratio of the radiation pressure to gas pressure,
+\(\Xi = P\rad/P\gas\). The value of \(\Xi\) in the shell is therefore
+\(\Xi\shell = \eta\shell^{-1}\) if magnetic pressure is negligible, which
+provides yet a third use for \(\eta\shell\), since the radiation
+parameter is paramount in determining whether the grains and gas
+remain well-coupled (see \S~4.4 of Paper~II).
 
 In this section and the remainder of the paper, we employ
-dimensionless versions of the stellar bolometric luminosity, \(L_*\),
-wind mass-loss rate, \(\dot{M}\), and terminal velocity, \(V\wind\),
-together with the ambient stream's mass density, \(\rho\), relative
-velocity \(v_\infty\), and effective dust opacity, \(\kappa\).  These are
-defined as follows:
+dimensionless versions of the star--apex distance, \(R_0\), stellar
+bolometric luminosity, \(L_*\), wind mass-loss rate, \(\dot{M}\), and
+terminal velocity, \(V\wind\), together with the ambient stream's mass
+density, \(\rho\), stream--star relative velocity \(v_\infty\), and effective
+dust opacity, \(\kappa\).  These are defined as follows:
 \begin{align*}
   % \label{eq:stellar-parameters}
+  R_{\text{pc}} &= R_0 / \bigl( \SI{1}{pc} \bigr) \\
   \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
@@
 (DW, RBW, or RBS cases) should lie on the diagonal line
-\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where we have used
-the ratio of grain radiation pressure efficiency to absorption
-efficiency found in the FUV band for the dust mixture shown in
-Paper~II's Figure~6.  Wind-supported bows should lie above this line
-and no bows should lie below the \(\eta\shell = \tau\) line, since
-\(Q_P\) cannot be smaller than \(Q_{\text{abs}}\).
+\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), see discussion
+following equation~\eqref{eq:tau-empirical}.  Wind-supported bows
+should lie above this line and no bows should lie below the
+\(\eta\shell = \tau\) line, since \(Q_P\) cannot be smaller than
+\(Q_{\text{abs}}\).
 

### 2019-06-22 papers/bs-bw-dw-03-submit/latexdiff/ms03-v1-expand.tex
Do latexdiff between the original and final versions of paper 3

--- 2019-04-08 papers/Papers1234/sec-observational-diagnostics.tex
@@
+\documentclass[useAMS, usenatbib, a4paper]{mnras}
+\pdfsuppresswarningpagegroup=1
+
+\usepackage{graphicx}
+\usepackage{microtype}
+\usepackage{xcolor}
+\usepackage{fixltx2e}
+\usepackage{booktabs}
+\usepackage{siunitx}
+\sisetup{separate-uncertainty = true}
+\usepackage{color}
+\usepackage{enumerate}
+\usepackage{pdflscape}
+\usepackage{rotating}
+\usepackage{xr-hyper}
+\usepackage{hyperref}
+
+\usepackage[T1]{fontenc} 
+\usepackage[utf8]{inputenc}
+
+% Fonts 
+\usepackage{newtxtext}
+% Note: newtxmath must come AFTER newtxtext
+\usepackage[varvw,smallerops]{newtxmath}
+
+\usepackage{chemgreek}
+\activatechemgreekmapping{newtx}
+\usepackage{listings}
+
+\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
+  urlcolor=blue!50!black}
+
+\usepackage{etoolbox}
+\robustify\bfseries
+\robustify\itshape
+
+%% The following hack solves a problem with
+%% ERROR: \pdfendlink ended up in different nesting level than \pdfstartlink.
+%% See https://tex.stackexchange.com/a/249743
+\makeatletter
+\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
+  \errmessage{\noexpand\@combinedblfloats could not be patched}%
+}%
+\makeatother
+
+%% Bold italic
+\newcommand\hmmax{0}            % we don't need heavy fonts
+\newcommand\bmmax{1}            % reduce use of math alphabets for bold
+\usepackage{bm}
+
+%% Bundled custom packages
+\usepackage{aastex-compat}
+
+\title
+{Bow shocks, bow waves, and dust waves. III. Diagnostics}
+
+\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
+  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
+  58090 Morelia, Michoac\'an, M\'exico}
+\author[Henney \& Arthur]{
+  William J. Henney\thanks{w.henney@irya.unam.mx}
+  \& S. J. Arthur\\
+  \AddressCRyA
+}
+
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2019}
+
+% start input ./bs-bw-dw-defs.tex
+\DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\Sin}{\mathcal{S}}
+\DeclareMathOperator{\Cos}{\mathcal{C}}
+\DeclareMathOperator{\Cot}{\mathcal{T}}
+\DeclareMathOperator{\GammaFunc}{\Gamma}
+\DeclareMathOperator\erf{erf}
+\newcommand\w{\ensuremath{\mathrm{w}}}
+\newcommand\C{\ensuremath{\mathrm{c}}}
+\providecommand{\abs}[1]{\lvert#1\rvert}
+\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
+\newcommand\TODO[1]{%
+  \begin{center}
+    \framebox{\parbox{0.8\linewidth}{
+        \texttt{\footnotesize\color{red} #1}}}
+  \end{center}}
+
+\newcommand\uvec[1]{\bm{\hat{#1}}}
+\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+
+\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
+\newcommand\Qpbar{\ensuremath{\bar{Q}_{\text{p}}}}
+\newcommand{\grain}{\ensuremath{_{\text{d}}}}
+\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
+\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
+\newcommand{\xsec}{\ensuremath{\sigma\grain}}
+\newcommand\frad{\ensuremath{f_{\text{rad}}}}
+\newcommand\fmax{\ensuremath{f_{\text{max}}}}
+\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
+\newcommand\drag{\ensuremath{_{\text{drag}}}}
+\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
+\newcommand{\wind}{\ensuremath{_{\text{w}}}}
+\newcommand{\trap}{\ensuremath{_{\text{abs}}}}
+\newcommand{\ke}{\ensuremath{_{\text{kin}}}}
+\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
+\newcommand\rad{\ensuremath{_{\text{rad}}}}
+\newcommand\Lya{\ensuremath{_{\text{Ly}\alpha}}}
+\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
+% Why do I need both of these?
+\newcommand\sound{\ensuremath{c_{\text{s}}}}
+\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
+\newcommand\starstar{\ensuremath{_{**}}}
+\newcommand\mmp{\ensuremath{_{\text{\tiny MMP83}}}}
+\newcommand\Hab{\ensuremath{_{\text{\tiny Habing}}}}
+\newcommand\IR{\ensuremath{_{\text{IR}}}}
+\newcommand{\thD}{\(\theta^1\)\,Ori~D}
+\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
+\newcommand\shell{\ensuremath{_{\text{sh}}}}
+\newcommand\M{\ensuremath{\mathcal{M}}}
+\newcommand\hii{\ion{H}{ii}}
+
+\newcommand\amu{\ensuremath{a_{\si{\um}}}}
+
+\newcommand\freeze{\ensuremath{_{\text{tight}}}}
+\newcommand\iftrap{\ensuremath{_{\text{trap}}}}
+\newcommand\LOS{\ensuremath{_{\text{los}}}}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "bs-bw-dw-01"
+%%% End:
+ % end input ./bs-bw-dw-defs.tex
+
+\begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+\begin{abstract}
+  Stellar bow shocks, bow waves, and dust waves all result from the
+  action of a star's wind and radiation pressure on a stream of dusty
+  plasma that flows past it.  The dust in these bows emits prominently
+  at mid-infrared wavelengths in the range \SIrange{8}{60}{\um}. We
+  propose a novel diagnostic method, the \(\tau\)--\(\eta\) diagram,
+  for analyzing these bows, which is based on comparing the fractions
+  of stellar radiative energy and stellar radiative momentum that is
+  trapped by the bow shell.  This diagram allows the discrimination of
+  wind-supported bow shocks, radiation-supported bow waves, and dust
+  waves in which grains decouple from the gas.  For the wind-supported
+  bow shocks, it allows the stellar wind mass-loss rate to be
+  determined.  We critically compare our method with a previous method
+  that has been proposed for determining wind mass-loss rates from bow
+  shock observations. This comparison points to ways in which both
+  methods can be improved and suggests a downward revision by a factor
+  of two with respect to previously reported mass-loss rates.  From a
+  sample of 23 mid-infrared bow-shaped sources, we identify at least 4
+  strong candidates for radiation-supported bow waves, which need to
+  be confirmed by more detailed studies, but no strong candidates for
+  dust waves.
+\end{abstract}
+
+\begin{keywords}
+  circumstellar matter -- radiation: dynamics -- stars: winds, outflows
+\end{keywords}
+
+\section{Introduction}
+\label{sec:introduction}
+
+Bow-shaped circumstellar nebulae are observed around a wide variety of
+stars \citep{Gull:1979a, Cox:2012a, Cordes:1993a} but are most
+numerous around luminous OB stars \citep{Kobulnicky:2016a}.  They are
+most commonly interpreted as bow shocks, due to a supersonic relative
+motion of the surrounding medium, which interacts with the stellar
+wind \citep{Wilkin:1996a}.  Early surveys for bow shocks around OB
+stars \citep{van-Buren:1995a} concentrated on runaway stars
+\citep{Blaauw:1961a, Hoogerwerf:2001a} that have been ejected at high
+velocities (\(> \SI{30}{km.s^{-1}}\)) due to multi-body encounters in
+star clusters or due to the core-collapse supernova explosion of a
+binary companion.  However, only a small fraction of runaways show
+detectable bow shocks \citep{Huthoff:2002a, Peri:2012a, Peri:2015a,
+  Prisegen:2019a}. Targeted searches at mid-infrared wavelengths of
+particular high-mass star forming regions such as M17 and RCW~49
+\citep{Povich:2008a}, Cygnus~X \citep{Kobulnicky:2010a}, and Carina
+\citep{Sexton:2015b} have revealed many bows around slower moving
+stars.  In many cases, it may be streaming motions in the interstellar
+medium that provide most of the relative velocity: weather vanes
+rather than runaways \citep{Povich:2008a}.  More recently, large-scale
+surveys of the Galactic plane \citep{Kobulnicky:2016a,
+  Kobulnicky:2017a} and of nearby stars in the Bright Star Catalog
+\citep{Bodensteiner:2018a} have revealed hundreds more such bow shocks.
+
+Analytic and semi-analytic thin-shell models of bow shocks have been
+developed \citep{van-Buren:1992a, Wilkin:1996a, Canto:1996},
+including the effects of non-spherical winds and nonaxisymmetric bows
+\citep{Wilkin:2000a, Henney:2002a, Canto:2005a, Tarango-Yong:2018a}.
+Increasingly realistic numerical hydrodynamic simulations have been
+performed \citep{Matsuda:1989a, Raga:1997a, Comeron:1998a, Arthur:2006a,
+  Meyer:2014b, Mackey:2015a}, including magnetic fields
+\citep{Meyer:2017a, Katushkina:2017a, Katushkina:2018a} and detailed
+predictions of the dust emission \citep{Meyer:2016a, Acreman:2016a,
+  Mackey:2016a}.
+
+% Despite the almost
+% universal use of the term ``bow shock'' to describe these objects, it
+% may be that slow subsonic velocities of a star through its \hii{}
+% region are sufficient \citep{Mackey:2015a, Mackey:2016a} to distort
+% the inner stellar wind shock and produce a bow appearance to the
+% mid-infrared emission, even though there is no shock in the dusty
+% ambient stream.
+
+In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
+presented a taxonomy of stellar bows, which we divided into
+wind-supported bow shocks (WBS) and various classes of
+radiation-supported bows.  When the dust and gas remains well-coupled
+(Paper~I), these are optically thin radiation-supported bow waves
+(RBW) and optically thick radiation-supported bow shocks (RBS).  When
+the dust decouples from the gas (Paper~II), inertia-confined dust
+waves (IDW) and drag-confined dust waves (DDW) can result.
+
+In Paper~I we derived expressions for the bow radius \(R_0\) in each of
+the three well-coupled regimes as a function of the parameters of the
+star and the ambient medium.  In Paper~II, we found the criteria for
+the dust to decouple from the gas to form a separate dust wave outside
+of the hydrodynamic bow shock.  The most important of these is that
+the ratio of radiation pressure to gas pressure should exceed a
+critical value, \(\Xi_\dag \sim 1000\).
+
+In order to provide an empirical anchor to our theoretical
+calculations, we now consider how the parameters of our models might
+be determined from observations.  The parameter-space diagrams, such
+as Figure~2 of Paper~I, are not always useful in this regard, since in
+many cases the ambient density and relative stellar velocity are not
+directly measured.  Instead, we aim to construct diagnostics based on
+the most common observations, which are of the infrared dust emission.
+Key questions that we wish to address include
+\begin{enumerate}[1.]
+\item Can we distinguish observationally between radiation support
+  (bow waves and dust waves) and wind support (bow shocks)?
+\item Are there any clear examples of sources with radiation-supported bows?
+\item In the case of wind support, can we reliably determine mass loss
+  rates from mid-infrared observations?
+\end{enumerate}
+
+The outline of the paper is as follows. In
+\S~\ref{sec:energy-trapp-vers} we describe how the optical depth and
+the gas pressure in the bow shell can be estimated from a small number
+of observed quantities.  In \S~\ref{sec:eta-tau-diagnostic} we place
+observed bow sources on a diagnostic diagram of these two quantities
+and discuss the influence of observational errors and systematic model
+uncertainties. In \S~\ref{sec:cand-radi-supp} we use the diagram to
+identify some candidates for radiation-supported bows. In
+\S~\ref{sec:grain-temp-emiss} we calculate the grain emissivity as a
+function of the stellar radiation field around OB stars.  In
+\S~\ref{sec:stellar-wind-mass} we compare two different methods of
+estimating the stellar wind mass loss rates from observations of the
+bows. In \S~\ref{sec:discussion} we discuss various groups of bows
+that require special treatment due to their diverse physical
+conditions. In \S~\ref{sec:conclusions} we summarise out findings.
+
+% start input ./sec-observational-diagnostics.tex
+
 % Are there any objects that might not be bow shocks?
@@
 wind (which is itself radiatively driven).  Radiatively supported bows
-(DW, RBW, or RBS cases) should lie on the diagonal line
+(DW, RBW, or RBS, or cases) should lie on the diagonal line
 \(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where we have used
@@
 
-\input{app-cloudy-dust-heating}
+% start input ./app-cloudy-dust-heating.tex
+\section{Mid-infrared grain emissivity}
+\label{sec:grain-temp-emiss}
+
+In preparation for our discussion of different wind mass-loss
+diagnostic methods below, in this section we calculate the grain
+emissivity predicted by models of dust heated by a nearby OB star.  We
+use the same simulations that we employed in \S~4.2 of Paper~II,
+% XREF: Paper II \ref{sec:cloudy-models-dust}
+which employ the plasma physics code Cloudy \citep{Ferland:2013a,
+  Ferland:2017a}.  In summary, simulations of spherically symmetric,
+steady-state, constant density \hii{} regions were carried out for
+four different stellar types from B1.5 to O5 (Table~2 of Paper~II), a
+range of gas densities from \SIrange{1}{e4}{cm^{-3}}, and using
+Cloudy's default ``ISM'' graphite/silicate dust mixture with 10 size
+bins from \SIrange{0.005}{0.25}{\um}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/grain-T-vs-U}
+  \caption{Grain temperature versus radiation field mean intensity,
+    \(U\), in units of the interstellar radiation field in the solar
+    neighborhood.  Line types and colors correspond to a variety of
+    stellar spectral shapes, gas densities, and grain species.  Dashed
+    lines show carbon grains, solid lines show silicate grains, with
+    line thickness and transparency increasing with grain size.
+    Stellar spectral types are O5\,V (blue), O9\,V (orange), B1.5\,V
+    (purple), and B0.7\,Ia (green), with lighter shades denoting
+    higher gas densities. }
+  \label{fig:grain-T-vs-U}
+\end{figure}
+
+Figure~\ref{fig:grain-T-vs-U} shows equilibrium grain temperatures for
+these Cloudy models as a function of the nominal energy density of the
+radiation field, \(U = u / u\mmp \), where \(u = L / 4 \pi R^2 c\) and
+\(u\mmp\) is the energy density of the interstellar radiation field
+for \(\lambda < \SI{8}{\um}\) in the solar neighborhood
+\citep{Mathis:1983a}:
+\begin{equation}
+  \label{eq:u-mmp83}
+  u\mmp\,c = \SI{0.0217}{erg.s^{-1}.cm^{-2}} \ .
+\end{equation}
+The tight relationship seen in Figure~\ref{fig:grain-T-vs-U} between
+\(T\) and \(U\) is evidence for the dominance of stellar radiative
+heating, which we justify on theoretical grounds in
+\S~\ref{sec:unimp-other-heat} below.  The variation about the mean
+relation is mainly due to differences in grain size and composition,
+with smaller grains and graphite grains being relatively hotter.  The
+downward hooks seen on the left end of each simulation's individual
+curve are due to the fact that our calculation of \(U\) does not
+account for internal absorption, which starts to become important near
+the ionization front.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/grain-j70-vs-U-edited}
+  \caption{Grain emissivity at \SI{70}{\um} for all Cloudy models,
+    with lines colored as in Fig.~\ref{fig:grain-T-vs-U}, but without
+    the variation in line type and thickness since emissivity is
+    integrated over all grain types and sizes.  For comparison, the
+    emissivity from the grain models of \citet{Draine:2007a} are shown
+    as dark gray symbols, which assume illumination by a scaled
+    interstellar radiation field with a SED with a very different
+    shape from that of an OB star, see Fig.~\ref{fig:sed-comparison}.
+    The light gray symbols show the effect of using an 8 times higher
+    \(U\) with the \citeauthor{Draine:2007a} models, which
+    approximately compensates for this difference in SED.  }
+  \label{fig:grain-j70}
+\end{figure}
+
+The grain emissivity at \SI{70}{\um} (Herschel PACS blue band) for the
+Cloudy simulations (colored lines) is shown in
+Figure~\ref{fig:grain-j70}, where it is compared with the same
+quantity from the grain models (dark gray symbols) of
+\citet{Draine:2007a}.  A clear difference is seen between the two sets
+of models, but this is due almost entirely to a difference in the
+assumed spectrum of the illuminating radiation, as illustrated in
+Figure~\ref{fig:sed-comparison}.  \citet{Draine:2007a} use a SED that
+is typical of the interstellar radiation field in the Galaxy, which is
+dominated by an old stellar population, which peaks in the near
+infrared, with only a small FUV contribution from younger stars (about
+8\% of the total energy density).  This is very different from the OB
+star SEDs, which are dominated by the FUV and EUV bands.  Since the
+grain absorption opacity is substantially higher at UV wavelengths
+than in the visible/IR (see Fig.~6 of Paper~II),
+% XREF: Paper II \ref{fig:cloudy-ism-dust-opacity}
+the effective grain heating efficiency of the OB star SED is
+correspondingly higher.  The light gray symbols show the effect on the
+\citet{Draine:2007a} models of multiplying the radiation field by a
+factor of \num{8} in order to offset this difference in efficiency,
+which can be seen to bring them into close agreement with the Cloudy
+models.  A further difference is that the \citet{Draine:2007a} model
+includes small PAH particles, which we do not include in our Cloudy
+models, since they are believed to be largely absent in photoionized
+regions \citep{Giard:1994a, Lebouteiller:2011a}.  However, this only
+effects the emissivity at shorter mid-infrared wavelengths
+\(< \SI{20}{\um}\).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/sed-comparison}
+  \caption{Comparison between the spectral energy distribution (SED)
+    of a typical OB star (blue line) and the interstellar radiation
+    field in the solar neighborhood (orange line).  The OB star is the
+    \SI{20}{M_\odot} model from Table~1 of Paper~I and is plotted for
+    a distance from the star of \SI{1}{pc}.  The interstellar SED is
+    from \citet{Mathis:1983a} and is multiplied by \num{80} so that
+    the total FUV-to-NIR flux is equal for the two SEDs.}
+  \label{fig:sed-comparison}
+\end{figure}
+
+In terms of the characteristic parameters introduced in
+\S~\ref{sec:energy-trapp-vers} the dimensionless radiation field
+becomes
+\begin{equation}
+  \label{eq:U-from-L4-and-Rpc}
+  U = 14.7\, L_4\, R_{\text{pc}}^{-2} \ ,
+\end{equation}
+or, alternatively, it can be expressed in terms of the ambient stream as
+\begin{equation}
+  \label{eq:U-from-ambient}
+  U = 3.01 \, n_\infty \, v_{10}^2 / x^2 \ , 
+\end{equation}
+where \(x = R_0/R_*\) is given by Paper~I's equation~(12).
+% XREF: Paper I \eqref{eq:x-cases}
+It can also be related to the radiation parameter \(\Xi\), defined in
+Paper~II's equation~(23), as
+% XREF: Paper II \eqref{eq:Xi-Prad-over-Pgas}
+\begin{equation}
+  \label{eq:U-vs-Xi}
+  U = 3.82 \, n T_4 \, \Xi \ .
+\end{equation}
+A common alternative approach to scaling the radiation field (see
+\citealp{Tielens:1985a} and citations thereof) is to normalize in the
+FUV band (\SIrange{0.0912}{0.24}{\um}), where the local interstellar
+value is known as the Habing flux \citep{Habing:1968a}:
+\begin{equation}
+  \label{eq:Habing-flux}
+  F\Hab = \SI{0.0016}{erg.s^{-1}.cm^{-2}} \ .
+\end{equation}
+The resultant dimensionless flux is often denoted by \(G_0\), and the
+relationship between \(G_0\) and \(U\) depends on the fraction
+\(f_{\text{fuv}}\) of the stellar luminosity that is emitted in the
+FUV band:
+\begin{equation}
+  \label{eq:G-vs-U}
+  G_0 = f_{\text{fuv}} \frac{u\mmp\, c}{F\Hab} \,U = (\text{\numrange{6}{10}}) \,U \ ,
+\end{equation}
+where we give the range corresponding to early O (\(f_{\text{fuv}} \approx 0.4\)) to early B (\(f_{\text{fuv}} \approx 0.7\)) stars.
+
+%% Single-photon heating of small grains
+
+\subsection{Unimportance of other heating mechanisms}
+\label{sec:unimp-other-heat}
+The grain temperature in bows around OB stars is determined
+principally by the steady-state equilibrium between the absorption of
+stellar UV radiation (heating) and the thermal emission of infrared
+radiation (cooling).  Other processes such as single-photon stochastic
+heating, Lyman~\(\alpha\) line radiation, and post-shock collisional
+heating can dominate in other contexts, but these are generally
+unimportant for circumstellar bows, as we now demonstrate.
+
+\subsubsection{Stochastic single-photon heating}
+\label{sec:stoch-single-phot}
+When the radiation field is sufficiently dilute, then a grain that
+absorbs a photon has sufficient time to radiate all that energy away
+before it absorbs another photon \citep{Duley:1973a}.  In this case,
+the emitted infrared spectrum for \(\lambda < \SI{50}{\um}\) becomes
+relatively insensitive of the energy density of the incident radiation
+\citep{Draine:2001a}.  However, this is most important for the very
+smallest grains.  From equation~(47) of \citet{Draine:2001a}, one
+finds that grains with sizes larger than
+\(a = \SI{0.005}{\um} = \SI{5}{nm}\) (the smallest size included in
+our Cloudy models) should be close to thermal equilibrium for
+\(U > 30\), which is small compared with typical bow shock values
+(\(U = \text{\numrange{e3}{e6}}\)).  As mentioned above, PAHs are not
+expected to be present in the interior of \hii{} regions.
+\citealp{Desert:1990a} found them to be strongly depleted for
+\(U > 100\) around O stars.  However, other types of ultra-small
+grains, down to sub-nm sizes \citep{Xie:2018a} may be present in bows,
+and stochastic heating \emph{would} be important for grains with
+\(a = \SI{1}{nm}\) if \(U < \num{e5}\).  Note, however that grains
+smaller than \SI{0.6}{nm} would be destroyed by sublimation after
+absorbing a single He-ionizing photon.
+
+\subsubsection{Lyman \(\alpha\) heating}
+
+On the scale of an entire \hii{} region, the dust heating is typically
+dominated by Lyman \(\alpha\) hydrogen recombination line photons, which
+are trapped by resonant scattering (e.g., \citealp{Spitzer:1978a}
+\S~9.1b).  However, this is no longer true on the much smaller scale
+of typical bow shocks.  An upper limit on the Lyman \(\alpha\) energy
+density can be found by assuming all line photons are ultimately
+destroyed by dust absorption rather than escaping in the line wings
+(e.g., \citealp{Henney:1998b}), which yields
+\begin{equation}
+  \label{eq:U-Lya}
+  U\Lya \approx 0.1 n / \kappa_{600} \ .
+\end{equation}
+This can be combined with equation~\eqref{eq:U-from-ambient} to give
+the ratio of Lyman \(\alpha\) to direct stellar radiation as
+\begin{equation}
+  \label{eq:Lya-over-stellar}
+  \frac{U\Lya}{U} \approx 0.03 \frac{x^2}{v_{10}^2 \kappa_{600}} \ .
+\end{equation}
+Taking the most favorable parameters imaginable of a slow stream
+(\(v_{10} = 2\)), very strong wind (\(x \approx 1\)), and reduced dust
+opacity (\(\kappa_{600} = 0.1\)) gives a Lyman \(\alpha\) contribution of only
+10\% of the stellar radiative energy density.  In any other
+circumstances, the fraction would be even lower.
+
+\subsubsection{Shock heating}
+\newcommand\kin{\ensuremath{_{\text{kin}}}}
+The outer shock thermalizes the kinetic energy of the ambient stream,
+which may in principle contribute to the infrared emission of the bow.
+In order for this process to be competitive, the following three
+conditions must all hold:
+\begin{enumerate}[1.]
+\item The post-shock gas must radiate efficiently with a cooling
+  length less than the bow size, see \S~3.2 of Paper~I.\@
+  % XREF Paper I \ref{sec:radi-cool-lengths}
+  This is satisfied for all but the lowest densities (Paper~I's
+  Fig.~2).
+  % XREF Paper I \ref{fig:zones-v-n-plane}
+\item A significant fraction of the shock energy must be radiated by
+  dust.  This requires that the post-shock temperature be greater than
+  \SI{e6}{K}, which requires a stream velocity
+  \(v_\infty > \SI{200}{km.s^{-1}}\) \citep{Draine:1981a}.  This also
+  coincides with the range of shock velocities where the smaller
+  grains will start to be destroyed by sputtering in the post-shock
+  gas.
+\item The kinetic energy flux through the shock must be significant,
+  compared with the fraction of the stellar radiation flux that is
+  absorbed and reprocessed by the bow shell.
+\end{enumerate}
+It turns out that the third condition is the most stringent, so we
+will consider it in detail.  The kinetic energy flux through the outer shock for an ambient stream of density \(\rho_\infty\) and velocity \(v_\infty\) is
+\begin{equation}
+  \label{eq:Fkin}
+  F\ke = \tfrac12 \rho_\infty v_\infty^3 = \tfrac12 P\shell v_\infty \ , 
+\end{equation}
+while the stellar radiative energy flux absorbed by the shell is
+\begin{equation}
+  \label{eq:Ftrap}
+  F\trap \approx \tau L / 4 \pi R_0^2 \ ,
+\end{equation}
+assuming an absorption optical depth \(\tau \ll 1\). The shell
+pressure in the WBS case can be equated to the ram pressure of the
+internal stellar wind (see
+% XREF Paper I \ref{sec:three-bow-regimes}
+\S~2.1 of Paper~I), so that the ratio of the two energy fluxes is
+\begin{equation}
+  \label{eq:F-ratio-shock}
+  \frac{F\ke}{F\trap} = \frac12 \frac{\eta\wind}{\tau} \frac{v_\infty}{c} \ .
+\end{equation}
+An upper limit to the stellar wind momentum efficiency \(\eta\wind\) is
+the shell momentum efficiency \(\eta\shell\) that is derived
+observationally in \S~\ref{sec:energy-trapp-vers}, where it is found
+that \(\eta\shell / \tau < 30\) for all sources considered.  Therefore, for
+a stream velocity \(v_\infty = \SI{200}{km.s^{-1}}\), we have
+\(F\ke/F\trap < 0.01\) and the shock-excited dust emission is still
+negligible.  Only in stars with \(v_\infty > \SI{1000}{km.s^{-1}}\) would
+the shock emission start to be significant, and such hyper-velocity
+stars \citep{Brown:2015a} do not show detectable bow shocks.
+
+So far, we have only considered the outer shock, but the inner shock
+that decelerates the stellar wind will have a velocity of
+\SIrange{1000}{3000}{km.s^{-1}} and therefore might have a significant
+kinetic energy flux by eq.~\eqref{eq:F-ratio-shock}.  However, the
+stellar wind from hot stars will be free of dust,\footnote{%
+  With the exception of Wolf-Rayet colliding wind binary systems
+  \citep{Tuthill:1999a, Callingham:2019a}.} %
+so that it would be necessary for the stellar wind protons to cross
+the contact/tangential discontinuity and deposit their energy in the
+dusty plasma of the shocked ambient stream in order for this source of
+energy to contribute to the grain emission.  This is not possible
+because the Larmor radius (see \S~5 of Paper~II)
+% XREF Paper II \ref{sec:magn-effects-grain}
+of a \SI{3000}{km.s^{-1}} proton in a \SI{1}{\micro G} field is only
+\SI{3e10}{cm}, which is millions of times smaller than typical bow
+sizes.  The magnetic field in the outer shell is unlikely to be
+smaller than \(\approx n^{1/2} \si{\micro G}\), given that Alfvén speeds of
+\SI{2}{km.s^{-1}} are typical of photoionized regions \citep{Arthur:2011a, Planck-Collaboration:2016c}
+% XREF Paper II \\ref{eq:alfven}
+and if the density were much lower than
+\SI{1}{cm^{-3}}, then the scale of the bow would be commensurately
+larger anyway.  Three-dimensional MHD simulations of bow shocks
+\citep{Katushkina:2017a, Gvaramadze:2018a} show that the magnetic
+field lines are always oriented parallel to the shell, so that high
+energy particles from the stellar wind would be efficiently reflected
+in a very thin layer and cannot contribute to grain heating.  For the
+same reason, heat conduction by electrons across the contact
+discontinuity is also greatly suppressed \citep{Meyer:2017a}.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "bs-bw-dw-03"
+%%% End:
+ % end input ./app-cloudy-dust-heating.tex
 
@@
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
-%   \caption{Discrepancies in \SI{70}{\um} emissivities that we have
-%     identified in K18.  Red crosses show the emissivities given in
-%     K18's Table~2 as a function of the radiation field \(U\), while
-%     the solid gray line shows the emissivities that they claim to be
-%     using from \citet{Draine:2007a}.  The dashed line shows the
-%     emissivities that we believe they should have been using, which
-%     correct for the marked difference in spectral energy distribution
-%     between OB stars and the Galactic interstellar radiation field
-%     (see \S~\ref{sec:grain-temp-emiss}).}
-%   \label{fig:k18-emissivity}
-% \end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
+  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
+    identified in K18.  Red crosses show the emissivities given in
+    K18's Table~2 as a function of the radiation field \(U\), while
+    the solid gray line shows the emissivities that they claim to be
+    using from \citet{Draine:2007a}.  The dashed line shows the
+    emissivities that we believe they should have been using, which
+    correct for the marked difference in spectral energy distribution
+    between OB stars and the Galactic interstellar radiation field
+    (see \S~\ref{sec:grain-temp-emiss}).}
+  \label{fig:k18-emissivity}
+\end{figure}
 
@@
 that the \citet{Draine:2007a} models require modification when applied
-to grains around OB stars.  A further discrepancy arises due to an
-interpolation error in K18, which resulted in values of \(j_{70}\)
-being overestimated by about a factor of 2 for sources with weak
-radiation fields (H.~Kobulnicky, priv.~comm.).
-
-% In addition, when attempting to replicate
-% the K18 values of \(j_{70}\) we find that they only follow the
-% \citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
-% constant value for weaker radiation fields.
-
-% The situation is
-% summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
-% directly from Table~2 of K18 are shown by red crosses, the values they
-% claim to be using are shown by the gray solid line (this curve is
-% consistent with that shown in K18 Fig.~2), and the values they
-% \textit{should} have been using are shown by the gray dashed
-% line. Note that this correction may also resolve the color temperature
-% discrepancy noted by \citet{Kobulnicky:2017a}.
+to grains around OB stars.  In addition, when attempting to replicate
+the K18 values of \(j_{70}\) we find that they only follow the
+\citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
+constant value for weaker radiation fields.  The situation is
+summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
+directly from Table~2 of K18 are shown by red crosses, the values they
+claim to be using are shown by the gray solid line (this curve is
+consistent with that shown in K18 Fig.~2), and the values they
+\textit{should} have been using are shown by the gray dashed
+line. Note that this correction may also resolve the color temperature
+discrepancy noted by \citet{Kobulnicky:2017a}.
+
+% If we replaced K3 with M3, then mass loss rates would be reduced by 1.86 across the board
 
@@
 unaffected but that sources with stronger radiation fields (lighter
-shading) have their mass-loss increasingly reduced.
-% , as could be
-% surmised from Figure~\ref{fig:k18-emissivity}.
-The average reduction is by a factor of about two.
+shading) have their mass-loss increasingly reduced, as could be
+surmised from Figure~\ref{fig:k18-emissivity}.  The average reduction
+is by a factor of about two.
 
@@
 In either case, the bow is expected to be smaller than \SI{0.1}{pc}
-for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~8 of
+for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~6 of
 Paper~I.\@
@@
 %%% End:
+ % end input ./sec-observational-diagnostics.tex
+
+\section{Summary}
+\label{sec:conclusions}
+
+We have proposed a novel diagnostic method, the \(\tau\)-\(\eta\shell\)
+diagram, for analyzing observations of stellar bow shocks around OB
+stars, which allows discrimination between radiation-supported and
+wind-supported bows.  Our principal results are as follows:
+\begin{enumerate}[1.]
+\item The UV optical depth \(\tau\) of the bow shell can be estimated
+  from the observed infrared shell luminosity \(L\IR\) and stellar
+  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\)
+  (\S~\ref{sec:energy-trapp-vers}).
+\item The shell momentum efficiency \(\eta\shell\), which is the
+  fraction of stellar radiative momentum that is transferred to the
+  shell either directly or indirectly (via stellar wind), can be
+  estimated from \(\tau\) and the observed shell radius \(R_0\), after
+  making some auxiliary assumptions about the physical conditions in
+  the shell (\S~\ref{sec:energy-trapp-vers}).
+\item By comparing \(\tau\) and \(\eta\shell\), it is possible to
+  discriminate between three regimes (\S~\ref{sec:eta-tau-diagnostic}
+  and see Paper~I): wind-supported bow shocks
+  (\(\eta\shell \gg \tau\)), radiation-supported bow waves
+  (\(\eta\shell \sim \tau < 1\)), and radiation-supported bow shocks
+  (\(\eta\shell \sim \tau > 1\)).
+\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a
+  fourth regime of dust waves, where gas--grain collisional coupling
+  breaks down (see Paper~II).
+\item By analyzing a published sample of 20 mid-infrared bow shock
+  candidates \citep[K18]{Kobulnicky:2018a}, plus additional compact
+  bows in Orion, we find 4 strong candidates for radiation-supported
+  bow waves plus 3 marginal cases (\S\S~\ref{sec:cand-radi-supp} and
+  \ref{sec:comm-prop-cand}).  No strong candidates for dust waves are
+  found.
+\item For wind-supported bow shocks, the stellar wind mass-loss rate
+  can be found from \(\tau\) and \(\eta\shell\)
+  (\S~\ref{sec:mass-loss-determ}). We compare this method with the
+  previously proposed method of K18 (\S~\ref{app:bow-shock-data}) and
+  suggest a correction to the dust emissivities used in the latter,
+  which reduces the mass-loss rates by a factor of about 2.
+\item After this correction, the two mass-loss methods agree well for
+  small bows (\(R_0 \le \SI{0.3}{pc}\)), but the
+  \(\tau\)--\(\eta\shell\) method under-predicts the mass-loss rate by
+  up to a factor of 10 for larger bows, which also tend to have
+  relatively thin shells (\S~\ref{sec:underst-diff-betw}).  This
+  discrepancy could be eliminated by extending the
+  \(\tau\)--\(\eta\shell\) method to include the observed shell
+  thickness.
+\item Disruption of the largest dust grains by rotational torques in
+  the strong circumstellar radiation field is predicted to have a
+  relatively modest effect on the optical properties of the dust
+  mixture (\S~\ref{sec:evolution-grain-size}), increasing the UV
+  opacity by about 50\%.
+\item The bow source KGK2010~2 is a low-luminosity B~star with an
+  anomalously high apparent mass-loss rate.  This discrepancy could be
+  eliminated if the bow shell has trapped the ionization front and is
+  predominantly neutral, in which case it would become yet another
+  candidate for radiation support.
+\end{enumerate}
+
+\section*{Acknowledgements}
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grant Programa de Apoyo a Proyectos de Investigación e
+Inovación Tecnológica IN107019.  This work has made extensive use of
+Python language libraries from the SciPy \citep{Jones:2001a}, AstroPy
+\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a} and
+Pandas \citep{McKinney:2010a} projects.  We thank Chip Kobulnicky for
+sharing results in advance of publication.
+
+\bibliographystyle{mnras}
+\begin{thebibliography}{}
+\makeatletter
+\relax
+\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
+\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
+  {\mn@doi@[]}}
+\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
+  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
+  \endgroup}
+\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
+\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
+\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
+  {dblp:#1}}
+\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
+  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
+  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
+  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
+  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}
+
+\bibitem[\protect\citeauthoryear{{Acreman}, {Stevens}  \& {Harries}}{{Acreman}
+  et~al.}{2016}]{Acreman:2016a}
+{Acreman} D.~M.,  {Stevens} I.~R.,   {Harries} T.~J.,  2016, \mnras, 456, 136
+
+\bibitem[\protect\citeauthoryear{{Alecian} et~al.,}{{Alecian}
+  et~al.}{2013}]{Alecian:2013a}
+{Alecian} E.,  et~al., 2013, \mnras, 429, 1001
+
+\bibitem[\protect\citeauthoryear{{Arthur} \& {Hoare}}{{Arthur} \&
+  {Hoare}}{2006}]{Arthur:2006a}
+{Arthur} S.~J.,  {Hoare} M.~G.,  2006, \apjs, 165, 283
+
+\bibitem[\protect\citeauthoryear{{Arthur}, {Henney}, {Mellema}, {de Colle}  \&
+  {V{\'a}zquez-Semadeni}}{{Arthur} et~al.}{2011}]{Arthur:2011a}
+{Arthur} S.~J.,  {Henney} W.~J.,  {Mellema} G.,  {de Colle} F.,
+  {V{\'a}zquez-Semadeni} E.,  2011, \mnras, 414, 1747
+
+\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
+  Collaboration} et~al.}{2013}]{Astropy-Collaboration:2013a}
+{Astropy Collaboration} et~al., 2013, \aap, 558, A33
+
+\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
+  Collaboration} et~al.}{2018}]{Astropy-Collaboration:2018a}
+{Astropy Collaboration} et~al., 2018, \aj, 156, 123
+
+\bibitem[\protect\citeauthoryear{{Balog} et~al.,}{{Balog}
+  et~al.}{2014}]{Balog:2014a}
+{Balog} Z.,  et~al., 2014, Experimental Astronomy, 37, 129
+
+\bibitem[\protect\citeauthoryear{{Beerer} et~al.,}{{Beerer}
+  et~al.}{2010}]{Beerer:2010a}
+{Beerer} I.~M.,  et~al., 2010, \apj, 720, 679
+
+\bibitem[\protect\citeauthoryear{{Beitia-Antero} \& {Gómez de
+  Castro}}{{Beitia-Antero} \& {Gómez de Castro}}{2017}]{Beitia-Antero:2017a}
+{Beitia-Antero} L.,  {Gómez de Castro} A.~I.,  2017, \mnras, 469, 2531
+
+\bibitem[\protect\citeauthoryear{{Blaauw}}{{Blaauw}}{1961}]{Blaauw:1961a}
+{Blaauw} A.,  1961, \bain, 15, 265
+
+\bibitem[\protect\citeauthoryear{{Bodensteiner}, {Baade}, {Greiner}  \&
+  {Langer}}{{Bodensteiner} et~al.}{2018}]{Bodensteiner:2018a}
+{Bodensteiner} J.,  {Baade} D.,  {Greiner} J.,   {Langer} N.,  2018, \aap, 618,
+  A110
+
+\bibitem[\protect\citeauthoryear{{Brand} \& {Blitz}}{{Brand} \&
+  {Blitz}}{1993}]{Brand:1993a}
+{Brand} J.,  {Blitz} L.,  1993, \aap, 275, 67
+
+\bibitem[\protect\citeauthoryear{{Brown}}{{Brown}}{2015}]{Brown:2015a}
+{Brown} W.~R.,  2015, \araa, 53, 15
+
+\bibitem[\protect\citeauthoryear{{Callingham}, {Tuthill}, {Pope}, {Williams},
+  {Crowther}, {Edwards}, {Norris}  \& {Kedziora-Chudczer}}{{Callingham}
+  et~al.}{2019}]{Callingham:2019a}
+{Callingham} J.~R.,  {Tuthill} P.~G.,  {Pope} B.~J.~S.,  {Williams} P.~M.,
+  {Crowther} P.~A.,  {Edwards} M.,  {Norris} B.,   {Kedziora-Chudczer} L.,
+  2019, Nature Astronomy, 3, 82
+
+\bibitem[\protect\citeauthoryear{{Canto}, {Raga}  \& {Wilkin}}{{Canto}
+  et~al.}{1996}]{Canto:1996}
+{Canto} J.,  {Raga} A.~C.,   {Wilkin} F.~P.,  1996, \mn@doi [\apj]
+  {10.1086/177820}, \href {http://adsabs.harvard.edu/abs/1996ApJ...469..729C}
+  {469, 729}
+
+\bibitem[\protect\citeauthoryear{{Cantó}, {Raga}  \& {González}}{{Cantó}
+  et~al.}{2005}]{Canto:2005a}
+{Cantó} J.,  {Raga} A.~C.,   {González} R.,  2005, \rmxaa, 41, 101
+
+\bibitem[\protect\citeauthoryear{{Comeron} \& {Kaper}}{{Comeron} \&
+  {Kaper}}{1998}]{Comeron:1998a}
+{Comeron} F.,  {Kaper} L.,  1998, \aap, 338, 273
+
+\bibitem[\protect\citeauthoryear{{Cordes}, {Romani}  \& {Lundgren}}{{Cordes}
+  et~al.}{1993}]{Cordes:1993a}
+{Cordes} J.~M.,  {Romani} R.~W.,   {Lundgren} S.~C.,  1993, \nat, 362, 133
+
+\bibitem[\protect\citeauthoryear{{Cox} et~al.,}{{Cox} et~al.}{2012}]{Cox:2012a}
+{Cox} N.~L.~J.,  et~al., 2012, \aap, 537, A35
+
+\bibitem[\protect\citeauthoryear{{Desert}, {Boulanger}  \& {Puget}}{{Desert}
+  et~al.}{1990}]{Desert:1990a}
+{Desert} F.-X.,  {Boulanger} F.,   {Puget} J.~L.,  1990, \aap, 237, 215
+
+\bibitem[\protect\citeauthoryear{{Draine}}{{Draine}}{1981}]{Draine:1981a}
+{Draine} B.~T.,  1981, \apj, 245, 880
+
+\bibitem[\protect\citeauthoryear{{Draine} \& {Li}}{{Draine} \&
+  {Li}}{2001}]{Draine:2001a}
+{Draine} B.~T.,  {Li} A.,  2001, \apj, 551, 807
+
+\bibitem[\protect\citeauthoryear{{Draine} \& {Li}}{{Draine} \&
+  {Li}}{2007}]{Draine:2007a}
+{Draine} B.~T.,  {Li} A.,  2007, \apj, 657, 810
+
+\bibitem[\protect\citeauthoryear{{Duley}}{{Duley}}{1973}]{Duley:1973a}
+{Duley} W.~W.,  1973, \apss, 23, 43
+
+\bibitem[\protect\citeauthoryear{{Engelbracht} et~al.,}{{Engelbracht}
+  et~al.}{2007}]{Engelbracht:2007a}
+{Engelbracht} C.~W.,  et~al., 2007, \pasp, 119, 994
+
+\bibitem[\protect\citeauthoryear{{Fairlamb}, {Oudmaijer}, {Mendigut{\'{\i}}a},
+  {Ilee}  \& {van den Ancker}}{{Fairlamb} et~al.}{2015}]{Fairlamb:2015a}
+{Fairlamb} J.~R.,  {Oudmaijer} R.~D.,  {Mendigut{\'{\i}}a} I.,  {Ilee} J.~D.,
+  {van den Ancker} M.~E.,  2015, \mnras, 453, 976
+
+\bibitem[\protect\citeauthoryear{{Ferland} et~al.,}{{Ferland}
+  et~al.}{2013}]{Ferland:2013a}
+{Ferland} G.~J.,  et~al., 2013, \rmxaa, 49, 137
+
+\bibitem[\protect\citeauthoryear{{Ferland} et~al.,}{{Ferland}
+  et~al.}{2017}]{Ferland:2017a}
+{Ferland} G.~J.,  et~al., 2017, \rmxaa, 53, 385
+
+\bibitem[\protect\citeauthoryear{{Fitzpatrick} \& {Massa}}{{Fitzpatrick} \&
+  {Massa}}{2007}]{Fitzpatrick:2007a}
+{Fitzpatrick} E.~L.,  {Massa} D.,  2007, \apj, 663, 320
+
+\bibitem[\protect\citeauthoryear{{Gaia Collaboration} et~al.,}{{Gaia
+  Collaboration} et~al.}{2016}]{Gaia-Collaboration:2016a}
+{Gaia Collaboration} et~al., 2016, \aap, 595, A1
+
+\bibitem[\protect\citeauthoryear{{Gaia Collaboration} et~al.,}{{Gaia
+  Collaboration} et~al.}{2018}]{Gaia-Collaboration:2018a}
+{Gaia Collaboration} et~al., 2018, \aap, 616, A1
+
+\bibitem[\protect\citeauthoryear{{Giard}, {Bernard}, {Lacombe}, {Normand}  \&
+  {Rouan}}{{Giard} et~al.}{1994}]{Giard:1994a}
+{Giard} M.,  {Bernard} J.~P.,  {Lacombe} F.,  {Normand} P.,   {Rouan} D.,
+  1994, \aap, 291, 239
+
+\bibitem[\protect\citeauthoryear{{Gull} \& {Sofia}}{{Gull} \&
+  {Sofia}}{1979}]{Gull:1979a}
+{Gull} T.~R.,  {Sofia} S.,  1979, \apj, 230, 782
+
+\bibitem[\protect\citeauthoryear{{Gvaramadze}, {Langer}  \&
+  {Mackey}}{{Gvaramadze} et~al.}{2012}]{Gvaramadze:2012a}
+{Gvaramadze} V.~V.,  {Langer} N.,   {Mackey} J.,  2012, \mnras, 427, L50
+
+\bibitem[\protect\citeauthoryear{{Gvaramadze}, {Alexashov}, {Katushkina}  \&
+  {Kniazev}}{{Gvaramadze} et~al.}{2018}]{Gvaramadze:2018a}
+{Gvaramadze} V.~V.,  {Alexashov} D.~B.,  {Katushkina} O.~A.,   {Kniazev} A.~Y.,
+   2018, \mnras, 474, 4421
+
+\bibitem[\protect\citeauthoryear{{Habing}}{{Habing}}{1968}]{Habing:1968a}
+{Habing} H.~J.,  1968, \bain, 19, 421
+
+\bibitem[\protect\citeauthoryear{{Hartigan}, {Reiter}, {Smith}  \&
+  {Bally}}{{Hartigan} et~al.}{2015}]{Hartigan:2015a}
+{Hartigan} P.,  {Reiter} M.,  {Smith} N.,   {Bally} J.,  2015, \aj, 149, 101
+
+\bibitem[\protect\citeauthoryear{{Hawley}}{{Hawley}}{1978}]{Hawley:1978a}
+{Hawley} S.~A.,  1978, \apj, 224, 417
+
+\bibitem[\protect\citeauthoryear{{Henney}}{{Henney}}{2002}]{Henney:2002a}
+{Henney} W.~J.,  2002, Revista Mexicana de Astronomia y Astrofisica, 38, 71
+
+\bibitem[\protect\citeauthoryear{{Henney} \& {Arthur}}{{Henney} \&
+  {Arthur}}{1998}]{Henney:1998b}
+{Henney} W.~J.,  {Arthur} S.~J.,  1998, \aj, 116, 322
+
+\bibitem[\protect\citeauthoryear{{Henney} \& {Arthur}}{{Henney} \&
+  {Arthur}}{2019a}]{Henney:2019a}
+{Henney} W.~J.,  {Arthur} S.~J.,  2019a, arXiv e-prints, \href
+  {http://adsabs.harvard.edu/abs/2019arXiv190303737H} {1903.03737 MNRAS
+  submitted (Paper I)}
+
+\bibitem[\protect\citeauthoryear{{Henney} \& {Arthur}}{{Henney} \&
+  {Arthur}}{2019b}]{Henney:2019b}
+{Henney} W.~J.,  {Arthur} S.~J.,  2019b, arXiv e-prints, \href
+  {http://adsabs.harvard.edu/abs/2019arXiv190307774H} {1903.07774 MNRAS
+  submitted (Paper II)}
+
+\bibitem[\protect\citeauthoryear{{Hirabayashi}}{{Hirabayashi}}{2015}]{Hirabayashi:2015a}
+{Hirabayashi} M.,  2015, \mnras, 454, 2249
+
+\bibitem[\protect\citeauthoryear{{Hoang}, {Tram}, {Lee}  \& {Ahn}}{{Hoang}
+  et~al.}{2018}]{Hoang:2018a}
+{Hoang} T.,  {Tram} L.~N.,  {Lee} H.,   {Ahn} S.-H.,  2018, arXiv, \href
+  {http://adsabs.harvard.edu/abs/2018arXiv181005557H} {}
+
+\bibitem[\protect\citeauthoryear{{Hoogerwerf}, {de Bruijne}  \& {de
+  Zeeuw}}{{Hoogerwerf} et~al.}{2001}]{Hoogerwerf:2001a}
+{Hoogerwerf} R.,  {de Bruijne} J.~H.~J.,   {de Zeeuw} P.~T.,  2001, \aap, 365,
+  49
+
+\bibitem[\protect\citeauthoryear{{Huthoff} \& {Kaper}}{{Huthoff} \&
+  {Kaper}}{2002}]{Huthoff:2002a}
+{Huthoff} F.,  {Kaper} L.,  2002, \aap, 383, 999
+
+\bibitem[\protect\citeauthoryear{{Jewitt}, {Agarwal}, {Li}, {Weaver},
+  {Mutchler}  \& {Larson}}{{Jewitt} et~al.}{2014}]{Jewitt:2014a}
+{Jewitt} D.,  {Agarwal} J.,  {Li} J.,  {Weaver} H.,  {Mutchler} M.,   {Larson}
+  S.,  2014, \apjl, 784, L8
+
+\bibitem[\protect\citeauthoryear{Jones, Oliphant, Peterson  et~al.}{Jones
+  et~al.}{2019}]{Jones:2001a}
+Jones E.,  Oliphant T.,  Peterson P.,   et~al., 2001--2019, {SciPy}: Open
+  source scientific tools for {Python}, \url {http://www.scipy.org/}
+
+\bibitem[\protect\citeauthoryear{{Katushkina}, {Alexashov}, {Izmodenov}  \&
+  {Gvaramadze}}{{Katushkina} et~al.}{2017}]{Katushkina:2017a}
+{Katushkina} O.~A.,  {Alexashov} D.~B.,  {Izmodenov} V.~V.,   {Gvaramadze}
+  V.~V.,  2017, \mnras, 465, 1573
+
+\bibitem[\protect\citeauthoryear{{Katushkina}, {Alexashov}, {Gvaramadze}  \&
+  {Izmodenov}}{{Katushkina} et~al.}{2018}]{Katushkina:2018a}
+{Katushkina} O.~A.,  {Alexashov} D.~B.,  {Gvaramadze} V.~V.,   {Izmodenov}
+  V.~V.,  2018, \mnras, 473, 1576
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Gilbert}  \&
+  {Kiminki}}{{Kobulnicky} et~al.}{2010}]{Kobulnicky:2010a}
+{Kobulnicky} H.~A.,  {Gilbert} I.~J.,   {Kiminki} D.~C.,  2010, \apj, 710, 549
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Lundquist}, {Bhattacharjee}  \&
+  {Kerton}}{{Kobulnicky} et~al.}{2012}]{Kobulnicky:2012a}
+{Kobulnicky} H.~A.,  {Lundquist} M.~J.,  {Bhattacharjee} A.,   {Kerton} C.~R.,
+  2012, \aj, 143, 71
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky} et~al.,}{{Kobulnicky}
+  et~al.}{2016}]{Kobulnicky:2016a}
+{Kobulnicky} H.~A.,  et~al., 2016, \apjs, 227, 18
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Schurhammer}, {Baldwin},
+  {Chick}, {Dixon}, {Lee}  \& {Povich}}{{Kobulnicky}
+  et~al.}{2017}]{Kobulnicky:2017a}
+{Kobulnicky} H.~A.,  {Schurhammer} D.~P.,  {Baldwin} D.~J.,  {Chick} W.~T.,
+  {Dixon} D.~M.,  {Lee} D.,   {Povich} M.~S.,  2017, \aj, 154, 201
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Chick}  \&
+  {Povich}}{{Kobulnicky} et~al.}{2018}]{Kobulnicky:2018a}
+{Kobulnicky} H.~A.,  {Chick} W.~T.,   {Povich} M.~S.,  2018, \apj, 856, 74
+  (K18)
+
+\bibitem[\protect\citeauthoryear{{Krti{\v c}ka}}{{Krti{\v
+  c}ka}}{2014}]{Krticka:2014a}
+{Krti{\v c}ka} J.,  2014, \aap, 564, A70
+
+\bibitem[\protect\citeauthoryear{{Krtička} \& {Kubát}}{{Krtička} \&
+  {Kubát}}{2017}]{Krticka:2017a}
+{Krtička} J.,  {Kubát} J.,  2017, \aap, 606, A31
+
+\bibitem[\protect\citeauthoryear{{Lanz} \& {Hubeny}}{{Lanz} \&
+  {Hubeny}}{2007}]{Lanz:2007a}
+{Lanz} T.,  {Hubeny} I.,  2007, \apjs, 169, 83
+
+\bibitem[\protect\citeauthoryear{{Lebouteiller}, {Brandl}, {Bernard-Salas},
+  {Devost}  \& {Houck}}{{Lebouteiller} et~al.}{2007}]{Lebouteiller:2007a}
+{Lebouteiller} V.,  {Brandl} B.,  {Bernard-Salas} J.,  {Devost} D.,   {Houck}
+  J.~R.,  2007, \apj, 665, 390
+
+\bibitem[\protect\citeauthoryear{{Lebouteiller}, {Bernard-Salas}, {Whelan},
+  {Brandl}, {Galliano}, {Charmandaris}, {Madden}  \& {Kunth}}{{Lebouteiller}
+  et~al.}{2011}]{Lebouteiller:2011a}
+{Lebouteiller} V.,  {Bernard-Salas} J.,  {Whelan} D.~G.,  {Brandl} B.,
+  {Galliano} F.,  {Charmandaris} V.,  {Madden} S.,   {Kunth} D.,  2011, \apj,
+  728, 45
+
+\bibitem[\protect\citeauthoryear{{Lee}, {Murray}  \& {Rahman}}{{Lee}
+  et~al.}{2012}]{Lee:2012a}
+{Lee} E.~J.,  {Murray} N.,   {Rahman} M.,  2012, \apj, 752, 146
+
+\bibitem[\protect\citeauthoryear{{Luri} et~al.,}{{Luri}
+  et~al.}{2018}]{Luri:2018a}
+{Luri} X.,  et~al., 2018, \aap, 616, A9
+
+\bibitem[\protect\citeauthoryear{{Mackey}, {Gvaramadze}, {Mohamed}  \&
+  {Langer}}{{Mackey} et~al.}{2015}]{Mackey:2015a}
+{Mackey} J.,  {Gvaramadze} V.~V.,  {Mohamed} S.,   {Langer} N.,  2015, \aap,
+  573, A10
+
+\bibitem[\protect\citeauthoryear{{Mackey}, {Haworth}, {Gvaramadze}, {Mohamed},
+  {Langer}  \& {Harries}}{{Mackey} et~al.}{2016}]{Mackey:2016a}
+{Mackey} J.,  {Haworth} T.~J.,  {Gvaramadze} V.~V.,  {Mohamed} S.,  {Langer}
+  N.,   {Harries} T.~J.,  2016, \aap, 586, A114
+
+\bibitem[\protect\citeauthoryear{{Marcolino}, {Bouret}, {Martins}, {Hillier},
+  {Lanz}  \& {Escolano}}{{Marcolino} et~al.}{2009}]{Marcolino:2009a}
+{Marcolino} W.~L.~F.,  {Bouret} J.-C.,  {Martins} F.,  {Hillier} D.~J.,  {Lanz}
+  T.,   {Escolano} C.,  2009, \aap, 498, 837
+
+\bibitem[\protect\citeauthoryear{{Martins}, {Schaerer}  \& {Hillier}}{{Martins}
+  et~al.}{2005}]{Martins:2005a}
+{Martins} F.,  {Schaerer} D.,   {Hillier} D.~J.,  2005, \aap, 436, 1049
+
+\bibitem[\protect\citeauthoryear{{Mathis}, {Mezger}  \& {Panagia}}{{Mathis}
+  et~al.}{1983}]{Mathis:1983a}
+{Mathis} J.~S.,  {Mezger} P.~G.,   {Panagia} N.,  1983, \aap, 128, 212
+
+\bibitem[\protect\citeauthoryear{{Matsuda}, {Fujimoto}, {Shima}, {Sawada}  \&
+  {Inaguchi}}{{Matsuda} et~al.}{1989}]{Matsuda:1989a}
+{Matsuda} T.,  {Fujimoto} Y.,  {Shima} E.,  {Sawada} K.,   {Inaguchi} T.,
+  1989, Progress of Theoretical Physics, 81, 810
+
+\bibitem[\protect\citeauthoryear{{Matzner}}{{Matzner}}{2002}]{Matzner:2002a}
+{Matzner} C.~D.,  2002, \apj, 566, 302
+
+\bibitem[\protect\citeauthoryear{McKinney}{McKinney}{2010}]{McKinney:2010a}
+McKinney W.,  2010, in van~der Walt S.,  Millman J.,  eds, Proceedings of the
+  9th Python in Science Conference. pp 51 -- 56
+
+\bibitem[\protect\citeauthoryear{{Meyer}, {Mackey}, {Langer}, {Gvaramadze},
+  {Mignone}, {Izzard}  \& {Kaper}}{{Meyer} et~al.}{2014}]{Meyer:2014b}
+{Meyer} D.~M.-A.,  {Mackey} J.,  {Langer} N.,  {Gvaramadze} V.~V.,  {Mignone}
+  A.,  {Izzard} R.~G.,   {Kaper} L.,  2014, \mnras, 444, 2754
+
+\bibitem[\protect\citeauthoryear{{Meyer}, {van Marle}, {Kuiper}  \&
+  {Kley}}{{Meyer} et~al.}{2016}]{Meyer:2016a}
+{Meyer} D.~M.-A.,  {van Marle} A.-J.,  {Kuiper} R.,   {Kley} W.,  2016, \mnras,
+  459, 1146
+
+\bibitem[\protect\citeauthoryear{{Meyer}, {Mignone}, {Kuiper}, {Raga}  \&
+  {Kley}}{{Meyer} et~al.}{2017}]{Meyer:2017a}
+{Meyer} D.~M.-A.,  {Mignone} A.,  {Kuiper} R.,  {Raga} A.~C.,   {Kley} W.,
+  2017, \mnras, 464, 3229
+
+\bibitem[\protect\citeauthoryear{{Najarro}, {Hanson}  \& {Puls}}{{Najarro}
+  et~al.}{2011}]{Najarro:2011a}
+{Najarro} F.,  {Hanson} M.~M.,   {Puls} J.,  2011, \aap, 535, A32
+
+\bibitem[\protect\citeauthoryear{{Ngoumou}, {Preibisch}, {Ratzka}  \&
+  {Burkert}}{{Ngoumou} et~al.}{2013}]{Ngoumou:2013a}
+{Ngoumou} J.,  {Preibisch} T.,  {Ratzka} T.,   {Burkert} A.,  2013, \apj, 769,
+  139
+
+\bibitem[\protect\citeauthoryear{{Nieva}}{{Nieva}}{2013}]{Nieva:2013a}
+{Nieva} M.-F.,  2013, \aap, 550, A26
+
+\bibitem[\protect\citeauthoryear{{O'Dell}}{{O'Dell}}{2001}]{ODell:2001c}
+{O'Dell} C.~R.,  2001, \aj, 122, 2662
+
+\bibitem[\protect\citeauthoryear{{Ochsendorf} \& {Tielens}}{{Ochsendorf} \&
+  {Tielens}}{2015}]{Ochsendorf:2015a}
+{Ochsendorf} B.~B.,  {Tielens} A.~G.~G.~M.,  2015, \aap, 576, A2
+
+\bibitem[\protect\citeauthoryear{{Ochsendorf}, {Cox}, {Krijt}, {Salgado},
+  {Bern{\'e}}, {Bernard}, {Kaper}  \& {Tielens}}{{Ochsendorf}
+  et~al.}{2014}]{Ochsendorf:2014b}
+{Ochsendorf} B.~B.,  {Cox} N.~L.~J.,  {Krijt} S.,  {Salgado} F.,  {Bern{\'e}}
+  O.,  {Bernard} J.~P.,  {Kaper} L.,   {Tielens} A.~G.~G.~M.,  2014, \aap, 563,
+  A65
+
+\bibitem[\protect\citeauthoryear{{Pecaut} \& {Mamajek}}{{Pecaut} \&
+  {Mamajek}}{2013}]{Pecaut:2013a}
+{Pecaut} M.~J.,  {Mamajek} E.~E.,  2013, \apjs, 208, 9
+
+\bibitem[\protect\citeauthoryear{{Peri}, {Benaglia}, {Brookes}, {Stevens}  \&
+  {Isequilla}}{{Peri} et~al.}{2012}]{Peri:2012a}
+{Peri} C.~S.,  {Benaglia} P.,  {Brookes} D.~P.,  {Stevens} I.~R.,   {Isequilla}
+  N.~L.,  2012, \aap, 538, A108
+
+\bibitem[\protect\citeauthoryear{{Peri}, {Benaglia}  \& {Isequilla}}{{Peri}
+  et~al.}{2015}]{Peri:2015a}
+{Peri} C.~S.,  {Benaglia} P.,   {Isequilla} N.~L.,  2015, \aap, 578, A45
+
+\bibitem[\protect\citeauthoryear{{Petit}, {Wade}, {Drissen}, {Montmerle}  \&
+  {Alecian}}{{Petit} et~al.}{2008}]{Petit:2008a}
+{Petit} V.,  {Wade} G.~A.,  {Drissen} L.,  {Montmerle} T.,   {Alecian} E.,
+  2008, \mnras, 387, L23
+
+\bibitem[\protect\citeauthoryear{{Planck Collaboration} et~al.,}{{Planck
+  Collaboration} et~al.}{2016}]{Planck-Collaboration:2016c}
+{Planck Collaboration} et~al., 2016, \aap, 586, A137
+
+\bibitem[\protect\citeauthoryear{{Pogodin}, {Malanushenko}, {Kozlova},
+  {Tarasova}  \& {Franco}}{{Pogodin} et~al.}{2006}]{Pogodin:2006a}
+{Pogodin} M.~A.,  {Malanushenko} V.~P.,  {Kozlova} O.~V.,  {Tarasova} T.~N.,
+  {Franco} G.~A.~P.,  2006, \aap, 452, 551
+
+\bibitem[\protect\citeauthoryear{{Povich}, {Benjamin}, {Whitney}, {Babler},
+  {Indebetouw}, {Meade}  \& {Churchwell}}{{Povich} et~al.}{2008}]{Povich:2008a}
+{Povich} M.~S.,  {Benjamin} R.~A.,  {Whitney} B.~A.,  {Babler} B.~L.,
+  {Indebetouw} R.,  {Meade} M.~R.,   {Churchwell} E.,  2008, \apj, 689, 242
+
+\bibitem[\protect\citeauthoryear{{Prišegen}}{{Prišegen}}{2019}]{Prisegen:2019a}
+{Prišegen} M.,  2019, \aap, 621, A37
+
+\bibitem[\protect\citeauthoryear{{Quireza}, {Rood}, {Balser}  \&
+  {Bania}}{{Quireza} et~al.}{2006a}]{Quireza:2006a}
+{Quireza} C.,  {Rood} R.~T.,  {Balser} D.~S.,   {Bania} T.~M.,  2006a, \apjs,
+  165, 338
+
+\bibitem[\protect\citeauthoryear{{Quireza}, {Rood}, {Bania}, {Balser}  \&
+  {Maciel}}{{Quireza} et~al.}{2006b}]{Quireza:2006b}
+{Quireza} C.,  {Rood} R.~T.,  {Bania} T.~M.,  {Balser} D.~S.,   {Maciel} W.~J.,
+   2006b, \apj, 653, 1226
+
+\bibitem[\protect\citeauthoryear{{Raga}, {Noriega-Crespo}, {Cantó}, {Steffen},
+  {van Buren}, {Mellema}  \& {Lundqvist}}{{Raga} et~al.}{1997}]{Raga:1997a}
+{Raga} A.~C.,  {Noriega-Crespo} A.,  {Cantó} J.,  {Steffen} W.,  {van Buren}
+  D.,  {Mellema} G.,   {Lundqvist} P.,  1997, \rmxaa, 33, 73
+
+\bibitem[\protect\citeauthoryear{{Robberto} et~al.,}{{Robberto}
+  et~al.}{2005}]{Robberto:2005a}
+{Robberto} M.,  et~al., 2005, \aj, 129, 1534
+
+\bibitem[\protect\citeauthoryear{{Salgado} et~al.,}{{Salgado}
+  et~al.}{2012}]{Salgado:2012a}
+{Salgado} F.,  et~al., 2012, \apjl, 749, L21
+
+\bibitem[\protect\citeauthoryear{{Salgado}, {Berné}, {Adams}, {Herter},
+  {Keller}  \& {Tielens}}{{Salgado} et~al.}{2016}]{Salgado:2016a}
+{Salgado} F.,  {Berné} O.,  {Adams} J.~D.,  {Herter} T.~L.,  {Keller} L.~D.,
+  {Tielens} A.~G.~G.~M.,  2016, \apj, 830, 118
+
+\bibitem[\protect\citeauthoryear{{Schlafly} et~al.,}{{Schlafly}
+  et~al.}{2016}]{Schlafly:2016a}
+{Schlafly} E.~F.,  et~al., 2016, \apj, 821, 78
+
+\bibitem[\protect\citeauthoryear{{Schneider} et~al.,}{{Schneider}
+  et~al.}{2016}]{Schneider:2016a}
+{Schneider} N.,  et~al., 2016, \aap, 591, A40
+
+\bibitem[\protect\citeauthoryear{{Sexton}, {Povich}, {Smith}, {Babler}, {Meade}
+   \& {Rudolph}}{{Sexton} et~al.}{2015}]{Sexton:2015b}
+{Sexton} R.~O.,  {Povich} M.~S.,  {Smith} N.,  {Babler} B.~L.,  {Meade} M.~R.,
+   {Rudolph} A.~L.,  2015, \mnras, 446, 1047
+
+\bibitem[\protect\citeauthoryear{{Simón-D{\'{\i}}az}
+  et~al.,}{{Simón-D{\'{\i}}az} et~al.}{2015}]{Simon-Diaz:2015a}
+{Simón-D{\'{\i}}az} S.,  et~al., 2015, \apj, 799, 169
+
+\bibitem[\protect\citeauthoryear{{Smith}, {Bally}, {Shuping}, {Morris}  \&
+  {Kassis}}{{Smith} et~al.}{2005}]{Smith:2005a}
+{Smith} N.,  {Bally} J.,  {Shuping} R.~Y.,  {Morris} M.,   {Kassis} M.,  2005,
+  \aj, 130, 1763
+
+\bibitem[\protect\citeauthoryear{{Spitzer}}{{Spitzer}}{1978}]{Spitzer:1978a}
+{Spitzer} L.,  1978, {Physical processes in the interstellar medium}.
+New York: Wiley-Interscience
+
+\bibitem[\protect\citeauthoryear{{Stark}}{{Stark}}{1984}]{Stark:1984a}
+{Stark} A.~A.,  1984, \apj, 281, 624
+
+\bibitem[\protect\citeauthoryear{{Sternberg}, {Hoffmann}  \&
+  {Pauldrach}}{{Sternberg} et~al.}{2003}]{Sternberg:2003a}
+{Sternberg} A.,  {Hoffmann} T.~L.,   {Pauldrach} A.~W.~A.,  2003, \apj, 599,
+  1333
+
+\bibitem[\protect\citeauthoryear{{Tarango-Yong} \& {Henney}}{{Tarango-Yong} \&
+  {Henney}}{2018}]{Tarango-Yong:2018a}
+{Tarango-Yong} J.~A.,  {Henney} W.~J.,  2018, \mnras, 477, 2431
+
+\bibitem[\protect\citeauthoryear{{Tielens} \& {Hollenbach}}{{Tielens} \&
+  {Hollenbach}}{1985}]{Tielens:1985a}
+{Tielens} A.~G.~G.~M.,  {Hollenbach} D.,  1985, \apj, 291, 722
+
+\bibitem[\protect\citeauthoryear{{Tjin A Djie}, {van den Ancker}, {Blondel},
+  {Shevchenko}, {Ezhkova}, {de Winter}  \& {Grankin}}{{Tjin A Djie}
+  et~al.}{2001}]{Tjin-A-Djie:2001a}
+{Tjin A Djie} H.~R.~E.,  {van den Ancker} M.~E.,  {Blondel} P.~F.~C.,
+  {Shevchenko} V.~S.,  {Ezhkova} O.~V.,  {de Winter} D.,   {Grankin} K.~N.,
+  2001, \mnras, 325, 1441
+
+\bibitem[\protect\citeauthoryear{{Tung} et~al.,}{{Tung}
+  et~al.}{2017}]{Tung:2017a}
+{Tung} A.~K.,  et~al., 2017, \aj, 154, 156
+
+\bibitem[\protect\citeauthoryear{{Tuthill}, {Monnier}  \& {Danchi}}{{Tuthill}
+  et~al.}{1999}]{Tuthill:1999a}
+{Tuthill} P.~G.,  {Monnier} J.~D.,   {Danchi} W.~C.,  1999, \nat, 398, 487
+
+\bibitem[\protect\citeauthoryear{{Vink}, {de Koter}  \& {Lamers}}{{Vink}
+  et~al.}{2000}]{Vink:2000a}
+{Vink} J.~S.,  {de Koter} A.,   {Lamers} H.~J.~G.~L.~M.,  2000, \aap, 362, 295
+
+\bibitem[\protect\citeauthoryear{{Weingartner} \& {Draine}}{{Weingartner} \&
+  {Draine}}{2001}]{Weingartner:2001a}
+{Weingartner} J.~C.,  {Draine} B.~T.,  2001, \apj, 548, 296
+
+\bibitem[\protect\citeauthoryear{{Wendker}, {Higgs}  \& {Landecker}}{{Wendker}
+  et~al.}{1991}]{Wendker:1991a}
+{Wendker} H.~J.,  {Higgs} L.~A.,   {Landecker} T.~L.,  1991, \aap, 241, 551
+
+\bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{1996}]{Wilkin:1996a}
+{Wilkin} F.~P.,  1996, \apjl, 459, L31
+
+\bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{2000}]{Wilkin:2000a}
+{Wilkin} F.~P.,  2000, \apj, 532, 400
+
+\bibitem[\protect\citeauthoryear{{Wright}, {Drew}  \& {Mohr-Smith}}{{Wright}
+  et~al.}{2015}]{Wright:2015a}
+{Wright} N.~J.,  {Drew} J.~E.,   {Mohr-Smith} M.,  2015, \mnras, 449, 741
+
+\bibitem[\protect\citeauthoryear{{Xie}, {Ho}, {Li}  \& {Shangguan}}{{Xie}
+  et~al.}{2018}]{Xie:2018a}
+{Xie} Y.,  {Ho} L.~C.,  {Li} A.,   {Shangguan} J.,  2018, \apj, 867, 91
+
+\bibitem[\protect\citeauthoryear{{Zhang}, {Richardson}, {Barnouin}, {Michel},
+  {Schwartz}  \& {Ballouz}}{{Zhang} et~al.}{2018}]{Zhang:2018a}
+{Zhang} Y.,  {Richardson} D.~C.,  {Barnouin} O.~S.,  {Michel} P.,  {Schwartz}
+  S.~R.,   {Ballouz} R.-L.,  2018, \apj, 857, 15
+
+\bibitem[\protect\citeauthoryear{{van Buren} \& {Mac Low}}{{van Buren} \& {Mac
+  Low}}{1992}]{van-Buren:1992a}
+{van Buren} D.,  {Mac Low} M.-M.,  1992, \apj, 394, 534
+
+\bibitem[\protect\citeauthoryear{{van Buren}, {Noriega-Crespo}  \&
+  {Dgani}}{{van Buren} et~al.}{1995}]{van-Buren:1995a}
+{van Buren} D.,  {Noriega-Crespo} A.,   {Dgani} R.,  1995, \aj, 110, 2914
+
+\bibitem[\protect\citeauthoryear{{van Leeuwen}}{{van
+  Leeuwen}}{2007}]{van-Leeuwen:2007a}
+{van Leeuwen} F.,  2007, \aap, 474, 653
+
+\makeatother
+\end{thebibliography}
+
+\appendix
+% start input ./app-k17-k18.tex
+\section{Covariance of derived quantities from propagation of observational uncertainties}
+\label{sec:comb-uncert-covar}
+
+\begin{table}
+  \centering
+  \caption[Derived]{Propagation of observational uncertainties to derived quantities}
+  \label{tab:derived-parameters}
+  \setlength\tabcolsep{3pt}
+  \begin{tabular}{l S S S S S S}
+    \toprule
+    \(x_i\) & {\(\sigma_{x_i}\)}
+    & {\(J_{x_i} (\tau)\)} & {\(J_{x_i} (\eta\shell)\)}
+    & {\(J_{x_i} (\dot M)\)} & {\(J_{x_i} (\dot M_{\text{K18}})\)}
+    & {\(J_{x_i} (L_*)\)}
+    \\
+    \midrule
+    \(D\)     & 0.08 & 2  & 3 & 3 & 2 & 0\\
+    \(L_*\)   & 0.18 & -1 & -2 & -1 & -0.5 & 1\\
+    \(F\IR\)  & 0.12 & 1 & 1 & 1 & 0 & 0\\
+    \(I_{70}\) & 0.12 & 0 & 0 & 0 & 1 & 0\\
+    \(\theta\) & 0.11 & 0 & 1 & 1 & 2 & 0\\
+    \(\ell/R\) & 0.08 & 0 & 0 & 0 & -1 & 0\\
+    \(V\wind\) & 0.18 & 0 & 0 & -1 & -1 & 0\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Even though errors in the fundamental observed quantities, \(x_i\),
+are assumed independent,\footnote{%
+  It is of course true that \(F\IR\) and \(I_{70}\) are not completely
+  independent from one another, but this does not matter since we
+  consider only derived quantities that are a function of one or the
+  other, not both.} %
+errors in the derived quantities, \(f_k(x_1, x_2, \dots)\), will not
+necessarily be so.  For the purposes of this paper:
+\begin{align}
+  \label{eq:observed-and-derived}
+  x_i \in &  \left\{D;\ L_*;\ F\IR;\ I_{70};\ \theta;\ \ell/R;\ V\wind \right\} \\
+  f_k \in & \left\{\tau;\ \eta\shell;\ \dot M;\ \dot M_{\text{K18}};\ L_* \right\}
+            \ .
+\end{align}
+Note that \(L_*\) appears in both lists because we use it as a graph
+axis in Figure~\ref{fig:mass-loss-vs-luminosity}.  For the case where
+each \(f_k\) is a simple product of powers of the \(x_i\), the
+propagation of errors reduces to linear algebra of log
+quantities. This is exactly true for \(\tau\) and \(\eta\shell\), but
+only approximately so for \(\dot M\) and
+\(\dot M_{\text{K18}}\).\footnote{%
+  For \(\dot M\) it is true for \(\eta\shell \gg 1.25 \tau\) and for
+  \(\dot M_{\text{K18}}\) it is true in the limit that the grain
+  emissivity can be expressed as a power law in \(U\).} %
+We define \(J_{x_i} (f_k)\) as the elements of the Jacobian matrix of
+logarithmic derivatives \(d \ln f_k / d \ln x_i \), which are given
+for our quantities in Table~\ref{tab:derived-parameters}.  Then, the
+elements of the variance--covariance matrix for the derived parameters
+are
+\begin{equation}
+  \label{eq:covariance}
+  C_{k,k'} = \sum_{i} J_{x_i} (f_k) \, \sigma_{x_i}^2 \, J_{x_i} (f_{k'}) \ , 
+\end{equation}
+where the \(\sigma_{x_i}\) are the rms dispersions in \(x_i\),
+measured in dex.  In Figure~\ref{fig:python-covar} we give example
+python code for calculating this matrix, using the \(\sigma_{x_i}\)
+derived in \S~\ref{sec:distance}--\ref{sec:stell-wind-veloc} for the
+K18 sources (second column of Tab.~\ref{tab:derived-parameters}), with
+results given in Table~\ref{tab:covariance}.  It can be seen that many
+of the off-diagonal elements are of similar magnitude to the diagonal
+elements, which is an indication of significant correlations between
+the errors in the different parameters.
+
+\begin{table}
+  \centering
+  \caption[Covariance]{Variance--covariance matrix \(C_{k,k'}\) for derived quantities}
+  \label{tab:covariance}
+  \setlength\tabcolsep{3pt}
+  \begin{tabular}{l S S S S S }
+    \toprule
+    & {\(\tau\)} & {\(\eta\shell\)}
+    & {\(\dot M\)} & {\(\dot M_{\text{K18}}\)} & {\(L_*\)}
+    \\
+    \midrule
+    \(\tau\)               &  0.0724 &  0.1176 &  0.0852 &  0.0418 & -0.0324 \\
+    \(\eta\shell\)         &  0.1176 &  0.2137 &  0.1489 &   0.095 & -0.0648 \\
+    \(\dot M\)             &  0.0852 &  0.1489 &  0.1489 &  0.1112 & -0.0324 \\
+    \(\dot M_{\text{K18}}\)&  0.0418 &   0.095 &  0.1112 &  0.1353 & -0.0162 \\
+    \(L_*\)                & -0.0324 & -0.0648 & -0.0324 & -0.0162 &  0.0324 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+For any particular pair of derived quantities, \(f_m\) and \(f_{n}\),
+one can find the \textit{error ellipse} that characterises the
+projection of observational errors onto the \(f_m\)--\(f_{n}\) plane.
+The ellipse is characterized by standard deviations along major and
+minor axes, \(\sigma_a\), \(\sigma_b\), together with the angle
+\(\theta_a\) between the \(f_m\) axis and the ellipse major axis.
+These are given via the eigenvalues and eigenvectors of the relevant
+\(2 \times 2\) submatrix of the covariance matrix:
+\begin{align}
+  \label{eq:error-ellipse}
+  \sigma_a^2 = & \frac12 \left\{   C_{m,m} + C_{n,n}
+                 + \left[ \left( C_{m,m} + C_{n,n} \right)^2
+                 - 4 C_{m,n}^2 \right]^{1/2}\right\} \\
+  \sigma_b^2 = & \frac12 \left\{   C_{m,m} + C_{n,n}
+                 - \left[ \left( C_{m,m} + C_{n,n} \right)^2
+                 - 4 C_{m,n}^2 \right]^{1/2}\right\} \\
+  \theta_a = & \frac12 \arctan \left( \frac{2 C_{m,n}}{C_{m,m} - C_{n,n}} \right) \ .
+\end{align}
+For instance, Table~\ref{tab:error-ellipse} shows the resultant error
+ellipse parameters (shown in blue on the respective graphs) for the
+relations plotted in Figures~\ref{fig:All-sources-eta-tau},
+\ref{fig:mass-loss-vs-luminosity}ab, and
+\ref{fig:mass-loss-comparison}.
+
+\begin{table}
+  \centering
+  \caption[Error ellipse]{Error ellipse parameters for particular pairs of derived quantities}
+  \label{tab:error-ellipse}
+  \begin{tabular}{l l S S S l}
+    \toprule
+    \(f_m\) & \(f_n\) &  {\(\sigma_a\)} & {\(\sigma_b\)}
+    & {\(\theta_a\), \si{\degree}} & Figure   \\
+    \midrule
+    \(\tau\) & \(\eta\) & 0.529 & 0.077 & 60.5 & \ref{fig:All-sources-eta-tau} \\
+    \(L_*\) & \(\dot M\) & 0.397 & 0.155 & -75.5 & \ref{fig:mass-loss-vs-luminosity}a \\
+    \(L_*\) & \(\dot M_{\text{K18}}\) & 0.371 & 0.173 & -81.3 & \ref{fig:mass-loss-vs-luminosity}b \\
+    \(\dot M_{\text{K18}}\) & \(\dot M\) & 0.503 & 0.175 & 46.7 & \ref{fig:mass-loss-comparison} \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{figure}
+  \centering
+  \footnotesize
+  \begin{verbatim}
+import numpy as np
+sig = np.diag([0.08, 0.18, 0.12, 0.12, 0.11, 0.08, 0.18])
+J = np.array([
+    [2, -1, 1, 0, 0, 0, 0],
+    [3, -2, 1, 0, 1, 0, 0],
+    [3, -1, 1, 0, 1, 0, -1],
+    [2, -0.5, 0, 1, 2, -1, -1],
+    [0, 1, 0, 0, 0, 0, 0]
+])
+C = J @ sig**2 @ J.T
+  \end{verbatim}
+  \vspace*{-\baselineskip}
+  \caption{Snippet of Python code that calculates the
+    covariance matrix of Table~\ref{tab:covariance}.  The last line
+    implements equation~\eqref{eq:covariance} by a triple matrix
+    product of the Jacobian matrix \texttt{J}, the square of a
+    diagonal matrix of observational standard deviations \texttt{sig},
+    and the transpose of \texttt{J}.}
+  \label{fig:python-covar}
+\end{figure}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "dusty-bow-wave"
+%%% End:
+ % end input ./app-k17-k18.tex
+
+% \section{Notes on particular sources}
+
+\section{The Herbig Be star V750~Mon}
+\label{sec:notes-part-sourc}
+\label{sec:hd-53367-v750}
+
+K18 source~380 (HD~53367, V750~Mon) is a Herbig Be star with spectral
+type B0V--B0III and mass 12 to \SI{15}{M_\odot}, which shows
+long-scale irregular photometric variability \citep{Tjin-A-Djie:2001a,
+  Pogodin:2006a} together with cyclic radial velocity variations,
+which are interpreted as an eccentric binary with a \SI{5}{M_\odot}
+pre-main-sequence companion.  It is located outside the solar circle
+and, although it was originally classified as part of the CMa OB
+association at about \SI{1}{kpc} \citep{Tjin-A-Djie:2001a}, more
+recent estimates put it much closer.  K18 assume a distance of
+\SI{260}{pc}, based on Hipparcos measurements
+\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
+\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
+puts it closer still at \SI{140 \pm 30}{pc}.  This is the median and
+90\% confidence interval, estimated from Bayesian
+inference\footnote{\url{https://github.com/agabrown/astrometry-inference-tutorials/}.}
+using an exponential density distribution with scale length of
+\SI{1350}{pc} as a prior.
+
+\citet{Quireza:2006b} report a kinematic distance to the associated
+\hii{} region IC~2177 (G\num{223.70}\num{-1.90}) of \SI{1.6}{kpc},
+based an LSR radio recombination line velocity of \SI{+16}{km.s^{-1}}
+\citep{Quireza:2006a} and the outer Galaxy rotation curve of
+\citet{Brand:1993a}.  However, given the dispersion in peculiar
+velocities of star-forming clouds (\SIrange{7}{9}{km.s^{-1}},
+\citealp{Stark:1984a}) and likely streaming motions of the ionized gas
+(\(\approx \SI{10}{km.s^{-1}}\), \citealp{Matzner:2002a, Lee:2012a}),
+this is still consistent with a much smaller distance, which would
+also help in bringing the radio continuum-derived nebular electron
+density into agreement with the value (\(\approx \SI{100}{cm^{-3}}\))
+derived from the optical [\ion{S}{ii}] line ratio
+\citep{Hawley:1978a}.
+
+\citet{Fairlamb:2015a} derive a distance of \SI{340 \pm 60}{pc} from
+combining a spectroscopically determined effective temperature,
+gravity, and reddening with photometry and pre-main sequence
+evolutionary tracks.  They also determine a luminosity of \SI{13000
+  \pm 1000}{L_\odot}, which is only half that assumed by K18, and
+would have to be even lower to bring the photometry into concordance
+with the Gaia distance.  Alternatively, the luminosity could remain
+the same if the total-to-selective extinction ratio were higher than
+the \(R_V = 3.1\) assumed by \citet{Fairlamb:2015a}.  Taking
+\(R_V = 5.5\) instead, as in Orion, would give \(A_V = 3.34\) and a
+predicted \(V\) magnitude of 6.7 if we assume \(L_4 = 1.3\),
+\(D = \SI{170}{pc}\) (furthest distance in Gaia 90\% confidence
+interval) and \(T_{\text{eff}} = \SI{29.5}{kK}\)
+\citep{Fairlamb:2015a} for a bolometric correction of \(-2.86\)
+\citep{Nieva:2013a}.  The observed brightness varies between
+\(V = 6.9\) and 7.2, which is still at least 20\% fainter than
+predicted, but this is the best that can be achieved without rejecting
+the Gaia parallax distance entirely.
+
+A final sanity check can be performed by considering the free-free
+radio continuum flux of V750~Mon's surrounding \hii{} region, which,
+after converting to a luminosity, should be proportional to the total
+recombination rate in the nebula and therefore, assuming
+photoionization equilibrium and negligible dust absorption in the
+ionized gas, also proportional to the ionizing photon luminosity of
+the star.  \citet{Quireza:2006b} report a flux density of \SI{6}{Jy}
+at \SI{8.6}{Ghz} for G\num{223.70}\num{-1.90}, as compared with a flux
+density of \SI{260}{Jy} for the Orion Nebula using the same
+instrumental setup.  Assuming an ionizing photon luminosity of
+\(S_{49} = 1\) and distance \SI{410}{pc} for the ionizing Trapezium
+stars in Orion, therefore implies
+\(S_{49} = 0.0027 (D/\SI{140}{pc})^2\) for V750~Mon.  Using an
+ionizing flux of \SI{3.2e22}{cm^{-2}.s^{-1}} from the curves in Fig.~4
+of \citet{Sternberg:2003a}, this translates to a bolometric luminosity
+of \(L_4 = 0.96 (D/\SI{140}{pc})^2\), which is consistent with the
+\citet{Fairlamb:2015a} value if we take a distance towards the high
+end of the Gaia range.
+
+% \subsection{Source 407, HD~93249}
+% \label{sec:source-407}
+
+% TODO
+
+% \subsection{Source 342}
+% \label{sec:source-342}
+
+% Source~342 is anomalous in both methods. Has high mass loss for low luminosity.
+
+% \subsection{Source 344}
+% \label{sec:source-344}
+
+% This has big disagreement between K18 and me.  My mass-loss rate seems too low, given its high luminosity. Why?
+
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
+\end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2019-06-22 papers/bs-bw-dw-03-submit/latexdiff/ms03-v2-expand.tex
Do latexdiff between the original and final versions of paper 3

--- 2019-06-22 papers/bs-bw-dw-03-submit/latexdiff/ms03-v1-expand.tex
@@
 \newcommand{\thD}{\(\theta^1\)\,Ori~D}
+\newcommand{\thC}{\(\theta^1\)\,Ori~C}
 \newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
@@
 wind (which is itself radiatively driven).  Radiatively supported bows
-(DW, RBW, or RBS, or cases) should lie on the diagonal line
-\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where we have used
-the ratio of grain radiation pressure efficiency to absorption
-efficiency found in the FUV band for the dust mixture shown in
-Paper~II's Figure~6.  Wind-supported bows should lie above this line
-and no bows should lie below the \(\eta\shell = \tau\) line, since
-\(Q_P\) cannot be smaller than \(Q_{\text{abs}}\).
+(DW, RBW, or RBS cases) should lie on the diagonal line
+\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), see discussion
+following equation~\eqref{eq:tau-empirical}.  Wind-supported bows
+should lie above this line and no bows should lie below the
+\(\eta\shell = \tau\) line, since \(Q_P\) cannot be smaller than
+\(Q_{\text{abs}}\).
 
@@
 
+\bibitem[\protect\citeauthoryear{{Abel}, {Hoof}, {Shaw}, {Ferland}  \&
+  {Elwert}}{{Abel} et~al.}{2008}]{Abel:2008a}
+{Abel} N.~P.,  {Hoof} P.~A.~M.~v.,  {Shaw} G.,  {Ferland} G.~J.,   {Elwert} T.,
+   2008, \apj, 686, 1125
+
 \bibitem[\protect\citeauthoryear{{Acreman}, {Stevens}  \& {Harries}}{{Acreman}
@@
   A110
+
+\bibitem[\protect\citeauthoryear{Bohren \& Huffman}{Bohren \&
+  Huffman}{1983}]{Bohren:1983a}
+Bohren C.~F.,  Huffman D.,  1983, Absorption and scattering of light by small
+  particles.
+Wiley-VCH
 
@@
   {Arthur}}{2019a}]{Henney:2019a}
-{Henney} W.~J.,  {Arthur} S.~J.,  2019a, arXiv e-prints, \href
-  {http://adsabs.harvard.edu/abs/2019arXiv190303737H} {1903.03737 MNRAS
-  submitted (Paper I)}
+{Henney} W.~J.,  {Arthur} S.~J.,  2019a, \mnras, \href
+  {http://adsabs.harvard.edu/abs/2019arXiv190303737H} {486, 3423 (Paper I)}
 
@@
   {Arthur}}{2019b}]{Henney:2019b}
-{Henney} W.~J.,  {Arthur} S.~J.,  2019b, arXiv e-prints, \href
-  {http://adsabs.harvard.edu/abs/2019arXiv190307774H} {1903.07774 MNRAS
-  submitted (Paper II)}
+{Henney} W.~J.,  {Arthur} S.~J.,  2019b, \mnras, \href
+  {http://adsabs.harvard.edu/abs/2019arXiv190307774H} {486, 4423 (Paper II)}
 
@@
 {Hoang} T.,  {Tram} L.~N.,  {Lee} H.,   {Ahn} S.-H.,  2018, arXiv, \href
-  {http://adsabs.harvard.edu/abs/2018arXiv181005557H} {}
+  {http://adsabs.harvard.edu/abs/2018arXiv181005557H} {1810.05557}
 
@@
 {Krtička} J.,  {Kubát} J.,  2017, \aap, 606, A31
+
+\bibitem[\protect\citeauthoryear{{Lanz} \& {Hubeny}}{{Lanz} \&
+  {Hubeny}}{2003}]{Lanz:2003a}
+{Lanz} T.,  {Hubeny} I.,  2003, \apjs, 146, 417
 
@@
   {Henney}}{2018}]{Tarango-Yong:2018a}
-{Tarango-Yong} J.~A.,  {Henney} W.~J.,  2018, \mnras, 477, 2431
+{Tarango-Yong} J.~A.,  {Henney} W.~J.,  2018, \mnras, 477, 2431 (Paper 0)
 
@@
 \bibitem[\protect\citeauthoryear{{Weingartner} \& {Draine}}{{Weingartner} \&
-  {Draine}}{2001}]{Weingartner:2001a}
-{Weingartner} J.~C.,  {Draine} B.~T.,  2001, \apj, 548, 296
+  {Draine}}{2001a}]{Weingartner:2001b}
+{Weingartner} J.~C.,  {Draine} B.~T.,  2001a, \apjs, 134, 263
+
+\bibitem[\protect\citeauthoryear{{Weingartner} \& {Draine}}{{Weingartner} \&
+  {Draine}}{2001b}]{Weingartner:2001a}
+{Weingartner} J.~C.,  {Draine} B.~T.,  2001b, \apj, 548, 296
 
@@
 {Wendker} H.~J.,  {Higgs} L.~A.,   {Landecker} T.~L.,  1991, \aap, 241, 551
+
+\bibitem[\protect\citeauthoryear{{Wibking}, {Thompson}  \&
+  {Krumholz}}{{Wibking} et~al.}{2018}]{Wibking:2018a}
+{Wibking} B.~D.,  {Thompson} T.~A.,   {Krumholz} M.~R.,  2018, \mnras, 477,
+  4665
 
@@
 \appendix
+
+\section{Dust opacity and optical depth}
+\label{app:dust-opacity}
+
+In the main body of the paper we use a frequency-averaged dust optical
+depth, \(\tau\), which we here relate to the frequency-dependent optical
+properties of the grains.  For simplicity, we assume a dust model that
+consists of a set \(k \in \{1 \dots N\}\) of discrete populations of
+solid spherical grains \citep[e.g.][]{Desert:1990a}, each with its own
+chemical composition and size distribution:
+\(y_{a,k} \equiv n_k^{-1} (d n_k / d a)\), where \(n_k\) is the volume
+density of the \(k\)-th population (\si{grain.cm^{-3}}) and \(a\) is
+the grain radius. The frequency-dependent dust opacity per unit mass
+of gas and dust is \(\kappa_\nu\), with units \si{cm^2.g^{-1}}, which can be
+expressed as
+\begin{equation}
+  \label{eq:dust-opacity-frequency}
+  \kappa_\nu = \rho^{-1} \sum_{k=1}^{N} \left[  n_k \int_0^\infty \!\!y_{a,k} \, Q_{a,k,\nu} \,\pi a^2 \, da\right]\ ,
+\end{equation}
+where \(\rho\) is the total material mass density and \(Q_{a,k,\nu}\) is
+the size-, composition-, and frequency-dependent dimensionless grain
+optical efficiency, which can be calculated from the grain refractive
+indices using Mie theory \citep{Bohren:1983a}.  There are different
+varieties of \(Q\), and therefore different varieties of opacity,
+according to whether one is interested in true absorption,
+\(Q_{\text{abs}}\), scattering, \(Q_{\text{scat}}\), or total
+extinction, \(Q_{\text{ext}} = Q_{\text{abs}} + Q_{\text{scat}}\).
+The relative importance of scattering is described by the grain
+albedo: \(\varpi = Q_{\text{scat}}/Q_{\text{ext}}\).  The radiation
+pressure acting on the grains is determined by a fourth variety of
+optical efficiency:
+\(Q_P = Q_{\text{abs}} + (1 - g) Q_{\text{scat}}\), where \(g\) is the
+mean scattering cosine.
+
+The monochromatic optical depth of a medium (in any of these 4
+varieties) along a path \(s\) is given by
+\begin{equation}
+  \label{eq:tau-monochromatic}
+  \tau_\nu = \int \rho \kappa_\nu \, ds \ .
+\end{equation}
+If the effects of multiple scattering are ignored, then the fraction
+of stellar radiation of frequency \(\nu\) that is absorbed by the shell
+is \(1 - e^{-\tau_\nu}\), in which the integral is performed with
+\(s\) along the radial direction, assuming the star to be effectively
+a point source at the position of the shell.  To find the fraction of
+radiative \emph{energy}, \(\kappa_\nu\) must be calculated using
+\(Q_{\text{abs}}\), whereas to find the fraction of radiative
+\emph{momentum}, it must be calculated using \(Q_P\).  This
+single-scattering regime \citep[e.g.][]{Wibking:2018a} is a good
+approximation so long as \(\varpi\) is not close to unity and the
+shell is optically thin at infrared wavelengths, which is always true
+for stellar bow shocks.
+
+The frequency-averaged optical depth \(\tau\) is defined such that the
+fraction of the frequency-integrated stellar radiative momentum
+absorbed by the shell is \(1 - e^{-\tau}\).  For a stellar spectrum of
+shape \(F_\nu\), this implies the formal relation
+\begin{equation}
+  \label{eq:tau-averaged}
+  \tau = - \ln \left[ \frac{\int_0^\infty F_\nu \, e^{-\tau_\nu} \, d\nu}{\int_0^\infty F_\nu  \, d\nu} \right] \ .
+\end{equation}
+Note that this equation is valid regardless of the physical units of
+\(F_\nu\) (e.g., flux or luminosity).  More approximately, \(\tau\) can
+simply be estimated by \(\tau_\nu\) at the peak frequency of the stellar
+radiation, which typically falls in the far-ultraviolet range,
+although this approximation breaks down if \(\tau_\nu > 1\) over a
+significant portion of the stellar spectrum.
+
+In the main body of the paper, we use \(\tau_P\) for the radiation pressure
+optical depth and \(\tau_{\text{abs}}\) for the absorption optical depth.  These are
+related by the ratio of the corresponding frequency-averaged optical
+efficiencies:
+\begin{equation}
+  \label{eq:tau_tauprime}
+  \tau_P = \frac{Q_P}{Q_{\text{abs}}} \tau_{\text{abs}} = \left(  1 + \varpi \frac{1 - g}{1 - \varpi}\right) \tau_{\text{abs}}\ .
+\end{equation}
+Specific results were given in Figure~6a of Paper~II for an example
+grain mixture, designed to reproduce average interstellar medium dust
+properties \citep{Weingartner:2001b, Abel:2008a, Ferland:2013a,
+  Ferland:2017a}.  For such a mixture the albedo is roughly constant
+at \(\varpi \approx 0.5\) throughout the ultraviolet and visible bands,
+falling to low values in the infrared.  The asymmetry parameter, or
+mean scattering cosine, falls across the ultraviolet band from
+\(g \approx 1\) at the highest frequencies to \(g\approx 0.5\) in the FUV.\@ This
+yields a conversion factor of
+\(Q_P / Q_{\text{abs}} = \text{\numrange{1.2}{1.3}}\) at EUV/FUV
+wavelengths.
+
 % start input ./app-k17-k18.tex

### 2019-06-27 papers/bs-bw-dw-03-submit/reply-to-referee.txt
re-submitted version of Paper III

			 ━━━━━━━━━━━━━━━━━━━━━━
			  REPLY TO THE REFEREE
			 ━━━━━━━━━━━━━━━━━━━━━━

We thank the referee for a most helpful report, which is full of useful
recommendations that we have tried to follow.  We comment on the
specific requests below.  We include a version of the manuscript with
differences highlighted, which was generated automatically using
latexdiff.  New material is in red and underlined.  Removed material is
in gray and struck through.

┌────
│ 
│ 1) My main comment is whether you can define terms where they are
│ first used.  This is especially acute in section 2 - what is R_0,
│ R_pc. The "Relative velocity" of what to what. What is the difference
│ between capital xi_{sh} and capital xi. I had assumed this was just a
│ typo, but then see Section 4.0
└────

This is a fair point.  We have tried to address these complaints by more
carefully defining the terms and relying less on the previous papers.
The "relative velocity" is between the star and the ambient stream.  The
symbol Xi refers to the general concept of the radiation parameter,
which in Paper II was applied in the ambient stream (outside the shell),
whereas Xi_sh refers to the value of Xi in the shell, which is generally
lower (since the gas pressure goes up in the shock).

┌────
│ Other examples - what is n_\infinity - is it just n.
└────

Yes, we have removed references to n_∞.  This was a hold-over from a
distinction that we made in Paper I that is not important for this
paper.

┌────
│ Use of v_\infinity - not for the wind terminal velocity (a bit
│ confusing as it is the standard symbol for wind terminal
│ velocity). Though I recognise the need for consistency through the
│ papers (as much as possible).
└────

Again, the difference was important in Paper I, but not for this paper.
So we agree that it is cleaner to remove the subscript ∞.

┌────
│ 2) As part of this, can you define tau and kappa a bit more
│ closely. These quantities are usually frequency dependent, but here
│ you are using an effective (or averaged) values. There is the footnote
│ in Section 2, but even that had to read closely as to determine
│ whether tau (Paper I) or tau (Paper II) was the larger. Where do the
│ assumed values of w and g come from for Q_p/Q_abs.
└────

Yes. On reflection, these do deserve a much fuller explanation.  Rather
than litter the text with footnotes, we have added a new appendix A in
order to address this. There we discuss the derivation of monochromatic
opacities from the dust model, including the differences between
scattering, absorption, and radiation pressure.  We describe the
frequency dependence of w, g and Q_p/Q_abs. Then we give the formal
equation for the frequency averaging process.

┌────
│ 
│ I know what was meant after re-reading it a few times, but the overall
│ effect was confusing (and involved reading parts of Paper I and Paper
│ II to understand what was going on).
└────

┌────
│ Minor points - the values of f_UV in Sect 4.0 - can you provide reference.
└────

The values were calculated from TLUSTY atmosphere models.  References
now given.

We made two further changes to the paper, which we hope are acceptable
to the referee.

First, we have slightly toned down the critique of the Kobulnicky+
(2018) paper in sec 5.2.  It turns out that the authors were partially
aware of their mistake about the emissivities and are addressing it in a
follow-up paper (in preparation).  We have therefore removed the
corresponding figure (Fig 7 in original MS).

Second, we changed the wording of conclusion 8 following conversations
with Thiem Hoang (lead author of the Radiative Torque Disruption
papers).

### 2019-06-27 papers/Papers1234/app-cloudy-dust-heating.tex
re-submitted version of Paper III

@@
   \SI{e6}{K}, which requires a stream velocity
-  \(v_\infty > \SI{200}{km.s^{-1}}\) \citep{Draine:1981a}.  This also
+  \(v > \SI{200}{km.s^{-1}}\) \citep{Draine:1981a}.  This also
   coincides with the range of shock velocities where the smaller
@@
 It turns out that the third condition is the most stringent, so we
-will consider it in detail.  The kinetic energy flux through the outer shock for an ambient stream of density \(\rho_\infty\) and velocity \(v_\infty\) is
+will consider it in detail.  The kinetic energy flux through the outer shock for an ambient stream of density \(\rho\) and velocity \(v\) is
 \begin{equation}
   \label{eq:Fkin}
-  F\ke = \tfrac12 \rho_\infty v_\infty^3 = \tfrac12 P\shell v_\infty \ , 
+  F\ke = \tfrac12 \rho v^3 = \tfrac12 P\shell v \ , 
 \end{equation}
@@
   \label{eq:F-ratio-shock}
-  \frac{F\ke}{F\trap} = \frac12 \frac{\eta\wind}{\tau} \frac{v_\infty}{c} \ .
+  \frac{F\ke}{F\trap} = \frac12 \frac{\eta\wind}{\tau} \frac{v}{c} \ .
 \end{equation}
@@
 that \(\eta\shell / \tau < 30\) for all sources considered.  Therefore, for
-a stream velocity \(v_\infty = \SI{200}{km.s^{-1}}\), we have
+a stream velocity \(v = \SI{200}{km.s^{-1}}\), we have
 \(F\ke/F\trap < 0.01\) and the shock-excited dust emission is still
-negligible.  Only in stars with \(v_\infty > \SI{1000}{km.s^{-1}}\) would
+negligible.  Only in stars with \(v > \SI{1000}{km.s^{-1}}\) would
 the shock emission start to be significant, and such hyper-velocity

### 2019-06-27 papers/bs-bw-dw-03-submit/latexdiff/ms03-v2-expand.tex
re-submitted version of Paper III

@@
 stellar photon momentum is available to support the shell (see \S~2.1
-of Paper~I).  But the same photons also heat the dust grains in the
-bow, which re-radiate that energy predominantly at mid-infrared
-wavelengths (roughly \SIrange{10}{100}{\um}) with luminosity \(L\IR\).
-Assuming that Ly\(\alpha\) and mechanical heating of the dust shell is
-negligible (see \S~\ref{sec:unimp-other-heat}) and that the emitting
-shell subtends a solid angle \(\Omega\), as seen from the star, then an
-absorption optical depth can be estimated as
+of Paper~I).  On the other hand, the same photons also heat the dust
+grains in the bow, which re-radiate that energy predominantly at
+mid-infrared wavelengths (roughly \SIrange{10}{100}{\um}) with
+luminosity \(L\IR\).  Assuming that Ly\(\alpha\) and mechanical heating of
+the dust shell is negligible (see \S~\ref{sec:unimp-other-heat}) and
+that the emitting shell subtends a solid angle \(\Omega\), as seen from the
+star, then an absorption optical depth can be estimated as
 \begin{equation}
@@
 terminal velocity, \(V\wind\), together with the ambient stream's mass
-density, \(\rho\), stream--star relative velocity \(v_\infty\), and effective
+density, \(\rho\), stream--star relative velocity \(v\), and effective
 dust opacity, \(\kappa\).  These are defined as follows:
@@
   L_4 &= L_* / \bigl(\SI{e4}{L_\odot}\bigr) \\
-  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
+  v_{10} &= v / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
   n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
@@
 abundance of very small grains is enhanced through radiative torque
-disruption of larger grains \citep{Hoang:2018a}.
+disruption of larger grains \citep{Hoang:2019b}.
 
@@
 other hand, are most vulnerable to Radiative Torque Disruption
-\citep[RATD;][]{Hoang:2018a}, see discussion in \S~6.4 of Paper~II.\@
+\citep[RATD;][]{Hoang:2019b}, see discussion in \S~6.4 of Paper~II.\@
 This is important for our diagnostics because it would tend to reduce
@@
 should be predominantly within a factor of about two below the
-critical size given in equation~(28) of \citet{Hoang:2018a}, as we
+critical size given in equation~(28) of \citet{Hoang:2019b}, as we
 assumed in Figure~\ref{fig:ratd}.
@@
 weak emitters at \SI{70}{\um}, whereas the background emission from
-the PDRs surrounding \hii{} regions is very bright and variable.  The
+the PDRs surrounding \hii{} regions is ion papervery bright and variable.  The
 contrast of the bow against the background is usually much higher at
@@
 In either case, the bow is expected to be smaller than \SI{0.1}{pc}
-for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~8 of
+for \(v \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~8 of
 Paper~I.\@
@@
 sharing results in advance of publication and Thiem Hoang for useful
-discussions.
+discussions.  We thank the anonymous referee for a useful report that
+led to improvements in the presentation of our results.
 
@@
 
-\bibitem[\protect\citeauthoryear{{Hoang}, {Tram}, {Lee}  \& {Ahn}}{{Hoang}
-  et~al.}{2018}]{Hoang:2018a}
-{Hoang} T.,  {Tram} L.~N.,  {Lee} H.,   {Ahn} S.-H.,  2018, arXiv, \href
-  {http://adsabs.harvard.edu/abs/2018arXiv181005557H} {1810.05557}
+\bibitem[\protect\citeauthoryear{Hoang, Tram, Lee  \& Ahn}{Hoang
+  et~al.}{2019}]{Hoang:2019b}
+Hoang T.,  Tram L.~N.,  Lee H.,   Ahn S.-H.,  2019, \mn@doi [Nature Astronomy]
+  {10.1038/s41550-019-0763-6}, \href
+  {https://ui.adsabs.harvard.edu/abs/2019NatAs.tmp..319H} {}
 

### 2019-06-27 papers/Papers1234/sec-obs-intro.tex
Paper IV Jane changes up to end of sec 1

@@
 as follows. In \S~\ref{sec:mid-infrared-arcs} we present an analysis
-of the shapes of several hundred bowshock candidates associated with
+of the shapes of several hundred bow shock candidates associated with
 OB stars from the \SI{24}{\um} survey of \citet{Kobulnicky:2016a}.
@@
 and stellar magnitude, while in \S~\ref{sec:corr-shape} we explore the
-correlations these parameters and the planitude and alatude.  In
+correlations between these parameters and the planitude and alatude.  In
 \S~\ref{sec:far-infrared-arcs} we compare with results for bow shocks
 around cool luminous stars and in \S~\ref{sec:stat-emiss-line} we
-compare with results for staionary emission line arcs in the Orion
+compare with results for stationary emission-line arcs in the Orion
 Nebula.  In \S~\ref{sec:discussion} we discuss the implications of our

### 2019-06-28 papers/Papers1234/sec-quadrics-observations.tex
Finish the discussion and summary for Paper IV
Paper 4 Jane comments up to end of section 4

@@
 \begin{figure*}
-  \setlength\tabcolsep{0pt}
-  \begin{tabular}{ll}
-    (a)
-    & (b) \\
-    \includegraphics
-    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0510-3-star}
-    & \includegraphics
-      [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0506-4-star} \\
-    (c)
-    & (d) \\
-    \includegraphics
-    [width=0.5\linewidth, trim=20 15 30 10, clip]{figs/0517-5-star}
-    & \multicolumn{1}{c}
-      {\includegraphics[width=0.35\linewidth, trim=20 20 20 20]
-      {figs/mipsgal-r0-r0-plus-dPA-edited}}
-  \end{tabular}
+  \includegraphics[width=\linewidth]{figs/mipsgal-example-panels}
   \caption[]{Examples of typical fits to the bow shock shapes of
-    MIPSGAL sources with different star ratings: (a) K510, 3-star
-    rating; (b) K506, 4-star rating; (c) K517, 5-star rating.  Right
-    panels of parts (a)--(c) show a 4\('\) square \SI{24}{\um} image,
-    centered on each source.  Contours are ten linearly spaced levels
-    between the median brightness of the entire image and the maximum
-    brightness of the bow shock arc. Grids of galactic coordinates
-    (light blue lines, parallel to the box sides) and equatorial
-    coordinates (tilted magenta lines) are shown.  The stellar source
-    and the bow shock axis, as determined by \citet{Kobulnicky:2016a}
-    are indicated by an orange star and an orange line, respectively,
-    where the line extends from \(-2 R_0\) to \(+2 R_0\).  The
-    automatically traced arc shapes using the ``mean'' and ``peak''
-    methods (see text) are shown by blue and red dots, respectively.
-    The magenta circle shows the fit to the arc points within
-    \(\pm 45^\circ\) of the nominal bowshock axis, with the magenta dot
-    showing the center of curvature and the magenta line showing the
-    fitted bow shock axis, which is the line passing through the
-    source and the center of curvature.  Left panels of parts (a)--(c)
-    show the radius measured from the source (upper panel) and
-    brightness (lower panel) of the arc points, plotted as a function
-    of angle \(\theta\) from the nominal bow shock axis, and with the same
-    color coding as used on the image. Angular ranges of
-    \(\theta = \pm 45\degr\) and \(\pm 90\degr\) are shown by gray shaded
-    boxes In the upper panel, the \(R_0\) value tabulated by
-    \citet{Kobulnicky:2016a} is shown by a horizontal blue line. (d)
-    Comparison of the bow shock sizes (scatter plot) and position
-    angles (inset histograms) determined from our fits with those
-    tabulated by \citet{Kobulnicky:2016a} for the MIPSGAL sources.
-    The horizontal dotted line on the main plot shows the MIPS
-    \SI{24}{\um} point spread function FWHM of \(5.5\arcsec\).  The
-    standard deviation (s.d.) of the position angle differences is
-    shown on each inset histogram.}
+    MIPSGAL sources.  %
+    (a)~Scatter plot of the bow shock sizes determined from our fits,
+    as compared with those tabulated by \citet[K16]{Kobulnicky:2016a}
+    for the MIPSGAL sources.  Different symbol sizes and colors
+    correspond to different star ratings, which indicate our
+    subjective judgement of the quality of the fit.  The horizontal
+    dotted line shows the MIPS \SI{24}{\um} point spread function
+    FWHM of \(5.5\arcsec\).  %
+    (b)~Histograms of the difference in bow shock position angles
+    between our fits and the K16 values for sources with 3- to 5-star
+    ratings.  %
+    (c--e)~Source K510, with a 3-star rating. %
+    (f--h)~Source K506, with a 4-star rating. %
+    (i--k)~Source K517, with a 5-star rating. %
+    Panels~(c, f, i) show a \SI{24}{\um} gray-scale image of a
+    \(160'' \times 160''\) field of view, centered on each source.
+    Contours are ten linearly spaced levels between the median
+    brightness of the entire image and the maximum brightness of the
+    bow shock arc. Grids of galactic coordinates (light blue lines,
+    parallel to the box sides) and equatorial coordinates (tilted
+    magenta lines) are shown.  The stellar source and the bow shock
+    axis, as determined by \citet{Kobulnicky:2016a} are indicated by
+    an orange star and an orange line, respectively, where the line
+    extends from \(-2 R_0\) to \(+2 R_0\).  The automatically traced
+    arc shapes using the ``mean'' and ``peak'' methods (see text) are
+    shown by blue and red dots, respectively.  The magenta circle
+    shows the fit to the arc points within \(\pm 45^\circ\) of the nominal
+    bowshock axis, with the magenta dot showing the center of
+    curvature and the magenta line showing the fitted bow shock axis,
+    which is the line passing through the source and the center of
+    curvature. %
+    Panels~(d, g, j) show plots of the radius measured from the source
+    of the arc points, plotted as a function of angle \(\theta\) from the
+    nominal bow shock axis, and with the same color coding as used on
+    the image. Angular ranges of \(\theta = \pm 45\degr\) and
+    \(\pm 90\degr\) are shown by gray shaded boxes.  The \(R_0\) value
+    tabulated by \citet{Kobulnicky:2016a} is shown by a horizontal
+    blue line. %
+    Panels~(e, h, k) show equivalent plots for the surface brightness.
+  }
   \label{fig:mipsgal-examples}
@@
 resolution limit of the MIPSGAL \SI{24}{\um} images (\(6\arcsec\),
-indicated by the dotted horizontal line in te figure).
+indicated by the dotted horizontal line in the figure).
 
@@
   \end{tabular}
+  \vspace*{-\baselineskip}
   \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
     of dimensionless radius of curvature versus perpendicular radius.
-    The regions corresponding to different classes of cuadrics are
+    The regions corresponding to different classes of quadrics are
     shown by shading (see \S~4 of Paper~0): oblate spheroids (light
     gray background); prolate spheroids (darker gray background);
-    paraboloids (curved black line); hyperboloids (white background).
+    paraboloids (black line); hyperboloids (white background).
     (a) Individual sources with bow shock fit quality rating of 3-star
@@
 shown in Figure~\ref{fig:mipsgal-shapes} on the \(\Pi\)--\(\Lambda\) plane,
-which was discussed extensively in Paper~0.  Panel a shows each
-individual source with horizontal error bars that represent the
-dispersion of traced points from the circle fit (step~\ref{step:Rc} of
-the previous section) and vertical error bars that show the wing
-asymmetry \(\Delta\Lambda\) (step~\ref{step:Pi-Lambda}).  The horizontal error
-bars, which are a proxy for observational uncertainties, become very
-small for the 4- and 5-star sources, whereas the vertical error bars
-remain at roughly the \(10\%\) level since they reflect real
-asymmetries in the shapes of the bow shocks.
+which was discussed extensively in Paper~0.
+Figure~\ref{fig:mipsgal-shapes}a shows each individual source with
+horizontal error bars that represent the dispersion of traced points
+from the circle fit (step~\ref{step:Rc} of the previous section) and
+vertical error bars that show the wing asymmetry \(\Delta\Lambda\)
+(step~\ref{step:Pi-Lambda}).  The horizontal error bars, which are a
+proxy for observational uncertainties, become very small for the 4-
+and 5-star sources, whereas the vertical error bars remain at roughly
+the \(10\%\) level since they reflect real asymmetries in the shapes
+of the bow shocks.
 
@@
 gray), and hyperboloids (white). The boundary between closed and open
-corresponds to the paraboloids, and is shown by the solid curved line
+corresponds to the paraboloids, and is shown by the solid line
 that divides the dark gray and white regions of the graph.
@@
   \includegraphics[width=0.86\textwidth]{figs/mipsgal-pairplot}
+  \vspace*{-\baselineskip}
   \caption[]{Matrix of pair plots that illustrate distributions of and
@@
 The catalog gives the \(K\)-band extinction, \(A_K\), derived using
-the method of \citet{Majewski:2011a}, but that assumes an intrinsic
-color of \((H - [\SI{4.5}{\um}])_0 = +0.08\) magnitudes, which is too
-red if the sources are assumed to be OB stars.  We therefore re-derive
-\(A_K\) from the catalog magnitudes combined with the
-\citet{Indebetouw:2005a} reddening law, but assuming
+the method of \citet{Majewski:2011a}. However, that assumes an
+intrinsic color of \((H - [\SI{4.5}{\um}])_0 = +0.08\) magnitudes,
+which is too red if the sources are assumed to be OB stars.  We
+therefore re-derive \(A_K\) from the catalog magnitudes combined with
+the \citet{Indebetouw:2005a} reddening law, but assuming
 \((H - [\SI{4.5}{\um}])_0 = -0.1\) magnitudes, which is more typical
@@
   \end{tabular}
+  \vspace*{-\baselineskip}
   \caption[]{Example comparisons between the distribution of bowshock
@@
   \end{tabular}
+  \vspace*{-\baselineskip}
   \caption[]{As Fig.~\ref{fig:mipsgal-uncorrelated} but for median
@@
     \(R_0\), divided into two equal-sized sub-samples: large (blue
-    symbols and blue filled contours) and small (red symbols and red
-    hollow contours).  (b)~Extinction-corrected \(H\)-band magnitude
-    of the stellar source, divided into two equal-sized sub-samples:
-    bright (red symbols and orange filled contours) and faint (green
-    symbols and green hollow contours).}
+    symbols and blue filled contours) and small (red hollow contours).
+    (b)~Extinction-corrected \(H\)-band magnitude of the stellar
+    source, divided into two equal-sized sub-samples: bright (red
+    symbols and orange filled contours) and faint (green symbols and
+    green hollow contours).}
   \label{fig:mipsgal-correlated}
@@
   {figs/mipsgal-boxplot-Rc-R90-versus-R0}
+  \vspace*{-\baselineskip}
   \caption{Box plots of the distributions of bow shock shape
@@
     constant.  No clear systematic changes are apparent in \(\Pi\)
-    (middle panel).}
+    (second panel).}
   \label{fig:mipsgal-boxplot}
@@
 \item We plot the KDEs of the two sub-samples separately on the
-  \(\Pi\)--\(\Lambda\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
-  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
+  \(\Pi\)--\(\Lambda\) plane (see Figs.~\ref{fig:mipsgal-uncorrelated} and
+  \ref{fig:mipsgal-correlated}) to check for any obvious
   differences.
@@
 
-The principal test used is the two-sample Anderson--Darling test
-\citep{Anderson:1952a, Scholz:1987a, Makarov:2017a}, which is a
+The principal test used is Kuiper's variant of the two-sample
+Kolmogorov--Smirnov test \citep[e.g.,][]{Stephens:1970a, Paltani:2004a}, as implemented by the Python library function \texttt{astropy.stats.kuiper\_two} \citep{Astropy-Collaboration:2018a}.
+This is a
 general test of the \textit{null hypothesis} that the two sub-samples
@@
 strict threshold of \(p < 0.05\) as an indicator of ``possible''
-difference.  We supplement the general-purpose Anderson--Darling test
+difference.  We supplement the general-purpose Kuiper test
 with two tests that probe specific features of the sample
@@
 extinction-corrected magnitude of the central star, \(H_0\), which are
-illustrated in Figure~\ref{fig:mipsgal-correlated}.  In both cases,
-the general purpose Anderson--Darling test indicates differences in the
-sub-sample distributions of \(\Lambda\) at the 2-\(\sigma\) level.  It
-is apparent from the histograms shown in the right-hand inset graphs
-of Figure~\ref{fig:mipsgal-correlated}a that in the case of the
-small/large \(R_0\) sub-samples it is the width rather than the
-central tendency of the distributions that is different, which is
-confirmed by the more specific Brown--Forsythe test, which indicates a
-difference between the sub-sample dispersions at the 3-\(\sigma\) level.
-In the case of the faint/bright \(H_0\) sub-samples
-(Fig.~\ref{fig:mipsgal-correlated}b), it is less clear what
-feature of the distributions differ.
+illustrated in Figure~\ref{fig:mipsgal-correlated}.  The general
+purpose Kuiper test indicates differences in the sub-sample
+distributions of \(\Lambda\) at the 2-\(\sigma\) level for \(H_0\) and at the
+3-\(\sigma\) level for \(R_0\).  It is apparent from the histograms shown
+in the right-hand inset graphs of Figure~\ref{fig:mipsgal-correlated}a
+that in the case of the small/large \(R_0\) sub-samples it is the
+width rather than the central tendency of the distributions that is
+different, which is confirmed by the more specific Brown--Forsythe
+test, which indicates a difference between the sub-sample dispersions
+at the 3-\(\sigma\) level.  In the case of the faint/bright \(H_0\)
+sub-samples (Fig.~\ref{fig:mipsgal-correlated}b), it is less clear
+what feature of the distributions differ.
 
@@
 the case of \(R_0\) shown as box plots in
-Figure~\ref{fig:mipsgal-boxplot}.  A systematic increase with \(R_0\)
-in the dispersion of \(\Lambda\) (upper panel of
-Fig.~\ref{fig:mipsgal-boxplot}a) is apparent from both the
-interquartile range (colored boxes) and interdecile range (error
-bars).  As a check on whether observational uncertainties might be
-contributing to this trend, the third and fourth rows of box plots
-show the statistics for, respectively, the fractional asymmetry of the
-bowshock wings and the standard deviation, \(\epsilon(\Lambda)\), of the individual
-points on the bow shock that go into determining \(\Lambda\) (see
-step~\ref{step:R90} of the tracing/fitting methodology described in
-\S~\ref{sec:autom-trac-fitt}).  It can be seen that neither of these
-quantities tends to increase with \(R_0\), and in fact there is a
-significant \emph{decrease} in \(\epsilon(\Lambda)\) with \(R_0\).  This implies
-that the increase with angular size of the diversity of bow shock wing
-shapes is real, and not due to observational uncertainties.  On the
-other hand, we find that no clear trends are evident as a function of
-source magnitude \(H_0\) (not illustrated), which leads us to suspect
-that the \(p < 0.05\) result obtained for the 2-sample
-Anderson--Darling test was a \emph{false positive}, as is also
-supported by the analysis in Appendix~\ref{sec:distr-p-values} and
-Figure~\ref{fig:histo-p-values}.
+Figure~\ref{fig:mipsgal-boxplot}.  This time the \(k\)-sample
+Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a,
+  Makarov:2017a} is used to determine the statistical significance of
+any observed differences.  A systematic increase with \(R_0\) in the
+dispersion of \(\Lambda\) (upper panel of Fig.~\ref{fig:mipsgal-boxplot}a)
+is apparent from both the interquartile range (colored boxes) and
+interdecile range (error bars).  As a check on whether observational
+uncertainties might be contributing to this trend, the third and
+fourth rows of box plots show the statistics for, respectively, the
+fractional asymmetry of the bowshock wings and the standard deviation,
+\(\epsilon(\Lambda)\), of the individual points on the bow shock that go into
+determining \(\Lambda\) (see step~\ref{step:R90} of the tracing/fitting
+methodology described in \S~\ref{sec:autom-trac-fitt}).  It can be
+seen that neither of these quantities tends to increase with \(R_0\),
+and in fact there is a significant \emph{decrease} in
+\(\epsilon(\Lambda)\) with \(R_0\).  This implies that the increase with angular
+size of the diversity of bow shock wing shapes is real, and not due to
+observational uncertainties.  On the other hand, we find that no clear
+trends are evident as a function of source magnitude \(H_0\) (not
+illustrated), which leads us to suspect that the \(p < 0.05\) result
+obtained for the 2-sample Kuiper test was a \emph{false positive}, as
+is also supported by the analysis in Appendix~\ref{sec:distr-p-values}
+and Figure~\ref{fig:histo-p-values}.
 
@@
   \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
+  \vspace*{-\baselineskip}
   \caption[]{Comparison of bow shock shapes between Herschel RSG/AGB
@@
 classes by \citeauthor{Cox:2012a}, according to the overall shape of
-the extended emission at \SI{70}{\um}: ``fermata~\textfermata'', or
-arcs (Class~I); ``eyes~\faEye'' (Class~II); ``rings~{\Large
-  \(\odot\)}'' (Class~III), and ``irregular~\staveXXV'' (Class~IV).  Of
-these, only the Class~I sources clearly correspond to bow shocks,
-which represent 22 out of 50 total sources detected with extended
-emission.  For our sample, we select the 16 Class~I sources where the
-shape parameters can be reliably measured, and which are shown in
+the extended emission at \SI{70}{\um} (see their Table~4):
+``fermata~\textfermata'', or arcs (Class~I); ``eyes~\faEye''
+(Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
+``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I
+sources clearly correspond to bow shocks, which represent 22 out of 50
+total sources detected with extended emission.  For our sample, we
+select the 16 Class~I sources where the shape parameters can be
+reliably measured, and which are shown in
 Figures~\ref{fig:herschel-arc-fits}
@@
 of bow shock shapes between the Herschel (RSG/AGB) and MIGSGAL (OB
-star) samples.  The Anderson--Darling test gives a highly significant
+star) samples.  The Kuiper test gives a highly significant
 difference between the \(\Lambda\) distributions of the two samples, but
@@
 distributions (detailed results are shown in Table~\ref{tab:big-p}).
-The Herschel sources show considerably smaller planitude (median
+The Herschel sources show considerably smaller alatude (median
 \(\Lambda \approx 1.4\)), implying bow shock wings that are more closed than in
@@
   \includegraphics[width=\linewidth]{figs/annotated-ll-arcs}
+  \vspace*{-\baselineskip}
   \caption[]{Stationary bow shock arcs in the Orion Nebula.  Images
@@
   \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion-R0-D}
+  \vspace*{-\baselineskip}
   \caption[]{Shape comparison between Orion Nebula arcs (green) and OB
@@
 a high-velocity jet flow is also seen to issue from the star
-\citep{Bally:2006a, Henney:2013a}.  We took care to when tracing the
-arcs of such sources to avoid regions where jet knot emission is
-projected on the bow shock shell.
+\citep{Bally:2006a, Henney:2013a}.  We took care when tracing the arcs
+of such sources to avoid regions where jet knot emission is projected
+on the bow shock shell.
 
@@
 statistically significant, as indicated by extremely low \(p\)-values
-for the Anderson--Darling tests.  It is also at least 4 times larger
+for the Kuiper tests.  It is also at least 4 times larger
 than the systematic fitting uncertainties discussed in the previous
@@
 \(\Lambda\) all have low \(R_0/D\).  However, the correlation is far from
-perfect, with a Pearson correlation coefficient of only \(r = 0.47\)
-between \(\Pi\) and \(R_0/D\).
+perfect, with a Pearson correlation coefficient of only \(r = 0.47\).
 

### 2019-06-28 papers/Papers1234/app-p-values.tex
Paper 4 - finish all Jane corrections!

@@
     \(p \le 10^{-6}\) included in the leftmost bin.  Short thin vertical
-    lines above the horizontal axis show the individual value.  The
-    thick vertical dashed lines shows the traditional threshold values
+    lines above the horizontal axis show the individual values.  The
+    thick vertical dashed lines show the traditional threshold values
     for significance: \(p = 0.003\) (\(\approx 3 \sigma\)) and
@@
 \(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see equations~(18) and (21)
-of Paper~0.  The difference \(\theta_{90} - \theta_0\) is always a declining
+of Paper~0.  The difference \(\theta_{90} - \theta_0\) is always a decreasing
 function of \(|i|\), so the oscillations of the tangent line become

### 2019-06-28 papers/Papers1234/figs/mipsgal-summary-stats-table-body.tex
Switch to Kuiper test instead of K-S
Paper 4 - finish all Jane corrections!

@@
 %%% Table automatically generated from mipsgal-summary-stats.tab
-%%% 2019-04-30 22:48:49.149121
+%%% 2019-05-01 22:39:47.636535
 %%%
@@
 \addlinespace
-Faint/bright & \(\Pi\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.123 & 0.303 & \itshape 1.654 & 0.254 & 0.111 & \itshape 0.0335\\
-\(H\) magnitude & \(\Lambda\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0156 & \itshape 0.0235 & 0.125\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.07 & 0.093 & 1.013 & 0.191 & 0.365 & 0.761\\
+Faint/bright & \(\Pi\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.123 & 0.303 & \itshape 1.654 & 0.572 & 0.111 & \itshape 0.0335\\
+\(H\) magnitude & \(\Lambda\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.018 & \itshape 0.0235 & 0.125\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.07 & 0.093 & 1.013 & 0.472 & 0.365 & 0.761\\
 \addlinespace
-Low/high & \(\Pi\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.1 & 0.043 & 0.774 & 0.358 & 0.192 & 0.599\\
-bow shock size, \(R_0\) & \(\Lambda\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.061 & 0.11 & \bfseries 1.342 & 0.0815 & 0.428 & \bfseries 0.00139\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.091 & 0.176 & 1.054 & \itshape 0.042 & 0.238 & 0.193\\
+Low/high & \(\Pi\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.1 & 0.043 & 0.774 & 0.508 & 0.192 & 0.599\\
+bow shock size, \(R_0\) & \(\Lambda\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.061 & 0.11 & \bfseries 1.342 & \bfseries 0.00208 & 0.428 & \bfseries 0.00139\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.091 & 0.176 & 1.054 & \itshape 0.00612 & 0.238 & 0.193\\
 \addlinespace
-Low/high & \(\Pi\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.082 & 0.139 & 1.116 & 0.254 & 0.285 & 0.982\\
-extinction, \(A_K\) & \(\Lambda\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.04 & 0.132 & 1.213 & 0.524 & 0.602 & 0.123\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & -0.039 & 0.057 & 1.326 & 0.421 & 0.61 & 0.112\\
+Low/high & \(\Pi\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.082 & 0.139 & 1.116 & 0.379 & 0.285 & 0.982\\
+extinction, \(A_K\) & \(\Lambda\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.04 & 0.132 & 1.213 & 0.572 & 0.602 & 0.123\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & -0.039 & 0.057 & 1.326 & 0.0609 & 0.61 & 0.112\\
 \addlinespace
-Low/high & \(\Pi\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.069 & 0.181 & 1.358 & 0.0568 & 0.368 & 0.0842\\
-\(\vert{}b\vert\) & \(\Lambda\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.02 & 0.008 & 0.796 & 0.323 & 0.795 & 0.0534\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.009 & 0.021 & 1.005 & 0.95 & 0.907 & 0.694\\
+Low/high & \(\Pi\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.069 & 0.181 & 1.358 & \itshape 0.0379 & 0.368 & 0.0842\\
+\(\vert{}b\vert\) & \(\Lambda\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.02 & 0.008 & 0.796 & 0.255 & 0.795 & 0.0534\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.009 & 0.021 & 1.005 & 0.884 & 0.907 & 0.694\\
 \addlinespace
-High/low & \(\Pi\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & -0.0 & -0.064 & 0.785 & 0.998 & 0.999 & 0.549\\
-\(\cos \ell\) & \(\Lambda\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & -0.049 & -0.093 & 1.152 & 0.554 & 0.532 & 0.159\\
-\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(\Delta \Lambda\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.054 & 0.122 & 1.1 & 0.791 & 0.491 & 0.365\\
+High/low & \(\Pi\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & -0.0 & -0.064 & 0.785 & 0.985 & 0.999 & 0.549\\
+\(\cos \ell\) & \(\Lambda\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & -0.049 & -0.093 & 1.152 & 0.504 & 0.532 & 0.159\\
+\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(\Delta \Lambda\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.054 & 0.122 & 1.1 & 0.761 & 0.491 & 0.365\\
 \midrule
@@
 \addlinespace
-Environment: & \(\Pi\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.042 & 0.11 & 1.053 & 0.67 & 0.676 & 0.377\\
-Isolated vs Facing & \(\Lambda\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & -0.07 & -0.142 & 1.194 & 0.877 & 0.49 & 0.392\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(\Delta \Lambda\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & -0.019 & 0.034 & 1.066 & 0.883 & 0.85 & 0.438\\
+Environment: & \(\Pi\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.042 & 0.11 & 1.053 & 0.717 & 0.676 & 0.377\\
+Isolated vs Facing & \(\Lambda\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & -0.07 & -0.142 & 1.194 & 0.965 & 0.49 & 0.392\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(\Delta \Lambda\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & -0.019 & 0.034 & 1.066 & 0.556 & 0.85 & 0.438\\
 \addlinespace
-Environment: & \(\Pi\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.024 & 0.174 & 1.118 & 0.587 & 0.875 & 0.255\\
-Isolated vs \hii & \(\Lambda\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & -0.13 & -0.193 & 1.092 & 0.67 & 0.391 & 0.782\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(\Delta \Lambda\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & -0.048 & -0.095 & 0.855 & 0.825 & 0.754 & 0.799\\
+Environment: & \(\Pi\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.024 & 0.174 & 1.118 & 0.284 & 0.875 & 0.255\\
+Isolated vs \hii & \(\Lambda\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & -0.13 & -0.193 & 1.092 & 0.701 & 0.391 & 0.782\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(\Delta \Lambda\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & -0.048 & -0.095 & 0.855 & 0.785 & 0.754 & 0.799\\
 \addlinespace
-Single/multiple & \(\Pi\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.027 & 0.076 & 1.198 & 0.965 & 0.756 & 0.605\\
-source candidate & \(\Lambda\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.074 & 0.177 & 1.09 & 0.431 & 0.396 & 0.338\\
-\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(\Delta \Lambda\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.093 & 0.136 & 0.987 & 0.293 & 0.284 & 0.97\\
+Single/multiple & \(\Pi\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.027 & 0.076 & 1.198 & 0.977 & 0.756 & 0.605\\
+source candidate & \(\Lambda\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.074 & 0.177 & 1.09 & 0.111 & 0.396 & 0.338\\
+\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(\Delta \Lambda\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.093 & 0.136 & 0.987 & 0.559 & 0.284 & 0.97\\
 \addlinespace
-With/without & \(\Pi\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & -0.012 & 0.101 & 1.547 & 0.948 & 0.904 & 0.2\\
-\SI{8}{\um} emission & \(\Lambda\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & -0.042 & -0.044 & 1.031 & 0.559 & 0.667 & 0.563\\
-\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(\Delta \Lambda\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.021 & -0.106 & 0.726 & 0.985 & 0.826 & 0.219\\
+With/without & \(\Pi\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & -0.012 & 0.101 & 1.547 & 0.875 & 0.904 & 0.2\\
+\SI{8}{\um} emission & \(\Lambda\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & -0.042 & -0.044 & 1.031 & 0.299 & 0.667 & 0.563\\
+\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(\Delta \Lambda\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.021 & -0.106 & 0.726 & 0.967 & 0.826 & 0.219\\
 \addlinespace
-3-star vs (4+5)-star & \(\Pi\) & 1.632 & 2.0 & 0.91 & 0.764 & 0.106 & 0.061 & \bfseries 0.386 & \bfseries 0.431 & 0.84 & \bfseries 5e-06 & \bfseries 7.66e-07 & 0.762\\
- & \(\Lambda\) & 1.661 & 1.812 & 0.288 & 0.286 & 0.247 & 0.216 & \bfseries 0.328 & \bfseries 0.525 & 0.99 & \bfseries 8.45e-05 & \bfseries 2.63e-05 & 0.403\\
-\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(\Delta \Lambda\) & 0.189 & 0.19 & 0.162 & 0.161 &   &   & -0.007 & 0.009 & 0.994 & 0.676 & 0.927 & 0.561\\
+3-star vs (4+5)-star & \(\Pi\) & 1.632 & 2.0 & 0.91 & 0.764 & 0.106 & 0.061 & \bfseries 0.386 & \bfseries 0.431 & 0.84 & \bfseries 3.75e-05 & \bfseries 7.66e-07 & 0.762\\
+ & \(\Lambda\) & 1.661 & 1.812 & 0.288 & 0.286 & 0.247 & 0.216 & \bfseries 0.328 & \bfseries 0.525 & 0.99 & \bfseries 0.000562 & \bfseries 2.63e-05 & 0.403\\
+\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(\Delta \Lambda\) & 0.189 & 0.19 & 0.162 & 0.161 &   &   & -0.007 & 0.009 & 0.994 & 0.539 & 0.927 & 0.561\\
 \midrule
@@
 \addlinespace
-MIPS vs Orion & \(\Pi\) & 1.784 & 3.09 & 0.871 & 1.666 &   &   & \bfseries 0.57 & \bfseries 1.37 & \bfseries 1.911 & \bfseries 8.55e-05 & \bfseries 5.73e-05 & \bfseries 0.00133\\
- & \(\Lambda\) & 1.723 & 2.532 & 0.297 & 0.749 &   &   & \bfseries 0.71 & \bfseries 2.308 & \bfseries 2.526 & \bfseries 6.62e-07 & \bfseries 5.49e-07 & \bfseries 1.49e-09\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(\Delta \Lambda\) & 0.19 & 0.658 & 0.162 & 0.513 &   &   & \bfseries 0.642 & \bfseries 2.243 & \bfseries 3.173 & \bfseries 4.98e-07 & \bfseries 5.95e-06 & \bfseries 1.07e-10\\
+MIPS vs Orion & \(\Pi\) & 1.784 & 3.09 & 0.871 & 1.666 &   &   & \bfseries 0.57 & \bfseries 1.37 & \bfseries 1.911 & \bfseries 0.00112 & \bfseries 5.73e-05 & \bfseries 0.00133\\
+ & \(\Lambda\) & 1.723 & 2.532 & 0.297 & 0.749 &   &   & \bfseries 0.71 & \bfseries 2.308 & \bfseries 2.526 & \bfseries 9.99e-06 & \bfseries 5.49e-07 & \bfseries 1.49e-09\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(\Delta \Lambda\) & 0.19 & 0.658 & 0.162 & 0.513 &   &   & \bfseries 0.642 & \bfseries 2.243 & \bfseries 3.173 & \bfseries 7.14e-06 & \bfseries 5.95e-06 & \bfseries 1.07e-10\\
 \addlinespace
-MIPS vs RSG & \(\Pi\) & 1.784 & 1.479 & 0.871 & 0.227 &   &   & -0.159 & -0.362 & \itshape 0.26 & \itshape 0.0129 & 0.288 & \itshape 0.0151\\
- & \(\Lambda\) & 1.723 & 1.41 & 0.297 & 0.101 &   &   & \bfseries -0.719 & \bfseries -1.089 & \itshape 0.339 & \bfseries 2.89e-06 & \bfseries 1.56e-06 & \itshape 0.004\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 16\) & \(\Delta \Lambda\) & 0.19 & 0.147 & 0.162 & 0.076 &   &   & -0.072 & -0.267 & 0.469 & 0.518 & 0.701 & 0.12
+MIPS vs RSG & \(\Pi\) & 1.784 & 1.479 & 0.871 & 0.227 &   &   & -0.159 & -0.362 & \itshape 0.26 & \bfseries 0.000594 & 0.288 & \itshape 0.0151\\
+ & \(\Lambda\) & 1.723 & 1.41 & 0.297 & 0.101 &   &   & \bfseries -0.719 & \bfseries -1.089 & \itshape 0.339 & \bfseries 2.78e-06 & \bfseries 1.56e-06 & \itshape 0.004\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 16\) & \(\Delta \Lambda\) & 0.19 & 0.147 & 0.162 & 0.076 &   &   & -0.072 & -0.267 & 0.469 & 0.191 & 0.701 & 0.12
 \\
@@
   (Cols.~12--14)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
-  (Col.~12)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
+  (Col.~12)~Kuiper 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
   (Col.~13)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive to differences in the central value of the distributions.

### 2019-06-28 papers/Papers1234/sec-standing-wave.tex
Paper 4 - finish all Jane corrections!

@@
 \(\abs{i} \to \ang{90}\) (see \S~5.3 of Paper~0).  The median observed
-value\footnote{In the presence of outliers, the median is a more
-  robust estimate of the central tendency than is the mean.} falls
-squarely inside this range for both the planitude and alatude, which
-is a remarkable triumph for the \citet{Wilkin:1996a} model.
+value falls squarely inside this range for both the planitude and
+alatude, which is a remarkable triumph for the \citet{Wilkin:1996a}
+model.
+
+\subsection{Diversity in bow shock shapes}
+\label{sec:diversity-bow-shock}
 
@@
 appearance.
+
+\subsubsection{The influence of projection effects}
+\label{sec:infl-proj-effects}
 
@@
 isolated.
+
+\subsubsection{Perturbations to the bow shape}
+\label{sec:pert-bow-shape}
 
@@
 % the planitude distribution.
+
+\subsection{Variations between different source classes}
+\label{sec:vari-betw-diff}
 

### 2019-06-29 papers/Papers1234/bsbwdw-04-v1-expand.tex
Submit paper IV to MNRAS and arxiv

--- 2019-06-28 papers/Papers1234/sec-quadrics-observations.tex
@@
+\documentclass[useAMS, usenatbib, a4paper]{mnras}
+\pdfsuppresswarningpagegroup=1
+
+\usepackage{graphicx}
+\usepackage{microtype}
+\usepackage{xcolor}
+\usepackage{fixltx2e}
+\usepackage{booktabs}
+\usepackage{siunitx}
+\usepackage{color}
+\usepackage{enumerate}
+\usepackage{pdflscape}
+\usepackage{rotating}
+\usepackage{hyperref}
+
+\usepackage[T1]{fontenc} 
+\usepackage[utf8]{inputenc}
+
+\usepackage{newtxtext}
+\usepackage[varvw,smallerops]{newtxmath}
+
+\usepackage{chemgreek}
+\activatechemgreekmapping{newtx}
+
+\let\ORIGna\na
+\usepackage{musixtex}
+\makeatletter
+\newcommand\textfermata{
+  {\let\extractline\relax
+    \setlines10\smallmusicsize \nobarnumbers \nostartrule
+    \staffbotmarg0pt \setclefsymbol1\empty \global\clef@skip0pt
+    \raisebox{0ex}[0ex][0ex]{
+      \startextract\addspace{-\afterruleskip}
+      \notes\fermataup{-2}\en
+      \zendextract}}}
+\makeatother
+\let\na\ORIGna
+
+\usepackage{fontawesome}
+\usepackage{staves}
+
+\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
+  urlcolor=blue!50!black}
+
+\usepackage{etoolbox}
+\robustify\bfseries
+\robustify\itshape
+
+\makeatletter
+\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{
+  \errmessage{\noexpand\@combinedblfloats could not be patched}
+}
+\makeatother
+
+\newcommand\hmmax{0}            
+\newcommand\bmmax{1}            
+\usepackage{bm}
+
+\usepackage{aastex-compat}
+
+\defcitealias{Tarango-Yong:2018a}{Paper~0}
+\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}
+
+\title[Bow shocks, bow waves, and dust waves. IV.] 
+{Bow shocks, bow waves, and dust waves. IV. Shell shape statistics}
+
+\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
+  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
+  58090 Morelia, Michoac\'an, M\'exico}
+\author[Henney et al.]{
+  William J. Henney,\thanks{Email: w.henney@irya.unam.mx}
+  Jorge A. Tarango-Yong,
+  Luis \'Angel Guti\'errez-Soto,\thanks{
+    Current address: Observatório do Valongo,
+    Universidade Federal do Rio de Janeiro,
+    Ladeira Pedro Antonio 43, 20080-090 Rio de Janeiro, Brazil}
+  \& S. J. Arthur
+  \\
+  \AddressCRyA
+}
+
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+\pubyear{2019}
+
+% start input ./bs-bw-dw-defs.tex
+\DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\Sin}{\mathcal{S}}
+\DeclareMathOperator{\Cos}{\mathcal{C}}
+\DeclareMathOperator{\Cot}{\mathcal{T}}
+\DeclareMathOperator{\GammaFunc}{\Gamma}
+\DeclareMathOperator\erf{erf}
+\newcommand\w{\ensuremath{\mathrm{w}}}
+\newcommand\C{\ensuremath{\mathrm{c}}}
+\providecommand{\abs}[1]{\lvert#1\rvert}
+\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
+\newcommand\TODO[1]{
+  \begin{center}
+    \framebox{\parbox{0.8\linewidth}{
+        \texttt{\footnotesize\color{red} #1}}}
+  \end{center}}
+
+\newcommand\uvec[1]{\bm{\hat{#1}}}
+\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}
+
+\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
+\newcommand\Qpbar{\ensuremath{\bar{Q}_{\text{p}}}}
+\newcommand{\grain}{\ensuremath{_{\text{d}}}}
+\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
+\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
+\newcommand{\xsec}{\ensuremath{\sigma\grain}}
+\newcommand\frad{\ensuremath{f_{\text{rad}}}}
+\newcommand\fmax{\ensuremath{f_{\text{max}}}}
+\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
+\newcommand\drag{\ensuremath{_{\text{drag}}}}
+\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
+\newcommand{\wind}{\ensuremath{_{\text{w}}}}
+\newcommand{\trap}{\ensuremath{_{\text{abs}}}}
+\newcommand{\ke}{\ensuremath{_{\text{kin}}}}
+\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
+\newcommand\rad{\ensuremath{_{\text{rad}}}}
+\newcommand\Lya{\ensuremath{_{\text{Ly}\alpha}}}
+\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
+\newcommand\sound{\ensuremath{c_{\text{s}}}}
+\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
+\newcommand\starstar{\ensuremath{_{**}}}
+\newcommand\mmp{\ensuremath{_{\text{\tiny MMP83}}}}
+\newcommand\Hab{\ensuremath{_{\text{\tiny Habing}}}}
+\newcommand\IR{\ensuremath{_{\text{IR}}}}
+\newcommand{\thD}{\(\theta^1\)\,Ori~D}
+\newcommand{\thC}{\(\theta^1\)\,Ori~C}
+\newcommand\alphaB{\ensuremath{\alpha_{\text{B}}}}
+\newcommand\shell{\ensuremath{_{\text{sh}}}}
+\newcommand\M{\ensuremath{\mathcal{M}}}
+\newcommand\hii{\ion{H}{ii}}
+
+\newcommand\amu{\ensuremath{a_{\si{\um}}}}
+
+\newcommand\freeze{\ensuremath{_{\text{tight}}}}
+\newcommand\iftrap{\ensuremath{_{\text{trap}}}}
+\newcommand\LOS{\ensuremath{_{\text{los}}}}
+
+ % end input ./bs-bw-dw-defs.tex
+
+\begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+\begin{abstract}
+  Stellar bow shocks result from relative motions between stars and
+  their environment. The interaction of the stellar wind and radiation
+  with gas and dust in the interstellar medium produces curved arcs of
+  emission at optical, infrared, and radio wavelengths.  We recently
+  proposed a new two-dimensional classification scheme for the shape
+  of such bow shocks, which we here apply to three very different
+  observational datasets: mid-infrared arcs around hot OB stars;
+  far-infrared arcs around luminous cool stars; and H\(\alpha\)
+  emission-line arcs around proplyds and other young stars in the
+  Orion Nebula.  For OB stars, the average shape is consistent with
+  simple thin-shell models for the interaction of a spherical wind
+  with a parallel stream, but the diversity of observed shapes is many
+  times larger than such models predict.  We propose that this may be
+  caused by time-dependent oscillations in the bow shocks, due to
+  either instabilities or wind variability.  Cool star bow shocks have
+  markedly more closed wings than hot star bow shocks, which may be
+  due to the dust emission arising in the shocked stellar wind instead
+  of the shocked interstellar medium.  The Orion Nebula arcs, on the
+  other hand, have both significantly more open wings and
+  significantly flatter apexes than the hot star bow shocks.  We test
+  several possible explanations for this difference (divergent ambient
+  stream, low Mach number, observational biases, and influence of
+  collimated jets), but the evidence for each is inconclusive.
+\end{abstract}
+
+\begin{keywords}
+  circumstellar matter -- methods: statistical -- stars: winds, outflows
+\end{keywords}
+
+% start input ./sec-obs-intro.tex
+
+\section{Introduction}
+\label{sec:introduction}
+
+Stellar bow shocks are produced by the relative motion between a star
+and its surrounding medium, and are commonly detected as curved arcs
+of emission at optical \citep{Gull:1979a, Brown:2005a}, infrared
+\citep{van-Buren:1988a, Kobulnicky:2016a}, or radio
+\citep{van-Buren:1990a, Benaglia:2010a} wavelengths.  The canonical
+theory for these objects is that they are formed by a two-shock
+interaction between the stellar wind and the interstellar medium
+\citep{Pikelner:1968a, Dyson:1972a}, which is distorted due to the
+supersonic motion of the star \citep{Baranov:1970a, Wilkin:1996a}.  In
+some instances, however, the absorbed stellar radiation pressure may
+be more important than the stellar wind in providing the inner support
+for the bow shell \citep[Paper~I]{Henney:2019a} and this may even be
+sufficient to break the collisional coupling between gas and dust
+grains \citep[Paper~II]{Henney:2019b}.  We have proposed a diagnostic
+method to distinguish between these cases, based on the bow shock size
+and the luminosity ratio between the bow shock and the star
+\citep[Paper~III]{Henney:2019c}. In other cases, the appearance of an
+infrared emission arc may be due to the illumination of the inner wall
+of an asymmetrical cavity \citep{Mackey:2016a}, rather than the
+formation of a dense shell, in which case the relative velocity of the
+star may be subsonic with respect to its surroundings
+\citep{Mackey:2015a}.
+
+The largest number of bow shocks have been detected around high-mass
+OB stars, via their mid-infrared dust emission \citep{van-Buren:1995a,
+  Noriega-Crespo:1997b, Povich:2008a, Kobulnicky:2010a, Peri:2012a,
+  Peri:2015a, Sexton:2015b, Kobulnicky:2016a, Bodensteiner:2018a}, and
+these have typical sizes ranging from \SIrange{0.01}{1}{pc}. In
+particularly dense environments, such as the inner Orion Nebula
+\citep{Smith:2005a} and the Galactic center region
+\citep{Geballe:2004a} they may be as small as \SI{0.003}{pc} and emit
+at near-infrared wavelengths \citep{Tanner:2005a,
+  Sanchez-Bermudez:2014a}.  Cometary ultracompact \hii{} regions
+detected at radio wavelengths \citep{Reid:1985a, Wood:1989a,
+  Klaassen:2018a} have also been interpreted as bow shocks
+\citep{van-Buren:1990a, Mac-Low:1991a}, although alternative models,
+such as a champagne flow caused by steep density gradients
+\citep{Cyganowski:2003a, Arthur:2006a, Immer:2014a, Steggles:2017a},
+are favored in many cases.  This illustrates a broader point: that it
+can be difficult to identify bow shocks from morphology alone, since
+other processes can give rise to emission arcs.  In particular, curved
+ionization fronts, as seen in evaporating globules \citep{Sahai:2012b}
+and proplyds \citep{ODell:1993a} can be mistaken for bow shocks.
+Kinematic observations can potentially resolve such ambiguities but
+are not always available.
+
+Stellar bow shocks are also observed around other types of stars. Bow
+shocks around cool red supergiant and asymptotic giant branch stars
+are detected at mid-infrared and far-infrared wavelengths
+\citep{Ueta:2006a, Ueta:2008a, Sahai:2010a, Cox:2012a}.  Pulsar bow
+shock nebulae are detected principally by their H\(\alpha\) emission
+\citep{Kulkarni:1988a, Brownsberger:2014a}.  In the Orion Nebula (M42,
+NGC~1976), at least three different classes of stellar bow shock have
+been identified. As well as a small number of OB bow shocks
+\citep{Smith:2005a, ODell:2001c}, bow shocks are also seen around the
+closest proplyds to the dominant O~star \thC{} \citep{Hayward:1994a,
+  Bally:1998a, Robberto:2005a}.  The proplyds \citep{ODell:2008b} are
+photoevaporating protoplanetary disks around low-mass young stars
+\citep{Johnstone:1998a} and the bow shocks have been modeled as the
+interaction between the disk's ionized photoevaporation flow and the
+supersonic stellar wind from \thC{} \citep{Garcia-Arredondo:2001a}.
+The third class of Orion Nebula bow shock is the LL~Ori-type objects
+\citetext{\citealp{Gull:1979a}; \S~5 of \citealp{Bally:2000a}; \S~3.2
+  of \citealp{Bally:2001a}; \citealp{Henney:2013a}}, which tend to be
+found in the outer regions of the nebula.  These are probably due to
+interactions between the Orion Nebula's champagne flow
+\citep{Zuckerman:1973a} and outflows from T~Tauri stars, which may or
+may not be proplyds \citep{Bally:2000a, Gutierrez-Soto:2015a}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\linewidth]{figs/obs-shape-terminology}
+  \caption[Terminology]{Terminology employed in this paper to describe
+    bow shock shapes, following \citet[Paper~0]{Tarango-Yong:2018a}.}
+  \label{fig:obs-shape-terminology}
+\end{figure}
+
+The shapes of stellar bow shocks are frequently compared with what has
+become known as the \textit{wilkinoid} surface \citep{Cox:2012a},
+which is the result of the idealized interaction between a spherical
+wind and a plane-parallel stream in the hydrodynamic thin-shell
+approximation.  Numerical approximations to this shape were used by
+various authors \citep{Baranov:1971a, Mac-Low:1991a} before an elegant
+analytic solution was found by \citet{Wilkin:1996a} and extended to
+the case of interaction between two spherical winds
+\citep{Canto:1996}.  In \citet[hereafter, Paper~0]{Tarango-Yong:2018a}
+the study of bow shock shapes and their projection on the plane of the
+sky was formalized. The term \textit{cantoid} was introduced for the
+\citet{Canto:1996} family of shapes, together with \textit{ancantoid}
+for a generalization to the case where one of the winds is
+anisotropic, as is appropriate for the proplyds.  In addition, Paper~0
+proposed the use of two dimensionless parameters, \textit{planitude}
+and \textit{alatude}, to describe a general bow shock shape, which we
+illustrate in Figure~\ref{fig:obs-shape-terminology}.  The planitude,
+\(\Pi = R_c / R_0\), measures the flatness of the bow shock apex, where
+\(R_0\) is the star--apex distance and \(R_c\) is the radius of
+curvature measured at the apex.  The alatude,
+\(\Lambda = R_{90}/R_0\), measures the openness of the bow shock wings,
+where \(R_{90}\) is the lateral size of the bow, measured from the
+star in the direction perpendicular to the star--apex direction.
+
+In this paper, we investigate the shapes of stellar bow shocks by
+calculating the distributions of planitude and alatude for different
+classes of bow shock source.  The remainder of the paper is organized
+as follows. In \S~\ref{sec:mid-infrared-arcs} we present an analysis
+of the shapes of several hundred bow shock candidates associated with
+OB stars from the \SI{24}{\um} survey of \citet{Kobulnicky:2016a}.
+Our algorithm for automatically fitting and tracing the shapes is
+described in \S~\ref{sec:autom-trac-fitt}, together with our ``star
+rating'' system for evaluating the fit quality, while in
+\S~\ref{sec:ob-shapes} we locate the sources on the planitude--alatude
+plane.  In \S~\ref{sec:corr-size} we study the correlations amongst
+non-shape parameters of the bow shock sources, such as angular size
+and stellar magnitude, while in \S~\ref{sec:corr-shape} we explore the
+correlations between these parameters and the planitude and alatude.  In
+\S~\ref{sec:far-infrared-arcs} we compare with results for bow shocks
+around cool luminous stars and in \S~\ref{sec:stat-emiss-line} we
+compare with results for stationary emission-line arcs in the Orion
+Nebula.  In \S~\ref{sec:discussion} we discuss the implications of our
+findings for physical models of bow shock formation in the different
+classes of sources, and in \S~\ref{sec:conclusion} we summarise our
+results.  Further details of the statistical tests that we have
+applied are provided in Appendix~\ref{sec:distr-p-values} and a simple
+model for time-dependent oscillations of the bow shock surface is
+presented in Appendix~\ref{sec:perturbed-bows}.
+
+ % end input ./sec-obs-intro.tex
+ % start input ./sec-quadrics-observations.tex
+
 \section{Mid-infrared arcs around early-type stars}
@@
   \caption[]{Examples of typical fits to the bow shock shapes of
-    MIPSGAL sources.  %
+    MIPSGAL sources.  
     (a)~Scatter plot of the bow shock sizes determined from our fits,
@@
     dotted line shows the MIPS \SI{24}{\um} point spread function
-    FWHM of \(5.5\arcsec\).  %
+    FWHM of \(5.5\arcsec\).  
     (b)~Histograms of the difference in bow shock position angles
     between our fits and the K16 values for sources with 3- to 5-star
-    ratings.  %
-    (c--e)~Source K510, with a 3-star rating. %
-    (f--h)~Source K506, with a 4-star rating. %
-    (i--k)~Source K517, with a 5-star rating. %
+    ratings.  
+    (c--e)~Source K510, with a 3-star rating. 
+    (f--h)~Source K506, with a 4-star rating. 
+    (i--k)~Source K517, with a 5-star rating. 
     Panels~(c, f, i) show a \SI{24}{\um} gray-scale image of a
@@
     which is the line passing through the source and the center of
-    curvature. %
+    curvature. 
     Panels~(d, g, j) show plots of the radius measured from the source
@@
     tabulated by \citet{Kobulnicky:2016a} is shown by a horizontal
-    blue line. %
+    blue line. 
     Panels~(e, h, k) show equivalent plots for the surface brightness.
@@
 \end{enumerate}
-% \subsubsection{Subjective evaluation of the fit quality}
 \label{sec:subj-eval-fit}
@@
 
-% 
 Figure~\ref{fig:mipsgal-examples}d compares the bow shock size,
@@
 discussed in \S~\ref{sec:corr-shape} below.
-% This is probably due to higher-rated sources
-% being on average bigger, as will be discussed further below.
 The bulk of the sources are concentrated around the paraboloid line,
@@
 
-%% Maybe talk about the other correlations later if we have time
-
 \subsection{Correlation between bow shock shape and other parameters}
@@
 and Figure~\ref{fig:histo-p-values}.
-
-% So, the only correlation that survives scrutiny is the increase in
-% dispersion of \(R_{90}/R_0\) with increasing \(R_0\), which is finally
-% presented in the greatest detail in
-% Figure~\ref{fig:mipsgal-heteroscedastic}, where we eschew any binning
-% and perform linear regressions of the individual sources as a function
-% of \(\log_{10} R_0\).  As expected from the previous 2-sample and
-% 5-sample analyses, the regression of \(R_{90}/R_0\) is almost flat,
-% with a low correlation coefficient, whereas a regression of the
-% absolute residuals to this fit against \(\log_{10} R_0\) shows a
-% significant positive slope.  This increase in dispersion of shape with
-% angular size is only evident for \(R_0 < 30''\), becoming flat at the
-% largest sizes (see middle panel of
-% Fig.~\ref{fig:mipsgal-heteroscedastic}).
 
@@
 
-%Mention future JWST observations with \(0.85\arcsec\) resolution at \SI{22}{\um}.
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "obs-bowshocks.tex"
-%%% End:
+ % end input ./sec-quadrics-observations.tex
+ % start input ./sec-standing-wave.tex
+
+\section{Discussion}
+\label{sec:discussion}
+
+In this section, we discuss the physical implications of our empirical
+findings regarding bow shock shapes.  Our most reliable result is the
+average shape of the OB bow shocks from the 227 MIPSGAL sources with
+quality rating of 3~stars or higher.  This yields mean values of
+\(\Pi = 1.78 \pm 0.06\) and \(\Lambda = 1.72 \pm 0.02\), or median values of
+\(\Pi = 1.57\) and \(\Lambda = 1.69\).  The uncertainty quoted on the mean
+values is the ``standard error of the mean'':
+\(\text{sem} = \sigma / \sqrt{n}\), where \(\sigma\) is the rms dispersion and
+\(n\) is the number of sources.  Note that in the case of the
+planitude \(\text{sem}(\Pi) = 0.06\) is considerably smaller than
+\(\text{mean}(\Pi) - \text{median}(\Pi) = 0.21\), so the latter would be a
+more conservative estimate of the uncertainty.\footnote{This is
+  because the distribution of \(\Pi\) is approximately log-normal, which
+  yields a significant tail towards high values when converted to
+  linear space.}  These values can be compared with the predictions of
+the thin-shell wilkinoid model \citep{Wilkin:1996a}, which are
+\(\Pi = 1.67\), \(\Lambda = 1.73\) when the bow shock axis lies in the plane
+of the sky (following Paper~0, this is defined as the zero point of
+the inclination angle, \(i\)).  When the axis is inclined, both
+planitude and alatude are predicted to decrease but not by very much,
+tending to \(\Pi = 1.5\), \(\Lambda = 1.63\) as
+\(\abs{i} \to \ang{90}\) (see \S~5.3 of Paper~0).  The median observed
+value falls squarely inside this range for both the planitude and
+alatude, which is a remarkable triumph for the \citet{Wilkin:1996a}
+model.
+
+\subsection{Diversity in bow shock shapes}
+\label{sec:diversity-bow-shock}
+
+On the other hand, turning now to the \emph{variety} of bow shock
+shapes, we see that the wilkinoid can no longer explain our results.
+The rms dispersions of the planitude and alatude distributions for the
+MIPSGAL sources are \(\sigma(\Pi) = 0.87\) and
+\(\sigma(\Lambda) = 0.30\) (Tab.~\ref{tab:big-p}), which are respectively 5 times
+and 3 times larger than the total range of variation of \(\Pi\) and
+\(\Lambda\) predicted for the wilkinoid surface.  Although some of the
+dispersion is due to uncertainties in the observations and the fitting
+algorithm, this contribution is expected to be small, especially for
+the larger, well-resolved sources, for which systematic uncertainties
+in the methods for determining \(\Pi\) and \(\Lambda\) will
+dominate. Conservative upper limits to the relative size of these
+uncertainties were estimated in \S~7 of Paper~0 to be \(< 20\%\) for
+\(\Pi\) and \(< 10\%\) for \(\Lambda\), whereas the observed dispersions are
+roughly twice as large: \(\sigma(\Pi)/\Pi = 55\%\) and
+\(\sigma(\Lambda)/\Lambda = 18\%\).  Furthermore, the variations in planitude and
+alatude are readily apparent by eye, as is demonstrated by the example
+bow shock images shown in Figure~\ref{fig:mipsgal-shapes}b.  Sources
+such as K123 have very typical shapes and fall near the center of the
+\(\Pi\)--\(\Lambda\) distribution, whereas high-\(\Pi\) sources such as K447 have
+a very flat apex region, while low-\(\Pi\) sources such as K566 have a
+pointier, almost triangular apex.  High-\(\Lambda\) sources, such as K517,
+have very open wings that bend away from the star, while
+low-\(\Lambda\) sources such as K489 have closed wings and a semi-circular
+appearance.
+
+\subsubsection{The influence of projection effects}
+\label{sec:infl-proj-effects}
+
+In Paper~0 we found that certain bow shock shapes can show a much
+greater variation in their projected appearance as a function of
+inclination angle than is seen for the wilkinoid.  For example, the
+cantoids and ancantoids, which have asymptotically hyperbolic far
+wings, can shift towards higher apparent planitude and alatude as the
+inclination increases, generally with \(\Lambda \ge \Pi\) (Fig.~20 of Paper~0).
+This might plausibly explain the vertical spur towards higher
+\(\Lambda\) seen in the empirical distribution (\S~\ref{sec:ob-shapes}). A
+different behavior is shown by bow shocks with very flat apex regions,
+such as the MHD simulation from \citet{Meyer:2017a} that is analyzed
+in the \S~6 of Paper~0.  This shows a high planitude \(\Pi\) when the
+orientation is exactly edge-on, but \(\Pi\) decreases sharply along a
+roughly horizontal track as the inclination \(\abs{i}\) increases
+(Fig.~25 of Paper~0).  This is similar to the principal axis of
+variation of the observed shapes (e.g.,
+Fig.~\ref{fig:mipsgal-shapes}a).
+
+If such variations in orientation do make a significant contribution
+to the observed distribution of bow shock shapes in the
+\(\Pi\)-\(\Lambda\) plane, then various predictions follow, which might be
+observationally tested.  High-planitude sources with \(\Pi > 3\) would
+be expected to have low inclinations, \(\abs{i} < \ang{30}\), whereas
+high-alatude sources with \(\Lambda > 2\) would be expected to have high
+inclinations, \(\abs{i} > \ang{45}\).  Unfortunately, determination of
+the inclination for individual sources requires high resolution
+spectroscopy of emission lines in order to map the kinematics of the
+flow in the bow shock shell \citep[e.g.,][]{Henney:2013a}.  This is
+not currently available for the majority of the MIPSGAL sources, which
+are detected only by their dust continuum emission.  A further
+prediction for the high-alatude sources is that the environmental flow
+should be divergent rather than plane-parallel, in order to give a
+cantoid shape instead of a wilkinoid.  This would tend to favor
+``weather-vane'' cases, where the interstellar medium is flowing past
+the star, and disfavor ``runaway'' cases, where the star is moving
+through a static medium.  However, in \S~\ref{sec:corr-shape} we found
+no significant difference in the shape distributions as a function of
+the bow shock environment.  Figure~\ref{fig:mipsgal-uncorrelated}a
+shows that the alatudes of sources that are facing \hii{} regions or
+\SI{8}{\um} bright-rimmed clouds (and therefore might be expected to
+be immersed in a champagne flow) are no higher than sources that are
+isolated.
+
+\subsubsection{Perturbations to the bow shape}
+\label{sec:pert-bow-shape}
+
+\begin{figure}
+  (a)\\
+  \includegraphics[width=\linewidth]
+  {figs/wave-R90-vs-Rc-A020-N10}
+  (b)\\
+  \includegraphics[width=\linewidth]
+  {figs/wave-R90-vs-Rc-A010-N20}
+  \vspace*{-\baselineskip}
+  \caption{Diagnostic diagram for perturbed shapes from standing wave
+    oscillations.  Each model is characterized by a base shape
+    (colored symbols, as described in key) and an amplitude, \(A\),
+    and wavenumber, \(N\), of the oscillation: (a)~breathing mode with
+    \(N = 1\), \(A = 0.2\); (b)~curling mode with \(N = 2\),
+    \(A = 0.1\) (see Fig.~\ref{fig:perturb-shapes} for the
+    phase-dependent intrinsic shapes).  The plotted points show the
+    varying planitude and alatude of the projected bow shock shapes
+    with uniform sampling over an entire period of the oscillation and
+    for varying inclinations (sampled according to an isotropic
+    distribution of orientations).  Each individual point is plotted
+    with a low opacity so that the crowding of points in certain
+    regions of the plane can be appreciated.}
+  \label{fig:perturb-Rc-R90}
+\end{figure}
+
+An alternative explanation for the variety of observed bow shock
+shapes is that they are due to time-dependent perturbations to an
+underlying base shape.  For instance, multiple studies have shown that
+stellar bow shock shells can be unstable \citep{Dgani:1996a,
+  Dgani:1996b, Blondin:1998a, Comeron:1998a, Meyer:2014a}, leading to
+large amplitude oscillations in the shell shape.  The oscillations are
+found to be most vigorous when the post shock cooling is highly
+efficient, allowing the formation of a thin shell (see Paper~I).  Even
+in cases where the shell is stable, oscillations may be driven by
+periodic variations in the stellar wind mass-loss rate or velocity, or
+by inhomogeneities in the ambient stream.  Rather than using a
+particular dynamical model of these oscillations, we instead crudely
+simulate their effect by assuming a constant amplitude standing wave
+perturbation to the base shape, as described in
+Appendix~\ref{sec:perturbed-bows}.  Example results are shown in
+Figure~\ref{fig:perturb-Rc-R90} for an ensemble of bow shocks with
+different orientations and phases of oscillation, considering three
+different underlying base shapes.  It can be seen that modest
+amplitudes of 10 to 20\% can give rise to a distribution in \(\Pi\) and
+\(\Lambda\) similar to that observed for the MIPSGAL sources when the
+oscillation wavelength is of the same order as the bow shock size.
+
+An attractive feature of the oscillation hypothesis is that it
+naturally explains why we find little correlation between the bow
+shock shape and other source parameters (\S~\ref{sec:corr-shape}),
+since the instantaneous shape at any instant is largely a matter of
+chance rather than being due to any intrinsic property of the source.
+The one significant correlation that we do find is that the alatude
+distribution is broader for bow shocks with larger angular sizes.
+This might be explained if the relative amplitude of oscillations were
+higher for sources with more powerful winds. \citet{Meyer:2016a} in
+their Fig.~2 plot the ``axis ratio'' (which is our \(\Lambda^{-1}\)) as a
+function of apex distance for a large set of hydrodynamic bow shock
+simulations.  They find the most unstable bow shocks (with the largest
+spread in \(\Lambda\)) to be those associated with the highest mass stars in
+a relatively dense medium, which have apex distances of
+\SIrange{0.3}{1}{pc}.  This corresponds to \(R_0 > 15''\) for
+distances less than \SI{4}{kpc}, which is larger than the median
+angular size for the MIPSGAL sources, making this a plausible explanation for our statistical result.
+
+\subsection{Variations between different source classes}
+\label{sec:vari-betw-diff}
+
+We now address the difference in shape distribution between the
+different classes of source.  Compared with the OB star bow shocks,
+the cool star sample from \citet{Cox:2012a}\footnote{Three of these
+  sources are high-mass red supergiant (RSG) stars, while the
+  remaining 13 are intermediate-mass asymptotic giant branch (AGB)
+  stars.} shows a significantly smaller alatude of
+\(\Lambda = 1.41 \pm 0.03\) (see
+Fig.~\ref{fig:herschel-compare-mipsgal}).\footnote{Although the
+  planitude also appears to be slightly smaller, this is not very
+  statistically significant due to the small number of cool star
+  sources and the large width of the OB star planitude distribution.}
+Such a closed shape for the wings is inconsistent with the wilkinoid
+value of \(\Lambda = \text{\numrange{1.63}{1.73}}\), which is surprising
+given that the emission shells in these sources are relatively narrow
+(Figs.~\ref{fig:herschel-arc-fits}
+and~\ref{fig:herschel-arc-fits-poor}), so one might have thought that
+the thin-shell approximation of \citet{Wilkin:1996a} would be
+\emph{more} appropriate than for the OB stars, but this is clearly not
+the case.  One possible explanation for this might be that the bow
+shocks have not had time to reach a steady-state configuration, as was
+suggested by \citet{Mohamed:2012a} for the case of \(\alpha\)~Ori.  The
+dynamical timescales, \(R_0 / V\wind\), for the cool star bow shocks
+are of order \SI{e4}{yr} and numerical simulations \citetext{e.g.,
+  Fig.~11 of \citealp{Mohamed:2012a} and Fig.~2 of
+  \citealp{van-Marle:2014a}} show that the bow shock wings take of
+order \SIrange{3e4}{e5}{yr} to fully unfold.  However, this is still
+short compared with typical RSG and AGB lifetimes, so while it might
+apply to a single source it does not work as an explanation for an
+entire class of sources, especially given that the alatude and
+planitude distributions for these sources are so narrow
+(Fig.~\ref{fig:herschel-compare-mipsgal}).  A more promising
+explanation is that the shape difference reflects a different origin
+for the infrared-emitting dust.  In hot stars, the stellar wind is
+dust-free, so the only dust shell comes from the interstellar medium
+and lies outside the astropause (contact discontinuity).  In cool
+stars, the stellar wind is also dusty, which could give rise to
+significant infrared emission from near the stellar wind's termination
+shock, as has been found from hydrodynamic simulations
+\citep{Meyer:2014b}.  This is certainly the case for at least one of
+our cool star sources, the C-AGB star CW~Leo (IRC+10216), where
+ultraviolet GALEX observations \citep{Sahai:2010a} clearly show
+\emph{both} the outer shock and the wind termination shock, and
+comparison with the Herschel images demonstrate that the infrared dust
+emission is associated with the latter.
+
+In the case of the Orion Nebula bow shocks
+(\S~\ref{sec:stat-emiss-line}), we have the opposite situation, where
+the alatude and planitude are both significantly larger on average
+than for the OB star sources (Fig.~\ref{fig:ll-compare-mipsgal}).  On
+the face of it, this is surprising because there are two differences
+between the source classes that would tend to work in the other
+direction.  First, many of the Orion sources are proplyds, or
+externally illuminated photoevaporating disks \citep{ODell:2008b}, in
+which the inner wind is not isotropic but instead is mildly
+concentrated towards the symmetry axis \citep{Garcia-Arredondo:2001a},
+so that simple models predict an \textit{ancantoid} shape
+\citep[\S~5]{Tarango-Yong:2018a} that is less open than for an
+isotropic wind.  Second, as was the case with the cool star sources,
+both the shocked inner wind and the shocked outer stream are expected
+to contribute to the emission arcs.  Indeed, in several of the sources
+of Figure~\ref{fig:ll-arcs} (LL~3, 116--3101, 266-558, 308-3036, and
+LL~5), a two-component emission structure is apparent.  In the case of
+the cool star bow shocks, we invoked this as a possible explanation of
+their \emph{low} alatude (see previous paragraph), so
+some stronger countervailing factor is necessary in order to explain
+why the opposite is seen in the Orion Nebula bow shocks.
+
+Four possible origins for this countervailing factor suggest
+themselves: (i)~the external flow may be more divergent in the Orion
+sources; (ii)~the Mach number of the external flow may be
+systematically lower; (iii)~the fact that the arcs are observed in
+recombination line emission instead of dust continuum may cause
+different observational biases; (iv)~the shapes may be influenced by
+collimated jet outflows from the young stars.  We now address each of
+these in turn.
+
+In case~(i) one would expect \(\Pi\) and \(\Lambda\) to be positively
+correlated with \(R_0/D\), where \(R_0\) is the bow shock size
+(star--apex separation) and \(D\) is the distance from the center of
+divergence of the external flow.  In \S~\ref{sec:stat-emiss-line} we
+found that these are indeed correlated, but only weakly.  A more
+serious objection to this idea is that according to hypersonic
+thin-shell models \citep{Canto:1996} the momentum ratio parameter
+\(\beta\) must be relatively large in order to give significantly open bow
+shock shapes.  From Figure~20 of Paper~0 we see that
+\(\beta > \num{e-3}\) is required in order to give
+\(\Pi, \Lambda > 2\).  However, for small \(\beta\) one has
+\(\beta \approx (R_0/D)^2\), which yields \(\beta = \num{4e-6}\) to \num{3e-4} for
+our sources, so that divergence ought to have little effect on the
+shapes.
+
+Case~(ii) arises from the fact that, if the hypersonic assumption is
+relaxed, then the opening angle between the outer bow shock and the
+contact discontinuity in the wings becomes increasingly large as the
+Mach number, \(\M\), drops towards unity.  This is a consequence of
+the \textit{shock polar} relation for oblique shocks \citep[\S\S~92
+and 113]{Landau:1987a} and applies to both the radiative and
+non-radiative case.  It will tend to produce more open shapes, at
+least in the case that the emission is dominated by the outer shell.
+At the same time, the relative thickness of the shell, \(h/R_0\), is
+predicted to increase as \(\M\) decreases \citetext{e.g., eq~[35] of
+  Paper~I}.  We have therefore measured \(h/R_0\) for the Orion
+sources, finding values ranging from \numrange{0.3}{0.8} with median
+of \num{0.5}.  We have not measured \(h/R_0\) for the full MIPSGAL
+sample, but Figure~11 of Paper~III gives the values for the sub-sample
+of OB bow shocks studied by \citep{Kobulnicky:2018a}.  The median
+value is 0.2, implying thinner shells than in the Orion Nebula bow
+shocks, which lends support to the idea that the Mach number may be
+lower in the latter.  However, among the Orion sources we find that
+\(h/R_0\) is completely uncorrelated with either \(\Pi\) or
+\(\Lambda\) (\(r = 0.02\) and \(-0.05\), respectively).
+
+Case~(iii) attempts to explain the difference in shapes as a result of
+an ``optical illusion'' whereby the OB star bow shocks are in reality
+more open than they appear. The hydrogen recombination line surface
+brightness from an isothermal shell is proportional to the emission
+measure (line of sight integral of the product of proton and electron
+densities), whereas the mid-infrared surface brightness is not simply
+proportional to the dust column density, since it results from the
+reprocessing of stellar radiation.  For typical bow shock grain
+temperatures \citetext{\(T = 50\) to \SI{100}{K},
+  \citealp{Kobulnicky:2017a}} the \SI{24}{\um} band used for the OB
+star sample lies on the short wavelength Wien side of the dust
+emission spectrum, which gives a very steep radial dependence of the
+emissivity.  \citet{Acreman:2016a} calculate synthetic emission maps
+from hydrodynamical simulations and show that, even for a relatively
+thin bow shock shell, the emission arc seen in H\(\alpha\) tends to be more
+open than the arc seen in the mid-infrared (see their Fig.~3).  The
+effect should be even larger for thicker shells, as demonstrated by
+\citet{Mackey:2016a}, who simulate the subsonic motion of an O star
+through its \hii{} region and show that this can give rise to an
+\emph{apparent} bow shock at \SI{24}{\um} even when there is no
+corresponding dense shell at all.
+
+Finally, case~(iv) arises from the observation that several of the
+Orion sources possess high velocity (\(> \SI{100}{km.s^{-1}}\))
+collimated jets \citep{Bally:2006a}, which produce strings of emission
+knots that partially overlap the wings of the bow shock.  In the case
+of 109--246, LL~1, LL~4, LL~5, and LL~6, the projected jet axis is
+roughly perpendicular to the projected bow shock axis, and two of
+these (109--246 and LL~6) have the most extreme high values of \(\Pi\)
+and \(\Lambda\).  There are several other Orion Nebula bow shock sources
+with perpendicular jets (LL~2, 203--3039, 261--3018, 344--3020, and
+LL~7), which we omitted from our sample because of difficulty in
+measuring \(\Lambda\), but the majority also have large planitudes
+\(\Pi > 5\). Only one source, 4468--605, has a jet oriented parallel to
+the bow shock axis, and this has the smallest \(\Pi\) and third-smallest
+\(\Lambda\) of the sample.  The circumstantial evidence thus points towards
+the jets playing some role in shaping the bow shocks when they are
+oriented perpendicular to the axis, even though we took care when
+tracing the bow shock ridges to avoid any region with superimposed jet
+knots.  This would break the cylindrical symmetry of the bow shock,
+which should have a kinematic signature.  However, in the only two
+sources that have been studied kinematically \citep{Henney:2013a}, the
+bow shock shell does not show any sign of the red/blue asymmetry that
+is seen in the jet knots, which argues against any such association.
+
+ % end input ./sec-standing-wave.tex
+ % start input ./sec-obs-conclusions.tex
+
+\section{Summary}
+\label{sec:conclusion}
+
+We have presented a statistical study of the shapes of three different
+classes of stellar bow shocks, as characterized by their flatness of
+apex (planitude, \(\Pi\)) and openness of wings (alatude,
+\(\Lambda\)), following the terminology of
+\citet[Paper~0]{Tarango-Yong:2018a}.  Our principal findings are as
+follows:
+\begin{enumerate}[1.]
+\item Bow shocks driven by hot OB stars, from the mid-infrared catalog
+  of \citet{Kobulnicky:2016a}, have an average shape
+  \((\Pi, \Lambda) \approx (1.6, 1.7)\) that is consistent with predictions of the
+  \citet{Wilkin:1996a} analytic model, but the dispersion in observed
+  shapes \((\sigma_\Pi, \sigma_\Lambda) \approx (0.9, 0.3)\) is many times larger than
+  predicted by that model.
+\item The bow shock shapes show little correlation with other
+  parameters of the source, such as stellar magnitude, Galactic
+  latitude or longitude, extinction, or type of environment (cluster
+  versus isolated).  The only exception is that the dispersion in
+  alatude is higher for bow shocks of larger angular size.
+\item A possible explanation for the previous results is that the
+  variation in shapes is caused by time dependent oscillations in the
+  bow shock surface, with relative amplitude of 10 to 20\% and
+  wavelength of order the bow shock size.  The oscillations may either
+  be due to dynamic instabilities in the bow shock shell or be driven
+  by temporal variations in the stellar wind.  If the oscillations
+  were more vigorous for stars with more powerful winds, it could
+  explain the correlation with angular size.
+\item Bow shocks driven by cool luminous stars (red supergiants and
+  asymptotic giant branch stars), from the catalog of
+  \citep{Cox:2012a}, have an average shape
+  \((\Pi, \Lambda) \approx (1.5, 1.4)\), which has a significantly smaller alatude
+  than the OB star sources, and which is not consistent with the
+  \citet{Wilkin:1996a} model.  We suggest that this may be due to
+  their dust emission being dominated by shocked stellar wind
+  material, instead of shocked ambient material as is the case with
+  the OB stars.
+\item Bow shocks driven by proplyds and other young stars in the outer
+  regions of the Orion Nebula, from the catalogs of
+  \citet{Bally:2006a} and \citet{Gutierrez-Soto:2015a}, have an
+  average shape of \((\Pi, \Lambda) \approx (2.7, 2.4)\), with a significant tail up
+  to \((\Pi, \Lambda) \approx (7, 4)\).  A minority of these sources
+  (\(\approx 20\%\)) have shapes similar to the OB star bow shocks, but the
+  remainder have much flatter apexes and more open wings.  We suggest
+  several possible mechanisms to explain this difference: divergent
+  ambient flow; low Mach number; observational biases; influence of
+  collimated jets, but the available evidence for and against each of
+  these is mixed.
+\end{enumerate}
+
+ % end input ./sec-obs-conclusions.tex
+
+\section*{Acknowledgements}
+We are grateful for financial support provided by Dirección General de
+Asuntos del Personal Académico, Universidad Nacional Autónoma de
+México, through grants Programa de Apoyo a Proyectos de Investigación
+e Inovación Tecnológica IN111215 and IN107019.
+
+\bibliographystyle{mnras}
+\begin{thebibliography}{}
+\makeatletter
+\relax
+\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
+\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
+  {\mn@doi@[]}}
+\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
+  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
+  \endgroup}
+\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
+\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
+\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
+  {dblp:#1}}
+\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
+  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
+  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
+  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
+  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}
+
+\bibitem[\protect\citeauthoryear{{Acreman}, {Stevens}  \& {Harries}}{{Acreman}
+  et~al.}{2016}]{Acreman:2016a}
+{Acreman} D.~M.,  {Stevens} I.~R.,   {Harries} T.~J.,  2016, \mnras, 456, 136
+
+\bibitem[\protect\citeauthoryear{Anderson \& Darling}{Anderson \&
+  Darling}{1952}]{Anderson:1952a}
+Anderson T.~W.,  Darling D.~A.,  1952, Ann. Math. Statist., 23, 193
+
+\bibitem[\protect\citeauthoryear{{Arthur} \& {Hoare}}{{Arthur} \&
+  {Hoare}}{2006}]{Arthur:2006a}
+{Arthur} S.~J.,  {Hoare} M.~G.,  2006, \apjs, 165, 283
+
+\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
+  Collaboration} et~al.}{2018}]{Astropy-Collaboration:2018a}
+{Astropy Collaboration} et~al., 2018, \aj, 156, 123
+
+\bibitem[\protect\citeauthoryear{{Bally} \& {Reipurth}}{{Bally} \&
+  {Reipurth}}{2001}]{Bally:2001a}
+{Bally} J.,  {Reipurth} B.,  2001, \apj, 546, 299
+
+\bibitem[\protect\citeauthoryear{{Bally}, {Sutherland}, {Devine}  \&
+  {Johnstone}}{{Bally} et~al.}{1998}]{Bally:1998a}
+{Bally} J.,  {Sutherland} R.~S.,  {Devine} D.,   {Johnstone} D.,  1998, \aj,
+  116, 293
+
+\bibitem[\protect\citeauthoryear{{Bally}, {O'Dell}  \& {McCaughrean}}{{Bally}
+  et~al.}{2000}]{Bally:2000a}
+{Bally} J.,  {O'Dell} C.~R.,   {McCaughrean} M.~J.,  2000, \aj, 119, 2919
+
+\bibitem[\protect\citeauthoryear{{Bally}, {Licht}, {Smith}  \&
+  {Walawender}}{{Bally} et~al.}{2006}]{Bally:2006a}
+{Bally} J.,  {Licht} D.,  {Smith} N.,   {Walawender} J.,  2006, \aj, 131, 473
+
+\bibitem[\protect\citeauthoryear{{Baranov}, {Krasnobaev}  \&
+  {Kulikovskii}}{{Baranov} et~al.}{1970}]{Baranov:1970a}
+{Baranov} V.~B.,  {Krasnobaev} K.~V.,   {Kulikovskii} A.~G.,  1970, Akademiia
+  Nauk SSSR Doklady, 194, 41
+
+\bibitem[\protect\citeauthoryear{{Baranov}, {Krasnobaev}  \&
+  {Kulikovskii}}{{Baranov} et~al.}{1971}]{Baranov:1971a}
+{Baranov} V.~B.,  {Krasnobaev} K.~V.,   {Kulikovskii} A.~G.,  1971, Soviet
+  Physics Doklady, 15, 791
+
+\bibitem[\protect\citeauthoryear{{Benaglia}, {Romero}, {Mart{\'{\i}}}, {Peri}
+  \& {Araudo}}{{Benaglia} et~al.}{2010}]{Benaglia:2010a}
+{Benaglia} P.,  {Romero} G.~E.,  {Mart{\'{\i}}} J.,  {Peri} C.~S.,   {Araudo}
+  A.~T.,  2010, \aap, 517, L10
+
+\bibitem[\protect\citeauthoryear{{Blondin} \& {Koerwer}}{{Blondin} \&
+  {Koerwer}}{1998}]{Blondin:1998a}
+{Blondin} J.~M.,  {Koerwer} J.~F.,  1998, \na, 3, 571
+
+\bibitem[\protect\citeauthoryear{{Bodensteiner}, {Baade}, {Greiner}  \&
+  {Langer}}{{Bodensteiner} et~al.}{2018}]{Bodensteiner:2018a}
+{Bodensteiner} J.,  {Baade} D.,  {Greiner} J.,   {Langer} N.,  2018, \aap, 618,
+  A110
+
+\bibitem[\protect\citeauthoryear{{Brown} \& {Bomans}}{{Brown} \&
+  {Bomans}}{2005}]{Brown:2005a}
+{Brown} D.,  {Bomans} D.~J.,  2005, \aap, 439, 183
+
+\bibitem[\protect\citeauthoryear{Brown \& Forsythe}{Brown \&
+  Forsythe}{1974}]{Brown:1974a}
+Brown M.~B.,  Forsythe A.~B.,  1974, Journal of the American Statistical
+  Association, 69, 364
+
+\bibitem[\protect\citeauthoryear{{Brownsberger} \& {Romani}}{{Brownsberger} \&
+  {Romani}}{2014}]{Brownsberger:2014a}
+{Brownsberger} S.,  {Romani} R.~W.,  2014, \apj, 784, 154
+
+\bibitem[\protect\citeauthoryear{{Canto}, {Raga}  \& {Wilkin}}{{Canto}
+  et~al.}{1996}]{Canto:1996}
+{Canto} J.,  {Raga} A.~C.,   {Wilkin} F.~P.,  1996, \mn@doi [\apj]
+  {10.1086/177820}, \href {http://adsabs.harvard.edu/abs/1996ApJ...469..729C}
+  {469, 729}
+
+\bibitem[\protect\citeauthoryear{{Carey} et~al.,}{{Carey}
+  et~al.}{2009}]{Carey:2009a}
+{Carey} S.~J.,  et~al., 2009, \pasp, 121, 76
+
+\bibitem[\protect\citeauthoryear{{Comeron} \& {Kaper}}{{Comeron} \&
+  {Kaper}}{1998}]{Comeron:1998a}
+{Comeron} F.,  {Kaper} L.,  1998, \aap, 338, 273
+
+\bibitem[\protect\citeauthoryear{{Cox} et~al.,}{{Cox} et~al.}{2012}]{Cox:2012a}
+{Cox} N.~L.~J.,  et~al., 2012, \aap, 537, A35
+
+\bibitem[\protect\citeauthoryear{Cureton}{Cureton}{1956}]{Cureton:1956a}
+Cureton E.~E.,  1956, Psychometrika, 21, 287
+
+\bibitem[\protect\citeauthoryear{{Cyganowski}, {Reid}, {Fish}  \&
+  {Ho}}{{Cyganowski} et~al.}{2003}]{Cyganowski:2003a}
+{Cyganowski} C.~J.,  {Reid} M.~J.,  {Fish} V.~L.,   {Ho} P.~T.~P.,  2003, \apj,
+  596, 344
+
+\bibitem[\protect\citeauthoryear{{Dgani}, {van Buren}  \&
+  {Noriega-Crespo}}{{Dgani} et~al.}{1996a}]{Dgani:1996a}
+{Dgani} R.,  {van Buren} D.,   {Noriega-Crespo} A.,  1996a, \apj, 461, 372
+
+\bibitem[\protect\citeauthoryear{{Dgani}, {van Buren}  \&
+  {Noriega-Crespo}}{{Dgani} et~al.}{1996b}]{Dgani:1996b}
+{Dgani} R.,  {van Buren} D.,   {Noriega-Crespo} A.,  1996b, \apj, 461, 927
+
+\bibitem[\protect\citeauthoryear{{Dyson} \& {de Vries}}{{Dyson} \& {de
+  Vries}}{1972}]{Dyson:1972a}
+{Dyson} J.~E.,  {de Vries} J.,  1972, \aap, 20, 223
+
+\bibitem[\protect\citeauthoryear{{Dzib} et~al.,}{{Dzib}
+  et~al.}{2017}]{Dzib:2017a}
+{Dzib} S.~A.,  et~al., 2017, \apj, 834, 139
+
+\bibitem[\protect\citeauthoryear{{Eker} et~al.,}{{Eker}
+  et~al.}{2015}]{Eker:2015a}
+{Eker} Z.,  et~al., 2015, \aj, 149, 131
+
+\bibitem[\protect\citeauthoryear{{Garc{\'{\i}}a-Arredondo}, {Henney}  \&
+  {Arthur}}{{Garc{\'{\i}}a-Arredondo} et~al.}{2001}]{Garcia-Arredondo:2001a}
+{Garc{\'{\i}}a-Arredondo} F.,  {Henney} W.~J.,   {Arthur} S.~J.,  2001, \apj,
+  561, 830
+
+\bibitem[\protect\citeauthoryear{{Geballe}, {Rigaut}, {Roy}  \&
+  {Draine}}{{Geballe} et~al.}{2004}]{Geballe:2004a}
+{Geballe} T.~R.,  {Rigaut} F.,  {Roy} J.-R.,   {Draine} B.~T.,  2004, \apj,
+  602, 770
+
+\bibitem[\protect\citeauthoryear{{Groenewegen} et~al.,}{{Groenewegen}
+  et~al.}{2011}]{Groenewegen:2011a}
+{Groenewegen} M.~A.~T.,  et~al., 2011, \aap, 526, A162
+
+\bibitem[\protect\citeauthoryear{{Gull} \& {Sofia}}{{Gull} \&
+  {Sofia}}{1979}]{Gull:1979a}
+{Gull} T.~R.,  {Sofia} S.,  1979, \apj, 230, 782
+
+\bibitem[\protect\citeauthoryear{Guti{\'e}rrez-Soto}{Guti{\'e}rrez-Soto}{2015}]{Gutierrez-Soto:2015a}
+Guti{\'e}rrez-Soto L.~{\'A}.,  2015, Master's thesis, Universidad Nacional
+  Aut{\'o}noma de M{\'e}xico
+
+\bibitem[\protect\citeauthoryear{{Gvaramadze} \& {Bomans}}{{Gvaramadze} \&
+  {Bomans}}{2008}]{Gvaramadze:2008a}
+{Gvaramadze} V.~V.,  {Bomans} D.~J.,  2008, \aap, 490, 1071
+
+\bibitem[\protect\citeauthoryear{{Hayward}, {Houck}  \& {Miles}}{{Hayward}
+  et~al.}{1994}]{Hayward:1994a}
+{Hayward} T.~L.,  {Houck} J.~R.,   {Miles} J.~W.,  1994, \apj, 433, 157
+
+\bibitem[\protect\citeauthoryear{Head, Holman, Lanfear, Kahn  \& Jennions}{Head
+  et~al.}{2015}]{Head:2015a}
+Head M.~L.,  Holman L.,  Lanfear R.,  Kahn A.~T.,   Jennions M.~D.,  2015, PLOS
+  Biology, 13, 1
+
+\bibitem[\protect\citeauthoryear{{Henney} \& {Arthur}}{{Henney} \&
+  {Arthur}}{2019a}]{Henney:2019a}
+{Henney} W.~J.,  {Arthur} S.~J.,  2019a, \mnras, \href
+  {http://adsabs.harvard.edu/abs/2019arXiv190303737H} {486, 3423 (Paper I)}
+
+\bibitem[\protect\citeauthoryear{{Henney} \& {Arthur}}{{Henney} \&
+  {Arthur}}{2019b}]{Henney:2019b}
+{Henney} W.~J.,  {Arthur} S.~J.,  2019b, \mnras, \href
+  {http://adsabs.harvard.edu/abs/2019arXiv190307774H} {486, 4423 (Paper II)}
+
+\bibitem[\protect\citeauthoryear{{Henney} \& {Arthur}}{{Henney} \&
+  {Arthur}}{2019c}]{Henney:2019c}
+{Henney} W.~J.,  {Arthur} S.~J.,  2019c, arXiv e-prints, \href
+  {http://adsabs.harvard.edu/abs/2019arXiv190400343H} {1904.00343 MNRAS
+  submitted (Paper III)}
+
+\bibitem[\protect\citeauthoryear{{Henney}, {Arthur}  \&
+  {Garc{\'{\i}}a-D{\'{\i}}az}}{{Henney} et~al.}{2005}]{Henney:2005a}
+{Henney} W.~J.,  {Arthur} S.~J.,   {Garc{\'{\i}}a-D{\'{\i}}az} M.~T.,  2005,
+  \apj, 627, 813
+
+\bibitem[\protect\citeauthoryear{{Henney}, {Garc{\'{\i}}a-D{\'{\i}}az},
+  {O'Dell}  \& {Rubin}}{{Henney} et~al.}{2013}]{Henney:2013a}
+{Henney} W.~J.,  {Garc{\'{\i}}a-D{\'{\i}}az} M.~T.,  {O'Dell} C.~R.,   {Rubin}
+  R.~H.,  2013, \mnras, 428, 691
+
+\bibitem[\protect\citeauthoryear{{Immer}, {Cyganowski}, {Reid}  \&
+  {Menten}}{{Immer} et~al.}{2014}]{Immer:2014a}
+{Immer} K.,  {Cyganowski} C.,  {Reid} M.~J.,   {Menten} K.~M.,  2014, \aap,
+  563, A39
+
+\bibitem[\protect\citeauthoryear{{Indebetouw} et~al.,}{{Indebetouw}
+  et~al.}{2005}]{Indebetouw:2005a}
+{Indebetouw} R.,  et~al., 2005, \apj, 619, 931
+
+\bibitem[\protect\citeauthoryear{{Johnstone}, {Hollenbach}  \&
+  {Bally}}{{Johnstone} et~al.}{1998}]{Johnstone:1998a}
+{Johnstone} D.,  {Hollenbach} D.,   {Bally} J.,  1998, \apj, 499, 758
+
+\bibitem[\protect\citeauthoryear{{Joye} \& {Mandel}}{{Joye} \&
+  {Mandel}}{2003}]{Joye:2003a}
+{Joye} W.~A.,  {Mandel} E.,  2003, in {Payne} H.~E.,  {Jedrzejewski} R.~I.,
+  {Hook} R.~N.,  eds,  Astronomical Society of the Pacific Conference Series
+  Vol. 295, Astronomical Data Analysis Software and Systems XII. p.~489
+
+\bibitem[\protect\citeauthoryear{{Kim}, {Lu}, {Konopacky}, {Chu}, {Toller},
+  {Anderson}, {Theissen}  \& {Morris}}{{Kim} et~al.}{2018}]{Kim:2018b}
+{Kim} D.,  {Lu} J.~R.,  {Konopacky} Q.,  {Chu} L.,  {Toller} E.,  {Anderson}
+  J.,  {Theissen} C.~A.,   {Morris} M.~R.,  2018, arXiv e-prints
+
+\bibitem[\protect\citeauthoryear{{Klaassen} et~al.,}{{Klaassen}
+  et~al.}{2018}]{Klaassen:2018a}
+{Klaassen} P.~D.,  et~al., 2018, \aap, 611, A99
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Gilbert}  \&
+  {Kiminki}}{{Kobulnicky} et~al.}{2010}]{Kobulnicky:2010a}
+{Kobulnicky} H.~A.,  {Gilbert} I.~J.,   {Kiminki} D.~C.,  2010, \apj, 710, 549
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky} et~al.,}{{Kobulnicky}
+  et~al.}{2016}]{Kobulnicky:2016a}
+{Kobulnicky} H.~A.,  et~al., 2016, \apjs, 227, 18
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Schurhammer}, {Baldwin},
+  {Chick}, {Dixon}, {Lee}  \& {Povich}}{{Kobulnicky}
+  et~al.}{2017}]{Kobulnicky:2017a}
+{Kobulnicky} H.~A.,  {Schurhammer} D.~P.,  {Baldwin} D.~J.,  {Chick} W.~T.,
+  {Dixon} D.~M.,  {Lee} D.,   {Povich} M.~S.,  2017, \aj, 154, 201
+
+\bibitem[\protect\citeauthoryear{{Kobulnicky}, {Chick}  \&
+  {Povich}}{{Kobulnicky} et~al.}{2018}]{Kobulnicky:2018a}
+{Kobulnicky} H.~A.,  {Chick} W.~T.,   {Povich} M.~S.,  2018, \apj, 856, 74
+  (K18)
+
+\bibitem[\protect\citeauthoryear{{Kulkarni} \& {Hester}}{{Kulkarni} \&
+  {Hester}}{1988}]{Kulkarni:1988a}
+{Kulkarni} S.~R.,  {Hester} J.~J.,  1988, \nat, 335, 801
+
+\bibitem[\protect\citeauthoryear{Landau \& Lifshitz}{Landau \&
+  Lifshitz}{1987}]{Landau:1987a}
+Landau L.~D.,  Lifshitz E.~M.,  1987, Fluid Mechanics, Second Edition: Volume 6
+  (Course of Theoretical Physics), 2 edn.
+Course of theoretical physics / by L. D. Landau and E. M. Lifshitz, Vol. 6,
+  Butterworth-Heinemann
+
+\bibitem[\protect\citeauthoryear{Leiva-Murillo \&
+  Art{\'e}s-Rodr\'{\i}guez}{Leiva-Murillo \&
+  Art{\'e}s-Rodr\'{\i}guez}{2012}]{Leiva-Murillo:2012a}
+Leiva-Murillo J.~M.,  Art{\'e}s-Rodr\'{\i}guez A.,  2012, Pattern Recogn.
+  Lett., 33, 1717
+
+\bibitem[\protect\citeauthoryear{{Mac Low}, {van Buren}, {Wood}  \&
+  {Churchwell}}{{Mac Low} et~al.}{1991}]{Mac-Low:1991a}
+{Mac Low} M.-M.,  {van Buren} D.,  {Wood} D.~O.~S.,   {Churchwell} E.,  1991,
+  \apj, 369, 395
+
+\bibitem[\protect\citeauthoryear{{Mackey}, {Gvaramadze}, {Mohamed}  \&
+  {Langer}}{{Mackey} et~al.}{2015}]{Mackey:2015a}
+{Mackey} J.,  {Gvaramadze} V.~V.,  {Mohamed} S.,   {Langer} N.,  2015, \aap,
+  573, A10
+
+\bibitem[\protect\citeauthoryear{{Mackey}, {Haworth}, {Gvaramadze}, {Mohamed},
+  {Langer}  \& {Harries}}{{Mackey} et~al.}{2016}]{Mackey:2016a}
+{Mackey} J.,  {Haworth} T.~J.,  {Gvaramadze} V.~V.,  {Mohamed} S.,  {Langer}
+  N.,   {Harries} T.~J.,  2016, \aap, 586, A114
+
+\bibitem[\protect\citeauthoryear{{Majewski}, {Zasowski}  \&
+  {Nidever}}{{Majewski} et~al.}{2011}]{Majewski:2011a}
+{Majewski} S.~R.,  {Zasowski} G.,   {Nidever} D.~L.,  2011, \apj, 739, 25
+
+\bibitem[\protect\citeauthoryear{Makarov \& Simonova}{Makarov \&
+  Simonova}{2017}]{Makarov:2017a}
+Makarov A.~A.,  Simonova G.~I.,  2017, Journal of Mathematical Sciences, 221,
+  580
+
+\bibitem[\protect\citeauthoryear{Mann \& Whitney}{Mann \&
+  Whitney}{1947}]{Mann:1947a}
+Mann H.~B.,  Whitney D.~R.,  1947, The Annals of Mathematical Statistics, 18,
+  50
+
+\bibitem[\protect\citeauthoryear{{Meyer}, {Gvaramadze}, {Langer}, {Mackey},
+  {Boumis}  \& {Mohamed}}{{Meyer} et~al.}{2014a}]{Meyer:2014a}
+{Meyer} D.~M.-A.,  {Gvaramadze} V.~V.,  {Langer} N.,  {Mackey} J.,  {Boumis}
+  P.,   {Mohamed} S.,  2014a, \mnras, 439, L41
+
+\bibitem[\protect\citeauthoryear{{Meyer}, {Mackey}, {Langer}, {Gvaramadze},
+  {Mignone}, {Izzard}  \& {Kaper}}{{Meyer} et~al.}{2014b}]{Meyer:2014b}
+{Meyer} D.~M.-A.,  {Mackey} J.,  {Langer} N.,  {Gvaramadze} V.~V.,  {Mignone}
+  A.,  {Izzard} R.~G.,   {Kaper} L.,  2014b, \mnras, 444, 2754
+
+\bibitem[\protect\citeauthoryear{{Meyer}, {van Marle}, {Kuiper}  \&
+  {Kley}}{{Meyer} et~al.}{2016}]{Meyer:2016a}
+{Meyer} D.~M.-A.,  {van Marle} A.-J.,  {Kuiper} R.,   {Kley} W.,  2016, \mnras,
+  459, 1146
+
+\bibitem[\protect\citeauthoryear{{Meyer}, {Mignone}, {Kuiper}, {Raga}  \&
+  {Kley}}{{Meyer} et~al.}{2017}]{Meyer:2017a}
+{Meyer} D.~M.-A.,  {Mignone} A.,  {Kuiper} R.,  {Raga} A.~C.,   {Kley} W.,
+  2017, \mnras, 464, 3229
+
+\bibitem[\protect\citeauthoryear{{Mohamed}, {Mackey}  \& {Langer}}{{Mohamed}
+  et~al.}{2012}]{Mohamed:2012a}
+{Mohamed} S.,  {Mackey} J.,   {Langer} N.,  2012, \aap, 541, A1
+
+\bibitem[\protect\citeauthoryear{{Noriega-Crespo}, {van Buren}  \&
+  {Dgani}}{{Noriega-Crespo} et~al.}{1997}]{Noriega-Crespo:1997b}
+{Noriega-Crespo} A.,  {van Buren} D.,   {Dgani} R.,  1997, \aj, 113, 780
+
+\bibitem[\protect\citeauthoryear{{O'Dell}}{{O'Dell}}{2001}]{ODell:2001c}
+{O'Dell} C.~R.,  2001, \aj, 122, 2662
+
+\bibitem[\protect\citeauthoryear{{O'Dell} \& {Wen}}{{O'Dell} \&
+  {Wen}}{1994}]{ODell:1994a}
+{O'Dell} C.~R.,  {Wen} Z.,  1994, \apj, 436, 194
+
+\bibitem[\protect\citeauthoryear{{O'Dell}, {Wen}  \& {Hu}}{{O'Dell}
+  et~al.}{1993}]{ODell:1993a}
+{O'Dell} C.~R.,  {Wen} Z.,   {Hu} X.,  1993, \apj, 410, 696
+
+\bibitem[\protect\citeauthoryear{{O'Dell}, {Muench}, {Smith}  \&
+  {Zapata}}{{O'Dell} et~al.}{2008}]{ODell:2008b}
+{O'Dell} C.~R.,  {Muench} A.,  {Smith} N.,   {Zapata} L.,  2008, {Star
+  Formation in the Orion Nebula II: Gas, Dust, Proplyds and Outflows}.
+p.~544
+
+\bibitem[\protect\citeauthoryear{{Paltani}}{{Paltani}}{2004}]{Paltani:2004a}
+{Paltani} S.,  2004, \aap, 420, 789
+
+\bibitem[\protect\citeauthoryear{{Peri}, {Benaglia}, {Brookes}, {Stevens}  \&
+  {Isequilla}}{{Peri} et~al.}{2012}]{Peri:2012a}
+{Peri} C.~S.,  {Benaglia} P.,  {Brookes} D.~P.,  {Stevens} I.~R.,   {Isequilla}
+  N.~L.,  2012, \aap, 538, A108
+
+\bibitem[\protect\citeauthoryear{{Peri}, {Benaglia}  \& {Isequilla}}{{Peri}
+  et~al.}{2015}]{Peri:2015a}
+{Peri} C.~S.,  {Benaglia} P.,   {Isequilla} N.~L.,  2015, \aap, 578, A45
+
+\bibitem[\protect\citeauthoryear{{Pikel'ner}}{{Pikel'ner}}{1968}]{Pikelner:1968a}
+{Pikel'ner} S.~B.,  1968, \aplett, 2, 97
+
+\bibitem[\protect\citeauthoryear{{Povich}, {Benjamin}, {Whitney}, {Babler},
+  {Indebetouw}, {Meade}  \& {Churchwell}}{{Povich} et~al.}{2008}]{Povich:2008a}
+{Povich} M.~S.,  {Benjamin} R.~A.,  {Whitney} B.~A.,  {Babler} B.~L.,
+  {Indebetouw} R.,  {Meade} M.~R.,   {Churchwell} E.,  2008, \apj, 689, 242
+
+\bibitem[\protect\citeauthoryear{{Puls} et~al.,}{{Puls}
+  et~al.}{1996}]{Puls:1996a}
+{Puls} J.,  et~al., 1996, \aap, 305, 171
+
+\bibitem[\protect\citeauthoryear{{Reid} \& {Ho}}{{Reid} \&
+  {Ho}}{1985}]{Reid:1985a}
+{Reid} M.~J.,  {Ho} P.~T.~P.,  1985, \apjl, 288, L17
+
+\bibitem[\protect\citeauthoryear{{Robberto} et~al.,}{{Robberto}
+  et~al.}{2005}]{Robberto:2005a}
+{Robberto} M.,  et~al., 2005, \aj, 129, 1534
+
+\bibitem[\protect\citeauthoryear{{Robberto} et~al.,}{{Robberto}
+  et~al.}{2013}]{Robberto:2013a}
+{Robberto} M.,  et~al., 2013, \apjs, 207, 10
+
+\bibitem[\protect\citeauthoryear{{Sahai} \& {Chronopoulos}}{{Sahai} \&
+  {Chronopoulos}}{2010}]{Sahai:2010a}
+{Sahai} R.,  {Chronopoulos} C.~K.,  2010, \apjl, 711, L53
+
+\bibitem[\protect\citeauthoryear{{Sahai}, {Güsten}  \& {Morris}}{{Sahai}
+  et~al.}{2012}]{Sahai:2012b}
+{Sahai} R.,  {Güsten} R.,   {Morris} M.~R.,  2012, \apjl, 761, L21
+
+\bibitem[\protect\citeauthoryear{{Sanchez-Bermudez}, {Schödel}, {Alberdi},
+  {Muzić}, {Hummel}  \& {Pott}}{{Sanchez-Bermudez}
+  et~al.}{2014}]{Sanchez-Bermudez:2014a}
+{Sanchez-Bermudez} J.,  {Schödel} R.,  {Alberdi} A.,  {Muzić} K.,  {Hummel}
+  C.~A.,   {Pott} J.-U.,  2014, \aap, 567, A21
+
+\bibitem[\protect\citeauthoryear{Scholz \& Stephens}{Scholz \&
+  Stephens}{1987}]{Scholz:1987a}
+Scholz F.~W.,  Stephens M.~A.,  1987, Journal of the American Statistical
+  Association, 82, 918
+
+\bibitem[\protect\citeauthoryear{Scott}{Scott}{2015}]{Scott:2015a}
+Scott D.~W.,  2015, Multivariate density estimation: theory, practice, and
+  visualization, 2nd edn.
+John Wiley \& Sons
+
+\bibitem[\protect\citeauthoryear{{Sexton}, {Povich}, {Smith}, {Babler}, {Meade}
+   \& {Rudolph}}{{Sexton} et~al.}{2015}]{Sexton:2015b}
+{Sexton} R.~O.,  {Povich} M.~S.,  {Smith} N.,  {Babler} B.~L.,  {Meade} M.~R.,
+   {Rudolph} A.~L.,  2015, \mnras, 446, 1047
+
+\bibitem[\protect\citeauthoryear{{Smith}, {Bally}, {Shuping}, {Morris}  \&
+  {Kassis}}{{Smith} et~al.}{2005}]{Smith:2005a}
+{Smith} N.,  {Bally} J.,  {Shuping} R.~Y.,  {Morris} M.,   {Kassis} M.,  2005,
+  \aj, 130, 1763
+
+\bibitem[\protect\citeauthoryear{{Steggles}, {Hoare}  \& {Pittard}}{{Steggles}
+  et~al.}{2017}]{Steggles:2017a}
+{Steggles} H.~G.,  {Hoare} M.~G.,   {Pittard} J.~M.,  2017, \mnras, 466, 4573
+
+\bibitem[\protect\citeauthoryear{Stephens}{Stephens}{1970}]{Stephens:1970a}
+Stephens M.~A.,  1970, Journal of the Royal Statistical Society. Series B
+  (Methodological), 32, 115
+
+\bibitem[\protect\citeauthoryear{{Tanner}, {Ghez}, {Morris}  \&
+  {Christou}}{{Tanner} et~al.}{2005}]{Tanner:2005a}
+{Tanner} A.,  {Ghez} A.~M.,  {Morris} M.~R.,   {Christou} J.~C.,  2005, \apj,
+  624, 742
+
+\bibitem[\protect\citeauthoryear{{Tarango-Yong} \& {Henney}}{{Tarango-Yong} \&
+  {Henney}}{2018}]{Tarango-Yong:2018a}
+{Tarango-Yong} J.~A.,  {Henney} W.~J.,  2018, \mnras, 477, 2431 (Paper 0)
+
+\bibitem[\protect\citeauthoryear{{Ueta} et~al.,}{{Ueta}
+  et~al.}{2006}]{Ueta:2006a}
+{Ueta} T.,  et~al., 2006, \apjl, 648, L39
+
+\bibitem[\protect\citeauthoryear{{Ueta} et~al.,}{{Ueta}
+  et~al.}{2008}]{Ueta:2008a}
+{Ueta} T.,  et~al., 2008, \pasj, 60, S407
+
+\bibitem[\protect\citeauthoryear{{Weilbacher} et~al.,}{{Weilbacher}
+  et~al.}{2015}]{Weilbacher:2015a}
+{Weilbacher} P.~M.,  et~al., 2015, \aap, 582, A114
+
+\bibitem[\protect\citeauthoryear{{Werner} et~al.,}{{Werner}
+  et~al.}{2004}]{Werner:2004a}
+{Werner} M.~W.,  et~al., 2004, \apjs, 154, 1
+
+\bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{1996}]{Wilkin:1996a}
+{Wilkin} F.~P.,  1996, \apjl, 459, L31
+
+\bibitem[\protect\citeauthoryear{{Wood} \& {Churchwell}}{{Wood} \&
+  {Churchwell}}{1989}]{Wood:1989a}
+{Wood} D.~O.~S.,  {Churchwell} E.,  1989, \apjs, 69, 831
+
+\bibitem[\protect\citeauthoryear{{Wright} et~al.,}{{Wright}
+  et~al.}{2010}]{Wright:2010a}
+{Wright} E.~L.,  et~al., 2010, \aj, 140, 1868
+
+\bibitem[\protect\citeauthoryear{{Zuckerman}}{{Zuckerman}}{1973}]{Zuckerman:1973a}
+{Zuckerman} B.,  1973, \apj, 183, 863
+
+\bibitem[\protect\citeauthoryear{{van Buren} \& {McCray}}{{van Buren} \&
+  {McCray}}{1988}]{van-Buren:1988a}
+{van Buren} D.,  {McCray} R.,  1988, \apjl, 329, L93
+
+\bibitem[\protect\citeauthoryear{{van Buren}, {Mac Low}, {Wood}  \&
+  {Churchwell}}{{van Buren} et~al.}{1990}]{van-Buren:1990a}
+{van Buren} D.,  {Mac Low} M.-M.,  {Wood} D.~O.~S.,   {Churchwell} E.,  1990,
+  \apj, 353, 570
+
+\bibitem[\protect\citeauthoryear{{van Buren}, {Noriega-Crespo}  \&
+  {Dgani}}{{van Buren} et~al.}{1995}]{van-Buren:1995a}
+{van Buren} D.,  {Noriega-Crespo} A.,   {Dgani} R.,  1995, \aj, 110, 2914
+
+\bibitem[\protect\citeauthoryear{{van Marle}, {Decin}  \& {Meliani}}{{van
+  Marle} et~al.}{2014}]{van-Marle:2014a}
+{van Marle} A.~J.,  {Decin} L.,   {Meliani} Z.,  2014, \aap, 561, A152
+
+\makeatother
+\end{thebibliography}
+
+\appendix
+% start input ./app-p-values.tex
+
+\section{Distribution of p-values for all correlations tested}
+\label{sec:distr-p-values}
+
+\begin{figure}
+  (a)\\
+  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
+  (b)\\
+  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
+  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
+    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
+    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
+    bins and logarithmic vertical axis, with all values
+    \(p \le 10^{-6}\) included in the leftmost bin.  Short thin vertical
+    lines above the horizontal axis show the individual values.  The
+    thick vertical dashed lines show the traditional threshold values
+    for significance: \(p = 0.003\) (\(\approx 3 \sigma\)) and
+    \(p = 0.05\) (\(\approx 2 \sigma\)). The red solid line shows the uniform
+    distribution of \(p\)-values that would be expected if the null
+    hypothesis were always true, that is, if no significant
+    correlations existed.}
+  \label{fig:histo-p-values}
+\end{figure}
+
+\begin{table*}
+  \sisetup{detect-all=true, detect-inline-weight=math}
+  \sisetup{round-mode=figures, round-precision=2}
+  \sisetup{table-align-exponent = false}
+  \setlength\tabcolsep{2pt}
+  \caption{Results of all statistical tests performed on observed bow
+    shock shape parameters. Significant correlations are shown in
+    \textbf{bold}, marginally significant correlations in
+    \textit{italic}}
+  \label{tab:big-p}
+  % start input ./figs/mipsgal-summary-stats-table-body.tex
+	\newlength\Width\settowidth\Width{Comparison}
+	\begin{tabular}{
+	  @{} ll @{\quad }
+	  S[round-mode=places]S[round-mode=places]
+	  S[round-mode=places]S[round-mode=places]
+	  SS
+	  @{\quad} SSS[round-mode=places]
+	  @{\quad}
+	  S[table-format = +1.2e1]
+	  S[table-format = +1.2e1]
+	  S[table-format = +1.2e1] @{}
+	  }\toprule
+	  & {Dependent}
+	  & \multicolumn{2}{c}{Mean}
+	  & \multicolumn{2}{c}{Std.\ Dev.}
+	  & \multicolumn{2}{c}{Obs.\ Disp.}
+	  & \multicolumn{3}{c @{} }{\dotfill Effect sizes\dotfill }
+	  & \multicolumn{3}{c @{}}{Non-parametric test \(p\)-values} \\ 
+	  {Comparison} & {Variable}
+	  & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)}
+	  & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)}
+	  & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)}
+	  & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)}
+	  & {K--S} & {Rank} &  {B--F}\\
+	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)}
+	  & {(3)} & {(4)}
+	  & {(5)} & {(6)}
+	  & {(7)} & {(8)}
+	  & {(9)} & {(10)} & {(11)}
+	  & {(12)} & {(13)} & {(14)}  \\  
+	  \midrule\multicolumn{10}{@{} l @{}}{\itshape Median split of continuous independent variables}\\
+\addlinespace
+Faint/bright & \(\Pi\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.123 & 0.303 & \itshape 1.654 & 0.572 & 0.111 & \itshape 0.0335\\
+\(H\) magnitude & \(\Lambda\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.018 & \itshape 0.0235 & 0.125\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.07 & 0.093 & 1.013 & 0.472 & 0.365 & 0.761\\
+\addlinespace
+Low/high & \(\Pi\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.1 & 0.043 & 0.774 & 0.508 & 0.192 & 0.599\\
+bow shock size, \(R_0\) & \(\Lambda\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.061 & 0.11 & \bfseries 1.342 & \bfseries 0.00208 & 0.428 & \bfseries 0.00139\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.091 & 0.176 & 1.054 & \itshape 0.00612 & 0.238 & 0.193\\
+\addlinespace
+Low/high & \(\Pi\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.082 & 0.139 & 1.116 & 0.379 & 0.285 & 0.982\\
+extinction, \(A_K\) & \(\Lambda\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.04 & 0.132 & 1.213 & 0.572 & 0.602 & 0.123\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & -0.039 & 0.057 & 1.326 & 0.0609 & 0.61 & 0.112\\
+\addlinespace
+Low/high & \(\Pi\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.069 & 0.181 & 1.358 & \itshape 0.0379 & 0.368 & 0.0842\\
+\(\vert{}b\vert\) & \(\Lambda\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.02 & 0.008 & 0.796 & 0.255 & 0.795 & 0.0534\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.009 & 0.021 & 1.005 & 0.884 & 0.907 & 0.694\\
+\addlinespace
+High/low & \(\Pi\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & -0.0 & -0.064 & 0.785 & 0.985 & 0.999 & 0.549\\
+\(\cos \ell\) & \(\Lambda\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & -0.049 & -0.093 & 1.152 & 0.504 & 0.532 & 0.159\\
+\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(\Delta \Lambda\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.054 & 0.122 & 1.1 & 0.761 & 0.491 & 0.365\\
+\midrule
+\multicolumn{10}{@{} l @{}}{\itshape Categorical independent variables}\\
+\addlinespace
+Environment: & \(\Pi\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.042 & 0.11 & 1.053 & 0.717 & 0.676 & 0.377\\
+Isolated vs Facing & \(\Lambda\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & -0.07 & -0.142 & 1.194 & 0.965 & 0.49 & 0.392\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(\Delta \Lambda\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & -0.019 & 0.034 & 1.066 & 0.556 & 0.85 & 0.438\\
+\addlinespace
+Environment: & \(\Pi\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.024 & 0.174 & 1.118 & 0.284 & 0.875 & 0.255\\
+Isolated vs \hii & \(\Lambda\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & -0.13 & -0.193 & 1.092 & 0.701 & 0.391 & 0.782\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(\Delta \Lambda\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & -0.048 & -0.095 & 0.855 & 0.785 & 0.754 & 0.799\\
+\addlinespace
+Single/multiple & \(\Pi\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.027 & 0.076 & 1.198 & 0.977 & 0.756 & 0.605\\
+source candidate & \(\Lambda\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.074 & 0.177 & 1.09 & 0.111 & 0.396 & 0.338\\
+\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(\Delta \Lambda\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.093 & 0.136 & 0.987 & 0.559 & 0.284 & 0.97\\
+\addlinespace
+With/without & \(\Pi\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & -0.012 & 0.101 & 1.547 & 0.875 & 0.904 & 0.2\\
+\SI{8}{\um} emission & \(\Lambda\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & -0.042 & -0.044 & 1.031 & 0.299 & 0.667 & 0.563\\
+\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(\Delta \Lambda\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.021 & -0.106 & 0.726 & 0.967 & 0.826 & 0.219\\
+\addlinespace
+3-star vs (4+5)-star & \(\Pi\) & 1.632 & 2.0 & 0.91 & 0.764 & 0.106 & 0.061 & \bfseries 0.386 & \bfseries 0.431 & 0.84 & \bfseries 3.75e-05 & \bfseries 7.66e-07 & 0.762\\
+ & \(\Lambda\) & 1.661 & 1.812 & 0.288 & 0.286 & 0.247 & 0.216 & \bfseries 0.328 & \bfseries 0.525 & 0.99 & \bfseries 0.000562 & \bfseries 2.63e-05 & 0.403\\
+\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(\Delta \Lambda\) & 0.189 & 0.19 & 0.162 & 0.161 &   &   & -0.007 & 0.009 & 0.994 & 0.539 & 0.927 & 0.561\\
+\midrule
+\multicolumn{10}{@{} l @{}}{\itshape Intercomparison with other datasets}\\
+\addlinespace
+MIPS vs Orion & \(\Pi\) & 1.784 & 3.09 & 0.871 & 1.666 &   &   & \bfseries 0.57 & \bfseries 1.37 & \bfseries 1.911 & \bfseries 0.00112 & \bfseries 5.73e-05 & \bfseries 0.00133\\
+ & \(\Lambda\) & 1.723 & 2.532 & 0.297 & 0.749 &   &   & \bfseries 0.71 & \bfseries 2.308 & \bfseries 2.526 & \bfseries 9.99e-06 & \bfseries 5.49e-07 & \bfseries 1.49e-09\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(\Delta \Lambda\) & 0.19 & 0.658 & 0.162 & 0.513 &   &   & \bfseries 0.642 & \bfseries 2.243 & \bfseries 3.173 & \bfseries 7.14e-06 & \bfseries 5.95e-06 & \bfseries 1.07e-10\\
+\addlinespace
+MIPS vs RSG & \(\Pi\) & 1.784 & 1.479 & 0.871 & 0.227 &   &   & -0.159 & -0.362 & \itshape 0.26 & \bfseries 0.000594 & 0.288 & \itshape 0.0151\\
+ & \(\Lambda\) & 1.723 & 1.41 & 0.297 & 0.101 &   &   & \bfseries -0.719 & \bfseries -1.089 & \itshape 0.339 & \bfseries 2.78e-06 & \bfseries 1.56e-06 & \itshape 0.004\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 16\) & \(\Delta \Lambda\) & 0.19 & 0.147 & 0.162 & 0.076 &   &   & -0.072 & -0.267 & 0.469 & 0.191 & 0.701 & 0.12
+\\
+\bottomrule
+\multicolumn{14}{@{}p{\linewidth}@{}}{
+  \textit{Description of columns:}
+  (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
+  (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
+  (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
+  (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source, as in steps~\ref{step:R0} and \ref{step:R90} of \S~\ref{sec:autom-trac-fitt}.
+Note that in the case of \(\Pi\), this is \(\epsilon(R_0)\), and so is not a direct measure of the observational uncertainty in \(\Pi\).
+  (Cols.~9--11)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
+  (Col.~9)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
+It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
+  (Col.~10)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
+  (Col.~11)~Ratio of standard deviations between the two sub-samples.
+  (Cols.~12--14)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
+  (Col.~12)~Kuiper 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
+  (Col.~13)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive to differences in the central value of the distributions.
+  (Col.~14)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
+}
+\end{tabular}
+ % end input ./figs/mipsgal-summary-stats-table-body.tex
+ \end{table*}
+
+Results from all the statistical tests of the shape distributions
+discussed in \S~\ref{sec:corr-shape} are given in
+Table~\ref{tab:big-p}.  The \(p\)-values are the probability of
+finding a difference between two populations at least as large as what
+is observed \emph{given} that there is no difference in the underlying
+distribution from which the two populations are drawn (that is, given
+that the null hypothesis is true).  Conventionally, the null
+hypothesis is rejected at a certain significance threshold \(\alpha\) when
+\(p < \alpha\).  Since we are blindly testing many different hypotheses at
+once, the commonly used \(\alpha = 0.05\) threshold is too lenient.  In
+Figure~\ref{fig:histo-p-values} we analyse the frequency distribution
+of \(p\) from all our tests \citep[see][]{Head:2015a}, finding a
+systematic excess over a uniform distribution only for \(p < 0.01\).
+We therefore take \(\alpha = 0.003\) as the optimum threshold in order to
+balance the risks of false positives and false negatives. A false
+positive is the erroneous rejection of the null hypothesis (the
+spurious detection of a correlation that is not really there), while a
+false negative is failing to detect a true correlation.
+
+\section{Perturbed bow shocks}
+\label{sec:perturbed-bows}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/compare_xyprime_wave-wilkinoid}
+  \caption{Small-amplitude standing wave perturbations to wilkinoid
+    bow shapes.  The maximum deviations from the base shape are seen
+    at phases \(\phi = 0\) (blue line) and \(\phi = 0.5\) (red line), while
+    the perturbation is zero at \(\phi = 0.25\) and \(0.75\) (black
+    line).  Results are shown left to right for increasing wave
+    numbers \(N\) and decreasing amplitudes \(A\): (a)~\(A = 0.2\),
+    \(N = 1.0\), (b)~\(A = 0.1\), \(N = 2.0\), (a)~\(A = 0.04\),
+    \(N = 5.0\).  The maximum curvature, proportional to \(A N\) is
+    the same in all three cases.}
+  \label{fig:perturb-shapes}
+\end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]
+  {figs/wave_xyprime-A010-N20-ancantoid-xi080-beta000500}
+  \caption{Plane-of-sky projections of perturbed bow shapes.  In all
+    cases, the base bow shape is ancantoid with \(\xi = 0.8\),
+    \(\beta = 0.005\) and the perturbation is the curling mode shown in
+    the central panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
+    \(A = 0.1\) and wave number \(N = 2.0\). Results are shown for
+    inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
+    color and thickness, see key) and for different fractional phases
+    of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
+    (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes}, the
+    spatial coordinates are normalized to the instantaneous projected
+    apex radius \(R_0'\) at each phase, so the apex does not appear to
+    move.}.
+  \label{fig:perturb-xy-prime}
+\end{figure*}
+
+In this appendix, we present a highly idealized model for small,
+time-varying perturbations to a steady-state bow shock shape, such as
+those discussed in \S~5 of Paper~0.  These perturbations may be due to
+periodic variations in the momentum-loss rate of one of the winds, or
+due to dynamical instabilities in the shocked shell.
+
+We consider fractional perturbations \(\Delta(\theta, t)\) of a base shape
+\(R(\theta)\), such that
+\(R(\theta) \to [1 + \Delta(\theta, t)] R(\theta)\).  For simplicity,
+\(\Delta(\theta, t)\) is a standing wave of constant amplitude \(A\), which is
+periodic in \(\theta\), with wave number \(N\).  We assume that the
+oscillation occurs simultaneously and coherently at all azimuths, so
+that cylindrical symmetry is maintained.  This implies that
+\(\Delta(\theta, t)\) must be even in \(\theta\), so can be expressed as
+\begin{equation}
+  \label{eq:standing-wave}
+  \Delta(\theta, t) = A \cos(N \theta) \cos(2\pi \varphi) . 
+\end{equation}
+For waves with period \(P\), the fractional phase \(\varphi\) will
+vary with time \(t\) as
+\begin{equation}
+  \label{eq:fractional-phase}
+  \varphi(t) = (\varphi_0 + t/P) \bmod 1.0\ ,
+\end{equation}
+where \(\varphi_0\) is an arbitrary reference phase.
+
+Example oscillations with wave numbers \(N = 1.0\), \(2.0\), and
+\(5.0\) superimposed on a wilkinoid base shape are shown in
+Figure~\ref{fig:perturb-shapes}.  There are \(N\) nodes of the
+oscillation between \(\theta = [0, \pi]\), always with an antinode at the apex
+(\(\theta = 0\)), as required by symmetry.  So, with \(N = 1.0\) there is a
+node (fixed point) in the near wing at \(\theta = \pi/2\), but an antinode in
+the far wing at \(\theta = \pi\), which is in antiphase with the oscillation
+of the apex, giving rise to a large-scale ``breathing'' mode of
+oscillation.  With \(N = 2.0\), there are nodes at \(\theta = \pi/4\) and
+\(3\pi/4\), while the antiphase antinode has moved to the near wing at
+\(\theta = \pi/2\).  There is still an antinode in the far wing at
+\(\theta = \pi\) but it is now in phase with the apex, giving rise to a
+``curling-up/straightening-out'' mode of oscillation.  With
+\(N = 5.0\), there are many more nodes and antinodes, giving a
+``ringing'' mode of oscillation.  Note that all our examples have
+\(A \propto 1/N\) in order to keep the local curvature relatively low.  If
+the product \(A N\) is not small compared to unity, then the local
+curvature can be so extreme as to reverse the concave shape of the
+base bow shape, producing locally convex regions.
+
+If the bow shape is viewed at different inclinations, then the effect
+of the oscillations on the projected shape will vary.  In particular,
+the apex-to-wing interval in body-frame angle changes from
+\(\theta = [0, \pi/2]\) at \(i = 0\) to
+\(\theta = [\theta_0, \theta_{90}]\) for general \(i\), see equations~(18) and (21)
+of Paper~0.  The difference \(\theta_{90} - \theta_0\) is always a decreasing
+function of \(|i|\), so the oscillations of the tangent line become
+increasingly stretched out as the inclination increases.  This effect
+can be seen in Figure~\ref{fig:perturb-xy-prime}, which shows an
+example of the variation in projected perturbed shape with inclination
+angle for 3 different phases, this time for an ancantoid base shape
+and the \(N = 2.0\) perturbation shown in
+Figure~\ref{fig:perturb-shapes}b.  The most marked changes with phase
+are seen for low inclinations (light colored lines), whereas the
+changes are smaller, although still noticeable, for
+\(|i| \ge 45^\circ\). If \(A N\) exceeds about 0.5, then the local curvature
+of the perturbations is so extreme that multiple tangent lines exist
+at intermediate inclinations, which produces the appearance of
+additional incomplete bright arcs inside the main arc of the bow.
+
+ % end input ./app-p-values.tex
+
+\bsp	
+\label{lastpage}
+
+\end{document}

### 2019-07-10 papers/Papers1234/sigma-ori-arcs.tex
Add N-T distro figure and write caption

@@
 
+\begin{figure}
+  \includegraphics[width=\linewidth]{figs/sigma-ori-N-T-histogram}
+  \caption{Joint distribution of dust temperature and gas column
+    density. Gray-scale image shows the fraction of the emission at
+    \SI{160}{\um} (cool component, upper-left) and \SI{24}{\um} (warm
+    component, lower right) that is contributed by pixels with a given
+    \((T, N)\) combination. Conversion from dust optical depth to
+    hydrogen column density is carried out using the empirical
+    calibration described in the text.}
+  \label{fig:N-T-distro}
+\end{figure}
+
 \section{Conclusions}

### 2019-08-14 papers/Papers1234/sec-observational-diagnostics.tex
Version 3 of Paper III submitted
Hopefully the last version

@@
 became aware of a new mass-loss study that greatly expands on the
-earlier results of K18 (H.~Kobulnicky, priv.~comm.).  The new study
+earlier results of K18 \citep{Kobulnicky:2019a}.  The new study
 includes 70 bow shock sources and incorporates Gaia distances and
@@
 being overestimated by about a factor of 2 for sources with weak
-radiation fields (H.~Kobulnicky, priv.~comm.).
+radiation fields \citep[corrected in][]{Kobulnicky:2019a}.
 

### 2020-02-06 Stellar-Bowshocks-2017/mipsgal-summary-stats-table-body.tex
First look at thickness statistics - uncorrelated with shape 😒

--- 2017-04-19 Stellar-Bowshocks-2017/mipsgal-summary-stats-table-body.tex
@@
 %%% Table automatically generated from mipsgal-summary-stats.tab
-%%% 2017-04-19 13:16:10.731012
+%%% 2020-02-05 22:21:40.747825
 %%%
@@
 	\newlength\Width\settowidth\Width{Comparison}
-	\begin{tabular}{@{} ll @{\quad } S[round-mode=places]S[round-mode=places] S[round-mode=places]S[round-mode=places] SS SS @{\quad\quad\quad} SSS[round-mode=places] @{\quad} S@{}S@{}S @{}}\toprule
-	  & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\
-	  {Comparison} & {Variable} & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)} & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)} & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)} & {\((\sigma/\!\sqrt n)_{\text{A}}\)} & {\((\sigma/\!\sqrt n)_{\text{B}}\)} & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)} & \multicolumn{1}{c}{Anderson--Darling} & \multicolumn{1}{c}{Rank biserial} &  \multicolumn{1}{c}{Brown--Forsythe}\\
-	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)} & {(3)} & {(4)} & {(5)} & {(6)} & {(7)} & {(8)} & {(9)} & {(10)}  & {(11)} & {(12)} & {(13)} & {(14)} & {(15)} & {(16)} \\  
-	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\
+	\begin{tabular}{
+	  @{} ll @{\quad }
+	  % Mean
+	  S[round-mode=places]S[round-mode=places]
+	  % Std Dev
+	  S[round-mode=places]S[round-mode=places]
+	  % Obs Disp
+	  SS
+	  % Effect sizes
+	  @{\quad} SSS[round-mode=places]
+	  % p values
+	  @{\quad}
+	  S[table-format = +1.2e1]
+	  S[table-format = +1.2e1]
+	  S[table-format = +1.2e1] @{}
+	  }\toprule
+	  & {Dependent}
+	  & \multicolumn{2}{c}{Mean}
+	  & \multicolumn{2}{c}{Std.\ Dev.}
+	  & \multicolumn{2}{c}{Obs.\ Disp.}
+	  & \multicolumn{3}{c @{} }{\dotfill Effect sizes\dotfill }
+	  & \multicolumn{3}{c @{}}{Non-parametric test \(p\)-values} \\ 
+	  {Comparison} & {Variable}
+	  & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)}
+	  & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)}
+	  & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)}
+	  & {\(r_b\)} & {Cohen \(d\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)}
+	  & {K--S} & {Rank} &  {B--F}\\
+	  {\makebox[\Width]{(1)}} & \multicolumn{1}{c@{\quad}}{(2)}
+	  & {(3)} & {(4)}
+	  & {(5)} & {(6)}
+	  & {(7)} & {(8)}
+	  & {(9)} & {(10)} & {(11)}
+	  & {(12)} & {(13)} & {(14)}  \\  
+	  \midrule\multicolumn{10}{@{} l @{}}{\itshape Median split of continuous independent variables}\\
 \addlinespace
-Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
-\(H\) magnitude & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\
+Faint/bright & \(\Pi\) & 1.701 & 1.872 & 0.605 & 0.806 & 0.101 & 0.084 & 0.103 & 0.24 & 1.333 & 0.379 & 0.182 & 0.0588\\
+\(H\) magnitude & \(\Lambda\) & 1.655 & 1.724 & 0.255 & 0.322 & 0.238 & 0.232 & 0.147 & 0.237 & 1.262 & \itshape 0.018 & 0.057 & 0.0884\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.176 & 0.196 & 0.152 & 0.155 &   &   & 0.087 & 0.13 & 1.019 & 0.921 & 0.261 & 0.833\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & \itshape 0.428 & \bfseries 0.00139\\
-bow shock size, \(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\
+Low/high & \(\Pi\) & 1.696 & 1.874 & 0.668 & 0.75 & 0.115 & 0.07 & \itshape 0.171 & \itshape 0.251 & 1.123 & 0.431 & \itshape 0.0261 & 0.66\\
+bow shock size, \(R_0\) & \(\Lambda\) & 1.67 & 1.71 & 0.266 & 0.314 & 0.251 & 0.22 & 0.103 & 0.135 & 1.18 & \itshape 0.0351 & 0.18 & 0.184\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.174 & 0.197 & 0.148 & 0.159 &   &   & 0.049 & 0.148 & 1.073 & 0.345 & 0.521 & 0.201\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
-extinction, \(A_K\) & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\
+Low/high & \(\Pi\) & 1.769 & 1.805 & 0.761 & 0.672 & 0.096 & 0.088 & 0.067 & 0.05 & 0.883 & 0.771 & 0.388 & 0.477\\
+extinction, \(A_K\) & \(\Lambda\) & 1.681 & 1.697 & 0.269 & 0.314 & 0.234 & 0.236 & 0.021 & 0.055 & 1.168 & 0.771 & 0.789 & 0.415\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.189 & 0.184 & 0.139 & 0.168 &   &   & -0.069 & -0.032 & 1.207 & 0.572 & 0.373 & 0.306\\
 \addlinespace
-Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
-\(\vert{}b\vert\) & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
-\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\
+Low/high & \(\Pi\) & 1.769 & 1.804 & 0.713 & 0.719 & 0.089 & 0.095 & 0.01 & 0.049 & 1.009 & 0.974 & 0.896 & 0.771\\
+\(\vert{}b\vert\) & \(\Lambda\) & 1.69 & 1.691 & 0.315 & 0.266 & 0.242 & 0.228 & 0.015 & 0.004 & 0.844 & 0.653 & 0.85 & 0.534\\
+\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(\Delta \Lambda\) & 0.182 & 0.19 & 0.151 & 0.157 &   &   & 0.045 & 0.05 & 1.04 & 0.415 & 0.556 & 0.683\\
 \addlinespace
-High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
-\(\cos \ell\) & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
-\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\
+High/low & \(\Pi\) & 1.797 & 1.771 & 0.714 & 0.719 & 0.094 & 0.089 & -0.027 & -0.035 & 1.007 & 0.724 & 0.728 & 0.999\\
+\(\cos \ell\) & \(\Lambda\) & 1.7 & 1.676 & 0.284 & 0.302 & 0.236 & 0.234 & -0.021 & -0.081 & 1.063 & 0.973 & 0.792 & 0.937\\
+\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(\Delta \Lambda\) & 0.174 & 0.204 & 0.146 & 0.164 &   &   & 0.088 & 0.197 & 1.124 & 0.871 & 0.262 & 0.327\\
 \midrule
-\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\
+\multicolumn{10}{@{} l @{}}{\itshape Categorical independent variables}\\
 \addlinespace
-Environment: & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
-Isolated vs Facing & \(\Delta R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\
+Environment: & \(\Pi\) & 1.802 & 1.784 & 0.705 & 0.738 & 0.093 & 0.085 & -0.035 & -0.026 & 1.046 & 0.259 & 0.727 & 0.671\\
+Isolated vs Facing & \(\Lambda\) & 1.699 & 1.674 & 0.281 & 0.304 & 0.239 & 0.223 & -0.078 & -0.088 & 1.081 & 0.883 & 0.439 & 0.919\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(\Delta \Lambda\) & 0.182 & 0.201 & 0.153 & 0.16 &   &   & 0.061 & 0.12 & 1.042 & 0.69 & 0.549 & 0.549\\
 \addlinespace
-Environment: & \(R_{90}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
-Isolated vs \hii & \(\Delta R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
-\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\
+Environment: & \(\Pi\) & 1.802 & 1.62 & 0.705 & 0.756 & 0.093 & 0.105 & -0.265 & -0.257 & 1.072 & \itshape 0.0201 & 0.0804 & 0.422\\
+Isolated vs \hii & \(\Lambda\) & 1.699 & 1.636 & 0.281 & 0.36 & 0.239 & 0.22 & -0.224 & -0.216 & 1.279 & 0.11 & 0.14 & 0.0601\\
+\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(\Delta \Lambda\) & 0.182 & 0.185 & 0.153 & 0.147 &   &   & 0.067 & 0.02 & 0.963 & 0.465 & 0.658 & 0.323\\
 \addlinespace
-Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
-source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
-\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\
+Single/multiple & \(\Pi\) & 1.738 & 1.919 & 0.668 & 0.82 & 0.094 & 0.087 & 0.134 & 0.254 & 1.228 & 0.779 & 0.125 & 0.258\\
+source candidate & \(\Lambda\) & 1.678 & 1.723 & 0.291 & 0.292 & 0.234 & 0.239 & 0.099 & 0.153 & 1.005 & 0.554 & 0.257 & 0.613\\
+\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(\Delta \Lambda\) & 0.182 & 0.197 & 0.157 & 0.145 &   &   & 0.067 & 0.097 & 0.927 & 0.544 & 0.439 & 0.379\\
 \addlinespace
-With/without & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
-\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
-\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\
+With/without & \(\Pi\) & 1.749 & 1.796 & 0.545 & 0.753 & 0.099 & 0.09 & -0.039 & 0.065 & 1.382 & 0.882 & 0.688 & 0.233\\
+\SI{8}{\um} emission & \(\Lambda\) & 1.687 & 1.691 & 0.298 & 0.29 & 0.222 & 0.238 & 0.012 & 0.014 & 0.973 & 0.91 & 0.9 & 0.89\\
+\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(\Delta \Lambda\) & 0.198 & 0.183 & 0.193 & 0.142 &   &   & 0.028 & -0.098 & 0.738 & 0.771 & 0.772 & 0.226\\
+\addlinespace
+3-star vs (4+5)-star & \(\Pi\) & 1.615 & 2.026 & 0.618 & 0.773 & 0.108 & 0.07 & \bfseries 0.39 & \bfseries 0.599 & 1.25 & \bfseries 0.000411 & \bfseries 5.64e-07 & 0.128\\
+ & \(\Lambda\) & 1.621 & 1.787 & 0.276 & 0.286 & 0.244 & 0.223 & \bfseries 0.369 & \bfseries 0.592 & 1.036 & \bfseries 0.000183 & \bfseries 2.24e-06 & 0.852\\
+\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(\Delta \Lambda\) & 0.183 & 0.189 & 0.153 & 0.156 &   &   & -0.0 & 0.039 & 1.017 & 0.479 & 0.999 & 0.4\\
 \midrule
-\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Intercomparison with other datasets \dotfill}\\
+\multicolumn{10}{@{} l @{}}{\itshape Intercomparison with other datasets}\\
 \addlinespace
-MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
- & \(\Delta R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\
+MIPS vs Orion & \(\Pi\) & 1.787 & 3.09 & 0.716 & 1.666 &   &   & \bfseries 0.557 & \bfseries 1.581 & \bfseries 2.325 & \bfseries 0.000456 & \bfseries 8.48e-05 & \bfseries 2.42e-05\\
+ & \(\Lambda\) & 1.69 & 2.532 & 0.292 & 0.749 &   &   & \bfseries 0.735 & \bfseries 2.428 & \bfseries 2.568 & \bfseries 4.28e-06 & \bfseries 2.13e-07 & \bfseries 1.26e-08\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(\Delta \Lambda\) & 0.186 & 0.329 & 0.154 & 0.257 &   &   & \itshape 0.349 & \itshape 0.874 & \itshape 1.666 & \itshape 0.0185 & \itshape 0.0137 & \itshape 0.0199\\
 \addlinespace
-MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
- & \(\Delta R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
-\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505
+MIPS vs RSG & \(\Pi\) & 1.787 & 1.479 & 0.716 & 0.227 &   &   & -0.238 & -0.443 & \itshape 0.317 & \bfseries 0.0011 & 0.112 & \itshape 0.0108\\
+ & \(\Lambda\) & 1.69 & 1.41 & 0.292 & 0.101 &   &   & \bfseries -0.648 & \bfseries -0.99 & \itshape 0.345 & \bfseries 2.19e-05 & \bfseries 1.5e-05 & \itshape 0.00549\\
+\(n_{\text{A}}, n_{\text{B}} = 227, 16\) & \(\Delta \Lambda\) & 0.186 & 0.073 & 0.154 & 0.038 &   &   & \itshape -0.442 & \itshape -0.743 & \itshape 0.246 & \itshape 0.013 & \itshape 0.0181 & \itshape 0.00698
 \\
 \bottomrule
+\multicolumn{14}{@{}p{\linewidth}@{}}{
+  \textit{Description of columns:}
+  (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
+  (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
+  (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
+  (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source, as in steps~\ref{step:R0} and \ref{step:R90} of \S~\ref{sec:autom-trac-fitt}.
+Note that in the case of \(\Pi\), this is \(\epsilon(R_0)\), and so is not a direct measure of the observational uncertainty in \(\Pi\).
+  % (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
+  (Cols.~9--11)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
+  (Col.~9)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.
+It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\).
+  (Col.~10)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
+  (Col.~11)~Ratio of standard deviations between the two sub-samples.
+  (Cols.~12--14)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
+  (Col.~12)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
+  (Col.~13)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive to differences in the central value of the distributions.
+  (Col.~14)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
+}
 \end{tabular}

### 2020-02-06 Stellar-Bowshocks-2017/mipsgal-trace-arc.py

@@ -50,7 +50,7 @@ OVERRIDE = {
     650: {'R0': 50},
 }
 STEP_BACK_FACTOR = 2.0
-CIRCLE_THETA = 45.0*u.deg
+CIRCLE_THETA = 60.0*u.deg
 
 THMIN, THMAX = coord.Angle([-160.0*u.deg, 160.0*u.deg])
 
